### 2021-04-08 project_ashish_lumi/paper.tex
ahish lumi project

\documentclass[final,3p]{CSP}
\usepackage{amssymb}
\usepackage{changepage}
\usepackage{float}
\usepackage{hyperref}
\usepackage{url}
\usepackage{afterpage}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}

\def\Student{Ashish Sehrawat}
\def\Title{THESIS PROJECT PROPOSAL}
\def\Prog{Doctorado en Ciencias (F\'{i}sica) }
\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
\def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
\def\ProjectTitle{ Measurement of ... }
\def\ResearchLine{Astrof\'{i}sica, Cosmolog\'{i}a y F\'{i}sica de Part\'{i}culas}

\newcommand{\SubItem}[1]{
    {\setlength\itemindent{15pt} \item[-] #1}
}

%%header and footer
\lhead{\Student}
\rhead{\Title}
\lfoot{\Dept}
\rfoot{Page \thepage}
\setlength{\headsep}{0.2in}
\renewcommand{\footrulewidth}{0.4pt}% default is 0pt

\begin{document}

%%%%Title Page
\begin{titlepage}
  \centering
  \hspace{0pt}
  \vfill
        {\scshape\Large \Title \par}

	\vspace{2cm}
        \begin{adjustwidth}{2cm}{2cm}{
            TITLE:\par
            {\large \ProjectTitle \par}
          }
        \end{adjustwidth}

	\vspace{0.5cm}
        \begin{adjustwidth}{2cm}{2cm}{
            RESEARCH LINE: \par
            \ResearchLine \par}
        \end{adjustwidth}

        \vspace{4cm}
        {\underline{\hspace{8cm}}\par}
	{\scshape\large \Student \par}
        {Student\par}

        \vspace{1cm}
        {\underline{\hspace{8cm}}\par}
	{\Director \par}
        {Director\par}

        \vspace{1cm}
        {\Prog \par}
        {\Dept \par}
        {Universidad de Sonora \par}

        \vspace{4cm}
	{\today}

\hspace{0pt}
\vfill

\end{titlepage}

%%%%% white page for print out
\shipout\null

%%%% Abstract Page
\newpage
\hspace{2pt}
\vfill

\begin{adjustwidth}{1cm}{1cm}

  \begin{center}
    {\Large \ProjectTitle \par}
    \vspace{1cm}
    {\itshape\textbf{Abstract}\par}
  \end{center}

  \vspace{1 cm}

  \onehalfspacing
  This research project proposes ...

\end{adjustwidth}

\hspace{2pt}
\vfill

%%%%%% Begin the body
\newpage
\section{BACKGROUND}

\onehalfspacing The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the 
weak nuclear force. Gravitational force is neglected as the strength of this force is very weak at the scales over which 
elementary particle interact with each other. The standard model (SM) of particle physics is divided into two categories, 
bosonic sector and fermionic sector. Bosonic sector contain particles called bosons which mediate the fundamental forces of 
nature and the fermionic sector contain particles called fermions which make up all the matter in our universe. SM has three 
generations of matter (fermions) particles. The first generation of fermions consists of up (u) quark, down (d) quark, electron 
and electron neutrino, second generation consist of charm (c) quark, strange (s) quark, muon and muon neutrino and the third 
generation of matter particles has top (t) quark, bottom (b) quark, tau and tau neutrino. The bosonic sector consist of gauge 
bosons like gluon, photon, $W^{\pm}$, $Z^0$ which mediate strong nuclear force, electromagnetic force and weak nuclear force respectively. There is one more particle in the standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}. All the standard model particles are shown in Figure 1. Higgs boson can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva, Switzerland.

The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large 
number of free-parameters and the fine tuning related to these parameters suggest new physics beyond SM as mentioned below.
\begin{itemize}
\item{Fine structure constant $\alpha$},
\item{Weinberg angle or the weak mixing angle $\theta_W$},
\item{The coupling constant of strong interaction $\alpha_s$},
\item{Electroweak symmetry breaking energy scale v},
\item{ Higgs potential self coupling $\lambda$ or the Higgs mass $m_H$},
\item{Three weak mixing angles and the CP-violating phase $\delta$ of the CKM matrix which tells us how quarks of different flavor mix with each other},
\item{Nine yukawa couplings $y_i$ (i = 1 to 9) which determine the mass of nine charged fermions}.
\end{itemize}

Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. 
These had eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was 
discovered in 1995 in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass 
energy of 1.8 TeV untill 2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 
colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years. The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC). It is designed to detect particles known as muons very accurately. The CMS detector has the form of a cylindrical onion, with several concentric layers of components. Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to bend them in opposite directions and measure momentum. A silicon tracker, made of about 75 
million electronic sensors arranged in concentric layers, identifies the tracks taken by these charged particles bent with very high precision \cite{Chatrchyan:2008aa}. The muons are detected by special subdetectors placed outside to detect them once they have crossed the solenoid as shown in Figure~\ref{figure5}. In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV. So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the Standard Model (SM).

LHC during the first run in 2011 and 2012 reached a peak instantaneous luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
 The LHC will deliver about 300 $fb^{-1}$ by 2024 \cite{collaborations2019report}.
The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles.
In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  place in parallel during one shutdown, at around 2023-25 (LS3), with some of the modification anticipated in 2019-2020 (LS2).
This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ by the year 2036 as shown in Figure~\ref{figure6}.
Figure~\ref{figureKappas} shows a summary of the current measurements of the Higgs coupling parameters with the LHC Run 1 dataset (2011,2012)  using ggF, VBF, VH, and ${t\bar{t}H}$ production modes \cite{Tanabashi:2018oca}.

\begin{figure}[H]
        \centering
        \includegraphics[width=\columnwidth]{./pg.png}
        \caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
        \label{figure 2}
\end{figure}

%\begin{figure}[H]
%  \centering
%   \includegraphics[width=\columnwidth]{./cd2.png}
%  \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
%   \label{figure 3}
%\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.4]{./couplings.png}
  \caption{ATLAS-CMS combined measurements of coupling strength modifiers \cite{Tanabashi:2018oca}.}
  \label{figureKappas}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.6\columnwidth]{./cms12.png}
  \caption{Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimeter, superconducting solenoid and muon chambers \cite{Chatrchyan:2008aa}.}
  \label{figure5}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.9\columnwidth]{./lum6.png}
  \caption{Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities. Points show instantaneous luminosity while the line shows luminosity accumulated \cite{collaborations2019report}.}
  \label{figure6}
\end{figure}

\newpage
\section{PROPOSAL}

\onehalfspacing
In this project, it is proposed to

\section{GENERAL OBJECTIVE}

%- motivation, tH production crossection, sign of $k_t$, search for BSM, ..

\onehalfspacing
There is currently a great enigma in physics since we know that ordinary matter comprises only $5\%$ of the universe, another $27\%$ includes Dark matter and the rest $68\%$ is Dark energy.

\section{HYPOTHESIS}
%%  - what we expect to find

\onehalfspacing

%\newpage
\section{SPECIFIC OBJECTIVES}

\onehalfspacing

In order to complete a journal publication ...

\begin{itemize}
\item Simulation..
\end{itemize}

Finally, the results of this project will be presented at national or international conferences and a publication in a scientific journal will be accomplished.

\section{METHODOLOGY}

\onehalfspacing
The methods for ...

\textsc{Root} is a \textsc{c++} based software that allows visualization of event distributions and variable correlations.

\section{EXPECTED RESULTS}
%- a limit, also predictions for future runs

\onehalfspacing The results from this project include the following items:
\begin{itemize}
\item The student will become part of an international collaboration.
\item A leading contribution ....  resulting in a publication in a scientific journal.
\item Participation in the CMS detector Phase II upgrade through development and possible installation of particle detectors possibly resulting in a technical report.
\item A presentation of a poster or a talk in one of the national conferences of the Division of Paticles and Fields of the Mexican Society of Physics or a presentation of a poster or a talk in an international physics conference.
\item An academic stay at a scientific center like CERN or Fermilab.
\end{itemize}

\section{CALENDAR OF ACTIVITIES}
\onehalfspacing
\begin{itemize}

\item {\bf Semester 1 (2019-2)}:
  \SubItem{ Readings on Standard Model theory}
  \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
  \SubItem{ Initial planning of the analysis strategy}

\item {\bf Semester 2 (2020-1)}:
  \SubItem{ Course I on particle physics and/or particle detection}
  \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
  \SubItem{ Readings on SM and tH literature}
  \SubItem{ Computing accounts at CERN and Fermilab}
  \SubItem{ CMS service work for authorship}
  \SubItem{ Possible summer stay at CERN or Fermilab}

\item {\bf Semester 3 (2020-2)}:
  \SubItem{ Course II on particle physics and/or particle detection.}
  \SubItem{ CMS service work for authorship}

\item {\bf Semester 4 (2021-1)}:
  \SubItem{ CMS service work for authorship}

\item {\bf Semester 5 (2021-2)}:
  \SubItem{ Presentation of poster or talk at national or international conference}

\item {\bf Semester 6 (2022-1)}:
  \SubItem{ Review process of the results within the CMS collaboration}
  \SubItem{ Presentation of poster or talk at national or international conference}
  \SubItem{ Writing of the paper publication}
  \SubItem{ Writing of the thesis}
\end{itemize}

\cleardoublepage
\onehalfspacing
\bibliographystyle{unsrt}
\bibliography{paper}

\end{document}

### 2021-04-08 project_ashish_lumi/compile.sh

@@ -1,0 +1,43 @@
+#!/bin/bash
+
+thesis="paper";
+
+if [ $1 = "clean" ]
+then
+	echo "Cleaning please wait ..."
+	rm -f *~
+	rm -rf *.aux
+	rm -rf *.bbl
+	rm -rf *.blg
+	rm -rf *.d
+	rm -rf *.fls
+	rm -rf *.ilg
+	rm -rf *.ind
+	rm -rf *.toc*
+	rm -rf *.lot*
+	rm -rf *.lof*
+	rm -rf *.log
+	rm -rf *.idx
+	rm -rf *.out*
+	rm -rf *.nlo
+	rm -rf *.nls
+	rm -rf $thesis.pdf
+	rm -rf $thesis.ps
+	rm -rf $thesis.dvi
+	rm -rf $thesis.spl
+	rm -rf *#* 
+	echo "Cleaning complete!"
+	exit
+else
+	echo "Compiling ...!"
+	pdflatex -interaction=nonstopmode $thesis.tex
+	bibtex $thesis.aux 	
+	makeindex $thesis.aux
+	makeindex $thesis.idx
+	makeindex $thesis.nlo -s nomencl.ist -o $thesis.nls
+	pdflatex -interaction=nonstopmode $thesis.tex
+	makeindex $thesis.nlo -s nomencl.ist -o $thesis.nls
+	pdflatex -interaction=nonstopmode $thesis.tex
+	echo "Success!"
+	exit
+fi

### 2021-04-29 project_ashish_lumi/paper.tex
updated

@@
 \def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
+\def\Institution{Universidad de Sonora}
 \def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
-\def\ProjectTitle{ Measurement of ... }
+\def\ProjectTitle{Measurement of the luminosity in proton-proton collisions at the CMS experiment of the Large Hadron Collider}
 \def\ResearchLine{Astrof\'{i}sica, Cosmolog\'{i}a y F\'{i}sica de Part\'{i}culas}
@@
       {\scshape\Large \Title \par}
+      revision requested december 2020
 
       \vspace{2cm}
-        \begin{adjustwidth}{2cm}{2cm}{
+      %\begin{adjustwidth}{2cm}{2cm}
+       {
          TITLE:\par
@@
        }
-        \end{adjustwidth}
+       %\end{adjustwidth}
 
        \vspace{0.5cm}
-        \begin{adjustwidth}{2cm}{2cm}{
+       %\begin{adjustwidth}{2cm}{2cm}
+       {
          RESEARCH LINE: \par
-            \ResearchLine \par}
-        \end{adjustwidth}
+         \ResearchLine \par
+       }
+       %\end{adjustwidth}
 
@@
        {\underline{\hspace{8cm}}\par}
-	{\scshape\large \Student \par}
+       {\scshape \Student \par}
        {Student\par}
@@
        {\underline{\hspace{8cm}}\par}
-	{\Director \par}
+       {\scshape \Director \par}
        {Director\par}
@@
        {\Dept \par}
-        {Universidad de Sonora \par}
+       {\Institution \par}
 
@@
 
-\onehalfspacing The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
-particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the 
-weak nuclear force. Gravitational force is neglected as the strength of this force is very weak at the scales over which 
-elementary particle interact with each other. The standard model (SM) of particle physics is divided into two categories, 
-bosonic sector and fermionic sector. Bosonic sector contain particles called bosons which mediate the fundamental forces of 
-nature and the fermionic sector contain particles called fermions which make up all the matter in our universe. SM has three 
-generations of matter (fermions) particles. The first generation of fermions consists of up (u) quark, down (d) quark, electron 
-and electron neutrino, second generation consist of charm (c) quark, strange (s) quark, muon and muon neutrino and the third 
-generation of matter particles has top (t) quark, bottom (b) quark, tau and tau neutrino. The bosonic sector consist of gauge 
-bosons like gluon, photon, $W^{\pm}$, $Z^0$ which mediate strong nuclear force, electromagnetic force and weak nuclear force respectively.
-There is one more particle in the standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}.
-All the standard model particles are shown in Figure 1.
-Higgs boson can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva, Switzerland.
+\onehalfspacing
+The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the weak nuclear force.
+%Gravitational force is neglected as the strength of this force is very weak at the scales over which elementary particle interact with each other.
+The SM is divided into two categories, bosonic sector and fermionic sector.
+The bosonic sector contain particles which mediate the fundamental forces of  nature and the fermionic sector contain particles which make up all the matter in our universe.
+There are three generations of fermion particles: the first generation consists of up (u) quark, down (d) quark, electron and electron neutrino, the second generation consist of charm (c) quark, strange (s) quark, muon and muon neutrino, and the third generation has the top (t) quark, bottom (b) quark, tau and tau neutrino.
+The bosonic sector consists of the gauge bosons: gluon, photon, $W^{\pm}$, $Z^0$ which mediate strong nuclear force, electromagnetic force and weak nuclear force respectively.
+The Higgs boson ($H$), is the last of the gauge bosons, it gives mass to the other particles via electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}.
+%All the standard model particles are shown in Figure 1.
+%Higgs boson can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva, Switzerland.
 
-The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large 
-number of free-parameters and the fine tuning related to these parameters suggest new physics beyond SM as mentioned below.
-\begin{itemize}
-\item{Fine structure constant $\alpha$},
-\item{Weinberg angle or the weak mixing angle $\theta_W$},
-\item{The coupling constant of strong interaction $\alpha_s$},
-\item{Electroweak symmetry breaking energy scale v},
-\item{ Higgs potential self coupling $\lambda$ or the Higgs mass $m_H$},
-\item{Three weak mixing angles and the CP-violating phase $\delta$ of the CKM matrix which tells us how quarks of different flavor mix with each other},
-\item{Nine yukawa couplings $y_i$ (i = 1 to 9) which determine the mass of nine charged fermions}.
-\end{itemize}
+%The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large number of free-parameters and the fine tuning related to these parameters suggest new physics beyond SM as mentioned below.
+%\begin{itemize}
+%\item{Fine structure constant $\alpha$},
+%\item{Weinberg angle or the weak mixing angle $\theta_W$},
+%\item{The coupling constant of strong interaction $\alpha_s$},
+%\item{Electroweak symmetry breaking energy scale v},
+%\item{ Higgs potential self coupling $\lambda$ or the Higgs mass $m_H$},
+%\item{Three weak mixing angles and the CP-violating phase $\delta$ of the CKM matrix which tells us how quarks of different flavor mix with each other},
+%\item{Nine yukawa couplings $y_i$ (i = 1 to 9) which determine the mass of nine charged fermions}.
+%\end{itemize}
 
+The heavy particles ($W^{\pm}$, $Z^0$, $H$, and top) can only be produced at high energy particle colliders like the Large Hadron Collider (LHC) operating at a center-of-mass energy of 13 TeV in Geneva, Switzerland.
 Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. 
-These had eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was 
-discovered in 1995 in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass 
-energy of 1.8 TeV untill 2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 
-colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years.
-The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC).
-It is designed to detect particles known as muons very accurately.
+These had eluded previous experiments due to difficulties in the production or reconstruction of its decays.
+The top quark was discovered in 1995 in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass energy of 1.8 TeV untill 2010.
+%The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years.
+In 2012, the ATLAS and CMS experiments, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
+This particle has been identified as the Higgs boson of the SM by measuring its properties and comparing to those predicted by the SM.
+%So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the Standard Model (SM).
+
+The Compact Muon Solenoid (CMS) experiment is located at one of the four interaction points of the LHC.
+%It is designed to detect particles known as muons very accurately.
 The CMS detector has the form of a cylindrical onion, with several concentric layers of components.
-Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to bend them in opposite directions and measure momentum.
-A silicon tracker, made of about 75
-million electronic sensors arranged in concentric layers, identifies the tracks taken by these charged particles bent with very high precision \cite{Chatrchyan:2008aa}.
-The muons are detected by special subdetectors placed outside to detect them once they have crossed the solenoid as shown in Figure~\ref{figure5}.
-In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
-So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the Standard Model (SM).
+A powerful magnet is used to bend charged particles as they move away from the point of collision to identify the charge of the particles to bend them in opposite directions and measure momentum.
+A silicon tracker, made of about 75 million electronic sensors arranged in concentric layers, measures the curvature of charged particles with very high precision \cite{Chatrchyan:2008aa}.
+The electromagnetic calorimeter detects photons and electrons while the hadronic calorimeter detects mainly pions and kaons.
+The muons are detected by special chambers placed outside the solenoid as shown in Figure~\ref{figure5}.
 
-LHC during the first run in 2011 and 2012 reached a peak instantaneous luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
- The LHC will deliver about 300 $fb^{-1}$ by 2024 \cite{collaborations2019report}.
-The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles.
-In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  place in parallel during one shutdown, at around 2023-25 (LS3), with some of the modification anticipated in 2019-2020 (LS2).
-This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ by the year 2036 as shown in Figure~\ref{figure6}.
-Figure~\ref{figureKappas} shows a summary of the current measurements of the Higgs coupling parameters with the LHC Run 1 dataset (2011,2012)  using ggF, VBF, VH, and ${t\bar{t}H}$ production modes \cite{Tanabashi:2018oca}.
+During Run 1 (2011 and 2012) the LHC reached a peak instantaneous luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
+%During Run 2 (2015-2018), the total delivered luminosity was about 150 $fb^{-1}$, but the precision on this value remains to be determined.
+%The LHC will deliver about 300 $fb^{-1}$ by 2024 \cite{collaborations2019report}.
+The goal of subsequent runs of the LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of the Higgs boson and other SM particles.
+%, in order to test the Standard Model pattern of couplings to elementary particles.
+%In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  place in parallel during one shutdown, at around 2023-25 (LS3), with some of the modification anticipated in 2019-2020 (LS2).
+For the final phase of the LHC, the  High Luminosity LHC (HL-LHC), the goal is to obtain a total of 3000 $fb^{-1}$ by the year 2036 as shown in Figure~\ref{figure6}.
+%Figure~\ref{figureKappas} shows a summary of the current measurements of the Higgs coupling parameters with the LHC Run 1 dataset (2011,2012)  using ggF, VBF, VH, and ${t\bar{t}H}$ production modes \cite{Tanabashi:2018oca}.
+%Figure~\ref{figureKappas} shows a summary of the current measurements of the Higgs coupling parameters with the LHC Run 1 dataset (2011,2012)  using ggF, VBF, VH, and ${t\bar{t}H}$ production modes \cite{Tanabashi:2018oca}.
+Figure~\ref{figureKappasUncs} shows the precision expected for the Higgs coupling parameters  with 3000 $fb^{-1}$, and shows that one of the dominant uncertainties remaining is due to the luminosity measurement.
 
-\begin{figure}[H]
-        \centering
-        \includegraphics[width=\columnwidth]{./pg.png}
-        \caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
-        \label{figure 2}
-\end{figure}
+During Run 2 (2015-2018), the total delivered luminosity was about 150 $fb^{-1}$, but the precise value and its uncertainty remains to be determined and is the subject of the project outlined in this document.
+
+%\begin{figure}[H]
+%        \centering
+%        \includegraphics[width=\columnwidth]{./pg.png}
+%        \caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
+%        \label{figure 2}
+%\end{figure}
 
@@
 
+%\begin{figure}[H]
+%  \centering
+%  \includegraphics[scale=0.4]{./couplings.png}
+%  \caption{ATLAS-CMS combined measurements of coupling strength modifiers \cite{Tanabashi:2018oca}.}
+%  \label{figureKappas}
+%\end{figure}
+
 \begin{figure}[H]
   \centering
-  \includegraphics[scale=0.4]{./couplings.png}
-  \caption{ATLAS-CMS combined measurements of coupling strength modifiers \cite{Tanabashi:2018oca}.}
-  \label{figureKappas}
+  \includegraphics[width=0.7\columnwidth]{./LHCcomplex.png}
+  \caption{Diagram of the LHC accelerator complex located in Geneva, Switzerland. Four interaction points are shown for the ALICE, ATLAS, LHCb, and CMS experiments.}
+  \label{figure5}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.6\columnwidth]{./cms12.png}
+  \includegraphics[width=0.7\columnwidth]{./cms12.png}
   \caption{Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimeter, superconducting solenoid and muon chambers \cite{Chatrchyan:2008aa}.}
@@
   \centering
-  \includegraphics[width=0.9\columnwidth]{./lum6.png}
+  \includegraphics[width=0.8\columnwidth]{./HLLHCLumi.png}
   \caption{Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities.
@@
 
-\newpage
+ \begin{figure}[H]
+   \centering
+   \includegraphics[width=0.5\columnwidth]{./higgs_couplings.png}
+   \caption{Expected uncertainties on the Higgs coupling strength modifiers with 3000 $fb^{-1}$ of proton-proton collision data.}
+   \label{figureKappasUncs}
+ \end{figure}
+
+%\newpage
 \section{PROPOSAL}

### 2021-04-30 project_ashish_monograph/CMS.tex
ashish monograph

--- 2021-04-08 project_ashish_lumi/paper.tex
@@
-\documentclass[final,3p]{CSP}
-\usepackage{amssymb}
-\usepackage{changepage}
-\usepackage{float}
-\usepackage{hyperref}
-\usepackage{url}
-\usepackage{afterpage}
-\usepackage{natbib}
-\usepackage{setspace}
-\usepackage{fancyhdr}
-\pagestyle{fancy}
-\fancyhf{}
+\section{The CMS experiment}
+\label{sec:cms}
+(describe the experiment in general, its discovery, mention the international collaboration)
 
-\def\Student{Ashish Sehrawat}
-\def\Title{THESIS PROJECT PROPOSAL}
-\def\Prog{Doctorado en Ciencias (F\'{i}sica) }
-\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
-\def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
-\def\ProjectTitle{ Measurement of ... }
-\def\ResearchLine{Astrof\'{i}sica, Cosmolog\'{i}a y F\'{i}sica de Part\'{i}culas}
-
-\newcommand{\SubItem}[1]{
-    {\setlength\itemindent{15pt} \item[-] #1}
-}
-
-%%header and footer
-\lhead{\Student}
-\rhead{\Title}
-\lfoot{\Dept}
-\rfoot{Page \thepage}
-\setlength{\headsep}{0.2in}
-\renewcommand{\footrulewidth}{0.4pt}% default is 0pt
-
-\begin{document}
-
-%%%%Title Page
-\begin{titlepage}
-  \centering
-  \hspace{0pt}
-  \vfill
-        {\scshape\Large \Title \par}
-
-	\vspace{2cm}
-        \begin{adjustwidth}{2cm}{2cm}{
-            TITLE:\par
-            {\large \ProjectTitle \par}
-          }
-        \end{adjustwidth}
-
-	\vspace{0.5cm}
-        \begin{adjustwidth}{2cm}{2cm}{
-            RESEARCH LINE: \par
-            \ResearchLine \par}
-        \end{adjustwidth}
-
-        \vspace{4cm}
-        {\underline{\hspace{8cm}}\par}
-	{\scshape\large \Student \par}
-        {Student\par}
-
-        \vspace{1cm}
-        {\underline{\hspace{8cm}}\par}
-	{\Director \par}
-        {Director\par}
-
-        \vspace{1cm}
-        {\Prog \par}
-        {\Dept \par}
-        {Universidad de Sonora \par}
-
-        \vspace{4cm}
-	{\today}
-
-\hspace{0pt}
-\vfill
-
-\end{titlepage}
-
-%%%%% white page for print out
-\shipout\null
-
-%%%% Abstract Page
-\newpage
-\hspace{2pt}
-\vfill
-
-\begin{adjustwidth}{1cm}{1cm}
-
-  \begin{center}
-    {\Large \ProjectTitle \par}
-    \vspace{1cm}
-    {\itshape\textbf{Abstract}\par}
-  \end{center}
-
-  \vspace{1 cm}
-
-  \onehalfspacing
-  This research project proposes ...
-
-\end{adjustwidth}
-
-\hspace{2pt}
-\vfill
-
-%%%%%% Begin the body
-\newpage
-\section{BACKGROUND}
-
-\onehalfspacing The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
-particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the 
-weak nuclear force. Gravitational force is neglected as the strength of this force is very weak at the scales over which 
-elementary particle interact with each other. The standard model (SM) of particle physics is divided into two categories, 
-bosonic sector and fermionic sector. Bosonic sector contain particles called bosons which mediate the fundamental forces of 
-nature and the fermionic sector contain particles called fermions which make up all the matter in our universe. SM has three 
-generations of matter (fermions) particles. The first generation of fermions consists of up (u) quark, down (d) quark, electron 
-and electron neutrino, second generation consist of charm (c) quark, strange (s) quark, muon and muon neutrino and the third 
-generation of matter particles has top (t) quark, bottom (b) quark, tau and tau neutrino. The bosonic sector consist of gauge 
-bosons like gluon, photon, $W^{\pm}$, $Z^0$ which mediate strong nuclear force, electromagnetic force and weak nuclear force respectively.
-There is one more particle in the standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}.
-All the standard model particles are shown in Figure 1.
-Higgs boson can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva, Switzerland.
-
-The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large 
-number of free-parameters and the fine tuning related to these parameters suggest new physics beyond SM as mentioned below.
-\begin{itemize}
-\item{Fine structure constant $\alpha$},
-\item{Weinberg angle or the weak mixing angle $\theta_W$},
-\item{The coupling constant of strong interaction $\alpha_s$},
-\item{Electroweak symmetry breaking energy scale v},
-\item{ Higgs potential self coupling $\lambda$ or the Higgs mass $m_H$},
-\item{Three weak mixing angles and the CP-violating phase $\delta$ of the CKM matrix which tells us how quarks of different flavor mix with each other},
-\item{Nine yukawa couplings $y_i$ (i = 1 to 9) which determine the mass of nine charged fermions}.
-\end{itemize}
-
-Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. 
-These had eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was 
-discovered in 1995 in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass 
-energy of 1.8 TeV untill 2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 
-colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years.
-The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC).
-It is designed to detect particles known as muons very accurately.
-The CMS detector has the form of a cylindrical onion, with several concentric layers of components.
-Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to bend them in opposite directions and measure momentum.
-A silicon tracker, made of about 75
-million electronic sensors arranged in concentric layers, identifies the tracks taken by these charged particles bent with very high precision \cite{Chatrchyan:2008aa}.
-The muons are detected by special subdetectors placed outside to detect them once they have crossed the solenoid as shown in Figure~\ref{figure5}.
-In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
-So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the Standard Model (SM).
-
-LHC during the first run in 2011 and 2012 reached a peak instantaneous luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
- The LHC will deliver about 300 $fb^{-1}$ by 2024 \cite{collaborations2019report}.
-The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles.
-In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  place in parallel during one shutdown, at around 2023-25 (LS3), with some of the modification anticipated in 2019-2020 (LS2).
-This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ by the year 2036 as shown in Figure~\ref{figure6}.
-Figure~\ref{figureKappas} shows a summary of the current measurements of the Higgs coupling parameters with the LHC Run 1 dataset (2011,2012)  using ggF, VBF, VH, and ${t\bar{t}H}$ production modes \cite{Tanabashi:2018oca}.
-
-\begin{figure}[H]
-        \centering
-        \includegraphics[width=\columnwidth]{./pg.png}
-        \caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
-        \label{figure 2}
-\end{figure}
-
-%\begin{figure}[H]
-%  \centering
-%   \includegraphics[width=\columnwidth]{./cd2.png}
-%  \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
-%   \label{figure 3}
-%\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[scale=0.4]{./couplings.png}
-  \caption{ATLAS-CMS combined measurements of coupling strength modifiers \cite{Tanabashi:2018oca}.}
-  \label{figureKappas}
-\end{figure}
+\subsection{CMS detector}
+(describe the detector components and what they do)
 
@@
   \caption{Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimeter, superconducting solenoid and muon chambers \cite{Chatrchyan:2008aa}.}
-  \label{figure5}
+  \label{fig:CMS}
 \end{figure}
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.9\columnwidth]{./lum6.png}
-  \caption{Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities.
-Points show instantaneous luminosity while the line shows luminosity accumulated \cite{collaborations2019report}.}
-  \label{figure6}
-\end{figure}
-
-\newpage
-\section{PROPOSAL}
-
-\onehalfspacing
-In this project, it is proposed to
-
-\section{GENERAL OBJECTIVE}
-
-%- motivation, tH production crossection, sign of $k_t$, search for BSM, ..
-
-\onehalfspacing
-There is currently a great enigma in physics since we know that ordinary matter comprises only $5\%$ of the universe, another $27\%$ includes Dark matter and the rest $68\%$ is Dark energy.
-
-\section{HYPOTHESIS}
-%%  - what we expect to find
-
-\onehalfspacing
-
-%\newpage
-\section{SPECIFIC OBJECTIVES}
-
-\onehalfspacing
-
-In order to complete a journal publication ...
-
-\begin{itemize}
-\item Simulation..
-\end{itemize}
-
-Finally, the results of this project will be presented at national or international conferences and a publication in a scientific journal will be accomplished.
-
-\section{METHODOLOGY}
-
-\onehalfspacing
-The methods for ...
-
-\textsc{Root} is a \textsc{c++} based software that allows visualization of event distributions and variable correlations.
-
-\section{EXPECTED RESULTS}
-%- a limit, also predictions for future runs
-
-\onehalfspacing The results from this project include the following items:
-\begin{itemize}
-\item The student will become part of an international collaboration.
-\item A leading contribution ....  resulting in a publication in a scientific journal.
-\item Participation in the CMS detector Phase II upgrade through development and possible installation of particle detectors possibly resulting in a technical report.
-\item A presentation of a poster or a talk in one of the national conferences of the Division of Paticles and Fields of the Mexican Society of Physics or a presentation of a poster or a talk in an international physics conference.
-\item An academic stay at a scientific center like CERN or Fermilab.
-\end{itemize}
-
-\section{CALENDAR OF ACTIVITIES}
-\onehalfspacing
-\begin{itemize}
-
-\item {\bf Semester 1 (2019-2)}:
-  \SubItem{ Readings on Standard Model theory}
-  \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
-  \SubItem{ Initial planning of the analysis strategy}
-
-\item {\bf Semester 2 (2020-1)}:
-  \SubItem{ Course I on particle physics and/or particle detection}
-  \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
-  \SubItem{ Readings on SM and tH literature}
-  \SubItem{ Computing accounts at CERN and Fermilab}
-  \SubItem{ CMS service work for authorship}
-  \SubItem{ Possible summer stay at CERN or Fermilab}
-
-\item {\bf Semester 3 (2020-2)}:
-  \SubItem{ Course II on particle physics and/or particle detection.}
-  \SubItem{ CMS service work for authorship}
-
-\item {\bf Semester 4 (2021-1)}:
-  \SubItem{ CMS service work for authorship}
-
-\item {\bf Semester 5 (2021-2)}:
-  \SubItem{ Presentation of poster or talk at national or international conference}
-
-\item {\bf Semester 6 (2022-1)}:
-  \SubItem{ Review process of the results within the CMS collaboration}
-  \SubItem{ Presentation of poster or talk at national or international conference}
-  \SubItem{ Writing of the paper publication}
-  \SubItem{ Writing of the thesis}
-\end{itemize}
-
-\cleardoublepage
-\onehalfspacing
-\bibliographystyle{unsrt}
-\bibliography{paper}
-
-\end{document}
+\subsection{The Pixel detector}

### 2021-04-30 project_ashish_monograph/LHC.tex
ashish monograph

--- 2021-04-08 project_ashish_lumi/paper.tex
@@
-\documentclass[final,3p]{CSP}
-\usepackage{amssymb}
-\usepackage{changepage}
-\usepackage{float}
-\usepackage{hyperref}
-\usepackage{url}
-\usepackage{afterpage}
-\usepackage{natbib}
-\usepackage{setspace}
-\usepackage{fancyhdr}
-\pagestyle{fancy}
-\fancyhf{}
-
-\def\Student{Ashish Sehrawat}
-\def\Title{THESIS PROJECT PROPOSAL}
-\def\Prog{Doctorado en Ciencias (F\'{i}sica) }
-\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
-\def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
-\def\ProjectTitle{ Measurement of ... }
-\def\ResearchLine{Astrof\'{i}sica, Cosmolog\'{i}a y F\'{i}sica de Part\'{i}culas}
-
-\newcommand{\SubItem}[1]{
-    {\setlength\itemindent{15pt} \item[-] #1}
-}
-
-%%header and footer
-\lhead{\Student}
-\rhead{\Title}
-\lfoot{\Dept}
-\rfoot{Page \thepage}
-\setlength{\headsep}{0.2in}
-\renewcommand{\footrulewidth}{0.4pt}% default is 0pt
-
-\begin{document}
-
-%%%%Title Page
-\begin{titlepage}
-  \centering
-  \hspace{0pt}
-  \vfill
-        {\scshape\Large \Title \par}
-
-	\vspace{2cm}
-        \begin{adjustwidth}{2cm}{2cm}{
-            TITLE:\par
-            {\large \ProjectTitle \par}
-          }
-        \end{adjustwidth}
-
-	\vspace{0.5cm}
-        \begin{adjustwidth}{2cm}{2cm}{
-            RESEARCH LINE: \par
-            \ResearchLine \par}
-        \end{adjustwidth}
-
-        \vspace{4cm}
-        {\underline{\hspace{8cm}}\par}
-	{\scshape\large \Student \par}
-        {Student\par}
-
-        \vspace{1cm}
-        {\underline{\hspace{8cm}}\par}
-	{\Director \par}
-        {Director\par}
-
-        \vspace{1cm}
-        {\Prog \par}
-        {\Dept \par}
-        {Universidad de Sonora \par}
-
-        \vspace{4cm}
-	{\today}
-
-\hspace{0pt}
-\vfill
-
-\end{titlepage}
-
-%%%%% white page for print out
-\shipout\null
-
-%%%% Abstract Page
-\newpage
-\hspace{2pt}
-\vfill
-
-\begin{adjustwidth}{1cm}{1cm}
-
-  \begin{center}
-    {\Large \ProjectTitle \par}
-    \vspace{1cm}
-    {\itshape\textbf{Abstract}\par}
-  \end{center}
-
-  \vspace{1 cm}
-
-  \onehalfspacing
-  This research project proposes ...
-
-\end{adjustwidth}
-
-\hspace{2pt}
-\vfill
-
-%%%%%% Begin the body
-\newpage
-\section{BACKGROUND}
-
-\onehalfspacing The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
-particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the 
-weak nuclear force. Gravitational force is neglected as the strength of this force is very weak at the scales over which 
-elementary particle interact with each other. The standard model (SM) of particle physics is divided into two categories, 
-bosonic sector and fermionic sector. Bosonic sector contain particles called bosons which mediate the fundamental forces of 
-nature and the fermionic sector contain particles called fermions which make up all the matter in our universe. SM has three 
-generations of matter (fermions) particles. The first generation of fermions consists of up (u) quark, down (d) quark, electron 
-and electron neutrino, second generation consist of charm (c) quark, strange (s) quark, muon and muon neutrino and the third 
-generation of matter particles has top (t) quark, bottom (b) quark, tau and tau neutrino. The bosonic sector consist of gauge 
-bosons like gluon, photon, $W^{\pm}$, $Z^0$ which mediate strong nuclear force, electromagnetic force and weak nuclear force respectively.
-There is one more particle in the standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}.
-All the standard model particles are shown in Figure 1.
-Higgs boson can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva, Switzerland.
-
-The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large 
-number of free-parameters and the fine tuning related to these parameters suggest new physics beyond SM as mentioned below.
-\begin{itemize}
-\item{Fine structure constant $\alpha$},
-\item{Weinberg angle or the weak mixing angle $\theta_W$},
-\item{The coupling constant of strong interaction $\alpha_s$},
-\item{Electroweak symmetry breaking energy scale v},
-\item{ Higgs potential self coupling $\lambda$ or the Higgs mass $m_H$},
-\item{Three weak mixing angles and the CP-violating phase $\delta$ of the CKM matrix which tells us how quarks of different flavor mix with each other},
-\item{Nine yukawa couplings $y_i$ (i = 1 to 9) which determine the mass of nine charged fermions}.
-\end{itemize}
-
-Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. 
-These had eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was 
-discovered in 1995 in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass 
-energy of 1.8 TeV untill 2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 
-colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years.
-The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC).
-It is designed to detect particles known as muons very accurately.
-The CMS detector has the form of a cylindrical onion, with several concentric layers of components.
-Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to bend them in opposite directions and measure momentum.
-A silicon tracker, made of about 75
-million electronic sensors arranged in concentric layers, identifies the tracks taken by these charged particles bent with very high precision \cite{Chatrchyan:2008aa}.
-The muons are detected by special subdetectors placed outside to detect them once they have crossed the solenoid as shown in Figure~\ref{figure5}.
-In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
-So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the Standard Model (SM).
-
-LHC during the first run in 2011 and 2012 reached a peak instantaneous luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
- The LHC will deliver about 300 $fb^{-1}$ by 2024 \cite{collaborations2019report}.
-The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles.
-In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  place in parallel during one shutdown, at around 2023-25 (LS3), with some of the modification anticipated in 2019-2020 (LS2).
-This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ by the year 2036 as shown in Figure~\ref{figure6}.
-Figure~\ref{figureKappas} shows a summary of the current measurements of the Higgs coupling parameters with the LHC Run 1 dataset (2011,2012)  using ggF, VBF, VH, and ${t\bar{t}H}$ production modes \cite{Tanabashi:2018oca}.
+\section{The Large Hadron Collider}
+\label{sec:lhc}
+(describe the accelerator complex, proton bunches, c.m. energy, all experiments, run periods, inst. and integrated lumi, Run 3 and HL-LHC plans)
 
@@
   \centering
-        \includegraphics[width=\columnwidth]{./pg.png}
-        \caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
-        \label{figure 2}
-\end{figure}
-
-%\begin{figure}[H]
-%  \centering
-%   \includegraphics[width=\columnwidth]{./cd2.png}
-%  \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
-%   \label{figure 3}
-%\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[scale=0.4]{./couplings.png}
-  \caption{ATLAS-CMS combined measurements of coupling strength modifiers \cite{Tanabashi:2018oca}.}
-  \label{figureKappas}
+  \includegraphics[width=0.7\columnwidth]{./LHCcomplex.png}
+  \caption{Diagram of the LHC accelerator complex located in Geneva, Switzerland. Four interaction points are shown for the ALICE, ATLAS
+, LHCb, and CMS experiments.}
+  \label{fig:LHC}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.6\columnwidth]{./cms12.png}
-  \caption{Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimeter, superconducting solenoid and muon chambers \cite{Chatrchyan:2008aa}.}
-  \label{figure5}
+  \includegraphics[width=0.8\columnwidth]{./HLLHCLumi.png}
+  \caption{Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and lumino
+sities. Points show instantaneous luminosity while the line shows luminosity accumulated \cite{collaborations2019report}.}
+  \label{fig:LHCPlans}
 \end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.9\columnwidth]{./lum6.png}
-  \caption{Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities.
-Points show instantaneous luminosity while the line shows luminosity accumulated \cite{collaborations2019report}.}
-  \label{figure6}
-\end{figure}
-
-\newpage
-\section{PROPOSAL}
-
-\onehalfspacing
-In this project, it is proposed to
-
-\section{GENERAL OBJECTIVE}
-
-%- motivation, tH production crossection, sign of $k_t$, search for BSM, ..
-
-\onehalfspacing
-There is currently a great enigma in physics since we know that ordinary matter comprises only $5\%$ of the universe, another $27\%$ includes Dark matter and the rest $68\%$ is Dark energy.
-
-\section{HYPOTHESIS}
-%%  - what we expect to find
-
-\onehalfspacing
-
-%\newpage
-\section{SPECIFIC OBJECTIVES}
-
-\onehalfspacing
-
-In order to complete a journal publication ...
-
-\begin{itemize}
-\item Simulation..
-\end{itemize}
-
-Finally, the results of this project will be presented at national or international conferences and a publication in a scientific journal will be accomplished.
-
-\section{METHODOLOGY}
-
-\onehalfspacing
-The methods for ...
-
-\textsc{Root} is a \textsc{c++} based software that allows visualization of event distributions and variable correlations.
-
-\section{EXPECTED RESULTS}
-%- a limit, also predictions for future runs
-
-\onehalfspacing The results from this project include the following items:
-\begin{itemize}
-\item The student will become part of an international collaboration.
-\item A leading contribution ....  resulting in a publication in a scientific journal.
-\item Participation in the CMS detector Phase II upgrade through development and possible installation of particle detectors possibly resulting in a technical report.
-\item A presentation of a poster or a talk in one of the national conferences of the Division of Paticles and Fields of the Mexican Society of Physics or a presentation of a poster or a talk in an international physics conference.
-\item An academic stay at a scientific center like CERN or Fermilab.
-\end{itemize}
-
-\section{CALENDAR OF ACTIVITIES}
-\onehalfspacing
-\begin{itemize}
-
-\item {\bf Semester 1 (2019-2)}:
-  \SubItem{ Readings on Standard Model theory}
-  \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
-  \SubItem{ Initial planning of the analysis strategy}
-
-\item {\bf Semester 2 (2020-1)}:
-  \SubItem{ Course I on particle physics and/or particle detection}
-  \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
-  \SubItem{ Readings on SM and tH literature}
-  \SubItem{ Computing accounts at CERN and Fermilab}
-  \SubItem{ CMS service work for authorship}
-  \SubItem{ Possible summer stay at CERN or Fermilab}
-
-\item {\bf Semester 3 (2020-2)}:
-  \SubItem{ Course II on particle physics and/or particle detection.}
-  \SubItem{ CMS service work for authorship}
-
-\item {\bf Semester 4 (2021-1)}:
-  \SubItem{ CMS service work for authorship}
-
-\item {\bf Semester 5 (2021-2)}:
-  \SubItem{ Presentation of poster or talk at national or international conference}
-
-\item {\bf Semester 6 (2022-1)}:
-  \SubItem{ Review process of the results within the CMS collaboration}
-  \SubItem{ Presentation of poster or talk at national or international conference}
-  \SubItem{ Writing of the paper publication}
-  \SubItem{ Writing of the thesis}
-\end{itemize}
-
-\cleardoublepage
-\onehalfspacing
-\bibliographystyle{unsrt}
-\bibliography{paper}
-
-\end{document}

### 2021-04-30 project_ashish_monograph/PCC.tex
ashish monograph

\section{The Pixel Cluster Counting (PCC) method}
\label{sec:pcc}
(describe cluster reconstruction, the module selection/veto, cluster counting per bx, per LS,..)

### 2021-04-30 project_ashish_monograph/bkg.tex
ashish monograph

\section{Backgrounds}
\label{sec:bkg}
(background in vdM, afterglow backgrounds in Physics, subtraction of these)

### 2021-04-30 project_ashish_monograph/conclusion.tex
ashish monograph

\section{Conclusions and outlook} 
\label{sec:conclusion}
sumarize the method and results, and TEPX upgrade work and plans

### 2021-04-30 project_ashish_monograph/syst.tex
ashish monograph

\section{Systematics}
\label{sec:syst}
(main systematics: vdM, non-linearity, stability, check others in the PAS)

### 2021-04-30 project_ashish_monograph/upgrade.tex
ashish monograph

\section{The TEPX upgrade for HL-LHC}
\label{sec:tepx}
(describe the TEPX detector design, algorithms clusters/coincidences, stat precision, linearity)

### 2021-04-30 project_ashish_monograph/vdM.tex
ashish monograph

\section{van der Meer calibration}
\label{sec:vdm}

### 2021-05-02 project_ashish_lumi/paper.tex
lumi project

@@
-\documentclass[final,3p]{CSP}
+%\documentclass[final,3p]{article}
+\documentclass[final,12p]{article}
+\usepackage{graphicx}
+\usepackage[letterpaper,margin=1.0in]{geometry}
 \usepackage{amssymb}
@@
 \fancyhf{}
+\usepackage[utf8]{inputenc} 
+\usepackage{lastpage}
 
@@
 
-\newcommand{\SubItem}[1]{
-    {\setlength\itemindent{15pt} \item[-] #1}
-}
+%%header and footer
+\lhead{\Student\ / \ \Dept}
+\rhead{\Title}
+\rfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}}
 
-%%header and footer
-\lhead{\Student}
-\rhead{\Title}
-\lfoot{\Dept}
-\rfoot{Page \thepage}
-\setlength{\headsep}{0.2in}
-\renewcommand{\footrulewidth}{0.4pt}% default is 0pt
+%%%%%%%comands
+\newcommand{\SubItem}[1]{ {\setlength\itemindent{15pt} \item[-] #1} }
+\newcommand{\lumi}[1]{{#1~fb$^{-1}$}}
+\newcommand{\instlumi}[1]{#1$\times 10^{34}$ cm$^{-2}$s$^{-1}$} }
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{document}
+\onehalfspacing
 
@@
 {\scshape\Large \Title \par}
-      revision requested december 2020
+project revised 2021-1
 
   \vspace{2cm}
-      %\begin{adjustwidth}{2cm}{2cm}
   {
     TITLE:\par
-         {\large \ProjectTitle \par}
+    {\bf \large \ProjectTitle \par}
   }
-       %\end{adjustwidth}
 
   \vspace{0.5cm}
-       %\begin{adjustwidth}{2cm}{2cm}
   {
@@
   }
-       %\end{adjustwidth}
 
@@
   {\underline{\hspace{8cm}}\par}
-       {\scshape \Student \par}
+  {\bf \scshape \Student \par}
   {Student\par}
@@
   \vspace{1cm}
-       {\Prog \par}
+  {\bf \Prog \par}
   {\Dept \par}
@@
 
-\begin{adjustwidth}{1cm}{1cm}
-
   \begin{center}
@@
 
-  \onehalfspacing
   This research project proposes ...
-
-\end{adjustwidth}
 
@@
 
-\onehalfspacing
 The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the weak nuclear force.
-%Gravitational force is neglected as the strength of this force is very weak at the scales over which elementary particle interact with each other.
-The SM is divided into two categories, bosonic sector and fermionic sector.
-The bosonic sector contain particles which mediate the fundamental forces of  nature and the fermionic sector contain particles which make up all the matter in our universe.
+The SM is divided into two categories, the bosonic sector and the fermionic sector.
+The bosonic sector contains particles which mediate the fundamental forces of  nature and the fermionic sector contains particles which make up all known matter in our universe.
 There are three generations of fermion particles: the first generation consists of up (u) quark, down (d) quark, electron and electron neutrino, the second generation consist of charm (c) quark, strange (s) quark, muon and muon neutrino, and the third generation has the top (t) quark, bottom (b) quark, tau and tau neutrino.
 The bosonic sector consists of the gauge bosons: gluon, photon, $W^{\pm}$, $Z^0$ which mediate strong nuclear force, electromagnetic force and weak nuclear force respectively.
-The Higgs boson ($H$), is the last of the gauge bosons, it gives mass to the other particles via electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}.
-%All the standard model particles are shown in Figure 1.
-%Higgs boson can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva, Switzerland.
-
-%The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large number of free-parameters and the fine tuning related to these parameters suggest new physics beyond SM as mentioned below.
-%\begin{itemize}
-%\item{Fine structure constant $\alpha$},
-%\item{Weinberg angle or the weak mixing angle $\theta_W$},
-%\item{The coupling constant of strong interaction $\alpha_s$},
-%\item{Electroweak symmetry breaking energy scale v},
-%\item{ Higgs potential self coupling $\lambda$ or the Higgs mass $m_H$},
-%\item{Three weak mixing angles and the CP-violating phase $\delta$ of the CKM matrix which tells us how quarks of different flavor mix with each other},
-%\item{Nine yukawa couplings $y_i$ (i = 1 to 9) which determine the mass of nine charged fermions}.
-%\end{itemize}
-
+The Higgs boson ($H$), is the last of the gauge bosons, it gives mass to the other particles via the electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}.
 The heavy particles ($W^{\pm}$, $Z^0$, $H$, and top) can only be produced at high energy particle colliders like the Large Hadron Collider (LHC) operating at a center-of-mass energy of 13 TeV in Geneva, Switzerland.
@@
 These had eluded previous experiments due to difficulties in the production or reconstruction of its decays.
-The top quark was discovered in 1995 in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass energy of 1.8 TeV untill 2010.
-%The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years.
-In 2012, the ATLAS and CMS experiments, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
-This particle has been identified as the Higgs boson of the SM by measuring its properties and comparing to those predicted by the SM.
-%So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the Standard Model (SM).
+The top quark was discovered in 1995 at the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center-of-mass energy of 1.8 TeV until 2010.
+In 2012, the ATLAS and CMS experiments, with detectors at two points where the protons collide in the LHC, announced the discovery of a new particle with a mass of 125 GeV.
+This particle has been identified as the Higgs boson by measuring its properties and comparing to those predicted by the SM.
 
-The Compact Muon Solenoid (CMS) experiment is located at one of the four interaction points of the LHC.
-%It is designed to detect particles known as muons very accurately.
-The CMS detector has the form of a cylindrical onion, with several concentric layers of components.
-A powerful magnet is used to bend charged particles as they move away from the point of collision to identify the charge of the particles to bend them in opposite directions and measure momentum.
-A silicon tracker, made of about 75 million electronic sensors arranged in concentric layers, measures the curvature of charged particles with very high precision \cite{Chatrchyan:2008aa}.
-The electromagnetic calorimeter detects photons and electrons while the hadronic calorimeter detects mainly pions and kaons.
-The muons are detected by special chambers placed outside the solenoid as shown in Figure~\ref{figure5}.
+Luminosity, $L$, is a key parameter at particle colliders long with the energy available in the colision.
+$L$ is one of the  main figures of merit that quantify the potential for observing new particles and measuring their properties.
+The instantaneous luminosity $L(t)$ is the process-independent ratio between the rate $R(t)$ of events produced per unit time and the cross section for a given process $\sigma$: $L(t) = R(t)/\sigma$.
+During Run 1 (2011-2012) the LHC reached a peak instantaneous luminosity of \instlumi{0.77} and delivered an integrated luminosity of about \lumi{25} with a precision of about 2.0\% 
+\footnote{1 barn is a unit of area corresponding to $10^{-24}$ cm${^2}$ and 1 femtobarn (fb) = $10^{-39}$ cm$^{2}$. For comparison, the total Higgs production cross section is 48600 fb.}.
+In the first part of Run 2 (2015-2016), the delivered luminosity has been measured to be \lumi{38.4} with an unprecedented precision of only 1.3\%.
+For the second part of Run 2 (2017-2018), the integrated luminosity is about \lumi{78}, but the precise value and its uncertainty remain to be determined and is one of the main objectives of this thesis project.
 
-During Run 1 (2011 and 2012) the LHC reached a peak instantaneous luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
-%During Run 2 (2015-2018), the total delivered luminosity was about 150 $fb^{-1}$, but the precision on this value remains to be determined.
-%The LHC will deliver about 300 $fb^{-1}$ by 2024 \cite{collaborations2019report}.
-The goal of subsequent runs of the LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of the Higgs boson and other SM particles.
-%, in order to test the Standard Model pattern of couplings to elementary particles.
-%In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  place in parallel during one shutdown, at around 2023-25 (LS3), with some of the modification anticipated in 2019-2020 (LS2).
-For the final phase of the LHC, the  High Luminosity LHC (HL-LHC), the goal is to obtain a total of 3000 $fb^{-1}$ by the year 2036 as shown in Figure~\ref{figure6}.
-%Figure~\ref{figureKappas} shows a summary of the current measurements of the Higgs coupling parameters with the LHC Run 1 dataset (2011,2012)  using ggF, VBF, VH, and ${t\bar{t}H}$ production modes \cite{Tanabashi:2018oca}.
-%Figure~\ref{figureKappas} shows a summary of the current measurements of the Higgs coupling parameters with the LHC Run 1 dataset (2011,2012)  using ggF, VBF, VH, and ${t\bar{t}H}$ production modes \cite{Tanabashi:2018oca}.
-Figure~\ref{figureKappasUncs} shows the precision expected for the Higgs coupling parameters  with 3000 $fb^{-1}$, and shows that one of the dominant uncertainties remaining is due to the luminosity measurement.
-
-During Run 2 (2015-2018), the total delivered luminosity was about 150 $fb^{-1}$, but the precise value and its uncertainty remains to be determined and is the subject of the project outlined in this document.
-
-%\begin{figure}[H]
-%        \centering
-%        \includegraphics[width=\columnwidth]{./pg.png}
-%        \caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
-%        \label{figure 2}
-%\end{figure}
-
-%\begin{figure}[H]
-%  \centering
-%   \includegraphics[width=\columnwidth]{./cd2.png}
-%  \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
-%   \label{figure 3}
-%\end{figure}
-
-%\begin{figure}[H]
-%  \centering
-%  \includegraphics[scale=0.4]{./couplings.png}
-%  \caption{ATLAS-CMS combined measurements of coupling strength modifiers \cite{Tanabashi:2018oca}.}
-%  \label{figureKappas}
-%\end{figure}
+The plans of the LHC up to the year 2038 are to obtain datasets with up to 10 times higher values of instanteneous luminosities in the final phase, the  High Luminosity LHC (HL-LHC), and corresponding integrated luminosities of order \lumi{3000} as shown in Figure~\ref{figure6}.
+These final datasets will provide  precise measurements of the properties of the Higgs boson and other SM particles as shown in Fig. ~\ref{figureKappasUncs}.
+This figure shows that one of the dominant uncertainties remaining is due to the luminosity measurement.
+In this project, we also perform studies for the design and construction of an upgraded luminosity measurement system to be installed for CMS in the HL-LHC phase.
 
@@
   \includegraphics[width=0.7\columnwidth]{./LHCcomplex.png}
-  \caption{Diagram of the LHC accelerator complex located in Geneva, Switzerland. Four interaction points are shown for the ALICE, ATLAS, LHCb, and CMS experiments.}
-  \label{figure5}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.7\columnwidth]{./cms12.png}
-  \caption{Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimeter, superconducting solenoid and muon chambers \cite{Chatrchyan:2008aa}.}
+  \caption{Diagram of the LHC accelerator complex located near Geneva, Switzerland.
+The complex consists of three accelerator stages: the proton (p) or lead (Pb) source, the Proton Synchrotron (PS), the Super Proton Synchrotron (SPS), and the 27 km LHC ring.
+Four colision points are shown corresponding to the ALICE, ATLAS, LHCb, and CMS detectors.
+}
   \label{figure5}
@@
    \centering
-   \includegraphics[width=0.5\columnwidth]{./higgs_couplings.png}
-   \caption{Expected uncertainties on the Higgs coupling strength modifiers with 3000 $fb^{-1}$ of proton-proton collision data.}
+   \includegraphics[width=0.7\columnwidth]{./pg.png}
+   \includegraphics[width=0.29\columnwidth]{./higgs_couplings.png}
+   \caption{
+     Left: Main production mechanisms for the Higgs boson at the LHC: gluon-gluon fusion (ggF), vector-boson fusion (VBF), associated vector boson (VH), associated top-quark pair (ttH), and  associated single-top quark production (tH).
+     Right: Expected uncertainties on the Higgs coupling parameters for  \lumi{3000} of proton-proton collision data at center-of-mass energy of 13 TeV.
+   }
    \label{figureKappasUncs}
@@
 
-%\newpage
 \section{PROPOSAL}
 
-\onehalfspacing
-In this project, it is proposed to
+This project has two main parts, in the first part we propose to perform an analysis of the LHC luminosity data  recorded by the CMS experiment during 2017 and 2018 using the Pixel Cluster Counting (PCC) method.
+In the second part we develop an upgraded luminosity measurement system for the HL-LHC phase (2026-2038).
 
@@
 
-%- motivation, tH production crossection, sign of $k_t$, search for BSM, ..
+The main objective of this work is to perform a measurement of the 2017-2018 LHC delivered luminosity with a precision at the level of 2\% or less using the CMS Pixel detector.
+The precision is necesary for tests of the SM of elementary particles and identification possible new physics which could elucidate the nature of the Dark Matter in our universe.
 
-\onehalfspacing
-There is currently a great enigma in physics since we know that ordinary matter comprises only $5\%$ of the universe, another $27\%$ includes Dark matter and the rest $68\%$ is Dark energy.
+A second objective is to develop an  upgraded luminosity measurement system for the HL-LHC phase using the Tracker Endcap Pixel detector (TEPX).
+The TEPX is part of the new tracker detector proposed by the CMS collaboration which will replace the current one during LS3 (2024-2026).
 
 \section{HYPOTHESIS}
-%%  - what we expect to find
 
-\onehalfspacing
+As mentioned in the introduction, the precision achieved in the measurement of integrated luminosity during Run 1 was about 2.5\% using  methods developed for the first time.
+In 2015 and 2016 the uncertainty achieved was 1.6\% and 1.2\%, respectively, for datasets corresponding to \lumi{2.5} and \lumi{36}.
+The methods used for the 2015 and 2016 data are similar to the ones we propose in this project.
+We expect that the final uncertainties for the 2017 and 2018 datasets will be similar, but the ultimate goal for CMS is to reduce the uncertainties below 1\%.
 
-%\newpage
+For the upgrade part of this project, we must consider that in the HL-LHC phase the higher expected pileup (number of proton colisions per bunch crossing) will lead to a more difficult scenario for the luminosity measurement due to increased detector occupancy and larger irradiation of the detector components.
+However, we expect that new methods to be introduced between now and the start of the HL-LHC phase will improve the measurement precision and compensate the higher backgrounds and detector aging.
+
 \section{SPECIFIC OBJECTIVES}
 
-\onehalfspacing
-
-In order to complete a journal publication ...
-
+For the luminosity measurement:
 \begin{itemize}
-\item Simulation..
+\item understand the CMS pixel detector layout including the barrel layers and endcap disks and their constituent modules,
+\item study the stability of the modules in the different layers or disks of the pixel detector and select the stable components,
+\item calculate the visible cross section corresponding to the PCC rate for proton-proton colisions at 13 TeV using the selected pixel detector components,
+\item study the stability and linearity of the PCC luminosity measurement by comparing to other CMS luminometers as a measurement of the systematic uncertainties,
+\item determine the delivered luminosity per lumisection (23 second intervals) and the total integrated luminosity and determine the corresponding uncertainty.
 \end{itemize}
 
-Finally, the results of this project will be presented at national or international conferences and a publication in a scientific journal will be accomplished.
+\par
+For the development of the HL-LHC upgrad system:
+\begin{itemize}
+\item study the different parts of the TEPX detector,
+\item study the pixel cluster counting at the HL-LHC conditions using simulations of the TEPX detector,
+\item develop an algorithm for counting cluster coincidences using sensor layers of the same disk in the TEPX detector in order to reduce backgrounds,
+\item determine the linearity and statistical precision of the PCC method and coincidence counting method for the TEPX detector and its constituent parts (disks and rings).
+\end{itemize}
 
@@
 
-\onehalfspacing
-The methods for ...
+The CMS experiment is located at one of the four interaction points of the LHC.
+The CMS detector has the form of a cylindrical onion, with several concentric layers of components.
+A powerful magnet is used to bend charged particles as they move away from the point of collision to identify the charge and measure their momentum.
+A silicon tracker, made of about 75 million electronic sensors arranged in concentric layers, measures the curvature of charged particles with very high precision \cite{Chatrchyan:2008aa}.
+The electromagnetic calorimeter detects photons and electrons while the hadronic calorimeter detects mainly pions and kaons.
+The muons are detected by special chambers placed outside the solenoid as shown in Figure~\ref{fig:CMS}.
 
-\textsc{Root} is a \textsc{c++} based software that allows visualization of event distributions and variable correlations.
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.7\columnwidth]{./cms12.png}
+  \caption{Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimeter, superconducting solenoid and muon chambers \cite{Chatrchyan:2008aa}.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.7\columnwidth,crop]{./PixelDetectorPhase1.png}
+  \includegraphics[width=0.27\columnwidth]{./PixelSensor.png}
+  \caption{
+    Left: diagram showing the layout of the CMS Pixel detector used during 2016-2018.
+    The layout consists includes 4 barrel layers and 2 endcap disks withw two rings each.
+    Right: a diagram showing the structure of one pixel sensor.
+    The entire detector consists of 1860 sensors and 65 million pixels.
+  }
+  \label{fig:pixeldet}
+\end{figure}
 
 \section{EXPECTED RESULTS}
-%- a limit, also predictions for future runs
 
-\onehalfspacing The results from this project include the following items:
+The results from this project include the following items:
 \begin{itemize}
@@
 \end{document}
+
+%The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large number of free-parameters and the fine tuning related to these parameters suggest new physics beyond SM as mentioned below.
+%\begin{itemize}
+%\item{Fine structure constant $\alpha$},
+%\item{Weinberg angle or the weak mixing angle $\theta_W$},
+%\item{The coupling constant of strong interaction $\alpha_s$},
+%\item{Electroweak symmetry breaking energy scale v},
+%\item{ Higgs potential self coupling $\lambda$ or the Higgs mass $m_H$},
+%\item{Three weak mixing angles and the CP-violating phase $\delta$ of the CKM matrix which tells us how quarks of different flavor mix with each other},
+%\item{Nine yukawa couplings $y_i$ (i = 1 to 9) which determine the mass of nine charged fermions}.
+%\end{itemize}
+
+%\begin{figure}[H]
+%  \centering
+%   \includegraphics[width=\columnwidth]{./cd2.png}
+%  \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
+%   \label{figure 3}
+%\end{figure}
+
+%\begin{figure}[H]
+%  \centering
+%  \includegraphics[scale=0.4]{./couplings.png}
+%  \caption{ATLAS-CMS combined measurements of coupling strength modifiers \cite{Tanabashi:2018oca}.}
+%  \label{figureKappas}
+%\end{figure}

### 2021-05-02 project_ashish_lumi/paper.tex
lumi project

@@
 
-For the luminosity measurement:
+For the Run 2 luminosity measurement:
 \begin{itemize}
@@
 \par
-For the development of the HL-LHC upgrad system:
+For the development of the HL-LHC upgrade system:
 \begin{itemize}
@@
 
+The PCC method for measuring luminosity uses the Pixel detector of the CMS tracker, the layout of the  detector used for recording the data during 2016-2018 is shown in Figure~\ref{fig:pixeldet}.
+The Pixel detector consists of 4 concentric cylindrical layers in the barrel and 2 disks in each endcap.
+Each detector part is composed by pixel sensors, a schematic of one sensor is shown in Figure~\ref{fig:pixeldet}.
+The entire Pixel detector contains 1856 sensor modules and a total of 65 million pixels.
+
+The PCC method consists of the reconstruction of track clusters produced by charged particle tracks as shown in Figure~\ref{fig:trackcluster}.
+Due to the fine granularity of the pixel sensors and the large number of total pixels, the hit occupancy in the sensors remains very small, order of 1\%, during normal collisions.
+This low occupancy makes the PCC  very linear as a function of pileup, an essential property of a good luminometer.
+
+The calibration of the luminomter consists of a van der Meer (vdM) scan performed in a special LHC run usually at the beginning of the run period (year).
+In this calibration setup, the proton beams are moved accross each other in separation steps of about 100 micrometers, by measuring the rates of clusters with the PCC algorithm and knowledge of the beam parameters during the vdM conditions, the calibration constant ($\sigma_{vis}$) is determined.
+This calibration constant is then used to normalize the measured PCC rates during normal running throughout the data-taking year.
+
+For the upgrade part of this project, the research consists of studying the expected performance of the TEPX disks of the CMS tracker in the HL-LHC phase.
+The current design of the this tracker is shown in Figure~\ref{fig:tepx}, where the TEPX part consists of the last 4 disks at $|z|>17$ cm.
+In the same figure a transverse view of one disk is shown, and shows the layout of the sensor modules along phi for each ring in the disk.
+Studies will be performed using simulated samples with HL-LHC beam conditions, currently the expected pileup for these conditions is about 200 proton collisions per bunch crossing.
+The linearity for the cluster countinng algorithm will be studied.
+In addition, a new algorithm will be developed to detect cluster coincidences between consecutive disk layers.
+It is expected that coincidences will be less sensitive to backgrounds in HL-LHC pileup conditions and therefore a more robust luminosity meausrement can be performed.
+
 \begin{figure}[H]
@@
   \centering
-  \includegraphics[width=0.7\columnwidth,crop]{./PixelDetectorPhase1.png}
+  \includegraphics[width=0.7\columnwidth]{./PixelDetectorPhase1.png}
   \includegraphics[width=0.27\columnwidth]{./PixelSensor.png}
@@
     Left: diagram showing the layout of the CMS Pixel detector used during 2016-2018.
-    The layout consists includes 4 barrel layers and 2 endcap disks withw two rings each.
+    The layout consists of 4 barrel layers and 2 endcap disks withw two rings each.
     Right: a diagram showing the structure of one pixel sensor.
-    The entire detector consists of 1860 sensors and 65 million pixels.
+    The entire detector consists of 1856 sensors and 65 million pixels.
   }
@@
 
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./bunchcrossing.jpg}
+  \includegraphics[width=0.4\columnwidth]{./vectorhit1.jpg}
+  \caption{
+    Left: Diagram showing the collision of two proton bunches at the LHC, bunches contain about $10^{11}$ protons.
+    Right: diagram showing example tracks originating from the colision at the beamspot and producing clusters at the pixel sensors in two detectors layers.
+  }
+  \label{fig:trackcluster}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.7\columnwidth]{./TEPX_rz.pdf}
+  \includegraphics[width=0.27\columnwidth]{./TEPX_rphi.pdf}
+  \caption{
+    Left: Longitudial view of the current design of the CMS tracker detector for the LH-LHC phase. The TEPX consists of the last 4 disks on each side at $|z|$>1700 mm.
+    Right: Transverse view of one TEPX disk showing the layout of the sensors in each of the 5 rings.
+  }
+  \label{fig:tepx}
+\end{figure}
+
 \section{EXPECTED RESULTS}
 
-The results from this project include the following items:
+From this project two main publications are expected:
 \begin{itemize}
-\item The student will become part of an international collaboration.
-\item A leading contribution ....  resulting in a publication in a scientific journal.
-\item Participation in the CMS detector Phase II upgrade through development and possible installation of particle detectors possibly resulting in a technical report.
-\item A presentation of a poster or a talk in one of the national conferences of the Division of Paticles and Fields of the Mexican Society of Physics or a presentation of a poster or a talk in an international physics conference.
-\item An academic stay at a scientific center like CERN or Fermilab.
+\item
+For the Run 2 luminosity mesurement, the student will perform the studies for the selection of good modules for the calculation of the luminosity using the PCC method.
+From past performance of this algorithm it is expected that this measurement will give one of the best linearity and stability systematic uncertainties for the integrated luminosity value.
+The results of these studies will be published in a peer-reviewed scientific journal.
+\item
+For the development of the HL-LHC upgrade system, we expect to produce a Technical Design Report (TDR) with the proposed design and algorithms to use the TEPX detector.
+This document will be published in the CERN document server (CDS) and submitted the LHC committee for the approval of the required funding for the construction and operation of the system.
 \end{itemize}
 
+Also, the student will become part of an international experiment and is expected to present his results at national or international scientific conferences.
+
 \section{CALENDAR OF ACTIVITIES}
-\onehalfspacing
+
 \begin{itemize}
@@
 \item {\bf Semester 2 (2020-1)}:
-  \SubItem{ Course I on particle physics and/or particle detection}
+  \SubItem{ Course I on particle physics, particle detection, or data analysis}
+  \SubItem{ Readings on the LHC and CMS experiments}
   \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
-  \SubItem{ Readings on SM and tH literature}
   \SubItem{ Computing accounts at CERN and Fermilab}
-  \SubItem{ CMS service work for authorship}
-  \SubItem{ Possible summer stay at CERN or Fermilab}
+  \SubItem{ Studies of the TEPX luminometer upgrade}
 
 \item {\bf Semester 3 (2020-2)}:
-  \SubItem{ Course II on particle physics and/or particle detection.}
-  \SubItem{ CMS service work for authorship}
+  \SubItem{ Course II on particle physics, particle detection, or  data analysis}
+  \SubItem{ Studies of the TEPX luminometer upgrade}
 
 \item {\bf Semester 4 (2021-1)}:
-  \SubItem{ CMS service work for authorship}
+  \SubItem{ Completion of the TEPX luminometer studies for the TDR document}
+  \SubItem{ Studies of the LHC Run 2 data using the PCC method}
+  \SubItem{ Writing of the monograph}
 
 \item {\bf Semester 5 (2021-2)}:
-  \SubItem{ Presentation of poster or talk at national or international conference}
+  \SubItem{ Publication of the TDR document in CDS and submission to the LHCC review}
+  \SubItem{ Presentation at national or international conferences of the TEPX upgrade studies}
+  \SubItem{ Studies of the LHC Run 2 data using the PCC method}
 
 \item {\bf Semester 6 (2022-1)}:
-  \SubItem{ Review process of the results within the CMS collaboration}
-  \SubItem{ Presentation of poster or talk at national or international conference}
-  \SubItem{ Writing of the paper publication}
-  \SubItem{ Writing of the thesis}
+  \SubItem{ Completion of the studies of the Run 2 data luminosity measurement}
+  \SubItem{ Writing of the Run 2 data luminosity measurement publication and review within the CMS collaboration}
+
+\item {\bf Semester 7 (2022-2)}:
+  \SubItem{ Publicaiton of the Run 2 data luminosity measurement in a peer reviewed journal}
+
+\item {\bf Semester 8 (2023-1)}: 
+  \SubItem{ Presentations at national or international conferences of both the Run 2 luminosity measurement}
+  \SubItem{ Writing of the Ph.D thesis}
+
 \end{itemize}
 
-\cleardoublepage
 \onehalfspacing
@@
 \end{document}
-
-%The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large number of free-parameters and the fine tuning related to these parameters suggest new physics beyond SM as mentioned below.
-%\begin{itemize}
-%\item{Fine structure constant $\alpha$},
-%\item{Weinberg angle or the weak mixing angle $\theta_W$},
-%\item{The coupling constant of strong interaction $\alpha_s$},
-%\item{Electroweak symmetry breaking energy scale v},
-%\item{ Higgs potential self coupling $\lambda$ or the Higgs mass $m_H$},
-%\item{Three weak mixing angles and the CP-violating phase $\delta$ of the CKM matrix which tells us how quarks of different flavor mix with each other},
-%\item{Nine yukawa couplings $y_i$ (i = 1 to 9) which determine the mass of nine charged fermions}.
-%\end{itemize}
-
-%\begin{figure}[H]
-%  \centering
-%   \includegraphics[width=\columnwidth]{./cd2.png}
-%  \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
-%   \label{figure 3}
-%\end{figure}
-
-%\begin{figure}[H]
-%  \centering
-%  \includegraphics[scale=0.4]{./couplings.png}
-%  \caption{ATLAS-CMS combined measurements of coupling strength modifiers \cite{Tanabashi:2018oca}.}
-%  \label{figureKappas}
-%\end{figure}

### 2021-05-02 project_ashish_lumi/paper.tex
added references

@@
 
-  This research project proposes ...
+  This research project proposes to determine precise value and corresponding uncertainity of luminosity delivered to Compact Muon Solenoid (CMS) experiment at CERN during 2017-2018 period using Pixel Cluster Counting (PCC) method and construction of luminosity measurement device using Tracker Endcap Pixel Detector (TEPX) for High Luminosity (HL)-LHC which will be able to withstand luminosities of up to 3000 $fb^{-1}$.
+Luminosity plays a vital role in determination of cross section for various production and decay processes of elementary particles and its accurate determination will assist in precise calculation of SM quantities like cross section, couplings and exploring physics beyond SM.
 
@@
 
-The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the weak nuclear force.
+The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary particles mediated by three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the weak nuclear force.
 The SM is divided into two categories, the bosonic sector and the fermionic sector.
@@
 The bosonic sector consists of the gauge bosons: gluon, photon, $W^{\pm}$, $Z^0$ which mediate strong nuclear force, electromagnetic force and weak nuclear force respectively.
-The Higgs boson ($H$), is the last of the gauge bosons, it gives mass to the other particles via the electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}.
+The Higgs boson ($H$), is the last of the gauge bosons, it gives mass to the other SM particles via electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}.
 The heavy particles ($W^{\pm}$, $Z^0$, $H$, and top) can only be produced at high energy particle colliders like the Large Hadron Collider (LHC) operating at a center-of-mass energy of 13 TeV in Geneva, Switzerland.
-Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. 
-These had eluded previous experiments due to difficulties in the production or reconstruction of its decays.
+Until the 90s, existence of almost all the SM particles were confirmed except the top quark and the Higgs boson. 
+These had eluded previous experiments due to difficulties in the production and reconstruction of its decay products.
 The top quark was discovered in 1995 at the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center-of-mass energy of 1.8 TeV until 2010.
-In 2012, the ATLAS and CMS experiments, with detectors at two points where the protons collide in the LHC, announced the discovery of a new particle with a mass of 125 GeV.
+In 2012, the ATLAS and CMS experiments, with detectors placed at two points where the proton beams collide in the LHC, announced the discovery of a new particle with a mass of 125 GeV.
 This particle has been identified as the Higgs boson by measuring its properties and comparing to those predicted by the SM.
 
-Luminosity, $L$, is a key parameter at particle colliders long with the energy available in the colision.
+Luminosity, $L$, is a key parameter at particle colliders along with the energy available in the collision.
 $L$ is one of the  main figures of merit that quantify the potential for observing new particles and measuring their properties.
 The instantaneous luminosity $L(t)$ is the process-independent ratio between the rate $R(t)$ of events produced per unit time and the cross section for a given process $\sigma$: $L(t) = R(t)/\sigma$.
-During Run 1 (2011-2012) the LHC reached a peak instantaneous luminosity of \instlumi{0.77} and delivered an integrated luminosity of about \lumi{25} with a precision of about 2.0\% 
+During Run 1 (2011-2012) LHC reached a peak instantaneous luminosity of \instlumi{0.77} and delivered an integrated luminosity of about \lumi{25} with a precision of about 2.0\% 
 \footnote{1 barn is a unit of area corresponding to $10^{-24}$ cm${^2}$ and 1 femtobarn (fb) = $10^{-39}$ cm$^{2}$. For comparison, the total Higgs production cross section is 48600 fb.}.
-In the first part of Run 2 (2015-2016), the delivered luminosity has been measured to be \lumi{38.4} with an unprecedented precision of only 1.3\%.
-For the second part of Run 2 (2017-2018), the integrated luminosity is about \lumi{78}, but the precise value and its uncertainty remain to be determined and is one of the main objectives of this thesis project.
+In the first part of Run 2 (2015-2016), the delivered luminosity has been measured to be \lumi{38.4} with an unprecedented precision of 1.3\% \cite{Sirunyan:2021qkt}.
+For the second part of Run 2 (2017-2018), the integrated luminosity is about \lumi{78}, but its precise value and uncertainty remain to be determined and is one of the main objectives of this thesis project \cite{CMS:2018elu}.
 
-The plans of the LHC up to the year 2038 are to obtain datasets with up to 10 times higher values of instanteneous luminosities in the final phase, the  High Luminosity LHC (HL-LHC), and corresponding integrated luminosities of order \lumi{3000} as shown in Figure~\ref{figure6}.
+The plan of the LHC till year 2038 is to obtain datasets with up to 10 times higher values of instanteneous luminosities in the final phase, the  High Luminosity LHC (HL-LHC), and corresponding integrated luminosities of order \lumi{3000} as shown in Figure~\ref{figure6}.
 These final datasets will provide  precise measurements of the properties of the Higgs boson and other SM particles as shown in Fig. ~\ref{figureKappasUncs}.
-This figure shows that one of the dominant uncertainties remaining is due to the luminosity measurement.
-In this project, we also perform studies for the design and construction of an upgraded luminosity measurement system to be installed for CMS in the HL-LHC phase.
+This figure shows that one of the dominant uncertainties which remain to be determined is due to the luminosity measurement.
+In this project, we also perform studies for the design and construction of an upgraded luminosity measurement system to be installed for CMS in the HL-LHC phase}\cite{Collaboration:2706512}.
 
@@
 The complex consists of three accelerator stages: the proton (p) or lead (Pb) source, the Proton Synchrotron (PS), the Super Proton Synchrotron (SPS), and the 27 km LHC ring.
-Four colision points are shown corresponding to the ALICE, ATLAS, LHCb, and CMS detectors.
+Four collision points are shown corresponding to the ALICE, ATLAS, LHCb, and CMS detectors  \cite{Mobs:2684277}.
 }
@@
    \caption{
-     Left: Main production mechanisms for the Higgs boson at the LHC: gluon-gluon fusion (ggF), vector-boson fusion (VBF), associated vector boson (VH), associated top-quark pair (ttH), and  associated single-top quark production (tH).
-     Right: Expected uncertainties on the Higgs coupling parameters for  \lumi{3000} of proton-proton collision data at center-of-mass energy of 13 TeV.
+     Left: Main production mechanisms for the Higgs boson at the LHC: gluon-gluon fusion (ggF), vector-boson fusion (VBF), associated vector boson (VH), associated top-quark pair (ttH), and  associated single-top quark production (tH)  \cite{Grojean:2017hsb}  \cite{Khachatryan:2015ota} .
+     Right: Expected uncertainties on the Higgs coupling parameters for  \lumi{3000} of proton-proton collision data at 13 TeV center-of-mass energy \cite{Cepeda:2019klc}.
    }
@@
 
-This project has two main parts, in the first part we propose to perform an analysis of the LHC luminosity data  recorded by the CMS experiment during 2017 and 2018 using the Pixel Cluster Counting (PCC) method.
+This project has two main parts, in the first part we propose to perform an analysis of the LHC luminosity data  recorded by the CMS experiment during 2017 and 2018 using Pixel Cluster Counting (PCC) method.
 In the second part we develop an upgraded luminosity measurement system for the HL-LHC phase (2026-2038).
@@
 The main objective of this work is to perform a measurement of the 2017-2018 LHC delivered luminosity with a precision at the level of 2\% or less using the CMS Pixel detector.
-The precision is necesary for tests of the SM of elementary particles and identification possible new physics which could elucidate the nature of the Dark Matter in our universe.
+This precision is necesary for testing SM of elementary particles and identifying possible new physics which could elucidate the nature of Dark Matter in our universe.
 
-A second objective is to develop an  upgraded luminosity measurement system for the HL-LHC phase using the Tracker Endcap Pixel detector (TEPX).
-The TEPX is part of the new tracker detector proposed by the CMS collaboration which will replace the current one during LS3 (2024-2026).
+The second objective is to develop an upgraded luminosity measurement system for the HL-LHC phase using Tracker Endcap Pixel detector (TEPX).
+TEPX is a part of new tracker detector proposed by the CMS collaboration which will replace the current one during LS3 (2024-2026).
 
@@
 
-As mentioned in the introduction, the precision achieved in the measurement of integrated luminosity during Run 1 was about 2.5\% using  methods developed for the first time.
-In 2015 and 2016 the uncertainty achieved was 1.6\% and 1.2\%, respectively, for datasets corresponding to \lumi{2.5} and \lumi{36}.
-The methods used for the 2015 and 2016 data are similar to the ones we propose in this project.
-We expect that the final uncertainties for the 2017 and 2018 datasets will be similar, but the ultimate goal for CMS is to reduce the uncertainties below 1\%.
+As mentioned in the introduction, precision achieved in the measurement of integrated luminosity during Run 1 was about 2.5\% using  methods developed for the first time.
+In 2015 and 2016 the uncertainty achieved was 1.6\% and 1.2\%, respectively, for datasets corresponding to \lumi{2.5} and \lumi{36}  \cite{Sirunyan:2021qkt}.
+The methods used for the 2015 and 2016 data are similar to the strategy we propose in this project.
+We expect that the final uncertainties for the 2017 and 2018 datasets to be similar, but the ultimate goal of the CMS collaboration is to reduce these uncertainties to below 1\%  \cite{Dainese:2019rgk}.
 
-For the upgrade part of this project, we must consider that in the HL-LHC phase the higher expected pileup (number of proton colisions per bunch crossing) will lead to a more difficult scenario for the luminosity measurement due to increased detector occupancy and larger irradiation of the detector components.
+For the upgrade part of this project, we must consider that in the HL-LHC phase the higher expected pileup (number of proton collisions per bunch crossing) will lead to more difficult scenarios for the luminosity measurement due to increased detector occupancy and larger irradiation of the detector components.
 However, we expect that new methods to be introduced between now and the start of the HL-LHC phase will improve the measurement precision and compensate the higher backgrounds and detector aging.
@@
 \begin{itemize}
-\item study the different parts of the TEPX detector,
-\item study the pixel cluster counting at the HL-LHC conditions using simulations of the TEPX detector,
-\item develop an algorithm for counting cluster coincidences using sensor layers of the same disk in the TEPX detector in order to reduce backgrounds,
+\item study the different parts of the TEPX detector.
+\item study the pixel cluster counting at the HL-LHC conditions using simulations of the TEPX detector.
+\item develop an algorithm for counting cluster coincidences using sensor layers of the same disk in the TEPX detector in order to reduce backgrounds.
 \item determine the linearity and statistical precision of the PCC method and coincidence counting method for the TEPX detector and its constituent parts (disks and rings).
@@
 
-The CMS experiment is located at one of the four interaction points of the LHC.
+The CMS experiment is located at one of the four interaction points of LHC.
 The CMS detector has the form of a cylindrical onion, with several concentric layers of components.
@@
 A silicon tracker, made of about 75 million electronic sensors arranged in concentric layers, measures the curvature of charged particles with very high precision \cite{Chatrchyan:2008aa}.
-The electromagnetic calorimeter detects photons and electrons while the hadronic calorimeter detects mainly pions and kaons.
+The electromagnetic calorimeter detects photons and electrons while the hadron calorimeter detects mainly pions and kaons.
 The muons are detected by special chambers placed outside the solenoid as shown in Figure~\ref{fig:CMS}.
@@
 The Pixel detector consists of 4 concentric cylindrical layers in the barrel and 2 disks in each endcap.
-Each detector part is composed by pixel sensors, a schematic of one sensor is shown in Figure~\ref{fig:pixeldet}.
+Each detector part is composed of pixel sensors, a schematic of one sensor is shown in Figure~\ref{fig:pixeldet}.
 The entire Pixel detector contains 1856 sensor modules and a total of 65 million pixels.
@@
 
-The calibration of the luminomter consists of a van der Meer (vdM) scan performed in a special LHC run usually at the beginning of the run period (year).
-In this calibration setup, the proton beams are moved accross each other in separation steps of about 100 micrometers, by measuring the rates of clusters with the PCC algorithm and knowledge of the beam parameters during the vdM conditions, the calibration constant ($\sigma_{vis}$) is determined.
+The calibration of the luminometer consists of a van der Meer (vdM) scan performed in a special LHC run usually at the beginning of the run period (year).
+In this calibration setup, proton beams are moved across each other in separation steps of about 100 micrometers, by measuring the rates of clusters with the PCC algorithm and knowledge of the beam parameters during the vdM conditions, the calibration constant ($\sigma_{vis}$) is determined.
 This calibration constant is then used to normalize the measured PCC rates during normal running throughout the data-taking year.
@@
 For the upgrade part of this project, the research consists of studying the expected performance of the TEPX disks of the CMS tracker in the HL-LHC phase.
-The current design of the this tracker is shown in Figure~\ref{fig:tepx}, where the TEPX part consists of the last 4 disks at $|z|>17$ cm.
+The current design of the this tracker is shown in Figure~\ref{fig:tepx}, where the TEPX part consists of the last 4 disks at $|z|>170$ cm.
 In the same figure a transverse view of one disk is shown, and shows the layout of the sensor modules along phi for each ring in the disk.
 Studies will be performed using simulated samples with HL-LHC beam conditions, currently the expected pileup for these conditions is about 200 proton collisions per bunch crossing.
-The linearity for the cluster countinng algorithm will be studied.
-In addition, a new algorithm will be developed to detect cluster coincidences between consecutive disk layers.
-It is expected that coincidences will be less sensitive to backgrounds in HL-LHC pileup conditions and therefore a more robust luminosity meausrement can be performed.
+The linearity of the cluster counting algorithm will be studied.
+In addition, a new algorithm will be developed to detect cluster coincidences between consecutive layers of a disk.
+It is expected that coincidences will be less sensitive to backgrounds in HL-LHC pileup conditions and therefore a more robust luminosity measurement can be performed.
 
@@
     Left: diagram showing the layout of the CMS Pixel detector used during 2016-2018.
-    The layout consists of 4 barrel layers and 2 endcap disks withw two rings each.
+    The layout consists of 4 barrel layers and 2 endcap disks with two rings each.
     Right: a diagram showing the structure of one pixel sensor.
-    The entire detector consists of 1856 sensors and 65 million pixels.
+    The entire detector consists of 1856 sensors and 65 million pixels \cite{TrackerGroupoftheCMS:2020bgg}.
   }
@@
   \caption{
-    Left: Diagram showing the collision of two proton bunches at the LHC, bunches contain about $10^{11}$ protons.
-    Right: diagram showing example tracks originating from the colision at the beamspot and producing clusters at the pixel sensors in two detectors layers.
+    Left: Diagram showing the collision of two proton bunches at LHC, bunches contain about $10^{11}$ protons  \cite{deMaria:2008zzb}.
+    Right: diagram showing example tracks originating from the collision at the beamspot and producing clusters at the pixel sensors in two detector layers.
   }
@@
   \caption{
-    Left: Longitudial view of the current design of the CMS tracker detector for the LH-LHC phase. The TEPX consists of the last 4 disks on each side at $|z|$>1700 mm.
-    Right: Transverse view of one TEPX disk showing the layout of the sensors in each of the 5 rings.
+    Left: Longitudial view of the current design of the CMS tracker detector for the HL-LHC phase. The TEPX consists of the last 4 disks on each side at $|z|>$ 1700 mm.
+    Right: Transverse view of one TEPX disk showing the layout of the sensors in each of the 5 rings \cite{Klein:2017nke}.
   }
@@
 \item
-For the Run 2 luminosity mesurement, the student will perform the studies for the selection of good modules for the calculation of the luminosity using the PCC method.
+For the Run 2 luminosity mesurement, the student will perform the studies for the selection of good modules for calculating luminosity using the PCC method.
 From past performance of this algorithm it is expected that this measurement will give one of the best linearity and stability systematic uncertainties for the integrated luminosity value.
@@
 For the development of the HL-LHC upgrade system, we expect to produce a Technical Design Report (TDR) with the proposed design and algorithms to use the TEPX detector.
-This document will be published in the CERN document server (CDS) and submitted the LHC committee for the approval of the required funding for the construction and operation of the system.
+This document will be published in the CERN document server (CDS) and submitted to the LHC committee for approval of required funding for the construction and operation of the system.
 \end{itemize}
 
-Also, the student will become part of an international experiment and is expected to present his results at national or international scientific conferences.
+Also, the student will become a part of an international experiment and is expected to present his results at national or international scientific conferences.
 
@@
 \item {\bf Semester 1 (2019-2)}:
-  \SubItem{ Readings on Standard Model theory}
+  \SubItem{ Readings on Standard Model of particle physics theory}
   \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
@@
 \item {\bf Semester 5 (2021-2)}:
-  \SubItem{ Publication of the TDR document in CDS and submission to the LHCC review}
+  \SubItem{ Publication of the TDR document in CDS and submission to the LHCC for review}
   \SubItem{ Presentation at national or international conferences of the TEPX upgrade studies}
@@
 \item {\bf Semester 7 (2022-2)}:
-  \SubItem{ Publicaiton of the Run 2 data luminosity measurement in a peer reviewed journal}
+  \SubItem{ Publication of the Run 2 data luminosity measurement in a peer reviewed journal}
 
 \item {\bf Semester 8 (2023-1)}: 
-  \SubItem{ Presentations at national or international conferences of both the Run 2 luminosity measurement}
+  \SubItem{ Presentations at national or international conferences for both the Run 2 luminosity measurement and TEPX luminometer for HL-LHC}
   \SubItem{ Writing of the Ph.D thesis}

### 2021-05-13 project_ashish_monograph/CMS.tex
progress

@@
 \label{sec:cms}
-(describe the experiment in general, its discovery, mention the international collaboration)
+(describe the experiment in general, its discovery, mention the international collaboration) \\
+
+\onehalfspacing Compact Muon Solenoid (CMS) is one of the major experiment at CERN's Large Hadron Collider (LHC) that have been built to search for new physics.
+CMS is designed to detect new particles produced in the LHC's high energy proton-proton and heavy-ion (Lead, Xenon) collisions.
+CMS will also measure the properties (mass, decay width, coupling) of already discovered particles like quarks and leptons with unprecedented precision and will be looking to discover completely new, beyond standard model of particle physics phenomena which will help us to get a better understanding of our Universe and may confirm or rule out multiverse hypothesis.
+This experiment has already confirmed the discovery of the most important particle in SM, the Higgs boson which gives mass to all bosons and fermions via electroweak symmetry breaking mechanism.
+It has also detected the decay of Higgs boson to a pair of photons, W bosons, bottom quarks and muons.
+\\
+
+The CMS experiment is one of the largest international scientific collaborations in history, involving 4300 particle physicists, engineers, technicians, students and support staff from 179 universities and institutes in 41 countries.
+\\
 
 \subsection{CMS detector}
-(describe the detector components and what they do)
+(describe the detector components and what they do) \\
+
+The CMS detector is build around a large superconducting solenoid magnet and has a cylindrical shape with many concentric layers where various components of this detector are placed.
+It is placed at one of the collision points around the LHC ring and consists of Silicon tracker, Electromagnetic calorimeter, Hadron calorimeter and Muon chambers as shown in the left part of Fig.
+4.
+\\
+
+The large solenoid magnet bend charged particles and studying the path taken by these charged particles produced in proton-proton collisions using Silicon pixel detector (innermost part of CMS tracker) as they fly away from the interaction point, we can identify the charge of a particle as positive and negative charged particle tracks bend in opposite directions by the magnetic field and can also be used to calculate the momentum of the charged particle using curvature of the track as shown in the right part of Fig.
+4.
+\\
+
+Energies of various particles produced in the collision is measured by calorimeters.
+The Electromagnetic Calorimeter measures the energy of electrons and photons while the Hadron Calorimeter measures energy of hadrons which are particle made up of quarks and gluons.
+\\
+
+The Muon chambers are used to detect muons that are charged particles just like electrons but 206 times heavier.
+Muons can travel several metres without interacting thats why muon chambers are placed at the periphery of the CMS experiment.
+Muons are important particles to detect because they are produced in the decay of new particles and are helpful in exploring physics beyond SM.
 
@@
   \centering
-  \includegraphics[width=0.6\columnwidth]{./cms12.png}
-  \caption{Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimeter, superconducting solenoid and muon chambers \cite{Chatrchyan:2008aa}.}
-  \label{fig:CMS}
+  \includegraphics[width=1\columnwidth]{./cmsdetector_merged.png}
+  \caption{Left: 3D design of CMS detector showing various concentric layers.
+Right: \onehalfspacing Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimete##r, superconducting solenoid and muon chambers \cite{Chatrchyan:2008aa}}
+  \label{fig:CMSdetector}
 \end{figure}
@@
 \subsection{The Pixel detector}
+
+The pixel detector is the innermost of CMS tracker that contains 60 million pixels and these pixels assist in tracking the paths of particles emerging from the collision point.
+It is the nearest detector to the beam pipe and so will be vital in reconstructing the tracks of very short-lived particles.
+As it is very close to the collision point which means that the number of particles passing through is huge, the rate of particles received at 8cm from the beam line will be around 10 million particles per square centimetre per second.
+This feature is used to calculate the instantaneous luminosity $(L_{inst})$ by counting the number of pixel clusters which are collection of pixels hit by a track.
+The pixel detector is able to disentangle and reconstruct all the tracks left by the particles coming from the interaction point and has a long duration of 10 years.
+\\
+
+The CMS Run 2 pixel detector consists of four concentric barrel layers (L1-L4) at radii of 29, 68, 109 and 160 mm and three disks (D1-D3) on each end at distances of 291, 396, and 516 mm from the center of the detector.
+It is built from 1856 segmented silicon sensor modules, where 1184 modules are used in the barrel pixel detector (BPIX) and 672 modules are used for the forward disks (FPIX).
+\\
+
+Each layer of the pixel detector is spilt into tiny square segments with each segment containing a silicon sensor having dimensions 100$\mu$m $\times$ 150$\mu$m as shown in the right part of Fig.
+5.
+When a charged particle passes through this silicon sensor, it transfers energy to silicon atoms which causes electrons to be ejected from it creating electron-hole pairs.
+Each pixel uses an electric current to collect these charges on the pixel surface as a small electric signal.
+A electronic silicon chip is attached to each segment which amplifies the signal.
+The particle trajectory is deduced by knowing the hit pixels and as the pixel detector is made of two dimensional segments with four layers, we can create a three-dimensional picture of the path taken by the charged particle.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1 \columnwidth]{./pixeldetector_merged1.png}
+  \caption{Left: Layout of the CMS Run 2 pixel detector compared to the original detector layout, in longitudinal view.
+Right: pixel detector diagram showing size of Silicon sensor, readout chip and data buffers.}
+  \label{fig:LHC}
+\end{figure}

### 2021-05-13 project_ashish_monograph/LHC.tex
progress

@@
 \label{sec:lhc}
-(describe the accelerator complex, proton bunches, c.m. energy, all experiments, run periods, inst. and integrated lumi, Run 3 and HL-LHC plans)
+(describe the accelerator complex, proton bunches, c.m. energy, all experiments, run periods, inst. and integrated lumi, Run 3 and HL-LHC plans) \\
+
+\onehalfspacing CERN accelerator complex is a progression of machines namely Linac 2, Proton Synchrotron Booster (PSB), Proton Synchrotron (PS), Super Proton Synchrotron (SPS) and Large Hadron Collider (LHC) as shown in Fig.
+1 that accelerate particles mainly protons to increasingly higher energies of 50 MeV, 1.4 GeV, 25 GeV, 450 GeV and 14 TeV respectively.
+Each machine is used to increase the energy of particle before the beam is injected into to the next machine.
+Linear accelerator (Linac2) is the starting point for protons used in various experiments at CERN.
+After proton energy reaches 50 MeV, protons enter PSB which further increases its energy before they are injected into PS which takes up its energy to 25 GeV.
+After reaching 25 GeV, protons enter SPS which further increases its energy to 450 GeV.
+The protons are finally transferred to two beam pipes of LHC kept at very high vacuum.
+\\
+
+The Large Hadron Collider (LHC) is the most powerful particle accelerator in the world primarily build to collide protons and heavy ions at 7, 8, 13 and 14 TeV during different LHC run period.
+The LHC consists of a 27 kilometre ring of superconducting magnets producing strong magnetic field which is used to guide particle beams along the LHC ring.
+Proton beam made up of bunches travelling in opposite directions kept in two ultrahigh vacuum tubes are accelerated close to the speed of light using time dependent electric field produced by radiofrequency cavities before they collide at four interaction points along the LHC ring where ATLAS, ALICE, CMS and LHCb detectors are placed.
+\\
+
+The first proton beam was successfully maneuvered around the LHC ring in September 2008 that marked the beginning of Run 1 with proton beams colliding at 7-8 TeV center-of-mass energy and this run period ended in 2013.
+Run 2 started in 2015 with protons colliding at 13 TeV center-of-mass energy and continued till October 2018.
+Run 3 is expected to begin at the start of March 2022 and High Luminosity (HL)-LHC phase is expected to begin in mid-2027.
+Proton Synchroton (PS) is responsible for providing proton bunches spaced 7 metres (25 ns) apart with each bunch containing more than 100 billion protons.
+The maximum number of bunches reached with the beam preparation method used during Run 2 is 2556.
+The number of protons in the colliding bunches, time of separation between the bunches and effective area of the bunch which depend on the rms transverse bunch size along horizontal and vertical directions is one of the ways to calculate instantaneous luminosity (L_{inst}).
+\\
+
+Luminosity is a key performance parameter of an accelerator as it is a measure of number of collisions.
+Luminosity can be categorized into two types: instantaneous and integrated luminosity.
+Instantaneous luminosity is defined as the number of collisions occuring per second in per centimeter square area while integrated luminosity is obtained by integrating instantaneous luminosity over a time interval.
+Both are very important variables as they are used to obtain the number of collision events.
+During Run 1, peak value of LHC instantaneous luminosity was $0.77 \times 10^{34} \: cm^{-2} s^{-1} $ with $30 \: fb^{-1}$ integrated luminosity.
+During Run 2, LHC instantaneous luminosity reached a peak value of $1.58 \times 10^{34}  \: cm^{-2} s^{-1}$ with $150 \: fb^{-1}$ integrated luminosity as shown in Fig.
+2.
+At the end of Run 3, we expect to achieve an integrated luminosity  of $300 \:fb^{-1}$ while Phase 2 HL-LHC is expected to collect $3000 \:fb^{-1}$ of data as shown in Fig.
+3 thereby increasing luminosity by a factor of 10 beyond the LHC's design value.
+\\
 
@@
   \centering
-  \includegraphics[width=0.7\columnwidth]{./LHCcomplex.png}
-  \caption{Diagram of the LHC accelerator complex located in Geneva, Switzerland. Four interaction points are shown for the ALICE, ATLAS
-, LHCb, and CMS experiments.}
+  \includegraphics[width=0.8\columnwidth]{./LHCcomplex.png}
+  \caption{\onehalfspacing Diagram of the LHC accelerator complex located in Geneva, Switzerland. Four interaction points are shown for the ALICE, ATLAS, LHCb and CMS experiments.}
   \label{fig:LHC}
@@
   \centering
-  \includegraphics[width=0.8\columnwidth]{./HLLHCLumi.png}
-  \caption{Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and lumino
-sities. Points show instantaneous luminosity while the line shows luminosity accumulated \cite{collaborations2019report}.}
+  \includegraphics[width=1 \columnwidth]{./run1-2_lumi.png}
+  \caption{\onehalfspacing Left: Instantaneous luminosities for Run 1 and Run 2 period. Right: Integrated luminosities for Run 1 and Run 2 period.}
+  \label{fig:LHClumi}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.7 \columnwidth]{./HLLHCLumi.png}
+  \caption{ \onehalfspacing Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS1, LS2, LS3, LS4, LS5) of the LHC and luminosities.
+Red points show instantaneous luminosity $(L_{inst})$ while the blue line shows integrated luminosity.
+\cite{collaborations2019report}.}
   \label{fig:LHCPlans}

### 2021-05-13 project_ashish_monograph/PCC.tex
progress

@@
 \label{sec:pcc}
-(describe cluster reconstruction, the module selection/veto, cluster counting per bx, per LS,..)
+(describe cluster reconstruction, the module selection/veto, cluster counting per bx, per LS,..) \\
+
+Pixel cluster counting (PCC)  method is an offline technique for the calculation of instantaneous luminosity $(L_{inst})$ for any LHC run period by counting the number of pixel clusters in the pixel detector (innermost segment of the CMS tracker) in a zero bias event which requires that only two bunches cross at the CMS interaction point.
+The mean number of pixel clusters can be expressed in terms of mean number of pixel clusters per proton-proton interaction and the number of proton-proton interaction per bunch crossing that is also called pileup (PU).
+\\
+
+$<N_{cluster}>$ = $<N_{cluster/interaction}>$ (PU)  or (PU) = $\frac{<N_{cluster}>}{<N_{cluster/interaction}>}$ \\
+
+The instantaneous luminosity per bunch crossing L is proportional to the number of proton-proton (pp) interactions per bunch crossing (pileup) and the proportionality constant is the ratio of  LHC orbit frequency f and the pp interaction cross section $\sigma_{interaction}$.
+\\
+
+L = $\frac{f}{\sigma_{interaction}}$ (PU)  \\
+
+L = $\frac{<N_{cluster}> \: f }{<N_{cluster/interaction}> \: \sigma_{interaction}}$ \\
+
+The PCC visible cross section $\sigma_{vis}$ which is a calibration constant between pixel clusters rate and luminosity can be defined as \\
+
+$\sigma_{vis}$ = $<N_{cluster/interaction}>$  $\sigma_{interaction}$
+
+Thus, instantaneous luminosity per bunch crossing is given by \\
+
+L = $\frac{<N_{cluster}> \: \sigma_{interaction} \: f }{ \:\sigma_{vis} \: \sigma_{interaction}}$ \\
+
+L = $\frac{<N_{cluster}> \:\: f}{\sigma_{vis}}$ \\
+
+The PCC visible cross section $\sigma_{vis}$ is determined using van der meer scan method which is described in section 5.
+Cluster counting can be done over different time periods like 1 bunch crossing (25 ns), 1 Lumi section (23.36 s), 4 Lumi nibble (1.46 s) and similarly instantaneous luminosity can be calculated over these time periods using PCC method.
+\\
+
+Specific techniques are employed for the reconstruction of clusters in the pixel detector and all reconstructed clusters are used for counting to calculate the instantaneous luminosity.
+Algorithm used for finding clusters starts by looking for pixels whose signal to noise ratio is more than 6 and then merge adjacent pixel.
+These algorithms estimates cluster position in two directions and cluster charge.
+A cluster is a set of adjacent pixels and only pixels above certain threshold charge are considered.
+Position of a cluster in X and Y direction are obtained by fitting X and Y prpjections to templates that are estimates for cluster shapes.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.6\columnwidth]{./pixel_reco.png}
+  \caption{ \onehalfspacing }
+  \label{fig:CMS}
+\end{figure}

### 2021-05-13 project_ashish_monograph/bkg.tex
progress

@@
 \label{sec:bkg}
-(background in vdM, afterglow backgrounds in Physics, subtraction of these)
+(background in vdM, afterglow backgrounds in Physics, subtraction of these) \\
+
+N= \sigma \:L + N_{background} \\
+L = $ \int L_{inst} \: dt = \int \frac{R(t)}{\sigma_{vis}} \:dt $  \\ \sigma = \sigma_{interaction} (\sqrt{s}) \: A \:\epsilon\\
+
+N: total number of event including signal and background. \\
+$\sigma_{vis}$: visible cross section for PCC.\\
+$L_{inst}$: instantaneous luminosity.\\
+$N_{background}$: Number of background events \\
+
+The pixel cluster counting (PCC) method produces a small out-of-time response (OOTR, or afterglow).\\
+Type 1: fake hits in the bunch crossing after the colliding bunches (signal charge spillover).\\
+Type 2: Activated material in the detector due to the large radiation doses, exponentially decays for many bunch crossings.\\
+Afterglow effects are tiny in the case of tracklets (2x and 3x coincidences).\\
+
+Due to both the late-arriving particles and energy originating from activated detector material, the pixel data need to be corrected for afterglow effects.
+This effect was studied in data taken using random triggers (triggers that fire randomly in bunch crossings spread over the whole LHC orbit except for the abort gap), considering the pixel cluster counts in bunch crossings after bunch trains.
+The resulting correction depends on the LHC filling scheme and for a typical 2011 fill with 1380 bunches corresponds to a subtraction of close to 2.8$\%$ of the integrated luminosity per luminosity section.
+\\
+
+The afterglow corrections for PCC during 2017 run are in the range 2-5 $\%$ for the Type 1 corrections and 2-3 $\%$ averaged over all active bunches for the Type 2 corrections.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./SingleBunchAfterglow.png}
+  \caption{Afterglow effect produced by a single colliding bunch.}
+  \label{fig:LHC}
+\end{figure}
+
+Figure 7 shows the afterglow noise induced by one colliding bunch.
+Since it is normalized to 1 at the first bin it means the first bin is the colliding bunch.
+The values at bins $>$ 1 are the cluster counts observed for bunches after the colliding bunch divided by the cluster counts observed by the colliding bunch.
+There are three parts to this distribution: \\
+
+bin 1: colliding bunch \\
+
+bin 2 (empty bunch): bunch after colliding bunch, noise observed is due to electronics signal on same pixels from colliding bunch. This is called Type 1. \\
+
+bins $>$ 2 (empty bunches): noise observed is due to "albedo" which is material activated by the radiation of the collisions, it decays exponentially with time just like radioactive material.
+It produces secondary particles which create hits late in time.
+This is called Type 2.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./afterglow.png}
+  \caption{Results of the pixel afterglow 'deconvolution fit'}
+  \label{fig:LHC}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.6\columnwidth]{./PCC_background.png}
+  \caption{ \onehalfspacing \cite{}.}
+  \label{fig:CMS}
+\end{figure}

### 2021-05-13 project_ashish_monograph/results.tex
progress

\section{Results}
\label{sec:results}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./316993.png}
  \caption{Top: Bunch crossing id (bcid) and PCC lumi as a function of lumi section. Bottom: PCC lumi as a function of lumi section (late RunD veto list is used) for run 2018A.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./ls_lumi.png}
  \caption{PCC luminosity as a function of lumi section.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./runs.png}
  \caption{PCC luminosity as a function of run number.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./2018A_lumiratio.png}
  \caption{Luminosity ratios for different subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018A.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./ProfileXcombined_2018A.png}
  \caption{X Profile of luminosity ratio vs lumi section graph showing luminosity fraction as a function of lumi section.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./319270.png}
  \caption{Top: Bunch crossing id (bcid) and PCC lumi as a function of lumi section. Bottom: PCC lumi as a function of lumi section (late RunD veto list is used) for run 2018B.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./ls_lumi_2018B.png}
  \caption{PCC luminosity as a function of lumi section.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./runs_2018B.png}
  \caption{PCC luminosity as a function of run number.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./2018B_lumiratio.png}
  \caption{Luminosity ratios for different subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018B.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./ProfileXcombined_2018B.png}
  \caption{X Profile of luminosity ratio vs lumi section graph showing luminosity fraction as a function of lumi section.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./320061.png}
  \caption{Top: Bunch crossing id (bcid) and PCC lumi as a function of lumi section. Bottom: PCC lumi as a function of lumi section (late RunD veto list is used) for run 2018C.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./ls_lumi_2018C.png}
  \caption{PCC luminosity as a function of lumi section.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./runs_2018C.png}
  \caption{PCC luminosity as a function of run number.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./2018C_lumiratio.png}
  \caption{Luminosity ratios for different subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018C. }
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5\columnwidth]{./ProfileXcombined_2018C.png}
  \caption{X Profile of luminosity ratio vs lumi section graph showing luminosity fraction as a function of lumi section.}
  \label{fig:CMS}
\end{figure}

### 2021-05-13 project_ashish_monograph/syst.tex
progress

@@
 (main systematics: vdM, non-linearity, stability, check others in the PAS)
+
+Systematic uncertainties Length scale, Orbit drift, x-y correlations, Beam-beam deflection, dynamic $\beta^*$, Beam current calibration, Ghosts and satellites, Scan to scan variation, Bunch to bunch variation, Cross-detector consistency, Afterglow effects, Linearity, CMS deadtime.
+\\
+
+1.
+Length Scale Calibration:  Value of the separation derived from currents in the corrector magnets, This is calibrated against central tracking system, Compare luminous region information (vertices distribution) versus nominal separation.
+\\
+
+2.
+Emittance growth: Beams size are known to increase in size during the fill.
+Effect is sizable during the ~30 minutes, Bias almost negligible if emittance grows linearly with time and if measurement are made in between X and Y scans.
+\\
+
+3.
+Orbit Drift: The beams can slowly drift in the transverse plane; effect is typically small but can be harmful in some cases.
+Drift of the orbit estimated by BPM measurements taken between scans and extrapolated to IP \\
+
+4.
+XY-Correlations: The VdM scan method assumes that the bunch proton density function is factorizable into independent x- and y-dependent terms.
+However, this assumption is not strictly valid, and can lead to a biased estimate of the beam overlap area.
+In order to measure this effect, special beam imaging scans are conducted.
+In these scans, the measured vertex position distributions are used to derive the bunch proton densities, which can then be used to estimate a correction to the visible cross section \\
+
+5. Beam-Beam Effects: Dipolar kick (beam-beam deflection):
+
+ Repulsive force deflects beams affecting nominal separation depends on the separation itself, the beam width and the current
+
+ Quadrupolar (de)focusing (dynamic b):  Effective beam width modified depending on the separation Peak luminosity (rate) affected \\

### 2021-05-13 project_ashish_monograph/upgrade.tex
progress

@@
 \label{sec:tepx}
-(describe the TEPX detector design, algorithms clusters/coincidences, stat precision, linearity)
+(describe the TEPX detector design, algorithms clusters/coincidences, stat precision, linearity)\\
+
+The High Luminosity (HL)-LHC will increase instantaneous luminosity to unprecedented values of $7 \times 10^{34} cm^{-2} s^{-1}$ which corresponds to 200 proton-proton collisions per bunch crossing (pileup).
+Run 2 pixel detector will not be able to handle the extreme radiation environment, resolve nearby particle tracks and operate properly for high pileup values.
+That is why Run 2 pixel detector will be replaced by a new pixel detector which will be composed of three subdetectors: tracker barrel pixel detector (TBPX), tracker forward pixel detector (TFPX) and tracker endcap pixel detector (TEPX).
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.6\columnwidth]{./up.png}
+  \caption{\onehalfspacing Left: View in the x-y plane of the double disk structure of one TEPX disk.
+The sensors in blue and red correspond to the two double disks at slightly different z positions.
+Right: Example of two- and threefold coincidence regions on a portion of a single TEPX disk \cite{}.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.6\columnwidth]{./up1.png}
+  \caption{ \onehalfspacing Left: A layout of the CMS Phase-2 inner tracker with the location of TEPX Disk 4, Ring 1 highlighted in dark red. Right: The x-y view of TEPX disk 4, ring 1 \cite{}.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.6\columnwidth]{./up2.png}
+  \caption{ \onehalfspacing Schematic view for one quarter of the tracker, illustrating the location of TEPX. \cite{}.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.6\columnwidth]{./tepx.png}
+  \caption{ \onehalfspacing Sketch of the TFPX and TEPX layouts, showing one quarter of the detector in r-z view.
+Modules of type 1 $\times$ 2 are shown in green, while 2 $\times$ 2 modules are represented in orange.
+The two layers of modules that populate the front- and back-side of a disc and that overlap in $r-\phi$ can be seen by zooming into the figure in the online version.
+\cite{}.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5 \columnwidth]{./xydisc.png}
+  \caption{ \onehalfspacing Sketch of the TEPX Disk layouts in x-y view. Modules of type 1 $\times$ 2 are shown in green, while 2 $\times$ 2 modules are represented in orange.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_totalcluster_linearity.png}
+  \caption{Simulated mean number of clusters for all entire TEPX detector as a function of pileup. A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_totalcluster_residuals.png}
+  \caption{Deviation from linearity for clusters for entire TEPX detector.
+The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.
+Non-linearity is within 1 \% for entire pileup range.
+Pileup 200 corresponds to High Luminosity (HL)-LHC environment.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_mean_number_of_clusters___bx_Linearity.png}
+  \caption{Simulated mean number of clusters for TEPX Disk 4 Ring 1 as a function of pileup.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_mean_number_of_clusters___bx_Linearity_residuals.png}
+  \caption{Deviation from linearity for clusters for TEPX Disk 4 Ring 1.
+The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_clusters_negativez_Linearity.png}
+  \caption{Simulated mean number of clusters for -z side TEPX disks as a function of pileup.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_clusters_per_disk_negativez_Linearity_residuals.png}
+  \caption{Deviation from linearity for clusters for -z side TEPX disks.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_clusters_per_disk_positivez_linearity.png}
+  \caption{Simulated mean number of clusters for +z side TEPX disks as a function of pileup.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_clusters_per_disk_postivez_Linearity_residuals.png}
+  \caption{Deviation from linearity for clusters for +z side TEPX disks.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_clusters_per_ringDisk4_Linearity.png}
+  \caption{Simulated mean number of clusters for TEPX Disk 4 all rings as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_clusters_per_ringDisk4_Linearity_residuals.png}
+  \caption{Deviation from linearity for clusters for TEPX Disk 4 all rings. Non-linearity is within $1\%$ for all rings over entire pileup range.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_mean_number_of_coincidences___bx_Linearity.png}
+  \caption{Simulated mean number of coincidences in $\phi$ and r for all entire TEPX detector as a function of pileup.
+A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_mean_number_of_coincidences___bx_Linearity_residuals.png}
+  \caption{Deviation from linearity for coincidence in $\phi$ and r for entire TEPX detector. The non-linearity is calculated as
+the relative difference between the data points and the values of the fit function at the respective pileup value.
+Non-linearity is within 1 \% for entire pileup range. Pileup 200 corresponds to High Luminosity (HL)-LHC
+environment.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_per_disk__pz_side_mean_number_of_coincidences___bx_Linearity.png}
+  \caption{Simulated mean number of coincidences in $\phi$ and r for +z side TEPX disks as a function of pileup.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_per_disk__pz_side_mean_number_of_coincidences___bx_Linearity_residuals.png}
+  \caption{Deviation from linearity for coincidences in $\phi$ and r for +z side TEPX disks.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_per_disk,_-z_side_Linearity.png}
+  \caption{Simulated mean number of coincidences in $\phi$ and r for -z side TEPX disks as a function of pileup.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_per_disk,_-z_side_Linearity_residuals.png}
+  \caption{Deviation from linearity for coincidences in $\phi$ and r for -z side TEPX disks.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_mean_number_of_coincidences___bx_Linearity.png}
+  \caption{Simulated mean number of coincidences in $\phi$ and r for TEPX Disk 4 Ring 1 as a function of pileup.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_mean_number_of_coincidences___bx_Linearity_residuals.png}
+  \caption{Deviation from linearity for coincidences in $\phi$ and r for TEPX Disk 4 Ring 1. The non-linearity is calculated as the
+relative difference between the data points and the values of the fit function at the respective pileup value.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_coincidences_in_phi__pz_side_mean_number_of_coincidences___bx_Linearity.png}
+  \caption{Simulated mean number of coincidences in $\phi$ for TEPX +z side Disk 4 Ring 1 as a function of pileup.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_coincidences_in_phi__pz_side_mean_number_of_coincidences___bx_Linearity_residuals.png}
+  \caption{Deviation from linearity for coincidences in $\phi$ for TEPX +z side Disk 4 Ring 1.
+The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_coincidences_in_r__pz_side_mean_number_of_coincidences___bx_Linearity.png}
+  \caption{Simulated mean number of coincidences in r for TEPX +z side Disk 4 Ring 1 as a function of pileup.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_coincidences_in_r__pz_side_mean_number_of_coincidences___bx_Linearity_residuals.png}
+  \caption{Deviation from linearity for coincidences in r for TEPX +z side Disk 4 Ring 1.
+The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_in_phi_per_ring_mean_number_of_coincidences___bxDisk4_Linearity.png}
+  \caption{Simulated mean number of coincidences in $\phi$ for +z side TEPX Disk 4 per ring as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_in_phi_per_ring_mean_number_of_coincidences___bxDisk4_Linearity_residuals.png}
+  \caption{Deviation from linearity for coincidences in $\phi$ for +z side TEPX Disk 4 per ring. Non-linearity is within 1\% for all rings over entire pileup range.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_inphi_per_ring__Disk_-4_Linearity.png}
+  \caption{Simulated mean number of coincidences in \phi for -z side TEPX Disk 4 per ring as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_inphi_per_ring__Disk_-4_Linearity_residuals.png}
+  \caption{Deviation from linearity for coincidences in $\phi$ for -z side TEPX Disk 4 per ring. Non-linearity is within 1\% for all rings over entire pileup range.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_in_r_per_ring__Disk_-4_Linearity.png}
+  \caption{Simulated mean number of coincidences in r for -z side TEPX Disk 4 per ring as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_in_r_per_ring__Disk_-4_Linearity_residuals.png}
+  \caption{Deviation from linearity for coincidences in $\phi$ for -z side TEPX Disk 4 per ring. Non-linearity is within 1\% for all rings over entire pileup range.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_in_r_per_ring_mean_number_of_coincidences___bxDisk4_Linearity.png}
+  \caption{Simulated mean number of coincidences in r for +z side TEPX Disk 4 per ring as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_in_r_per_ring_mean_number_of_coincidences___bxDisk4_Linearity_residuals.png}
+  \caption{Deviation from linearity for coincidences in r for +z side TEPX Disk 4 per ring. Non-linearity is within 1\% for all rings over entire pileup range.}
+  \label{fig:CMS}
+\end{figure}

### 2021-05-13 project_ashish_monograph/vdM.tex
progress

@@
 \label{sec:vdm}
+Van der Meer (VdM) scans are done to calculate the visible cross section $\sigma_{vis}$ which is a calibration constant in the relation between rate of a quantity (clusters, coincidences) read out by the detector and the instantaneous luminosity.
+\\
+
+The instantaneous luminosity when the crossing angle between the colliding bunches is negligible and bunches collide head on is given by the following integral, \\
+
+L = N_1 N_2 f \int^{+\infty}_{-\infty} \rho_1(x,y) \rho_2(x+\Delta x, y+ \Delta y) dx dy \\
+
+where $N_1, N_2$ are the number of protons in the colliding bunches, f is the LHC orbit frequency whose value is 11246Hz,  $\rho_1(x,y)$ and $\rho_2(x+\Delta x,y+\Delta y)$ are the two dimensional particle density distribution functions for each colliding bunch separated by $\Delta x$ and $\Delta y$.
+\\
+
+Assuming complete factorization of particle density distribution function along x and y directions for both the bunches, we get \\
+
+L = N_1 N_2 f \int^{+\infty}_{-\infty} \rho_{1x}(x) \rho_{2x}(x+\Delta x)  dx   \int^{+\infty}_{-\infty} \rho_{1y}(y) \rho_{2y}(y+\Delta y)  dy \\
+
+where $\rho_1(x,y) = \rho_{1x}(x,y) \rho_{1y} (x,y)$ and $\rho_2(x+\Delta x,y + \Delta y) = \rho_{2x}(x+\Delta x,y+\Delta y) \rho_{2y} (x+\Delta,y+\Delta y)$ \\
+
+The VdM scan determines the beam overlap integrals $\int \rho_{x1} (x) \rho_{x2} (x+\Delta x) dx$ and  $\int \rho_{y1}(y) \rho_{y2} (y+\Delta y) dy$ by measuring pixel clusters rate as a function of bunch separation $\Delta x$ and $\Delta y$ along x and y directions as shown in Fig.
+7.
+\\
+
+\int \rho_{x1} (x) \rho_{x2} (x+\Delta x) dx = \frac{R_x(0)}{\int R_x(\Delta x)dx} \\
+
+\int \rho_{y1} (y) \rho_{y2} (y + \Delta y) dy = \frac{R_y(0)}{\int R_y(\Delta y)dy} \\
+
+Bunch overlap widths $\Sigma_x$ and $\Sigma_y$ along x and y directions are defined as \\
+
+\Sigma_x = \frac{1}{\sqrt{2 \pi}} \frac{\int R_x(\Delta x)dx}{R_x(0)} \\
+
+\Sigma_y =  \frac{1}{\sqrt{2 \pi}} \frac{\int R_y(\Delta y)dy}{R_y(0)} \\
+
+$\Sigma_x \Sigma_y = \frac{1}{2 \pi} \frac{\int R_x(\Delta x)dx \int R_y(\Delta y) dy}{R_x(0) R_y(0)}$  is the bunch overlapping area as shown in Fig. 8 by the red region.\\
+
+Thus, the expression for instantaneous luminosity is given by \\
+
+L = $\frac{N_1 N_2 f}{2\pi \Sigma_x \Sigma_y}$ \\
+
+and the PCC visible cross section defined in terms of beam parameters and rate is given by \\
+
+\sigma_{vis} = \frac{2 \pi \Sigma_x \Sigma_y R}{N_1 N_2} \\
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.7\columnwidth]{./vdmfit.png}
+  \caption{ \onehalfspacing Example vdM scans for PCC for BCID 41, from the last scan pair in fill 4954, showing the rate normalized by the product of beam currents as a function of the beam separation $\Delta x$ and $\Delta y$ in the x (left) and y (right) direction, and the fitted curves.
+The purple curve shows the overall double-Gaussian fit, while the blue, yellow, and green curves show the first and second Gaussian components and the constant component, respectively.
+The lower panels display the difference between the measured and fitted values
+divided by the statistical uncertainty\cite{}.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=\columnwidth]{./vdm_image.png}
+  \caption{ \onehalfspacing }
+  \label{fig:CMS}
+\end{figure}

### 2021-05-14 project_ashish_monograph/CMS.tex
progress

@@
   \caption{Left: 3D design of CMS detector showing various concentric layers.
-Right: \onehalfspacing Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimete##r, superconducting solenoid and muon chambers \cite{Chatrchyan:2008aa}}
+Right: \onehalfspacing Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimete##r, superconducting solenoid and muon chambers.
+\cite{Chatrchyan:2008aa}}
   \label{fig:CMSdetector}

### 2021-05-14 project_ashish_monograph/PCC.tex
progress

@@
 
-The instantaneous luminosity per bunch crossing L is proportional to the number of proton-proton (pp) interactions per bunch crossing (pileup) and the proportionality constant is the ratio of  LHC orbit frequency f and the pp interaction cross section $\sigma_{interaction}$.
+The instantaneous luminosity per bunch crossing L is proportional to the number of proton-proton (pp) interactions per bunch crossing (pileup) and the proportionality constant is the ratio of  LHC orbit frequency f and the pp interaction cross section $\sigma_{interaction}(\sqrt{s})$ where s is the proton-proton collision center-of-mass energy.
 \\
@@
 
-L = $\frac{<N_{cluster}> \: f }{<N_{cluster/interaction}> \: \sigma_{interaction}}$ \\
+L = $\frac{<N_{cluster}> \: f }{<N_{cluster/interaction}> \: \sigma_{interaction}(\sqrt{s})}$ \\
 
@@
 
-$\sigma_{vis}$ = $<N_{cluster/interaction}>$  $\sigma_{interaction}$
+$\sigma_{vis}$ = $<N_{cluster/interaction}>$  $\sigma_{interaction}(\sqrt{s})$ \\
 
-Thus, instantaneous luminosity per bunch crossing is given by \\
+\newpage Thus, instantaneous luminosity per bunch crossing is given by \\
 
-L = $\frac{<N_{cluster}> \: \sigma_{interaction} \: f }{ \:\sigma_{vis} \: \sigma_{interaction}}$ \\
+L = $\frac{<N_{cluster}> \: \sigma_{interaction}(\sqrt{s}) \: f }{ \:\sigma_{vis} \: \sigma_{interaction}(\sqrt{s})}$ \\
 

### 2021-05-14 project_ashish_monograph/bkg.tex
progress

@@
-\section{Backgrounds}
+\newpage \section{Backgrounds}
 \label{sec:bkg}
@@
 N= \sigma \:L + N_{background} \\
-L = $ \int L_{inst} \: dt = \int \frac{R(t)}{\sigma_{vis}} \:dt $  \\ \sigma = \sigma_{interaction} (\sqrt{s}) \: A \:\epsilon\\
+
+L = $ \int L_{inst} \: dt = \int \frac{R(t)}{\sigma_{vis}} \:dt $  \\
+
+\sigma = \sigma_{interaction} (\sqrt{s}) \: A \:\epsilon\\
 
 N: total number of event including signal and background. \\
-$\sigma_{vis}$: visible cross section for PCC.\\
-$L_{inst}$: instantaneous luminosity.\\
+
+$R(t) = \frac{d}{dt} <N_{cluster}>$ is the time dependent cluster rate. \\
+
 $N_{background}$: Number of background events \\
 
-The pixel cluster counting (PCC) method produces a small out-of-time response (OOTR, or afterglow).\\
+$\sigma_{vis}$: PCC visible cross section.\\
+
+$\sigma_{interaction}$ : proton-proton interaction cross section. \\
+
+s: center of mass energy of colliding protons. \\
+
+A: acceptance of the pixel detector. \\
+
+$\epsilon$ : efficiency of the pixel detector. \\
+
+$L_{inst}$: instantaneous luminosity.\\
+
+The pixel cluster counting (PCC) method produces a small out-of-time response (OOTR, or afterglow) that has two types.\\
+
 Type 1: fake hits in the bunch crossing after the colliding bunches (signal charge spillover).\\
+
 Type 2: Activated material in the detector due to the large radiation doses, exponentially decays for many bunch crossings.\\
+
 Afterglow effects are tiny in the case of tracklets (2x and 3x coincidences).\\
@@
 
-Figure 7 shows the afterglow noise induced by one colliding bunch.
+Fig.
+7 shows the afterglow noise induced by one colliding bunch.
 Since it is normalized to 1 at the first bin it means the first bin is the colliding bunch.

### 2021-05-14 project_ashish_monograph/results.tex
progress

@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./316993.png}
+  \includegraphics[width=0.52\columnwidth]{./316993.png}
   \caption{Top: Bunch crossing id (bcid) and PCC lumi as a function of lumi section. Bottom: PCC lumi as a function of lumi section (late RunD veto list is used) for run 2018A.}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./ls_lumi.png}
+  \includegraphics[width=0.52\columnwidth]{./ls_lumi.png}
   \caption{PCC luminosity as a function of lumi section.}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./runs.png}
+  \includegraphics[width=0.52\columnwidth]{./runs.png}
   \caption{PCC luminosity as a function of run number.}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./2018A_lumiratio.png}
-  \caption{Luminosity ratios for different subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018A.}
+  \includegraphics[width=0.52\columnwidth]{./2018A_lumiratio.png}
+  \caption{Luminosity ratios for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018A.}
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./ProfileXcombined_2018A.png}
-  \caption{X Profile of luminosity ratio vs lumi section graph showing luminosity fraction as a function of lumi section.}
+  \includegraphics[width=0.52\columnwidth]{./ProfileXcombined_new.png}
+  \caption{X Profile of luminosity ratio vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section.}
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./319270.png}
+  \includegraphics[width=0.52\columnwidth]{./319270.png}
   \caption{Top: Bunch crossing id (bcid) and PCC lumi as a function of lumi section. Bottom: PCC lumi as a function of lumi section (late RunD veto list is used) for run 2018B.}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./ls_lumi_2018B.png}
+  \includegraphics[width=0.52\columnwidth]{./ls_lumi_2018B.png}
   \caption{PCC luminosity as a function of lumi section.}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./runs_2018B.png}
+  \includegraphics[width=0.52\columnwidth]{./runs_2018B.png}
   \caption{PCC luminosity as a function of run number.}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./2018B_lumiratio.png}
-  \caption{Luminosity ratios for different subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018B.}
+  \includegraphics[width=0.52\columnwidth]{./2018B_lumiratio.png}
+  \caption{Luminosity ratios for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018B.}
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./ProfileXcombined_2018B.png}
-  \caption{X Profile of luminosity ratio vs lumi section graph showing luminosity fraction as a function of lumi section.}
+  \includegraphics[width=0.5\columnwidth]{./ProfileXcombinedB_new.png}
+  \caption{X Profile of luminosity ratio vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section.}
   \label{fig:CMS}
@@
   \includegraphics[width=0.5\columnwidth]{./2018C_lumiratio.png}
-  \caption{Luminosity ratios for different subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018C. }
+  \caption{Luminosity ratios for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018C. }
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./ProfileXcombined_2018C.png}
-  \caption{X Profile of luminosity ratio vs lumi section graph showing luminosity fraction as a function of lumi section.}
+  \includegraphics[width=0.5\columnwidth]{./ProfileXcombinedC_new.png}
+  \caption{X Profile of luminosity ratio vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section.}
   \label{fig:CMS}

### 2021-05-14 project_ashish_monograph/syst.tex
progress

--- 2021-04-30 project_ashish_monograph/syst.tex
@@
 \label{sec:syst}
-(main systematics: vdM, non-linearity, stability, check others in the PAS)
+(main systematics: vdM, non-linearity, stability, check others in the PAS) \\
+
+Systematic uncertainties in the bunch overlap widths along x and y directions measured during VdM scans can arise from length scale calibration, orbit drift, x-y correlations of bunch proton density function, emittance growth, bunch-bunch deflection, dynamic $\beta$ which tells us whether bunches are narrow or wide, bunch current calibration, ghosts and satellites, scan to scan variation, bunch to bunch variation, cross-detector consistency, afterglow effects, linearity and CMS deadtime.
+\\
+
+1.
+Length scale calibration:  Value of the separation derived from currents in the corrector magnets, calibrated against central tracking system and compare luminous region information (vertices distribution) versus nominal separation.
+\\
+
+2.
+Emittance growth: Bunches size are known to increase in size during the fill.
+Effect is sizable during the ~30 minutes, Bias almost negligible if emittance grows linearly with time and if measurement are made in between X and Y scans.
+\\
+
+3.
+Orbit drift: The beams can slowly drift in the transverse plane.
+This effect is typically small but can be harmful in some cases.
+Drift of the orbit estimated by BPM measurements taken between scans and extrapolated to interaction point.
+\\
+
+4.
+xy-correlations: The VdM scan method assumes that the bunch proton density function is factorizable into independent x- and y-dependent terms which is not fully true and can lead to a biased estimate of the bunch overlap area.
+In order to measure this effect, special beam imaging scans are conducted.
+In these scans, the measured vertex position distributions are used to derive the bunch proton densities, which can then be used to estimate a correction to the visible cross section $\sigma_{vis}$.
+\\
+
+5. Non-linearity: \\
+
+6. Stability:  \\
+
+7. Bunch-Bunch Effects: \\
+
+Dipolar kick (bunch-bunch deflection): Repulsive force deflects beams affecting nominal separation depends on the separation itself, the beam width and the current. \\
+
+ Quadrupolar (de)focusing (dynamic $\beta$): Effective beam width is modified depending on the separation which in turn affects the peak luminosity (rate) value. \\

### 2021-05-14 project_ashish_monograph/upgrade.tex
progress

@@
-\section{The TEPX upgrade for HL-LHC}
+\newpage \section{The TEPX upgrade for HL-LHC}
 \label{sec:tepx}
-(describe the TEPX detector design, algorithms clusters/coincidences, stat precision, linearity)\\
+(describe the TEPX detector design, algorithms clusters/coincidences, D4R1 as HL-LHC luminometer, stat precision, linearity)\\
 
-The High Luminosity (HL)-LHC will increase instantaneous luminosity to unprecedented values of $7 \times 10^{34} cm^{-2} s^{-1}$ which corresponds to 200 proton-proton collisions per bunch crossing (pileup).
-Run 2 pixel detector will not be able to handle the extreme radiation environment, resolve nearby particle tracks and operate properly for high pileup values.
-That is why Run 2 pixel detector will be replaced by a new pixel detector which will be composed of three subdetectors: tracker barrel pixel detector (TBPX), tracker forward pixel detector (TFPX) and tracker endcap pixel detector (TEPX).
+The High Luminosity (HL)-LHC will increase instantaneous luminosity to unprecedented value of $7.5 \times 10^{34} cm^{-2} s^{-1}$ which corresponds to 200 proton-proton collisions per bunch crossing (pileup).
+Run 2 pixel detector will not be able to handle the extreme radiation environment, resolve nearby particle tracks and operate properly to give a reliable estimate of the instantaneous luminosity for high pileup values.
+That is why it will be replaced by a new pixel detector which will be composed of three subdetectors: tracker barrel pixel detector (TBPX), tracker forward pixel detector (TFPX) and tracker endcap pixel detector (TEPX).
+TEPX will have better radiation tolerance, increased granularity, improved two-track separation, improved estimation of hit rate and statistical precision, extended tracking acceptance $|\eta|=4$ with Disk 4 Ring 1 operating as an independent luminometer.
+\\
+
+Tracker endcap pixel detector (TEPX) consists of four double disks per side (-Z and +Z) as shown in Fig.
+27 with each double disk containing five rings as shown in Fig.
+28 having 20, 28, 36, 44 and 48 modules respectively.
+One double disk has four surfaces with +Z side containing modules with even module number in front layers (L1 $\&$ L2) and modules with odd module number in back layers (L3 $\&$ L4) from Ring 1 to Ring 4 and for Ring 5, modules with odd module number in front layers and modules with even module number in back layers as shown in Fig.
+29.
+For -Z side, four surfaces contain modules with odd module number in front layer and modules with even module number in back layer from Ring 1 to Ring 4 and for Ring 5, modules with even module number in front layer and modules with odd module number in back layer.
+\\
+
+Instantaneous luminosity determination using PCC method for Phase 2 HL-LHC can be based on counting the number of clusters or coincidences.
+The innermost ring of the last disk of TEPX (D4R1) is located at 2.65 m away from the interaction point that is beyond the tracking acceptance ($|\eta = 4|$) and as this region has few tracking points, it can be solely used for the purpose of luminosity measurement by using the full available trigger rate and bandwidth.
+Two fold coincidences are those hits which are created by the module overlap regions between various layers of one TEPX double disk.
+Two fold coincidences are better way to distinguish between a real hit and random electrical noise.
+They are more likely to be real hit than random electrical noise.
+Two fold coincidence in $\phi$ will involve modules overlapping in the same ring in front and back layers of one double disk as shown in top part of Fig.
+30 and Fig.
+31 while two fold coincidence in r will require modules overlapping between successive rings in the front (L1 $\&$ L2) and back layers (L3 $\&$ L4) of one double disk as shown in bottom part of Fig.
+30.
+Luminosity calculated based on counting coincidences has an advantage over clusters that afterglow effects are tiny in the case of coincidences.
+\\
+
+Nonlinearity is one of the systematic uncertainty in the calculation of instantaneous luminosity using PCC and PCC visible cross section $\sigma_{vis}$.
+A Linear relation between the number of clusters and pileup (PU) would imply that\\
+
+$<N_{cluster/interaction}> = \frac{<N_{cluster}>}{(PU)} = \frac{\sigma_{visible}}{\sigma_{interaction} (\sqrt{s})}$ \\
+
+$<N_{cluster}> =  \frac{\sigma_{visible}}{\sigma_{interaction}(\sqrt{s})} (PU)$ \\
+
+\newpage Linearity indicates that the PCC visible cross section $\sigma_{vis}$ does not depend on the per bunch instantaneous luminosity (ideal luminometer).
+In ideal  scenario, $\sigma_{vis}$ is not dependent on pileup, but this a potential problem with the luminometer.
+A non-linear relation $<N_{cluster}> = \alpha (PU)^{\gamma}, \gamma \neq 1$ would add non-linear terms in the rate equation $R = \sigma L$  and cause $\sigma_{vis}$ to vary with the per bunch instantaneous luminosity and pileup values.
 
@@
   \centering
-  \includegraphics[width=0.6\columnwidth]{./up.png}
-  \caption{\onehalfspacing Left: View in the x-y plane of the double disk structure of one TEPX disk.
-The sensors in blue and red correspond to the two double disks at slightly different z positions.
-Right: Example of two- and threefold coincidence regions on a portion of a single TEPX disk \cite{}.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.6\columnwidth]{./up1.png}
-  \caption{ \onehalfspacing Left: A layout of the CMS Phase-2 inner tracker with the location of TEPX Disk 4, Ring 1 highlighted in dark red. Right: The x-y view of TEPX disk 4, ring 1 \cite{}.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.6\columnwidth]{./up2.png}
-  \caption{ \onehalfspacing Schematic view for one quarter of the tracker, illustrating the location of TEPX. \cite{}.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.6\columnwidth]{./tepx.png}
-  \caption{ \onehalfspacing Sketch of the TFPX and TEPX layouts, showing one quarter of the detector in r-z view.
-Modules of type 1 $\times$ 2 are shown in green, while 2 $\times$ 2 modules are represented in orange.
-The two layers of modules that populate the front- and back-side of a disc and that overlap in $r-\phi$ can be seen by zooming into the figure in the online version.
-\cite{}.}
+  \includegraphics[width=0.8\columnwidth]{./tepx_geometry.png}
+  \caption{ \onehalfspacing A layout of the CMS Phase-2 inner tracker showing four TEPX disks, eight TFPX disks and 4 barrel layers.}
   \label{fig:CMS}
@@
   \caption{ \onehalfspacing Sketch of the TEPX Disk layouts in x-y view. Modules of type 1 $\times$ 2 are shown in green, while 2 $\times$ 2 modules are represented in orange.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1 \columnwidth]{./fourlayers.png}
+  \caption{ \onehalfspacing Fours layers of one double disk of TEPX showing module arrangement in rings for all layers.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{./coincidences.png}
+  \caption{ \onehalfspacing Diagram showing modules overlap between the front and back layers of one double disk of TEPX that creates two fold coincidences in $\phi$ and r.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{./up.png}
+  \caption{\onehalfspacing Left: View in the x-y plane of the double disk structure of one TEPX disk.
+The sensors in blue and red correspond to the two double disks at slightly different z positions.
+Right: Example of two- and threefold coincidence regions on a portion of a single TEPX disk.}
   \label{fig:CMS}
@@
 \end{figure}
+
+VdM (PU 0.5) $\:\:$  Trigger frequency (kHz) $\:\:$ 1 bx, 30 s $\:\:$ 100 bx, 30 s \\
+TEPX D4R1 2x Coincidences in $\phi$  $\:\:$  800        $\:\:$   1.7         $\:\:$       0.17   \\
+TEPX 2x Coincidences in $\phi$   $\:\:$     500        $\:\:$   0.485       $\:\:$       0.0485   \\
+
+Physics (PU 200)  $\:\:$ Trigger frequency (kHz)   $\:\:$   1 bx, 4 LN (1.46 s)   $\:\:$     2500 bx, 1 LS (23 s)  \\
+                                                      $\:\:$           ``Online''          $\:\:$           ``Offline''      \\
+TEPX D4R1 2x Coincidences in $\phi$  $\:\:$   800                $\:\:$   0.386           $\:\:$            0.00193         \\
+TEPX 2x Coincidences in $\phi$       $\:\:$   75           $\:\:$         0.284           $\:\:$            0.00142         \\

### 2021-05-14 project_ashish_monograph/vdM.tex
progress

@@
-\section{van der Meer calibration}
+\newpage \section{van der Meer calibration}
 \label{sec:vdm}
@@
 
-where $N_1, N_2$ are the number of protons in the colliding bunches, f is the LHC orbit frequency whose value is 11246Hz,  $\rho_1(x,y)$ and $\rho_2(x+\Delta x,y+\Delta y)$ are the two dimensional particle density distribution functions for each colliding bunch separated by $\Delta x$ and $\Delta y$.
+where $N_1, N_2$ are the number of protons in the colliding bunches, f is the LHC orbit frequency whose value is 11246Hz,  $\rho_1(x,y)$ and $\rho_2(x+\Delta x,y+\Delta y)$ are the two dimensional particle density distribution functions for each colliding bunch separated by $\Delta x$ and $\Delta y$ in the x and y directions.
 \\
@@
 
-The VdM scan determines the beam overlap integrals $\int \rho_{x1} (x) \rho_{x2} (x+\Delta x) dx$ and  $\int \rho_{y1}(y) \rho_{y2} (y+\Delta y) dy$ by measuring pixel clusters rate as a function of bunch separation $\Delta x$ and $\Delta y$ along x and y directions as shown in Fig.
+The VdM scan determines the bunch  overlap integrals $\int \rho_{x1} (x) \rho_{x2} (x+\Delta x) dx$ and  $\int \rho_{y1}(y) \rho_{y2} (y+\Delta y) dy$ by measuring pixel clusters rate as a function of bunch separation $\Delta x$ and $\Delta y$ along x and y directions as shown in Fig.
 7.
@@
   \includegraphics[width=\columnwidth]{./vdm_image.png}
-  \caption{ \onehalfspacing }
+  \caption{\onehalfspacing Figure showing two LHC bunches in green and blue approaching each other and colliding giving rise to an overlapping region showing in red whose area is determined during VdM scans.}
   \label{fig:CMS}

### 2021-05-14 project_ashish_monograph/upgrade.tex
updated
TEPX linearity figures updated

@@
 Nonlinearity is one of the systematic uncertainty in the calculation of instantaneous luminosity using PCC and PCC visible cross section $\sigma_{vis}$.
-A Linear relation between the number of clusters and pileup (PU) would imply that\\
+A linear relation between the number of clusters and pileup (PU) would imply that\\
 
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_totalcluster_linearity.png}
-  \caption{Simulated mean number of clusters for all entire TEPX detector as a function of pileup. A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_totalcluster_residuals.png}
-  \caption{Deviation from linearity for clusters for entire TEPX detector.
+  \includegraphics[width=1\columnwidth]{./totalclusters.png}
+  \caption{\onehalfspacing Left: Simulated mean number of clusters for all entire TEPX detector as a function of pileup.
+A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.
+Right: Deviation from linearity for clusters for entire TEPX detector.
 The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_mean_number_of_clusters___bx_Linearity.png}
-  \caption{Simulated mean number of clusters for TEPX Disk 4 Ring 1 as a function of pileup.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_mean_number_of_clusters___bx_Linearity_residuals.png}
-  \caption{Deviation from linearity for clusters for TEPX Disk 4 Ring 1.
+  \includegraphics[width=1\columnwidth]{./clustersD4R1.png}
+  \caption{\onehalfspacing Left: Simulated mean number of clusters for TEPX Disk 4 Ring 1 as a function of pileup.
+Right: Deviation from linearity for clusters for TEPX Disk 4 Ring 1.
 The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_clusters_negativez_Linearity.png}
-  \caption{Simulated mean number of clusters for -z side TEPX disks as a function of pileup.}
+  \includegraphics[width=1 \columnwidth]{./clustersperdisk-z.png}
+  \caption{Left: Simulated mean number of clusters for -z side TEPX disks as a function of pileup. Right: Deviation from linearity for clusters for -z side TEPX disks.}
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_clusters_per_disk_negativez_Linearity_residuals.png}
-  \caption{Deviation from linearity for clusters for -z side TEPX disks.}
+  \includegraphics[width=1 \columnwidth]{./clustersperdisk+z.png}
+  \caption{Left: Simulated mean number of clusters for +z side TEPX disks as a function of pileup. Right: Deviation from linearity for clusters for +z side TEPX disks.}
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_clusters_per_disk_positivez_linearity.png}
-  \caption{Simulated mean number of clusters for +z side TEPX disks as a function of pileup.}
+  \includegraphics[width=1\columnwidth]{./clustersperringD-4.png}
+  \caption{Left: Simulated mean number of clusters for TEPX Disk 4 all rings as a function of pileup.
+Ring 1 has highest slope and Ring 5 has least slope.
+Right: Deviation from linearity for clusters for TEPX Disk 4 all rings.
+Non-linearity is within $1\%$ for all rings over entire pileup range.}
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_clusters_per_disk_postivez_Linearity_residuals.png}
-  \caption{Deviation from linearity for clusters for +z side TEPX disks.}
+  \includegraphics[width=1\columnwidth]{./clustersperringD+4.png}
+  \caption{Left: Simulated mean number of clusters for TEPX Disk 4 all rings as a function of pileup.
+Ring 1 has highest slope and Ring 5 has least slope.
+Right: Deviation from linearity for clusters for TEPX Disk 4 all rings.
+Non-linearity is within $1\%$ for all rings over entire pileup range.}
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_clusters_per_ringDisk4_Linearity.png}
-  \caption{Simulated mean number of clusters for TEPX Disk 4 all rings as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope.}
+  \includegraphics[width=1 \columnwidth]{./totalcoincidences.png}
+  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for all entire TEPX detector as a function of pileup.
+A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.
+Right: Deviation from linearity for coincidence in $\phi$ and r for entire TEPX detector.
+The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.
+Non-linearity is within 1 \% for entire pileup range.
+Pileup 200 corresponds to High Luminosity (HL)-LHC
+environment. }
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_clusters_per_ringDisk4_Linearity_residuals.png}
-  \caption{Deviation from linearity for clusters for TEPX Disk 4 all rings. Non-linearity is within $1\%$ for all rings over entire pileup range.}
+  \includegraphics[width=1\columnwidth]{.//coincidencesperdisk-z.png}
+  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for -z side TEPX disks as a function of pileup.
+Right: Deviation from linearity for coincidences in $\phi$ and r for -z side TEPX disks.}
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_mean_number_of_coincidences___bx_Linearity.png}
-  \caption{Simulated mean number of coincidences in $\phi$ and r for all entire TEPX detector as a function of pileup.
-A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.}
+  \includegraphics[width=1\columnwidth]{./coincidencesperdisk+z.png}
+  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for +z side TEPX disks as a function of pileup.
+Right: Deviation from linearity for coincidences in $\phi$ and r for +z side TEPX disks.}
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_mean_number_of_coincidences___bx_Linearity_residuals.png}
-  \caption{Deviation from linearity for coincidence in $\phi$ and r for entire TEPX detector. The non-linearity is calculated as
-the relative difference between the data points and the values of the fit function at the respective pileup value.
-Non-linearity is within 1 \% for entire pileup range. Pileup 200 corresponds to High Luminosity (HL)-LHC
-environment.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_per_disk__pz_side_mean_number_of_coincidences___bx_Linearity.png}
-  \caption{Simulated mean number of coincidences in $\phi$ and r for +z side TEPX disks as a function of pileup.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_per_disk__pz_side_mean_number_of_coincidences___bx_Linearity_residuals.png}
-  \caption{Deviation from linearity for coincidences in $\phi$ and r for +z side TEPX disks.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_per_disk,_-z_side_Linearity.png}
-  \caption{Simulated mean number of coincidences in $\phi$ and r for -z side TEPX disks as a function of pileup.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_per_disk,_-z_side_Linearity_residuals.png}
-  \caption{Deviation from linearity for coincidences in $\phi$ and r for -z side TEPX disks.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_mean_number_of_coincidences___bx_Linearity.png}
-  \caption{Simulated mean number of coincidences in $\phi$ and r for TEPX Disk 4 Ring 1 as a function of pileup.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_mean_number_of_coincidences___bx_Linearity_residuals.png}
-  \caption{Deviation from linearity for coincidences in $\phi$ and r for TEPX Disk 4 Ring 1. The non-linearity is calculated as the
-relative difference between the data points and the values of the fit function at the respective pileup value.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_coincidences_in_phi__pz_side_mean_number_of_coincidences___bx_Linearity.png}
-  \caption{Simulated mean number of coincidences in $\phi$ for TEPX +z side Disk 4 Ring 1 as a function of pileup.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_coincidences_in_phi__pz_side_mean_number_of_coincidences___bx_Linearity_residuals.png}
-  \caption{Deviation from linearity for coincidences in $\phi$ for TEPX +z side Disk 4 Ring 1.
+  \includegraphics[width=1\columnwidth]{./totalcoincidencesD4R1.png}
+  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for TEPX Disk 4 Ring 1 as a function of pileup.
+Right: Deviation from linearity for coincidences in $\phi$ and r for TEPX Disk 4 Ring 1.
 The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_coincidences_in_r__pz_side_mean_number_of_coincidences___bx_Linearity.png}
-  \caption{Simulated mean number of coincidences in r for TEPX +z side Disk 4 Ring 1 as a function of pileup.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_Disk_4_Ring_1_coincidences_in_r__pz_side_mean_number_of_coincidences___bx_Linearity_residuals.png}
-  \caption{Deviation from linearity for coincidences in r for TEPX +z side Disk 4 Ring 1.
+  \includegraphics[width=1\columnwidth]{./coincidencesinphiD4R1z+.png}
+  \caption{Left: Simulated mean number of coincidences in $\phi$ for TEPX +z side Disk 4 Ring 1 as a function of pileup.
+Right: Deviation from linearity for coincidences in $\phi$ for TEPX +z side Disk 4 Ring 1.
 The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_in_phi_per_ring_mean_number_of_coincidences___bxDisk4_Linearity.png}
-  \caption{Simulated mean number of coincidences in $\phi$ for +z side TEPX Disk 4 per ring as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope.}
+  \includegraphics[width=1\columnwidth]{./coincidencesinrD4R1z+.png}
+  \caption{Left: Simulated mean number of coincidences in r for TEPX +z side Disk 4 Ring 1 as a function of pileup.
+Right: Deviation from linearity for coincidences in r for TEPX +z side Disk 4 Ring 1.
+The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_in_phi_per_ring_mean_number_of_coincidences___bxDisk4_Linearity_residuals.png}
-  \caption{Deviation from linearity for coincidences in $\phi$ for +z side TEPX Disk 4 per ring. Non-linearity is within 1\% for all rings over entire pileup range.}
+  \includegraphics[width=1\columnwidth]{./coincidencesinphiperringD-4.png}
+  \caption{Left: Simulated mean number of coincidences in $\phi$ for -z side TEPX Disk 4 per ring as a function of pileup.
+Ring 1 has highest slope and Ring 5 has least slope.
+Right: Deviation from linearity for coincidences in $\phi$ for -z side TEPX Disk 4 per ring.
+Non-linearity is within 1\% for all rings over entire pileup range.}
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_inphi_per_ring__Disk_-4_Linearity.png}
-  \caption{Simulated mean number of coincidences in \phi for -z side TEPX Disk 4 per ring as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope.}
+  \includegraphics[width=1\columnwidth]{./coincidencesinphiperringD+4.png}
+  \caption{Left: Simulated mean number of coincidences in $\phi$ for +z side TEPX Disk 4 per ring as a function of pileup.
+Ring 1 has highest slope and Ring 5 has least slope.
+Right: Deviation from linearity for coincidences in $\phi$ for +z side TEPX Disk 4 per ring.
+Non-linearity is within 1\% for all rings over entire pileup range.}
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_inphi_per_ring__Disk_-4_Linearity_residuals.png}
-  \caption{Deviation from linearity for coincidences in $\phi$ for -z side TEPX Disk 4 per ring. Non-linearity is within 1\% for all rings over entire pileup range.}
+  \includegraphics[width=1\columnwidth]{./coincidencesinrperringD-4.png}
+  \caption{Left: Simulated mean number of coincidences in $\phi$ for -z side TEPX Disk 4 per ring as a function of pileup.
+Ring 1 has highest slope and Ring 5 has least slope.
+Right: Deviation from linearity for coincidences in $\phi$ for -z side TEPX Disk 4 per ring.
+Non-linearity is within $1\%$ for all rings over entire pileup range.}
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_in_r_per_ring__Disk_-4_Linearity.png}
-  \caption{Simulated mean number of coincidences in r for -z side TEPX Disk 4 per ring as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_in_r_per_ring__Disk_-4_Linearity_residuals.png}
-  \caption{Deviation from linearity for coincidences in $\phi$ for -z side TEPX Disk 4 per ring. Non-linearity is within 1\% for all rings over entire pileup range.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_in_r_per_ring_mean_number_of_coincidences___bxDisk4_Linearity.png}
-  \caption{Simulated mean number of coincidences in r for +z side TEPX Disk 4 per ring as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\columnwidth]{./TEPX_coincidences_in_r_per_ring_mean_number_of_coincidences___bxDisk4_Linearity_residuals.png}
-  \caption{Deviation from linearity for coincidences in r for +z side TEPX Disk 4 per ring. Non-linearity is within 1\% for all rings over entire pileup range.}
+  \includegraphics[width=1\columnwidth]{./coincidencesinrperringD+4.png}
+  \caption{Left: Simulated mean number of coincidences in $\phi$ for +z side TEPX Disk 4 per ring as a function of pileup.
+Ring 1 has highest slope and Ring 5 has least slope.
+Right: Deviation from linearity for coincidences in $\phi$ for +z side TEPX Disk 4 per ring.
+Non-linearity is within $1\%$ for all rings over entire pileup range.}
   \label{fig:CMS}

### 2021-05-14 project_ashish_monograph/upgrade.tex
updated

@@
 
+\newpage
 \begin{figure}[H]
@@
   \includegraphics[width=1\columnwidth]{./coincidencesinrperringD-4.png}
-  \caption{Left: Simulated mean number of coincidences in $\phi$ for -z side TEPX Disk 4 per ring as a function of pileup.
+  \caption{Left: Simulated mean number of coincidences in r for -z side TEPX Disk 4 per ring as a function of pileup.
 Ring 1 has highest slope and Ring 5 has least slope.
-Right: Deviation from linearity for coincidences in $\phi$ for -z side TEPX Disk 4 per ring.
+Right: Deviation from linearity for coincidences in r for -z side TEPX Disk 4 per ring.
 Non-linearity is within $1\%$ for all rings over entire pileup range.}
@@
   \includegraphics[width=1\columnwidth]{./coincidencesinrperringD+4.png}
-  \caption{Left: Simulated mean number of coincidences in $\phi$ for +z side TEPX Disk 4 per ring as a function of pileup.
+  \caption{Left: Simulated mean number of coincidences in r for +z side TEPX Disk 4 per ring as a function of pileup.
 Ring 1 has highest slope and Ring 5 has least slope.
-Right: Deviation from linearity for coincidences in $\phi$ for +z side TEPX Disk 4 per ring.
+Right: Deviation from linearity for coincidences in r for +z side TEPX Disk 4 per ring.
 Non-linearity is within $1\%$ for all rings over entire pileup range.}

### 2021-05-15 project_ashish_monograph/upgrade.tex
updated

@@
 Non-linearity is within 1 \% for entire pileup range.
-Pileup 200 corresponds to High Luminosity (HL)-LHC
-environment. }
+Pileup 200 corresponds to High Luminosity (HL)-LHC environment.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{./totalcoincidencesD4R1.png}
+  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for TEPX Disk 4 Ring 1 as a function of pileup.
+Right: Deviation from linearity for coincidences in $\phi$ and r for TEPX Disk 4 Ring 1.
+The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=1\columnwidth]{./totalcoincidencesD4R1.png}
-  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for TEPX Disk 4 Ring 1 as a function of pileup.
-Right: Deviation from linearity for coincidences in $\phi$ and r for TEPX Disk 4 Ring 1.
-The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
   \includegraphics[width=1\columnwidth]{./coincidencesinphiD4R1z+.png}
@@
 The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{./coincidencesperringD-4.png}
+  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for -z side TEPX Disk 4 per ring as a function of pileup.
+Ring 1 has highest slope and Ring 5 has least slope.
+Right: Deviation from linearity for coincidences in $\phi$ and r for -z side TEPX Disk 4 per ring.
+Non-linearity is within 1\% for all rings over entire pileup range.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{./coincidencesperringD+4.png}
+  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for +z side TEPX Disk 4 per ring as a function of pileup.
+Ring 1 has highest slope and Ring 5 has least slope.
+Right: Deviation from linearity for coincidences in $\phi$ and r for +z side TEPX Disk 4 per ring.
+Non-linearity is within 1\% for all rings over entire pileup range.}
   \label{fig:CMS}

### 2021-05-17 project_ashish_monograph/CMS.tex
references added

@@
 CMS is designed to detect new particles produced in the LHC's high energy proton-proton and heavy-ion (Lead, Xenon) collisions.
-CMS will also measure the properties (mass, decay width, coupling) of already discovered particles like quarks and leptons with unprecedented precision and will be looking to discover completely new, beyond standard model of particle physics phenomena which will help us to get a better understanding of our Universe and may confirm or rule out multiverse hypothesis.
-This experiment has already confirmed the discovery of the most important particle in SM, the Higgs boson which gives mass to all bosons and fermions via electroweak symmetry breaking mechanism.
+CMS will also measure the properties (mass, decay width, coupling) of already discovered particles like quarks and leptons with unprecedented precision and will be looking to discover completely new, beyond standard model of particle physics phenomena which will help us to get a better understanding of our Universe and may confirm or rule out multiverse hypothesis \cite{Chatrchyan:1129810}.
+This experiment has already confirmed the discovery of the most important particle in SM, the Higgs boson which gives mass to all bosons and fermions via electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}.
 It has also detected the decay of Higgs boson to a pair of photons, W bosons, bottom quarks and muons.
@@
 The CMS Run 2 pixel detector consists of four concentric barrel layers (L1-L4) at radii of 29, 68, 109 and 160 mm and three disks (D1-D3) on each end at distances of 291, 396, and 516 mm from the center of the detector.
-It is built from 1856 segmented silicon sensor modules, where 1184 modules are used in the barrel pixel detector (BPIX) and 672 modules are used for the forward disks (FPIX).
+It is built from 1856 segmented silicon sensor modules, where 1184 modules are used in the barrel pixel detector (BPIX) and 672 modules are used for the forward disks (FPIX) \cite{TrackerGroupoftheCMS:2020bgg}.
 \\

### 2021-05-17 project_ashish_monograph/LHC.tex
progress
references added

@@
 \onehalfspacing CERN accelerator complex is a progression of machines namely Linac 2, Proton Synchrotron Booster (PSB), Proton Synchrotron (PS), Super Proton Synchrotron (SPS) and Large Hadron Collider (LHC) as shown in Fig.
-1 that accelerate particles mainly protons to increasingly higher energies of 50 MeV, 1.4 GeV, 25 GeV, 450 GeV and 14 TeV respectively.
+1 that accelerate particles mainly protons to increasingly higher energies of 50 MeV, 1.4 GeV, 25 GeV, 450 GeV and 14 TeV respectively \cite {CERN-Brochure-2017-002-Eng}.
 Each machine is used to increase the energy of particle before the beam is injected into to the next machine.
@@
 The LHC consists of a 27 kilometre ring of superconducting magnets producing strong magnetic field which is used to guide particle beams along the LHC ring.
-Proton beam made up of bunches travelling in opposite directions kept in two ultrahigh vacuum tubes are accelerated close to the speed of light using time dependent electric field produced by radiofrequency cavities before they collide at four interaction points along the LHC ring where ATLAS, ALICE, CMS and LHCb detectors are placed.
+Proton beam made up of bunches travelling in opposite directions kept in two ultrahigh vacuum tubes are accelerated close to the speed of light using time dependent electric field produced by radiofrequency cavities before they collide at four interaction points along the LHC ring where ATLAS, ALICE, CMS and LHCb detectors are placed \cite {CERN-Brochure-2017-002-Eng}.
 \\
 
-The first proton beam was successfully maneuvered around the LHC ring in September 2008 that marked the beginning of Run 1 with proton beams colliding at 7-8 TeV center-of-mass energy and this run period ended in 2013.
-Run 2 started in 2015 with protons colliding at 13 TeV center-of-mass energy and continued till October 2018.
-Run 3 is expected to begin at the start of March 2022 and High Luminosity (HL)-LHC phase is expected to begin in mid-2027.
+The first proton beam was successfully maneuvered around the LHC ring in September 2008 that marked the beginning of Run 1 with proton beams colliding at 7-8 TeV center-of-mass energy and this run period ended in 2013 \cite{cmsrun}.
+Run 2 started in 2015 with protons colliding at 13 TeV center-of-mass energy and continued till October 2018 \cite{Wenninger:2668326}.
+Run 3 is expected to begin at the start of March 2022 and High Luminosity (HL)-LHC phase is expected to begin in mid-2027 \cite{Dainese:2019rgk}.
 Proton Synchroton (PS) is responsible for providing proton bunches spaced 7 metres (25 ns) apart with each bunch containing more than 100 billion protons.
-The maximum number of bunches reached with the beam preparation method used during Run 2 is 2556.
+The maximum number of bunches reached with the beam preparation method used during Run 2 is 2556 \cite{Wenninger:2668326}.
 The number of protons in the colliding bunches, time of separation between the bunches and effective area of the bunch which depend on the rms transverse bunch size along horizontal and vertical directions is one of the ways to calculate instantaneous luminosity (L_{inst}).
@@
 Both are very important variables as they are used to obtain the number of collision events.
-During Run 1, peak value of LHC instantaneous luminosity was $0.77 \times 10^{34} \: cm^{-2} s^{-1} $ with $30 \: fb^{-1}$ integrated luminosity.
+During Run 1, peak value of LHC instantaneous luminosity was $0.77 \times 10^{34} \: cm^{-2} s^{-1} $ with $30 \: fb^{-1}$ integrated luminosity \cite{cmsrun1lumi}  .
 During Run 2, LHC instantaneous luminosity reached a peak value of $1.58 \times 10^{34}  \: cm^{-2} s^{-1}$ with $150 \: fb^{-1}$ integrated luminosity as shown in Fig.
-2.
+2 \cite{CMS:2018elu}.
 At the end of Run 3, we expect to achieve an integrated luminosity  of $300 \:fb^{-1}$ while Phase 2 HL-LHC is expected to collect $3000 \:fb^{-1}$ of data as shown in Fig.
-3 thereby increasing luminosity by a factor of 10 beyond the LHC's design value.
+3 thereby increasing luminosity by a factor of 10 beyond the LHC's design value \cite{Dainese:2019rgk}.
 \\
@@
   \includegraphics[width=0.8\columnwidth]{./LHCcomplex.png}
-  \caption{\onehalfspacing Diagram of the LHC accelerator complex located in Geneva, Switzerland. Four interaction points are shown for the ALICE, ATLAS, LHCb and CMS experiments.}
+  \caption{\onehalfspacing Diagram of the LHC accelerator complex located in Geneva, Switzerland. Four interaction points are shown for the ALICE, ATLAS, LHCb and CMS experiments. \cite{Mobs:2684277}}
   \label{fig:LHC}
@@
   \includegraphics[width=1 \columnwidth]{./run1-2_lumi.png}
-  \caption{\onehalfspacing Left: Instantaneous luminosities for Run 1 and Run 2 period. Right: Integrated luminosities for Run 1 and Run 2 period.}
+  \caption{\onehalfspacing Left: Instantaneous luminosities for Run 1 and Run 2 period. Right: Integrated luminosities for Run 1 and Run 2 period. \cite{lumi}}
   \label{fig:LHClumi}
@@
   \centering
-  \includegraphics[width=0.7 \columnwidth]{./HLLHCLumi.png}
+  \includegraphics[width=0.7 \columnwidth]{./lumi_projection.png}
   \caption{ \onehalfspacing Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS1, LS2, LS3, LS4, LS5) of the LHC and luminosities.

### 2021-05-17 project_ashish_monograph/PCC.tex
references added

@@
 
-The instantaneous luminosity per bunch crossing L is proportional to the number of proton-proton (pp) interactions per bunch crossing (pileup) and the proportionality constant is the ratio of  LHC orbit frequency f and the pp interaction cross section $\sigma_{interaction}(\sqrt{s})$ where s is the proton-proton collision center-of-mass energy.
+The instantaneous luminosity per bunch crossing L is proportional to the number of proton-proton (pp) interactions per bunch crossing (pileup) and the proportionality constant is the ratio of  LHC orbit frequency f and the pp interaction cross section $\sigma_{interaction}(\sqrt{s})$ where s is the proton-proton collision center-of-mass energy \cite{CMS-PAS-LUM-12-001}.
 \\
@@
 A cluster is a set of adjacent pixels and only pixels above certain threshold charge are considered.
-Position of a cluster in X and Y direction are obtained by fitting X and Y prpjections to templates that are estimates for cluster shapes.
+Position of a cluster in X and Y direction are obtained by fitting X and Y projections to templates that are estimates for cluster shapes \cite{Chatrchyan:2014fea}.
 

### 2021-05-17 project_ashish_monograph/bkg.tex
references added

@@
 
-The afterglow corrections for PCC during 2017 run are in the range 2-5 $\%$ for the Type 1 corrections and 2-3 $\%$ averaged over all active bunches for the Type 2 corrections.
+The afterglow corrections for PCC during 2017 run are in the range 2-5 $\%$ for the Type 1 corrections and 2-3 $\%$ averaged over all active bunches for the Type 2 corrections \cite{Sirunyan:2759951}.
 

### 2021-05-17 project_ashish_monograph/upgrade.tex
references added

@@
 That is why it will be replaced by a new pixel detector which will be composed of three subdetectors: tracker barrel pixel detector (TBPX), tracker forward pixel detector (TFPX) and tracker endcap pixel detector (TEPX).
-TEPX will have better radiation tolerance, increased granularity, improved two-track separation, improved estimation of hit rate and statistical precision, extended tracking acceptance $|\eta|=4$ with Disk 4 Ring 1 operating as an independent luminometer.
+TEPX will have better radiation tolerance, increased granularity, improved two-track separation, improved estimation of hit rate and statistical precision, extended tracking acceptance $|\eta|=4$ with Disk 4 Ring 1 operating as an independent luminometer \cite{Klein:2017nke}.
 \\
@@
 29.
-For -Z side, four surfaces contain modules with odd module number in front layer and modules with even module number in back layer from Ring 1 to Ring 4 and for Ring 5, modules with even module number in front layer and modules with odd module number in back layer.
+For -Z side, four surfaces contain modules with odd module number in front layer and modules with even module number in back layer from Ring 1 to Ring 4 and for Ring 5, modules with even module number in front layer and modules with odd module number in back layer .
 \\
@@
 Luminosity calculated based on counting coincidences has an advantage over clusters that afterglow effects are tiny in the case of coincidences.
-\\
+\cite{Collaboration:2706512} \\
 
@@
   \includegraphics[width=0.8\columnwidth]{./tepx_geometry.png}
-  \caption{ \onehalfspacing A layout of the CMS Phase-2 inner tracker showing four TEPX disks, eight TFPX disks and 4 barrel layers.}
+  \caption{ \onehalfspacing A layout of the CMS Phase-2 inner tracker showing four TEPX disks, eight TFPX disks and 4 barrel layers. \cite{Klein:2017nke}}
   \label{fig:CMS}

### 2021-05-17 project_ashish_monograph/vdM.tex
references added

@@
 
-The instantaneous luminosity when the crossing angle between the colliding bunches is negligible and bunches collide head on is given by the following integral, \\
+The instantaneous luminosity when the crossing angle between the colliding bunches is negligible and bunches collide head on is given by the following integral, \cite{CMS-PAS-LUM-13-001} \\
 
@@
 The lower panels display the difference between the measured and fitted values
-divided by the statistical uncertainty\cite{}.}
+divided by the statistical uncertainty\cite{CMS-PAS-LUM-15-001}.}
   \label{fig:CMS}

### 2021-05-17 project_ashish_monograph/LHC.tex
references updated

@@
 \onehalfspacing CERN accelerator complex is a progression of machines namely Linac 2, Proton Synchrotron Booster (PSB), Proton Synchrotron (PS), Super Proton Synchrotron (SPS) and Large Hadron Collider (LHC) as shown in Fig.
-1 that accelerate particles mainly protons to increasingly higher energies of 50 MeV, 1.4 GeV, 25 GeV, 450 GeV and 14 TeV respectively \cite {CERN-Brochure-2017-002-Eng}.
+1 that accelerate particles mainly protons to increasingly higher energies of 50 MeV, 1.4 GeV, 25 GeV, 450 GeV and 14 TeV respectively \cite {CERNBrochure2017002Eng}.
 Each machine is used to increase the energy of particle before the beam is injected into to the next machine.
@@
 
-The first proton beam was successfully maneuvered around the LHC ring in September 2008 that marked the beginning of Run 1 with proton beams colliding at 7-8 TeV center-of-mass energy and this run period ended in 2013 \cite{cmsrun}.
+The first proton beam was successfully maneuvered around the LHC ring in September 2008 that marked the beginning of Run 1 with proton beams colliding at 7-8 TeV center-of-mass energy and this run period ended in 2013 \cite{cmsrun} \cite{Alemany-Fernandez:1631030}.
 Run 2 started in 2015 with protons colliding at 13 TeV center-of-mass energy and continued till October 2018 \cite{Wenninger:2668326}.

### 2021-05-17 project_ashish_monograph/LHC.tex
references updated

@@
 The LHC consists of a 27 kilometre ring of superconducting magnets producing strong magnetic field which is used to guide particle beams along the LHC ring.
-Proton beam made up of bunches travelling in opposite directions kept in two ultrahigh vacuum tubes are accelerated close to the speed of light using time dependent electric field produced by radiofrequency cavities before they collide at four interaction points along the LHC ring where ATLAS, ALICE, CMS and LHCb detectors are placed \cite {CERN-Brochure-2017-002-Eng}.
+Proton beam made up of bunches travelling in opposite directions kept in two ultrahigh vacuum tubes are accelerated close to the speed of light using time dependent electric field produced by radiofrequency cavities before they collide at four interaction points along the LHC ring where ATLAS, ALICE, CMS and LHCb detectors are placed \cite {CERNBrochure2017002Eng}.
 \\

### 2021-05-17 project_ashish_monograph/upgrade.tex
references updated

@@
 Instantaneous luminosity determination using PCC method for Phase 2 HL-LHC can be based on counting the number of clusters or coincidences.
-The innermost ring of the last disk of TEPX (D4R1) is located at 2.65 m away from the interaction point that is beyond the tracking acceptance ($|\eta = 4|$) and as this region has few tracking points, it can be solely used for the purpose of luminosity measurement by using the full available trigger rate and bandwidth.
+The innermost ring of the last disk of TEPX (D4R1) is located at 2.65 m away from the interaction point that is beyond the tracking acceptance ($|\eta| = 4$) and as this region has few tracking points, it can be solely used for the purpose of luminosity measurement by using the full available trigger rate and bandwidth.
 Two fold coincidences are those hits which are created by the module overlap regions between various layers of one TEPX double disk.

### 2021-05-19 project_ashish_monograph/CMS.tex
references/figures updated

@@
   \includegraphics[width=1\columnwidth]{./cmsdetector_merged.png}
-  \caption{Left: 3D design of CMS detector showing various concentric layers.
-Right: \onehalfspacing Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimete##r, superconducting solenoid and muon chambers.
+  \caption{ \onehalfspacing Left: 3D design of CMS detector showing various concentric layers.
+Right: Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimeter, superconducting solenoid and muon chambers.
 \cite{Chatrchyan:2008aa}}
@@
 The CMS Run 2 pixel detector consists of four concentric barrel layers (L1-L4) at radii of 29, 68, 109 and 160 mm and three disks (D1-D3) on each end at distances of 291, 396, and 516 mm from the center of the detector.
-It is built from 1856 segmented silicon sensor modules, where 1184 modules are used in the barrel pixel detector (BPIX) and 672 modules are used for the forward disks (FPIX) \cite{TrackerGroupoftheCMS:2020bgg}.
+It is built from 1856 segmented silicon sensor modules, where 1184 modules are used in the barrel pixel detector (BPIX) and 672 modules are used for the forward disks (FPIX) .
 \\
@@
   \includegraphics[width=1 \columnwidth]{./pixeldetector_merged1.png}
-  \caption{Left: Layout of the CMS Run 2 pixel detector compared to the original detector layout, in longitudinal view.
-Right: pixel detector diagram showing size of Silicon sensor, readout chip and data buffers.}
+  \caption{ \onehalfspacing Left: Layout of the CMS Run 2 pixel detector compared to the original detector layout, in longitudinal view.
+Right: pixel detector diagram showing size of silicon sensor, readout chip and data buffers.
+\cite{TrackerGroupoftheCMS:2020bgg}}
   \label{fig:LHC}

### 2021-05-19 project_ashish_monograph/LHC.tex
references/figures updated

@@
 Both are very important variables as they are used to obtain the number of collision events.
-During Run 1, peak value of LHC instantaneous luminosity was $0.77 \times 10^{34} \: cm^{-2} s^{-1} $ with $30 \: fb^{-1}$ integrated luminosity \cite{cmsrun1lumi}  .
-During Run 2, LHC instantaneous luminosity reached a peak value of $1.58 \times 10^{34}  \: cm^{-2} s^{-1}$ with $150 \: fb^{-1}$ integrated luminosity as shown in Fig.
+During Run 1, peak value of LHC instantaneous luminosity was $0.77 \times 10^{34} \: cm^{-2} s^{-1} $ with $30 \: fb^{-1}$ integrated luminosity \cite{cmsrun1lumi}.
+During Run 2, LHC instantaneous luminosity reached a peak value of $2.1 \times 10^{34}  \: cm^{-2} s^{-1}$ with $163 \: fb^{-1}$ integrated luminosity as shown in Fig.
 2 \cite{CMS:2018elu}.
@@
   \includegraphics[width=0.8\columnwidth]{./LHCcomplex.png}
-  \caption{\onehalfspacing Diagram of the LHC accelerator complex located in Geneva, Switzerland. Four interaction points are shown for the ALICE, ATLAS, LHCb and CMS experiments. \cite{Mobs:2684277}}
+  \caption{\onehalfspacing Diagram of the LHC accelerator complex located in Geneva, Switzerland.
+Four interaction points are shown where the ALICE, ATLAS, LHCb and CMS detectors are stationed.
+\cite{Mobs:2684277}}
   \label{fig:LHC}
@@
   \centering
-  \includegraphics[width=1 \columnwidth]{./run1-2_lumi.png}
-  \caption{\onehalfspacing Left: Instantaneous luminosities for Run 1 and Run 2 period. Right: Integrated luminosities for Run 1 and Run 2 period. \cite{lumi}}
+  \includegraphics[width=1 \columnwidth]{./peakintlumi_run12.png}
+  \caption{\onehalfspacing Left: Instantaneous luminosity for Run 1 and Run 2 period. Right: Integrated luminosity for Run 1 and Run 2 period. \cite{lumi}}
   \label{fig:LHClumi}

### 2021-05-19 project_ashish_monograph/PCC.tex
references/figures updated

--- 2021-05-14 project_ashish_monograph/PCC.tex
@@
 
-The instantaneous luminosity per bunch crossing L is proportional to the number of proton-proton (pp) interactions per bunch crossing (pileup) and the proportionality constant is the ratio of  LHC orbit frequency f and the pp interaction cross section $\sigma_{interaction}(\sqrt{s})$ where s is the proton-proton collision center-of-mass energy.
+The instantaneous luminosity per bunch crossing $L_{inst/bunch}$ is proportional to the number of proton-proton (pp) interactions per bunch crossing (pileup) and the proportionality constant is the ratio of  LHC orbit frequency f and the pp interaction cross section $\sigma_{interaction}(\sqrt{s})$ where s is the proton-proton collision center-of-mass energy \cite{CMS-PAS-LUM-12-001}.
 \\
 
-L = $\frac{f}{\sigma_{interaction}}$ (PU)  \\
+$L_{inst/bunch}$ = $\frac{f}{\sigma_{interaction}}$ (PU)  \\
 
-L = $\frac{<N_{cluster}> \: f }{<N_{cluster/interaction}> \: \sigma_{interaction}(\sqrt{s})}$ \\
+$L_{inst/bunch}$ = $\frac{<N_{cluster}> \: f }{<N_{cluster/interaction}> \: \sigma_{interaction}(\sqrt{s})}$ \\
 
@@
 
-L = $\frac{<N_{cluster}> \: \sigma_{interaction}(\sqrt{s}) \: f }{ \:\sigma_{vis} \: \sigma_{interaction}(\sqrt{s})}$ \\
+$L_{inst/bunch}$ = $\frac{<N_{cluster}> \: \sigma_{interaction}(\sqrt{s}) \: f }{ \:\sigma_{vis} \: \sigma_{interaction}(\sqrt{s})}$ \\
 
-L = $\frac{<N_{cluster}> \:\: f}{\sigma_{vis}}$ \\
+$L_{inst/bunch}$ = $\frac{<N_{cluster}> \:\: f}{\sigma_{vis}}$ \\
 
 The PCC visible cross section $\sigma_{vis}$ is determined using van der meer scan method which is described in section 5.
-Cluster counting can be done over different time periods like 1 bunch crossing (25 ns), 1 Lumi section (23.36 s), 4 Lumi nibble (1.46 s) and similarly instantaneous luminosity can be calculated over these time periods using PCC method.
+Cluster counting can be done over different time periods like 1 bunch crossing (25ns), 1 Lumi section (23.36s), 4 Lumi nibble (1.46s) and similarly instantaneous luminosity can be calculated over these time periods using PCC method.
 \\
 
-Specific techniques are employed for the reconstruction of clusters in the pixel detector and all reconstructed clusters are used for counting to calculate the instantaneous luminosity.
-Algorithm used for finding clusters starts by looking for pixels whose signal to noise ratio is more than 6 and then merge adjacent pixel.
+Specific techniques are employed for the reconstruction of clusters in the pixel detector and all the reconstructed clusters are used for counting to calculate the instantaneous luminosity.
+Algorithm used for finding clusters check for pixels whose signal to noise ratio is more than 6 and then merge adjacent pixel.
 These algorithms estimates cluster position in two directions and cluster charge.
-A cluster is a set of adjacent pixels and only pixels above certain threshold charge are considered.
-Position of a cluster in X and Y direction are obtained by fitting X and Y prpjections to templates that are estimates for cluster shapes.
+A cluster is a set of adjacent pixels and only pixels above certain minimum value of charge are considered.
+Position of a cluster in X and Y directions are obtained by fitting X and Y projections to templates that are estimates for cluster shapes \cite{Chatrchyan:2014fea}.
 
@@
   \includegraphics[width=0.6\columnwidth]{./pixel_reco.png}
-  \caption{ \onehalfspacing }
+  \caption{ \onehalfspacing Diagram showing pixel cluster with charge accumulation in each pixel expressed in terms of thousands of electrons.
+Green numbers represent charge accumulation below the 2000 electron threshold which are excluded clusters.
+The dotted red line indicates the particle trajectory projection in the module plane and the red cross shows the position of true hit.}
   \label{fig:CMS}

### 2021-05-19 project_ashish_monograph/results.tex
references added
references/figures updated

@@
-\section{Results}
+\newpage \section{Results}
 \label{sec:results}
+
+The stability of luminosity determination using pixel detector based on PCC method is investigated using late Run2018D veto list.
 
@@
   \includegraphics[width=0.52\columnwidth]{./316993.png}
-  \caption{Top: Bunch crossing id (bcid) and PCC lumi as a function of lumi section. Bottom: PCC lumi as a function of lumi section (late RunD veto list is used) for run 2018A.}
+  \caption{Top: Bunch crossing id (bcid) and PCC lumi as a function of lumi section (1 lumi section is 23.36s).
+Bottom: PCC lumi as a function of lumi section (late RunD veto list is used) for run 2018A.}
   \label{fig:CMS}
@@
   \includegraphics[width=0.52\columnwidth]{./ls_lumi.png}
-  \caption{PCC luminosity as a function of lumi section.}
+  \caption{PCC luminosity ($\mu b^{-1}$) as a function of lumi section (1 lumi section is 23.36s).}
   \label{fig:CMS}
@@
   \includegraphics[width=0.52\columnwidth]{./runs.png}
-  \caption{PCC luminosity as a function of run number.}
+  \caption{PCC luminosity ($\mu b^{-1}$) as a function of run number.}
   \label{fig:CMS}
@@
   \includegraphics[width=0.52\columnwidth]{./ProfileXcombined_new.png}
-  \caption{X Profile of luminosity ratio vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section.}
+  \caption{X Profile of luminosity ratios vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section (1 lumi section is 23.36s).}
   \label{fig:CMS}
@@
   \includegraphics[width=0.5\columnwidth]{./ProfileXcombinedB_new.png}
-  \caption{X Profile of luminosity ratio vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section.}
+  \caption{X Profile of luminosity ratios vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section.}
   \label{fig:CMS}
@@
   \includegraphics[width=0.5\columnwidth]{./ProfileXcombinedC_new.png}
-  \caption{X Profile of luminosity ratio vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section.}
+  \caption{X Profile of luminosity ratios vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section.
+\cite{lumidpg}}
   \label{fig:CMS}

### 2021-05-19 project_ashish_monograph/syst.tex
references added
references/figures updated

@@
 
-Systematic uncertainties in the bunch overlap widths along x and y directions measured during VdM scans can arise from length scale calibration, orbit drift, x-y correlations of bunch proton density function, emittance growth, bunch-bunch deflection, dynamic $\beta$ which tells us whether bunches are narrow or wide, bunch current calibration, ghosts and satellites, scan to scan variation, bunch to bunch variation, cross-detector consistency, afterglow effects, linearity and CMS deadtime.
+Systematic uncertainties in the bunch overlap widths along x and y directions measured during vdM scans, $\sigma_{vis}$ and CMS luminosity can arise from length scale calibration, orbit drift, x-y correlations of bunch proton density function, emittance growth, bunch-bunch deflection, dynamic $\beta$ which tells us whether bunches are narrow or wide, bunch current calibration, ghosts and satellites, scan to scan variation and bunch to bunch variation.
+Systematic uncertainty during physics runs (high pileup) can be due to cross-detector consistency, afterglow effects, linearity and CMS deadtime.
 \\
@@
 4.
-xy-correlations: The VdM scan method assumes that the bunch proton density function is factorizable into independent x- and y-dependent terms which is not fully true and can lead to a biased estimate of the bunch overlap area.
+xy-correlations: The vdM scan method assumes that the bunch proton density function is factorizable into independent x- and y-dependent terms which is not fully true and can lead to a biased estimate of the bunch overlap area.
 In order to measure this effect, special beam imaging scans are conducted.
@@
 
-5. Non-linearity: \\
+5. Linearity: \\
 
@@
 
- Quadrupolar (de)focusing (dynamic $\beta$): Effective beam width is modified depending on the separation which in turn affects the peak luminosity (rate) value. \\
+ Quadrupolar (de)focusing (dynamic $\beta$): Effective beam width is modified depending on the separation which in turn affects the peak luminosity (rate) value. \cite{CMS-PAS-LUM-18-002} \\

### 2021-05-19 project_ashish_monograph/upgrade.tex
references/figures updated

@@
-\newpage \section{The TEPX upgrade for HL-LHC}
+ \section{The TEPX upgrade for HL-LHC}
 \label{sec:tepx}
@@
 Tracker endcap pixel detector (TEPX) consists of four double disks per side (-Z and +Z) as shown in Fig.
-27 with each double disk containing five rings as shown in Fig.
+28 with each double disk containing five rings as shown in Fig.
 28 having 20, 28, 36, 44 and 48 modules respectively.
 One double disk has four surfaces with +Z side containing modules with even module number in front layers (L1 $\&$ L2) and modules with odd module number in back layers (L3 $\&$ L4) from Ring 1 to Ring 4 and for Ring 5, modules with odd module number in front layers and modules with even module number in back layers as shown in Fig.
-29.
-For -Z side, four surfaces contain modules with odd module number in front layer and modules with even module number in back layer from Ring 1 to Ring 4 and for Ring 5, modules with even module number in front layer and modules with odd module number in back layer .
+30.
+For -Z side, four surfaces contain modules with odd module number in front layer and modules with even module number in back layer from Ring 1 to Ring 4 and for Ring 5, modules with even module number in front layer and modules with odd module number in back layer.
 \\
 
-Instantaneous luminosity determination using PCC method for Phase 2 HL-LHC can be based on counting the number of clusters or coincidences.
+Instantaneous luminosity determination using PCC method for Phase II HL-LHC can be based on counting the number of clusters or coincidences.
 The innermost ring of the last disk of TEPX (D4R1) is located at 2.65 m away from the interaction point that is beyond the tracking acceptance ($|\eta| = 4$) and as this region has few tracking points, it can be solely used for the purpose of luminosity measurement by using the full available trigger rate and bandwidth.
+TEPX Disk 4 Ring 1 layout is shown in Fig.
+29.
 Two fold coincidences are those hits which are created by the module overlap regions between various layers of one TEPX double disk.
@@
 Two fold coincidence in $\phi$ will involve modules overlapping in the same ring in front and back layers of one double disk as shown in top part of Fig.
-30 and Fig.
-31 while two fold coincidence in r will require modules overlapping between successive rings in the front (L1 $\&$ L2) and back layers (L3 $\&$ L4) of one double disk as shown in bottom part of Fig.
-30.
+31 and Fig.
+32 while two fold coincidence in r will require modules overlapping between successive rings in the front (L1 $\&$ L2) and back layers (L3 $\&$ L4) of one double disk as shown in bottom part of Fig.
+31.
 Luminosity calculated based on counting coincidences has an advantage over clusters that afterglow effects are tiny in the case of coincidences.
@@
 
-Nonlinearity is one of the systematic uncertainty in the calculation of instantaneous luminosity using PCC and PCC visible cross section $\sigma_{vis}$.
-A linear relation between the number of clusters and pileup (PU) would imply that\\
+Linearity is one of the systematic uncertainty in the calculation of instantaneous luminosity using PCC and PCC visible cross section $\sigma_{vis}$.
+A linear relation between the number of clusters and pileup (PU) imply that \\
 
@@
 In ideal scenario, $\sigma_{vis}$ is not dependent on pileup, but this a potential problem with the luminometer.
-A non-linear relation $<N_{cluster}> = \alpha (PU)^{\gamma}, \gamma \neq 1$ would add non-linear terms in the rate equation $R = \sigma L$  and cause $\sigma_{vis}$ to vary with the per bunch instantaneous luminosity and pileup values.
+Linearity results for simulated TEPX clusters and coincidences from low to high pileup values are shown from Fig.
+33 to Fig.
+50.
+TEPX luminometer proposed for Phase II shows excellent linearity over entire pileup range.
+A non-linear relation $<N_{cluster}> = \alpha (PU)^{\gamma}, \gamma \neq 1$ would add non-linear terms in the rate equation $R = \sigma_{vis} L_{inst}$  and cause $\sigma_{vis}$ to vary with the per bunch instantaneous luminosity and pileup values.
 
@@
   \centering
-  \includegraphics[width=0.5 \columnwidth]{./xydisc.png}
-  \caption{ \onehalfspacing Sketch of the TEPX Disk layouts in x-y view. Modules of type 1 $\times$ 2 are shown in green, while 2 $\times$ 2 modules are represented in orange.}
+  \includegraphics[width=0.4 \columnwidth]{./D4R1.png}
+  \caption{ \onehalfspacing Sketch of the TEPX Disk 4 Ring 1.}
   \label{fig:CMS}
@@
 
-\newpage
 \begin{figure}[H]
@@
 
-VdM (PU 0.5) $\:\:$  Trigger frequency (kHz) $\:\:$ 1 bx, 30 s $\:\:$ 100 bx, 30 s \\
+vdM (PU 0.5) $\:\:$  Trigger frequency (kHz) $\:\:$ 1 bx, 30 s $\:\:$ 100 bx, 30 s \\
 TEPX D4R1 2x Coincidences in $\phi$  $\:\:$  800        $\:\:$   1.7         $\:\:$       0.17   \\

### 2021-05-19 project_ashish_monograph/vdM.tex
references/figures updated

--- 2021-05-14 project_ashish_monograph/vdM.tex
@@
 \label{sec:vdm}
-Van der Meer (VdM) scans are done to calculate the visible cross section $\sigma_{vis}$ which is a calibration constant in the relation between rate of a quantity (clusters, coincidences) read out by the detector and the instantaneous luminosity.
+Van der Meer (vdM) scans are done to calculate the visible cross section $\sigma_{vis}$ of the pixel detector which is a calibration constant in the relation between rate of a quantity (clusters, coincidences) read out by the detector and the instantaneous luminosity.
 \\
 
-The instantaneous luminosity when the crossing angle between the colliding bunches is negligible and bunches collide head on is given by the following integral, \\
+The instantaneous luminosity  per bunch crossing when the crossing angle between the colliding bunches is negligible and bunches collide head on as shown in Fig.
+7 is given by the following integral, \cite{CMS-PAS-LUM-13-001} \\
 
-L = N_1 N_2 f \int^{+\infty}_{-\infty} \rho_1(x,y) \rho_2(x+\Delta x, y+ \Delta y) dx dy \\
+$L_{inst/bunch}$ = N_1 N_2 f \int^{+\infty}_{-\infty} \rho_1(x,y) \rho_2(x+\Delta x, y+ \Delta y) dx dy \\
 
@@
 
-L = N_1 N_2 f \int^{+\infty}_{-\infty} \rho_{1x}(x) \rho_{2x}(x+\Delta x)  dx   \int^{+\infty}_{-\infty} \rho_{1y}(y) \rho_{2y}(y+\Delta y)  dy \\
+$L_{inst/bunch}$ = N_1 N_2 f \int^{+\infty}_{-\infty} \rho_{1x}(x) \rho_{2x}(x+\Delta x)  dx   \int^{+\infty}_{-\infty} \rho_{1y}(y) \rho_{2y}(y+\Delta y)  dy \\
 
@@
 
-The VdM scan determines the bunch  overlap integrals $\int \rho_{x1} (x) \rho_{x2} (x+\Delta x) dx$ and  $\int \rho_{y1}(y) \rho_{y2} (y+\Delta y) dy$ by measuring pixel clusters rate as a function of bunch separation $\Delta x$ and $\Delta y$ along x and y directions as shown in Fig.
-7.
+The vdM scan determines the bunch  overlap integrals $\int \rho_{x1} (x) \rho_{x2} (x+\Delta x) dx$ and  $\int \rho_{y1}(y) \rho_{y2} (y+\Delta y) dy$ by measuring pixel clusters rate as a function of bunch separation $\Delta x$ and $\Delta y$ along x and y directions as shown in Fig.
+8.
 \\
@@
 \int \rho_{y1} (y) \rho_{y2} (y + \Delta y) dy = \frac{R_y(0)}{\int R_y(\Delta y)dy} \\
+
+where $R_x(0)$ is the measured cluster rate along x direction when the bunch separation is zero and $R_x(\Delta x)$ is the measured cluster rate when bunches are separated by distance $\Delta x$ and $R_y(0)$ is the measured cluster rate along y direction when the bunch separation is zero and $R_y(\Delta y)$ is the measured cluster rate when bunches are separated by distance $\Delta y$.
+\\
 
@@
 
-$\Sigma_x \Sigma_y = \frac{1}{2 \pi} \frac{\int R_x(\Delta x)dx \int R_y(\Delta y) dy}{R_x(0) R_y(0)}$  is the bunch overlapping area as shown in Fig. 8 by the red region.\\
+$\Sigma_x \Sigma_y = \frac{1}{2 \pi} \frac{\int R_x(\Delta x)dx \int R_y(\Delta y) dy}{R_x(0) R_y(0)}$  is the bunch overlapping area as shown in Fig. 9 by the red region.\\
 
-Thus, the expression for instantaneous luminosity is given by \\
+\newpage Thus, the expression for instantaneous luminosity is given by \\
 
-L = $\frac{N_1 N_2 f}{2\pi \Sigma_x \Sigma_y}$ \\
+$L_{inst/bunch}$ = $\frac{N_1 N_2 f}{2\pi \Sigma_x \Sigma_y}$ \\
 
@@
 
+where R = $\frac{d}{dt} <N_{cluster}>$  is cluster rate.\\
+
 \begin{figure}[H]
   \centering
-  \includegraphics[width=0.7\columnwidth]{./vdmfit.png}
-  \caption{ \onehalfspacing Example vdM scans for PCC for BCID 41, from the last scan pair in fill 4954, showing the rate normalized by the product of beam currents as a function of the beam separation $\Delta x$ and $\Delta y$ in the x (left) and y (right) direction, and the fitted curves.
-The purple curve shows the overall double-Gaussian fit, while the blue, yellow, and green curves show the first and second Gaussian components and the constant component, respectively.
-The lower panels display the difference between the measured and fitted values
-divided by the statistical uncertainty\cite{}.}
+  \includegraphics[width=0.6\columnwidth]{./LHCReport_1_image_cut.png}
+  \caption{ \onehalfspacing Diagram showing colliding bunches in each LHC beam separated by 25ns.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.7\columnwidth]{./vdm_ratefit.png}
+  \caption{ \onehalfspacing Cluster rate profile fit during vdM scans as a function of bunch separation $\Delta x$ and $\Delta y$ along x and y directions. \cite{CMS-PAS-LUM-15-001}.}
   \label{fig:CMS}
@@
   \includegraphics[width=\columnwidth]{./vdm_image.png}
-  \caption{\onehalfspacing Figure showing two LHC bunches in green and blue approaching each other and colliding giving rise to an overlapping region showing in red whose area is determined during VdM scans.}
+  \caption{\onehalfspacing Figure showing two LHC bunches in green and blue approaching each other and colliding giving rise to an overlapping region showing in red whose area is determined during vdM scans.}
   \label{fig:CMS}

### 2021-05-19 project_ashish_monograph/LHC.tex
monograph updated

@@
 2 \cite{CMS:2018elu}.
-At the end of Run 3, we expect to achieve an integrated luminosity  of $300 \:fb^{-1}$ while Phase 2 HL-LHC is expected to collect $3000 \:fb^{-1}$ of data as shown in Fig.
+At the end of Run 3, we expect to achieve an integrated luminosity  of $300 \:fb^{-1}$ while Phase II HL-LHC is expected to collect $3000 \:fb^{-1}$ of data as shown in Fig.
 3 thereby increasing luminosity by a factor of 10 beyond the LHC's design value \cite{Dainese:2019rgk}.

### 2021-05-19 project_ashish_monograph/PCC.tex
monograph updated

@@
 Position of a cluster in X and Y directions are obtained by fitting X and Y projections to templates that are estimates for cluster shapes \cite{Chatrchyan:2014fea}.
+\\
+
+1. Run2018A \\
+
+Run number ranges from 315255 to 316995 \\
+Number of runs per period is 146 \\
+
+2. Run2018B\\
+
+Run number ranges from 317080 to 319311\\
+Number of runs per period is 132\\
+
+3. Run2018C\\
+
+Run number ranges from 319337 to 320065\\
+Number of runs per period is 88 \\
+
+The veto lists corresponds to second Run2018D and select each detector part L2, L3, L4, D1, D2, D3 \cite{vetolist}. \\
+
+1. vetolateRunDlowcuttight (Number of vetoed modules 1387) \\
+2. vetolateRunDlowcuttightB1 (Number of vetoed modules 1850)\\
+3. vetolateRunDlowcuttightB2 (Number of vetoed modules 1766)\\
+4. vetolateRunDlowcuttightB3 (Number of vetoed modules 1641)\\
+5. vetolateRunDlowcuttightF1 (Number of vetoed modules 1813)\\
+6. vetolateRunDlowcuttightF2 (Number of vetoed modules 1799)\\
+7. vetolateRunDlowcuttightF3 (Number of vetoed modules 1800)\\
 

### 2021-05-19 project_ashish_monograph/results.tex
monograph updated

@@
 
-The stability of luminosity determination using pixel detector based on PCC method is investigated using late Run2018D veto list.
+The stability of CMS integrated luminosity for Phase I pixel detector calculated using PCC method is investigated using late Run2018D veto list.
 
@@
   \includegraphics[width=0.52\columnwidth]{./316993.png}
-  \caption{Top: Bunch crossing id (bcid) and PCC lumi as a function of lumi section (1 lumi section is 23.36s).
-Bottom: PCC lumi as a function of lumi section (late RunD veto list is used) for run 2018A.}
+  \caption{Top: Bunch crossing id (bcid) and PCC luminosity as a function of lumi section (1 lumi section is 23.36s).
+Bottom: PCC lumi as a function of lumi section using late run 2018D veto list for run 2018A.}
   \label{fig:CMS}
@@
   \includegraphics[width=0.52\columnwidth]{./ls_lumi.png}
-  \caption{PCC luminosity ($\mu b^{-1}$) as a function of lumi section (1 lumi section is 23.36s).}
+  \caption{PCC luminosity ($\mu b^{-1}$) as a function of luminosity section (1 lumi section is 23.36s).}
   \label{fig:CMS}
@@
   \includegraphics[width=0.52\columnwidth]{./319270.png}
-  \caption{Top: Bunch crossing id (bcid) and PCC lumi as a function of lumi section. Bottom: PCC lumi as a function of lumi section (late RunD veto list is used) for run 2018B.}
+  \caption{Top: Bunch crossing id (bcid) and PCC luminosity as a function of lumi section. Bottom: PCC lumi as a function of lumi section using late run 2018D veto list for run 2018B.}
   \label{fig:CMS}
@@
   \includegraphics[width=0.5\columnwidth]{./320061.png}
-  \caption{Top: Bunch crossing id (bcid) and PCC lumi as a function of lumi section. Bottom: PCC lumi as a function of lumi section (late RunD veto list is used) for run 2018C.}
+  \caption{Top: Bunch crossing id (bcid) and PCC luminosity as a function of lumi section. Bottom: PCC lumi as a function of lumi section using late run 2018D veto list for run 2018C.}
   \label{fig:CMS}

### 2021-05-19 project_ashish_monograph/syst.tex
monograph updated

@@
 
-Systematic uncertainties in the bunch overlap widths along x and y directions measured during vdM scans, $\sigma_{vis}$ and CMS luminosity can arise from length scale calibration, orbit drift, x-y correlations of bunch proton density function, emittance growth, bunch-bunch deflection, dynamic $\beta$ which tells us whether bunches are narrow or wide, bunch current calibration, ghosts and satellites, scan to scan variation and bunch to bunch variation.
+Systematic uncertainties in the beam overlap widths along x and y directions measured during vdM scans, $\sigma_{vis}$ and CMS luminosity can arise from length scale calibration, orbit drift, XY correlations of beam proton density distribution function, emittance growth, beam-beam deflection, dynamic $\beta$ which tells us whether bunches are narrow or wide, beam current calibration, ghosts and satellites, scan to scan variation and bunch to bunch variation.
 Systematic uncertainty during physics runs (high pileup) can be due to cross-detector consistency, afterglow effects, linearity and CMS deadtime.
@@
 
+\textbf{Systematics uncertainties during vdM scans or in $\bf{\sigma_{vis}}$:} \\
+
 1.
-Length scale calibration:  Value of the separation derived from currents in the corrector magnets, calibrated against central tracking system and compare luminous region information (vertices distribution) versus nominal separation.
+Length scale calibration: Acurracy of the beam positions from the LHC magnetic currents is limited that is why length scale calibration is done in which beams are moved in forward and backward directions at constant separation.
+A linear fit between the measured position and nominal position is plotted and deviation of the slope of this curve from one is used as correction.
 \\
@@
 2.
-Emittance growth: Bunches size are known to increase in size during the fill.
-Effect is sizable during the ~30 minutes, Bias almost negligible if emittance grows linearly with time and if measurement are made in between X and Y scans.
+Emittance growth: Beam size is known to increase during the fill which affects the cluster rate profile amplitude, its width and luminosity.
+Their variation is studied as a function of time and a linear fit is performed to obtain correction.
+Effect is sizable during a period of 30 minutes.
 \\
@@
 3.
-Orbit drift: The beams can slowly drift in the transverse plane.
-This effect is typically small but can be harmful in some cases.
-Drift of the orbit estimated by BPM measurements taken between scans and extrapolated to interaction point.
+Orbit drift: Beams can slowly drift from their nominal positions in the transverse plane which causes beam separation to vary over a period of vdM scan step.
+LHC beam position monitoring systems are used to correct for beam separation.
 \\
@@
 4.
-xy-correlations: The vdM scan method assumes that the bunch proton density function is factorizable into independent x- and y-dependent terms which is not fully true and can lead to a biased estimate of the bunch overlap area.
-In order to measure this effect, special beam imaging scans are conducted.
-In these scans, the measured vertex position distributions are used to derive the bunch proton densities, which can then be used to estimate a correction to the visible cross section $\sigma_{vis}$.
+XY correlations: The vdM scan method assumes that the shape of the bunch proton density function is factorizable into independent X and Y dependent terms which is not fully true and can lead to a biased estimate of the bunch overlap area $\Sigma_x \Sigma_y$.
+In order to measure this effect, special beam imaging scans are conducted in which one beam is fixed and other beam is moved across.
+In these scans, the measured vertex position distributions are used to derive the beam proton densities where Super Double Gaussian function is used as best fit and correction to the visible cross section $\sigma_{vis}$ is estimated.
 \\
 
-5. Linearity: \\
+5. Beam-Beam Effects: \\
 
-6. Stability:  \\
+Dipolar kick (beam-beam deflection): Repulsive force due to beam's electric field deflects other beam which affect nominal separation, the beam width and beam current. \\
+Quadrupolar defocusing (dynamic $\beta$): Beam can get defocused by other beam's magnetic quadrupole field.
+Effective beam width is modified depending on the separation which in turn affects the peak instantaneous luminosity value because collision rate is decreased by 10 \%.
+\\
 
-7. Bunch-Bunch Effects: \\
+\newpage
+\textbf{Systematics uncertaintities during physics runs (high pileup)}:\\
 
-Dipolar kick (bunch-bunch deflection): Repulsive force deflects beams affecting nominal separation depends on the separation itself, the beam width and the current. \\
+6.
+Non-Linearity: extrapolation of $\sigma_{vis}$ from vdM scans to high pileup physics data-taking periods can cause it to vary with per bunch instantaneous luminosity and pileup if the relation between luminosity and pileup is not linear.
+\\
 
- Quadrupolar (de)focusing (dynamic $\beta$): Effective beam width is modified depending on the separation which in turn affects the peak luminosity (rate) value. \cite{CMS-PAS-LUM-18-002} \\
+7.
+Stability: Instability can arise from variation of measured cluster rate over time for different subdetectors in pixel detector and change of detector conditions over time for example detector noise, aging effects, radiation damage, etc.
+Results for PCC luminosity stability for 2018 data is described in the next section.
+\\
+
+8.
+Cross-detector comparisons: After corrections of out-of-time effects and efficiency changes monitored by emittance scans, residual effects are evaluated by cross-detector comparison.
+\\
+
+8. Afterglow effects: A small out of time response appears in unfilled bunches after colliding bunches. These effects are described in detail in the previous section \cite{CMS-PAS-LUM-18-002}.

### 2021-05-19 project_ashish_monograph/upgrade.tex
monograph updated

@@
 
-Instantaneous luminosity determination using PCC method for Phase II HL-LHC can be based on counting the number of clusters or coincidences.
+Instantaneous luminosity determination using PCC method for Phase II HL-LHC will be based on counting the number of clusters or coincidences.
 The innermost ring of the last disk of TEPX (D4R1) is located at 2.65 m away from the interaction point that is beyond the tracking acceptance ($|\eta| = 4$) and as this region has few tracking points, it can be solely used for the purpose of luminosity measurement by using the full available trigger rate and bandwidth.
@@
 Luminosity calculated based on counting coincidences has an advantage over clusters that afterglow effects are tiny in the case of coincidences.
-\cite{Collaboration:2706512} \\
+\cite{Collaboration:2706512} \cite{brilsim} \cite{brilsim1}\cite{brilsim2}\\
 
@@
 
-\newpage Linearity indicates that the PCC visible cross section $\sigma_{vis}$ does not depend on the per bunch instantaneous luminosity (ideal luminometer).
+Linearity indicates that the PCC visible cross section $\sigma_{vis}$ does not depend on the per bunch instantaneous luminosity (ideal luminometer).
 In ideal scenario, $\sigma_{vis}$ is not dependent on pileup, but this a potential problem with the luminometer.
@@
   \includegraphics[width=1 \columnwidth]{./fourlayers.png}
-  \caption{ \onehalfspacing Fours layers of one double disk of TEPX showing module arrangement in rings for all layers.}
+  \caption{ \onehalfspacing Fours layers of one double disk of TEPX showing module arrangement in rings for each layer.}
   \label{fig:CMS}

### 2021-05-19 project_ashish_monograph/results.tex
monograph updated

--- 2021-05-14 project_ashish_monograph/results.tex
@@
-\section{Results}
+\newpage \section{Results}
 \label{sec:results}
+
+The stability of CMS integrated luminosity for Phase I pixel detector calculated using PCC method is investigated using late Run2018D veto list.
 
@@
   \includegraphics[width=0.52\columnwidth]{./316993.png}
-  \caption{Top: Bunch crossing id (bcid) and PCC lumi as a function of lumi section. Bottom: PCC lumi as a function of lumi section (late RunD veto list is used) for run 2018A.}
+  \caption{Top: Bunch crossing id (bcid) and PCC luminosity as a function of lumi section (1 lumi section is 23.36s).
+Bottom: PCC lumi as a function of lumi section using late run 2018D veto list for Run2018A.}
   \label{fig:CMS}
@@
   \includegraphics[width=0.52\columnwidth]{./ls_lumi.png}
-  \caption{PCC luminosity as a function of lumi section.}
+  \caption{PCC luminosity ($\mu b^{-1}$) as a function of luminosity section (1 lumi section is 23.36s) for Run2018A.}
   \label{fig:CMS}
@@
   \includegraphics[width=0.52\columnwidth]{./runs.png}
-  \caption{PCC luminosity as a function of run number.}
+  \caption{PCC luminosity ($\mu b^{-1}$) as a function of run number for Run2018A.}
   \label{fig:CMS}
@@
   \includegraphics[width=0.52\columnwidth]{./ProfileXcombined_new.png}
-  \caption{X Profile of luminosity ratio vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section.}
+  \caption{X Profile of luminosity ratios vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section (1 lumi section is 23.36s) for Run2018A.}
   \label{fig:CMS}
@@
   \includegraphics[width=0.52\columnwidth]{./319270.png}
-  \caption{Top: Bunch crossing id (bcid) and PCC lumi as a function of lumi section. Bottom: PCC lumi as a function of lumi section (late RunD veto list is used) for run 2018B.}
+  \caption{Top: Bunch crossing id (bcid) and PCC luminosity as a function of lumi section. Bottom: PCC lumi as a function of lumi section using late run 2018D veto list for Run2018B.}
   \label{fig:CMS}
@@
   \includegraphics[width=0.52\columnwidth]{./ls_lumi_2018B.png}
-  \caption{PCC luminosity as a function of lumi section.}
+  \caption{PCC luminosity as a function of lumi section for Run2018B.}
   \label{fig:CMS}
@@
   \includegraphics[width=0.52\columnwidth]{./runs_2018B.png}
-  \caption{PCC luminosity as a function of run number.}
+  \caption{PCC luminosity as a function of run number for Run2018B.}
   \label{fig:CMS}
@@
   \includegraphics[width=0.5\columnwidth]{./ProfileXcombinedB_new.png}
-  \caption{X Profile of luminosity ratio vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section.}
+  \caption{X Profile of luminosity ratios vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section for Run2018B.}
   \label{fig:CMS}
@@
   \includegraphics[width=0.5\columnwidth]{./320061.png}
-  \caption{Top: Bunch crossing id (bcid) and PCC lumi as a function of lumi section. Bottom: PCC lumi as a function of lumi section (late RunD veto list is used) for run 2018C.}
+  \caption{Top: Bunch crossing id (bcid) and PCC luminosity as a function of lumi section. Bottom: PCC lumi as a function of lumi section using late run 2018D veto list for Run2018C.}
   \label{fig:CMS}
@@
   \includegraphics[width=0.5\columnwidth]{./ls_lumi_2018C.png}
-  \caption{PCC luminosity as a function of lumi section.}
+  \caption{PCC luminosity as a function of lumi section for Run2018C.}
   \label{fig:CMS}
@@
   \includegraphics[width=0.5\columnwidth]{./runs_2018C.png}
-  \caption{PCC luminosity as a function of run number.}
+  \caption{PCC luminosity as a function of run number for Run2018C.}
   \label{fig:CMS}
@@
   \includegraphics[width=0.5\columnwidth]{./2018C_lumiratio.png}
-  \caption{Luminosity ratios for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018C. }
+  \caption{Luminosity ratios for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018C.}
   \label{fig:CMS}
@@
   \includegraphics[width=0.5\columnwidth]{./ProfileXcombinedC_new.png}
-  \caption{X Profile of luminosity ratio vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section.}
+  \caption{X Profile of luminosity ratios vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section for Run2018C.
+\cite{lumidpg}}
   \label{fig:CMS}

### 2021-05-19 project_ashish_monograph/PCC.tex
monograph updated

--- 2021-05-19 project_ashish_monograph/PCC.tex
@@
 
+LHC 2018 run can be categorized as follows, \\
+
+1. Run2018A \\
+
+Run number ranges from 315255 to 316995 \\
+Number of runs per period is 146 \\
+
+2. Run2018B\\
+
+Run number ranges from 317080 to 319311\\
+Number of runs per period is 132\\
+
+3. Run2018C \\
+
+Run number ranges from 319337 to 320065\\
+Number of runs per period is 88 \\
+
+Modules which are observed to function efficiently are considered for luminosity calculation.
+The module veto lists correspond to second Run2018D and select each detector part L2, L3, L4, D1, D2 and D3.
+Barrel layer 1 (L1) is not used for luminosity determination \cite{vetolist}.
+\\
+
+1. veto lateRunD lowcut tight   (Number of vetoed modules 1387) \\
+2. veto lateRunD lowcut tight B1 (Number of vetoed modules 1850)\\
+3. veto lateRunD lowcut tight B2 (Number of vetoed modules 1766)\\
+4. veto lateRunD lowcut tight B3 (Number of vetoed modules 1641)\\
+5. veto lateRunD lowcut tight F1 (Number of vetoed modules 1813)\\
+6. veto late RunD lowcut tight F2 (Number of vetoed modules 1799)\\
+7. veto late RunD lowcut tight F3 (Number of vetoed modules 1800)\\
+
 Specific techniques are employed for the reconstruction of clusters in the pixel detector and all the reconstructed clusters are used for counting to calculate the instantaneous luminosity.
@@
 Position of a cluster in X and Y directions are obtained by fitting X and Y projections to templates that are estimates for cluster shapes \cite{Chatrchyan:2014fea}.
+\\
 

### 2021-05-19 project_ashish_monograph/bkg.tex
references/figures updated
monograph updated

--- 2021-05-14 project_ashish_monograph/bkg.tex
@@
-\newpage \section{Backgrounds}
+\section{Backgrounds}
 \label{sec:bkg}
@@
 
-N= \sigma \:L + N_{background} \\
+The cluster rate equation is modified in the presence of background events. \\
 
-L = $ \int L_{inst} \: dt = \int \frac{R(t)}{\sigma_{vis}} \:dt $  \\
+N = \sigma \:L_{int} + N_{background} \\
+
+L_{int} = $ \int L_{inst} \: dt = \int \frac{R(t)}{\sigma_{vis}} \:dt $  \\
 
@@
 
-N: total number of event including signal and background. \\
+N: total number of signal and background events. \\
 
@@
 
+$L_{inst}$: instantaneous luminosity.\\
+
+$L_{int}$: integrated luminosity. \\
+
 $\sigma_{vis}$: PCC visible cross section.\\
@@
 
-s: center of mass energy of colliding protons. \\
+s: center-of-mass energy of colliding protons. \\
 
@@
 
-$L_{inst}$: instantaneous luminosity.\\
+$N_{background}$ need to be subtracted during vdM scans for precise determination of $\sigma_{vis}$.
+During high pileup physics runs, background contribution to instantaneous luminosity/$\sigma_{vis}$ based on the pixel cluster counting (PCC) method arises from a small out-of-time response (OOTR, or afterglow) that has two types.\\
 
-The pixel cluster counting (PCC) method produces a small out-of-time response (OOTR, or afterglow) that has two types.\\
+Type I: fake hits in the bunch crossing after the colliding bunches (signal charge spillover).\\
 
-Type 1: fake hits in the bunch crossing after the colliding bunches (signal charge spillover).\\
+Type II: Activated material in the detector due to the large radiation doses, exponentially decays for many bunch crossings.\\
 
-Type 2: Activated material in the detector due to the large radiation doses, exponentially decays for many bunch crossings.\\
+Fig.
+11 shows the afterglow noise induced by one colliding bunch.
+Since the distribution is normalized to 1 at the first bin it means the first bin is the colliding bunch.
+The values at bins $>$ 1 are the cluster counts observed for bunches after the colliding bunch divided by the cluster counts observed by the colliding bunch.
+There are three parts to this distribution: \\
 
-Afterglow effects are tiny in the case of tracklets (2x and 3x coincidences).\\
+(i) bin 1 is the colliding bunch \\
 
-Due to both the late-arriving particles and energy originating from activated detector material, the pixel data need to be corrected for afterglow effects.
-This effect was studied in data taken using random triggers (triggers that fire randomly in bunch crossings spread over the whole LHC orbit except for the abort gap), considering the pixel cluster counts in bunch crossings after bunch trains.
-The resulting correction depends on the LHC filling scheme and for a typical 2011 fill with 1380 bunches corresponds to a subtraction of close to 2.8$\%$ of the integrated luminosity per luminosity section.
+(ii) bin 2 (empty bunch) is the bunch after colliding bunch, noise observed is due to electronics signal on same pixels from colliding bunch. This is Type I afterglow effect. \\
+
+(iii) bins greater than 2 are all empty bunches.
+Noise observed is due to "albedo" which is material activated by the radiation of the collisions, it decays exponentially with time just like radioactive material.
+It produces secondary particles which create hits late in time.
+This is called Type II afterglow effect.
 \\
 
-The afterglow corrections for PCC during 2017 run are in the range 2-5 $\%$ for the Type 1 corrections and 2-3 $\%$ averaged over all active bunches for the Type 2 corrections.
+ Afterglow effects for various bunches in a beam is shown in Fig.
+12 where the intial rising curve correspong to Type I and decay curve correspond to Type II afterglow effect.
+It was studied in data taken using random triggers (triggers that fire randomly in bunch crossings spread over the whole LHC orbit except for the abort gap), considering the pixel cluster counts in bunch crossings after bunch trains.
+The resulting correction depends on the LHC filling scheme and for a typical 2011 fill with 1380 bunches corresponds to a subtraction of close to 2.8$\%$ of the integrated luminosity per lumi section.
+The afterglow corrections for PCC during 2017 run are in the range 2-5 $\%$ for the Type I corrections and 2-3 $\%$ averaged over all active bunches for the Type II corrections \cite{Sirunyan:2759951}.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./PCC_background.png}
+  \caption{ \onehalfspacing \cite{}.}
+  \label{fig:CMS}
+\end{figure}
 
@@
 
-Fig.
-7 shows the afterglow noise induced by one colliding bunch.
-Since it is normalized to 1 at the first bin it means the first bin is the colliding bunch.
-The values at bins $>$ 1 are the cluster counts observed for bunches after the colliding bunch divided by the cluster counts observed by the colliding bunch.
-There are three parts to this distribution: \\
-
-bin 1: colliding bunch \\
-
-bin 2 (empty bunch): bunch after colliding bunch, noise observed is due to electronics signal on same pixels from colliding bunch. This is called Type 1. \\
-
-bins $>$ 2 (empty bunches): noise observed is due to "albedo" which is material activated by the radiation of the collisions, it decays exponentially with time just like radioactive material.
-It produces secondary particles which create hits late in time.
-This is called Type 2.
-
 \begin{figure}[H]
@@
   \includegraphics[width=0.5\columnwidth]{./afterglow.png}
-  \caption{Results of the pixel afterglow 'deconvolution fit'}
+  \caption{Results of the pixel afterglow fit.}
   \label{fig:LHC}
 \end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.6\columnwidth]{./PCC_background.png}
-  \caption{ \onehalfspacing \cite{}.}
-  \label{fig:CMS}
-\end{figure}

### 2021-05-19 project_ashish_monograph/syst.tex
monograph updated

@@
 
-\newpage
 \textbf{Systematics uncertaintities during physics runs (high pileup)}:\\
@@
 6.
-Non-Linearity: extrapolation of $\sigma_{vis}$ from vdM scans to high pileup physics data-taking periods can cause it to vary with per bunch instantaneous luminosity and pileup if the relation between luminosity and pileup is not linear.
+Non-Linearity: extrapolation of $\sigma_{vis}$ from vdM scans to high pileup physics data-taking periods can cause $\sigma_{vis}$ to vary with per bunch instantaneous luminosity and pileup if the relation between luminosity and pileup is not linear.
 \\

### 2021-05-19 project_ashish_monograph/vdM.tex
monograph updated

@@
-\newpage \section{van der Meer calibration}
+ \section{van der Meer calibration}
 \label{sec:vdm}
@@
 
-\newpage Thus, the expression for instantaneous luminosity is given by \\
+Thus, the expression for instantaneous luminosity is given by \\
 
@@
   \includegraphics[width=\columnwidth]{./vdm_image.png}
-  \caption{\onehalfspacing Figure showing two LHC bunches in green and blue approaching each other and colliding giving rise to an overlapping region showing in red whose area is determined during vdM scans.}
+  \caption{\onehalfspacing Figure showing two LHC bunches in green and blue approaching each other and colliding giving rise to an overlapping region shown in red whose area is determined during vdM scans.}
   \label{fig:CMS}

### 2021-05-19 project_ashish_monograph/results.tex
monograph updated
updated

@@
 
-The stability of CMS integrated luminosity for Phase I pixel detector calculated using PCC method is investigated using late Run2018D veto list.
+The stability of run 2018 CMS integrated luminosity for Phase I pixel detector calculated using PCC method is investigated by employing late Run2018D veto list.
 

### 2021-05-19 project_ashish_monograph/syst.tex
updated

@@
 
-8.
-Cross-detector comparisons: After corrections of out-of-time effects and efficiency changes monitored by emittance scans, residual effects are evaluated by cross-detector comparison.
-\\
+8. Afterglow effects: A small out of time response appears in unfilled bunches after colliding bunches. These effects are described in detail in the previous section. \\
 
-8. Afterglow effects: A small out of time response appears in unfilled bunches after colliding bunches. These effects are described in detail in the previous section \cite{CMS-PAS-LUM-18-002}.
+9.
+Cross-detector comparisons: After corrections of out-of-time effects (afterglow), stability and linearity are applied, luminosity measurement from various detector like BCM1F, PLT and HFOC can be compared to do very precise luminosity determination by taking into account exact corrections \cite{CMS-PAS-LUM-18-002}.

### 2021-05-19 project_ashish_monograph/CMS.tex
updated

@@
 
-The CMS Run 2 pixel detector consists of four concentric barrel layers (L1-L4) at radii of 29, 68, 109 and 160 mm and three disks (D1-D3) on each end at distances of 291, 396, and 516 mm from the center of the detector.
+The CMS Run 2 pixel detector consists of four concentric barrel layers (L1-L4) at radii of 29, 68, 109 and 160 mm and three forward disks (D1-D3) on each end at distances of 291, 396, and 516 mm from the center of the detector.
 It is built from 1856 segmented silicon sensor modules, where 1184 modules are used in the barrel pixel detector (BPIX) and 672 modules are used for the forward disks (FPIX) .

### 2021-05-19 project_ashish_monograph/PCC.tex
updated

@@
 
-LHC 2018 run can be categorized as follows, \\
+LHC 2018 run is divided into A, B, C and D as described below. \\
 
@@
 
+4.Run2018D \\
+
+Run number ranges from 320500 to 323699 \\
+Number of runs per period is 262 \\
+
+5. late Run2018D \\
+
+Run number ranges from 320500 to 325175 \\
+Number of runs per period is 339 \\
+
 Modules which are observed to function efficiently are considered for luminosity calculation.
-The module veto lists correspond to second Run2018D and select each detector part L2, L3, L4, D1, D2 and D3.
+The module veto lists correspond to late Run2018D that select each detector part barrel layers L2, L3, L4 and forward disks D1, D2, D3.
 Barrel layer 1 (L1) is not used for luminosity determination \cite{vetolist}.

### 2021-05-23 project_ashish_monograph/CMS.tex
updated

--- 2021-05-19 project_ashish_monograph/CMS.tex
@@
 \label{sec:cms}
-(describe the experiment in general, its discovery, mention the international collaboration) \\
 
@@
 This experiment has already confirmed the discovery of the most important particle in SM, the Higgs boson which gives mass to all bosons and fermions via electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}.
-It has also detected the decay of Higgs boson to a pair of photons, W bosons, bottom quarks and muons.
+It has also detected the decay of Higgs boson to a pair of photons, W and Z bosons, bottom quarks, muons and taus.
 \\
@@
 It is placed at one of the collision points around the LHC ring and consists of Silicon tracker, Electromagnetic calorimeter, Hadron calorimeter and Muon chambers as shown in the left part of Fig.
-4.
+9.
 \\
 
-The large solenoid magnet bend charged particles and studying the path taken by these charged particles produced in proton-proton collisions using Silicon pixel detector (innermost part of CMS tracker) as they fly away from the interaction point, we can identify the charge of a particle as positive and negative charged particle tracks bend in opposite directions by the magnetic field and can also be used to calculate the momentum of the charged particle using curvature of the track as shown in the right part of Fig.
-4.
+The large solenoid magnet bend charged particles.
+Studying the path taken by these charged particles produced in proton-proton collisions using Silicon pixel detector (innermost part of CMS tracker) as they fly away from the interaction point, we can identify the charge of a particle as positive and negative charged particle tracks bend in opposite directions by the magnetic field.
+Particle trajectory can also be used to calculate the momentum of the charged particle using curvature of the track as shown in the right part of Fig.
+9.
 \\
@@
   \caption{ \onehalfspacing Left: 3D design of CMS detector showing various concentric layers.
-Right: Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimeter, superconducting solenoid and muon chambers.
-\cite{Chatrchyan:2008aa}}
+Right: Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimeter, superconducting solenoid and muon chambers \cite{Chatrchyan:2008aa}.}
   \label{fig:CMSdetector}
@@
 This feature is used to calculate the instantaneous luminosity $(L_{inst})$ by counting the number of pixel clusters which are collection of pixels hit by a track.
-The pixel detector is able to disentangle and reconstruct all the tracks left by the particles coming from the interaction point and has a long duration of 10 years.
 \\
 
-The CMS Run 2 pixel detector consists of four concentric barrel layers (L1-L4) at radii of 29, 68, 109 and 160 mm and three disks (D1-D3) on each end at distances of 291, 396, and 516 mm from the center of the detector.
-It is built from 1856 segmented silicon sensor modules, where 1184 modules are used in the barrel pixel detector (BPIX) and 672 modules are used for the forward disks (FPIX) .
+The CMS Run 2 pixel detector consists of four concentric barrel layers (L1-L4) at radii of 29, 68, 109 and 160 mm and three forward disks (D1-D3) on each end at distances of 291, 396, and 516 mm from the center of the detector as shown in the left part of Fig.
+10.
+It is built from 1856 segmented silicon sensor modules, where 1184 modules are used in the barrel pixel detector (BPIX) and 672 modules are used for the forward disks (FPIX) as shown in the right part of Fig.
+10.
+A module consists of one or two silicon sensors with 160 $\times$ 416 pixels which are small square units connected to 16 readout chips (ROCs).
 \\
 
-Each layer of the pixel detector is spilt into tiny square segments with each segment containing a silicon sensor having dimensions 100$\mu$m $\times$ 150$\mu$m as shown in the right part of Fig.
-5.
+Each layer of the pixel detector is spilt into tiny square segments with each segment called pixel containing a silicon sensor with dimensions 100$\mu$m $\times$ 150$\mu$m as shown in the right part of Fig.
+10.
 When a charged particle passes through this silicon sensor, it transfers energy to silicon atoms which causes electrons to be ejected from it creating electron-hole pairs.
@@
 The particle trajectory is deduced by knowing the hit pixels and as the pixel detector is made of two dimensional segments with four layers, we can create a three-dimensional picture of the path taken by the charged particle.
+\\
 
@@
   \caption{ \onehalfspacing Left: Layout of the CMS Run 2 pixel detector compared to the original detector layout, in longitudinal view.
-Right: pixel detector diagram showing size of silicon sensor, readout chip and data buffers.
-\cite{TrackerGroupoftheCMS:2020bgg}}
+Right: pixel detector diagram showing size of silicon sensor, readout chip and data buffers \cite{TrackerGroupoftheCMS:2020bgg}.}
   \label{fig:LHC}
 \end{figure}
+
+\subsection{Cluster reconstruction}
+Specific techniques are employed for the reconstruction of clusters in the pixel detector and all the reconstructed clusters are used for counting to calculate the instantaneous luminosity.
+Algorithm used for finding clusters check for pixels whose signal to noise ratio is more than 6 and then merge adjacent pixel.
+These algorithms estimates cluster position in two directions and cluster charge.
+A cluster is a set of adjacent pixels and only pixels above certain minimum value of charge are considered.
+Position of a cluster in X and Y directions are obtained by fitting X and Y projections to templates that are estimates for cluster shapes \cite{Chatrchyan:2014fea}.
+\\
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.6\columnwidth]{./pixel_reco.png}
+  \caption{ \onehalfspacing Diagram showing pixel cluster with charge accumulation in each pixel expressed in terms of thousands of electrons.
+Green numbers represent charge accumulation below the 2000 electron threshold which are excluded clusters.
+The dotted red line indicates the particle trajectory projection in the module plane and the red cross shows the position of true hit.}
+  \label{fig:CMS}
+\end{figure}

### 2021-05-23 project_ashish_monograph/LHC.tex
updated

@@
 \label{sec:lhc}
-(describe the accelerator complex, proton bunches, c.m. energy, all experiments, run periods, inst. and integrated lumi, Run 3 and HL-LHC plans) \\
+
+\subsection{CERN complex}
 
 \onehalfspacing CERN accelerator complex is a progression of machines namely Linac 2, Proton Synchrotron Booster (PSB), Proton Synchrotron (PS), Super Proton Synchrotron (SPS) and Large Hadron Collider (LHC) as shown in Fig.
-1 that accelerate particles mainly protons to increasingly higher energies of 50 MeV, 1.4 GeV, 25 GeV, 450 GeV and 14 TeV respectively \cite {CERNBrochure2017002Eng}.
+3 that accelerate particles mainly protons to increasingly higher energies of 50 MeV, 1.4 GeV, 25 GeV, 450 GeV and 14 TeV respectively \cite {CERNBrochure2017002Eng}.
 Each machine is used to increase the energy of particle before the beam is injected into to the next machine.
@@
 After reaching 25 GeV, protons enter SPS which further increases its energy to 450 GeV.
-The protons are finally transferred to two beam pipes of LHC kept at very high vacuum.
+The protons are finally transferred to two beam pipes of LHC kept at very high vacuum to collide at the interaction points and then proton beam is dumped after sometime (1-35 hours).
+This entire procedure defines a single LHC fill generally consisting of $10^{14}$ protons, grouped into bunches to form the proton beam as shown in Fig.
+4.
 \\
@@
 The Large Hadron Collider (LHC) is the most powerful particle accelerator in the world primarily build to collide protons and heavy ions at 7, 8, 13 and 14 TeV during different LHC run period.
-The LHC consists of a 27 kilometre ring of superconducting magnets producing strong magnetic field which is used to guide particle beams along the LHC ring.
-Proton beam made up of bunches travelling in opposite directions kept in two ultrahigh vacuum tubes are accelerated close to the speed of light using time dependent electric field produced by radiofrequency cavities before they collide at four interaction points along the LHC ring where ATLAS, ALICE, CMS and LHCb detectors are placed \cite {CERNBrochure2017002Eng}.
-\\
-
-The first proton beam was successfully maneuvered around the LHC ring in September 2008 that marked the beginning of Run 1 with proton beams colliding at 7-8 TeV center-of-mass energy and this run period ended in 2013 \cite{cmsrun} \cite{Alemany-Fernandez:1631030}.
-Run 2 started in 2015 with protons colliding at 13 TeV center-of-mass energy and continued till October 2018 \cite{Wenninger:2668326}.
-Run 3 is expected to begin at the start of March 2022 and High Luminosity (HL)-LHC phase is expected to begin in mid-2027 \cite{Dainese:2019rgk}.
-Proton Synchroton (PS) is responsible for providing proton bunches spaced 7 metres (25 ns) apart with each bunch containing more than 100 billion protons.
-The maximum number of bunches reached with the beam preparation method used during Run 2 is 2556 \cite{Wenninger:2668326}.
-The number of protons in the colliding bunches, time of separation between the bunches and effective area of the bunch which depend on the rms transverse bunch size along horizontal and vertical directions is one of the ways to calculate instantaneous luminosity (L_{inst}).
-\\
-
-Luminosity is a key performance parameter of an accelerator as it is a measure of number of collisions.
-Luminosity can be categorized into two types: instantaneous and integrated luminosity.
-Instantaneous luminosity is defined as the number of collisions occuring per second in per centimeter square area while integrated luminosity is obtained by integrating instantaneous luminosity over a time interval.
-Both are very important variables as they are used to obtain the number of collision events.
-During Run 1, peak value of LHC instantaneous luminosity was $0.77 \times 10^{34} \: cm^{-2} s^{-1} $ with $30 \: fb^{-1}$ integrated luminosity \cite{cmsrun1lumi}.
-During Run 2, LHC instantaneous luminosity reached a peak value of $2.1 \times 10^{34}  \: cm^{-2} s^{-1}$ with $163 \: fb^{-1}$ integrated luminosity as shown in Fig.
-2 \cite{CMS:2018elu}.
-At the end of Run 3, we expect to achieve an integrated luminosity  of $300 \:fb^{-1}$ while Phase II HL-LHC is expected to collect $3000 \:fb^{-1}$ of data as shown in Fig.
-3 thereby increasing luminosity by a factor of 10 beyond the LHC's design value \cite{Dainese:2019rgk}.
+The LHC consists of a 27 km ring of superconducting magnets producing strong magnetic field which is used to guide particle beams along the LHC ring.
+Proton beam is made up of bunches travelling in opposite directions kept in two ultrahigh vacuum tubes are accelerated close to the speed of light using time dependent electric field produced by radiofrequency cavities before they collide at four interaction points along the LHC ring where ATLAS, ALICE, CMS and LHCb detectors are placed \cite {CERNBrochure2017002Eng}.
 \\
@@
   \caption{\onehalfspacing Diagram of the LHC accelerator complex located in Geneva, Switzerland.
-Four interaction points are shown where the ALICE, ATLAS, LHCb and CMS detectors are stationed.
-\cite{Mobs:2684277}}
+Four interaction points are shown where the ALICE, ATLAS, LHCb and CMS detectors are stationed \cite{Mobs:2684277}.}
   \label{fig:LHC}
@@
   \centering
+  \includegraphics[width=1 \columnwidth]{./lhcfill.png}
+  \caption{ \onehalfspacing A typical operational LHC cycle which involves set up (beam is accepted from injector complex), injection (beam is injected into LHC ring in form of bunch train), ramp (current in dipole increased to reach highest energy), squeeze (bunches are squeezed to have minimum proton separation in them), adjust (separation between beams at the interaction point is removed) and stable beams (collision settings are invoked and data taking period starts) \cite{fill}.}
+  \label{fig:LHCPlans}
+\end{figure}
+
+\subsection {Run 1 and 2 of LHC}
+The first proton beam was successfully maneuvered around the LHC ring in September 2008 that marked the beginning of Run 1 with proton beams colliding at 7-8 TeV center-of-mass energy and this run period ended in 2013 \cite{cmsrun} \cite{Alemany-Fernandez:1631030}.
+Run 2 started in 2015 with protons colliding at 13 TeV center-of-mass energy and continued till October 2018 \cite{Wenninger:2668326}.
+Run 3 is expected to begin at the start of March 2022 and High Luminosity (HL)-LHC phase is expected to begin in mid-2027 \cite{Dainese:2019rgk}.
+Proton Synchroton (PS) is responsible for providing proton bunches spaced 7 metres (25 ns) apart with each bunch containing more than 100 billion protons as shown in Fig.
+5.
+The maximum number of bunches reached with the beam preparation method used during Run 2 is 2556 \cite{Wenninger:2668326}.
+The number of protons in the colliding bunches, time of separation between the bunches and effective area of the bunch which depend on the rms transverse bunch size along horizontal and vertical directions as shown in Fig.
+6 is one of the ways to calculate instantaneous luminosity $(L_{inst})$.
+The number of proton proton collisions per bunch crossing is called pileup ($\mu$).\\
+
+Rate of collision = $\sigma$ L = $(60 mb) (7.5 $\times$ 10^{34} cm^{-2} s^{-1})$ = $(60 $\times$ 10^{-3} $\times$ 10^{-24}) (7.5 $\times$ 10^{34})$ = 6000 million/s \\
+
+where $1 \:barn = 10^{-24} cm^2$ and $1 \:mb = 10^{-27} cm^2$.\\
+
+Colliding bunch rate = number of colliding bunches $\times$ LHC revolution frequency = 2800 $\times$ 11246\:Hz = 28.7\:MHz = 31.4 \:million/s \\
+
+Pileup ($\mu$) = $\frac{Rate \:\:of \:\:collision}{colliding \:\:bunch\:\: rate} = \frac{6000 \:million/s}{31.4 \:million/s}$ = 200   for HL-LHC.    \\
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.6\columnwidth]{./LHCReport_1_image_cut.png}
+  \caption{ \onehalfspacing Diagram showing colliding bunches in each LHC beam separated by 25ns.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=\columnwidth]{./vdm_image.png}
+  \caption{\onehalfspacing Figure showing two LHC bunches in green and blue approaching each other and colliding giving rise to bunch overlapping region shown in red.}
+  \label{fig:CMS}
+\end{figure}
+
+\subsection{Luminosity and Phase II HL-LHC}
+Luminosity is a key performance parameter of an accelerator as it is a measure of number of collisions.
+Luminosity can be categorized into two types: instantaneous and integrated luminosity.
+Instantaneous luminosity corresponds to the number of collisions occuring per second in per centimeter square area while integrated luminosity is obtained by integrating instantaneous luminosity over a time interval.
+Both are very important variables as they are used to obtain the number of collision events.
+During Run 1, peak value of LHC instantaneous luminosity was $0.77 \times 10^{34} \: cm^{-2} s^{-1} $ with $30 \: fb^{-1}$ integrated luminosity \cite{cmsrun1lumi}.
+During Run 2, LHC instantaneous luminosity reached a peak value of $2.1 \times 10^{34}  \: cm^{-2} s^{-1}$ with $163 \: fb^{-1}$ integrated luminosity as shown in Fig.
+7 \cite{CMS:2018elu}.
+At the end of Run 3, we expect to achieve an integrated luminosity of $300 \:fb^{-1}$ while Phase II HL-LHC is expected to collect $3000 \:fb^{-1}$ of data as shown in Fig.
+8 thereby increasing luminosity by a factor of 10 beyond the LHC's design value \cite{Dainese:2019rgk}.
+\\
+
+\begin{figure}[H]
+  \centering
   \includegraphics[width=1 \columnwidth]{./peakintlumi_run12.png}
-  \caption{\onehalfspacing Left: Instantaneous luminosity for Run 1 and Run 2 period. Right: Integrated luminosity for Run 1 and Run 2 period. \cite{lumi}}
+  \caption{\onehalfspacing Left: Instantaneous luminosity for Run 1 and Run 2 period. Right: Integrated luminosity for Run 1 and Run 2 period \cite{lumi}.}
   \label{fig:LHClumi}
@@
   \caption{ \onehalfspacing Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS1, LS2, LS3, LS4, LS5) of the LHC and luminosities.
-Red points show instantaneous luminosity $(L_{inst})$ while the blue line shows integrated luminosity.
-\cite{collaborations2019report}.}
+Red points show instantaneous luminosity $(L_{inst})$ while the blue line shows integrated luminosity \cite{collaborations2019report}.}
   \label{fig:LHCPlans}

### 2021-05-23 project_ashish_monograph/PCC.tex
updated

--- 2021-05-19 project_ashish_monograph/PCC.tex
@@
 \label{sec:pcc}
-(describe cluster reconstruction, the module selection/veto, cluster counting per bx, per LS,..) \\
 
+\subsection{Luminosity determination based on PCC}
 Pixel cluster counting (PCC)  method is an offline technique for the calculation of instantaneous luminosity $(L_{inst})$ for any LHC run period by counting the number of pixel clusters in the pixel detector (innermost segment of the CMS tracker) in a zero bias event which requires that only two bunches cross at the CMS interaction point.
-The mean number of pixel clusters can be expressed in terms of mean number of pixel clusters per proton-proton interaction and the number of proton-proton interaction per bunch crossing that is also called pileup (PU).
+The mean number of pixel clusters $<N_{cl}>$ can be expressed in terms of mean number of pixel clusters per proton-proton interaction  $<N_{cl/pp}>$ and pileup ($\mu$) assuming that clusters do not overlap which is a reasonable assumption given the fine granularity of pixel detector.
 \\
 
-$<N_{cluster}>$ = $<N_{cluster/interaction}>$ (PU)  or (PU) = $\frac{<N_{cluster}>}{<N_{cluster/interaction}>}$ \\
+$<N_{cl}> = <N_{cl/pp}> \mu$ \\
 
-The instantaneous luminosity per bunch crossing $L_{inst/bunch}$ is proportional to the number of proton-proton (pp) interactions per bunch crossing (pileup) and the proportionality constant is the ratio of  LHC orbit frequency f and the pp interaction cross section $\sigma_{interaction}(\sqrt{s})$ where s is the proton-proton collision center-of-mass energy \cite{CMS-PAS-LUM-12-001}.
+$\mu = \frac{<N_{cl}>}{<N_{cl/pp}>}$ \\
+
+The instantaneous luminosity per bunch crossing $L_{b}$ is proportional to the number of proton-proton (pp) interactions per bunch crossing (pileup) and the proportionality constant is the ratio of  LHC orbit frequency f and the pp interaction cross section $\sigma_{pp}$ \cite{CMS-PAS-LUM-12-001}.
 \\
 
-$L_{inst/bunch}$ = $\frac{f}{\sigma_{interaction}}$ (PU)  \\
-
-$L_{inst/bunch}$ = $\frac{<N_{cluster}> \: f }{<N_{cluster/interaction}> \: \sigma_{interaction}(\sqrt{s})}$ \\
+$L_{b}$ = $\frac{f}{\sigma_{pp}}$ $\mu$  or $L_{b}$ = $\frac{<N_{cl}> \: f }{<N_{cl/pp}> \: \sigma_{pp}}$ \\
 
@@
 
-$\sigma_{vis}$ = $<N_{cluster/interaction}>$  $\sigma_{interaction}(\sqrt{s})$ \\
+$\sigma_{vis}$ = $<N_{cl/pp}>$  $\sigma_{pp}$ \\
 
-\newpage Thus, instantaneous luminosity per bunch crossing is given by \\
+Thus, instantaneous luminosity per bunch crossing $L_b$ is given by \\
 
-$L_{inst/bunch}$ = $\frac{<N_{cluster}> \: \sigma_{interaction}(\sqrt{s}) \: f }{ \:\sigma_{vis} \: \sigma_{interaction}(\sqrt{s})}$ \\
+$L_{b}$ = $\frac{<N_{cl}> \: \sigma_{pp} \: f }{ \:\sigma_{vis} \: \sigma_{pp}}$ or $L_{b}$ = $\frac{<N_{cluster}> \:\: f}{\sigma_{vis}}$ \\
 
-$L_{inst/bunch}$ = $\frac{<N_{cluster}> \:\: f}{\sigma_{vis}}$ \\
-
-The PCC visible cross section $\sigma_{vis}$ is determined using van der meer scan method which is described in section 5.
-Cluster counting can be done over different time periods like 1 bunch crossing (25ns), 1 Lumi section (23.36s), 4 Lumi nibble (1.46s) and similarly instantaneous luminosity can be calculated over these time periods using PCC method.
+The PCC visible cross section $\sigma_{vis}$ is determined using van der Meer scan method which is described in section 5.
+Cluster counting can be done over different time periods like per bunch or orbit integrated, 1 Lumi section (23.36s), 4 Lumi nibble (1.46s) and similarly instantaneous luminosity can be calculated over these time periods using PCC method \cite{CMS:2018elu}.
 \\
 
-Specific techniques are employed for the reconstruction of clusters in the pixel detector and all the reconstructed clusters are used for counting to calculate the instantaneous luminosity.
-Algorithm used for finding clusters check for pixels whose signal to noise ratio is more than 6 and then merge adjacent pixel.
-These algorithms estimates cluster position in two directions and cluster charge.
-A cluster is a set of adjacent pixels and only pixels above certain minimum value of charge are considered.
-Position of a cluster in X and Y directions are obtained by fitting X and Y projections to templates that are estimates for cluster shapes \cite{Chatrchyan:2014fea}.
-\\
+\subsection{Run 2018 CMS Data} \\
 
+CMS 2018 data is a collection of runs for each fill in different periods defined during the LHC operation period.
+
+LHC 2018 run is divided into A, B, C and D as described below. \\
+\begin{flushleft}
 1. Run2018A \\
-
 Run number ranges from 315255 to 316995 \\
@@
 2. Run2018B\\
-
 Run number ranges from 317080 to 319311\\
@@
 
-3. Run2018C\\
-
+3. Run2018C \\
 Run number ranges from 319337 to 320065\\
@@
 
-The veto lists corresponds to second Run2018D and select each detector part L2, L3, L4, D1, D2, D3 \cite{vetolist}. \\
+4.Run2018D \\
+Run number ranges from 320500 to 323699 \\
+Number of runs per period is 262 \\
 
-1. vetolateRunDlowcuttight (Number of vetoed modules 1387) \\
-2. vetolateRunDlowcuttightB1 (Number of vetoed modules 1850)\\
-3. vetolateRunDlowcuttightB2 (Number of vetoed modules 1766)\\
-4. vetolateRunDlowcuttightB3 (Number of vetoed modules 1641)\\
-5. vetolateRunDlowcuttightF1 (Number of vetoed modules 1813)\\
-6. vetolateRunDlowcuttightF2 (Number of vetoed modules 1799)\\
-7. vetolateRunDlowcuttightF3 (Number of vetoed modules 1800)\\
+5. late Run2018D \\
+Run number ranges from 320500 to 325175 \\
+Number of runs per period is 339 \\
+\end{flushleft}
+
+\subsection{Pixel detector Module Selection}
+Selection of modules in pixel detector is required because module may experience dynamic inefficiency, bad module chips can stop sending data, chips may not work properly and need reconfiguring.
+Modules which are observed to function efficiently are considered for luminosity estimation.
+The module veto lists correspond to late Run2018D that select each detector part barrel layers L2, L3, L4 and forward disks D1, D2, D3 as shown in Fig.
+12 and 13.
+Barrel layer 1 (L1) is not used for luminosity determination \cite{vetolist}.
+\\
+
+\begin{flushleft}
+1. Total number of vetoed modules 1387. \\
+2. Number of vetoed modules for L2 1850.\\
+3. Number of vetoed modules for L3 1766.\\
+4. Number of vetoed modules for L4 1641.\\
+5. Number of vetoed modules for D1 1813.\\
+6. Number of vetoed modules for D2  1799.\\
+7. Number of vetoed modules for D3 1800.\\
+\end{flushleft}
 
@@
   \centering
-  \includegraphics[width=0.6\columnwidth]{./pixel_reco.png}
-  \caption{ \onehalfspacing Diagram showing pixel cluster with charge accumulation in each pixel expressed in terms of thousands of electrons.
-Green numbers represent charge accumulation below the 2000 electron threshold which are excluded clusters.
-The dotted red line indicates the particle trajectory projection in the module plane and the red cross shows the position of true hit.}
+  \includegraphics[width=0.8 \columnwidth]{./PDDisk_R12.png}
+  \caption{ \onehalfspacing Diagram showing coordinates of modules in one forward disk of pixel detector having two rings.
+FPIX 0 correspond to ring 1 and FPIX 1 to ring 2.
+Yellow regions shows coordinates of vetoed modules while white regions shows coordinates of good modules used for luminosity determination.}
   \label{fig:CMS}
 \end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1 \columnwidth]{./bpixL2-L4.png}
+  \caption{ \onehalfspacing Diagram showing z coordinate (signed module) and phi coordinate (signed ladder) of modules in three barrel layers (L2, L3 and L4) of pixel detector.
+Yellow regions shows coordinates of vetoed modules while white regions shows coordinates of good modules used in luminosity determination.
+}
+  \label{fig:CMS}
+\end{figure}

### 2021-05-23 project_ashish_monograph/bkg.tex
updated

@@
 \label{sec:bkg}
-(background in vdM, afterglow backgrounds in Physics, subtraction of these) \\
+\subsection{vdM background}
 
-The cluster rate equation is modified in the presence of background events. \\
+The cluster rate equation is modified in the presence of background events.\\
 
-N = \sigma \:L_{int} + N_{background} \\
-
-L_{int} = $ \int L_{inst} \: dt = \int \frac{R(t)}{\sigma_{vis}} \:dt $  \\
-
-\sigma = \sigma_{interaction} (\sqrt{s}) \: A \:\epsilon\\
+N = \sigma \:L_{int} + N_{bg} \\
 
@@
 
-$R(t) = \frac{d}{dt} <N_{cluster}>$ is the time dependent cluster rate. \\
+$N_{bg}$: Number of background events \\
 
-$N_{background}$: Number of background events \\
+$N_{bg}$ need to be subtracted during vdM scans for precise determination of $\sigma_{vis}$.
+These contributions to the measured cluster rate are either subtracted before the fit as measured from noncolliding, unpaired bunches or from periods during which the beams were kept at a large distance, or determined in the fit as a constant term added to the fit function as shown in Fig.
+13.
 
-$L_{inst}$: instantaneous luminosity.\\
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.7\columnwidth]{./PCC_bg.png}
+  \caption{ \onehalfspacing Visible cross section $\sigma_{vis}$ with only background subtraction.}
+  \label{fig:CMS}
+\end{figure}
 
-$L_{int}$: integrated luminosity. \\
+\subsection{High pileup physics run background}
 
-$\sigma_{vis}$: PCC visible cross section.\\
-
-$\sigma_{interaction}$ : proton-proton interaction cross section. \\
-
-s: center-of-mass energy of colliding protons. \\
-
-A: acceptance of the pixel detector. \\
-
-$\epsilon$ : efficiency of the pixel detector. \\
-
-$N_{background}$ need to be subtracted during vdM scans for precise determination of $\sigma_{vis}$.
-During high pileup physics runs, background contribution to instantaneous luminosity/$\sigma_{vis}$ based on the pixel cluster counting (PCC) method arises from a small out-of-time response (OOTR, or afterglow) that has two types.\\
+During high pileup physics runs, background contribution to instantaneous luminosity based on the pixel cluster counting (PCC) method arises from a small out-of-time response (OOTR, or afterglow) that has two types.\\
 
@@
 Fig.
-11 shows the afterglow noise induced by one colliding bunch.
+14 shows the afterglow noise induced by one colliding bunch.
 Since the distribution is normalized to 1 at the first bin it means the first bin is the colliding bunch.
-The values at bins $>$ 1 are the cluster counts observed for bunches after the colliding bunch divided by the cluster counts observed by the colliding bunch.
+The values at bins greater than 1 are the cluster counts observed for bunches after the colliding bunch divided by the cluster counts observed by the colliding bunch.
 There are three parts to this distribution: \\
@@
 
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.6\columnwidth]{./SingleBunchAfterglow.png}
+  \caption{Afterglow effect produced by a single colliding bunch.}
+  \label{fig:LHC}
+\end{figure}
+
  Afterglow effects for various bunches in a beam is shown in Fig.
-12 where the intial rising curve correspong to Type I and decay curve correspond to Type II afterglow effect.
+15 where the intial rising curve correspond to Type I and decay curve correspond to Type II afterglow effect.
 It was studied in data taken using random triggers (triggers that fire randomly in bunch crossings spread over the whole LHC orbit except for the abort gap), considering the pixel cluster counts in bunch crossings after bunch trains.
@@
 The afterglow corrections for PCC during 2017 run are in the range 2-5 $\%$ for the Type I corrections and 2-3 $\%$ averaged over all active bunches for the Type II corrections \cite{Sirunyan:2759951}.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\columnwidth]{./PCC_background.png}
-  \caption{ \onehalfspacing \cite{}.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\columnwidth]{./SingleBunchAfterglow.png}
-  \caption{Afterglow effect produced by a single colliding bunch.}
-  \label{fig:LHC}
-\end{figure}
 

### 2021-05-23 project_ashish_monograph/intro.tex
updated

\section{Introduction}
\label{sec:intro}

\subsection{Standard model of particle physics}
\onehalfspacing The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the weak nuclear force. Gravitational force is neglected as the strength of this force is very weak at the scales over which elementary particle interact with each other. The standard model (SM) of particle physics is divided into two categories, bosonic sector and fermionic sector. Bosonic sector contain particles called bosons which mediate the fundamental forces of nature and the fermionic sector contain particles called fermions which make up all the matter in our universe. SM has three generations of matter (fermions) particles. The first generation of fermions consists of up (u) quark, down (d) quark, electron and electron neutrino, second generation consist of charm (c) quark, strange (s) quark, muon and muon neutrino and the third generation of matter particles has top (t) quark, bottom (b) quark, tau and tau neutrino. The bosonic sector consist of gauge bosons like gluon, photon, $W^{\pm}$, $Z^0$ which mediate strong nuclear force, electromagnetic force and weak nuclear force respectively. There is one more particle in the standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}. All the standard model particles are shown in Figure 1. Higgs boson can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva, Switzerland. \\

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\columnwidth]{./SM.png}
  \caption{\onehalfspacing Standard model of particle physics showing matter and force carrier particles \cite{smpp}.}
  \label{fig:LHC}
\end{figure}

\subsection{Projections for Phase II High Luminosity (HL)-LHC}
LHC during the first run in 2011 and 2012 reached a peak instantaneous luminosity of 0.77 $\times$ $10^{34}$ $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 30 $fb^{-1}$ to each ATLAS and CMS. The LHC will deliver about 300 $fb^{-1}$ by 2024 \cite{collaborations2019report}. The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles. In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  place in parallel during one shutdown, at around 2023-25 (LS3), with some of the modification anticipated in 2019-2020 (LS2). This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ by the year 2036 as shown in Fig. 6. Figure 2 shows a summary of the projected uncertainties in the Higgs boson coupling parameters for Phase II HL-LHC using ggF, VBF, VH, and ${t\bar{t}H}$ production modes where luminosity is one of the dominant uncertainty in Higgs boson coupling measurement \cite{Tanabashi:2018oca}. \\

\begin{figure}[H]
  \centering
  \includegraphics[width=1 \columnwidth]{./hig_pro.png}
  \caption{\onehalfspacing Left: Main production mechanisms for the Higgs boson at the LHC: gluon-gluon fusion (ggF), vector-boson fusion (VBF), associated vector boson (VH), associated top-quark pair (ttH), and associated single-top quark production (tH). Right: Expected uncertainties on the Higgs coupling parameters for 3000 $fb^{-1}$ of proton-proton collision data at 13 TeV center-of-mass energy \cite{Tanabashi:2018oca}.}
  \label{fig:LHC}
\end{figure}

### 2021-05-23 project_ashish_monograph/results.tex
updated

--- 2021-05-19 project_ashish_monograph/results.tex
@@
-\newpage \section{Results}
+\section{Results}
 \label{sec:results}
 
-The stability of CMS integrated luminosity for Phase I pixel detector calculated using PCC method is investigated using late Run2018D veto list.
+\subsection{PCC count and luminosity}
 
@@
   \centering
-  \includegraphics[width=0.52\columnwidth]{./316993.png}
-  \caption{Top: Bunch crossing id (bcid) and PCC luminosity as a function of lumi section (1 lumi section is 23.36s).
-Bottom: PCC lumi as a function of lumi section using late run 2018D veto list for run 2018A.}
+  \includegraphics[width=1\columnwidth]{./crop.png}
+  \caption{PCC luminosity ($\mu b^{-1}$) and PCC/hfoc luminosity ratio for Run2018A using late Run2018D veto list for pixel detector modules.}
   \label{fig:CMS}
@@
   \centering
+  \includegraphics[width=1\columnwidth]{./317438(1).png}
+  \caption{PCC luminosity ($\mu b^{-1}$) and PCC/hfoc luminosity ratio for Run2018B using late Run2018D veto list for pixel detector modules.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{./319659.png}
+  \caption{PCC luminosity ($\mu b^{-1}$) and PCC/hfoc luminosity ratio for Run2018C using late Run2018D veto list for pixel detector modules.}
+  \label{fig:CMS}
+\end{figure}
+
+PCC cluster counts and calculated integrated luminosity after applying luminosity calibration (visible cross section) for Run2018 A, B and C are shown below.
+
+ \begin{figure}[H]
+  \centering
   \includegraphics[width=0.52\columnwidth]{./ls_lumi.png}
-  \caption{PCC luminosity ($\mu b^{-1}$) as a function of luminosity section (1 lumi section is 23.36s).}
+  \caption{PCC count as a function of luminosity section (1 lumi section is 23.36s) for Run2018A.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./ls_lumi_2018B.png}
+  \caption{PCC count as a function of lumi section for Run2018B.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{./ls_lumi_2018C.png}
+  \caption{PCC count as a function of lumi section for Run2018C.}
   \label{fig:CMS}
@@
   \includegraphics[width=0.52\columnwidth]{./runs.png}
-  \caption{PCC luminosity ($\mu b^{-1}$) as a function of run number.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.52\columnwidth]{./2018A_lumiratio.png}
-  \caption{Luminosity ratios for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018A.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.52\columnwidth]{./ProfileXcombined_new.png}
-  \caption{X Profile of luminosity ratios vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section (1 lumi section is 23.36s).}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.52\columnwidth]{./319270.png}
-  \caption{Top: Bunch crossing id (bcid) and PCC luminosity as a function of lumi section. Bottom: PCC lumi as a function of lumi section using late run 2018D veto list for run 2018B.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.52\columnwidth]{./ls_lumi_2018B.png}
-  \caption{PCC luminosity as a function of lumi section.}
+  \caption{PCC integrated luminosity ($\mu b^{-1}$) as a function of run number for Run2018A.}
   \label{fig:CMS}
@@
   \includegraphics[width=0.52\columnwidth]{./runs_2018B.png}
-  \caption{PCC luminosity as a function of run number.}
+  \caption{PCC integrated luminosity ($\mu b^{-1}$) as a function of run number for Run2018B.}
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=0.52\columnwidth]{./2018B_lumiratio.png}
-  \caption{Luminosity ratios for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018B.}
+  \includegraphics[width=0.52\columnwidth]{./runs_2018C.png}
+  \caption{PCC integrated luminosity ($\mu b^{-1}$) as a function of run number for Run2018C.}
+  \label{fig:CMS}
+\end{figure}
+
+\subsection{Stability of PCC luminosity for Run 2018 data}
+
+The stability of run 2018 CMS integrated luminosity for Phase I pixel detector calculated using PCC method is investigated by employing late Run2018D veto list and including afterglow effects.
+New module selections will be determined and used for 2018 luminosity determination.
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{./t25ld-kgsjf.png}
+  \caption{Left: Luminosity ratios for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018A.
+Right: X Profile of luminosity ratios vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section (1 lumi section is 23.36s) for Run2018A.}
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./ProfileXcombinedB_new.png}
-  \caption{X Profile of luminosity ratios vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section.}
+  \includegraphics[width=1\columnwidth]{./tjag3-rger6.png}
+  \caption{Left: Luminosity ratios for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018B.
+Right: X Profile of luminosity ratios vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section for Run2018B.
+}
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./320061.png}
-  \caption{Top: Bunch crossing id (bcid) and PCC luminosity as a function of lumi section. Bottom: PCC lumi as a function of lumi section using late run 2018D veto list for run 2018C.}
+  \includegraphics[width=1\columnwidth]{./tfkx3-uyzgt.png}
+  \caption{Left: Luminosity ratios for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018C.
+Right: X Profile of luminosity ratios vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section for Run2018C \cite{lumidpg}.}
   \label{fig:CMS}
 \end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\columnwidth]{./ls_lumi_2018C.png}
-  \caption{PCC luminosity as a function of lumi section.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\columnwidth]{./runs_2018C.png}
-  \caption{PCC luminosity as a function of run number.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\columnwidth]{./2018C_lumiratio.png}
-  \caption{Luminosity ratios for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018C. }
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\columnwidth]{./ProfileXcombinedC_new.png}
-  \caption{X Profile of luminosity ratios vs lumi section graph for various subdetectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section.
-\cite{lumidpg}}
-  \label{fig:CMS}
-\end{figure}

### 2021-05-23 project_ashish_monograph/syst.tex
updated

@@
-\section{Systematics}
+\section{Systematic uncertainties in luminosity measurement}
 \label{sec:syst}
-(main systematics: vdM, non-linearity, stability, check others in the PAS) \\
 
-Systematic uncertainties in the beam overlap widths along x and y directions measured during vdM scans, $\sigma_{vis}$ and CMS luminosity can arise from length scale calibration, orbit drift, XY correlations of beam proton density distribution function, emittance growth, beam-beam deflection, dynamic $\beta$ which tells us whether bunches are narrow or wide, beam current calibration, ghosts and satellites, scan to scan variation and bunch to bunch variation.
-Systematic uncertainty during physics runs (high pileup) can be due to cross-detector consistency, afterglow effects, linearity and CMS deadtime.
+Systematic uncertainties in the beam overlap widths along x and y directions measured during vdM scans, $\sigma_{vis}$ and luminosity can arise from length scale calibration, orbit drift, XY correlations of beam proton density distribution function, emittance growth, beam-beam deflection, dynamic $\beta$ which tells us whether bunches are narrow or wide, beam current calibration, ghosts and satellites, scan to scan variation and bunch to bunch variation.
+Systematic uncertainty during physics runs (high pileup) can be due to, afterglow effects, linearity, cross-detector consistency and CMS deadtime.
 \\
 
-\textbf{Systematics uncertainties during vdM scans or in $\bf{\sigma_{vis}}$:} \\
+\subsection{Systematics uncertainties for vdM scans or $\bf{\sigma_{vis}}$:} \\
 
@@
 
-\textbf{Systematics uncertaintities during physics runs (high pileup)}:\\
+\subsection{Systematics uncertaintities for physics runs (high pileup):}\\
 
@@
 
-9.
-Cross-detector comparisons: After corrections of out-of-time effects (afterglow), stability and linearity are applied, luminosity measurement from various detector like BCM1F, PLT and HFOC can be compared to do very precise luminosity determination by taking into account exact corrections \cite{CMS-PAS-LUM-18-002}.
+Cross-detector comparisons: After corrections of out-of-time effects (afterglow), stability and linearity are applied, luminosity measurement from various detector like BCM1F, PLT and HFOC can be compared to do very precise luminosity determination by taking into account exact corrections and systematic uncertainties\cite{CMS-PAS-LUM-18-002}.

### 2021-05-23 project_ashish_monograph/upgrade.tex
updated

@@
 \label{sec:tepx}
-(describe the TEPX detector design, algorithms clusters/coincidences, D4R1 as HL-LHC luminometer, stat precision, linearity)\\
 
@@
 
-Tracker endcap pixel detector (TEPX) consists of four double disks per side (-Z and +Z) as shown in Fig.
-28 with each double disk containing five rings as shown in Fig.
-28 having 20, 28, 36, 44 and 48 modules respectively.
+\subsection{TEPX detector for Phase II}
+
+Tracker endcap pixel detector (TEPX) consists of four double disks per side (-Z and +Z) with each double disk containing five rings as shown in Fig.
+29 having 20, 28, 36, 44 and 48 modules respectively.
 One double disk has four surfaces with +Z side containing modules with even module number in front layers (L1 $\&$ L2) and modules with odd module number in back layers (L3 $\&$ L4) from Ring 1 to Ring 4 and for Ring 5, modules with odd module number in front layers and modules with even module number in back layers as shown in Fig.
@@
 
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1 \columnwidth]{./tepx_tt.png}
+  \caption{ \onehalfspacing Left: A layout of the CMS Phase-2 inner tracker showing four TEPX disks, eight TFPX disks and four barrel layers.
+Right: Diagram showing one double disk of TEPX with five rings \cite{Klein:2017nke}.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1 \columnwidth]{./fourlayers.png}
+  \caption{ \onehalfspacing Fours layers of one double disk of TEPX showing module arrangement in rings for each layer. Ring 1, 2, 3, 4 and 5 consists of 20, 28, 36, 44 and 48 modules respectively. }
+  \label{fig:CMS}
+\end{figure}
+
+\subsection{Phase II CMS simulation samples}
+
+\onelinespacing Simulated data samples for Phase II include full CMS detector description and uses official CMS software (CMSSW) version $10-6-0-patch2$ which calls GEANT4 for particle and energy deposit simulation as well as for reconstruction \cite{Agostinelli:2002hh}.
+These samples contain single-neutrino event overlaid with a variable number of minimum-bias events (events with any amount of real energy detected in CMS) to simulate different pileup values.
+The statistics for samples with average pileup values from 0.5 to 2 is 500000 events per step and for average pileup values between 10 and 200, statistics is 100000.
+\\
+
+\subsection{Luminosity determination - counting clusters/coincidences}
+
 Instantaneous luminosity determination using PCC method for Phase II HL-LHC will be based on counting the number of clusters or coincidences.
 The innermost ring of the last disk of TEPX (D4R1) is located at 2.65 m away from the interaction point that is beyond the tracking acceptance ($|\eta| = 4$) and as this region has few tracking points, it can be solely used for the purpose of luminosity measurement by using the full available trigger rate and bandwidth.
-TEPX Disk 4 Ring 1 layout is shown in Fig.
-29.
 Two fold coincidences are those hits which are created by the module overlap regions between various layers of one TEPX double disk.
@@
 31.
-Luminosity calculated based on counting coincidences has an advantage over clusters that afterglow effects are tiny in the case of coincidences.
-\cite{Collaboration:2706512} \cite{brilsim} \cite{brilsim1}\cite{brilsim2}\\
+Luminosity calculated based on counting coincidences has an advantage over clusters that afterglow effects are tiny in the case of coincidences  \cite{Collaboration:2706512} \cite{brilsim} \cite{brilsim1}\cite{brilsim2}.\\
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{./2foldinrphi.png}
+  \caption{ \onehalfspacing Diagram showing modules overlap between the front (L1 \& L2) and back (L3 \& L4) layers of one double disk of TEPX that creates two fold coincidences in $\phi$ and r.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.6\columnwidth]{./23coin.png}
+  \caption{\onehalfspacing Example of two- and threefold coincidence regions on a portion of a single TEPX disk.}
+  \label{fig:CMS}
+\end{figure}
+
+\subsection{Results: TEPX linearity}
 
@@
 
-$<N_{cluster/interaction}> = \frac{<N_{cluster}>}{(PU)} = \frac{\sigma_{visible}}{\sigma_{interaction} (\sqrt{s})}$ \\
+$<N_{cl/pp}> = \frac{<N_{cl}>}{\mu} = \frac{\sigma_{vis}}{\sigma_{pp}}$ \\
 
-$<N_{cluster}> =  \frac{\sigma_{visible}}{\sigma_{interaction}(\sqrt{s})} (PU)$ \\
+$<N_{cl}> =  \frac{\sigma_{vis}}{\sigma_{pp}} \mu $ \\
 
@@
 A non-linear relation $<N_{cluster}> = \alpha (PU)^{\gamma}, \gamma \neq 1$ would add non-linear terms in the rate equation $R = \sigma_{vis} L_{inst}$  and cause $\sigma_{vis}$ to vary with the per bunch instantaneous luminosity and pileup values.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.8\columnwidth]{./tepx_geometry.png}
-  \caption{ \onehalfspacing A layout of the CMS Phase-2 inner tracker showing four TEPX disks, eight TFPX disks and 4 barrel layers. \cite{Klein:2017nke}}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.4 \columnwidth]{./D4R1.png}
-  \caption{ \onehalfspacing Sketch of the TEPX Disk 4 Ring 1.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1 \columnwidth]{./fourlayers.png}
-  \caption{ \onehalfspacing Fours layers of one double disk of TEPX showing module arrangement in rings for each layer.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.8\columnwidth]{./coincidences.png}
-  \caption{ \onehalfspacing Diagram showing modules overlap between the front and back layers of one double disk of TEPX that creates two fold coincidences in $\phi$ and r.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.8\columnwidth]{./up.png}
-  \caption{\onehalfspacing Left: View in the x-y plane of the double disk structure of one TEPX disk.
-The sensors in blue and red correspond to the two double disks at slightly different z positions.
-Right: Example of two- and threefold coincidence regions on a portion of a single TEPX disk.}
-  \label{fig:CMS}
-\end{figure}
 
@@
   \centering
-  \includegraphics[width=1 \columnwidth]{./clustersperdisk-z.png}
-  \caption{Left: Simulated mean number of clusters for -z side TEPX disks as a function of pileup. Right: Deviation from linearity for clusters for -z side TEPX disks.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
   \includegraphics[width=1 \columnwidth]{./clustersperdisk+z.png}
   \caption{Left: Simulated mean number of clusters for +z side TEPX disks as a function of pileup. Right: Deviation from linearity for clusters for +z side TEPX disks.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{./clustersperringD-4.png}
-  \caption{Left: Simulated mean number of clusters for TEPX Disk 4 all rings as a function of pileup.
-Ring 1 has highest slope and Ring 5 has least slope.
-Right: Deviation from linearity for clusters for TEPX Disk 4 all rings.
-Non-linearity is within $1\%$ for all rings over entire pileup range.}
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=1\columnwidth]{.//coincidencesperdisk-z.png}
-  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for -z side TEPX disks as a function of pileup.
-Right: Deviation from linearity for coincidences in $\phi$ and r for -z side TEPX disks.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
   \includegraphics[width=1\columnwidth]{./coincidencesperdisk+z.png}
@@
   \centering
-  \includegraphics[width=1\columnwidth]{./coincidencesperringD-4.png}
-  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for -z side TEPX Disk 4 per ring as a function of pileup.
-Ring 1 has highest slope and Ring 5 has least slope.
-Right: Deviation from linearity for coincidences in $\phi$ and r for -z side TEPX Disk 4 per ring.
-Non-linearity is within 1\% for all rings over entire pileup range.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
   \includegraphics[width=1\columnwidth]{./coincidencesperringD+4.png}
@@
 Right: Deviation from linearity for coincidences in $\phi$ and r for +z side TEPX Disk 4 per ring.
-Non-linearity is within 1\% for all rings over entire pileup range.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{./coincidencesinphiperringD-4.png}
-  \caption{Left: Simulated mean number of coincidences in $\phi$ for -z side TEPX Disk 4 per ring as a function of pileup.
-Ring 1 has highest slope and Ring 5 has least slope.
-Right: Deviation from linearity for coincidences in $\phi$ for -z side TEPX Disk 4 per ring.
 Non-linearity is within 1\% for all rings over entire pileup range.}
@@
   \centering
-  \includegraphics[width=1\columnwidth]{./coincidencesinrperringD-4.png}
-  \caption{Left: Simulated mean number of coincidences in r for -z side TEPX Disk 4 per ring as a function of pileup.
-Ring 1 has highest slope and Ring 5 has least slope.
-Right: Deviation from linearity for coincidences in r for -z side TEPX Disk 4 per ring.
-Non-linearity is within $1\%$ for all rings over entire pileup range.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
   \includegraphics[width=1\columnwidth]{./coincidencesinrperringD+4.png}
@@
 
-vdM (PU 0.5) $\:\:$  Trigger frequency (kHz) $\:\:$ 1 bx, 30 s $\:\:$ 100 bx, 30 s \\
-TEPX D4R1 2x Coincidences in $\phi$  $\:\:$  800        $\:\:$   1.7         $\:\:$       0.17   \\
-TEPX 2x Coincidences in $\phi$   $\:\:$     500        $\:\:$   0.485       $\:\:$       0.0485   \\
+\subsection{Statistical precision for Phase II luminometer - TEPX}
+Statistical precision is another uncertainty that need to be considered for luminosity measurement. It must be kept minimal to achieve 1 $\%$ accuracy for HL-LHC luminosity measurement. \\
 
-Physics (PU 200)  $\:\:$ Trigger frequency (kHz)   $\:\:$   1 bx, 4 LN (1.46 s)   $\:\:$     2500 bx, 1 LS (23 s)  \\
-                                                      $\:\:$           ``Online''          $\:\:$           ``Offline''      \\
-TEPX D4R1 2x Coincidences in $\phi$  $\:\:$   800                $\:\:$   0.386           $\:\:$            0.00193         \\
-TEPX 2x Coincidences in $\phi$       $\:\:$   75           $\:\:$         0.284           $\:\:$            0.00142         \\
+Relative statistical uncertainty in $\%$ = $\frac{\sqrt{N}}{N} \times 100$ \\
+
+where N = (Number of counts per event)$\times$(Trigger Frequency)$\times$(Time Integration period). \\
+
+Table 1: Expected statistical precision (in $\%$) in head-on collisions during typical vdM conditions with pileup of 0.5 for TEPX two fold coincidences in $\phi$  over different integration time period.
+\begin{center}
+    \begin{tabular}{ | l | l | l | p{5cm} |}
+    \hline
+    vdM (PU 0.5) & Trigger frequency (kHz) & 1 bx, 30 s & 100 bx, 30 s\\ \hline
+    TEPX D4R1 2x Coincidences in $\phi$  & 800  & 1.7 & 0.17\\ \hline  
+    TEPX 2x Coincidences in $\phi$  & 500  & 0.485 & 0.0485 \\ \hline 
+    \hline
+    \end{tabular}
+\end{center} \\
+
+Table 2: Expected statistical precision (in $\%$) in head-on collisions during physics conditions with pileup of 200 for TEPX two fold coincidences in $\phi$  over different integration time period. 
+\begin{center}
+    \begin{tabular}{ | l | l | l | p{5cm} |}
+    \hline
+    Physics (PU 200) & Trigger frequency (kHz) & 1 bx, 4 LN (1.46 s) & 2500 bx, 1 LS (23 s)\\ \hline
+    TEPX D4R1 2x Coincidences in $\phi$  & 800  & 0.386 & 0.00193\\ \hline  
+    TEPX 2x Coincidences in $\phi$  & 75  & 0.284 & 0.00142\\ \hline 
+    \hline
+    \end{tabular}
+\end{center} \\
+
+Table 3: Expected statistical precision (in $\%$) in head-on collisions during typical vdM conditions with pileup of 0.5 for TEPX clusters and two fold coincidences over different integration time period.
+\begin{center}
+    \begin{tabular}{ | l | l | l | p{5cm} |}
+    \hline
+    vdM (PU 0.5) & Trigger frequency (kHz) & 1 bx, 1 s & 1 bx, 30 s \\ \hline
+    TEPX D4R1 clusters  & 1000  & 1.8  & 0.33 \\ \hline  
+    TEPX D4R1 2x Coincidences  & 1000  & 5.8 & 1.1 \\ \hline  
+    TEPX clusters  & 500  & 0.74  & 0.14\\ \hline
+    TEPX 2x Coincidences  & 500  & 2.7 & 0.49\\ \hline
+    \hline
+    \end{tabular}
+\end{center}
+
+Table 4: Expected statistical precision (in $\%$) per second in head-on collisions during physics conditions with pileup of 200 for TEPX clusters and two fold coincidences over different integration time period.
+\begin{center}
+    \begin{tabular}{ | l | l | l | p{5cm} |}
+    \hline
+    Algorithm & Trigger frequency (kHz) & 1 bx, 1 s & 2500 bx, 1 s \\ \hline
+    TEPX D4R1 clusters  & 825  & 0.10 & 0.002 \\ \hline  
+    TEPX D4R1 2x Coincidences  & 825  & 0.32  & 0.006\\ \hline  
+    TEPX clusters  & 75  & 0.095  & 0.002\\ \hline
+    TEPX 2x Coincidences  & 75  & 0.35 &0.007 \\ \hline
+    \hline
+    \end{tabular}
+\end{center}

### 2021-05-23 project_ashish_monograph/vdM.tex
updated

@@
  \label{sec:vdm}
+
+ \subsection{Luminosity calibration}
 Van der Meer (vdM) scans are done to calculate the visible cross section $\sigma_{vis}$ of the pixel detector which is a calibration constant in the relation between rate of a quantity (clusters, coincidences) read out by the detector and the instantaneous luminosity.
@@
 
-The instantaneous luminosity  per bunch crossing when the crossing angle between the colliding bunches is negligible and bunches collide head on as shown in Fig.
-7 is given by the following integral, \cite{CMS-PAS-LUM-13-001} \\
+The instantaneous luminosity  per bunch crossing when the crossing angle between the colliding bunches is negligible and bunches collide head on is given by the following integral \cite{CMS-PAS-LUM-13-001}, \\
 
-$L_{inst/bunch}$ = N_1 N_2 f \int^{+\infty}_{-\infty} \rho_1(x,y) \rho_2(x+\Delta x, y+ \Delta y) dx dy \\
+$L_{b}$ = N_1 N_2 f \int^{+\infty}_{-\infty} \rho_1(x,y) \rho_2(x, y) dx dy \\
 
-where $N_1, N_2$ are the number of protons in the colliding bunches, f is the LHC orbit frequency whose value is 11246Hz,  $\rho_1(x,y)$ and $\rho_2(x+\Delta x,y+\Delta y)$ are the two dimensional particle density distribution functions for each colliding bunch separated by $\Delta x$ and $\Delta y$ in the x and y directions.
+where $N_1, N_2$ are the number of protons in the colliding bunches, f is the LHC orbit frequency whose value is 11246Hz,  $\rho_1(x,y)$ and $\rho_2(x,y)$ are the two dimensional particle density distribution functions for each colliding bunch in x and y directions.
 \\
@@
 
-$L_{inst/bunch}$ = N_1 N_2 f \int^{+\infty}_{-\infty} \rho_{1x}(x) \rho_{2x}(x+\Delta x)  dx   \int^{+\infty}_{-\infty} \rho_{1y}(y) \rho_{2y}(y+\Delta y)  dy \\
+$L_{b}$ = N_1 N_2 f \int^{+\infty}_{-\infty} \rho_{1x}(x) \rho_{2x}(x)  dx   \int^{+\infty}_{-\infty} \rho_{1y}(y) \rho_{2y}(y)  dy \\
 
-where $\rho_1(x,y) = \rho_{1x}(x,y) \rho_{1y} (x,y)$ and $\rho_2(x+\Delta x,y + \Delta y) = \rho_{2x}(x+\Delta x,y+\Delta y) \rho_{2y} (x+\Delta,y+\Delta y)$ \\
+where $\rho_1(x,y) = \rho_{1x}(x) \rho_{1y} (y)$ and $\rho_2(x,y) = \rho_{2x}(x) \rho_{2y} (y)$ \\
 
-The vdM scan determines the bunch  overlap integrals $\int \rho_{x1} (x) \rho_{x2} (x+\Delta x) dx$ and  $\int \rho_{y1}(y) \rho_{y2} (y+\Delta y) dy$ by measuring pixel clusters rate as a function of bunch separation $\Delta x$ and $\Delta y$ along x and y directions as shown in Fig.
-8.
+The vdM scan determines the bunch  overlap integrals $\int \rho_{x1} (x) \rho_{x2} (x) dx$ and  $\int \rho_{y1}(y) \rho_{y2} (y) dy$ by measuring pixel clusters rate as a function of bunch separation $\Delta x$ and $\Delta y$ along x and y directions as shown in Fig.
+12.
 \\
 
-\int \rho_{x1} (x) \rho_{x2} (x+\Delta x) dx = \frac{R_x(0)}{\int R_x(\Delta x)dx} \\
+\int \rho_{x1} (x) \rho_{x2} (x) dx = \frac{R_x(0)}{\int R_x(\Delta x)dx} \\
 
-\int \rho_{y1} (y) \rho_{y2} (y + \Delta y) dy = \frac{R_y(0)}{\int R_y(\Delta y)dy} \\
+\int \rho_{y1} (y) \rho_{y2} (y) dy = \frac{R_y(0)}{\int R_y(\Delta y)dy} \\
 
@@
 
-$\Sigma_x \Sigma_y = \frac{1}{2 \pi} \frac{\int R_x(\Delta x)dx \int R_y(\Delta y) dy}{R_x(0) R_y(0)}$  is the bunch overlapping area as shown in Fig. 9 by the red region.\\
-
 Thus, the expression for instantaneous luminosity is given by \\
 
-$L_{inst/bunch}$ = $\frac{N_1 N_2 f}{2\pi \Sigma_x \Sigma_y}$ \\
+$L_{b}$ = $\frac{N_1 N_2 f}{2\pi \Sigma_x \Sigma_y}$ \\
 
@@
 
-\sigma_{vis} = \frac{2 \pi \Sigma_x \Sigma_y R}{N_1 N_2} \\
+\sigma_{vis} = \frac{2 \pi \Sigma_x \Sigma_y R(0)}{N_1 N_2} \\
 
-where R = $\frac{d}{dt} <N_{cluster}>$  is cluster rate.\\
+where R(0) is the peak cluster rate measured by the pixel detector after applying module selection.\\
 
@@
   \centering
-  \includegraphics[width=0.6\columnwidth]{./LHCReport_1_image_cut.png}
-  \caption{ \onehalfspacing Diagram showing colliding bunches in each LHC beam separated by 25ns.}
+  \includegraphics[width=0.7\columnwidth]{./cropped.jpg}
+  \caption{ \onehalfspacing Cluster rate profile fit during vdM scans as a function of bunch separation $\Delta x$ and $\Delta y$ along x and y directions \cite{CMS-PAS-LUM-15-001}.}
   \label{fig:CMS}
 \end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.7\columnwidth]{./vdm_ratefit.png}
-  \caption{ \onehalfspacing Cluster rate profile fit during vdM scans as a function of bunch separation $\Delta x$ and $\Delta y$ along x and y directions. \cite{CMS-PAS-LUM-15-001}.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=\columnwidth]{./vdm_image.png}
-  \caption{\onehalfspacing Figure showing two LHC bunches in green and blue approaching each other and colliding giving rise to an overlapping region shown in red whose area is determined during vdM scans.}
-  \label{fig:CMS}
-\end{figure}

### 2021-05-24 project_ashish_monograph/CMS.tex
updated

@@
 
-\subsection{CMS detector}
-(describe the detector components and what they do) \\
+\subsection{The CMS detector}
 
@@
 
-\subsection{The Pixel detector}
+\subsection{The CMS Phase I Pixel detector}
 
@@
 
-\subsection{Cluster reconstruction}
+\subsection{Cluster reconstruction in pixel detector}
 Specific techniques are employed for the reconstruction of clusters in the pixel detector and all the reconstructed clusters are used for counting to calculate the instantaneous luminosity.
@@
 These algorithms estimates cluster position in two directions and cluster charge.
-A cluster is a set of adjacent pixels and only pixels above certain minimum value of charge are considered.
+A cluster is a set of adjacent pixels hit by a track originating from interaction point and only pixels above certain minimum value of charge are considered.
 Position of a cluster in X and Y directions are obtained by fitting X and Y projections to templates that are estimates for cluster shapes \cite{Chatrchyan:2014fea}.

### 2021-05-24 project_ashish_monograph/PCC.tex
updated

@@
 
-CMS 2018 data is a collection of runs for each fill in different periods defined during the LHC operation period.
+CMS 2018 data is a collection of runs for each fill in different periods defined during the LHC operation period. LHC 2018 run is divided into A, B, C and D as described below. \\
 
-LHC 2018 run is divided into A, B, C and D as described below. \\
 \begin{flushleft}
@@
 Number of runs per period is 146 \\
+\end{flushleft}
 
+  \begin{flushleft}
 2. Run2018B\\
@@
 Number of runs per period is 132\\
+\end{flushleft}
 
+  \begin{flushleft}
 3. Run2018C \\
@@
 Number of runs per period is 88 \\
+\end{flushleft}
 
+  \begin{flushleft}
 4.Run2018D \\
@@
 Number of runs per period is 262 \\
+\end{flushleft}
 
+  \begin{flushleft}
 5. late Run2018D \\
@@
 
-\subsection{Pixel detector Module Selection}
+\subsection{Pixel detector module selection}
 Selection of modules in pixel detector is required because module may experience dynamic inefficiency, bad module chips can stop sending data, chips may not work properly and need reconfiguring.
@@
 \begin{flushleft}
-1. Total number of vetoed modules 1387. \\
-2. Number of vetoed modules for L2 1850.\\
-3. Number of vetoed modules for L3 1766.\\
-4. Number of vetoed modules for L4 1641.\\
-5. Number of vetoed modules for D1 1813.\\
-6. Number of vetoed modules for D2  1799.\\
-7. Number of vetoed modules for D3 1800.\\
+Total number of modules: 1856 \\
+BPIX modules per layer:  96 , 224 , 352 , 512\\
+FPIX modules per disk:  112 , 112 , 112 , 112 , 112 , 112\\
 \end{flushleft}

### 2021-05-24 project_ashish_monograph/bkg.tex
updated

@@
 These contributions to the measured cluster rate are either subtracted before the fit as measured from noncolliding, unpaired bunches or from periods during which the beams were kept at a large distance, or determined in the fit as a constant term added to the fit function as shown in Fig.
-13.
+15.
 
@@
 Fig.
-14 shows the afterglow noise induced by one colliding bunch.
+16 shows the afterglow noise induced by one colliding bunch.
 Since the distribution is normalized to 1 at the first bin it means the first bin is the colliding bunch.
@@
  Afterglow effects for various bunches in a beam is shown in Fig.
-15 where the intial rising curve correspond to Type I and decay curve correspond to Type II afterglow effect.
+17 where the intial rising curve correspond to Type I and decay curve correspond to Type II afterglow effect.
 It was studied in data taken using random triggers (triggers that fire randomly in bunch crossings spread over the whole LHC orbit except for the abort gap), considering the pixel cluster counts in bunch crossings after bunch trains.
@@
   \includegraphics[width=0.5\columnwidth]{./afterglow.png}
-  \caption{Results of the pixel afterglow fit.}
+  \caption{Results of the pixel afterglow fit.
+Type I afterglow effect results from fake electronic pulse response after actual bunch crossing and Type II results from activation of detector material shown as exponentially decaying.
+}
   \label{fig:LHC}

### 2021-05-24 project_ashish_monograph/conclusion.tex
progress
updated

@@
-\section{Conclusions and outlook} 
+\newpage \section{Summary and Plans} 
 \label{sec:conclusion}
-sumarize the method and results, and TEPX upgrade work and plans
+
+In the first part, we processed 2018 CMS data set for period A, B and C to compute luminosity ratios for various subdetectors (L2, L3, L4, D1, D2, D3) of pixel detector.
+Luminosity determined for pixel subdetectors L3 and F1 shows large instabilities for large lumi section values.
+We will carry out a detailed study to understand these fluctuations/instabilities observed in the luminosity ratios using new module selections.
+We will also study vdM background, systematics uncertainties in luminosity measurement and determination of $\sigma_{vis}$ for other luminosity measurement device used during Run 2018 like HFOC.\\
+
+In the second part, we performed a linearity study for Phase II luminosity measurement device Tracker Endcap Pixel Detector (TEPX).
+Simulated samples from low to high pileup values mimicking Phase II HL-LHC conditions were produced using full CMS detector description and used them to study the behaviour of clusters under different pileup conditions.
+Different selections on separation between variables defined using cluster position dr and $d\phi$ were applied to study the behaviour of two fold coincidences with pileup to take into account track angle and its curvature.
+We used different cut values for different TEPX disks and rings to obtain a behaviour closest to linearity for two fold coincidences in $\phi$ and implemented a similar procedure for two fold coincidences in r.
+New tighter selections dependent on TEPX disks and rings based on truth-match cluster distributions removed physics noise at high pileup.
+Residual non-linearity for TEPX clusters is with 0.5 \% and for two fold coincidences in $\phi$, r and combined is within 1 \% for all TEPX disks, rings and entire TEPX detector except Ring 5 up to pileup 200.\\
+
+Statistical precision is also calculated for TEPX clusters and coincidences during typical vdM and high pileup physics conditions over different integration time period.
+For HL-LHC conditions which correspond to pileup 200, the statistical precision which is an important uncertainty for any luminometer is found to be less than 1\%.

### 2021-05-24 project_ashish_monograph/intro.tex
updated

@@
 This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ by the year 2036 as shown in Fig.
-6.
-Figure 2 shows a summary of the projected uncertainties in the Higgs boson coupling parameters for Phase II HL-LHC using ggF, VBF, VH, and ${t\bar{t}H}$ production modes where luminosity is one of the dominant uncertainty in Higgs boson coupling measurement \cite{Tanabashi:2018oca}.
+8.
+Figure 2 shows a summary of the projected uncertainties in the Higgs boson coupling parameters for Phase II HL-LHC using ggF, VBF, VH, and ${t\bar{t}H}$ production modes where uncertainty in luminosity measurement is one of the dominant uncertainty in Higgs boson coupling measurement \cite{Tanabashi:2018oca}.
 \\

### 2021-05-24 project_ashish_monograph/results.tex
updated

@@
   \centering
-  \includegraphics[width=1\columnwidth]{./crop.png}
-  \caption{PCC luminosity ($\mu b^{-1}$) and PCC/hfoc luminosity ratio for Run2018A using late Run2018D veto list for pixel detector modules.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{./317438(1).png}
-  \caption{PCC luminosity ($\mu b^{-1}$) and PCC/hfoc luminosity ratio for Run2018B using late Run2018D veto list for pixel detector modules.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{./319659.png}
-  \caption{PCC luminosity ($\mu b^{-1}$) and PCC/hfoc luminosity ratio for Run2018C using late Run2018D veto list for pixel detector modules.}
+  \includegraphics[width=1\columnwidth]{./lhcfill_t.png}
+  \caption{Left: Instantaneous luminosity as measured offline by the HFOC luminometer for LHC fill 7270.
+Right: Ratios of instantaneous luminosity as measured offline by the CMS luminometers as a function of instantaneous luminosity measured by HFOC.}
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=0.52\columnwidth]{./ls_lumi.png}
-  \caption{PCC count as a function of luminosity section (1 lumi section is 23.36s) for Run2018A.}
+  \includegraphics[width=1\columnwidth]{./lumiA_merged.png}
+  \caption{Left: PCC count as a function of luminosity section (1 lumi section is 23.36s) for Run2018A. Right: PCC integrated luminosity ($\mu b^{-1}$) as a function of run number for Run2018A.}
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./ls_lumi_2018B.png}
-  \caption{PCC count as a function of lumi section for Run2018B.}
+  \includegraphics[width=1\columnwidth]{./lumiB_merged.png}
+  \caption{Left: PCC count as a function of lumi section for Run2018B. Right: PCC integrated luminosity ($\mu b^{-1}$) as a function of run number for Run2018B}
   \label{fig:CMS}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./ls_lumi_2018C.png}
-  \caption{PCC count as a function of lumi section for Run2018C.}
+  \includegraphics[width=1\columnwidth]{./lumiC_merged.png}
+  \caption{Left: PCC count as a function of lumi section for Run2018C. Right: PCC integrated luminosity ($\mu b^{-1}$) as a function of run number for Run2018C.}
   \label{fig:CMS}
@@
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.52\columnwidth]{./runs.png}
-  \caption{PCC integrated luminosity ($\mu b^{-1}$) as a function of run number for Run2018A.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.52\columnwidth]{./runs_2018B.png}
-  \caption{PCC integrated luminosity ($\mu b^{-1}$) as a function of run number for Run2018B.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.52\columnwidth]{./runs_2018C.png}
-  \caption{PCC integrated luminosity ($\mu b^{-1}$) as a function of run number for Run2018C.}
-  \label{fig:CMS}
-\end{figure}
-
-\subsection{Stability of PCC luminosity for Run 2018 data}
+\subsection{Stability of PCC luminosity for Run 2018 CMS data}
 
 The stability of run 2018 CMS integrated luminosity for Phase I pixel detector calculated using PCC method is investigated by employing late Run2018D veto list and including afterglow effects.
+Luminosity ratios for various subdetectors in pixel detector are computed with respect to total pixel detector luminosity after applying module veto lists for each subdetector.
 New module selections will be determined and used for 2018 luminosity determination.

### 2021-05-24 project_ashish_monograph/upgrade.tex
updated

@@
- \section{The TEPX upgrade for HL-LHC}
+ \section{The TEPX upgrade for Phase II HL-LHC}
 \label{sec:tepx}
@@
 Tracker endcap pixel detector (TEPX) consists of four double disks per side (-Z and +Z) with each double disk containing five rings as shown in Fig.
-29 having 20, 28, 36, 44 and 48 modules respectively.
+25 having 20, 28, 36, 44 and 48 modules respectively.
 One double disk has four surfaces with +Z side containing modules with even module number in front layers (L1 $\&$ L2) and modules with odd module number in back layers (L3 $\&$ L4) from Ring 1 to Ring 4 and for Ring 5, modules with odd module number in front layers and modules with even module number in back layers as shown in Fig.
-30.
+26.
 For -Z side, four surfaces contain modules with odd module number in front layer and modules with even module number in back layer from Ring 1 to Ring 4 and for Ring 5, modules with even module number in front layer and modules with odd module number in back layer.
@@
   \includegraphics[width=1 \columnwidth]{./tepx_tt.png}
-  \caption{ \onehalfspacing Left: A layout of the CMS Phase-2 inner tracker showing four TEPX disks, eight TFPX disks and four barrel layers.
+  \caption{ \onehalfspacing Left: A layout of the CMS Phase II inner tracker showing four TEPX disks, eight TFPX disks and four barrel layers.
 Right: Diagram showing one double disk of TEPX with five rings \cite{Klein:2017nke}.}
@@
 
-\subsection{Luminosity determination - counting clusters/coincidences}
+\subsection{Luminosity determination using TEPX - counting clusters/coincidences}
 
-Instantaneous luminosity determination using PCC method for Phase II HL-LHC will be based on counting the number of clusters or coincidences.
-The innermost ring of the last disk of TEPX (D4R1) is located at 2.65 m away from the interaction point that is beyond the tracking acceptance ($|\eta| = 4$) and as this region has few tracking points, it can be solely used for the purpose of luminosity measurement by using the full available trigger rate and bandwidth.
+Instantaneous luminosity determination using PCC method for Phase II HL-LHC will be based on counting the number of clusters in TEPX Disk 4 Ring 1.
+The innermost ring of the last disk of TEPX (D4R1) is located at 2.65 m away from the interaction point that is beyond the tracking acceptance ($|\eta| = 4$) and as this region has few tracking points, it can be solely used for the purpose of luminosity measurement by using the full available trigger rate and bandwidth.\\
+
+A new algorithm for luminosity determination based on counting two fold coincidences is proposed that applies selections using dr and $d\phi$ variables to minimize non-linearity for high pileup values as these variables take into account track angle and its curvature.
 Two fold coincidences are those hits which are created by the module overlap regions between various layers of one TEPX double disk.
@@
 Two fold coincidence in $\phi$ will involve modules overlapping in the same ring in front and back layers of one double disk as shown in top part of Fig.
-31 and Fig.
-32 while two fold coincidence in r will require modules overlapping between successive rings in the front (L1 $\&$ L2) and back layers (L3 $\&$ L4) of one double disk as shown in bottom part of Fig.
-31.
+27 and Fig.
+28 while two fold coincidence in r will require modules overlapping between successive rings in the front (L1 $\&$ L2) and back layers (L3 $\&$ L4) of one double disk as shown in bottom part of Fig.
+27.
 Luminosity calculated based on counting coincidences has an advantage over clusters that afterglow effects are tiny in the case of coincidences  \cite{Collaboration:2706512} \cite{brilsim} \cite{brilsim1}\cite{brilsim2}.\\
@@
   \centering
-  \includegraphics[width=0.8\columnwidth]{./2foldinrphi.png}
+  \includegraphics[width=0.7\columnwidth]{./2foldinrphi.png}
   \caption{ \onehalfspacing Diagram showing modules overlap between the front (L1 \& L2) and back (L3 \& L4) layers of one double disk of TEPX that creates two fold coincidences in $\phi$ and r.}
@@
   \includegraphics[width=0.6\columnwidth]{./23coin.png}
-  \caption{\onehalfspacing Example of two- and threefold coincidence regions on a portion of a single TEPX disk.}
+  \caption{\onehalfspacing Example of two and threefold coincidence regions on a portion of a single TEPX disk.}
   \label{fig:CMS}
@@
 
-\subsection{Results: TEPX linearity}
+\subsection{TEPX linearity}
 
-Linearity is one of the systematic uncertainty in the calculation of instantaneous luminosity using PCC and PCC visible cross section $\sigma_{vis}$.
+Linearity is one of the systematic uncertainty in the calculation of instantaneous luminosity and PCC visible cross section $\sigma_{vis}$.
 A linear relation between the number of clusters and pileup (PU) imply that \\
@@
 Linearity results for simulated TEPX clusters and coincidences from low to high pileup values are shown from Fig.
-33 to Fig.
-50.
+29 to Fig.
+40.
 TEPX luminometer proposed for Phase II shows excellent linearity over entire pileup range.
@@
   \includegraphics[width=1\columnwidth]{./clustersperringD+4.png}
-  \caption{Left: Simulated mean number of clusters for TEPX Disk 4 all rings as a function of pileup.
+  \caption{Left: Simulated mean number of clusters for +z side TEPX Disk 4 all rings as a function of pileup.
 Ring 1 has highest slope and Ring 5 has least slope.
-Right: Deviation from linearity for clusters for TEPX Disk 4 all rings.
+Right: Deviation from linearity for clusters for TEPX Disk +4 all rings.
 Non-linearity is within $1\%$ for all rings over entire pileup range.}
@@
 
-\subsection{Statistical precision for Phase II luminometer - TEPX}
-Statistical precision is another uncertainty that need to be considered for luminosity measurement. It must be kept minimal to achieve 1 $\%$ accuracy for HL-LHC luminosity measurement. \\
+\subsection{Statistical precision for TEPX luminometer}
+Statistical precision is another uncertainty that need to be considered for precise luminosity measurement. It must be kept minimal to achieve 1 $\%$ accuracy for HL-LHC luminosity measurement. \\
 
@@
 
-Table 1: Expected statistical precision (in $\%$) in head-on collisions during typical vdM conditions with pileup of 0.5 for TEPX two fold coincidences in $\phi$  over different integration time period.
+\newpage
+\begin{flushleft} 
+  Table 1: Expected statistical precision (in $\%$) in head-on collisions during typical vdM conditions with pileup of 0.5 for TEPX clusters and two fold coincidences over different integration time period.
+\end{flushleft}
+
 \begin{center}
-    \begin{tabular}{ | l | l | l | p{5cm} |}
+\scalebox{1}{
+\begin{tabular}{|l | c | c | c |c|}
 \hline
-    vdM (PU 0.5) & Trigger frequency (kHz) & 1 bx, 30 s & 100 bx, 30 s\\ \hline
-    TEPX D4R1 2x Coincidences in $\phi$  & 800  & 1.7 & 0.17\\ \hline  
-    TEPX 2x Coincidences in $\phi$  & 500  & 0.485 & 0.0485 \\ \hline 
+vdM (PU 0.5)  & Readout Rate (kHz) &1 bx, 1s & 1 bx, 30s & 100 bx, 30s\\
 \hline
-    \end{tabular}
-\end{center} \\
-
-Table 2: Expected statistical precision (in $\%$) in head-on collisions during physics conditions with pileup of 200 for TEPX two fold coincidences in $\phi$  over different integration time period. 
-\begin{center}
-    \begin{tabular}{ | l | l | l | p{5cm} |}
+TEPXD4R1 Clusters&1000&2.74&0.5 & 0.05\\
 \hline
-    Physics (PU 200) & Trigger frequency (kHz) & 1 bx, 4 LN (1.46 s) & 2500 bx, 1 LS (23 s)\\ \hline
-    TEPX D4R1 2x Coincidences in $\phi$  & 800  & 0.386 & 0.00193\\ \hline  
-    TEPX 2x Coincidences in $\phi$  & 75  & 0.284 & 0.00142\\ \hline 
+TEPXD4R1 2x Coincidences in phi &1000&8.34&1.52 & 0.152\\
 \hline
-    \end{tabular}
-\end{center} \\
-
-Table 3: Expected statistical precision (in $\%$) in head-on collisions during typical vdM conditions with pileup of 0.5 for TEPX clusters and two fold coincidences over different integration time period.
-\begin{center}
-    \begin{tabular}{ | l | l | l | p{5cm} |}
+TEPXD4R1 2x Coincidences in r &1000&16&2.92 & 0.292\\
 \hline
-    vdM (PU 0.5) & Trigger frequency (kHz) & 1 bx, 1 s & 1 bx, 30 s \\ \hline
-    TEPX D4R1 clusters  & 1000  & 1.8  & 0.33 \\ \hline  
-    TEPX D4R1 2x Coincidences  & 1000  & 5.8 & 1.1 \\ \hline  
-    TEPX clusters  & 500  & 0.74  & 0.14\\ \hline
-    TEPX 2x Coincidences  & 500  & 2.7 & 0.49\\ \hline
+TEPXD4R1 2x Coincidences &1000&7.4&1.35 & 0.135\\
 \hline
-    \end{tabular}
+TEPX Clusters&500&0.709&0.129 & 0.0129\\
+\hline
+TEPX 2x Coincidences in phi &500&2.65&0.485 & 0.0485\\
+\hline
+TEPX 2x Coincidences in r &500&4.59&0.838 & 0.0838\\
+\hline
+TEPX 2x Coincidences &500&2.3&0.42 & 0.042\\
+\hline
+\end{tabular}}
 \end{center}
 
-Table 4: Expected statistical precision (in $\%$) per second in head-on collisions during physics conditions with pileup of 200 for TEPX clusters and two fold coincidences over different integration time period.
+\begin{flushleft} 
+Table 2: Expected statistical precision (in $\%$) in head-on collisions during physics conditions with pileup of 200 for TEPX clusters and two fold coincidences over different integration time period.
+\end{flushleft}
+
 \begin{center}
-    \begin{tabular}{ | l | l | l | p{5cm} |}
+\scalebox{1}{
+\begin{tabular}{|l | c | c | c |c |}
 \hline
-    Algorithm & Trigger frequency (kHz) & 1 bx, 1 s & 2500 bx, 1 s \\ \hline
-    TEPX D4R1 clusters  & 825  & 0.10 & 0.002 \\ \hline  
-    TEPX D4R1 2x Coincidences  & 825  & 0.32  & 0.006\\ \hline  
-    TEPX clusters  & 75  & 0.095  & 0.002\\ \hline
-    TEPX 2x Coincidences  & 75  & 0.35 &0.007 \\ \hline
+ Algorithm & Readout Rate (kHz)& 1 bx, 1s &2500 bx, 1s   & 2500 bx, 1 LS \\
 \hline
-    \end{tabular}
+TEPXD4R1 Clusters&825&0.151&0.00302&0.000624\\
+\hline
+TEPXD4R1 2x Coincidences in phi &825&0.459&0.00918&0.0019\\
+\hline
+TEPXD4R1 2x Coincidences in r &825&0.88&0.0176&0.00364\\
+\hline
+TEPXD4R1 2x Coincidences  &825&0.407&0.00814&0.00169\\
+\hline
+TEPX Clusters&75&0.0915&0.00183&0.000379\\
+\hline
+TEPX 2x Coincidences in phi &75&0.343&0.00685&0.00142\\
+\hline
+TEPX 2x Coincidences in r &75&0.593&0.0119&0.00245\\
+\hline
+TEPX 2x Coincidences &75&0.297&0.00594&0.00123\\
+\hline
+\end{tabular}}
 \end{center}

### 2021-05-24 project_ashish_monograph/vdM.tex
updated

@@
 
-$L_{b}$ = N_1 N_2 f \int^{+\infty}_{-\infty} \rho_1(x,y) \rho_2(x, y) dx dy \\
+$L_{b}$ = N_1 N_2 f \int^{+\infty}_{-\infty} \rho_1(x,y) \rho_2(x+\Delta x, y+\Delta y) dx dy \\
 
-where $N_1, N_2$ are the number of protons in the colliding bunches, f is the LHC orbit frequency whose value is 11246Hz,  $\rho_1(x,y)$ and $\rho_2(x,y)$ are the two dimensional particle density distribution functions for each colliding bunch in x and y directions.
+where $N_1, N_2$ are the number of protons in the colliding bunches, f is the LHC orbit frequency whose value is 11246Hz,  $\rho_1(x,y)$ and $\rho_2(x+\Delta x,y+\Delta y)$ are the two dimensional particle density distribution functions for each colliding bunch separated by $\Delta x$ and $\Delta y$ in x and y directions.
 \\
@@
 
-$L_{b}$ = N_1 N_2 f \int^{+\infty}_{-\infty} \rho_{1x}(x) \rho_{2x}(x)  dx   \int^{+\infty}_{-\infty} \rho_{1y}(y) \rho_{2y}(y)  dy \\
+$L_{b}$ = N_1 N_2 f \int^{+\infty}_{-\infty} \rho_{1x}(x) \rho_{2x}(x+\Delta x)  dx   \int^{+\infty}_{-\infty} \rho_{1y}(y) \rho_{2y}(y+\Delta y)  dy \\
 
-where $\rho_1(x,y) = \rho_{1x}(x) \rho_{1y} (y)$ and $\rho_2(x,y) = \rho_{2x}(x) \rho_{2y} (y)$ \\
+where $\rho_1(x,y) = \rho_{1x}(x) \rho_{1y} (y)$ and $\rho_2(x,y) = \rho_{2x}(x+\Delta x) \rho_{2y} (y+\Delta y)$ \\
 
-The vdM scan determines the bunch  overlap integrals $\int \rho_{x1} (x) \rho_{x2} (x) dx$ and  $\int \rho_{y1}(y) \rho_{y2} (y) dy$ by measuring pixel clusters rate as a function of bunch separation $\Delta x$ and $\Delta y$ along x and y directions as shown in Fig.
-12.
+The vdM scan determines the bunch  overlap integrals $\int \rho_{x1} (x) \rho_{x2} (x+\Delta x) dx$ and  $\int \rho_{y1}(y) \rho_{y2} (y+\Delta y) dy$ by measuring pixel clusters rate as a function of bunch separation $\Delta x$ and $\Delta y$ along x and y directions as shown in Fig.
+14.
 \\
 
-\int \rho_{x1} (x) \rho_{x2} (x) dx = \frac{R_x(0)}{\int R_x(\Delta x)dx} \\
+\int \rho_{x1} (x) \rho_{x2} (x+\Delta x) dx = \frac{R_x(0)}{\int R_x(\Delta x)dx} \\
 
-\int \rho_{y1} (y) \rho_{y2} (y) dy = \frac{R_y(0)}{\int R_y(\Delta y)dy} \\
+\int \rho_{y1} (y) \rho_{y2} (y+\Delta y) dy = \frac{R_y(0)}{\int R_y(\Delta y)dy} \\
 

### 2021-06-14 project_rodolfo/paper.tex
rodolfo

--- 2021-05-02 project_ashish_lumi/paper.tex
@@
 
-\def\Student{Ashish Sehrawat}
-\def\Title{THESIS PROJECT PROPOSAL}
-\def\Prog{Doctorado en Ciencias (F\'{i}sica) }
-\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
+\def\Student{Jesus Rodolfo MORENO CHAVEZ }
+\def\Title{MASTERS THESIS PROJECT}
+\def\TitleESP{(ANTEPROYECTO)}
+\def\Prog{Maestria en Ciencias (F\'{i}sica) }
+%\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
+\def\Dept{DIFUS}
 \def\Institution{Universidad de Sonora}
 \def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
-\def\ProjectTitle{Measurement of the luminosity in proton-proton collisions at the CMS experiment of the Large Hadron Collider}
-\def\ResearchLine{Astrof\'{i}sica, Cosmolog\'{i}a y F\'{i}sica de Part\'{i}culas}
+\def\ProjectTitle{Measurement of the Large Hadron Collider luminosity using the CMS silicon pixel detector}
+\def\ProjectTitleESP{Medic\'{i}on de la luminosidad del Gran Colisionador de Hadrones usando el detector de pixeles de silicio de CMS}
+\def\ResearchLine{Fisica Matematica}
 
@@
 \lhead{\Student\ / \ \Dept}
-\rhead{\Title}
+\rhead{\TitleESP}
 \rfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}}
@@
 \hspace{0pt}
-\vfill
-{\scshape\Large \Title \par}
-project revised 2021-1
+%\vfill
+{\scshape\Large \Title \\ \TitleESP \par}
+%%project revised 2021-1
 
-  \vspace{2cm}
+  \vspace{1cm}
   {
@@
     {\bf \large \ProjectTitle  \par}
+    \\
+    \vspace{0.4cm}
+    TITULO:\par
+    {\bf \large \ProjectTitleESP \par}
   }
 
-  \vspace{0.5cm}
+  \vspace{1cm}
   {
-    RESEARCH LINE: \par
+    RESEARCH LINE (LGAC): \par
     \ResearchLine \par
@@
 
-  \vspace{4cm}
+  \vspace{2cm}
   {\underline{\hspace{8cm}}\par}
@@
 
-  \vspace{4cm}
+  \vspace{2cm}
   {\today}
@@
 
-  This research project proposes to determine precise value and corresponding uncertainity of luminosity delivered to Compact Muon Solenoid (CMS) experiment at CERN during 2017-2018 period using Pixel Cluster Counting (PCC) method and construction of luminosity measurement device using Tracker Endcap Pixel Detector (TEPX) for High Luminosity (HL)-LHC which will be able to withstand luminosities of up to 3000 $fb^{-1}$.
-Luminosity plays a vital role in determination of cross section for various production and decay processes of elementary particles and its accurate determination will assist in precise calculation of SM quantities like cross section, couplings and exploring physics beyond SM.
-
+  This research project consists on the precise determination of the luminosity delivered by the Large Hadron Collider to the Compact Muon Solenoid (CMS) experiment at CERN during 2017-2018 period  using the Pixel Cluster Counting (PCC) method.
+  Luminosity plays a fundamental role in the  measurement of physics processes of elementary particles of the Standard Model, a precise determination of the delivered luminosity allows for precise tests of the Standard Model and searches for new physics.
+The PCC method consists of the reconstruction and counting of track clusters produced by charged particle tracks using the Inner Tracker of the CMS detector.
+Due to the fine granularity of the pixel sensors of the Inner Tracker, the hit occupancy in the sensors remains very small ($<1\%$) during the proton collisions, this leads to a very linear response and small overall systematic uncertainties for the luminosity measurement.
   \hspace{2pt}
@@
 During Run 1 (2011-2012) LHC reached a peak instantaneous luminosity of \instlumi{0.77} and delivered an integrated luminosity of about \lumi{25} with a precision of about 2.0\% 
-\footnote{1 barn is a unit of area corresponding to $10^{-24}$ cm${^2}$ and 1 femtobarn (fb) = $10^{-39}$ cm$^{2}$. For comparison, the total Higgs production cross section is 48600 fb.}.
+\footnote{1 barn is a unit of area corresponding to $10^{-24}$ cm${^2}$ and 1 femtobarn (fb) = $10^{-39}$ cm$^{2}$.
+For comparison, the total Higgs production cross section is 48600 fb.}.
 In the first part of Run 2 (2015-2016), the delivered luminosity has been measured to be \lumi{38.4} with an unprecedented precision of 1.3\% \cite{Sirunyan:2021qkt}.
@@
 This figure shows that one of the dominant uncertainties which remain to be determined is due to the luminosity measurement.
-In this project, we also perform studies for the design and construction of an upgraded luminosity measurement system to be installed for CMS in the HL-LHC phase}\cite{Collaboration:2706512}.
+%In this project, we also perform studies for the design and construction of an upgraded luminosity measurement system to be installed for CMS in the HL-LHC phase\cite{Collaboration:2706512}.
 
@@
 
-This project has two main parts, in the first part we propose to perform an analysis of the LHC luminosity data  recorded by the CMS experiment during 2017 and 2018 using Pixel Cluster Counting (PCC) method.
-In the second part we develop an upgraded luminosity measurement system for the HL-LHC phase (2026-2038).
+In the first part we propose to perform an analysis of the LHC luminosity data  recorded by the CMS experiment during 2017 and 2018 using Pixel Cluster Counting (PCC) method.
 
@@
 
-The second objective is to develop an upgraded luminosity measurement system for the HL-LHC phase using Tracker Endcap Pixel detector (TEPX).
+%The second objective is to develop an upgraded luminosity measurement system for the HL-LHC phase using Tracker Endcap Pixel detector (TEPX).
 TEPX is a part of new tracker detector proposed by the CMS collaboration which will replace the current one during LS3 (2024-2026).
@@
 
-For the upgrade part of this project, we must consider that in the HL-LHC phase the higher expected pileup (number of proton collisions per bunch crossing) will lead to more difficult scenarios for the luminosity measurement due to increased detector occupancy and larger irradiation of the detector components.
-However, we expect that new methods to be introduced between now and the start of the HL-LHC phase will improve the measurement precision and compensate the higher backgrounds and detector aging.
+%For the upgrade part of this project, we must consider that in the HL-LHC phase the higher expected pileup (number of proton collisions per bunch crossing) will lead to more difficult scenarios for the luminosity measurement due to increased detector occupancy and larger irradiation of the detector components.
+%However, we expect that new methods to be introduced between now and the start of the HL-LHC phase will improve the measurement precision and compensate the higher backgrounds and detector aging.
 
@@
 \item determine the delivered luminosity per lumisection (23 second intervals) and the total integrated luminosity and determine the corresponding uncertainty.
-\end{itemize}
-
-\par
-For the development of the HL-LHC upgrade system:
-\begin{itemize}
-\item study the different parts of the TEPX detector.
-\item study the pixel cluster counting at the HL-LHC conditions using simulations of the TEPX detector.
-\item develop an algorithm for counting cluster coincidences using sensor layers of the same disk in the TEPX detector in order to reduce backgrounds.
-\item determine the linearity and statistical precision of the PCC method and coincidence counting method for the TEPX detector and its constituent parts (disks and rings).
 \end{itemize}
@@
 
-For the upgrade part of this project, the research consists of studying the expected performance of the TEPX disks of the CMS tracker in the HL-LHC phase.
-The current design of the this tracker is shown in Figure~\ref{fig:tepx}, where the TEPX part consists of the last 4 disks at $|z|>170$ cm.
-In the same figure a transverse view of one disk is shown, and shows the layout of the sensor modules along phi for each ring in the disk.
-Studies will be performed using simulated samples with HL-LHC beam conditions, currently the expected pileup for these conditions is about 200 proton collisions per bunch crossing.
-The linearity of the cluster counting algorithm will be studied.
-In addition, a new algorithm will be developed to detect cluster coincidences between consecutive layers of a disk.
-It is expected that coincidences will be less sensitive to backgrounds in HL-LHC pileup conditions and therefore a more robust luminosity measurement can be performed.
-
 \begin{figure}[H]
   \centering
-  \includegraphics[width=0.7\columnwidth]{./cms12.png}
+  \includegraphics[width=0.7\columnwidth]{./cms_layers.png}
   \caption{Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimeter, superconducting solenoid and muon chambers \cite{Chatrchyan:2008aa}.}
@@
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.7\columnwidth]{./TEPX_rz.pdf}
-  \includegraphics[width=0.27\columnwidth]{./TEPX_rphi.pdf}
-  \caption{
-    Left: Longitudial view of the current design of the CMS tracker detector for the HL-LHC phase. The TEPX consists of the last 4 disks on each side at $|z|>$ 1700 mm.
-    Right: Transverse view of one TEPX disk showing the layout of the sensors in each of the 5 rings \cite{Klein:2017nke}.
-  }
-  \label{fig:tepx}
-\end{figure}
-
 \section{EXPECTED RESULTS}
 
-From this project two main publications are expected:
-\begin{itemize}
-\item
 For the Run 2 luminosity mesurement, the student will perform the studies for the selection of good modules for calculating luminosity using the PCC method.
@@
 The results of these studies will be published in a peer-reviewed scientific journal.
-\item
-For the development of the HL-LHC upgrade system, we expect to produce a Technical Design Report (TDR) with the proposed design and algorithms to use the TEPX detector.
-This document will be published in the CERN document server (CDS) and submitted to the LHC committee for approval of required funding for the construction and operation of the system.
-\end{itemize}
 
@@
 
-\item {\bf Semester 1 (2019-2)}:
+\item {\bf Summer 2021}:
   \SubItem{ Readings on Standard Model of particle physics theory}
-  \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
+  \SubItem{ Readings on the LHC and CMS experiments}
+  \SubItem{ Linux/Computing skills (\textsc{Bash, Emacs, c/c++, python, ROOT})}
+  \SubItem{ Computing accounts at CERN and Fermilab}
   \SubItem{ Initial planning of the analysis strategy}
 
-\item {\bf Semester 2 (2020-1)}:
-  \SubItem{ Course I on particle physics, particle detection, or data analysis}
-  \SubItem{ Readings on the LHC and CMS experiments}
-  \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
-  \SubItem{ Computing accounts at CERN and Fermilab}
-  \SubItem{ Studies of the TEPX luminometer upgrade}
+\item {\bf Semester 2021-2}:
+  \SubItem{ Course I: on particle physics, particle detection, or data analysis}
+  \SubItem{ Analysis/Computing skills (\textsc{Bash, Emacs, c/c++, python, ROOT})}
+  \SubItem{ Analysis of the LHC Run 2 data using the PCC method}
 
-\item {\bf Semester 3 (2020-2)}:
+\item {\bf Semester 2022-1}:
+  \SubItem{ Completion of the analysis of the LHC Run 2 data using the PCC method}
+  \SubItem{ Presentation of results at national or international conference}
+  \SubItem{ Thesis writing}
   \SubItem{ Course II on particle physics, particle detection, or  data analysis}
-  \SubItem{ Studies of the TEPX luminometer upgrade}
-
-\item {\bf Semester 4 (2021-1)}:
-  \SubItem{ Completion of the TEPX luminometer studies for the TDR document}
-  \SubItem{ Studies of the LHC Run 2 data using the PCC method}
-  \SubItem{ Writing of the monograph}
-
-\item {\bf Semester 5 (2021-2)}:
-  \SubItem{ Publication of the TDR document in CDS and submission to the LHCC for review}
-  \SubItem{ Presentation at national or international conferences of the TEPX upgrade studies}
-  \SubItem{ Studies of the LHC Run 2 data using the PCC method}
-
-\item {\bf Semester 6 (2022-1)}:
-  \SubItem{ Completion of the studies of the Run 2 data luminosity measurement}
-  \SubItem{ Writing of the Run 2 data luminosity measurement publication and review within the CMS collaboration}
-
-\item {\bf Semester 7 (2022-2)}:
-  \SubItem{ Publication of the Run 2 data luminosity measurement in a peer reviewed journal}
-
-\item {\bf Semester 8 (2023-1)}: 
-  \SubItem{ Presentations at national or international conferences for both the Run 2 luminosity measurement and TEPX luminometer for HL-LHC}
-  \SubItem{ Writing of the Ph.D thesis}
 

### 2021-06-14 project_rodolfo/paper.tex
rodolfo anteproyecto

@@
-%\documentclass[final,3p]{article}
-\documentclass[final,12p]{article}
+\documentclass[final,12pt]{article}
 \usepackage{graphicx}
@@
 \newcommand{\lumi}[1]{{#1~fb$^{-1}$}}
-\newcommand{\instlumi}[1]{#1$\times 10^{34}$ cm$^{-2}$s$^{-1}$} }
+\newcommand{\instlumi}[1]{#1$\times 10^{34}$ cm$^{-2}$s$^{-1}$}
 
@@
 In the first part of Run 2 (2015-2016), the delivered luminosity has been measured to be \lumi{38.4} with an unprecedented precision of 1.3\% \cite{Sirunyan:2021qkt}.
-For the second part of Run 2 (2017-2018), the integrated luminosity is about \lumi{78}, but its precise value and uncertainty remain to be determined and is one of the main objectives of this thesis project \cite{CMS:2018elu}.
+For the second part of Run 2 (2017-2018), the integrated luminosity is about \lumi{78}, but its precise value and uncertainty remain to be determined and is the main objective of this thesis project \cite{CMS:2018elu}.
 
@@
 This figure shows that one of the dominant uncertainties which remain to be determined is due to the luminosity measurement.
-%In this project, we also perform studies for the design and construction of an upgraded luminosity measurement system to be installed for CMS in the HL-LHC phase\cite{Collaboration:2706512}.
 
@@
 
-In the first part we propose to perform an analysis of the LHC luminosity data  recorded by the CMS experiment during 2017 and 2018 using Pixel Cluster Counting (PCC) method.
+We propose to perform an analysis of the LHC luminosity data recorded by the CMS experiment during 2017 and 2018 using the Pixel Cluster Counting (PCC) method~\cite{LUM12001}.
 
@@
 
-The main objective of this work is to perform a measurement of the 2017-2018 LHC delivered luminosity with a precision at the level of 2\% or less using the CMS Pixel detector.
+The main objective of this work is to perform a measurement of the 2017-2018 luminosity with a precision at the level of 2\% or less using the CMS Pixel detector.
 This precision is necesary for testing SM of elementary particles and identifying possible new physics which could elucidate the nature of Dark Matter in our universe.
-
-%The second objective is to develop an upgraded luminosity measurement system for the HL-LHC phase using Tracker Endcap Pixel detector (TEPX).
-TEPX is a part of new tracker detector proposed by the CMS collaboration which will replace the current one during LS3 (2024-2026).
 
@@
 
-As mentioned in the introduction, precision achieved in the measurement of integrated luminosity during Run 1 was about 2.5\% using  methods developed for the first time.
-In 2015 and 2016 the uncertainty achieved was 1.6\% and 1.2\%, respectively, for datasets corresponding to \lumi{2.5} and \lumi{36}  \cite{Sirunyan:2021qkt}.
+As mentioned in the introduction, the precision achieved in the measurement of the integrated luminosity during Run 1 (2011-2012) was about 2.5\% using  methods developed for the first time.
+In 2015 and 2016 runs, the uncertainty achieved was 1.6\% and 1.2\%, respectively, for datasets corresponding to \lumi{2.5} and \lumi{36}  \cite{Sirunyan:2021qkt}.
 The methods used for the 2015 and 2016 data are similar to the strategy we propose in this project.
@@
 
-%For the upgrade part of this project, we must consider that in the HL-LHC phase the higher expected pileup (number of proton collisions per bunch crossing) will lead to more difficult scenarios for the luminosity measurement due to increased detector occupancy and larger irradiation of the detector components.
-%However, we expect that new methods to be introduced between now and the start of the HL-LHC phase will improve the measurement precision and compensate the higher backgrounds and detector aging.
-
 \section{SPECIFIC OBJECTIVES}
 
-For the Run 2 luminosity measurement:
 \begin{itemize}
-\item understand the CMS pixel detector layout including the barrel layers and endcap disks and their constituent modules,
-\item study the stability of the modules in the different layers or disks of the pixel detector and select the stable components,
-\item calculate the visible cross section corresponding to the PCC rate for proton-proton colisions at 13 TeV using the selected pixel detector components,
-\item study the stability and linearity of the PCC luminosity measurement by comparing to other CMS luminometers as a measurement of the systematic uncertainties,
-\item determine the delivered luminosity per lumisection (23 second intervals) and the total integrated luminosity and determine the corresponding uncertainty.
+\item Understand the CMS pixel detector layout including the barrel layers and endcap disks and their constituent silicon pixel modules.
+\item Study the stability of the modules in the different layers or disks of the pixel detector and select the stable components.
+\item Determine the calibration constant corresponding to the PCC luminometer for proton-proton colisions at 13 TeV using the selected pixel detector components.
+\item Determine the delivered luminosity per lumisection (23 second intervals) and the total integrated luminosity for 2017 or 2018 data.
+\item Study some of the systematic uncertainties related to the measurement of the luminosity using the PCC. For example, calibration uncertainties, stability, and linearity.
 \end{itemize}
@@
 The PCC method consists of the reconstruction of track clusters produced by charged particle tracks as shown in Figure~\ref{fig:trackcluster}.
-Due to the fine granularity of the pixel sensors and the large number of total pixels, the hit occupancy in the sensors remains very small, order of 1\%, during normal collisions.
+Due to the fine granularity of the pixel sensors and the large number of total pixels, the hit occupancy in the sensors remains very small (order of 1\%) during physics runs.
 This low occupancy makes the PCC  very linear as a function of pileup, an essential property of a good luminometer.
@@
 The calibration of the luminometer consists of a van der Meer (vdM) scan performed in a special LHC run usually at the beginning of the run period (year).
-In this calibration setup, proton beams are moved across each other in separation steps of about 100 micrometers, by measuring the rates of clusters with the PCC algorithm and knowledge of the beam parameters during the vdM conditions, the calibration constant ($\sigma_{vis}$) is determined.
+In this calibration setup, proton beams are moved across each other in separation steps of about 100 micrometers,
+by measuring the rates of clusters with the PCC algorithm and knowledge of the beam parameters during the vdM conditions, the calibration constant ($\sigma_{vis}$) is determined.
 This calibration constant is then used to normalize the measured PCC rates during normal running throughout the data-taking year.
@@
 
-For the Run 2 luminosity mesurement, the student will perform the studies for the selection of good modules for calculating luminosity using the PCC method.
-From past performance of this algorithm it is expected that this measurement will give one of the best linearity and stability systematic uncertainties for the integrated luminosity value.
-The results of these studies will be published in a peer-reviewed scientific journal.
-
-Also, the student will become a part of an international experiment and is expected to present his results at national or international scientific conferences.
+\begin{itemize}
+\item Final selection of good modules for calculating luminosity using the PCC method.
+\item Determination of the PCC calibration constant by analyzing the vdM scan data.
+\item Determination of the luminosity per lumi section and integrated for the 2017 or 2018 data.
+\item Estimation of the systematic uncertainties associated with the calibration constant or the integrated luminosity values.
+\item A presentation of the results in a national or international conference.
+\item Publication of the results in a peer-reviewed scientific journal.
+\end{itemize}
 
@@
 \item {\bf Summer 2021}:
-  \SubItem{ Readings on Standard Model of particle physics theory}
-  \SubItem{ Readings on the LHC and CMS experiments}
+  \SubItem{ Readings on Standard Model of particle physics,  the LHC and CMS experiments}
   \SubItem{ Linux/Computing skills (\textsc{Bash, Emacs, c/c++, python, ROOT})}
@@
   \SubItem{ Analysis/Computing skills (\textsc{Bash, Emacs, c/c++, python, ROOT})}
-  \SubItem{ Analysis of the LHC Run 2 data using the PCC method}
+  \SubItem{ Analysis of the LHC Run 2 luminosity data using the PCC method}
 
 \item {\bf Semester 2022-1}:
-  \SubItem{ Completion of the analysis of the LHC Run 2 data using the PCC method}
+  \SubItem{ Course II on particle physics, particle detection, or  data analysis}
+  \SubItem{ Completion of the analysis of the LHC Run 2 luminosity data using the PCC method}
   \SubItem{ Presentation of results at national or international conference}
   \SubItem{ Thesis writing}
-  \SubItem{ Course II on particle physics, particle detection, or  data analysis}
 

### 2021-06-15 project_rodolfo/paper.tex
rodolf

@@
 The Higgs boson ($H$), is the last of the gauge bosons, it gives mass to the other SM particles via electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}.
-The heavy particles ($W^{\pm}$, $Z^0$, $H$, and top) can only be produced at high energy particle colliders like the Large Hadron Collider (LHC) operating at a center-of-mass energy of 13 TeV in Geneva, Switzerland.
+The heavy particles ($W^{\pm}$, $Z^0$, $H$, and top) can only be produced at high energy particle colliders like the Large Hadron Collider (LHC) operating at a center-of-mass energy of 13 TeV in Geneva, Switzerland (Figure ~\ref{figure5}).
 Until the 90s, existence of almost all the SM particles were confirmed except the top quark and the Higgs boson. 

### 2021-06-16 project_rodolfo/paper.tex
rod

@@
 For comparison, the total Higgs production cross section is 48600 fb.}.
-In the first part of Run 2 (2015-2016), the delivered luminosity has been measured to be \lumi{38.4} with an unprecedented precision of 1.3\% \cite{Sirunyan:2021qkt}.
-For the second part of Run 2 (2017-2018), the integrated luminosity is about \lumi{78}, but its precise value and uncertainty remain to be determined and is the main objective of this thesis project \cite{CMS:2018elu}.
+In the first part of Run 2 (2015-2016), the delivered luminosity has been measured to be \lumi{38.4} with an unprecedented precision of 1.3\% \cite{Sirunyan:2021qkt-corr}.
+For the second part of Run 2 (2017-2018), the integrated luminosity is about \lumi{78}, but its precise value and uncertainty remain to be determined and is the main objective of this thesis project \cite{CMS:2018elu-corr}.
 
-The plan of the LHC till year 2038 is to obtain datasets with up to 10 times higher values of instanteneous luminosities in the final phase, the  High Luminosity LHC (HL-LHC), and corresponding integrated luminosities of order \lumi{3000} as shown in Figure~\ref{figure6}.
+The plan of the LHC till year 2038 is to obtain datasets with up to 10 times higher values of instanteneous luminosities in the final phase, the  High Luminosity LHC (HL-LHC), and corresponding integrated luminosities of order \lumi{3000} \cite{Dainese:3}; the most updated projected luminosity performance along the  whole  life  of  LHC/HL-LHC  machine is shown Figure~\ref{figure6}.
 These final datasets will provide  precise measurements of the properties of the Higgs boson and other SM particles as shown in Fig. ~\ref{figureKappasUncs}.
@@
 The complex consists of three accelerator stages: the proton (p) or lead (Pb) source, the Proton Synchrotron (PS), the Super Proton Synchrotron (SPS), and the 27 km LHC ring.
-Four collision points are shown corresponding to the ALICE, ATLAS, LHCb, and CMS detectors  \cite{Mobs:2684277}.
-}
+Four collision points are shown corresponding to the ALICE, ATLAS, LHCb, and CMS detectors  \cite{wiki:xxx}.} % Mobs:2684277
   \label{figure5}
@@
   \centering
-  \includegraphics[width=0.8\columnwidth]{./HLLHCLumi.png}
-  \caption{Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities.
-Points show instantaneous luminosity while the line shows luminosity accumulated \cite{collaborations2019report}.}
+  \includegraphics[width=0.8\columnwidth]{./lumint.png}
+  \caption{Forecast for peak luminosity (red dots) and integrated luminosity (violetline) in the HL-LHC era with nominal HL-LHC parameters\cite{BejarAlonso:2749422}.}  %\cite{collaborations2019report} era la [5] de la ant fig2
   \label{figure6}
@@
    \caption{
-     Left: Main production mechanisms for the Higgs boson at the LHC: gluon-gluon fusion (ggF), vector-boson fusion (VBF), associated vector boson (VH), associated top-quark pair (ttH), and  associated single-top quark production (tH)  \cite{Grojean:2017hsb}  \cite{Khachatryan:2015ota} .
-     Right: Expected uncertainties on the Higgs coupling parameters for  \lumi{3000} of proton-proton collision data at 13 TeV center-of-mass energy \cite{Cepeda:2019klc}.
+     Left: Main production mechanisms for the Higgs boson at the LHC: gluon-gluon fusion (ggF), vector-boson fusion (VBF), associated vector boson (VH), associated top-quark pair (ttH), and  associated single-top quark production (tH)  \cite{Grojean:2017hsb-corr}  \cite{Khachatryan:2015ota} .
+     Right: Expected uncertainties on the Higgs coupling parameters for  \lumi{3000} of proton-proton collision data at 13 TeV center-of-mass energy \cite{Cepeda:2019klc-corr}.
    }
@@
 As mentioned in the introduction, the precision achieved in the measurement of the integrated luminosity during Run 1 (2011-2012) was about 2.5\% using  methods developed for the first time.
-In 2015 and 2016 runs, the uncertainty achieved was 1.6\% and 1.2\%, respectively, for datasets corresponding to \lumi{2.5} and \lumi{36}  \cite{Sirunyan:2021qkt}.
+In 2015 and 2016 runs, the uncertainty achieved was 1.6\% and 1.2\%, respectively, for datasets corresponding to \lumi{2.5} and \lumi{36}  \cite{Sirunyan:2021qkt-corr}.
 The methods used for the 2015 and 2016 data are similar to the strategy we propose in this project.
-We expect that the final uncertainties for the 2017 and 2018 datasets to be similar, but the ultimate goal of the CMS collaboration is to reduce these uncertainties to below 1\%  \cite{Dainese:2019rgk}.
+We expect that the final uncertainties for the 2017 and 2018 datasets to be similar, but the ultimate goal of the CMS collaboration is to reduce these uncertainties to below 1\%  \cite{Dainese:3}.
 
@@
 by measuring the rates of clusters with the PCC algorithm and knowledge of the beam parameters during the vdM conditions, the calibration constant ($\sigma_{vis}$) is determined.
-This calibration constant is then used to normalize the measured PCC rates during normal running throughout the data-taking year.
+This calibration constant is then used to normalize the measured PCC rates during normal running throughout the data-taking year \cite{pas:2018vdm}.
 

### 2022-04-20 tesis_Hedwin/Abstract/abstract.tex
Hedwin thesis

\begin{abstract}
\begin{center}
    {\huge Abstract}
\end{center}
    The design and expected performance of the Tracker End-cap Pixel (TEPX) and other subdetectors as luminometers for the CMS experiment at the upcoming High-Luminosity LHC (HL-LHC) is described. The TEPX detector is composed of 4 double sided disks covering a range on $|z|$ from 175 to 265 cm, each one made of 5 rings composed of silicon sensors with a high number of pixels. Disk 4 Ring 1 (TEPXD4R1) will be designated for luminosity measurements only, utilising the same method as the TEPX luminometer, the pixel cluster counting (PCC) method. For the HL-LHC, the goal is to achieve a final uncertainty of $1\%$ for the luminosity measurements. The expected performance and linearity of the TEPX, TEPXD4R1 and other luminometers in terms of statistical precision, for van der Meer (vdM) scan calibration  and for physics conditions, are presented. The bandwidth needed for the transfer of the luminosity data and disk needed for storage are estimated.
\end{abstract}

### 2022-04-20 tesis_Hedwin/Abstract/resumen.tex
Hedwin thesis

\begin{abstract}
    \begin{center}
    {\huge Resumen}
\end{center}
Se describe el diseño y el rendimiento esperado del Tracker End-cap Pixel (TEPX) y otros sub detectores como luminómetros para el experimento CMS, en el próximo LHC de alta luminosidad (HL-LHC). El detector TEPX está compuesto por 4 discos de doble cara que cubren un rango en $ | z | $ de 175 a 265 cm, cada uno compuesto por 5 anillos hechos de sensores de silicio con un alto número de píxeles. El Disco 4 Anillo 1 (TEPXD4R1) se designará solo para mediciones de luminosidad, utilizando el mismo método que el luminómetro TEPX, el método de conteo de conjuntos de píxeles (PCC). Para la etapa del HL-LHC, el objetivo es lograr una incertidumbre final de $ 1 \% $ para las mediciones de luminosidad. Se presentan el rendimiento esperado y la linealidad de TEPX, TEPXD4R1 y otros luminómetros en términos de precisión estadística, para la calibración de escaneo de van der Meer (vdM) y para condiciones físicas. El ancho de banda necesario para la transferencia de los datos de luminosidad y el disco necesario para su almacenamiento es estimado.

\end{abstract}

### 2022-04-20 tesis_Hedwin/Chapter3/chapter3.tex
Hedwin thesis

\chapter{  Luminometer system description}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Pixel Clusters and the PCC method}

Luminosity measurements at CMS are provided by the several luminometers in the detector.
Each luminometer measures the event rate by reading out a specific quantity of objects observed by the detector, These can be for example clusters, coincidences or tracks. For the TEPX luminometers these objects are pixel clusters and coincidences, using the pixel cluster counting (PCC) method to provide offline luminosity measurements. This method was one of the main source of luminosity measurements for CMS, during the 2016-2018 data taking period, and it is expected to be the same for the Phase-2 upgrade.\\
The clustering algorithm is very complex, but striping it down to the most simple example: the algorithm considers a cluster of pixels only if two hits, or more,  activate neighboring pixels horizontally, vertically or diagonally, within the same module. Figure\ref{pixclust} shows an example of this.
\begin{figure}[H]
\begin{minipage}[b]{0.5\linewidth}
\centering
\begin{tikzpicture}
    [%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        box/.style={rectangle,draw=black,thick, minimum size=1cm},
    ]%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\foreach \x in {0,1,...,4}{
    \foreach \y in {0,1,...,4}
        \node[box] at (\x,\y){};
}

\node[box,fill=red  ] at (1,4){};  
\node[box,fill=red ] at (0,4){};  
\node[box,fill=red ] at (0,3){}; 
\node[box,fill=red  ] at (1,3){};
\end{tikzpicture}
\end{minipage}
\begin{minipage}[b]{0.5\linewidth}
\centering
\begin{tikzpicture}
    [%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        box/.style={rectangle,draw=black,thick, minimum size=1cm},
    ]%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\foreach \x in {0,1,...,4}{
    \foreach \y in {0,1,...,4}
        \node[box] at (\x,\y){};
}

\node[box,fill=red  ] at (0,4){};  
\node[box,fill=red ] at (2,4){};  
\node[box,fill=red ] at (1,1){}; 
\node[box,fill=red ] at (4,2){}; 
\end{tikzpicture}
\end{minipage}
\caption[Pixel cluster selection algorithm]{The figure shows a representation of the pixel modules, \textit{left}: four hits (red) on four neighbouring pixels, these is considered a pixel cluster by the clustering algorithm. \textit{right}: the hits activate random pixel in the module, these will not be considered as a cluster by the clustering algorithm.}
\label{pixclust}
\end{figure}
A hit occurs when a charged particle passes through a silicon pixel, depositing an amount of energy in the pixel. The PCC method takes advantage of the high densities of pixels, and the relative low occupancy of the CMS tracker, to provide precise luminosity measurements, with good stable measurements over time. The number of pixel clusters activated, per bunch crossing, is a linear function of the number of proton-proton interactions per bunch crossing (pileup). During several zero-bias events, where the only requirement is that the bunches pass through one another on the interaction point, a mean number of pixel clusters, $\left\langle N_{\text {cluster }}\right\rangle
$,is activated:
\begin{equation}
\left\langle N_{\text {cluster }}\right\rangle\equiv\left\langle N_{\text {cluster/int}}\right\rangle\mu
\label{pcc}
\end{equation}
where $\left\langle N_{\text {cluster/int}}\right\rangle$ is the mean number of clusters activated per interaction and $\mu$ is the pileup. Using equation \ref{pileup} and \ref{pcc}, a calibration constant between the mean number of pixel cluster and the instantaneous luminosity can be defined:

\begin{equation}
    \left\langle N_{\text {cluster }}\right\rangle\equiv\frac{\sigma_{vis}}{f}\mathcal{L}_{ins}
\end{equation}
where the calibration constant, $\sigma_{vis}$, is   
\begin{equation}
    \sigma_{vis}=\sigma_{tot}\left\langle N_{\text {cluster/int}}\right\rangle
\end{equation}
The value of $\sigma_{vis}$ is determined using a van der Meer (vdM) scan, with 
\begin{equation}
    \sigma_{vis}= \frac{\left\langle N_{\text {cluster/vdM }}\right\rangle f }{\mathcal{L}_{ins/vdM}}
\end{equation}
where $\left\langle N_{\text {cluster/vdmM }}\right\rangle$ is the mean number of pixel cluster at the peak of the scan and $\mathcal{L}_{ins/vdM}$ is the instantaneous luminosity obtained in the scan \cite{CMS-PAS-LUM-12-001}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Cluster coincidence algorithm }

The other object used by the TEPX luminometer to measure the event rate are two-fold coincidences. Coincidences are less prone to contamination by false hits produced in the detector after a bunch crossing (afterglow), due to the slow dissipation of charge and neutrons produced by the surrounding material (albedo). Two-fold coincidences are created when a particle hits overlapping modules, in the different layers of the TEPX disks. Due to this, coincidences are more likely to be a real hit than random electrical noise. The cylinder/disk like geometry of the TEPX detector allows for coincidences to be constructed in two ways: coincidences in $\phi$ require modules overlapping in the same ring, in front and in the back of a double sided disk, while coincidences in $r$ requires overlapping modules from different layers. These two ways of constructing two-fold coincidences are illustrated in Figure \ref{3x2x}. The surface area of overlapping modules tends to be larger in $\phi$ than in the $r$ direction. In order for a 2x coincidence to be considered, activated pixel clusters must fall in to specific cuts (on their $\delta r$ and $\delta \phi$ separations). Finally, three-fold coincidences can occur as well, however, these types of coincidences are beyond the scope of this work.\\
Coincidences provide another method of measuring luminosity and bring more stability, linearity and precision to the TEPX luminometers.
\begin{center}
\begin{figure}[H]
    \centering
    \includegraphics[scale=.4]{Chapter3/3x2x.png}
    \caption[Regions where two-fold coincidences can occur in r and $\phi$.  ]{Diagram of the regions in r and $\phi$ where pixel modules overlap, between the front and the back layers of one double-sided disk, from which two-fold coincidences come. }
    \label{3x2x}
\end{figure}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Calibration using the van der Meer method }
The calibration of the luminometrs is done by performing van der Meer scans, where the goal is to determine the calibration constant $\sigma_{\text {vis}}$.\\
In practice, the normalized bunch transverse distributions of each beam is not known, thus the overlap width integrals in \ref{lumy2} cannot be solved analytically. The vdM scans determines the valued of these integrals by separating the two beams and moving them across each other while measuring the resulting rates (Figure \ref{vdm1} (left) illustrates this process)
\begin{equation}
    \int \rho_1(x)\rho_{2}(x)dx=\frac{R_{x}(0)}{\int R_{x}(\Delta x)d\Delta x}
\end{equation}
where $R_{x}(\Delta x)$ is the measured rate, when the beams are separated a distance $\Delta x$. Defining the beam overlap  width as
\begin{equation}
\Sigma_{x}=\frac{1}{\sqrt{2\pi}}\frac{\int R_{x}(\Delta x) d\Delta x}{R_{x}(0)}
\label{sigma2}
\end{equation}
doing the same can be done for $\Sigma_{y}$, equation \ref{lumy2} can be rewritten: 
\begin{equation}
    \mathcal{L}=\frac{N_1N_2N_p f}{2\pi\Sigma_x\Sigma_y}
\end{equation}
Once measurements have been taken, the rate is plotted as a function of beam separation and a Gaussian-like function is fitted to the data, as shown id Figure \ref{vdm1} (right). Using this function, the integral in equation \ref{sigma2} can be solved and the overlap width determined. Using \ref{lumy0} and \ref{lumy2} the calibration constant $\sigma_{vis}$ can be determined:
\begin{equation}
    \sigma_{vis}=\frac{2\pi \Sigma_x\Sigma_y}{N_1N_2N_p f} R_{peak}
    \label{sigmavis}
\end{equation}
where $R_{peak}$ is the measured rate at the peak of the scan \cite{CMS-PAS-LUM-18-002}\cite{CMS-PAS-LUM-12-001}. The original procedure can be found in \cite{vanderMeer:296752}.
\newcommand\gauss[2]{1/(#2*sqrt(2*pi))*exp(-((x-#1)^2)/(2*#2^2))} % Gauss function, parameters mu and sigma

\begin{figure}[ht]
\begin{minipage}[b]{0.5\linewidth}
\centering
\begin{tikzpicture}[x=.5cm,y=.5cm, scale=1.6]

\draw[<->,very thick] (-4.5,0) -- (4.5,0)node[right] {$x$};
\draw[<->,very thick] (0,-3) -- (0,3) node[above] {$ y$};

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\draw[fill=red, opacity=0.6] (0,-1.6) ellipse (4 mm and 2.5 mm);
\draw[fill=blue, opacity=0.6] (0,-2) ellipse (4 mm and 2.5 mm);

\draw[fill=red, opacity=0.6] (0,0) ellipse (4 mm and 2.5 mm);
\draw[fill=blue, opacity=0.6] (0,0) ellipse (4 mm and 2.5 mm);

\draw[fill=red, opacity=0.6] (0,1.6) ellipse (4 mm and 2.5 mm);
\draw[fill=blue, opacity=0.6] (0,2) ellipse (4 mm and 2.5 mm);

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\draw[fill=red, opacity=0.6] (-2.6,0) ellipse (4 mm and 2.5 mm);
\draw[fill=blue, opacity=0.6] (-3,0) ellipse (4 mm and 2.5 mm);

\draw[fill=red, opacity=0.6] (0,0) ellipse (4 mm and 2.5 mm);
\draw[fill=blue, opacity=0.6] (0,0) ellipse (4 mm and 2.5 mm);

\draw[fill=red, opacity=0.6] (2.6,0) ellipse (4 mm and 2.5 mm);
\draw[fill=blue, opacity=0.6] (3,0) ellipse (4 mm and 2.5 mm);
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\draw[->,]  (1,2) -- (1,0.5)node[pos=0.25, right] {\text {scan in y}};
\draw[->,]  (-3,.7) -- (-0.5,.7)node[pos=0.5, above] {\text {scan in x}};
\end{tikzpicture}
\end{minipage}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[b]{0.5\linewidth}
\centering
\begin{tikzpicture}
\begin{axis}[every axis plot post/.append style={ color=black,
  mark=x ,domain=-4:4,samples=9,smooth,fill=blue,opacity=0.4, mark size=5pt,mark options={color=red}}, % All plots: from -2:2, 50 samples, smooth, no marks
axis x  line=bottom,very thick, % no box around the plot, only x and y axis
axis y line=left,very thick, % the * suppresses the arrow tips
enlargelimits=upper, xmin=-4.5,
xlabel=\(\Delta x/y\),
ylabel=\(Rate\),
ytick={5},xtick={5},
every axis y label/.style={
    at={(ticklabel* cs:1.05)},
    anchor=south,
},
every axis x label/.style={
    at={(ticklabel* cs:1.05)},
    anchor=west,
},] % extend the axes a bit to the right and top
\addplot[]  {\gauss{0}{2}};

\end{axis}
\draw[<->,very thick] (1.8,2.83) -- (4.8,2.83)node[pos=0.5,below] {$\Sigma_{x/y}$};
\draw[dashed,very thick] (0,5.18) -- (3.33,5.18)node[pos=0.5,below] {\text {Peak Rate}};
\end{tikzpicture}

\end{minipage}
\caption[vdM scan process.]{\textit{Left}: A diagram that shows how the two beams are scanned across the x and y axis. \textit{ Right}: An example of a Gaussian-like function (Blue), being fitted to the rate measurements (red xs) taken during a VDM scan.}
\label{vdm1}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data acquisition}
After event rate measurements have been taken, the data needs to be safely transferred and stored. In order to do this, several systems are put in place. Every subdetector has a dedicated CMS subsystem or a dedicated BRIL (Beam Radiation, Instrumentation, and Luminosity) system that takes care of this process. In the case of the TEPX, and other luminometers described in section 3.4.1, a combination of CMS and BRIL systems will be used, while TEPXD4R1 will be solely operated by BRIL.\\
The way counts per bunch crossing measured by a given luminometer are stored in CMS, is by using histograms. Every time a full orbit of bunches collides (3564 bunches), the counts per bunch crossing is histogramed and stored. Depending on the geometry of the subdetector, the number of histograms generated by each changes. In the case of TEPX and TEPXD4R1 a histogram is created per quarter ring, this means that a total of 152 histograms are created by TEPX (not including the histograms from D4R1) and 8 by TEPXD4R1, in one orbit. The histograming is done by the dedicated back-end of each subdetector, a combination of software and hardware components in charge of creating these histograms. Once the histograms have been correctly created they are read, processed and stored by the BRILDAQ (BRIL data acquisition) system. Figure \ref{histhit} shows an example of a histograms for TEPX in the case of pixel clusters.
\begin{center}
    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.5]{Chapter3/histbx.png}
        \caption[Histogram of the mean number of pixel clusters per bunch crossing (BX) measured by the Phase-1 pixel detector.]{The histogram shows the mean number of pixel clusters per bunch crossing (BX) for one lumisection (23.3 seconds), measured by the Phase-1 pixel detector during regular physics runs. The measurements from the 2018 data taking period.}
        \label{histhit}
    \end{figure}
\end{center}
Once histograms have been created, safely transferring and storing them is important, in order to do this the memory required to store them needs to be known. The memory size of each histogram depends on the information in each of  them. All histograms have 3564 bins, one bin for each bunch crossing, these bins store the number of counts measured in a given bunch crossing, thus, the bits of information stored in these bins will give the memory of each histogram.
\begin{equation}
    \text {Memory per Hist}= \text {No. of Bins}\times \text {bits per Bin}
    \label{histm}
\end{equation}
 where the bits per Bin are calculated using 
 \begin{equation}
     \text {bits per Bin}= log_2(N)
     \label{logn}
 \end{equation}
where $N$ is the maximum expected number of counts per bunch crossing for a given integration period, it is worth mentioning that the results from equation \ref{logn} are rounded up to the closes integer. The maximum expected number of counts per bunch crossing is given by

\begin{equation}
    N=n\frac{\text {Total Trigger Rate}}{3564}t
    \label{N}
\end{equation}
where $n$ is the mean number of counts per event and $t$ is the integration period. Equation \ref{N} assumes that the Total Trigger Rate is distributed uniformly. Once the memory of the histogram is known, the data bandwidth needed to store all the histograms can be calculated, the Data Transfer Rate is given by 
\begin{equation}
    \text {Data Transfer Rate}=\frac{No. Hist\times Memory per Hist}{t}
    \label{drate}
\end{equation}
where No. Hist is the number of histograms created by the detector and t is the time in which the information is transferred.\\

\subsection*{32-bit word implementation}
The data at CMS is not transferred bit by bit, rather, is transferred in packages of information called words. Each word contains 32-bits of information, this means that all data transferred has to, first, be converted in to a 32-bit word. The way this is applied to the histograms is by converting the information in each bin in to a word, this is done in two ways:
\begin{itemize}
    \item If the Bits per bin$\leq16$ bits, the number of bits is
rounded to 16 and two bins are grouped in one word.
\item If $16\leq$ Bits per bin$\leq32$,  the number of bits is
rounded to 32-bit word and one word is used for each bin.
\end{itemize}

Aside from this, the TEPX luminometers use additional words for the overhead of the histograms data format:
\begin{itemize}
    \item 9 words for the header for TEPX and D4R1.
    \item  768 words for errors for TEPX and 160 for D4R1.
    \item 4 words for the mask for TEPX and 2 forD4R1.
\end{itemize}
These additional data has to be taken in to account for each histograms, when calculating the needed memory to store and transfer them. Finally, using equation \ref{logn} the bits per bin can be calculated, using data from the high pileup simulation \cite{datarates}. The results for the TEPX luminometers is shown in Table \ref{bitsperbin}.
\begin{table}[ht]
\centering
\caption[ Memory bits required per histogram bin for the TEPX luminometers.]{Table shows the Trigger rate (kHz), counts per event per detector unit (histogram), number of counts per bx per integration period (1s) and the memory bits required per histogram bin.}
\scalebox{.7}{
\begin{tabular}{|l |c |c |c |c|}
\hline
&  Trigger rate (kHz) & Counts per event & Counts/bx/1s&Bits/bin\\
\hline
TEPXD4R1 Clusters&825&539&1.25e+05&17\\
\hline
TEPXD4R1 2x Coincidences&825&54&1.25e+04&14\\
\hline
TEPX Clusters&75&539&1.13e+04&14\\
\hline
TEPX 2x Coincidences&75&54&1.14e+03&11\\
\hline
\end{tabular}}
\label{bitsperbin}
\end{table}
Using this and equation \ref{drate}, the data rates can be calculated, the results are shown in Table \ref{dataratet} for a transferring time of 1 s.
\begin{table}[ht]
\centering
\caption[Data transfer rates for the TEPX luminometers.]{Data transfer rates for the TEPX luminometers for pileup 200. Columns shown are number of histograms, memory per histogram and data transfer rates (Mbps) for an integration period of 1s. }
\scalebox{.8}{

\begin{tabular}{|l  |c |c |c|}
\hline
&  Number of Histograms & Memory per histogram (Kb) & Data Transfer Rates (Mbps)\\
\hline
TEPXD4R1 Clusters&8&124&0.95\\
\hline
TEPXD4R1 2x Coincidences&8&67&0.5\\
\hline
TEPX Clusters&152&82&12.5\\
\hline
TEPX 2x Coincidences&152&82&12.5\\
\hline
\end{tabular}}
\label{dataratet}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Other luminometers}

The TEPX luminometer is not the only luminometer of the CMS Phase-2 detector, each layer of the detector will have a dedicated luminometer, and corresponding algorithm, to ensure the best luminosity measurements possible.
Figure \ref{cmslum} shows the location of the different luminometers at the CMS detector, for the Phase-2 upgrade. A brief description of the luminometers is presented below.
\begin{center}
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.3]{Chapter3/cmdlum.png}
    \caption[Different subsystems and luminometrs at CMS.]{Layout of the different subsystems and luminometrs at CMS. }
    \label{cmslum}
\end{figure}
\end{center}
\subsection*{Outer tracker layer 6}
From the outer tracker (OT), layer 6 will be a designated luminometer. The object used by these luminometer are track stubs, which are two-hit coincidences between closely spaced silicon modules. Figure \ref{ot} show the layout of the new Phase-2 outer tracker, layer 6 is located in the outer tracker barrel, specifically, the TB2S section.
\begin{center}
\begin{figure}[H]
    \centering
    \includegraphics[scale=.4]{Chapter3/ot.png}
    \caption[Outter tracker layout.]{Diagram of the different parts that conform the outer tracker, the two barrel regions, TBPS and TB2S, and the end-cap region TEDD. The OT layer 6 luminometer corresponds to the last upper layer of TB2S. }
    \label{ot}
\end{figure}
\end{center}

Layer 6 consists of 76 ladders of 12 strip modules made of two Si-strip sensors, as shown in Figure \ref{otlather} (left). The ladders span fully, in the azimuthal range, at each end of the CMS detector. The reconstruction method of the track stubs is shown in Figure \ref{otlather} (right) as well. The tracks are reconstructed at 40 MHz.
\begin{center}
\begin{figure}[H]
    \centering
    \includegraphics[scale=.7]{Chapter3/otlather.PNG}
    \caption[Example of an OT layer 6 ladder and the stub selection process.]{\textit{Left}: An example of a ladder with the the 12 strip modules (regions in yellow). \textit{Right}: Diagram of the stub selection process. The black squares represent hits, and the green squares represent the regions where the other hit could take place, to be considered a stub.}
    \label{otlather}
\end{figure}
\end{center}

The OT layer 6 luminometers, creates one histograms per one 12 module ladder, for a total of 152. As well as the TEPX luminometers, the histograms created in layer 6 will have additional words for the overhead of the histograms data format:
\begin{itemize}
    \item 9 words for the header.
    \item  192 words for errors.
    \item 4 words for the mask.
\end{itemize}

Figure \ref{otstubs} shows the expected number of track stubs per bunch crossing as function of the ladders ID. Tables 3.3
and 3.4 show the expected Bits per Bin and the Data Transfer Rates for the OT layer 6 luminometer, calculated using data from the high pileup simulation.
\begin{center}
\begin{figure}[H]
    \centering
    \includegraphics[scale=.4]{Chapter3/OT-Rates.png}
    \caption[Simulated expected number of stubs per ladder per event.]{Simulated expected number of stubs per ladder per event as a function of ladder ID.}
    \label{otstubs}
\end{figure}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Muon drift tube}
The muon DT luminometer follows the same design described in section 2.2. The entire DT system is formed by 250 gas chambers, installed in the barrel yoke of the CMS detector, as shown in Figure \ref{Muons}. The chambers are distributed across 5 wheels labeled YB0, YB$\pm1$ and YB$\pm2$, four radial stations, MB1-MB4, and 12 $\phi$ sectors \cite{ABBIENDI2009192}.

The objects used by this luminometer are called trigger primitives, which are reconstructed muon track segments per DT chamber. The tracks are reconstructed at a trigger frequency of  40 $MHz$,  using hits from the DT and RPC detectors. The rate of trigger primitives has being studied and extrapolated to the expected  instantaneous luminosity of the HL-LHC, $7.5\times 10^{34}$ $cm^{-2}s^{-1}$, using  the data from Run 2. Figure \ref{dtrate} shows the expected rates for the YB0 and YB+2 wheels. The large difference on the measured rate, between the MB1 and the rest of the chambers in the MB2 and MB3 stations, is due to a significant contribution of particle from punch-through jets.
\begin{figure}[H]
\centering
\includegraphics[width=.48\textwidth]{Chapter3/DT_Trigger_extraploation_YB.pdf}
\includegraphics[width=.48\textwidth]{Chapter3/DT_Trigger_extraploation_YBp2.pdf}
\caption[Expected rates of trigger primitives per DT chamber]{Expected rates of trigger primitives per DT chamber for the YB0 (left) and YB+2 (right) wheels.}
\label{dtrate}
\end{figure}
The DT luminometer will create one histogram per DT chamber, giving a total of 250 histograms. Tables \ref{bitsperbinall} and \ref{dataratesall} show the expected Bits per Bin and the  Data Transfer Rates for the DT luminometer, using extrapolated data from the 2018 data taking period.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{BMTF }
The Barrel Muon Track Finder (BMTF) is an algorithm that uses reconstructed muon tracks to provide luminosity measurements. As its name suggests, The algorithm uses information from all the DT and RPC gas chambers, located in the barrel of the muon system, to reconstruct muon tracks.
One histograms is created by the algorithm. Tables \ref{bitsperbinall} and \ref{dataratesall} show the expected Bits per Bin and the  Data Transfer Rates for the BMTF algorithm \cite{Bachtis:2648953}. As well as the DT luminometer, BTMS uses  extrapolated data from the 2018 data taking period.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Data transfer rates for all luminometers}
Using the number of histograms, as well as the mean number of counts per event for each luminometer \cite{datarates}, the number of Bits per Bin as well as the Data Transfer Rates can be calculated for all luminometers. This is shown is Tables \ref{bitsperbinall} and \ref{dataratesall} respectively.
\begin{table}[H]
\centering
\caption[Memory bits required per histogram bin for all luminometers.]{Triger rate (kHz), counts per event per detector unit (histogram), number of counts per bx per integration period (1s) and the memory bits required per histogram bin.}
\scalebox{.7}{
\begin{tabular}{|l |c |c |c |c|}
\hline
&  Trigger rate (kHz) & Counts per event & Counts/bx/1s&Bits/bin\\
\hline
TEPXD4R1 Clusters&825&539&1.25e+05&17\\
\hline
TEPXD4R1 2x Coincidences&825&54&1.25e+04&14\\
\hline
TEPX Clusters&75&539&1.13e+04&14\\
\hline
TEPX 2x Coincidences&75&54&1.14e+03&11\\
\hline
OT Layer 6 track stubs&40000&8&8.98e+04&17\\
\hline
DT Trigger Primitives&40000&0.0125&140&8\\
\hline
BMTF Tracks&40000&0.041&460&9\\
\hline
\end{tabular}}
\label{bitsperbinall}
\end{table}
\begin{table}[H]
\centering
\caption[Data transfer rates for the different luminometers.]{Data transfer rates for the different luminometers for pileup 200. Columns shown are number of histograms, memory per histogram and data transfer rates (Mbps) for an integration period of 1s. }
\scalebox{.8}{
\begin{tabular}{|l  |c |c |c|}
\hline
&  Number of Histograms & Memory per histogram (Kb) & Data Transfer Rates (Mbps)\\
\hline
TEPXD4R1 Clusters&8&124&0.95\\
\hline
TEPXD4R1 2x Coincidences&8&67&0.5\\
\hline
TEPX Clusters&152&82&12.5\\
\hline
TEPX 2x Coincidences&152&82&12.5\\
\hline
OT Layer 6 track stubs&152&120&18.3\\
\hline
DT Trigger Primitives&250&28&7.13\\
\hline
BMTF Track&1&57&0.057\\
\hline
\end{tabular}}
\label{dataratesall}
\end{table}

From these tables it can be concluded that the minimum bandwidth required will be 18.3 Mbps, corresponding to the OT luminometer. The total storage needed per day for all luminometers presented here can be calculated, assuming an operation time of 12 hours, the total storage needed will be 280.46 GB. Since other luminometers will be in operation, besides the ones discussed here, 280.46 GB is the minimum storage per day required to ensure no data is lost.

### 2022-04-20 tesis_Hedwin/Chapter5/chapter5.tex
Hedwin thesis

\chapter{Conclusion and Summary }
With the new luminosity goal of the HL-LHC, the CMS detector will receive several upgrades, in order to keep up with the new luminosity demands. These upgrades will come to several systems, which includes various subdetectors and luminometers. One of these subdetectors TEPX,
will perform luminosity measurements with high statistics. 
One of its rings, TEPXD4R1, will perform luminosity measurements only. The TEPX will be operated by BRIL, utilizing the pixel cluster counting (PCC) method, as the main source of luminosity measurements.

The PCC algorithm will take advantage of the low occupancy and the 800 million pixels distributed across the 2 $m^2$ of the TEPX luminometer, to provide precise luminosity measurements. The TEPX luminometers will provide event rate measurements utilizing two types of objects: pixel clusters and two-fold coincidences.

In this work, the statistical precision of the TEPX luminometers, and other luminometers, is studied using simulated data. For physics runs (pileup of 200), the TEPX luminometers achieved a statistical precision per bunch per 1 s, below $0.1\%$ for pixel clusters and below $0.4\%$ for two-fold coincidences. In vdM conditions (pileup of 0.5), the precision is below $0.4\%$ per bunch per 30 s, for pixel clusters and below $0.8\%$ for coincidences. This translates to a precision under $0.1\%$ per bunch for the calibration constant ($\sigma_{vis}$) for pixel clusters, and below $0.3\%$ for coincidences. Both luminometers also achieve linearity deviations well below $1\%$ up to a pileup of 200. 
These results show an excellent expected performance for TEPX luminometers, and in combination with the rest of the luminometers (OT layer 6, DT and BMTF), will provide precise luminosity measurements for the HL-LHC phase.

The network bandwith and disk storage needed for the BRIL Phase 2 luminosity systems has been also estimated. Concluding that a bandwith of at least 18.3 Mbps is required, and a disk storage of 280.46 GB per day is needed.

### 2022-04-20 tesis_Hedwin/Dedication/dedication.tex
Hedwin thesis

\begin{dedication}
\begin{center}
    \section*{Acknowledgements}
\end{center}
\justify{ 
Thanks to my family for their unconditional support and patience and for always being there when I needed them the most, without them I would not be here.\\
To my friends Carolina, Alejandro and Luisa, for all the help and for making my studies more fun.\\
To my advisor Dr. José Feliciano Benítez,  for always being there to answer my doubts, his patience, and for the opportunity of letting me work in the CMS collaboration. \\
Finally, thanks to CONACYT for supporting my studies with financial aid.}

\end{dedication}

### 2022-04-29 tesis_Rodolfo/Abstract/abstract.tex
Draft_0

--- 2022-04-20 tesis_Hedwin/Abstract/abstract.tex
@@
 \end{center}
-    The design and expected performance of the Tracker End-cap Pixel (TEPX) and other subdetectors as luminometers for the CMS experiment at the upcoming High-Luminosity LHC (HL-LHC) is described.
-The TEPX detector is composed of 4 double sided disks covering a range on $|z|$ from 175 to 265 cm, each one made of 5 rings composed of silicon sensors with a high number of pixels.
-Disk 4 Ring 1 (TEPXD4R1) will be designated for luminosity measurements only, utilising the same method as the TEPX luminometer, the pixel cluster counting (PCC) method.
-For the HL-LHC, the goal is to achieve a final uncertainty of $1\%$ for the luminosity measurements.
-The expected performance and linearity of the TEPX, TEPXD4R1 and other luminometers in terms of statistical precision, for van der Meer (vdM) scan calibration  and for physics conditions, are presented.
-The bandwidth needed for the transfer of the luminosity data and disk needed for storage are estimated.
+    van der Meer calibration is decribed
 \end{abstract}

### 2022-04-29 tesis_Rodolfo/Abstract/resumen.tex
Draft_0

--- 2022-04-20 tesis_Hedwin/Abstract/resumen.tex
@@
 \end{center}
-Se describe el diseño y el rendimiento esperado del Tracker End-cap Pixel (TEPX) y otros sub detectores como luminómetros para el experimento CMS, en el próximo LHC de alta luminosidad (HL-LHC).
-El detector TEPX está compuesto por 4 discos de doble cara que cubren un rango en $ | z | $ de 175 a 265 cm, cada uno compuesto por 5 anillos hechos de sensores de silicio con un alto número de píxeles.
-El Disco 4 Anillo 1 (TEPXD4R1) se designará solo para mediciones de luminosidad, utilizando el mismo método que el luminómetro TEPX, el método de conteo de conjuntos de píxeles (PCC).
-Para la etapa del HL-LHC, el objetivo es lograr una incertidumbre final de $ 1 \% $ para las mediciones de luminosidad.
-Se presentan el rendimiento esperado y la linealidad de TEPX, TEPXD4R1 y otros luminómetros en términos de precisión estadística, para la calibración de escaneo de van der Meer (vdM) y para condiciones físicas.
-El ancho de banda necesario para la transferencia de los datos de luminosidad y el disco necesario para su almacenamiento es estimado.
-
+Calibracion de van der Meer
 \end{abstract}

### 2022-04-29 tesis_Rodolfo/Chapter1/chapter1.tex
Draft_0

\chapter{Introduction}
The Standard Model (SM) in particle physics is the theory that describes the interactions between three fundamental forces, out of the four known  (gravitational, electromagnetic, strong and weak), and the known fundamental particles. The gravitational force is not included in the SM, since the magnitude of its strength is neglectable in comparison with the other three forces.

The  theory was developed throughout the second half of the  20th century by the hard work of physicists around the world, with the current formulation being established in the mid 70s.\\
In high energy physics, precise measurements are the core of any experiment. A key quantity is the luminosity, and its precise determination is an important aspect. The search for low incidence processes whose observation is not yet confirmed, such as the $H\rightarrow\gamma + Z$ channel, relies in the accumulation and precise measurements of luminosity.
\section{The Standard Model}

 The SM classifies all known fundamental particles into two major groups, fermions, particles with spin $1/2$, and bosons, particles responsible for mediating the fundamental forces and integer spin.
Fermions are divided into two families of particles, leptons and quarks. There exist 6 leptons in the SM, first there are charged particles,  electrons ($e$), muons ($\mu$) and the taus ($\tau$) with an electric charge of $-1$ and spin of $1/2$. To each of these particles corresponds a chargeless neutrino, $\nu_{e}$,$\nu_{\mu}$ and $\nu_{\tau}$.

Leptons can be found in nature existing by themselves, and along with quarks, comprise the majority of matter in the universe. Electrons can be found “circling”  atoms, muons can be found raining from the sky due to cosmic rays interacting with particles on the atmosphere and, while taus are a little bit tricky to find due to their short life time ($2.9\times10^{-13}$ s), they do exist by themselves; however, this cannot be said for quarks, since they are only found forming other particles called  hadrons. Hadrons can be a combination of two quarks called mesons, usually a quark-antiquark combination or a combination of three quarks called baryons, an example of a meson would be a pion ($\pi$). Neutrons and protons are made by a combination of three quarks, so they are classified as baryons.
Quarks were first theorised by Murray Gell-Mann and George Zweig in 1964 and later discovered by experiments conducted at the Stanford Linear Accelerator Center (SLAC) in 1968 \cite{griff}. A total of 6 quarks were discovered over a period of 26 years, in order of discovery these are: up ($u$) (1968), down ($d$) (1968), strange ($s$) (1968), charm ($c$) (1974), bottom ($b$) (1977), top ($t$) (1995).

Quarks are the only fermions that interact with all three fundamental forces included in the SM, they possess electric charge, color charge (the strong force equivalent of electric charge), weak charge, mass and spin $ 1/2$ as do all fermions. The $u$, $c$ and $t$ quarks have an electric charge of $2 /3$ and the $d$, $s$ and $b$ quark have an electric charge of $-1/3$. Table \ref{SM table} shows which fermions interact with the different forces. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[H]
\centering
\caption[Fundamental forces and the fermions]{Fundamental forces and the fermions they interact with \cite{Thomson:2013zua}.}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|c|c c c|c|c|c|}
\hline 
\multicolumn{2}{|c}{}&  & & Electromagnetic & Strong & Weak\\
\hline
\multirow{2}{*}{Quarks}&u&c&t &\multirow{2}{*}{\checkmark}&\multirow{2}{*}{\checkmark}&\multirow{2}{*}{\checkmark}\\
& d&s&b&&&\\
\hline
\multirow{2}{*}{Fermions}& $e$&$\mu$&$\tau$ &\checkmark& &\checkmark\\
&$\nu_{e}$&$\nu_{\mu}$&$\nu_{\tau}$&&&\checkmark\\
\hline
\end{tabular} 
\label{SM table}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 For each fermion that exists, there corresponds an antiparticle. Antiparticles have the same properties as their counterparts, with the only distinction being that they possess opposite electric charge. If an antiparticle comes in contact with a particle, let's say a positron (anti-electron) and an electron, they would annihilate each other.

The SM also comprises particles with integer spin  such as the bosons. Bosons are force carrier particles in charge of mediating the interactions between particles, let's take  classical electromagnetism as an example. Classically, the electrostatic force is described by a scalar field and while this is sufficient for classical electromagnetism, it is fundamentally wrong for quantum dynamics. This would mean that two charged particles interact with each other at a distance, without contact of any kind \cite{Thomson:2013zua}.

In  particle physics, each fundamental force is described by a quantum field theory (QFT) and the interaction between two particles are mediated by gauge boson, a spin-1 particle.  For example,  the electromagnetic force is described by Quantum Electrodynamics (QED)  and mediated by the photon, a  particle with no charge or mass. The strong force is described by Quantum Chromodynamics (QCD) and mediated by a gluon, which has no mass or electric charge, gluons are what bind quarks together to form hadron and like quarks, are only found in these bind states. Finally the weak force is mediated by the $Z$ and $W^{\pm}$ bosons, massive particles with 0 an $\pm 1$ electric charge respectively
\cite{Thomson:2013zua}.\\
The Higgs boson is the last member of the SM, unlike the gauge bosons, the Higgs has spin-0 and is the only fundamental scalar discovered. Figure \ref{sm1} shows all the particles included in the SM.

\begin{center}
  \begin{figure}[ht]
    \centering
    \includegraphics[scale=0.3]{Chapter1/sm1.png}
    \caption[ Standard model of particles]{Particles that compose the standard model and their properties \cite{smtable}.}
    \label{sm1}
  \end{figure}
\end{center}

\section{The Higgs Boson }
The Higgs boson is the latest member of the SM, first theorised in 1964 by Peter Higgs, Robert Brout, François Englert, Gerald Guralnik, C. Richard Hagen and Tom Kibble and later discovered by the ATLAS and CMS experiments at the Large Hadron Collider (LHC) in Geneva Switzerland in 2012. The experiment consisted in proton-proton collisions with a center of mass energy of 7 and 8 TeV, the data analysed from the experiment corresponds to five decay channels: $\gamma\gamma$, $ZZ$, $W^{\pm}W^{\pm}$, $\tau^+\tau^-$ and $b\bar{b}$. With the discovery being made in the  $\gamma\gamma$ and $ZZ$ channels
\cite{higgsd}\cite{Aad_2012}.
The Higgs plays a vital role in the SM, it is responsible for the mechanism that gives every particle their mass. It has a mass of $125.78\pm 0.26$ GeV \cite{CMS:2019drq}, consistent with SM predictions, it does not possess electric or color charge and it is the only fundamental scalar and spin-0 boson.\\
 The discovery of the Higgs is one of the greatest accomplishments of the SM, it shows the hard work that has gone in to developing the theories that compose it \cite{Thomson:2013zua}.

\section{Particle colliders and
detectors}
The discovery of the Higgs marked an important milestone in particle physics, however, this feat required the construction of the LHC, the largest and most powerful particle collider in the world. Particle colliders are the devices where particle physics experiments are conducted. As their name suggests, colliders propel bunches of particles like electrons, protons, positrons, etc. using powerful electromagnetic/electrostatic fields, and make them collide with a fixed target or other particles. These collisions produce other particles that are measured by particle detectors in the site of the collision, this is the means by which new particles are discovered.

Particle colliders come in two types: linear  and circular. Linear colliders  use changing electromagnetic fields to accelerate particles along a straight beam path and make them collide with a fixed target, where particle detectors are located, an example of the linear accelerator would be the Stanford Linear Accelerator Center. While circular colliders to accelerate bunches of particles  in opposite directions in a circular beam fashion, making them collide at key points around the accelerator where particle detectors are located.  The LHC is an example of a circular collider.

The majority of modern experiments in particle physics are conducted in circular colliders, since these are the only ones that can provide the center of mass energy needed to produce heavier particles, like the Higgs or the Top quark. Due to the high energy requirements, circular accelerators are very complex machines composed of many parts, but for the sake of this work, we will only focus on the particle detectors. Modern particle detectors are composed of many layers of subdetectors tasked with measuring the effects that particles have on them, when they pass through. For example, a subdetector may measure the number of hits, tracks or pixel clusters activated during a collision.

The layout of the detector will change to best accommodate the experiments being performed, but in general, these subdetectors can be classified into three categories: Tracking devices, to track the path of a particle; calorimeters, they measure the energy deposited by a particle when it hits and particle identifiers, that use various techniques and the measurements from other subdetectors, to identify the different particles produced in a collision \cite{detector}. The CMS detector and the LHC is an example of a layered particle detector.

Finally, two parameters are used to measure the efficiency of a particle collider, the beam energy and the luminosity.  The higher the beam energy, the more particles can be created and thus the higher chance that new effects can be observed. The luminosity ($\mathcal{L}$) is a measure of the efficiency of a particle collider to produce meaningful interaction between colliding bunches of particles.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Luminosity }

As mentioned before, the LHC collides particles by grouping them into bunches, where trains of $N_b$ bunches are made. The groups of bunches are circulated both clockwise and anticlockwise and are forced to cross at specific detection points, where several interactions occur. A collision between bunches is called an event, and several particle interactions are produced during these events, the quantity that measures the ability of any particle collider to produce these useful interactions is called Luminosity. Thus, the event rate $R$, of a particular type $p$, with cross-section  $\sigma_p$, is given by \cite{White}:
\begin{equation}
    R=\mathcal{L}_{ins}\sigma_p
    \label{lumy0}
\end{equation}

Where the instantaneous luminosity, $\mathcal{L}_{ins}$, is the proportionality constant, the cross section is the likelihood of that event taking place and has units of $cm^{2}$, thus the luminosity has units of $cm^{-2}s^{-1}$ \cite{White}. Since the probability of a rare event increases the more the rate of interactions grows, the luminosity is a key figure in the performance of a particle collider.\\
Let's consider $N_b$ colliding bunches, assuming all the bunches have a head-on collision, the luminosity of all the colliding bunches is given by \cite{CERN-THESIS-2018-051}: 
\begin{equation}
    \mathcal{L}_{ins}=  N_b N_1 N_2f\int^{\infty}_{-\infty}dx\int^{\infty}_{-\infty}dy \rho_1(x,y)\rho_2(x,y)
    \label{lumy1}
\end{equation}
where $N_{1,2}$ are the particles per bunch, $f$ is the revolution frequency and $\rho_{1,2}$ are the normalized densities in the transverse plane. Assuming that the normalized densities are uncorrelated in all planes, the distribution functions can be factorized as:
\begin{equation}
    \rho_i(x,y)=\rho(x)\rho(y) \text { where i=1,2}
    \label{dens1}
\end{equation}
Thus, equation \ref{lumy1} can be writhe as

\begin{equation}
    \mathcal{L}_{ins}=  N_b N_1 N_2f\int^{\infty}_{-\infty}\rho_1(x)\rho_2(x)dx\int^{\infty}_{-\infty}dy \rho_1(y)\rho_2(y)
    \label{lumy2}
\end{equation}
For the case of head-on colliding bunches, a Gaussian charge distribution can be used, equation \ref{dens1} can be written
\begin{equation}
    \rho(u)=\frac{1}{\sqrt{2\pi}\sigma_u} exp\left(-\frac{u^2}{2\sigma_u^2}\right) \text { where u=x,y.}
    \label{dens2}
\end{equation}
using this, equation \ref{lumy2} can be integrated analytically, giving 
\begin{equation}
    \mathcal{L}_{ins}=\frac{N_1N_2N_b f}{2\pi
    \sqrt{\sigma^2_{x1}+\sigma^2_{x2}}\sqrt{\sigma^2_{y1}+\sigma^2_{y2}}}
    \label{lumy3}
\end{equation}
In practice, the bunch densities in the transverse plane are not known and a calibration of the detectors has to be done, in order to obtain these values. At the LHC, this is done by a dedicated machine setup.  
The performances of a particle collider over a period of time is given by the integrated luminosity :
\begin{equation}
L=\int \mathcal{L}_{ins}(t)dt
\label{lum0}
\end{equation}

The average number of interaction per bunch crossing is given by the pileup, $\mu$, and directly proportional to the luminosity
\begin{equation}
    \mu=\frac{\mathcal{L}_{ins}\sigma_{tot}}{f}
    \label{pileup}
\end{equation}
where the $\sigma_{tot}$ is the total cross-section of the collided particles \cite{CERN-THESIS-2018-051}.\\
It is worth noting that a head-on collision is not always the case. The bunches can collide in different ways, such as an off-set a crossing angle or both. In these cases, the overlapping integral in equation \ref{lumy1} is reduced. This is done by applying a reduction factor to equation \ref{lumy2} \cite{CERN-THESIS-2018-051}, however, this work is only concerned with the head-on collision case, the other scenarios can be found in \cite{White}.

### 2022-04-29 tesis_Rodolfo/Chapter2/chapter2.tex
Draft_0

\chapter{Experiment Description }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Large Hadron Collider}

The LHC is one of the most powerful particle collider in the world, it started construction in 1998 on the France–Switzerland border near Geneva, using the 26.7 km tunnel, constructed for the CERN LEP machine. It came into operation on the 10 of September of 2008, and it is the latest addition to the CERN accelerator complex. It was first approved on December 1994 by the CERN council, with  a center-of-mass-energy of 14 Tev \cite{Bruning:782076}.

The LHC consists of two separate rings, kept in an ultrahigh vacuum, where two the beams of particles are located. To achieve the circular motion of the beams, 1232 dipole magnets are used to maintain trajectory, and 392 quadrupole magnets are used to keep the beams focused. Near the interaction points, stronger quadruple magnets are used to increase the probability of interaction between the beams.  These magnets are made of coils of special superconductive cable, cooled to a temperature of 1.8 K with superfluid helium, producing an electromagnetic field of above 8 T \cite{Bruning:782076}.

 The beams in each ring are made of bunches for particles traveling near the speed of light. These bunches can be made of protons or ions (like lead nucleons), depending on the running experiment, however, the majority of events at the LHC are produced by proton-proton (pp) bunch collision.\\
A diagram of CERN’s accelerator complex can be seen in Figure \ref{cernc}. The proton bunches start as ionised hydrogen gas and are accelerated to an energy of 50 MeV, by the Linac 2 linear accelerator. Once they leave the Linac 2, they are further accelerated to an energy of 1.4 GeV by the Proton Synchrotron Booster (PSB) and dumped on the  Proton Synchrotron (PS). In the PS, the bunches are accelerated to an energy of 25 GeV and arranged into a bunch trains, with a spacing of 25 ns, in total, one orbit contains 3564 bunches, arranged in to several trains. Finally, the bunches pass from the PS to the Super Proton Synchrotron (SPS), where they are injected into the LHC with an energy of 450 GeV. In the LHC, the beams reach a peak energy of 6.5 TeV, and are made to collide in one of the 4 detectors, ALICE, ATLAS, CMS and the LHCb. 
\begin{center}
  \begin{figure}[ht]
    \centering
    \includegraphics[scale=.7]{Chapter2/CERNC.jpg}
    \caption[CERN accelerator complex.]{A diagram of the CERN accelerator complex \cite{cernpg}.}
    \label{cernc}
  \end{figure}
\end{center}
The four detectors are tasked with measuring all the particles produced in pp collisions. Two specialized detectors are integrated to the LHC, ALICE and LHCb. ALICE is dedicated to heavy ion collisions physics, where the quark-gluon plasma is studied. The LHCb investigated the differences between matter and antimatter, by studying the “beauty quark” \cite{lhcb}.\\
The two remaining detectors, CMS and ATLAS, are general purpose detectors, tasked with studying a wide range of physics, from the search of the Higgs boson, to extra dimensions and particles that could make the dark matter in the universe \cite{cmsweb}.

Two operation runs have been completed so far at the LHC, and two long shutdowns, where maintenance and several minor upgrades were made to the machine.  Run 1 lasted from 2010-2012, while Run 2 lasted from  2015-2018. As of Run 2, the LHC has achieved a peak luminosity of $2\times 10^{-34} cm^{-2}s^-1$, two times the amount for which the LHC was designed. The integrated luminosity, since the LHC began operations, has reached $160 fb^{-1}$ for the ATLAS and CMS experiments \cite{lumi2180}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The CMS detector }
The Compact Muon Solenoid (CMS) experiment is one of the four major experiments currently running in the LHC, and along with ATLAS, one of the two high luminosity experiments at CERN. It receives its name from the huge solenoid magnet, from which the detector is built around. This solenoid takes the form of a coil made of super conductive wire, capable of producing an electromagnetic field of 4 T. The field is confined by a steal yoke, that weights 14,000 tones.

CMS is a layered detector, 21 m in length, with a height and width of 15 m, and it is composed of four main subdetectors, the inner silicon tracker, electromagnetic and hadron calorimeters and the muon detectors. The strong magnetic field produced by the detector’s solenoid, separates the particles produced in the coalitions and provides a better momentum resolution. Figure \ref{cms} shows a diagram of the detectors layout. 
\begin{center}
  \begin{figure}[ht]
    \centering
    \includegraphics[scale=.2]{Chapter2/CMSl.png}
    \caption[CMS detector diagram]{Diagram of the CMS detector showing the various subdetectors that comprise it \cite{cms-manual}.}
    \label{cms}
  \end{figure}
\end{center}
The CMS experiment has a broad range of goals in particle physics, from studying the SM in search of new particles and phenomena, to searching for extra dimensions and discovering new particles that could make the dark matter in the universe.  The experiment has achieved great things in the scientific community, however, one of its greatest, was the discovery of the Higgs boson  alongside the ATLAS experiment in 2012. In the next subsection a brief description of the different subdetectors is provided \cite{cms-manual}.
\subsection{ Silicon tracker}
At the heart of the CMS detector lies the inner silicon tracker. As its name suggests, the purpose of this subdetector is to reconstruct the track of charged particles generated during collisions, by using silicon strips and pixels to register the paths of charged particles. Once the track of a charged particle is reconstructed, its momentum can be extracted, by calculating the curb of its trajectory, produced by the electromagnetic field. Also, the vertex, the origin of the track, can be determined. The Tracker, which consists of an Inner Tracker (pixels) and an Outer Tracker (strips), is the first subdetector encountered by the particles, and thus the smallest, with an outer radius of 110 cm and a total length of 5.4 m, Figure \ref{tracker} shows the layout of the inner tracker.
\begin{center}
\begin{figure}[ht]
    \centering
    \includegraphics[width=1\textwidth]{Chapter2/pixel-detector.png}
    \caption[CMS tracker.]{Diagram showing the layout of the CMS Phase-1 inner tracker. The barrel pixel detector (BPIX) and the forward disks pixel detector (FPIX) are shown \cite{CMSTrackerGroup:2020edz}.}
    \label{tracker}
\end{figure}
\end{center}
The tracker is divided into two subtrackers: one is the silicon strip tracker, made of 9.6 million silicon strips. This subtracker is divided in two parts: the Tracker Inner Barrel (TIB) and the Tracker Outer Barrel (TOB). The TIB is made of 4 layers that cover up to $|z|<65$ cm. The TOB has 6 layers, and a coverage of $|z|<110$ cm. The encaps are again divided into two regions,  Tracker End Cap (TEC) and Tracker Inner Disk (TID). The TEC is composed of 9 disks that extend in the region 120 cm $<|z|<$ 280 cm, while the TID has 3 disks that fill the gaps in between the TIB and the TEC. The TEC and the TID are made of rings centered on the beam, and possess stripst that point towards the beam.\\
The strip tracker encompass and area of 200 $m^2$, and it is made of almost 15,400 modules, running at a  temperature of $-20^{\circ} C$.

The other subtracker is the pixel tracker, made of three layers of barrels possessing a radius of 4.4 cm, 7.3 cm and 10.2 cm with a length of  53 cm, and consisting of 66 million pixels.  In each end of the barrels, two  end cap disks reside, extending from 6 to 15 cm in radius and located at $|z|=34.5$ cm and 44.5 cm, in total, the pixel tracker has an area of roughly 1$m^2$\\
768 pixel modules are housed in the barrel, all arranged into half lathers of 4 identical modules. The end cap disks are designed in a turbine-like geometry, with blades rotated $20^{\circ}$. The blades are made of 7 different pixel modules, with a total of 768 modules being housed in the end cap disks \cite{cms-manual}.
\subsection{CMS calorimetry system}
The calorimetry system of the CMS detector is composed of two types of calorimeters: the electromagnetic and hadronic calorimeters. Both subdetectors form a complete and hermetic calorimetry system with a coverage of $-5<\eta<5$. The calorimeters are a crucial part of the CMS detector, since the identification and reconstruction of photons and electrons is done using measurements from the calorimetry system, as well as the measurements of jets and missing transverse momentum. A brief description of the electromagnetic and hadronic calorimeter is provided below.

\subsubsection*{Electromagnetic calorimeter}
The electromagnetic calorimeter (ECAL) measures the energy of electrons and photons. Once charged particles enter the ECAL, they produce a shower for secondary electrons and photons. These electrons pass through the lead tungstate ($PbWO_4$) crystals, which scintillates when electrons hit their crystalline structure, producing light that is measured by photodiodes in the calorimeter.\\
It is made of 75848 tungstate crystals \cite{Contardo:2020886}. It is an hermetic, homogeneous calorimeter composed of a central barrel and two end-caps. Silicon avalanche photodiodes (APDs) are used in the barrel and vacuum phototriodes (VPTs) in the end caps.

The central barrel has an inner radius of 129 cm and a structure of 36 “supermodules”, that cover half the barrel's length. It has a coverage of $|\eta|<1.479$. The APDs used on the barrel have an active area of $5\times5$ $mm^2$, and two of them are glued to the back of each crystal.\\
The two end caps have a pseudorapidity range of $1.479<|\eta|<3$, and are located at a distance of 314 cm from the vertex. It consists of crystals with an identical shape,  grouped in mechanical units of $5\times 5$ \cite{cms-manual}.
\subsubsection*{Hadron calorimeter}
The Hadron calorimeter (HCAL), along with the ECAL, form a complete and hermetic calorimetry system  with the purpose of measuring  jets and missing transverse energy. The HCAL surrounds the ECAL and its design is heavily influenced by the magnet parameters, since it is located inside the solenoid magnet. The HCAL is divided into 4 parts: the hadron barrel (HB), hadron outer (HO), hadron endcap (HE) and hadron forward. The absorber material is brass since it has a short interaction length, is non-magnetic and is easy to machine. Tile/fiber technology, embedded between the absorber plates, is used to detect the particle showers. The technology consists of plastic scintillator tiles embedded with  wavelength- shifting (WLS) fibers. The fibers are connected to high-attenuation-length clear fibers that carry the light to the readout system.\\
The photodetection readout is handled by multi-channel hybrid photodiodes (HPDs).

The HB has an inner radius of 1777 mm and an outer radius of 2876.5 mm and has 17 scintillator layers and is composed of 2 half barrels covering a range of  $-1.4<\eta<1.4$, resulting in a total of 2304 towers.
The HO covers a region of $-1.26<\eta<1.26$ and it contains scintillators with a thickness of 10 mm, lining the outside of the outer vacuum tank of the solenoid. The HE consists of 14 towers with a range of $1.3<\eta<3.0$. It is made entirely of brass plates, with a thickness of 78 mm.

The HF calorimeter has a range of $3<\eta<5$ and is made of steel and quartz fibers. It is located 11.2 m from the interaction point, providing fast collection of Cherenkov light. The modules of the HF are constructed of 18 wedges arranged in a non-projective geometry, Figure \ref{wedge} shows and $r-\phi$ view of an HF wedge. The quartz fibers have a diameter of 0.6 mm and are placed 5 mm apart, forming a square grid. Two different lengths are used for the quartz fibers, 1.43 m and 1.65, effectively creating 2 longitudinal samplings. In total, 13 towers exist in $\eta$ with a size of $\Delta\eta\approx 0.175$, except for the lowest and highest-$\eta$ towers, which have a size of $\Delta\eta\approx 0.1$ and $\Delta\eta\approx 0.3$ respectively. A $\Delta\phi\approx 10^{\circ}$ exists for all towers but the highest-$\eta$ tower, which has a segmentation of $\Delta\phi\approx 20^{\circ}$. In total the HF calorimeter consist of 900 towers and 1800 channels \cite{cms-manual}.
\begin{center}

\begin{figure}
    \centering
    \includegraphics[scale=0.5]{Chapter2/hfes.PNG}
    \caption[Hadron forward wadge.]{And r-$\phi$ view of a HF wadge.}
    \label{wedge}
\end{figure}
\end{center}
\subsection{Muon Detector}
The last subdetector of the CMS experiment is the muon detector system located in the magnet return yokes. The muon system consists of 3 types of gaseous detectors, used to detect muons and their momenta. These detectors are:  the drift tube chambers (DT), the cathode strips chambers (CSC) and the resistive plate chamber (RPC). These detector are distributed across the 2 central parts of the muon detector, the barrel and endcap sessions, with a coverage of $|\eta|<1.2$ and $|\eta|<2.4$ respectively. The distribution of these detectors is shown in Figure \ref{Muons}.
\begin{figure}[H]
    \centering
    \includegraphics[scale=.45]{Chapter3/dt.png}
    \caption[One quarter of the CMS muon system. ]{The diagram shows the layout of one quarter of the muon system at CMS \cite{cms-manual}.}
    \label{Muons}
\end{figure}

The barrel DT detector  has a coverage of $|\eta|<1.2$, and consist of 250 chambers arranged in 4 layers inside the magnet return yoke, at a radii of approximately 4, 4.9, 5.9 and 7 meters from the beam line. The basic element of the DT detectors are cells, with a transverse size of $42\times 13$ $mm^2$, filled with a gas mixture of $85\%$ Ar and $15\%$ $CO_2$ \cite{cms7}. The cells have a gold-plated stainless steel anode wire, connected at their center. The wire has a diameter of 50 $\mu m$ and it operates at a voltage of +3600 V. \\
The barrel detectors are divided into 12 sectors, each covering $30^{\circ}$ in the azimuthal direction.

Installed on the encap regions, the CSC chambers are installed, covering a range of $0.9<\eta<2.4$. Their fast response time and their tolerance to non-uniform magnetic fields, makes the perfect for the high muon rates and background levels found in this region. The 6 layers of the CSC measure the muon positions in 2 coordinates. The cathode strips provide precise measurements on the r-$\phi$ bending plane, while the wires provide a coarse measurement in the radial direction. Each layer of the CSC contains 80 cathode strips with anode wires, of diameter 50 $\mu m$, running almost parallel to the cathodes.\\
In total, the 2 encaps are comprised of 468 CSC chambers, filled with a gas mixture of $50\%$ $CO_2$, $40\%$ Ar and $10\%$ $CF_4$ \cite{cms7}.

The RPC detectors is located in the barrel and encap regions of the muons system, complementing the DT and CSC detectors. It covers a region of $|\eta|<1.6$ and it provides fast, independent trigger events. The RPC are double-gap chambers, each gap consisting of 2 mm thick resistive bakelite plates, separated by a 2 mm thick gas gap.  Readout strips are aligned in the $\eta$ direction in between the gas gaps. The gaps are filled with a gas mixture of $95.2\%$ Freon $(C_2H_2F_4)$, $4.5\%$ isobutane $(i-C_4H_{10})$, and $0.3\%$ sulphur hexafluoride $(SF_6)$. Water vapor is added to reach a mixture humidity of $40\%$-$50\%$ \cite{cms7}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{High Luminosity LHC}
The LHC is the most powerful particle collider in the world, and it is to remain the most powerful for the next two decades. To ensure this, the LHC will receive major upgrades during the 2020s, to increase its luminosity by a factor of 5 beyond the original design. About 10 years will be needed to study and prototype the technologies required for the new High Luminosity LHC (HL-LHC). The HL-LHC project was created at the end of  2010 by CERN, as a response to the  European strategy for particle physics, to fully exploit the capabilities of the LHC. The project was approved on 30 of May of 2013 by the CERN council in charge at the time. For the next decade the HL-LHC is the major construction project of CERN. Several new technologies will be used to achieve the luminosity goal, some of them include: superconducting magnets capable of producing a magnetic field of 11 to 12 T, superconducting  cavities, compact and with phase control, for beam rotation, long high-power superconducting links with zero energy dissipation and new technologies for beam collimation \cite{cern3}.
\begin{center}
\begin{figure}[H]
    \centering
    \includegraphics[scale=1.5]{Chapter2/schedulelhc.jpg}
    \caption[schedule of the LHC.]{The past and future schedule of the LHC. The red line corresponds to the center-of-mass-energy of the pp collisions, while the light-red line shows the expected luminosity \cite{schedule}.}
    \label{programing}
\end{figure}
\end{center}
Figure \ref{programing} shows the  schedule of the LHC up until 2025, where the new phase of the LHC, the HL-LHC, will  begin. After reaching a center-of-mass-energy of 13 during 2015, the LHC has doubled the luminosity for which it was designed, as  of the end of Run 2.

The main objectives of the HL-LHC is to reach a peak luminosity of 5 to $7.5\times10^{34}$ $cm^{-2}s^{-1}$, and an integrated luminosity of 250 $fb^{-1}$ per year, with the goal of reaching a total integrated luminosity of 3000 $fb^{-1}$, in the first 12 years of the machines operation. For this, intensive studies have, and are, being conducted to determine the hardware and the configuration needed to achieve these goals.\\
The new hardware of the HL-LHC is to be installed during the third long shutdown (LS3). To ensure that the integrated luminosity goal is met, all equipment is being designed with a $50\%$ margin in regards to the required luminosity. This means that the High Luminosity LHC can reach peak luminosity valued of 7 to $7.5\times10^{34}$ $cm^{-2}s^{-1}$, this will mean an increase in total pileup (rate of pp collision per bunch crossing) up to 200 \cite{cern3}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Tracker End-Cap Pixel luminometer}

Along with the new HL-LHC upgrade, several upgrades will come to the CMS detector to accommodate the new luminosity and pileup requirements.  The tracker, muon end caps, trigger and beam radiation protection are just a few of the new upgrades scheduled for the CMS detector. However, the focus of this work will be solely on the tracker upgrades, more specifically, the inner  tracker end cap pixel (TEPX) luminometer.

For Phase-2 of the CMS tracking the entire existing pixel and strip tracker will be replaced. Figure \ref{TEPXl} shows the r-z layout of the three sections of the Phase-2 inner tracker: the  tracker barrel pixel (TBPX), composed of four cylindrical layers of modules, the tracker’s forward (TFPX) and the tracker end-cap (TEPX) pixel detectors, made of 8 and 4 disks of pixel modules respectively. The new tracker will include: increased granularity, forward acceptance and radiation hardness as well as compatibility with longer trigger latency and higher data rates.
The silicon pixel modules will have a thickness of 100-150 $\mu m$, while the pixel cells will have an area of 2500 $\mu m^2$ ($25\times 100$ $\mu m^2$) \cite{CERN-LHCC-2017-009}\cite{DelBurgo:2706637}. Two types of modules will be used in the inner tracker, modules with 2 and 4 pixel chips. The modules will be arranged in $2\times1$ and $2\times 2$, these modules are depicted as green and yellow respectively in  Figure \ref{TEPXl}. TBPX and TFPX will be composed of both types of modules, while TEPX will only use $2\times 2$ modules \cite{DelBurgo:2706637}. 
\begin{center}
\begin{figure}[H]
    \centering
    \includegraphics[scale=.2]{Chapter2/TEPX.png}
    \caption[Diagram of the Phase-2 inner tracker upgrade.]{\textit{Lefts}: Diagram of the Phase-2 inner tracker upgrade. The last four yellow lines between 1700 mm and 2700 mm, correspond to the TEPX subdetector. \textit{Right}:  Front view of one of the disks of the TEPX subdetector \cite{DelBurgo:2706637}.}
    \label{TEPXl}
\end{figure}
\end{center}
For Phase-2 the TEPX portion of the tracker will be designated for tracking and luminosity measurements, while disk 4 ring 1 (TEPXD4R1) of the detector will designated for luminosity measurements only. The TEPX detector is located at each extremity of the tracker of the CMS detector, with a range  from 175 cm to 265 cm on the $|z|$ direction and a radius  between 63 mm and 255 mm. The detector is composed of 4 double sided disks, each one made of 5 concentric rings of pixel modules. To guarantee hermetic coverage, each ring has a different number of pixel modules. TEPX is composed of 800 million pixels, distributed over an area of 2$m^2$, and will operate at trigger frequency of 75KHz during physics runs. Table \ref{rings} shows the number of modules per ring, as well as the radius of each ring.

\begin{table}[H]
\centering
\caption[Radius and number of pixel modules that comprise the rings of the TEPX subdetector.]{ Table shows the inner ($r_{in}$) and outer ($r_{out}$) radius, as well as the number of pixel modules that comprise each ring of each disk of the TEPX subdetector}
\scalebox{.8}{
\begin{tabular}{|l | c | c | c |c|c|}
\hline
 Ring & 1& 2&3&4&5   \\
\hline
$r_{in}$ (mm) & 62.9&100.55 &137.85 &174.45 &210.5\\
\hline
$r_{out}$ (mm)&107.69 &144.99 &182.09 &218.56 &254.51 \\
\hline
 No. of modules&20 &28 &36 &44&48 \\
\hline
\end{tabular}}
\label{rings}
\end{table}

The innermost ring of the last disk, disk 4 ring 1 (TEPXD4R1), lies beyond a pseudorapidity of $|\eta|=4$ and due to the low number of tracking points in this region, this ring will be designated for luminosity measurements only. The ring consists of 20 modules, and it has an inner radius of 62.9 mm and an outer radius of  107.69 mm. Finally, the luminometer may run at a trigger frequency of 825kHz to several MHz.\\
Luminosity measurements with the TEPX's detectors will be carried out using the Pixel cluster counting (PCC) method described in the next chapter.

### 2022-04-29 tesis_Rodolfo/Chapter3/chapter3.tex
Draft_0

--- 2022-04-20 tesis_Hedwin/Chapter3/chapter3.tex
@@
-\chapter{  Luminometer system description}
+\chapter{ Luminometer system and calibration description}
+
+%%%%Introduction%%%%%%%%%%%%%%%%%%%%5
+
+A total of seven systems are used for measuring luminosity at CMS, being the PCC one of them.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Cluster coincidence algorithm }
-
-The other object used by the TEPX luminometer to measure the event rate are two-fold coincidences.
-Coincidences are less prone to contamination by false hits produced in the detector after a bunch crossing (afterglow), due to the slow dissipation of charge and neutrons produced by the surrounding material (albedo).
-Two-fold coincidences are created when a particle hits overlapping modules, in the different layers of the TEPX disks.
-Due to this, coincidences are more likely to be a real hit than random electrical noise.
-The cylinder/disk like geometry of the TEPX detector allows for coincidences to be constructed in two ways: coincidences in $\phi$ require modules overlapping in the same ring, in front and in the back of a double sided disk, while coincidences in $r$ requires overlapping modules from different layers.
-These two ways of constructing two-fold coincidences are illustrated in Figure \ref{3x2x}.
-The surface area of overlapping modules tends to be larger in $\phi$ than in the $r$ direction.
-In order for a 2x coincidence to be considered, activated pixel clusters must fall in to specific cuts (on their $\delta r$ and $\delta \phi$ separations).
-Finally, three-fold coincidences can occur as well, however, these types of coincidences are beyond the scope of this work.\\
-Coincidences provide another method of measuring luminosity and bring more stability, linearity and precision to the TEPX luminometers.
-\begin{center}
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=.4]{Chapter3/3x2x.png}
-    \caption[Regions where two-fold coincidences can occur in r and $\phi$.
-]{Diagram of the regions in r and $\phi$ where pixel modules overlap, between the front and the back layers of one double-sided disk, from which two-fold coincidences come.
-}
-    \label{3x2x}
-\end{figure}
-\end{center}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Data acquisition}
-After event rate measurements have been taken, the data needs to be safely transferred and stored.
-In order to do this, several systems are put in place.
-Every subdetector has a dedicated CMS subsystem or a dedicated BRIL (Beam Radiation, Instrumentation, and Luminosity) system that takes care of this process.
-In the case of the TEPX, and other luminometers described in section 3.4.1, a combination of CMS and BRIL systems will be used, while TEPXD4R1 will be solely operated by BRIL.\\
-The way counts per bunch crossing measured by a given luminometer are stored in CMS, is by using histograms.
-Every time a full orbit of bunches collides (3564 bunches), the counts per bunch crossing is histogramed and stored.
-Depending on the geometry of the subdetector, the number of histograms generated by each changes.
-In the case of TEPX and TEPXD4R1 a histogram is created per quarter ring, this means that a total of 152 histograms are created by TEPX (not including the histograms from D4R1) and 8 by TEPXD4R1, in one orbit.
-The histograming is done by the dedicated back-end of each subdetector, a combination of software and hardware components in charge of creating these histograms.
-Once the histograms have been correctly created they are read, processed and stored by the BRILDAQ (BRIL data acquisition) system.
-Figure \ref{histhit} shows an example of a histograms for TEPX in the case of pixel clusters.
+\section{2018 Calibration Scan program}
+The VdM scans, and other scans regarding to calibrations, were performed during the LHC fill 6868 on June 30 and July 1, 2018 at $\sqrt{s}=13TeV$.
+The LHC filling scheme used 124 colliding bunch pairs at the CMS interaction point (IP5) widely spread over the orbit to reduce long range beam-beam effects and detector afterglow.
+The resulting beam size $\sigma_{b}$ at the beginning of the fill was in the range of approximately 85–95 and 80–90 $\mu m$ in $x$ and $y$, respectively, increasing over time in the $x$ dimension and decreasing over time in the $y$ dimension.No crossing angle was used for collisions at ATLAS and CMS.
+The resulting peak pileup was approximately $\mu = 0.6$ , much lower than in a regular physics fill.
+
+The bunch intensities were approximately $7-9 \times 10^{10} $ protons per filled bunch, resulting in a total beam intensity of slightly above $10^{13}$ protons per beam.
+The total beam intensities were measured with the DC Current Transformers (DCCT) [15], and the bunch currents were measured with the Fast Beam Current Transformers (FBCT) [16].
+The beam orbit was monitored using two systems, the DOROS beam position monitors (BPMs) [17] located near IP5, and the arcBPMs located in the LHC arcs adjacent to CMS.
+***The orbit is also tracked using movements of the luminous region based on reconstructed vertices.
+The arc BPM measurements are translated to a beam position at IP5 using the LHC optics file; the specific optics file used for this scan is R2016c A19mC19mA19mL24.
+
+To ensure a dataset with a high event count for PCC even at large beam separations, CMS recorded the zero-bias triggers on 5 bunch pairs (BCIDs 265, 865, 1780, 2192, and 3380) and recorded events with a total rate of $27.7kHz$.
+
+The CMS VdM scan program was conducted in two parts (``takes''), due to an alarm.
+The first part consisted of a total of six x-y scan pairs.
+Two (``emit1'' and ``emit'') were short ``emittance'' scans, in which the two beams were separated by $4sigma_{b}$ in 9 steps with 10 seconds integration time at each scan point.***
+Scan pair ``norm1'' was a standard VdM scan, in which the two beams were separated by $6\sigma_{b} \approx 600 \mu m$  and scanned across one another in a sequence of 25 steps with 30 seconds per step.
+
+The second part of the scan program was conducted in the same fill but about $7.5$ hours later.
+It consisted of twelve scan pairs.
+Scan pair ``emit3'' was a short emittance scan, followed by scan pairs ``imag2'' and ``imag3'' of the beam imaging kind, an offset scan pair ``offset2'', and finally two normal VdM scan pairs ``norm2'' and ``norm3''.
+The latter two allow us to test the reproducibility of the measuremen.
+
+****After ``norm3'' scan pair, there were the first superseparation period, in which the beams are separated a distance of $6 \sigma_{b}$ in both $x$ and $y1 direction$ for $5$ minutes long in order to get a bakcground estimation.**** source: Analyis Note 2018
+
+A length scale calibration (LSC) was performed after scan pair ``norm3'' using two different methods.
+The first, ``lsc1'', was the ``constant separation'' scan, in which the two beams were separated by $1.4\sigma_{b}$ (approximately equal to $1\Sigma$) and moved together in steps of $1\sigma_{b}$ across and back, for a total of $10$ steps with $70$ seconds per step, once in each transverse direction.
+A second ``variable separation'' method with scan pair ``lsc2'' was also executed, in which one beam (starting with beam 1) is moved to $-2.5\sigma_{b}$ and then a three-point scan (a ``miniscan'') is performed with the other beam (starting with beam 2) at a relative position of $-1.25\sigma_{b}$, $0$, and $+ 1.25 \sigma_{b}$.
+The position of the first beam is then translated in five steps in the same direction to $+2.5 \sigma_{b}$, repeating the miniscan at each step.
+This procedure is repeated four times, with two directions for each of the two beams.
+Each scan point has a duration of about $46s$.
+
+Finally, a normal VdM scan pair “norm4”,*** a second super separation period***,  and two short emittance scan pairs “emit4” and“emit5” concluded the program.
+
+In each scan pair, the scan was performed first in the x direction and then in the y direction, with the exception of the variable separation length scale calibration scan pairs, which were done the other way around.
+Figure \ref{2018sp} shows the beam positions for the two beams in the x and y directions as measured by the DOROS BPMs during the scan program, showing all 18 scan pairs.
 \begin{center}
@@
         \centering
-        \includegraphics[scale=0.5]{Chapter3/histbx.png}
-        \caption[Histogram of the mean number of pixel clusters per bunch crossing (BX) measured by the Phase-1 pixel detector.]{The histogram shows the mean number of pixel clusters per bunch crossing (BX) for one lumisection (23.3 seconds), measured by the Phase-1 pixel detector during regular physics runs.
-The measurements from the 2018 data taking period.}
-        \label{histhit}
-    \end{figure}
-\end{center}
-Once histograms have been created, safely transferring and storing them is important, in order to do this the memory required to store them needs to be known.
-The memory size of each histogram depends on the information in each of  them.
-All histograms have 3564 bins, one bin for each bunch crossing, these bins store the number of counts measured in a given bunch crossing, thus, the bits of information stored in these bins will give the memory of each histogram.
-\begin{equation}
-    \text {Memory per Hist}= \text {No. of Bins}\times \text {bits per Bin}
-    \label{histm}
-\end{equation}
- where the bits per Bin are calculated using 
- \begin{equation}
-     \text {bits per Bin}= log_2(N)
-     \label{logn}
- \end{equation}
-where $N$ is the maximum expected number of counts per bunch crossing for a given integration period, it is worth mentioning that the results from equation \ref{logn} are rounded up to the closes integer.
-The maximum expected number of counts per bunch crossing is given by
-
-\begin{equation}
-    N=n\frac{\text {Total Trigger Rate}}{3564}t
-    \label{N}
-\end{equation}
-where $n$ is the mean number of counts per event and $t$ is the integration period.
-Equation \ref{N} assumes that the Total Trigger Rate is distributed uniformly.
-Once the memory of the histogram is known, the data bandwidth needed to store all the histograms can be calculated, the Data Transfer Rate is given by
-\begin{equation}
-    \text {Data Transfer Rate}=\frac{No. Hist\times Memory per Hist}{t}
-    \label{drate}
-\end{equation}
-where No. Hist is the number of histograms created by the detector and t is the time in which the information is transferred.\\
-
-\subsection*{32-bit word implementation}
-The data at CMS is not transferred bit by bit, rather, is transferred in packages of information called words.
-Each word contains 32-bits of information, this means that all data transferred has to, first, be converted in to a 32-bit word.
-The way this is applied to the histograms is by converting the information in each bin in to a word, this is done in two ways:
-\begin{itemize}
-    \item If the Bits per bin$\leq16$ bits, the number of bits is
-rounded to 16 and two bins are grouped in one word.
-\item If $16\leq$ Bits per bin$\leq32$,  the number of bits is
-rounded to 32-bit word and one word is used for each bin.
-\end{itemize}
-
-Aside from this, the TEPX luminometers use additional words for the overhead of the histograms data format:
-\begin{itemize}
-    \item 9 words for the header for TEPX and D4R1.
-    \item  768 words for errors for TEPX and 160 for D4R1.
-    \item 4 words for the mask for TEPX and 2 forD4R1.
-\end{itemize}
-These additional data has to be taken in to account for each histograms, when calculating the needed memory to store and transfer them.
-Finally, using equation \ref{logn} the bits per bin can be calculated, using data from the high pileup simulation \cite{datarates}.
-The results for the TEPX luminometers is shown in Table \ref{bitsperbin}.
-\begin{table}[ht]
-\centering
-\caption[ Memory bits required per histogram bin for the TEPX luminometers.]{Table shows the Trigger rate (kHz), counts per event per detector unit (histogram), number of counts per bx per integration period (1s) and the memory bits required per histogram bin.}
-\scalebox{.7}{
-\begin{tabular}{|l |c |c |c |c|}
-\hline
-&  Trigger rate (kHz) & Counts per event & Counts/bx/1s&Bits/bin\\
-\hline
-TEPXD4R1 Clusters&825&539&1.25e+05&17\\
-\hline
-TEPXD4R1 2x Coincidences&825&54&1.25e+04&14\\
-\hline
-TEPX Clusters&75&539&1.13e+04&14\\
-\hline
-TEPX 2x Coincidences&75&54&1.14e+03&11\\
-\hline
-\end{tabular}}
-\label{bitsperbin}
-\end{table}
-Using this and equation \ref{drate}, the data rates can be calculated, the results are shown in Table \ref{dataratet} for a transferring time of 1 s.
-\begin{table}[ht]
-\centering
-\caption[Data transfer rates for the TEPX luminometers.]{Data transfer rates for the TEPX luminometers for pileup 200.
-Columns shown are number of histograms, memory per histogram and data transfer rates (Mbps) for an integration period of 1s.
-}
-\scalebox{.8}{
-
-\begin{tabular}{|l  |c |c |c|}
-\hline
-&  Number of Histograms & Memory per histogram (Kb) & Data Transfer Rates (Mbps)\\
-\hline
-TEPXD4R1 Clusters&8&124&0.95\\
-\hline
-TEPXD4R1 2x Coincidences&8&67&0.5\\
-\hline
-TEPX Clusters&152&82&12.5\\
-\hline
-TEPX 2x Coincidences&152&82&12.5\\
-\hline
-\end{tabular}}
-\label{dataratet}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Other luminometers}
-
-The TEPX luminometer is not the only luminometer of the CMS Phase-2 detector, each layer of the detector will have a dedicated luminometer, and corresponding algorithm, to ensure the best luminosity measurements possible.
-Figure \ref{cmslum} shows the location of the different luminometers at the CMS detector, for the Phase-2 upgrade. A brief description of the luminometers is presented below.
-\begin{center}
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.3]{Chapter3/cmdlum.png}
-    \caption[Different subsystems and luminometrs at CMS.]{Layout of the different subsystems and luminometrs at CMS. }
-    \label{cmslum}
-\end{figure}
-\end{center}
-\subsection*{Outer tracker layer 6}
-From the outer tracker (OT), layer 6 will be a designated luminometer.
-The object used by these luminometer are track stubs, which are two-hit coincidences between closely spaced silicon modules.
-Figure \ref{ot} show the layout of the new Phase-2 outer tracker, layer 6 is located in the outer tracker barrel, specifically, the TB2S section.
-\begin{center}
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=.4]{Chapter3/ot.png}
-    \caption[Outter tracker layout.]{Diagram of the different parts that conform the outer tracker, the two barrel regions, TBPS and TB2S, and the end-cap region TEDD.
-The OT layer 6 luminometer corresponds to the last upper layer of TB2S.
-}
-    \label{ot}
+        \includegraphics[scale=0.5]{Chapter3/2018Scanprogram.png}
+        \caption[2018 San program.]{Relative change in beam positions measured by the DOROS BPMs during the 2018 scan program for the two individual beams in the horizontal x and vertical y planes, as a function of the elapsed time from the beginning of the program.
+The top row shows the portion ofthe scan program before the alarm at CMS, while the bottom two rows show the scan program after the alarm.[source: pas-lum-18]}
+        \label{2018sp}
     \end{figure}
@@
 
-Layer 6 consists of 76 ladders of 12 strip modules made of two Si-strip sensors, as shown in Figure \ref{otlather} (left).
-The ladders span fully, in the azimuthal range, at each end of the CMS detector.
-The reconstruction method of the track stubs is shown in Figure \ref{otlather} (right) as well.
-The tracks are reconstructed at 40 MHz.
-\begin{center}
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=.7]{Chapter3/otlather.PNG}
-    \caption[Example of an OT layer 6 ladder and the stub selection process.]{\textit{Left}: An example of a ladder with the the 12 strip modules (regions in yellow).
-\textit{Right}: Diagram of the stub selection process.
-The black squares represent hits, and the green squares represent the regions where the other hit could take place, to be considered a stub.}
-    \label{otlather}
-\end{figure}
-\end{center}
+The beam imaging and offset scans are intended for specific studies on the beam shapes described in Section 4**, and they can also be analyzed as traditional van der Meer scans.
+Both the LSC and beam imaging scans are discussed in detail in Ref.
+[18**].
+The offset scan data is analyzed for the first time in 2018.
 
-The OT layer 6 luminometers, creates one histograms per one 12 module ladder, for a total of 152.
-As well as the TEPX luminometers, the histograms created in layer 6 will have additional words for the overhead of the histograms data format:
+source: pas-lum-18
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Corrections and systematic uncertainties}
+There are several systematic effects which affect the beam overlap width measurement, and hence the $\sigma_{vis}$ is extracted from the VdM scan procedure.
+These effects are measured and, where applicable, corrected as described below, and a systematic uncertainty is assigned to the resulting measured cross section for each source.
+
+Framework correction flags
+
 \begin{itemize}
-    \item 9 words for the header.
-    \item  192 words for errors.
-    \item 4 words for the mask.
+ \item ghost and satellite
+ \item Background (several types, in our case from SS)
+ \item Orbit drift (sep and rate)
+ \item Beam Beam
+ \item DynamicBeta
+ \item Length Scale
+ \item PeakToPeak
 \end{itemize}
 
-Figure \ref{otstubs} shows the expected number of track stubs per bunch crossing as function of the ladders ID. Tables 3.3
-and 3.4 show the expected Bits per Bin and the Data Transfer Rates for the OT layer 6 luminometer, calculated using data from the high pileup simulation.
-\begin{center}
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=.4]{Chapter3/OT-Rates.png}
-    \caption[Simulated expected number of stubs per ladder per event.]{Simulated expected number of stubs per ladder per event as a function of ladder ID.}
-    \label{otstubs}
-\end{figure}
-\end{center}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Muon drift tube}
-The muon DT luminometer follows the same design described in section 2.2.
-The entire DT system is formed by 250 gas chambers, installed in the barrel yoke of the CMS detector, as shown in Figure \ref{Muons}.
-The chambers are distributed across 5 wheels labeled YB0, YB$\pm1$ and YB$\pm2$, four radial stations, MB1-MB4, and 12 $\phi$ sectors \cite{ABBIENDI2009192}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-The objects used by this luminometer are called trigger primitives, which are reconstructed muon track segments per DT chamber.
-The tracks are reconstructed at a trigger frequency of  40 $MHz$,  using hits from the DT and RPC detectors.
-The rate of trigger primitives has being studied and extrapolated to the expected  instantaneous luminosity of the HL-LHC, $7.5\times 10^{34}$ $cm^{-2}s^{-1}$, using  the data from Run 2.
-Figure \ref{dtrate} shows the expected rates for the YB0 and YB+2 wheels.
-The large difference on the measured rate, between the MB1 and the rest of the chambers in the MB2 and MB3 stations, is due to a significant contribution of particle from punch-through jets.
-\begin{figure}[H]
-\centering
-\includegraphics[width=.48\textwidth]{Chapter3/DT_Trigger_extraploation_YB.pdf}
-\includegraphics[width=.48\textwidth]{Chapter3/DT_Trigger_extraploation_YBp2.pdf}
-\caption[Expected rates of trigger primitives per DT chamber]{Expected rates of trigger primitives per DT chamber for the YB0 (left) and YB+2 (right) wheels.}
-\label{dtrate}
-\end{figure}
-The DT luminometer will create one histogram per DT chamber, giving a total of 250 histograms.
-Tables \ref{bitsperbinall} and \ref{dataratesall} show the expected Bits per Bin and the  Data Transfer Rates for the DT luminometer, using extrapolated data from the 2018 data taking period.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{BMTF }
-The Barrel Muon Track Finder (BMTF) is an algorithm that uses reconstructed muon tracks to provide luminosity measurements.
-As its name suggests, The algorithm uses information from all the DT and RPC gas chambers, located in the barrel of the muon system, to reconstruct muon tracks.
-One histograms is created by the algorithm.
-Tables \ref{bitsperbinall} and \ref{dataratesall} show the expected Bits per Bin and the  Data Transfer Rates for the BMTF algorithm \cite{Bachtis:2648953}.
-As well as the DT luminometer, BTMS uses  extrapolated data from the 2018 data taking period.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Data transfer rates for all luminometers}
-Using the number of histograms, as well as the mean number of counts per event for each luminometer \cite{datarates}, the number of Bits per Bin as well as the Data Transfer Rates can be calculated for all luminometers.
-This is shown is Tables \ref{bitsperbinall} and \ref{dataratesall} respectively.
-\begin{table}[H]
-\centering
-\caption[Memory bits required per histogram bin for all luminometers.]{Triger rate (kHz), counts per event per detector unit (histogram), number of counts per bx per integration period (1s) and the memory bits required per histogram bin.}
-\scalebox{.7}{
-\begin{tabular}{|l |c |c |c |c|}
-\hline
-&  Trigger rate (kHz) & Counts per event & Counts/bx/1s&Bits/bin\\
-\hline
-TEPXD4R1 Clusters&825&539&1.25e+05&17\\
-\hline
-TEPXD4R1 2x Coincidences&825&54&1.25e+04&14\\
-\hline
-TEPX Clusters&75&539&1.13e+04&14\\
-\hline
-TEPX 2x Coincidences&75&54&1.14e+03&11\\
-\hline
-OT Layer 6 track stubs&40000&8&8.98e+04&17\\
-\hline
-DT Trigger Primitives&40000&0.0125&140&8\\
-\hline
-BMTF Tracks&40000&0.041&460&9\\
-\hline
-\end{tabular}}
-\label{bitsperbinall}
-\end{table}
-\begin{table}[H]
-\centering
-\caption[Data transfer rates for the different luminometers.]{Data transfer rates for the different luminometers for pileup 200.
-Columns shown are number of histograms, memory per histogram and data transfer rates (Mbps) for an integration period of 1s.
-}
-\scalebox{.8}{
-\begin{tabular}{|l  |c |c |c|}
-\hline
-&  Number of Histograms & Memory per histogram (Kb) & Data Transfer Rates (Mbps)\\
-\hline
-TEPXD4R1 Clusters&8&124&0.95\\
-\hline
-TEPXD4R1 2x Coincidences&8&67&0.5\\
-\hline
-TEPX Clusters&152&82&12.5\\
-\hline
-TEPX 2x Coincidences&152&82&12.5\\
-\hline
-OT Layer 6 track stubs&152&120&18.3\\
-\hline
-DT Trigger Primitives&250&28&7.13\\
-\hline
-BMTF Track&1&57&0.057\\
-\hline
-\end{tabular}}
-\label{dataratesall}
-\end{table}
+\subsection{Beam beam correction}
+Beam beam correction:
 
-From these tables it can be concluded that the minimum bandwidth required will be 18.3 Mbps, corresponding to the OT luminometer.
-The total storage needed per day for all luminometers presented here can be calculated, assuming an operation time of 12 hours, the total storage needed will be 280.46 GB.
-Since other luminometers will be in operation, besides the ones discussed here, 280.46 GB is the minimum storage per day required to ensure no data is lost.
+\subsection{Veto module correction?}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-04-29 tesis_Rodolfo/Chapter4/chapter4.tex
Draft_0

\chapter{Analysis and Results}

\section{Fitted Graphs}
Fit
\section{$\sigma_{vis}$}
xsec

### 2022-04-29 tesis_Rodolfo/Chapter5/chapter5.tex
Draft_0

\chapter{Conclusion and Summary }
This is a conlcusion

### 2022-04-29 tesis_Rodolfo/Portada/Portada.tex
Draft_0

 %% Aquí comienza el documento.
\thispagestyle{empty} %% PARA QUITAR FORMATO DE PIES Y ENCABEZADOS DE PÁGINA A LA PORTADA
%
%
%
%
%
%
%
%   ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%%%%%%%%% MINIPAGE PARA EL LOGO DEL LADO IZQUIERDO (UNIVERSIDAD) %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%
%\fbox{
\begin{minipage}[c][0.15\textheight][c]{0.25\textwidth}
    \begin{center}
        \includegraphics[height=3.2cm, keepaspectratio=true]{unison-logo.png} %% LOGO IZQUIERDO
    \end{center}
\end{minipage}
%}
%
%
%
%
%
%
%   ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%%%%%%%%%%%%% MINIPAGE PARA EL CUERPO DE LA PORTADA (NOMBRES, TITULOS, ETC.) %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%
%
%
%
%\fbox{
\begin{minipage}[c][0.17\textheight][t]{0.7\textwidth}
    \begin{center}
        {\scshape\LARGE UNIVERSITY OF SONORA} %% NOMBRE DE LA UNIVERSIDAD
        \vspace{.5cm}   %% DEFINE EL ESPACIO ENTRE EL NOMBRE DE LA UNIVERSIDAD Y LA LÍNEA DOBLE
        \hrule height2.5pt  %% DEFINE EL ANCHO DE LA PRIMER LÍNEA
        \vspace{.1cm}    %% DEFINE EL ESPACIO ENTRE LAS DOS LINEAS
        \hrule height1pt  %% DEFINE EL ANCHO DE LA SEGUNDA LINEA (NORMALMENTE ES MAS DELGADA)
        \vspace{.4cm}   %% DEFINE EL ESPACIO ENTRE LA DOBLE LINEA Y EL NOMBRE DE LA DIVISIÓN
        {\scshape \large Division of Exact and Natural Sciences}
        {\scshape Physics Research Department} %% NOMBRE DE LA DIVISIÓN
    \end{center}
\end{minipage}
%}
%
%
%
%
%
%   ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%
%   ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%%%%%%%%%%%%%%%%%%%%%%% MINIPAGE PARA EL LOGO DEL LADO DERECHO (DIVISIÓN ACADÉMICA)
%
%
%
%
%\fbox{

%
%
%
%
%
%    ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%
%%%%%%% RENGLÓN DE ABAJO DEJADO INTENCIONALMENTE EN BLANCO PARA GENERAR NUEVO COMIENZO DE PÁRRAFO  %%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%
%
%  ESPACIO COMENTADO PARA EVITAR DESAJUSTES POR GENERACIÓN DE NUEVO PÁRRAFO (NO DEJAR ESPACIOS ENTRE MINIPAGES)
%
%
%
%
%
%
%%%%%%%%%%%%%%%% 5TO MINIPAGE PARA EL CUERPO DE LA PORTADA (NOMBRES, TÍTULO, ETC.) %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
%
%
%\fbox{
\begin{minipage}[l][0.78\textheight][t]{0.1\textwidth}
    \begin{center}
    \hskip0pt
    \vrule width2.5pt height17cm    %% height definde la altura de la linea gruesa
        \hskip1mm
        \vrule width1pt height17cm  %% height define la altura de la linea delgada
        \end{center}
\end{minipage}
%}
%\fbox{
\begin{minipage}[c][0.78\textheight][t]{0.8\textwidth}
      \begin{center}
      \vspace{2cm}
        {\Large \scshape {Measurements of the Large Hadron Collider Luminosity using the CMS silicon pixel detector}}

        \vspace{3cm}

        \makebox[5cm][c]{\LARGE THESIS}  \\[20pt]
         in partial fulfillment of the
requirements for the degree of:\\[5pt]
        {\Large \textbf{{Master of Science in Physics}}}\\[40pt]
        By:\\[12pt]
        \textbf{  {\large Moreno Chávez Jesús Rodolfo}}

        \vspace{2cm}

        { \large Director}:\\Dr. José Feliciano Benítez Rubio

        \vspace{2.5cm}

        { Hermosillo, Sonora} \hskip2.5cm {April X, 2022}
      \end{center}
\end{minipage}
%}

### 2022-04-29 tesis_Rodolfo/compiler_thesis.py

@@ -1,0 +1,35 @@
+import os
+# colorama_demo.py
+from colorama import init, Fore, Back, Style
+
+# Initializes Colorama
+init(autoreset=True)
+
+print(Style.BRIGHT + Back.WHITE + Fore.RED + "Cleaning Some Files...")
+dir_name = os.getcwd()
+test = os.listdir(dir_name)
+
+for item in test:
+    if item.endswith("~"):
+        os.remove(os.path.join(dir_name, item))
+    if item.endswith(".toc"):
+        os.remove(os.path.join(dir_name, item))
+    if item.endswith(".bbl"):
+        os.remove(os.path.join(dir_name, item))
+    if item.endswith(".log"):
+        os.remove(os.path.join(dir_name, item))
+    if item.endswith(".out"):
+        os.remove(os.path.join(dir_name, item))
+    if item.endswith(".blg"):
+        os.remove(os.path.join(dir_name, item))
+print(Style.BRIGHT + Back.WHITE + Fore.BLUE + "Cleaning... DONE")
+
+print(Style.BRIGHT + Back.BLACK + Fore.RED + "Compiling thesis.tex (1st)")
+os.system("pdflatex thesis.tex")
+print(Style.BRIGHT + Back.BLACK + Fore.RED + "Compiling thesis.aux")
+os.system("bibtex thesis.aux")
+print(Style.BRIGHT + Back.BLACK + Fore.BLUE + "Compiling thesis.tex (2nd)")
+os.system("pdflatex thesis.tex")
+print(Style.BRIGHT + Back.BLACK + Fore.GREEN + "Compiling thesis.tex (3rd)")
+os.system("pdflatex thesis.tex")
+print(Style.BRIGHT + Back.BLACK + Fore.GREEN + "DONE: thesis.pdf'")

### 2022-05-06 project_Luis/paper.tex
Luis project

--- 2021-06-16 project_rodolfo/paper.tex
@@
   \centering
-  \includegraphics[width=0.7\columnwidth]{./LHCcomplex.png}
+  \includegraphics[width=0.7\columnwidth]{./LHC-cpx-book.png}
   \caption{Diagram of the LHC accelerator complex located near Geneva, Switzerland.
-The complex consists of three accelerator stages: the proton (p) or lead (Pb) source, the Proton Synchrotron (PS), the Super Proton Synchrotron (SPS), and the 27 km LHC ring.
-Four collision points are shown corresponding to the ALICE, ATLAS, LHCb, and CMS detectors  \cite{wiki:xxx}.} % Mobs:2684277
+The complex consists of the accelerator stages: Linear accelerator 2 (LINAC2; linear accelerator in which the protons are accelerated in bunches) , the Proton Synchrotron (PS), the Super Proton Synchrotron (SPS), and the 27 km LHC ring.
+Four collision points are shown corresponding to the ALICE, ATLAS, LHCb, and CMS detectors \cite{Zinser2018}.} % \cite{wiki:xxx}.} % Mobs:2684277
   \label{figure5}

### 2022-05-19 project_Luis/paper.tex
test commit
test commit 2
Actualizando anteproyecto

@@
 
-\def\Student{Jesus Rodolfo MORENO CHAVEZ }
+\def\Student{Luis Enrique CUEVAS PICOS }
 \def\Title{MASTERS THESIS PROJECT}
@@
 \def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
-\def\ProjectTitle{Measurement of the Large Hadron Collider luminosity using the CMS silicon pixel detector}
-\def\ProjectTitleESP{Medic\'{i}on de la luminosidad del Gran Colisionador de Hadrones usando el detector de pixeles de silicio de CMS}
+\def\ProjectTitle{Development and calibration of the luminosity measurement system CMS Silicon Pixel Detector}
+\def\ProjectTitleESP{Desarrollo y calibraci\'{o}n del sistema de medici\'{o}n de luminosidad CMS Silicon Pixel Detector}
 \def\ResearchLine{Fisica Matematica}
@@
     {\bf \large \ProjectTitle  \par}
-    \\
+
     \vspace{0.4cm}
@@
 
-  This research project consists on the precise determination of the luminosity delivered by the Large Hadron Collider to the Compact Muon Solenoid (CMS) experiment at CERN during 2017-2018 period  using the Pixel Cluster Counting (PCC) method.
-  Luminosity plays a fundamental role in the  measurement of physics processes of elementary particles of the Standard Model, a precise determination of the delivered luminosity allows for precise tests of the Standard Model and searches for new physics.
-The PCC method consists of the reconstruction and counting of track clusters produced by charged particle tracks using the Inner Tracker of the CMS detector.
-Due to the fine granularity of the pixel sensors of the Inner Tracker, the hit occupancy in the sensors remains very small ($<1\%$) during the proton collisions, this leads to a very linear response and small overall systematic uncertainties for the luminosity measurement.
+  This  project consists on  perform an analysis and calibration of the LHC luminosity data recorded
+by the CMS experiment during the new phase starting in 2022 (Run 3) using the Pixel Cluster Counting (PCC) method, to develop the upgraded luminosity measurement system for Run 3 and the HL-LHC phases.
+Luminosity gives a measure of how many collisions are happening in a particle accelerator  and a precise determination of this will allows us precise tests of the Standard Model and searches for new physics like dark matter and supersymmetry theories.
+The (PCC) method is an offline technique for the calculation of instantaneous luminosity  by counting the number of pixel clusters in the detector.
+The high densities of pixels of the Inner Tracker gives a low hit occupancy in the sensors during the proton-proton collisions, this leads to a very linear response and small  uncertainties for the luminosity measurement.
   \hspace{2pt}
@@
 
-We propose to perform an analysis of the LHC luminosity data recorded by the CMS experiment during 2017 and 2018 using the Pixel Cluster Counting (PCC) method~\cite{LUM12001}.
+We propose to perform an analysis and calibration of the LHC luminosity data recorded by the CMS experiment during the new phase starting in 2022 (Run 3) using the Pixel Cluster Counting (PCC) method.
+To develop the upgraded luminosity measurement system for Run 3 and the HL-LHC.
 
@@
 
-The main objective of this work is to perform a measurement of the 2017-2018 luminosity with a precision at the level of 2\% or less using the CMS Pixel detector.
-This precision is necesary for testing SM of elementary particles and identifying possible new physics which could elucidate the nature of Dark Matter in our universe.
+To perform an analysis and calibration of the LHC luminosity data recorded by the CMS experiment during the new phase starting in 2022 (Run 3) using the Pixel Cluster Counting (PCC) method.
+To develop the upgraded luminosity measurement system for Run 3 and the HL-LHC phases.
+This will allows us precise tests of the Standard Model and searches for new physics like dark matter and supersymmetry theories.
 
@@
 
-As mentioned in the introduction, the precision achieved in the measurement of the integrated luminosity during Run 1 (2011-2012) was about 2.5\% using  methods developed for the first time.
-In 2015 and 2016 runs, the uncertainty achieved was 1.6\% and 1.2\%, respectively, for datasets corresponding to \lumi{2.5} and \lumi{36}  \cite{Sirunyan:2021qkt-corr}.
-The methods used for the 2015 and 2016 data are similar to the strategy we propose in this project.
-We expect that the final uncertainties for the 2017 and 2018 datasets to be similar, but the ultimate goal of the CMS collaboration is to reduce these uncertainties to below 1\%  \cite{Dainese:3}.
+ \cite{Dainese:3}.
 
@@
 \begin{itemize}
-\item Understand the CMS pixel detector layout including the barrel layers and endcap disks and their constituent silicon pixel modules.
-\item Study the stability of the modules in the different layers or disks of the pixel detector and select the stable components.
-\item Determine the calibration constant corresponding to the PCC luminometer for proton-proton colisions at 13 TeV using the selected pixel detector components.
-\item Determine the delivered luminosity per lumisection (23 second intervals) and the total integrated luminosity for 2017 or 2018 data.
-\item Study some of the systematic uncertainties related to the measurement of the luminosity using the PCC. For example, calibration uncertainties, stability, and linearity.
+\item 
+\item 
+\item 
+\item 
+\item 
 \end{itemize}
@@
 
-The CMS experiment is located at one of the four interaction points of LHC.
-The CMS detector has the form of a cylindrical onion, with several concentric layers of components.
-A powerful magnet is used to bend charged particles as they move away from the point of collision to identify the charge and measure their momentum.
-A silicon tracker, made of about 75 million electronic sensors arranged in concentric layers, measures the curvature of charged particles with very high precision \cite{Chatrchyan:2008aa}.
-The electromagnetic calorimeter detects photons and electrons while the hadron calorimeter detects mainly pions and kaons.
-The muons are detected by special chambers placed outside the solenoid as shown in Figure~\ref{fig:CMS}.
+~\ref{fig:CMS}.
 
@@
 \begin{itemize}
-\item Final selection of good modules for calculating luminosity using the PCC method.
-\item Determination of the PCC calibration constant by analyzing the vdM scan data.
-\item Determination of the luminosity per lumi section and integrated for the 2017 or 2018 data.
-\item Estimation of the systematic uncertainties associated with the calibration constant or the integrated luminosity values.
-\item A presentation of the results in a national or international conference.
-\item Publication of the results in a peer-reviewed scientific journal.
+\item 
+\item 
+\item 
+\item 
+\item 
+\item 
 \end{itemize}

### 2022-05-20 project_Luis/paper.tex
fixing compile
Fix compile
updates

@@
 \fancyhf{}
-\usepackage[utf8]{inputenc} 
+\usepackage[latin1]{inputenc} 
 \usepackage{lastpage}
@@
 \def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
-\def\ProjectTitle{Development and calibration of the luminosity measurement system CMS Silicon Pixel Detector}
-\def\ProjectTitleESP{Desarrollo y calibraci\'{o}n del sistema de medici\'{o}n de luminosidad CMS Silicon Pixel Detector}
+\def\ProjectTitle{Studies of the CMS Pixel Cluster Counting luminometer using Run 3 data}
+\def\ProjectTitleESP{Estudios del luminometro Pixel Cluster Counting del CMS usando datos de la corrida 3}
 \def\ResearchLine{Fisica Matematica}
@@
 
-%%%%%%%comands
+%%comands
 \newcommand{\SubItem}[1]{ {\setlength\itemindent{15pt} \item[-] #1} }
@@
     {\bf \large \ProjectTitle  \par}
-
+    \vspace{\baselineskip}   
     \vspace{0.4cm}
@@
   This  project consists on  perform an analysis and calibration of the LHC luminosity data recorded
-by the CMS experiment during the new phase starting in 2022 (Run 3) using the Pixel Cluster Counting (PCC) method, to develop the upgraded luminosity measurement system for Run 3 and the HL-LHC phases.
+  by the CMS experiment during the new phase starting in 2022 (Run 3) using the Pixel Cluster Counting (PCC) method.
+%to develop the upgraded luminosity measurement system for Run 3 and the HL-LHC phases.
 Luminosity gives a measure of how many collisions are happening in a particle accelerator  and a precise determination of this will allows us precise tests of the Standard Model and searches for new physics like dark matter and supersymmetry theories.
-The (PCC) method is an offline technique for the calculation of instantaneous luminosity  by counting the number of pixel clusters in the detector.
-The high densities of pixels of the Inner Tracker gives a low hit occupancy in the sensors during the proton-proton collisions, this leads to a very linear response and small  uncertainties for the luminosity measurement.
+The PCC method is an offline technique for the calculation of instantaneous luminosity  by counting the number of pixel clusters in the detector.
+The high densities of pixels of the Inner Tracker of the CMS detector gives a low hit occupancy in the sensors during the proton-proton collisions, this leads to a very linear response and small  uncertainties for the luminosity measurement.
   \hspace{2pt}
@@
 In the first part of Run 2 (2015-2016), the delivered luminosity has been measured to be \lumi{38.4} with an unprecedented precision of 1.3\% \cite{Sirunyan:2021qkt-corr}.
-For the second part of Run 2 (2017-2018), the integrated luminosity is about \lumi{78}, but its precise value and uncertainty remain to be determined and is the main objective of this thesis project \cite{CMS:2018elu-corr}.
+For the second part of Run 2 (2017-2018), the integrated luminosity is about \lumi{78}.
+%but its precise value and uncertainty remain to be determined and is the main objective of this thesis project \cite{CMS:2018elu-corr}.
+After many upgrades to the different parts of the experiment, Run 3 is restarting this year 2022.
+The main objective of this thesis project is to analize the first data recorded this year and provide a preliminary result of the luminosity recorded by the CMS experiment.
 
-The plan of the LHC till year 2038 is to obtain datasets with up to 10 times higher values of instanteneous luminosities in the final phase, the  High Luminosity LHC (HL-LHC), and corresponding integrated luminosities of order \lumi{3000} \cite{Dainese:3}; the most updated projected luminosity performance along the  whole  life  of  LHC/HL-LHC  machine is shown Figure~\ref{figure6}.
+The plan of the LHC till year 2038 is to obtain datasets with up to 10 times higher values of instanteneous luminosities in the final phase,
+the  High Luminosity LHC (HL-LHC), and corresponding integrated luminosities of order \lumi{3000} \cite{Dainese:3};
+the most updated projected luminosity performance along the  whole  life  of  LHC/HL-LHC  machine is shown Figure~\ref{figure6}.
 These final datasets will provide  precise measurements of the properties of the Higgs boson and other SM particles as shown in Fig. ~\ref{figureKappasUncs}.
@@
 We propose to perform an analysis and calibration of the LHC luminosity data recorded by the CMS experiment during the new phase starting in 2022 (Run 3) using the Pixel Cluster Counting (PCC) method.
-To develop the upgraded luminosity measurement system for Run 3 and the HL-LHC.
+In particular, we plan to perform studies of detector components and the calibration data recording using the van Der Meer (vdM) scans that allow to obtain the calibration of this luminometer with high precision.
+%To develop the upgraded luminosity measurement system for Run 3 and the HL-LHC.
 
@@
 To perform an analysis and calibration of the LHC luminosity data recorded by the CMS experiment during the new phase starting in 2022 (Run 3) using the Pixel Cluster Counting (PCC) method.
-To develop the upgraded luminosity measurement system for Run 3 and the HL-LHC phases.
+%To develop the upgraded luminosity measurement system for Run 3 and the HL-LHC phases.
 This will allows us precise tests of the Standard Model and searches for new physics like dark matter and supersymmetry theories.
@@
 
- \cite{Dainese:3}.
-
-\section{SPECIFIC OBJECTIVES}
-
-\begin{itemize}
-\item 
-\item 
-\item 
-\item 
-\item 
-\end{itemize}
+For this preliminary measurement of the luminosity data collected in 2022, we expect that the methods used in this analisis will lead to a measurement uncertainty better than 2\%. 
+% \cite{Dainese:3}.
 
@@
 
+\section{SPECIFIC OBJECTIVES}
+
+\begin{itemize}
+\item
+
+\end{itemize}
+
 \section{EXPECTED RESULTS}
@@
 \item
-\item 
-\item 
-\item 
-\item 
-\item 
+
 \end{itemize}

### 2022-05-20 project_rodolfo/compile.sh

@@ -27,7 +27,6 @@ then
 	rm -rf $thesis.spl
 	rm -rf *#* 
 	echo "Cleaning complete!"
-	exit
 else
 	echo "Compiling ...!"
 	pdflatex -interaction=nonstopmode $thesis.tex
@@ -39,5 +38,4 @@ else
 	makeindex $thesis.nlo -s nomencl.ist -o $thesis.nls
 	pdflatex -interaction=nonstopmode $thesis.tex
 	echo "Success!"
-	exit
 fi

### 2022-05-24 project_Luis/paper.tex
luis
pictures changed

@@
     {\bf \large \ProjectTitle  \par}
-    \vspace{\baselineskip}   
+
     \vspace{0.4cm}
@@
   \centering
-  \includegraphics[width=0.8\columnwidth]{./lumint.png}
+  \includegraphics[width=0.8\columnwidth]{./HL-LHC_2022.pdf}
   \caption{Forecast for peak luminosity (red dots) and integrated luminosity (violetline) in the HL-LHC era with nominal HL-LHC parameters\cite{BejarAlonso:2749422}.}  %\cite{collaborations2019report} era la [5] de la ant fig2
@@
    \centering
-   \includegraphics[width=0.7\columnwidth]{./pg.png}
-   \includegraphics[width=0.29\columnwidth]{./higgs_couplings.png}
+   \includegraphics[width=0.6\columnwidth]{./pg.png}
+   \includegraphics[width=0.39\columnwidth]{./Higgs-cross-sections-for-several-production-channels.png}
    \caption{
      Left: Main production mechanisms for the Higgs boson at the LHC: gluon-gluon fusion (ggF), vector-boson fusion (VBF), associated vector boson (VH), associated top-quark pair (ttH), and  associated single-top quark production (tH)  \cite{Grojean:2017hsb-corr}  \cite{Khachatryan:2015ota} .
-     Right: Expected uncertainties on the Higgs coupling parameters for  \lumi{3000} of proton-proton collision data at 13 TeV center-of-mass energy \cite{Cepeda:2019klc-corr}.
+     Right: Higgs boson cross sections for several production channels versus the LHC centre of mass energy  \cite{Cepeda:2019klc-corr}.
    }
@@
 
-~\ref{fig:CMS}.
+%~\ref{fig:CMS}.
 
@@
 \begin{itemize}
-\item
+
+\item Understand the CMS silicon pixel detector including the barrel and endcap sensors.
+
+\item Study the stability and linearity of the sensors in the different layers or disks of the pixel detector and select the stable components.
+
+\item Determine new methods for measurement of the stability and linearity of the system.
 
@@
   \SubItem{ Analysis/Computing skills (\textsc{Bash, Emacs, c/c++, python, ROOT})}
-  \SubItem{ Analysis of the LHC Run 2 luminosity data using the PCC method}
+  \SubItem{ Analysis of the LHC Run 3 luminosity data using the PCC method}
 
@@
   \SubItem{ Course II on particle physics, particle detection, or  data analysis}
-  \SubItem{ Completion of the analysis of the LHC Run 2 luminosity data using the PCC method}
+  \SubItem{ Completion of the analysis of the LHC Run 3 luminosity data using the PCC method}
   \SubItem{ Presentation of results at national or international conference}

### 2022-11-11 project_Antonio/paper.tex
Add files via upload

\documentclass[final,3p]{CSP}
\usepackage{amssymb}
\usepackage{changepage}
\usepackage{float}
\usepackage{hyperref}
\usepackage{url}
\usepackage{afterpage}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}

\def\Student{Antonio Paredes Sotelo}
\def\Title{THESIS PROJECT PROPOSAL}
\def\Prog{Doctorado en Ciencias (F\'{i}sica) }
\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
\def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
\def\ProjectTitle{}
\def\ResearchLine{Astrof\'{i}sica, Cosmolog\'{i}a y F\'{i}sica de Part\'{i}culas}

\newcommand{\SubItem}[1]{
    {\setlength\itemindent{15pt} \item[-] #1}
}

%%header and footer
\lhead{\Student}
\rhead{\Title}
\lfoot{\Dept}
\rfoot{Page \thepage}
\setlength{\headsep}{0.2in}
\renewcommand{\footrulewidth}{0.4pt}% default is 0pt

\begin{document}

%%%%Title Page
\begin{titlepage}
  \centering
  \hspace{0pt}
  \vfill
        {\scshape\Large \Title \par}

	\vspace{2cm}
        \begin{adjustwidth}{2cm}{2cm}{
            TITLE:\par
            {\large \ProjectTitle \par}
          }
        \end{adjustwidth}

	\vspace{0.5cm}
        \begin{adjustwidth}{2cm}{2cm}{
            RESEARCH LINE: \par
            \ResearchLine \par}
        \end{adjustwidth}

        \vspace{4cm}
        {\underline{\hspace{8cm}}\par}
	{\scshape\large \Student \par}
        {Student\par}

        \vspace{1cm}
        {\underline{\hspace{8cm}}\par}
	{\Director \par}
        {Director\par}

        \vspace{1cm}
        {\Prog \par}
        {\Dept \par}
        {Universidad de Sonora \par}

        \vspace{4cm}
	{\today}

\hspace{0pt}
\vfill

\end{titlepage}

%%%%% white page for print out
\shipout\null

%%%% Abstract Page
\newpage
\hspace{2pt}
\vfill

\begin{adjustwidth}{1cm}{1cm}

  \begin{center}
    {\Large \ProjectTitle \par}
    \vspace{1cm}
    {\itshape\textbf{Abstract}\par}
  \end{center}

  \vspace{1 cm}

\iffalse
\onehalfspacing This research project proposes to study the unobserved production channel of the Higgs boson in associated with a single top quark (tH) using Higgs boson decay to multilepton final state. The dataset collected during the Run II (2015-2018) of Large Hadron Collider (LHC) will be used corresponding to an integrated luminosity of 150 $fb^{-1}$. Increasing the collider luminosity is expected to increase the number of event for this Higgs boson production mode. The measurement of this production mode has ramifications for other measurements related to coupling parameter $y_t$ of the top quark and the Higgs boson which is part of the physics program of the international CMS and ATLAS collaborations. Previous measurements using dataset with an integrated luminosity 36 $fb^{-1}$ has put an upper limit of 2.04 pb on the production cross section which is far from standard model predicted value of 0.077 pb. We plan to obtain more stringent upper limits on the production cross section and get constraints on the Higgs top quark coupling parameter $y_t$. \par
\fi

\onehalfspacing This research project proposes to study the unobserved decays modes of the Higgs boson. \iffalse associated with a single top quark (tH) using Higgs boson decay to multilepton final state \fi The dataset collected during the Run II (2015-2018) of Large Hadron Collider (LHC) will be used corresponding to an integrated luminosity of 150 $fb^{-1}$. Serches for decays of the Higgs boson into pairs of $J$

Increasing the collider luminosity is expected to increase the number of event for this Higgs boson production mode. The measurement of this production mode has ramifications for other measurements related to coupling parameter $y_t$ of the top quark and the Higgs boson which is part of the physics program of the international CMS and ATLAS collaborations. Previous measurements using dataset with an integrated luminosity 36 $fb^{-1}$ has put an upper limit of 2.04 pb on the production cross section which is far from standard model predicted value of 0.077 pb. We plan to obtain more stringent upper limits on the production cross section and get constraints on the Higgs top quark coupling parameter $y_t$. \par

\onehalfspacing In this project, it is proposed to search for the decays of the Higgs boson to pairs of $J/\psi$ or $upsilon$ in the CMS detector based at the Large Hadron Collider of the CERN laboratory.

For these studies the data of the LHC Run 2

\end{adjustwidth}

\hspace{2pt}
\vfill

%%%%%% Begin the body
\newpage
\section{BACKGROUND}

\onehalfspacing The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the 
weak nuclear force. Gravitational force is neglected as the strength of this force is very weak at the scales over which 
elementary particle interact with each other. The standard model (SM) of particle physics is divided into two categories, 
bosonic sector and fermionic sector. Bosonic sector contain particles called bosons which mediate the fundamental forces of 
nature and the fermionic sector contain particles called fermions which make up all the matter in our universe. SM has three 
generations of matter (fermions) particles. The first generation of fermions consists of up (u) quark, down (d) quark, electron 
and electron neutrino, second generation consist of charm (c) quark, strange (s) quark, muon and muon neutrino and the third 
generation of matter particles has top (t) quark, bottom (b) quark, tau and tau neutrino. The bosonic sector consist of gauge 
bosons like gluon, photon, $W^{\pm}$, $Z^0$ which mediate strong nuclear force, electromagnetic force and weak nuclear force respectively. There is one more particle in the standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}. All the standard model particles are shown in Figure 1. Higgs boson can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva, Switzerland.

\begin{figure}[H]
	\centering
	\includegraphics[width= 0.5 \columnwidth]{./sm.png}
	\caption{Elementary particles in standard model of particle physics with their mass, spin and charge.}
	\label{figure 1}
\end{figure}

% \newpage

There are various production modes of Higgs boson like the gluon gluon fusion (ggF), vector boson fusion (VBF), Higgs 
production in association with vector boson (VH, V = $W^{\pm}$ or Z), Higgs production with top quark and top anti-quark ($t\bar{t}H$) and Higgs 
production in association with a single top quark and a quark jet (tHq). Each production channel has its own importance to probe the 
various properties like spin, parity and the coupling strength parameters of Higgs boson to fermions and bosons. The main production mode of Higgs boson at LHC is 
gluon gluon fusion (ggF). As bosons like gluons and photons are massless, they do not interact directly with the Higgs boson 
and processes like ggF or Higgs boson decay to pair of photons are not possible at tree level and can only proceed via loop 
diagrams which involve $W^{\pm}$ boson, top quark or bottom quark in the loop. The Higgs boson can also decay to other particles and these decay 
channels have different branching ratios which are computed using the partial decay widths. Higgs boson can decay to a pair of $W^{\pm}$ bosons, Z bosons, photons, bottom quarks, 
muons and electrons. Higgs boson can also decay to Z boson and a photon. The important SM Higgs Boson production modes are shown in Figure 2. The production cross section and branching ratios of various decay channels of Higgs boson are shown in Figure 3.

%\afterpage{
\begin{figure}[H]
	\centering
	\includegraphics[width=\columnwidth]{./pg.png}
	\caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
	\label{figure 2}
\end{figure}

\begin{figure}[H]
  \centering
   \includegraphics[scale=0.7]{./cd2.png}
  \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels \cite{Tanabashi:2018oca}.}
   \label{figure 3}
\end{figure}
\clearpage

 \newpage

The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large 
number of free-parameters and the fine tuning related to these parameters suggest new physics beyond SM as mentioned below.
\begin{itemize}
\item{Fine structure constant $\alpha$},
\item{Weinberg angle or the weak mixing angle $\theta_W$},
\item{The coupling constant of strong interaction $\alpha_s$},
\item{Electroweak symmetry breaking energy scale v},
\item{ Higgs potential self coupling $\lambda$ or the Higgs mass $m_H$},
\item{Three weak mixing angles and the CP-violating phase $\delta$ of the CKM matrix which tells us how quarks of different flavor mix with each other},
\item{Nine yukawa couplings $y_i$ (i = 1 to 9) which determine the mass of nine charged fermions}.
\end{itemize}
 The fine 
tunings related to the Higgs 
mass and the free parameters in SM suggests new physics beyond Standard model (BSM). There are lot of specific 
BSM theories and most of these 
models involve new heavy particles. In order to identify which new physics lies beyond the 
electroweak (EW) scale, the new parameters 
of such theories may be constrained by the actual low energy experiments.

There is another approach immitating 
Fermi's treatment of beta decay 
which consists of considering the SM as the first order approximation of the actual theory 
and by completing it with a series 
of higher dimensional operators. When the electroweak symmetry breaking takes place well 
below the mass of the new particles, 
the BSM physics is taken into account at the EW scale and below by adding higher dimensional 
operators to the SM Lagrangian. 
They are built out of SM fields and supposed to be invariant under its gauge group which is $SU(3)_C \times SU(2)_L \times U(1)_Y$.
%Those 
%operators are the low-energy residue 
%of the high energy theory. This approach does not pretend to guess the complete high-energy 
%model and it is based solely on 
%the symmetry of the  theory. The operators are general and the only model dependence is 
%encoded in the size of the operator
%coefficients, which is to be set from experiments. The Higgs boson and fermions (quarks and leptons) coupling will deviate from the standard 
%model predictions if these higher 
%dimensional operators are present in low energy effective SM theory. We can consider 
%anomalous Higgs and Higgs-gauge effective 
%dimension 6 operators like $-\frac{1}{3}(\phi^{\dagger}\phi)^3$, $\frac{1}{2} \partial_{\mu} 
%(\phi^{\dagger} \phi) 
%\partial^{\mu}(\phi^{\dagger} \phi)$ and $(\phi^{\dagger} \phi)(D_{\mu} \phi)^{\dagger} 
%(D^{\mu} \phi)$ to calculate the 
%deviation of Higgs boson-fermion couplings from SM. The first operator $-\frac{1}{3}(\phi^{\dagg%er}\phi)^3$ shift the minimum of 
%the Higgs potential. Also as there 
%will be rescaling of the Higgs field due to the introduction of these operators in the 
%potential term, Higgs-fermion (quarks 
%and leptons) couplings will be modified.
%The yukawa coupling of top quark with Higgs boson will be modified due to the presence of such higher dimensional operators.

\iffalse
\begin{figure}[ht]
	\centering
	\includegraphics[width=\columnwidth]{./cms.png}
	\caption{Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
	\label{figure 4}
\end{figure}
\fi

\iffalse
The production of Higgs boson in association with single top quark is one of the rare Higgs 
boson production mode \cite{sirunyan2019search}. As the top 
quark is the heaviest fundamental particle in the standard model, due to its large mass, the 
top quark decay before 
hardronization which allow the possibility to reconstruct top quark from its decay products 
unlike the lighter quarks which 
undergo hardronization and are seen as bundles of particles in detector called jets. The most 
probable decay of the top quark is 
into bottom (b) quark and $W^{\pm}$ boson \cite{{Tanabashi:2018oca}}. Using b-jet tagging algorithms, the jet originating from 
b-quark can be reconstructed to 
identity the top quark. In SM, the couplings of the Higgs boson to fermions (quarks and leptons) known as Yukawa couplings are proportional to the mass 
of the fermions. Thus heavy quarks like top, bottom and charm couple strongly to Higgs boson 
which means that out of all known 
quarks, top quark couple most strongly to the Higgs boson. So, it has a large value of Yukawa 
coupling $y_t$ \cite{Aad_2016}. That is why the 
Yukawa coupling of the top quark with the Higgs boson $y_t$ has lot of importance as any 
deviation from standard model prediction might give an indication of new physics. The two 
processes at LHC which will allow us to directly probe the Yukawa 
coupling between Higgs boson and top quark are Higgs boson production in association with top 
quark pair ($t\bar{t}H$) via 
strong interaction and the production of single top quark with a Higgs boson (tH). As tH 
occur via electroweak interaction, it 
is more rare than t$\bar{t}$H production \cite{Sirunyan:2018ygk}. The Higgs boson in the tH channel can be radiated 
off by a $W^{\pm}$ boson or by a top quark as shown in Figure 4.

These two processes in standard model have destructive interference which allow us to 
probe the relative sign between 
the coupling of top quark with Higgs boson $y_t$ and the coupling of $W^{\pm}$ boson to the Higgs 
boson $g_{HWW}$ \cite{Sirunyan:2018lzm}. If the Yukawa coupling between top quark and Higgs boson $y_t$ deviate from the SM 
prediction or even if $y_t$ has a negative sign, both would cause a strong increase in the tH 
production cross section which is a special property of tH production channel making it an 
interesting production channel to probe using LHC 2016, 2017 and 2018 data \cite{farina2013lifting}. The coupling 
strength modifier $\kappa_t$ is defined as $\kappa_t = \frac{y_t}{y^{SM}_t}$ which will tell 
us the deviation of $y_t$ from the SM prediction.

The LHC is sensitive to an anomalous Higgs coupling to the top quark in the Higgs boson-top quark associated production mode. 
The anomalous coupling will arise when we add interaction terms (dimension 6 operators in effective SM theory) in the Higgs potential.
As there is strong destructive inteference in the t-channel for the standard model  couplings, this production mode is sensitive to both the sign and the magnitude of any coupling beyond the SM between Higgs  boson and top quark induced by higher dimensional operators in effective beyond SM theory \cite{sirunyan2019search}.
\fi

Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. 
These had eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was 
discovered in 1995 in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass 
energy of 1.8 TeV untill 2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 
colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years. The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC). It is designed to detect particles known as muons very accurately. The CMS detector has the form of a cylindrical onion, with several concentric layers of components. Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to bend them in opposite directions and measure momentum. A silicon tracker, made of about 75 
million electronic sensors arranged in concentric layers, identifies the tracks taken by these charged particles bent with very high precision \cite{Chatrchyan:2008aa}. The muons are detected by special subdetectors placed outside to detect them once they have crossed the solenoid as shown in Figure~\ref{figure5}. In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV. So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the Standard Model (SM).

%\afterpage{
  \begin{figure}[H]
    \centering
    \includegraphics[width=0.6\columnwidth]{./cms12.png}
    \caption{Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimeter, superconducting solenoid and muon chambers \cite{Chatrchyan:2008aa}.}
    \label{figure5}
  \end{figure}

  \begin{figure}[H]
    \centering
    \includegraphics[width=0.9\columnwidth]{./lum6.png}
    \caption{Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities. Points show instantaneous luminosity while the line shows luminosity accumulated \cite{collaborations2019report}.}
    \label{figure6}
  \end{figure}
  \clearpage

%\clearpage

LHC during the first run in 2011 and 2012 reached a peak instantaneous luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
 The LHC will deliver about 300 $fb^{-1}$ by 2024 \cite{collaborations2019report}.
The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles.
In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  place in parallel during one shutdown, at around 2023-25 (LS3), with some of the modification anticipated in 2019-2020 (LS2).
This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ by the year 2036 as shown in Figure~\ref{figure6}.
Figure~\ref{figureKappas} shows a summary of the current measurements of the Higgs coupling parameters with the LHC Run 1 dataset (2011,2012)  using ggF, VBF, VH, and ${t\bar{t}H}$ production modes \cite{Tanabashi:2018oca}.
Higgs boson production in association with single top quark has been studied to derive constraints on the magnitude and relative sign of Higgs boson couplings to top quarks and vector bosons.
Constaints on $\kappa_t$ can be derived using a likelihood ratio scan of $L(\kappa_t)/L(\hat{\kappa_t})$ where $\hat{\kappa_t}$ is the best fit value of $\kappa_t$ as shown in Figure~\ref{figureKt} \cite{Sirunyan:2018lzm}.
Multilepton final states like ee, $\mu\mu$ and $e\mu$ and final states with single lepton with a pair of bottom quarks were combined with Higgs decay to two photons to get the final result. The data slightly favor positive value of top quark yukawa coupling for SM Higgs boson and excludes ranges outside the intervals [-0.9,-0.5] and [1.0,2.1] times $y^{SM}_t$ at the 95 $\%$ confidence level.
\newpage
%\afterpage{
  \begin{figure}[H]
    \centering
    \includegraphics[scale=0.4]{./couplings.png}
    \caption{ATLAS-CMS combined measurements of coupling strength modifiers \cite{Tanabashi:2018oca}.}
    \label{figureKappas}
  \end{figure}

  \begin{figure}[H]
    \centering
    \includegraphics[width=0.4 \columnwidth]{./cms13.png}
    \caption{Scan of -2 $\Delta$ ln(L) versus $\kappa_t$ for the 2016 LHC data (black line) and the individual channels (blue, red, and green), compared to Asimov data sets corresponding to the SM expectations (dashed lines) \cite{sirunyan2019search}.}
    \label{figureKt}
  \end{figure}

\newpage
\section{PROPOSAL}

\iffalse
\onehalfspacing In this project, it is proposed to search for the production of Higgs boson associated with a single top quark in the CMS detector based at the Large Hadron Collider of the CERN laboratory.
It is proposed to study the sensitivity with the current data in the channel where the events are identified with two muons of the same sign, electron muon or with three leptons of electron or muon type.
Leptons of tau type are not considered due to complications in their identification in the detector.
\fi

\onehalfspacing In this project, it is proposed to search for the decays of the Higgs boson to pairs of $J/\psi$ or $upsilon$ in the CMS detector based at the Large Hadron Collider of the CERN laboratory. For these studies the data of the LHC Run 2 (2015-2018) will be used corresponding to an integrated luminosity of about 150 fb$^{-1}$, this is 4 times larger than the dataset used for current results. An observation of such decay  with this sample would indicate the presence of physics beyond the standard model. It is also expected to estimate projections of the sensitivity to the High Luminosity phase of the LHC (HL-LHC) (2026-2036) which will accumulate up to 100 times the data used for current measurements.

%It is proposed to study the sensitivity with the current data in the channel where the events are identified with two muons of the same sign, electron muon or with three leptons of electron or muon type. Leptons of tau type are not considered due to complications in their identification in the detector.

\section{GENERAL OBJECTIVE}

%- motivation, tH production crossection, sign of $k_t$, search for BSM, ..

\iffalse
\onehalfspacing There is currently a great enigma in physics since we know that ordinary matter comprises only $5\%$ of the universe, another $27\%$ includes Dark matter and the rest $68\%$ is Dark energy.
Understanding the production of the Higgs boson, as well as its decays are an important part of the physics program of CERN laboratory experiments to verify the Standard Model and look for new particles. Through this project we will investigate the production of the Higgs boson in association with a single top quark (tH) in proton-proton collisions with the CMS experiment at the LHC. The tH  production process has not been observed so far.
\fi

\onehalfspacing There is currently a great enigma in physics since we know that ordinary matter comprises only $5\%$ of the universe, another $27\%$ includes Dark matter and the rest $68\%$ is Dark energy.
Understanding the production of the Higgs boson, as well as its decays are an important part of the physics program of CERN laboratory experiments to verify the Standard Model and look for new particles. Through this project we will investigate the decay of the Higgs boson to $J/\psi$ in proton-proton collisions with the CMS experiment at the LHC. The decay to $J/\psi$ has not been observed so far.

\iffalse
The measurement of this process complements other measurements of the yukawa coupling parameter $y_t$ of the top quark and Higgs boson and is a part of the physics program of CMS and ATLAS international collaborations. Through these measurements we seek to complete the measurements of the Standard Model parameters to high precision and also to find evidence of deviations in yukawa couplings which point to new particles which may explain current enigmas like the origin of Dark Matter.
\fi

\section{HYPOTHESIS}
%%  - what we expect to find

\onehalfspacing Studies about the decay of the Higgs boson production channel have already started within the CMS and ATLAS collaboration and publications are based on data from the 2011-2012 run and some data from the second run of 2015-2016.
In these results, there was no evidence of signal and upper limits were set on the production cross-section.
The current results combine three types of searches: H$\rightarrow WW/ZZ/\tau\tau \rightarrow$leptons, H$\rightarrow\gamma\gamma$, and H$\rightarrow b\bar{b}$.
%The most sensitive channel is  with leptons, however this channel is a combination of two sub-channels: two-lepton and three-lepton.
The currently published result uses 36 fb$^{-1}$ of collision data and obtains an upper limit of 2.04 pb while only 0.077 pb are expected in the SM \cite{sirunyan2019search}, the limit is 26 times larger than the expected value.
In BSM models, for example with $\kappa_t = -1$,  the expected cross-section increases up to 0.834 pb due to quantum interference effects; in this case also the observed upper limit changes to 0.86 pb at 95$\%$ confidence level, the current data almost rules out this model.

With this project we propose to incorporate the full Run 2 dataset corresponding to 150 fb$^{-1}$.
A factor of 4 increase in number of collision events will improve the limits by a factor of approximately 2 due to the nature of statistical uncertainties.
This mean that the limit for the SM case will improve to about 13 times the expected cross-section, while for the modified model ($\kappa_t = -1$) we expect to be excluded.

Additionally, in subsequent phases of the LHC (2021-2023 and 2026-2038) the amount of data will increase by a factor of up to 100, which implies the upper limit for the SM case will reduce to about 2.6 times the expected cross-section. This implies that even for the HL-LHC it will be difficult to observe the tH production, but at the same time more and more phase space of BSM models will be excluded.

\iffalse
In this search the reconstruction methods do not allow to separate $t$H from $t\bar{t}H$ production because the cross-section of $t\bar{t}H$ is much larger than that of tH and some events pass the selections designed for tH.
The fraction of tH events over tH + $t\bar{t}H$ is currently only 5$\%$ with the analysis techniques used.
We expect to improve the analysis techniques using multi-variate techniques, for example boosted decision trees or other algorithms, to improve the identification of signal events over the rest of the backgrounds.
This will provide additional improvements in the limits and a possible observation of the SM signal as well as stringent exclusions for BSM models.
\fi

%\newpage
\section{SPECIFIC OBJECTIVES}

\onehalfspacing

\iffalse
The measurement of the tH production mechanism is a collaborative effort in the LHC experiment due to the various channels that need to be combined.
This project focuses on the channels with leptons in the final state: two-lepton ($\ell\ell$) or three-lepton ($\ell\ell\ell$).
The $\ell\ell$ sub-channel uses events with same sign dimuon ($\mu^\pm\mu^\pm$) or electron-muon ($e^\pm\mu^\pm$).
The $\ell\ell\ell$ sub-channel uses events in the topologies: $\mu\mu\mu$, $\mu\mu e$, $\mu e e$ and $e e e$, where no charge requirements are made.
The leptons are generated from the decays of the $W$ and $Z$ bosons or $\tau$ leptons from decays of the Higgs or top quarks.
Furthermore, light-quark and b-quark jets are generated from the initial state collision and from the decay of the top quark, these must be used in the signal identification.
\fi

In order to complete a journal publication of a  
%measurement of tH production using one of these channels, several aspects  must be worked on:
\begin{itemize}
\item Simulation of the signal events using Monte Carlo generators which implement the theoretical model.
\item Implementation of event reconstruction and selection algorithms which select high quality signal events and reduce the background events to a minimum.
\item Studies of lepton and jet identification algorithms which improve the background rejection.
\item Due to the small signal over background ratio, a multi-variate algorithm is employed which combines different event variables and exploits the correlations to construct a final discriminant. This algorithm must be trained using simulated signal and background events.
\item A model for the observed data must be constructed from the known background processes. These processes are normally simulated individually and then summed together with the signal to construct the final statistical model.
\item An algorithm is developed that adjusts the model to the observed data distribution and incorporates several systematic uncertainties due to differences between simulation and real data.
\item The signal strength observed from the statistical analysis must be interpreted as evidence of a signal or in the absence as a limit. Further analysis is required to place constraints on paramater space of BSM models.
\end{itemize}

In addition to the above objectives, members of the CMS collaboration are expected to participate in the detector operation and upgrade activities (or service work).
During shut-down periods, these activities include testing and installation of new detectors.
During regular data-taking periods, activities include monitoring the data acquisition systems and data quality through comparisons of new data and old data.
In addition to the data analysis plans described before, another objective is to contribute in one of the developments of the CMS detector to  prepare for the HL-LHC phase.
%

Finally, the results of this project will be presented at national or international conferences and a publication in a scientific journal will be accomplished.

\section{METHODOLOGY}
%- methods used in the search: which dataset,  lepton reconstruction, selections, jets, BDT, backgrounds, statistical analysis

%\afterpage{
%\begin{figure}[H]
%	\centering
%	\includegraphics[width=0.5\columnwidth]{./topology.png}
%	\caption{Topology of a tH signal event in a proton-proton collision. The decay products from the top quark include a b-jet and a W boson decaying to a lepton and neutrino. In this diagram the Higgs decays to a pair of W bosons, one decays to a lepton and neutrino while the other one can decay leptonically or hadronically. In addition there is a forward jet from initial collision of the quarks.}
%	\label{figureTopology}
%\end{figure}
%\clearpage

\onehalfspacing The methods for a measurement of the 
%coupling of the Higgs boson and the top quark in proton collisions are extensive and require several stages.

Accelerating the protons to extremely high energies and causing them to collide at high rates in order to produce rare but interesting events is the work of a separate accelerator group.
However, the members of the CMS collaboration must monitor the quality and rate of proton collisions at the interaction point at the center of the detector in order to collect a high quality dataset which can be stored for many years to do analysis.
Calibration and maintenance of all parts of the detector is necessary in order to achieve close to $100\%$ particle detection efficiency and noise levels to a minimum. This work is achieved by participating in the detector operation groups and performing data acquisition shifts during run time.  
Presence at CERN or at a remote control center like Fermilab is required in order to perform these activities.

The reconstruction and selection of signal events is studied using the \textsc{MadGraph}~\cite{alwall2014automated} Monte Carlo generator which implements the theoretical model and predict the amount and distribution of events for a given LHC dataset.

\iffalse
\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\columnwidth]{./topology.png}
	\caption{Topology of a tH signal event in a proton-proton collision. The decay products from the top quark include a b-jet and a $W^{\pm}$ boson decaying to a lepton and neutrino. In this diagram the Higgs decays to a pair of $W^{\pm}$ bosons, one decays to a lepton and neutrino while the other one can decay leptonically or hadronically. In addition there is a forward jet from initial collision of the quarks.}
	\label{figureTopology}
\end{figure}
\fi

%Figure~\ref{figureTopology} shows the main features of the topology of a tH event, including the subsequent decay products of the top quark and Higgs boson, these are the particles which are generated at the interaction point before entering the detector components.
A separate simulation of the detector is employed using \textsc{Geant}~\cite{agostinelli2003geant4} which simulates the trajectory of the stable particles, response and efficiency of each sensor in the CMS detector.
The information obtained from this chain is saved as raw data similar to the one obtained from the real experiment and is later reconstructed in the same way.

The event reconstruction is designed to capture the distinguishing features of the signal topology.
%In the channels which are the focus of this project, we require that there exist at least two leptons of electron or muon type, however also jets need to be identified as shown in the Figure 9.
The event reconstruction begins with the identification of the different types of particles: photon, electrons, muons, taus, and jets.
Particle lists are formed for each kind using a general purpose event reconstruction software called \textsc{CMSSW}~\cite{Bayatian:922757} which is maintained by the collaboration and which includes basic calibration of the various particle energy and momenta.

The Tracker subdetector of CMS shown in Figure~\ref{figure5} is composed of silicon sensors which detect minimum ionizing charged particles coming from the interaction region. The Tracker consists of an inner Pixel detector with layers of pixel sensors and an outer Strip detector. The Pixel system consists of 66 Million pixels while the Strip system comprises of 9.6 Million strip sensors. The Tracker provides a precision measurement of the track curvature (momentum) and position at the interaction region.

Electrons are reconstructed from clusters of energy in the Electromagnetic calorimeter (ECAL). The ECAL is made of rectangular transparent crystals which cause a shower of secondary photons and electrons. The energy deposited in the crystal is read out and determines the energy of the primary electron. The cluster must match to a track in the Tracker subdetector. Photons are similar to electrons, but a track must not be matched in this case.

Muons are identified by tracks which exit the inner subdetectors and cross the solenoid into the Muon chambers. Drift Tubes (DT's) in the barrel region or Cathode Strip Chambers (CSC's) in the forward region use ionizing gas to detect the passage of muon tracks.  The track in the Muon chambers is matched to the track in the Tracker to provide a measurement of the muon momentum.

Jets are reconstructed from energetic clusters found in both the ECAL and the Hadronic calorimeter (HCAL).
Pions, kaons, and other hadrons create showers of secondary particles in the dense metal plates of the HCAL, the ionization energy of secondary particles is read out with scintillating plastics interleaved with the metal plates.  
Jets originate at the interaction region from collisions of quarks and gluons which create showers of mesons and baryons (mainly pions).

%Jets which originate from b quarks are important in this study because they identify the decay of a top quark, b-jets are identified with a multivariate algorithm which searches for secondary vertices in the Tracker and electrons or muons (from decays of B-mesons) within the cone of the jet.

A new data structure with the above particle reconstruction defines new  datasets (\textsc{CMSSW}) stored in computing centers around the world which are available to students and scientists at all research institutions.
These  datasets are processed using computing clusters which use high-performance computing systems, normally using HTCondor~\cite{HTCondor} to link the processing nodes, which allows hundreds of jobs to run at the same time by individual users and save the output in \textsc{Root} format \cite{brun2003root}.
In this processing, the particle lists are used to require certain event selections and filter out uninteresting events.

%In the search for tH events using the dimuon channel the following event selections are applied:
\begin{itemize}
\item
\item
\item
\item

\end{itemize}

\textsc{Root} is a \textsc{c++} based software that allows visualization of event distributions and variable correlations.
Further optimization of the event selections is performed by considering the different processes which contribute to the background.
In this search several SM processes contribute to the background due to their decays to 
%leptons: $pp\rightarrow ZZ, WZ, WW, ZZZZ, t\bar{t}W, t\bar{t}Z, t\bar{t}H, tWZ, tZq,$ and $t\bar{t}t\bar{t}$.
These backgrounds must be determined from MC simulation and normalized to their predicted SM cross sections.

Due to the small signal over noise ratio in this search, a multivariate algorithm is trained to help separate signal events from background events.
A typical algorithm used is the Boosted Decision Tree~\cite{hoecker2007tmva}, which takes as input several event variables related to the signal topology.
In the previous search for tH these variables included:
\begin{itemize}
\item
\item
\item
\item
\end{itemize}
The multivariate algorithm takes into account the correlations between the variables and combines the information into a single discriminant.

Due to the maximum separation of the signal and background in the multivariate discriminant, this distribution is used for the statisical analysis of the events.
A fit is applied using the \textsc{RooFit} software package~\cite{verkerke2008roofit} which constructs a model for the data consisting of the sum of the backgrounds and the signal simulations. A likelihood function is constructed from a Poisson function using the expected and measured number of events.
Systematic uncertainties are incorporated as nuisance parameters using gaussian probability functions, these account for uncertaintes in the normalization and shapes of the background.
The signal strength extracted from this fit determines if there is any evidence for a signal.
In the absence of a signal an upper limit is placed on the signal strength using the likelihood function and subsequently translated into a limit in the 
%tH production cross section and the Higgs coupling parameters.

\section{EXPECTED RESULTS}
%- a limit, also predictions for future runs

\onehalfspacing The results from this project include the following items:
\begin{itemize}
\item The student will become part of an international collaboration.
\item A leading contribution in one of the search channels for the tH process using the data from the Run II of the LHC, resulting in a publication in a scientific journal.
\item Participation in the CMS detector Phase II upgrade through development and possible installation of particle detectors possibly resulting in a technical report.
\item A presentation of a poster or a talk in one of the national conferences of the Division of Paticles and Fields of the Mexican Society of Physics or a presentation of a poster or a talk in an international physics conference.
\item An academic stay at a scientific center like CERN or Fermilab.
\item A high quality thesis.
\end{itemize}

\section{CALENDAR OF ACTIVITIES}
\onehalfspacing
\begin{itemize}
\item {\bf Semester 1 (2022-2)}:
  \SubItem{ Readings on Standard Model theory}
  \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
  \SubItem{ Initial planning of the analysis strategy}
\item {\bf Semester 2 (2023-1)}:
  \SubItem{ Course I on particle physics and/or particle detection}
  \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
  \SubItem{ Readings on SM and tH literature}
  \SubItem{ Computing accounts at CERN and Fermilab}
  \SubItem{ Studies of the tH event selections}
  \SubItem{ CMS service work for authorship}
  \SubItem{ Possible summer stay at CERN or Fermilab}
\item {\bf Semester 3 (2023-2)}:
  \SubItem{ Course II on particle physics and/or particle detection.}
  \SubItem{ Studies of the tH event selections}
  \SubItem{ Development of a Multivariate algorithm for the event selections}
  \SubItem{ Studies of the background processes}
  \SubItem{ CMS service work for authorship}
\item {\bf Semester 4 (2024-1)}:
  \SubItem{ CMS service work for authorship}
  \SubItem{ Studies of the tH event selections}
  \SubItem{ Development of a Multivariate algorithm for the event selections}
  \SubItem{ Studies of the tH background processes}
  \SubItem{ Development of the statistical model and signal extraction}
  \SubItem{ Possible summer stay at CERN or Fermilab}
\item {\bf Semester 5 (2024-2)}:
  \SubItem{ Studies of the tH event selections}
  \SubItem{ Development of a Multivariate algorithm for the event selections}
  \SubItem{ Studies of the tH background processes}
  \SubItem{ Development of the statistical model and signal extraction}
  \SubItem{ Presentation of poster or talk at national or international conference}
\item {\bf Semester 6 (2025-1)}:
  \SubItem{ Development of software for the statistical analysis and interpretation of the results}
  \SubItem{ Review process of the results within the CMS collaboration}
  \SubItem{ Presentation of poster or talk at national or international conference}
  \SubItem{ Writing of the paper publication}
  \SubItem{ Writing of the thesis}
\end{itemize}

\cleardoublepage
\onehalfspacing
\bibliographystyle{unsrt}
\bibliography{paper}

\end{document}

### 2022-11-12 project_Antonio/paper.tex
Add files via upload

@@
 \def\Student{Antonio Paredes Sotelo}
-\def\Title{THESIS PROJECT PROPOSAL}
+\def\Title{Anteproyecto}
 \def\Prog{Doctorado en Ciencias (F\'{i}sica) }
@@
 \def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
-\def\ProjectTitle{}
-\def\ResearchLine{Astrof\'{i}sica, Cosmolog\'{i}a y F\'{i}sica de Part\'{i}culas}
+\def\ProjectTitle{B\'usqueda de part\'iculas de Higgs con modelos de f\'sica m\'as all\'a del Modelo Est\'andar y medici\'on de la luminosidad usando el m\'etodo de Pixel Cluster Counting en el experimento CMS del CERN}
+\def\ProjectTitleEnglish{Search for Higgs bosons using models of physics beyond the Standard Model and measurement of luminosity using the Pixel Cluster Counting method in the CMS experiment at CERN}
+\def\ResearchLine{F\'{i}sica Matematicas}
 
@@
 
-	\vspace{2cm}
+	\vspace{1cm}
         \begin{adjustwidth}{2cm}{2cm}{
-            TITLE:\par
+            T\'ITULO:\par
             {\large \ProjectTitle \par}
@@
         \begin{adjustwidth}{2cm}{2cm}{
-            RESEARCH LINE: \par
+            TITLE:\par
+            {\large \ProjectTitleEnglish \par}
+          }
+          \end{adjustwidth}
+
+	\vspace{0.5cm}
+        \begin{adjustwidth}{2cm}{2cm}{
+            RESEARCH LINE (LGAC):  \par
             \ResearchLine \par}
@@
   \begin{center}
-    {\Large \ProjectTitle \par}
+    {\Large \ProjectTitleEnglish \par}
     \vspace{1cm}
@@
 \iffalse associated with a single top quark (tH) using Higgs boson decay to multilepton final state \fi The dataset collected during the Run II (2015-2018) of Large Hadron Collider (LHC) will be used corresponding to an integrated luminosity of 150 $fb^{-1}$.
-Serches for decays of the Higgs boson into pairs of $J$
+Serches for decays of the Higgs boson into pairs of $J/\psi$ or $\Upsilon$.
 
-Increasing the collider luminosity is expected to increase the number of event for this Higgs boson production mode.
+%Increasing the collider luminosity is expected to increase the number of event for this Higgs boson production mode.
 The measurement of this production mode has ramifications for other measurements related to coupling parameter $y_t$ of the top quark and the Higgs boson which is part of the physics program of the international CMS and ATLAS collaborations.
@@
 
-\onehalfspacing In this project, it is proposed to search for the decays of the Higgs boson to pairs of $J/\psi$ or $upsilon$ in the CMS detector based at the Large Hadron Collider of the CERN laboratory.
+%\onehalfspacing In this project, it is proposed to search for the decays of the Higgs boson to pairs of $J/\psi$ or $upsilon$ in the CMS detector based at the Large Hadron Collider of the CERN laboratory.
 
-For these studies the data of the LHC Run 2
+%For these studies the data of the LHC Run 2
 
@@
 various properties like spin, parity and the coupling strength parameters of Higgs boson to fermions and bosons. The main production mode of Higgs boson at LHC is 
-gluon gluon fusion (ggF). As bosons like gluons and photons are massless, they do not interact directly with the Higgs boson 
-and processes like ggF or Higgs boson decay to pair of photons are not possible at tree level and can only proceed via loop 
-diagrams which involve $W^{\pm}$ boson, top quark or bottom quark in the loop. The Higgs boson can also decay to other particles and these decay 
-channels have different branching ratios which are computed using the partial decay widths. Higgs boson can decay to a pair of $W^{\pm}$ bosons, Z bosons, photons, bottom quarks, 
+gluon gluon fusion (ggF). Higgs boson can decay to a pair of $W^{\pm}$ bosons, Z bosons, photons, bottom quarks, 
 muons and electrons.
@@
 The production cross section and branching ratios of various decay channels of Higgs boson are shown in Figure 3.
+Figure 3 also show the main decays channels by the SM.
 
@@
 	\centering
-	\includegraphics[width=\columnwidth]{./pg.png}
-	\caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
+	\includegraphics[width=\columnwidth]{./production_mode.png}
+	\caption{Important production processes of Standard model Higgs boson ggF, VBF, VH in proton collisions.}
 	\label{figure 2}
@@
 The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large 
-number of free-parameters and the fine tuning related to these parameters suggest new physics beyond SM as mentioned below.
-\begin{itemize}
-\item{Fine structure constant $\alpha$},
-\item{Weinberg angle or the weak mixing angle $\theta_W$},
-\item{The coupling constant of strong interaction $\alpha_s$},
-\item{Electroweak symmetry breaking energy scale v},
-\item{ Higgs potential self coupling $\lambda$ or the Higgs mass $m_H$},
-\item{Three weak mixing angles and the CP-violating phase $\delta$ of the CKM matrix which tells us how quarks of different flavor mix with each other},
-\item{Nine yukawa couplings $y_i$ (i = 1 to 9) which determine the mass of nine charged fermions}.
-\end{itemize}
- The fine 
-tunings related to the Higgs 
-mass and the free parameters in SM suggests new physics beyond Standard model (BSM). There are lot of specific 
-BSM theories and most of these 
-models involve new heavy particles. In order to identify which new physics lies beyond the 
-electroweak (EW) scale, the new parameters 
-of such theories may be constrained by the actual low energy experiments.
-
-There is another approach immitating 
-Fermi's treatment of beta decay 
-which consists of considering the SM as the first order approximation of the actual theory 
-and by completing it with a series 
-of higher dimensional operators. When the electroweak symmetry breaking takes place well 
-below the mass of the new particles, 
-the BSM physics is taken into account at the EW scale and below by adding higher dimensional 
-operators to the SM Lagrangian. 
-They are built out of SM fields and supposed to be invariant under its gauge group which is $SU(3)_C \times SU(2)_L \times U(1)_Y$.
-%Those 
-%operators are the low-energy residue 
-%of the high energy theory. This approach does not pretend to guess the complete high-energy 
-%model and it is based solely on 
-%the symmetry of the  theory. The operators are general and the only model dependence is 
-%encoded in the size of the operator
-%coefficients, which is to be set from experiments. The Higgs boson and fermions (quarks and leptons) coupling will deviate from the standard 
-%model predictions if these higher 
-%dimensional operators are present in low energy effective SM theory. We can consider 
-%anomalous Higgs and Higgs-gauge effective 
-%dimension 6 operators like $-\frac{1}{3}(\phi^{\dagger}\phi)^3$, $\frac{1}{2} \partial_{\mu} 
-%(\phi^{\dagger} \phi) 
-%\partial^{\mu}(\phi^{\dagger} \phi)$ and $(\phi^{\dagger} \phi)(D_{\mu} \phi)^{\dagger} 
-%(D^{\mu} \phi)$ to calculate the 
-%deviation of Higgs boson-fermion couplings from SM. The first operator $-\frac{1}{3}(\phi^{\dagg%er}\phi)^3$ shift the minimum of 
-%the Higgs potential. Also as there 
-%will be rescaling of the Higgs field due to the introduction of these operators in the 
-%potential term, Higgs-fermion (quarks 
-%and leptons) couplings will be modified.
-%The yukawa coupling of top quark with Higgs boson will be modified due to the presence of such higher dimensional operators.
-
-\iffalse
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=\columnwidth]{./cms.png}
-	\caption{Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
-	\label{figure 4}
-\end{figure}
-\fi
-
-\iffalse
-The production of Higgs boson in association with single top quark is one of the rare Higgs 
-boson production mode \cite{sirunyan2019search}. As the top 
-quark is the heaviest fundamental particle in the standard model, due to its large mass, the 
-top quark decay before 
-hardronization which allow the possibility to reconstruct top quark from its decay products 
-unlike the lighter quarks which 
-undergo hardronization and are seen as bundles of particles in detector called jets. The most 
-probable decay of the top quark is 
-into bottom (b) quark and $W^{\pm}$ boson \cite{{Tanabashi:2018oca}}. Using b-jet tagging algorithms, the jet originating from 
-b-quark can be reconstructed to 
-identity the top quark. In SM, the couplings of the Higgs boson to fermions (quarks and leptons) known as Yukawa couplings are proportional to the mass 
-of the fermions. Thus heavy quarks like top, bottom and charm couple strongly to Higgs boson 
-which means that out of all known 
-quarks, top quark couple most strongly to the Higgs boson. So, it has a large value of Yukawa 
-coupling $y_t$ \cite{Aad_2016}. That is why the 
-Yukawa coupling of the top quark with the Higgs boson $y_t$ has lot of importance as any 
-deviation from standard model prediction might give an indication of new physics. The two 
-processes at LHC which will allow us to directly probe the Yukawa 
-coupling between Higgs boson and top quark are Higgs boson production in association with top 
-quark pair ($t\bar{t}H$) via 
-strong interaction and the production of single top quark with a Higgs boson (tH). As tH 
-occur via electroweak interaction, it 
-is more rare than t$\bar{t}$H production \cite{Sirunyan:2018ygk}. The Higgs boson in the tH channel can be radiated 
-off by a $W^{\pm}$ boson or by a top quark as shown in Figure 4.
-
-These two processes in standard model have destructive interference which allow us to 
-probe the relative sign between 
-the coupling of top quark with Higgs boson $y_t$ and the coupling of $W^{\pm}$ boson to the Higgs 
-boson $g_{HWW}$ \cite{Sirunyan:2018lzm}. If the Yukawa coupling between top quark and Higgs boson $y_t$ deviate from the SM 
-prediction or even if $y_t$ has a negative sign, both would cause a strong increase in the tH 
-production cross section which is a special property of tH production channel making it an 
-interesting production channel to probe using LHC 2016, 2017 and 2018 data \cite{farina2013lifting}. The coupling 
-strength modifier $\kappa_t$ is defined as $\kappa_t = \frac{y_t}{y^{SM}_t}$ which will tell 
-us the deviation of $y_t$ from the SM prediction.
-
-The LHC is sensitive to an anomalous Higgs coupling to the top quark in the Higgs boson-top quark associated production mode. 
-The anomalous coupling will arise when we add interaction terms (dimension 6 operators in effective SM theory) in the Higgs potential.
-As there is strong destructive inteference in the t-channel for the standard model  couplings, this production mode is sensitive to both the sign and the magnitude of any coupling beyond the SM between Higgs  boson and top quark induced by higher dimensional operators in effective beyond SM theory \cite{sirunyan2019search}.
-\fi
+number of free-parameters and the fine tuning related to these parameters suggest new physics beyond SM. There are lot of specific 
+BSM theories and most of these models involve new heavy particles. In order to identify which new physics lies beyond the 
+electroweak (EW) scale, the new parameters  of such theories may be constrained by the actual low energy experiments. \\ 
+%The fine tunings related to the Higgs mass and the free parameters in SM suggests new physics beyond Standard model (BSM).
 
@@
 It is designed to detect particles known as muons very accurately.
+In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
+So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the Standard Model (SM).
+\\
+
 The CMS detector has the form of a cylindrical onion, with several concentric layers of components.
@@
 The muons are detected by special subdetectors placed outside to detect them once they have crossed the solenoid as shown in Figure~\ref{figure5}.
-In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
-So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the Standard Model (SM).
 
@@
   \end{figure}
-  \clearpage
 
@@
 LHC during the first run in 2011 and 2012 reached a peak instantaneous luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
+The luminosity delivered by the LHC during Run 1 (2011-2012),  Run 2 (2015-2018), and the expected luminosity for Run 3 and HL-LHC is shown in Figure 5.
+
+\clearpage
+\iffalse
 The LHC will deliver about 300 $fb^{-1}$ by 2024 \cite{collaborations2019report}.
@@
 In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  place in parallel during one shutdown, at around 2023-25 (LS3), with some of the modification anticipated in 2019-2020 (LS2).
+
 This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ by the year 2036 as shown in Figure~\ref{figure6}.
@@
 Higgs boson production in association with single top quark has been studied to derive constraints on the magnitude and relative sign of Higgs boson couplings to top quarks and vector bosons.
+
 Constaints on $\kappa_t$ can be derived using a likelihood ratio scan of $L(\kappa_t)/L(\hat{\kappa_t})$ where $\hat{\kappa_t}$ is the best fit value of $\kappa_t$ as shown in Figure~\ref{figureKt} \cite{Sirunyan:2018lzm}.
@@
 The data slightly favor positive value of top quark yukawa coupling for SM Higgs boson and excludes ranges outside the intervals [-0.9,-0.5] and [1.0,2.1] times $y^{SM}_t$ at the 95 $\%$ confidence level.
+
 \newpage
@@
 \newpage
+\fi
 \section{PROPOSAL}
@@
 
-\onehalfspacing In this project, it is proposed to search for the decays of the Higgs boson to pairs of $J/\psi$ or $upsilon$ in the CMS detector based at the Large Hadron Collider of the CERN laboratory.
+\onehalfspacing In this project, it is proposed to search for the decays of the Higgs boson to pairs of $J/\psi$ or $\Upsilon$ in the CMS detector based at the Large Hadron Collider of the CERN laboratory.
 For these studies the data of the LHC Run 2 (2015-2018) will be used corresponding to an integrated luminosity of about 150 fb$^{-1}$, this is 4 times larger than the dataset used for current results.
-An observation of such decay  with this sample would indicate the presence of physics beyond the standard model.
-It is also expected to estimate projections of the sensitivity to the High Luminosity phase of the LHC (HL-LHC) (2026-2036) which will accumulate up to 100 times the data used for current measurements.
+Previously CMS has carried out studies with the data from 2017 \cite{2019134811} corresponding to 37.5 fb$^{-1}$ and ATLAS in 2015 \cit{Aad_2015}.
+
+%It is also expected to estimate projections of the sensitivity to the High Luminosity phase of the LHC (HL-LHC) (2026-2036) which will accumulate up to 100 times the data used for current measurements.
 
@@
 
-%- motivation, tH production crossection, sign of $k_t$, search for BSM, ..
+\onehalfspacing There is currently a great enigma in physics since we know that ordinary matter comprises only $5\%$ of the universe, another $27\%$ includes Dark matter and the rest $68\%$ is Dark energy.
+Understanding the production of the Higgs boson, as well as its decays are an important part of the physics program of CERN laboratory experiments to verify the Standard Model and look for new particles.
+Through this project we will investigate the decay of the Higgs boson to pairs of $J/\psi$ or $\Upsilon$ in proton-proton collisions with the CMS experiment at the LHC.
+An observation of such decay  with this sample would indicate the presence of physics beyond the standard model.
+The decay to pairs of $J/\psi$ or $\Upsilon$ has not been observed so far.
+An observation of such decay  with this sample would indicate the presence of physics beyond the standard model.
 
@@
 \fi
-
-\onehalfspacing There is currently a great enigma in physics since we know that ordinary matter comprises only $5\%$ of the universe, another $27\%$ includes Dark matter and the rest $68\%$ is Dark energy.
-Understanding the production of the Higgs boson, as well as its decays are an important part of the physics program of CERN laboratory experiments to verify the Standard Model and look for new particles.
-Through this project we will investigate the decay of the Higgs boson to $J/\psi$ in proton-proton collisions with the CMS experiment at the LHC.
-The decay to $J/\psi$ has not been observed so far.
 
@@
 
-\onehalfspacing Studies about the decay of the Higgs boson production channel have already started within the CMS and ATLAS collaboration and publications are based on data from the 2011-2012 run and some data from the second run of 2015-2016.
-In these results, there was no evidence of signal and upper limits were set on the production cross-section.
-The current results combine three types of searches: H$\rightarrow WW/ZZ/\tau\tau \rightarrow$leptons, H$\rightarrow\gamma\gamma$, and H$\rightarrow b\bar{b}$.
-%The most sensitive channel is  with leptons, however this channel is a combination of two sub-channels: two-lepton and three-lepton.
-The currently published result uses 36 fb$^{-1}$ of collision data and obtains an upper limit of 2.04 pb while only 0.077 pb are expected in the SM \cite{sirunyan2019search}, the limit is 26 times larger than the expected value.
-In BSM models, for example with $\kappa_t = -1$,  the expected cross-section increases up to 0.834 pb due to quantum interference effects; in this case also the observed upper limit changes to 0.86 pb at 95$\%$ confidence level, the current data almost rules out this model.
+% Studies about the decay of the Higgs boson have already started within the CMS and ATLAS collaboration and publications are based on data from the 2011-2012 run and some data from the second run of 2015-2016.
+
+\onehalfspacing With the CMS search mentioned above using 2017 data, an upper limit of $1.8 \times 10^{-3}$ was obtained in the $J/\psi$ pair while in the $\Upsilon$ pair channel, the limit was $1.4 \times 10^{-3}$.
 
@@
 A factor of 4 increase in number of collision events will improve the limits by a factor of approximately 2 due to the nature of statistical uncertainties.
-This mean that the limit for the SM case will improve to about 13 times the expected cross-section, while for the modified model ($\kappa_t = -1$) we expect to be excluded.
+In case of observing a signal with this data this would mean evidence of physics beyond the standard model.
 
+\iffalse
 Additionally, in subsequent phases of the LHC (2021-2023 and 2026-2038) the amount of data will increase by a factor of up to 100, which implies the upper limit for the SM case will reduce to about 2.6 times the expected cross-section.
@@
 
-\iffalse
+%these were the results
+%The currently published result \cite{} uses 37.5 fb$^{-1}$ of collision data and obtains 
+%CMS collaboration has perfomed
+%pairexpected in the SM \cite{sirunyan2019search}, the limit is 26 times larger than the expected value.
+%The most sensitive channel is  with leptons, however this channel is a combination of two sub-channels: two-lepton and three-lepton.
+%The currently published result uses 36 fb$^{-1}$ of collision data and obtains an upper limit of 2.04 pb while only 0.077 pb are expected in the SM \cite{sirunyan2019search}, the limit is 26 times larger than the expected value.
+%In BSM models, for example with $\kappa_t = -1$,  the expected cross-section increases up to 0.834 pb due to quantum interference effects; in this case also the observed upper limit changes to 0.86 pb at 95$\%$ confidence level, the current data almost rules out this model.
+
+%This mean that the limit for the SM case will improve to about 13 times the expected cross-section, while for the modified model ($\kappa_t = -1$) we expect to be excluded.
 In this search the reconstruction methods do not allow to separate $t$H from $t\bar{t}H$ production because the cross-section of $t\bar{t}H$ is much larger than that of tH and some events pass the selections designed for tH.
@@
 
-In order to complete a journal publication of a  
-%measurement of tH production using one of these channels, several aspects  must be worked on:
+In order to complete a journal publication of this search the following are need it:
+%production using one of these channels, several aspects  must be worked on:
+%of these search
 \begin{itemize}
@@
 \item Implementation of event reconstruction and selection algorithms which select high quality signal events and reduce the background events to a minimum.
-\item Studies of lepton and jet identification algorithms which improve the background rejection.
-\item Due to the small signal over background ratio, a multi-variate algorithm is employed which combines different event variables and exploits the correlations to construct a final discriminant.
+\item Studies of lepton algorithms which improve the background rejection.
+\item Due to the small signal over background ratio, a multi-variate algorithm is maybe employed which combines different event variables and exploits the correlations to construct a final discriminant.
 This algorithm must be trained using simulated signal and background events.
 \item A model for the observed data must be constructed from the known background processes. 
-These processes are normally simulated individually and then summed together with the signal to construct the final statistical model.
+%These processes are normally simulated individually and then summed together with the signal to construct the final statistical model.
+\item Reconstruction of $J/\psi$ and $\Upsilon$ with two muons \cite{Khachatryan_2014,Sirunyan_2018}.
 \item An algorithm is developed that adjusts the model to the observed data distribution and incorporates several systematic uncertainties due to differences between simulation and real data.
 \item The signal strength observed from the statistical analysis must be interpreted as evidence of a signal or in the absence as a limit.
-Further analysis is required to place constraints on paramater space of BSM models.
+%Further analysis is required to place constraints on paramater space of BSM models.
 \end{itemize}
@@
 In addition to the above objectives, members of the CMS collaboration are expected to participate in the detector operation and upgrade activities (or service work).
-During shut-down periods, these activities include testing and installation of new detectors.
-During regular data-taking periods, activities include monitoring the data acquisition systems and data quality through comparisons of new data and old data.
-In addition to the data analysis plans described before, another objective is to contribute in one of the developments of the CMS detector to  prepare for the HL-LHC phase.
+During shut-down periods, these activities include testing and installation of new detectors.The luminosity data of run 3 will be studied and a luminosity measurement is planned for run 3.
+For run 2 we have these results \cite{CMS-PAS-LUM-17-004,CMS-PAS-LUM-18-002}.
+
+%During regular data-taking periods, activities include monitoring the data acquisition systems and data quality through comparisons of new data and old data.
+%In addition to the data analysis plans described before, another objective is to contribute in one of the developments of the CMS detector to  prepare for the HL-LHC phase.
 %
 
-Finally, the results of this project will be presented at national or international conferences and a publication in a scientific journal will be accomplished.
+%Finally, the results of this project will be presented at national or international conferences and a publication in a scientific journal will be accomplished.
 
@@
 
-\onehalfspacing The methods for a measurement of the 
+%\onehalfspacing The methods for a measurement of the 
 %coupling of the Higgs boson and the top quark in proton collisions are extensive and require several stages.
 
-Accelerating the protons to extremely high energies and causing them to collide at high rates in order to produce rare but interesting events is the work of a separate accelerator group.
+\onehalfspacing Accelerating the protons to extremely high energies and causing them to collide at high rates in order to produce rare but interesting events is the work of a separate accelerator group.
 However, the members of the CMS collaboration must monitor the quality and rate of proton collisions at the interaction point at the center of the detector in order to collect a high quality dataset which can be stored for many years to do analysis.
@@
 
+Luminosity is one of the most omportant parameter for a particle accelerator.
+It is the measure of number of proton-proton collisions occurring in unit centimetre square area per second.
+The installation of the CMS Phase-1 pixel detector took place during the extended year-end technical stop of the LHC in 2016/2017.
+The CMS Phase-1 pixel detector consists of four concentric barrel layers anf three disks.
+The CMS Phase-1 pixel detector is built from 1856 segmented silicon sensor modules,
+where 1184 modules are used in the barrel pixel detector (BPIX) and 672 modules are used for the forward disks (FPIX).
+Each module consists of a sensor with 160x416 pixels connected to 16 readout chips (ROCs).One of the systems used for measuring luminosity at CMS is a technique called Pixel Cluster Counting (PCC) method.
+The PCC method uses the rate of pixel clusters in the CMS pixel detector to provide an luminosity measurement.
+
 A new data structure with the above particle reconstruction defines new  datasets (\textsc{CMSSW}) stored in computing centers around the world which are available to students and scientists at all research institutions.
@@
 %In the search for tH events using the dimuon channel the following event selections are applied:
+\iffalse
 \begin{itemize}
@@
 \end{itemize}
+\fi
 
-\textsc{Root} is a \textsc{c++} based software that allows visualization of event distributions and variable correlations.
+%\textsc{Root} is a \textsc{c++} based software that allows visualization of event distributions and variable correlations.
 Further optimization of the event selections is performed by considering the different processes which contribute to the background.
@@
 A typical algorithm used is the Boosted Decision Tree~\cite{hoecker2007tmva}, which takes as input several event variables related to the signal topology.
-In the previous search for tH these variables included:
-\begin{itemize}
-\item
-\item
-\item
-\item
-\end{itemize}
 The multivariate algorithm takes into account the correlations between the variables and combines the information into a single discriminant.
 
-Due to the maximum separation of the signal and background in the multivariate discriminant, this distribution is used for the statisical analysis of the events.
 A fit is applied using the \textsc{RooFit} software package~\cite{verkerke2008roofit} which constructs a model for the data consisting of the sum of the backgrounds and the signal simulations.
-A likelihood function is constructed from a Poisson function using the expected and measured number of events.
 Systematic uncertainties are incorporated as nuisance parameters using gaussian probability functions, these account for uncertaintes in the normalization and shapes of the background.
 The signal strength extracted from this fit determines if there is any evidence for a signal.
-In the absence of a signal an upper limit is placed on the signal strength using the likelihood function and subsequently translated into a limit in the 
-%tH production cross section and the Higgs coupling parameters.
+In the absence of a signal an upper limit is placed on the signal strength using the likelihood function and subsequently translated into a limit.
 
@@
 \item The student will become part of an international collaboration.
-\item A leading contribution in one of the search channels for the tH process using the data from the Run II of the LHC, resulting in a publication in a scientific journal.
-\item Participation in the CMS detector Phase II upgrade through development and possible installation of particle detectors possibly resulting in a technical report.
+\item A leading contribution in one of the search for decays of the Higgs boson into pairs of $J/\psi$ or $\Upsilon$ using the data from the Run II of the LHC, resulting in a publication in a scientific journal.
+%\item Participation in the CMS detector Phase II upgrade through development and possible installation of particle detectors possibly resulting in a technical report.
+\item Improve limits on the branching fraction of these decays channels.
+\item Luminosity study for RUN3 data.
 \item A presentation of a poster or a talk in one of the national conferences of the Division of Paticles and Fields of the Mexican Society of Physics or a presentation of a poster or a talk in an international physics conference.

### 2022-11-13 project_Antonio/paper.tex
Add files via upload

@@
 For these studies the data of the LHC Run 2 (2015-2018) will be used corresponding to an integrated luminosity of about 150 fb$^{-1}$, this is 4 times larger than the dataset used for current results.
-Previously CMS has carried out studies with the data from 2017 \cite{2019134811} corresponding to 37.5 fb$^{-1}$ and ATLAS in 2015 \cit{Aad_2015}.
+Previously CMS has carried out studies with the data from 2017 ~\cite{2019134811} corresponding to 37.5 fb$^{-1}$ and ATLAS in 2015 ~\cite{Aad_2015} corresponding to 20.3 fb$^{-1}$.
 
@@
 The decay to pairs of $J/\psi$ or $\Upsilon$ has not been observed so far.
-An observation of such decay  with this sample would indicate the presence of physics beyond the standard model.
 
+%An observation of such decay  with this sample would indicate the presence of physics beyond the standard model. 
 \iffalse
@@
 \onehalfspacing With the CMS search mentioned above using 2017 data, an upper limit of $1.8 \times 10^{-3}$ was obtained in the $J/\psi$ pair while in the $\Upsilon$ pair channel, the limit was $1.4 \times 10^{-3}$.
-
 With this project we propose to incorporate the full Run 2 dataset corresponding to 150 fb$^{-1}$.
 A factor of 4 increase in number of collision events will improve the limits by a factor of approximately 2 due to the nature of statistical uncertainties.
-In case of observing a signal with this data this would mean evidence of physics beyond the standard model.
 
+%In case of observing a signal with this data this would mean evidence of physics beyond the standard model.
 \iffalse
@@
 %These processes are normally simulated individually and then summed together with the signal to construct the final statistical model.
-\item Reconstruction of $J/\psi$ and $\Upsilon$ with two muons \cite{Khachatryan_2014,Sirunyan_2018}.
+\item Reconstruction of $J/\psi$ and $\Upsilon$ with two muons ~\cite{Khachatryan_2014,Sirunyan_2018}.
 \item An algorithm is developed that adjusts the model to the observed data distribution and incorporates several systematic uncertainties due to differences between simulation and real data.
@@
 In addition to the above objectives, members of the CMS collaboration are expected to participate in the detector operation and upgrade activities (or service work).
-During shut-down periods, these activities include testing and installation of new detectors.The luminosity data of run 3 will be studied and a luminosity measurement is planned for run 3.
-For run 2 we have these results \cite{CMS-PAS-LUM-17-004,CMS-PAS-LUM-18-002}.
+During shut-down periods, these activities include testing and installation of new detectors.The luminosity data of run 3 will be studied and a luminosity measurement is planned for Run 3.
+For Run 2 we have these results ~\cite{CMS_PAS_LUM_17_004,CMS_PAS_LUM_18_002}.
 

### 2022-11-14 project_Antonio/paper.tex
Add files via upload

@@
 For these studies the data of the LHC Run 2 (2015-2018) will be used corresponding to an integrated luminosity of about 150 fb$^{-1}$, this is 4 times larger than the dataset used for current results.
-Previously CMS has carried out studies with the data from 2017 ~\cite{2019134811} corresponding to 37.5 fb$^{-1}$ and ATLAS in 2015 ~\cite{Aad_2015} corresponding to 20.3 fb$^{-1}$.
+Previously CMS has carried out studies with the data from 2017 ~\cite{2019134811} corresponding to 37.5 fb$^{-1}$ and ATLAS in 2015 ~\cite{PhysRevLett.114.121801} corresponding to 20.3 fb$^{-1}$.
 

### 2022-11-14 project_Antonio/paper.tex
Add files via upload

@@
   \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
-  \SubItem{ Readings on SM and tH literature}
+  \SubItem{ Readings on SM and $J/\psi$ and $\Upsilon$ literature}
   \SubItem{ Computing accounts at CERN and Fermilab}
-  \SubItem{ Studies of the tH event selections}
+  \SubItem{ Studies of the $J/\psi$ and $\Upsilon$ event selections}
   \SubItem{ CMS service work for authorship}
@@
   \SubItem{ Course II on particle physics and/or particle detection.}
-  \SubItem{ Studies of the tH event selections}
+  \SubItem{ Studies of the $J/\psi$ and $\Upsilon$ event selections}
   \SubItem{ Development of a Multivariate algorithm for the event selections}
@@
   \SubItem{ CMS service work for authorship}
-  \SubItem{ Studies of the tH event selections}
+  \SubItem{ Studies of the $J/\psi$ and $\Upsilon$ event selections}
   \SubItem{ Development of a Multivariate algorithm for the event selections}
-  \SubItem{ Studies of the tH background processes}
+  \SubItem{ Studies of the $J/\psi$ and $\Upsilon$ background processes}
   \SubItem{ Development of the statistical model and signal extraction}
@@
 \item {\bf Semester 5 (2024-2)}:
-  \SubItem{ Studies of the tH event selections}
+  \SubItem{ Studies of the $J/\psi$ and $\Upsilon$ event selections}
   \SubItem{ Development of a Multivariate algorithm for the event selections}
-  \SubItem{ Studies of the tH background processes}
+  \SubItem{ Studies of the $J/\psi$ and $\Upsilon$ background processes}
   \SubItem{ Development of the statistical model and signal extraction}

### 2022-11-14 tesis_Hedwin/compile.sh
compile scripts

@@ -1,12 +1,13 @@
 #!/bin/bash
 
-thesis="paper";
+thesis="thesis";
 
 if [ $1 = "clean" ]
 then
 	echo "Cleaning please wait ..."
 	rm -f *~
 	rm -rf *.aux
+	rm -rf ./*/*.aux
 	rm -rf *.bbl
 	rm -rf *.blg
 	rm -rf *.d
@@ -27,7 +28,6 @@ then
 	rm -rf $thesis.spl
 	rm -rf *#* 
 	echo "Cleaning complete!"
-
 else
 	echo "Compiling ...!"
 	pdflatex -interaction=nonstopmode $thesis.tex
@@ -39,5 +39,4 @@ else
 	makeindex $thesis.nlo -s nomencl.ist -o $thesis.nls
 	pdflatex -interaction=nonstopmode $thesis.tex
 	echo "Success!"
-
 fi

### 2022-11-14 project_Antonio/paper.tex
antonio proyecto

@@
 \def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
-\def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
+\def\Director{Dr. Jos\'{e} Feliciano BEN\'{I}TEZ RUBIO}
 \def\ProjectTitle{B\'usqueda de part\'iculas de Higgs con modelos de f\'sica m\'as all\'a del Modelo Est\'andar y medici\'on de la luminosidad usando el m\'etodo de Pixel Cluster Counting en el experimento CMS del CERN}
@@
 \hspace{2pt}
-\vfill
 
@@
 
-\iffalse
-\onehalfspacing This research project proposes to study the unobserved production channel of the Higgs boson in associated with a single top quark (tH) using Higgs boson decay to multilepton final state.
+\onehalfspacing This research project proposes to study the unobserved decays modes of the Higgs boson into pairs of $J/\psi$ or $\Upsilon$.
 The dataset collected during the Run II (2015-2018) of Large Hadron Collider (LHC) will be used corresponding to an integrated luminosity of 150 $fb^{-1}$.
-Increasing the collider luminosity is expected to increase the number of event for this Higgs boson production mode.
-The measurement of this production mode has ramifications for other measurements related to coupling parameter $y_t$ of the top quark and the Higgs boson which is part of the physics program of the international CMS and ATLAS collaborations.
-Previous measurements using dataset with an integrated luminosity 36 $fb^{-1}$ has put an upper limit of 2.04 pb on the production cross section which is far from standard model predicted value of 0.077 pb.
-We plan to obtain more stringent upper limits on the production cross section and get constraints on the Higgs top quark coupling parameter $y_t$.
-\par
-\fi
-
-\onehalfspacing This research project proposes to study the unobserved decays modes of the Higgs boson.
-\iffalse associated with a single top quark (tH) using Higgs boson decay to multilepton final state \fi The dataset collected during the Run II (2015-2018) of Large Hadron Collider (LHC) will be used corresponding to an integrated luminosity of 150 $fb^{-1}$.
-Serches for decays of the Higgs boson into pairs of $J/\psi$ or $\Upsilon$.
-
-%Increasing the collider luminosity is expected to increase the number of event for this Higgs boson production mode.
-The measurement of this production mode has ramifications for other measurements related to coupling parameter $y_t$ of the top quark and the Higgs boson which is part of the physics program of the international CMS and ATLAS collaborations.
-Previous measurements using dataset with an integrated luminosity 36 $fb^{-1}$ has put an upper limit of 2.04 pb on the production cross section which is far from standard model predicted value of 0.077 pb.
-We plan to obtain more stringent upper limits on the production cross section and get constraints on the Higgs top quark coupling parameter $y_t$.
-\par
-
-%\onehalfspacing In this project, it is proposed to search for the decays of the Higgs boson to pairs of $J/\psi$ or $upsilon$ in the CMS detector based at the Large Hadron Collider of the CERN laboratory.
-
-%For these studies the data of the LHC Run 2
+Previous searches for these decays were done with only 37 $fb^{-1}$, the increased luminosity and improved analysis strategy will provide more stringent limits for these decays and more sensitivity to physics beyond the Standard Model.
 
@@
 
-\onehalfspacing The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
+\onehalfspacing The Standard Model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
 particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the 
@@
 bosonic sector and fermionic sector. Bosonic sector contain particles called bosons which mediate the fundamental forces of 
-nature and the fermionic sector contain particles called fermions which make up all the matter in our universe. SM has three 
+nature and the fermionic sector contain particles which make up all the matter in our universe. SM has three 
 generations of matter (fermions) particles. The first generation of fermions consists of up (u) quark, down (d) quark, electron 
@@
 bosons like gluon, photon, $W^{\pm}$, $Z^0$ which mediate strong nuclear force, electromagnetic force and weak nuclear force respectively.
-There is one more particle in the standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}.
+There is one more particle in the standard model called the Higgs boson which gives mass to SM particles via electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}.
 All the standard model particles are shown in Figure 1.
@@
 
+There are various production modes of Higgs boson like the gluon gluon fusion (ggF), vector boson fusion (VBF), Higgs 
+production in association with vector boson (VH, V = $W^{\pm}$ or Z), Higgs production with top quark and top anti-quark ($t\bar{t}H$) and Higgs 
+production in association with a single top quark and a quark jet (tHq). Each production channel has its own importance to probe the 
+various properties like spin, parity and the coupling strength parameters of Higgs boson to fermions and bosons.
+The main production mode of Higgs boson at LHC is gluon gluon fusion (ggF).
+Higgs boson can decay to a pair of $W^{\pm}$ bosons, Z bosons, photons, bottom , charm, or strange quarks, also to taus and muons .
+The important SM Higgs Boson production modes are shown in Figure 2. The production cross section and branching ratios of various decay channels of Higgs boson are shown in Figure 3.
+Figure 3 also show the main decays channels by the SM.
+
+\clearpage
 \begin{figure}[H]
@@
 
-% \newpage
-
-There are various production modes of Higgs boson like the gluon gluon fusion (ggF), vector boson fusion (VBF), Higgs 
-production in association with vector boson (VH, V = $W^{\pm}$ or Z), Higgs production with top quark and top anti-quark ($t\bar{t}H$) and Higgs 
-production in association with a single top quark and a quark jet (tHq). Each production channel has its own importance to probe the 
-various properties like spin, parity and the coupling strength parameters of Higgs boson to fermions and bosons. The main production mode of Higgs boson at LHC is 
-gluon gluon fusion (ggF). Higgs boson can decay to a pair of $W^{\pm}$ bosons, Z bosons, photons, bottom quarks, 
-muons and electrons.
-Higgs boson can also decay to Z boson and a photon.
-The important SM Higgs Boson production modes are shown in Figure 2.
-The production cross section and branching ratios of various decay channels of Higgs boson are shown in Figure 3.
-Figure 3 also show the main decays channels by the SM.
-
-%\afterpage{
 \begin{figure}[H]
@@
 \end{figure}
+
 \clearpage
@@
 
-%\afterpage{
+LHC during the first run in 2011 and 2012 reached a peak instantaneous luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
+The luminosity delivered by the LHC during Run 1 (2011-2012),  Run 2 (2015-2018), and the expected luminosity for Run 3 and HL-LHC is shown in Figure 5.
+
+\clearpage
   \begin{figure}[H]
@@
     \centering
-    \includegraphics[width=0.9\columnwidth]{./lum6.png}
+    \includegraphics[width=0.9\columnwidth]{./HLLHCLumi.png}
     \caption{Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities.
@@
 
-%\clearpage
-
-LHC during the first run in 2011 and 2012 reached a peak instantaneous luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
-The luminosity delivered by the LHC during Run 1 (2011-2012),  Run 2 (2015-2018), and the expected luminosity for Run 3 and HL-LHC is shown in Figure 5.
-
 \clearpage
-\iffalse
-The LHC will deliver about 300 $fb^{-1}$ by 2024 \cite{collaborations2019report}.
-The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles.
-In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  place in parallel during one shutdown, at around 2023-25 (LS3), with some of the modification anticipated in 2019-2020 (LS2).
-
-This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ by the year 2036 as shown in Figure~\ref{figure6}.
-Figure~\ref{figureKappas} shows a summary of the current measurements of the Higgs coupling parameters with the LHC Run 1 dataset (2011,2012)  using ggF, VBF, VH, and ${t\bar{t}H}$ production modes \cite{Tanabashi:2018oca}.
-Higgs boson production in association with single top quark has been studied to derive constraints on the magnitude and relative sign of Higgs boson couplings to top quarks and vector bosons.
-
-Constaints on $\kappa_t$ can be derived using a likelihood ratio scan of $L(\kappa_t)/L(\hat{\kappa_t})$ where $\hat{\kappa_t}$ is the best fit value of $\kappa_t$ as shown in Figure~\ref{figureKt} \cite{Sirunyan:2018lzm}.
-Multilepton final states like ee, $\mu\mu$ and $e\mu$ and final states with single lepton with a pair of bottom quarks were combined with Higgs decay to two photons to get the final result.
-The data slightly favor positive value of top quark yukawa coupling for SM Higgs boson and excludes ranges outside the intervals [-0.9,-0.5] and [1.0,2.1] times $y^{SM}_t$ at the 95 $\%$ confidence level.
-
-\newpage
-%\afterpage{
-  \begin{figure}[H]
-    \centering
-    \includegraphics[scale=0.4]{./couplings.png}
-    \caption{ATLAS-CMS combined measurements of coupling strength modifiers \cite{Tanabashi:2018oca}.}
-    \label{figureKappas}
-  \end{figure}
-
-  \begin{figure}[H]
-    \centering
-    \includegraphics[width=0.4 \columnwidth]{./cms13.png}
-    \caption{Scan of -2 $\Delta$ ln(L) versus $\kappa_t$ for the 2016 LHC data (black line) and the individual channels (blue, red, and green), compared to Asimov data sets corresponding to the SM expectations (dashed lines) \cite{sirunyan2019search}.}
-    \label{figureKt}
-  \end{figure}
-
-\newpage
-\fi
 \section{PROPOSAL}
-
-\iffalse
-\onehalfspacing In this project, it is proposed to search for the production of Higgs boson associated with a single top quark in the CMS detector based at the Large Hadron Collider of the CERN laboratory.
-It is proposed to study the sensitivity with the current data in the channel where the events are identified with two muons of the same sign, electron muon or with three leptons of electron or muon type.
-Leptons of tau type are not considered due to complications in their identification in the detector.
-\fi
-
 \onehalfspacing In this project, it is proposed to search for the decays of the Higgs boson to pairs of $J/\psi$ or $\Upsilon$ in the CMS detector based at the Large Hadron Collider of the CERN laboratory.
 For these studies the data of the LHC Run 2 (2015-2018) will be used corresponding to an integrated luminosity of about 150 fb$^{-1}$, this is 4 times larger than the dataset used for current results.
-Previously CMS has carried out studies with the data from 2017 ~\cite{2019134811} corresponding to 37.5 fb$^{-1}$ and ATLAS in 2015 ~\cite{PhysRevLett.114.121801} corresponding to 20.3 fb$^{-1}$.
+Previously CMS has carried out studies with the data from 2017 ~\cite{2019134811} corresponding to 37.5 fb$^{-1}$ and ATLAS in 2012 ~\cite{PhysRevLett.114.121801} corresponding to 20.3 fb$^{-1}$.
 
-%It is also expected to estimate projections of the sensitivity to the High Luminosity phase of the LHC (HL-LHC) (2026-2036) which will accumulate up to 100 times the data used for current measurements.
-
-%It is proposed to study the sensitivity with the current data in the channel where the events are identified with two muons of the same sign, electron muon or with three leptons of electron or muon type.
-Leptons of tau type are not considered due to complications in their identification in the detector.
+\onehalfspacing We also propose to work on the luminosity measurement for the new LHC Run 3 which has just started in the year 2022.
+The measurement of the integrated luminosity is essential for many physics studies at CMS.
 
 \section{GENERAL OBJECTIVE}
-
 \onehalfspacing There is currently a great enigma in physics since we know that ordinary matter comprises only $5\%$ of the universe, another $27\%$ includes Dark matter and the rest $68\%$ is Dark energy.
@@
 An observation of such decay  with this sample would indicate the presence of physics beyond the standard model.
-The decay to pairs of $J/\psi$ or $\Upsilon$ has not been observed so far.
-
-%An observation of such decay  with this sample would indicate the presence of physics beyond the standard model. 
-\iffalse
-\onehalfspacing There is currently a great enigma in physics since we know that ordinary matter comprises only $5\%$ of the universe, another $27\%$ includes Dark matter and the rest $68\%$ is Dark energy.
-Understanding the production of the Higgs boson, as well as its decays are an important part of the physics program of CERN laboratory experiments to verify the Standard Model and look for new particles.
-Through this project we will investigate the production of the Higgs boson in association with a single top quark (tH) in proton-proton collisions with the CMS experiment at the LHC.
-The tH  production process has not been observed so far.
-\fi
-
-\iffalse
-The measurement of this process complements other measurements of the yukawa coupling parameter $y_t$ of the top quark and Higgs boson and is a part of the physics program of CMS and ATLAS international collaborations.
-Through these measurements we seek to complete the measurements of the Standard Model parameters to high precision and also to find evidence of deviations in yukawa couplings which point to new particles which may explain current enigmas like the origin of Dark Matter.
-\fi
+The decay to pairs of $J/\psi$ or $\Upsilon$ is expected to be extremely small, below  current detection limitations.
 
 \section{HYPOTHESIS}
-%%  - what we expect to find
-
-% Studies about the decay of the Higgs boson have already started within the CMS and ATLAS collaboration and publications are based on data from the 2011-2012 run and some data from the second run of 2015-2016.
-
 \onehalfspacing With the CMS search mentioned above using 2017 data, an upper limit of $1.8 \times 10^{-3}$ was obtained in the $J/\psi$ pair while in the $\Upsilon$ pair channel, the limit was $1.4 \times 10^{-3}$.
@@
 
-%In case of observing a signal with this data this would mean evidence of physics beyond the standard model.
-\iffalse
-Additionally, in subsequent phases of the LHC (2021-2023 and 2026-2038) the amount of data will increase by a factor of up to 100, which implies the upper limit for the SM case will reduce to about 2.6 times the expected cross-section.
-This implies that even for the HL-LHC it will be difficult to observe the tH production, but at the same time more and more phase space of BSM models will be excluded.
-
-%these were the results
-%The currently published result \cite{} uses 37.5 fb$^{-1}$ of collision data and obtains 
-%CMS collaboration has perfomed
-%pairexpected in the SM \cite{sirunyan2019search}, the limit is 26 times larger than the expected value.
-%The most sensitive channel is  with leptons, however this channel is a combination of two sub-channels: two-lepton and three-lepton.
-%The currently published result uses 36 fb$^{-1}$ of collision data and obtains an upper limit of 2.04 pb while only 0.077 pb are expected in the SM \cite{sirunyan2019search}, the limit is 26 times larger than the expected value.
-%In BSM models, for example with $\kappa_t = -1$,  the expected cross-section increases up to 0.834 pb due to quantum interference effects; in this case also the observed upper limit changes to 0.86 pb at 95$\%$ confidence level, the current data almost rules out this model.
-
-%This mean that the limit for the SM case will improve to about 13 times the expected cross-section, while for the modified model ($\kappa_t = -1$) we expect to be excluded.
-In this search the reconstruction methods do not allow to separate $t$H from $t\bar{t}H$ production because the cross-section of $t\bar{t}H$ is much larger than that of tH and some events pass the selections designed for tH.
-The fraction of tH events over tH + $t\bar{t}H$ is currently only 5$\%$ with the analysis techniques used.
-We expect to improve the analysis techniques using multi-variate techniques, for example boosted decision trees or other algorithms, to improve the identification of signal events over the rest of the backgrounds.
-This will provide additional improvements in the limits and a possible observation of the SM signal as well as stringent exclusions for BSM models.
-\fi
-
-%\newpage
 \section{SPECIFIC OBJECTIVES}
@@
 \onehalfspacing 
-
-\iffalse
-The measurement of the tH production mechanism is a collaborative effort in the LHC experiment due to the various channels that need to be combined.
-This project focuses on the channels with leptons in the final state: two-lepton ($\ell\ell$) or three-lepton ($\ell\ell\ell$).
-The $\ell\ell$ sub-channel uses events with same sign dimuon ($\mu^\pm\mu^\pm$) or electron-muon ($e^\pm\mu^\pm$).
-The $\ell\ell\ell$ sub-channel uses events in the topologies: $\mu\mu\mu$, $\mu\mu e$, $\mu e e$ and $e e e$, where no charge requirements are made.
-The leptons are generated from the decays of the $W$ and $Z$ bosons or $\tau$ leptons from decays of the Higgs or top quarks.
-Furthermore, light-quark and b-quark jets are generated from the initial state collision and from the decay of the top quark, these must be used in the signal identification.
-\fi
-
-In order to complete a journal publication of this search the following are need it:
-%production using one of these channels, several aspects  must be worked on:
-%of these search
+In order to complete a journal publication of this search the following are needed:
 \begin{itemize}
@@
 \item Studies of lepton algorithms which improve the background rejection.
-\item Due to the small signal over background ratio, a multi-variate algorithm is maybe employed which combines different event variables and exploits the correlations to construct a final discriminant.
+\item Reconstruction of $J/\psi$ and $\Upsilon$ with two muons ~\cite{Khachatryan_2014,Sirunyan_2018}.
+\item Due to the small signal over background ratio, a multi-variate algorithm may be employed which combines different event variables and exploits the correlations to construct a final discriminant.
 This algorithm must be trained using simulated signal and background events.
 \item A model for the observed data must be constructed from the known background processes. 
-%These processes are normally simulated individually and then summed together with the signal to construct the final statistical model.
-\item Reconstruction of $J/\psi$ and $\Upsilon$ with two muons ~\cite{Khachatryan_2014,Sirunyan_2018}.
-\item An algorithm is developed that adjusts the model to the observed data distribution and incorporates several systematic uncertainties due to differences between simulation and real data.
-\item The signal strength observed from the statistical analysis must be interpreted as evidence of a signal or in the absence as a limit.
-%Further analysis is required to place constraints on paramater space of BSM models.
+\item An fitting algorithm is developed that adjusts the model to the observed data distribution and incorporates several systematic uncertainties due to differences between simulation and real data.
+The signal strength observed from the statistical analysis must be interpreted as evidence of a signal or in the absence as a limit.
 \end{itemize}
@@
 
-%During regular data-taking periods, activities include monitoring the data acquisition systems and data quality through comparisons of new data and old data.
-%In addition to the data analysis plans described before, another objective is to contribute in one of the developments of the CMS detector to  prepare for the HL-LHC phase.
-%
-
-%Finally, the results of this project will be presented at national or international conferences and a publication in a scientific journal will be accomplished.
-
 \section{METHODOLOGY}
-%- methods used in the search: which dataset,  lepton reconstruction, selections, jets, BDT, backgrounds, statistical analysis
-
-%\afterpage{
-%\begin{figure}[H]
-%	\centering
-%	\includegraphics[width=0.5\columnwidth]{./topology.png}
-%	\caption{Topology of a tH signal event in a proton-proton collision.
-The decay products from the top quark include a b-jet and a W boson decaying to a lepton and neutrino.
-In this diagram the Higgs decays to a pair of W bosons, one decays to a lepton and neutrino while the other one can decay leptonically or hadronically.
-In addition there is a forward jet from initial collision of the quarks.}
-%	\label{figureTopology}
-%\end{figure}
-%\clearpage
-
-%\onehalfspacing The methods for a measurement of the 
-%coupling of the Higgs boson and the top quark in proton collisions are extensive and require several stages.
 
@@
 
-\iffalse
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.5\columnwidth]{./topology.png}
-	\caption{Topology of a tH signal event in a proton-proton collision.
-The decay products from the top quark include a b-jet and a $W^{\pm}$ boson decaying to a lepton and neutrino.
-In this diagram the Higgs decays to a pair of $W^{\pm}$ bosons, one decays to a lepton and neutrino while the other one can decay leptonically or hadronically.
-In addition there is a forward jet from initial collision of the quarks.}
-	\label{figureTopology}
-\end{figure}
-\fi
-
-%Figure~\ref{figureTopology} shows the main features of the topology of a tH event, including the subsequent decay products of the top quark and Higgs boson, these are the particles which are generated at the interaction point before entering the detector components.
 A separate simulation of the detector is employed using \textsc{Geant}~\cite{agostinelli2003geant4} which simulates the trajectory of the stable particles, response and efficiency of each sensor in the CMS detector.
@@
 The event reconstruction is designed to capture the distinguishing features of the signal topology.
-%In the channels which are the focus of this project, we require that there exist at least two leptons of electron or muon type, however also jets need to be identified as shown in the Figure 9.
 The event reconstruction begins with the identification of the different types of particles: photon, electrons, muons, taus, and jets.
@@
 
-%Jets which originate from b quarks are important in this study because they identify the decay of a top quark, b-jets are identified with a multivariate algorithm which searches for secondary vertices in the Tracker and electrons or muons (from decays of B-mesons) within the cone of the jet.
-
-Luminosity is one of the most omportant parameter for a particle accelerator.
+Luminosity is one of the most important parameter for a particle accelerator.
 It is the measure of number of proton-proton collisions occurring in unit centimetre square area per second.
@@
 
-%In the search for tH events using the dimuon channel the following event selections are applied:
-\iffalse
-\begin{itemize}
-\item
-\item
-\item
-\item
-
-\end{itemize}
-\fi
-
-%\textsc{Root} is a \textsc{c++} based software that allows visualization of event distributions and variable correlations.
-Further optimization of the event selections is performed by considering the different processes which contribute to the background.
-In this search several SM processes contribute to the background due to their decays to
-%leptons: $pp\rightarrow ZZ, WZ, WW, ZZZZ, t\bar{t}W, t\bar{t}Z, t\bar{t}H, tWZ, tZq,$ and $t\bar{t}t\bar{t}$.
-These backgrounds must be determined from MC simulation and normalized to their predicted SM cross sections.
-
 Due to the small signal over noise ratio in this search, a multivariate algorithm is trained to help separate signal events from background events.
@@
 \section{EXPECTED RESULTS}
-%- a limit, also predictions for future runs
-
 \onehalfspacing The results from this project include the following items:
 \begin{itemize}
-\item The student will become part of an international collaboration.
+\item Becoming author of an international collaboration.
 \item A leading contribution in one of the search for decays of the Higgs boson into pairs of $J/\psi$ or $\Upsilon$ using the data from the Run II of the LHC, resulting in a publication in a scientific journal.
-%\item Participation in the CMS detector Phase II upgrade through development and possible installation of particle detectors possibly resulting in a technical report.
 \item Improve limits on the branching fraction of these decays channels.
-\item Luminosity study for RUN3 data.
+\item Luminosity measurements for RUN3 data.
 \item A presentation of a poster or a talk in one of the national conferences of the Division of Paticles and Fields of the Mexican Society of Physics or a presentation of a poster or a talk in an international physics conference.
 \item An academic stay at a scientific center like CERN or Fermilab.
-\item A high quality thesis.
 \end{itemize}
 
+\cleardoublepage
 \section{CALENDAR OF ACTIVITIES}
@@
 \begin{itemize}
+\setlength\itemsep{-0.5em}
 \item {\bf Semester 1 (2022-2)}: 
@@
   \SubItem{ Initial planning of the analysis strategy}
+  \SubItem{ Initial work on 2022 luminosity measurement}
 \item {\bf Semester 2 (2023-1)}:
-  \SubItem{ Course I on particle physics and/or particle detection}
+  \SubItem{ Course I on particle physics and/or particle detection and analysis}
   \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
@@
   \SubItem{ Studies of the $J/\psi$ and $\Upsilon$ event selections}
-  \SubItem{ CMS service work for authorship}
+  \SubItem{ Work on 2022 luminosity measurement}
   \SubItem{ Possible summer stay at CERN or Fermilab}
 \item {\bf Semester 3 (2023-2)}:
-  \SubItem{ Course II on particle physics and/or particle detection.}
+  \SubItem{ Course II on particle physics and/or particle detection and analysis}
   \SubItem{ Studies of the $J/\psi$ and $\Upsilon$ event selections}
-  \SubItem{ Development of a Multivariate algorithm for the event selections}
   \SubItem{ Studies of the background processes}
-  \SubItem{ CMS service work for authorship}
+  \SubItem{ Work on 2023 luminosity measurement}
 \item {\bf Semester 4 (2024-1)}:
-  \SubItem{ CMS service work for authorship}
   \SubItem{ Studies of the $J/\psi$ and $\Upsilon$ event selections}
@@
   \SubItem{ Development of the statistical model and signal extraction}
+  \Subitem{ Work on 2023 luminosity measurement}
   \SubItem{ Possible summer stay at CERN or Fermilab}
@@
   \SubItem{ Development of the statistical model and signal extraction}
-  \SubItem{ Presentation of poster or talk at national or international conference}
+  \Subitem{ Work on 2024 luminosity measurement}
 \item {\bf Semester 6 (2025-1)}:
+  \SubItem{ Completion of the Higgs reconstruction and background estimation methods}
   \SubItem{ Development of software for the statistical analysis and interpretation of the results}
   \SubItem{ Review process of the results within the CMS collaboration}
+\item {\bf Semester 7 (2025-2)}:
+  \SubItem{ Completion of the analisis work}
+  \SubItem{ Writing of the paper publication}
   \SubItem{ Presentation of poster or talk at national or international conference}
-  \SubItem{ Writing of the paper publication}
+\item {\bf Semester 8 (2026-1)}:
   \SubItem{ Writing of the thesis}
+  \SubItem{ Completion of the paper publication}
+
 \end{itemize}

### 2022-11-16 project_Antonio/paper.tex
fix title

@@
 \def\Director{Dr. Jos\'{e} Feliciano BEN\'{I}TEZ RUBIO}
-\def\ProjectTitle{B\'usqueda de part\'iculas de Higgs con modelos de f\'sica m\'as all\'a del Modelo Est\'andar y medici\'on de la luminosidad usando el m\'etodo de Pixel Cluster Counting en el experimento CMS del CERN}
+\def\ProjectTitle{B\'usqueda de part\'iculas de Higgs con modelos de f\'isica m\'as all\'a del Modelo Est\'andar y medici\'on de la luminosidad usando el m\'etodo de Pixel Cluster Counting en el experimento CMS del CERN}
 \def\ProjectTitleEnglish{Search for Higgs bosons using models of physics beyond the Standard Model and measurement of luminosity using the Pixel Cluster Counting method in the CMS experiment at CERN}
-\def\ResearchLine{F\'{i}sica Matematicas}
+\def\ResearchLine{F\'{i}sica Matematica}
 

### 2022-12-29 tesis_Rodolfo/Abstract/abstract.tex
Rodolfo Thesis

@@
 \end{center}
-    van der Meer calibration is decribed
+The calibration of the luminosity measurement from the analysis of the van der Meer scan program by the CMS experiment in the 2018 proton-proton data taking at $\sqrt{s}=$13 TeV with the CMS Silicon Pixel detector is reported.
+The recorded data was reprocessed using a selection of the Pixel detector corresponding to the period from 2018-05-28 to 2018-07-07, based on luminosity stability studies.
+The background estimation corresponding to this module selection is reported.
+The analysis of the van der Meer scans presented here results in the calibration constant $\sigma_{vis}= 9229 \pm 8 (\text{stat.}) \pm 28 (\text{syst.})\text{ mb}$.
+
 \end{abstract}

### 2022-12-29 tesis_Rodolfo/Abstract/resumen.tex
Rodolfo Thesis

@@
 \end{center}
-Calibracion de van der Meer
+Se reporta la calibraci\'on de la medici\'on de luminosidad realizada a trav\'es del programa de escaneo de van der Meer del CMS en 2018 en la toma de datos prot\'on-prot\'on a $\sqrt{s}=$13 TeV, para el detector de pixeles de silicio (Silicon Pixel detector).
+Los datos han sido reprocesados aplicando una selecci\'on de m\'odulos del detector de pixeles que corresponde al periodo 28/05/2018 a 07/07/2018, basada en un estudio de estabilidad de luminosidad.
+La estimaci\'on del ruido de fondo en las mediciones correspondiente a esta selecci\'on de m\'odulos es tambi\'en reportada.
+El an\'alisis de los escaneos de van der Meer presentados en este trabajo resulta en la constante de calibraci\'on $\sigma_{vis}= 9229 \pm 8 (\text{stat.}) \pm 28 (\text{syst.})\text{ mb}$.
 \end{abstract}

### 2022-12-29 tesis_Rodolfo/Chapter1/chapter1.tex
Rodolfo Thesis

@@
 \chapter{Introduction}
-The Standard Model (SM) in particle physics is the theory that describes the interactions between three fundamental forces, out of the four known  (gravitational, electromagnetic, strong and weak), and the known fundamental particles.
-The gravitational force is not included in the SM, since the magnitude of its strength is neglectable in comparison with the other three forces.
+\label{ch1}
 
-The  theory was developed throughout the second half of the  20th century by the hard work of physicists around the world, with the current formulation being established in the mid 70s.\\
-In high energy physics, precise measurements are the core of any experiment.
-A key quantity is the luminosity, and its precise determination is an important aspect.
-The search for low incidence processes whose observation is not yet confirmed, such as the $H\rightarrow\gamma + Z$ channel, relies in the accumulation and precise measurements of luminosity.
-\section{The Standard Model}
+%%%%% https://cerncourier.com/a/pushing-the-precision-frontier/
+% https://home.cern/news/news/physics/why-precision-luminosity-measurements-matter
 
- The SM classifies all known fundamental particles into two major groups, fermions, particles with spin $1/2$, and bosons, particles responsible for mediating the fundamental forces and integer spin.
-Fermions are divided into two families of particles, leptons and quarks.
-There exist 6 leptons in the SM, first there are charged particles,  electrons ($e$), muons ($\mu$) and the taus ($\tau$) with an electric charge of $-1$ and spin of $1/2$.
-To each of these particles corresponds a chargeless neutrino, $\nu_{e}$,$\nu_{\mu}$ and $\nu_{\tau}$.
+Particle physics studies the fundamental constituents of the Universe, the elementary particles, and the interactions between them, the forces.
+To produce and study most of the elementary particles, experiments are carried out in  particle colliders of high energy, where a wide range of technologies are employed to detect and measure the properties of the particles produced, and to measure the collider parameters for its perfomance.\\  This chapter gives a brief background of the elementary particles and particle colliders, as well as relevant concepts-definitions about the measurements studied in this thesis project.
 
-Leptons can be found in nature existing by themselves, and along with quarks, comprise the majority of matter in the universe.
-Electrons can be found “circling”  atoms, muons can be found raining from the sky due to cosmic rays interacting with particles on the atmosphere and, while taus are a little bit tricky to find due to their short life time ($2.9\times10^{-13}$ s), they do exist by themselves; however, this cannot be said for quarks, since they are only found forming other particles called  hadrons.
-Hadrons can be a combination of two quarks called mesons, usually a quark-antiquark combination or a combination of three quarks called baryons, an example of a meson would be a pion ($\pi$).
-Neutrons and protons are made by a combination of three quarks, so they are classified as baryons.
-Quarks were first theorised by Murray Gell-Mann and George Zweig in 1964 and later discovered by experiments conducted at the Stanford Linear Accelerator Center (SLAC) in 1968 \cite{griff}.
-A total of 6 quarks were discovered over a period of 26 years, in order of discovery these are: up ($u$) (1968), down ($d$) (1968), strange ($s$) (1968), charm ($c$) (1974), bottom ($b$) (1977), top ($t$) (1995).
+\section{Fundamental Particles}
 
-Quarks are the only fermions that interact with all three fundamental forces included in the SM, they possess electric charge, color charge (the strong force equivalent of electric charge), weak charge, mass and spin $ 1/2$ as do all fermions.
-The $u$, $c$ and $t$ quarks have an electric charge of $2 /3$ and the $d$, $s$ and $b$ quark have an electric charge of $-1/3$.
-Table \ref{SM table} shows which fermions interact with the different forces.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[H]
+In our current understanding matter is made up of a group of particles with spin $1/2$, the fermions.
+The interactions between them, the forces, are described by the exchange of particles, which consist of a group of particles with integer spin: the gauge bosons.
+Three of the four forces: electromagnetic force, weak force and strong nuclear force, are mediated by the gauge bosons: photon, $W^{\pm}$ and $Z^{0}$, and gluons ($g$, eight of them), respectively.
+The description of the gravitational force in particle physics is yet an unresolved challenge.
+Apart from these vector bosons, there is a special scalar boson called Higgs boson, associated with the mechanism that give mass to all fundamental particles.\\
+The group of fermions is categorized in two types: leptons and quarks, giving a total of twelve fundamental particles that compose the matter.
+There are six leptons, three charged: electron ($e$), muon ($\mu$) and tau ($\tau$), and their corresponding  neutrinos: electron-neutrino ($\nu_{e}$), muon-neutrino ($\nu_{\mu}$) and tau-neutrino ($\nu_{\tau}$).
+The other group of fermions are the quarks, which cannot be found as individual particles, they can only be found coupled forming particles called hadrons.
+The group of quarks is formed by the up quark ($u$), down quark ($d$), charm quark ($c$), strange quark ($s$), top quark ($t$) and bottom quark ($q$) \cite{griff}.
+The force experienced by the fermions is shown in table \ref{tab:table1}.
+\begin{table}[h!]
+  \begin{center}
+    \caption{Force experienced by the fermions}
+    \label{tab:table1}
+    \begin{tabular}{l c c c c}
+    &    &  \textbf{Electromagnetic} & \textbf{Weak} & \textbf{Strong}\\
+      \midrule[1.1pt]
+      \multirow{2}{*}{Leptons} & $e$ \hspace{0.3cm}  $\mu$\hspace{0.3cm} $\tau$ & \checkmark & \checkmark & \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
+      & $ \nu_{e} $ \hspace{0.3cm}  $\nu_{\mu}$ \hspace{0.3cm} $\nu_{\tau}$  &  & \checkmark\\ % <-- Content of first column omitted.
+      \hline
+      \multirow{2}{*}{Quarks} & $u$ \hspace{0.5cm}  $c$\hspace{0.5cm} $t$ & \checkmark & \checkmark& \checkmark\\
+      & $d$ \hspace{0.5cm}  $s$\hspace{0.5cm} $b$ & \checkmark & \checkmark & \checkmark\\
+%      \hline
+%      3&3 & 23.113231 & c\\
+%      4&4 & 25.113231 & d\\
+    \end{tabular}
+  \end{center}
+\end{table}
+
+All these particles are described by the Standard Model (SM), so far the best theoretical model that provides a successful description of the experimental data.
+Most of the experimental data comes from particle colliders because most of the particles of the SM can only be produced and studied using collisions of high energy.
+One example of this, is the last member of the SM: the Higgs boson, observed in the Large Hadron Collider in proton-proton collisions at energy of $7$ and $8$ $TeV$ in the CMS and ATLAS detectors \cite{higgs_CMS,higgs_ATLAS}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Particle Colliders}
+
+Particle physics experiments are designed to detect and identify the particles produced in high-energy collision. The colliding beams produce particle bunch interactions referred to as events. \\
+Only the stable and relatively long-lived particles are the observables of particle physics collider experiments.
+The techniques employed to detect and identify the different particles depends on the nature of their interactions with matter.
+There are three main types of interactions (broadly speaking): interactions of charged particles, electromagnetic interactions of electrons and photons, and strong interactions of charged and neutral hadrons.
+The large particle physics detector systems use a wide range of technologies to detect and measure the properties of the particles produced in these high-energy collisions, with the aim of reconstructing the primary particles produced in the interaction from the signals in the different detector systems \cite{thomson_2013}.\\
+Apart from the technologies of detection, the most importar features for the performance of a particle collider are its center-of-mass (CM) energy and the luminosity.
+Achieving a high energy is required to collide %the initial
+particles and produce (possibly many) different particles.
+Some of them with considerably higher masses than the incident particles, for example massive particles such as the $W^{\pm}$, $Z$ and $H$ bosons.
+The total energy of a incoming particle plus the target particle depends on the reference frame.
+The frame that is relevant for the production of high mass particles is the CM frame for which the incoming and target particle have equal and opposite momentum of magnitude $p$.
+Considering the Lorentz invariant quantity $s$ :
+\begin{equation*}
+s= (E_{1} +E_{2} )^{2}- (\mathbf{p}_{1}+ \mathbf{p}_{2})^{2}c^{2}
+\end{equation*}
+
+In the CM frame, where the momenta are equal and opposite, the second term vanishes so that
+
+\begin{equation*}
+s= 4 E^{2}
+\end{equation*}
+
+where $E$ is the energy of each incoming particle and $s$ is the square of the total incoming energy in the CM frame ;this is a quantity that appears often in particle physics and the notation $\sqrt{s}$ is always used to refer the CM energy.
+Using  colliding beams of particle with equal mass having the same energy and therefore equal but opposite momentum, makes the experiment taking place in the CM frame and the full energy delivered by the accelerator, $\sqrt{s}=2E$, can be used to produce high mass particles \cite{undergraduate_accelerators_chapter}.
+Colliding beam machines are used in particle physics experiments due the advantage of  achieving much higher centre-of-mass energies in contrast with a fixed target experiment.\\
+The other important parameter of a colllider, the luminosity $\mathcal{L}$, is the quantity that defines ability to produce large numbers of events \cite{ref_lib_vol3}.
+It quantifies the potential of the collider for delivering a statistically significant sample of a given class of events.
+A high luminosity is of utmost importance in the search for rare events and new phenomena \cite{lumi_paper_def_and_concept}.
+This quantity relates the event rates (number of events in time) and the cross section ($\sigma_{p}$) of a particular event; the cross section is a measure of quantum mechanical probability for the interaction.
+
+\section{Cross section}
+In order to illustrate the concept of cross section, we shall consider a simple case where a beam of particles of type $a$, with flux $\phi_{a}$, is crossing a region of space in which there are $n_{b}$ particles per unit volume of type $b$.
+The interaction rate per target particle $r_{b}$ will be proportional to the incident particle flux, and can be written as \cite{thomson_2013}:
+
+\begin{equation*}
+  r_{b}=\sigma \phi_{a}
+\end{equation*}
+
+The fundamental physics is contained in $\sigma$, which has dimensions of area, and is termed as interaction cross section.
+There are cases where the cross section is closely related to the physical cross sectional area of the target, for example, neutron absorption by a nucleus.
+However, in general, the cross section is simply an expression of the underlying quantum mechanical probability that an interaction will occur \cite{thomson_2013}.\\
+Fig.
+\ref{cs_draw_1} (left) illustrates the definition of cross section, where a single incident particle of type $a$ is travelling with a velocity $v_{a}$ in a region defined by the area $A$, containing $n_{b}$ particles of type$ b$ per unit volume moving with a velocity $v_{b}$ in the opposite direction to $v_{a}$.
+
+\begin{center}
+  \begin{figure}[h!]
     \centering
-\caption[Fundamental forces and the fermions]{Fundamental forces and the fermions they interact with \cite{Thomson:2013zua}.}
-\renewcommand{\arraystretch}{1.5}
-\begin{tabular}{|c|c c c|c|c|c|}
-\hline 
-\multicolumn{2}{|c}{}&  & & Electromagnetic & Strong & Weak\\
-\hline
-\multirow{2}{*}{Quarks}&u&c&t &\multirow{2}{*}{\checkmark}&\multirow{2}{*}{\checkmark}&\multirow{2}{*}{\checkmark}\\
-& d&s&b&&&\\
-\hline
-\multirow{2}{*}{Fermions}& $e$&$\mu$&$\tau$ &\checkmark& &\checkmark\\
-&$\nu_{e}$&$\nu_{\mu}$&$\nu_{\tau}$&&&\checkmark\\
-\hline
-\end{tabular} 
-\label{SM table}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
- For each fermion that exists, there corresponds an antiparticle.
-Antiparticles have the same properties as their counterparts, with the only distinction being that they possess opposite electric charge.
-If an antiparticle comes in contact with a particle, let's say a positron (anti-electron) and an electron, they would annihilate each other.
+    \includegraphics[scale=.25]{Chapter1/cs_draw_1.png} \includegraphics[scale=.25]{Chapter1/cs_draw_2.png}
+    \caption[Cross section illustration]{Left: single incident particle of type $a$ traversing a region containing particles of type $b$.
+Right: projected view of the region traversed by the incident particle in time $\delta t$ \cite{thomson_2013}.}
+    \label{cs_draw_1}
+  \end{figure}
+\end{center}
 
-The SM also comprises particles with integer spin  such as the bosons.
-Bosons are force carrier particles in charge of mediating the interactions between particles, let's take  classical electromagnetism as an example.
-Classically, the electrostatic force is described by a scalar field and while this is sufficient for classical electromagnetism, it is fundamentally wrong for quantum dynamics.
-This would mean that two charged particles interact with each other at a distance, without contact of any kind \cite{Thomson:2013zua}.
+For a time $\delta t$, the particle a crosses a region containing $\delta N= nb(v_{a}+v_{b}) A \delta t$ of type $b$.
+The interaction probability can be obtained from the effective total cross sectional area of the $\delta N$ particles divided by the area $A$, which can be interpreted of as the probability that the incident particle passes through one of the regions of area $\sigma$ drawn around each of the $\delta N$ target particles, as shown in Fig.
+\ref{cs_draw_1} (right) \cite{thomson_2013}.
+The interaction probability $\delta P$ is therefore
 
-In  particle physics, each fundamental force is described by a quantum field theory (QFT) and the interaction between two particles are mediated by gauge boson, a spin-1 particle.
-For example,  the electromagnetic force is described by Quantum Electrodynamics (QED)  and mediated by the photon, a  particle with no charge or mass.
-The strong force is described by Quantum Chromodynamics (QCD) and mediated by a gluon, which has no mass or electric charge, gluons are what bind quarks together to form hadron and like quarks, are only found in these bind states.
-Finally the weak force is mediated by the $Z$ and $W^{\pm}$ bosons, massive particles with 0 an $\pm 1$ electric charge respectively
-\cite{Thomson:2013zua}.\\
-The Higgs boson is the last member of the SM, unlike the gauge bosons, the Higgs has spin-0 and is the only fundamental scalar discovered. Figure \ref{sm1} shows all the particles included in the SM.
+\begin{equation}
+\delta P= \frac{\delta N \sigma}{A}= n_{b}v\sigma \delta t
+\end{equation}
+
+where $v=v_{a}+v_{b}$. The interaction rate for each particle of type $a$ is
+
+\begin{equation}
+r_{a}= \frac{dP}{dt}= n_{b} v\sigma
+\end{equation}
+
+For a beam of particles of type $a$ with number density $n_{a}$ confined to a volume $V$, the total interaction rate is
+
+\begin{equation*}
+\text{rate}=r_{a}n_{a}V=(n_{b}v\sigma) n_{a}V= (n_{a}v)(n_{b}V)\sigma
+\end{equation*}
+
+\begin{equation*}
+\text{rate}=\phi N_{b} \sigma
+\end{equation*}
+
+so that the total rate is equal to
+
+\begin{equation}
+\text{rate}= \text{flux} \times \text{number of target particles} \times \text{cross section}
+\end{equation}
+
+Thus, the cross section for a process is defined as
+
+\begin{equation}
+\sigma=\frac{\text{number of interaction per unit time per target particle}}{\text{incident flux}}
+\end{equation}
+
+where the flux $\phi$ accounts for the relative motion of particles.
+%One approach, the simplest one is: 
+One approach to calculate the cross section for a particular process can be using the relativistic formulation of Fermi’s golden rule and the appropriate Lorentz-invariant expression for the particle flux.
+
+The cross section for the production of a general final state $O$ at the LHC is given by \cite{lumi_motiv}:
+\begin{equation}
+  \sigma (pp\rightarrow O +X)= \int dx_{1} dx_{2} \sum_{i,j} f_{i} (x_{1},Q) f_{j}(x_{2},Q) \hat{\sigma}(ij \rightarrow O)(M_{O},g_{ijO}, \cdots)
+ \label{cs_theo}
+\end{equation}
+where $f_{i}(x,Q)$ is the density fo partons\footnote{Before quarks and gluons were generally accepted, Feynman proposed that the proton was made up of point-like constituents, termed partons \cite{thomson_2013}.} (PDF) of type $i$ (quarks of different flavours or gluons) inside the proton, carrying a fraction $x$ of the proton momentum at a resolution scale $Q$.
+Theory predicts the PDFs to be independent of $O$.
+$\hat{\sigma}(ij \rightarrow O)$ is the partonic cross section to produce the final state $O$ in the collisions of partons $i$ and $j$.
+It depends on properties of the final state (for example the mass of $O$, $M_{O}$, the momentum of the various particles involved, etc.), and on the the nature of the interactions involved in the process (for example the strength, $g_{ijO}$, of the coupling between $i$, $j$ and $O$).
+Parameters like $M_{O}$ and $g_{ijO}$ are therefore what defines the underlying theory, and extracting their value as accurately as possible is the ultimate goal of an experimental measurement \cite{lumi_motiv}.
+The precision of the extraction of these parameters is determined by \cite{lumi_motiv}:
+i) The precision of the calculation of $\hat{\sigma}(ij \rightarrow O)$ as a function of $M_{O}$, $g_{ijO}$, etc.; this is a theoretical aspect.
+Inclusion of higher and higher orders of perturbation theory makes the prediction more accurate.
+ii) The precision of the knowledge of the PDFs; a theoretical and experimental aspect.
+For example, experimental data from measurements such as deep inelastic scattering (DIS) are necessary to extract the PDFs, by fitting these data to the DIS equivalent of an equation like \ref{cs_theo}.
+Likewise, is expected to use the LHC data themselves to improve the knowledge of the PDFs, by including the functions $f_{i}$ to the list of parameters in eq.
+\ref{cs_theo} that are allowed to float in order to fit the data.
+
+\section{Luminosity }
+
+Luminosity, $\mathcal{L}$ , is defined as the proportionality factor between the number of events per second $R$ (event rates) and the cross section $\sigma_p$ for a given process $p$ \cite{ref_lib_vol3}:
+
+\begin{equation}
+R=\mathcal{L}_{inst} \cdot \sigma_{p}
+\end{equation}
+
+Cross section has units $cm^{2}$, therefore the unit of luminosity is $cm^{-2}s^{-1}$.\\
+To derive a general expression of luminosity, we will consider the case of colliding beams at head-on.
+%a relevant case for LHC context[relibvol3]. foot page?
+At head on collision, the instantaneous luminosity for $N_{b}$ colliding bunches is given by:
+
+\begin{equation}
+  \mathcal{L}_{inst}= N_{b} N_{1}N_{2}f \int_{-\infty}^{\infty} dx\int_{-\infty}^{\infty} dy \rho_{1}(x,y)\rho_{2}(x,y)
+    \label{lumi_1}
+\end{equation}
+
+where $N_{1,2}$ are the particles per bunch, $f$ the revolution frequency and $\rho_{1,2}$ are the distribution functions of the two beams in the transverse plane.
+Assuming that $\rho$ can be factorized into independent terms in $x$ and $y$, i.e.
+uncorrelated bunch densities in all planes:
+
+\begin{eqnarray}
+  \rho_{i}(x,y)= \rho_{i}(x)\rho_{i}(y) & &i=1,2
+\end{eqnarray}
+
+So that eq. \ref{lumi_1}
+
+\begin{equation}
+  \mathcal{L}_{inst}= N_{b} N_{1}N_{2}f \int_{-\infty}^{\infty}\rho_{1}(x)\rho_{2}(x)  dx\int_{-\infty}^{\infty}\rho_{1}(y)\rho_{2}(y) dy
+    \label{lumi_2}
+\end{equation}
+
+If the bunch densities have Gaussian profile in both directions, i.e
+
+\begin{eqnarray}
+\rho(u)= \frac{1}{\sqrt{2\pi} \sigma_{u}} exp \biggl(-\frac{u^{2}}{2\sigma_{u}^{2}} \biggr)&  &  u=x,y
+\end{eqnarray}
+
+The integration yields
+\begin{equation}
+  \mathcal{L}_{inst}= \frac{N_{1} N_{2} N_{b}f }{4\pi \sigma_{x} \sigma_{y}}
+  \label{lumi_theor}
+\end{equation}
+
+In practice, the properties of the colliding beams are not know precisely, such as the bunch density profile, so that the integral in  \ref{lumi_2} cannot be solved analytically.
+In LHC a experimental technique is implemented with a dedicated machine setup to estimate the integrals, yielding a similar expression as \ref{lumi_theor}.
+This is discussed in chapter \ref{ch3}.\\
+%%%%%%%%%%%%%%%%%%%%%%NEW%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Luminosity  is a general concept that can be interpreted from geometry and flux of particles per unit of time.
+Considering two bunches of particles $N_{1,2}$ in a circular collider, colliding in an interaction region as shown in Figure 2.1.
+, the luminosity is expressed as [Simón-these]:
+%\begin{equation}
+%\mathcal{L}= \frac{N_{1}N_{2}f}{A_{eff}}
+%\end{equation}
+%where $A_{eff}$ is the effective transverse area in which the collisions take place and $f$ is the revolution frequency.
+The only unknown parameter that needs to be measured is the effective transverse area.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The instantaneous luminosity measure is of great importance beacuse it reflects the performance of the collider, but  this is not the only measurement concerned with luminosity.
+Another important measurement of luminosity is the integrated luminosity \cite{ref_lib_vol3}:
+
+\begin{equation}
+  \mathcal{L}_{int}=\int_{0}^{T} \mathcal {L}_{\text{inst}}(t) dt
+\end{equation}
+
+The integral is taken over a period of time $T$ (excluding possible dead time).
+The integrated luminosity has units of $cm^{-2}$ and is often expressed in inverse barn ($1 barn= 10^{-24}cm^{2}$).
+The importance of the integrated luminosity  is because it directly relates to the number of observed events: $ \mathcal{L}_{int}\cdot \sigma_{p}$.
+\\Another important parameter for a beam with high luminosity and bunched beams are the number of particle collisions per bunch crossing, called pileup ($\mu$).
+Pileup and luminosity are related by  $f \mu= \mathcal{L}_{\text{inst}} \sigma_{p}$ .\\
+Up to date, the particle collider with the highest luminosity and energy is the Large Hadron Collider (LHC) built by CERN, located in 	Geneva, Switzerland.
+
+%\subsection{Luminosity measurement}
+
+%Experimentally, the luminosity is measured with luminometers, which reads out a rate of the specific quantities observed in the detector (hits, tracks, clusters, etc.).
+This rate, R, should be proportional to the instantaneous luminosity , $\mathcal{L}_{inst}$, with the constant of proportionality given by the visisble cros section $\sigma_{vis}$ [pas-18 ?]:
+
+%\begin{equation}
+%R= \mathcal{L}_{inst} \sigma_{vis}
+%\end{equation}
+
+%The determination of $\sigma_{vis}$ is carried out throuhg vand der Meer (vdM) scans performed with a dedicated LHC machine setup.
+In the practice, the assumption [simon tese cern thesis] of the gaussian profile can not be known, and the integrals are solved using the van der Meer method, yielding a similar expression for Luminosity as the previous one.
+So that lumi expresion is substituted in eq prev and sigma vis obtained.
+
+\section{Importance of Luminosity precision}
+
+The precision of the measured cross section, $\sigma_{exp}(O)$, is determined by the quantities on the right hand-side of: $\sigma_{exp}(O) = N_{\text{events}}(O)/\mathcal{L}_{int}$.
+$N_{\text{events}}$ depends on the accurate knowledge of signal and background acceptances and efficiencies.
+\\
+The target of the programme of precision measurements is therefore to bring to the same level the accuracy of all elements in the following relation:
+$$\sigma (pp \rightarrow O)= \frac{N_{\text{events}}(O)}{\mathcal{L}_{int}}$$
+The possibility to have a very accurate absolute luminosity determination, and therefore very accurate experimental cross section measurements, allows to develop a physics programme in which this precise information can help improve, at the same time, the theoretical calculations, the PDF knowledge, and ultimately the measurement of the theory parameters such as masses and couplings\cite{lumi_motiv}.
+The experimental techniques to determine signal rates are mature enough, where the understanding of acceptances, detector biases, reconstruction efficiencies or background subtraction is at the subpercent level, so that the final precision of the physics measurement is dominated by the luminosity uncertainty \cite{lumi_paper_def_and_concept}.
+\\
+The precision in the measurement of the luminosity directly impacts the precision in the measurement of the cross section, and therefore has a large impact in our understanding of the Standard Model parameters.
+
+\section{The Large Hadron Collider}
+
+The LHC was designed to collide proton beams with a centre-of-mass energy of 14  TeV and a luminosity of $10^{34}cm^{-2}s^{-1}$.
+It was also designed to collide heavy ($Pb$) ions with an energy of 2.8 TeV per nucleon and a peak luminosity of $10^{27}cm^{-2}s^{-1}$ \cite{lhcmachine2008}.\\
+The LHC consists of two rings of 27 km of circumference which guide accelerated bunches of protons (or Pb) at high energy to collide.
+Figure \ref{lhc_com} shows the CERN accelerator complex.
+The bunches are previously accelerated by a chain of pre-accelerators.
+First, protons are produced by ionizing hydrogen and then are transferred to the Linear Accelerator 2 (LINAC2) where the protons are accelerated in bunches up to an energy of 50 MeV, and then the bunches pass trough three circular accelerator: the Booster, the Proton Synchrotron (PS) and the Super Proton Synchrotron (SPS), giving an energy of 1.4 GeV, 26GeV and 450 GeV, respecectively.
+After these three preaccelerators, the bunches are finally circulating in oposite directions in the LHC ring, where are further accelerated to reach energies up to 7 TeV (per bunch).
+This entire procedure defines a single LHC fill generally consisting of $10^{14}$ protons, grouped into bunches to form the proton beam.\\
+There are four experiments placed around the LHC ring: Compact Muon Solenoid (CMS) \cite{CMS_Exp_2008}, A Toroidal LHC ApparatuS (ATLAS) \cite{Atlas_Exp_2008}, A large Ion Colliding Experiment (ALICE) \cite{ALICE_Exp_2008} and LHCb \cite{LHCb_Exp_2008}.
+CMS and ATLAS are for general-purpose detectors to investigate the largest range of SM and Beyond SM (BSM) physics.
+ALICE and LHCb have detectors specialized to study specific phenomena.
 
@@
     \centering
-    \includegraphics[scale=0.3]{Chapter1/sm1.png}
-    \caption[ Standard model of particles]{Particles that compose the standard model and their properties \cite{smtable}.}
-    \label{sm1}
+    \includegraphics[scale=.41]{Chapter1/lhc_complex_fig.png}
+    \caption[LHC Complex]{Diagram of the LCH complex \cite{lhc_complex}.}
+    \label{lhc_com}
   \end{figure}
@@
 
-\section{The Higgs Boson }
-The Higgs boson is the latest member of the SM, first theorised in 1964 by Peter Higgs, Robert Brout, François Englert, Gerald Guralnik, C.
-Richard Hagen and Tom Kibble and later discovered by the ATLAS and CMS experiments at the Large Hadron Collider (LHC) in Geneva Switzerland in 2012.
-The experiment consisted in proton-proton collisions with a center of mass energy of 7 and 8 TeV, the data analysed from the experiment corresponds to five decay channels: $\gamma\gamma$, $ZZ$, $W^{\pm}W^{\pm}$, $\tau^+\tau^-$ and $b\bar{b}$.
-With the discovery being made in the  $\gamma\gamma$ and $ZZ$ channels
-\cite{higgsd}\cite{Aad_2012}.
-The Higgs plays a vital role in the SM, it is responsible for the mechanism that gives every particle their mass.
-It has a mass of $125.78\pm 0.26$ GeV \cite{CMS:2019drq}, consistent with SM predictions, it does not possess electric or color charge and it is the only fundamental scalar and spin-0 boson.\\
- The discovery of the Higgs is one of the greatest accomplishments of the SM, it shows the hard work that has gone in to developing the theories that compose it \cite{Thomson:2013zua}.
+\section{LHC Luminosity}
+The LHC has had two Runs and two long shutdowns for maintenance and  upgrades.
+Run 1 lasted from 2010-2012, while Run 2 lasted from 2015-2018.
+In Run1, LHC reached a peak instantaneous luminosity of  $0.77 \times 10^{34}$  and an integrated luminosity of $25 fb^{-1}$  for proton-proton collisions at $\sqrt{s}=\text{8 TeV}$ in 2012\cite{LHC_status_2013}.
+For the first part of Run-2 (2015-2016) in proton-proton colissions at $\sqrt{s}=\text{13TeV}$ in CMS detector, the integrated luminosities when CMS was fully operational are $2.2$7 and $36.3$ $fb^{-1}$ in 2015 and 2016, with a relative precision of 1.6\% and 1.2\%, respectively \cite{lumi_precise_2015_2016}.
+For the second part of Run 2 (2017-2018), the integrated luminosity is about $49.8 fb^{-1} $ and $67.9 fb^{-1}$ for 2017 and 2018, respectively, as can be seen in Fig.
+\ref{lumi_per_year_int}.
+The total systematic uncertainty in the calibration of luminosity measurement is 2.3\% in 2017\cite{pas_17} and 2.5\% in 2018 \cite{pas_18}, but its precision remains to be improved.
+The main objective of this thesis project is to contribute to the improvement of the precision of 2018 luminosity calibration.
 
-\section{Particle colliders and
-detectors}
-The discovery of the Higgs marked an important milestone in particle physics, however, this feat required the construction of the LHC, the largest and most powerful particle collider in the world.
-Particle colliders are the devices where particle physics experiments are conducted.
-As their name suggests, colliders propel bunches of particles like electrons, protons, positrons, etc.
-using powerful electromagnetic/electrostatic fields, and make them collide with a fixed target or other particles.
-These collisions produce other particles that are measured by particle detectors in the site of the collision, this is the means by which new particles are discovered.
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[scale=.3]{Chapter1/int_lumi_per_year.png}
+    \caption[CMS Luminosity per year]{Delivered luminosity versus time for Run-1 (2010-2012) and Run-2 (2015-2018); pp data only.
+Cumulative luminosity versus day delivered to CMS during stable beams for pp collisions at nominal center-of-mass energy.
+These plots use the best available offline calibrations for each year.
+For 2017 and  2018 the plots are based on \cite{pas_17} and \cite{pas_18}, respectively \cite{wikicern}.}
+    \label{lumi_per_year_int}
+  \end{figure}
+\end{center}
 
-Particle colliders come in two types: linear  and circular.
-Linear colliders  use changing electromagnetic fields to accelerate particles along a straight beam path and make them collide with a fixed target, where particle detectors are located, an example of the linear accelerator would be the Stanford Linear Accelerator Center.
-While circular colliders to accelerate bunches of particles  in opposite directions in a circular beam fashion, making them collide at key points around the accelerator where particle detectors are located.
-The LHC is an example of a circular collider.
+%lumi values:
+% https://inspirehep.net/files/11b4a1d6569e8e066e7431f17a55d69c
 
-The majority of modern experiments in particle physics are conducted in circular colliders, since these are the only ones that can provide the center of mass energy needed to produce heavier particles, like the Higgs or the Top quark.
-Due to the high energy requirements, circular accelerators are very complex machines composed of many parts, but for the sake of this work, we will only focus on the particle detectors.
-Modern particle detectors are composed of many layers of subdetectors tasked with measuring the effects that particles have on them, when they pass through.
-For example, a subdetector may measure the number of hits, tracks or pixel clusters activated during a collision.
+% https://arxiv.org/pdf/1504.06519.pdf
 
-The layout of the detector will change to best accommodate the experiments being performed, but in general, these subdetectors can be classified into three categories: Tracking devices, to track the path of a particle; calorimeters, they measure the energy deposited by a particle when it hits and particle identifiers, that use various techniques and the measurements from other subdetectors, to identify the different particles produced in a collision \cite{detector}.
-The CMS detector and the LHC is an example of a layered particle detector.
-
-Finally, two parameters are used to measure the efficiency of a particle collider, the beam energy and the luminosity.
-The higher the beam energy, the more particles can be created and thus the higher chance that new effects can be observed.
-The luminosity ($\mathcal{L}$) is a measure of the efficiency of a particle collider to produce meaningful interaction between colliding bunches of particles.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Luminosity }
-
-As mentioned before, the LHC collides particles by grouping them into bunches, where trains of $N_b$ bunches are made.
-The groups of bunches are circulated both clockwise and anticlockwise and are forced to cross at specific detection points, where several interactions occur.
-A collision between bunches is called an event, and several particle interactions are produced during these events, the quantity that measures the ability of any particle collider to produce these useful interactions is called Luminosity.
-Thus, the event rate $R$, of a particular type $p$, with cross-section  $\sigma_p$, is given by \cite{White}:
-\begin{equation}
-    R=\mathcal{L}_{ins}\sigma_p
-    \label{lumy0}
-\end{equation}
-
-Where the instantaneous luminosity, $\mathcal{L}_{ins}$, is the proportionality constant, the cross section is the likelihood of that event taking place and has units of $cm^{2}$, thus the luminosity has units of $cm^{-2}s^{-1}$ \cite{White}.
-Since the probability of a rare event increases the more the rate of interactions grows, the luminosity is a key figure in the performance of a particle collider.\\
-Let's consider $N_b$ colliding bunches, assuming all the bunches have a head-on collision, the luminosity of all the colliding bunches is given by \cite{CERN-THESIS-2018-051}: 
-\begin{equation}
-    \mathcal{L}_{ins}=  N_b N_1 N_2f\int^{\infty}_{-\infty}dx\int^{\infty}_{-\infty}dy \rho_1(x,y)\rho_2(x,y)
-    \label{lumy1}
-\end{equation}
-where $N_{1,2}$ are the particles per bunch, $f$ is the revolution frequency and $\rho_{1,2}$ are the normalized densities in the transverse plane.
-Assuming that the normalized densities are uncorrelated in all planes, the distribution functions can be factorized as:
-\begin{equation}
-    \rho_i(x,y)=\rho(x)\rho(y) \text { where i=1,2}
-    \label{dens1}
-\end{equation}
-Thus, equation \ref{lumy1} can be writhe as
-
-\begin{equation}
-    \mathcal{L}_{ins}=  N_b N_1 N_2f\int^{\infty}_{-\infty}\rho_1(x)\rho_2(x)dx\int^{\infty}_{-\infty}dy \rho_1(y)\rho_2(y)
-    \label{lumy2}
-\end{equation}
-For the case of head-on colliding bunches, a Gaussian charge distribution can be used, equation \ref{dens1} can be written
-\begin{equation}
-    \rho(u)=\frac{1}{\sqrt{2\pi}\sigma_u} exp\left(-\frac{u^2}{2\sigma_u^2}\right) \text { where u=x,y.}
-    \label{dens2}
-\end{equation}
-using this, equation \ref{lumy2} can be integrated analytically, giving 
-\begin{equation}
-    \mathcal{L}_{ins}=\frac{N_1N_2N_b f}{2\pi
-    \sqrt{\sigma^2_{x1}+\sigma^2_{x2}}\sqrt{\sigma^2_{y1}+\sigma^2_{y2}}}
-    \label{lumy3}
-\end{equation}
-In practice, the bunch densities in the transverse plane are not known and a calibration of the detectors has to be done, in order to obtain these values.
-At the LHC, this is done by a dedicated machine setup.
-The performances of a particle collider over a period of time is given by the integrated luminosity :
-\begin{equation}
-L=\int \mathcal{L}_{ins}(t)dt
-\label{lum0}
-\end{equation}
-
-The average number of interaction per bunch crossing is given by the pileup, $\mu$, and directly proportional to the luminosity
-\begin{equation}
-    \mu=\frac{\mathcal{L}_{ins}\sigma_{tot}}{f}
-    \label{pileup}
-\end{equation}
-where the $\sigma_{tot}$ is the total cross-section of the collided particles \cite{CERN-THESIS-2018-051}.\\
-It is worth noting that a head-on collision is not always the case.
-The bunches can collide in different ways, such as an off-set a crossing angle or both.
-In these cases, the overlapping integral in equation \ref{lumy1} is reduced.
-This is done by applying a reduction factor to equation \ref{lumy2} \cite{CERN-THESIS-2018-051}, however, this work is only concerned with the head-on collision case, the other scenarios can be found in \cite{White}.
+%ATLAS 2015-2018: https://arxiv.org/pdf/1911.04632.pdf

### 2022-12-29 tesis_Rodolfo/Chapter2/chapter2.tex
Rodolfo Thesis

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Large Hadron Collider}
+The Compact Muon Solenoid (CMS) detector is a multi-purpose apparatus that operates at the LHC at CERN.
+Its name comes from the fact that is quite compact for all the detector material it contains ( 15 meters high and 21 meters long), it is designed to detect muons very accurately, and it has it has the most powerful solenoid magnet ever made.
+Along with ATLAS, is one of the two high luminosity experiments at CERN.
+In this chaper the components of the CMS are described.
+The silicon pixel tracker is described with more detail due the purposes of this thesis.
 
-The LHC is one of the most powerful particle collider in the world, it started construction in 1998 on the France–Switzerland border near Geneva, using the 26.7 km tunnel, constructed for the CERN LEP machine.
-It came into operation on the 10 of September of 2008, and it is the latest addition to the CERN accelerator complex.
-It was first approved on December 1994 by the CERN council, with  a center-of-mass-energy of 14 Tev \cite{Bruning:782076}.
+\section{The Compact Muon Solenoid}
 
-The LHC consists of two separate rings, kept in an ultrahigh vacuum, where two the beams of particles are located.
-To achieve the circular motion of the beams, 1232 dipole magnets are used to maintain trajectory, and 392 quadrupole magnets are used to keep the beams focused.
-Near the interaction points, stronger quadruple magnets are used to increase the probability of interaction between the beams.
-These magnets are made of coils of special superconductive cable, cooled to a temperature of 1.8 K with superfluid helium, producing an electromagnetic field of above 8 T \cite{Bruning:782076}.
-
- The beams in each ring are made of bunches for particles traveling near the speed of light.
-These bunches can be made of protons or ions (like lead nucleons), depending on the running experiment, however, the majority of events at the LHC are produced by proton-proton (pp) bunch collision.\\
-A diagram of CERN’s accelerator complex can be seen in Figure \ref{cernc}.
-The proton bunches start as ionised hydrogen gas and are accelerated to an energy of 50 MeV, by the Linac 2 linear accelerator.
-Once they leave the Linac 2, they are further accelerated to an energy of 1.4 GeV by the Proton Synchrotron Booster (PSB) and dumped on the  Proton Synchrotron (PS).
-In the PS, the bunches are accelerated to an energy of 25 GeV and arranged into a bunch trains, with a spacing of 25 ns, in total, one orbit contains 3564 bunches, arranged in to several trains.
-Finally, the bunches pass from the PS to the Super Proton Synchrotron (SPS), where they are injected into the LHC with an energy of 450 GeV.
-In the LHC, the beams reach a peak energy of 6.5 TeV, and are made to collide in one of the 4 detectors, ALICE, ATLAS, CMS and the LHCb.
+The Compact Muon Solenoid (CMS) experiment is one of four detectors placed  around the LHC.
+The CMS detector consist of several detection layers, having a total length of 21.6 m with a diameter of 14.6 m.
+It consist of a silicon tracker to provide a measurement of the trajectories of charged particles, a 3.8 Tesla superconducting solenoid, an electronic and hadronic calorimeter to meausure particle energy, and a muon detection system \cite{CMS_Exp_2008}.
+A diagram of a perspective view of the CMS detector is shown in Fig.
+\ref{detector_CMS}.\\
+%%%%%%%%%%%% PARAGRAPH TO SUMMARY THE LAST 3 SECTION (ECAL, HCAL AND MUONS SYSTEM)%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The electromagnetic calorimeter of CMS (ECAL) is a hermetic homogeneous calorimeter made of 61 200 lead tungstate (PbWO4) crystals mounted in the central barrel part, closed by 7 324 crystals in each of the two endcaps.
+A preshower detector is placed in front of the endcap crystals.
+Avalanche photodiodes (APDs) are used as photodetectors in the barrel and vacuum phototriodes (VPTs) in the endcaps \cite{CMS_Exp_2008}.\\
+The ECAL is surrounded by a brass/scintillator sampling hadron calorimeter (HCAL).
+The scintillation light is converted by wavelength-shifting (WLS) fibres embedded in the scintillator tiles and channeled to photodetectors via clear fibres.
+This light is detected by photodetectors (hybrid photodiodes, or HPDs) that can provide gain and operate in high axial magnetic fields.
+The Cerenkov light emitted in the quartz fibres is detected by photomultipliers \cite{CMS_Exp_2008}.\\
+After the HCAL and the 13-m-long, 6-m-inner-diameter, 4-T superconducting solenoid, the muon detector system is placed.
+CMS uses 3 types of gaseous particle detectors for muon identification.
+Due to the shape of the solenoid magnet, the muon system was naturally driven to have a cylindrical, barrel section and 2 planar endcap regions \cite{CMS_Exp_2008}.\\
+The tracker system is described with detail in the next section.\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
+A sketch of a transverse slice of the CMS detector, with specific particle interactions, is shown in Fig.
+\ref{slice_CMS}.
+A simplified summary of particle interaction (and detection) is described as follows.
+Starting from the beam interaction region, particles first enter a tracker, in which charged-particle trajectories (tracks) and origins (vertices) are reconstructed from signals (hits) in the sensitive layers.
+The tracker is immersed in a magnetic field that bends the trajectories and allows the electric charges and momenta of charged particles to be measured.
+Electrons and photons are then absorbed in an electromagnetic calorimeter (ECAL).
+The corresponding electromagnetic showers are detected as clusters of energy recorded in neighbouring cells, from which the energy and direction of the particles can be determined.
+Charged and neutral hadrons may initiate a hadronic shower in the ECAL as well, which is subsequently absorbed in the hadron calorimeter (HCAL).
+Muons and neutrinos traverse the calorimeters with little or no interactions.
+While neutrinos escape undetected, muons produce hits in additional tracking layers called muon system, located outside the calorimeters \cite{det_summary}.\\
 \begin{center}
@@
     \centering
-    \includegraphics[scale=.7]{Chapter2/CERNC.jpg}
-    \caption[CERN accelerator complex.]{A diagram of the CERN accelerator complex \cite{cernpg}.}
-    \label{cernc}
+    \includegraphics[scale=.3]{Chapter2/CMS_detector_simple.png}
+    \caption[Perspective view of the CMS detector]{Perspective view of the CMS detector.}
+    \label{detector_CMS}
   \end{figure}
 \end{center}
-The four detectors are tasked with measuring all the particles produced in pp collisions.
-Two specialized detectors are integrated to the LHC, ALICE and LHCb.
-ALICE is dedicated to heavy ion collisions physics, where the quark-gluon plasma is studied.
-The LHCb investigated the differences between matter and antimatter, by studying the “beauty quark” \cite{lhcb}.\\
-The two remaining detectors, CMS and ATLAS, are general purpose detectors, tasked with studying a wide range of physics, from the search of the Higgs boson, to extra dimensions and particles that could make the dark matter in the universe \cite{cmsweb}.
 
-Two operation runs have been completed so far at the LHC, and two long shutdowns, where maintenance and several minor upgrades were made to the machine.
-Run 1 lasted from 2010-2012, while Run 2 lasted from  2015-2018.
-As of Run 2, the LHC has achieved a peak luminosity of $2\times 10^{-34} cm^{-2}s^-1$, two times the amount for which the LHC was designed.
-The integrated luminosity, since the LHC began operations, has reached $160 fb^{-1}$ for the ATLAS and CMS experiments \cite{lumi2180}.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The CMS detector }
-The Compact Muon Solenoid (CMS) experiment is one of the four major experiments currently running in the LHC, and along with ATLAS, one of the two high luminosity experiments at CERN.
-It receives its name from the huge solenoid magnet, from which the detector is built around.
-This solenoid takes the form of a coil made of super conductive wire, capable of producing an electromagnetic field of 4 T.
-The field is confined by a steal yoke, that weights 14,000 tones.
-
-CMS is a layered detector, 21 m in length, with a height and width of 15 m, and it is composed of four main subdetectors, the inner silicon tracker, electromagnetic and hadron calorimeters and the muon detectors.
-The strong magnetic field produced by the detector’s solenoid, separates the particles produced in the coalitions and provides a better momentum resolution.
-Figure \ref{cms} shows a diagram of the detectors layout.
 \begin{center}
@@
     \centering
-    \includegraphics[scale=.2]{Chapter2/CMSl.png}
-    \caption[CMS detector diagram]{Diagram of the CMS detector showing the various subdetectors that comprise it \cite{cms-manual}.}
-    \label{cms}
+    \includegraphics[scale=.3]{Chapter2/slice_det.png}
+    \caption[Transverse slice fo CMS detector]{Sketch of a transverse slice of the CMS detector with specific particle interactions, from the beam interaction region to the muon detector.
+The muon and the charged pion are positively charged, and the electron is negatively charged \cite{det_summary}.}
+    \label{slice_CMS}
   \end{figure}
 \end{center}
-The CMS experiment has a broad range of goals in particle physics, from studying the SM in search of new particles and phenomena, to searching for extra dimensions and discovering new particles that could make the dark matter in the universe.
-The experiment has achieved great things in the scientific community, however, one of its greatest, was the discovery of the Higgs boson  alongside the ATLAS experiment in 2012.
-In the next subsection a brief description of the different subdetectors is provided \cite{cms-manual}.
-\subsection{ Silicon tracker}
-At the heart of the CMS detector lies the inner silicon tracker.
-As its name suggests, the purpose of this subdetector is to reconstruct the track of charged particles generated during collisions, by using silicon strips and pixels to register the paths of charged particles.
-Once the track of a charged particle is reconstructed, its momentum can be extracted, by calculating the curb of its trajectory, produced by the electromagnetic field.
-Also, the vertex, the origin of the track, can be determined.
-The Tracker, which consists of an Inner Tracker (pixels) and an Outer Tracker (strips), is the first subdetector encountered by the particles, and thus the smallest, with an outer radius of 110 cm and a total length of 5.4 m, Figure \ref{tracker} shows the layout of the inner tracker.
+
+The coordinate system adopted by CMS has the origin at the center of the detector, the $y$-axis pointing vertically upward, and the $x$-axis pointing radially inward toward the center of the LHC.
+Thus, the z-axis points along the beam direction toward the Jura mountains from LHC Point 5.
+The azimuthal angle $\varphi$ is measured from the $x$-axis in the $x-y$ plane and the radial coordinate in this plane is denoted by $r$.
+The polar angle $\theta$ is measured from the $z$-axis.
+Pseudorapidity is defined as $\eta=- \ln \tan (\theta/2)$ \cite{CMS_Exp_2008}.\\
+%The components of the CMS detector, the tracking system, electromagnetic and hadronic calorimeter, and the muon system, are discribed briefly in the following subsections.
+
+\section{CMS Tracking System}
+The measurement of the momenta of charged particles is an essential aspect of any large particle physics experiment.
+Regardless of the medium through which a charged particle travels, it leaves a trail of ionised atoms and liberated electrons.
+By detecting this ionisation it is possible to reconstruct the trajectory of a charged particle.
+A charged particle will leave a hit in a silicon sensor in each cylindrical layer from which the trajectory of the charged particle track can be reconstructed.\cite{thomson_2013}.\\
+When a charged particle passes through a medium, it interacts electromagnetically with the atomic electrons and loses energy through the ionisation of the atoms \cite{thomson_2013}.
+The theory of such losses, which are due dominantly to Coulomb scattering from the atomic electrons, was worked out by Bethe, Bloch and others in the 1930s.
+The result is called the Bethe–Bloch formula: \cite{Martin2017_book}:
+
+\begin{equation}
+  -\frac{dE}{dx}= \frac{Dq^{2}n_{e}}{\beta ^{2}} \biggl[ \ln \left(\frac{2m_{e}c^{2}\gamma^{2}}{I} \right) -\beta^{2} -\frac{\delta(\gamma)}{2}  \biggr]
+  \label{bethe}
+\end{equation}
+
+$x$ is the distance travelled through the medium, $m_{e}$ is the electron mass, $\beta=v/c$,  $\gamma =(1-\beta^{2})^{-1/2}$ and $D=\frac{4\pi \alpha^{2} \hslash^{2}}{m_{e}}=$5.1$\times 10^{-25}$MeV cm$^{2}$.
+The other constants refers to the medium: $n_{e}$ is the electron density, $I$ is the mean ionisation potencial of the atoms averaged over all electrons (given approximately by $I$=10$Z$eV for $Z>$20) and $\delta$ is a dielectric screening correction that is only important for highly relativistic particles.
+%The corresponding formula for spin–1/2 particles differs from this, but in practice the differences are small and may be neglected for the discussion of the main features of ionisation energy losses.
+It is common practice to divide eq.
+\ref{bethe} by the mass density $\rho$ and to redefine $x$ as the density multiplied by the distance travelled, so that $\frac{dE}{dx}\rightarrow -\frac{1}{\rho}\frac{dE}{dx}$, beeing $x$ now measured in g/cm$^{2}$.
+As can be seen in \ref{bethe}, $-dE/dx$ falls rapidly as the velocity increases from zero because of the $1/\beta$ factor.
+All particles have a region of ‘minimum ionisation’ for $\beta \gamma$ \cite{Martin2017_book}.\\
+
+The tracking detector in the CMS experiment is based on semiconductor technology using silicon pixels and strips.
+It is composed of two sub systems, the pixel tracker (the closest to the interaction vertex) and the  strip tracker \cite{CMS_Exp_2008}.
+The Pixel detector is described below.
+
+\subsection{Pixel Detector and Clustering}
+\label{pixel_clust_reco}
+The pixel tracker originally consisted of three barrel layers at radii of 44, 73, and 102 mm and two endcap disks on each end \cite{CMS_Exp_2008}.
+With the upgrade of the accelerators during the first long shutdown (LS1, 2013-2014) the original pixel detector has been replaced by a new system referred to as the CMS Phase-1 pixel detector.
+The installation of the CMS Phase-1 pixel detector took place during the extended year-end technical stop of the LHC in 2016/2017.
+The layout of the CMS Phase-1 pixel detector is optimized to have four-hit coverage over the pseudorapidity range ($|\eta|<2.5$), improved pattern recognition and track reconstruction, and added redundancy to cope with hit losses \cite{phase1_Pixel_Detector}.
+\\
+The CMS Phase-1 pixel detector consists of four concentric barrel layers (L1-L4) at radii of 29, 68, 109, and 160 mm, and three disks (D1-D3) on each end at distances of 291, 396, and 516 mm from the center of the detector.
+The layout of the CMS Phase-1 pixel detector is shown  in Fig.
+\ref{phase1_pixel_detector}.
+The total silicon area of the CMS Phase-1 pixel detector is 1.9 $\text{m}^{2}$, while the total silicon area of the original pixel detector was 1.1 $\text{m}^{2}$.
+
 \begin{center}
@@
     \centering
-    \includegraphics[width=1\textwidth]{Chapter2/pixel-detector.png}
-    \caption[CMS tracker.]{Diagram showing the layout of the CMS Phase-1 inner tracker.
-The barrel pixel detector (BPIX) and the forward disks pixel detector (FPIX) are shown \cite{CMSTrackerGroup:2020edz}.}
-    \label{tracker}
+    \includegraphics[scale=.26]{Chapter2/phase1_PixelDetector.png}
+    \caption[CMS Phase-1 pixel detector]{Layout of the CMS Phase-1 pixel detector in longitudinal view\cite{phase1_Pixel_Detector}.}
+    \label{phase1_pixel_detector}
   \end{figure}
 \end{center}
-The tracker is divided into two subtrackers: one is the silicon strip tracker, made of 9.6 million silicon strips.
-This subtracker is divided in two parts: the Tracker Inner Barrel (TIB) and the Tracker Outer Barrel (TOB).
-The TIB is made of 4 layers that cover up to $|z|<65$ cm.
-The TOB has 6 layers, and a coverage of $|z|<110$ cm.
-The encaps are again divided into two regions,  Tracker End Cap (TEC) and Tracker Inner Disk (TID).
-The TEC is composed of 9 disks that extend in the region 120 cm $<|z|<$ 280 cm, while the TID has 3 disks that fill the gaps in between the TIB and the TEC.
-The TEC and the TID are made of rings centered on the beam, and possess stripst that point towards the beam.\\
-The strip tracker encompass and area of 200 $m^2$, and it is made of almost 15,400 modules, running at a  temperature of $-20^{\circ} C$.
 
-The other subtracker is the pixel tracker, made of three layers of barrels possessing a radius of 4.4 cm, 7.3 cm and 10.2 cm with a length of  53 cm, and consisting of 66 million pixels.
-In each end of the barrels, two  end cap disks reside, extending from 6 to 15 cm in radius and located at $|z|=34.5$ cm and 44.5 cm, in total, the pixel tracker has an area of roughly 1$m^2$\\
-768 pixel modules are housed in the barrel, all arranged into half lathers of 4 identical modules.
-The end cap disks are designed in a turbine-like geometry, with blades rotated $20^{\circ}$.
-The blades are made of 7 different pixel modules, with a total of 768 modules being housed in the end cap disks \cite{cms-manual}.
-\subsection{CMS calorimetry system}
-The calorimetry system of the CMS detector is composed of two types of calorimeters: the electromagnetic and hadronic calorimeters.
-Both subdetectors form a complete and hermetic calorimetry system with a coverage of $-5<\eta<5$.
-The calorimeters are a crucial part of the CMS detector, since the identification and reconstruction of photons and electrons is done using measurements from the calorimetry system, as well as the measurements of jets and missing transverse momentum.
-A brief description of the electromagnetic and hadronic calorimeter is provided below.
-
-\subsubsection*{Electromagnetic calorimeter}
-The electromagnetic calorimeter (ECAL) measures the energy of electrons and photons.
-Once charged particles enter the ECAL, they produce a shower for secondary electrons and photons.
-These electrons pass through the lead tungstate ($PbWO_4$) crystals, which scintillates when electrons hit their crystalline structure, producing light that is measured by photodiodes in the calorimeter.\\
-It is made of 75848 tungstate crystals \cite{Contardo:2020886}.
-It is an hermetic, homogeneous calorimeter composed of a central barrel and two end-caps.
-Silicon avalanche photodiodes (APDs) are used in the barrel and vacuum phototriodes (VPTs) in the end caps.
-
-The central barrel has an inner radius of 129 cm and a structure of 36 “supermodules”, that cover half the barrel's length.
-It has a coverage of $|\eta|<1.479$.
-The APDs used on the barrel have an active area of $5\times5$ $mm^2$, and two of them are glued to the back of each crystal.\\
-The two end caps have a pseudorapidity range of $1.479<|\eta|<3$, and are located at a distance of 314 cm from the vertex.
-It consists of crystals with an identical shape,  grouped in mechanical units of $5\times 5$ \cite{cms-manual}.
-\subsubsection*{Hadron calorimeter}
-The Hadron calorimeter (HCAL), along with the ECAL, form a complete and hermetic calorimetry system  with the purpose of measuring  jets and missing transverse energy.
-The HCAL surrounds the ECAL and its design is heavily influenced by the magnet parameters, since it is located inside the solenoid magnet.
-The HCAL is divided into 4 parts: the hadron barrel (HB), hadron outer (HO), hadron endcap (HE) and hadron forward.
-The absorber material is brass since it has a short interaction length, is non-magnetic and is easy to machine.
-Tile/fiber technology, embedded between the absorber plates, is used to detect the particle showers.
-The technology consists of plastic scintillator tiles embedded with  wavelength- shifting (WLS) fibers.
-The fibers are connected to high-attenuation-length clear fibers that carry the light to the readout system.\\
-The photodetection readout is handled by multi-channel hybrid photodiodes (HPDs).
-
-The HB has an inner radius of 1777 mm and an outer radius of 2876.5 mm and has 17 scintillator layers and is composed of 2 half barrels covering a range of  $-1.4<\eta<1.4$, resulting in a total of 2304 towers.
-The HO covers a region of $-1.26<\eta<1.26$ and it contains scintillators with a thickness of 10 mm, lining the outside of the outer vacuum tank of the solenoid.
-The HE consists of 14 towers with a range of $1.3<\eta<3.0$.
-It is made entirely of brass plates, with a thickness of 78 mm.
-
-The HF calorimeter has a range of $3<\eta<5$ and is made of steel and quartz fibers.
-It is located 11.2 m from the interaction point, providing fast collection of Cherenkov light.
-The modules of the HF are constructed of 18 wedges arranged in a non-projective geometry, Figure \ref{wedge} shows and $r-\phi$ view of an HF wedge.
-The quartz fibers have a diameter of 0.6 mm and are placed 5 mm apart, forming a square grid.
-Two different lengths are used for the quartz fibers, 1.43 m and 1.65, effectively creating 2 longitudinal samplings.
-In total, 13 towers exist in $\eta$ with a size of $\Delta\eta\approx 0.175$, except for the lowest and highest-$\eta$ towers, which have a size of $\Delta\eta\approx 0.1$ and $\Delta\eta\approx 0.3$ respectively.
-A $\Delta\phi\approx 10^{\circ}$ exists for all towers but the highest-$\eta$ tower, which has a segmentation of $\Delta\phi\approx 20^{\circ}$.
-In total the HF calorimeter consist of 900 towers and 1800 channels \cite{cms-manual}.
+The CMS Phase-1 pixel detector is built from 1856 segmented silicon sensor modules, where 1184 modules are used in the barrel pixel detector (BPIX) and 672 modules are used for the forward disks (FPIX).
+Each module consists of a sensor with 160$\times$416 pixels connected to 16 readout chips (ROCs).
+In total there are 124 million readout channels \cite{phase1_Pixel_Detector}.\\
+The CMS Phase-1 pixel detector uses a similar module design as the BPIX modules of the original detector.
+A pixel detector module is built from a planar silicon sensor with a size of 18.6 $\times$ 66.6 $\text{mm}^{2}$ (active area of 16.2 $\times$ 64.8 $\text{mm}^{2}$), bump-bonded to an array of 2$\times$8 ROCs.
+Each ROC is segmented into 4160 readout channels and reads out the pulse height information for each pixel.
+The standard pixel size is 100$\times$150 $\mu m^{2}$, as in the original pixel detector.% Since two ROCs can only be placed at some minimum distance from each other, pixels along the ROC boundaries have twice the area and those at the corners have four times the area of a standard pixel.
+In order to simplify module production and maintenance, the same rectangular module geometry is used for the BPIX and FPIX detectors.
+Drawings of the CMS Phase-1 pixel detector modules are shown in Fig. \ref{modules_drawing} \cite{phase1_Pixel_Detector}.\\
 \begin{center}
-
-\begin{figure}
+  \begin{figure}[ht]
     \centering
-    \includegraphics[scale=0.5]{Chapter2/hfes.PNG}
-    \caption[Hadron forward wadge.]{And r-$\phi$ view of a HF wadge.}
-    \label{wedge}
+    \includegraphics[scale=.2]{Chapter2/modules_drawing.png}
+    \caption[Pixel detector modules]{ Drawings of the pixel detector modules for BPIX L1 (left), BPIX L2–4 (middle), and the FPIX detector (right)\cite{phase1_Pixel_Detector}.}
+    \label{modules_drawing}
   \end{figure}
 \end{center}
-\subsection{Muon Detector}
-The last subdetector of the CMS experiment is the muon detector system located in the magnet return yokes.
-The muon system consists of 3 types of gaseous detectors, used to detect muons and their momenta.
-These detectors are:  the drift tube chambers (DT), the cathode strips chambers (CSC) and the resistive plate chamber (RPC).
-These detector are distributed across the 2 central parts of the muon detector, the barrel and endcap sessions, with a coverage of $|\eta|<1.2$ and $|\eta|<2.4$ respectively.
-The distribution of these detectors is shown in Figure \ref{Muons}.
-\begin{figure}[H]
+
+In the BPIX detector, the orientation of the sensor surface of the modules is parallel to the magnetic field.
+The pixels are oriented with the long side parallel to the beam line.
+In the FPIX detector, the modules in the outer rings are rotated by 20$^{\circ}$ in a turbine-like geometry.
+However, to obtain optimal resolution in both the azimuthal and radial directions for the inner ring, the modules in the inner ring are arranged in an inverted cone array tilted by 12$^{\circ}$ with respect to the beam line, combined with the 20$^{\circ}$ rotation.
+The sensor orientation in the FPIX detector is such that the long side of the pixel is in the radial direction \cite{phase1_Pixel_Detector}.
+
+The sensors of the BPIX and FPIX detectors were produced by different companies in order not to depend on a single source.
+The concept and design were tailored to each vendor's production process, leading to two different sensor types.
+Both types of sensors are made of silicon and follow the n-in-n approach, with strongly n-doped (n+) pixelated implants on an n-doped silicon bulk and a p-doped back side.
+In a reverse-bias configuration, the n+ implants collect electrons \cite{phase1_Pixel_Detector}.\\
+%%%%%%
+%In the pixels, the interface between the silicon substrate and the silicon oxide carries a slight positive charge which increases by orders of magnitudes after ionizing radiation.
+This causes a conducting electron accumulation layer, which may short the electron-collecting electrodes.
+Therefore an n-side isolation is required.
+The technical implementation of this isolation has a large impact on the pixel cell layout and was chosen to best match the techniques offered by the two vendors.
+A Photograph of four pixel cells on a BPIX sensor and schematic of two pixel cells on an FPIX sensor is shown in Fig.
+\ref{photo_pixel}.% In the case of the BPIX sensors, the n-side isolation was implemented through the moderated p-spray technique with a punch-through biasing grid (Fig \ref{photo_pixel} left).
+The FPIX sensors use open p-stops for n-side isolation.
+Each pixel is surrounded by an individual p-stop which has an opening on one side (Fig.
+\ref{photo_pixel} right) \cite{phase1_Pixel_Detector}.
+\begin{center}
+  \begin{figure}[ht]
     \centering
-    \includegraphics[scale=.45]{Chapter3/dt.png}
-    \caption[One quarter of the CMS muon system. ]{The diagram shows the layout of one quarter of the muon system at CMS \cite{cms-manual}.}
-    \label{Muons}
-\end{figure}
-
-The barrel DT detector  has a coverage of $|\eta|<1.2$, and consist of 250 chambers arranged in 4 layers inside the magnet return yoke, at a radii of approximately 4, 4.9, 5.9 and 7 meters from the beam line.
-The basic element of the DT detectors are cells, with a transverse size of $42\times 13$ $mm^2$, filled with a gas mixture of $85\%$ Ar and $15\%$ $CO_2$ \cite{cms7}.
-The cells have a gold-plated stainless steel anode wire, connected at their center.
-The wire has a diameter of 50 $\mu m$ and it operates at a voltage of +3600 V.
-\\
-The barrel detectors are divided into 12 sectors, each covering $30^{\circ}$ in the azimuthal direction.
-
-Installed on the encap regions, the CSC chambers are installed, covering a range of $0.9<\eta<2.4$.
-Their fast response time and their tolerance to non-uniform magnetic fields, makes the perfect for the high muon rates and background levels found in this region.
-The 6 layers of the CSC measure the muon positions in 2 coordinates.
-The cathode strips provide precise measurements on the r-$\phi$ bending plane, while the wires provide a coarse measurement in the radial direction.
-Each layer of the CSC contains 80 cathode strips with anode wires, of diameter 50 $\mu m$, running almost parallel to the cathodes.\\
-In total, the 2 encaps are comprised of 468 CSC chambers, filled with a gas mixture of $50\%$ $CO_2$, $40\%$ Ar and $10\%$ $CF_4$ \cite{cms7}.
-
-The RPC detectors is located in the barrel and encap regions of the muons system, complementing the DT and CSC detectors.
-It covers a region of $|\eta|<1.6$ and it provides fast, independent trigger events.
-The RPC are double-gap chambers, each gap consisting of 2 mm thick resistive bakelite plates, separated by a 2 mm thick gas gap.
-Readout strips are aligned in the $\eta$ direction in between the gas gaps.
-The gaps are filled with a gas mixture of $95.2\%$ Freon $(C_2H_2F_4)$, $4.5\%$ isobutane $(i-C_4H_{10})$, and $0.3\%$ sulphur hexafluoride $(SF_6)$.
-Water vapor is added to reach a mixture humidity of $40\%$-$50\%$ \cite{cms7}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{High Luminosity LHC}
-The LHC is the most powerful particle collider in the world, and it is to remain the most powerful for the next two decades.
-To ensure this, the LHC will receive major upgrades during the 2020s, to increase its luminosity by a factor of 5 beyond the original design.
-About 10 years will be needed to study and prototype the technologies required for the new High Luminosity LHC (HL-LHC).
-The HL-LHC project was created at the end of  2010 by CERN, as a response to the  European strategy for particle physics, to fully exploit the capabilities of the LHC.
-The project was approved on 30 of May of 2013 by the CERN council in charge at the time.
-For the next decade the HL-LHC is the major construction project of CERN.
-Several new technologies will be used to achieve the luminosity goal, some of them include: superconducting magnets capable of producing a magnetic field of 11 to 12 T, superconducting  cavities, compact and with phase control, for beam rotation, long high-power superconducting links with zero energy dissipation and new technologies for beam collimation \cite{cern3}.
-\begin{center}
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=1.5]{Chapter2/schedulelhc.jpg}
-    \caption[schedule of the LHC.]{The past and future schedule of the LHC.
-The red line corresponds to the center-of-mass-energy of the pp collisions, while the light-red line shows the expected luminosity \cite{schedule}.}
-    \label{programing}
+    \includegraphics[scale=.2]{Chapter2/pixel_foto.png}
+    \caption[Photograph of four pixels cells on a BPIX sensor and schematic of two pixel cells on an FPIX sensor]{ Photograph of four pixel cells on a BPIX -sensor (left) and schematic of two pixel cells on an FPIX sensor (right) \cite{phase1_Pixel_Detector}.}
+    \label{photo_pixel}
   \end{figure}
 \end{center}
-Figure \ref{programing} shows the  schedule of the LHC up until 2025, where the new phase of the LHC, the HL-LHC, will  begin.
-After reaching a center-of-mass-energy of 13 during 2015, the LHC has doubled the luminosity for which it was designed, as  of the end of Run 2.
-
-The main objectives of the HL-LHC is to reach a peak luminosity of 5 to $7.5\times10^{34}$ $cm^{-2}s^{-1}$, and an integrated luminosity of 250 $fb^{-1}$ per year, with the goal of reaching a total integrated luminosity of 3000 $fb^{-1}$, in the first 12 years of the machines operation.
-For this, intensive studies have, and are, being conducted to determine the hardware and the configuration needed to achieve these goals.\\
-The new hardware of the HL-LHC is to be installed during the third long shutdown (LS3).
-To ensure that the integrated luminosity goal is met, all equipment is being designed with a $50\%$ margin in regards to the required luminosity.
-This means that the High Luminosity LHC can reach peak luminosity valued of 7 to $7.5\times10^{34}$ $cm^{-2}s^{-1}$, this will mean an increase in total pileup (rate of pp collision per bunch crossing) up to 200 \cite{cern3}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Tracker End-Cap Pixel luminometer}
-
-Along with the new HL-LHC upgrade, several upgrades will come to the CMS detector to accommodate the new luminosity and pileup requirements.
-The tracker, muon end caps, trigger and beam radiation protection are just a few of the new upgrades scheduled for the CMS detector.
-However, the focus of this work will be solely on the tracker upgrades, more specifically, the inner  tracker end cap pixel (TEPX) luminometer.
-
-For Phase-2 of the CMS tracking the entire existing pixel and strip tracker will be replaced.
-Figure \ref{TEPXl} shows the r-z layout of the three sections of the Phase-2 inner tracker: the  tracker barrel pixel (TBPX), composed of four cylindrical layers of modules, the tracker’s forward (TFPX) and the tracker end-cap (TEPX) pixel detectors, made of 8 and 4 disks of pixel modules respectively.
-The new tracker will include: increased granularity, forward acceptance and radiation hardness as well as compatibility with longer trigger latency and higher data rates.
-The silicon pixel modules will have a thickness of 100-150 $\mu m$, while the pixel cells will have an area of 2500 $\mu m^2$ ($25\times 100$ $\mu m^2$) \cite{CERN-LHCC-2017-009}\cite{DelBurgo:2706637}.
-Two types of modules will be used in the inner tracker, modules with 2 and 4 pixel chips.
-The modules will be arranged in $2\times1$ and $2\times 2$, these modules are depicted as green and yellow respectively in  Figure \ref{TEPXl}.
-TBPX and TFPX will be composed of both types of modules, while TEPX will only use $2\times 2$ modules \cite{DelBurgo:2706637}.
+%The calibration procedure includes the adjustment of phases for programming and readout signals, the determination and equalization of pixel charge thresholds, the calibration of pixel charge measurements, as well as the masking of non-working channels \cite{phase1_Pixel_Detector}.\\
+%By design, the position resolution of the CMS Phase-1 pixel detector depends strongly on the charge sharing between pixels.
+The pixel shape of 100 $\times$ 150$\mu\text{m}^{2}$ means that in order to obtain an optimal position measurement in the azimuthal direction (the bending plane for charged particle tracks within the CMS magnet) the charge width  has to be of the order of the pixel pitch, that is 100$\mu \text{m}$.
+The charge width is defined as the projection on the module coordinates of the area where the charge is collected on the detector surface.
+In the strong magnetic field of 3.8 T provided by the CMS magnet, the Lorentz angle (LA) for the drifting electrons has a value of about 27$^{\circ}$.
+With the sensor thickness of 285 $\mu \text{m}$, this produces a charge width of 145 $\mu \text{m}$, which is sufficient to share the charge between at least two pixels \cite{phase1_Pixel_Detector}.\\
+The most probable value of energy deposition for normally incident minimum-ionizing particles (MIPs) in a silicon sensor with a thickness of 285 $\mu \text{m}$ corresponds to approximately 21000 electrons.
+This charge is frequently spread over more than one pixel due to Lorentz drift and diffusion of collected electrons, leading to charge clusters.
+In the track reconstruction step, hit pixels are combined to form clusters from neighboring pixels.
+The charge measured within the cluster corresponds to the charge deposited by a single charged particle \cite{phase1_Pixel_Detector}.
+\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%% LO DE NOISE AND TRESHOLDS LO MUEVO AL SIG. CAPITULO%%%%%%%%%%%%%%%%
+%The LA depends strongly on the bias voltage of the sensor and weakly on the temperature. It is also affected by the
+%The lowest possible value that can be chosen for the threshold of a given pixel is an important performance parameter, since thresholds directly influence the position resolution.
+The strategy adopted is to adjust each ROC to its lowest possible threshold, which results in a non-uniform threshold distribution between different ROCs (with a standard deviation of about 150-200$e^{-}$).
+Within ROCs, pixels are trimmed to a common threshold using the available 3-bit adjustment in each pixel (resulting in an average standard deviation per ROC of about 75-100$e^{-}$).
+The ROCs in BPIX L1 had to be adjusted to thresholds higher than the possible minimum due to the larger cross-talk noise.\\
+%The threshold and the noise are determined by recording the S-curves (as described inSec.
+3.6) for a number of pixels per ROC.
+A subset of 81 pixels per ROC was found to be sufficient to determine the average threshold and noise values per ROC.
+After the initial adjustment of the pixel thresholds, periodic re-adjustments are needed.
+Radiation influences various parameters of the ROC, which results in threshold shifts.
+The pixel thresholds are closely monitored over the course of the data-taking period, and re-adjusted if necessary.
+During the technical stops in 2017 and at the beginning of 2018, the thresholds have been re-optimized.
+The BPIX L2-4 thresholds stayed roughly constant at about 1400 $e^{-}$, similarly for the FPIX detector at about 1500 $e^{-}$.
+For BPIX L about 2600 $e^{-}$ in 2017.
+After optimization in 2018, the L1 thresholds were about 2200 $e^{-}$.\\
+%With these pixel thresholds the number of noise hits was very low, below 10 pixels per bunch crossing per layer, resulting in a per pixel noise hit probability of less than  $10^{-6}$.
+Individual pixels that showed a hit probability exceeding 0.1\% were masked during operation.
+The total fraction of masked pixels was less than 0.01\%
+%The hit efficiency is the probability to find a cluster in a given silicon sensor that has been traversed by a charged particle <-- from 
+%%%%% HEREEE
+%\subsection{Strip tracker}
+The rest of the tracker system surrounds the Pixel detector: the Strip tracker, as can be seen in Fig.
+\ref{strip_layout}.
+It is composed of for subsystems: the Tracker Inner Barrel (TIB) and Disks (TID), the Tracker Outer Barrel (TOB) and The Tracker EndCaps (TEC).
+TIB and TID are composed of four barrel layers, supplemented by three disks at each end; TOB consists of six barrel layers; Each TEC is composed of nine disks, containing up to seven concentric rings of silicon strip modules.
+The strip tracker has in total  15 148 silicon modules, which cover an active area of about 198$\text{m}^{2}$ and have 9.3 million strips \cite{CMS_Exp_2008}.
+%Original text:
+% The strip tracker is composed of for subsystems: the Tracker Inner Barrel (TIB) and Disks (TID), the Tracker Outer Barrel (TOB) and The Tracker EndCaps (TEC).
+Fig.
+\ref{strip_layout} shows an schematic cross section through the CMS trackers with the four subsystems.
+The TIB and TID cover $ r <\text{55 cm}$ and $|z| <\text{118 cm} 118$, and are composed of four barrel layers, supplemented by three disks at each end.
+The TOB covers $r > \text{55 cm}$ and $|z| < \text{118 cm} $and consists of six barrel layers providing position measurements in $r\phi$ with a resolution of approximately 18–47$\mu \text{m}$.
+The TEC cover the region 124 $< |z|$ < 282 cm.
+Each TEC is composed of nine disks, each containing up to seven concentric rings of silicon strip modules, yielding a range of resolutions similar to that of the TOB \cite{CMS_Exp_2008}.\\ The strip tracker has in total  15 148 silicon modules, which cover an active area of about 198$\text{m}^{2}$ and have 9.3 million strips \cite{CMS_Exp_2008}.
 \begin{center}
-\begin{figure}[H]
+  \begin{figure}[ht]
     \centering
-    \includegraphics[scale=.2]{Chapter2/TEPX.png}
-    \caption[Diagram of the Phase-2 inner tracker upgrade.]{\textit{Lefts}: Diagram of the Phase-2 inner tracker upgrade.
-The last four yellow lines between 1700 mm and 2700 mm, correspond to the TEPX subdetector.
-\textit{Right}:  Front view of one of the disks of the TEPX subdetector \cite{DelBurgo:2706637}.}
-    \label{TEPXl}
+    \includegraphics[scale=.23]{Chapter2/strip_layout.png}
+    \caption[Schematic cross section through the CMS tracker]{Schematic cross section through the CMS tracker.
+Each line represents a detector module \cite{CMS_Exp_2008}.
+The Pixel tracker here is not the CMS Phase-1 pixel detector.}
+    \label{strip_layout}
   \end{figure}
 \end{center}
-For Phase-2 the TEPX portion of the tracker will be designated for tracking and luminosity measurements, while disk 4 ring 1 (TEPXD4R1) of the detector will designated for luminosity measurements only.
-The TEPX detector is located at each extremity of the tracker of the CMS detector, with a range  from 175 cm to 265 cm on the $|z|$ direction and a radius  between 63 mm and 255 mm.
-The detector is composed of 4 double sided disks, each one made of 5 concentric rings of pixel modules.
-To guarantee hermetic coverage, each ring has a different number of pixel modules.
-TEPX is composed of 800 million pixels, distributed over an area of 2$m^2$, and will operate at trigger frequency of 75KHz during physics runs.
-Table \ref{rings} shows the number of modules per ring, as well as the radius of each ring.
 
-\begin{table}[H]
-\centering
-\caption[Radius and number of pixel modules that comprise the rings of the TEPX subdetector.]{ Table shows the inner ($r_{in}$) and outer ($r_{out}$) radius, as well as the number of pixel modules that comprise each ring of each disk of the TEPX subdetector}
-\scalebox{.8}{
-\begin{tabular}{|l | c | c | c |c|c|}
-\hline
- Ring & 1& 2&3&4&5   \\
-\hline
-$r_{in}$ (mm) & 62.9&100.55 &137.85 &174.45 &210.5\\
-\hline
-$r_{out}$ (mm)&107.69 &144.99 &182.09 &218.56 &254.51 \\
-\hline
- No. of modules&20 &28 &36 &44&48 \\
-\hline
-\end{tabular}}
-\label{rings}
-\end{table}
+%\subsection{Hit/Cluster reconstruction in the Pixel detector}
+The first step of the track reconstruction process is referred to as local reconstruction.
+It consists of the clustering of zero-suppressed signals above specified thresholds in pixel channels into hits, and then estimating the cluster positions and their uncertainties defined in a local orthogonal coordinate system $(u,v)$ in the plane of each sensor.
+The pixel sensor consists of 100 $\times$ 150$\mu \text{m}^{2}$ pixels with the u-axis oriented parallel to the shorter pixel edge.
+Offline, pixel clusters are formed from adjacent pixels, including both side-by-side and corner-by corner adjacent cells.
+Each cluster must have a minimum charge equivalent to 4000 electrons \cite{Track_Reco_2014}.
+%Two algorithms are used to determine the position of pixel clusters.
+A fast algorithm, referred to as ``First-pass hit reconstruction'' ,is used during track seeding and pattern recognition, and a more precise algorithm, referred to as ``Template-based hit reconstruction'', is  based on cluster shaped and is used in the final track fit \cite{Track_Reco_2014} .\\
+%1st algorithm
+%The First-pass hit reconstruction consists of the following.
+The position of a pixel cluster along the transverse $(u)$ and longitudinal $(v)$ directions in the local orthogonal system are estimated independently with the same procedure.
+The cluster is projected onto the $u$-axis by summing the charge collected in pixels with the same $u$-coordinate.
+The result is referred to as a projected cluster.
+For projected clusters that are only one pixel large, the $u$-position is given by the centre of that pixel, corrected for the Lorentz drift of the collected charge in the CMS magnetic field.
+For larger projected clusters, the hit position is determined using the relative charge in the two pixels at each end of the projected cluster \cite{Track_Reco_2014}.\\
+% For the pixel barrel, the Lorentz shift is approximately 59µm
+%2nd algorithm
+%The template-based hit reconstruction comes from the fact that the high level of radiation exposure of the pixel detector can affect significantly the collection of charge by the pixels during the detector’s useful life.
+This degrades particularly the performance of the standard hit reconstruction algorithm mentioned before.\\% In the template-based reconstruction algorithm, the observed distribution of the cluster charge is compared to expected projected distributions, called templates, to estimate the positions of hits.
+The templates are generated based on a large number of simulated particles traversing pixel modules, which are modelled using the detailed simulation of pixel sensors (PIXELAV).
+Since the PIXELAV program can describe the behaviour of irradiated sensors, new templates can be generated over the life of the detector to maintain the performance of the hit reconstruction.
+To allow the template-based algorithm to be applied to tracks crossing the silicon at various angles, different sets of templates are generated for several ranges of the angle between the particle trajectory and the sensor \cite{Track_Reco_2014}.\\
+%The track reconstruction is done by using the hits, obtained from the local reconstruction, to obtain estimates for the momentum and position parameters of the charged particles responsible for the hits (tracks).
+%NOTA: En la seccion 10.5 del paper de phase 2 pixel, menciononan cuantos electrones se porducen aprox. Algo de ionixacion minima
+%10.4 tambien
 
-The innermost ring of the last disk, disk 4 ring 1 (TEPXD4R1), lies beyond a pseudorapidity of $|\eta|=4$ and due to the low number of tracking points in this region, this ring will be designated for luminosity measurements only.
-The ring consists of 20 modules, and it has an inner radius of 62.9 mm and an outer radius of  107.69 mm.
-Finally, the luminometer may run at a trigger frequency of 825kHz to several MHz.\\
-Luminosity measurements with the TEPX's detectors will be carried out using the Pixel cluster counting (PCC) method described in the next chapter.
+%%%%%%%%%%%%%% FOLLOWING SECTIONS ARE SUMMARIZED ~ 2ND PARAGRAPH OF THIS CHAPTER%%%%%%5
+%%%%\section{Electromagnetic calorimeter}
+%%%%
+%%%%The electromagnetic calorimeter of CMS (ECAL) is a hermetic homogeneous calorimeter made of 61 200 lead tungstate (PbWO4) crystals mounted in the central barrel part, closed by 7 324 crystals in each of the two endcaps.
+A preshower detector is placed in front of the endcap crystals.
+Avalanche photodiodes (APDs) are used as photodetectors in the barrel and vacuum phototriodes (VPTs) in the endcaps.
+The use of high density crystals has allowed the design of a calorimeter which is fast, has fine granularity and is radiation resistant, all important characteristics in the LHC environment \cite{CMS_Exp_2008}.\\
+%%%%The barrel section (EB) has an inner radius of 129 cm.
+It is structured as 36 identical “supermodules,” each covering half the barrel length and corresponding to a pseudorapidity interval of 0 $< |\eta| <$ 1.479.
+The crystals are quasi-projective (the axes are tilted at 3$^{\circ}$ with respect to the line from the nominal vertex position) and cover 0.0174 (i.e.
+1$^{\circ}$) in$ \Delta \varphi$ and $\Delta \eta$.
+The crystals have a front face cross-section of $\approx$22$\times$22 mm$^{2}$ and a length of 230 mm \cite{TDR_CMS}.\\
+%%%%The endcaps (EE), at a distance of 314 cm from the vertex and covering a pseudorapidity range of 1.479 $< |\eta| <$ 3.0, are each structured as 2 “Dees”, consisting of semi-circular aluminium plates from which are cantilevered structural units of 5$\times$5 crystals, known as “supercrystals.” The endcap crystals, like the barrel crystals, off-point from the nominal vertex position, but are arranged in an x-y grid (i.e.
+not an $\eta - \varphi$ grid).
+They are all identical and have a front face cross section of 28.6$\times$28.6 mm2 and a length of 220 mm.
+A preshower device is placed in front of the crystal calorimeter over much of the endcap pseudorapidity range.
+The active elements of this device are 2 planes of silicon strip detectors, with a pitch of 1.9 mm, which lie behind disks of lead absorber \cite{TDR_CMS}.
+Fig.
+\ref{ECAL} shows a transverse section of the ECAL.
+%%%%
+%%%%
+%%%%\begin{center}
+%%%%  \begin{figure}[ht]
+%%%%    \centering
+%%%%    \includegraphics[scale=.25]{Chapter2/ECAL.png}
+%%%%    \caption[Electromagnetic Calorimeter]{Transverse section of the  Electromagnetic calorimeter, showing geometrical configuration \cite{TDR_CMS}.}
+%%%%    \label{ECAL}
+%%%%  \end{figure}
+%%%%\end{center}
+%%%%
+%%%%
+%%%%\section{Hadron calorimeter}
+%%%%The ECAL is surrounded by a brass/scintillator sampling hadron calorimeter (HCAL) with coverage up to $|\eta|<$3.0.
+The scintillation light is converted by wavelength-shifting (WLS) fibres embedded in the scintillator tiles and channeled to photodetectors via clear fibres.
+This light is detected by photodetectors (hybrid photodiodes, or HPDs) that can provide gain and operate in high axial magnetic fields.
+This central calorimetry is complemented by a tail-catcher in the barrel region (HO) ensuring that hadronic showers are sampled with nearly 11 hadronic interaction lengths.
+Coverage up to a pseudorapidity of 5.0 is provided by an iron/quartz-fibre calorimeter.
+The Cerenkov light emitted in the quartz fibres is detected by photomultipliers \cite{CMS_Exp_2008}.
+Fig.
+\ref{HCAL} shows a longitudinal view of the CMS detector showing the locations of the HCAL subsystems.\\
+%%%%The Hadron Barrel (HB) is a sampling calorimeter covering the pseudorapidity range $|\eta|<$ 1.3.
+The HB is divided into two half-barrel sections, each half-section being inserted from either end of the barrel cryostat of the superconducting solenoid and subsequently hung from rails in the median plane.
+The hadron calorimeter endcaps (HE) cover a substantial portion of the rapidity range, 1.3 $< |\eta| <$ 3 (13.2\% of the solid angle), a region containing about 34\% of the particles produced in the final state.
+In the central pseudorapidity region, the combined stopping power of EB plus HB does not provide sufficient containment for hadron showers.
+To ensure adequate sampling depth for $|\eta | <$ 1.3, the hadron calorimeter is extended outside the solenoid with a tail catcher called the HO or outer calorimeter.
+The forward calorimeters (HF) ensure full geometric coverage for the measurement of the transverse energy in the event.
+The calorimeter consists of a steel absorber structure that is composed of 5 mm thick grooved plates.
+The detector is functionally subdivided into two longitudinal segments.
+Half of the fibres run over the full depth of the absorber (165 cm )while the other half starts at a depth of 22 cm from the front of the detector.
+An even higher forward coverage is obtained with additional dedicated calorimeters CASTOR (Centauro And Strange Object Research) and ZDC (Zero degree calorimeter) and with the TOTEM (experiment TOTal Elastic and diffractive cross section Measurement) tracking detectors \cite{CMS_Exp_2008}.
+%%%%
+%%%%\begin{center}
+%%%%  \begin{figure}[ht]
+%%%%    \centering
+%%%%    \includegraphics[scale=.3]{Chapter2/HCAL.png}
+%%%%    \caption[Hadron Calorimeter]{ Longitudinal view of the CMS detector showing the locations of the hadron barrel (HB), endcap (HE), outer (HO) and forward (HF) calorimeters  \cite{CMS_Exp_2008}.}
+%%%%    \label{HCAL}
+%%%%  \end{figure}
+%%%%\end{center}
+%%%%
+%%%%
+%%%%\section{Muon system}
+%%%%
+%%%%After the HCAL and the 13-m-long, 6-m-inner-diameter, 4-T superconducting solenoid, the muons detector system is placed.
+The CMS muon system is designed to have the capability of reconstructing the momentum and charge of muons over the the entire kinematic range of the LHC; CMS uses 3 types of gaseous particle detectors for muon identification.
+Due to the shape of the solenoid magnet, the muon system was naturally driven to have a cylindrical, barrel section and 2 planar endcap regions, where are distributed three subsystems: the Barrel Drift Tube (DT), the Cathode Strip Chambers (CSC) and the Resistive Plate Chambers (RPC) \cite{CMS_Exp_2008}.
+A schematic diagram of the CMS detector showing the three subsystems is shown in figure \ref{Muon_detector}.
+\\
+%%%%The barrel DT chambers cover the pseudorapidity region $|\eta| <$ 1.2 and are organized into 4 stations interspersed among the layers of the flux return plates.
+The first 3 stations each contain 8 chambers, in 2 groups of 4, which measure the muon coordinate in the $r- \varphi$ bending plane, and 4 chambers which provide a measurement in the $z$ direction, along the beam line.
+The fourth station does not contain the $z$-measuring planes \cite{CMS_Exp_2008}.\\
+%%%%In the 2 endcap regions of CMS,  the muon system uses cathode  CCS.
+The  CSCs identify muons between $|\eta|$ values of 0.9 and 2.4.
+There are 4 stations of CSCs in each endcap, with chambers positioned perpendicular to the beam line and interspersed between the flux return plates.
+The cathode strips of each chamber run radially outward and provide a precision measurement in the $r-\varphi $ bending plane.
+The anode wires run approximately perpendicular to the strips and are also read out in order to provide measurements of $\eta$ and the beam-crossing time of a muon.
+Each 6-layer CSC provides robust pattern recognition for rejection of non-muon backgrounds and efficient matching of hits to those in other stations and to the CMS inner tracker \cite{CMS_Exp_2008}.\\
+%%%%A complementary, dedicated trigger system consisting of RPC was added in both the barrel and endcap regions.
+The RPCs provide a fast, independent, and highly-segmented trigger with a sharp $p_{T}$ threshold over a large portion of the rapidity range  ($|eta| <$ 1.6) of the muon system.
+A total of 6 layers of RPCs are embedded in the barrel muon system, 2 in each of the first 2 stations, and 1 in each of the last 2 stations \cite{CMS_Exp_2008}.
+%%%%
+%%%%
+%%%%\begin{center}
+%%%%  \begin{figure}[ht]
+%%%%    \centering
+%%%%    \includegraphics[scale=.3]{Chapter2/MuonDetector_Layout.png}
+%%%%    \caption[Muon Detector]{ An $R-z$ cross section of a quadrant of the CMS detector with the axis parallel to the beam ($z$) running horizontally and the radius ($R$) increasing upward.
+The locations of the various muon stations are shown.
+The drift tube stations (DTs) are labeled MB (“Muon Barrel”) and the cathode strip chambers (CSCs) are labeled ME (“Muon Endcap”).
+Resistive plate chambers (RPCs) are mounted in both the barrel and endcaps of CMS, where they are labeled RB and RE, respectively \cite{MuonDetPerf_CMS}.}
+%%%%    \label{Muon_detector}
+%%%%  \end{figure}
+%%%%\end{center}
+%%%%
+
+\subsection{CMS Luminometers}
+Various systems are used for measuring luminosity at CMS.
+The Pixel Luminosity Telescope (PLT) and Fast Beam Conditions Monitor (BCM1F) are dedicated systems for luminosity measurement, while the hadronic forward calorimeter (HF) uses a dedicated readout on an existing system; these three use a separate data acquisition (DAQ) system, BRILDAQ, which operates independently of the main CMS readout \cite{pas_18}.\\
+The PLT uses silicon pixel sensors arranged into 16 “telescopes”, each having three sensor planes arranged nearly parallel to the beam pipe, where the rate of “triple coincidences” is measured; a hit is observed in all three planes.\\
+BCM1F consists of a total of 24 sensors mounted on the same carriage as the PLT, consisting of a total of 10 silicon sensors, 10 polycrystalline diamond (pCVD) sensors, and 4 single-crystal diamond (sCVD) sensors.\\
+The HF luminosity measurement uses a dedicated readout system installed in the HF calorimeter.
+Only two HF rings are used for luminosity measurement, to ensure relatively uniform occupancy.
+Two algorithms are available: the first relies on the fraction of occupied towers (HFOC), and the second is based on the sum of the transverse energy ET (HFET).\\
+In addition other methods that uses data from existing parts of the CMS detector performs a luminosity measurement using the main CMS DAQ system.
+One of them is the drift tube luminosity (DT) which uses the rate of muon track stubs in the muon barrel track finder.
+Also, the RAMSES detectors, a CERN radiation and environmental monitoring sytem, although not being designed as a luminometer does function quite well as a luminosity measurement; it uses the rate observed in the detectors (primarily photons within the energy range of 50 keV to 7 MeV).\\ Other method is the pixel cluster counting (PCC), which will be described with more detail in chapter 3.

### 2022-12-29 tesis_Rodolfo/Chapter3/chapter3.tex
Rodolfo Thesis

@@
-\chapter{ Luminometer system and calibration description}
+\chapter{Luminosity  Measurement and Calibration}
+\label{ch3}
+%%%%%%%%%%%%%%Introduction%%%%%%%%%%%%%%%%%%%%
 
-%%%%Introduction%%%%%%%%%%%%%%%%%%%%5
-
-A total of seven systems are used for measuring luminosity at CMS, being the PCC one of them.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Pixel Clusters and the PCC method}
-
-Luminosity measurements at CMS are provided by the several luminometers in the detector.
-Each luminometer measures the event rate by reading out a specific quantity of objects observed by the detector, These can be for example clusters, coincidences or tracks.
-For the TEPX luminometers these objects are pixel clusters and coincidences, using the pixel cluster counting (PCC) method to provide offline luminosity measurements.
-This method was one of the main source of luminosity measurements for CMS, during the 2016-2018 data taking period, and it is expected to be the same for the Phase-2 upgrade.\\
-The clustering algorithm is very complex, but striping it down to the most simple example: the algorithm considers a cluster of pixels only if two hits, or more,  activate neighboring pixels horizontally, vertically or diagonally, within the same module.
-Figure\ref{pixclust} shows an example of this.
-\begin{figure}[H]
-\begin{minipage}[b]{0.5\linewidth}
-\centering
-\begin{tikzpicture}
-    [%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-        box/.style={rectangle,draw=black,thick, minimum size=1cm},
-    ]%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\foreach \x in {0,1,...,4}{
-    \foreach \y in {0,1,...,4}
-        \node[box] at (\x,\y){};
-}
-
-\node[box,fill=red  ] at (1,4){};  
-\node[box,fill=red ] at (0,4){};  
-\node[box,fill=red ] at (0,3){}; 
-\node[box,fill=red  ] at (1,3){};
-\end{tikzpicture}
-\end{minipage}
-\begin{minipage}[b]{0.5\linewidth}
-\centering
-\begin{tikzpicture}
-    [%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-        box/.style={rectangle,draw=black,thick, minimum size=1cm},
-    ]%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\foreach \x in {0,1,...,4}{
-    \foreach \y in {0,1,...,4}
-        \node[box] at (\x,\y){};
-}
-
-\node[box,fill=red  ] at (0,4){};  
-\node[box,fill=red ] at (2,4){};  
-\node[box,fill=red ] at (1,1){}; 
-\node[box,fill=red ] at (4,2){}; 
-\end{tikzpicture}
-\end{minipage}
-\caption[Pixel cluster selection algorithm]{The figure shows a representation of the pixel modules, \textit{left}: four hits (red) on four neighbouring pixels, these is considered a pixel cluster by the clustering algorithm.
-\textit{right}: the hits activate random pixel in the module, these will not be considered as a cluster by the clustering algorithm.}
-\label{pixclust}
-\end{figure}
-A hit occurs when a charged particle passes through a silicon pixel, depositing an amount of energy in the pixel.
-The PCC method takes advantage of the high densities of pixels, and the relative low occupancy of the CMS tracker, to provide precise luminosity measurements, with good stable measurements over time.
-The number of pixel clusters activated, per bunch crossing, is a linear function of the number of proton-proton interactions per bunch crossing (pileup).
-During several zero-bias events, where the only requirement is that the bunches pass through one another on the interaction point, a mean number of pixel clusters, $\left\langle N_{\text {cluster }}\right\rangle
-$,is activated:
-\begin{equation}
-\left\langle N_{\text {cluster }}\right\rangle\equiv\left\langle N_{\text {cluster/int}}\right\rangle\mu
-\label{pcc}
-\end{equation}
-where $\left\langle N_{\text {cluster/int}}\right\rangle$ is the mean number of clusters activated per interaction and $\mu$ is the pileup.
-Using equation \ref{pileup} and \ref{pcc}, a calibration constant between the mean number of pixel cluster and the instantaneous luminosity can be defined:
+The precision measurement of the luminosity delivered to the CMS by the LHC is important for a variety of reasons.
+Online, the luminosity measurement provides realtime feedback on the LHC performance and operation.
+Offline, the luminosity measurement is a crucial component of physics analysis, either for measuring the cross section of observed processes or for setting upper limits in searches for processes BSM \cite{pas_18}.\\
+A total of seven systems are used for measuring luminosity at CMS.
+These systems are referred to as luminometers.
+Each luminometer reads out a rate of the specific quantities observed in the detector (hits, tracks, clusters, etc.).
+This rate, R, should be proportional to the instantaneous luminosity,$\mathcal{L}_{inst}$, with the constant of proportionality given by the visible cross section $\sigma_{vis}$ \cite{pas_18}:
 
 \begin{equation}
-    \left\langle N_{\text {cluster }}\right\rangle\equiv\frac{\sigma_{vis}}{f}\mathcal{L}_{ins}
+R=\mathcal{L}_{inst}\sigma_{vis}
+\label{lumi_exp_gen}
 \end{equation}
-where the calibration constant, $\sigma_{vis}$, is   
+
+The determination of $\sigma_{vis}$ is carried out through van der Meer (vdM) scans performed with a dedicated LHC machine setup, exploited by S.
+Van der Meer for luminosity measurements at ISR \cite{vdM_cal}.
+
+\section{Pixel Cluster Counting method}
+The Pixel Cluster Counting method exploits the very large number of pixels in the tracker of the CMS detector.
+At design luminosity of $10^{34}cm^{-2}s^{-1}$, the detector occupancy is less than 0.1\% on average (the average number of clusters per minimum bias interaction is about 50 and the average number of pixels per cluster is about 5) \cite{pas-13}.
+The very low occupancy leads to an excellent linear detector response with increasing LHC luminosity \cite{pas_18}.
+\\
+The PCC method uses the rate of pixel clusters in the CMS pixel detector to provide an offline luminosity measurement.
+Pixel clusters are formed from adjacent pixels, as mentioned in section \ref{pixel_clust_reco}.
+PCC measurement uses the data collected with the standard CMS trigger system with triggers requiring colliding bunches but not any specific event activity; this is referred as "zero-bias trigger'' \cite{pas_18}.\\
+Each bunch crossing gives rise to some number of pp interactions, with each such interaction resulting in some number of pixel clusters.
+If the average over several zero-bias events is taken, the mean number of pixel clusters per event is \cite{PCC_PAS_12_001}:
+
 \begin{equation}
-    \sigma_{vis}=\sigma_{tot}\left\langle N_{\text {cluster/int}}\right\rangle
+\left < N_{\text{cluster}} \right > = \left < N_{\text{pixel}/\text{interaction}} \right >  \left < N_{\text{interactions}} \right > \equiv \left < N_{\text{pixel}/\text{interaction}} \right > \mu
 \end{equation}
-The value of $\sigma_{vis}$ is determined using a van der Meer (vdM) scan, with 
-\begin{equation}
-    \sigma_{vis}= \frac{\left\langle N_{\text {cluster/vdM }}\right\rangle f }{\mathcal{L}_{ins/vdM}}
-\end{equation}
-where $\left\langle N_{\text {cluster/vdmM }}\right\rangle$ is the mean number of pixel cluster at the peak of the scan and $\mathcal{L}_{ins/vdM}$ is the instantaneous luminosity obtained in the scan \cite{CMS-PAS-LUM-12-001}.
+
+where in the last step, the average number of interactions per bunch crossing, pileup, is denoted by the symbol $\mu$.
 
@@
 
-\section{Calibration using the van der Meer method }
-The calibration of the luminometrs is done by performing van der Meer scans, where the goal is to determine the calibration constant $\sigma_{\text {vis}}$.\\
-In practice, the normalized bunch transverse distributions of each beam is not known, thus the overlap width integrals in \ref{lumy2} cannot be solved analytically.
-The vdM scans determines the valued of these integrals by separating the two beams and moving them across each other while measuring the resulting rates (Figure \ref{vdm1} (left) illustrates this process)
+\section{Luminosity calibration: van der Meer method}
+In the practice, as mentioned in chapter 1, the properties of the colliding beams are not know precisely, such as the bunch density profile, so that the integral in \ref{lumi_2} cannot be solved analytically.
+In LHC a experimental techinque know as vdM method is implemented  with a dedicated machine setup to bring the bunch density profiles close to Guassian distributions.\\
+The VdM scan method, %, exploited by S. Van der Meer for luminosity measurements at ISR  \cite{vdM_cal} and
+applied by LHC Experiments in Run 1 and Run 2, allows to measure and evaluate the integral over the proton bunch densities in eq.
+\ref{lumi_2}.
+For the vdM scan method to be applicable it is also assumed that the two bunch $\rho$ can be factorized into independent terms in x and y \cite{pas-15}.
+The value of the two beam overlap integrals in Eq.
+(2) is determined by varying the beam separation and measuring the resulting rates \cite{pas_18}:
+
 \begin{equation}
-    \int \rho_1(x)\rho_{2}(x)dx=\frac{R_{x}(0)}{\int R_{x}(\Delta x)d\Delta x}
+\int \rho_{x1}(x) \rho_{x2}(x) dx = \frac{R_{x}(0)}{\int R_{x}(\Delta) d\Delta}
 \end{equation}
-where $R_{x}(\Delta x)$ is the measured rate, when the beams are separated a distance $\Delta x$. Defining the beam overlap  width as
+
+where $R_{x}(\Delta)$ is the rate measured when the two beams are separated in x by a distance $\Delta$; a asimilar equation can be written in y.
+Then the beam overlap width $\Sigma_{x}$ (and similarly $\Sigma_{y}$) is defined as \cite{pas_18}:
+
 \begin{equation}
-\Sigma_{x}=\frac{1}{\sqrt{2\pi}}\frac{\int R_{x}(\Delta x) d\Delta x}{R_{x}(0)}
-\label{sigma2}
+\Sigma_{x}= \frac{1}{\sqrt{2\pi}} \frac{\int R_{x}(\Delta)d\Delta}{R_{x}(0)}
 \end{equation}
-doing the same can be done for $\Sigma_{y}$, equation \ref{lumy2} can be rewritten: 
+
+yielding the final expression for luminosity (for one single bunch):
+
 \begin{equation}
-    \mathcal{L}=\frac{N_1N_2N_p f}{2\pi\Sigma_x\Sigma_y}
+\mathcal{L}_{inst}=\frac{N_{1} N_{2}f}{2 \pi \Sigma_{x}\Sigma_{y}}
 \end{equation}
-Once measurements have been taken, the rate is plotted as a function of beam separation and a Gaussian-like function is fitted to the data, as shown id Figure \ref{vdm1} (right).
-Using this function, the integral in equation \ref{sigma2} can be solved and the overlap width determined.
-Using \ref{lumy0} and \ref{lumy2} the calibration constant $\sigma_{vis}$ can be determined:
+
+where $N_{1,2}$ are the particles per bunch (bunch current) and  $f= 11246$ Hz is the bunch orbit frequency around the LHC ring.\\
+This expression can be finally used in \ref{lumi_exp_gen} to get $\sigma_{vis}$:
+
 \begin{equation}
-    \sigma_{vis}=\frac{2\pi \Sigma_x\Sigma_y}{N_1N_2N_p f} R_{peak}
-    \label{sigmavis}
+  \sigma_{vis}=\frac{2\pi \Sigma_{x} \Sigma_{y} R(0, 0)}{N_{1}N_{2} f}
+  \label{sigmavis_eq}
 \end{equation}
-where $R_{peak}$ is the measured rate at the peak of the scan \cite{CMS-PAS-LUM-18-002}\cite{CMS-PAS-LUM-12-001}. The original procedure can be found in \cite{vanderMeer:296752}.
-\newcommand\gauss[2]{1/(#2*sqrt(2*pi))*exp(-((x-#1)^2)/(2*#2^2))} % Gauss function, parameters mu and sigma
 
+Experimentally, two separate scans in the x and y directions are performed.
+The beams are scanned against each other  while measuring the rate (normalized by the product of the beam currents) at a certain number of separation steps, fitting the resulting points with a functional form, and using the fitted function to extract $\Sigma_{x,y}$ and $R(0,0)$ in \ref{sigmavis_eq}.
+Fig.
+\ref{vdm_sketch} shows an sketch of the beam positions during vdM scans in X and Y planes together with the detector rate as a function of beam separation.
+
+\begin{center}
   \begin{figure}[ht]
-\begin{minipage}[b]{0.5\linewidth}
     \centering
-\begin{tikzpicture}[x=.5cm,y=.5cm, scale=1.6]
-
-\draw[<->,very thick] (-4.5,0) -- (4.5,0)node[right] {$x$};
-\draw[<->,very thick] (0,-3) -- (0,3) node[above] {$ y$};
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\draw[fill=red, opacity=0.6] (0,-1.6) ellipse (4 mm and 2.5 mm);
-\draw[fill=blue, opacity=0.6] (0,-2) ellipse (4 mm and 2.5 mm);
-
-\draw[fill=red, opacity=0.6] (0,0) ellipse (4 mm and 2.5 mm);
-\draw[fill=blue, opacity=0.6] (0,0) ellipse (4 mm and 2.5 mm);
-
-\draw[fill=red, opacity=0.6] (0,1.6) ellipse (4 mm and 2.5 mm);
-\draw[fill=blue, opacity=0.6] (0,2) ellipse (4 mm and 2.5 mm);
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\draw[fill=red, opacity=0.6] (-2.6,0) ellipse (4 mm and 2.5 mm);
-\draw[fill=blue, opacity=0.6] (-3,0) ellipse (4 mm and 2.5 mm);
-
-\draw[fill=red, opacity=0.6] (0,0) ellipse (4 mm and 2.5 mm);
-\draw[fill=blue, opacity=0.6] (0,0) ellipse (4 mm and 2.5 mm);
-
-\draw[fill=red, opacity=0.6] (2.6,0) ellipse (4 mm and 2.5 mm);
-\draw[fill=blue, opacity=0.6] (3,0) ellipse (4 mm and 2.5 mm);
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\draw[->,]  (1,2) -- (1,0.5)node[pos=0.25, right] {\text {scan in y}};
-\draw[->,]  (-3,.7) -- (-0.5,.7)node[pos=0.5, above] {\text {scan in x}};
-\end{tikzpicture}
-\end{minipage}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{minipage}[b]{0.5\linewidth}
-\centering
-\begin{tikzpicture}
-\begin{axis}[every axis plot post/.append style={ color=black,
-  mark=x ,domain=-4:4,samples=9,smooth,fill=blue,opacity=0.4, mark size=5pt,mark options={color=red}}, % All plots: from -2:2, 50 samples, smooth, no marks
-axis x  line=bottom,very thick, % no box around the plot, only x and y axis
-axis y line=left,very thick, % the * suppresses the arrow tips
-enlargelimits=upper, xmin=-4.5,
-xlabel=\(\Delta x/y\),
-ylabel=\(Rate\),
-ytick={5},xtick={5},
-every axis y label/.style={
-    at={(ticklabel* cs:1.05)},
-    anchor=south,
-},
-every axis x label/.style={
-    at={(ticklabel* cs:1.05)},
-    anchor=west,
-},] % extend the axes a bit to the right and top
-\addplot[]  {\gauss{0}{2}};
-
-\end{axis}
-\draw[<->,very thick] (1.8,2.83) -- (4.8,2.83)node[pos=0.5,below] {$\Sigma_{x/y}$};
-\draw[dashed,very thick] (0,5.18) -- (3.33,5.18)node[pos=0.5,below] {\text {Peak Rate}};
-\end{tikzpicture}
-
-\end{minipage}
-\caption[vdM scan process.]{\textit{Left}: A diagram that shows how the two beams are scanned across the x and y axis.
-\textit{ Right}: An example of a Gaussian-like function (Blue), being fitted to the rate measurements (red xs) taken during a VDM scan.}
-\label{vdm1}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{2018 Calibration Scan program}
-The VdM scans, and other scans regarding to calibrations, were performed during the LHC fill 6868 on June 30 and July 1, 2018 at $\sqrt{s}=13TeV$.
-The LHC filling scheme used 124 colliding bunch pairs at the CMS interaction point (IP5) widely spread over the orbit to reduce long range beam-beam effects and detector afterglow.
-The resulting beam size $\sigma_{b}$ at the beginning of the fill was in the range of approximately 85–95 and 80–90 $\mu m$ in $x$ and $y$, respectively, increasing over time in the $x$ dimension and decreasing over time in the $y$ dimension.No crossing angle was used for collisions at ATLAS and CMS.
-The resulting peak pileup was approximately $\mu = 0.6$ , much lower than in a regular physics fill.
-
-The bunch intensities were approximately $7-9 \times 10^{10} $ protons per filled bunch, resulting in a total beam intensity of slightly above $10^{13}$ protons per beam.
-The total beam intensities were measured with the DC Current Transformers (DCCT) [15], and the bunch currents were measured with the Fast Beam Current Transformers (FBCT) [16].
-The beam orbit was monitored using two systems, the DOROS beam position monitors (BPMs) [17] located near IP5, and the arcBPMs located in the LHC arcs adjacent to CMS.
-***The orbit is also tracked using movements of the luminous region based on reconstructed vertices.
-The arc BPM measurements are translated to a beam position at IP5 using the LHC optics file; the specific optics file used for this scan is R2016c A19mC19mA19mL24.
-
-To ensure a dataset with a high event count for PCC even at large beam separations, CMS recorded the zero-bias triggers on 5 bunch pairs (BCIDs 265, 865, 1780, 2192, and 3380) and recorded events with a total rate of $27.7kHz$.
-
-The CMS VdM scan program was conducted in two parts (``takes''), due to an alarm.
-The first part consisted of a total of six x-y scan pairs.
-Two (``emit1'' and ``emit'') were short ``emittance'' scans, in which the two beams were separated by $4sigma_{b}$ in 9 steps with 10 seconds integration time at each scan point.***
-Scan pair ``norm1'' was a standard VdM scan, in which the two beams were separated by $6\sigma_{b} \approx 600 \mu m$  and scanned across one another in a sequence of 25 steps with 30 seconds per step.
-
-The second part of the scan program was conducted in the same fill but about $7.5$ hours later.
-It consisted of twelve scan pairs.
-Scan pair ``emit3'' was a short emittance scan, followed by scan pairs ``imag2'' and ``imag3'' of the beam imaging kind, an offset scan pair ``offset2'', and finally two normal VdM scan pairs ``norm2'' and ``norm3''.
-The latter two allow us to test the reproducibility of the measuremen.
-
-****After ``norm3'' scan pair, there were the first superseparation period, in which the beams are separated a distance of $6 \sigma_{b}$ in both $x$ and $y1 direction$ for $5$ minutes long in order to get a bakcground estimation.**** source: Analyis Note 2018
-
-A length scale calibration (LSC) was performed after scan pair ``norm3'' using two different methods.
-The first, ``lsc1'', was the ``constant separation'' scan, in which the two beams were separated by $1.4\sigma_{b}$ (approximately equal to $1\Sigma$) and moved together in steps of $1\sigma_{b}$ across and back, for a total of $10$ steps with $70$ seconds per step, once in each transverse direction.
-A second ``variable separation'' method with scan pair ``lsc2'' was also executed, in which one beam (starting with beam 1) is moved to $-2.5\sigma_{b}$ and then a three-point scan (a ``miniscan'') is performed with the other beam (starting with beam 2) at a relative position of $-1.25\sigma_{b}$, $0$, and $+ 1.25 \sigma_{b}$.
-The position of the first beam is then translated in five steps in the same direction to $+2.5 \sigma_{b}$, repeating the miniscan at each step.
-This procedure is repeated four times, with two directions for each of the two beams.
-Each scan point has a duration of about $46s$.
-
-Finally, a normal VdM scan pair “norm4”,*** a second super separation period***,  and two short emittance scan pairs “emit4” and“emit5” concluded the program.
-
-In each scan pair, the scan was performed first in the x direction and then in the y direction, with the exception of the variable separation length scale calibration scan pairs, which were done the other way around.
-Figure \ref{2018sp} shows the beam positions for the two beams in the x and y directions as measured by the DOROS BPMs during the scan program, showing all 18 scan pairs.
-\begin{center}
-    \begin{figure}[H]
-        \centering
-        \includegraphics[scale=0.5]{Chapter3/2018Scanprogram.png}
-        \caption[2018 San program.]{Relative change in beam positions measured by the DOROS BPMs during the 2018 scan program for the two individual beams in the horizontal x and vertical y planes, as a function of the elapsed time from the beginning of the program.
-The top row shows the portion ofthe scan program before the alarm at CMS, while the bottom two rows show the scan program after the alarm.[source: pas-lum-18]}
-        \label{2018sp}
+    \includegraphics[scale=.37]{Chapter3/vdm_sketch.png}
+    \caption[Sketch of a vdM scan in X and Y planes and example of fitting resulting rates]{ The sketch of a vdM scan in X and Y planes.
+The indent sketch is an example of the fitting of the resulting rates \cite{vdM_sketch}.}
+    \label{vdm_sketch}
   \end{figure}
@@
 
-The beam imaging and offset scans are intended for specific studies on the beam shapes described in Section 4**, and they can also be analyzed as traditional van der Meer scans.
-Both the LSC and beam imaging scans are discussed in detail in Ref.
-[18**].
-The offset scan data is analyzed for the first time in 2018.
+%In practice, the integral in Eq.
+(4) is evaluated by performing two separate scans in the x and y directions, measuring the rate (normalized by the product of the beam currents) at a certain number of separation steps, fitting the resulting points with a functional form, and using the fitted function to determine the overall integral [PAS-18].
+ADD HEDWING FIGURE.
+"this is illsutrated in fig N".
+Once Σx and Σy are determined, then Eq.
+(1) can be used to obtain the overall visible cross section σvis [pas-18].
 
-source: pas-lum-18
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%NOTA: Hay un pas, creo,en donde dicen lode beam current normalizado, haciendo referencia a la gráfica.
+Pero tal vez esto vendría en la siguiente seeción, la de resultados, ya que muestre las fitted graphs.
 
-\section{Corrections and systematic uncertainties}
-There are several systematic effects which affect the beam overlap width measurement, and hence the $\sigma_{vis}$ is extracted from the VdM scan procedure.
-These effects are measured and, where applicable, corrected as described below, and a systematic uncertainty is assigned to the resulting measured cross section for each source.
+% https://pos.sissa.it/364/194/pdf
 
-Framework correction flags
+%DUDA: En la qe.
+lumi_2 decimos n_b colliding bunches y aquí hablaremos de solo un coliding buch.
+Lumi inst.
+se refiere a un solo coliding bunch?
+Cuál es la diferencia?
+En el vdM Scan usamos un solo colliding bunch?
 
-\begin{itemize}
- \item ghost and satellite
- \item Background (several types, in our case from SS)
- \item Orbit drift (sep and rate)
- \item Beam Beam
- \item DynamicBeta
- \item Length Scale
- \item PeakToPeak
-\end{itemize}
+\subsection*{Backgrounds}
+Before performing the fit to extract $\Sigma_{x}$ and $\Sigma_{y}$, the raw measured rates must be corrected for background in the detector.
+The background contribution is estimated independently, using a special period known as Super Separation period where the beams are separated, ensuring that the only contribution is from background either beam-induced background or detector noise.
+There are three sources of beam-induced background: Beam Gas Elastic (BGE), Beam Gas Inelastic (BGI) and Beam Halo (BH).
+BGE contribution are all coherent and quasi-elastic nuclear elastic and coulomb scattering for multi-turn beam-gas interactions around the ring; typically the interaction of the primary beam proton and the aperture takes place at the collimator.
+BGI  are all inelastic interactions of primary beam protons with rest gas in the beam pipe.
+The interaction rate is dominated by the vacuum quality in the various beam line elements upstream CMS; therefore the origin of this contribution is distributed all along the long straight section.
+BH component is caused by the inefficiency of the main collimation system.
+Protons can escape from one collimator and being intercepted by another collimator \cite{bkg_source}.\\
+%https://cds.cern.ch/record/1316945/files/CR2010_169.pdf
+%https://cds.cern.ch/record/2816679/files/document.pdf
+% Electronic noise?:
+%  https://cds.cern.ch/record/1293521/files/Thesis-2002-Gu.pdf
+Several other corrections are applied to the raw data before the vdM fit is performed.\\
+%These corrections take into account drifts in the position of the LHC orbit, beam-beam interaction effects, and the beam separation length scale.
+The intensities are measured by the LHC beam current monitors and are corrected for bunched spurious (so-called “ghost” and “satellite”) charges \cite{pas_18}.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%----------- MOVE TO NEXT CHAPTER-------------%
 
-\subsection{Beam beam correction}
-Beam beam correction:
+%Before performing the fit to extract $\Sigma_{x}$ and $\Sigma_{y}$, the raw measured rates must be corrected for background in the detector.
+The background contribution is estimated independently, using two special periods, each 5 minutes long, during the VdM scan where the beams were separated by 6$\sigma$ (where $\sigma_{b}$ is the beam size) in both $x$ and $y$ directions, ensuring that the only contribution is from background (either beam-induced background or detector noise).
+The estimated background is then subtracted from the raw data before the fit is performed using a Gaussian-kind  function, which was found in 2018 to adequately describe the measured rates as a function of beam separation.\\
+%Several other corrections are applied to the raw data before the VdM fit is performed.
+These corrections take into account drifts in the position of the LHC%orbit, beam-beam interaction effects, and the beam separation length scale.
+The event rates are normalized by the bunch intensities before the fit.
+The intensities are measured by the LHC beam current monitors and are corrected for bunched spurious (so-called “ghost” and “satellite”) charges.
 
-\subsection{Veto module correction?}
+%\section{Data set: 2018 vdm scan program}
+%
+%For 2018, the VdM scans were performed during LHC fill 6868 on June 30 and July 1 at $\sqrt{s}=13 \text{TeV}$.
+The LHC filling scheme used  124 colliding bunch pairs at the CMS interaction point (IP5) widely spread over the orbit to reduce long-range beam-beam effects and detector afterglow.
+The resulting beam size $\sigma_{b}$ at the beginning of the fill was in the range of approximately 85–95 and 80–90 $\mu$m in x and y, respectively, increasing over time in the x dimension and decreasing over time in the y dimension.
+No crossing angle was used for collisions.
+The resulting peak pileup was approximately $\mu$ = 0.6, much lower than in a regular physics fill \cite{pas_18}.\\
+%The bunch intensities were approximately 7–9$\times 10^{10}$ protons per filled bunch, resulting in a total beam intensity of slightly above $10^{10}$ protons per beam.
+The total beam intensities were measured with the DC Current Transformers (DCCT), and the bunch currents were measured with the Fast Beam Current Transformers (FBCT) \cite{pas_18}.\\
+%To ensure a dataset with a high event count for PCC even at large beam separations, CMS gated the zero-bias triggers on 5 bunch pairs (BCIDs 265, 865, 1780, 2192, and 3380) and recorded events with a total rate of 27.7 kHz \cite{pas_18}.\\
+%The CMS VdM scan program was conducted in two parts (``takes'') due to an alarm.
+Apart from the vdM scans other studies were carried out.
+Betwen that studies, only the imaging scans are used to compute $\sigma_{vis}$.
+The standar vdM scans are referred as ``norm'' and the imaging scans as ``img''.
+In the first take of the VdM scan program a vdM scan ``norm1'' and a imaging scan ``img1'' were carried out.
+The second part consisted of the scans ``img2'', ``img3'', ``norm2'', ``norm3'' and ``norm4'' were done.
+In total are 7 scans to determine $\sigma_{vis}$ \cite{pas_18}.\\
+%In the vdM scans the two beams were separated by $6 \sigma_{b} \approx 600 \mu$m and scanned across one another in a sequence of 25 steps with 30 seconds per step.
+For the beam imaging scans  one beam (beam 1 in the first pair, followed by beam 2 in the second pair) is kept fixed at its nominal position while the other is separated and scanned in 19 steps from  $+$4.5$\sigma_{b}$ to $-$4.5$\sigma_{b}$ with 46 seconds per step.
+In each of both scans (scan  pairs), the scan was performed first in the x direction and then in the y direction \cite{pas_18}.\\
+%Fig. \ref{scan_prog}  shows the beam positions for the two beams in the x and y directions as measured by the DOROS BPMs during the scan program, showing all scan pairs of the 2018 scan program.
+%
+%\begin{center}
+%  \begin{figure}[ht]
+%    \centering
+%    \includegraphics[scale=.45]{Chapter4/2018Scanprogram.png}
+%    \caption[2018 scan program]{Relative change in beam positions measured by the DOROS BPMs during the 2018 scan program for the two individual beams in the horizontal x and vertical y planes, as a function of the elapsed time from the beginning of the program.
+The top row shows the take 1 of the program before the alarm at CMS, while the bottom two rows show the program after the alarm \cite{pas_18}.}
+%    \label{scan_prog}
+%  \end{figure}
+%\end{center}
+%
+%
 

### 2022-12-29 tesis_Rodolfo/Chapter4/chapter4.tex
Rodolfo Thesis

@@
 
-\section{Fitted Graphs}
-Fit
-\section{$\sigma_{vis}$}
-xsec
+%These corrections take into account drifts in the position of the LHC orbit, beam-beam interaction effects, and the beam separation length scale.
+The intensities are measured by the LHC beam current monitors and are corrected for bunched spurious (so-called “ghost” and “satellite”) charges \cite{pas_18}.
+
+\section{2018 vdM scan program}
+
+For 2018, the vdM scans were performed during LHC fill 6868 on June 30 and July 1 at pp collision energy $\sqrt{s}$ of 13 TeV.
+The LHC filling scheme used  124 colliding bunch pairs at the CMS interaction point (IP5) widely spread over the orbit to reduce long-range beam-beam effects and detector afterglow.
+The resulting beam size $\sigma_{b}$ at the beginning of the fill was in the range of approximately 85–95 $\mu$m and 80–90 $\mu$m in x and y, respectively, increasing over time in the x dimension and decreasing over time in the y dimension.
+No crossing angle was used for collisions.
+The resulting peak pileup was approximately $\mu$ = 0.6, much lower than in a regular physics fill ($<\mu>$= 32 in 2018 ) \cite{pas_18}.\\ %pileup phys: https://twiki.cern.ch/twiki/bin/view/CMSPublic/LumiPublicResults
+The bunch intensities were approximately 7–9$\times 10^{10}$ protons per filled bunch, resulting in a total beam intensity of slightly above $10^{13}$ protons per beam.
+The total beam intensities were measured with the DC Current Transformers (DCCT), and the bunch currents were measured with the Fast Beam Current Transformers (FBCT) \cite{pas_18}.\\
+To ensure a dataset with a high event count for PCC even at large beam separations, CMS gated the zero-bias triggers on 5 bunch pairs: BCIDs (Bunch Crossing ID) 265, 865, 1780, 2192, and 3380; and recorded events with a total rate of 27.7 kHz \cite{pas_18}.\\
+The CMS vdM scan program was conducted in two parts due to an alarm.
+Apart from the vdM scans other studies were carried out called Imaging Scans, which can also be used to measure $\sigma_{vis}$.
+Imaging scans are performed by moving only one beam.
+The standard vdM scans are referred as ``norm'' and the imaging scans as ``img''.
+In the first part of the scan program a vdM scan ``norm1'' and a imaging scan ``img1'' were carried out.
+The second part consisted of the scans ``img2'', ``img3'', ``norm2'', ``norm3'' and ``norm4'' were done.
+In total are 7 scans to determine $\sigma_{vis}$ \cite{pas_18}.\\
+In the vdM scans the two beams were separated by $6 \sigma_{b} \approx 600 \mu$m and scanned across one another in a sequence of 25 steps with 30 seconds per step.
+For the beam imaging scans  one beam (beam 1 in the first pair, followed by beam 2 in the second pair) is kept fixed at its nominal position while the other is separated and scanned in 19 steps from  $+$4.5$\sigma_{b}$ to $-$4.5$\sigma_{b}$ with 46 seconds per step.
+In each of both scans (scan  pairs), the scan was performed first in the x direction and then in the y direction.
+\\For the background estimation, two Super Separation (SS) periods were carried out during the scan program, each 5 minutes long where the beams were separated by $6\sigma_{b}$ (where $\sigma_{b}$ the beam size) in both the x and y directions; the first SS period took place after norm3 and the second after norm4.\\
+Fig. \ref{scan_prog} shows the beam positions for the two beams in the x and y directions as measured by the DOROS BPMs during the scan program, showing all scan pairs of the 2018 scan program.
+
+\begin{center}
+  \begin{figure}[ht]
+    \centering
+    \includegraphics[scale=.45]{Chapter3/2018Scanprogram.png}
+    \caption[2018 scan program]{Relative change in beam positions measured by the DOROS BPMs during the 2018 scan program for the two individual beams in the horizontal x and vertical y planes, as a function of the elapsed time from the beginning of the program.
+The top row shows the take 1 of the program before the alarm at CMS, while the bottom two rows show the program after the alarm \cite{pas_18}.}
+    \label{scan_prog}
+  \end{figure}
+\end{center}
+
+\section{Data analysis}
+
+The data recorded was processed with the CMS software (CMSSW) storing the data into a Hierarchical Data Format (HDF) with hd5 format, containing the times, beam positions, beam currents, and rates.\\
+The data collected during the vdM scans is analysed with a software framework called ``vdM Framework'' (vdM FW), which is written in Python2 and uses the CERN’s data analysis package ``ROOT'' trough the ``PyRoot'' library.
+With the analysis and plotting tools, the vdM FW reads the hd5 file, producing some intermediate files: scan file, beam currents file, rates file and correction files, and applies some corrections to rates (Background, DynamicBeta), separation (OrbitDrift, LengthScale, BeamBeam) and beam currents (FBCT to DCCT calibration, Ghost and Satellite) and creates a graph file.
+This graph file contains the normalized rates (i.e.
+$R/N_{1}N_{2}$) and beam position.
+Each point correspond to the averaged rates in a time window of 30s and 46s for vdM scans (norm) and imaging scans, respectively.
+The points are then fitted with a predefined function to extract $\Sigma_{x,y}$ and peak values to compute $\sigma_{\text{vis}}$ for all the bunches in the scan.
+
+%Description vdM FW:
+%https://cds.cern.ch/record/2647770/files/CERN-THESIS-2018-245.pdf
+%https://cds.cern.ch/record/2775639/files/CERN-THESIS-2021-086.pdf
+%https://vdmdoc.docs.cern.ch/tutorial/tutorial.html
+For some luminometers the rates are reprocessed, for example for backround subtracting.
+In the case of PCC the data was reprocessed for two purposes: i) the use of new data format and ii) a different selection of the pixel detector modules.\\
+For PCC, the rates (and the corresponding times) were originally stored  per event into a ROOT file.
+Due the vdM FW procedures, the data analysis with the ROOT file carries some limitations, leading to the  use of only 1\% of the statistics.
+For this reason, the PCC data was reprocessed  to store the data into an hd5 files containing the rates stored per 1.32 s (NB4), allowing the use of the full statistics.
+This leads to a large improvement in the statistical uncertainty in the rates by a factor of 10, improved the fit model and the better determination of the beam parameters, relative to the previous analysis reported in ref.
+\cite{pas_18}.
+%%\begin{center}
+%%  \begin{figure}[ht]
+%%    \centering
+%%    \includegraphics[scale=.23]{Chapter4/fit_comparison.png}
+%%    \caption[Comparison of statistics: example]{Single Gaussian fit of BCID 3380 from Y vdM scan (without corrections) using the old data format (left) and new data format (right).
+Figure used only to illustrate the difference and improvement of data formats described in the text.}
+%%    \label{fitcomp}
+%%  \end{figure}
+%%\end{center}
+%%
+
+\section{Module selection}
+The implementation of a different selection of the modules in the pixel detector aims to remove instabilities in luminosity measurement.
+Previously, the same selection of modules was used for most of the year, for many run periods.
+Run periods corresponds to a division of time periods of the data set, for 2018 the calibration period is contained in the run period 2018-05-28 to 2018-07-07.\\
+Using a different selection of modules per run period is more realistic as each period can have different number of good performing modules.
+The pixel detector conditions change over the time, for example by detector noise, aging effects and radiaiton damage.\\
+The selection is done trough a module stability study.
+Module stability is based on variation of cluster count relative to total cluster count (module weight), root mean square (RMS) of weights distribution.
+The variations are considered in an interval of 23s (lumi section), which corresponds to the granularity (that is, the scale or level of detail in a set of data) of the luminosity database.
+Modules in barrel layer 1 are removed as these modules were not used in luminosity measurement.
+The module stability is re-evaluated (RMS values, 4\% RMS selection) by using iterative process until stable luminosity is attained.
+Fig.
+\ref{goodmodule} shows an example of a good and bad module.\\
+For the calibration period, the module selection provided has 802 bad modules and 1054 good modules.\\
+The results obtained from the analysis with the new selection of modules are shown below.
+%: rms (root mean square) of weights distribution.  Module stability is re-evaluated by using iterative process until stable luminosity is attained \cite{ashish_stb1}.
+% LS: it corresponds to the granularity (that is, the scale or level of detail in a set of data) of the luminosity database.
+\begin{center}
+  \begin{figure}[ht]
+    \centering
+    \includegraphics[scale=.23]{Chapter4/good_module.png}
+    \caption[Good-bad module stability profile example]{ Graphs showing stability profile for good and bad modules where weight is plotted as a function of lumi section.} %\cite{ashish_stb1}. } 
+    \label{goodmodule}
+  \end{figure}
+\end{center}
+%https://indico.unison.mx/event/152/
+%https://indico.cern.ch/event/1125423/
+%presentacion de sem inv ashish:
+%https://indico.unison.mx/event/152/
+%For the calibration period, the module selection provided has 802 bad modules and 1054 good modules.\\ %\cite{ashish_stb2}.\\%[https://indico.cern.ch/event/1157940/contributions/4862596/attachments/2437712/4176063/AshishSehrawat.pdf]
+%The results obtained from the analysis with the new selection of modules are shown below.
+
+\section{Background estimation}
+To estimate the constant term in the measurements two super separation periods were carried out.
+Fig \ref{ssp_wide_bx1780} shows PCC per NB4 versus time for BCID 1780 to illustrate the two SS periods.
+The lower regions corresponds to the time window of 5 min where the beams were separate a distance of $6\sigma_{b}$, ensuring thatensuring that the only contribution is from background (either beam-induced background or electronics noise).
+%\begin{center}
+%\begin{figure}[ht]
+%\centering
+%\includegraphics[width=.49\textwidth]{Chapter4/plots/SS1_WIDE_BX1780.png}
+%\includegraphics[width=.49\textwidth]{Chapter4/plots/SS2_WIDE_BX1780.png}
+%\caption[Super Separation periods for BCID 1780]{PCC per NB4 versus time for BCID 1780. The lower regions corresponds to the super separation period I (left) and II (right).}
+%\label{ssp_wide_bx1780}
+%\end{figure}
+%\end{center}
+The background value in each BCID is estimated as the mean value of the distribution (or profile) of PCC per NB4.
+Fig \ref{ss1_hist_1780} shows the distribution of PCC per NB4 for BCID 1780 for SS period I, having a mean value of 0.322 with a standard error of the mean (SEM) of 0.018.
+
+\newpage
+
+\begin{center}
+\begin{figure}[ht]
+\centering
+\includegraphics[width=.49\textwidth]{Chapter4/plots/SS1_WIDE_BX1780.png}
+\includegraphics[width=.49\textwidth]{Chapter4/plots/SS2_WIDE_BX1780.png}
+\caption[Super Separation periods for BCID 1780]{PCC per NB4 versus time for BCID 1780. The lower regions corresponds to the super separation period I (left) and II (right).}
+\label{ssp_wide_bx1780}
+\end{figure}
+\end{center}
+
+\begin{center}
+  \begin{figure}[ht]
+    \centering
+    \includegraphics[scale=.18]{Chapter4/plots/ss1_histo_bx1780.png}
+    \caption[PCC per NB4 profile for BCID 1780 from SS period I]{ PCC per NB4 profile for BCID 1780 from SS period I.} 
+    \label{ss1_hist_1780}
+  \end{figure}
+\end{center}
+
+\begin{table}[h!]
+  \begin{center}
+    \caption{Background mean value and SEM of each BCID for both SS periods .}
+    \label{ss_per_bx}
+    \begin{tabular}{|c | c | c | }
+      \multicolumn{1}{c}{} & \multicolumn{1}{c}{\textbf{SS period I}} & \multicolumn{1}{c}{}  \\
+      \hline
+ \textbf{BCID}   & \textbf{Mean}   &  \textbf{SEM}\\
+     \hline %\midrule[1.1pt]
+      265 & 0.3111 & 0.0172\\
+      \hline
+      865 & 0.2732 & 0.0135\\ 
+      \hline
+      1780 & 0.3223 & 0.0187\\ 
+      \hline
+      2192 & 0.2875 & 0.0159\\ 
+      \hline
+      3380 & 0.3157 & 0.0162\\ 
+      \hline
+      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}\\
+      \multicolumn{1}{c}{$\text{SSI}_{\text{Avg}}=$} & \multicolumn{1}{l}{$0.302 \pm 0.0073$} & \multicolumn{1}{c}{}\\
+%      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}
+    \end{tabular}
+    \hspace{0.5cm}
+    \begin{tabular}{|c | c | c | }
+      \multicolumn{1}{c}{} & \multicolumn{1}{c}{\textbf{SS period II}} & \multicolumn{1}{c}{ }  \\
+      \hline
+ \textbf{BCID}   & \textbf{Mean}   &  \textbf{SEM}\\
+     \hline %\midrule[1.1pt]
+      265 & 0.3027 & 0.0148\\
+      \hline
+      865 & 0.297 & 0.0156\\ 
+      \hline
+      1780 & 0.304 & 0.0167\\ 
+      \hline
+      2192 & 0.2225 & 0.0114\\ 
+      \hline
+      3380 & 0.3064 & 0.0169\\ 
+      \hline
+      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}\\
+      \multicolumn{1}{c}{$\text{SSII}_{\text{Avg}}=$} & \multicolumn{1}{l}{$ 0.287 \pm 0.0068$} & \multicolumn{1}{c}{}
+    \end{tabular}   
+  \end{center}
+\end{table}
+
+Table \ref{ss_per_bx} shows the mean en SEM values for each BCID for both SS periods and the average and error ($AvgErr= \sqrt{SEM_1^2+SEM_2^2+\cdots SEM_{N}}/N) $) per SS period.
+Having both average values of SS, the average and error is taken, being this the value applied as a background correction:  $ 0.29 \pm 0.005$.
+
+\section{Corrections}
+The PCC rates per NB4 are averaged per scan step (30s) and the uncertainty is calculated as the SEM. The following corrections are applied in the vdM FW:
+
+\begin{enumerate}
+\item Ghost and Satellite.
+Corrects for the presence of ghost and satellite spurious charges.
+This correction affects bunch currents.
+Satellite charges refers to charge in the colliding bunch crossing but not in the colliding RF bucket, while spurious charges refers to charge not in any nominally filled bunch slot.%
+% The satellite charges are measured by the FBCT, and the DCCT measurements integrate over all charges, thus include both type of contributions.
+so a correction of the beam intensities is needed in order to obtain an accurate value.
+For the 2018 VdM fill, these contributions are measured using the LHC longitudinal density monitors [23, 24].
+Ghost charge measurement is also performed using the beamgas imaging method [25] by comparing the beam-gas rates in beam-empty and empty-empty crossings at the LHCb interaction point (IP8).\\
+%The correction data is taken and the correction is performed as $B_{1,2}*(1-ghos)$ and $B_{1,2}*(1-sat)x$
+\item Background.
+Value estimated above is subtracted to the rates.% lumB = lum - bkg;  %  lumErrB = np.sqrt(lumErr**2 + bkgErr**2).
+Bkg value in the prev sect.
+is subtracted and the error is propahated as : sqrt
+\item Orbit drift.
+The Orbit Drift (OD) correction is composed of two independent corrections: separation correction and a rate correction.
+OD separation aims at correcting for the orbit drift in the scanning direction and only affects beam separation.
+OD rate aims at correcting for the orbit drift in the direction orthogonal to the scanning direction and only affects luminometer rate.
+The derived correction assumes that the beam overlap has a single gaussian shape.
+The correction reads the $\Sigma$ in the orthogonal direction from the previous correction.
+%entry.lumiPerBX[bx] = [ rate * np.exp( ody**2 / (2*CS[bx]**2) ) for rate, ody in zip(entry.lumiPerBX[bx], OD_Y) ]
+%entry.lumiErrPerBX[bx] = [ rateErr * np.exp( ody**2 / (2*CS[bx]**2) ) for rateErr, ody in zip(entry.lumiErrPerBX[bx], OD_Y) ]
+%CS es en la ortogogonal y el od creo que es el de la OD sep.
+
+\item Beam Beam. Corrects Beam Beam deflection (BB) that happens during bunch crossings at the collision point. The deflection is calculated and added to the nominal separation.
+  %https://gitlab.cern.ch/bril/VdMFramework/-/blob/even_more_fits_aa/Code/dataPrep_corr/makeBeamBeamFile.py
+  %import BB -> formula?
+
+\item Dynamic Beta.
+The so-called dynamic-$\beta*$ effect, which accounts for the fact that each beam has a defocusing effect on the other.
+This effect is calculated using reference beam transport simulations that are scaled to the beam energies, the  $\beta ^{*}$ settings, and the measured intensities and convoluted beam widths.
+%Rate normalized?
+%correction_factor en framework.
+makedynfile y dyncoor.
+
+\item Length Scale.
+It applies a linear scaling to the beam separation to convert it from the "CMS scale" to the actual "physics scale".
+This correction is estimated by analyzing pp collision vertices reconstruced by the CMS tracker.
+%scaling but sepErr is 0...
+
+\item Peak to peak.
+Corrects for error in peak calculation, when the scan does not cover the actual head-on collision of the beams.
+%peakToPeakFactor = np.exp( mean**2 / (2 * capSigma**2) );  peakToPeakFactorErr = peakToPeakFactor * mean / capSigma**3 * np.sqrt( capSigma**2 * meanErr**2 + mean**2 * capSigmaErr**2)
+
+%https://gitlab.cern.ch/bril/VdMFramework/-/wikis/od-flag
+\end{enumerate}
+
+\section{van der Meer Scans and $\sigma_{vis}$ Results}
+
+The measurements of PCC, beam separation and beam currents were plotted, fitted and corrected with the corrections described above. The fit model impleted is a guassian-like function:
+
+$$Poly\mathbf{2}G= P \cdot \Biggl[1+r_{2} \cdot \Biggl( \frac{x-\bar{x}}{\frac{\sigma}{1+r_{2}}} \Biggr)^{2}   \Biggr]\cdot \exp \Biggl[ - \frac{1}{2} \Biggl(  \frac{x-\bar{x}}{ \frac{\sigma}{1+r_{2}} }  \Biggr)^{2} \Biggr] $$
+
+where $P$ is the peak value, $\bar{x}$ the mean, and $\sigma$ (standard deviation) and $r_{2}$ are fit parameters.
+This model will be referred as ``Poly2G''.
+Fig.
+\ref{vdM1_1780_XYscan} shows the fitted graphs of the first vdM scan pair for BCID 1780.
+Fig.
+\ref{vdM1_1780_XYscan_logy} shows the same graphs in logarithmic scale.
+Note that rates are normalized by the beam currents, which is a factor of eq.
+\ref{sigmavis_eq}  ($R(0,0)/N_{1}N_{2}$).
+
+The rest of the BCIDs, vdM and imaging scans present a very similar behaviour.
+Fig \ref{chi2/ndof} shows a plot of the chi2/ndof for all the seven scan pairs, having a mean value of 2.23.
+In all cases the fits converged.
+The $\Sigma_{x,y}$  (referred also as CapSigma) and peak values were extracted from the fits to compute $\sigma_{vis}$.
+Fig \ref{capsigma_peak} shows $\Sigma_{x,y}$ and peak values for all scan pairs.
+As can be seen, both values reflects the fact that beam size increased over time in the $x$ dimension and decreased over time in the $y$ dimension.
+\begin{center}
+\begin{figure}[ht]
+\centering
+%\includegraphics[width=.45\textwidth]{Chapter4/plots/vdM1_BX1780_XScan_v2.pdf}
+%\includegraphics[width=.45\textwidth]{Chapter4/plots/vdM1_BX1780_YScan_v2.pdf}\\
+%\includegraphics[width=.45\textwidth]{Chapter4/plots/vdM1_BX1780_XScan_v2_LOGY.pdf}
+%\includegraphics[width=.45\textwidth]{Chapter4/plots/vdM1_BX1780_YScan_v2_LOGY.pdf}
+\includegraphics[width=.38\textwidth]{Chapter4/plots/xscan.png}
+\includegraphics[width=.38\textwidth]{Chapter4/plots/yscan.png}\\
+%\includegraphics[width=.39\textwidth]{Chapter4/plots/xscan_logy.png}
+%\includegraphics[width=.39\textwidth]{Chapter4/plots/yscan_logy.png}
+\caption[vdM1 BCID 1780 (linear scale)]{Normalized rates and the resulting fitted curves with the Poly2G fit model (see text) as a function of
+  the beam separation ($\Delta$) for BCID 1780 for X (left) and Y (right) scan for the first vdM scan.
+Background subtraction and the corrections described in the previous section have been applied to the raw data before the fit.}
+\label{vdM1_1780_XYscan}
+\end{figure}
+\end{center}
+
+\begin{center}
+\begin{figure}[ht]
+\centering
+\includegraphics[width=.39\textwidth]{Chapter4/plots/xscan_logy.png}
+\includegraphics[width=.39\textwidth]{Chapter4/plots/yscan_logy.png}
+\caption[vdM1 BCID 1780 (logarithmic scale)]{Fig. \ref{vdM1_1780_XYscan} in logarithmic scale.}
+\label{vdM1_1780_XYscan_logy}
+\end{figure}
+\end{center}
+
+\begin{center}
+  \begin{figure}[ht]
+    \centering
+    \includegraphics[scale=.20]{Chapter4/plots_thesis/chi2_Poly2G.png}
+    \caption[chi2/ndof for all scan pairs]{ chi2/ndof for all the scan pairs.
+Vertical blue lines divide the X (left) and Y (right) scans.
+In each scan, the BCIDs follow the same order: 265, 865, 1780, 2192, 3380.} %[ https://indico.cern.ch/event/1099207/contributions/4625225/attachments/2351526/4011953/PCC_Stability_Study_23_11_2021.pdf]
+    \label{chi2/ndof}
+  \end{figure}
+\end{center}
+
+\begin{center}
+  \begin{figure}[ht]
+    \centering
+    \includegraphics[width=.49\textwidth]{Chapter4/plots_thesis/CapSigma_Poly2G.png}
+    \includegraphics[width=.49\textwidth]{Chapter4/plots_thesis/peak_Poly2G.png}
+    \caption[$\Sigma$ and peak values for all scan pairs]{$\Sigma$ (left) and Peak values (right) extracted from the fitted graph to compute $\sigma_{vis}$.
+Vertical blue lines divide the X (left) and Y (right) scans.
+In each scan, the BCIDs follow the same order: 265, 865, 1780, 2192, 3380.} %[ https://indico.cern.ch/event/1099207/contributions/4625225/attachments/2351526/4011953/PCC_Stability_Study_23_11_2021.pdf]
+    \label{capsigma_peak}
+  \end{figure}
+\end{center}
+%Eos results path:
+%/eos/user/j/jmorenoc/Results_v1/NewVeto/Period_B/Tests_Poly246G/No_Limits_Poly246G_SuperG/Output/plots_Poly2G/CapSigma_Poly2G.png
+The $\sigma_{vis}$ of each BCID is computed from the fit results parameters showed in previous section ($\Sigma_{x,y}$ and peak) using \ref{sigmavis_eq} with  $R(0,0)=(Peak_{x}+Peak_{y})/2$; $Peak_{x,y}$ values are already normalized so \ref{sigmavis_eq} is rewritten as $\sigma= 2\pi \Sigma_{x} \Sigma_{y} (Peak_{x}+Peak_{y})/2$.\\
+Fig \ref{sigmavis_perbcid} shows  $\sigma_{vis}$ per BCID for all the scans.
+The error on $\sigma_{vis}$ is assigned as $\sigma_{vis\text{Err}}= 2 \pi \sqrt{ (\Sigma_{y} \cdot R \cdot \Sigma_{x\text{Err}})^{2} + (\Sigma_{x} \cdot R \cdot \Sigma_{y \text{Err}})^{2} + (\Sigma_{x} \Sigma_{y} R_{\text{Err}})^{2} }$.\\ %The mean value is 9232.26 mb  with a standard deviation (bunch spread) of  44.33 mb (0.48 \%).
+Fig \ref{sigmavis_perscan} shows $\sigma_{vis}$ per Scan, which corresponds to the weighted average of the five BCIDs with the weight as $1/\sigma_{vis\text{Err}}^{2}$.
+The error is assigned as $1/\sqrt{\sum \frac{1}{\sigma_{vis\text{Err}}^{2}}}$.\\
+
+%\begin{equation*}
+%\frac{1}{\sqrt{\sum_{i}^{N}\frac{1}{\sigma Err^{2}_{i}}}}
+%\end{equation*}
+
+%and the systematic uncertainty as
+
+%$$\sqrt{RMS^{2}-stat^{2}}$$
+\begin{center}
+  \begin{figure}[ht]
+    \centering
+    \includegraphics[scale=.25]{Chapter4/plots_thesis/Poly2G_xsec.png}
+    \caption[$\sigma_{vis}$ per BCID for all scans]{ $\sigma_{vis}$ per BCID for all the scans.
+In each scan the BCIDs follow the same order: 265, 865, 1780, 2192, 3380.} %[ https://indico.cern.ch/event/1099207/contributions/4625225/attachments/2351526/4011953/PCC_Stability_Study_23_11_2021.pdf]
+    \label{sigmavis_perbcid}
+  \end{figure}
+\end{center}
+
+The $\sigma_{vis}$ per scan are averaged and assigning the error in the same way described above, giving a value of $9229 \pm 8 \text{(stat.)} \text{mb}$.\\
+As can be seen in  Fig \ref{sigmavis_perscan}  (and Fig \ref{sigmavis_perbcid}), there is some systematic variation in $\sigma_{vis}$ from scan to scan, being the first vdM scan lower than the rest of the scans.
+The systematic error is assigned as $\sqrt{RMS^{2}-stat^{2}}$.
+\\
+Therefore the $\sigma_{vis}$ value is
+
+\begin{equation}
+\sigma_{vis} = 9229 \pm 8 \text{(stat.)} \pm 28 \text{(syst.)} \text{ mb} .
+\end{equation}
+
+This value is higher than the previously reported in ref.
+\cite{pas_18}: 5982 mb, which corresponds to a different selection of modules in the pixel detector.
+In the previous result, 1069 modules were removed, whereas the value of 9229 mb corresponds to 802 modules removed; the rate of pixel clusters is proportional to the number of modules.
+
+\begin{center}
+  \begin{figure}[ht]
+    \centering
+    \includegraphics[scale=0.37]{Chapter4/plots/xsec_perscan_v2.png}
+    \caption[$\sigma_{vis}$ per Scan]{ $\sigma_{vis}$  per scan.} %[ https://indico.cern.ch/event/1099207/contributions/4625225/attachments/2351526/4011953/PCC_Stability_Study_23_11_2021.pdf]
+    \label{sigmavis_perscan}
+  \end{figure}
+\end{center}

### 2022-12-29 tesis_Rodolfo/Chapter5/chapter5.tex
Rodolfo Thesis

@@
-\chapter{Conclusion and Summary }
-This is a conlcusion
+\chapter{Summary and Outlook}
+This work focuses on the luminosity calibration for the PCC CMS luminometer from the van der Meer scans performed by the CMS Collaboration in summer 2018 for proton-proton collisions at $\sqrt{s}=$ 13 TeV.
+Some aspects such as the luminosity and its importance, the CMS experiment, the PCC luminometer, and the calibration procedure to estimate $\sigma_{vis}$ were covered.
+
+A key part of this work was the reprocessing of the recorded data.
+One part of the reprocessing was applying a different selection of the Pixel detector modules, based on removing instabilities in luminosity measurement for the corresponding calibration period.
+The other part of the reprocessing concerns to the data process work flow, where a new step was added, exploiting the full statistics of the data, providing an improvement in the statistical uncertainty in the rates by a factor of 10, in the fit model and a better determination of the beam parameters, relative to the previous analysis reported.
+This new data implied the estimation of the background correction to the rates (PCC) from the two super separation periods, being this estimation also part of the analysis of this work.
+
+To determine $\sigma_{vis}$, seven scan pairs (four standar vdM and three Imaging scans) were used.
+A systematic variation is observed from bunch to bunch and scan to scan, being the first vdM scan lower than the rest of the scans.
+The assinged value of the calibration is $\sigma_{vis}= 9229 \pm 8(stat.)\pm 28 (syst.) \text{ mb}$.
+
+The analysis and results reported in this work will be useful for an analysis of the precise luminosity measurement for Run2 in the CMS experiment of LHC, where the rest of the luminometers and its uncertainties will be studied (and improved).
+
+%$$RMS=\sqrt{\frac{1}{N} \sum^{N}_{i}(x_{i}-\mu)^{2} } $$
+%$$RMS=\sqrt{\frac{1}{N} \sum^{N}_{i}(x_{i})^{2} } $$
+%$$Syst_{\text{unc}}=RMS-Stat_{\text{unc}} $$

### 2022-12-29 tesis_Rodolfo/Portada/Portada.tex
Rodolfo Thesis

@@
     \begin{center}
-        {\scshape\LARGE UNIVERSITY OF SONORA} %% NOMBRE DE LA UNIVERSIDAD
+        {\scshape\LARGE UNIVERSIDAD DE SONORA} %% NOMBRE DE LA UNIVERSIDAD
         \vspace{.5cm}   %% DEFINE EL ESPACIO ENTRE EL NOMBRE DE LA UNIVERSIDAD Y LA LÍNEA DOBLE
@@
         \vspace{.4cm}   %% DEFINE EL ESPACIO ENTRE LA DOBLE LINEA Y EL NOMBRE DE LA DIVISIÓN
-        {\scshape \large Division of Exact and Natural Sciences}
-        {\scshape Physics Research Department} %% NOMBRE DE LA DIVISIÓN
+        {\scshape \large Divisi\'on de Ciencias Exactas y Naturales}
+        {\scshape Departamento de Investigaci\'on en F\'isica} %% NOMBRE DE LA DIVISIÓN
     \end{center}
@@
       \vspace{2cm}
-        {\Large \scshape {Measurements of the Large Hadron Collider Luminosity using the CMS silicon pixel detector}}
+        {\Large \scshape {Measurements of the Large Hadron Collider luminosity using the CMS silicon pixel detector}}
 
@@
 requirements for the degree of:\\[5pt]
-        {\Large \textbf{{Master of Science in Physics}}}\\[40pt]
+        {\Large \textbf{{Maestr\'ia en Ciencias (F\'isica)}}}\\[40pt]
         By:\\[12pt]
-        \textbf{  {\large Moreno Chávez Jesús Rodolfo}}
+        \textbf{  {\large Jesus Rodolfo MORENO CHAVEZ}}
 
@@
 
-        { \large Director}:\\Dr. José Feliciano Benítez Rubio
+        { \large Director}:\\Dr. Jose Feliciano BENITEZ RUBIO
 
@@
 
-        { Hermosillo, Sonora} \hskip2.5cm {April X, 2022}
+        { Hermosillo, Sonora} \hskip2.5cm {December 08, 2022}
       \end{center}

### 2022-12-29 tesis_Rodolfo/compiler_thesis.py

@@ -1,3 +1,7 @@
+######Instructions######
+#Run as :
+#>python3 compiler_thesis.py
+#######################
 import os
 # colorama_demo.py
 from colorama import init, Fore, Back, Style

### 2023-02-16 tesis_Luis/Chapter1/chapter1.tex
Add files via upload

--- 2022-04-29 tesis_Rodolfo/Chapter1/chapter1.tex
@@
 \chapter{Introduction}
-The Standard Model (SM) in particle physics is the theory that describes the interactions between three fundamental forces, out of the four known  (gravitational, electromagnetic, strong and weak), and the known fundamental particles.
-The gravitational force is not included in the SM, since the magnitude of its strength is neglectable in comparison with the other three forces.
+\label{ch1}
 
-The  theory was developed throughout the second half of the  20th century by the hard work of physicists around the world, with the current formulation being established in the mid 70s.\\
-In high energy physics, precise measurements are the core of any experiment.
-A key quantity is the luminosity, and its precise determination is an important aspect.
-The search for low incidence processes whose observation is not yet confirmed, such as the $H\rightarrow\gamma + Z$ channel, relies in the accumulation and precise measurements of luminosity.
-\section{The Standard Model}
+%%%%% https://cerncourier.com/a/pushing-the-precision-frontier/
+% https://home.cern/news/news/physics/why-precision-luminosity-measurements-matter
 
- The SM classifies all known fundamental particles into two major groups, fermions, particles with spin $1/2$, and bosons, particles responsible for mediating the fundamental forces and integer spin.
-Fermions are divided into two families of particles, leptons and quarks.
-There exist 6 leptons in the SM, first there are charged particles,  electrons ($e$), muons ($\mu$) and the taus ($\tau$) with an electric charge of $-1$ and spin of $1/2$.
-To each of these particles corresponds a chargeless neutrino, $\nu_{e}$,$\nu_{\mu}$ and $\nu_{\tau}$.
+\section{Fundamental Particles}
 
-Leptons can be found in nature existing by themselves, and along with quarks, comprise the majority of matter in the universe.
-Electrons can be found “circling”  atoms, muons can be found raining from the sky due to cosmic rays interacting with particles on the atmosphere and, while taus are a little bit tricky to find due to their short life time ($2.9\times10^{-13}$ s), they do exist by themselves; however, this cannot be said for quarks, since they are only found forming other particles called  hadrons.
-Hadrons can be a combination of two quarks called mesons, usually a quark-antiquark combination or a combination of three quarks called baryons, an example of a meson would be a pion ($\pi$).
-Neutrons and protons are made by a combination of three quarks, so they are classified as baryons.
-Quarks were first theorised by Murray Gell-Mann and George Zweig in 1964 and later discovered by experiments conducted at the Stanford Linear Accelerator Center (SLAC) in 1968 \cite{griff}.
-A total of 6 quarks were discovered over a period of 26 years, in order of discovery these are: up ($u$) (1968), down ($d$) (1968), strange ($s$) (1968), charm ($c$) (1974), bottom ($b$) (1977), top ($t$) (1995).
+ shown in table \ref{tab:table1}.  
+\begin{table}[h!]
+  \begin{center}
+    \caption{Force experienced by the fermions}
+    \label{tab:table1}
+    \begin{tabular}{l c c c c}
+    &    &  \textbf{Electromagnetic} & \textbf{Weak} & \textbf{Strong}\\
+      \midrule[1.1pt]
+      \multirow{2}{*}{Leptons} & $e$ \hspace{0.3cm}  $\mu$\hspace{0.3cm} $\tau$ & \checkmark & \checkmark & \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
+      & $ \nu_{e} $ \hspace{0.3cm}  $\nu_{\mu}$ \hspace{0.3cm} $\nu_{\tau}$  &  & \checkmark\\ % <-- Content of first column omitted.
+      \hline
+      \multirow{2}{*}{Quarks} & $u$ \hspace{0.5cm}  $c$\hspace{0.5cm} $t$ & \checkmark & \checkmark& \checkmark\\
+      & $d$ \hspace{0.5cm}  $s$\hspace{0.5cm} $b$ & \checkmark & \checkmark & \checkmark\\
+%      \hline
+%      3&3 & 23.113231 & c\\
+%      4&4 & 25.113231 & d\\
+    \end{tabular}
+  \end{center}
+\end{table}
 
-Quarks are the only fermions that interact with all three fundamental forces included in the SM, they possess electric charge, color charge (the strong force equivalent of electric charge), weak charge, mass and spin $ 1/2$ as do all fermions.
-The $u$, $c$ and $t$ quarks have an electric charge of $2 /3$ and the $d$, $s$ and $b$ quark have an electric charge of $-1/3$.
-Table \ref{SM table} shows which fermions interact with the different forces.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table}[H]
-\centering
-\caption[Fundamental forces and the fermions]{Fundamental forces and the fermions they interact with \cite{Thomson:2013zua}.}
-\renewcommand{\arraystretch}{1.5}
-\begin{tabular}{|c|c c c|c|c|c|}
-\hline 
-\multicolumn{2}{|c}{}&  & & Electromagnetic & Strong & Weak\\
-\hline
-\multirow{2}{*}{Quarks}&u&c&t &\multirow{2}{*}{\checkmark}&\multirow{2}{*}{\checkmark}&\multirow{2}{*}{\checkmark}\\
-& d&s&b&&&\\
-\hline
-\multirow{2}{*}{Fermions}& $e$&$\mu$&$\tau$ &\checkmark& &\checkmark\\
-&$\nu_{e}$&$\nu_{\mu}$&$\nu_{\tau}$&&&\checkmark\\
-\hline
-\end{tabular} 
-\label{SM table}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
- For each fermion that exists, there corresponds an antiparticle.
-Antiparticles have the same properties as their counterparts, with the only distinction being that they possess opposite electric charge.
-If an antiparticle comes in contact with a particle, let's say a positron (anti-electron) and an electron, they would annihilate each other.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-The SM also comprises particles with integer spin  such as the bosons.
-Bosons are force carrier particles in charge of mediating the interactions between particles, let's take  classical electromagnetism as an example.
-Classically, the electrostatic force is described by a scalar field and while this is sufficient for classical electromagnetism, it is fundamentally wrong for quantum dynamics.
-This would mean that two charged particles interact with each other at a distance, without contact of any kind \cite{Thomson:2013zua}.
+\section{Particle Colliders}
 
-In  particle physics, each fundamental force is described by a quantum field theory (QFT) and the interaction between two particles are mediated by gauge boson, a spin-1 particle.
-For example,  the electromagnetic force is described by Quantum Electrodynamics (QED)  and mediated by the photon, a  particle with no charge or mass.
-The strong force is described by Quantum Chromodynamics (QCD) and mediated by a gluon, which has no mass or electric charge, gluons are what bind quarks together to form hadron and like quarks, are only found in these bind states.
-Finally the weak force is mediated by the $Z$ and $W^{\pm}$ bosons, massive particles with 0 an $\pm 1$ electric charge respectively
-\cite{Thomson:2013zua}.\\
-The Higgs boson is the last member of the SM, unlike the gauge bosons, the Higgs has spin-0 and is the only fundamental scalar discovered. Figure \ref{sm1} shows all the particles included in the SM.
+\section{Cross section}
 
-\begin{center}
-  \begin{figure}[ht]
-    \centering
-    \includegraphics[scale=0.3]{Chapter1/sm1.png}
-    \caption[ Standard model of particles]{Particles that compose the standard model and their properties \cite{smtable}.}
-    \label{sm1}
+\section{Luminosity }
+
+\section{Importance of Luminosity precision}
+
+\section{The Large Hadron Collider}
+
+\section{LHC Luminosity}
+
+    \label{lumi_per_year_int}
   \end{figure}
@@
 
-\section{The Higgs Boson }
-The Higgs boson is the latest member of the SM, first theorised in 1964 by Peter Higgs, Robert Brout, François Englert, Gerald Guralnik, C.
-Richard Hagen and Tom Kibble and later discovered by the ATLAS and CMS experiments at the Large Hadron Collider (LHC) in Geneva Switzerland in 2012.
-The experiment consisted in proton-proton collisions with a center of mass energy of 7 and 8 TeV, the data analysed from the experiment corresponds to five decay channels: $\gamma\gamma$, $ZZ$, $W^{\pm}W^{\pm}$, $\tau^+\tau^-$ and $b\bar{b}$.
-With the discovery being made in the  $\gamma\gamma$ and $ZZ$ channels
-\cite{higgsd}\cite{Aad_2012}.
-The Higgs plays a vital role in the SM, it is responsible for the mechanism that gives every particle their mass.
-It has a mass of $125.78\pm 0.26$ GeV \cite{CMS:2019drq}, consistent with SM predictions, it does not possess electric or color charge and it is the only fundamental scalar and spin-0 boson.\\
- The discovery of the Higgs is one of the greatest accomplishments of the SM, it shows the hard work that has gone in to developing the theories that compose it \cite{Thomson:2013zua}.
+%lumi values:
+% https://inspirehep.net/files/11b4a1d6569e8e066e7431f17a55d69c
 
-\section{Particle colliders and
-detectors}
-The discovery of the Higgs marked an important milestone in particle physics, however, this feat required the construction of the LHC, the largest and most powerful particle collider in the world.
-Particle colliders are the devices where particle physics experiments are conducted.
-As their name suggests, colliders propel bunches of particles like electrons, protons, positrons, etc.
-using powerful electromagnetic/electrostatic fields, and make them collide with a fixed target or other particles.
-These collisions produce other particles that are measured by particle detectors in the site of the collision, this is the means by which new particles are discovered.
+% https://arxiv.org/pdf/1504.06519.pdf
 
-Particle colliders come in two types: linear  and circular.
-Linear colliders  use changing electromagnetic fields to accelerate particles along a straight beam path and make them collide with a fixed target, where particle detectors are located, an example of the linear accelerator would be the Stanford Linear Accelerator Center.
-While circular colliders to accelerate bunches of particles  in opposite directions in a circular beam fashion, making them collide at key points around the accelerator where particle detectors are located.
-The LHC is an example of a circular collider.
-
-The majority of modern experiments in particle physics are conducted in circular colliders, since these are the only ones that can provide the center of mass energy needed to produce heavier particles, like the Higgs or the Top quark.
-Due to the high energy requirements, circular accelerators are very complex machines composed of many parts, but for the sake of this work, we will only focus on the particle detectors.
-Modern particle detectors are composed of many layers of subdetectors tasked with measuring the effects that particles have on them, when they pass through.
-For example, a subdetector may measure the number of hits, tracks or pixel clusters activated during a collision.
-
-The layout of the detector will change to best accommodate the experiments being performed, but in general, these subdetectors can be classified into three categories: Tracking devices, to track the path of a particle; calorimeters, they measure the energy deposited by a particle when it hits and particle identifiers, that use various techniques and the measurements from other subdetectors, to identify the different particles produced in a collision \cite{detector}.
-The CMS detector and the LHC is an example of a layered particle detector.
-
-Finally, two parameters are used to measure the efficiency of a particle collider, the beam energy and the luminosity.
-The higher the beam energy, the more particles can be created and thus the higher chance that new effects can be observed.
-The luminosity ($\mathcal{L}$) is a measure of the efficiency of a particle collider to produce meaningful interaction between colliding bunches of particles.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Luminosity }
-
-As mentioned before, the LHC collides particles by grouping them into bunches, where trains of $N_b$ bunches are made.
-The groups of bunches are circulated both clockwise and anticlockwise and are forced to cross at specific detection points, where several interactions occur.
-A collision between bunches is called an event, and several particle interactions are produced during these events, the quantity that measures the ability of any particle collider to produce these useful interactions is called Luminosity.
-Thus, the event rate $R$, of a particular type $p$, with cross-section  $\sigma_p$, is given by \cite{White}:
-\begin{equation}
-    R=\mathcal{L}_{ins}\sigma_p
-    \label{lumy0}
-\end{equation}
-
-Where the instantaneous luminosity, $\mathcal{L}_{ins}$, is the proportionality constant, the cross section is the likelihood of that event taking place and has units of $cm^{2}$, thus the luminosity has units of $cm^{-2}s^{-1}$ \cite{White}.
-Since the probability of a rare event increases the more the rate of interactions grows, the luminosity is a key figure in the performance of a particle collider.\\
-Let's consider $N_b$ colliding bunches, assuming all the bunches have a head-on collision, the luminosity of all the colliding bunches is given by \cite{CERN-THESIS-2018-051}: 
-\begin{equation}
-    \mathcal{L}_{ins}=  N_b N_1 N_2f\int^{\infty}_{-\infty}dx\int^{\infty}_{-\infty}dy \rho_1(x,y)\rho_2(x,y)
-    \label{lumy1}
-\end{equation}
-where $N_{1,2}$ are the particles per bunch, $f$ is the revolution frequency and $\rho_{1,2}$ are the normalized densities in the transverse plane.
-Assuming that the normalized densities are uncorrelated in all planes, the distribution functions can be factorized as:
-\begin{equation}
-    \rho_i(x,y)=\rho(x)\rho(y) \text { where i=1,2}
-    \label{dens1}
-\end{equation}
-Thus, equation \ref{lumy1} can be writhe as
-
-\begin{equation}
-    \mathcal{L}_{ins}=  N_b N_1 N_2f\int^{\infty}_{-\infty}\rho_1(x)\rho_2(x)dx\int^{\infty}_{-\infty}dy \rho_1(y)\rho_2(y)
-    \label{lumy2}
-\end{equation}
-For the case of head-on colliding bunches, a Gaussian charge distribution can be used, equation \ref{dens1} can be written
-\begin{equation}
-    \rho(u)=\frac{1}{\sqrt{2\pi}\sigma_u} exp\left(-\frac{u^2}{2\sigma_u^2}\right) \text { where u=x,y.}
-    \label{dens2}
-\end{equation}
-using this, equation \ref{lumy2} can be integrated analytically, giving 
-\begin{equation}
-    \mathcal{L}_{ins}=\frac{N_1N_2N_b f}{2\pi
-    \sqrt{\sigma^2_{x1}+\sigma^2_{x2}}\sqrt{\sigma^2_{y1}+\sigma^2_{y2}}}
-    \label{lumy3}
-\end{equation}
-In practice, the bunch densities in the transverse plane are not known and a calibration of the detectors has to be done, in order to obtain these values.
-At the LHC, this is done by a dedicated machine setup.
-The performances of a particle collider over a period of time is given by the integrated luminosity :
-\begin{equation}
-L=\int \mathcal{L}_{ins}(t)dt
-\label{lum0}
-\end{equation}
-
-The average number of interaction per bunch crossing is given by the pileup, $\mu$, and directly proportional to the luminosity
-\begin{equation}
-    \mu=\frac{\mathcal{L}_{ins}\sigma_{tot}}{f}
-    \label{pileup}
-\end{equation}
-where the $\sigma_{tot}$ is the total cross-section of the collided particles \cite{CERN-THESIS-2018-051}.\\
-It is worth noting that a head-on collision is not always the case.
-The bunches can collide in different ways, such as an off-set a crossing angle or both.
-In these cases, the overlapping integral in equation \ref{lumy1} is reduced.
-This is done by applying a reduction factor to equation \ref{lumy2} \cite{CERN-THESIS-2018-051}, however, this work is only concerned with the head-on collision case, the other scenarios can be found in \cite{White}.
+%ATLAS 2015-2018: https://arxiv.org/pdf/1911.04632.pdf

### 2023-02-16 tesis_Luis/Chapter2/chapter2.tex
Add files via upload

--- 2022-04-29 tesis_Rodolfo/Chapter2/chapter2.tex
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The Large Hadron Collider}
+\section{The Compact Muon Solenoid}
 
-The LHC is one of the most powerful particle collider in the world, it started construction in 1998 on the France–Switzerland border near Geneva, using the 26.7 km tunnel, constructed for the CERN LEP machine.
-It came into operation on the 10 of September of 2008, and it is the latest addition to the CERN accelerator complex.
-It was first approved on December 1994 by the CERN council, with  a center-of-mass-energy of 14 Tev \cite{Bruning:782076}.
+\section{CMS Tracking System}
 
-The LHC consists of two separate rings, kept in an ultrahigh vacuum, where two the beams of particles are located.
-To achieve the circular motion of the beams, 1232 dipole magnets are used to maintain trajectory, and 392 quadrupole magnets are used to keep the beams focused.
-Near the interaction points, stronger quadruple magnets are used to increase the probability of interaction between the beams.
-These magnets are made of coils of special superconductive cable, cooled to a temperature of 1.8 K with superfluid helium, producing an electromagnetic field of above 8 T \cite{Bruning:782076}.
+\begin{equation}
+  -\frac{dE}{dx}= \frac{Dq^{2}n_{e}}{\beta ^{2}} \biggl[ \ln \left(\frac{2m_{e}c^{2}\gamma^{2}}{I} \right) -\beta^{2} -\frac{\delta(\gamma)}{2}  \biggr]
+  \label{bethe}
+\end{equation}
 
- The beams in each ring are made of bunches for particles traveling near the speed of light.
-These bunches can be made of protons or ions (like lead nucleons), depending on the running experiment, however, the majority of events at the LHC are produced by proton-proton (pp) bunch collision.\\
-A diagram of CERN’s accelerator complex can be seen in Figure \ref{cernc}.
-The proton bunches start as ionised hydrogen gas and are accelerated to an energy of 50 MeV, by the Linac 2 linear accelerator.
-Once they leave the Linac 2, they are further accelerated to an energy of 1.4 GeV by the Proton Synchrotron Booster (PSB) and dumped on the  Proton Synchrotron (PS).
-In the PS, the bunches are accelerated to an energy of 25 GeV and arranged into a bunch trains, with a spacing of 25 ns, in total, one orbit contains 3564 bunches, arranged in to several trains.
-Finally, the bunches pass from the PS to the Super Proton Synchrotron (SPS), where they are injected into the LHC with an energy of 450 GeV.
-In the LHC, the beams reach a peak energy of 6.5 TeV, and are made to collide in one of the 4 detectors, ALICE, ATLAS, CMS and the LHCb.
-\begin{center}
-  \begin{figure}[ht]
-    \centering
-    \includegraphics[scale=.7]{Chapter2/CERNC.jpg}
-    \caption[CERN accelerator complex.]{A diagram of the CERN accelerator complex \cite{cernpg}.}
-    \label{cernc}
-  \end{figure}
-\end{center}
-The four detectors are tasked with measuring all the particles produced in pp collisions.
-Two specialized detectors are integrated to the LHC, ALICE and LHCb.
-ALICE is dedicated to heavy ion collisions physics, where the quark-gluon plasma is studied.
-The LHCb investigated the differences between matter and antimatter, by studying the “beauty quark” \cite{lhcb}.\\
-The two remaining detectors, CMS and ATLAS, are general purpose detectors, tasked with studying a wide range of physics, from the search of the Higgs boson, to extra dimensions and particles that could make the dark matter in the universe \cite{cmsweb}.
+\subsection{Pixel Detector and Clustering}
+\label{pixel_clust_reco}
 
-Two operation runs have been completed so far at the LHC, and two long shutdowns, where maintenance and several minor upgrades were made to the machine.
-Run 1 lasted from 2010-2012, while Run 2 lasted from  2015-2018.
-As of Run 2, the LHC has achieved a peak luminosity of $2\times 10^{-34} cm^{-2}s^-1$, two times the amount for which the LHC was designed.
-The integrated luminosity, since the LHC began operations, has reached $160 fb^{-1}$ for the ATLAS and CMS experiments \cite{lumi2180}.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{The CMS detector }
-The Compact Muon Solenoid (CMS) experiment is one of the four major experiments currently running in the LHC, and along with ATLAS, one of the two high luminosity experiments at CERN.
-It receives its name from the huge solenoid magnet, from which the detector is built around.
-This solenoid takes the form of a coil made of super conductive wire, capable of producing an electromagnetic field of 4 T.
-The field is confined by a steal yoke, that weights 14,000 tones.
-
-CMS is a layered detector, 21 m in length, with a height and width of 15 m, and it is composed of four main subdetectors, the inner silicon tracker, electromagnetic and hadron calorimeters and the muon detectors.
-The strong magnetic field produced by the detector’s solenoid, separates the particles produced in the coalitions and provides a better momentum resolution.
-Figure \ref{cms} shows a diagram of the detectors layout.
-\begin{center}
-  \begin{figure}[ht]
-    \centering
-    \includegraphics[scale=.2]{Chapter2/CMSl.png}
-    \caption[CMS detector diagram]{Diagram of the CMS detector showing the various subdetectors that comprise it \cite{cms-manual}.}
-    \label{cms}
-  \end{figure}
-\end{center}
-The CMS experiment has a broad range of goals in particle physics, from studying the SM in search of new particles and phenomena, to searching for extra dimensions and discovering new particles that could make the dark matter in the universe.
-The experiment has achieved great things in the scientific community, however, one of its greatest, was the discovery of the Higgs boson  alongside the ATLAS experiment in 2012.
-In the next subsection a brief description of the different subdetectors is provided \cite{cms-manual}.
-\subsection{ Silicon tracker}
-At the heart of the CMS detector lies the inner silicon tracker.
-As its name suggests, the purpose of this subdetector is to reconstruct the track of charged particles generated during collisions, by using silicon strips and pixels to register the paths of charged particles.
-Once the track of a charged particle is reconstructed, its momentum can be extracted, by calculating the curb of its trajectory, produced by the electromagnetic field.
-Also, the vertex, the origin of the track, can be determined.
-The Tracker, which consists of an Inner Tracker (pixels) and an Outer Tracker (strips), is the first subdetector encountered by the particles, and thus the smallest, with an outer radius of 110 cm and a total length of 5.4 m, Figure \ref{tracker} shows the layout of the inner tracker.
-\begin{center}
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=1\textwidth]{Chapter2/pixel-detector.png}
-    \caption[CMS tracker.]{Diagram showing the layout of the CMS Phase-1 inner tracker.
-The barrel pixel detector (BPIX) and the forward disks pixel detector (FPIX) are shown \cite{CMSTrackerGroup:2020edz}.}
-    \label{tracker}
-\end{figure}
-\end{center}
-The tracker is divided into two subtrackers: one is the silicon strip tracker, made of 9.6 million silicon strips.
-This subtracker is divided in two parts: the Tracker Inner Barrel (TIB) and the Tracker Outer Barrel (TOB).
-The TIB is made of 4 layers that cover up to $|z|<65$ cm.
-The TOB has 6 layers, and a coverage of $|z|<110$ cm.
-The encaps are again divided into two regions,  Tracker End Cap (TEC) and Tracker Inner Disk (TID).
-The TEC is composed of 9 disks that extend in the region 120 cm $<|z|<$ 280 cm, while the TID has 3 disks that fill the gaps in between the TIB and the TEC.
-The TEC and the TID are made of rings centered on the beam, and possess stripst that point towards the beam.\\
-The strip tracker encompass and area of 200 $m^2$, and it is made of almost 15,400 modules, running at a  temperature of $-20^{\circ} C$.
-
-The other subtracker is the pixel tracker, made of three layers of barrels possessing a radius of 4.4 cm, 7.3 cm and 10.2 cm with a length of  53 cm, and consisting of 66 million pixels.
-In each end of the barrels, two  end cap disks reside, extending from 6 to 15 cm in radius and located at $|z|=34.5$ cm and 44.5 cm, in total, the pixel tracker has an area of roughly 1$m^2$\\
-768 pixel modules are housed in the barrel, all arranged into half lathers of 4 identical modules.
-The end cap disks are designed in a turbine-like geometry, with blades rotated $20^{\circ}$.
-The blades are made of 7 different pixel modules, with a total of 768 modules being housed in the end cap disks \cite{cms-manual}.
-\subsection{CMS calorimetry system}
-The calorimetry system of the CMS detector is composed of two types of calorimeters: the electromagnetic and hadronic calorimeters.
-Both subdetectors form a complete and hermetic calorimetry system with a coverage of $-5<\eta<5$.
-The calorimeters are a crucial part of the CMS detector, since the identification and reconstruction of photons and electrons is done using measurements from the calorimetry system, as well as the measurements of jets and missing transverse momentum.
-A brief description of the electromagnetic and hadronic calorimeter is provided below.
-
-\subsubsection*{Electromagnetic calorimeter}
-The electromagnetic calorimeter (ECAL) measures the energy of electrons and photons.
-Once charged particles enter the ECAL, they produce a shower for secondary electrons and photons.
-These electrons pass through the lead tungstate ($PbWO_4$) crystals, which scintillates when electrons hit their crystalline structure, producing light that is measured by photodiodes in the calorimeter.\\
-It is made of 75848 tungstate crystals \cite{Contardo:2020886}.
-It is an hermetic, homogeneous calorimeter composed of a central barrel and two end-caps.
-Silicon avalanche photodiodes (APDs) are used in the barrel and vacuum phototriodes (VPTs) in the end caps.
-
-The central barrel has an inner radius of 129 cm and a structure of 36 “supermodules”, that cover half the barrel's length.
-It has a coverage of $|\eta|<1.479$.
-The APDs used on the barrel have an active area of $5\times5$ $mm^2$, and two of them are glued to the back of each crystal.\\
-The two end caps have a pseudorapidity range of $1.479<|\eta|<3$, and are located at a distance of 314 cm from the vertex.
-It consists of crystals with an identical shape,  grouped in mechanical units of $5\times 5$ \cite{cms-manual}.
-\subsubsection*{Hadron calorimeter}
-The Hadron calorimeter (HCAL), along with the ECAL, form a complete and hermetic calorimetry system  with the purpose of measuring  jets and missing transverse energy.
-The HCAL surrounds the ECAL and its design is heavily influenced by the magnet parameters, since it is located inside the solenoid magnet.
-The HCAL is divided into 4 parts: the hadron barrel (HB), hadron outer (HO), hadron endcap (HE) and hadron forward.
-The absorber material is brass since it has a short interaction length, is non-magnetic and is easy to machine.
-Tile/fiber technology, embedded between the absorber plates, is used to detect the particle showers.
-The technology consists of plastic scintillator tiles embedded with  wavelength- shifting (WLS) fibers.
-The fibers are connected to high-attenuation-length clear fibers that carry the light to the readout system.\\
-The photodetection readout is handled by multi-channel hybrid photodiodes (HPDs).
-
-The HB has an inner radius of 1777 mm and an outer radius of 2876.5 mm and has 17 scintillator layers and is composed of 2 half barrels covering a range of  $-1.4<\eta<1.4$, resulting in a total of 2304 towers.
-The HO covers a region of $-1.26<\eta<1.26$ and it contains scintillators with a thickness of 10 mm, lining the outside of the outer vacuum tank of the solenoid.
-The HE consists of 14 towers with a range of $1.3<\eta<3.0$.
-It is made entirely of brass plates, with a thickness of 78 mm.
-
-The HF calorimeter has a range of $3<\eta<5$ and is made of steel and quartz fibers.
-It is located 11.2 m from the interaction point, providing fast collection of Cherenkov light.
-The modules of the HF are constructed of 18 wedges arranged in a non-projective geometry, Figure \ref{wedge} shows and $r-\phi$ view of an HF wedge.
-The quartz fibers have a diameter of 0.6 mm and are placed 5 mm apart, forming a square grid.
-Two different lengths are used for the quartz fibers, 1.43 m and 1.65, effectively creating 2 longitudinal samplings.
-In total, 13 towers exist in $\eta$ with a size of $\Delta\eta\approx 0.175$, except for the lowest and highest-$\eta$ towers, which have a size of $\Delta\eta\approx 0.1$ and $\Delta\eta\approx 0.3$ respectively.
-A $\Delta\phi\approx 10^{\circ}$ exists for all towers but the highest-$\eta$ tower, which has a segmentation of $\Delta\phi\approx 20^{\circ}$.
-In total the HF calorimeter consist of 900 towers and 1800 channels \cite{cms-manual}.
-\begin{center}
-
-\begin{figure}
-    \centering
-    \includegraphics[scale=0.5]{Chapter2/hfes.PNG}
-    \caption[Hadron forward wadge.]{And r-$\phi$ view of a HF wadge.}
-    \label{wedge}
-\end{figure}
-\end{center}
-\subsection{Muon Detector}
-The last subdetector of the CMS experiment is the muon detector system located in the magnet return yokes.
-The muon system consists of 3 types of gaseous detectors, used to detect muons and their momenta.
-These detectors are:  the drift tube chambers (DT), the cathode strips chambers (CSC) and the resistive plate chamber (RPC).
-These detector are distributed across the 2 central parts of the muon detector, the barrel and endcap sessions, with a coverage of $|\eta|<1.2$ and $|\eta|<2.4$ respectively.
-The distribution of these detectors is shown in Figure \ref{Muons}.
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=.45]{Chapter3/dt.png}
-    \caption[One quarter of the CMS muon system. ]{The diagram shows the layout of one quarter of the muon system at CMS \cite{cms-manual}.}
-    \label{Muons}
-\end{figure}
-
-The barrel DT detector  has a coverage of $|\eta|<1.2$, and consist of 250 chambers arranged in 4 layers inside the magnet return yoke, at a radii of approximately 4, 4.9, 5.9 and 7 meters from the beam line.
-The basic element of the DT detectors are cells, with a transverse size of $42\times 13$ $mm^2$, filled with a gas mixture of $85\%$ Ar and $15\%$ $CO_2$ \cite{cms7}.
-The cells have a gold-plated stainless steel anode wire, connected at their center.
-The wire has a diameter of 50 $\mu m$ and it operates at a voltage of +3600 V.
-\\
-The barrel detectors are divided into 12 sectors, each covering $30^{\circ}$ in the azimuthal direction.
-
-Installed on the encap regions, the CSC chambers are installed, covering a range of $0.9<\eta<2.4$.
-Their fast response time and their tolerance to non-uniform magnetic fields, makes the perfect for the high muon rates and background levels found in this region.
-The 6 layers of the CSC measure the muon positions in 2 coordinates.
-The cathode strips provide precise measurements on the r-$\phi$ bending plane, while the wires provide a coarse measurement in the radial direction.
-Each layer of the CSC contains 80 cathode strips with anode wires, of diameter 50 $\mu m$, running almost parallel to the cathodes.\\
-In total, the 2 encaps are comprised of 468 CSC chambers, filled with a gas mixture of $50\%$ $CO_2$, $40\%$ Ar and $10\%$ $CF_4$ \cite{cms7}.
-
-The RPC detectors is located in the barrel and encap regions of the muons system, complementing the DT and CSC detectors.
-It covers a region of $|\eta|<1.6$ and it provides fast, independent trigger events.
-The RPC are double-gap chambers, each gap consisting of 2 mm thick resistive bakelite plates, separated by a 2 mm thick gas gap.
-Readout strips are aligned in the $\eta$ direction in between the gas gaps.
-The gaps are filled with a gas mixture of $95.2\%$ Freon $(C_2H_2F_4)$, $4.5\%$ isobutane $(i-C_4H_{10})$, and $0.3\%$ sulphur hexafluoride $(SF_6)$.
-Water vapor is added to reach a mixture humidity of $40\%$-$50\%$ \cite{cms7}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{High Luminosity LHC}
-The LHC is the most powerful particle collider in the world, and it is to remain the most powerful for the next two decades.
-To ensure this, the LHC will receive major upgrades during the 2020s, to increase its luminosity by a factor of 5 beyond the original design.
-About 10 years will be needed to study and prototype the technologies required for the new High Luminosity LHC (HL-LHC).
-The HL-LHC project was created at the end of  2010 by CERN, as a response to the  European strategy for particle physics, to fully exploit the capabilities of the LHC.
-The project was approved on 30 of May of 2013 by the CERN council in charge at the time.
-For the next decade the HL-LHC is the major construction project of CERN.
-Several new technologies will be used to achieve the luminosity goal, some of them include: superconducting magnets capable of producing a magnetic field of 11 to 12 T, superconducting  cavities, compact and with phase control, for beam rotation, long high-power superconducting links with zero energy dissipation and new technologies for beam collimation \cite{cern3}.
-\begin{center}
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=1.5]{Chapter2/schedulelhc.jpg}
-    \caption[schedule of the LHC.]{The past and future schedule of the LHC.
-The red line corresponds to the center-of-mass-energy of the pp collisions, while the light-red line shows the expected luminosity \cite{schedule}.}
-    \label{programing}
-\end{figure}
-\end{center}
-Figure \ref{programing} shows the  schedule of the LHC up until 2025, where the new phase of the LHC, the HL-LHC, will  begin.
-After reaching a center-of-mass-energy of 13 during 2015, the LHC has doubled the luminosity for which it was designed, as  of the end of Run 2.
-
-The main objectives of the HL-LHC is to reach a peak luminosity of 5 to $7.5\times10^{34}$ $cm^{-2}s^{-1}$, and an integrated luminosity of 250 $fb^{-1}$ per year, with the goal of reaching a total integrated luminosity of 3000 $fb^{-1}$, in the first 12 years of the machines operation.
-For this, intensive studies have, and are, being conducted to determine the hardware and the configuration needed to achieve these goals.\\
-The new hardware of the HL-LHC is to be installed during the third long shutdown (LS3).
-To ensure that the integrated luminosity goal is met, all equipment is being designed with a $50\%$ margin in regards to the required luminosity.
-This means that the High Luminosity LHC can reach peak luminosity valued of 7 to $7.5\times10^{34}$ $cm^{-2}s^{-1}$, this will mean an increase in total pileup (rate of pp collision per bunch crossing) up to 200 \cite{cern3}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Tracker End-Cap Pixel luminometer}
-
-Along with the new HL-LHC upgrade, several upgrades will come to the CMS detector to accommodate the new luminosity and pileup requirements.
-The tracker, muon end caps, trigger and beam radiation protection are just a few of the new upgrades scheduled for the CMS detector.
-However, the focus of this work will be solely on the tracker upgrades, more specifically, the inner  tracker end cap pixel (TEPX) luminometer.
-
-For Phase-2 of the CMS tracking the entire existing pixel and strip tracker will be replaced.
-Figure \ref{TEPXl} shows the r-z layout of the three sections of the Phase-2 inner tracker: the  tracker barrel pixel (TBPX), composed of four cylindrical layers of modules, the tracker’s forward (TFPX) and the tracker end-cap (TEPX) pixel detectors, made of 8 and 4 disks of pixel modules respectively.
-The new tracker will include: increased granularity, forward acceptance and radiation hardness as well as compatibility with longer trigger latency and higher data rates.
-The silicon pixel modules will have a thickness of 100-150 $\mu m$, while the pixel cells will have an area of 2500 $\mu m^2$ ($25\times 100$ $\mu m^2$) \cite{CERN-LHCC-2017-009}\cite{DelBurgo:2706637}.
-Two types of modules will be used in the inner tracker, modules with 2 and 4 pixel chips.
-The modules will be arranged in $2\times1$ and $2\times 2$, these modules are depicted as green and yellow respectively in  Figure \ref{TEPXl}.
-TBPX and TFPX will be composed of both types of modules, while TEPX will only use $2\times 2$ modules \cite{DelBurgo:2706637}.
-\begin{center}
-\begin{figure}[H]
-    \centering
-    \includegraphics[scale=.2]{Chapter2/TEPX.png}
-    \caption[Diagram of the Phase-2 inner tracker upgrade.]{\textit{Lefts}: Diagram of the Phase-2 inner tracker upgrade.
-The last four yellow lines between 1700 mm and 2700 mm, correspond to the TEPX subdetector.
-\textit{Right}:  Front view of one of the disks of the TEPX subdetector \cite{DelBurgo:2706637}.}
-    \label{TEPXl}
-\end{figure}
-\end{center}
-For Phase-2 the TEPX portion of the tracker will be designated for tracking and luminosity measurements, while disk 4 ring 1 (TEPXD4R1) of the detector will designated for luminosity measurements only.
-The TEPX detector is located at each extremity of the tracker of the CMS detector, with a range  from 175 cm to 265 cm on the $|z|$ direction and a radius  between 63 mm and 255 mm.
-The detector is composed of 4 double sided disks, each one made of 5 concentric rings of pixel modules.
-To guarantee hermetic coverage, each ring has a different number of pixel modules.
-TEPX is composed of 800 million pixels, distributed over an area of 2$m^2$, and will operate at trigger frequency of 75KHz during physics runs.
-Table \ref{rings} shows the number of modules per ring, as well as the radius of each ring.
-
-\begin{table}[H]
-\centering
-\caption[Radius and number of pixel modules that comprise the rings of the TEPX subdetector.]{ Table shows the inner ($r_{in}$) and outer ($r_{out}$) radius, as well as the number of pixel modules that comprise each ring of each disk of the TEPX subdetector}
-\scalebox{.8}{
-\begin{tabular}{|l | c | c | c |c|c|}
-\hline
- Ring & 1& 2&3&4&5   \\
-\hline
-$r_{in}$ (mm) & 62.9&100.55 &137.85 &174.45 &210.5\\
-\hline
-$r_{out}$ (mm)&107.69 &144.99 &182.09 &218.56 &254.51 \\
-\hline
- No. of modules&20 &28 &36 &44&48 \\
-\hline
-\end{tabular}}
-\label{rings}
-\end{table}
-
-The innermost ring of the last disk, disk 4 ring 1 (TEPXD4R1), lies beyond a pseudorapidity of $|\eta|=4$ and due to the low number of tracking points in this region, this ring will be designated for luminosity measurements only.
-The ring consists of 20 modules, and it has an inner radius of 62.9 mm and an outer radius of  107.69 mm.
-Finally, the luminometer may run at a trigger frequency of 825kHz to several MHz.\\
-Luminosity measurements with the TEPX's detectors will be carried out using the Pixel cluster counting (PCC) method described in the next chapter.
+\subsection{CMS Luminometers}

### 2023-02-16 tesis_Luis/Chapter3/chapter3.tex
Add files via upload

--- 2022-12-29 tesis_Rodolfo/Chapter3/chapter3.tex
@@
 %%%%%%%%%%%%%%Introduction%%%%%%%%%%%%%%%%%%%%
-
-The precision measurement of the luminosity delivered to the CMS by the LHC is important for a variety of reasons.
-Online, the luminosity measurement provides realtime feedback on the LHC performance and operation.
-Offline, the luminosity measurement is a crucial component of physics analysis, either for measuring the cross section of observed processes or for setting upper limits in searches for processes BSM \cite{pas_18}.\\
-A total of seven systems are used for measuring luminosity at CMS.
-These systems are referred to as luminometers.
-Each luminometer reads out a rate of the specific quantities observed in the detector (hits, tracks, clusters, etc.).
-This rate, R, should be proportional to the instantaneous luminosity,$\mathcal{L}_{inst}$, with the constant of proportionality given by the visible cross section $\sigma_{vis}$ \cite{pas_18}:
 
@@
 
-The determination of $\sigma_{vis}$ is carried out through van der Meer (vdM) scans performed with a dedicated LHC machine setup, exploited by S.
-Van der Meer for luminosity measurements at ISR \cite{vdM_cal}.
-
 \section{Pixel Cluster Counting method}
-The Pixel Cluster Counting method exploits the very large number of pixels in the tracker of the CMS detector.
-At design luminosity of $10^{34}cm^{-2}s^{-1}$, the detector occupancy is less than 0.1\% on average (the average number of clusters per minimum bias interaction is about 50 and the average number of pixels per cluster is about 5) \cite{pas-13}.
-The very low occupancy leads to an excellent linear detector response with increasing LHC luminosity \cite{pas_18}.
  \\
-The PCC method uses the rate of pixel clusters in the CMS pixel detector to provide an offline luminosity measurement.
-Pixel clusters are formed from adjacent pixels, as mentioned in section \ref{pixel_clust_reco}.
-PCC measurement uses the data collected with the standard CMS trigger system with triggers requiring colliding bunches but not any specific event activity; this is referred as "zero-bias trigger'' \cite{pas_18}.\\
-Each bunch crossing gives rise to some number of pp interactions, with each such interaction resulting in some number of pixel clusters.
-If the average over several zero-bias events is taken, the mean number of pixel clusters per event is \cite{PCC_PAS_12_001}:
 
@@
 \section{Luminosity calibration: van der Meer method}
-In the practice, as mentioned in chapter 1, the properties of the colliding beams are not know precisely, such as the bunch density profile, so that the integral in \ref{lumi_2} cannot be solved analytically.
-In LHC a experimental techinque know as vdM method is implemented  with a dedicated machine setup to bring the bunch density profiles close to Guassian distributions.\\
-The VdM scan method, %, exploited by S. Van der Meer for luminosity measurements at ISR  \cite{vdM_cal} and
-applied by LHC Experiments in Run 1 and Run 2, allows to measure and evaluate the integral over the proton bunch densities in eq.
-\ref{lumi_2}.
-For the vdM scan method to be applicable it is also assumed that the two bunch $\rho$ can be factorized into independent terms in x and y \cite{pas-15}.
-The value of the two beam overlap integrals in Eq.
-(2) is determined by varying the beam separation and measuring the resulting rates \cite{pas_18}:
 
@@
 
-Experimentally, two separate scans in the x and y directions are performed.
-The beams are scanned against each other  while measuring the rate (normalized by the product of the beam currents) at a certain number of separation steps, fitting the resulting points with a functional form, and using the fitted function to extract $\Sigma_{x,y}$ and $R(0,0)$ in \ref{sigmavis_eq}.
-Fig.
-\ref{vdm_sketch} shows an sketch of the beam positions during vdM scans in X and Y planes together with the detector rate as a function of beam separation.
-
 \begin{center}
@@
 
-%In practice, the integral in Eq.
-(4) is evaluated by performing two separate scans in the x and y directions, measuring the rate (normalized by the product of the beam currents) at a certain number of separation steps, fitting the resulting points with a functional form, and using the fitted function to determine the overall integral [PAS-18].
-ADD HEDWING FIGURE.
-"this is illsutrated in fig N".
-Once Σx and Σy are determined, then Eq.
-(1) can be used to obtain the overall visible cross section σvis [pas-18].
-
-%NOTA: Hay un pas, creo,en donde dicen lode beam current normalizado, haciendo referencia a la gráfica.
-Pero tal vez esto vendría en la siguiente seeción, la de resultados, ya que muestre las fitted graphs.
-
 % https://pos.sissa.it/364/194/pdf
 
-%DUDA: En la qe.
-lumi_2 decimos n_b colliding bunches y aquí hablaremos de solo un coliding buch.
-Lumi inst.
-se refiere a un solo coliding bunch?
-Cuál es la diferencia?
-En el vdM Scan usamos un solo colliding bunch?
-
 \subsection*{Backgrounds}
-Before performing the fit to extract $\Sigma_{x}$ and $\Sigma_{y}$, the raw measured rates must be corrected for background in the detector.
-The background contribution is estimated independently, using a special period known as Super Separation period where the beams are separated, ensuring that the only contribution is from background either beam-induced background or detector noise.
-There are three sources of beam-induced background: Beam Gas Elastic (BGE), Beam Gas Inelastic (BGI) and Beam Halo (BH).
-BGE contribution are all coherent and quasi-elastic nuclear elastic and coulomb scattering for multi-turn beam-gas interactions around the ring; typically the interaction of the primary beam proton and the aperture takes place at the collimator.
-BGI  are all inelastic interactions of primary beam protons with rest gas in the beam pipe.
-The interaction rate is dominated by the vacuum quality in the various beam line elements upstream CMS; therefore the origin of this contribution is distributed all along the long straight section.
-BH component is caused by the inefficiency of the main collimation system.
-Protons can escape from one collimator and being intercepted by another collimator \cite{bkg_source}.\\
-%https://cds.cern.ch/record/1316945/files/CR2010_169.pdf
-%https://cds.cern.ch/record/2816679/files/document.pdf
-% Electronic noise?:
-%  https://cds.cern.ch/record/1293521/files/Thesis-2002-Gu.pdf
-Several other corrections are applied to the raw data before the vdM fit is performed.\\
-%These corrections take into account drifts in the position of the LHC orbit, beam-beam interaction effects, and the beam separation length scale.
-The intensities are measured by the LHC beam current monitors and are corrected for bunched spurious (so-called “ghost” and “satellite”) charges \cite{pas_18}.
-
-%----------- MOVE TO NEXT CHAPTER-------------%
-
-%Before performing the fit to extract $\Sigma_{x}$ and $\Sigma_{y}$, the raw measured rates must be corrected for background in the detector.
-The background contribution is estimated independently, using two special periods, each 5 minutes long, during the VdM scan where the beams were separated by 6$\sigma$ (where $\sigma_{b}$ is the beam size) in both $x$ and $y$ directions, ensuring that the only contribution is from background (either beam-induced background or detector noise).
-The estimated background is then subtracted from the raw data before the fit is performed using a Gaussian-kind  function, which was found in 2018 to adequately describe the measured rates as a function of beam separation.\\
-%Several other corrections are applied to the raw data before the VdM fit is performed.
-These corrections take into account drifts in the position of the LHC%orbit, beam-beam interaction effects, and the beam separation length scale.
-The event rates are normalized by the bunch intensities before the fit.
-The intensities are measured by the LHC beam current monitors and are corrected for bunched spurious (so-called “ghost” and “satellite”) charges.
-
-%\section{Data set: 2018 vdm scan program}
-%
-%For 2018, the VdM scans were performed during LHC fill 6868 on June 30 and July 1 at $\sqrt{s}=13 \text{TeV}$.
-The LHC filling scheme used  124 colliding bunch pairs at the CMS interaction point (IP5) widely spread over the orbit to reduce long-range beam-beam effects and detector afterglow.
-The resulting beam size $\sigma_{b}$ at the beginning of the fill was in the range of approximately 85–95 and 80–90 $\mu$m in x and y, respectively, increasing over time in the x dimension and decreasing over time in the y dimension.
-No crossing angle was used for collisions.
-The resulting peak pileup was approximately $\mu$ = 0.6, much lower than in a regular physics fill \cite{pas_18}.\\
-%The bunch intensities were approximately 7–9$\times 10^{10}$ protons per filled bunch, resulting in a total beam intensity of slightly above $10^{10}$ protons per beam.
-The total beam intensities were measured with the DC Current Transformers (DCCT), and the bunch currents were measured with the Fast Beam Current Transformers (FBCT) \cite{pas_18}.\\
-%To ensure a dataset with a high event count for PCC even at large beam separations, CMS gated the zero-bias triggers on 5 bunch pairs (BCIDs 265, 865, 1780, 2192, and 3380) and recorded events with a total rate of 27.7 kHz \cite{pas_18}.\\
-%The CMS VdM scan program was conducted in two parts (``takes'') due to an alarm.
-Apart from the vdM scans other studies were carried out.
-Betwen that studies, only the imaging scans are used to compute $\sigma_{vis}$.
-The standar vdM scans are referred as ``norm'' and the imaging scans as ``img''.
-In the first take of the VdM scan program a vdM scan ``norm1'' and a imaging scan ``img1'' were carried out.
-The second part consisted of the scans ``img2'', ``img3'', ``norm2'', ``norm3'' and ``norm4'' were done.
-In total are 7 scans to determine $\sigma_{vis}$ \cite{pas_18}.\\
-%In the vdM scans the two beams were separated by $6 \sigma_{b} \approx 600 \mu$m and scanned across one another in a sequence of 25 steps with 30 seconds per step.
-For the beam imaging scans  one beam (beam 1 in the first pair, followed by beam 2 in the second pair) is kept fixed at its nominal position while the other is separated and scanned in 19 steps from  $+$4.5$\sigma_{b}$ to $-$4.5$\sigma_{b}$ with 46 seconds per step.
-In each of both scans (scan  pairs), the scan was performed first in the x direction and then in the y direction \cite{pas_18}.\\
-%Fig. \ref{scan_prog}  shows the beam positions for the two beams in the x and y directions as measured by the DOROS BPMs during the scan program, showing all scan pairs of the 2018 scan program.
-%
-%\begin{center}
-%  \begin{figure}[ht]
-%    \centering
-%    \includegraphics[scale=.45]{Chapter4/2018Scanprogram.png}
-%    \caption[2018 scan program]{Relative change in beam positions measured by the DOROS BPMs during the 2018 scan program for the two individual beams in the horizontal x and vertical y planes, as a function of the elapsed time from the beginning of the program.
-The top row shows the take 1 of the program before the alarm at CMS, while the bottom two rows show the program after the alarm \cite{pas_18}.}
-%    \label{scan_prog}
-%  \end{figure}
-%\end{center}
-%
-%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-02-16 tesis_Luis/Chapter4/chapter4.tex
Add files via upload

--- 2022-12-29 tesis_Rodolfo/Chapter4/chapter4.tex
@@
 \chapter{Analysis and Results}
-
-%These corrections take into account drifts in the position of the LHC orbit, beam-beam interaction effects, and the beam separation length scale.
-The intensities are measured by the LHC beam current monitors and are corrected for bunched spurious (so-called “ghost” and “satellite”) charges \cite{pas_18}.
 
@@
 
-For 2018, the vdM scans were performed during LHC fill 6868 on June 30 and July 1 at pp collision energy $\sqrt{s}$ of 13 TeV.
-The LHC filling scheme used  124 colliding bunch pairs at the CMS interaction point (IP5) widely spread over the orbit to reduce long-range beam-beam effects and detector afterglow.
-The resulting beam size $\sigma_{b}$ at the beginning of the fill was in the range of approximately 85–95 $\mu$m and 80–90 $\mu$m in x and y, respectively, increasing over time in the x dimension and decreasing over time in the y dimension.
-No crossing angle was used for collisions.
-The resulting peak pileup was approximately $\mu$ = 0.6, much lower than in a regular physics fill ($<\mu>$= 32 in 2018 ) \cite{pas_18}.\\ %pileup phys: https://twiki.cern.ch/twiki/bin/view/CMSPublic/LumiPublicResults
-The bunch intensities were approximately 7–9$\times 10^{10}$ protons per filled bunch, resulting in a total beam intensity of slightly above $10^{13}$ protons per beam.
-The total beam intensities were measured with the DC Current Transformers (DCCT), and the bunch currents were measured with the Fast Beam Current Transformers (FBCT) \cite{pas_18}.\\
-To ensure a dataset with a high event count for PCC even at large beam separations, CMS gated the zero-bias triggers on 5 bunch pairs: BCIDs (Bunch Crossing ID) 265, 865, 1780, 2192, and 3380; and recorded events with a total rate of 27.7 kHz \cite{pas_18}.\\
-The CMS vdM scan program was conducted in two parts due to an alarm.
-Apart from the vdM scans other studies were carried out called Imaging Scans, which can also be used to measure $\sigma_{vis}$.
-Imaging scans are performed by moving only one beam.
-The standard vdM scans are referred as ``norm'' and the imaging scans as ``img''.
-In the first part of the scan program a vdM scan ``norm1'' and a imaging scan ``img1'' were carried out.
-The second part consisted of the scans ``img2'', ``img3'', ``norm2'', ``norm3'' and ``norm4'' were done.
-In total are 7 scans to determine $\sigma_{vis}$ \cite{pas_18}.\\
-In the vdM scans the two beams were separated by $6 \sigma_{b} \approx 600 \mu$m and scanned across one another in a sequence of 25 steps with 30 seconds per step.
-For the beam imaging scans  one beam (beam 1 in the first pair, followed by beam 2 in the second pair) is kept fixed at its nominal position while the other is separated and scanned in 19 steps from  $+$4.5$\sigma_{b}$ to $-$4.5$\sigma_{b}$ with 46 seconds per step.
-In each of both scans (scan  pairs), the scan was performed first in the x direction and then in the y direction.
-\\For the background estimation, two Super Separation (SS) periods were carried out during the scan program, each 5 minutes long where the beams were separated by $6\sigma_{b}$ (where $\sigma_{b}$ the beam size) in both the x and y directions; the first SS period took place after norm3 and the second after norm4.\\
-Fig. \ref{scan_prog} shows the beam positions for the two beams in the x and y directions as measured by the DOROS BPMs during the scan program, showing all scan pairs of the 2018 scan program.
-
-\begin{center}
-  \begin{figure}[ht]
-    \centering
-    \includegraphics[scale=.45]{Chapter3/2018Scanprogram.png}
-    \caption[2018 scan program]{Relative change in beam positions measured by the DOROS BPMs during the 2018 scan program for the two individual beams in the horizontal x and vertical y planes, as a function of the elapsed time from the beginning of the program.
-The top row shows the take 1 of the program before the alarm at CMS, while the bottom two rows show the program after the alarm \cite{pas_18}.}
-    \label{scan_prog}
-  \end{figure}
-\end{center}
-
 \section{Data analysis}
 
-The data recorded was processed with the CMS software (CMSSW) storing the data into a Hierarchical Data Format (HDF) with hd5 format, containing the times, beam positions, beam currents, and rates.\\
-The data collected during the vdM scans is analysed with a software framework called ``vdM Framework'' (vdM FW), which is written in Python2 and uses the CERN’s data analysis package ``ROOT'' trough the ``PyRoot'' library.
-With the analysis and plotting tools, the vdM FW reads the hd5 file, producing some intermediate files: scan file, beam currents file, rates file and correction files, and applies some corrections to rates (Background, DynamicBeta), separation (OrbitDrift, LengthScale, BeamBeam) and beam currents (FBCT to DCCT calibration, Ghost and Satellite) and creates a graph file.
-This graph file contains the normalized rates (i.e.
-$R/N_{1}N_{2}$) and beam position.
-Each point correspond to the averaged rates in a time window of 30s and 46s for vdM scans (norm) and imaging scans, respectively.
-The points are then fitted with a predefined function to extract $\Sigma_{x,y}$ and peak values to compute $\sigma_{\text{vis}}$ for all the bunches in the scan.
-
-%Description vdM FW:
-%https://cds.cern.ch/record/2647770/files/CERN-THESIS-2018-245.pdf
-%https://cds.cern.ch/record/2775639/files/CERN-THESIS-2021-086.pdf
-%https://vdmdoc.docs.cern.ch/tutorial/tutorial.html
-For some luminometers the rates are reprocessed, for example for backround subtracting.
-In the case of PCC the data was reprocessed for two purposes: i) the use of new data format and ii) a different selection of the pixel detector modules.\\
-For PCC, the rates (and the corresponding times) were originally stored  per event into a ROOT file.
-Due the vdM FW procedures, the data analysis with the ROOT file carries some limitations, leading to the  use of only 1\% of the statistics.
-For this reason, the PCC data was reprocessed  to store the data into an hd5 files containing the rates stored per 1.32 s (NB4), allowing the use of the full statistics.
-This leads to a large improvement in the statistical uncertainty in the rates by a factor of 10, improved the fit model and the better determination of the beam parameters, relative to the previous analysis reported in ref.
-\cite{pas_18}.
-%%\begin{center}
-%%  \begin{figure}[ht]
-%%    \centering
-%%    \includegraphics[scale=.23]{Chapter4/fit_comparison.png}
-%%    \caption[Comparison of statistics: example]{Single Gaussian fit of BCID 3380 from Y vdM scan (without corrections) using the old data format (left) and new data format (right).
-Figure used only to illustrate the difference and improvement of data formats described in the text.}
-%%    \label{fitcomp}
-%%  \end{figure}
-%%\end{center}
-%%
-
 \section{Module selection}
-The implementation of a different selection of the modules in the pixel detector aims to remove instabilities in luminosity measurement.
-Previously, the same selection of modules was used for most of the year, for many run periods.
-Run periods corresponds to a division of time periods of the data set, for 2018 the calibration period is contained in the run period 2018-05-28 to 2018-07-07.\\
-Using a different selection of modules per run period is more realistic as each period can have different number of good performing modules.
-The pixel detector conditions change over the time, for example by detector noise, aging effects and radiaiton damage.\\
-The selection is done trough a module stability study.
-Module stability is based on variation of cluster count relative to total cluster count (module weight), root mean square (RMS) of weights distribution.
-The variations are considered in an interval of 23s (lumi section), which corresponds to the granularity (that is, the scale or level of detail in a set of data) of the luminosity database.
-Modules in barrel layer 1 are removed as these modules were not used in luminosity measurement.
-The module stability is re-evaluated (RMS values, 4\% RMS selection) by using iterative process until stable luminosity is attained.
-Fig.
-\ref{goodmodule} shows an example of a good and bad module.\\
-For the calibration period, the module selection provided has 802 bad modules and 1054 good modules.\\
-The results obtained from the analysis with the new selection of modules are shown below.
-%: rms (root mean square) of weights distribution.  Module stability is re-evaluated by using iterative process until stable luminosity is attained \cite{ashish_stb1}.
-% LS: it corresponds to the granularity (that is, the scale or level of detail in a set of data) of the luminosity database.
-\begin{center}
-  \begin{figure}[ht]
-    \centering
-    \includegraphics[scale=.23]{Chapter4/good_module.png}
-    \caption[Good-bad module stability profile example]{ Graphs showing stability profile for good and bad modules where weight is plotted as a function of lumi section.} %\cite{ashish_stb1}. } 
-    \label{goodmodule}
-  \end{figure}
-\end{center}
-%https://indico.unison.mx/event/152/
-%https://indico.cern.ch/event/1125423/
-%presentacion de sem inv ashish:
-%https://indico.unison.mx/event/152/
-%For the calibration period, the module selection provided has 802 bad modules and 1054 good modules.\\ %\cite{ashish_stb2}.\\%[https://indico.cern.ch/event/1157940/contributions/4862596/attachments/2437712/4176063/AshishSehrawat.pdf]
-%The results obtained from the analysis with the new selection of modules are shown below.
 
 \section{Background estimation}
-To estimate the constant term in the measurements two super separation periods were carried out.
-Fig \ref{ssp_wide_bx1780} shows PCC per NB4 versus time for BCID 1780 to illustrate the two SS periods.
-The lower regions corresponds to the time window of 5 min where the beams were separate a distance of $6\sigma_{b}$, ensuring thatensuring that the only contribution is from background (either beam-induced background or electronics noise).
-%\begin{center}
-%\begin{figure}[ht]
-%\centering
-%\includegraphics[width=.49\textwidth]{Chapter4/plots/SS1_WIDE_BX1780.png}
-%\includegraphics[width=.49\textwidth]{Chapter4/plots/SS2_WIDE_BX1780.png}
-%\caption[Super Separation periods for BCID 1780]{PCC per NB4 versus time for BCID 1780. The lower regions corresponds to the super separation period I (left) and II (right).}
-%\label{ssp_wide_bx1780}
-%\end{figure}
-%\end{center}
-The background value in each BCID is estimated as the mean value of the distribution (or profile) of PCC per NB4.
-Fig \ref{ss1_hist_1780} shows the distribution of PCC per NB4 for BCID 1780 for SS period I, having a mean value of 0.322 with a standard error of the mean (SEM) of 0.018.
-
-\newpage
-
-\begin{center}
-\begin{figure}[ht]
-\centering
-\includegraphics[width=.49\textwidth]{Chapter4/plots/SS1_WIDE_BX1780.png}
-\includegraphics[width=.49\textwidth]{Chapter4/plots/SS2_WIDE_BX1780.png}
-\caption[Super Separation periods for BCID 1780]{PCC per NB4 versus time for BCID 1780. The lower regions corresponds to the super separation period I (left) and II (right).}
-\label{ssp_wide_bx1780}
-\end{figure}
-\end{center}
-
-\begin{center}
-  \begin{figure}[ht]
-    \centering
-    \includegraphics[scale=.18]{Chapter4/plots/ss1_histo_bx1780.png}
-    \caption[PCC per NB4 profile for BCID 1780 from SS period I]{ PCC per NB4 profile for BCID 1780 from SS period I.} 
-    \label{ss1_hist_1780}
-  \end{figure}
-\end{center}
 

### 2023-02-16 tesis_Luis/Dedication/dedication.tex
Add files via upload

--- 2022-04-20 tesis_Hedwin/Dedication/dedication.tex
@@
 \justify{
-Thanks to my family for their unconditional support and patience and for always being there when I needed them the most, without them I would not be here.\\
-To my friends Carolina, Alejandro and Luisa, for all the help and for making my studies more fun.\\
-To my advisor Dr. José Feliciano Benítez,  for always being there to answer my doubts, his patience, and for the opportunity of letting me work in the CMS collaboration. \\
-Finally, thanks to CONACYT for supporting my studies with financial aid.}
 

### 2023-02-16 tesis_Luis/compiler_thesis.py

@@ -1,0 +1,39 @@
+######Instructions######
+#Run as :
+#>python3 compiler_thesis.py
+#######################
+import os
+# colorama_demo.py
+from colorama import init, Fore, Back, Style
+
+# Initializes Colorama
+init(autoreset=True)
+
+print(Style.BRIGHT + Back.WHITE + Fore.RED + "Cleaning Some Files...")
+dir_name = os.getcwd()
+test = os.listdir(dir_name)
+
+for item in test:
+    if item.endswith("~"):
+        os.remove(os.path.join(dir_name, item))
+    if item.endswith(".toc"):
+        os.remove(os.path.join(dir_name, item))
+    if item.endswith(".bbl"):
+        os.remove(os.path.join(dir_name, item))
+    if item.endswith(".log"):
+        os.remove(os.path.join(dir_name, item))
+    if item.endswith(".out"):
+        os.remove(os.path.join(dir_name, item))
+    if item.endswith(".blg"):
+        os.remove(os.path.join(dir_name, item))
+print(Style.BRIGHT + Back.WHITE + Fore.BLUE + "Cleaning... DONE")
+
+print(Style.BRIGHT + Back.BLACK + Fore.RED + "Compiling thesis.tex (1st)")
+os.system("pdflatex thesis.tex")
+print(Style.BRIGHT + Back.BLACK + Fore.RED + "Compiling thesis.aux")
+os.system("bibtex thesis.aux")
+print(Style.BRIGHT + Back.BLACK + Fore.BLUE + "Compiling thesis.tex (2nd)")
+os.system("pdflatex thesis.tex")
+print(Style.BRIGHT + Back.BLACK + Fore.GREEN + "Compiling thesis.tex (3rd)")
+os.system("pdflatex thesis.tex")
+print(Style.BRIGHT + Back.BLACK + Fore.GREEN + "DONE: thesis.pdf'")

### 2023-03-01 tesis_Luis/Abstract/abstract.tex
Add files via upload
changes

--- 2022-04-29 tesis_Rodolfo/Abstract/abstract.tex
@@
 \end{center}
-    van der Meer calibration is decribed
+The calibration of the luminosity measurement from the analysis of the van der Meer scanning program for the  CMS experiment in the  2022 proton-proton collision data-taking at $\sqrt{s}=$13.6 TeV with the CMS Silicon Pixel detector is described.
+The data collection period was on November 11 for the LHC fill 8381, the recorded data collected was reprocessed along with a selection of good modules based on luminosity stability studies.
+The Analysis of the van der Meer scans with some especific corrections present results in the calibration constant  $\sigma_{vis}= 4163 \pm 3 (\text{stat.}) \pm 12 (\text{syst.})\text{ mb}$.
+
 \end{abstract}

### 2023-03-01 tesis_Luis/Chapter3/chapter3.tex
changes

@@
 \chapter{Luminosity  Measurement and Calibration}
-\label{ch3}
-%%%%%%%%%%%%%%Introduction%%%%%%%%%%%%%%%%%%%%
-
-\begin{equation}
-R=\mathcal{L}_{inst}\sigma_{vis}
-\label{lumi_exp_gen}
-\end{equation}
-
-\section{Pixel Cluster Counting method}
- \\
-
-\begin{equation}
-\left < N_{\text{cluster}} \right > = \left < N_{\text{pixel}/\text{interaction}} \right >  \left < N_{\text{interactions}} \right > \equiv \left < N_{\text{pixel}/\text{interaction}} \right > \mu
-\end{equation}
-
-where in the last step, the average number of interactions per bunch crossing, pileup, is denoted by the symbol $\mu$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\begin{equation}
-\int \rho_{x1}(x) \rho_{x2}(x) dx = \frac{R_{x}(0)}{\int R_{x}(\Delta) d\Delta}
-\end{equation}
-
-where $R_{x}(\Delta)$ is the rate measured when the two beams are separated in x by a distance $\Delta$; a asimilar equation can be written in y.
-Then the beam overlap width $\Sigma_{x}$ (and similarly $\Sigma_{y}$) is defined as \cite{pas_18}:
-
-\begin{equation}
-\Sigma_{x}= \frac{1}{\sqrt{2\pi}} \frac{\int R_{x}(\Delta)d\Delta}{R_{x}(0)}
-\end{equation}
-
-yielding the final expression for luminosity (for one single bunch):
-
-\begin{equation}
-\mathcal{L}_{inst}=\frac{N_{1} N_{2}f}{2 \pi \Sigma_{x}\Sigma_{y}}
-\end{equation}
-
-where $N_{1,2}$ are the particles per bunch (bunch current) and  $f= 11246$ Hz is the bunch orbit frequency around the LHC ring.\\
-This expression can be finally used in \ref{lumi_exp_gen} to get $\sigma_{vis}$:
-
-\begin{equation}
-  \sigma_{vis}=\frac{2\pi \Sigma_{x} \Sigma_{y} R(0, 0)}{N_{1}N_{2} f}
-  \label{sigmavis_eq}
-\end{equation}
-
-\begin{center}
-  \begin{figure}[ht]
-    \centering
-    \includegraphics[scale=.37]{Chapter3/vdm_sketch.png}
-    \caption[Sketch of a vdM scan in X and Y planes and example of fitting resulting rates]{ The sketch of a vdM scan in X and Y planes.
-The indent sketch is an example of the fitting of the resulting rates \cite{vdM_sketch}.}
-    \label{vdm_sketch}
-  \end{figure}
-\end{center}
-
-% https://pos.sissa.it/364/194/pdf
-
 \subsection*{Backgrounds}

### 2023-03-01 tesis_Luis/Dedication/dedication.tex
changes

@@
 \justify{ 
+I would like to thank my wife Elizabeth for her unconditional support in the challenges I set myself, without her this would not be possible.
+To my advisor, Dr.
+Jos\'e Ben\'itez, for giving me guidance, patience and, above all, the opportunity to work in such a professional team and join the CMS experiment, that was a dream for me.
+To the University of Sonora and CONACYT for supporting me in completing this important challenge in my professional career.
 

### 2023-03-20 tesis_Luis/Chapter4/chapter4.tex
changes
actual

--- 2022-04-29 tesis_Rodolfo/Chapter4/chapter4.tex
@@
 
-\section{Fitted Graphs}
-Fit
-\section{$\sigma_{vis}$}
-xsec
+\section{2022 vdM scan program}
+
+The main VdM scan program for the CMS experiment was performed in November 2022 during LHC fills 8379 and 8381.
+In fill 8381 on 10 and  11 Nov 2022 at pp collision energy $\sqrt{s}$ of 13.6 TeV, 144 bunch pairs were colliding at the CMS intertion points at zero crossing angle, with two additional unpaired bunches present in each beam.
+Four VdM scan pairs, two beam-imaging (BI) scan pairs, and one length scale scan pair where performed, where each scan pair consists of two scans in the transverse planes x and y, as well as other scan types not included in this analysis.
+In a VdM scan, the two beams are separated by $6\sigmab$ ≈ 578 $\mu m$ and scanned across one another in a sequence of 25 steps of 30 s with a step size of $0.5\sigma_{b} \thickapprox 48 \mu m$, where $\sigma_{b}$ is the transverse bunch size.
+In the BI scans, one beam is kept fixed at its nominal head-on position while the other is separated and scanned in 19 steps of 46 s from $-4.5\sigma_{b}$ to $+4.5\sigma_{b} \thickapprox 433 \mu m$.
+In a length scale scan, the beams are separated by a constant amount of $\sqrt{2} \sigma_{b} \thickapprox  106 \mu m$  and moved coherently forward and backward in five steps each in the same transverse direction.
+The scan program during fill 8381 is summarized in Fig.
+\ref{scan_prog}.
+
+The VdM calibration itself is based on scans recorded during Fill 8381.
+Six scan pairs are used that are either of standard VdM type They are labeled consecutively as they were recorded in time, as “VdM1”, “BI1”, “BI2”, “VdM2”, “VdM3”, and “VdM4”.
+During the VdM2 scan pair, the central CMS data taking was not operational, so no data was recorded for PCC, and this scan pair is skipped in the PCC VdM analysis.
+To ensure a dataset with a high event count for PCC even at large beam separations, CMS gated the zero-bias triggers on 5 bunch pairs: BCIDs (Bunch Crossing ID) 282, 822, 2944, 3123, and 3302 ; and recorded events with a total rate of 27.23 kHz .
+
+\begin{center}
+  \begin{figure}[h]
+    \centering
+    \includegraphics[scale=.25]{Chapter4/2022Scanprorgam.png}
+    \caption[2022 scan program]{Nominal horizontal and vertical positions of the proton beams during LHC fill 8381}
+    \label{scan_prog}
+  \end{figure}
+\end{center}
+
+The rate measured by each detector and normalized with the measured beam population is
+fitted as a function of the separation. Corrections to the measured proton numbers and to
+the nominal separation are discussed in the following sections. Here, the fit model and the
+background subtraction are discussed. Technically, the fits are performed with the VdMFramework.
+
+%CMS BRIL Project, “VdMFramework documentation”. CMS Website, 2023.
+%https://vdmdoc.docs.cern.ch/.
+
+%For the background estimation, two Super Separation (SS) periods were carried out during the scan program, each 5 minutes long where the beams were separated by $6\sigma_{b}$ (where $\sigma_{b}$ the beam size) in both the x and y directions.
+
+\section{Data analysis}
+
+The data taken by the  PCC luminometer was reprocessed to perform a cluster reconstruction.
+The datasets containing the cluster information per event were stored in 16 different Zero Bias datasets.
+The first step we took was to extract the data corresponding to the events that belong to our 6 VdM Scans (Runs, Pixel cluster clusters, timestamps, etc.) in a file with ROOT format that is the CERN's data analysis package.
+This was done through the CMS software (CMSSW), which is written in Python2 and C++.\
+Afterward, we have the 16  resuulting datasets, uno for each Zero Bias.
+These files are reprocessed to generate the final file containing the rates stored per 1.32 s (NB4) with Hierarchical Data Format (HD5).
+Within this data reprocessing, we clean the information by subtracting the background and also select the modules that were previously analyzed by a stability study.
+
+The final hd5 file containing the rates from the detector with data collected during the vdM scans is analyzed using a software framework called the "vdM Framework" (vdM FW), which is the latest version and is written in Python3.
+The vdM FW uses data analysis package, "ROOT," through the "PyRoot" library.
+With the analysis and plotting tools, the vdM FW reads the hd5 file, producing several intermediate files: scan file, beam currents file, rates file, and correction files.
+It then applies corrections to the rates (Background, DynamicBeta), separation (OrbitDrift, LengthScale, BeamBeam), and creates a graph file.
+This graph file contains the normalized rates (i.e., $R/N_{1}N_{2}$) and beam position.
+Each point corresponds to the averaged rates in a time window of 30s and 46s for vdM scans and BI scans, respectively.
+The points are then fitted with a predefined function to extract $\Sigma_{x,y}$ and peak values to compute $\sigma_{\text{vis}}$ for all the bunches in the scan.
+
+\section{Module selection}
+
+To ensure accurate luminosity measurement, a veto list is created to remove any modules exhibiting long-term performance variations, indicating a non-physical shift in their cluster counts.
+With a total of 1856 modules in the pixel system, all of them can be considered in the luminosity measurement; however, non-zero occupancy and non-linear effects can pose challenges for accurate measurement.
+Thus, to identify "good" and "stable" modules, a subset is selected by eliminating  underperforming or "bad" modules and comparing their relative contributions to the cross section.
+Those with relatively consistent contributions across standard physics runs are kept, while those with significant changes in their relative cross section compared to the averaged relative contribution are rejected.
+The Module selection is made as:
+\begin{itemize}
+\item Poor statistics lumisections are removed by applying selection on total PCC.
+\item Barrel layer-1 modules are removed, as these modules are significantly affected by dynamic inefficiency.
+\item A loose selection of 7\% based on RMS/mean of module weight is applied. Modules with significantly large RMS/mean are removed with this selection as shown in \ref{goodmodule}.
+\item The module stability is re-evaluated based on RMS/mean values using an iterative method where appropriate selections are applied to remove underperforming modules until a stable luminosity is attained.
+\end{itemize}
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[scale=.20]{Chapter4/RMSmean.png}
+    \caption[RMS/mean Module  Stability]{ RMS/mean values of module weight for all pixel modules. Each pixel module is represented by a module number index.} 
+    \label{goodmodule}
+  \end{figure}
+\end{center}
+
+To ensure accurate measurements, a pixel module veto list is established for each period, recognizing that different periods may have varying numbers of well-performing modules.
+The pixel detector is subject to changing conditions over time, such as detector noise, aging effects, and radiation damage.
+Stability of the pixel modules is assessed based on changes in the module PCC ratio relative to the total PCC, known as module weight.
+These variations are evaluated over an interval of 23 seconds, corresponding to the granularity of the luminosity database.
+The pixel module veto list is first generated for the period 2022F containing the vdM fill and subsequently for the periods ,C, D, E and G,  following the same procedure.
+
+\noindent To further improve the stability of the PCC measurement, a 4\% RMS common module vetolist is created as shown in table \ref{common  veto module}.
+The approach to derive the common module veto list is to start by combining module vetolists of period C and D; then combine C, D and E; and so on.
+The zero-bias PCC data is reprocessed using this common module vetolist.
+
+\begin{table}[h!]
+\centering
+\caption{Number of good and bad modules for the combined vetolist, after each iteration of the 4\% RMS selection with an additional period.}
+\begin{tabular}{ccc}
+\textbf{Period} & \textbf{\# bad modules} & \textbf{\# good modules}  \\ 
+\toprule
+2022C+D         & 886                     & 970                       \\
+2022C+D+E       & 1106                    & 750                       \\
+2022C+D+E+F     & 1307                    & 549                       \\
+2022C+D+E+F+G   & 1411                    & 445                   
+\label{common  veto module}   
+\end{tabular}
+\end{table}
+
+\noindent This final common veto in conjunction with background subtraction  is used for the last reprocesing data file used for e VdMFramework.
+
+\section{Background estimation}
+
+To determine the final PCC rate, the background estimation is conducted using two available super-separation scans SS1 and SS2 shown in the figure \ref{scan_prog}, which are carried out independently and then compared.
+In order to illustrate the two SS periods, Figure \ref{ssp_wide_bx282} displays the PCC per NB4 versus time for BCID 282.
+The lower regions of the plot correspond to a time window of 5 minutes during which the beams were separated by a distance of $6\sigma_{b}$, guaranteeing that the sole contribution is from the background, which could either be beam-induced or electronics noise.
+
+\begin{center}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=.49\textwidth]{Chapter4/BX_282_Rates_SS1.png}
+\includegraphics[width=.49\textwidth]{Chapter4/BX_282_Rates_SS2.png}
+\caption[Super Separation periods for BCID 282]{PCC per NB4 versus time for BCID 282. The lower regions corresponds to the super separation period I (left) and II (right).}
+\label{ssp_wide_bx282}
+\end{figure}
+\end{center}
+\\
+
+To estimate the background value in each BCID, the mean value of the PCC per NB4 rates distribution is computed.
+The mean and error per super-separation (SS) period are obtained by plotting the PCC per NB4 as a function of time and then taking the y projection.
+The error is calculated using the formula $AvgErr = \sqrt{SEM_1^2 + SEM_2^2 + \cdots + SEM_N}/N$.
+To illustrate this process for each BCID, the distribution or profile of PCC per NB4 for each SS period is plotted.
+Figure \ref{ss1_hist_282} displays the PCC per NB4 distribution for SS period I specifically for BCID 282, but the same plot is created for every BCID.\\
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[scale=.18]{Chapter4/ss1_histo_bx282.png}
+    \caption[PCC per NB4 profile for BCID 282 from SS period I]{ PCC per NB4 profile for BCID 282 from SS period I.} 
+    \label{ss1_hist_282}
+  \end{figure}
+\end{center}
+
+\newpage
+\begin{table}[h!]
+  \begin{center}
+    \caption{Mean and standard error on mean (SEM) for the PCC background estimated with the SS1 and SS2 data, separately for all five BCIDs and averaged.}
+    \label{ss_per_bx}
+    \begin{tabular}{|c | c | c | }
+      \multicolumn{1}{c}{} & \multicolumn{1}{c}{\textbf{SS period I}} & \multicolumn{1}{c}{}  \\
+      \hline
+ \textbf{BCID}   & \textbf{Mean}   &  \textbf{SEM}\\
+     \hline %\midrule[1.1pt]
+      282 & 0.7712 & 0.0054\\
+      \hline
+      822 & 0.7744 & 0.0055\\ 
+      \hline
+      2944 & 0.7695 & 0.0057\\ 
+      \hline
+      3123 & 0.7469 & 0.0049\\ 
+      \hline
+      3302 & 0.7708 & 0.0049\\ 
+      \hline
+      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}\\
+      \multicolumn{1}{c}{$\text{SSI}_{\text{Avg}}=$} & \multicolumn{1}{l}{$0.7665 \pm 0.0023$} & \multicolumn{1}{c}{}\\
+%      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}
+    \end{tabular}
+    \hspace{0.5cm}
+    \begin{tabular}{|c | c | c | }
+      \multicolumn{1}{c}{} & \multicolumn{1}{c}{\textbf{SS period II}} & \multicolumn{1}{c}{ }  \\
+      \hline
+ \textbf{BCID}   & \textbf{Mean}   &  \textbf{SEM}\\
+     \hline %\midrule[1.1pt]
+      282 & 0.7192 & 0.0048\\
+      \hline
+      822 & 0.7257 & 0.0057\\ 
+      \hline
+      2944 & 0.7292 & 0.0058\\ 
+      \hline
+      3123 & 0.7028 & 0.0052\\ 
+      \hline
+      3302 & 0.7208 & 0.0053\\ 
+      \hline
+      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}\\
+      \multicolumn{1}{c}{$\text{SSII}_{\text{Avg}}=$} & \multicolumn{1}{l}{$ 0.7195 \pm 0.0024$} & \multicolumn{1}{c}{}
+    \end{tabular}   
+  \end{center}
+\end{table}
+
+Table  \ref{ss_per_bx} shows the results for five different BCIDs, using the reprocessed PCC data for Fill 8381.
+The overall background correction applied to raw PCC rate is $0.74305 \pm 0.002407$, which is calculated by taking the average of the mean values of SS1 and SS2.
+
+\section{Corrections}
+
+There are several systematic effects that affect the measurement of beam overlap width and therefore the extraction of $\sigma_{vis}$ from the VdM scan procedure.
+These effects are measured and, where applicable, corrected as described below.
+A systematic uncertainty is assigned to the resulting measured cross-section, and the following corrections are applied in the VdM Framework:
+
+\begin{enumerate}
+
+\item Ghost and Satellite.
+This correction corrects for the presence of ghost and satellite spurious charges, which affect bunch currents.
+Satellite charges refer to additional charges outside the actual colliding bunch, while spurious charges refer to charge not in any nominally filled bunch slot.
+These results in corrections of up to 0.5\% to $\sigma_{vis}$.
+The overall uncertainty in the bunch current measurement is estimated to be 0.4%.
+
+\item Background. This refers to the noise in the detector where there are no collisions. This value, estimated above, is subtracted from the rates.
+
+\item Orbit drift.
+The orbit drift correction accounts for potential movement of the LHC orbit during the VdM scans.
+Time-dependent changes of the transverse beam positions for fixed machine parameters can alter the beam separation.
+This correction is composed of two independent corrections:
+
+\begin{itemize}
+
+\item Orbit drift separation "ODS", correction that aims to correct for the orbit drift in the scanning direction and only affects beam separation.
+
+\item  Orbit drift rate "ODR", correction that aims to correct for the orbit drift in the direction orthogonal to the scanning direction and only affects the luminometer rate.
+The derived correction assumes that the beam overlap has a single Gaussian shape.
+The correction reads the $\Sigma_{vis}$ in the orthogonal direction from the previous correction.
+\end{itemize}
+
+Applying this correction improves the agreement between the $\sigma_{vis}$ values derived with different scan pairs and changes the average $\Sigma_{vis}$ by about 0.3\%.
+The full size of the correction is considered as uncertainty.
+
+\item Beam Beam corrections.  The electromagnetic interaction between the two colliding proton bunches leads to two ef- fects in beam-separation scans:
+
+\begin{itemize}
+
+\item Beam Beam deflection.
+Corrects Beam Beam deflection (BB) that happens during bunch crossings at the collision point.accounts for the electrical repulsion of the beams, which increases the lateral
+separation  The deflection is calculated and added to the nominal separation.
+
+\item Dynamic Beta.
+The so-called dynamic-$\beta*$ effect, which accounts for any changes in the proton density distributions of the bunches due to the single-particle interactions.
+As a result, the non-linear change during separation steps in transverse bunch profiles is observed, and can described by the effective change of the $\beta*$  value.
+\end{itemize}
+The corrections are calculated for each proton bunch pair individually, and the combined effect of the two corrections is an increase of σvis by 1.0\%, with an uncertainty of 0.5\%.
+
+\item Length Scale.
+It applies a linear scaling to the beam separation to convert it from the "CMS scale" to the actual "physics scale".
+This is  calibrated by analyzing pp collision vertices reconstruced by the CMS tracker using data from the five length scale scan pairs performed in fills 8178, 8379, and 8381.%Length scale factors of (−0.56 ± 0.08)\% in x and (−0.43 ± 0.10)\% in y are found.
+The quoted uncertainty accounts for the statistical uncertainty,
+This correction reduces $\sigma_{vis}$ by 1.0\% and results in an uncertainty of 0.12\%.
+
+%https://gitlab.cern.ch/bril/VdMFramework/-/wikis/od-flag
+\end{enumerate}
+
+\newpage
+\section{van der Meer Scans and $\sigma_{vis}$ Results}
+
+In the previous section, inconsistencies were observed in the background values, which resulted in a very high chi-square value.
+Therefore, it was decided not to use background subtraction.
+Instead, a fitting function was used, which applies a constant to achieve optimal values in the fit and improve the chi-square.
+To correct the measurements of PCC, beam separation, and beam currents, the corrections mentioned earlier were applied.
+The implemented fit model is a double Gaussian function combined with a constant-like function refered as "DG+Const":
+
+\begin{equation}
+DG+Const=
+ C+P \cdot \Biggl[ F \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 \sigma_{1}^{2} } \Biggr) + (1-F) \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 \sigma_{2}^{2} } \Biggr) \Biggr] 
+\end{equation}
+
+%\begin{equation}
+%DG+Const=
+ %C+P \cdot \Biggl[ F \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 ( \frac{\sigma_{1}}{F_{Ratio}+1-F})^{2} } \Biggr) + (1-F) \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 ( \frac{\sigma_{2}}{F_{Ratio}+1-F})^{2} } \Biggr) \Biggr]
+%\end{equation}
+where $F$ is the weight between 0 and 1 of the first Gaussian in the sum, $x$ is the beam separation $C$ is the constant value, $P$ the peak rate, $\bar{x}$ the mean and $\sigma_{1,2}$ the standard deviations are fit parameters.
+Fig.
+\ref{vdM1_282_XYscan} shows the fitted graphs of the first vdM scan pair for BCID 282 where  all the corrections described in the previous section have been applied and where  rates are normalized by the beam currents, which is a factor of eq.
+\ref{sigmavis_eq}  ($R(0,0)/N_{1}N_{2}$).
+
+\begin{center}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=.37\textwidth]{Chapter4/xscan.png}
+\includegraphics[width=.37\textwidth]{Chapter4/yscan.png}\\
+\caption[vdM1 BCID 282]{Normalized rates and the resulting fitted curves with the DG+Const fit model as a function of the beam separation ($\Delta$) for BCID 282 for X (left) and Y (right) scan for the first vdM scan.}
+\label{vdM1_282_XYscan}
+\end{figure}
+\end{center}
+
+\newpage
+For the remaining BCID's, the fits for both vdM and BI scans exhibit a very similar behavior, and in all cases, the fits have converged successfully.
+To evaluate the goodness of fit, Fig.
+\ref{chi2/ndof} displays a plot of the chi2/ndof for all the five scan pairs, which has a mean value of 1.88.
+To compute $\sigma_{vis}$, the CapSigma $\Sigma_{x,y}$ and peak values have been extracted from the fits.
+Fig.
+\ref{capsigma_peak} presents the $\Sigma_{x,y}$ and peak values for all scan pairs.
+The plot clearly illustrates that both values reflect the fact that beam size increased over time in the $x$ dimension and decreased over time in the $y$ dimension.
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[scale=.03]{Chapter4/DGConst_chi2.png}
+    \caption[chi2/ndof for all scan pairs]{ chi2/ndof for all the scan pairs.
+where the red dots represent the X scans, and the blue dots represent the Y scans.
+It is important to note that in each scan, the BCIDs follow the same order, which is 282, 822, 2944, 3123, and 3302.}
+    \label{chi2/ndof}
+  \end{figure}
+\end{center}
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[width=.49\textwidth]{Chapter4/DGConst_CapSigma.png}
+    \includegraphics[width=.48\textwidth]{Chapter4/DGConst_peak.png}
+    \caption[$\Sigma_{x,y}$ and peak values for all scan pairs]{$\Sigma_{x,y}$ (left) and Peak values (right) extracted from the fitted graph to compute $\sigma_{vis}$, where the red dots represent the X scans, and the blue dots represent the Y scans, note that in each scan, the BCIDs follow the same order, which is 282, 822, 2944, 3123, and 3302.}
+    \label{capsigma_peak}
+  \end{figure}
+\end{center}
+
+The sigma visibe $\sigma_{vis}$ for all BCID's (vdM a BI acans) is computed from the fit results parameters Capital sigma $\Sigma_{x,y}$ and $peak_{x,y}$, this is done using the equation \ref{sigmavis_eq}.
+The value of $R(0,0)$ is obtained by taking the average of the peaks in the x and y directions ($R(0,0)=(Peak_{x}+Peak_{y})/2$), which have already been normalized, so \ref{sigmavis_eq} is rewritten as:
+
+\begin{equation}
+ \sigma= 2\pi \Sigma_{x} \Sigma_{y} \Biggl( \frac{Peak_{x}+Peak_{y}}{2} \Biggl)
+ \end{equation}
+
+Fig \ref{sigmavis_perbcid} shows the  value of sigma visible $\sigma_{vis}$ per BCID for all the scans. where the error on $\sigma_{vis}$ is assigned as:
+
+\begin{equation}
+\sigma_{vis\text{Err}}= 2 \pi \sqrt{ (\Sigma_{y} \cdot R \cdot \Sigma_{x\text{Err}})^{2} + (\Sigma_{x} \cdot R \cdot \Sigma_{y \text{Err}})^{2} + (\Sigma_{x} \Sigma_{y} R_{\text{Err}})^{2} }
+\end{equation}
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[scale=.25]{Chapter4/DGConst_xsec.png}
+    \caption[$\sigma_{vis}$ per BCID for all scans]{ $\sigma_{vis}$ per BCID for all the scans,  in each scan, the BCID's follow the same order, which is 282, 822, 2944, 3123, and 3302.}
+    \label{sigmavis_perbcid}
+  \end{figure}
+\end{center}
+
+Fig \ref{sigmavis_perscan} shows the final  $\sigma_{vis}$ per Scan, which corresponds to the weighted average of the five BCIDs with the weight as:
+
+\begin{eqnarray}
+\frac{1}{\sigma_{vis\text{Err}}^{2}}  \text{     where the error is     } \frac{1}{\sqrt{\sum \frac{1}{\sigma_{vis\text{Err}}^{2}}}}
+\label{error}
+\end{eqnarray}
+
+After averaging the values of $\sigma_{vis}$ per scan, the error is assigned in the same manner as described in equation (\ref{error}).
+Figures \ref{sigmavis_perscan} and \ref{sigmavis_perbcid} illustrate that there is a systematic variation in $\sigma_{vis}$ between scans.
+To account for this, a systematic error is assigned as follows:
+
+\begin{equation}
+\sqrt{RMS^{2}-stat^{2}}
+\end{equation}
+
+Obtaining a final  $\sigma_{vis}$ result of:
+
+\begin{equation}
+\sigma_{vis} = 4163 \pm 3 \text{(stat.)} \pm 12 \text{(syst.)} \text{ mb} .
+\end{equation}
+
+\begin{center}
+  \begin{figure}[ht]
+    \centering
+    \includegraphics[scale=0.37]{Chapter4/xsec_perscan_v2.png}
+    \caption[$\sigma_{vis}$ per Scan]{ $\sigma_{vis}$  per scan.} 
+    \label{sigmavis_perscan}
+  \end{figure}
+\end{center}

### 2023-03-27 tesis_Luis/Chapter1/chapter1.tex
updated

@@
 % https://home.cern/news/news/physics/why-precision-luminosity-measurements-matter
+Particle physics is the branch of physics that focuses on studying the fundamental particles and forces that make up matter and radiation in the universe.
+The Standard Model classifies the fundamental particles and their interactions as fermions, which are matter particles, and bosons, which are force-carrying particles.
+High-energy particle accelerators are used to study these interactions by measuring various parameters and properties of the particles produced during collisions.
+This chapter provides a brief overview of elementary particles, particle colliders, and the measurement of their performance.
+It emphasizes the concepts and definitions necessary for understanding this thesis project.
 
@@
 
- shown in table \ref{tab:table1}.  
+The universe is composed of several different particles.
+Atoms are bound states of negatively charged electrons $(e^{-})$, which orbit around a central nucleus consisting of positively charged protons $(p)$ and electrically neutral neutrons $(n)$.
+The electrons are bound to the nucleus by the electrostatic attraction between opposite charges, while the protons and neutrons are held together by the strong nuclear force.
+Completing the fundamental interactions of particle physics are the weak force and gravity.
+The weak force is responsible for nuclear β-decays and nuclear fusion, while gravity, although extremely weak, is always attractive and therefore responsible for the large-scale structure in the universe.
+While this is a simple physical model, at higher energy scales, more complex structures are observed, leading to the discovery of 17 fundamental particles that make up our entire universe.
+These particles are divided into two groups: fermions with spin $1/2$ and bosons with integer spin \cite{thomson_2013}.\\
+
+Fermions are the particles that constitute matter, consisting of twelve fundamental particles classified into two types: leptons and quarks.
+These particles are further divided into three generations, with each member of a higher generation having a greater mass than the corresponding particle of the previous generation.
+The six leptons include three charged particles: electron ($e$\textsuperscript{-}), muon (${\mu}$\textsuperscript{-}), and tau (${\tau}$\textsuperscript{-}), as well as their corresponding neutrinos: electron-neutrino ($\nu_{e}$), muon-neutrino ($\nu_{\mu}$), and tau-neutrino ($\nu_{\tau}$).
+Quarks, on the other hand, can only be found in particles called hadrons.
+The group of quarks consists of the up quark ($u$), down quark ($d$), charm quark ($c$), strange quark ($s$), top quark ($t$), and bottom quark ($b$) \cite{griff,thomson_2013}.
+The properties of these twelve particles are summarized in Table \ref{tab:table1}.
+
 \begin{table}[h!]
 	\begin{center}
-    \caption{Force experienced by the fermions}
+%\centering
+	\caption{The twelve fundamental fermions divided into quarks and leptons.\
+The masses of the quarks are the current masses \cite{thomson_2013}.}
 		\label{tab:table1}
+		\begin{tabular}{lllrcllrc}
+                                                                                & \multicolumn{4}{c}{\textbf{Leptons}}                                                                     & \multicolumn{4}{c}{\textbf{Quarks}}                                                \\
+%\cline{2-9}
+ \midrule[1.1pt]
+                                                                                & \multicolumn{2}{c}{Particle } & \multicolumn{1}{c}{\textit{Q}} & mass/GeV                          & \multicolumn{2}{c}{Particle} & \multicolumn{1}{c}{\textit{Q}} & mass/GeV  \\
+\hline
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}First\\~~~ generation\end{tabular}}  & electron & ($e$\textsuperscript{-})                 & -1                             & 0.0005                            & down    & ($d$)                & -1/3                           & 0.003     \\
+                                                                                & neutrino & ($\nu_{e}$)                 & 0                              & \textless{}10\textsuperscript{-9} & up      & ($u$)                & +2/3                           & 0.005     \\
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Second\\~~~ generation\end{tabular}} & muon     & (${\mu}$\textsuperscript{-})                 & -1                             & 0.106                             & strange & ($s$)                & -1/3                           & 0.1       \\
+                                                                                & neutrino & ($\nu_{\mu}$)                 & 0                              & \textless{}10\textsuperscript{-9} & charm   & ($c$)                & +2/3                           & 1.3       \\
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Third \\~~~ generation\end{tabular}} & tau      & ({$\tau}$\textsuperscript{-})                 & -1                             & 1.78                              & bottom  & ($b$)                & -1/3                           & 4.5       \\
+                                                                                & neutrino & ($\nu_{\tau}$)                 & 0                              & \textless{}10\textsuperscript{-9} & top     &($t$)                & +2/3                           & 174
+\end{tabular}
+	\end{center}
+		\end{table}
+
+The bosons are responsible for describing the interactions between fermions through the exchange of particles.
+These exchange particles are known as gauge bosons and include the photon $\gamma$, $W^{\pm}$, $Z^{0}$ and gluons $g$ \cite{thomson_2013}.
+Additionally, there is a scalar boson called the Higgs boson, which is associated with the mechanism that gives mass to all fundamental particles.
+The forces experienced by fermions can be seen in table  \ref{tab:table2}.
+
+\begin{table}[h!]
+  \begin{center}
+    \caption{Force experienced by the fermions \cite{thomson_2013}.}
+    \label{tab:table2}
     \begin{tabular}{l c c c c}
@@
       \midrule[1.1pt]
-      \multirow{2}{*}{Leptons} & $e$ \hspace{0.3cm}  $\mu$\hspace{0.3cm} $\tau$ & \checkmark & \checkmark & \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
+      \multirow{2}{*}{Leptons} & ${e}$\textsuperscript{-} \hspace{0.3cm}  ${\mu}$\textsuperscript{-} \hspace{0.3cm} ${\tau}$\textsuperscript{-} & \checkmark & \checkmark & \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
       & $ \nu_{e} $ \hspace{0.3cm}  $\nu_{\mu}$ \hspace{0.3cm} $\nu_{\tau}$  &  & \checkmark\\ % <-- Content of first column omitted.
@@
       & $d$ \hspace{0.5cm}  $s$\hspace{0.5cm} $b$ & \checkmark & \checkmark & \checkmark\\
-%      \hline
-%      3&3 & 23.113231 & c\\
-%      4&4 & 25.113231 & d\\
+
     \end{tabular}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+All of these particles are described by the Standard Model (SM), which is the best theoretical model to date for providing a successful description of experimental data.
+However, most of this data comes from particle colliders since these particles can only be produced and studied through collisions of high energy.
 
@@
 
+Most of the recent breakthroughs in particle physics have resulted from experiments conducted at high-energy particle accelerators.
+These accelerators are the most powerful microscopes for observing the tiniest inner structures of cells, genes, molecules, atoms, and their constituent particles such as protons, neutrons, electrons, neutrinos, and quarks.
+Moreover, they may also help discover yet unknown fundamental building blocks of the universe, such as dark matter and dark energy.\\
+
+Particle Colliders produce and accelerate beams of charged particles at high speeds (close to the speed of light) using electromagnetic fields; the high-energy collisions of these beams produce individual interactions referred to as events.
+These collisions produce massive particles, such as the Higgs boson or the top quark.
+These particles only last in the blink of an eye, and cannot be observed directly, almost immediately they transform (or decay) into lighter particles, which in turn also decay.
+They are measured and identified by a wide range of experiments (particle detectors), whose technologies, techniques and designs are based on the properties of the particles and on the nature of their interactions with matter \cite{thomson_2013}.\\
+
+In general, a particle detector is composed of a cylindrical or polygonal barrel section, with its axis aligned parallel to the incoming colliding beams.
+The cylindrical structure is sealed by two flat end caps, providing almost complete solid angle coverage down to the beam pipe.
+The innermost region of the detector is designed for the tracking of charged particles, while the tracking volume is surrounded by an electromagnetic calorimeter that detects isolated energy deposits from electrons and photons and charged particle tracks, respectively.
+The relatively large-volume hadronic calorimeter, which detects and measures the energies of hadrons, is located outside the electromagnetic calorimeter.
+Dedicated detectors are positioned outside the experiment to record signals from any high-energy muons produced in the collisions, which are the only particles, apart from neutrinos, that can penetrate through the hadronic calorimeter.
+Muons can be identified as charged particle tracks associated with small energy depositions in both the calorimeters and signals in the muon detectors on the outside of the detector system.
+While neutrinos do not leave signals in the detector, their presence can often be inferred from the presence of missing momentum \cite{thomson_2013}.\\
+
+The performance of particle colliders is typically evaluated based on two parameters: the beam energy and the luminosity.
+The available energy for producing new effects is one of the most important parameters, as it determines the types of particles that can be studied or discovered.
+Colliding beams experiments are required to achieve the necessary high center-of-mass energy.
+In these experiments, particles are accelerated and two beams are brought together at an intersection point where they collide.\\ %The total energy of a projectile particle and a target particle depends on the reference frame.\\
+
+Colliding beam machines have the advantage that they can achieve much higher centre-of-mass energies, at various points the beams intersect and scattering takes place.
+If the incident particles have the same energy (equal mass) and therefore equal but opposite momentum, then the experiment is taking place in the centre-of-mass (CM) frame and the full energy delivered by the accelerator, can be used to produce high mass particles  \cite{undergraduate_accelerators_chapter}.\\
+
+Consider the Lorentz invariant quantity $s$ used in particle physics to denote the square of the total incoming energy in the CM frame:
+
+\begin{equation}
+s = \left ( \sum_{i = 1,2}^{}E_{i} \right )^{2}-\left ( \sum_{i = 1,2}^{}p_{i} \right )^{2}c^{2}
+\end{equation}
+
+Where $E$ and \textbf{$p$}  are the energy and the momenta of each incoming particle respectively, in this  frame, where the momenta are equal and opposite, the second term vanishes and:
+
+\begin{equation}
+s = 4E^2 
+\end{equation}
+
+The second important parameter of the collider's performance is the luminosity, defined as the  quantity that measures the ability of a particle accelerator to produce the required number of interactions and is the proportionality factor  between the number of events per second $dR/dt$ and the quantum mechanical probability for the interaction called cross section \sigma_{p} \cite{ref_lib_vol3}.
+
 \section{Cross section}
 
+The technical meaning of "cross section" in particle physics is quite different from its common usage.
+While "cross section" typically refers to a slice of an object, in particle physics, it often refers to the probability that two particles will collide and react in a specific manner.
+When proton beams cross in a particle accelerator, a variety of different processes can occur.
+The cross section of a given process depends on the type and energy of the colliding particles.
+At the Large Hadron Collider (LHC), certain particles such as  $W^{\pm}$ and $Z^{0}$ bosons have large cross sections $\sigma_{p}$, making their observation more frequent, while the production of a Higgs boson has a much lower cross section $\sigma_{p}$, making it more difficult to produce \cite{thomson_2013}.\\
+
+In the simplest scenario, a beam of particles of type $a$, with a flux denoted by $\phi_{a}$, passes through a region of space containing $n_{b}$ particles per unit volume of type $b$.
+The interaction rate per target particle $r_{b}$ is proportional to the incident particle flux and can be expressed as follows \cite{thomson_2013}:
+
+\begin{equation*}
+  r_{b}=\sigma \phi_{a}
+\end{equation*}
+
+The essence of fundamental physics is encapsulated in $\sigma$, which has units of area and is referred to as the interaction cross section.
+It can be useful to conceptualize $\sigma$ as the effective cross-sectional area associated with each target particle, in general, the cross section merely represents the underlying quantum mechanical likelihood that an interaction will occur \cite{thomson_2013}.\\The definition of the cross section is illustrated in Figure \ref{cross_section}(a) ,
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+%    \includegraphics[scale=.25]{Chapter1/cs_draw_1.png} \includegraphics[scale=.25]{Chapter1/cs_draw_2.png}
+\includegraphics[scale=.35]{Chapter1/cross_section.png} 
+ \caption[Cross section illustration]{Left hand (a): single incident particle of type $a$ traversing a region containing particles of type $b$.
+Right-hand plot (b): projected view of the region traversed by the incident particle in time $\delta t$ \cite{thomson_2013}.}
+    \label{cross_section}
+  \end{figure}
+\end{center}
+
+where a single incident particle of type $a$ is travelling with a velocity $v_{a}$ in a region defined by the area $A$, wish contains $n_{b}$ particles of type$ b$ per unit volume moving with a velocity $v_{b}$ in the opposite direction to $v_{a}$.
+In  time $\delta t$, the particle a crosses a region containing $\delta N= nb(v_{a}+v_{b}) A \delta t$ of type $b$.
+The interaction probability can be obtained from the $effective$ total cross sectional area of the $\delta N$ particles divided by the area $A$, which can be thougth of as the probability that the incident particle passes through one of the regions of area $\sigma$ drawn around each of the $\delta N$ target particles, as shown in Fig.
+\ref{cross_section}(b) \cite{thomson_2013}.
+The interaction probability $\delta P$ is therefore:
+
+\begin{equation}
+\delta P= \frac{\delta N \sigma}{A}=\frac{n_{b}(v_{a}+v_{b})A\sigma \dela t}{A}= n_{b}v\sigma \delta t ,
+\end{equation}
+
+where $v=v_{a}+v_{b}$. The interaction rate for each particle of type $a$ is
+
+\begin{equation}
+r_{a}= \frac{dP}{dt}= n_{b} v\sigma
+\end{equation}
+
+For a beam of particles of type $a$ with number density $n_{a}$ confined to a volume $V$, the total interaction rate is:
+
+\begin{equation}
+\text{rate}=r_{a}n_{a}V=(n_{b}v\sigma) n_{a}V= (n_{a}v)(n_{b}V)\sigma
+\end{equation}
+
+\begin{equation}
+\text{rate}=(n_{a}v)(n_{b}V) \sigma = \phi N_{b} \sigma
+\end{equation}
+
+Thus the total rate is equal to
+
+\begin{equation}
+\text{rate}= \text{flux} \times \text{number of target particles} \times \text{cross section}
+\end{equation}
+
+More formally, the cross section for a process is defined as:
+
+\begin{equation}
+\sigma=\frac{\text{number of interaction per unit time per target particle}}{\text{incident flux}}
+\end{equation}
+
+Where the flux $\phi$ accounts for the relative motion of particles.
+The value of the cross section is crucial in calculating luminosity, as it represents the constant of proportionality between the rate measured by the detector and the luminosity.
+
 \section{Luminosity }
+%W. Herr, Concept of Luminosity, Proceedings of CERN Accelerator School, Zeuthen 2003, CERN-2006-002 (2006).
+%https://cds.cern.ch/record/941318/files/p361.pdf
+
+In particle physics experiments the energy available for the production of new effects is the most important parameter.
+Besides the energy the number of useful interactions (events), is important.
+The quantity that measures the ability of a particle accelerator to produce the required number of interactions is called the luminosity $\mathcal{L}_{inst}$ and is the proportionality factor between the number of events per second ($dR/dt$) and the cross section $\sigma_{p}$ \cite{concept_of_luminosity}: %\cite{ref_lib_vol3}:
+
+\begin{equation}
+\frac{dR}{dt}=\mathcal{L}_{inst} \cdot \sigma_{p}
+\end{equation}
+
+Where t he unit of luminosity is $cm^{-2}s^{-1}$.
+
+To derive a general expression for luminosity in the case of two colliding beams, we consider both beams to serve as the target and the incoming beam simultaneously.
+We will assume that the beams are "bunched", meaning that the particles are grouped into packets or bunches.
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+\includegraphics[scale=.25]{Chapter1/luminosity.png} 
+ \caption[Colliding beam interaction]{Schematic view of a colliding beam interaction\cite{concept_of_luminosity}}
+    \label{luminosity}
+  \end{figure}
+\end{center}
+
+A schematic picture is shown in Fig.
+\ref{luminosity}.
+Since the two beams are not stationary but are moving through each other, the overlap integral depends on the longitudinal position of the bunches, and therefore on time.
+As the beams move towards and through each other, the two beams have different distribution functions and a different number of particles in the beams.
+The overlap integral, which is proportional to the luminosity ($\mathcal{L}_{inst}$), can then be written as \cite{concept_of_luminosity}:
+
+\begin{equation}
+  \mathcal{L}_{inst}\propto K\cdot \int\int \int_{-\infty}^{\infty} \rho_{1}(x,y,s,-s_{0}) \rho_{2}(x,y,s,s_{0})dxdydsds_{0}
+    \label{lumi_1}
+\end{equation}
+
+Where  $\rho_{1}(x,y,s,-s_{0})$ and $\rho_{2}(x,y,s,s_{0})$ are the time dependent beam density distribution functions.
+We assume, that the two bunches meet at $s_{0} = 0$.
+Because the beams are moving against each other, we have to multiply this expression with a kinematic factor:
+
+\begin{equation}
+ K = \sqrt{(\vec{v_{1}}-\vec{v_{2}})^{2}-(\vec{v_{1}}\times \vec{v_{2}})^{2}/c^{2}}
+    \label{kinematic}
+\end{equation}
+
+Assuming head-on collisions $( \vec{v_{1}}=-\vec{v_{2}} )$ and that all densities are uncorrelated in all planes.
+In that case we can factorize the density distributions and get for the overlap integral:
+
+\begin{equation}
+  \mathcal{L}_{inst}= 2N_{b} N_{1}N_{2}f \int\int\int\int_{-\infty}^{\infty}  \rho_{1x}(x)\rho_{1y}(y)\rho_{1s}(s-s_{0})\rho_{2x}(x)\rho_{2y}(y)\rho_{2s}(s+s_{0}) dxdydsds_{0}
+    \label{luminosity_2}
+\end{equation}
+
+where $N_{1} \textit{ and } } N_{2}$ are the particles per bunch, $f$ the revolution frequency and $N_{b}$ is the number of bunches in one beam.\\
+
+Assuming Gaussian profiles in all dimensions of the form:
+
+\begin{eqnarray}
+\rho_{iz}(z)= \frac{1}{\sqrt{2\pi} \sigma_{z}} exp \biggl(-\frac{z^{2}}{2\sigma_{z}^{2}} \biggr)&z=x,y&i=1,2 
+\end{eqnarray}
+
+\begin{eqnarray}
+\rho_{s}(s\pm s_{0})= \frac{1}{\sqrt{2\pi} \sigma_{s}} exp \biggl(-\frac{(s\pm s_{0})^{2}}{2\sigma_{s}^{2}} \biggr)
+\end{eqnarray}
+
+In the case of exactly head-on collisions of bunches travelling almost at the speed of light, the kinematic factor becomes 2, assuming approximately equal bunch
+lengths $\sigma_{1s}\approx \sigma_{2s}$. Solving  eq. \ref{luminosity_2}:\\
+
+For a general case where $\sigma_{1x}\neq \sigma_{2x} \text{ and } \sigma_{1y}\neq \sigma_{2y}$:
+
+\begin{equation}
+  \mathcal{L}_{inst}= \frac{N_{1} N_{2} N_{b}f }{2\pi \sqrt{\sigma_{1x}^{2}+\sigma_{2x}^{2}}\sqrt{\sigma_{2y}^{2}+\sigma_{2y}^{2}}}
+  \label{lumi_general}
+\end{equation}
+
+For a specific case, asuming equal beams, $\sigma_{1x}= \sigma_{2x} ,\sigma_{1y}= \sigma_{2y} \text{ and } \sigma_{1s}= \sigma_{2s}$:
+
+\begin{equation}
+  \mathcal{L}_{inst}= \frac{N_{1} N_{2} N_{b}f }{4\pi \sigma_{x} \sigma_{y}}
+  \label{lumi_theor}
+\end{equation}
+
+This is the well known expression for the luminosity of two Gaussian beams colliding head-on.
+It shows how the luminosity depends on the number of particles per bunch and the beam sizes.
+This reflects the 2-dimensional target charge density we have seen in the evaluation of the fixed target luminosity \cite{concept_of_luminosity}.
+
+In practice,the integral in  \ref{luminosity_2} cannot be solved analytically because   the properties of the colliding beams are not know precisely, so a experimental technique is implemented with a dedicated machine setup to estimate the integrals, yielding a similar expression as \ref{lumi_theor}.
+
+The instantaneous luminosity and therefore the maximum luminosity measure is very important  because reflects the performance of the collider, but  this is not the only measurement concerned with luminosity.
+Another important measurement and in the final figure of merit of luminosity is the so-called integrated luminosity \cite{concept_of_luminosity}:
+
+\begin{equation}
+  \mathcal{L}_{int}=\int_{0}^{T} \mathcal {L}_{\text{inst}}(t') dt'
+\end{equation}
+
+because it directly relates to the number of observed events:
+
+\begin{equation}
+  \mathcal{L}_{int} \ndot \sigma_{p}= \text{number of events of interest}
+\end{equation}
+
+The integral is taken over a period of time $T$ (excluding possible dead time). The integrated luminosity has units of $cm^{-2}$ and is often expressed in inverse barn ($1 barn= 10^{-24}cm^{2}$). \\
+
+Understanding luminosity with the best possible precision is crucial for physics analyses, as luminosity is one of the fundamental parameters used to measure the performance of an accelerator.
 
@@
 
+Luminosity is one of the fundamental parameters used to measure the performance of an accelerator, when two bunches of protons pass through each other, only a few protons from each bunch interact with those circulating in the opposite direction, and luminosity is a measure of the number of these interactions, understanding luminosity with the best possible precision is crucial for physics analyses such as searches for new particles, rare processes, or measurements of known particle properties \cite{lumi_motiv}.
+\\
+
+Knowing the integrated luminosity enables physicists to compare their observations with theoretical predictions and simulations.
+For instance, they can search for dark matter particles that escape collisions undetected by examining the energies and momenta of all particles generated in a collision.
+If there is an imbalance, it could be due to an undetected, potentially dark matter, particle that carries energy away.
+This is a powerful method of searching for new phenomena, but many effects, such as neutrinos produced in collisions, need to be considered.
+Neutrinos also escape undetected and leave an energy imbalance, making them indistinguishable from new phenomena.
+Therefore, to determine if something unexpected has been produced, physicists must look at the numbers \cite{luminosity_importance} .\\
+
+For example,If 11,000 events show an energy imbalance, and the simulations predict 10,000 events containing neutrinos, this could be significant.
+But if physicists only know the luminosity with a precision of 10\%, they could have easily had 11,000 neutrino events, and there were just 10\% more collisions than assumed.
+Clearly, a precise determination of luminosity is critical   \cite{luminosity_importance}.\\
+
+There are also types of analyses that depend much less on absolute knowledge of the number of collisions.
+For example, in measurements of ratios of different particle decays, such as the recent LHCb measurement, uncertainties in luminosity get canceled out in the ratio calculations.
+Other searches for new particles look for peaks in mass distribution and rely more on the shape of the observed distribution and less on the absolute number of events.
+But these also need to know the luminosity for any interpretation of the results \cite{luminosity_importance}.\\
+
+The experimental techniques to determine signal rates are mature enough, where the understanding of acceptances, detector biases, reconstruction efficiencies, or background subtraction is at the sub-percent level, so that the final precision of the physics measurement is dominated by the luminosity uncertainty \cite{lumi_paper_def_and_concept}.\\
+Ultimately, the greater the precision of the luminosity measurement, the more physicists can understand their observations and delve into hidden corners beyond our current knowledge.
+
 \section{The Large Hadron Collider}
+
+The Large Hadron Collider (LHC) is the world’s largest and most powerful particle accelerator.
+It first started up on 10 September 2008, and remains the latest addition to CERN’s accelerator complex.
+The LHC consists of a 27-kilometre ring of superconducting magnets with a number of accelerating structures to boost the energy of the particles along the way.
+Inside the accelerator, two high-energy particle beams travel at close to the speed of light before they are made to collide.
+The beams travel in opposite directions in separate beam pipes – two tubes kept at ultrahigh vacuum.
+They are guided around the accelerator ring by a strong magnetic field maintained by superconducting electromagnets.
+The electromagnets are built from coils of special electric cable that operates in a superconducting state, efficiently conducting electricity without resistance or loss of energy.
+This requires chilling the magnets to ‑271.3°C – a temperature colder than outer space \cite{LHC}.\\
+Magnets of different varieties and sizes are used to direct the beams around the accelerator.
+These include 1232 dipole magnets, 15 metres in length, which bend the beams, and 392 quadrupole magnets, each 5–7 metres long, which focus the beams.
+Just prior to collision, another type of magnet is used to "squeeze" the particles closer together to increase the chances of collisions .\\
+
+The production of proton beams for the LHC involves a complex series of pre-acceleration stages.
+To begin with, hydrogen is ionized to produce protons, which are then accelerated in bunches up to 50 MeV within the Linear Accelerator 2 (LINAC2).
+Subsequently, these proton bunches are routed through three circular accelerators - the Booster, the Proton Synchrotron (PS), and the Super Proton Synchrotron (SPS) - in order to gradually increase their energy levels to 1.4 GeV, 26 GeV, and 450 GeV, respectively.
+Following these pre-acceleration stages, the proton bunches are injected into the LHC ring where they are accelerated to reach energies of up to 7 TeV per bunch while circulating in opposite directions.
+This entire sequence of steps defines a single LHC fill, which typically involves $10^{14}$ protons that are grouped into bunches to form the proton beam.
+Figure \ref{lhc_com} depicts the complete CERN accelerator complex.
+\\
+
+The responsibility for overseeing all controls, services, and technical infrastructure of the LHC lies with the CERN Control Centre.
+This is the central location where proton beams are directed to collide at four distinct positions along the accelerator ring, corresponding to the positions of the four particle detectors: CMS and ATLAS, which are general-purpose detectors specifically designed to investigate a broad range of Standard Model (SM) and Beyond SM (BSM) physics, while ALICE and LHCb serve as specialized detectors, specifically focused on studying particular phenomena.
+
+\begin{center}
+  \begin{figure}[h]
+    \centering
+    \includegraphics[scale=.35]{Chapter1/lhc_complex_fig.png}
+    \caption[LHC Complex]{Diagram of the LCH complex \cite{lhc_complex}.}
+    \label{lhc_com}
+  \end{figure}
+\end{center}
 
@@
 
+The LHC has undergone three runs and two lengthy shutdowns to facilitate maintenance and upgrades. The instantaneous and integrated luminosity for each of these runs is presented below.
+
+Run 1 of the physics program at the Large Hadron Collider began in 2010 with proton-proton collisions at a center-of-mass (CM) energy of 7 TeV.
+By the end of 2011, CMS had collected a data sample with an integrated luminosity of $6 fb^{-1}$.
+This run concluded in August 2012 at a CM energy of 8 TeV, with instantaneous peak luminosities approaching $0.77 \times 10^{34}$ and an integrated luminosity of $25 fb^{-1}$ \cite{LHC_status_2013}.
+
+Run 2 was divided into two stages.
+The first stage took place from 2015 to 2016, with proton-proton collisions at a center-of-mass energy of $\sqrt{s}=\text{13 TeV}$ in the CMS detector, reaching integrated luminosities of $2.2$ and $36.3$ $fb^{-1}$ with relative precision of 1.6$%$ and 1.2$%$, respectively \cite{lumi_precise_2015_2016}.
+For the second part of Run 2 (2017-2018), the integrated luminosity was approximately $49.8 fb^{-1}$ and $67.9 fb^{-1}$ for 2017 and 2018, respectively.
+The total systematic uncertainty in the calibration of luminosity measurement was 2.3$%$ in 2017 \cite{pas_17} and 2.5$%$ in 2018 \cite{pas_18}, but there is a need for further improvement in its precision.
+
+Run 3 began in 2022 and is currently ongoing. The primary objective of this thesis project is to contribute to the improvement of the LHC luminosity precision calibration for this stage.
+Figure \ref{lumi_per_year_int} depicts the delivered luminosity versus time for the 3 runs.
+
+\begin{center}
+  \begin{figure}[h]
+    \centering
+    \includegraphics[scale=.3]{Chapter1/int_lumi_per_year.png}
+    \caption[CMS Luminosity per year]{Delivered luminosity versus time for Run-1 (2010-2012)\cite{pas_17} and Run-2 (2015-2018)\cite{pas_18} and Run-3 that is still ongoing .
+Cumulative luminosity versus day delivered to CMS during stable beams for pp collisions at nominal center-of-mass energy.
+\cite{wikicern}.}
     \label{lumi_per_year_int}
@@
 
-%lumi values:
-% https://inspirehep.net/files/11b4a1d6569e8e066e7431f17a55d69c
-
-% https://arxiv.org/pdf/1504.06519.pdf
-
-%ATLAS 2015-2018: https://arxiv.org/pdf/1911.04632.pdf
+%https://twiki.cern.ch/twiki/bin/view/CMSPublic/LumiPublicResults

### 2023-03-27 tesis_Luis/Chapter4/chapter4.tex
updated

@@
 The main VdM scan program for the CMS experiment was performed in November 2022 during LHC fills 8379 and 8381.
-In fill 8381 on 10 and  11 Nov 2022 at pp collision energy $\sqrt{s}$ of 13.6 TeV, 144 bunch pairs were colliding at the CMS intertion points at zero crossing angle, with two additional unpaired bunches present in each beam.
-Four VdM scan pairs, two beam-imaging (BI) scan pairs, and one length scale scan pair where performed, where each scan pair consists of two scans in the transverse planes x and y, as well as other scan types not included in this analysis.
+In fill 8381 on 10 and  11 Nov 2022 at pp collision energy $\sqrt{s}$ of 13.6 TeV  144 bunch pairs were colliding at the CMS intertion points at zero crossing angle, with two additional unpaired bunches present in each beam.
+Four VdM scan pairs, two beam-imaging (BI) scan pairs and one length scale scan pair where performed, where each scan pair consists of two scans in the transverse planes x and y, as well as other scan types not included in this analysis.
 In a VdM scan, the two beams are separated by $6\sigmab$ ≈ 578 $\mu m$ and scanned across one another in a sequence of 25 steps of 30 s with a step size of $0.5\sigma_{b} \thickapprox 48 \mu m$, where $\sigma_{b}$ is the transverse bunch size.
 In the BI scans, one beam is kept fixed at its nominal head-on position while the other is separated and scanned in 19 steps of 46 s from $-4.5\sigma_{b}$ to $+4.5\sigma_{b} \thickapprox 433 \mu m$.
-In a length scale scan, the beams are separated by a constant amount of $\sqrt{2} \sigma_{b} \thickapprox  106 \mu m$  and moved coherently forward and backward in five steps each in the same transverse direction.
+In a length scale scan, the beams are separated by a constant amount of $\sqrt{2} \sigma_{b} \thickapprox  106 \mu m$  and moved coherently forward and backward in five steps each in the same transverse direction, finally two super separation periods were performed for the analysis and Background sustraction, here the two beams were sepated at a distance of $6\sigma$.
 The scan program during fill 8381 is summarized in Fig.
-\ref{scan_prog}.
+\ref{scan_prog}.\\
 
-The VdM calibration itself is based on scans recorded during Fill 8381.
-Six scan pairs are used that are either of standard VdM type They are labeled consecutively as they were recorded in time, as “VdM1”, “BI1”, “BI2”, “VdM2”, “VdM3”, and “VdM4”.
-During the VdM2 scan pair, the central CMS data taking was not operational, so no data was recorded for PCC, and this scan pair is skipped in the PCC VdM analysis.
-To ensure a dataset with a high event count for PCC even at large beam separations, CMS gated the zero-bias triggers on 5 bunch pairs: BCIDs (Bunch Crossing ID) 282, 822, 2944, 3123, and 3302 ; and recorded events with a total rate of 27.23 kHz .
+The VdM calibration itself is based on scans recorded during the fill 8381, where the  Six scan pairs using for  this analysis were performed, they are labeled consecutively as they were recorded in time, as “VdM1”, “BI1”, “BI2”, “VdM2”, “VdM3”, and “VdM4” as shown in figure \ref{scan_prog} .
+During the "VdM2" scan pair, the central CMS data taking was not operational, so no data was recorded for PCC, and this scan pair is skipped in the PCC VdM analysis.
+To ensure a dataset with a high event count for PCC even at large beam separations, CMS gated the zero-bias triggers on 5 bunch pairs: BCIDs (Bunch Crossing ID) 282, 822, 2944, 3123, and 3302 and recorded events with a total rate of 27.23 kHz.\\
 
@@
     \includegraphics[scale=.25]{Chapter4/2022Scanprorgam.png}
-    \caption[2022 scan program]{Nominal horizontal and vertical positions of the proton beams during LHC fill 8381}
+    \caption[2022 scan program]{Nominal horizontal and vertical positions of the proton beams during LHC fill 8381, showing the four normal VdM scans, two BI scans and the two Super Separation Periods (SS)}
     \label{scan_prog}
@@
 
-The data taken by the  PCC luminometer was reprocessed to perform a cluster reconstruction.
-The datasets containing the cluster information per event were stored in 16 different Zero Bias datasets.
+The data taken by the  PCC luminometer was reprocessed for the CMS team to perform a cluster reconstruction.
+The datasets containing the cluster information per event were stored in 16 different "zero Bias" datasets.
 The first step we took was to extract the data corresponding to the events that belong to our 6 VdM Scans (Runs, Pixel cluster clusters, timestamps, etc.) in a file with ROOT format that is the CERN's data analysis package.
 This was done through the CMS software (CMSSW), which is written in Python2 and C++.\
-Afterward, we have the 16  resuulting datasets, uno for each Zero Bias.
-These files are reprocessed to generate the final file containing the rates stored per 1.32 s (NB4) with Hierarchical Data Format (HD5).
+Afterward, we have the 16  resuulting datasets, uno for each "zero Bias" dataset.
+These files are reprocessed to generate the final file containing the rates stored per 1.32 s (NB4) with a hierarchical data format (HD5).
 Within this data reprocessing, we clean the information by subtracting the background and also select the modules that were previously analyzed by a stability study.
 
-The final hd5 file containing the rates from the detector with data collected during the vdM scans is analyzed using a software framework called the "vdM Framework" (vdM FW), which is the latest version and is written in Python3.
+The final "hd5" file containing the rates from the detector with data collected during the vdM scans is analyzed using a software framework called the "vdM Framework" (vdM FW), which is the latest version and is written in Python3.
 The vdM FW uses data analysis package, "ROOT," through the "PyRoot" library.
@@
 
-\section{Module selection}
+\section{Background estimation}
 
-To ensure accurate luminosity measurement, a veto list is created to remove any modules exhibiting long-term performance variations, indicating a non-physical shift in their cluster counts.
-With a total of 1856 modules in the pixel system, all of them can be considered in the luminosity measurement; however, non-zero occupancy and non-linear effects can pose challenges for accurate measurement.
-Thus, to identify "good" and "stable" modules, a subset is selected by eliminating  underperforming or "bad" modules and comparing their relative contributions to the cross section.
-Those with relatively consistent contributions across standard physics runs are kept, while those with significant changes in their relative cross section compared to the averaged relative contribution are rejected.
-The Module selection is made as:
+To extract $\Sigma_{x,y}$ through fitting, it is necessary to correct the raw measured rates for background in the detector beforehand.
+The background contribution is estimated independently during the Super Separation (SS) period comented in the above section.
+During this period, the beams are separated by $6\sigma_{b}$, ensuring that the only contribution is from background.
+There are three principal sources of beam-induced background to consider:
+
 \begin{itemize}
-\item Poor statistics lumisections are removed by applying selection on total PCC.
-\item Barrel layer-1 modules are removed, as these modules are significantly affected by dynamic inefficiency.
-\item A loose selection of 7\% based on RMS/mean of module weight is applied. Modules with significantly large RMS/mean are removed with this selection as shown in \ref{goodmodule}.
-\item The module stability is re-evaluated based on RMS/mean values using an iterative method where appropriate selections are applied to remove underperforming modules until a stable luminosity is attained.
+
+\item Beam Gas Elastic (BGE).
+The elastic beam gas contribution are all coherent and quasi-elastic nuclear elastic and coulomb scattering for multi-turn beam-gas interactions around the ring.
+Typically the interaction of the primary beam proton and the takes place at the TCT collimator, so that this background contribution has an almost point- like source \cite{bkg_source}.
+
+\item Beam Gas Inelastic (BGI).
+These are all inelastic interactions of primary beam protons with rest gas in the beam pipe.
+The interaction rate is dominated by the vacuum quality in the various beam line elements upstream CMS.
+Therefore the origin of this contribution is distributed all along the long straight section \cite{bkg_source}.
+
+\item Beam Halo (BH).
+This component of the machine induced background is caused by the inefficiency of the main collimation system.
+Protons can escape from one collimator and being intercepted by another collimator \cite{bkg_source}.
 \end{itemize}
 
-\begin{center}
-  \begin{figure}[h!]
-    \centering
-    \includegraphics[scale=.20]{Chapter4/RMSmean.png}
-    \caption[RMS/mean Module  Stability]{ RMS/mean values of module weight for all pixel modules. Each pixel module is represented by a module number index.} 
-    \label{goodmodule}
-  \end{figure}
-\end{center}
-
-To ensure accurate measurements, a pixel module veto list is established for each period, recognizing that different periods may have varying numbers of well-performing modules.
-The pixel detector is subject to changing conditions over time, such as detector noise, aging effects, and radiation damage.
-Stability of the pixel modules is assessed based on changes in the module PCC ratio relative to the total PCC, known as module weight.
-These variations are evaluated over an interval of 23 seconds, corresponding to the granularity of the luminosity database.
-The pixel module veto list is first generated for the period 2022F containing the vdM fill and subsequently for the periods ,C, D, E and G,  following the same procedure.
-
-\noindent To further improve the stability of the PCC measurement, a 4\% RMS common module vetolist is created as shown in table \ref{common  veto module}.
-The approach to derive the common module veto list is to start by combining module vetolists of period C and D; then combine C, D and E; and so on.
-The zero-bias PCC data is reprocessed using this common module vetolist.
-
-\begin{table}[h!]
-\centering
-\caption{Number of good and bad modules for the combined vetolist, after each iteration of the 4\% RMS selection with an additional period.}
-\begin{tabular}{ccc}
-\textbf{Period} & \textbf{\# bad modules} & \textbf{\# good modules}  \\ 
-\toprule
-2022C+D         & 886                     & 970                       \\
-2022C+D+E       & 1106                    & 750                       \\
-2022C+D+E+F     & 1307                    & 549                       \\
-2022C+D+E+F+G   & 1411                    & 445                   
-\label{common  veto module}   
-\end{tabular}
-\end{table}
-
-\noindent This final common veto in conjunction with background subtraction  is used for the last reprocesing data file used for e VdMFramework.
-
-\section{Background estimation}
-
-To determine the final PCC rate, the background estimation is conducted using two available super-separation scans SS1 and SS2 shown in the figure \ref{scan_prog}, which are carried out independently and then compared.
-In order to illustrate the two SS periods, Figure \ref{ssp_wide_bx282} displays the PCC per NB4 versus time for BCID 282.
-The lower regions of the plot correspond to a time window of 5 minutes during which the beams were separated by a distance of $6\sigma_{b}$, guaranteeing that the sole contribution is from the background, which could either be beam-induced or electronics noise.
+In order to illustrate the two SS periods for this analisys, Figure \ref{ssp_wide_bx282} displays the PCC per NB4 versus time for BCID 282.
+The lower regions of the plot correspond to a time window of 5 minutes during which the beams were separated by a distance of $6\sigma_{b}$.\\
 
@@
 \end{center}
-\\
 
@@
 
-\newpage
 \begin{table}[h!]
@@
 The derived correction assumes that the beam overlap has a single Gaussian shape.
-The correction reads the $\Sigma_{vis}$ in the orthogonal direction from the previous correction.
+The correction reads the $\sigma_{vis}$ in the orthogonal direction from the previous correction.
 \end{itemize}
@@
 
-Obtaining a final  $\sigma_{vis}$ result of:
-
-\begin{equation}
-\sigma_{vis} = 4163 \pm 3 \text{(stat.)} \pm 12 \text{(syst.)} \text{ mb} .
-\end{equation}
+Obtaining a final sigma visible for the calibration $\sigma_{vis}=4163 \pm 3 \text{(stat.)} \pm 12 \text{(syst.)} \text{ mb}$.
+This result will be useful for a precise luminosity measurement analysis for Run 3 in the CMS experiment of LHC.
 

### 2023-03-29 tesis_Luis/Abstract/abstract.tex
updated

--- 2022-04-29 tesis_Rodolfo/Abstract/abstract.tex
@@
 \end{center}
-    van der Meer calibration is decribed
+The calibration of the luminosity measurement from the analysis of the van der Meer scanning program for the  CMS experiment in the  2022 proton-proton collision data-taking at $\sqrt{s}=$13.6 TeV with the CMS Silicon Pixel detector is described.
+The data collection period was on November 10 and 11 for the LHC fill 8381, the data collected was reprocessed along with a selection of good modules based on stability studies.
+The analysis of the van der Meer scans with some especific corrections results in the calibration constant  $\sigma_{vis}= 4163 \pm 3 (\text{stat.}) \pm 12 (\text{syst.})\text{ mb}$ for the Pixel Cluster Counting luminometer.
+
 \end{abstract}

### 2023-03-29 tesis_Luis/Abstract/resumen.tex
Add files via upload
updated

--- 2022-04-29 tesis_Rodolfo/Abstract/resumen.tex
@@
 \end{center}
-Calibracion de van der Meer
+Se describe la calibraci\'on de la medici\'on de luminosidad para la corrida 3 del gran colisionador de hadrones (LHC),  realizada mediante el programa de escaneo  "Van der Meer"  para el experimento CMS  durante 10 y 11 de Noviembre del 2022 .
+La toma de datos  proton-proton a $\sqrt{s}=$13.6 TeV fue con  el detector de pixeles de silicio (Silicon Pixel detector) para el  fill 8381, dichos datos se reprocesaron  aplicando una selecci\'on de  m\'odulos "buenos" en el  detector, basandose en un estudio de estabilidad de \'estos.
+El an\'alisis de 5 escaneos de Van der Meer presentados en este trabajo arroja en la constante de calibraci\'on $\sigma_{vis}$ un valor de:   $4163 \pm 3 (\text{stat.}) \pm 12 (\text{syst.})\text{ mb}$.
 \end{abstract}

### 2023-03-29 tesis_Luis/Chapter2/chapter2.tex
changes
updated

@@
 \chapter{Experiment Description }
+
+Modern general-purpose detectors used in high-energy colliders typically employ cylindrical detection layers arranged around the beam axis.
+One such example is the Compact Muon Solenoid (CMS), which is part of the LHC at CERN and is considered one of the largest international scientific collaborations in history.
+The CMS is designed for a broad physics program that includes studying the Standard Model.
+This chapter provides a description of the various components of the CMS detector,incliding the several systems to measure the luminosity with a particular focus on the silicon pixel tracker, which is described in greater detail due to its relevance to the thesis.
 
@@
 
+The CMS experiment is one of the four general-purpose detectors situated at the LHC.
+The CMS detector is constructed around a massive solenoid magnet, which is a cylindrical coil of superconducting cable generating a magnetic field of 4 tesla, this field is used to separate the calorimeter energy deposits of charged and neutral particles in jets.
+The field is confined by a steel "yoke" which constitutes the bulk of the detector's weight of 14,000 tonnes \cite{CMS_Exp_2008}.
+The CMS detector has a complete length of 21.6 meters and a diameter of 14.6 meters that  comprises various detection layers that include separate parts of the detector.
+
+These layers are the fine-grained silicon tracker, which provides efficient and precise reconstruction of charged-particle trajectory.
+The highly-segmented electromagnetic calorimeter (ECAL) wish principal purpose is the detection of  electromagnetic energy and the identification of electrons and photons.
+The hadronic calorimeter (HCAL) wish principal purpose is the detection of hadrons in jets  \cite{CMS_Exp_2008}.
+Additionally, there is an excellent muon tracking system, .
+A schematic representation of the CMS detector is shown in \ref{detector_CMS}.\.%% is a summary
+%%The energies of the particles are crucial to understanding what occurred at the collision point.
+This information is collected from two calorimeters in the CMS.
+The inner layer is the Electromagnetic Calorimeter
+
+\begin{center}
+  \begin{figure}[ht]
+    \centering
+    \includegraphics[scale=.3]{Chapter2/CMS_detector_simple.png}
+    \caption[Perspective view of the CMS detector]{Perspective view of the CMS detector.}
+    \label{detector_CMS}
+  \end{figure}
+\end{center}
+
+A powerful magnet is required to bend charged particles as they travel outward from the collision point.
+Bending the trajectory of the particles serves two purposes: first, it helps identify the charge of the particle, as positively and negatively charged particles bend in opposite directions in the same magnetic field; and second, it enables measurement of the particle's momentum.
+
+The CMS must identify the paths of these deflected charged particles with high precision.
+This is achieved using a silicon tracker composed of approximately 75 million individual electronic sensors arranged in concentric layers \cite{CMS_Exp_2008}.
+When a charged particle passes through a Tracker layer, it interacts electromagnetically with the silicon and produces a hit.
+These individual hits can be combined to identify the track of the traversing particle.
+
+(descipcion )
+(ECAL), which measures the energy of electrons and photons by completely stopping them.
+It is a hermetic, homogeneous calorimeter consisting of 61,200 lead tungstate (PbWO4) crystals mounted in the central barrel part and closed by 7,324 crystals in each of the two endcaps.
+In front of the endcap crystals, a preshower detector is placed.
+Avalanche photodiodes (APDs) are used as photodetectors in the barrel and vacuum phototriodes (VPTs) in the endcaps.
+Hadrons, which are composite particles made up of quarks and gluons, travel through the ECAL and are stopped by the outer layer, called the Hadron Calorimeter (HCAL) \cite{det_summary}.
+
+The final particle that the CMS directly observes is the muon.
+Muons are approximately 200 times heavier than electrons and are not stopped by the calorimeters.
+Therefore, special sub-detectors have to be constructed to detect them as they traverse the CMS.
+These sub-detectors are interleaved with the return yoke of the solenoid.
+The large magnet of the CMS also allows us to measure each muon's momentum both inside the superconducting coil (using the tracking devices) and outside of it (using the muon chambers) \cite{det_summary}.
+
+A transverse slice of the CMS detector, depicting specific particle interactions, is shown in Figure \ref{slice_CMS}.
+
+\begin{center}
+  \begin{figure}[ht]
+    \centering
+    \includegraphics[scale=.3]{Chapter2/slice_det.png}
+    \caption[Transverse slice fo CMS detector]{Transverse slice of the CMS detector with some particle interactions (from the beam interaction region to the muon detector).  \cite{det_summary}.}
+    \label{slice_CMS}
+  \end{figure}
+\end{center}
+
+The CMS's coordinate system has its origin located at the center of the detector, with the $y$-axis oriented vertically upwards and the $x$-axis directed radially inward, toward the center of the LHC.
+As a result, the z-axis aligns with the direction of the beam.
+In this system, the azimuthal angle $\varphi$ is measured from the $x$-axis within the $x-y$ plane, while the radial coordinate in this plane is represented by $r$.
+Furthermore, the polar angle $\theta$ is measured with respect to the z-axis \cite{CMS_Exp_2008}.
+
+\section{CMS Luminometers}
+
+A total of seven systems are used for measuring luminosity at CMS.
+The Pixel Luminosity Telescope (PLT) and Fast Beam Conditions Monitor (BCM1F) are dedicated systems for luminosity measurement, while the hadronic forward calorimeter (HF) uses a dedicated readout on an existing system.
+Additionally, three other methods, the drift tube luminosity (DT), the pixel cluster counting method (PCC), and the vertex counting method (VTX), use data from existing parts of the CMS detector to perform a luminosity measurement using the main CMS DAQ system.
+The PCC measurement uses the data collected with the standard CMS trigger system with triggers requiring colliding bunches but not any specific event activity, known as "zero-bias" triggers.
+Finally, the RAMSES detectors are part of the LHC environmental protection and monitoring systems, but they can also be used to provide a luminosity measurement readout through Timber(operational data and LHC logging service) \cite{pas_18}.
+A brief overview of the CMS luminometers is provided below:
+%%%%%%% no bullets
+\begin{itemize}
+
+\item PLT Is a dedicated system for measuring luminosity using silicon pixel sensors.
+There are a total of 48 sensors arranged into 16 “telescopes”,eight at either end of CMS outside the pixel endcap, where each telescope contains three sensor planes arranged nearly parallel to the beam pipe.
+The PLT measures the rate of “triple coincidences”, where a hit is observed in all three planes, typically corresponding to a track from a particle originating at the interaction point.
+The overall mean rate for PLT  is estimated using the zero-counting method, where it is assumed that the number of observed triple coincidences follows a Poisson distribution \cite{pas_18}.
+
+\item BCM1F comprises a total of 24 sensors mounted on the same carriage as the PLT, consisting of 10 silicon sensors, 10 polycrystalline diamond (pCVD) sensors, and 4 single-crystal diamond (sCVD) sensors.The BCM1F readout features a fast readout with 6.25 ns time resolution; the precise time measurement, in conjunction with the position of BCM1F 1.8 m from the center of CMS, allows hits from collision products to be separated from hits from machine-induced background, because the incoming background is separated in time from the outgoing collision products  \cite{pas_18}.
+
+\item HF luminosity measurement uses a dedicated readout system installed in the HF calorimeter.
+Only two HF rings are used for luminosity measurement to ensure relatively uniform occupancy.
+Two algorithms are available: the first relies on the fraction of occupied towers (HFOC), and the second is based on the sum of the transverse energy ET (HFET)  \cite{pas_18}.
+
+\item Drift tube luminosity (DT), which uses the rate of muon track stubs in the muon barrel track finder and  RAMSES detectors, a CERN radiation and environmental monitoring system, although not designed as a luminometer, function quite well as a luminosity measurement, using the rate observed in the detectors (primarily photons within the energy range of 50 keV to 7 MeV) \cite{pas_18}.
+
+\item RAMSES.
+Althoug is not designed as a luminometer, the rate observed in this detector does function quite well as a luminosity measurement.
+RAMSES is a CERN radiation and environmental monitoring sytem, currently a part of the REMUS supervisory system.
+The sensor itself is a cylindrical plastic ionization chamber filled with 3 L of air at atmospheric ressure and it primarily detects photons.
+The overall rate in the RAMSES detectors is small, which means that it is not capable of making bunch-by-bunch measurements and cannot be independently calibrated using a VdM scan; however, this also means it is less affected by issues such as instability caused by radiation damage or nonlinearity \cite{pas_18}.
+
+\item The PCC method uses the rate of pixel clusters in the CMS pixel detector to provide a luminosity measurement this method will be described in more detail in chapter 3.  
+\end{itemize}
+
+The location of the 7 luminometers in the CMS experiment are shown in Figure \ref{luminometers}.
+
+\begin{center}
+  \begin{figure}[ht]
+    \centering
+    \includegraphics[scale=.3]{Chapter2/detectors.png}
+    \caption[CMS Luminometers]{The seven luminometers that make up the CMS luminosity measurement system.
+Multiple independent systems used online: BCM1F, HFET, HFOC, PLT (independently calibrated) ,REMUS and  DT (cross-calibrated) , Pixel cluster counting is used after offline processing.}
+    \label{luminometers}
+  \end{figure}
+\end{center}
+
 \section{CMS Tracking System}
 
-\begin{equation}
-  -\frac{dE}{dx}= \frac{Dq^{2}n_{e}}{\beta ^{2}} \biggl[ \ln \left(\frac{2m_{e}c^{2}\gamma^{2}}{I} \right) -\beta^{2} -\frac{\delta(\gamma)}{2}  \biggr]
-  \label{bethe}
-\end{equation}
+The tracking system plays a crucial role in precisely measuring the trajectories and momenta of charged particles generated by collisions in the LHC, as well as reconstructing secondary vertices.
+It has a physical size of 5.8 m in length and 2.5 m in diameter and is surrounded by the CMS solenoid, which provides a homogeneous magnetic field of 4T throughout the tracker's volume \cite{CMS_Exp_2008}.
 
-\subsection{Pixel Detector and Clustering}
-\label{pixel_clust_reco}
+The CMS tracking detector relies on semiconductor technology that uses silicon pixels and strips, this is divided in two systems: a pixel detector with four barrel layers located between 2.9 cm and 16 cm radii and a silicon strip tracker with ten barrel detection layers extending to a radius of 1.1 m.
+Each part includes endcaps, with the pixel detector having three disks and the strip tracker having three plus nine disks on each side of the barrel \cite{CMS_Exp_2008}.
+This extends the tracker's acceptance up to a pseudorapidity of $|\eta| < 2.5$, with an active silicon area of approximately 200 $m^2$.
+The construction of the CMS tracker have 1440 pixel and 15148 strip detector modules.
+The layout of the CMS tracker is presented in the following figure:
 
-\subsection{CMS Luminometers}
+\begin{center}
+  \begin{figure}[ht]
+    \centering
+    \includegraphics[scale=.23]{Chapter2/strip_layout.png}
+    \caption[Schematic cross section through the CMS tracker]{Schematic cross section through the CMS tracker. Each line represents a detector module \cite{CMS_Exp_2008}.}
+    \label{strip_layout}
+  \end{figure}
+\end{center}
+
+In Figure \ref{strip_layout}, we can observe the pixel detector at the center, surrounded by the Strip tracker.
+The Strip tracker is comprised of two subsystems: the first being the Tracker Inner Barrel (TIB) and Disks (TID), which is further divided into four barrel layers and three disks at each endcap.
+The second subsystem is the Tracker Outer Barrel (TOB), which consists of six barrel layers and the Tracker EndCaps (TEC) comprising of nine disks.
+The Strip tracker in total comprises of 15148 silicon modules, covering an active area of about 198$\text{m}^{2}$, and consists of 9.3 million strips \cite{CMS_Exp_2008}.
+On the other hand, the silicon pixel tracker, which is situated closest to the interaction point, will be elaborated on in the following section.
+
+\section{Silicon Pixel Detector}
+
+The CMS experiment conducted at the Large Hadron Collider (LHC) at CERN comprises a silicon pixel detector, which forms the innermost component of the tracking system.
+This detector facilitates the provision of 3-dimensional space points in the area nearest to the interaction point, which, in turn, enables precise tracking of charged particles and vertex reconstruction.
+The pixel detector operates in a radiation-rich environment, marked by high track density \cite{phase1_Pixel_Detector}.\\
+
+The CMS pixel detector encompasses four concentric barrel layers (L1-L4), each with radii measuring 29, 68, 109, and 160 mm, and three disks (D1-D3) on either end positioned at distances of 291, 396, and 516 mm from the detector's center.
+A schematic of the CMS Phase-1 pixel detector's arrangement is depicted in Figure \ref{phase1_pixel_detector} where the total silicon area of the CMS Phase-1 pixel detector spans 1.9 $\text{m}^{2}$.
+
+\begin{center}
+  \begin{figure}[h]
+    \centering
+    \includegraphics[scale=.26]{Chapter2/phase1_PixelDetector.png}
+    \caption[CMS Phase-1 pixel detector]{Layout of the CMS Phase-1 pixel detector in longitudinal view\cite{phase1_Pixel_Detector}.}
+    \label{phase1_pixel_detector}
+  \end{figure}
+\end{center}
+
+The BPIX and FPIX detectors are equipped with four service half-cylinders each, with a combined length of 540 mm.
+These cylinders host the readout and control circuits, and provide guidance for the power lines and cooling tubes of the detector.
+The BPIX detector is bifurcated into two mechanically self-sufficient halves, both of which are made up of a half detector and two service half-cylinders.
+The orientation of the sensor surface of the modules in both halves is parallel to the magnetic field.
+On the other hand, the FPIX detector is segmented into four mechanically independent quadrants, each of which comprises three half-disks housed in a service half-cylinder.
+The sensor orientation in the FPIX detector is arranged such that the long side of the pixel is aligned with the radial direction and has a coverage from 45 to 161 mm.
+The half-disks are additionally subdivided into inner and outer half-rings that support 22 and 34 modules, respectively \cite{phase1_Pixel_Detector}.\\
+
+The pixel detector is built from 1856 segmented silicon sensor modules, where 1184 modules are used in the barrel pixel detector (BPIX) and 672 modules are used for the forward disks (FPIX).
+Each module consists of a sensor with 160$\times$416 pixels connected to 16 readout chips (ROCs).
+In total there are 124 million readout channels \cite{phase1_Pixel_Detector}.
+A pixel detector module is built from a planar silicon sensor with a size of 18.6 $\times$ 66.6 $\text{mm}^{2}$ (active area of 16.2 $\times$ 64.8 $\text{mm}^{2}$), bump-bonded to an array of 2$\times$8 ROCs.
+Each ROC is segmented into 4160 readout channels and reads out the pulse height information for each pixel.
+The standard pixel size is 100$\times$150 $\mu m^{2}$, as in the original pixel detector.
+The figures depicting the modules of the CMS Phase-1 pixel detector can be found in Figure \ref{modules_drawing} \cite{phase1_Pixel_Detector}.
+
+\begin{center}
+  \begin{figure}[h]
+    \centering
+    \includegraphics[scale=.2]{Chapter2/modules_drawing.png}
+    \caption[Pixel detector modules]{ Drawings of the pixel detector modules for BPIX L1 (left), BPIX L2–4 (middle), and the FPIX detector (right)\cite{phase1_Pixel_Detector}.}
+    \label{modules_drawing}
+  \end{figure}
+\end{center}
+
+\section{Pixel Cluster Reconstruction}
+
+The track reconstruction process involves several steps.
+Firstly, zero-suppressed signals above specified thresholds in pixel channels are clustered into hits.
+These hit pixels are then combined to form clusters from neighboring pixels.
+The charge measured within each cluster corresponds to the charge deposited by a single charged particle.
+Next, the cluster positions and their uncertainties are estimated in a local orthogonal coordinate system  in the plane of each sensor \cite{Track_Reco_2014}.
+The pixel sensor used in this process consists of 100 $\times$ 150$\mu \text{m}^{2}$ pixels  this is shown en the figure \ref{module and hit}.
+
+\begin{center}
+  \begin{figure}[h]
+    \centering
+    \includegraphics[scale=.3]{Chapter2/PixelSensor.png} \includegraphics[scale=.3]{Chapter2/hit.png}
+    \caption[PixelSensor]{ left: Pixel sensor diagram, right: hits detection in a corresponding  pixel sensor \citep{thomson_2013}. }
+    \label{module and hit}
+  \end{figure}
+\end{center}
+
+To be considered a valid cluster, each one must have a minimum charge equivalent to 4000 electrons \cite{Track_Reco_2014,phase1_Pixel_Detector}.
+For normally incident minimum-ionizing particles (MIPs) in a silicon sensor with a thickness of 285 $\mu \text{m}$, the most probable value of energy deposition corresponds to approximately 21,000 electrons.
+However, this charge is often spread over more than one pixel due to Lorentz drift and diffusion of collected electrons, leading to charge clusters.\\
+
+Figure \ref{cluster} is shown a pixel cluster example at $\eta$ = 1.83, here the  charge deposition in each pixel is shown in thousands of electrons, the numbers shown in green correspond to charge depositions below the 2000 electron threshold which are not included in the cluster.
+The dotted red line indicates the particle trajectory projection in the module plane and the red cross shows the true hit position.
+Where the corresponding coordinate systems is based in the  geometry of the CMS barrel and forward pixel detectors \cite{Pixel_Hit_Reconstruction}.
+
+\begin{center}
+  \begin{figure}[h]
+    \centering
+    \includegraphics[scale=.3]{Chapter2/pixel_cluster.png} 
+    \caption[Pixel cluster]{ Left: Geometry of the CMS barrel and forward pixel detectors and the corresponding coordinate systems. Right: A pixel cluster example at $\eta$ = 1.83 }
+    \label{cluster}
+  \end{figure}
+\end{center}

### 2023-03-29 tesis_Luis/Chapter3/chapter3.tex
updated

@@
 \chapter{Luminosity  Measurement and Calibration}
+\label{ch3}
+
+Accurately measuring the luminosity delivered to the CMS experiment by the LHC is essential for various reasons.
+Online, the luminosity measurement provides feedback on the LHC and CMS performance and operations, including measuring trigger rates.
+In offline analysis, the luminosity measurement is a critical component for measuring the cross-section of observed processes or setting upper limits in searches for processes beyond the standard model.
+
+As we see, to measure luminosity, a total of seven luminometers are used at CMS, and each of them reads out a specific quantity observed in the detector, such as hits, tracks, or clusters.
+The rate R measured by the luminometer is proportional to the instantaneous luminosity, $\mathcal{L}_{inst}$, with the constant of proportionality given by the visible cross-section $\sigma{vis}$ \cite{pas_18}.
+
+\begin{equation}
+R(t)=\mathcal{L}_{inst}\sigma_{vis}
+\label{lumi_exp_gen}
+\end{equation}
+
+The determination of $\sigma_{vis}$ is performed through van der Meer (vdM) scans using a specialized LHC machine setup.
+This chapter provides a description of this procedure, specifically applied with the PCC method.
+Additionally, the selection of stable "good" modules necessary for precise luminosity measurements will also be discussed.
+
+\section{Pixel Cluster Counting method}
+
+The PCC method utilizes the rate of pixel clusters in the CMS silicon pixel detector to determine an offline luminosity measurement, this method exploits the very large number of pixels in the inner part of the CMS tracking system,it means that the probability of a given pixel being hit by two different charged particles from the same bunch crossing is exceedingly small, this large area and low occupancy yield measurements with excellent linear response with the pile-up (number of interactions per bunch crossing)$\mu$ \citep{lumi_precise_2015_2016}, therefore an accurate measure of instantaneous luminosity with a high statistical precision.\\
+
+However, the statistical precision for a single 23-second period or "luminosity section" is not as high as for online luminometers due to the limited CMS trigger bandwidth available for collecting data.
+Nonetheless, over longer time periods, this method provides a stable and highly precise luminosity measurement.
+On average, the detector occupancy is less than 0.1\% \cite{pas_18}.\\
+
+Figure  \ref{pileup} shows a simulation made in 2016 with a representative PCC distribution at $\mu$ = 45 and the average PCC as a function of $\mu$.
+The latter distribution is fitted with a first-order polynomial, assuming no correlations among different values of $\mu$.
+Good agreement is seen based on the estimated goodness-of-fit $\chi^{2}$ per degree of freedom (dof) value of about 0.5 , indicating linearity under simulated conditions \cite{lumi_precise_2015_2016}.
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[scale=.3]{Chapter3/pileup_lineality.png} 
+    \caption[Linearity with pile-up]{ The left plot shows the number of pixel clusters and their statistical uncertainty from simulation of pileup following a Poisson distribution with a mean of 45.
+The right plot shows the mean number of pixel clusters from simulation as a function of mean pileup.
+The red curve is a first-order polynomial fit with slope and $\chi^{2}/ndof$ values shown in the legend.
+The lower panel of the right plot shows the difference between the simulation and the linear fit in black points.
+The green band is the final linearity uncertainty for the 2016 data set \cite{lumi_precise_2015_2016} }
+    \label{pileup}
+  \end{figure}
+\end{center}
+
+To obtain the mean number of pixel clusters per event, several zero-bias events are averaged. This value is given by :
+
+\begin{equation}
+\left < N_{\text{cluster}} \right > = \left < N_{\text{pixel}/\text{interaction}} \right >  \left < N_{\text{interactions}} \right > \equiv \left < N_{\text{pixel}/\text{interaction}} \right > \mu
+\end{equation}
+
+where $\mu$ is the average number of interactions per bunch crossing and is refered as pileup \cite{PCC_PAS_12_001}. Under minimum bias conditions, $\mu$ can be expressed as:
+
+\begin{equation}
+\mu = \frac{\sigma_{\text{minBias}}}{f} \cdot \mathcal{L}_{inst}
+\end{equation}
+
+where $f$ is the LHC revolution frequency and $\mathcal{L}_{inst}$ is the single bunch instantaneous luminosity (SBIL).
+The minimum bias cross section here is related to the PCC visible cross section by the mean number of clusters per interaction:
+
+\begin{equation}
+\sigma_{vis}^{PCC}= \left < N_{\text{pixel}/\text{interaction}} \right >\cdot \sigma_{\text{minBias}}
+\end{equation}
+
+Combining everything, the PCC luminosity measurement is obtained as:
+
+\begin{equation}
+\mathcal{L}_{inst}=\frac{\left < N_{\text{cluster}} \right >}{\sigma_{vis}^{PCC}} \cdot f
+\end{equation}
+
+In the PCC measurement, the innermost layer of the pixel detector is excluded from the analysis due to significant dynamic inefficiency effects \cite{pas_18}.
+At higher $\mathcal{L}_{inst}$, the hit efficiency in this layer decreases because the readout chip cannot process all of the hits.
+Only modules that consistently perform well for luminosity purposes throughout the year are utilized in the measurement.
+
+For the VdM measurement, a special trigger mode is employed, which enables a higher data rate for PCC to acquire the required statistical precision.
+However, this mode is only active for five bunch crossings, and data are taken exclusively during this period.
+
+\section{2022 CMS Data Summary}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Module selection}
+
+To ensure accurate luminosity measurement, a veto list is created to remove any modules exhibiting long-term performance variations, indicating a non-physical shift in their cluster counts.
+With a total of 1856 modules in the pixel system, all of them can be considered in the luminosity measurement; however, non-zero occupancy and non-linear effects can pose challenges for accurate measurement.
+Thus, to identify "good" and "stable" modules, a subset is selected by eliminating  underperforming or "bad" modules and comparing their relative contributions to the cross section.
+Those with relatively consistent contributions across standard physics runs are kept, while those with significant changes in their relative cross section compared to the averaged relative contribution are rejected.
+The Module selection is made as:
+
+\begin{itemize}
+\item Poor statistics lumisections are removed by applying selection on total PCC.
+\item Barrel layer-1 modules are removed, as these modules are significantly affected by dynamic inefficiency.
+\item A loose selection of 7\% based on RMS/mean of module weight is applied. Modules with significantly large RMS/mean are removed with this selection as shown in \ref{goodmodule}.
+\item The module stability is re-evaluated based on RMS/mean values using an iterative method where appropriate selections are applied to remove underperforming modules until a stable luminosity is attained.
+\end{itemize}
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[scale=.20]{Chapter4/RMSmean.png}
+    \caption[RMS/mean Module  Stability]{ RMS/mean values of module weight for all pixel modules. Each pixel module is represented by a module number index.} 
+    \label{goodmodule}
+  \end{figure}
+\end{center}
+
+To ensure accurate measurements, a pixel module veto list is established for each period, recognizing that different periods may have varying numbers of well-performing modules.
+The pixel detector is subject to changing conditions over time, such as detector noise, aging effects, and radiation damage.
+Stability of the pixel modules is assessed based on changes in the module PCC ratio relative to the total PCC, known as module weight.
+These variations are evaluated over an interval of 23 seconds, corresponding to the granularity of the luminosity database.
+The pixel module veto list is first generated for the period 2022F containing the vdM fill and subsequently for the periods ,C, D, E and G,  following the same procedure.
+
+To further improve the stability of the PCC measurement, a 4\% RMS common module vetolist is created as shown in table \ref{common  veto module}.
+The approach to derive the common module veto list is to start by combining module vetolists of period C and D; then combine C, D and E; and so on.
+The zero-bias PCC data is reprocessed using this common module vetolist.
+
+\begin{table}[ht]
+\centering
+\caption{Number of good and bad modules for the combined vetolist, after each iteration of the 4\% RMS selection with an additional period.}
+\begin{tabular}{ccc}
+\textbf{Period} & \textbf{\# bad modules} & \textbf{\# good modules}  \\ 
+\toprule
+2022C+D         & 886                     & 970                       \\
+2022C+D+E       & 1106                    & 750                       \\
+2022C+D+E+F     & 1307                    & 549                       \\
+2022C+D+E+F+G   & 1411                    & 445                   
+\label{common  veto module}   
+\end{tabular}
+\end{table}
+
+\noindent This final common veto in conjunction with background subtraction  is used for the last reprocesing data analysed with the VdM scan.
 
@@
 
-\subsection*{Backgrounds}
+As discussed in Chapter 1, the instantaneous luminosity for a single colliding bunch is described by Eq.
+(\ref{luminosity_2}).
+In practice, while the measurement of the beam currents $N_{1,2}$ is well determined, the individual proton density functions cannot be directly measured.
+To address this, the VdM method involves a specific machine setup that allows for the determination of the two beam overlap integrals.
+This is achieved by varying the separation between the beams and measuring the resulting rates, which can be used to obtain density profiles that are close to normal distributions.
+
+\begin{equation}
+\int \rho_{x1}(x) \rho_{x2}(x) dx = \frac{R_{x}(0)}{\int R_{x}(\Delta) d\Delta}
+\end{equation}
+
+where $R_{x}(\Delta)$ is the rate measured when the two beams are separated in $x$ by a distance $\Delta$; a asimilar equation can be written in $y$.
+Then the beam overlap width $\Sigma_{x}$ (and similarly $\Sigma_{y}$) is defined as \cite{pas_18}:
+
+\begin{equation}
+\Sigma_{x}= \frac{1}{\sqrt{2\pi}} \frac{\int R_{x}(\Delta)d\Delta}{R_{x}(0)}
+\label{CapSigma}
+\end{equation}
+
+This process leads to the final expression for luminosity for a single colliding bunch:
+
+\begin{equation}
+\mathcal{L}_{inst}=\frac{N_{1} N_{2}f}{2 \pi \Sigma_{x}\Sigma_{y}}
+\end{equation}
+
+where $N_{1,2}$ are the particles per bunch (bunch current) and  $f= 11246$ Hz is the bunch orbit frequency around the LHC ring.\\
+
+Therefore, the formula used to measure the visible cross sections $\sigma_{vis}$ takes the following form:
+
+\begin{equation}
+  \sigma_{vis}=\frac{2\pi \Sigma_{x} \Sigma_{y} R(0, 0)}{N_{1}N_{2} f}
+  \label{sigmavis_eq}
+\end{equation}
+
+Experimentally, the quantities $\Sigma_{x}$ and $\Sigma_{y}$, as defined in Eq.
+(\ref{CapSigma}), are determined by conducting two separate scans in the $x$ and $y$ directions, respectively.
+These scans are performed by varying the separation between the beams in each direction and measuring the rate $R(0,0)$, which is normalized by the product of the beam currents, at a fixed number of separation steps.
+The separation steps are determined through curve fitting of the scan data based on the luminometer rate measurements obtained during the vdM scans.
+While the beam widths are the same for all luminometers, the peaks of the corresponding scan curves are luminometer-specific.
+Figure \ref{vdm_sketch} depicts a schematic of the beam positions during vdM scans in the $x$ and $y$ planes, along with the detector rate as a function of beam separation  \cite{pas_18}.
+
+Only modules that are found to operate consistently well for luminosity purposes during the year of the VdM scan are used in the measurement, a brief description of the procedure to the selection of these a presented in the next section.
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[scale=.37]{Chapter3/vdm_sketch.png}
+    \caption[Sketch of a vdM scan in x and y planes and example of fitting resulting rates]{ The sketch of a vdM scan in $x$ and $y$ planes.
+The indent sketch is an example of the fitting of the resulting rates \cite{vdM_sketch}.}
+    \label{vdm_sketch}
+  \end{figure}
+\end{center}

### 2023-03-29 tesis_Luis/Chapter5/chapter5.tex
updated

\chapter{Summary and Outlook}

This work aims to focus on the calibration of luminosity for the PCC  luminometer, based on the van der Meer scans conducted by the CMS Collaboration on November 10 and 11 of 2022 for the fill 8381 of proton-proton collisions at $\sqrt{s}=$ 13.6 TeV, where five scan pairs (3 standard vdM and three BI scans) were analyzed with this method.
A explanation of luminosity importance,the LHC and the CMS experiment, the PCC method as luminometer, and the calibration procedure for estimating $\sigma_{vis}$ were all covered in this work.

This study provides a comprehensive explanation of how data was recorded and procesing, starting from the raw files with cluster reconstruction and processing them with a  selection of  "good" Pixel detector modules. This approach aimed to remove instabilities in luminosity measurement for the corresponding calibration periods,  data also was processed with the  estimation of the background correction to the rates (PCC) from the two super separation periods in this program. The study concludes that the fit obtained for this  estimation is not the best due the background value varied over time for the two SS periods, leading to the decision that the fit model should be changed to one with a constant. All the parameters for this analysis were reported.

The assigned value of the calibration is $\sigma_{vis} = 4163 \pm 3 \text{(stat.)} \pm 12 \text{(syst.)} \text{ mb}$. The analysis and results reported in this work will be useful for a precise luminosity measurement analysis for Run 3 in the CMS experiment of LHC, together with the rest of the luminometers  for a final publication that presents all these final results.

### 2023-03-29 tesis_Luis/compiler_thesis.py

@@ -1,39 +1,0 @@
-######Instructions######
-#Run as :
-#>python3 compiler_thesis.py
-#######################
-import os
-# colorama_demo.py
-from colorama import init, Fore, Back, Style
-
-# Initializes Colorama
-init(autoreset=True)
-
-print(Style.BRIGHT + Back.WHITE + Fore.RED + "Cleaning Some Files...")
-dir_name = os.getcwd()
-test = os.listdir(dir_name)
-
-for item in test:
-    if item.endswith("~"):
-        os.remove(os.path.join(dir_name, item))
-    if item.endswith(".toc"):
-        os.remove(os.path.join(dir_name, item))
-    if item.endswith(".bbl"):
-        os.remove(os.path.join(dir_name, item))
-    if item.endswith(".log"):
-        os.remove(os.path.join(dir_name, item))
-    if item.endswith(".out"):
-        os.remove(os.path.join(dir_name, item))
-    if item.endswith(".blg"):
-        os.remove(os.path.join(dir_name, item))
-print(Style.BRIGHT + Back.WHITE + Fore.BLUE + "Cleaning... DONE")
-
-print(Style.BRIGHT + Back.BLACK + Fore.RED + "Compiling thesis.tex (1st)")
-os.system("pdflatex thesis.tex")
-print(Style.BRIGHT + Back.BLACK + Fore.RED + "Compiling thesis.aux")
-os.system("bibtex thesis.aux")
-print(Style.BRIGHT + Back.BLACK + Fore.BLUE + "Compiling thesis.tex (2nd)")
-os.system("pdflatex thesis.tex")
-print(Style.BRIGHT + Back.BLACK + Fore.GREEN + "Compiling thesis.tex (3rd)")
-os.system("pdflatex thesis.tex")
-print(Style.BRIGHT + Back.BLACK + Fore.GREEN + "DONE: thesis.pdf'")

### 2023-04-07 tesis_Luis/Chapter1/chapter1.tex
updated

--- 2023-02-16 tesis_Luis/Chapter1/chapter1.tex
@@
 % https://home.cern/news/news/physics/why-precision-luminosity-measurements-matter
+Particle physics is the branch of physics that focuses on studying the fundamental particles and forces that make up matter and radiation in the universe.
+The Standard Model classifies the fundamental particles and their interactions as fermions, which are matter particles, and bosons, which are force-carrying particles.
+High-energy particle accelerators are used to study these interactions by measuring various parameters and properties of the particles produced during collisions.
+This chapter provides a brief overview of elementary particles, particle colliders, and the measurement of their performance.
+It emphasizes the concepts and definitions necessary for understanding this thesis project.
 
-\section{Fundamental Particles}
+\section{Particle Physics and The Standard Model}
 
- shown in table \ref{tab:table1}.  
+The universe is composed of several different particles.
+Atoms are bound states of negatively charged electrons $(e^{-})$, which orbit around a central nucleus consisting of positively charged protons $(p)$ and electrically neutral neutrons $(n)$.
+The electrons are bound to the nucleus by the electrostatic attraction between opposite charges, while the protons and neutrons are held together by the strong nuclear force.
+Completing the fundamental interactions of particle physics are the weak force and gravity.
+The weak force is responsible for nuclear $\beta$ decays and nuclear fusion, while gravity, although extremely weak, is always attractive and therefore responsible for the large-scale structure in the universe.
+While this is a simple physical model, at higher energy scales, more complex structures are observed, leading to the discovery of 17 fundamental particles that make up our entire universe.
+These particles are divided into two groups: fermions with spin $1/2$ and bosons with integer spin \cite{thomson_2013}.\\
+
+Fermions are the particles that constitute matter, consisting of twelve fundamental particles classified into two types: leptons and quarks.
+These particles are further divided into three generations, with each member of a higher generation having a greater mass than the corresponding particle of the previous generation.
+The six leptons include three charged particles: electron ($e$\textsuperscript{-}), muon (${\mu}$\textsuperscript{-}), and tau (${\tau}$\textsuperscript{-}), as well as their corresponding neutrinos: electron-neutrino ($\nu_{e}$), muon-neutrino ($\nu_{\mu}$), and tau-neutrino ($\nu_{\tau}$).
+Quarks, on the other hand, can only be found in particles called hadrons.
+The group of quarks consists of the up quark ($u$), down quark ($d$), charm quark ($c$), strange quark ($s$), top quark ($t$), and bottom quark ($b$) \cite{griff,thomson_2013}.
+The properties of these twelve particles are summarized in Table \ref{tab:table1}.
+
 \begin{table}[h!]
 	\begin{center}
-    \caption{Force experienced by the fermions}
+%\centering
+	\caption{The twelve fundamental fermions divided into quarks and leptons.\
+The masses of the quarks are the current masses \cite{thomson_2013}.}
 		\label{tab:table1}
+		\begin{tabular}{lllrcllrc}
+                                                                                & \multicolumn{4}{c}{\textbf{Leptons}}                                                                     & \multicolumn{4}{c}{\textbf{Quarks}}                                                \\
+%\cline{2-9}
+ \midrule[1.1pt]
+                            \multicolumn{1}{c}{Generation }& \multicolumn{2}{c}{Particle } & \multicolumn{1}{c}{\textit{Q}} & mass/GeV                          & \multicolumn{2}{c}{Particle} & \multicolumn{1}{c}{\textit{Q}} & mass/GeV  \\
+\hline
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}First\end{tabular}}  & electron & ($e$\textsuperscript{-})                 & -1                             & 0.0005                            & down    & ($d$)                & -1/3                           & 0.003     \\
+                                                                                & $e$-neutrino & ($\nu_{e}$)                 & 0                              & \textless{}10\textsuperscript{-9} & up      & ($u$)                & +2/3                           & 0.005     \\
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Second\end{tabular}} & muon     & (${\mu}$\textsuperscript{-})                 & -1                             & 0.106                             & strange & ($s$)                & -1/3                           & 0.1       \\
+                                                                                & $\mu$-neutrino & ($\nu_{\mu}$)                 & 0                              & \textless{}10\textsuperscript{-9} & charm   & ($c$)                & +2/3                           & 1.3       \\
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Third\end{tabular}} & tau      & ({$\tau}$\textsuperscript{-})                 & -1                             & 1.78                              & bottom  & ($b$)                & -1/3                           & 4.5       \\
+                                                                                & $\tau$-neutrino & ($\nu_{\tau}$)                 & 0                              & \textless{}10\textsuperscript{-9} & top     &($t$)                & +2/3                           & 174
+\end{tabular}
+	\end{center}
+		\end{table}
+
+The bosons are responsible for describing the interactions between fermions through the exchange of particles.
+These exchange particles are known as gauge bosons and include the photon $\gamma$ for electromagnetic force, $W^{\pm}$ and $Z^{0}$ for the weak force and gluons $g$ for the strong force \cite{thomson_2013}.
+Additionally, there is a scalar boson called the "Higgs boson", which is associated with the mechanism that gives mass to all fundamental particles.
+The forces experienced by fermions can be seen in table  \ref{tab:table2}.
+
+\begin{table}[h!]
+  \begin{center}
+    \caption{Force experienced by the fermions \cite{thomson_2013}.}
+    \label{tab:table2}
     \begin{tabular}{l c c c c}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+All of these particles are described by the Standard Model (SM), which is the best theoretical model to date for providing a successful description of experimental data.
+However, most of this data comes from particle colliders since these particles can only be produced and studied through collisions at high energy.
 
-\section{Particle Colliders}
+\section{Particle Colliders and production cross section}
 
-\section{Cross section}
+Most of the recent breakthroughs in particle physics have resulted from experiments conducted at high-energy particle accelerators.
+These accelerators are the most powerful microscopes for observing the tiniest inner structures of cells, genes, molecules, atoms, and their constituent particles such as protons, neutrons, electrons, neutrinos, and quarks.
+Moreover, they may also help discover yet unknown fundamental building blocks of the universe, such as dark matter and dark energy.\\
 
+Particle colliders produce and accelerate beams of charged particles at high speeds (close to the speed of light) using electromagnetic fields; the high-energy collisions of these beams produce individual interactions referred to as events.
+These collisions produce massive particles, such as the Higgs boson or the top quark.
+These particles  cannot be observed directly, almost immediately they transform (or decay) into lighter particles, which in turn also decay.
+They are measured and identified by a wide range of experiments (particle detectors), whose technologies, techniques and designs are based on the properties of the particles and on the nature of their interactions with matter \cite{thomson_2013}.\\
+
+In general, a particle detector is composed of a cylindrical or polygonal barrel section, with its axis aligned parallel to the incoming colliding beams.
+The cylindrical structure is sealed by two flat end caps, providing almost complete solid angle coverage down to the beam pipe, esta compuesto por varias capas dddicadas a detecta diferentes particulas.\\
+
+In general, particle detector is typically constructed as a cylindrical or polygonal barrel section, oriented parallel to the incoming colliding beams.
+Two flat end caps seal the cylindrical structure, ensuring nearly complete solid angle coverage all the way down to the beam pipe.
+This detector comprises multiple layers, each designed to detect the different particles generated during collisions \cite{thomson_2013}.\\
+
+The performance of particle colliders is typically evaluated based on two parameters: the beam energy and the luminosity.
+The available energy for producing new effects is one of the most important parameters, as it determines the types of particles that can be studied or discovered.
+In these experiments, particles are accelerated and two beams are brought together at an intersection point where they collide.\\
+
+Colliding beam machines have the advantage that they can achieve much higher centre-of-mass energies, at various points the beams intersect and scattering takes place.
+If the incident particles have the same energy (equal mass) and therefore equal but opposite momentum, then the experiment is taking place in the centre-of-mass (CM) frame and the full energy delivered by the accelerator, can be used to produce high mass particles  \cite{undergraduate_accelerators_chapter}.
+In particle physics the Lorentz invariant quantity $s$ denote the square of the total incoming energy and is defined as: 
+\begin{equation}
+s = \left ( \sum_{i = 1,2}^{}E_{i} \right )^{2}-\left ( \sum_{i = 1,2}^{}p_{i} \right )^{2}c^{2}
+\end{equation}
+Where $E$ and \textbf{$p$}  are the energy and the momenta of each incoming particle respectively, in the CM frame, where the momenta are equal and opposite, the second term vanishes and  $s = 4E^2$.
+
+The second important parameter of the collider's performance is the luminosity, defined as the  quantity that measures the ability of a particle accelerator to produce the required number of interactions and is the proportionality factor  between the number of events of particular physics process per second $dR/dt$ and the quantum mechanical probability for the interaction called cross section \sigma_{p} \cite{ref_lib_vol3}.
+
+%\section{Cross section}
+%%resumir en un parrafo de 1.3 a 1.7
+The technical meaning of "cross section" in particle physics is quite different from its common usage, while "cross section" typically refers to a slice of an object, in particle physics, it often refers to the probability that two particles will collide and react in a specific manner.
+When two beams cross in a particle accelerator, a variety of different processes can occur and  the cross section of a given process depends on the type and energy of the colliding particles.
+At the Large Hadron Collider (LHC), certain particles such as  $W^{\pm}$ and $Z^{0}$ bosons have large cross sections , making their observation more frequent, while the production of a Higgs boson has a much lower cross section, making it more difficult to produce \cite{thomson_2013}.\\
+
+To show better this concept, we present the most simplest scenario, where a beam of particles of type $a$, with a flux denoted by $\phi_{a}$, passes through a region of space containing $n_{b}$ particles per unit volume of type $b$.
+The interaction rate per target particle $r_{b}$ is proportional to the incident particle flux and can be expressed as follows \cite{thomson_2013}:
+
+\begin{equation*}
+  r_{b}=\sigma \phi_{a}
+\end{equation*}
+
+The essence of fundamental physics is encapsulated in $\sigma$, which has units of area and is referred to as the interaction cross section.
+It can be useful to conceptualize $\sigma$ as the effective cross-sectional area associated with each target particle, in general, the cross section merely represents the underlying quantum mechanical likelihood that an interaction will occur \cite{thomson_2013}.
+The definition of the cross section is illustrated in Figure \ref{cross_section}(a), where a single incident particle of type $a$ is travelling with a velocity $v_{a}$ in a region defined by the area $A$, wish contains $n_{b}$ particles of type $b$ per unit volume moving with a velocity $v_{b}$ in the opposite direction to $v_{a}$.
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+\includegraphics[scale=.35]{Chapter1/cross_section.png} 
+ \caption[Cross section illustration]{Left hand (a): single incident particle of type $a$ traversing a region containing particles of type $b$.
+Right-hand plot (b): projected view of the region traversed by the incident particle in time $\delta t$ \cite{thomson_2013}.}
+    \label{cross_section}
+  \end{figure}
+\end{center}
+
+In  a time $\delta t$, the particle $a$  crosses a region containing $\delta N= nb(v_{a}+v_{b}) A \delta t$ of type $b$.
+The interaction probability can be obtained from the $effective$ total cross sectional area of the $\delta N$ particles divided by the area $A$, which can be thougth of as the probability that the incident particle passes through one of the regions of area $\sigma$ drawn around each of the $\delta N$ target particles, as shown in Fig.
+\ref{cross_section}(b).
+For a beam of particles of type $a$ with number density $n_{a}$ confined to a volume $V$, the total interaction rate is $\text{rate}=(n_{a}v)(n_{b}V) \sigma = \phi N_{b} \sigma$,  more formally, the cross section for a process is defined as \cite{thomson_2013}:
+
+\begin{equation}
+\sigma=\frac{\text{number of interaction per unit time per target particle}}{\text{incident flux}}
+\end{equation}
+
+Where the flux $\phi$ accounts for the relative motion of particles.
+The value of the cross section is crucial as it represents the constant of proportionality between the rate measured by the detector and the luminosity.
+
+%begin{equation}
+%\sigma=\frac{\text{number of interaction per unit time per target particle}}{\text{incident flux}}
+%\end{equation}
+
+%\delta P= \frac{\delta N \sigma}{A}=\frac{n_{b}(v_{a}+v_{b})A\sigma \dela t}{A}= n_{b}v\sigma \delta t$
+%where $v=v_{a}+v_{b}$. The interaction rate for each particle of type $a$ is $r_{a}= \frac{dP}{dt}= n_{b} v\sigma$.
+%For a beam of particles of type $a$ with number density $n_{a}$ confined to a volume $V$, the total interaction rate is:
+%$\text{rate}=r_{a}n_{a}V=(n_{b}v\sigma) n_{a}V= (n_{a}v)(n_{b}V)\sigma$
+
+%$\text{rate}=(n_{a}v)(n_{b}V) \sigma = \phi N_{b} \sigma$
+
+%Thus the total rate is equal to
+%$\text{rate}= \text{flux} \times \text{number of target particles} \times \text{cross section}$
+
+%More formally, the cross section for a process is defined as:
 \section{Luminosity }
 
-\section{Importance of Luminosity precision}
+In particle physics experiments besides the energy, the number of useful interactions (events) is the most important parameter.
+The quantity that measures the ability of a particle accelerator to produce these interactions is called instantaneous luminosity $\mathcal{L}_{inst}$ and is the proportionality factor between the number of events per second ($dR/dt$) and the cross section $\sigma_{p}$ \cite{concept_of_luminosity}:
+
+\begin{equation}
+\frac{dR}{dt}=\mathcal{L}_{inst} \cdot \sigma_{p}
+\end{equation}
+
+Where the unit of luminosity is $cm^{-2}s^{-1}$.
+
+To derive a general expression for luminosity in the case of two colliding beams, we consider both beams to serve as the target and the incoming beam simultaneously.
+We will assume that the beams are "bunched", meaning that the particles are grouped into packets or bunches.
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+\includegraphics[scale=.25]{Chapter1/luminosity.png} 
+ \caption[Colliding beam interaction]{Schematic view of a colliding beam interaction\cite{concept_of_luminosity}}
+    \label{luminosity}
+  \end{figure}
+\end{center}
+
+A schematic picture is shown in Fig.
+\ref{luminosity}.
+Since the two beams are not stationary but are moving through each other, the overlap integral depends on the longitudinal position of the bunches, and therefore on time.
+As the beams move towards and through each other, the two beams have different distribution functions and a different number of particles in the beams \cite{concept_of_luminosity}.
+The overlap integral, which is proportional to the luminosity $\mathcal{L}_{inst}$, can then be written as:
+
+\begin{equation}
+  \mathcal{L}_{inst}\propto K\cdot \int\int \int_{-\infty}^{\infty} \rho_{1}(x,y,s,-s_{0}) \rho_{2}(x,y,s,s_{0})dxdydsds_{0}
+    \label{lumi_1}
+\end{equation}
+
+Where  $\rho_{1}(x,y,s,-s_{0})$ and $\rho_{2}(x,y,s,s_{0})$ are the time dependent beam density distribution functions.
+We assume, that the two bunches meet at $s_{0} = 0$.
+Because the beams are moving against each other, we have to multiply this expression with a relativistic kinematic factor:
+
+\begin{equation}
+ K = \sqrt{(\vec{v_{1}}-\vec{v_{2}})^{2}-(\vec{v_{1}}\times \vec{v_{2}})^{2}/c^{2}}
+    \label{kinematic}
+\end{equation}
+
+Specifically, in the case of exactly head-on collisions of bunches travelling almost at the speed of light, this factor becomes 2.\\
+Assuming uncorrelated densities in all planes and head-on collisions where the velocities of the two bunches are opposite $(\vec{v_{1}}=-\vec{v_{2}})$, the overlap integral can be factorized as:
+
+\begin{equation}
+  \mathcal{L}_{inst}= 2N_{b} N_{1}N_{2}f \int\int\int\int_{-\infty}^{\infty}  \rho_{1x}(x)\rho_{1y}(y)\rho_{1s}(s-s_{0})\rho_{2x}(x)\rho_{2y}(y)\rho_{2s}(s+s_{0}) dxdydsds_{0}
+    \label{luminosity_2}
+\end{equation}
+
+where $N_{1}$ and $N_{2}$ are the particles per bunch, $f$ the revolution frequency and $N_{b}$ is the number of bunches in one beam.\\
+
+%\begin{eqnarray}
+%\rho_{iz}(z)= \frac{1}{\sqrt{2\pi} \sigma_{z}} exp \biggl(-\frac{z^{2}}{2\sigma_{z}^{2}} \biggr)&z=x,y&i=1,2 
+%\end{eqnarray}
+
+%\begin{eqnarray}
+%\rho_{s}(s\pm s_{0})= \frac{1}{\sqrt{2\pi} \sigma_{s}} exp \biggl(-\frac{(s\pm s_{0})^{2}}{2\sigma_{s}^{2}} \biggr)
+%\end{eqnarray}
+
+Assuming Gaussian profiles in all dimensions and approximately equal bunch lengths $(\sigma_{1s}\approx \sigma_{2s})$, the equation \ref{luminosity_2} can be solved.
+For a general case where $\sigma_{1x}\neq \sigma_{2x} \text{ and } \sigma_{1y}\neq \sigma_{2y}$
+
+\begin{equation}
+  \mathcal{L}_{inst}= \frac{N_{1} N_{2} N_{b}f }{2\pi \sqrt{\sigma_{1x}^{2}+\sigma_{2x}^{2}}\sqrt{\sigma_{2y}^{2}+\sigma_{2y}^{2}}}
+  \label{lumi_general}
+\end{equation}
+
+For a specific case, asuming equal beams, $\sigma_{1x}= \sigma_{2x} ,\sigma_{1y}= \sigma_{2y}$:
+
+\begin{equation}
+  \mathcal{L}_{inst}= \frac{N_{1} N_{2} N_{b}f }{4\pi \sigma_{x} \sigma_{y}}
+  \label{lumi_theor}
+\end{equation}
+
+This is the well known expression for the luminosity of two Gaussian beams colliding head-on.
+It shows how the luminosity depends on the number of particles per bunch and the beam sizes \cite{concept_of_luminosity}.
+
+In practice,the integral in  \ref{luminosity_2} cannot be solved analytically because   the properties of the colliding beams are not know precisely, so a experimental technique is implemented with a dedicated machine setup to estimate the integrals, yielding a similar expression as \ref{lumi_theor}.
+
+In order to evaluate the total number of events we use integrated luminosity,it is a measurement of the collected data size, and it is an important value to characterize the performance of an accelerator, defined as \cite{concept_of_luminosity}:
+
+\begin{equation}
+  \mathcal{L}_{int}=\int_{0}^{T} \mathcal {L}_{\text{inst}}(t') dt'
+\end{equation}
+
+Where the value of $\mathcal{L}{\text{inst}}$ is evaluated over time $T$ (excluding possible dead time) because its intensity decreases as the number of protons reduces during the collisions of the fill.
+So $\mathcal{L}{int}$ is directly related to the number of observed events as:
+
+\begin{equation}
+  \mathcal{L}_{int} \ndot \sigma_{p}= \text{number of events of interest}
+\end{equation}
+
+The integrated luminosity has units of $cm^{-2}$ and is often expressed in inverse barn ($1 barn= 10^{-24}cm^{2}$). \\
+
+Luminosity is one of the fundamental parameters used to measure the performance of an accelerator, understanding luminosity with the best possible precision is crucial for physics analyses such as searches for new particles, rare processes, or measurements of known particle properties \cite{lumi_motiv}.
+The experimental techniques to determine signal rates are mature enough, where the understanding of acceptances, detector biases, reconstruction efficiencies, or background subtraction is at the sub-percent level, so that the final precision of the physics measurement is dominated by the luminosity uncertainty \cite{lumi_paper_def_and_concept}.
+Ultimately, the greater the precision of the luminosity measurement, the more physicists can understand their observations and delve into hidden corners beyond our current knowledge.
+%Knowing the integrated luminosity enables physicists to compare their observations with theoretical predictions and simulations.
+For instance, they can search for dark matter particles that escape collisions undetected by examining the energies and momenta of all particles generated in a collision.
+If there is an imbalance, it could be due to an undetected, potentially dark matter, particle that carries energy away.
+This is a powerful method of searching for new phenomena, but many effects, such as neutrinos produced in collisions, need to be considered.
+Neutrinos also escape undetected and leave an energy imbalance, making them indistinguishable from new phenomena.
+Therefore, to determine if something unexpected has been produced, physicists must look at the numbers \cite{luminosity_importance} .
+
+%For example, if 11,000 events show an energy imbalance, and the simulations predict 10,000 events containing neutrinos, this could be significant.
+But if physicists only know the luminosity with a precision of 10\%, they could have easily had 11,000 neutrino events, and there were just 10\% more collisions than assumed.
+Clearly, a precise determination of luminosity is critical   \cite{luminosity_importance}.
+
+%There are also types of analyses that depend much less on absolute knowledge of the number of collisions.
+For example, in measurements of ratios of different particle decays, such as the recent LHCb measurement, uncertainties in luminosity get canceled out in the ratio calculations.
+Other searches for new particles look for peaks in mass distribution and rely more on the shape of the observed distribution and less on the absolute number of events.
+But these also need to know the luminosity for any interpretation of the results \cite{luminosity_importance}.
 
@@
 
-\section{LHC Luminosity}
+The Large Hadron Collider (LHC) is the world’s largest and most powerful particle accelerator.
+It first started up on 10 September 2008, and remains the latest addition to CERN’s accelerator complex.
+The LHC consists of a 27-kilometre ring of superconducting magnets with a number of accelerating structures to boost the energy of the particles along the way.
+Inside the accelerator, two high-energy particle beams travel at close to the speed of light before they are made to collide.
+The beams travel in opposite directions in separate beam pipe where the two tubes kept at ultrahigh vacuum.
+They are guided around the accelerator ring by a strong magnetic field maintained by superconducting electromagnets, these are built from coils of special electric cable that operates in a superconducting state, efficiently conducting electricity without resistance or loss of energy.
+This requires chilling the magnets to 271.3°C  a temperature colder than outer space \cite{LHC}.\\
 
+Magnets of different varieties and sizes are used to direct the beams around the accelerator.
+These include 1232 dipole magnets, 15 metres in length, which bend the beams, and 392 quadrupole magnets, each 5–7 metres long, which focus the beams.
+Just prior to collision, another type of magnet is used to "squeeze" the particles closer together to increase the chances of collisions .
+\\
+
+The production of proton beams for the LHC involves a complex series of pre-acceleration stages.
+To begin with, hydrogen is ionized to produce protons, which are then accelerated in bunches up to 50 MeV within the Linear Accelerator 2 (LINAC2).
+Subsequently, these proton bunches are routed through three circular accelerators - the Booster, the Proton Synchrotron (PS), and the Super Proton Synchrotron (SPS)  in order to gradually increase their energy levels to 1.4 GeV, 26 GeV, and 450 GeV, respectively.
+Following these pre-acceleration stages, the proton bunches are injected into the LHC ring where they are accelerated to reach energies of up to 7 TeV per bunch while circulating in opposite directions.
+This entire sequence of steps defines a single LHC fill, which typically involves $10^{14}$ protons that are grouped into bunches to form the proton beam.
+Figure \ref{lhc_com} depicts the complete CERN accelerator complex.
+
+\begin{center}
+  \begin{figure}[h]
+    \centering
+    \includegraphics[scale=.45]{Chapter1/lhc_complex_fig.png}
+    \caption[LHC Complex]{Diagram of the LCH complex \cite{lhc_complex}.}
+    \label{lhc_com}
+  \end{figure}
+\end{center}
+
+The responsibility for overseeing all controls, services, and technical infrastructure of the LHC lies with the CERN Control Centre.
+This is the central location where proton beams are directed to collide at four distinct positions along the accelerator ring, corresponding to the positions of the four particle detectors: CMS and ATLAS, which are general-purpose detectors specifically designed to investigate a broad range of Standard Model (SM) and Beyond SM (BSM) physics, while ALICE and LHCb serve as specialized detectors, specifically focused on studying particular phenomena.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Expected  Luminosity precision for LHC Run 3}
+
+Since its inception in 2010 the LHC has undergone three runs and two lengthy shutdowns for maintenance and upgrades. 
+Run1 began in 2010 with proton-proton collisions at a center-of-mass energy of $\sqrt{s}=\text{7 TeV}$ and concluded in August 2012 at  $\sqrt{s}=\text{8 TeV}$\cite{LHC_status_2013}.
+Run 2, which took place at $\sqrt{s}=\text{13 TeV}$, was divided into two stages; the first  occurred from 2015 to 2016, and the second part  was carried out   from 2017 to 2018 \cite{pas_17,pas_18}, efforts are currently underway to further improve the precision of this run.
+Finally  Run3, which began in 2022 at $\sqrt{s}=\text{13.6 TeV}$ and is currently ongoing.
+This thesis project aims to contribute to the improvement of the precision of the luminosity for Run 3, where it is expected to obtain an approximate luminosity of $390 fb^{-1}$.
+
+The integrated luminosity for each of these runs and years, and their corresponding uncertainty values are presented in table \ref{lumi_values} (luminosity values includes the time from the start of stable beams until the beam is dumped by the LHC), also a visualization of these values measured with CMS is shown in Figure \ref{lumi_per_year_int}, which depicts the delivered luminosity versus time for each year.
+
+\begin{table}[h!]
+    \begin{center}
+    \caption{Integrated luminosity values recorder by each Run}
+	\label{lumi_values}
+\begin{tabular}{cccc}
+\textbf{Run} & \textbf{Energy $\sqrt{s}$} & \begin{tabular}[c]{@{}c@{}}\textbf{Integrated}\\\textbf{Luminosity}\end{tabular} & \textbf{Precision}    \\ 
+\toprule
+1(2010-2012) & 8 TeV           & $30 fb^{-1}$                                                                               & 2.5\%                 \\
+2(2015-2016) & 13 TeV          & $45.9 fb^{-1}$                                                                             & 1.3\%                 \\
+2(2017-2018) & 13 TeV          & $118 fb^{-1}$                                                                              & 2.5\%                 \\
+3(2022-2024) & 13.6 TeV        & \begin{tabular}[c]{@{}c@{}}$45 fb^{-1}$(current)\\$390 fb^{-1}$(expected)\end{tabular}                  & \begin{tabular}[c]{@{}c@{}}currently\\estimating  \end{tabular}\\
+\end{tabular}
+    \end{center}
+\end{table}
+
+\begin{table}[h!]
+\begin{center}
+    \caption{Integrated luminosity values recorder by each Run}
+	\label{lumi_values2}
+\begin{tabular}{ccccc}
+\multicolumn{1}{l}{\textbf{Run}} & \textbf{Year} & \textbf{Energy $\sqrt{s}$} & \begin{tabular}[c]{@{}c@{}}\textbf{Integrated}\\\textbf{Luminosity}\end{tabular} & \textbf{Precision}    \\ 
+\toprule
+\multirow{3}{*}{1}               & 2010          & 7 TeV           & $45 pb^{-1}$                                                                                 & 2.5\%                 \\
+                                 & 2011          & 7 TeV           & $6.1 fb^{-1}$                                                                                & 2.4\%                 \\
+                                 & 2012          & 8 TeV           & $23.3 fb^{-1}$                                                                               & 2.5\%                 \\ 
+\hline
+\multirow{2}{*}{2}               & 2015          & 13 TeV          & $4.3 fb^{-1}$                                                                              & 1.6\%                 \\
+                                 & 2016          & 13 TeV          & $2.6 fb^{-1}$                                                                              & 1.2\%                 \\ 
+\hline
+\multirow{2}{*}{2}               & 2017          & 13 TeV          & $49.8 fb^{-1}$                                                                             & 2.3\%                 \\
+                                 & 2018          & 13 TeV          & $67.9 fb^{-1}$                                                                              & 2.5\%                 \\ 
+\hline
+\multirow{2}{*}{3}               & 2022          & 13.6 TeV        & $45 fb^{-1}$                                                                                & currently estimating  \\
+                                 & 2023          & 13.6 TeV        & currently recording                                                              & currently estimating 
+\end{tabular}
+ \end{center}
+\end{table}
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[scale=.28]{Chapter1/int_lumi_per_year.png}
+    \caption[CMS Luminosity per year]{Delivered luminosity versus time for Run-1 (2010-2012)\cite{pas_17} and Run-2 (2015-2018)\cite{pas_18} and Run-3 that is still ongoing .
+Cumulative luminosity versus day delivered to CMS during stable beams for pp collisions at nominal center-of-mass energy.
+\cite{wikicern}.}
     \label{lumi_per_year_int}
@@
 \end{center}
-
-%lumi values:
-% https://inspirehep.net/files/11b4a1d6569e8e066e7431f17a55d69c
-
-% https://arxiv.org/pdf/1504.06519.pdf
-
-%ATLAS 2015-2018: https://arxiv.org/pdf/1911.04632.pdf
+%% tabla con ano , luminosidad y presicion

### 2023-04-07 tesis_Luis/Chapter2/chapter2.tex
updated

@@
 The CMS detector is constructed around a massive solenoid magnet, which is a cylindrical coil of superconducting cable generating a magnetic field of 4 tesla, this field is used to separate the calorimeter energy deposits of charged and neutral particles in jets.
-The field is confined by a steel "yoke" which constitutes the bulk of the detector's weight of 14,000 tonnes \cite{CMS_Exp_2008}.
-The CMS detector has a complete length of 21.6 meters and a diameter of 14.6 meters that  comprises various detection layers that include separate parts of the detector.
+The field is confined by a steel "yoke" which constitutes the bulk of the detector's weight of 14,000 tonnes, the complete detector has a length of 21.6 meters and a diameter of 14.6 meters.
+\cite{CMS_Exp_2008}.
+\\
 
-These layers are the fine-grained silicon tracker, which provides efficient and precise reconstruction of charged-particle trajectory.
+The CMS detector comprises various detection layers that include separate parts of the detector, these layers are the fine-grained silicon tracker, which provides efficient and precise reconstruction of charged-particle trajectory.
 The highly-segmented electromagnetic calorimeter (ECAL) wish principal purpose is the detection of  electromagnetic energy and the identification of electrons and photons.
 The hadronic calorimeter (HCAL) wish principal purpose is the detection of hadrons in jets  \cite{CMS_Exp_2008}.
-Additionally, there is an excellent muon tracking system, .
-A schematic representation of the CMS detector is shown in \ref{detector_CMS}.\.%% is a summary
-%%The energies of the particles are crucial to understanding what occurred at the collision point.
-This information is collected from two calorimeters in the CMS.
-The inner layer is the Electromagnetic Calorimeter
+Additionally, there is an excellent muon tracking system.
+A schematic representation of the CMS detector is shown in \ref{detector_CMS}.
 
@@
 A powerful magnet is required to bend charged particles as they travel outward from the collision point.
-Bending the trajectory of the particles serves two purposes: first, it helps identify the charge of the particle, as positively and negatively charged particles bend in opposite directions in the same magnetic field; and second, it enables measurement of the particle's momentum.
+Bending the trajectory of the particles serves two purposes: first, it helps identify the charge of the particle, as positively and negatively charged particles bend in opposite directions in the same magnetic field; and second, it enables measurement of the particle's momentum.\\
 
-The CMS must identify the paths of these deflected charged particles with high precision.
-This is achieved using a silicon tracker composed of approximately 75 million individual electronic sensors arranged in concentric layers \cite{CMS_Exp_2008}.
-When a charged particle passes through a Tracker layer, it interacts electromagnetically with the silicon and produces a hit.
-These individual hits can be combined to identify the track of the traversing particle.
+To achieve high precision identification of the paths of deflected charged particles, the CMS employs a silicon tracker as its most inner detector to the beam pipe.
+This tracker system utilizes silicon strips and pixels that are divided into several layers in order to register the tracks of these particles.
+As a charged particle passes through a Tracker layer, it interacts electromagnetically with the silicon and produces a hit.
+By combining these individual hits, the track of the traversing particle can be identified.
+Further details about the tracker system can be found in the next section.
+\cite{CMS_Exp_2008}\\
 
-(descipcion )
-(ECAL), which measures the energy of electrons and photons by completely stopping them.
+ECAL measures the energy of electrons and photons by completely stopping them.
 It is a hermetic, homogeneous calorimeter consisting of 61,200 lead tungstate (PbWO4) crystals mounted in the central barrel part and closed by 7,324 crystals in each of the two endcaps.
 In front of the endcap crystals, a preshower detector is placed.
-Avalanche photodiodes (APDs) are used as photodetectors in the barrel and vacuum phototriodes (VPTs) in the endcaps.
-Hadrons, which are composite particles made up of quarks and gluons, travel through the ECAL and are stopped by the outer layer, called the Hadron Calorimeter (HCAL) \cite{det_summary}.
+Avalanche photodiodes (APDs) are used as photodetectors in the barrel and vacuum phototriodes (VPTs) in the endcaps.\\
+
+The HCAL surrounds the ECAL and together they complete a hermetic calorimetry system designed to measure jets and missing transverse energy.
+When hadrons, which are composite particles consisting of quarks and gluons, travel through the ECAL, they are stopped by the HCAL, to achieve  this, the HCAL is divided into four parts: the hadron barrel (HB), hadron outer (HO), hadron endcap (HE), and hadron forward \cite{det_summary}.\\
 
@@
 Finally, the RAMSES detectors are part of the LHC environmental protection and monitoring systems, but they can also be used to provide a luminosity measurement readout through Timber(operational data and LHC logging service) \cite{pas_18}.
-A brief overview of the CMS luminometers is provided below:
-%%%%%%% no bullets
-\begin{itemize}
+A brief overview of the CMS luminometers is provided below:\\
 
-\item PLT Is a dedicated system for measuring luminosity using silicon pixel sensors.
+PLT Is a dedicated system for measuring luminosity using silicon pixel sensors.
 There are a total of 48 sensors arranged into 16 “telescopes”,eight at either end of CMS outside the pixel endcap, where each telescope contains three sensor planes arranged nearly parallel to the beam pipe.
@@
 
-\item BCM1F comprises a total of 24 sensors mounted on the same carriage as the PLT, consisting of 10 silicon sensors, 10 polycrystalline diamond (pCVD) sensors, and 4 single-crystal diamond (sCVD) sensors.The BCM1F readout features a fast readout with 6.25 ns time resolution; the precise time measurement, in conjunction with the position of BCM1F 1.8 m from the center of CMS, allows hits from collision products to be separated from hits from machine-induced background, because the incoming background is separated in time from the outgoing collision products  \cite{pas_18}.
+BCM1F comprises a total of 24 sensors mounted on the same carriage as the PLT, consisting of 10 silicon sensors, 10 polycrystalline diamond (pCVD) sensors, and 4 single-crystal diamond (sCVD) sensors.The BCM1F readout features a fast readout with 6.25 ns time resolution; the precise time measurement, in conjunction with the position of BCM1F 1.8 m from the center of CMS, allows hits from collision products to be separated from hits from machine-induced background, because the incoming background is separated in time from the outgoing collision products  \cite{pas_18}.\\
 
-\item HF luminosity measurement uses a dedicated readout system installed in the HF calorimeter.
+HF luminosity measurement uses a dedicated readout system installed in the HF calorimeter.
 Only two HF rings are used for luminosity measurement to ensure relatively uniform occupancy.
-Two algorithms are available: the first relies on the fraction of occupied towers (HFOC), and the second is based on the sum of the transverse energy ET (HFET)  \cite{pas_18}.
+Two algorithms are available: the first relies on the fraction of occupied towers (HFOC), and the second is based on the sum of the transverse energy ET (HFET)  \cite{pas_18}.\\
 
-\item Drift tube luminosity (DT), which uses the rate of muon track stubs in the muon barrel track finder and  RAMSES detectors, a CERN radiation and environmental monitoring system, although not designed as a luminometer, function quite well as a luminosity measurement, using the rate observed in the detectors (primarily photons within the energy range of 50 keV to 7 MeV) \cite{pas_18}.
+Drift tube luminosity (DT), which uses the rate of muon track stubs in the muon barrel track finder and  RAMSES detectors, a CERN radiation and environmental monitoring system, although not designed as a luminometer, function quite well as a luminosity measurement, using the rate observed in the detectors (primarily photons within the energy range of 50 keV to 7 MeV) \cite{pas_18}.\\
 
-\item RAMSES.
+RAMSES.
 Althoug is not designed as a luminometer, the rate observed in this detector does function quite well as a luminosity measurement.
@@
 The sensor itself is a cylindrical plastic ionization chamber filled with 3 L of air at atmospheric ressure and it primarily detects photons.
-The overall rate in the RAMSES detectors is small, which means that it is not capable of making bunch-by-bunch measurements and cannot be independently calibrated using a VdM scan; however, this also means it is less affected by issues such as instability caused by radiation damage or nonlinearity \cite{pas_18}.
+The overall rate in the RAMSES detectors is small, which means that it is not capable of making bunch-by-bunch measurements and cannot be independently calibrated using a VdM scan; however, this also means it is less affected by issues such as instability caused by radiation damage or nonlinearity \cite{pas_18}.\\
 
-\item The PCC method uses the rate of pixel clusters in the CMS pixel detector to provide a luminosity measurement this method will be described in more detail in chapter 3.  
-\end{itemize}
+The PCC method uses the rate of pixel clusters in the CMS pixel detector to provide a luminosity measurement this method will be described in more detail in chapter 3.
 
@@
 The tracking system plays a crucial role in precisely measuring the trajectories and momenta of charged particles generated by collisions in the LHC, as well as reconstructing secondary vertices.
-It has a physical size of 5.8 m in length and 2.5 m in diameter and is surrounded by the CMS solenoid, which provides a homogeneous magnetic field of 4T throughout the tracker's volume \cite{CMS_Exp_2008}.
+It has a total physical size of 5.8 m in length and 2.5 m in diameter.
+The CMS tracking detector relies on semiconductor technology, this is divided in two systems, the pixel detector and the Strip tracker \cite{CMS_Exp_2008}.In Figure \ref{strip_layout}, we can observe the pixel detector at the center, surrounded by the Strip tracker.\\
 
-The CMS tracking detector relies on semiconductor technology that uses silicon pixels and strips, this is divided in two systems: a pixel detector with four barrel layers located between 2.9 cm and 16 cm radii and a silicon strip tracker with ten barrel detection layers extending to a radius of 1.1 m.
-Each part includes endcaps, with the pixel detector having three disks and the strip tracker having three plus nine disks on each side of the barrel \cite{CMS_Exp_2008}.
-This extends the tracker's acceptance up to a pseudorapidity of $|\eta| < 2.5$, with an active silicon area of approximately 200 $m^2$.
-The construction of the CMS tracker have 1440 pixel and 15148 strip detector modules.
-The layout of the CMS tracker is presented in the following figure:
+The Strip tracker is comprised of two subsystems: the first being the Tracker Inner Barrel (TIB) and Disks (TID), which is further divided into four barrel layers and three disks at each endcap.
+The second subsystem is the Tracker Outer Barrel (TOB), which consists of six barrel layers and the Tracker EndCaps (TEC) comprising of nine disks.
+The Strip tracker in total comprises of 15148 silicon modules, covering an active area of about 198$\text{m}^{2}$, and consists of 9.3 million strips \cite{CMS_Exp_2008}.
+\\
+
+The innermost part of the tracking system is made up of the silicon pixel tracker, which consists of four concentric barrel layers (BPIX) and three disks on each endcap (FPIX).
+This component comprises a total of 70 million pixels and extends the tracker's acceptance up to a pseudorapidity of $|\eta| < 2.5$.
+Additionally, the active silicon area of this component covers approximately 200 $m^2$.
+More information about this detector is provided in the following section.
 
@@
 
-In Figure \ref{strip_layout}, we can observe the pixel detector at the center, surrounded by the Strip tracker.
-The Strip tracker is comprised of two subsystems: the first being the Tracker Inner Barrel (TIB) and Disks (TID), which is further divided into four barrel layers and three disks at each endcap.
-The second subsystem is the Tracker Outer Barrel (TOB), which consists of six barrel layers and the Tracker EndCaps (TEC) comprising of nine disks.
-The Strip tracker in total comprises of 15148 silicon modules, covering an active area of about 198$\text{m}^{2}$, and consists of 9.3 million strips \cite{CMS_Exp_2008}.
-On the other hand, the silicon pixel tracker, which is situated closest to the interaction point, will be elaborated on in the following section.
-
 \section{Silicon Pixel Detector}
 
-The CMS experiment conducted at the Large Hadron Collider (LHC) at CERN comprises a silicon pixel detector, which forms the innermost component of the tracking system.
-This detector facilitates the provision of 3-dimensional space points in the area nearest to the interaction point, which, in turn, enables precise tracking of charged particles and vertex reconstruction.
+The silicon pixel detector  forms the innermost component of the tracking system.
+This detector facilitates the provides  3-dimensional space points in the area nearest to the interaction point, which, in turn, enables precise tracking of charged particles and vertex reconstruction.
 The pixel detector operates in a radiation-rich environment, marked by high track density \cite{phase1_Pixel_Detector}.\\
@@
 The CMS pixel detector encompasses four concentric barrel layers (L1-L4), each with radii measuring 29, 68, 109, and 160 mm, and three disks (D1-D3) on either end positioned at distances of 291, 396, and 516 mm from the detector's center.
-A schematic of the CMS Phase-1 pixel detector's arrangement is depicted in Figure \ref{phase1_pixel_detector} where the total silicon area of the CMS Phase-1 pixel detector spans 1.9 $\text{m}^{2}$.
+A schematic of the CMS Phase-1 pixel detector's arrangement is depicted in Figure \ref{phase1_pixel_detector} where the total silicon area spans 1.9 $\text{m}^{2}$.
 
@@
 These cylinders host the readout and control circuits, and provide guidance for the power lines and cooling tubes of the detector.
-The BPIX detector is bifurcated into two mechanically self-sufficient halves, both of which are made up of a half detector and two service half-cylinders.
+%  cambiar a otra palabras ..The BPIX detector is bifurcated into two mechanically self-sufficient halves, both of which are made up of a half detector and two service half-cylinders.
 The orientation of the sensor surface of the modules in both halves is parallel to the magnetic field.
+
+%% separadas
 On the other hand, the FPIX detector is segmented into four mechanically independent quadrants, each of which comprises three half-disks housed in a service half-cylinder.
-The sensor orientation in the FPIX detector is arranged such that the long side of the pixel is aligned with the radial direction and has a coverage from 45 to 161 mm.
+The sensor orientation in the FPIX detector is arranged such that the long side of the pixel is aligned with the radial direction.
 The half-disks are additionally subdivided into inner and outer half-rings that support 22 and 34 modules, respectively \cite{phase1_Pixel_Detector}.\\
 
-The pixel detector is built from 1856 segmented silicon sensor modules, where 1184 modules are used in the barrel pixel detector (BPIX) and 672 modules are used for the forward disks (FPIX).
+The pixel detector is built from 1856 segmented silicon sensor modules, where 1184 modules are used in the BPIX and 672 modules are used for the FPIX.
 Each module consists of a sensor with 160$\times$416 pixels connected to 16 readout chips (ROCs).
@@
 The track reconstruction process involves several steps.
-Firstly, zero-suppressed signals above specified thresholds in pixel channels are clustered into hits.
-These hit pixels are then combined to form clusters from neighboring pixels.
+Firstly, zero-suppressed signals above specified thresholds in pixel  channels  are used to form clusters.
 The charge measured within each cluster corresponds to the charge deposited by a single charged particle.
 Next, the cluster positions and their uncertainties are estimated in a local orthogonal coordinate system  in the plane of each sensor \cite{Track_Reco_2014}.
-The pixel sensor used in this process consists of 100 $\times$ 150$\mu \text{m}^{2}$ pixels  this is shown en the figure \ref{module and hit}.
-
+%The pixel sensor used in this process consists of 100 $\times$ 150$\mu \text{m}^{2}$ pixels  this is shown en the figure \ref{module and hit}. 
+%% cambiar imagen para arriba
 \begin{center}
@@
 Where the corresponding coordinate systems is based in the  geometry of the CMS barrel and forward pixel detectors \cite{Pixel_Hit_Reconstruction}.
+%% quitar el detector
+%%  usar clusters clasicos
 

### 2023-04-11 tesis_Luis/Chapter1/chapter1.tex
updated

@@
 
-In general, a particle detector is composed of a cylindrical or polygonal barrel section, with its axis aligned parallel to the incoming colliding beams.
-The cylindrical structure is sealed by two flat end caps, providing almost complete solid angle coverage down to the beam pipe, esta compuesto por varias capas dddicadas a detecta diferentes particulas.\\
-
 In general, particle detector is typically constructed as a cylindrical or polygonal barrel section, oriented parallel to the incoming colliding beams.
@@
 \end{equation}
-Where $E$ and \textbf{$p$}  are the energy and the momenta of each incoming particle respectively, in the CM frame, where the momenta are equal and opposite, the second term vanishes and  $s = 4E^2$.
+Where $E$ and \textbf{$p$}  are the energy and the momenta of each incoming particle respectively, in the CM frame, where the momenta are equal and opposite, the second term vanishes and  $s = 4E^2$.\\
 
-The second important parameter of the collider's performance is the luminosity, defined as the  quantity that measures the ability of a particle accelerator to produce the required number of interactions and is the proportionality factor  between the number of events of particular physics process per second $dR/dt$ and the quantum mechanical probability for the interaction called cross section \sigma_{p} \cite{ref_lib_vol3}.
+The second important parameter of the collider's performance is the luminosity, defined as the  quantity that measures the ability of a particle accelerator to produce the required number of interactions and is the proportionality factor  between the number of events of particular physics process per second $dR/dt$ and the quantum mechanical probability for the interaction called cross section \sigma_{p} \cite{ref_lib_vol3}.\\
 
-%\section{Cross section}
-%%resumir en un parrafo de 1.3 a 1.7
 The technical meaning of "cross section" in particle physics is quite different from its common usage, while "cross section" typically refers to a slice of an object, in particle physics, it often refers to the probability that two particles will collide and react in a specific manner.
@@
 
-Where the value of $\mathcal{L}{\text{inst}}$ is evaluated over time $T$ (excluding possible dead time) because its intensity decreases as the number of protons reduces during the collisions of the fill.
-So $\mathcal{L}{int}$ is directly related to the number of observed events as:
+Where the value of $\mathcal{L}_{inst}$ is evaluated over time $T$ (excluding possible dead time) because its intensity decreases as the number of protons reduces during the collisions of the fill.
+So $\mathcal{L}_{int}$ is directly related to the number of observed events as:
 
@@
 
-Luminosity is one of the fundamental parameters used to measure the performance of an accelerator, understanding luminosity with the best possible precision is crucial for physics analyses such as searches for new particles, rare processes, or measurements of known particle properties \cite{lumi_motiv}.
+Understanding luminosity with the best possible precision is crucial for physics analyses such as searches for new particles, rare processes, or measurements of known particle properties \cite{lumi_motiv}.
 The experimental techniques to determine signal rates are mature enough, where the understanding of acceptances, detector biases, reconstruction efficiencies, or background subtraction is at the sub-percent level, so that the final precision of the physics measurement is dominated by the luminosity uncertainty \cite{lumi_paper_def_and_concept}.
 Ultimately, the greater the precision of the luminosity measurement, the more physicists can understand their observations and delve into hidden corners beyond our current knowledge.
-%Knowing the integrated luminosity enables physicists to compare their observations with theoretical predictions and simulations.
-For instance, they can search for dark matter particles that escape collisions undetected by examining the energies and momenta of all particles generated in a collision.
-If there is an imbalance, it could be due to an undetected, potentially dark matter, particle that carries energy away.
-This is a powerful method of searching for new phenomena, but many effects, such as neutrinos produced in collisions, need to be considered.
-Neutrinos also escape undetected and leave an energy imbalance, making them indistinguishable from new phenomena.
-Therefore, to determine if something unexpected has been produced, physicists must look at the numbers \cite{luminosity_importance} .
-
-%For example, if 11,000 events show an energy imbalance, and the simulations predict 10,000 events containing neutrinos, this could be significant.
-But if physicists only know the luminosity with a precision of 10\%, they could have easily had 11,000 neutrino events, and there were just 10\% more collisions than assumed.
-Clearly, a precise determination of luminosity is critical   \cite{luminosity_importance}.
-
-%There are also types of analyses that depend much less on absolute knowledge of the number of collisions.
-For example, in measurements of ratios of different particle decays, such as the recent LHCb measurement, uncertainties in luminosity get canceled out in the ratio calculations.
-Other searches for new particles look for peaks in mass distribution and rely more on the shape of the observed distribution and less on the absolute number of events.
-But these also need to know the luminosity for any interpretation of the results \cite{luminosity_importance}.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Expected  Luminosity precision for LHC Run 3}
@@
 This thesis project aims to contribute to the improvement of the precision of the luminosity for Run 3, where it is expected to obtain an approximate luminosity of $390 fb^{-1}$.
+\\
 
@@
 \end{table}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{comment}
 \begin{table}[h!]
@@
 \end{table}
-
+\end{comment}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
   \begin{center}
-  \begin{figure}[h!]
+  \begin{figure}[ht]
     \centering

### 2023-04-11 tesis_Luis/Chapter3/chapter3.tex
updated

--- 2023-03-01 tesis_Luis/Chapter3/chapter3.tex
@@
 \chapter{Luminosity  Measurement and Calibration}
+\label{ch3}
+
+Accurately measuring the luminosity delivered to the CMS experiment by the LHC is essential for various reasons.
+Online, the luminosity measurement provides feedback on the LHC and CMS performance and operations, including measuring trigger rates.
+In offline analysis, the luminosity measurement is a critical component for measuring the cross-section of observed processes or setting upper limits in searches for processes beyond the standard model.
+
+As we see, to measure luminosity, a total of seven luminometers are used at CMS, and each of them reads out a specific quantity observed in the detector, such as hits, tracks, or clusters.
+The rate R measured by the luminometer is proportional to the instantaneous luminosity, $\mathcal{L}_{inst}$, with the constant of proportionality given by the visible cross-section $\sigma_{vis}$ \cite{pas_18}.
+
+\begin{equation}
+R(t)=\mathcal{L}_{inst}\sigma_{vis}
+\label{lumi_exp_gen}
+\end{equation}
+
+The determination of $\sigma_{vis}$ is performed through van der Meer (vdM) scans using a specialized LHC machine setup.
+This chapter provides a description of this procedure, specifically applied with the PCC method.
+
+\section{Pixel Cluster Counting method}
+
+The PCC method utilizes the mean number of pixel clusters in the CMS silicon pixel detector to determine an offline luminosity measurement, this method exploits the very large number of pixels in the inner part of the CMS tracking system, it means that the probability of a given pixel being hit by two different charged particles from the same bunch crossing is exceedingly small, this large granularity and low occupancy yield measurements with excellent linear response with the pile-up (number of interactions per bunch crossing)$\mu$ \cite{PCC_PAS_12_001},  on average, the detector occupancy is less than 0.1\%\cite{lumi_precise_2015_2016}.\\
+
+Figure  \ref{pileup} shows a simulation with pp collision zero-bias events with a full CMS detector response made in 2016, it contain only in time pileup and detector noise, where the mean number of pixel clusters is of the order of  100 per event.
+For simplicity, the number of pileup interactions present in each event is randomly generated from a representative PCC distribution at $\mu$ = 45 and the average PCC as a function of $\mu$.
+The latter distribution is fitted with a first-order polynomial, assuming no correlations among different values of $\mu$.
+Good agreement is seen based on the estimated goodness-of-fit $\chi^{2}$ per degree of freedom (dof) value of about 0.5 , indicating linearity under simulated conditions \cite{lumi_precise_2015_2016}.
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[scale=.3]{Chapter3/pileup_lineality.png} 
+    \caption[Linearity with pile-up]{ The left plot shows the number of pixel clusters and their statistical spread from simulation of pileup following a Poisson distribution with a mean of 45.
+The right plot shows the mean number of pixel clusters from simulation as a function of mean pileup.
+The red curve is a first-order polynomial fit with slope and $\chi^{2}/ndof$ values shown in the legend.
+The lower panel of the right plot shows the difference between the simulation and the linear fit in black points.
+The green band is the final linearity uncertainty for the 2016 data set \cite{lumi_precise_2015_2016} }
+    \label{pileup}
+  \end{figure}
+\end{center}
+
+To obtain the mean number of pixel clusters per event, several zero-bias events are averaged. This value is given by :
+
+\begin{equation}
+\left < N_{\text{cluster}} \right > \equiv \left < N_{\text{cluster}/\text{interaction}} \right > \mu
+\end{equation}
+
+Under minimum bias conditions, $\mu$ can be expressed as:
+
+\begin{equation}
+\mu = \frac{\sigma_{\text{minBias}}}{f} \cdot \mathcal{L}_{inst}
+\end{equation}
+
+where $f$ is the LHC revolution frequency and $\mathcal{L}_{inst}$ is the single bunch instantaneous luminosity (SBIL).
+The minimum bias cross section $\sigma_{\text{minBias}}$ here is related to the PCC visible cross section by the mean number of clusters per interaction:
+
+\begin{equation}
+\sigma_{vis}= \left < N_{\text{cluster}/\text{interaction}} \right >\cdot \sigma_{\text{minBias}}
+\end{equation}
+
+Combining everything, the PCC luminosity measurement is obtained as:
+
+\begin{equation}
+\mathcal{L}_{inst}=\frac{\left < N_{\text{cluster}} \right >}{\sigma_{vis}} \cdot f
+\end{equation}
+
+This method is capable of providing a precise luminosity measurement over longer time periods, but it cannot do so for a single luminosity section (23 seconds) as is possible with online luminometers.
+The reason for this limitation is the limited CMS trigger bandwidth available for collecting data \cite{pas_18}.
+A detailed discussion on this topic can be found in the next chapter.\\
+
+In the PCC measurement, the innermost layer of the pixel detector is excluded from the analysis due to significant dynamic inefficiency effects \cite{pas_18}.
+At higher $\mathcal{L}_{inst}$, the hit efficiency in this layer decreases because the readout chip cannot process all of the hits.\\
+
+\section{2022 CMS Data collected}
+
+On July 12th, 2022, the data collection for Run3 of the Large Hadron Collider (LHC) began, which resulted in a total luminosity of $38.48 fb^{-1}$.
+This collection period encompassed the duration from the start of stable beams until the beam was dumped, or when stable beams ceased for other reasons, such as beam studies.
+The luminosity delivered by the LHC to CMS (blue) and the luminosity recorded by CMS (orange) during stable beams and proton-proton collisions at a center-of-mass energy of $\sqrt{s}$ 13.6 TeV in 2022 are depicted in Figure \ref{Lumi_2022}.
+Note that  the special runs that occurred at injection energy (450 GeV) are not represented in these graphs.
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[width=.45\textwidth]{Chapter3/lumi_per_day_cumulative_pp_2022.png}
+    \includegraphics[width=.45\textwidth]{Chapter3/lumi_per_day_pp_2022.png}
+    \caption[Integrated Luminosity 2022]{(left) Cumulative day-by-day integrated luminosity, 2022 Cumulative measured luminosity versus day delivered.
+Note that this plot may not include data taken within the most recent 24 hours.
+(rigth) Day-by-day integrated luminosity, 2022 As the first plot, but not cumulative.}
+    \label{Lumi_2022}
+  \end{figure}
+\end{center}
+
+\section{Module selection}
+
+To ensure accurate luminosity measurement, a module selection is created to remove any modules exhibiting long-term performance variations, indicating a non-physical shift in their cluster counts.
+With a total of 1856 modules in the pixel system, all of them can be considered in the luminosity measurement; however, non-zero occupancy and non-linear effects can pose challenges for accurate measurement.
+Thus, to identify "good" and "stable" modules, a subset is selected by eliminating  underperforming or "bad" modules and comparing their relative contributions to the cross section.
+Those with relatively consistent contributions across standard physics runs are kept, while those with significant changes in their relative cross section compared to the averaged relative contribution are rejected.
+The Module selection is achieved  with the following procedure:
+
+\begin{itemize}
+\item Poor statistics lumisections are removed by applying selection on total PCC.
+\item Barrel layer-1 modules are removed, as these modules are significantly affected by dynamic inefficiency.
+\item A loose selection of 7\% based on RMS/mean frome the module weight distribution (changes in the module PCC ratio relative to the total PCC) is applied.
+Modules with significantly large RMS/mean are removed with this selection as shown in \ref{goodmodule}.
+\item The module stability is re-evaluated based on RMS/mean values using an iterative method where the second iteration is made with a loose selection of 4\%.
+\end{itemize}
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[scale=.17]{Chapter4/good_module.png}\includegraphics[scale=.15]{Chapter4/RMSmean.png}
+    \caption[RMS/mean Module  Stability]{ left: stability profile for good and bad modules where weight is plotted as a function of lumi section.
+Right: RMS/mean values of module weight for all pixel modules  where each pixel module is represented by a module number index (same happen for the 4\% iteration).}
+    \label{goodmodule}
+  \end{figure}
+\end{center}
+
+The changing conditions of the pixel detector over time, such as detector noise, aging effects, and radiation damage, can cause variations in the number of well-performing modules during different periods.
+Recognizing this, these variations are evaluated over a 23-second interval, which corresponds to the granularity of the luminosity database.\\
+
+To ensure the accuracy of the measurements, pixel module veto lists were generated for five different time periods, namely C, D, E, F, and G, using the procedure described above for each period.
+To further enhance the stability of the PCC measurement, a common module vetolist was created by combining the lists from all five periods were the number of bad modules per period were added and modules with equal ID were removed , as shown in table \ref{common veto module}.
+The PCC data with zero bias was then reprocessed using this common module vetolist and ultimately used for the VdM analysis.
+
+\begin{table}[ht]
+\centering
+\caption{After each iteration for each period, the periods C and D are combined, followed by the periods C, D, and E, then the periods C, D, E, and F, and finally, the common veto list is created using the periods C, D, E, F, and G.}
+\begin{tabular}{ccc}
+\textbf{Period} & \textbf{\# bad modules} & \textbf{\# good modules}  \\ 
+\toprule
+2022C+D         & 886                     & 970                       \\
+2022C+D+E       & 1106                    & 750                       \\
+2022C+D+E+F     & 1307                    & 549                       \\
+2022C+D+E+F+G   & 1411                    & 445                   
+\label{common  veto module}   
+\end{tabular}
+\end{table}
 
@@
 
-\subsection*{Backgrounds}
+As discussed in Chapter 1, the instantaneous luminosity for a single colliding bunch is described by Eq.
+(\ref{luminosity_2}).
+In practice, while the measurement of the beam currents $N_{1,2}$ is well determined, the individual proton density functions cannot be directly measured.
+To address this, the VdM method involves a specific machine setup that allows for the determination of the two beam overlap integrals.
+This is achieved by varying the separation between the beams and measuring the resulting rates, which can be used to obtain density profiles that are close to normal distributions.
+
+\begin{equation}
+\int \rho_{x1}(x) \rho_{x2}(x) dx = \frac{R_{x}(0)}{\int R_{x}(\Delta) d\Delta}
+\end{equation}
+
+where $R_{x}(\Delta)$ is the rate measured when the two beams are separated in $x$ by a distance $\Delta$; a asimilar equation can be written in $y$.
+Then the beam overlap width $\Sigma_{x}$ (and similarly $\Sigma_{y}$) is defined as \cite{pas_18}:
+
+\begin{equation}
+\Sigma_{x}= \frac{1}{\sqrt{2\pi}} \frac{\int R_{x}(\Delta)d\Delta}{R_{x}(0)}
+\label{CapSigma}
+\end{equation}
+
+This process leads to the final expression for luminosity for a single colliding bunch:
+
+\begin{equation}
+\mathcal{L}_{inst}=\frac{N_{1} N_{2}f}{2 \pi \Sigma_{x}\Sigma_{y}}
+\end{equation}
+
+where $N_{1,2}$ are the particles per bunch (bunch current) and  $f= 11246$ Hz is the bunch orbit frequency around the LHC ring determined by the energy of the protons.\\
+
+Therefore, the equation \ref{lumi_exp_gen} used to measure the visible cross sections $\sigma_{vis}$ takes the following form:
+
+\begin{equation}
+  \sigma_{vis}=\frac{2\pi \Sigma_{x} \Sigma_{y} R(0, 0)}{N_{1}N_{2} f}
+  \label{sigmavis_eq}
+\end{equation}
+
+Experimentally, the quantities $\Sigma_{x}$ and $\Sigma_{y}$, as defined in Eq. (\ref{CapSigma}), are determined by conducting two separate scans in the $x$ and $y$ directions, respectively. 
+These scans are performed by varying the separation between the beams in each direction  at a fixed number of separation steps.The separation steps are determined through curve fitting of the scan data based on the luminometer rate measurements obtained during the vdM scans.\\
+
+The measured rate, denoted by $R(0,0)$, is determined as the highest value among the rates obtained in the $x$-scan $R_x(0)$, and the rates obtained in the $y$-scan $R_y(0)$.
+Although the beam widths are identical for all luminometers, the peaks of the scan curves are specific to each luminometer.\\
+
+Figure \ref{vdm_sketch} depicts a schematic of the beam positions during vdM scans in the $x$ and $y$ planes, along with the detector rate as a function of beam separation  \cite{pas_18}.
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[scale=.37]{Chapter3/vdm_sketch.png}
+    \caption[Sketch of a vdM scan in x and y planes and example of fitting resulting rates]{ The sketch of a vdM scan in $x$ and $y$ planes.
+The indent sketch is an example of the fit of the resulting rates \cite{vdM_sketch}.}
+    \label{vdm_sketch}
+  \end{figure}
+\end{center}

### 2023-04-18 tesis_Luis/Chapter4/chapter4.tex
updated

@@
 
-The main VdM scan program for the CMS experiment was performed in November 2022 during LHC fills 8379 and 8381.
-In fill 8381 on 10 and  11 Nov 2022 at pp collision energy $\sqrt{s}$ of 13.6 TeV  144 bunch pairs were colliding at the CMS intertion points at zero crossing angle, with two additional unpaired bunches present in each beam.
-Four VdM scan pairs, two beam-imaging (BI) scan pairs and one length scale scan pair where performed, where each scan pair consists of two scans in the transverse planes x and y, as well as other scan types not included in this analysis.
-In a VdM scan, the two beams are separated by $6\sigmab$ ≈ 578 $\mu m$ and scanned across one another in a sequence of 25 steps of 30 s with a step size of $0.5\sigma_{b} \thickapprox 48 \mu m$, where $\sigma_{b}$ is the transverse bunch size.
-In the BI scans, one beam is kept fixed at its nominal head-on position while the other is separated and scanned in 19 steps of 46 s from $-4.5\sigma_{b}$ to $+4.5\sigma_{b} \thickapprox 433 \mu m$.
-In a length scale scan, the beams are separated by a constant amount of $\sqrt{2} \sigma_{b} \thickapprox  106 \mu m$  and moved coherently forward and backward in five steps each in the same transverse direction, finally two super separation periods were performed for the analysis and Background sustraction, here the two beams were sepated at a distance of $6\sigma$.
-The scan program during fill 8381 is summarized in Fig.
-\ref{scan_prog}.\\
+In 2022, the main vdM scan program for the CMS experiment was conducted during LHC fills 8379 and 8381 on 10 and 11 November.
+During fill 8381, a total of 144 bunch pairs were collided head-on , with a proton-proton collision energy $\sqrt{s}$ of 13.6 TeV.
+During this fill, various types of scan pairs with different characteristics were conducted.
+These scan pairs are described below.
+Each scan pair consisted of two scans in the transverse planes $x$ and $y$.
+In addition to these scans, other types of scans were also conducted, which are not included in this analysis.\\
 
-The VdM calibration itself is based on scans recorded during the fill 8381, where the  Six scan pairs using for  this analysis were performed, they are labeled consecutively as they were recorded in time, as “VdM1”, “BI1”, “BI2”, “VdM2”, “VdM3”, and “VdM4” as shown in figure \ref{scan_prog} .
-During the "VdM2" scan pair, the central CMS data taking was not operational, so no data was recorded for PCC, and this scan pair is skipped in the PCC VdM analysis.
-To ensure a dataset with a high event count for PCC even at large beam separations, CMS gated the zero-bias triggers on 5 bunch pairs: BCIDs (Bunch Crossing ID) 282, 822, 2944, 3123, and 3302 and recorded events with a total rate of 27.23 kHz.\\
+The calibration program included four scan pairs, vdM1,vdM2, vdM3 and vdM4, these are considered the standard vdM scans in the program, used specifically to compute $\sigma_{vis}$.
+In this type of scan the two beams are separated by $6\sigma_{b} \thickapprox 578\mu m$, where $\sigma_{b}$ represents the transverse bunch size.
+The beams are then scanned across each other in a sequence of 25 steps, each lasting 30 seconds with a step size of $0.5\sigma_{b} \thickapprox 48 \mu m$.\\
+
+The calibration program also included two beam-imaging scan pairs, BI1 and BI2 .
+These scans were developed for studies on beam shapes, estimating the uncertainty caused by the not strictly valid assumption seen in previous sections that the bunch proton density function is factorizable into independent $x$ and $y$ densitys, this correction is called  ($x$-$y$ nonfactorization).
+BI acans also are used to compute of $\sigma_{vis}$, independent of the standard vdM's scans.
+During the BI scans, one beam is kept fixed at its nominal head-on position, while the other beam is separated and scanned in 19 steps, each step lasts 46 seconds and covers a range from $-4.5\sigma_{b}$ to $+4.5\sigma_{b} \thickapprox 433 \mu m$.\\
+
+Two length scale LS scans were conducted, one during fill 8381 and another during fill 8379.
+The LS scan is a special scan designed to apply a correction to the results of  $\sigma_{vis}$ obtained from the vdM scan program, this correction will be described further in this section.
+During this scan, the beams are separated by a constant amount of $\sqrt{2} \sigma_{b} \thickapprox 106 \mu m$, and they are moved coherently forward and backward in five steps each, all in the same transverse direction.\\
+
+Finally two super separation periods SS1 and SS2 were performed for the background estimation, here the two beams were sepated at a distance of $6\sigma_{b}$ during 5 minutes, at this distance the overlap of the beams is minimal and the contribution of collision is negligible.
+%23:31-23:36 11:47-11:52
+
+The scan program during fill 8381 is summarized in Figure \ref{scan_prog} where all the scans mentioned and described above are labeled.
 
@@
     \centering
-    \includegraphics[scale=.25]{Chapter4/2022Scanprorgam.png}
-    \caption[2022 scan program]{Nominal horizontal and vertical positions of the proton beams during LHC fill 8381, showing the four normal VdM scans, two BI scans and the two Super Separation Periods (SS)}
+    \includegraphics[scale=.35]{Chapter4/2022Scanprorgam.png}
+    \caption[2022 scan program]{Nominal horizontal and vertical positions of the proton beams during LHC fill 8381, showing the four standard vdM scans, two BI scans, one LS scan and the two Super Separation Periods (SS)}
     \label{scan_prog}
@@
 
-The rate measured by each detector and normalized with the measured beam population is
-fitted as a function of the separation. Corrections to the measured proton numbers and to
-the nominal separation are discussed in the following sections. Here, the fit model and the
-background subtraction are discussed. Technically, the fits are performed with the VdMFramework.
+\section{Data aquisition and processing}
+\label{data}
+In order to achieve a high statistical precision in data for each colliding bunch pairs the system trigger  bandwidth  limitations do not allow the use of all of them, beacause this, CMS implemented a zero-bias triggers only on five Bunch crossing id (BCID): 282, 822, 2944, 3123, and 3302.
+This data is saved randomly with the highest possible rate of 27.23 kHz using the High Level Trigger (HLT) through the CMS data acquisition (DAQ) system.
+Due to the weight of the events, 16 different streams are required to save the full data.
+Here the datasets are in their RAW format, which contains information per event (bunch crossing) and the amount of charge deposited in each pixel.\\
+During the vdM2 scan pair, the central CMS data taking was not operational, so no data was recorded for PCC, and this scan pair was skipped from the full calibration.\\
 
-%CMS BRIL Project, “VdMFramework documentation”. CMS Website, 2023.
-%https://vdmdoc.docs.cern.ch/.
+The data is then reprocessed by the CMS collaboration to enable a cluster reconstruction, resulting in the datasets (ALCARECO version) that contain a module collection and their number of clusters per event , the data here is in the CMSSW format.
+These datasets will be used as the starting point for our own data reprocessing and analysis.\\
 
-%For the background estimation, two Super Separation (SS) periods were carried out during the scan program, each 5 minutes long where the beams were separated by $6\sigma_{b}$ (where $\sigma_{b}$ the beam size) in both the x and y directions.
+The ALCARECO samples are processed using CMSSW software (written in Python and C++) to extract the clusters per module.
+Due to the large size of the datasets, all the datasets were sent for reprocessing through The Worldwide LHC Computing Grid (WLCG), wish consists of a grid-based computer network infrastructure,designed by CERN to handle the big volume of data produced by LHC experiments.
+In this  process, we obtained the required cluster counts, which was saved in a dataset with a ROOT format.
+This format uses TTrees and TBranches, that are containers to maintain the information in a hierarchical and organized manner.
+The information is stored in one TTree that contains the information per event distributed in several TBranches, such as the number of pixel clusters, the BCID, the module identifiers, number of run, the number of lumisection (where 1 LS = 23 s), the number of luminible LN (where 1 LN is equivalent to 0.32 s) and time where that event took place (timestamp begin).\\
 
-\section{Data analysis}
+In order to maintain full statistical precision despite the limitations of the vdM framework (vdMFW), which was utilized for the final fit of our data, the rates were stored  each 1.32 s (NB4) time that corresponding to 4 LN, this was done making  an average  between clusters and the number of events that fall within this time span.
+During this process, the module veto list mentioned in the previous section is introduced and the modules detected in these list were removed.
+In this phase, the information is merged into a single file using a hierarchical data format (hd5) that organizes the data into tables, this final format is the required by the vdMFW.
+All the  process is carried out using lxbatch, a cluster of computers located within CERN.\\
 
-The data taken by the  PCC luminometer was reprocessed for the CMS team to perform a cluster reconstruction.
-The datasets containing the cluster information per event were stored in 16 different "zero Bias" datasets.
-The first step we took was to extract the data corresponding to the events that belong to our 6 VdM Scans (Runs, Pixel cluster clusters, timestamps, etc.) in a file with ROOT format that is the CERN's data analysis package.
-This was done through the CMS software (CMSSW), which is written in Python2 and C++.\
-Afterward, we have the 16  resuulting datasets, uno for each "zero Bias" dataset.
-These files are reprocessed to generate the final file containing the rates stored per 1.32 s (NB4) with a hierarchical data format (HD5).
-Within this data reprocessing, we clean the information by subtracting the background and also select the modules that were previously analyzed by a stability study.
-
-The final "hd5" file containing the rates from the detector with data collected during the vdM scans is analyzed using a software framework called the "vdM Framework" (vdM FW), which is the latest version and is written in Python3.
-The vdM FW uses data analysis package, "ROOT," through the "PyRoot" library.
-With the analysis and plotting tools, the vdM FW reads the hd5 file, producing several intermediate files: scan file, beam currents file, rates file, and correction files.
-It then applies corrections to the rates (Background, DynamicBeta), separation (OrbitDrift, LengthScale, BeamBeam), and creates a graph file.
-This graph file contains the normalized rates (i.e., $R/N_{1}N_{2}$) and beam position.
-Each point corresponds to the averaged rates in a time window of 30s and 46s for vdM scans and BI scans, respectively.
-The points are then fitted with a predefined function to extract $\Sigma_{x,y}$ and peak values to compute $\sigma_{\text{vis}}$ for all the bunches in the scan.
+Finally the hd5 file containing the rates collected during the vdM scans  is analyzed using the vdMFW, which is written in Python and uses the ROOT data analysis package through the PyRoot library.
+The vdMFW  extracts the necessary information using its analysis tools.
+During the process, several corrections are applied to the rates which will be described later.
+In the processing the vdMFW generates the final information and plots, which contain the normalized rates ($R/N_{1}N_{2}$) and beam position.
+A mathematical function is then used to fit the points to extract $\Sigma_{x,y}$ and peak values to compute $\sigma_{\text{vis}}$ for all the bunches in the scan.
 
 \section{Background estimation}
-
-To extract $\Sigma_{x,y}$ through fitting, it is necessary to correct the raw measured rates for background in the detector beforehand.
-The background contribution is estimated independently during the Super Separation (SS) period comented in the above section.
-During this period, the beams are separated by $6\sigma_{b}$, ensuring that the only contribution is from background.
-There are three principal sources of beam-induced background to consider:
+\label{bkg}
+To perform accurate fitting of the data, it is necessary to take into account the following background contributions to the PCC rates.
+These contributions are estimated independently during the Super Separation (SS) periods discussed in the previous section.
+Three primary sources of beam-induced background should be considered:
 
@@
 \item Beam Gas Elastic (BGE).
-The elastic beam gas contribution are all coherent and quasi-elastic nuclear elastic and coulomb scattering for multi-turn beam-gas interactions around the ring.
-Typically the interaction of the primary beam proton and the takes place at the TCT collimator, so that this background contribution has an almost point- like source \cite{bkg_source}.
+The elastic beam gas contribution are all coherent and quasi-elastic, nuclear elastic and coulomb scattering for multi-turn beam-gas interactions around the ring.
+Typically the interaction of the primary beam proton and the takes place at the tertiary TCT collimator jaw \cite{bkg_source}.
 
@@
 To estimate the background value in each BCID, the mean value of the PCC per NB4 rates distribution is computed.
-The mean and error per super-separation (SS) period are obtained by plotting the PCC per NB4 as a function of time and then taking the y projection.
+The mean and error per super separation (SS) period are obtained by plotting the PCC per NB4 as a function of time and then taking the $y$ projection.
 The error is calculated using the formula $AvgErr = \sqrt{SEM_1^2 + SEM_2^2 + \cdots + SEM_N}/N$.
@@
 Table  \ref{ss_per_bx} shows the results for five different BCIDs, using the reprocessed PCC data for Fill 8381.
-The overall background correction applied to raw PCC rate is $0.74305 \pm 0.002407$, which is calculated by taking the average of the mean values of SS1 and SS2.
+This analysis reveals notable inconsistencies in the background values obtained from the two Super Separation (SS) periods.
+As a result, the quality of the fit was affected, and thus, this data was excluded from subsequent analyses.
+Further details on this matter will be discussed in a later section.
 
-\section{Corrections}
+\section{Beam Corrections}
 
-There are several systematic effects that affect the measurement of beam overlap width and therefore the extraction of $\sigma_{vis}$ from the VdM scan procedure.
+There are several systematic effects that affect the measurement of beam overlap width and therefore the extraction of $\sigma_{vis}$ from the vdM scan procedure.
 These effects are measured and, where applicable, corrected as described below.
-A systematic uncertainty is assigned to the resulting measured cross-section, and the following corrections are applied in the VdM Framework:
+A systematic uncertainty is assigned to the resulting measured cross section $\sigma_{vis}$, and the following corrections are applied in the vdM Framework:
 
@@
 \item Ghost and Satellite.
-This correction corrects for the presence of ghost and satellite spurious charges, which affect bunch currents.
-Satellite charges refer to additional charges outside the actual colliding bunch, while spurious charges refer to charge not in any nominally filled bunch slot.
+This correction corrects for the presence of spurious charges, which affect bunch currents.
+Satellite charges refer to additional charges outside the actual colliding bunch, while ghost charges refer to charge not in any nominally filled bunch slot.
 These results in corrections of up to 0.5\% to $\sigma_{vis}$.
-The overall uncertainty in the bunch current measurement is estimated to be 0.4%.
-
-\item Background. This refers to the noise in the detector where there are no collisions. This value, estimated above, is subtracted from the rates.
+The overall uncertaintys estimate the bunch current measurement  to be 0.4\%.
 
 \item Orbit drift.
-The orbit drift correction accounts for potential movement of the LHC orbit during the VdM scans.
+The orbit drift correction accounts for potential movement of the LHC orbit during the vdM scans.
 Time-dependent changes of the transverse beam positions for fixed machine parameters can alter the beam separation.
@@
 
-Applying this correction improves the agreement between the $\sigma_{vis}$ values derived with different scan pairs and changes the average $\Sigma_{vis}$ by about 0.3\%.
+Applying this correction improves the agreement between the $\sigma_{vis}$ values derived with different scan pairs and changes the average $\sigma_{vis}$ by about 0.3\%.
 The full size of the correction is considered as uncertainty.
 
-\item Beam Beam corrections.  The electromagnetic interaction between the two colliding proton bunches leads to two ef- fects in beam-separation scans:
+\item Beam Beam corrections.  The electromagnetic interaction between the two colliding proton bunches leads to two effects in beam-separation scans:
 
@@
 \item Beam Beam deflection.
-Corrects Beam Beam deflection (BB) that happens during bunch crossings at the collision point.accounts for the electrical repulsion of the beams, which increases the lateral
-separation  The deflection is calculated and added to the nominal separation.
+Corrects Beam Beam deflection (BB) that happens during bunch crossings at the collision point.
+Accounts for the electrical repulsion of the beams, which increases the lateral separation.
+The deflection is calculated and added to the nominal separation.
 
 \item Dynamic Beta.
-The so-called dynamic-$\beta*$ effect, which accounts for any changes in the proton density distributions of the bunches due to the single-particle interactions.
-As a result, the non-linear change during separation steps in transverse bunch profiles is observed, and can described by the effective change of the $\beta*$  value.
+The so-called dynamic $\beta^{*}$  effect, which accounts for any changes in the proton density distributions of the bunches due to the single-particle interactions.
+As a result, the non-linear change during separation steps in transverse bunch profiles is observed, and can described by the effective change of the $\beta^{*}$  value.
 \end{itemize}
-The corrections are calculated for each proton bunch pair individually, and the combined effect of the two corrections is an increase of σvis by 1.0\%, with an uncertainty of 0.5\%.
+The corrections are calculated for each proton bunch pair individually, and the combined effect of the two corrections is an increase of $\sigma_{vis}$ by 1.0\%, with an uncertainty of 0.5\%.
 
@@
 It applies a linear scaling to the beam separation to convert it from the "CMS scale" to the actual "physics scale".
-This is  calibrated by analyzing pp collision vertices reconstruced by the CMS tracker using data from the five length scale scan pairs performed in fills 8178, 8379, and 8381.%Length scale factors of (−0.56 ± 0.08)\% in x and (−0.43 ± 0.10)\% in y are found.
-The quoted uncertainty accounts for the statistical uncertainty,
-This correction reduces $\sigma_{vis}$ by 1.0\% and results in an uncertainty of 0.12\%.
+This is  calibrated by analyzing pp collision vertices reconstruced by the CMS tracker using data from the five length scale scan pairs performed in fills 8178, 8379, and 8381.This correction reduces $\sigma_{vis}$ by 1.0\% and results in an uncertainty of 0.12\%.
 
-%https://gitlab.cern.ch/bril/VdMFramework/-/wikis/od-flag
 \end{enumerate}
 
-\newpage
-\section{van der Meer Scans and $\sigma_{vis}$ Results}
+\section{Fit Model  Selection}
 
-In the previous section, inconsistencies were observed in the background values, which resulted in a very high chi-square value.
-Therefore, it was decided not to use background subtraction.
-Instead, a fitting function was used, which applies a constant to achieve optimal values in the fit and improve the chi-square.
-To correct the measurements of PCC, beam separation, and beam currents, the corrections mentioned earlier were applied.
-The implemented fit model is a double Gaussian function combined with a constant-like function refered as "DG+Const":
+As we have seen in previous sections, the points generated for each step of the scan need to be fitted using a mathematical function.
+This allows us to extract the parameters we need, such as $\Sigma_{x,y}$ and peak values for all the bunches in the scan, in order to finally compute $\sigma_{\text{vis}}$.
+Within vdMFW, there are several pre-defined functions that use a combination of Gaussian functions with different adjustable parameters to achieve a better fit.
+These functions include Double Gaussian (DG), Single Gaussian (SG), Poly Gaussians (PG), among others.
+All of the above functions exist in versions with an additive constant to the entire function, typically used to fit to the background levels.\\
+
+For this analysis, various fit functions were tested, and the one with the best quality of fit was selected.
+The quality of the fit is primarily based on the convergence of the function with the points being fitted for each BCID.
+The convergence is assessed based on the covariance matrix, which measure the linear relationship between each pair of elements or variables.
+A  covariance status equal to 3 means a good convergence of the function.\\
+
+The second most important parameter for measuring the quality of the fit is having a good  Chi-square $\chi^2$.
+The  Chi-square goodness of fit test is a statistical hypothesis test that helps to determine whether a variable is likely to come from a specified distribution or not.
+This test provides a way to assess whether the data values have a good enough fit to our model, or if the model is questionable.
+In more general terms, this test compares observed values with expected or theoretical values according to the hypothesis.
+The goal is to minimize the calculation of the $\chi^2$ as defined in equation \ref{x^2}, from here is  inferred that the lower the value of $\chi^2$, the better the fit is considered to be.
 
 \begin{equation}
-DG+Const=
- C+P \cdot \Biggl[ F \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 \sigma_{1}^{2} } \Biggr) + (1-F) \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 \sigma_{2}^{2} } \Biggr) \Biggr] 
+\chi^{2}(\theta)=\sum_{i=1}^{N} \frac{(y_{i}-\lambda(x_{i},\theta))^{2}}{\sigma_{i}^{2}}
+\label{x^2}
 \end{equation}
 
-%\begin{equation}
-%DG+Const=
- %C+P \cdot \Biggl[ F \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 ( \frac{\sigma_{1}}{F_{Ratio}+1-F})^{2} } \Biggr) + (1-F) \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 ( \frac{\sigma_{2}}{F_{Ratio}+1-F})^{2} } \Biggr) \Biggr]
-%\end{equation}
-where $F$ is the weight between 0 and 1 of the first Gaussian in the sum, $x$ is the beam separation $C$ is the constant value, $P$ the peak rate, $\bar{x}$ the mean and $\sigma_{1,2}$ the standard deviations are fit parameters.
-Fig.
-\ref{vdM1_282_XYscan} shows the fitted graphs of the first vdM scan pair for BCID 282 where  all the corrections described in the previous section have been applied and where  rates are normalized by the beam currents, which is a factor of eq.
-\ref{sigmavis_eq}  ($R(0,0)/N_{1}N_{2}$).
+where $N$ observed values $y_{1}$,···, $y_{N}$ are measured with errors $\sigma_{1}$,···,$\sigma_{N}$" at the values of $x$ given without error by $x_{1}$,..., $x_{N}$.
+The theoretical  value $\lambda_{i}$ of $y_{i}$ is given by a function $\lambda_{i} = \lambda(x_{i},\theta)$.
+The value of $\theta$ is adjusted to minimize the value of $\chi^2$ \cite{Statistical_Data_Analysis}.
+
+After probe  several mathematical fit models, those requiring background subtraction from SS periods analysis were ultimately discarded due to the unacceptably high chi-square values obtained, this was due to the inconsistencies mentioned the section \ref{bkg}.
+Therefore, it was decided to use functions that include a constant to model the background in the fit.
+The chosen model with the best fit quality and after applying all the corrections mentioned earlier, was a double Gaussian function plus a constant, referred to as "DG+Const":
+
+\begin{equation}
+DG+Const= C+P \cdot \Biggl[ F \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 \sigma_{1}^{2} } \Biggr) + (1-F) \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 \sigma_{2}^{2} } \Biggr) \Biggr] 
+\end{equation}
+
+\begin{equation}
+DG+Const= C+P \cdot \Biggl[ F \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2(\frac{\sigma\cdot R}{F \cdot R+1-F} )^{2} } \Biggr) + (1-F) \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 (\frac{\sigma}{F \cdot R+1-F} )^{2} } \Biggr) \Biggr]
+\end{equation}
+%[5] + [2]*([3]*exp(-(x-[4])**2/(2*([0]*[1]/([3]*[1]+1-[3]))**2))
+    %    + (1-[3])*exp(-(x-[4])**2/(2*([0]/([3]*[1]+1-[3]))**2)) )
+%("#Sigma","#sigma_{1}/#sigma_{2}","peak","Frac","Mean","Const")
+%[0] -> [0]*[1]/([3]*[1]+1-[3])
+ %[1] -> [0]/([3]*[1]+1-[3])"""
+\begin{itemize}
+\item $C$ is the constant value.
+\item $P$ the $peak$ rate.
+\item $F$ is the weight between 0 and 1 of the first Gaussian in the sum.
+\item $x$ is the beam position.
+\item $\bar{x}$ is the mean.
+\item $\sigma$ the standard deviation of the gaussian.
+\item $R$ is the Ratio $\sigma_{1}/\sigma_{2}$.
+\end{itemize}
+
+Figure \ref{vdM1_282_XYscan} shows the fit graphs of the first vdM scan pair for BCID 282 where  all the corrections described in the previous section have been applied and where  rates are normalized by the beam currents ($R(0,0)/N_{1}N_{2}$), which is according of Eq.
+\ref{sigmavis_eq}.
 
@@
 \centering
-\includegraphics[width=.37\textwidth]{Chapter4/xscan.png}
-\includegraphics[width=.37\textwidth]{Chapter4/yscan.png}\\
+\includegraphics[width=.40\textwidth]{Chapter4/xscan.png}
+\includegraphics[width=.40\textwidth]{Chapter4/yscan.png}\\
 \caption[vdM1 BCID 282]{Normalized rates and the resulting fitted curves with the DG+Const fit model as a function of the beam separation ($\Delta$) for BCID 282 for X (left) and Y (right) scan for the first vdM scan.}
@@
 \end{center}
-
-\newpage
 For the remaining BCID's, the fits for both vdM and BI scans exhibit a very similar behavior, and in all cases, the fits have converged successfully.
-To evaluate the goodness of fit, Fig.
-\ref{chi2/ndof} displays a plot of the chi2/ndof for all the five scan pairs, which has a mean value of 1.88.
-To compute $\sigma_{vis}$, the CapSigma $\Sigma_{x,y}$ and peak values have been extracted from the fits.
-Fig.
-\ref{capsigma_peak} presents the $\Sigma_{x,y}$ and peak values for all scan pairs.
-The plot clearly illustrates that both values reflect the fact that beam size increased over time in the $x$ dimension and decreased over time in the $y$ dimension.
+The evaluation of the goodness of fit is shown in Fig.
+\ref{chi2/ndof} where displays a plot of the $\chi^{2}/ndof$ for all the five scan pairs, which has a mean value of 1.88.
 
@@
     \centering
-    \includegraphics[scale=.03]{Chapter4/DGConst_chi2.png}
+    \includegraphics[scale=.025]{Chapter4/DGConst_chi2.png}
     \caption[chi2/ndof for all scan pairs]{ chi2/ndof for all the scan pairs.
@@
 \end{center}
+
+\section{Results}
+
+To compute $\sigma_{vis}$, the CapSigma $\Sigma_{x,y}$ and $Peak$ values have been extracted, the behavior of these values ​​for all scans pair are shown in the  Figure \ref{capsigma_peak} where those belonging to the scan in $x$ are presented in red and those belonging to the scan in $y$ are shown in blue.\\
+
+The values of $\Sigma_{x,y}$, which represent the standard deviation in the fit, provide a direct measurement of the beam shape, as we can seen in the plot for $\Sigma_{x,y}$  these values decrease in both the $x$ and $y$ directions during the fill time, this is due to a phenomenon called "damping" which causes the beam to gradually focus with time.
+On the other hand the values ​​for the peak in figure \ref{capsigma_peak} (right) are then a direct consequence of this, since a more focused beam means more collisions and thus a higher rate.\\
+
+The figure also displays a sharp decline in values between the BI2 and vdM3 scans, which can be attributed to the exclusion of the vdM2 scan for the reasons mentioned in the section \ref{data} .
 
@@
 
-The sigma visibe $\sigma_{vis}$ for all BCID's (vdM a BI acans) is computed from the fit results parameters Capital sigma $\Sigma_{x,y}$ and $peak_{x,y}$, this is done using the equation \ref{sigmavis_eq}.
-The value of $R(0,0)$ is obtained by taking the average of the peaks in the x and y directions ($R(0,0)=(Peak_{x}+Peak_{y})/2$), which have already been normalized, so \ref{sigmavis_eq} is rewritten as:
+The $\sigma_{vis}$ for all BCID's (vdM and BI scans) is then computed from the fit results $\Sigma_{x,y}$ and $peak_{x,y}$ shown above, this is done using the Eq.
+\ref{sigmavis_eq}.
+The value of $R(0,0)$ is obtained through a specific correction where the rate is taken from the higher value between the scans $x$ and $y$.
+The difference in these rates values is attributed to the fact that some scans are not centered on the axes.
+After this correction, the final peak, which has already been normalized, is obtained.
+As a result, Equation \ref{sigmavis_eq} is rewritten as:
 
 \begin{equation}
- \sigma= 2\pi \Sigma_{x} \Sigma_{y} \Biggl( \frac{Peak_{x}+Peak_{y}}{2} \Biggl)
+ \sigma_{vis}= 2\pi \Sigma_{x} \Sigma_{y}Peak
  \end{equation}
 
-Fig \ref{sigmavis_perbcid} shows the  value of sigma visible $\sigma_{vis}$ per BCID for all the scans. where the error on $\sigma_{vis}$ is assigned as:
+Figure \ref{sigmavis_perbcid} shows the  value of sigma visible $\sigma_{vis}$ per BCID for all the scans where the error on $\sigma_{vis}$ is assigned as:
 
 \begin{equation}
-\sigma_{vis\text{Err}}= 2 \pi \sqrt{ (\Sigma_{y} \cdot R \cdot \Sigma_{x\text{Err}})^{2} + (\Sigma_{x} \cdot R \cdot \Sigma_{y \text{Err}})^{2} + (\Sigma_{x} \Sigma_{y} R_{\text{Err}})^{2} }
+\sigma_{vis\text{Err}}= 2 \pi \sqrt{ (\Sigma_{y} \cdot Peak \cdot \Sigma_{x\text{Err}})^{2} + (\Sigma_{x} \cdot Peak \cdot \Sigma_{y \text{Err}})^{2} + (\Sigma_{x} \Sigma_{y} Peak_{\text{Err}})^{2} }
 \end{equation}
@@
     \centering
-    \includegraphics[scale=.25]{Chapter4/DGConst_xsec.png}
+    \includegraphics[scale=.22]{Chapter4/DGConst_xsec.png}
     \caption[$\sigma_{vis}$ per BCID for all scans]{ $\sigma_{vis}$ per BCID for all the scans,  in each scan, the BCID's follow the same order, which is 282, 822, 2944, 3123, and 3302.}
@@
 
-Fig \ref{sigmavis_perscan} shows the final  $\sigma_{vis}$ per Scan, which corresponds to the weighted average of the five BCIDs with the weight as:
+To obtain the final value of sigma visible , we first perform a weighted average using 5 BCIDs for each scan as shown in Figure \ref{sigmavis_perscan} with blue dots.
+Subsequently, we perform another weighted average among the results of these 5 scans, this final value is represented by the red line in Figure \ref{sigmavis_perscan}.
+In both calcuation, it is assumed that there is no correlation between the BCIDs and the scans.
+Therefore, the computation of the weighted average and the error is assigned as follows:
 
 \begin{eqnarray}
-\frac{1}{\sigma_{vis\text{Err}}^{2}}  \text{     where the error is     } \frac{1}{\sqrt{\sum \frac{1}{\sigma_{vis\text{Err}}^{2}}}}
+\sigma_{visErrTotal}=\frac{1}{\sqrt{ \displaystyle\sum_{\textbf{i}} \frac{1}{\sigma_{vis\textbf{i}Err}^{2}}}}
 \label{error}
@@
 
-After averaging the values of $\sigma_{vis}$ per scan, the error is assigned in the same manner as described in equation (\ref{error}).
-Figures \ref{sigmavis_perscan} and \ref{sigmavis_perbcid} illustrate that there is a systematic variation in $\sigma_{vis}$ between scans.
-To account for this, a systematic error is assigned as follows:
-
+\begin{eqnarray}
+\sigma_{vis}=\Biggl(\displaystyle\sum_{\textbf{i}} \frac{\sigma_{vis\textbf{i}}}{\sigma^{2}_{vis\textbf{i}Err}} \Biggr)(\sigma_{visErrTotal})^{2}
+\label{average}
+\end{eqnarray}
+After completing the calibration procedure, the final result obtained is:
 \begin{equation}
-\sqrt{RMS^{2}-stat^{2}}
+\sigma_{vis}=4163.34 \pm 3.30 \text{ (stat)  mb}
 \end{equation}
-
-Obtaining a final sigma visible for the calibration $\sigma_{vis}=4163 \pm 3 \text{(stat.)} \pm 12 \text{(syst.)} \text{ mb}$.
-This result will be useful for a precise luminosity measurement analysis for Run 3 in the CMS experiment of LHC.
 
@@
     \centering
-    \includegraphics[scale=0.37]{Chapter4/xsec_perscan_v2.png}
+    \includegraphics[scale=0.45]{Chapter4/xsec_perscan_v2.png}
     \caption[$\sigma_{vis}$ per Scan]{ $\sigma_{vis}$  per scan.} 
@@
 \end{center}
+
+As shown in figure \ref{sigmavis_perscan}, the scans exhibit an RMS of $12882 \mu b$ for the values of visible sigma.
+Among them, vdM1 and vdM3 demonstrate the largest variations, approximately 2 standard deviations away from the mean.
+These variations can be attributed to the presence of systematic effects during the scans.

### 2023-05-03 tesis_Luis/Abstract/resumen.tex
updated

--- 2022-04-29 tesis_Rodolfo/Abstract/resumen.tex
@@
     \begin{center}
-    {\huge Resumen}
+    {\LARGE Desarrollo y calibración del sistema de medición de luminosidad CMS Silicon Pixel Detector}
 \end{center}
-Calibracion de van der Meer
+
+Se describe la calibraci\'on del lumin\'ometro de conteo de píxeles del CMS realizada mediante el programa de escaneo "Van der Meer" para el experimento CMS en la toma de datos en colisiones protón-protón a $\sqrt{s}=$13.6 TeV en el 2022.
+El período de recopilación de datos fue el 10 y 11 de noviembre para el fill 8381 del LHC, los datos se procesaron  aplicando una selecci\'on de  m\'odulos "buenos" en el  detector, basandose en un estudio de estabilidad de \'estos.
+El análisis de los escaneos van der Meer con algunas correcciones específicas arroja en la constante de calibraci\'on $\sigma_{vis}$ un valor de:   $4163.3 \pm 3.3 (\text{stat.}) \pm 13 (\text{syst.})\text{ mb}$.
+
+%Se describe la calibraci\'on de la medici\'on de luminosidad para la corrida 3 del gran colisionador de hadrones (LHC),  realizada mediante el programa de escaneo  "Van der Meer"  para el experimento CMS  durante 10 y 11 de Noviembre del 2022 .
+La toma de datos  proton-proton a $\sqrt{s}=$13.6 TeV fue con  el detector de pixeles de silicio (Silicon Pixel detector) para el  fill 8381, dichos datos se reprocesaron  aplicando una selecci\'on de  m\'odulos "buenos" en el  detector, basandose en un estudio de estabilidad de \'estos.
+El an\'alisis de 5 escaneos de Van der Meer presentados en este trabajo arroja en la constante de calibraci\'on $\sigma_{vis}$ un valor de:   $4163 \pm 3 (\text{stat.}) \pm 12 (\text{syst.})\text{ mb}$.
 \end{abstract}

### 2023-05-03 tesis_Luis/Chapter1/chapter1.tex
updated

@@
 \begin{equation}
-  \mathcal{L}_{inst}\propto K\cdot \int\int \int_{-\infty}^{\infty} \rho_{1}(x,y,s,-s_{0}) \rho_{2}(x,y,s,s_{0})dxdydsds_{0}
+  \mathcal{L}_{inst}\propto K\cdot \int\int\int \int_{-\infty}^{\infty} \rho_{1}(x,y,s,-s_{0}) \rho_{2}(x,y,s,s_{0})dxdydsds_{0}
     \label{lumi_1}
@@
 
-For a specific case, asuming equal beams, $\sigma_{1x}= \sigma_{2x} ,\sigma_{1y}= \sigma_{2y}$:
+For a specific case, asuming equal beams, $\sigma_{1x}= \sigma_{2x} \text{ and } \sigma_{1y}= \sigma_{2y}$:
 
@@
 This is the well known expression for the luminosity of two Gaussian beams colliding head-on.
-It shows how the luminosity depends on the number of particles per bunch and the beam sizes \cite{concept_of_luminosity}.
+It shows how the luminosity depends on the number of particles per bunch and the beam sizes \cite{concept_of_luminosity}.\\
 
@@
 
-In order to evaluate the total number of events we use integrated luminosity,it is a measurement of the collected data size, and it is an important value to characterize the performance of an accelerator, defined as \cite{concept_of_luminosity}:
+In order to evaluate the total number of events we use integrated luminosity, it is a measurement of the collected data size, and it is an important value to characterize the performance of an accelerator, defined as \cite{concept_of_luminosity}:
 
@@
 
-Understanding luminosity with the best possible precision is crucial for physics analyses such as searches for new particles, rare processes, or measurements of known particle properties \cite{lumi_motiv}.
-The experimental techniques to determine signal rates are mature enough, where the understanding of acceptances, detector biases, reconstruction efficiencies, or background subtraction is at the sub-percent level, so that the final precision of the physics measurement is dominated by the luminosity uncertainty \cite{lumi_paper_def_and_concept}.
-Ultimately, the greater the precision of the luminosity measurement, the more physicists can understand their observations and delve into hidden corners beyond our current knowledge.
+Understanding luminosity with the best possible precision is crucial for physics analyses such as searches for new particles, rare processes, or measurements of known particle properties.
+The experimental techniques to determine signal rates are mature enough, where the understanding of acceptances, detector biases, reconstruction efficiencies, or background subtraction is at the sub-percent level, so that the final precision of the physics measurement is dominated by the luminosity uncertainty .
+Ultimately, the greater the precision of the luminosity measurement, the more physicists can understand their observations and delve into hidden corners beyond our current knowledge \cite{luminosity_importance}.
 
@@
 They are guided around the accelerator ring by a strong magnetic field maintained by superconducting electromagnets, these are built from coils of special electric cable that operates in a superconducting state, efficiently conducting electricity without resistance or loss of energy.
-This requires chilling the magnets to 271.3°C  a temperature colder than outer space \cite{LHC}.\\
+This requires chilling the magnets to -271.3°C  a temperature colder than outer space \cite{LHC}.\\
 
@@
 To begin with, hydrogen is ionized to produce protons, which are then accelerated in bunches up to 50 MeV within the Linear Accelerator 2 (LINAC2).
-Subsequently, these proton bunches are routed through three circular accelerators - the Booster, the Proton Synchrotron (PS), and the Super Proton Synchrotron (SPS)  in order to gradually increase their energy levels to 1.4 GeV, 26 GeV, and 450 GeV, respectively.
+Subsequently, these proton bunches are routed through three circular accelerators - the Booster, the Proton Synchrotron (PS), and the Super Proton Synchrotron (SPS)  in order to gradually increase their energy levels to 1.4 GeV, 26 GeV, and 450 GeV, respectively \cite{lhc_complex}.
 Following these pre-acceleration stages, the proton bunches are injected into the LHC ring where they are accelerated to reach energies of up to 7 TeV per bunch while circulating in opposite directions.
@@
 Since its inception in 2010 the LHC has undergone three runs and two lengthy shutdowns for maintenance and upgrades. 
-Run1 began in 2010 with proton-proton collisions at a center-of-mass energy of $\sqrt{s}=\text{7 TeV}$ and concluded in August 2012 at  $\sqrt{s}=\text{8 TeV}$\cite{LHC_status_2013}.
-Run 2, which took place at $\sqrt{s}=\text{13 TeV}$, was divided into two stages; the first  occurred from 2015 to 2016, and the second part  was carried out   from 2017 to 2018 \cite{pas_17,pas_18}, efforts are currently underway to further improve the precision of this run.
+Run1 began in 2010 with proton-proton collisions at a center-of-mass energy of $\sqrt{s}=\text{7 TeV}$ and concluded in 2012 at  $\sqrt{s}=\text{8 TeV}$.
+Run 2, which took place at $\sqrt{s}=\text{13 TeV}$, was divided into two stages; the first  occurred from 2015 to 2016, and the second part  was carried out   from 2017 to 2018, efforts are currently underway to further improve the precision of this run.
 Finally  Run3, which began in 2022 at $\sqrt{s}=\text{13.6 TeV}$ and is currently ongoing.
-This thesis project aims to contribute to the improvement of the precision of the luminosity for Run 3, where it is expected to obtain an approximate luminosity of $390 fb^{-1}$.
-\\
+This thesis project aims to contribute to the improvement of the precision of the luminosity for Run 3, where it is expected to obtain an approximate luminosity of $450 fb^{-1}$ \cite{
+hl-lhc}. \\
 
 The integrated luminosity for each of these runs and years, and their corresponding uncertainty values are presented in table \ref{lumi_values} (luminosity values includes the time from the start of stable beams until the beam is dumped by the LHC), also a visualization of these values measured with CMS is shown in Figure \ref{lumi_per_year_int}, which depicts the delivered luminosity versus time for each year.
-
+% ref. TDR Bril para los 390
+%separar por lumpas , poner  referencia, poner periodo en vez de Run
+%-  en incertidumbre  no conocida, dejar solamente 2022
 \begin{table}[h!]
@@
 \begin{tabular}{cccc}
-\textbf{Run} & \textbf{Energy $\sqrt{s}$} & \begin{tabular}[c]{@{}c@{}}\textbf{Integrated}\\\textbf{Luminosity}\end{tabular} & \textbf{Precision}    \\ 
+\textbf{Period} & \textbf{Energy $\sqrt{s}$} & \begin{tabular}[c]{@{}c@{}}\textbf{Integrated}\\\textbf{Luminosity}\end{tabular} & \textbf{Precision}    \\ 
 \toprule
-1(2010-2012) & 8 TeV           & $30 fb^{-1}$                                                                               & 2.5\%                 \\
-2(2015-2016) & 13 TeV          & $45.9 fb^{-1}$                                                                             & 1.3\%                 \\
-2(2017-2018) & 13 TeV          & $118 fb^{-1}$                                                                              & 2.5\%                 \\
-3(2022-2024) & 13.6 TeV        & \begin{tabular}[c]{@{}c@{}}$45 fb^{-1}$(current)\\$390 fb^{-1}$(expected)\end{tabular}                  & \begin{tabular}[c]{@{}c@{}}currently\\estimating  \end{tabular}\\
+Run 1(2010-2012) \cite{PCC_PAS_12_001} & 8 TeV                   & $30 fb^{-1}$                         & 2.5\%                 \\
+Run 2(2015-2016) \cite{lumi_precise_2015_2016} & 13 TeV   & $45.9 fb^{-1}$                     & 1.3\%                 \\
+Run 2(2017) \cite{pas_17} & 13 TeV                                                   & $49.8 fb^{-1}$                     & 2.5\%                 \\
+Run 2(2018) \cite{pas_18} & 13 TeV                                                  & $67.9 fb^{-1}$                      & 2.5\%                 \\
+Run 3(2022) \cite{wikicern} & 13.6 TeV                                            & $42 fb^{-1}$                        &      -                       \\
 \end{tabular}
@@
 \end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{comment}
-\begin{table}[h!]
-\begin{center}
-    \caption{Integrated luminosity values recorder by each Run}
-	\label{lumi_values2}
-\begin{tabular}{ccccc}
-\multicolumn{1}{l}{\textbf{Run}} & \textbf{Year} & \textbf{Energy $\sqrt{s}$} & \begin{tabular}[c]{@{}c@{}}\textbf{Integrated}\\\textbf{Luminosity}\end{tabular} & \textbf{Precision}    \\ 
-\toprule
-\multirow{3}{*}{1}               & 2010          & 7 TeV           & $45 pb^{-1}$                                                                                 & 2.5\%                 \\
-                                 & 2011          & 7 TeV           & $6.1 fb^{-1}$                                                                                & 2.4\%                 \\
-                                 & 2012          & 8 TeV           & $23.3 fb^{-1}$                                                                               & 2.5\%                 \\ 
-\hline
-\multirow{2}{*}{2}               & 2015          & 13 TeV          & $4.3 fb^{-1}$                                                                              & 1.6\%                 \\
-                                 & 2016          & 13 TeV          & $2.6 fb^{-1}$                                                                              & 1.2\%                 \\ 
-\hline
-\multirow{2}{*}{2}               & 2017          & 13 TeV          & $49.8 fb^{-1}$                                                                             & 2.3\%                 \\
-                                 & 2018          & 13 TeV          & $67.9 fb^{-1}$                                                                              & 2.5\%                 \\ 
-\hline
-\multirow{2}{*}{3}               & 2022          & 13.6 TeV        & $45 fb^{-1}$                                                                                & currently estimating  \\
-                                 & 2023          & 13.6 TeV        & currently recording                                                              & currently estimating 
-\end{tabular}
- \end{center}
-\end{table}
-\end{comment}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     \centering
-    \includegraphics[scale=.28]{Chapter1/int_lumi_per_year.png}
-    \caption[CMS Luminosity per year]{Delivered luminosity versus time for Run-1 (2010-2012)\cite{pas_17} and Run-2 (2015-2018)\cite{pas_18} and Run-3 that is still ongoing .
+    \includegraphics[scale=.35]{Chapter1/int_lumi_per_year.png}
+    \caption[CMS Luminosity per year]{Delivered luminosity versus time for Run-1 (2010-2012) and Run-2 (2015-2018) and Run-3 that is still ongoing .
 Cumulative luminosity versus day delivered to CMS during stable beams for pp collisions at nominal center-of-mass energy.

### 2023-05-03 tesis_Luis/Chapter4/chapter4.tex
updated

@@
 \item Ghost and Satellite.
-This correction corrects for the presence of spurious charges, which affect bunch currents.
-Satellite charges refer to additional charges outside the actual colliding bunch, while ghost charges refer to charge not in any nominally filled bunch slot.
-These results in corrections of up to 0.5\% to $\sigma_{vis}$.
+Corrects the presence of spurious charges, which affect bunch currents.
+Satellite charges refer to additional charges outside the actual colliding bunch, while ghost charges refer to charge not in any nominally filled bunch slot, these results in corrections of up to 0.5\% to $\sigma_{vis}$.
 The overall uncertaintys estimate the bunch current measurement  to be 0.4\%.
@@
 \item Orbit drift.
-The orbit drift correction accounts for potential movement of the LHC orbit during the vdM scans.
-Time-dependent changes of the transverse beam positions for fixed machine parameters can alter the beam separation.
-This correction is composed of two independent corrections:
+This correction accounts for potential movement of the LHC orbit during the vdM scans.
+Time-dependent changes of the transverse beam positions for fixed machine parameters can alter the beam separation, this correction is composed of two independent corrections:
 
-\begin{itemize}
+Orbit drift separation "ODS", correction that aims to correct for the orbit drift in the scanning direction and only affects beam separation and  Orbit drift rate "ODR", correction that aims to correct for the orbit drift in the direction orthogonal to the scanning direction and only affects the luminometer rate.
+%The derived correction assumes that the beam overlap has a single Gaussian shape. The correction reads the $\sigma_{vis}$ in the orthogonal direction from the previous correction.
 
-\item Orbit drift separation "ODS", correction that aims to correct for the orbit drift in the scanning direction and only affects beam separation.
-
-\item  Orbit drift rate "ODR", correction that aims to correct for the orbit drift in the direction orthogonal to the scanning direction and only affects the luminometer rate.
-The derived correction assumes that the beam overlap has a single Gaussian shape.
-The correction reads the $\sigma_{vis}$ in the orthogonal direction from the previous correction.
-\end{itemize}
-
-Applying this correction improves the agreement between the $\sigma_{vis}$ values derived with different scan pairs and changes the average $\sigma_{vis}$ by about 0.3\%.
-The full size of the correction is considered as uncertainty.
+Applying this correction improves the agreement between the $\sigma_{vis}$ values derived with different scan pairs and changes the average $\sigma_{vis}$ by about 0.3\%, considering the full size of the correction is as uncertainty.
 
@@
 
-\begin{itemize}
-
-\item Beam Beam deflection.
-Corrects Beam Beam deflection (BB) that happens during bunch crossings at the collision point.
+Beam Beam deflection (BB).
+Corrects Beam Beam deflection that happens during bunch crossings at the collision point.
 Accounts for the electrical repulsion of the beams, which increases the lateral separation.
@@
 
-\item Dynamic Beta.
+Dynamic Beta.
 The so-called dynamic $\beta^{*}$  effect, which accounts for any changes in the proton density distributions of the bunches due to the single-particle interactions.
 As a result, the non-linear change during separation steps in transverse bunch profiles is observed, and can described by the effective change of the $\beta^{*}$  value.
-\end{itemize}
+
 The corrections are calculated for each proton bunch pair individually, and the combined effect of the two corrections is an increase of $\sigma_{vis}$ by 1.0\%, with an uncertainty of 0.5\%.
@@
 \begin{equation}
-\chi^{2}(\theta)=\sum_{i=1}^{N} \frac{(y_{i}-\lambda(x_{i},\theta))^{2}}{\sigma_{i}^{2}}
+\chi^{2}(\theta)=\sum_{i=1}^{N} \frac{(y_{i}-f(x_{i},\theta))^{2}}{\sigma_{i}^{2}}
 \label{x^2}
@@
 
-where $N$ observed values $y_{1}$,···, $y_{N}$ are measured with errors $\sigma_{1}$,···,$\sigma_{N}$" at the values of $x$ given without error by $x_{1}$,..., $x_{N}$.
-The theoretical  value $\lambda_{i}$ of $y_{i}$ is given by a function $\lambda_{i} = \lambda(x_{i},\theta)$.
+where the observed values $y_{1}$,···, $y_{N}$ are measured with errors $\sigma_{1}$,···,$\sigma_{N}$" at the values of $x$ given without error by $x_{1}$,..., $x_{N}$.
+The theoretical  value is given by the function $f(x_{i},\theta)$.
 The value of $\theta$ is adjusted to minimize the value of $\chi^2$ \cite{Statistical_Data_Analysis}.
 
-After probe  several mathematical fit models, those requiring background subtraction from SS periods analysis were ultimately discarded due to the unacceptably high chi-square values obtained, this was due to the inconsistencies mentioned the section \ref{bkg}.
+After testing several mathematical fit models, those requiring background subtraction from SS periods analysis were ultimately discarded due to the unacceptably high chi-square values obtained, this was due to the inconsistencies mentioned the section \ref{bkg}.
 Therefore, it was decided to use functions that include a constant to model the background in the fit.
-The chosen model with the best fit quality and after applying all the corrections mentioned earlier, was a double Gaussian function plus a constant, referred to as "DG+Const":
-
+The chosen model with the best fit quality and after applying all the corrections mentioned earlier, was a double Gaussian function plus a constant:
+%https://gitlab.cern.ch/bril/VdMFramework/-/blob/main/src/plotting/capsigma_over_time.py#L90
+%\begin{equation}
+%DG+Const= C+P \cdot \Biggl[ F \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 \sigma_{1}^{2} } \Biggr) + (1-F) \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 \sigma_{2}^{2} } \Biggr) \Biggr] 
+%\end{equation}
 \begin{equation}
-DG+Const= C+P \cdot \Biggl[ F \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 \sigma_{1}^{2} } \Biggr) + (1-F) \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 \sigma_{2}^{2} } \Biggr) \Biggr] 
-\end{equation}
-
-\begin{equation}
-DG+Const= C+P \cdot \Biggl[ F \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2(\frac{\sigma\cdot R}{F \cdot R+1-F} )^{2} } \Biggr) + (1-F) \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 (\frac{\sigma}{F \cdot R+1-F} )^{2} } \Biggr) \Biggr]
+f(x)= C+P \cdot \Biggl[ F \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2(\frac{\Sigma\cdot R}{F \cdot R+1-F} )^{2} } \Biggr) + (1-F) \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 (\frac{\Sigma}{F \cdot R+1-F} )^{2} } \Biggr) \Biggr]
 \end{equation}
@@
 \item $P$ the $peak$ rate.
-\item $F$ is the weight between 0 and 1 of the first Gaussian in the sum.
+\item $F$ is the fraction of the peak rate attributed to the first Gaussian in the sum.
 \item $x$ is the beam position.
 \item $\bar{x}$ is the mean.
-\item $\sigma$ the standard deviation of the gaussian.
-\item $R$ is the Ratio $\sigma_{1}/\sigma_{2}$.
+\item $\Sigma$ is the overllap between the beams.
+\item $R$ is the ratio between the standard deviations of the  Gaussians (first over the second).
 \end{itemize}
 
-Figure \ref{vdM1_282_XYscan} shows the fit graphs of the first vdM scan pair for BCID 282 where  all the corrections described in the previous section have been applied and where  rates are normalized by the beam currents ($R(0,0)/N_{1}N_{2}$), which is according of Eq.
+Figure \ref{vdM1_282_XYscan} shows the fit graphs of the first vdM scan pair for BCID 282 where  all the corrections described in the previous section have been applied and where  rates are normalized by the beam currents ($N_{1}N_{2}$), which is according of Eq.
 \ref{sigmavis_eq}.
@@
 \includegraphics[width=.40\textwidth]{Chapter4/yscan.png}\\
-\caption[vdM1 BCID 282]{Normalized rates and the resulting fitted curves with the DG+Const fit model as a function of the beam separation ($\Delta$) for BCID 282 for X (left) and Y (right) scan for the first vdM scan.}
+\caption[vdM1 BCID 282]{Normalized rates and the resulting fitted curves with  fit model as a function of the beam separation ($\Delta$) for BCID 282 for $x$ (left) and $y$ (right) scan for the first vdM scan.}
 \label{vdM1_282_XYscan}
@@
     \caption[chi2/ndof for all scan pairs]{ chi2/ndof for all the scan pairs.
-where the red dots represent the X scans, and the blue dots represent the Y scans.
+where the red dots represent the $x$-scans, and the blue dots represent the $y$-scans.
 It is important to note that in each scan, the BCIDs follow the same order, which is 282, 822, 2944, 3123, and 3302.}
@@
 
-To compute $\sigma_{vis}$, the CapSigma $\Sigma_{x,y}$ and $Peak$ values have been extracted, the behavior of these values ​​for all scans pair are shown in the  Figure \ref{capsigma_peak} where those belonging to the scan in $x$ are presented in red and those belonging to the scan in $y$ are shown in blue.\\
+To compute $\sigma_{vis}$, the $\Sigma_{x,y}$ and $peak_{x,y}$ values have been extracted, the behavior of these values ​​for all scans pair are shown in the  Fig.
+\ref{capsigma_peak} (left) for $\Sigma_{x,y}$ and Fig.
+\ref{capsigma_peak} (right) for the $peak_{x,y}$ values , where those belonging to the scan in $x$ are presented in red and those belonging to the scan in $y$ are shown in blue.\\
 
-The values of $\Sigma_{x,y}$, which represent the standard deviation in the fit, provide a direct measurement of the beam shape, as we can seen in the plot for $\Sigma_{x,y}$  these values decrease in both the $x$ and $y$ directions during the fill time, this is due to a phenomenon called "damping" which causes the beam to gradually focus with time.
-On the other hand the values ​​for the peak in figure \ref{capsigma_peak} (right) are then a direct consequence of this, since a more focused beam means more collisions and thus a higher rate.\\
+The values of $\Sigma_{x,y}$ wish provide a direct measurement of the beam shape show a decrease in both the $x$ and $y$ directions during the fill time, this is due to a phenomenon called "damping", which occurs due to the interaction between the particles in the beam and the electromagnetic fields in the LHC ring, these fields exert a force on the particles, causing them to lose energy and amplitude, which causes the beam to gradually focus with time.
+On the other hand the values ​​for the $peak$ are then a direct consequence of this effect, since a more focused beam means more collisions and thus a higher rate.\\
 
-The figure also displays a sharp decline in values between the BI2 and vdM3 scans, which can be attributed to the exclusion of the vdM2 scan for the reasons mentioned in the section \ref{data} .
+The figure also displays a discontinuity in values between the BI2 and vdM3 scans, which can be attributed to the exclusion of the vdM2 scan for the reasons mentioned in the section \ref{data} .
 
@@
     \includegraphics[width=.48\textwidth]{Chapter4/DGConst_peak.png}
-    \caption[$\Sigma_{x,y}$ and peak values for all scan pairs]{$\Sigma_{x,y}$ (left) and Peak values (right) extracted from the fitted graph to compute $\sigma_{vis}$, where the red dots represent the X scans, and the blue dots represent the Y scans, note that in each scan, the BCIDs follow the same order, which is 282, 822, 2944, 3123, and 3302.}
+    \caption[$\Sigma_{x,y}$ and peak values for all scan pairs]{$\Sigma_{x,y}$ (left) and peak values (right) extracted from the fit to compute $\sigma_{vis}$, where the red dots represent the $x$-scans, and the blue dots represent the $y$-scans, note that in each scan, the BCIDs follow the same order, which is 282, 822, 2944, 3123, and 3302.}
     \label{capsigma_peak}
@@
 
-The $\sigma_{vis}$ for all BCID's (vdM and BI scans) is then computed from the fit results $\Sigma_{x,y}$ and $peak_{x,y}$ shown above, this is done using the Eq.
+The $\sigma_{vis}$ for all BCIDs (vdM and BI scans) is then computed from the fit results $\Sigma_{x,y}$ and $peak_{x,y}$ shown above, this is done using the Eq.
 \ref{sigmavis_eq}.
-The value of $R(0,0)$ is obtained through a specific correction where the rate is taken from the higher value between the scans $x$ and $y$.
-The difference in these rates values is attributed to the fact that some scans are not centered on the axes.
-After this correction, the final peak, which has already been normalized, is obtained.
+The value of $R(0,0)$ is obtained is obtained by taking the average of the peaks in the $x$ and $y$ scans, which has already been normalized.
 As a result, Equation \ref{sigmavis_eq} is rewritten as:
@@
 \begin{equation}
- \sigma_{vis}= 2\pi \Sigma_{x} \Sigma_{y}Peak
+ \sigma_{vis}= 2\pi \Sigma_{x} \Sigma_{y} \Biggl( \frac{peak_{x}+peak_{y}}{2} \Biggr)
  \end{equation}
 
-Figure \ref{sigmavis_perbcid} shows the  value of sigma visible $\sigma_{vis}$ per BCID for all the scans where the error on $\sigma_{vis}$ is assigned as:
+Figure \ref{sigmavis_perbcid} shows the  value of $\sigma_{vis}$ per BCID for all the scans where the error on $\sigma_{vis}$ is assigned as:
 
 \begin{equation}
-\sigma_{vis\text{Err}}= 2 \pi \sqrt{ (\Sigma_{y} \cdot Peak \cdot \Sigma_{x\text{Err}})^{2} + (\Sigma_{x} \cdot Peak \cdot \Sigma_{y \text{Err}})^{2} + (\Sigma_{x} \Sigma_{y} Peak_{\text{Err}})^{2} }
+\sigma_{vis\text{Err}}= 2 \pi \sqrt{ (\Sigma_{y} \cdot P \cdot \Sigma_{x\text{Err}})^{2} + (\Sigma_{x} \cdot P \cdot \Sigma_{y \text{Err}})^{2} + (\Sigma_{x} \Sigma_{y} P_{\text{Err}})^{2} }
 \end{equation}
@@
     \includegraphics[scale=.22]{Chapter4/DGConst_xsec.png}
-    \caption[$\sigma_{vis}$ per BCID for all scans]{ $\sigma_{vis}$ per BCID for all the scans,  in each scan, the BCID's follow the same order, which is 282, 822, 2944, 3123, and 3302.}
+    \caption[$\sigma_{vis}$ per BCID for all scans]{ $\sigma_{vis}$ per BCID for all the scans,  in each scan, the BCIDs follow the same order, which is 282, 822, 2944, 3123, and 3302.}
     \label{sigmavis_perbcid}
@@
 In both calcuation, it is assumed that there is no correlation between the BCIDs and the scans.
-Therefore, the computation of the weighted average and the error is assigned as follows:
+Therefore, the computation of the weighted average and the total error  follows Equations \ref{average} and \ref{error} respectively, where the weight is assigned as $w_{i} = 1/\sigma_{visErr}^{2}$.
 
 \begin{eqnarray}
-\sigma_{visErrTotal}=\frac{1}{\sqrt{ \displaystyle\sum_{\textbf{i}} \frac{1}{\sigma_{vis\textbf{i}Err}^{2}}}}
+\sigma_{vis}^{Avg}=\Biggl(\displaystyle\sum_{i} w_{i}\sigma_{vis}^{i} \Biggr)\Biggl(\sqrt{ \displaystyle\sum_{i} w_{i}} \Biggr)^{-2}
+\label{average}
+\end{eqnarray}
+
+\begin{eqnarray}
+\sigma_{vis,Err}^{Avg}=\frac{1}{\sqrt{ \displaystyle\sum_{i} w_{i}}} 
 \label{error}
@@
 
-\begin{eqnarray}
-\sigma_{vis}=\Biggl(\displaystyle\sum_{\textbf{i}} \frac{\sigma_{vis\textbf{i}}}{\sigma^{2}_{vis\textbf{i}Err}} \Biggr)(\sigma_{visErrTotal})^{2}
-\label{average}
-\end{eqnarray}
-After completing the calibration procedure, the final result obtained is:
+The final result obtained is:
 \begin{equation}
-\sigma_{vis}=4163.34 \pm 3.30 \text{ (stat)  mb}
+\sigma_{vis}=4163.3 \pm 3.3 \text{ (stat)  mb}
 \end{equation}
@@
 
-As shown in figure \ref{sigmavis_perscan}, the scans exhibit an RMS of $12882 \mu b$ for the values of visible sigma.
-Among them, vdM1 and vdM3 demonstrate the largest variations, approximately 2 standard deviations away from the mean.
-These variations can be attributed to the presence of systematic effects during the scans.
+As depicted in Figure \ref{sigmavis_perscan}, the scans demonstrate an RMS of $12.8 \text{ mb}$ for the $\sigma_{vis}$ values, which is larger than the statistical uncertainty.
+Notably, vdM1 and vdM3 exhibit the largest variations, deviating by approximately 2 standard deviations from the mean.
+These discrepancies can be attributed to systematic effects in the detector during the scans.
+Given that other luminometers display a similar trend, this could be due to a common systematic effect such as beam position or beam current $(N_{1}*N_{2})$.
+A study of the sources of systematic uncertainty will be performed in the future.
+In this work, we assign the RMS value as an estimate of the systematic uncertainty.

### 2023-05-05 tesis_Luis/Chapter2/chapter2.tex
updated

@@
-\chapter{Experiment Description }
-
+\chapter{Experiment Description}
 Modern general-purpose detectors used in high-energy colliders typically employ cylindrical detection layers arranged around the beam axis.
@@
 The CMS is designed for a broad physics program that includes studying the Standard Model.
-This chapter provides a description of the various components of the CMS detector,incliding the several systems to measure the luminosity with a particular focus on the silicon pixel tracker, which is described in greater detail due to its relevance to the thesis.
+This chapter provides a description of the various components of the CMS detector, including the several systems to measure the luminosity with a particular focus on the silicon pixel tracker, which is described in greater detail due to its relevance to the thesis.
 
@@
 Additionally, there is an excellent muon tracking system.
-A schematic representation of the CMS detector is shown in \ref{detector_CMS}.
+A schematic representation of the CMS detector is shown in Fig.
+\ref{detector_CMS}.
 
@@
 As a charged particle passes through a Tracker layer, it interacts electromagnetically with the silicon and produces a hit.
-By combining these individual hits, the track of the traversing particle can be identified.
-Further details about the tracker system can be found in the next section.
-\cite{CMS_Exp_2008}\\
+By combining these individual hits, the track of the traversing particle can be identified \cite{CMS_Exp_2008}.
+Further details about the tracker system can be found in the next section.\\
 
@@
     \includegraphics[scale=.3]{Chapter2/slice_det.png}
-    \caption[Transverse slice fo CMS detector]{Transverse slice of the CMS detector with some particle interactions (from the beam interaction region to the muon detector).  \cite{det_summary}.}
+    \caption[Transverse slice view of the CMS detector]{Transverse slice of the CMS detector with some particle interactions (from the beam interaction region to the muon detector) \cite{det_summary}.}
     \label{slice_CMS}
@@
 In this system, the azimuthal angle $\varphi$ is measured from the $x$-axis within the $x-y$ plane, while the radial coordinate in this plane is represented by $r$.
-Furthermore, the polar angle $\theta$ is measured with respect to the z-axis \cite{CMS_Exp_2008}.
+Furthermore, the polar angle $\theta$ is measured with respect to the z-axis, seudorapidity is defined as $\eta = − ln tan(\theta/2)$ \cite{CMS_Exp_2008}.
 
@@
 The PCC measurement uses the data collected with the standard CMS trigger system with triggers requiring colliding bunches but not any specific event activity, known as "zero-bias" triggers.
-Finally, the RAMSES detectors are part of the LHC environmental protection and monitoring systems, but they can also be used to provide a luminosity measurement readout through Timber(operational data and LHC logging service) \cite{pas_18}.
-A brief overview of the CMS luminometers is provided below:\\
+Finally, the RAMSES detectors are part of the LHC environmental protection and monitoring systems, but they can also be used to provide a luminosity measurement readout through Timber (operational data and LHC logging service) \cite{pas_18}.
+A brief overview of the CMS luminometers is provided below.\\
 
 PLT Is a dedicated system for measuring luminosity using silicon pixel sensors.
-There are a total of 48 sensors arranged into 16 “telescopes”,eight at either end of CMS outside the pixel endcap, where each telescope contains three sensor planes arranged nearly parallel to the beam pipe.
+There are a total of 48 sensors arranged into 16 “telescopes”, eight at either end of CMS outside the pixel endcap, where each telescope contains three sensor planes arranged nearly parallel to the beam pipe.
 The PLT measures the rate of “triple coincidences”, where a hit is observed in all three planes, typically corresponding to a track from a particle originating at the interaction point.
 The overall mean rate for PLT  is estimated using the zero-counting method, where it is assumed that the number of observed triple coincidences follows a Poisson distribution \cite{pas_18}.
+\\
 
-BCM1F comprises a total of 24 sensors mounted on the same carriage as the PLT, consisting of 10 silicon sensors, 10 polycrystalline diamond (pCVD) sensors, and 4 single-crystal diamond (sCVD) sensors.The BCM1F readout features a fast readout with 6.25 ns time resolution; the precise time measurement, in conjunction with the position of BCM1F 1.8 m from the center of CMS, allows hits from collision products to be separated from hits from machine-induced background, because the incoming background is separated in time from the outgoing collision products  \cite{pas_18}.\\
+BCM1F for Run 2 comprised a total of 24 sensors mounted on the same carriage as the PLT, consisting of 10 silicon sensors, 10 polycrystalline diamond (pCVD) sensors, and 4 single-crystal diamond (sCVD) sensors.
+The BCM1F readout features a fast readout with 6.25 ns time resolution; the precise time measurement, in conjunction with the position of BCM1F at 1.8 m from the center of CMS, allows hits from collision products to be separated from hits from machine-induced background, because the incoming background is separated in time from the outgoing collision products  \cite{pas_18}.\\
 
-HF luminosity measurement uses a dedicated readout system installed in the HF calorimeter.
+HF luminosity measurement uses a dedicated readout system installed in the HF ccalorimeter readout electronics.
 Only two HF rings are used for luminosity measurement to ensure relatively uniform occupancy.
@@
 
-Drift tube luminosity (DT), which uses the rate of muon track stubs in the muon barrel track finder and  RAMSES detectors, a CERN radiation and environmental monitoring system, although not designed as a luminometer, function quite well as a luminosity measurement, using the rate observed in the detectors (primarily photons within the energy range of 50 keV to 7 MeV) \cite{pas_18}.\\
+DT luminosity measurement uses the rate of muon track stubs in the muon barrel track finder.
+The DT algorithm used does not provide bunch-by-bunch measurements and is thus applicable only for the total luminosity measurement.
+DT measurement is generally  stable and linea so it provides a complementary offline reference measurement.
+The rate in DT during VdM fills is too low to allow for calibration using the vdM scan, so it is cross-calibrated to another detector \cite{pas_18}.\\
 
-RAMSES.
+RAMSES  is a CERN radiation and environmental monitoring sytem.
 Althoug is not designed as a luminometer, the rate observed in this detector does function quite well as a luminosity measurement.
-RAMSES is a CERN radiation and environmental monitoring sytem, currently a part of the REMUS supervisory system.
 The sensor itself is a cylindrical plastic ionization chamber filled with 3 L of air at atmospheric ressure and it primarily detects photons.
-The overall rate in the RAMSES detectors is small, which means that it is not capable of making bunch-by-bunch measurements and cannot be independently calibrated using a VdM scan; however, this also means it is less affected by issues such as instability caused by radiation damage or nonlinearity \cite{pas_18}.\\
+The overall rate is small, which means that it is not capable of making bunch by bunch measurements and cannot be independently calibrated using a vdM scan; however, this also means it is less affected by issues such as instability caused by radiation damage or nonlinearity \cite{pas_18}.\\
 
@@
     \includegraphics[scale=.3]{Chapter2/detectors.png}
-    \caption[CMS Luminometers]{The seven luminometers that make up the CMS luminosity measurement system.
+    \caption[Layout of the luminometers in the CMS detector]{The seven luminometers that make up the CMS luminosity measurement system.
 Multiple independent systems used online: BCM1F, HFET, HFOC, PLT (independently calibrated) ,REMUS and  DT (cross-calibrated) , Pixel cluster counting is used after offline processing.}
@@
 It has a total physical size of 5.8 m in length and 2.5 m in diameter.
-The CMS tracking detector relies on semiconductor technology, this is divided in two systems, the pixel detector and the Strip tracker \cite{CMS_Exp_2008}.In Figure \ref{strip_layout}, we can observe the pixel detector at the center, surrounded by the Strip tracker.\\
+The CMS tracking detector relies on semiconductor technology, this is divided in two systems, the pixel detector and the Strip tracker \cite{CMS_Exp_2008}.
+In Figure \ref{strip_layout}, we can observe the pixel detector at the center, surrounded by the Strip tracker.\\
 
@@
 This component comprises a total of 70 million pixels and extends the tracker's acceptance up to a pseudorapidity of $|\eta| < 2.5$.
-Additionally, the active silicon area of this component covers approximately 200 $m^2$.
 More information about this detector is provided in the following section.
@@
     \includegraphics[scale=.23]{Chapter2/strip_layout.png}
-    \caption[Schematic cross section through the CMS tracker]{Schematic cross section through the CMS tracker. Each line represents a detector module \cite{CMS_Exp_2008}.}
+    \caption[Schematic cross section through the CMS tracker]{Schematic cross section through the CMS tracker \cite{CMS_Exp_2008}.}
     \label{strip_layout}
@@
 The silicon pixel detector  forms the innermost component of the tracking system.
-This detector facilitates the provides  3-dimensional space points in the area nearest to the interaction point, which, in turn, enables precise tracking of charged particles and vertex reconstruction.
-The pixel detector operates in a radiation-rich environment, marked by high track density \cite{phase1_Pixel_Detector}.\\
+This detector facilitates the provides complete spatial coverage over the area nearest to the interaction point, which, in turn, enables precise tracking of charged particles and vertex reconstruction.
+The coverage of the pixel detector is in the pseudorapidity range $(|\eta| < 2.5)$, operating in a radiation rich environment, marked by high track density \cite{phase1_Pixel_Detector}.\\
 
 The CMS pixel detector encompasses four concentric barrel layers (L1-L4), each with radii measuring 29, 68, 109, and 160 mm, and three disks (D1-D3) on either end positioned at distances of 291, 396, and 516 mm from the detector's center.
-A schematic of the CMS Phase-1 pixel detector's arrangement is depicted in Figure \ref{phase1_pixel_detector} where the total silicon area spans 1.9 $\text{m}^{2}$.
+The complete detector is built from 1856 segmented silicon sensor modules.\\
 
+A schematic of the CMS Phase-1 pixel detector's arrangement is depicted in Figure \ref{phase1_pixel_detector} where the total silicon area spans 1.9 $\text{m}^{2}$, here The BPIX and FPIX detectors are equipped with four service half-cylinders each, with a combined length of 540 mm.
+These cylinders host the readout and control circuits, and provide guidance for the power lines and cooling tubes of the detector.
 \begin{center}
@@
 
-The BPIX and FPIX detectors are equipped with four service half-cylinders each, with a combined length of 540 mm.
-These cylinders host the readout and control circuits, and provide guidance for the power lines and cooling tubes of the detector.
-%  cambiar a otra palabras ..The BPIX detector is bifurcated into two mechanically self-sufficient halves, both of which are made up of a half detector and two service half-cylinders.
-The orientation of the sensor surface of the modules in both halves is parallel to the magnetic field.
+The BPIX detector is bifurcated into two mechanically self-sufficient halves, both of which are made up of a half detector and two service half-cylinders.
+BPIX is built in total from 1184 segmented silicon sensor modules where the orientation of their surface  in both halves is parallel to the magnetic field.\\
 
-%% separadas
 On the other hand, the FPIX detector is segmented into four mechanically independent quadrants, each of which comprises three half-disks housed in a service half-cylinder.
 The sensor orientation in the FPIX detector is arranged such that the long side of the pixel is aligned with the radial direction.
-The half-disks are additionally subdivided into inner and outer half-rings that support 22 and 34 modules, respectively \cite{phase1_Pixel_Detector}.\\
+FPIX is built in total from 672 segmented silicon sensor modules and the half-disks are additionally subdivided into inner and outer half-rings that support 22 and 34 modules, respectively \cite{phase1_Pixel_Detector}.\\
 
-The pixel detector is built from 1856 segmented silicon sensor modules, where 1184 modules are used in the BPIX and 672 modules are used for the FPIX.
-Each module consists of a sensor with 160$\times$416 pixels connected to 16 readout chips (ROCs).
-In total there are 124 million readout channels \cite{phase1_Pixel_Detector}.
-A pixel detector module is built from a planar silicon sensor with a size of 18.6 $\times$ 66.6 $\text{mm}^{2}$ (active area of 16.2 $\times$ 64.8 $\text{mm}^{2}$), bump-bonded to an array of 2$\times$8 ROCs.
-Each ROC is segmented into 4160 readout channels and reads out the pulse height information for each pixel.
-The standard pixel size is 100$\times$150 $\mu m^{2}$, as in the original pixel detector.
-The figures depicting the modules of the CMS Phase-1 pixel detector can be found in Figure \ref{modules_drawing} \cite{phase1_Pixel_Detector}.
+A pixel detector module is built from a planar silicon sensor with a size of 18.6 $\times$ 66.6 $\text{mm}^{2}$ (active area of 16.2 $\times$ 64.8 $\text{mm}^{2}$).
+Each module consists of a sensor with 160$\times$416 pixels  bump-bonded to an array of 2$\times$8 readout chips (ROC's).
+Each ROC is segmented into 4160 readout channels and reads out the pulse height information for each pixel, in total there are 124 million readout channels.
+The standard pixel size is 100$\times$150 $\mu m^{2}$\\
+
+Figure \ref{modules_drawing} illustrates the modules of the CMS Phase-1 pixel detector \cite{phase1_Pixel_Detector}, while Figure \ref{module and hit} on the left depicts the layout of the silicon sensor connected to the readout chip.
+On the right side of Figure \ref{module and hit}, a charged particle can be seen passing through a pixel, providing enough energy to eject electrons from the silicon atoms.
+A voltage applied to the sensor allows the collection of these charges as a small electric signal, which is then amplified by an electronic readout chip.
 
@@
     \includegraphics[scale=.2]{Chapter2/modules_drawing.png}
-    \caption[Pixel detector modules]{ Drawings of the pixel detector modules for BPIX L1 (left), BPIX L2–4 (middle), and the FPIX detector (right)\cite{phase1_Pixel_Detector}.}
+    \caption[Types of modules in the pixel detector]{ Drawings of the pixel detector modules for BPIX L1 (left), BPIX L2–4 (middle), and the FPIX detector (right)\cite{phase1_Pixel_Detector}.}
     \label{modules_drawing}
+  \end{figure}
+\end{center}
+
+\begin{center}
+  \begin{figure}[h]
+    \centering
+    \includegraphics[scale=.3]{Chapter2/PixelSensor.png} \includegraphics[scale=.3]{Chapter2/hit.png}
+    \caption[Schematic view of a pixel sensor and its connection to the readout channels]{ left: layout pixel sensor conected to a readout chip , right: hits detection in a corresponding  pixel sensor \citep{thomson_2013}.
+}
+    \label{module and hit}
   \end{figure}
@@
 Next, the cluster positions and their uncertainties are estimated in a local orthogonal coordinate system  in the plane of each sensor \cite{Track_Reco_2014}.
-%The pixel sensor used in this process consists of 100 $\times$ 150$\mu \text{m}^{2}$ pixels  this is shown en the figure \ref{module and hit}. 
-%% cambiar imagen para arriba
+\\
+
+To be considered a valid cluster, each one must have a minimum charge equivalent to 4000 electrons \cite{Track_Reco_2014,phase1_Pixel_Detector}.
+For normally incident minimum-ionizing particles (MIPs) in a silicon sensor with a thickness of 285 $\mu \text{m}$, the most probable value of energy deposition corresponds to approximately 21,000 electrons.
+However, this charge is often spread over more than one pixel due to Lorentz drift,  which causes the electrons to be pushed due to the force generated by the electromagnetic field, leading to charge clusters.\\
+
+Figure \ref{cluster}  shown an example of how a pixel cluster is constructed.
+Each square in the figure represents a pixel.
+The red pixels indicate that they have the required charge up to 2000 electrons to be considered valid pixels and are therefore included in the cluster.
+On the other hand, the green pixels correspond to charge depositions below the 2000 electron threshold and are not included in the cluster.
+The dotted blue line in the figure represents the trajectory of the particle traveling parallel to the x-z plane.
+As it travels, it activates pixels in its path precisely, as well as pixels that are deviated from its trajectory due to the Lorentz drift \cite{Pixel_Hit_Reconstruction}.\\
+\newpage
 \begin{center}
@@
     \centering
-    \includegraphics[scale=.3]{Chapter2/PixelSensor.png} \includegraphics[scale=.3]{Chapter2/hit.png}
-    \caption[PixelSensor]{ left: Pixel sensor diagram, right: hits detection in a corresponding  pixel sensor \citep{thomson_2013}. }
-    \label{module and hit}
-  \end{figure}
-\end{center}
-
-To be considered a valid cluster, each one must have a minimum charge equivalent to 4000 electrons \cite{Track_Reco_2014,phase1_Pixel_Detector}.
-For normally incident minimum-ionizing particles (MIPs) in a silicon sensor with a thickness of 285 $\mu \text{m}$, the most probable value of energy deposition corresponds to approximately 21,000 electrons.
-However, this charge is often spread over more than one pixel due to Lorentz drift and diffusion of collected electrons, leading to charge clusters.\\
-
-Figure \ref{cluster} is shown a pixel cluster example at $\eta$ = 1.83, here the  charge deposition in each pixel is shown in thousands of electrons, the numbers shown in green correspond to charge depositions below the 2000 electron threshold which are not included in the cluster.
-The dotted red line indicates the particle trajectory projection in the module plane and the red cross shows the true hit position.
-Where the corresponding coordinate systems is based in the  geometry of the CMS barrel and forward pixel detectors \cite{Pixel_Hit_Reconstruction}.
-%% quitar el detector
-%%  usar clusters clasicos
-
-\begin{center}
-  \begin{figure}[h]
-    \centering
-    \includegraphics[scale=.3]{Chapter2/pixel_cluster.png} 
-    \caption[Pixel cluster]{ Left: Geometry of the CMS barrel and forward pixel detectors and the corresponding coordinate systems. Right: A pixel cluster example at $\eta$ = 1.83 }
+    \includegraphics[scale=.25]{Chapter2/pixel_cluster.png} 
+    \caption[Construction of a pixel cluster]{ The figure illustrates a pixel cluster example with a total charge up of 4,000 electrons, required to be a valid cluster.
+The red pixels have the required charge while the green one does not.}
     \label{cluster}

### 2023-05-05 tesis_Luis/Chapter4/chapter4.tex
updated

@@
     \includegraphics[scale=.35]{Chapter4/2022Scanprorgam.png}
-    \caption[2022 scan program]{Nominal horizontal and vertical positions of the proton beams during LHC fill 8381, showing the four standard vdM scans, two BI scans, one LS scan and the two Super Separation Periods (SS)}
+    \caption[2022 vdM scan program]{Nominal horizontal and vertical positions of the proton beams during LHC fill 8381, showing the four standard vdM scans, two BI scans, one LS scan and the two Super Separation Periods (SS)}
     \label{scan_prog}
@@
 To illustrate this process for each BCID, the distribution or profile of PCC per NB4 for each SS period is plotted.
-Figure \ref{ss1_hist_282} displays the PCC per NB4 distribution for SS period I specifically for BCID 282, but the same plot is created for every BCID.\\
+Figure \ref{ss1_hist_282} displays the PCC per NB4 distribution for SS period I, specifically for BCID 282, but the same plot is created for every BCID.\\
 
@@
     \centering
-    \includegraphics[scale=.18]{Chapter4/ss1_histo_bx282.png}
+    \includegraphics[scale=.30]{Chapter4/ss1_histo_bx282.png}
     \caption[PCC per NB4 profile for BCID 282 from SS period I]{ PCC per NB4 profile for BCID 282 from SS period I.} 
@@
   \begin{center}
-    \caption{Mean and standard error on mean (SEM) for the PCC background estimated with the SS1 and SS2 data, separately for all five BCIDs and averaged.}
+    \caption[Background values for the two super separation periods]{Mean and standard error on mean (SEM) for the PCC background estimated with the SS1 and SS2 data, separately for all five BCIDs and averaged.}
     \label{ss_per_bx}
@@
 \centering
-\includegraphics[width=.40\textwidth]{Chapter4/xscan.png}
-\includegraphics[width=.40\textwidth]{Chapter4/yscan.png}\\
-\caption[vdM1 BCID 282]{Normalized rates and the resulting fitted curves with  fit model as a function of the beam separation ($\Delta$) for BCID 282 for $x$ (left) and $y$ (right) scan for the first vdM scan.}
+\includegraphics[width=.45\textwidth]{Chapter4/xscan.png}
+\includegraphics[width=.45\textwidth]{Chapter4/yscan.png}\\
+\caption[Fit for the vdM1 BCIDs 282 (x and y directions)]{Normalized rates and the resulting fitted curves with  fit model as a function of the beam separation ($\Delta$) for BCID 282 for $x$ (left) and $y$ (right) scan for the first vdM scan.}
 \label{vdM1_282_XYscan}
@@
     \centering
-    \includegraphics[scale=.025]{Chapter4/DGConst_chi2.png}
-    \caption[chi2/ndof for all scan pairs]{ chi2/ndof for all the scan pairs.
+    \includegraphics[scale=.030]{Chapter4/DGConst_chi2.png}
+    \caption[$\chi^{2}$/ndof per BCID for all scan pairs]{ chi2/ndof for all the scan pairs.
 where the red dots represent the $x$-scans, and the blue dots represent the $y$-scans.
@@
     \includegraphics[width=.48\textwidth]{Chapter4/DGConst_peak.png}
-    \caption[$\Sigma_{x,y}$ and peak values for all scan pairs]{$\Sigma_{x,y}$ (left) and peak values (right) extracted from the fit to compute $\sigma_{vis}$, where the red dots represent the $x$-scans, and the blue dots represent the $y$-scans, note that in each scan, the BCIDs follow the same order, which is 282, 822, 2944, 3123, and 3302.}
+    \caption[$\Sigma_{x,y}$ and peak values per BCID for all scan pairs]{$\Sigma_{x,y}$ (left) and peak values (right) extracted from the fit to compute $\sigma_{vis}$, where the red dots represent the $x$-scans, and the blue dots represent the $y$-scans, note that in each scan, the BCIDs follow the same order, which is 282, 822, 2944, 3123, and 3302.}
     \label{capsigma_peak}
@@
 \begin{eqnarray}
-\sigma_{vis}^{Avg}=\Biggl(\displaystyle\sum_{i} w_{i}\sigma_{vis}^{i} \Biggr)\Biggl(\sqrt{ \displaystyle\sum_{i} w_{i}} \Biggr)^{-2}
+\sigma_{vis}^{Avg}=\Biggl(\displaystyle\sum_{i} w_{i}\sigma_{vis}^{i} \Biggr)\Biggl( \displaystyle\sum_{i} w_{i} \Biggr)^{-1}
 \label{average}
@@
     \includegraphics[scale=0.45]{Chapter4/xsec_perscan_v2.png}
-    \caption[$\sigma_{vis}$ per Scan]{ $\sigma_{vis}$  per scan.} 
+    \caption[$\sigma_{vis}$ average per scan and final result]{ $\sigma_{vis}$  per scan.} 
     \label{sigmavis_perscan}

### 2023-06-16 tesis_Ashish/Abstract/abstract.tex
Your commit message

\begin{abstract}
\begin{center}
    {\huge Abstract}
\end{center}

The Pixel Cluster Counting (PCC) luminosity measurement method has emerged as a reliable offline technique for luminosity measurement during LHC run periods. The PCC method is based on the rate of pixel clusters in the CMS pixel detector, which is the innermost part of the CMS tracker. PCC is studied for its stability and accuracy in luminosity measurements using 2018 AlCa Reco datasets. The results of these studies demonstrate that the PCC luminosity measurement method is stable and accurate, able to achieve ??\% systematic uncertainty on the final luminosity measurement for Run 2 data. Moreover, the algorithms and optimization for the Phase II High Luminosity LHC (HL-LHC) luminosity measurement are also developed, using the Tracker Endcap Pixel Detector (TEPX). This detector is expected to provide excellent statistical and linearity performance, which is essential for accurate luminosity measurements at the HL-LHC. The TEPX detector will replace the upgraded Phase I pixel detector and is expected to provide even higher precision luminosity measurement.

\end{abstract}

### 2023-06-16 tesis_Ashish/Acknowledgement/acknowledgement.tex
Your commit message

I would like to express my sincere gratitude to all those who have supported and guided me throughout my journey in completing my PhD thesis in particle physics, specifically focusing on the CMS experiment at CERN. Their unwavering support, encouragement, and expertise have been invaluable to my success.

First and foremost, I would like to extend my deepest appreciation to my esteemed thesis supervisor, Dr. Jose Feliciano Benitez. His exceptional guidance, profound knowledge, and unwavering commitment to scientific exploration have shaped my research endeavors and allowed me to delve into the fascinating world of particle physics. His mentorship and continuous support have been instrumental in every step of my thesis, from conceptualization to the final stages of completion. I am truly grateful for the opportunity to work under his supervision, and I have grown immensely both as a researcher and as an individual thanks to his invaluable guidance.

I would also like to express my heartfelt gratitude to my loving parents, whose unconditional love, encouragement, and sacrifices have been the cornerstone of my academic journey. Their unwavering belief in my abilities and their constant support have given me the strength and motivation to overcome challenges and pursue my passion for scientific exploration. I am eternally grateful for their constant presence in my life and their unwavering support throughout this demanding academic endeavor.

Furthermore, I would like to extend my appreciation to my sisters for their unwavering encouragement, understanding, and motivation during the course of my PhD. Their belief in my abilities and their continuous support have been an immense source of inspiration and strength, reminding me to remain focused and determined even during the most challenging times.

I would also like to acknowledge the collective efforts of the scientific community at CERN and all those who have contributed to the CMS experiment. Their collaboration, expertise, and dedication have created an enriching environment for research and have allowed me to be a part of groundbreaking discoveries in the field of particle physics.

Lastly, I am deeply grateful to all my friends and colleagues who have provided valuable insights, stimulating discussions, and endless support throughout this journey. Their encouragement, camaraderie, and intellectual exchanges have played a significant role in shaping my research and personal growth.

To each and every person mentioned above, as well as those who may not be named individually, I offer my sincerest thanks. Your contributions have been invaluable, and I am humbled by the generosity and unwavering support I have received. This thesis would not have been possible without your guidance, encouragement, and belief in me.

Thank you from the bottom of my heart.

### 2023-06-16 tesis_Ashish/Chapter1/chapter1.tex
Your commit message

\chapter{Introduction to collider experiments}  %Title of the First Chapter

\ifpdf
    \graphicspath{{Chapter1/Figs/Raster/}{Chapter1/Figs/PDF/}{Chapter1/Figs/}}
\else
    \graphicspath{{Chapter1/Figs/Vector/}{Chapter1/Figs/}}
\fi

%\section{Introduction to collider experiments}
%\label{sec:introduction}

Collider experiments are a type of particle physics experiment that involve colliding particles, typically protons or electrons, at very high energies. These collisions can lead to the creation of new particles or the detection of new phenomena, providing insight into the fundamental nature of matter. Colliders are designed to accelerate particles to nearly the speed of light and guide them along a circular or linear path using magnetic fields. By colliding particles head-on or at oblique angles, physicists can study the resulting particle showers and detect the products of the collision using complex detectors. Collider experiments have played a crucial role in advancing our understanding of particle physics and continue to be a vital tool for scientific exploration.

\section{Luminosity and its importance in particle physics}

Luminosity is a measure of the number of particle collisions that occur per unit time and per unit area. In particle physics, luminosity is a crucial parameter that determines the rate at which particles are produced in a collider experiment.

The luminosity of a collider is given by the following equation:

\begin{equation}
L = \frac{N_1 N_2 f}{A} 
\end{equation}

where $N_1$ and $N_2$ are the number of particles in each beam, f is the frequency of bunch crossings, and A is a parameter that takes into account the overlap between the two beams.

The importance of luminosity in particle physics lies in its direct relationship with the production rate of particles of interest. The production rate of a given particle is proportional to the product of the luminosity and the cross-section of the process. Thus, luminosity directly affects the ability to detect rare events and make precise measurements. The more collisions that occur, the higher the probability of rare events happening, such as the creation of new particles or the detection of new phenomena. Additionally, precise measurements require a large number of collisions to be able to statistically determine the properties of the particles being studied.

The production rate of a given particle can be expressed as:

\begin{equation}
R = L  \sigma,
\end{equation}

where R is the production rate, L is the luminosity, and $\sigma$ is the cross-section of the process that produces the particle. The cross-section is a measure of the probability that a given process will occur, and it is typically a very small number, on the order of picobarns ($10^{-36} m^2$).
In order to achieve high luminosity, particle accelerators use various techniques to increase the number of particles in the beams and focus them to a small cross-sectional area. This is done by using superconducting magnets to guide the particles along a circular path and keep them confined to a small area. Another technique is to use radio frequency cavities to accelerate the particles to higher energies increasing the frequency of bunch crossings. Increasing the number of particles in each bunch is another way to increase luminosity. In high-energy particle accelerators, such as the Large Hadron Collider (LHC) at CERN, the luminosity is typically measured in units of inverse femtobarns ($fb^{-1}$), which is a measure of the total number of collisions per unit area during the course of an experiment. For example, the LHC has a design luminosity of $10^{34} cm^{-2}s^{-1}$, which means that there are $10^{34}$ proton-proton collisions per second per square centimeter of the detector. The importance of luminosity can be seen in the many discoveries that have been made in particle physics due to high-luminosity experiments. For example, the discovery of the Higgs boson at the LHC was made possible by the high luminosity of the collider, which allowed physicists to observe the rare Higgs boson signal over the background noise of other particles. In addition to discoveries, high luminosity experiments are also important for precision measurements. For example, the measurement of the properties of the top quark, the heaviest known elementary particle, requires a large number of collisions to be able to distinguish the signal from the background noise.

\section{Motivation for precision luminosity measurement}

%One important measurement in particle physics is the measurement of the luminosity of the colliding beams. The luminosity is a measure of the number of collisions that are occurring per unit time in unit area. This measurement is important because it provides information about the rate at which rare processes occur, and it is necessary for precise measurements of cross sections and other properties of particles like couplings to fermions and bosons. The luminosity measurement with the pixel detector at the CMS experiment is a crucial measurement for the understanding of the LHC physics. The main motivation for this study is to improve the accuracy of the luminosity measurement, which is essential for many physics analyses, including searches for new particles and measurements of the properties of known particles. Luminosity uncertainty is one of the dominant uncertainty in Higgs Boson cross section and coupling measurement with other gauge bosons and fermions as shown in Fig.~\ref{fig:lum_unc}. Uncertainty in cross section and coupling measurement can not be better than uncertainty in luminosity measurement.

In particle physics, the luminosity of colliding beams is a crucial measurement as it provides information about the rate at which rare processes occur and enables precise measurements of particle properties such as cross sections and couplings to fermions, bosons. Cross sections are fundamental quantities in particle physics, used to predict the number of events a certain process will produce. Luminosity depends on several variables, including the number of protons in each beam, the size and shape of the beams, and their relative positioning. A slight change in any of these variables can significantly alter the luminosity, which in turn affects the interpretation of collision data. Therefore, it is crucial to measure the luminosity with high precision.
%The measurement of luminosity with the pixel detector at the CMS experiment is particularly important  as it is a highly precise detector that is capable of measuring luminosity with great accuracy. It provides information about the number of charged particles passing through the detector, which is directly proportional to the number of collisions. This information is then used to calculate the luminosity. 
Improving the uncertainty in luminosity measurements is essential for many physics analyses, including searches for new particles and measurements of the properties of known particles. It is a dominant factor in the measurement of Higgs Boson cross sections and couplings to other gauge bosons and fermions, as shown in Fig~\ref{fig:lum_unc}. As such, the uncertainty in cross-section and coupling measurements cannot be better than the uncertainty in luminosity measurement. Therefore, ongoing efforts are focused on improving the accuracy of luminosity measurements, with the pixel detector at CMS being a key component of this effort. By reducing the luminosity uncertainty, physicists can make more precise measurements of particle properties and potentially discover new physics beyond the Standard Model.

%In particle physics, the luminosity of colliding beams plays a crucial role as it provides crucial data about the frequency at which rare processes take place. This enables the precise measurement of particle properties such as cross sections and couplings to fermions and bosons. Measuring luminosity with high accuracy is paramount, as it gives information about the number of charged particles that are involved in collisions. This data is then employed to determine the luminosity. Enhancing the precision of luminosity measurements is vital for numerous physics analyses, including the search for new particles and determining the properties of known particles. Luminosity uncertainty is a significant factor in the measurement of Higgs Boson cross sections and its couplings to other gauge bosons and fermions, as depicted in Fig~\ref{fig:lum_unc}. Consequently, the uncertainty in cross-section and coupling measurements cannot surpass the uncertainty in luminosity measurement. For this reason, continuous efforts are being made to increase the accuracy of luminosity measurements. By decreasing the luminosity uncertainty, physicists can achieve more accurate measurements of particle properties and potentially uncover new physics that lies beyond the confines of the Standard Model.

\begin{figure}[!htp]
\centering
\includegraphics[width=0.42\textwidth]{ashish_thesis/lumi_precision.png}
\caption{%
   Higgs boson production processes cross section projected uncertainty. In the most precisely measured Higgs boson production process, gluon fusion (ggH), luminosity uncertainty will dominate the experimental systematic uncertainty at the High Luminosity (HL)-LHC.
}
\label{fig:lum_unc}
\end{figure}

\section{Large Hadron Collider (LHC) and the CMS Experiment}

The CERN accelerator complex consists of a series of accelerators that work together to produce beams of particles at ever-increasing energies. These beams are then fed into the LHC for further acceleration and collision. The first step in the accelerator complex is the Linac 2, a linear accelerator that produces beams of protons with an energy of 50 MeV (mega-electronvolts). The protons are then sent to the Proton Synchrotron Booster (PSB), which accelerates them to an energy of 1.4 GeV (giga-electronvolts). From there, the proton beams are sent to the Proton Synchrotron (PS), which further accelerates them to an energy of 25 GeV. The next step in the complex is the Super Proton Synchrotron (SPS), which accelerates the protons to an energy of 450 GeV. The SPS also produces beams of heavy ions, such as lead nuclei, which are used for experiments in nuclear physics and other fields. Finally, the proton beams are sent to the LHC, where they are accelerated to their maximum energy of 6.5 TeV per proton. LHC consists of a 27-kilometer ring of superconducting magnets, which guide two counter-rotating beams of protons to collide at four different locations around the ring, where four major experiments, ATLAS, the CMS (Compact Muon Solenoid) experiment, ALICE and LHCb are located as shown in Fig.~\ref{fig:lhc}. The protons are organized into "bunches," with each bunch containing around 100 billion protons. The bunches are spaced apart by 25 nanoseconds, and the LHC can contain up to 2,808 bunches per beam. The bunches in the LHC are designed to have a "bunch current" of 0.55 amperes. It uses radiofrequency (RF) cavities to accelerate the proton beams. The RF frequency used is 400 MHz, which corresponds to a wavelength of 75 centimeters. The LHC uses quadrupole magnets to focus the proton beams and keep them tightly collimated. The LHC uses a total of 1,232 superconducting dipole magnets to bend the proton beams around the circular accelerator ring. The dipole magnets are cooled to a temperature of 1.9 Kelvin (-271.3°C) using liquid helium, and are capable of producing a magnetic field of up to 8.3 tesla. The LHC's detectors record data from proton-proton collisions at a rate of around 40 million collisions per second, but only a tiny fraction of these are actually recorded for analysis. The LHC operates at a vacuum pressure of around $10^{-13}$ atmospheres, which is lower than the pressure on the surface of the moon.

\begin{figure}[!htp]
\centering
\includegraphics[width=0.6\textwidth]{ashish_thesis/lhc_schematic.png}
\caption{%
    CERN accelerator complex consists of Linac 2, Proton Synchrotron Booster (PSB), Proton Synchrotron (PS), Super Proton Synchrotron (SPS) and Large Hadron Collider (LHC). LHC ring showing four interaction points where the ALICE, ATLAS, LHCb and CMS detectors are stationed.
}
\label{fig:lhc}
\end{figure}

The CMS experiment is a multi-purpose particle detector that is designed to detect and study the particles produced in the collisions at the LHC. The CMS detector is a complex instrument that consists of several layers of sub-detectors, each designed to detect different types of particles and measure different properties of the particles.

\begin{itemize}

%\item The tracker is a key component of the Compact Muon Solenoid (CMS) detector, located at the Large Hadron Collider (LHC) at CERN. The tracker is responsible for measuring the trajectories of charged particles produced in collisions at the LHC, providing crucial information about the particles' momentum and charge. The CMS tracker consists of two main sub-detectors, the silicon pixel detector and the silicon strip tracker. The silicon pixel detector is the innermost layer of the tracker and is designed to provide precise measurements of the particles' positions. It is composed of millions of tiny silicon pixels, each capable of detecting the passage of a charged particle and measuring its position to within a few microns. The pixel detector consists of four layers and three forward disks. The silicon strip tracker is located outside the pixel detector and is made up of tens of thousands of thin silicon strips. The strips are arranged in layers perpendicular to the beam axis and provide information about the particles' position in the plane perpendicular to their trajectory. Together, the pixel detector and the strip tracker provide a precise measurement of the particles' trajectory, allowing physicists to reconstruct the paths of particles produced in the collision. Pseudorapidity coverage of the tracker is $|\eta| < 2.5$.

%\item The tracker is the innermost subdetector of the CMS detector, consisting of two components: the pixel detector and the strip detector. It is designed to track the trajectories of charged particles produced in proton-proton collisions. The pixel detector has four layers and three forward disks, while the strip detector has ten layers. The key parameters of the tracker include its resolution, which is about 10 microns in the pixel detector and 20-50 microns in the strip detector, and its coverage, which extends up to a pseudorapidity of 2.5.

\item The tracker is a cylindrical-shaped detector designed to reconstruct the trajectories of charged particles with high precision. The tracker is composed of two main subsystems: the pixel detector, located closest to the interaction point, and the silicon strip detector, surrounding the pixel detector. The pixel detector is the innermost subsystem of the CMS tracker, providing high-resolution spatial measurements essential for precise track reconstruction and vertex identification. The pixel detector consists of four barrel layers (BPIX) and two endcap regions, each with three disks (FPIX). The pixel detector is built from hybrid pixel detector modules, which consist of a silicon sensor and readout electronics. The silicon sensor is segmented into an array of individual pixels, each with dimensions of approximately $100 x 150 \mu m^2$. When charged particles traverse the silicon sensor, they create electron-hole pairs, which drift under the influence of an electric field to the nearest pixel electrode, inducing a current. The readout electronics, implemented using custom Application Specific Integrated Circuits (ASICs), amplify, shape, and digitize the signals, enabling precise measurement of the particle's position. During the 2018 data-taking period, the pixel detector employed the upgraded Phase-1 detector, which featured enhanced radiation tolerance and improved readout electronics. The upgraded pixel detector incorporated more than 120 million pixels, providing excellent granularity and high hit efficiency ($>99\%$) for charged particles. the pixel detector has a spatial resolution of approximately 10 $\mu m$ in the local x-coordinate (transverse to the beam direction, azimuthal) and 30 $\mu m$ in the local y-coordinate (vertical to the beam direction, radial). The silicon strip detector surrounds the pixel detector and is responsible for providing additional tracking points to improve the overall track reconstruction efficiency and momentum resolution. The strip detector is divided into two subsystems: the Tracker Inner Barrel and Disks (TIB/TID) and the Tracker Outer Barrel and Endcaps (TOB/TEC). The TIB/TID consists of four barrel layers and three endcap disks on either side of the barrel region. The TOB/TEC has six barrel layers and nine endcap disks on each side. In total, there are ten barrel layers and twelve endcap disks in the strip detector. The silicon strip sensors are segmented into elongated strips, with a pitch ranging from 80 to 205 $\mu m$, depending on the detector region. As charged particles pass through the silicon strip sensors, they generate electron-hole pairs similar to the pixel detector. The induced signals on the strip electrodes are then amplified, shaped, and digitized by the readout electronics. The silicon strip detector offers a spatial resolution of 20-30 $\mu m$ in the barrel region and 30-45 $\mu m$ in the endcap region.

%To cope with the high particle flux and radiation environment, the strip detector employs radiation-hardened sensors and readout electronics. Additionally, an efficient cooling system is used to maintain a stable operating temperature, ensuring consistent performance throughout the data-taking period.

%\item The tracker is a crucial component of the CMS detector, which is located at the LHC at CERN. The tracker is responsible for measuring the trajectories of charged particles produced in collisions at the LHC, providing essential information about the particles' momentum and charge. The CMS tracker consists of two main sub-detectors: the silicon pixel detector and the silicon strip tracker. The silicon pixel detector is the innermost layer of the tracker and is designed to provide precise measurements of the particles' positions. It consists of millions of tiny silicon pixels, each capable of detecting the passage of a charged particle and measuring its position to within a few microns. The pixel detector has four layers arranged around the beam axis and three forward disks located at each end. The forward disks provide coverage at higher pseudorapidity values, where particles are produced at more extreme angles with respect to the beam axis. The silicon strip tracker is located outside the pixel detector and is made up of tens of thousands of thin silicon strips arranged in layers perpendicular to the beam axis. The strips provide information about the particles' position in the plane perpendicular to their trajectory, complementing the precise position measurements provided by the pixel detector. The strip tracker covers a wider area than the pixel detector and has more layers, allowing for more precise measurements of the particles' trajectories. The pseudorapidity coverage of the tracker is $|\eta| < 2.5$. This means that the tracker can measure particles produced at a wide range of angles with respect to the beam axis, up to approximately 75 degrees away from the beamline. The coverage of the tracker is important because it ensures that particles produced at all angles can be detected, providing a complete picture of the collision event.

\item The Electromagnetic Calorimeter (ECAL) is an important component of the Compact Muon Solenoid (CMS) detector located inside the solenoid magnet of the Compact Muon Solenoid (CMS) detector. Its main function is to measure the energy of photons and electrons that are produced in collisions. The ECAL is made up of more than 75,000 lead tungstate (PbWO4) crystals, arranged in a cylindrical shape around the interaction point. When photons or electrons enter the crystals, they interact with the lead atoms, producing a shower of secondary particles. These particles, in turn, produce scintillation light that is detected by photodetectors at the end of each crystal. The scintillation light produced by the crystals is proportional to the energy of the incoming photon or electron. By measuring the amount of light produced in each crystal, the ECAL is able to determine the energy of the incoming particle with great precision. The ECAL covers the pseudorapidity range $|\eta| < 3.0$, which corresponds to a solid angle of approximately 11,000 square degrees. This ensures that the detector can measure photons and electrons produced at a wide range of angles with respect to the beam axis. The ECAL is arranged in a cylindrical shape around the interaction point, with a barrel region and two endcap regions. The barrel covers the range $|\eta| < 1.479$, while the endcaps cover the range $1.479 < |\eta| < 3.0$. The crystals in the barrel are oriented perpendicular to the beam axis, while those in the endcaps are tilted to match the curvature of the particle trajectories. The PbWO4 crystals in the ECAL have a front face of 22 x 22 $mm^2$ in the barrel region and 28.62 x 28.62 $mm^2$ in the endcaps. The crystals are 230 mm long in the barrel and 220 mm long in the endcaps, allowing for a total of 25.8 radiation lengths of material to absorb the energy of the incoming photons and electrons. The ECAL has an energy resolution of better than 0.5\% for electrons with energies of 50 GeV, and better than 1\% for photons with energies of 100 GeV. This high precision is achieved through a combination of the small crystal size, high light yield of the PbWO4 crystals, and sophisticated calibration procedures. The ECAL also has excellent timing resolution, with a precision of better than 100 picoseconds for most particles. This is important for distinguishing between particles produced in the same collision event, as well as for rejecting background events.

%\item Electromagnetic Calorimeter (ECAL) is designed to measure the energy of electrons and photons produced in proton-proton collisions. It is made up of lead tungstate crystals and has a coverage of up to a pseudorapidity of 3. The key parameters of the ECAL include its energy resolution, which is about 0.5\% for electrons with energies of 100 GeV, and its granularity, which is about 0.0174 in pseudorapidity and 0.0174 radians in phi.

\item The Hadron Calorimeter (HCAL) is a crucial component of the Compact Muon Solenoid (CMS) detector, located outside of the Electromagnetic Calorimeter (ECAL). The HCAL is responsible for measuring the energy of hadrons, which are particles made up of quarks bound together by the strong nuclear force. Hadrons are produced in abundance in high-energy collisions at the LHC and can carry significant amounts of energy. The HCAL is designed to measure the energy of hadrons by absorbing their energy as they pass through the calorimeter. The HCAL is made up of alternating layers of brass, a dense material that absorbs the energy of hadrons, and plastic scintillator, which emits light when particles pass through it. The light emitted by the plastic scintillator is detected by photodetectors, which convert the light into an electrical signal that can be measured. The HCAL is divided into four sections: the barrel region, which covers the central part of the detector, and the endcap regions, which cover the forward and backward directions. The barrel region is divided into 36 wedges, each of which contains alternating layers of brass and plastic scintillator. The endcap regions consist of brass and plastic scintillator layers arranged in a cylindrical shape around the beam axis. The HCAL provides coverage for particles produced at angles up to $|\eta| < 5.2$. This ensures that the HCAL can detect hadrons produced at a wide range of angles with respect to the beam axis. The HCAL also provides coverage for particles with a wide range of energies, up to several hundred GeV.

%\item Hadron Calorimeter (HCAL) is designed to measure the energy of hadrons produced in proton-proton collisions. It is made up of alternating layers of brass and scintillator and has a coverage of up to a pseudorapidity of 5. The key parameters of the HCAL include its energy resolution, which is about 10\% for hadrons with energies of 100 GeV, and its granularity, which is about 0.087 in pseudorapidity and 0.087 radians in phi.

\item The Muon Chambers are an essential component of the Compact Muon Solenoid (CMS) detector, which is one of the four main particle detectors at the Large Hadron Collider (LHC) at CERN. The CMS detector is designed to detect a wide range of particles produced in high-energy collisions at the LHC, including muons, which are charged particles that pass through most materials easily and are difficult to detect using other methods. The muon chambers are located on the outermost layer of the CMS detector and are designed to detect muons as they pass through the detector. The muon chambers consist of three types of detectors: drift tubes (DTs), cathode strip chambers (CSCs), and resistive plate chambers (RPCs). The DTs are located in the barrel region, which covers the central part of the detector, while the CSCs are located in the endcap regions, which cover the forward and backward directions. The RPCs are also located in the barrel and endcap regions and are used to provide a fast trigger signal for muon detection. The muon chambers are positioned on the outermost layer of the CMS detector because muons are highly penetrating particles that can pass through many layers of material without interacting. The muon chambers detect muons by measuring the ionization produced when a muon passes through the gas in the detectors. By measuring the trajectories of muons as they pass through the CMS detector, physicists can study the properties of these particles and search for new physics beyond the Standard Model.

%\item The muon chambers are designed to detect muons produced in proton-proton collisions. They are located outside the solenoid and consist of three types of detectors: drift tubes (DTs), cathode strip chambers (CSCs), and resistive plate chambers (RPCs). The key parameters of the muon chambers include their spatial resolution, which is about 100-300 microns in the DTs and CSCs and 1-2 cm in the RPCs, and their coverage, which extends up to a pseudorapidity of 2.4.

\item The Compact Muon Solenoid (CMS) experiment at the Large Hadron Collider (LHC) at CERN uses a powerful superconducting solenoid magnet to produce a strong and uniform magnetic field, which is essential for detecting and measuring the properties of charged particles produced in high-energy collisions. The CMS solenoid magnet is made of niobium-titanium (NbTi) superconducting wire, which is cooled to a temperature of -268.5°C using liquid helium. This low temperature allows the wire to become superconducting, which means it has zero electrical resistance and can carry large electrical currents without generating heat. The magnet is shaped like a cylinder and is 13 meters long and 6 meters in diameter, making it one of the largest solenoid magnets ever constructed. The solenoid magnet generates a magnetic field of 3.8 Tesla, which is about 100,000 times stronger than the Earth's magnetic field. The magnetic field is used to bend the trajectories of charged particles produced in high-energy collisions, allowing their momentum to be measured as shown in Fig.~\ref{fig:cms}. By measuring the momentum and charge of these particles, physicists can identify and study the properties of various particles, such as the Higgs boson, which was discovered in 2012 using the CMS detector. The combination of the solenoid magnet with other components of the CMS detector, such as the tracker, the calorimeters, and the muon chambers, enables physicists to reconstruct the properties of particles produced in collisions.

%The magnet is a superconducting solenoid that produces a magnetic field of 3.8 Tesla. It is designed to bend the trajectories of charged particles produced in proton-proton collisions, allowing for their momentum to be measured as shown in Fig.~\ref{fig:cms}.

\end{itemize}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/cms_exp.png}
\caption{%
   Compact muon solenoid (CMS) detector with all of the sub detectors showing silicon tracker, electromagnetic and hadron calorimeters and muon chambers. 
}
\label{fig:cms}
\end{figure}

%In summary, luminosity is a critical parameter in particle physics experiments that determines the rate at which particles are produced and detected. The higher the luminosity, the greater the probability of detecting rare or low-probability events. The production rate of a particle of interest is proportional to the product of the luminosity and the cross-section of the process that produces the particle, and increasing the luminosity is essential for increasing the production rate of rare particles.Luminosity is a fundamental concept in particle physics that describes the rate at which particles collide in a particle accelerator. It is defined as the number of particles per unit time and unit cross-sectional area of the particle beams. In other words, it is a measure of the intensity of the particle beams and determines the number of collisions that occur within a given time. The importance of luminosity in particle physics lies in the fact that it directly affects the ability to detect rare events and make precise measurements. The more collisions that occur, the higher the probability of rare events happening, such as the creation of new particles or the detection of new phenomena. Additionally, precise measurements require a large number of collisions to be able to statistically determine the properties of the particles being studied. In high-energy particle accelerators, such as the Large Hadron Collider (LHC) at CERN, the luminosity is typically measured in units of inverse femtobarns ($fb^{-1}$), which is a measure of the total number of collisions per unit area during the course of an experiment. For example, the LHC has a design luminosity of $10^{34} cm^{-2}s^{-1}$, which means that there are $10^{34}$ proton-proton collisions per second per square centimeter of the detector. In order to achieve high luminosity, particle accelerators use various techniques to increase the number of particles in the beams and focus them to a small cross-sectional area. One technique is to use superconducting magnets to guide the particles along a circular path and keep them confined to a small area. Another technique is to use radio frequency cavities to accelerate the particles to higher energies. The importance of luminosity can be seen in the many discoveries that have been made in particle physics due to high-luminosity experiments. For example, the discovery of the Higgs boson at the LHC was made possible by the high luminosity of the collider, which allowed physicists to observe the rare Higgs boson signal over the background noise of other particles. In addition to discoveries, high luminosity experiments are also important for precision measurements. For example, the measurement of the properties of the top quark, the heaviest known elementary particle, requires a large number of collisions to be able to distinguish the signal from the background noise.

\section{Run 1 and Run 2 luminosity measurement}

During the operation of the CMS experiment, two main data-taking periods were conducted: Run 1, which spanned from 2010 to 2013, and Run 2, which took place from 2015 to 2018. During these periods, the CMS experiment measured the instantaneous and integrated luminosity of the proton-proton collisions produced by the Large Hadron Collider (LHC) shown in Fig.~\ref{fig:lumi}. During Run 1, the CMS experiment achieved a peak instantaneous luminosity of up to $5 \times 10^{33} cm^{-2} s^{-1}$, while during Run 2, the luminosity reached a peak value of up to $2 \times 10^{34} cm^{-2} s^{-1}$. The luminosity measurements during both runs were accompanied by careful assessments of the systematic uncertainties to ensure accurate and reliable results as shown in Table. \ref{tab:lumi}.

%\begin{tabular}{c c c c}
%Year & Center of Mass Energy (TeV) & Integrated Luminosity (fb$^{-1}$) & Systematic Uncertainty (\%) \\
%\hline
%2010 & 7 & 0.04 & N/A \\
%2011 & 7 and 8 & 5.6 & 4.5 \\
%2012 & 8 & 23.3 & 2.5 \\
%2015 & 13 & 3.8 & 2.3 \\
%2016 & 13 & 40.8 & 2.5 \\
%2017 & 13 & 49.8 & 2.3 \\
%2018 & 13 & 67.9 & 2.5 \\
%\end{tabular}

\begin{table}[h]
\centering
\caption{Summary of center of mass energy, integrated luminosity, and systematic uncertainty per year during the CMS luminosity measurement.}
\begin{tabular}{c c c c}
Year & Center of Mass Energy (TeV) & Integrated Luminosity (fb$^{-1}$) & Systematic Uncertainty (\%) \\
\hline
2010 & 7 & 0.045 & 11 \\
2011 & 7 and 8 & 6.1 & 4.5 \\
2012 & 8 & 23.3 & 2.5 \\
2015 & 13 & 4.3 & 2.3 \\
2016 & 13 & 41.6 & 2.5 \\
2017 & 13 & 49.8 & 2.3 \\
2018 & 13 & 67.9 &  2.5\\
\end{tabular}
\label{tab:lumi}
\end{table}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/CMS_luminosity.png}
\caption{%
    Delivered luminosity versus time for Run 1 and Run 2 of the CMS experiment.
}
\label{fig:lumi}
\end{figure}

### 2023-06-16 tesis_Ashish/Chapter2/chapter2.tex
Your commit message

\chapter{Luminosity measurement at CMS experiment}  %Title of the First Chapter

\ifpdf
    \graphicspath{{Chapter2/Figs/Raster/}{Chapter2/Figs/PDF/}{Chapter2/Figs/}}
\else
    \graphicspath{{Chapter2/Figs/Vector/}{Chapter2/Figs/}}
\fi

%\section{Luminosity measurement at CMS experiment}
%\label{sec:luminositycms}

Luminosity measurement is a crucial aspect of particle physics experiments such as the Compact Muon Solenoid (CMS) experiment at the Large Hadron Collider (LHC). Luminosity refers to the rate at which particles collide within the detector, and accurate measurement of luminosity is essential for precise determination of particle collision rates and cross-sections. The CMS experiment uses several different devices to measure luminosity, including the Pixel Luminosity Telescope (PLT), Fast Beam Condition Monitor (BCM1F), Hadron forward (HF), Drift tubes (DT), radiation monitoring system for environment and safety (RAMSES) as shown in Fig.~\ref{fig:lumino_cms}. The DT luminometer covers the pseudorapidity range from 0 to 1.2, which is the central region of the CMS detector. The PCC luminometer covers the pseudorapidity range from 0 to 2.5, which covers the central and forward regions of the CMS detector. The HF luminometer covers the pseudorapidity range from 3 to 5, which is the most forward region of the CMS detector. The BCM1F luminometer covers the pseudorapidity range from 3.1 to 4.7, which is also in the forward region of the detector. The RAMSES luminometer covers the pseudorapidity range from 4 to 5, which is also in the forward region of the detector. The PLT luminometer covers the pseudorapidity range from 2.8 to 4.7, which is in the forward region of the CMS detector as shown in Fig.~\ref{fig:lumino_cms_pseudo}. In addition, the Pixel Cluster Counting (PCC) and zero counting method are a commonly used techniques for luminosity measurement at the CMS experiment.

\section{Luminosity measurement methods}

%\subsubsection{Luminosity measurement devices at the CMS Experiment}

\begin{itemize}

%\item Pixel Luminosity Telescope (PLT) : The PLT consists of six planes of silicon pixel sensors, which are placed around the beam pipe, covering a total of 13.6 meters in length. Each sensor is divided into many small pixels, which are sensitive to charged particles passing through them. The sensors are positioned at a distance of about 2 mm from the beam center and measure the number of particles that pass through them. Silicon pixel sensors are divided into pixels of size 100 $\times$ 150 $\mu m^2$. The sensors have a thickness of 285 µm and are designed to operate at high radiation levels. PLT's luminosity measurement is to count the number of particles produced in the proton-proton collisions that pass through the silicon pixel sensors. The more particles that pass through the sensors, the higher the luminosity of the collisions. When a proton-proton collision occurs, it produces a shower of particles that pass through the sensors, creating a "hit" in each sensor. The PLT then uses the number of hits recorded by each sensor to determine the luminosity of the collisions.

\item Pixel Luminosity Telescope (PLT) : The PLT consists of four layers of silicon pixel sensors arranged in a stack, with each layer containing over 8 million individual pixels. The first three layers are located very close to the interaction point where the proton beams collide, and the fourth layer is located further away. The innermost layer is located 2.9 cm from the interaction point. The second layer is located 3.9 cm from the interaction point. The third layer is located 4.9 cm from the interaction point. The outermost layer is located 10.2 cm from the interaction point. The pixel sensors are designed to detect charged particles produced in the collisions as they pass through the detector layers. The PLT operates in what is called the "fast-OR" mode, which detects charged particles produced in a single bunch crossing of the proton beams. In this mode, the PLT triggers on any pixel in the detector that registers a signal above a certain threshold. This signal is called the "fast-OR signal" and indicates that a charged particle has passed through the detector. The PLT uses the information from all four detector planes to reconstruct the trajectories of the charged particles produced in the collisions. This is done by analyzing the signals from the individual pixels and using algorithms to determine the path of the particle through the detector. To measure the luminosity of the collisions, the PLT counts the number of charged particles produced in each bunch crossing, and uses this information to calculate the rate of collisions. The luminosity is then calculated by dividing the collision rate by the cross-section of the proton-proton interactions. The PLT uses a specialized algorithm called the "triple coincidence filter" to identify charged particles that are produced in the collisions and to reject background noise. The filter requires a charged particle to be detected in at least three of the four detector planes, which corresponds to a "triple coincidence" detection. This helps to reduce the contribution of background noise and improve the precision of the luminosity measurement.

\item Fast Beam Conditions Monitor (BCM1F) : The BCM1F is a device used in the CMS (Compact Muon Solenoid) experiment at CERN's Large Hadron Collider (LHC) to measure the luminosity of proton-proton collisions. The luminosity is a measure of the rate of collision events per unit time and per unit area of the beam. The BCM1F is specifically designed to detect the ionization produced by charged particles passing through its diamond sensors, and to convert this signal into a measurement of the beam intensity and luminosity. The BCM1F consists of 24 diamond sensors, each with an active area of 1 cm², arranged in six rings around the beam pipe. The diamond sensors are positioned very close to the CMS detector, just 10 cm away from the beam pipe. This allows the sensors to detect the charged particles produced by the proton-proton collisions. When charged particles pass through the diamond sensors, they ionize the carbon atoms in the diamond crystal, producing electrons and holes. The electrons and holes are then collected by metal electrodes embedded in the diamond, producing a voltage signal proportional to the ionization produced by the charged particles. The voltage signal is then amplified by fast electronics and converted into a digital signal, which is sent to the CMS data acquisition system for further analysis. To measure the luminosity, the BCM1F counts the number of charged particles passing through each diamond sensor per unit time. The signal from each sensor is integrated over a short time interval (usually 25 ns), corresponding to the time it takes for a single proton bunch to pass through the sensors. The integrated signal is then converted into a measure of the instantaneous luminosity, which is proportional to the product of the number of charged particles per bunch and the collision frequency. The number of charged particles per bunch is determined by calibrating the BCM1F with data from other detectors in the CMS experiment, such as the silicon pixel detector and the pixel luminosity telescope. These detectors are used to measure the total number of charged particles produced by the proton-proton collisions, which is then used to calibrate the BCM1F.

%\item Fast Beam Conditions Monitor (BCM1F) : The BCM1F measures the luminosity by detecting the particles that are produced in the proton-proton collisions and scattered at very small angles from the beam direction. These particles, called "forward protons," travel along the beamline and can be detected by the BCM1F. The BCM1F consists of two arrays of scintillating fibers, placed symmetrically around the beam pipe, at a distance of about 20 cm from the beam center. The fibers are sensitive to charged particles passing through them, and their signals are used to measure the position and intensity of the forward protons. The forward protons that are detected by the BCM1F travel along the beamline and reach the end of the detector at different times, depending on their energy and direction. The time-of-flight (TOF) of each proton is measured by using the difference in arrival times between the two arrays of scintillating fibers. The BCM1F measures the luminosity of the proton-proton collisions by counting the number of forward protons that pass through the detector and by measuring their time-of-flight.

\item Beam Halo Monitor (BHM):  The Beam Halo Monitor (BHM) is a device used in particle accelerators to measure the halo of particles that surround the main beam. The halo is a region of low-density particles that surrounds the main beam and can cause damage to accelerator components or experimental detectors. The BHM is designed to detect these halo particles and measure their flux. The BHM consists of two arrays of scintillating fibers, placed on either side of the beam pipe. The fibers are arranged in a grid pattern and are sensitive to the ionization produced by charged particles passing through them. When a halo particle passes through a fiber, it produces scintillation light, which is detected by photomultiplier tubes at the ends of the fibers. The signal from the photomultiplier tubes is then processed by electronics to provide a measurement of the halo flux. To measure the luminosity, the BHM uses a technique called "optical theorem," which relates the total scattering cross-section of the halo particles to the luminosity of the beam. The scattering cross-section is the probability that a halo particle will scatter off a proton in the main beam, and is proportional to the luminosity of the beam. The BHM measures the total scattering cross-section by counting the number of halo particles passing through the scintillating fibers and calculating the fraction of particles that scatter off the main beam. This fraction is then used to calculate the luminosity of the beam. One advantage of the BHM is that it can detect halo particles with energies as low as a few keV, making it sensitive to a wide range of halo particles. It is also a non-destructive technique, which means that it does not affect the main beam or experimental detectors.

%\item Beam Halo Monitor (BHM): The BHM measures the luminosity by detecting the particles that are produced in the proton-proton collisions and scattered at large angles from the beam direction. These particles, called "beam halo," can interact with the BHM sensors and produce signals that are proportional to the luminosity. The BHM consists of a set of sensors that are placed around the beam pipe, at a distance of about 1.6 meters from the beam center. The sensors are sensitive to charged particles passing through them, and their signals are used to measure the position and intensity of the beam halo. The signals from the BHM sensors are processed to extract the information about the beam halo. The signals are first amplified and shaped, and then digitized and recorded. The recorded data are then used to reconstruct the position and intensity of the beam halo. The BHM measures the luminosity of the proton-proton collisions by detecting the beam halo particles that interact with the BHM sensors and produce signals.

\item Hadron Forward Calorimeter: The Hadron Forward (HF) Calorimeter is a critical component of the Compact Muon Solenoid (CMS) experiment at the Large Hadron Collider (LHC) at CERN. It is a subdetector that measures the energy and position of particles produced during proton-proton collisions in the LHC. The HF Calorimeter is designed specifically to measure hadronic particles, which are particles made up of quarks and gluons, in the forward region (i.e., close to the beamline) of the CMS detector. The HF Calorimeter is located at the very front and back of the CMS detector, at a distance of about 11.2 meters from the interaction point. This placement allows it to cover a pseudorapidity range of 2.9 to 5.2, which is important for measuring particles produced at small angles relative to the beamline. The HF Calorimeter is a sampling calorimeter, which means it consists of alternating layers of active and passive materials. The active material, in this case, is scintillating quartz fibers, which emit light when they interact with charged particles. The passive material is steel absorber plates, which serve to initiate hadronic showers, causing the incident hadronic particles to interact and create secondary particles. As these secondary particles pass through the scintillating fibers, they produce light, which is collected by photodetectors and converted into an electrical signal proportional to the particle's energy. Two of the methods used for luminosity measurement in the HF Calorimeter are the Zero Counting (ZC) method and the Missing Energy (ME) method.

%The Zero Counting method is a threshold-based approach for estimating the luminosity. In this method, the total number of inelastic collisions, which produce new particles, is counted by measuring the energy deposited in the HF Calorimeter. To separate inelastic collisions from background noise and other processes, a threshold on the energy deposition is applied. During data-taking, the HF Calorimeter measures the energy deposited in each bunch crossing (when two bunches of protons pass through each other in the LHC). When the energy deposition in both HF Calorimeter sides (HF+ and HF-) is below a certain threshold, it is considered a "zero count" event, which means no inelastic collision has occurred. The number of zero count events is subtracted from the total number of bunch crossings, giving the number of inelastic collisions. The luminosity can then be calculated by dividing the number of inelastic collisions by the integrated time and the inelastic cross-section. The ZC method has the advantage of being robust against pile-up (simultaneous multiple proton-proton collisions) since it relies on counting the events where no energy is deposited. However, it may be affected by detector noise and other background processes that can lead to a non-zero energy deposition.
The zero counting method is another method used by particle colliders to measure the luminosity of collisions. In this method, the luminosity is estimated by counting the number of events with zero particles detected in a specific region of the detector. The basic idea behind the zero counting method is that the probability of having zero particles detected in a given region of the detector is proportional to the probability of having no collisions in that region. This probability can be related to the luminosity of the collisions through the following equation:

\begin{equation}
L = \frac{-ln(N/N_0)}{\sigma_{vis}}
\end{equation}

where L is the luminosity, N is the number of events with zero particles detected in the region of interest, $N_0$ is the total number of events, $\sigma_{vis}$ is the visible cross-section.One advantage is that it is a simple and robust method that does not require sophisticated detectors or calibration procedures. However, it can be affected by background events, such as cosmic rays or beam-gas interactions, which can produce zero particles in the region of interest and increase the uncertainty in the luminosity measurement.
The Missing Energy method is an alternative approach for luminosity measurement in the HF Calorimeter. This method relies on measuring the total transverse energy (Et) deposited in the calorimeter and comparing it with the expected average transverse energy for inelastic collisions. The idea behind the ME method is that the total transverse energy should be conserved in a collision event. Inelastic collisions are expected to produce a certain amount of transverse energy on average, which can be estimated from simulations and theoretical calculations. The missing energy in an event is defined as the difference between the expected average transverse energy and the measured transverse energy in the HF Calorimeter. For each bunch crossing, the missing energy is calculated, and a distribution of missing energy values is obtained. This distribution is then fitted to a functional form, which includes a term for the inelastic collisions and terms for various background processes (e.g., detector noise, beam-gas interactions). The fit allows extracting the number of inelastic collisions, which can then be used to calculate the luminosity by dividing it by the integrated time and the inelastic cross-section. The ME method is sensitive to the energy scale calibration of the detector and the modeling of background processes. However, it provides an independent and complementary measurement to the ZC method, which helps to reduce systematic uncertainties in the luminosity determination.

%\item Hadron Forward Calorimeter: The HF sub-detector measures the luminosity by detecting the neutral particles produced in the proton-proton collisions that interact with the hadron forward calorimeter. These particles include neutrons, photons, and neutral hadrons, and they are produced in the forward region of the detector at a large pseudorapidity, which means they are produced at small angles with respect to the beam axis. The HF sub-detector consists of two arrays of steel absorbers, each followed by radiation-hard quartz fibers that detect the Cherenkov light produced when particles pass through them. The two arrays are placed symmetrically on either side of the beam pipe at about 11 meters from the interaction point. The signals produced by the quartz fibers are collected and digitized to produce time and energy measurements of the particles that pass through the Hadron Forward Calorimeter. The HF sub-detector measures the luminosity of the proton-proton collisions by counting the neutral particles that interact with the Hadron Forward Calorimeter and using this information to calculate the luminosity.

%\subsubsection{Luminosity measurement techniques at the CMS Experiment}

\item Muon drift tubes: The DT system is part of the CMS muon system, which also includes the Resistive Plate Chambers (RPCs) and the Cathode Strip Chambers (CSCs). Drift Tubes (DTs) in the CMS experiment are designed to accurately measure the trajectory and momentum of muons produced in proton-proton collisions at the LHC. The DT system is located in the barrel region of the CMS detector, covering the pseudorapidity range of $|\eta| < 1.2$. The CMS Drift Tubes consist of rectangular drift cells filled with a gas mixture, typically of argon and carbon dioxide. Each drift cell contains a thin anode wire held at a high voltage relative to the cell walls, which act as the cathode. When a charged particle like a muon passes through the gas-filled cell, it ionizes the gas molecules, producing free electrons and positively charged ions. These free electrons drift towards the anode wire under the influence of the electric field, while the positive ions drift towards the cathode. The drift time of electrons to the anode wire is measured, and by knowing the drift velocity in the gas mixture, the distance between the ionizing particle's trajectory and the anode wire can be determined. Combining the information from multiple drift cells, the trajectory of the muon can be reconstructed with high precision. It is not a primary method for luminosity measurement, as the system is specifically designed for muon detection and momentum measurement. However, one could potentially use the muon rates detected by the DT system for an indirect luminosity measurement. This would involve correlating the rate of muons detected in specific processes, such as those from W and Z boson decays, with the underlying luminosity. By measuring the rate of these processes and comparing them to the known production cross-sections, the luminosity could be inferred. This approach would require careful control of various experimental factors, such as the efficiency and acceptance of the DT system, the precise determination of the production cross-sections, and corrections for pile-up and background processes. It is important to note that this would not be a primary luminosity measurement technique, but it could provide a complementary cross-check to the main methods used in the CMS experiment.

\item Pixel Cluster Counting (PCC): The pixel detector in the CMS experiment is made up of multiple layers of silicon sensors arranged in a cylindrical shape around the beam pipe. When charged particles from the collisions pass through the silicon sensors, they create electric charge that is read out as a signal. The signals from adjacent sensors are combined to form clusters, which represent the position of the particle track in the detector. The total number of clusters detected over a certain period of time is used to estimate the luminosity. The PCC provides a precise measurement of the luminosity and is particularly useful when the collision rate is high.

\end{itemize}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/luminometer_cms.png}
\caption{%
   Compact muon solenoid (CMS) detector with all of the luminosity measurement devices showing PLT, BCM1F, HF, DT, PCC and RAMSES. 
}
\label{fig:lumino_cms}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/luminometer_cms_pseudo.png}
\caption{%
    Cross section of the CMS detector in the r-z plane showing all Run 2 luminometer PLT, BCM1F, DTs, and HF location. The two RAMSES monitors used as a luminometer in Run 2 are located directly behind HF. 
}
\label{fig:lumino_cms_pseudo}
\end{figure}

%\newpage
\section{Pixel detector}

The pixel detector is one of the subdetectors of the CMS experiment that is closest to the interaction point where the proton beams collide. It consists of four barrel layers (L1-L4) at radii of 29, 68, 109 and 160 mm and three forward disks (D1-D3) on each end at distances of 291, 396, and 516 mm of pixel sensors from the center of the detector as shown in Fig.~\ref{fig:phaseI_upgrade}. It is built from 1856 silicon sensor modules, 1184 modules in the barrel layers (BPIX) and 672 modules for the forward disks (FPIX). Modules for barrel layers and forward disks are shown in Fig.~\ref{fig:pixelmodule}.  The modules in BPIX L1 are designed to handle high particle densities and radiation levels. Each module in this layer consists of a matrix of 4160 pixels, arranged in 160 rows and 26 columns. The pixel size in BPIX L1 is approximately 100x150 µm², which allows for high-resolution position measurements of charged particles. The modules in BPIX L2-4 layers are designed to withstand lower radiation levels compared to BPIX L1. Each module in BPIX L2-4 consists of a matrix of 66560 pixels, arranged in 260 rows and 256 columns. The pixel size in BPIX L2-4 is also approximately 100x150 µm². The FPIX modules are also designed to handle high particle densities and radiation levels. Each module in the FPIX consists of a matrix of 16128 pixels, arranged in 160 rows and 101 columns. The pixel size in the FPIX is approximately 100x150 µm². It provide high-precision position measurements of the charged particles produced in the collisions. These position measurements are used to reconstruct the trajectories of the particles and to identify the particles themselves. The pixel detector has a high position resolution, with a spatial resolution of 10-20 microns in the transverse direction and 20-30 microns in the longitudinal direction. The pixel detector also has a high time resolution, with a readout time of 25 nanoseconds. The pixel detector is capable of detecting charged particles with a wide range of energies, from a few hundred MeV to several TeV. The pixel detector is able to operate at very high particle fluxes, with a hit rate of up to $100 MHz/cm^2$. To achieve this high rate capability, the pixel detector uses fast readout electronics, which can read out the signals from the pixels in a few microseconds. The pixel detector is also designed to operate at a high radiation level, with a dose of up to $5 \times 10^{14} neutrons/cm^2$ expected over the lifetime of the detector. To mitigate the effects of radiation damage, the pixel detector uses sensors made of high-purity silicon and a cooling system that keeps the detector at a temperature of -20°C. The pixel detector is also used for the measurement of the luminosity at the CMS experiment. The luminosity measurement is based on counting the number of pixel clusters produced in the detector by the proton-proton collisions. The higher the collision rate, the more clusters are produced in the pixel detector. However, there are several challenges to accurately measure the luminosity with the pixel detector. One challenge is the high rate of particles that pass through the detector, which can cause pileup (multiple particles passing through the detector at the same time). Another challenge is the non-linearity of the pixel detector response, which can lead to inaccuracies in the luminosity measurement. Therefore, the motivation of this work is to develop and test more precise techniques for measuring the luminosity with the pixel detector, in order to improve the accuracy of the luminosity measurement and to better understand the effects of detector response on the measurement.

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/phaseI_upgrade_pixel_detector.png}
\caption{%
   Layout of the CMS Phase-1 pixel detector in longitudinal view. 
}
\label{fig:phaseI_upgrade}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/silicon_pixel_module.png}
\caption{%
   Pixel detector modules for BPIX L1 (left), BPIX L2-4 (middle), and
the FPIX detector (right). 
}
\label{fig:pixelmodule}
\end{figure}

\begin{table}
  \begin{center}
    \begin{tabular}{ccccc}  
    \textbf{Layer/Disk}   & \textbf{\# modules} \\ \hline
     L1      &    96        \\  
       L2    &     224   \\ 
        L3   &       352 \\ 
         L4   &       512 \\ 
         D1 inner ring & 88     \\ 
         D1 outer ring &   136    \\ 
         D2 inner ring &      88 \\ 
         D2 outer ring &   136   \\ 
          D3 inner ring&     88  \\ 
         D3 outer ring &    136  \\ 
      \end{tabular}
    \caption{Number of pixel detector modules in each layer and disk}
    \label{tab:modpix}
  \end{center}
\end{table}

\section{Pixel cluster counting (PCC) method}

The Pixel Cluster Counting (PCC) method is one of the two primary luminosity measurement methods used at the CMS experiment. The PCC method is based on counting the number of pixel clusters produced by the collisions in the CMS pixel detector, which is a high-resolution silicon detector located close to the collision point. The pixel detector is made up of more than 65 million pixels, each of which is 100 micrometers by 150 micrometers in size. The detector is designed to detect charged particles produced in the collisions, and the pixel clusters are formed when several neighboring pixels are hit by a single particle. The PCC method is based on the assumption that the number of pixel clusters produced is proportional to the number of collisions, and therefore to the luminosity. The proportionality constant is called the pixel cluster visible cross section, and it can be determined from a calibration measurement. The PCC method is implemented in two stages: the online and offline stages. In the online stage, the pixel clusters are counted in real time by the CMS data acquisition system, which uses a custom-designed ASIC chip to process the pixel detector signals. The online luminosity measurement is therefore available within seconds of the collisions, and it is used to monitor the stability of the detector and to provide feedback to the LHC operators. In the offline stage, the raw data from the pixel detector is analyzed using dedicated software to determine the pixel clusters and to calculate the luminosity. The offline luminosity measurement is more accurate than the online measurement, as it takes into account various corrections and calibrations that are not possible in real time. The offline luminosity measurement is also used to determine the luminosity scale and the absolute luminosity, which is the total number of collisions per unit time and per unit area. Steps involved in the PCC method for measuring luminosity are as follows,

\begin{itemize}

\item Pixel detector data acquisition is the process of collecting and digitizing the signals from the silicon pixel detectors in the CMS experiment. When a particle passes through the silicon pixel detector, it creates a small amount of charge in the pixel sensor. The charge is collected by the electrodes in the pixel sensor and converted into a voltage signal. The voltage signal is then digitized using an analog-to-digital converter (ADC) to create a digital signal. The ADC measures the voltage at regular intervals, called sampling intervals, and assigns a digital value to each voltage measurement. The digital signal is then stored in a buffer in the front-end electronics of the pixel detector. The buffer is a small amount of memory that temporarily holds the data before it is transmitted to the data acquisition system. The data acquisition system continuously monitors the data from the pixel detectors to detect interesting events. When an event of interest is detected, a trigger signal is sent to the front-end electronics of the pixel detector to read out the data from the buffer. The readout electronics in the pixel detector then transmit the data to the data acquisition system using high-speed optical fibers. The data is sent in packets, called data frames, which contain information about the event, such as the time of the event, the position of the particle, and the amount of charge deposited in the pixel sensor. The data acquisition system processes the data frames to reconstruct the particle tracks and identify the types of particles that passed through the pixel detector. The data is then stored in a format that can be used for further analysis.

\item Pixel cluster reconstruction is the process of identifying groups of adjacent pixels that have been fired by a single particle passing through the detector. The first step in the pixel cluster reconstruction process is to identify individual pixel hits in the data frames obtained from the pixel detector data acquisition system. A pixel hit is a small region of the pixel detector where charge has been deposited by a particle. The next step is to identify "seed" pixels, which are individual pixels with a high signal-to-noise ratio. A seed pixel is defined as a pixel hit with a signal above a certain threshold, which is typically set at a few times the noise level of the pixel detector. Once seed pixels have been identified, the next step is to build pixel clusters around each seed pixel. This is done by adding adjacent pixels with a signal above a lower threshold, called the cluster threshold. The cluster threshold is typically set at a level that minimizes the number of fake clusters while maximizing the efficiency of cluster finding. After pixel clusters have been built, the next step is to split or merge clusters as needed. This is done to remove fake clusters caused by noise or overlapping particles, and to merge clusters that are split due to inefficiencies in the cluster building process. Once the pixel clusters have been identified and merged/split as necessary, they are parameterized by their position and energy. The position of the cluster is determined by the center of gravity of the pixels in the cluster, and the energy is determined by summing the signal of all the pixels in the cluster. Finally, a set of selection criteria are applied to the pixel clusters to remove any remaining fake clusters and select only those clusters that are likely to be from real particle interactions. These selection criteria typically include requirements on the size, shape, and energy of the clusters.

\item The number of pixel clusters is counted for a given time interval, known as lumi section. One lumi section is 23.36 seconds time interval. The first step in the pixel cluster counting process is to select events of interest from the large dataset obtained from the CMS experiment. This is typically done using trigger systems that select events that are likely to be of interest based on their energy, particle multiplicity, or other criteria. Once the events of interest have been selected, the next step is to reconstruct the pixel clusters in each event using the algorithm described in the previous answer. This involves identifying individual pixel hits, identifying seed pixels, building pixel clusters around each seed pixel, and parameterizing the clusters. After the pixel clusters have been reconstructed in each event, the next step is to count the number of clusters in each event. This can be done using simple counting algorithms that count the number of clusters above a certain energy threshold, or more sophisticated algorithms that use machine learning techniques to identify and count clusters. The number of pixel clusters in each event is affected by various sources of background noise, such as electronic noise and cosmic ray background. To accurately measure the number of signal clusters in each event, these background sources must be subtracted from the total cluster count. This can be done using techniques such as sideband subtraction or template fitting. Finally, to obtain an accurate measurement of the number of particles that passed through the pixel detector, the cluster counts must be corrected for the inefficiencies in the cluster reconstruction process. This can be done using simulation or other techniques to estimate the efficiency of the cluster finding algorithm as a function of the particle energy, position, and type.

\item The number of pixel clusters is calibrated to account for various factors that affect the luminosity measurement, such as the efficiency of the pixel detector and the beam intensity. The calibration step is an important part of the PCC (Pixel Cluster Counting) method for measuring luminosity at the CMS experiment. The purpose of calibration is to account for various factors that can affect the measurement of the number of pixel clusters, which is directly proportional to the number of collisions that occurred during a given time interval. These factors include the efficiency of the pixel detector and the beam intensity. The efficiency of the pixel detector refers to the probability that a charged particle passing through the detector will create a signal in one or more pixels. The efficiency of the detector can vary with time, and it can also depend on the energy and angle of the charged particle. To account for the detector efficiency, calibration factors are applied to the number of pixel clusters that are counted. These calibration factors are determined by comparing the number of pixel clusters measured by the detector to the number of collisions predicted by other detectors or simulations. The beam intensity refers to the number of protons circulating in the LHC at any given time. The beam intensity can vary over time and can affect the measurement of the collision rate. To account for the beam intensity, the number of pixel clusters is normalized by the instantaneous luminosity, which is a measure of the collision rate at the interaction point. The instantaneous luminosity is determined by other detectors or by theoretical calculations. After applying the calibration factors, the number of pixel clusters is converted to the number of collisions that occurred during the given time interval. This number is then used along with other parameters such as the frequency at which the LHC is operating and the size of the interaction region to calculate the luminosity of the collision using the formula $L = \frac{N_{cl}  f_{rev}} {\sigma_{vis}} $. The resulting luminosity measurement provides valuable information about the collision rate and the physics processes occurring at the CMS experiment.

\item The number of pixel clusters is used to calculate the luminosity using the following formula:

\begin{equation}
 L = \frac{N_{cl} f_{rev} } {\sigma_{vis}}   
\end{equation}

where L is the luminosity, $N_{cl}$ is the number of clusters, $f_{rev}$ is the revolution frequency of the LHC, and $\sigma_{vis}$ is the visible cross section of the interaction region.

\end{itemize}

\section{Advantages of the pixel cluster counting method}

The PCC method has several advantages over the other luminosity measurement methods used by the CMS experiment. One advantage is its high precision and stability, as it is based on a well-understood physical process and has a small systematic uncertainty. Another advantage is its independence from the beam conditions, as the pixel detector is insensitive to the beam halo and the beam-gas interactions. The PCC method is also robust against pile-up, which is the presence of multiple proton-proton interactions in a single bunch crossing, as it can distinguish between pixel clusters produced by different collisions. The PCC method is based on the pixel detector, which has a high spatial resolution and can accurately measure the position and energy of charged particles. This allows for precise measurements of the luminosity, even when the particle collision rate is high. Advantages of the PCC method are described below,

\begin{itemize}

\item High precision: The pixel detector has a high granularity and can detect individual particles with high precision. This allows for a precise measurement of the luminosity, with uncertainties typically below 2\%.

\item High efficiency: The pixel detector has a high detection efficiency, meaning that it can detect a large fraction of the particles produced in the collisions. This allows for a high signal-to-noise ratio and a low level of background noise, resulting in a more accurate measurement of the luminosity.

\item Long-term stability: The pixel detector has a high level of stability over long periods of time, which is important for accurate luminosity measurements over extended periods of data-taking.

%\item Fast and real-time: The pixel cluster counting method can provide luminosity measurements in real-time, allowing researchers to quickly analyze the data and make adjustments to the experiment as needed. This is particularly important for experiments that need to optimize their data-taking strategies based on the luminosity measurements.

\item Low sensitivity to pileup: Pileup refers to the number of additional collisions that occur within the same bunch crossing as the primary collision being studied. The pixel cluster counting method is relatively insensitive to pileup, meaning that it can still provide accurate luminosity measurements even when pileup is high.

\item Wide dynamic range: The pixel cluster counting method has a wide dynamic range, meaning that it can measure luminosities over a wide range of values, from low to high. This is important for experiments that need to measure luminosities over different energy ranges.

\item Insensitivity to beam conditions: The pixel cluster counting method is relatively insensitive to beam conditions such as beam intensity and beam size. This makes it a reliable technique for luminosity measurement, even when the beam conditions vary.

\item Independent of beam crossing angle: The pixel cluster counting method is independent of the beam crossing angle, which is the angle at which the beams intersect. This makes it easier to compare results obtained under different beam crossing angles.

\item Independence from trigger systems: The PCC method operates independently of the CMS experiment's trigger systems, which means it is not affected by any biases or inefficiencies that might be present in the trigger.

\end{itemize}

%However, the PCC method also has some limitations and challenges. One limitation is its sensitivity to the pixel detector efficiency and the noise level, as the cluster formation probability depends on the number of hit pixels and their signal-to-noise ratio. The PCC method also requires a precise knowledge of the pixel cluster cross section, which can be affected by various factors such as the beam spot size, the beam divergence, and the pile-up conditions. The PCC method is also affected by various sources of background, such as cosmic rays, machine-induced noise, and photon conversions, which can mimic pixel clusters produced by collisions. To mitigate these limitations and challenges, the CMS employs several techniques and strategies in the PCC method. One technique is the use of pixel clustering algorithms that are optimized for different beam conditions and pile-up levels, and that incorporate various quality criteria to reject noisy and fake clusters. Another technique is the use of dedicated calibration measurements using known luminosity sources, such as Van der Meer scans and beam-gas events, which provide a precise determination of the pixel cluster cross section and its variations as a function of the beam conditions. The CMS also employs various data-driven and simulation-based methods to estimate the background contributions and their uncertainties, and to correct for their effects on the luminosity measurement.

The PCC method has been extensively tested and validated by the CMS during the LHC Run 1 and Run 2, which corresponded to proton-proton collisions at center-of-mass energies of 7-8 TeV and 13 TeV, respectively. The PCC method has achieved a relative luminosity precision of about 2-3 \%, which is well within the design goals of the CMS. In the future, the PCC method will continue to be a key component of the CMS luminosity measurement strategy, as it provides a precise and robust measurement of the luminosity ratio between different datasets and periods. The PCC method will also benefit from the upgrades and improvements planned for the CMS pixel detector and the LHC, which will increase the luminosity and the collision rate, and will challenge the performance and the calibration of the PCC method. The CMS is planning to install a new pixel detector for the High-Luminosity LHC (HL-LHC) era, which will feature smaller pixel sizes, faster readout electronics, and radiation-hard materials. The CMS is also planning to develop new techniques and algorithms for the PCC method, such as machine learning methods, deep neural networks, and real-time analysis tools.

%The Pixel Cluster Counting (PCC) method is a powerful and reliable technique for measuring the luminosity of proton-proton collisions at the CMS detector at the LHC. The PCC method is based on the counting of pixel clusters produced by the collisions in the CMS pixel detector, and it provides a precise and stable measurement of the relative luminosity between different datasets and periods. The PCC method has several advantages, such as its high precision, stability, and independence from the beam conditions, and it has several limitations and challenges, such as its sensitivity to the pixel detector efficiency and the noise level, and its dependence on the pixel cluster cross-section and the background contributions. The PCC method has been extensively tested and validated by the CMS, and it will continue to play a crucial role in the future physics program of the CMS and the LHC.

%Pixel Cluster Counting (PCC) is a method for measuring the luminosity of particle collisions in high-energy physics experiments, such as those conducted at the Large Hadron Collider (LHC). The PCC method is based on counting the number of clusters of charged particles produced in the collision that are detected by the pixel detector of the experiment.

%Measuring the luminosity of particle collisions is an essential part of high-energy physics experiments. Luminosity is a measure of the rate at which particles are colliding and is directly related to the number of events observed in the experiment. The luminosity measurement is critical for understanding rare physics processes, such as the production of new particles or the measurement of the properties of known particles.

%Several techniques are used to measure luminosity in particle physics experiments, including the use of scintillators, Cherenkov detectors, and other radiation detectors. However, the most commonly used technique is the measurement of the rate of particles produced in the collision.

%The PCC method is based on counting the number of clusters of charged particles produced in the collision that are detected by the pixel detector of the experiment. The pixel detector is a high-resolution detector that is designed to provide precise measurements of the position and energy of charged particles.

%In the PCC method, the charged particles produced in the collision pass through the pixel detector, where they create clusters of pixels that are read out by the detector electronics. The number of clusters produced in each collision is proportional to the luminosity of the collision.

%In conclusion, the PCC method is a powerful technique for measuring the luminosity of particle collisions in high-energy physics experiments. The PCC method is based on counting the number of clusters of charged particles produced in the collision that are detected by the pixel detector of the experiment. The PCC method has several advantages over other luminosity measurement techniques, including its high spatial resolution, insensitivity to background radiation, insensitivity to the energy of the charged particles, and insensitivity to the material used in the detector. These advantages make the PCC method a valuable tool for understanding rare physics processes in particle physics experiments.

%Pixel cluster counting is the process of counting the number of pixel clusters that are reconstructed from the data acquired by the silicon pixel detectors during a given time interval, known as an LHC orbit. An orbit is the time it takes for the LHC to complete one revolution.

%The pixel detectors record the energy deposited by particles passing through them, and the data from the detectors is acquired by the CMS data acquisition system. The acquired data is then processed to reconstruct pixel clusters. A pixel cluster is a group of adjacent pixels that have been fired by a single particle passing through the detector. Pixel clusters are reconstructed using algorithms that take into account the shape and size of the charge deposited by the particles in the pixels.

%Once the pixel clusters are reconstructed, they are counted for a given time interval, typically the duration of one LHC orbit, which is about 89 microseconds. The number of pixel clusters is directly proportional to the number of collisions that occurred during that time interval. Therefore, counting the number of pixel clusters provides a way to measure the collision rate, which is an important input for calculating the luminosity of the collision.

%However, it is important to note that not all pixel clusters correspond to actual collisions. Some pixel clusters may be produced by background events, such as cosmic rays, that are not relevant for measuring the collision rate. Therefore, it is necessary to calibrate the number of pixel clusters to account for various factors that affect the luminosity measurement, such as the efficiency of the pixel detector and the beam intensity, before using it to calculate the luminosity.

\section{Previous studies related to PCC luminosity measurement}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Run2018A_old.png}
\caption{%

}
\label{fig:pixelmodule}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Run2018B_old.png}
\caption{%

}
\label{fig:pixelmodule}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Run2018B_old.png}
\caption{%

}
\label{fig:pixelmodule}
\end{figure}

### 2023-06-16 tesis_Ashish/Chapter3/chapter3.tex
Your commit message

\chapter{PCC luminometer calibration}  %Title of the First Chapter

\ifpdf
    \graphicspath{{Chapter3/Figs/Raster/}{Chapter3/Figs/PDF/}{Chapter3/Figs/}}
\else
    \graphicspath{{Chapter3/Figs/Vector/}{Chapter3/Figs/}}
\fi

%\section{PCC luminometer calibration}
%\label{sec:vdMcab}

One widely used method for the calibration of luminosity measurement devices is the van der Meer (VdM) scan. This method is named after Simon van der Meer, a Dutch physicist and Nobel laureate, who developed the technique in the 1960s. van der Meer calibration is a technique used to determine the absolute luminosity of colliding beams in particle accelerators. It involves scanning the beams across each other in the horizontal and vertical planes to measure the beam overlap integral, which is proportional to the luminosity. The first step in the VdM calibration is to scan the colliding beams across each other. This is done by displacing the beams in the horizontal (x) and vertical (y) planes independently while keeping the other direction fixed. The scans are performed at several different positions along the collision point, creating a series of data points for each plane. The data points collected during the scans are then fitted with Gaussian function or other suitable function like double gaussian, Poly2G, Poly4G, etc to determine the beam overlap integrals in the x and y directions. The product of the integrals in the two planes yields the total beam overlap integral. %The event rate is proportional to the luminosity and is given by the product of the cross-section ($\sigma$) and luminosity. 
The beam overlap integral is the integral of the product of the beam overlap width in the horizontal and vertical planes over the entire interaction region. It is an essential parameter in determining the absolute luminosity.

\section{van der Meer (vdM) calibration}

van der Meer (vdM) scans are done to measure change in rate as a function of beam overlap that is used to determine the visible cross section $\sigma_{vis}$ of the pixel detector which is a calibration constant in the relation between rate of a quantity (clusters, coincidences) read out by the detector and the instantaneous luminosity.

The instantaneous luminosity  per bunch crossing when the crossing angle between the colliding bunches is negligible and bunches collide head on is given by the following integral \cite{CMS-PAS-LUM-13-001},

\begin{equation}
L_{b} = N_1 N_2 f \int^{+\infty}_{-\infty} \rho_1(x,y) \rho_2(x+\Delta x, y+\Delta y) dx dy 
\end{equation}

where $N_1, N_2$ are the number of protons in the colliding bunches, f is the LHC orbit frequency whose value is 11246Hz,  $\rho_1(x,y)$ and $\rho_2(x+\Delta x,y+\Delta y)$ are the two dimensional particle density distribution functions for each colliding bunch separated by $\Delta x$ and $\Delta y$ in x and y directions.

Assuming complete factorization of particle density distribution function along x and y directions for both the bunches, we get

\begin{equation}
L_{b} = N_1 N_2 f \int^{+\infty}_{-\infty} \rho_{1x}(x) \rho_{2x}(x+\Delta x)  dx   \int^{+\infty}_{-\infty} \rho_{1y}(y) \rho_{2y}(y+\Delta y)  dy 
\end{equation}

where $\rho_1(x,y) = \rho_{1x}(x) \rho_{1y} (y)$ and $\rho_2(x,y) = \rho_{2x}(x+\Delta x) \rho_{2y} (y+\Delta y)$

The vdM scan determines the bunch  overlap integrals $\int \rho_{x1} (x) \rho_{x2} (x+\Delta x) dx$ and  $\int \rho_{y1}(y) \rho_{y2} (y+\Delta y) dy$ by measuring pixel clusters rate as a function of bunch separation $\Delta x$ and $\Delta y$ along x and y directions as shown in Fig. 14.

\begin{equation}
\int \rho_{x1} (x) \rho_{x2} (x+\Delta x) dx = \frac{R_x(0)}{\int R_x(\Delta x)dx} 
\end{equation}

\begin{equation}
\int \rho_{y1} (y) \rho_{y2} (y+\Delta y) dy = \frac{R_y(0)}{\int R_y(\Delta y)dy} 
\end{equation}

where $R_x(0)$ is the measured cluster rate along x direction when the bunch separation is zero and $R_x(\Delta x)$ is the measured cluster rate when bunches are separated by distance $\Delta x$ and $R_y(0)$ is the measured cluster rate along y direction when the bunch separation is zero and $R_y(\Delta y)$ is the measured cluster rate when bunches are separated by distance $\Delta y$.

Bunch overlap widths $\Sigma_x$ and $\Sigma_y$ along x and y directions are defined as

\begin{equation}
\Sigma_x = \frac{1}{\sqrt{2 \pi}} \frac{\int R_x(\Delta x)dx}{R_x(0)} 
\end{equation}

\begin{equation}
\Sigma_y =  \frac{1}{\sqrt{2 \pi}} \frac{\int R_y(\Delta y)dy}{R_y(0)} 
\end{equation}

Thus, the expression for instantaneous luminosity is given by

\begin{equation}
L_{b} = \frac{N_1 N_2 f}{2\pi \Sigma_x \Sigma_y}
\end{equation}

and the PCC visible cross section defined in terms of beam parameters and rate is given by

\begin{equation}
\sigma_{vis} = \frac{2 \pi \Sigma_x \Sigma_y R(0)}{N_1 N_2} 
\end{equation}

where R(0) is the peak cluster rate measured by the pixel detector after applying appropriate stability module selection.

%Van der Meer (vdM) calibration is a method used in particle physics experiments to calibrate the absolute luminosity measurement of particle colliders. The principle behind the vdM calibration is based on the measurement of the beam size and the beam crossing angle, which are used to calculate the luminosity. The vdM calibration procedure involves the following steps,

\begin{comment}
\begin{itemize}

\item  The beam size is measured using specialized detectors called beam position monitors (BPMs). These detectors are positioned along the beam pipe and measure the position of the beam at different points along its path. By analyzing the data from these detectors, the size of the beam can be determined.

\item  The beam crossing angle is the angle at which the two beams cross each other. This angle is measured using specialized detectors called luminosity monitors. These detectors measure the rate of particle collisions and their distribution along the beam pipe. By analyzing this data, the beam crossing angle can be determined.

\item  Once the beam size and the beam crossing angle are determined, the luminosity can be calculated using the vdM formula:

\begin{equation}
L = f_{rev} N_1 N_2 / (4 \pi \sigma_x \sigma_y) \sqrt{1 + (\theta_c \sigma_z / 2 \sigma_x)^2}
\end{equation}

where L is the luminosity, $f_{rev}$ is the revolution frequency of the beams, $N_1$ and $N_2$ are the number of particles in the two beams, $\sigma_x$ and $\sigma_y$ are the horizontal and vertical beam sizes, $\sigma_z$ is the longitudinal beam size, and $\theta_c$ is the beam crossing angle.

\item The beam position monitors and luminosity monitors need to be calibrated to ensure accurate measurements. This is done by comparing their readings with known values obtained from other calibration methods.

\item The luminosity measurement obtained from the vdM calibration is verified using other independent methods, such as the measurement of the number of particle collisions or the measurement of the rates of specific types of particle collisions.

\end{itemize}
\end{comment}

\section{Background Estimation}

Background contributions can arise from several sources, such as beam-gas interactions, electronic noise, cosmic rays, or other processes that produce signals in the detectors. These contributions can affect the precision of the luminosity measurement and lead to systematic uncertainties in the calibration. Beam-separation scans can be performed with increased beam separations (i.e., with the beams not fully overlapped). These scans can provide an estimate of the background contributions when the beams are not colliding. Sources of machine induced backgrounds are as follows,

\begin{itemize}

\item Beam-gas elastic interactions: In these interactions, beam particles scatter off residual gas molecules in the beam pipe without breaking the molecular structure of the gas. The scattered beam particle and the gas molecule maintain their initial identities but change their direction and energy. Although the primary beam particle does not produce secondary particles in this type of interaction, the scattered particle can still enter the detector, causing background noise. Maintaining an ultra-high vacuum inside the beam pipe helps reduce the likelihood of such interactions.

\item Beam-gas inelastic interactions: In contrast to elastic interactions, beam-gas inelastic interactions involve the beam particle and the residual gas molecule undergoing a collision that alters the structure of the gas molecule. The beam particle transfers some of its energy to the gas molecule, leading to the creation of new particles or the excitation of the gas molecule. These new particles or de-excitations can generate secondary particles, which may enter the detector and contribute to the background. As with elastic interactions, maintaining a high vacuum in the beam pipe and using beam collimation systems can help minimize beam-gas inelastic interactions.

\item Beam-halo interactions: Beam-halo refers to the particles that are not part of the beam's core but reside in the outer regions of the beam. These particles can interact with the detector materials or other elements in the beamline, such as collimators, beam pipe walls, or shielding. These interactions can produce showers of secondary particles that may enter the detector and contribute to the background. Beam-halo interactions can be mitigated using collimators to clean the halo particles from the beam and shielding the sensitive parts of the detector from direct exposure to halo particles. Additionally, continuous monitoring of the beam halo and adjusting the beam optics can help reduce the impact of beam-halo interactions.

\end{itemize}

\section{vdM fit model}

The poly2G model, or the "polynomial plus two Gaussians" model, is a fitting function that combines a second-order polynomial function and two Gaussian functions. It is a versatile and flexible model that can be used to fit various types of data, including the PCC rate plot in the context of the Van der Meer (VdM) calibration process. In a PCC rate plot, the event rate is plotted as a function of the beam separation. The poly2G model can be employed to fit the PCC rate plot to extract the beam parameters, such as the beam widths and the center positions, which are essential for the luminosity measurement. The general form of the poly2G model is as follows,

%\begin{equation}
%F(x) = p_0 + p_1x + p_2x^2 + A_1 e^{-\frac{1}{2} \left(\frac{x - \mu_1}%{\sigma_1}\right)^2} + A_2 e^{-\frac{1}{2} \left(\frac{x - \mu_2}{\sigma_2}\right)^2}
%\end{equation}

%F(x) is the value of the fitting function at position x. $p_0$, $p_1$, and $p_2$ are the coefficients of the second-order polynomial function. $A_1$ and $A_2$ are the amplitudes of the two Gaussian functions. $\mu_1$ and $\mu_2$ are the means (center positions) of the two Gaussian functions. $\sigma_1$ and $\sigma_2$ are the standard deviations (widths) of the two Gaussian functions. This equation describes the poly2G model, which combines a second-order polynomial function with two Gaussian functions. The various parameters $(p_0, p_1, p_2, A_1, A_2, \mu_1, \mu_2, \sigma_1, \sigma_2)$ can be adjusted to fit the PCC rate plot in the context of the Van der Meer calibration process. The polynomial component of the poly2G model accounts for the background contributions and any underlying trends in the data, while the Gaussian components represent the signal from the colliding beams. By fitting the PCC rate plot with the poly2G model, the beam parameters can be extracted, and any background contributions can be effectively separated from the signal.

\begin{equation}
Poly2G = Peak  \left [1+r2 \left(\frac{x-\mu} {\frac{\sigma}{1+r2}}\right)^2 \right] exp \left[-\frac{1}{2}\left(\frac{x-\mu}{\frac{\sigma}{1+r2}}\right)^2\right]
\end{equation}

where Peak is the maximum PCC rate, $\mu$ is the mean, $\sigma$ and r2 are the fit parameters.

The background estimation for the PCC rate is done with two super-separation scans SS1 and SS2. The mean and error are obtained from the $y$ projection of PCC per NB4 plotted as a function of time. The results for five different BCIDs are shown in Table~\ref{tab:vdm:SS1_SS2}, using the reprocessed PCC data for Fill 6868. The overall background correction applied to raw PCC rate is $0.02757\pm0.01987$, which is calculated by taking the average of the mean values of SS1 and SS2.

\begin{table}
  \begin{center}
    \begin{tabular}{ccccc}
    \textbf{BCID}   & \textbf{Mean (SS1)} & \textbf{Mean (SS2)} \\ \hline
      265     &  0.02902    &  0.02743    \\
        865  &    0.02572  &     0.0281  \\
       1780    &  0.02862   &     0.0286  \\
       2192   &  0.02729  &     0.02323  \\
        3380  &  0.02882  &    0.02896   \\
      \end{tabular}
    \caption{Mean for the background estimated with the SS1 and SS2 data, separately for all five BCIDs and averaged.}
    \label{tab:vdm:SS1_SS2}
  \end{center}
\end{table}

Fig. \ref{fig:fitquality} shows chi2/ndof for vdM and imaging scans with an average value of 0.4514 where the Poly2G fit model converges for all BCIDs. Peak value and beam overlap along X and Y are extracted from fit to calculate PCC visible cross section $\sigma_{vis}$. PCC visible cross section for $2\%$ rms common module vetolist is 960.601 $\pm$ 0.851(stat.) mb.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{ashish_thesis/vdM_fit_cveto.png}
    \caption{vdM fit 2\% rms common veto.}
    \label{fig:fitquality}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\textwidth]{ashish_thesis/fit_quality_chisquare.png}
    \caption{chi2/ndof for all vdM and imaging scans.}
    \label{fig:fitquality}
\end{figure}

The visible cross section per scan is averaged over all BCIDs and its scan to scan variation is shown in Fig. \ref{fig:sigmaperscan}.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{ashish_thesis/sigma_vis_per_scan.png}
    \caption{$\sigma_{vis}$ per scan where red line shows the average value.}
    \label{fig:sigmaperscan}
\end{figure}

%The Poly2G (Polynomial 2D Gaussian) fit model is a mathematical function used in Van der Meer (vdM) scans to extract the luminosity from the data obtained in the CMS experiment at the Large Hadron Collider (LHC).

%The Poly2G fit model combines a 2D Gaussian function, which describes the transverse profile of the proton beams, with a second-degree polynomial function, which describes the variation of the beam overlap with the transverse position of the beams.

%The 2D Gaussian function takes the form:

%where x and y are the transverse positions of the beams, A is the amplitude of the Gaussian function, x0 and y0 are the centers of the Gaussian function in the x and y directions, and $sigma_x$ and $sigma_y$ are the standard deviations of the Gaussian function in the x and y directions.

%The second-degree polynomial function takes the form:

%where c0, c1, c2, c3, c4, and c5 are coefficients that describe the variation of the beam overlap with the transverse position of the beams.

%The Poly2G fit model is used to fit the luminosity data obtained in vdM scans, which involve measuring the luminosity at different transverse positions of the proton beams. The fit model is fitted to the data using a least-squares minimization technique to determine the values of the fit parameters.

%The Poly2G fit model is particularly useful because it can accurately describe the transverse profile of the proton beams, which is important for accurately determining the beam overlap and hence the luminosity. The second-degree polynomial function also provides a flexible way to model the variation of the beam overlap with the transverse position of the beams, which can help to account for non-uniformities in the beam profile. Overall, the Poly2G fit model is a powerful tool for accurately extracting the luminosity from vdM scan data in the CMS experiment at the LHC.

### 2023-06-16 tesis_Ashish/Chapter4/chapter4.tex
Your commit message

\chapter{Methodology}  %Title of the First Chapter

\ifpdf
    \graphicspath{{Chapter4/Figs/Raster/}{Chapter4/Figs/PDF/}{Chapter4/Figs/}}
\else
    \graphicspath{{Chapter4/Figs/Vector/}{Chapter4/Figs/}}
\fi

%\section{Methodology}
%\label{sec:method}

\section{Datasets}

2018 luminosity data taking is divided into seven periods namely A, B, C, D1, D2, D3 and D4 as shown in Fig. \ref{fig:period_bound}. vdM data is shown during period B corresponding to Fill 6868. Run range for each period is shown in Table \ref{tab:period run ranges}.

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/period_boundary.png}
\caption{%
   2018 luminosity data taking periods showing data taking period boundaries and vdM calibration data.
}
\label{fig:period_bound}
\end{figure}

\begin{table}[htbp]
  \centering
  \begin{tabular}{@{}c@{\hspace{1cm}}p{5.5cm}p{5.5cm}@{}}
    \textbf{Period} & \textbf{Random Trigger Dataset} & \textbf{Zero Bias Dataset} \\
    2018A & \begin{tabular}{@{}p{5.5cm}@{}}/AlCaLumiPixels/Run2018A-AlCaPCCRandom-15Apr2023\_UL2018\_315252\_316062\_PCCRandom\_-v1/ALCARECO, \\ /StreamALCALUMIPIXELSEXPRESS/Run2018A-AlCaPCCRandom-Express-v1/ALCARECO\end{tabular} & /AlCaLumiPixels/Run2018A-AlCaPCCZeroBias-13Mar2023\_UL2018\_PCC-v1/ALCARECO \\
    2018B & /StreamALCALUMIPIXELSEXPRESS/Run2018B-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018B-AlCaPCCZeroBias-13Mar2023\_UL2018\_PCC-v1/ALCARECO \\
    2018C & /StreamALCALUMIPIXELSEXPRESS/Run2018C-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018C-AlCaPCCZeroBias-13Mar2023\_UL2018\_PCC-v1/ALCARECO \\
    2018D & /StreamALCALUMIPIXELSEXPRESS/Run2018D-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018D-AlCaPCCZeroBias-PromptReco-v2/ALCARECO \\
  \end{tabular}
  \caption{Dataset Information}
  \label{tab:datasets}
\end{table}

\textbf{/AlCaLumiPixels/Run2018A-AlCaPCCRandom15Apr2023\_UL2018\_315252\_316062\_PCCRandom\_-v1/ALCARECO}

%\textbf{/AlCaLumiPixels/Run2018A-AlCaPCCRandom15Apr2023_UL2018_315252_316062_PCCRandom_-v1/ALCARECO}

\begin{itemize}

\item /AlCaLumiPixels/Run2018A: This indicates that the dataset is related to the "AlCa" (ALignment and CALibration) stream, specifically for the "LumiPixels" subdetector. The data corresponds to the Run2018A period, which means it was collected during the first run period in 2018.

\item AlCaPCCRandom: This tag represents the primary dataset and the trigger path used to collect the data. "PCC" stands for "Pixel Cluster Counting" and is a method for luminosity measurement. "Random" indicates that this dataset was collected using a random trigger, which is a method to sample a fraction of the events by applying trigger on both colliding and non-colliding bunch crossings.

\item $15Apr2023_UL2018_315252_316062_PCCRandom_-v1$: This part represents the processing version, date, and run range of the dataset. "15Apr2023" is the date when this specific version of the dataset was created. "UL2018" indicates that this data has been processed using the "Ultra Legacy" (UL) campaign for the 2018 dataset, which aims to provide the highest quality data for physics analysis. The numbers $"315252_316062"$ represent the range of run numbers included in the dataset. $"PCCRandom_"$ is a reference to the Pixel Cluster Counting method used for luminosity measurement and the random trigger. "v1" denotes the version number of this processed dataset.

\item ALCARECO:
This acronym stands for "ALignment and CALibration RECOstruction." It is a data tier representing the output of specific reconstruction algorithms applied to the raw data to produce high-level objects needed for the alignment and calibration tasks.

\end{itemize}

%To summarize, this dataset is a collection of events from the CMS experiment during the Run2018A period, sampled using a random trigger. It is specifically related to the luminosity measurement using the Pixel Cluster Counting method. The dataset has been processed using the Ultra Legacy campaign, and the output contains high-level objects required for alignment and calibration tasks.

$\textbf{/StreamALCALUMIPIXELSEXPRESS/Run2018A-AlCaPCCRandom-Express-v1/ALCARECO}$

\begin{itemize}

\item /StreamALCALUMIPIXELSEXPRESS/Run2018A:
This indicates that the dataset is related to the "AlCa" (ALignment and CALibration) stream, specifically for the "LumiPixels" subdetector, and is part of the "Express" data processing tier. The data corresponds to the Run2018A period, which means it was collected during the first run period in 2018.

\item AlCaPCCRandom:
This tag represents the primary dataset and the trigger path used to collect the data. "PCC" stands for "Pixel Cluster Counting" and is a method for luminosity measurement. "Random" indicates that this dataset was collected using a random trigger, which is a method to sample a fraction of the events without specific selection criteria (i.e., unbiased events).

\item Express-v1:
This part represents the processing version and the type of data processing. "Express" indicates that this data has been processed using the "Express" campaign, which is a near-real-time processing of the data as it is collected. This type of processing is essential for providing timely feedback to the experiments and enabling rapid identification of any issues. "v1" denotes the version number of this processed dataset.

\item ALCARECO:
This acronym stands for "ALignment and CALibration RECOstruction." It is a data tier representing the output of specific reconstruction algorithms applied to the raw data to produce high-level objects needed for the alignment and calibration tasks.

\end{itemize}

%In summary, this dataset is a collection of events from the CMS experiment during the Run2018A period, sampled using a random trigger. It is specifically related to the luminosity measurement using the Pixel Cluster Counting method. The dataset has been processed using the Express campaign, and the output contains high-level objects required for alignment and calibration tasks.

%$\textbf{/AlCaLumiPixels/Run2018A-AlCaPCCZeroBias-13Mar2023_UL2018_PCC-v1/ALCARECO}$

$\textbf{/AlCaLumiPixels/Run2018A-AlCaPCCZeroBias-13Mar2023\_UL2018\_PCC-v1/ALCARECO}$

\begin{itemize}

\item /AlCaLumiPixels/Run2018A:
This indicates that the dataset is related to the "AlCa" (ALignment and CALibration) stream, specifically for the "LumiPixels" subdetector. The data corresponds to the Run2018A period, which means it was collected during the first run period in 2018.

\item AlCaPCCZeroBias:
This tag represents the primary dataset and the trigger path used to collect the data. "PCC" stands for "Pixel Cluster Counting" and is a method for luminosity measurement. "ZeroBias" indicates that this dataset was collected using a trigger with no specific selection criteria (i.e., unbiased events).

\item $13Mar2023_UL2018_PCC-v1$:
This part represents the processing version and the date of the dataset. "13Mar2023" is the date when this specific version of the dataset was created. "UL2018" indicates that this data has been processed using the "Ultra Legacy" (UL) campaign for the 2018 dataset, which aims to provide the highest quality data for physics analysis. "PCC" is again a reference to the Pixel Cluster Counting method used for luminosity measurement. "v1" denotes the version number of this processed dataset.

\item ALCARECO:
This acronym stands for "ALignment and CALibration RECOstruction." It is a data tier representing the output of specific reconstruction algorithms applied to the raw data to produce high-level objects needed for the alignment and calibration tasks.

\end{itemize}

%So, to summarize, this dataset is a collection of unbiased events from the CMS experiment during the Run2018A period. It is specifically related to the luminosity measurement using the Pixel Cluster Counting method. The dataset has been processed using the Ultra Legacy campaign, and the output contains high-level objects required for alignment and calibration tasks.

$\textbf{/AlCaLumiPixels/Run2018D-AlCaPCCZeroBias-PromptReco-v2/ALCARECO}$

\begin{itemize}

\item /AlCaLumiPixels/Run2018D:
This indicates that the dataset is related to the "AlCa" (ALignment and CALibration) stream, specifically for the "LumiPixels" subdetector. The data corresponds to the Run2018D period, which means it was collected during the fourth run period in 2018.

\item AlCaPCCZeroBias:
This tag represents the primary dataset and the trigger path used to collect the data. "PCC" stands for "Pixel Cluster Counting" and is a method for luminosity measurement. "ZeroBias" indicates that this dataset was collected using a trigger with no specific selection criteria (i.e., unbiased events).

\item PromptReco-v2:
This part represents the processing version and the type of data processing. "PromptReco" indicates that this data has been processed using the "Prompt Reconstruction" campaign, which is a near-real-time processing of the data as it is collected. This type of processing is essential for providing timely feedback to the experiments and enabling rapid identification of any issues. "v2" denotes the version number of this processed dataset.

\item ALCARECO:
This acronym stands for "ALignment and CALibration RECOstruction." It is a data tier representing the output of specific reconstruction algorithms applied to the raw data to produce high-level objects needed for the alignment and calibration tasks.

\end{itemize}

%In summary, this dataset is a collection of unbiased events from the CMS experiment during the Run2018D period, specifically related to the luminosity measurement using the Pixel Cluster Counting method. The dataset has been processed using the Prompt Reconstruction campaign, and the output contains high-level objects required for alignment and calibration tasks.

\begin{comment}

The dataset /StreamALCALUMIPIXELSEXPRESS/Run2018A-AlCaPCCRandom-Express-v1/ALCARECO, is a dataset from the CMS experiment at CERN's Large Hadron Collider (LHC). This dataset is specifically collected for luminosity measurements using pixel cluster counting (PCC) in the CMS detector by applying trigger on colliding and non-colliding bunches.

\begin{itemize}

\item StreamALCALUMIPIXELSEXPRESS: This indicates that the dataset is related to the "AlCa" (Alignment and Calibration) sub-system of the CMS detector, specifically focused on luminosity measurements using the pixel detector. The "EXPRESS" in the name signifies that this dataset is processed using the Express Stream, which is a fast data processing system for near real-time analysis of CMS data.

\item Run2018A: This represents the run period during which the data was collected. In this case, it refers to the 2018 data-taking period, specifically the "A" run.

\item AlCaPCCRandom: This indicates that the dataset is related to the "PCC" (Pixel Cluster Counting) method of luminosity measurement, and "Random" refers to the trigger used for data collection. In this case, a random trigger is used, selecting events without any specific bias.

\item Express-v1: This signifies that the dataset has been processed using the Express Stream system. The "-v1" indicates the version of the processing.

\item ALCARECO: This is the final data format of the dataset, specifically designed for alignment and calibration tasks.

%\item Data collection: The CMS detector collects data from proton-proton collisions at the LHC. For this dataset, a random trigger is used , ensuring a representative sample of events for luminosity measurements.

%\item Data processing: The raw data is processed using the Express Stream system. This is a fast processing system used for near real-time analysis of CMS data. During this process, the raw data is converted into higher-level objects, such as tracks and vertices, which are more convenient for analysis.

%\item Data filtering: ALCARECO datasets are created by applying specific filters and selections to the processed data. In this case, the filters are chosen to focus on pixel cluster counting for luminosity measurements.

%\item Dataset storage: The final ALCARECO dataset is stored and made available for analysis by researchers working on alignment, calibration, and luminosity-related studies.

\end{itemize}

 The dataset /AlCaLumiPixels/Run2018D-AlCaPCCZeroBias-PromptReco-v2/ALCARECO, is specifically collected for luminosity measurements using pixel cluster counting (PCC) in the CMS detector by applying trigger on only colliding bunches.

\begin{itemize}

\item AlCaLumiPixels: This indicates that the dataset is related to the "AlCa" (Alignment and Calibration) sub-system of the CMS detector, specifically focused on luminosity measurements using the pixel detector.

\item Run2018A: This represents the run period during which the data was collected. In this case, it refers to the 2018 data-taking period, specifically the "A" run.

\item AlCaPCCZeroBias: This indicates that the dataset is related to the "PCC" (Pixel Cluster Counting) method of luminosity measurement, and "ZeroBias" refers to the trigger used for data collection. ZeroBias triggers are unbiased, meaning they are randomly triggered and do not rely on any specific event characteristics.

\item PromptReco-v2: This signifies that the dataset has been processed using the "PromptReco" (Prompt Reconstruction) system, which is a fast processing system for real-time analysis of CMS data. The "-v2" indicates the version of the processing.

\item ALCARECO: This is the final data format of the dataset, specifically designed for alignment and calibration tasks.

%\item Data collection: The CMS detector collects data from proton-proton collisions at the LHC. For this dataset, the ZeroBias trigger is used, ensuring an unbiased sample of events for luminosity measurements.

%\item Data processing: The raw data is processed using the Prompt Reconstruction system. During this process, the raw data is converted into higher-level objects, such as tracks and vertices, which are more convenient for analysis.

%\item Data filtering: ALCARECO datasets are created by applying specific filters and selections to the processed data. In this case, the filters are chosen to focus on pixel cluster counting for luminosity measurements.

%\item Dataset storage: The final ALCARECO dataset is stored and made available for analysis by researchers working on alignment, calibration, and luminosity-related studies.

\end{itemize}

The dataset "AlCaLumiPixels/Run2018D-AlCaPCCZeroBias-PromptReco-v2/ALCARECO" dataset is a specialized dataset that provides information related to luminosity measurements using pixel detectors.

\begin{itemize}

\item AlCaLumiPixels: The term "AlCaLumiPixels" indicates that the dataset focuses on luminosity measurements obtained from the pixel detectors. The pixel detectors are part of the CMS experiment's innermost layers and are designed to precisely track the paths of charged particles produced in proton-proton collisions.

\item Run2018D: The "Run2018D" refers to a specific data-taking period or run period of the CMS experiment. The LHC operates in cycles of data-taking known as runs, which are typically identified by a year and a letter. In this case, "2018D" corresponds to a particular period of data collection in 2018.

\item AlCaPCCZeroBias: "AlCaPCCZeroBias" is a term that likely indicates the specific algorithm and event type used for luminosity measurement. The "PCC" stands for "Pixel Cluster Counting," which is an algorithm employed to estimate the instantaneous luminosity based on the information recorded by the pixel detectors. The "ZeroBias" events represent a special category of collisions where all the CMS detector systems trigger, regardless of the specific physics processes involved. These events are particularly useful for luminosity measurements.

\item PromptReco-v2: "PromptReco" refers to the reconstruction process for the prompt data. Prompt reconstruction involves the real-time processing and calibration of the recorded data immediately after it is taken. The "-v2" indicates a specific version or iteration of the prompt reconstruction process.

\item ALCARECO: "ALCARECO" stands for "ALignment CALibration RECOnditioned" data. It is a category of specialized reconstructed datasets produced with specific requirements for alignment and calibration studies. These datasets are carefully processed and conditioned to ensure accurate alignment of the CMS detector elements and precise calibration of the recorded data.

\end{itemize}

PromptReco (Prompt Reconstruction) and AlCaReco (ALignment and CALibration REConstructed Objects) are two different data processing and formatting systems used in the CMS experiment at CERN's Large Hadron Collider (LHC). While both systems are related to the processing of data collected by the CMS detector, they serve different purposes and have distinct features. Here is a comparison of the two systems:

Purpose: \\ 
PromptReco: The primary goal of the PromptReco system is to rapidly convert the raw data collected by the CMS detector into a format more suitable for physics analysis. It reconstructs the raw data into higher-level objects like tracks, vertices, and calorimeter clusters, which are then used by researchers to study various aspects of the particle collisions.

AlCaReco: The main purpose of the AlCaReco system is to provide specialized datasets for detector alignment, calibration, and other related tasks. AlCaReco datasets are generated by applying specific filters and selections to the reconstructed data (RECO), focusing on events and information that are particularly useful for alignment, calibration, and performance monitoring.

Data format: \\
PromptReco: The output of the PromptReco system is the RECO (REConstructed Objects) data format. This is the primary data format used for physics analysis in the CMS experiment, containing reconstructed objects such as tracks, vertices, and calorimeter clusters.

AlCaReco: The AlCaReco data format is designed specifically for alignment, calibration, and performance monitoring tasks. It is a more focused and compact data format, containing only the events and information relevant to the specific task, resulting in reduced data volume compared to the full RECO data.

Data processing:\\
PromptReco: The PromptReco system processes the raw data at Tier-0 of the Worldwide LHC Computing Grid (WLCG), using a series of algorithms to reconstruct the detector information into higher-level physics objects.

AlCaReco: The AlCaReco processing stream is applied after the PromptReco system, using the reconstructed data (RECO) as input. AlCaReco datasets are generated by applying specific filters and selections tailored to the needs of the alignment, calibration, and performance monitoring tasks.

%The main difference between PromptReco and AlCaReco is their purpose and the type of data they produce. PromptReco is focused on the rapid reconstruction of raw data into a format suitable for physics analysis, while AlCaReco is designed to provide specialized datasets for detector alignment, calibration, and performance monitoring tasks. Both systems play a crucial role in the overall data processing and analysis pipeline of the CMS experiment.

%AlCaReco stands for "ALignment and CALibration REConstructed Objects." It is a specific data format and processing stream used by the CMS experiment at CERN's Large Hadron Collider (LHC) for the purpose of detector alignment, calibration, and other specialized tasks. AlCaReco datasets are designed to be smaller and more focused compared to the primary reconstructed data (RECO), making them suitable for specialized analyses that require a specific set of event characteristics or detector information. The AlCaReco data format and processing stream serve several important functions: Customized event selection: AlCaReco datasets are generated by applying specific filters and selections to the reconstructed data (RECO). These filters are tailored to select events that are particularly useful for alignment, calibration, and other specialized tasks. For example, certain triggers or event topologies might be more suitable for studying the performance of a specific detector subsystem or measuring certain quantities. By selecting events with these specific characteristics, the AlCaReco datasets provide a more focused sample for the targeted analyses. Reduced data volume: One of the main advantages of AlCaReco datasets is their reduced data volume compared to the full RECO data. By selecting only the events and information relevant to the specific task, the AlCaReco data format helps save storage space and computational resources, making the data processing and analysis more efficient. Detector performance monitoring: AlCaReco datasets are used to monitor the performance of the CMS detector and its subsystems. By analyzing the data in these specialized datasets, researchers can track the detector's performance over time and identify any potential issues or areas for improvement. This information can then be used to optimize the detector's operation and ensure accurate data collection. Alignment and calibration: Accurate detector alignment and calibration are crucial for the overall performance of the CMS experiment. AlCaReco datasets provide the necessary information to perform these tasks, allowing researchers to refine the detector's geometry, timing, and energy response. This, in turn, improves the quality of the data collected by the CMS detector and increases the accuracy of the physics analyses. In summary, AlCaReco is a specialized data format and processing stream used by the CMS experiment for tasks related to detector alignment, calibration, and performance monitoring. By providing focused datasets with reduced data volume, AlCaReco enables efficient and accurate analysis of the data needed to maintain and optimize the performance of the CMS detector. AlCaReco: The main purpose of the AlCaReco system is to provide specialized datasets for detector alignment, calibration, and other related tasks. AlCaReco datasets are generated by applying specific filters and selections to the reconstructed data (RECO), focusing on events and information that are particularly useful for alignment, calibration, and performance monitoring. AlCaReco: The AlCaReco data format is designed specifically for alignment, calibration, and performance monitoring tasks. It is a more focused and compact data format, containing only the events and information relevant to the specific task, resulting in reduced data volume compared to the full RECO data. AlCaReco: The AlCaReco processing stream is applied after the PromptReco system, using the reconstructed data (RECO) as input. AlCaReco datasets are generated by applying specific filters and selections tailored to the needs of the alignment, calibration, and performance monitoring tasks.

\end{comment}

The calibration of luminosity measurement by the CMS experiment in the 2018 proton-proton data taking at $\sqrt{s}$ = 13 TeV was performed during

\begin{itemize}
\item LHC fill 6868 on June 30 and July 1, 2018 at $\sqrt{s}$ = 13 TeV
\item Zero-bias triggers on 5 bunch pairs (BCIDs 265, 865, 1780, 2192, and 3380)
recorded events rate is 27.7 kHz. 
\item "lsc1", was the "constant separation" scan, two beams were separated by 1.4 $\sigma$ and moved together in steps of 1 $\sigma$ across and back.
\item "lsc2", was the "variable separation" scan method, one beam (starting with beam 1) is moved to -2.5 $\sigma$ and then a three-point scan (a "miniscan") is performed with the other beam.
\item a normal VdM scan pair "norm4" and two short emittance scan pairs "emit4" and "emit5" were also performed.
\end{itemize}

To measure the luminosity using the pixel cluster counting method, pixel detector is divided into modules, each consisting of a number of pixels arranged in a grid. The number of pixel clusters produced in each module per unit time is proportional to the instantaneous luminosity of the collider. To implement this method, the pixel detector is operated in an integrated mode, where the detector is read out at a fixed time interval called a "lumi section". During each lumi section, the number of pixel clusters produced in each module is recorded, the rate of number of pixel clusters and visible cross section is used to determine the instantaneous luminosity of the collider. CMS software (CMSSW) version $10{\_}2{\_}2$  and $10{\_}6{\_}30$ are used for reprocessing PCC data. Datasets can be obtained by applying triggers on all bunches (colliding and non colliding) and only on colliding bunches to get random trigger and zero bias data respectively as described in previous section. Random trigger PCC dataset is reprocessed with new module vetolist to obtain afterglow corrections with improved module stability selections. Zero bias dataset is reprocessed after applying afterglow corrections using same module vetolist with more stringent selections on module stability to obtain PCC luminosity.

%To ensure accurate luminosity measurements, it is necessary to correct for various effects, such as detector inefficiencies and pileup (the presence of additional proton-proton collisions in the same bunch crossing). This is achieved through careful calibration of the detector and by using dedicated algorithms to estimate the contribution of pileup to the observed pixel cluster counts.

\begin{table}
  \begin{center}
    \begin{tabular}{ccccc}  
    \textbf{Period}   & \textbf{Run range} \\ \hline
     2018A      &        315252-316995         \\ 
     2018B      &        317080-319311         \\ 
     2018C      &        319337-320065         \\ 
     2018D1     &        320500-321665        \\ 
     2018D2     &        321710-322964         \\ 
     2018D3     &        323363-324420         \\ 
     2018D4     &        324564-325175        \\ 
      \end{tabular}
    \caption{2018 luminosity data periods with run ranges.}
    \label{tab:period run ranges}
  \end{center}
\end{table}

\section{Software tools}

%CERN ROOT is a software framework commonly used in particle physics to analyze large datasets generated by particle detectors such as the CMS experiment at CERN. One of the important measurements performed at CMS is the determination of the instantaneous luminosity, which is a measure of the rate at which particles are colliding in the detector. To measure the luminosity at CMS, the detector records signals from various sub-detectors, such as the silicon tracker and the calorimeters, which are used to reconstruct the tracks and energy deposits of particles produced in the collisions. These signals are then processed using the CERN ROOT framework to extract relevant information such as the number of collisions per second and the total integrated luminosity over a given period of time.The CERN ROOT framework is used to analyze the data from van der Meer scans and extract the luminosity calibration factors needed to convert the collision rates into actual luminosity measurements. To extract Pixel Cluster Counting (PCC) datasets from the CMS Data Aggregation Service (DAS) using a shell script, we can use the dasgoclient command-line tool. For example, following command can copy names of all root files into a text file.

%\begin{verbatim}
 % dasgoclient -query="file dataset=/AlCaLumiPixels/Run2018A-AlCaPCCZeroBias- 27Oct2022_UL2018_PCC-v1/ALCARECO instance=prod/global | grep file.name | grep  '.root'" > Run2018A.txt   
%\end{verbatim}

%\begin{itemize}

%\item  In the CMS experiment at CERN, luminosity measurements using the Pixel Cluster Counting (PCC) method are typically performed using the CMSSW framework. The luminosity module and configuration files used in CMSSW to perform PCC luminosity measurements can be generated using C++ code and Python scripts.

%\item  HTCondor is used to process PCC datasets, is a high-throughput computing (HTC) system that can be used to submits jobs for each run to efficiently manage large-scale data processing tasks, such as those required in the analysis of data from high-energy physics experiments. HTCondor provides a framework for distributing and managing the processing of this data across a large number of computing nodes. This allows the luminosity measurement to be performed more quickly and efficiently than would be possible using a traditional computing approach. Specifically,

%\item HTCondor is used to manage the processing of so-called "luminosity blocks" of data, which correspond to periods of time during which the accelerator was operating at a certain luminosity. These blocks can contain many terabytes of data, and processing them requires significant computing resources. With HTCondor, the processing of these blocks can be distributed across a large number of computing nodes, allowing the analysis to be performed in parallel. Additionally, HTCondor provides features for managing the scheduling of jobs and ensuring that data is transferred between nodes efficiently, which is critical for achieving high throughput in the analysis.

%\end{itemize}

\begin{itemize}
\item CMSSW: The CMS Software (CMSSW) is a comprehensive software framework developed for the Compact Muon Solenoid (CMS) experiment at the Large Hadron Collider (LHC) at CERN. CMSSW is used for the simulation, processing, and analysis of data collected by the CMS detector. It is designed to handle various tasks, from the generation of simulated events to the reconstruction of raw detector data, calibration, and high-level analysis. CMSSW is composed of several interconnected components and follows a modular architecture to promote flexibility, reusability, and maintainability. Some key aspects of CMSSW include, Event Data Model (EDM): The EDM serves as the foundation of CMSSW, defining the structure and organization of data objects, such as particle candidates, detector hits, and reconstructed vertices. It is designed to handle the storage, retrieval, and manipulation of these objects efficiently. The CMSSW framework is responsible for the management of software modules, the flow of data between modules, and the execution of the necessary tasks. It also handles the scheduling of tasks and the parallelization of processes, enabling efficient use of computing resources. Modules: CMSSW is built upon a collection of software modules, each responsible for a specific task, such as event generation, detector simulation, reconstruction, or analysis. These modules can be combined and customized to create a complete processing chain for a given use case. The software includes a detailed description of the CMS detector geometry, material properties, and readout electronics. This information is used during the simulation and reconstruction processes to accurately model the detector's response to particles. 
Simulation: CMSSW integrates several external tools and libraries, such as the GEANT4 toolkit, to simulate the passage of particles through the CMS detector. This includes the interactions of particles with the detector material, the production of secondary particles, and the generation of detector signals. Reconstruction: The reconstruction algorithms in CMSSW process the raw detector data, converting it into meaningful physics objects, such as tracks, calorimeter clusters, and particle candidates. These algorithms use a variety of techniques, including pattern recognition, clustering, and fitting, to extract the relevant information from the detector signals. CMSSW includes tools for the calibration of detector components and the alignment of the detector geometry. These tasks are crucial for ensuring the accurate reconstruction of physics objects and the extraction of meaningful results from the data. Analysis: The software provides a rich set of high-level analysis tools and libraries, enabling researchers to perform a wide range of physics analyses, from searches for new particles to precision measurements of Standard Model processes. Data storage and management: CMSSW uses the ROOT data format for the storage and management of data objects. ROOT is a powerful and flexible data storage and processing framework developed at CERN, which provides efficient data handling, advanced statistical analysis tools, and extensive data visualization capabilities.

\item Conditions Database (CondDB): The Conditions Database (CondDB) is a centralized data storage and management system used in high-energy physics experiments, such as the Compact Muon Solenoid (CMS) at the Large Hadron Collider (LHC) at CERN. The primary purpose of CondDB is to store non-event-related data, known as "conditions data," which is essential for the proper interpretation and analysis of the experimental data. Conditions data includes information on the detector's configuration, calibration constants, alignment parameters, and other time-dependent data that characterize the performance and status of the detector and its components. Since the conditions data is critical for accurate data processing and analysis, it must be readily accessible and easily managed. CondDB provides a central repository for storing conditions data from various sources, such as detector control systems, calibration measurements, and offline analyses. This centralization simplifies data management and ensures that all data processing tasks have access to the same, consistent information. Time-dependent data management: The database is designed to handle time-dependent data efficiently. Each data record stored in CondDB is associated with a specific time interval, known as the "IOV" (Interval of Validity). This enables the retrieval of the correct conditions data corresponding to a specific data-taking period. Data versioning: CondDB supports versioning of the conditions data, allowing researchers to track changes and updates to the data over time. This feature ensures reproducibility of results and facilitates comparisons between different data processing and analysis workflows. Access control: The database provides fine-grained access control mechanisms, enabling authorized users to read, write, and modify conditions data. This ensures the integrity of the data and prevents unauthorized modifications. CondDB is designed to handle the large volume of conditions data generated by high-energy physics experiments, with efficient data storage and retrieval mechanisms. The database is built on robust and scalable technologies, such as relational databases (e.g., Oracle, MySQL, or PostgreSQL), to ensure high performance and reliability. Integration with data processing frameworks: The Conditions Database is designed to integrate seamlessly with data processing and analysis frameworks, such as the CMS Software (CMSSW). This integration allows for the automatic retrieval and usage of conditions data during the data processing workflow, ensuring the correct data is used at each step of the process.

\item HTCondor: HTCondor is a specialized workload management system designed for distributed computing environments. Developed at the University of Wisconsin-Madison, HTCondor is an open-source system that facilitates the efficient utilization of computing resources by managing and scheduling compute jobs across a network of computers. It is widely used in various scientific domains, including high-energy physics, bioinformatics, and computer science, to handle large-scale computational tasks. HTCondor is designed to discover, monitor, and manage a heterogeneous collection of computing resources, including desktop computers, dedicated clusters, and cloud computing resources. It can efficiently allocate jobs to resources based on the requirements of the jobs and the availability of the resources. HTCondor provides a sophisticated job scheduling system, which prioritizes and assigns jobs to appropriate resources based on various criteria, such as resource availability, job requirements, and user-defined policies. The scheduler supports various scheduling strategies, including fair-sharing, priority-based, and opportunistic scheduling. HTCondor is designed to be fault-tolerant and can automatically recover from failures or interruptions in the computing environment. In case a job fails to complete due to a system crash or network disconnection, HTCondor can reschedule the job to another available resource, ensuring that the job eventually completes. Data management: HTCondor provides built-in data management capabilities, allowing users to transfer input and output files between the submitting machine and the executing machines. This feature simplifies data handling in distributed computing environments and ensures that jobs have access to the required data. HTCondor provides a range of security mechanisms to protect the integrity and confidentiality of both the jobs and the computing resources. These mechanisms include authentication, authorization, data encryption, and sandboxing, which prevent unauthorized access and tampering. HTCondor enables users to monitor the progress of their jobs, providing information on job status, resource usage, and performance. Users can also control their jobs by pausing, resuming, or canceling them as needed. Interoperability and extensibility: HTCondor is designed to interoperate with other computing systems and can be easily integrated into existing workflows. It supports various job submission languages, such as the Job Submission Description Language (JSDL) and the ClassAd language, and can be extended with custom plugins and scripts. HTCondor is compatible with a wide range of operating systems, including Linux, macOS, and Windows, enabling users to harness the full potential of their computing resources, regardless of the underlying platform.

\item CMS Data Aggregation System (DAS): The CMS Data Aggregation System (DAS) is a data management tool designed for the Compact Muon Solenoid (CMS) experiment at the Large Hadron Collider (LHC) at CERN. It serves as a centralized query system that simplifies the process of locating and accessing various types of CMS data and metadata. DAS aggregates information from multiple data services and presents it in a unified manner, enabling researchers to easily search for and retrieve the data they need for their analyses. DAS provides a unified query language that allows users to perform searches across different data services using a single, consistent syntax. This simplifies the process of data discovery and reduces the learning curve associated with using multiple data services. DAS is designed to aggregate data from various data services within the CMS experiment, including data storage systems, data catalogs, and data processing services. By consolidating this information, DAS enables researchers to easily search for and access the data they need, without having to interact with multiple data services individually. Data caching: To improve performance and reduce the load on the underlying data services, DAS employs a caching mechanism that temporarily stores the results of previous queries. This allows DAS to quickly return results for frequently requested queries, without having to query the data services each time. DAS can merge data from multiple sources, providing users with a consolidated view of the information. This feature simplifies data analysis by eliminating the need for researchers to manually merge data from different sources. DAS supports data transformation operations, such as filtering, sorting, and aggregation, allowing users to customize the output of their queries to meet their specific needs. This feature helps researchers focus on the most relevant information and reduces the amount of data they need to process. DAS is designed to be extensible, enabling the integration of additional data services as needed. This allows DAS to adapt to the evolving needs of the CMS experiment and continue to provide a unified interface for data discovery and access. DAS offers a web-based user interface that allows users to submit queries and view the results using a standard web browser. This makes it easy for researchers to access and use the system, regardless of their location or computing environment. API access: In addition to the web-based user interface, DAS provides an Application Programming Interface (API) that allows users to programmatically submit queries and retrieve results. This enables the integration of DAS with other software tools and workflows used by the CMS experiment.

\item Brilcalc: The brilcalc tool is a software package designed to calculate and analyze luminosity data for the Compact Muon Solenoid (CMS) experiment at the Large Hadron Collider (LHC) at CERN. Luminosity is a crucial parameter in high-energy physics experiments like CMS, as it measures the rate of collisions in a particle accelerator and directly affects the statistical significance of experimental results. Brilcalc serves as a command-line interface (CLI) tool, which allows users to extract, manipulate, and visualize luminosity data from the CMS experiment. It is built upon the BRIL (Beam Radiation Instrumentation and Luminosity) project, which is responsible for the development and maintenance of beam monitoring and luminosity measurement systems at the CMS experiment. Users can extract luminosity data for a specific data-taking period or data range from the CMS database. The data can be filtered by various criteria, such as run number, fill number, and data-taking conditions. Data manipulation: The tool offers the capability to process and manipulate the extracted luminosity data. Users can perform operations such as unit conversion, data scaling, and data normalization to make the data suitable for further analysis. Brilcalc allows users to perform basic statistical analyses on the luminosity data, such as calculating integrated luminosity, average luminosity, and instantaneous luminosity. These analyses help physicists understand the performance of the CMS detector and plan future data-taking strategies. The tool can generate plots and graphs to visualize the luminosity data, making it easier for researchers to interpret the results and identify trends or anomalies. Brilcalc is designed to be extensible, allowing users to develop custom plugins and scripts for advanced data analysis and visualization tasks.

\item CERN ROOT: The ROOT data analysis framework, developed by CERN, is widely used in high-energy physics experiments, including CMS. ROOT offers a rich set of tools for data processing, statistical analysis, and visualization. In the context of PCC luminosity measurement, ROOT is employed to analyze and process the output data from CMSSW, perform statistical analyses, and generate plots for data visualization.

\item Shell/Bash Scripting: Shell and bash scripting are widely used in high-energy physics research to automate repetitive tasks and manage workflows. These scripting languages offer flexibility and portability, allowing researchers to create custom scripts tailored to their specific needs. In the context of PCC luminosity measurement, shell/bash scripts are employed to streamline data processing, automate job submission to HTCondor, and manage the overall workflow, enhancing productivity and reducing the chances of human error.

\item DASgoclient: The DASgoclient is a command-line interface for the CMS Data Aggregation System (DAS). It offers researchers an alternative method for accessing various CMS data services without using the web-based DAS interface. The DASgoclient allows users to query and retrieve data in a more scriptable and automated manner, making it an essential tool for managing datasets and streamlining the data retrieval process for PCC luminosity measurements.

\end{itemize}

\section{Pixel module veto list}

The goal of minimizing instabilities in PCC (Pixel Cluster Counting) luminosity measurement is to ensure accurate and consistent results. To achieve this, a pixel module vetolist is created for each run period to keep track of good and bad modules. The stability of each module is determined based on the change in the ratio of module PCC and total PCC, referred to as the module weight as shown in Fig. \ref{fig:mod_weight}.

\begin{itemize}
\item Lumi section duration: The data collected for luminosity measurements are divided into lumi sections, each lasting for 23.36 seconds.

\item Analyzing module weights: During each lumi section, the module weights for all pixel modules are studied to track their performance over time. This helps in identifying good and bad modules, as shown in Fig. \ref{fig:goodbadmodules}.

\item Pixel detector composition: The pixel detector used for the 2018 luminosity measurement comprises two main components - the BPIX (barrel pixel detector) with 4 barrel layers, and the FPIX (forward pixel detector) with three forward disks. These two components consist of 1184 and 672 pixel modules, respectively.

\item Selection criteria: Only pixel modules that demonstrate consistent and reliable performance throughout the entire 2018 year are considered good and included in the analysis. Modules that do not meet these criteria are classified as bad and excluded from the luminosity measurements.
\end{itemize}

By carefully analyzing the module weights and excluding the bad modules from the analysis, the instabilities in PCC luminosity measurements can be minimized. This process ensures that the data used for luminosity measurements are of high quality and can produce accurate results.

%To minimize instabilities in PCC luminosity measurement, pixel module vetolist is created for each run period. Module stability is based on change in the ratio of module PCC and total PCC which is defined as module weight. Change in module weights with lumi section (23.36s) is studied for all modules and used to select good and bad modules as shown in Fig. \ref{fig:goodbadmodules}. Pixel detector used for 2018 luminosity measurement consists of 4 barrel layers (BPIX) and three forward disks (FPIX) including 1184 and 672 pixel modules respectively. Only pixel modules that are found to show good performance during the entire 2018 year are selected.

\begin{figure}[!htp]
\centering
\includegraphics[width=0.9\textwidth]{ashish_thesis/Module_weight.png}
\caption{%
   Method to obtain module weights as a function of lumi section for categorizing good and bad modules. X profile of TH2F histogram (module PCC/total PCC per lumi section) is obtained. X profile is then filled in a TGraph after removing points with error $>$ 0.05. TGraph is normalized with the mean of Y projection of TH2F histogram to obtain module stability profile.
}
\label{fig:mod_weight}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/good_bad_modules.png}
\caption{%
   Variation of normalized module weight with time. Modules showing significant change in module weight (shown in right figure) over time having large rms/mean values are used to make module vetolist.
}
\label{fig:goodbadmodules}
\end{figure}

Module vetolist is first created for period B, vdM Fill and then for other periods A, C, D1, D2, D3 and D4 as follows,

Run 2018B and vdM Fill:
\begin{itemize}

\item Poor statistics lumi sections are removed by applying selection on total PCC Fig. \ref{fig:PCC_cut} and \ref{fig:f_it}.

\item All barrel layer 1 modules are removed as these modules are significantly affected by dynamic inefficiency effects, where the hit efficiency decreases at higher $L_{inst}$ due to the readout chip not being able to process all of the hits.                                                                              
\item A loose selection of 7\% based on rms/mean of module weight profile is applied where mean and rms values are obtained from y projection of module weight profile. Modules with significantly large rms/mean are removed with this loose selection as shown in Fig. \ref{fig:outliermodules}.

\item Module stability is re-evaluated based on rms/mean values using an iterative method where in each step, appropriate selections are applied to remove bad modules until stable luminosity is attained as sshown in Fig. \ref{fig:sec_it_cut}.                                                      
\end{itemize}

Run 2018A, C and D:                                                                      
\begin{itemize}

\item Period B module veto list is applied to these periods to determine remaining bad modules.

\item same procedure is used as period B.

\item module weight comparisons between period B and these periods is done and modules with more than 3 sigma change in module weights are removed as shown in Fig. \ref{fig:mod_w_com} and Fig \ref{fig:mod_w_com_1}.      .                                                                             
\end{itemize}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/Run2018B_totalPCC_cut.png}
\caption{%
 Total PCC as a function of lumi section for period 2018B.  Appropriate selection on total PCC is applied to remove low statistics lumi sections.
}
\label{fig:PCC_cut}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/first_iteration.png}
\caption{%
   A loose cut of 7\% is applied on rms/mean values of module stability profile to remove outlier modules.
}
\label{fig:f_it}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/cut_selection.png}
\caption{%
   RMS/mean of module weight profile for all modules. A loose selection of 7\% is applied to remove bad modules. Appropriate selections are applied in each iterative step to remove other bad modules.
}
\label{fig:outliermodules}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/second_iteration_cut.png}
\caption{%
 Final selection on RMS/mean of 2\% is applied to obtain module veto list for each period.
}
\label{fig:sec_it_cut}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/mod_weight_comparison.png}
\caption{%
   Change in module weights between period A and B for all modules left after applying 2\% rms module vetolist.
}
\label{fig:mod_w_com}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/mod_weight_comp_1.png}
\caption{%
   Projection of change in module weights between period A and B. Modules showing more than 3 sigma change are added to the module vetolist.
}
\label{fig:mod_w_com_1}
\end{figure}

 2\% selection on rms/mean of module weight profile gives the best stability for all pixel detector barrel layers and forward disks. Bad modules found after applying this 2\% selection in the final iterative step are used to constitute a 2 $\%$ rms module veto list for each period as shown in Table \ref{tab:per period veto}.

\begin{table}
  \begin{center}
    \begin{tabular}{ccccc}  
    \textbf{Period}   & \textbf{\# bad modules} & \textbf{\# good modules} \\ \hline
     2018A      &   1276   &  580    \\  
     2018B      &    802  &     1054  \\ 
     2018C      &   1076  &    780   \\ 
     2018D1     &  1169  &     687  \\ 
     2018D2     &  1184  &    672   \\ 
     2018D3     &  1081  &    775   \\ 
     2018D4     &  1032  &     824  \\ 
      \end{tabular}
    \caption{2 \% rms module vetolist for each period showing number of good and bad modules.}
    \label{tab:per period veto}
  \end{center}
\end{table}

To further improve the stability of PCC luminometer, $2\%$ rms common module vetolist is created as shown in Table \ref{tab:2commonveto}. Common module veto list is a combination of module veto list of all run periods A, B, C, D1, D2, D3 and D4. Approach to make a common module veto list is to start by combining module vetolists of period A,B and C, then combine A,B, C, D1 and so on. Less than $9\%$ of the pixel modules remain after applying module stability selections to be used for final luminosity measurement.

\begin{table}
  \begin{center}
    \begin{tabular}{ccccc}  
    \textbf{Period}   & \textbf{\# bad modules} & \textbf{\# good modules} \\  \hline
     2018A + B + C      &  1417   &  439    \\  
     2018A + B + C + D1      &   1534  &   322    \\ 
     2018A + B + C + D1 + D2      &   1629 &    227   \\ 
     2018A + B + C + D1 + D2 + D3     &   1668 &   188    \\ 
     2018A + B + C + D1 + D2 + D3 + D4     &  1701 &     155  \\ 
      \end{tabular}
    \caption{2\% rms common module vetolist. This vetolist is created by combining module vetolists for each period.}
    \label{tab:2commonveto}
  \end{center}
\end{table}

The relative contribution to PCC luminosity from each pixel detector layer and disk after removing low statistics lumi sections and applying 2\% rms common module vetolist is shown in Fig. \ref{fig:stabprof}.

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/ProfileX_combined_testing_LUM_20-001.png}
\caption{%
   Stability profiles of pixel detector layer and disk modules for 2\% rms common module vetolist.
}
\label{fig:stabprof}
\end{figure}

%\subsection{Reasons for the inclusion of certain modules in the veto list}

The module veto list in particle physics experiments is a list of detector modules that are excluded from the analysis of data due to their known or suspected high rate of background events or other issues that could affect the accuracy of the measurement. The inclusion of certain modules in the veto list is based on various factors, including:

\begin{itemize}

\item Radiation damage: The harsh radiation environment in the LHC can cause damage to the silicon pixel sensors over time, leading to increased leakage currents, noise, or reduced charge collection efficiency.

\item Manufacturing defects: Defects in the silicon material or issues during the manufacturing process can result in poorly performing pixel modules. These defects may not be immediately evident but can become more pronounced over time.

\item Electronic noise: Noisy electronic components or crosstalk between channels can lead to an increased number of false signals or noise in the pixel module data.

\item Temperature variations: Temperature fluctuations can affect the performance of the pixel modules, leading to changes in their noise levels, gain, or charge collection efficiency.

\item High voltage issues: Problems with the high voltage supply to the pixel modules can result in unstable operation, leading to erratic behavior or complete module failure.

\item Partial module failure: A pixel module may suffer from partial failure, with some pixels or readout channels not functioning properly. This can lead to an increased number of dead or noisy pixels in the module.

\item Readout or data acquisition issues: Errors in the readout electronics or data acquisition system can lead to data corruption or loss, affecting the performance of the pixel modules.

\item Calibration issues: Inaccurate or outdated calibration parameters can result in incorrect measurements, leading to the appearance of abnormal behavior in the pixel module data.

\item Firmware or software issues: Bugs in the firmware or software responsible for controlling and reading out the pixel modules can lead to abnormal behavior or incorrect measurements.

\item Mechanical or alignment issues: Mechanical stresses or misalignments during the installation or operation of the pixel detector can affect the performance of the pixel modules or cause them to fail.

\item Contamination or environmental factors: Contamination of the pixel modules by dust, moisture, or other substances can affect their performance or cause them to fail. Similarly, external environmental factors, such as magnetic fields or vibrations, can impact the operation of the pixel modules.

\end{itemize}

The inclusion of certain modules in the veto list is based on a careful analysis of the detector performance and the expected background rates in a given experiment. By excluding modules with high background rates or other issues, the analysis can be improved and the accuracy of the measurement can be increased.

\section{Afterglow corrections}

Type 1 and Type 2 afterglow corrections are essential for obtaining accurate PCC measurements. Type 1 afterglow noise, also known as electronic spillover, is caused by the long waveform of the signal in silicon. On the other hand, Type 2 afterglow noise is the exponentially decaying detector activation due to the production of secondary particles when high-energy particles interact with the detector material as shown in Fig. \ref{fig:pcc_afterglow}. Afterglow noise is corrected by creating a model of the afterglow tail of a single colliding bunch, which is then normalized to the luminosity of the colliding bunch crossing. A bunch-by-bunch histogram containing bunch trains undergoes afterglow correction, where the afterglow model is multiplied with the luminosity of each colliding bunch pair and subsequently subtracted from all following bunches. This correction process is performed iteratively for all colliding bunch pairs, ensuring that a given bunch crossing is fully corrected before being used to correct the subsequent bunch crossings. The afterglow correction, or scale factor, is calculated by taking the ratio of the corrected and uncorrected PCC. This scale factor is then applied to individual bunch-by-bunch histograms in the zero bias data. In addition to afterglow corrections, pedestal correction is another important aspect to consider. Pedestal correction refers to the adjustment of baseline values in the detector readout to account for any systematic offsets or drifts. This process involves measuring the detector's output when no signal is present and subtracting this baseline value from the measured signal during data collection. By performing pedestal correction, the accuracy and stability of the detector's measurements are significantly improved, contributing to more reliable PCC measurements.

%Type 1 and 2 afterglow corrections are measured and applied to the PCC measurement. Type 1 afterglow noise is electronic spillover due to long waveform of the signal 549 in silicon and Type 2 afterglow noise is exponentially decaying detector activation due to production of secondary particles when high energy particles interact with detector material as shown in Fig. 15. Afterglow noise is corrected by making a model of afterglow tail of a single colliding bunch, normalized to the luminosity of the colliding bunch crossing. Bunch-by-bunch histogram containing bunch trains is corrected for afterglow where afterglow models is multi554 plied with the luminosity of each colliding bunch pair and subtracted from all following bunches. This correction is performed iteratively over all colliding bunch pairs such that a given bunch crossing is fully corrected before it is used to correct the succeeding bunch crossings. The afterglow correction (or scale factor) can be calculated by taking the ratio of corrected and uncorrected PCC. This scale factor is applied to individual bunch-by-bunch histograms in the zero bias data.

\begin{itemize}

\item Type 1 afterglow correction: Type 1 afterglow refers to the residual signals in the detector caused by particles from previous bunch crossings. These particles can be trapped in the detector's sensitive volume, leading to an overestimation of the actual number of pixel clusters. The Type 1 afterglow correction aims to correct for this by subtracting the expected contribution of these residual signals from the raw PCC data.

\item Type 2 afterglow correction: Type 2 afterglow is associated with the activation of detector material due to high-energy particle interactions. When high-energy particles interact with the detector material, they can cause the material to become radioactive. The decay of these radioactive isotopes produces additional signals in the detector, which can lead to an overestimation of the number of pixel clusters. The Type 2 afterglow correction aims to account for these additional signals by subtracting the expected contribution of the activation-induced background from the raw PCC data.

\item Pedestal afterglow correction: The pedestal afterglow refers to the baseline noise level in the detector, which can be influenced by factors such as temperature fluctuations, electronic noise, and radiation damage. This noise can cause an over- or underestimation of the actual number of pixel clusters. The pedestal afterglow correction aims to correct for this by adjusting the raw PCC data based on a measurement of the pedestal noise level.

\end{itemize}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/afterglow_type1_type2.png}
\caption{%
Afterglow corrections are calculated from cluster rate measurements in empty bunches. Electronic spillover (“Type-1”). Type-1 noise is due to long waveform of the signal in silicon. First empty bunch after bunch train is used to calculate it. Exponentially decaying detector activation (“Type-2”).  Type-2 noise is due to production of secondary particles when high energy particles interact with detector material. All empty bunches after bunch train are used to calculate it.
}
\label{fig:pcc_afterglow}
\end{figure}

### 2023-06-16 tesis_Ashish/Chapter5/chapter5.tex
Your commit message

\chapter{Systematic uncertainty in PCC luminosity measurement}  %Title of the First Chapter

\ifpdf
    \graphicspath{{Chapter1/Figs/Raster/}{Chapter1/Figs/PDF/}{Chapter1/Figs/}}
\else
    \graphicspath{{Chapter1/Figs/Vector/}{Chapter1/Figs/}}
\fi

%\section{Systematic uncertainty in PCC luminosity measurement}
%\label{sec:sysunc}

\section{Uncertainties associated with the Van der Meer calibration}

\begin{itemize}

\item Orbit Drift: Refers to the gradual displacement of the beam orbit from its ideal trajectory due to various effects such as ground motion, magnetic field fluctuations, and thermal expansion. This can result in reduced beam intensity and beam quality.

\item X-Y Nonfactorization: Refers to the failure of the x and y coordinates of a particle beam to factorize, meaning that the beam profile cannot be expressed as a product of independent x and y profiles. This can result in beam asymmetries and other effects.

\item Beam-Beam Deflection: Refers to the mutual interaction of two colliding particle beams, resulting in the deflection of the individual beams due to the electromagnetic fields generated by the other beam. This effect can lead to beam losses and reduced luminosity.

\item Dynamic $\beta$: Refers to the time-varying beta function of a particle beam, which describes the rate at which the beam diverges or converges as it propagates. This effect can be important for beam stability and the control of beam emittance.

\item Beam Current Calibration: Refers to the process of accurately measuring the current of a particle beam, which is essential for many beam diagnostics and control systems.

\item Ghosts and Satellites: Refers to unwanted signals in a detector or measurement system that can arise from various sources such as scattered radiation, electronic noise, or interference from other particles. These can lead to inaccurate measurements and reduced data quality.

\item Scan to Scan Variation: Refers to the variation in experimental results obtained from different scans or measurements, which can arise from various sources such as statistical fluctuations, instrument drift, or systematic errors.

\item Bunch to Bunch Variation: Refers to the variation in the properties of individual particle bunches within a beam, such as their intensity, energy spread, or emittance. This effect can be important for beam tuning and optimization.

\item Cross-Detector Consistency: Refers to the agreement between measurements obtained from different detectors or measurement systems. This is important for verifying the accuracy and reliability of experimental results.

\item Background Subtraction: Refers to the process of removing unwanted signals from a measurement or detector system that arise from sources other than the physical phenomenon of interest, such as noise, cosmic rays, or other particles. This is essential for obtaining accurate measurements of the physical signal.

\end{itemize}

\section{Uncertainties associated with physics data taking}

\begin{itemize}

\item Stability: The CMS pixel detector is a complex instrument with many components, including silicon sensors and readout electronics, that must operate consistently and with high precision over long periods. Any variations in the performance of the detector can affect the efficiency of the pixel cluster counting method and lead to uncertainties in the luminosity measurement.

One example of how the stability of the detector can affect the luminosity measurement is through changes in the detector's noise level. The noise level refers to the level of electronic noise present in the detector, which can interfere with the detection of pixel clusters produced by proton-proton collisions. If the noise level increases, the efficiency of the pixel cluster counting method may decrease, leading to an underestimation of the luminosity. Conversely, if the noise level decreases, the efficiency of the method may increase, leading to an overestimation of the luminosity.

Another example is changes in the efficiency of the pixel detector. The efficiency of the detector refers to the fraction of proton-proton collisions that produce pixel clusters that can be detected and counted by the method. Any changes in the efficiency of the detector, for example due to changes in the gain or response of the silicon sensors, can lead to uncertainties in the luminosity measurement.

To mitigate these uncertainties, the CMS collaboration performs regular calibrations and monitoring of the detector performance, as well as cross-checks with other luminosity measurement techniques

Systematic uncertainties due to stability in the detector itself for the pixel cluster counting method are typically estimated by studying the performance of the method over time and comparing it to simulations or other measurements. Uncertainties due to changes in the noise level and detector efficiency are typically estimated separately and combined to obtain the total systematic uncertainty

\item Linearity: the luminosity obtained from the PCC method is compared to that obtained from the HFOC method for a given set of collisions. Any deviations between the two measurements are used to estimate the linearity uncertainty in the PCC method.

The linearity uncertainty is typically quantified as a systematic uncertainty in the luminosity measurement, expressed as a percentage of the measured luminosity. This uncertainty can be estimated by fitting the PCC and HFOC measurements to a linear function and calculating the deviation of the PCC measurement from the linear fit.

\item Type 1 afterglow refers to the persistence of charge in the pixels of the detector after a collision event. This charge can be produced by various sources, such as ionization due to the passage of charged particles, or leakage currents in the readout electronics. If this charge is not properly accounted for, it can be mistakenly counted as pixel clusters produced by subsequent collision events, leading to an overestimation of the luminosity.

Type 2 afterglow refers to the persistence of noise in the detector after a collision event. This noise can be produced by various sources, such as thermal or radiation-induced effects, and can also interfere with subsequent collisions. If this noise is not properly accounted for, it can lead to a reduction in the efficiency of the pixel cluster counting method and an underestimation of the luminosity.

\end{itemize}

\section{Comparison of PCC with HFOC luminosity}

### 2023-06-16 tesis_Ashish/Chapter6/chapter6.tex
Your commit message

\chapter{Results}  %Title of the First Chapter

\ifpdf
    \graphicspath{{Chapter1/Figs/Raster/}{Chapter1/Figs/PDF/}{Chapter1/Figs/}}
\else
    \graphicspath{{Chapter1/Figs/Vector/}{Chapter1/Figs/}}
\fi

%\section{Results}
%\label{sec:result}

\section{Luminosity measurement results using the pixel cluster counting method}
\section{Comparison of the luminosity results for different module veto list}
\section{Comparison of the results with other luminosity measurement techniques}
\section{Final uncertainties in PCC luminosity measurement}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/pcc_stability_begin.png}
\caption{%
   Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
}
\label{fig:PCC_stab_begin}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/rms_mean_all_modules_B.png}
\caption{%
   Mean and rms values are obtained from module weight distribution by obtaining its y projection to plot rms/mean as a function of module number index.
}
\label{fig:rms_mean_B}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/first_iteration_stability.png}
\caption{%
   Luminosity fractions of various layer and disk after applying 7\% loose selection.
}
\label{fig:f_it_stability}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/remaining_second_iteration.png}
\caption{%
 rms/mean of module stability profile after applying 7\% loose cut.
}
\label{fig:sec_it_remain}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/second_iteration_stability.png}
\caption{%
   Luminosity fraction after applying third selection of 2\% on rms/mean values to removed tail. After final iteration, profile for layers and disks is very stable. Only one Fill around lumi section 27000 shows instability.
}
\label{fig:sec_it_stability}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/vdm_rms_mean.png}
\caption{%
   rms/mean values of module stability profile for vdM data. 
}
\label{fig:vdm_cut}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/first_iteration_vdm.png}
\caption{%
   rms/mean values of module stability profile after applying a selection of 4\% cut . 
}
\label{fig:vdm_cut}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/vdm_stability.png}
\caption{%
   Pixel layer and disk for vdM data shows excellent stability with the 2\% rms module veto list consisting of 800 bad modules. After applying module veto list from physics run period B on top of module veto list formed by outliers, pixel layers and disks luminosity ratios shows excellent stability.
}
\label{fig:vdm_stability}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/module_weights_per_period_veto.png}
\caption{%
   Module weights for 2\% rms module vetolist consisting of 800 good modules and 1056 bad modules.
}
\label{fig:mod_weight_new_veto}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/vdm_beam_position.png}
\caption{%
   X and Y positions of two beams showing length scale scans, vdM scans and emittance scans.
}
\label{fig:beam_plot_vdm}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/before_after_vdm_stability.png}
\caption{%
   Luminosity fraction (stability plots) before and after applying 2\% rms module vetolist.
}
\label{fig:b_a_stability_vdm}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.8\textwidth]{ashish_thesis/old_new_veto.png}
\caption{%
   klm
}
\label{fig:old_new_vetolist}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2018A_before_after_stability.png}
\caption{%
   Stability plots for period A before and after applying module vetolist.
}
\label{fig:stability_A}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Run2018C_before_after_stability.png}
\caption{%
   Stability plots for period C before and after applying module vetolist.
}
\label{fig:stability_C}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Run2018D1_before_after_stability.png}
\caption{%
   Stability plots for period D1 before and after applying module vetolist.
}
\label{fig:stability_D1}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Run2018D2_before_after_stability.png}
\caption{%
   Stability plots for period D2 before and after applying module vetolist.
}
\label{fig:stability_D2}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Run2018D3_before_after_stability.png}
\caption{%
   Stability plots for period D3 before and after applying module vetolist.
}
\label{fig:stability_D3}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Run2018D4_before_after_stability.png}
\caption{%
   Stability plots for period D4 before and after applying module vetolist.
}
\label{fig:stability_D4}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/raw_corr_hist.png}
\caption{%
   Raw and corrected PCC with its ratio.
}
\label{fig:stability_D4}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Run2018A_old_new_veto.png}
\caption{%
   PCC as a function of lumi section for old and new vetolist with its ratio for period A.
}
\label{fig:old_new_veto_A}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Run2018B_old_new_veto.png}
\caption{%
    PCC as a function of lumi section for old and new vetolist with its ratio for period B.
}
\label{fig:old_new_veto_B}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Run2018C_old_new_veto.png}
\caption{%
    PCC as a function of lumi section for old and new vetolist with its ratio for period C.
}
\label{fig:old_new_veto_C}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Run2018D1_old_new_veto.png}
\caption{%
    PCC as a function of lumi section for old and new vetolist with its ratio for period D1.
}
\label{fig:old_new_veto_D1}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Run2018D2_old_new_veto.png}
\caption{%
   PCC as a function of lumi section for old and new vetolist with its ratio for period D2.
}
\label{fig:old_new_veto_D2}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Run2018D3_old_new_veto.png}
\caption{%
    PCC as a function of lumi section for old and new vetolist with its ratio for period D3.
}
\label{fig:old_new_veto_D3}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Run2018D4_old_new_veto.png}
\caption{%
    PCC as a function of lumi section for old and new vetolist with its ratio for period D4.
}
\label{fig:old_new_veto_D3}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/vdm_fit_old_new_veto.png}
\caption{%
  PCC rate fit for old and new veto.
}
\label{fig:old_new_veto_vdmfit}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/sigmavis_old_new_veto.png}
\caption{%
   PCC visible cross section averaged over bunch ids for each scan for old and new veto.
}
\label{fig:old_new_veto_sigmavis}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/4per_rms_veto.png}
\caption{%
   klm
}
\label{fig:4per_veto}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2per_rms_veto.png}
\caption{%
   X and Y plane vdM fit for BCID 0865 using 2\% rms  vetolist.
}
\label{fig:2per_veto}
\end{figure}

\begin{comment}

\begin{figure}[!htp]
\centering
\includegraphics[width=|\textwidth]{ashish_thesis/new_framework_vdm.png}
\caption{%
   klm
}
\label{fig:vdm_new_f}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/vdm_fit_4per_rms_veto.png}
\caption{%
   vdM fit for 4\% rms common module vetolist.
}
\label{fig:vdm_fit_4rms}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/sigmavis_4per_rms.png}
\caption{%
   PCC visible cross section for 4 percent rms common vetolist.
}
\label{fig:sigmavis_4rms}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/sigmavis_diff_veto.png}
\caption{%
   klm
}
\label{fig:sigmavis_diff_veto}
\end{figure}

\begin{table}[!ht]
\centering
\topcaption{%
    pcc visible cross section for different module vetolist.
}
\begin{tabular}{ccccc}
    \textbf{Module veto list} & \textbf{PCC visible cross section values (mb)} & \textbf{Uncertainty} \\ \hline
    Old veto (LUM PAS 2018) & 5982 & 37 (0.08%) stat+syst \\
    New per period veto (Period B) & 9229.4  & 7.7 (0.08%) stat \\
    4\% rms common veto & 1673.49  & 0.93 (0.05%) stat \\
    2\% rms common veto & 959.94  & 0.92 (0.09%) stst \\
\end{tabular}
\label{tab:pccvis_diffveto}
\end{table}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/sys_unc_totPCC_cut.png}
\caption{%
   Selection on total PCC to remove low statistics lumi section for all period.
}
\label{fig:totpcccut_sys_unc}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/emittance_scans.png}
\caption{%
   Emittance scans are vdM like scans performed at the beginning and end of almost every LHC Fill to monitor stability of luminometers. 2018 emittance scans were done in 9 separation steps, collecting data for 10 s at each step. We observed instabilities in the ratio of PCC and HFOC luminometers during emittance scans. 
}
\label{fig:emitscan}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_hfoc_ratio_stability_old_veto.png}
\caption{%
   Left: X profile of PCC/HFOC luminosity ratio as a function of lumi section for old veto showing instabilities.  Right: Y projection of the X profile of the luminosity ratio. The standard deviation of this projection is taken as the systematic uncertainty due to stability.
}
\label{fig:pcc_hfoc_old}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_hfoc_ratio_stability_new_veto.png}
\caption{%
  Left: X profile of PCC/HFOC luminosity ratio as a function of lumi section for new veto showing instabilities.  Right: Y projection of the X profile of the luminosity ratio. The standard deviation of this projection is taken as the systematic uncertainty due to stability.
}
\label{fig:pcc_hfoc_new}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_hfoc_mean_rms_periods_new_veto.png}
\caption{%

}
\label{fig:pcc_hfoc_new_mean_rms}
\end{figure}

\begin{table}[!ht]
\centering
\topcaption{%
    PCC/ HFOC luminosity mean and rms values for new per period vetolist showing variation in mean values across period.
}
\begin{tabular}{ccccc}
    \textbf{Period} & \textbf{mean} & \textbf{rms} &  \textbf{rms/mean} \\ \hline
    A & 1.006 & 0.004183 & 0.004158 \\
    B & 0.9981  & 0.003133 & 0.0031389 \\
    C & 0.9989  & 0.003009 & 0.003012\\
    D1 & 1.003  & 0.002441 & 0.002433 \\
    D2 & 1.001  & 0.0029 & 0.00289 \\
   D3  & 1  & 0.002115 & 0.002115 \\
   D4  & 1.002  & 0.003673 & 0.003666 \\ 
\end{tabular}
\label{tab:pccvis_diffveto}
\end{table}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/4per_rms_common_veto.png}
\caption{%
   4 per common veto
}
\label{fig:4per common veto}
\end{figure}

\begin{table}[!ht]
\centering
\topcaption{%
    A method to make 4\% rms commpon module vetolist.
}
\begin{tabular}{ccccc}
    \textbf{Common module vetolist} & \textbf{# bad modules} & \textbf{# good modules} \\ \hline
    A, B, C & 1293 & 563  \\
    A, B, C, D1 & 1421  & 435  \\
    A, B, C, D1, D2 & 1522  & 334 \\
    A, B, C, D1, D2, D3 & 1574  & 282  \\
   A, B, C, D1, D2, D3, D4  & 1615  & 241 \\
\end{tabular}
\label{tab:pccvis_diffveto}
\end{table}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_hfoc_ratio_stability_4per_common_veto.png}
\caption{%
   Left: X profile of PCC/HFOC luminosity ratio as a function of lumi section for 4\% rms commpon module veto showing instabilities.  Right: Y projection of the X profile of the luminosity ratio. The standard deviation of this projection is taken as the systematic uncertainty due to stability.
}
\label{fig:4per common veto sys}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/2per_rms_common_veto.png}
\caption{%
   A method to make 2\% rms common veto.
}
\label{fig:2per common veto}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_hfoc_ratio_stability_2per_common_veto.png}
\caption{%
   Left: X profile of PCC/HFOC luminosity ratio as a function of lumi section for 2\% rms commpon module veto showing instabilities.  Right: Y projection of the X profile of the luminosity ratio. The standard deviation of this projection is taken as the systematic uncertainty due to stability.
}
\label{fig:2per common veto pcc hfoc}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_hfoc_4_2_rms_mean.png}
\caption{%
  iygjh
}
\label{fig:twoper common veto pcc hfoc rms mean}
\end{figure}

\begin{table}[!ht]
\centering
\topcaption{%
    A method to make 4\% rms commpon module vetolist.
}
\begin{tabular}{ccccc}
    \textbf{Period} & \textbf{# bad modules} & \textbf{# good modules} \\ \hline
    A & 1293 & 563  \\
    B & 1421  & 435  \\
    C & 1522  & 334 \\
    D1 & 1574  & 282  \\
   D2  & 1615  & 241 \\
\end{tabular}
\label{tab:pccvis_diffveto}
\end{table}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_layer_disk_stability_2per_veto.png}
\caption{%
PCC stability plots for each layer/Disk for all period using 2\% rms common module veto.
}
\label{fig:pcclayerdisktwopercommonveto}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/stability_unc_diff_veto.png}
\caption{%
kjbhgjklh
}
\label{fig:stabilityuncallveto}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_hfoc_linearity_sys_unc.png}
\caption{%
kjbhgjklh
}
\label{fig:linearitypcchfoc}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_hfoc_new_veto_linearity.png}
\caption{%
kjbhgjklh
}
\label{fig:linearitypcchfoc}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_hfoc_linearity_sys_unc_2per_common_veto.png}
\caption{%
kjbhgjklh
}
\label{fig:linearitypcchfoc}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/lineairty_diff_veto_sys_unc.png}
\caption{%
kjbhgjklh
}
\label{fig:linearitypcchfoc}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_layer_disk_stability_4_commonveto.png}
\caption{%
kjbhgjklh
}
\label{fig:linearitypcchfoc}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/pcc_layer_disk_mean_rms.png}
\caption{%
kjbhgjklh
}
\label{fig:linearitypcchfoc}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/lineairty_diff_veto_period_variation_slope.png}
\caption{%
kjbhgjklh
}
\label{fig:linearitypcchfoc}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/type1_type2_af_residuals_oldveto_oldp.png}
\caption{%
kjbhgjklh
}
\label{fig:linearitypcchfoc}
\end{figure}

\end{comment}

### 2023-06-16 tesis_Ashish/Chapter7/chapter7.tex
Your commit message

\chapter{Phase II upgrade of the CMS Tracker}  %Title of the First Chapter

\ifpdf
    \graphicspath{{Chapter7/Figs/Raster/}{Chapter7/Figs/PDF/}{Chapter7/Figs/}}
\else
    \graphicspath{{Chapter7/Figs/Vector/}{Chapter7/Figs/}}
\fi

%\section{Overview of the Phase II upgrade of the CMS Tracker}
%\label{sec:PhaseIItracker}

The Phase II upgrade of the CMS Tracker is a crucial project undertaken to maintain the effectiveness of the CMS experiment during the High Luminosity LHC (HL-LHC) run, which is expected to start in 2027. The HL-LHC will significantly increase the instantaneous luminosity, leading to a higher number of proton-proton collisions per bunch crossing. This higher collision rate poses several challenges, including increased radiation levels, higher data rates, and more complex event environments. The Phase II upgrade of the CMS tracker comprises two main components: the Inner Tracker (IT) and the Outer Tracker (OT). The Inner Tracker consists of three main sub-components: the TEPX (Tracker Endcap Pixel), the TFPX (Tracker Forward Pixel), and the TBPX (Tracker Barrel Pixel) detectors. These sub-components are designed to handle the increased radiation levels and data rates in the HL-LHC environment. The Outer Tracker is responsible for detecting charged particles in the outer region of the CMS detector. It consists of two key subsystems: the silicon strip tracker and the silicon macro pixel tracker.

%The Phase II upgrade of the CMS tracker is a major upgrade of the tracking system of the Compact Muon Solenoid (CMS) experiment at the Large Hadron Collider (LHC) at CERN. The upgrade is designed to improve the performance of the CMS tracker, enabling more precise measurements of the properties of particles produced in proton-proton collisions at the LHC.

\begin{enumerate}

\item Inner Tracker: The Inner Tracker is the innermost part of the CMS Tracker, closest to the collision point. It is designed to provide high-resolution position measurements of charged particles in a high-density environment, as well as excellent radiation tolerance. The Inner Tracker is crucial for the precise determination of the primary and secondary vertices (interaction points) and the accurate reconstruction of decay paths of short-lived particles. The Inner Tracker of the CMS experiment during the Phase II Upgrade will consist of three main subcomponents: TEPX (Tracker Endcap Pixel), TFPX (Tracker Forward Pixel), and TBPX (Tracker Barrel Pixel). These subsystems together form the new high-resolution, highly granular, and radiation-tolerant pixel tracking system.

\begin{itemize}

\item TBPX (Tracker Barrel Pixel): The TBPX subsystem is located in the central region of the Inner Tracker, arranged in a barrel geometry around the beam axis. It consists of several concentric cylindrical layers of high-resolution pixel sensors, providing precise measurements of charged particle trajectories in the xy-plane. The upgraded TBPX will feature higher granularity pixel sensors to better handle the increased event rates and radiation levels expected during the HL-LHC era.

\item TFPX (Tracker Forward Pixel): The TFPX subsystem covers the forward regions of the Inner Tracker, extending the coverage in the pseudorapidity ($\eta$) direction. Like the TBPX, it consists of high-resolution pixel sensors, arranged in multiple concentric discs around the beam axis. The TFPX will provide precise position measurements for charged particles in the forward and backward regions, complementing the coverage provided by the TBPX.

\item TEPX (Tracker Endcap Pixel): The TEPX subsystem is located further out in the forward and backward regions, surrounding the TFPX subsystem. It consists of additional concentric discs of pixel sensors, further extending the tracking coverage in the pseudorapidity direction. The TEPX helps to ensure efficient tracking performance in the high-$\eta$ regions, where the particle density is lower compared to the central region.

\end{itemize}

%The TBPX, TFPX, and TEPX subsystems will form a highly efficient, high-resolution Inner Tracker capable of providing precise position measurements for charged particles produced in proton-proton collisions at the LHC. The upgraded pixel-based Inner Tracker will be crucial for maintaining the CMS experiment's excellent performance during the high-luminosity and high-radiation environment expected during the HL-LHC era.

\item Outer Tracker: The Outer Tracker is designed to provide additional tracking points for charged particles as they traverse through the CMS detector. This extra information helps improve the overall track reconstruction accuracy and efficiency. In the Phase II Upgrade, the Outer Tracker will be based on the novel concept of "Tracker-Trigger," which combines tracking and triggering functionalities.

\begin{itemize}

\item In the upgraded Outer Tracker, silicon strip sensors will be used to form "trigger primitives" - early-stage track candidates - that are passed to the Level-1 Trigger system. This approach helps to reduce the data volume and allows the CMS experiment to maintain its excellent physics performance in the face of increased event rates.

\item The Outer Tracker will consist of multiple layers of strip sensor modules, organized in barrel and endcap regions. The sensor modules will be connected to custom-designed readout electronics that process the data in real-time and transmit the trigger primitives to the Level-1 Trigger system.

\end{itemize}

%\end{enumerate}

%\item Pixel Detector: The new pixel detector will have smaller pixels than the existing one, which will improve the spatial resolution of the detector. The new pixels will be 50 x 50 micrometers in size, compared to 100 x 150 micrometers in the existing detector. The new detector will also be more radiation tolerant, which means that it will be able to withstand the high radiation levels near the LHC beamline without losing performance. The new detector will consist of four barrel layers and six forward disks, providing coverage out to a pseudorapidity of 4.

%\begin{enumerate}
%\renewcommand{\labelenumi}{\roman{enumi})}
 %\item Tracker Endcap Pixel detector (TEPX): TEPX is a specialized pixel detector that will be added to the endcap region of the CMS tracker. It will be located in the forward region of the detector, covering a pseudorapidity range of 1.8 to 2.9. TEPX will consist of two disks on each side of the detector, with each disk containing 96 modules of pixel sensors.

%\item Tracker Forward Pixel detector (TFPX): TFPX is a specialized pixel detector that will be added to the forward region of the CMS tracker. It will be located in front of the existing pixel detector and will cover a pseudorapidity range of 2.5 to 4.0. TFPX will consist of four disks on each side of the detector, with each disk containing 24 modules of pixel sensors.

%\item Tracker Barrel Pixel detector (TBPX): TBPIX is a specialized pixel detector that will be added to the barrel region of the CMS tracker. It will be located in between the existing pixel detector layers and will cover a pseudorapidity range of 0 to 2.5. TBPIX will consist of four layers of pixel sensors, each layer containing 192 modules.

%\end{enumerate}

%\item Strip Detector: The new strip detector will have larger and thinner silicon sensors, which will improve the spatial resolution of the detector. The new sensors will be 100 micrometers thick, compared to 320 micrometers in the existing detector, and they will be up to 12 centimeters long, compared to 10 centimeters in the existing detector. The new readout electronics will be faster and more radiation tolerant than the existing ones. The new strip detector will have a total of 10 layers, providing coverage out to a pseudorapidity of 2.7.

\item Timing layer is a new addition to the CMS Tracker during the Phase II upgrade, designed to provide precise time measurements of charged particles passing through the detector. These measurements help in distinguishing between particles originating from different vertices in the same event and reducing the impact of pileup on event reconstruction. The timing layer uses Low Gain Avalanche Detectors (LGAD) as the active material. LGADs are a type of silicon sensor that incorporates a multiplication layer to generate an avalanche of charge carriers when a charged particle passes through the detector. This multiplication process results in a faster signal response and improved time resolution compared to traditional silicon sensors. When a charged particle traverses the timing layer, it creates electron-hole pairs in the LGAD sensor. The electric field within the sensor separates these charge carriers, and the multiplication layer amplifies the signal through the avalanche process. The charge carriers generated by the passing particle are collected by the pixel or strip electrodes on the LGAD sensor. These electrodes are designed to minimize the signal collection time, further improving the timing layer's time resolution. The electrical signals from the LGAD sensors are processed by custom-designed front-end electronics. These electronics amplify, shape, and digitize the signals, converting them into a form suitable for further processing and analysis. The front-end electronics also include time-to-digital converters (TDCs) to precisely measure the arrival time of the signals. The timing layer aims to achieve a time resolution of approximately 30-40 picoseconds. This high-resolution timing information enables the CMS Tracker to distinguish between particles from different vertices, effectively reducing the impact of pileup on event reconstruction and improving the accuracy of particle identification. The timing layer covers a pseudorapidity range of $|\eta| < 2.5$, providing precise timing measurements throughout the CMS Tracker. This wide coverage ensures that accurate timing information is available for particles originating from a broad range of interaction points within the detector. The timing layer's mechanical support structure is designed to be lightweight and radiation-tolerant, minimizing the impact on the overall material budget of the CMS Tracker. The support structure also incorporates efficient cooling systems to manage the heat generated by the sensors and electronics, ensuring stable operation and performance.

%\item Timing Layer: The new timing layer will consist of small, fast silicon sensors that will provide precise timing information for particles passing through the detector. The sensors will have a time resolution of less than 50 picoseconds, which will enable the separation of particles that are produced close together in time. The timing layer will be located in the forward region of the detector, where the particle flux is highest.

%\item Mechanical Support: The new tracker will be supported by a new lightweight, carbon-fiber support structure, which will reduce the amount of material in front of the detector and improve its performance. The new support structure will also be more compact than the existing one, which will allow more space for other detector components.

%\item Data Acquisition: The data acquisition system of the CMS tracker will be upgraded to handle the increased data rates and provide faster readout times. The upgraded system will use new custom-designed ASICs (Application-Specific Integrated Circuits) that will be able to process the data from the tracker at a rate of 320 gigabits per second.

\item Data Acquisition (DAQ) system for the Phase II CMS Tracker must handle the increased data rates and complexity associated with the high-luminosity phase of the LHC (HL-LHC). The HL-LHC is expected to achieve a peak luminosity of about $5-7.5 \times 10^{34} cm^{-2}s^{-1}$, which is around 5-7 times higher than the initial LHC design luminosity. This increased luminosity leads to a higher collision rate and more complex events, which the DAQ system must handle. Data Rates: The upgraded CMS Tracker will generate a large amount of data due to the increased granularity of the pixel and strip sensors. The data rates from the tracker modules are expected to be several terabits per second (Tbps) during the HL-LHC operation. Trigger Rate: The Level-1 Trigger system in the Phase II Upgrade is designed to accept events at a rate of up to 750 kHz. The DAQ system must handle the transmission of trigger primitives to the Level-1 Trigger system and buffer the full event data until the trigger decision is made. Optical Links: The high-speed optical links used for data transmission between the Front-End Electronics (FEE) and off-detector electronics are expected to operate at data rates of 10-25 Gbps or higher to handle the large data volumes generated by the upgraded tracker. Buffering and Storage: The off-detector electronics must be able to buffer and store the full event data generated by the tracker modules until the Level-1 Trigger decision is made. The required buffering capacity depends on the trigger rate and the average event size but is expected to be in the order of several terabytes to accommodate the high data rates and trigger latencies. Processing Latency: The DAQ system must process the raw detector data and form trigger primitives within a very tight time constraint. The processing latency budget for the formation of trigger primitives in the Outer Tracker is expected to be around a few microseconds.

\end{enumerate}

\section{New Inner tracker and its features}
\label{sec:tepx}

The High Luminosity (HL)-LHC will increase instantaneous luminosity to unprecedented value of $7.5 \times 10^{34} cm^{-2} s^{-1}$ which corresponds to 200 proton-proton collisions per bunch crossing (pileup). Run 2 pixel detector will not be able to handle the extreme radiation environment, resolve nearby particle tracks and operate properly to give a reliable estimate of the instantaneous luminosity for high pileup values. That is why it will be replaced by a new pixel detector which will be composed of three subdetectors: tracker barrel pixel detector (TBPX), tracker forward pixel detector (TFPX) and tracker endcap pixel detector (TEPX). TEPX will have better radiation tolerance, increased granularity, improved two-track separation, improved estimation of hit rate and statistical precision, extended tracking acceptance $|\eta|=4$ with Disk 4 Ring 1 operating as an independent luminometer \cite{Klein:2017nke}. \\

\section{Phase II TEPX detector}

Tracker endcap pixel detector (TEPX) consists of four double disks per side (-Z and +Z) with each double disk containing five rings as shown in Fig. 25 having 20, 28, 36, 44 and 48 modules respectively. One double disk has four surfaces with +Z side containing modules with even module number in front layers (L1 $\&$ L2) and modules with odd module number in back layers (L3 $\&$ L4) from Ring 1 to Ring 4 and for Ring 5, modules with odd module number in front layers and modules with even module number in back layers as shown in Fig. 26. For -Z side, four surfaces contain modules with odd module number in front layer and modules with even module number in back layer from Ring 1 to Ring 4 and for Ring 5, modules with even module number in front layer and modules with odd module number in back layer. \\

\begin{figure}[H]
  \centering
  \includegraphics[width=1 \columnwidth]{./tepx_tt.png}
  \caption{ \onehalfspacing Left: A layout of the CMS Phase II inner tracker showing four TEPX disks, eight TFPX disks and four barrel layers. Right: Diagram showing one double disk of TEPX with five rings \cite{Klein:2017nke}.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1 \columnwidth]{./fourlayers.png}
  \caption{ \onehalfspacing Fours layers of one double disk of TEPX showing module arrangement in rings for each layer. Ring 1, 2, 3, 4 and 5 consists of 20, 28, 36, 44 and 48 modules respectively. }
  \label{fig:CMS}
\end{figure}

%\subsection{Expected improvements in luminosity measurement with the new TEPX detector}
\subsection{Phase II CMS simulation samples}

 Simulated data samples for Phase II include full CMS detector description and uses official CMS software (CMSSW) version $10-6-0-patch2$ which calls GEANT4 for particle and energy deposit simulation as well as for reconstruction \cite{Agostinelli:2002hh}. These samples contain single-neutrino event overlaid with a variable number of minimum-bias events (events with any amount of real energy detected in CMS) to simulate different pileup values. The statistics for samples with average pileup values from 0.5 to 2 is 500000 events per step and for average pileup values between 10 and 200, statistics is 100000.

\begin{table}[htbp]
  \centering
  \caption{Phase II upgrade of CMS tracker datasets}
  \label{tab:sample}
  \begin{tabular}{ccc}
    \hline
    \textbf{pileup} & \textbf{Total number of events} & \textbf{Dataset name} \\
    \hline
    noPU  & 500000 & /RelValNuGun/CMSSW_10_6_0_patch2-106X_upgrade2023_realistic_v3_2023D42noPU-v1/GEN-SIM-RECO \\
     0.5& 500000 &  /RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU0p5-v1/GEN-SIM-RECO\\
     1&  & 500000 &   /RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU1-v1/GEN-SIM-RECO\\
     1.5 & 500000 &   /RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU1p5-v1/GEN-SIM-RECO\\
     2&  &  500000 &   /RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU2-v1/GEN-SIM-RECO\\
     10&  &  100000&   /RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU10-v1/GEN-SIM-RECO\\
      30&  &  100000&   /RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU30-v1/GEN-SIM-RECO\\
     50&  &  100000&   /RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU50-v1/GEN-SIM-RECO \\
     100&  & 100000 & /RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU100-v2/GEN-SIM-RECO\\
      140&  &  99600&  /RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU140-v2/GEN-SIM-RECO\\
     200&  &  100000&  /RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU200-v1/GEN-SIM-RECO\\
    %\hline
  \end{tabular}
\end{table}

$/RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU200-v1/GEN-SIM-RECO$
This dataset represents a simulated event sample generated using the CMS software framework, CMSSW, for the phase-2 upgrade of the CMS detector at the Large Hadron Collider (LHC).

\begin{itemize}

\item RelValNuGun: This refers to the type of generated events in this dataset. "RelVal" is short for "Release Validation," meaning that this sample is used for validating the performance of the CMS software release. "NuGun" refers to the specific event generator setup used for this dataset, which is a neutrino gun. In this setup, neutrinos are produced uniformly throughout the detector, providing a simple event topology for testing the software and detector response.

\item $CMSSW_10_6_0_patch2$: This refers to the version of the CMS Software (CMSSW) used to generate and process the dataset. In this case, it is version 10.6.0 with patch 2 applied, containing specific software improvements or bug fixes.

\item $PU25ns_106X_upgrade2023_realistic_v3_2023D42PU200$: This part contains several details about the dataset conditions:

\item PU25ns: This indicates that the dataset includes simulated pileup events with an average of 25 collisions per bunch crossing, separated by 25 nanoseconds.
\item 106X: This refers to the software release cycle (10.6.X) used for this dataset.
\item $upgrade2023_realistic_v3$: This specifies that the dataset is for the planned 2023 upgrade of the CMS detector, using a "realistic" geometry and conditions version 3, which simulates the expected detector performance and environment.
\item 2023D42PU200: This is a specific identifier for the simulated detector layout (D42) and conditions for the 2023 upgrade, with an emphasis on the 200 pileup events included in the simulation.
GEN-SIM-RECO: These are the processing steps applied to the dataset:

\item GEN: The "Generator" step, where the initial particle-level events are generated using Monte Carlo methods.
\item SIM: The "Simulation" step, where the detector's response to the generated particles is simulated, taking into account the detector geometry, materials, and electronics.
\item RECO: The "Reconstruction" step, where the simulated detector hits are processed to reconstruct the physics objects (e.g., particles and their trajectories), which are then used for further analysis.

This dataset represents a set of simulated neutrino gun events, generated and processed with the CMS software version $10.6.0_patch2$, for the phase-2 upgrade of the CMS detector in 2023. The dataset includes realistic detector geometry and conditions, and 25ns pileup events, with an emphasis on 200 pileup events. The dataset has undergone the generation, simulation, and reconstruction steps, making it suitable for validation and analysis tasks.

\end{itemize}

\begin{table}[htbp]
  \centering
  \caption{Events per file for each pileup}
  \label{tab:sample}
  \begin{tabular}{ccc}
     \textbf{Pileup} & \textbf{Events per file} \\
     \hline
     noPU &   2000\\
     0.5 &   2000\\
     1&    1800\\
      1.5&  1500\\
      2&   1400\\
     10&    500\\
     30&    200\\
      50&   100\\
      100&   100\\
     140&    100\\
       200&    100\\
  \end{tabular}
\end{table}

\begin{table}[htbp]
  \centering
  \caption{Events processed for each pileup}
  \label{tab:sample}
  \begin{tabular}{ccc}
     \textbf{Pileup} & \textbf{Number of events processed} \\
     \hline
     noPU & 10000  \\
     0.5 &  100600 \\
     1&    87400\\
      1.5& 74900 \\
      2&  66200 \\
     10&   21800 \\
     30&    10000\\
      50&   5000\\
      100&   5000\\
     140&    5000\\
       200&    5000\\
  \end{tabular}
\end{table}

\section{Luminosity determination using TEPX - counting clusters/coincidences}

Luminosity determination using PCC method for Phase II HL-LHC will be based on counting the number of clusters in TEPX Disk 4 Ring 1. The innermost ring of the last disk of TEPX (D4R1) is located at 2.65 m away from the interaction point that is beyond the tracking acceptance ($|\eta| = 4$) and as this region has few tracking points, it can be solely used for the purpose of luminosity measurement by using the full available trigger rate and bandwidth.

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/tepx_clusters.png}
  \caption{TEPX cluster map in the XY plane for pileup 200 simulated sample. Map showing coordinates of TEPX clusters in CMS global coordinate system. It shows clusters in one TEPX disk consisting of 5 rings. Hot regions are showing the module overlap for all rings (red, orange, green, yellow). Number of x bins is 1000, x bins range from -50 to 50. x bin size is 0.1 cm. Number of y bins is 1000, y bins range from -50 to 50. y bin size is 0.1 cm.}
  \label{fig:tepx_cl}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/tepx_D4R!_clusters._allpupng.png}
  \caption{Left: Distribution of number of clusters for TEPX Disk 4 Ring 1 for all pileup values. Right: Distribution of number of clusters for TEPX Disk 4 Ring 1 for all low pileup values. }
  \label{fig:tepx_cl_allPU}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/tepx_coincidences.png}
  \caption{Left: TEPX coincidences in phi map in the XY plane for pileup 200 simulated sample. Right:TEPX coincidences in R map in the XY plane for pileup 200 simulated sample. Number of x bins is 1000, x bins range from -50 to 50. x bin size is 0.1 cm and Number of y bins is 1000, y bins range from -50 to 50. y bin size is 0.1 cm.}
  \label{fig:tepx_coinc}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/tepx_D4R1_coin_allpu.png}
  \caption{Left: Distribution of number of two fold coincidences for TEPX Disk 4 Ring 1 for all pileup values. Right: Distribution of number of two fold coincidences for TEPX Disk 4 Ring 1 for all low pileup values.}
  \label{fig:tepx_coin_allPU}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/tepx_D4_3foldcoin_allpu.png}
  \caption{Distribution of number of three fold coincidences for TEPX Disk 4 all rings for all pileup values.}
  \label{fig:tepx_3foldcoin_allPU}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/tepx_D4_3foldcoin_lowpu.png}
  \caption{Distribution of number of three fold coincidences for TEPX Disk 4 all rings for low pileup values.}
  \label{fig:tepx_3foldcoin_allPU}
\end{figure}

\subsubsection{Old algorithm for counting TEPX two fold coincidences}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/oldvariable_xy.png}
\caption{%
   Old X, Y variables used for defining two fold coincidences clusters in phi.
}
\label{fig:oldvar_xy}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/overlap_modules2_Ring1.png}
\caption{%
 XY cluster map showing module overlap within the same ring in a disk that gives rise to two fold coincidences in phi.
}
\label{fig:overlap_2foldinphi}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/twofoldcoin_inphi_PU0p5_200.png}
\caption{%
 Separation between X coordinates of two clusters for pileup 0.5 and 200 showing distribution total, true and fake two fold coincidences in phi.
}
\label{fig:dx_twofold}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/twofoldcoin_cluster_y.png}
\caption{%
    Separation between Y coordinates of two clusters for pileup 0.5 and 200 showing distribution total, true and fake two fold coincidences in phi.
}
\label{fig:dy_twofold}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/cut_optimization_twofoldcoin.png}
\caption{%
 Cut optimization for two fold coincidences based on x, y variables to compute coincidence cluster separation.
}
\label{fig:cutopdxdy}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/cut_optimization_residual.png}
\caption{%
  Residual obtained after doing linear fit for different values of dx and dy. Two fold coincidences does not show decrement for high pileup when more stringent selections are applied on dx, dy variables.
}
\label{fig:res_dxdycut}
\end{figure}

\subsection{New algorithm for counting TEPX two fold coincidences}

\subsection{TEPX two fold coincidences in phi}

A new algorithm for luminosity determination based on counting two fold coincidences is proposed that applies selections using dr and $d\phi$ variables to minimize non-linearity for high pileup values as these variables take into account track angle and its curvature. Two fold coincidences are those hits which are created by the module overlap regions between various layers of one TEPX double disk. Two fold coincidences are better way to distinguish between a real hit and random electrical noise. They are more likely to be real hit than random electrical noise. Two fold coincidence in $\phi$ will involve modules overlapping in the same ring in front and back layers of one double disk as shown in top part of Fig. 27 and Fig. 28 while two fold coincidence in r will require modules overlapping between successive rings in the front (L1 $\&$ L2) and back layers (L3 $\&$ L4) of one double disk as shown in bottom part of Fig. 27. Luminosity calculated based on counting coincidences has an advantage over clusters that afterglow effects are tiny in the case of coincidences  %\cite{Collaboration:2706512} \cite{brilsim} \cite{brilsim1}\cite{brilsim2}.

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/dr_dphi_variables.png}
\caption{%
  New r, phi variables used to define coincidence clusters. These variables take into account track angle and curvature.
}
\label{fig:drdphi_diagram}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/new_variables.png}
\caption{%
   Possible new variable to replace x, y variable for defining coincidence clusters.
}
\label{fig:newvar}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/deltaR.png}
\caption{%
 dR
}
\label{fig:dR}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/delta_r.png}
\caption{%
  dr
}
\label{fig:dr}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/dphi.png}
\caption{%
 dphi 
}
\label{fig:dphi}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/D4R1_S2_drdphi_cut.png}
\caption{%
  Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 1 (+Z). Appropriate selection on dr, dphi are used to minimize fake two fold coincidence clusters.
}
\label{fig:cluster_dr_dphi_dist}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/D4R2_S2_drdphicut.png}
\caption{%
   Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 2 (+Z). Appropriate selection on dr, dphi are used to minimize fake two fold coincidence clusters.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/D4R3_S2_drdphi_cut.png}
\caption{%
  Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 3 (+Z). Appropriate selection on dr, dphi are used to minimize fake two fold coincidence clusters.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/D4R5_drdphicut.png}
\caption{%
  Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 5 (+Z). Appropriate selection on dr, dphi are used to minimize fake two fold coincidence clusters.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/D4R1S2_fit.png}
\caption{%
   Example fit using single gaussian function of cluster count as a function of dr variable for Disk 4 Ring 1 (+Z).
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/D4R1S2_dr_dphi_cut.png}
\caption{%
 Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 1 (+Z). 1 sigma selection on dr and dphi equal to 0.04 are used to minimize fake two fold coincidence clusters.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/D4R2S2_dr_dphi_cut.png}
\caption{%
   Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 2 (+Z). 1 sigma selection on dr and dphi equal to 0.04 are used to minimize fake two fold coincidence clusters.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/D4R3S2_dr_dphi_cut.png}
\caption{%
    Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 3 (+Z). 1 sigma selection on dr and dphi equal to 0.04 are used to minimize fake two fold coincidence clusters.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/D4R4S2_dr_dphi_cut.png}
\caption{%
  Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 4 (+Z). 1 sigma selection on dr and dphi equal to 0.04 are used to minimize fake two fold coincidence clusters.  
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/D4R5S2_dr_dphi_cut.png}
\caption{%
  Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 5 (+Z). 1 sigma selection on dr and dphi equal to 0.04 are used to minimize fake two fold coincidence clusters.  
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/D4R1S2_fit_PU0p5.png}
\caption{%
  Example fit using single Gaussian function of cluster count as a function of dr variable for pileup 0.5 Disk 4 Ring 1 (+Z).
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/D4R5_fit_PU0p5.png}
\caption{%
 Example fit using single Gaussian function of cluster count as a function of dr variable for pileup 0.5 Disk 4 Ring 5 (+Z). 
}
\label{fig:cluster_ring}
\end{figure}

\begin{table}[htbp]
  \centering
  \caption{dr cut values for two fold coincidences in phi for all disks and rings}
  \label{tab:disk_values}
  \begin{tabular}{cccccc}
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} & \textbf{Ring 4} & \textbf{Ring 5} \\
    \hline
    -1 & 0.00633554 & 0.00709231 & 0.00757662 & 0.008659   & 0.00872148 \\
    -2 & 0.00594206 & 0.00663493 & 0.00718173 & 0.00766371 & 0.00797059 \\
    -3 & 0.00594206 & 0.00663493 & 0.00660603 & 0.00713035 & 0.00679445 \\
    -4 & 0.00530235 & 0.00587692 & 0.00616465 & 0.00661972 & 0.00660599 \\
    1  & 0.00635769 & 0.0071538  & 0.00780034 & 0.00863764 & 0.00883121 \\
    2  & 0.00587583 & 0.00656126 & 0.00700576 & 0.00773345 & 0.00786885 \\
    3  & 0.00557387 & 0.00617934 & 0.00664346 & 0.0070085  & 0.00727192 \\
    4  & 0.0053299  & 0.00586655 & 0.0061499  & 0.00667791 & 0.00678366 \\
  \end{tabular}
\end{table}

\begin{table}[htbp]
  \centering
  \caption{dphi cut values for two fold coincidences in phi for all disks and rings}
  \label{tab:mdphi_cuts_values}
  \begin{tabular}{cccccc}
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} & \textbf{Ring 4} & \textbf{Ring 5} \\
    \hline
    -1 & 0.000856727  & 0.00128078   & 0.00151297   & 0.00151297   & 0.0016561    \\
    -2 & 0.000765842  & 0.00110698   & 0.00131104   & 0.00143555   & 0.00150265   \\
    -3 & 0.000684645  & 0.000975385  & 0.00115899   & 0.00126858   & 0.00131598   \\
    -4 & 0.000598839  & 0.000862728  & 0.00104327   & 0.00112621   & 0.00115609   \\
    1  & 0.000877912  & 0.00125898   & 0.0015378    & 0.00164165   & 0.00173015   \\
    2  & 0.00076339   & 0.00110755   & 0.00132174   & 0.00144755   & 0.00150547   \\
    3  & 0.000679543  & 0.000972429  & 0.00116735   & 0.00125955   & 0.00132885   \\
    4  & 0.000609859  & 0.000881345  & 0.00101584   & 0.00112554   & 0.00118477   \\
  \end{tabular}
\end{table}

\begin{table}[htbp]
  \centering
  \caption{dr mean values obtained from fit for two fold coincidences in phi for all disks and rings}
  \label{tab:mdr_cuts_offset_values}
  \begin{tabular}{cccccc}
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} & \textbf{Ring 4} & \textbf{Ring 5} \\
    \hline
    -1 & 0.0342041  & 0.0511416 & 0.0676943 & 0.0834355 & 0.0984932 \\
    -2 & 0.0298276  & 0.0445398 & 0.0589828 & 0.0727454 & 0.0853587 \\
    -3 & 0.0260326  & 0.0386608 & 0.05122   & 0.0632478 & 0.0746467 \\
    -4 & 0.0227089  & 0.0336467 & 0.044476  & 0.0551065 & 0.06484   \\
    1  & 0.0341565  & 0.0511018 & 0.0676485 & 0.0835835 & 0.0984028 \\
    2  & 0.0298515  & 0.0444016 & 0.0589681 & 0.0727789 & 0.0854843 \\
    3  & 0.0260239  & 0.0387303 & 0.0511824 & 0.0633755 & 0.0742994 \\
    4  & 0.022729   & 0.0336624 & 0.0445526 & 0.0550466 & 0.0644863 \\
  \end{tabular}
\end{table}

\subsection{TEPX two fold coincidences in R}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.5\textwidth]{ashish_thesis/2foldinR.png}
\caption{%
  All possible module overlaps between different rings that can give rise to two fold coincidences in R.
}
\label{fig:cluster_ring}
\end{figure}

\begin{table}[htbp]
\centering
\caption{Various types of two fold coincidences in R in one TEPX double disk with module overlaps and z separation is shown in the table.}
\label{tab:module_connections}
\begin{tabular}{ccc}
\textbf{Two fold in R types} & \textbf{Module overlaps} & \textbf{dz} \\ \hline
A & R1L3-R2L4 & 0.4 \\
B & R1L1-R2L4 & 1.2 \\
C & R1L1-R2L2 & 0.4 \\
D & R3L3-R2L4 & 0.4 \\
E & R2L2-R3L3 & 0.4 \\
F & R3L1-R2L2 & 0.4 \\
G & R3L3-R4L4 & 0.4 \\
H & R3L1-R4L4 & 1.2 \\
I & R3L1-R4L2 & 0.4 \\
J & R5L3-R4L4 & 0.4 \\
K & R4L2-R5L3 & 0.4 \\
L & R5L1-R4L2 & 0.4 \\ 
\end{tabular}
\end{table}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/moduleoverlapinR_1.png}
\caption{%
  Example of module overlap between different ring modules that can give rise to two fold coincidences in R.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/twofoldinRmethod.png}
\caption{%
  Example of module overlap between different ring modules in the first two and last two layers of one tepx double disk that can give rise to two fold coincidences in R.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/moduleoverlapfortwofoldinR.png}
\caption{%
   Module overlap between different ring modules that can give rise to two fold coincidences in R.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/onetoonemoduleoverlap2xinR_table.png}
\caption{%
   Module overlap between different ring modules that can give rise to two fold coincidences in R.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/l1l2_2xinr.png}
\caption{%
   Module overlap between different ring modules that can give rise to two fold coincidences in R.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/l3l4_2xinr.png}
\caption{%
   Module overlap between different ring modules that can give rise to two fold coincidences in R.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/l1l2_l3l4_2xinr.png}
\caption{%
   Module overlap between different ring modules that can give rise to two fold coincidences in R.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/XY_map_2xinphi_2xinr.png}
\caption{%
   Module overlap between different ring modules that can give rise to two fold coincidences in R.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/l1l2_dr_dphi_D4R1S2.png}
\caption{%
   Module overlap between different ring modules that can give rise to two fold coincidences in R.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/l1l2_drdphi_2xinr_PU200.png}
\caption{%
   Module overlap between different ring modules that can give rise to two fold coincidences in R.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/l1l2_drdphi_2xinr_PU200.png}
\caption{%
   Module overlap between different ring modules that can give rise to two fold coincidences in R.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/fit_l1l2_dr_2xinr.png}
\caption{%
   Module overlap between different ring modules that can give rise to two fold coincidences in R.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/fit_l3l4_dr_2xinr.png}
\caption{%
   Module overlap between different ring modules that can give rise to two fold coincidences in R.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/residuaL_L1L2_L3L4_2xinr.png}
\caption{%
   Module overlap between different ring modules that can give rise to two fold coincidences in R.
}
\label{fig:cluster_ring}
\end{figure}

\begin{comment}

\begin{table}[htbp]
  \centering
  \caption{m\_dr\_cuts\_offset\_InR\_f Values}
  \label{tab:mdr_cuts_offset_InR_f_values}
  \begin{tabular}{cccc}
    \hline
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} &  \textbf{Ring 4}\\
    \hline
    -1 & 0.0230881 & 0.0309854 & 0.0387241 & 0.0464962 \\
    -2 & 0.0199761 & 0.0270206 & 0.0338467 & 0.0403068 \\
    -3 & 0.017385  & 0.0233397 & 0.0294101 & 0.0348779 \\
    -4 & 0.0150614 & 0.0202725 & 0.0255259 & 0.0303849 \\
    1  & 0.0229736 & 0.0311421 & 0.0390871 & 0.0468038 \\
    2  & 0.0202136 & 0.0268963 & 0.0337796 & 0.040398  \\
    3  & 0.0174894 & 0.0233893 & 0.0293971 & 0.0351501 \\
    4  & 0.0149661 & 0.020194  & 0.0255051 & 0.0305483 \\
    \hline
  \end{tabular}
\end{table}

\begin{table}[htbp]
  \centering
  \caption{m\_dphi\_cuts\_InR\_f Values}
  \label{tab:mdphi_cuts_InR_f_values}
  \begin{tabular}{cccc}
    \hline
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} \\
    \hline
    -1 & 0.000628313 & 0.000828659 & 0.000975585 & 0.00101984  \\
    -2 & 0.000545699 & 0.000722289 & 0.00081899  & 0.000918094 \\
    -3 & 0.000495422 & 0.000649127 & 0.000754224 & 0.000839347 \\
    -4 & 0.000451069 & 0.000604104 & 0.000689508 & 0.000755603 \\
    1  & 0.000627781 & 0.000814669 & 0.000941641 & 0.0010221   \\
    2  & 0.000573352 & 0.000761853 & 0.000851161 & 0.000901014 \\
    3  & 0.000523361 & 0.000662691 & 0.000778358 & 0.000834924 \\
    4  & 0.000471669 & 0.000589938 & 0.000692007 & 0.000750302 \\
    \hline
  \end{tabular}
\end{table}

\begin{table}[htbp]
  \centering
  \caption{m\_dr\_cuts\_InR\_f Values}
  \label{tab:mdr_cuts_InR_f_values}
  \begin{tabular}{cccc}
    \hline
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} \\
    \hline
    -1 & 0.00458531 & 0.00466448 & 0.00486059 & 0.0052905  \\
    -2 & 0.00444971 & 0.0046465  & 0.00472138 & 0.00490022 \\
    -3 & 0.00453556 & 0.00471864 & 0.00465781 & 0.00503102 \\
    -4 & 0.00457346 & 0.00458345 & 0.00478342 & 0.00497171 \\
    1  & 0.00448255 & 0.00445856 & 0.00474102 & 0.0051553  \\
    2  & 0.00442349 & 0.00472485 & 0.00474663 & 0.0050426  \\
    3  & 0.00450002 & 0.0045179  & 0.00492058 & 0.00494887 \\
    4  & 0.00444657 & 0.00468584 & 0.00493828 & 0.00488064 \\
    \hline
  \end{tabular}
\end{table}

\begin{table}[htbp]
  \centering
  \caption{m\_dr\_cuts\_InR\_S Values}
  \label{tab:mdr_cuts_InR_S_values}
  \begin{tabular}{cccc}
    \hline
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} \\
    \hline
    -1 & 0.00448255 & 0.00445856 & 0.00474102 & 0.0051553  \\
    -2 & 0.00442349 & 0.00472485 & 0.00474663 & 0.0050426  \\
    -3 & 0.00450002 & 0.0045179  & 0.00492058 & 0.00494887 \\
    -4 & 0.00444657 & 0.00468584 & 0.00493828 & 0.00488064 \\
    1  & 0.00458531 & 0.00466448 & 0.00486059 & 0.0052905  \\
    2  & 0.00444971 & 0.0046465  & 0.00472138 & 0.00490022 \\
    3  & 0.00453556 & 0.00471864 & 0.00465781 & 0.00503102 \\
    4  & 0.00457346 & 0.00458345 & 0.00478342 & 0.00497171 \\
    \hline
  \end{tabular}
\end{table}

\begin{table}[htbp]
  \centering
  \caption{m\_dphi\_cuts\_InR\_S Values}
  \label{tab:mdphi_cuts_InR_S_values}
  \begin{tabular}{cccc}
    \hline
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} \\
    \hline
    -1 & 0.000627781 & 0.000814669 & 0.000941641 & 0.0010221   \\
    -2 & 0.000573352 & 0.000761853 & 0.000851161 & 0.000901014 \\
    -3 & 0.000523361 & 0.000662691 & 0.000778358 & 0.000834924 \\
    -4 & 0.000471669 & 0.000589938 & 0.000692007 & 0.000750302 \\
    1  & 0.000628313 & 0.000828659 & 0.000975585 & 0.00101984  \\
    2  & 0.000545699 & 0.000722289 & 0.00081899  & 0.000918094 \\
    3  & 0.000495422 & 0.000649127 & 0.000754224 & 0.000839347 \\
    4  & 0.000451069 & 0.000604104 & 0.000689508 & 0.000755603 \\
    \hline
  \end{tabular}
\end{table}

\begin{table}[htbp]
  \centering
  \caption{m\_dr\_cuts\_offset\_InR\_S Values}
  \label{tab:mdr_cuts_offset_InR_S_values}
  \begin{tabular}{cccc}
    \hline
    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} \\
    \hline
    -1 & 0.0229736 & 0.0311421 & 0.0390871 & 0.0468038 \\
    -2 & 0.0202136 & 0.0268963 & 0.0337796 & 0.040398  \\
    -3 & 0.0174894 & 0.0233893 & 0.0293971 & 0.0351501 \\
    -4 & 0.0149661 & 0.020194  & 0.0255051 & 0.0305483 \\
    1  & 0.0230881 & 0.0309854 & 0.0387241 & 0.0464962 \\
    2  & 0.0199761 & 0.0270206 & 0.0338467 & 0.0403068 \\
    3  & 0.017385  & 0.0233397 & 0.0294101 & 0.0348779 \\
    4  & 0.0150614 & 0.0202725 & 0.0255259 & 0.0303849 \\
    \hline
  \end{tabular}
\end{table}

\end{comment}

%\begin{figure}[!htp]
%\centering
%\includegraphics[width=0.7\textwidth]%{ashish_thesis/events_processed_twofoldcoin_newcuts.png}
%\caption{%

%}
%\label{fig:cluster_ring}
%\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/D4R1S2_linear_fit_twofoldcoin.png}
\caption{%
  Fit two fold coincidences Disk 4 Ring 1 side 2
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Alldisk_S1_twofoldcoin_residuals.png}
\caption{%
   fit residual two fold coincidences 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/Alldisk_S2_twofoldcoin_residuals.png}
\caption{%
  fit residual two fold coincidences all disk.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/D4R1_z_dr_dphi_total_fake_twofold.png}
\caption{%
  jhgil
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/D4R5_z_dr_dphi_twofoldcoin_total_fake.png}
\caption{%
   klbjihvb
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/fake_rate_D4allring.png}
\caption{%
  lhivbhiv
}
\label{fig:cluster_ring}
\end{figure}

\begin{table}[htbp]
  \centering
  \caption{Sample Table}
  \label{tab:sample}
  \begin{tabular}{cc}
    \textbf{Disk 4} & \textbf{Fake two fold coincidence rate (\%)} \\
    \hline
    Ring 1 &  1.1\\
    Ring 2 &  1.9\\
    Ring 3 &  2.0\\
    Ring 4 &  2.5\\
    Ring 5 &  2.3\\
  \end{tabular}
\end{table}

\begin{table}[htbp]
  \centering
  \caption{Sample Table}
  \label{tab:sample}
  \begin{tabular}{cccc}
    \textbf{Pileup} & \textbf{Fake two fold coincidence in phi rate ()} & \textbf{Fake two fold coincidence in R rate ()} & \textbf{Fake two fold coincidence rate ()} \\
    \hline
   0.5  &  0.78& 0.99 & 0.83 \\
     1& 0.79 &  1.01 &0.85\\
    1.5 &  0.80& 1.02 & 0.86 \\
     2 & 0.79 & 1.02&  0.84\\
    10 &  0.83&  1.04&  0.88\\
     30&  0.94&  1.09&  0.98\\
     50 &  1.04&  1.14&  1.07\\
    100  & 1.31 & 1.29& 1.31\\
     140  & 1.53 & 1.41& 1.50\\
    200   & 1.85 & 1.57 &1.78\\
  \end{tabular}
\end{table}

\begin{table}[htbp]
  \centering
  \caption{Sample Table}
  \label{tab:sample}
  \begin{tabular}{cccc}
    \textbf{Pileup} & \textbf{efficiency for two fold coincidence in phi} & \textbf{Efficiency for Fake two fold coincidence in R} & \textbf{Efficiency for two fold coincidence ()} \\
    \hline 
     0.5  & 99.21 &99.00  &99.16  \\
     1& 99.20 &98.98  & 99.14 \\
    1.5 & 99.19 & 98.97 & 99.13 \\
     2& 99.20 & 98.97 & 99.13 \\
    10 & 99.16 & 98.95 & 99.11 \\
     30& 99.05 & 98.90 & 99.01 \\
     50 & 98.95 & 98.85 & 98.92 \\
    100& 98.68 & 98.70 & 98.68 \\
     140& 98.46 & 98.58 & 98.49 \\
    200 &98.14  & 98.42 &98.21  \\
  \end{tabular}
\end{table}

\begin{figure}[!htp]
\centering
\includegraphics[width=1\textwidth]{ashish_thesis/D4R1_fake_true_ratio.png}
\caption{%
  Ratio of fake and total two fold coincidences for disk 4 ring 1.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/D4R5_fake_true_ratio.png}
\caption{%
  Ratio of fake and total two fold coincidences for disk 4 ring 5.
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\columnwidth]{./2foldinrphi.png}
  \caption{ \onehalfspacing Diagram showing modules overlap between the front (L1 \& L2) and back (L3 \& L4) layers of one double disk of TEPX that creates two fold coincidences in $\phi$ and r.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.6\columnwidth]{./23coin.png}
  \caption{\onehalfspacing Example of two and threefold coincidence regions on a portion of a single TEPX disk.}
  \label{fig:CMS}
\end{figure}

\subsection{TEPX linearity}

Linearity is one of the systematic uncertainty in the calculation of instantaneous luminosity and PCC visible cross section $\sigma_{vis}$. A linear relation between the number of clusters and pileup (PU) imply that \\

$<N_{cl/pp}> = \frac{<N_{cl}>}{\mu} = \frac{\sigma_{vis}}{\sigma_{pp}}$ \\

$<N_{cl}> =  \frac{\sigma_{vis}}{\sigma_{pp}} \mu $ \\

Linearity indicates that the PCC visible cross section $\sigma_{vis}$ does not depend on the per bunch instantaneous luminosity (ideal luminometer). In ideal scenario, $\sigma_{vis}$ is not dependent on pileup, but this a potential problem with the luminometer. Linearity results for simulated TEPX clusters and coincidences from low to high pileup values are shown from Fig. 29 to Fig. 40. TEPX luminometer proposed for Phase II shows excellent linearity over entire pileup range. A non-linear relation $<N_{cluster}> = \alpha (PU)^{\gamma}, \gamma \neq 1$ would add non-linear terms in the rate equation $R = \sigma_{vis} L_{inst}$  and cause $\sigma_{vis}$ to vary with the per bunch instantaneous luminosity and pileup values.

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./totalclusters.png}
  \caption{\onehalfspacing Left: Simulated mean number of clusters for all entire TEPX detector as a function of pileup. A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200. Right: Deviation from linearity for clusters for entire TEPX detector. The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value. Non-linearity is within 1 \% for entire pileup range. Pileup 200 corresponds to High Luminosity (HL)-LHC environment.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./clustersD4R1.png}
  \caption{\onehalfspacing Left: Simulated mean number of clusters for TEPX Disk 4 Ring 1 as a function of pileup. Right: Deviation from linearity for clusters for TEPX Disk 4 Ring 1. The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1 \columnwidth]{./clustersperdisk+z.png}
  \caption{Left: Simulated mean number of clusters for +z side TEPX disks as a function of pileup. Right: Deviation from linearity for clusters for +z side TEPX disks.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./clustersperringD+4.png}
  \caption{Left: Simulated mean number of clusters for +z side TEPX Disk 4 all rings as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope. Right: Deviation from linearity for clusters for TEPX Disk +4 all rings. Non-linearity is within $1\%$ for all rings over entire pileup range.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1 \columnwidth]{./totalcoincidences.png}
  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for all entire TEPX detector as a function of pileup. A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200. Right: Deviation from linearity for coincidence in $\phi$ and r for entire TEPX detector. The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value. Non-linearity is within 1 \% for entire pileup range. Pileup 200 corresponds to High Luminosity (HL)-LHC environment.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./totalcoincidencesD4R1.png}
  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for TEPX Disk 4 Ring 1 as a function of pileup. Right: Deviation from linearity for coincidences in $\phi$ and r for TEPX Disk 4 Ring 1. The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./coincidencesperdisk+z.png}
  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for +z side TEPX disks as a function of pileup. Right: Deviation from linearity for coincidences in $\phi$ and r for +z side TEPX disks.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./coincidencesinphiD4R1z+.png}
  \caption{Left: Simulated mean number of coincidences in $\phi$ for TEPX +z side Disk 4 Ring 1 as a function of pileup. Right: Deviation from linearity for coincidences in $\phi$ for TEPX +z side Disk 4 Ring 1. The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./coincidencesinrD4R1z+.png}
  \caption{Left: Simulated mean number of coincidences in r for TEPX +z side Disk 4 Ring 1 as a function of pileup. Right: Deviation from linearity for coincidences in r for TEPX +z side Disk 4 Ring 1. The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./coincidencesperringD+4.png}
  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for +z side TEPX Disk 4 per ring as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope. Right: Deviation from linearity for coincidences in $\phi$ and r for +z side TEPX Disk 4 per ring. Non-linearity is within 1\% for all rings over entire pileup range.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./coincidencesinphiperringD+4.png}
  \caption{Left: Simulated mean number of coincidences in $\phi$ for +z side TEPX Disk 4 per ring as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope. Right: Deviation from linearity for coincidences in $\phi$ for +z side TEPX Disk 4 per ring. Non-linearity is within 1\% for all rings over entire pileup range.}
  \label{fig:CMS}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{./coincidencesinrperringD+4.png}
  \caption{Left: Simulated mean number of coincidences in r for +z side TEPX Disk 4 per ring as a function of pileup. Ring 1 has highest slope and Ring 5 has least slope. Right: Deviation from linearity for coincidences in r for +z side TEPX Disk 4 per ring. Non-linearity is within $1\%$ for all rings over entire pileup range.}
  \label{fig:CMS}
\end{figure}

\subsection{Statistical precision for TEPX luminometer}
Statistical precision is another uncertainty that need to be considered for precise luminosity measurement. It must be kept minimal to achieve 1 $\%$ accuracy for HL-LHC luminosity measurement.

Relative statistical uncertainty in $\%$ = $\frac{\sqrt{N}}{N} \times 100$ \\

where N = (Number of counts per event)$\times$(Trigger Frequency)$\times$(Time Integration period).

\newpage
\begin{flushleft} 
Table 1: Expected statistical precision (in $\%$) in head-on collisions during typical vdM conditions with pileup of 0.5 for TEPX clusters and two fold coincidences over different integration time period.
\end{flushleft} 
\begin{center}
\scalebox{1}{
\begin{tabular}{|l | c | c | c |c|}
\hline
 vdM (PU 0.5) & Readout Rate (kHz) &1 bx, 1s & 1 bx, 30s & 100 bx, 30s\\
\hline
TEPXD4R1 Clusters&1000&1.82&0.332 & 0.0332\\
\hline
TEPXD4R1 2x Coincidences in phi &1000&5.98&1.09 & 0.109\\
\hline
TEPXD4R1 2x Coincidences in r &1000&11.1&2.02 & 0.202\\
\hline
TEPXD4R1 2x Coincidences &1000&5.27&0.962 & 0.0962\\
\hline
TEPX Clusters&500&0.709&0.129 & 0.0129\\
\hline
TEPX 2x Coincidences in phi &500&2.65&0.485 & 0.0485\\
\hline
TEPX 2x Coincidences in r &500&4.59&0.838 & 0.0838\\
\hline
TEPX 2x Coincidences &500&2.3&0.42 & 0.042\\
\hline
\end{tabular}}
\end{center}

\begin{flushleft} 
  Table 2: Expected statistical precision (in $\%$) in head-on collisions during physics conditions with pileup of 200 for TEPX clusters and two fold coincidences over different integration time period.
  \end{flushleft} 
\begin{center}
\scalebox{1}{
\begin{tabular}{|l | c | c | c |c |}
\hline
Algorithm & Readout Rate (kHz)& 1 bx, 1s &2500 bx, 1s   & 2500 bx, 1 LS \\
\hline
TEPXD4R1 Clusters&825&0.1&0.002&0.000414\\
\hline
TEPXD4R1 2x Coincidences in phi &825&0.329&0.00659&0.00136\\
\hline
TEPXD4R1 2x Coincidences in r &825&0.61&0.0122&0.00252\\
\hline
TEPXD4R1 2x Coincidences  &825&0.29&0.0058&0.0012\\
\hline
TEPX Clusters &75&0.0915&0.00183&0.000379\\
\hline
TEPX 2x Coincidences in phi &75&0.343&0.00685&0.00142\\
\hline
TEPX 2x Coincidences in r &75&0.593&0.0119&0.00245\\
\hline
TEPX 2x Coincidences &75&0.297&0.00594&0.00123\\
\hline
\end{tabular}}
\end{center}

\section{Summary of the planned upgrade schedule}

The Phase II upgrade of the CMS detector is a major project that will take several years to complete. The design and development of the upgraded components is currently underway, and the installation of the new detectors and electronics is scheduled to take place over the next few years. The commissioning and testing phase will be critical to ensure that the upgraded detector is functioning properly, and full operation of the upgraded CMS detector is expected to begin in 2026. Planned upgrade schedule for the Phase II upgrade of the CMS detector:

\begin{itemize}

\item 2018-2024: Design and development of the upgraded components, including the new pixel and strip detectors, timing layer, and data acquisition system.

\item 2022-2023: Installation of the new carbon-fiber support structure for the upgraded tracker.

\item 2023-2025: Installation of the new detectors and electronics in the CMS detector, including the pixel and strip detectors, timing layer, and data acquisition system.

\item 2025-2026: Commissioning and testing of the upgraded detector.

\item 2026: Full operation of the upgraded CMS detector.

\end{itemize}

\begin{comment}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/xvsy_cluster.png}
\caption{%
  cluster map tepx 
}
\label{fig:cluster_xvsy}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/cluster_ring.png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/tepx_dataset.png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/tepx_events_processed.png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/tepx_cluster_pu100.png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/clusters_tepx_disk4.png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/clusters_tepx_pu10_allrings.png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/lowpu_clusters_fit_D4R1.png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/fit_extrapol_D4R1.png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/twofoldcoin_D4_allring (1).png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/twofold_geometry_pu30.png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/lowpufit_twofold_D4R1.png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/twofoldcoincidences_extrapolation_D4R1.png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/twofold_residual_D4R1.png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/events_per_file_tepx_sim.png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/clusters_D4R1_low_allPU.png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/twofoldcoin_low_allpu_D4R1.png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/threefoldcoin_D4_PU100.png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/threefoldcoin_D4_allpu.png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/threefoldcoin_D4_lowPU.png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/stat_prec_d4r1.png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/cut_optimization_twofold.png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\begin{figure}[!htp]
\centering
\includegraphics[width=0.7\textwidth]{ashish_thesis/cut_optimization_twofold.png}
\caption{%
  cluster per event ring tepx 
}
\label{fig:cluster_ring}
\end{figure}

\end{comment}

### 2023-06-16 tesis_Ashish/Chapter8/chapter8.tex
Your commit message

\section{Summary and Plans} 
\label{sec:con}

\subsection{Summary of the study and its findings}
\subsection{Limitations and potential improvements of the pixel cluster counting method}
\subsection{Future work related to luminosity measurement at the LHC}
\subsection{Conclusion and final remarks}

### 2023-06-16 tesis_Ashish/Portada/Portada.tex
Your commit message

--- 2022-12-29 tesis_Rodolfo/Portada/Portada.tex
@@
       \vspace{2cm}
-        {\Large \scshape {Measurements of the Large Hadron Collider luminosity using the CMS silicon pixel detector}}
+        {\Large \scshape {Luminosity measurement with the Pixel detector at the CMS experiment of the Large Hadron Collider}
 
@@
 requirements for the degree of:\\[5pt]
-        {\Large \textbf{{Maestr\'ia en Ciencias (F\'isica)}}}\\[40pt]
+        {\Large \textbf{{Doctorado en Ciencias (F\'isica)}}}\\[40pt]
         By:\\[12pt]
-        \textbf{  {\large Jesus Rodolfo MORENO CHAVEZ}}
+        \textbf{  {\large Ashish Sehrawat}}
 
@@
 
-        { Hermosillo, Sonora} \hskip2.5cm {December 08, 2022}
+        { Hermosillo, Sonora} \hskip2.5cm {June, 2023}
       \end{center}

### 2023-06-16 tesis_Ashish/chap_originales/Chapter3/chapter3.tex
Your commit message

--- 2023-04-11 tesis_Luis/Chapter3/chapter3.tex
@@
 
-Figure  \ref{pileup} shows a simulation with pp collision zero-bias events with a full CMS detector response made in 2016, it contain only in time pileup and detector noise, where the mean number of pixel clusters is of the order of  100 per event.
-For simplicity, the number of pileup interactions present in each event is randomly generated from a representative PCC distribution at $\mu$ = 45 and the average PCC as a function of $\mu$.
-The latter distribution is fitted with a first-order polynomial, assuming no correlations among different values of $\mu$.
-Good agreement is seen based on the estimated goodness-of-fit $\chi^{2}$ per degree of freedom (dof) value of about 0.5 , indicating linearity under simulated conditions \cite{lumi_precise_2015_2016}.
+Figure \ref{pileup} shows a simulation with pp collision zero-bias events with the pixel cluster counting rate as a function of pileup in the pileup range observed in Run 2 from 0 to about 50 $\mu$.
+Where the mean number of pixel clusters is of the order of  111 per event.
+The red curve is a first-order polynomial fit with slope, a good agreement is seen based on the estimated goodness-of-fit $\chi^{2}$ per degree of freedom (dof) with a value of about 0.5, showing that the PCC rate is highly linear in this range under simulated conditions \cite{ Phase2_Upgrade,lumi_precise_2015_2016}.
 
@@
     \centering
-    \includegraphics[scale=.3]{Chapter3/pileup_lineality.png} 
-    \caption[Linearity with pile-up]{ The left plot shows the number of pixel clusters and their statistical spread from simulation of pileup following a Poisson distribution with a mean of 45.
-The right plot shows the mean number of pixel clusters from simulation as a function of mean pileup.
-The red curve is a first-order polynomial fit with slope and $\chi^{2}/ndof$ values shown in the legend.
-The lower panel of the right plot shows the difference between the simulation and the linear fit in black points.
-The green band is the final linearity uncertainty for the 2016 data set \cite{lumi_precise_2015_2016} }
+    \includegraphics[scale=.35]{Chapter3/pileup_lineality.png} 
+    \caption[Linearity with pile-up]{ Linearity of pixel cluster counting over the pileup range observed in Run 2 (from 0 to about 50) from simulation.
+The red line is a linear fit to the points \cite{Phase2_Upgrade} }
     \label{pileup}
@@
 
-This method is capable of providing a precise luminosity measurement over longer time periods, but it cannot do so for a single luminosity section (23 seconds) as is possible with online luminometers.
+%This method is capable of providing a precise luminosity measurement over longer time periods, but it cannot do so for a single luminosity section (23 seconds) as is possible with online luminometers.
 The reason for this limitation is the limited CMS trigger bandwidth available for collecting data \cite{pas_18}.
 A detailed discussion on this topic can be found in the next chapter.\\
+
+%PCC si calcula lumi por cada lumi section.
+Esto no tiene que ver con online vs offline.
+PCC es un offline luminometro, quiere decir que los datos llegan tarde.
+Con PCC solo podemos calcular lumi cada lumi section, debido a la baja estadistica (por la lectura de los datos de zero bias).
+otros luminometros tienen precision con NB4 (HF, PLT, BCM1F).
 
@@
 
-On July 12th, 2022, the data collection for Run3 of the Large Hadron Collider (LHC) began, which resulted in a total luminosity of $38.48 fb^{-1}$.
+On July 12th, 2022, the data collection for Run3 of the Large Hadron Collider (LHC) began, which resulted in a total recorded luminosity of $38.48 fb^{-1}$.
 This collection period encompassed the duration from the start of stable beams until the beam was dumped, or when stable beams ceased for other reasons, such as beam studies.
 The luminosity delivered by the LHC to CMS (blue) and the luminosity recorded by CMS (orange) during stable beams and proton-proton collisions at a center-of-mass energy of $\sqrt{s}$ 13.6 TeV in 2022 are depicted in Figure \ref{Lumi_2022}.
-Note that  the special runs that occurred at injection energy (450 GeV) are not represented in these graphs.
+Note that  the special runs that occurred at injection energy (450 GeV) are not represented in these graphs \citep{wikicern}.
 
@@
     \includegraphics[width=.45\textwidth]{Chapter3/lumi_per_day_pp_2022.png}
-    \caption[Integrated Luminosity 2022]{(left) Cumulative day-by-day integrated luminosity, 2022 Cumulative measured luminosity versus day delivered.
-Note that this plot may not include data taken within the most recent 24 hours.
-(rigth) Day-by-day integrated luminosity, 2022 As the first plot, but not cumulative.}
+    \caption[Integrated Luminosity 2022]{(left) Cumulative day by day integrated luminosity. (rigth) Day by day integrated luminosity, 2022 as the first plot, but not cumulative.} 
     \label{Lumi_2022}
@@
 To ensure accurate luminosity measurement, a module selection is created to remove any modules exhibiting long-term performance variations, indicating a non-physical shift in their cluster counts.
-With a total of 1856 modules in the pixel system, all of them can be considered in the luminosity measurement; however, non-zero occupancy and non-linear effects can pose challenges for accurate measurement.
+With a total of 1856 modules in the pixel system, all of them can be considered in the luminosity measurement; however, instabilities and non-linear effects can pose challenges for accurate measurement.
 Thus, to identify "good" and "stable" modules, a subset is selected by eliminating  underperforming or "bad" modules and comparing their relative contributions to the cross section.
@@
 \begin{itemize}
-\item Poor statistics lumisections are removed by applying selection on total PCC.
+\item Poor statistics lumisections are removed from applying selection on total PCC.
 \item Barrel layer-1 modules are removed, as these modules are significantly affected by dynamic inefficiency.
@@
 To further enhance the stability of the PCC measurement, a common module vetolist was created by combining the lists from all five periods were the number of bad modules per period were added and modules with equal ID were removed , as shown in table \ref{common veto module}.
-The PCC data with zero bias was then reprocessed using this common module vetolist and ultimately used for the VdM analysis.
+The PCC data with zero bias was then reprocessed using this common module vetolist and ultimately used for the vdM analysis.
 
@@
 In practice, while the measurement of the beam currents $N_{1,2}$ is well determined, the individual proton density functions cannot be directly measured.
-To address this, the VdM method involves a specific machine setup that allows for the determination of the two beam overlap integrals.
+To address this, the vdM method involves a specific machine setup that allows for the determination of the two beam overlap integrals.
 This is achieved by varying the separation between the beams and measuring the resulting rates, which can be used to obtain density profiles that are close to normal distributions.

### 2023-06-16 tesis_Ashish/chap_originales/Chapter5/chapter5.tex
Your commit message

--- 2023-03-29 tesis_Luis/Chapter5/chapter5.tex
@@
 This work aims to focus on the calibration of luminosity for the PCC  luminometer, based on the van der Meer scans conducted by the CMS Collaboration on November 10 and 11 of 2022 for the fill 8381 of proton-proton collisions at $\sqrt{s}=$ 13.6 TeV, where five scan pairs (3 standard vdM and three BI scans) were analyzed with this method.
-A explanation of luminosity importance,the LHC and the CMS experiment, the PCC method as luminometer, and the calibration procedure for estimating $\sigma_{vis}$ were all covered in this work.
+A explanation of luminosity importance,the LHC and the CMS experiment, the PCC method as luminometer, and the calibration procedure for estimating $\sigma_{vis}$ were all covered in this work.\\
 
@@
 This approach aimed to remove instabilities in luminosity measurement for the corresponding calibration periods,  data also was processed with the  estimation of the background correction to the rates (PCC) from the two super separation periods in this program.
-The study concludes that the fit obtained for this  estimation is not the best due the background value varied over time for the two SS periods, leading to the decision that the fit model should be changed to one with a constant.
-All the parameters for this analysis were reported.
+The study concludes that the fit obtained for this  estimation is not the best due the background value varied over time for the two SS periods, leading to the decision that the fit model should be changed to one with a variable background level.
+The variation of the beam overlap integrals and peak rates per BCID are reported in this work..\\
 
-The assigned value of the calibration is $\sigma_{vis} = 4163 \pm 3 \text{(stat.)} \pm 12 \text{(syst.)} \text{ mb}$.
+The assigned value of the calibration is $\sigma_{vis} = 4163.3 \pm 3.3 \text{(stat.)} \pm 13 \text{(syst.)} \text{ mb}$.
 The analysis and results reported in this work will be useful for a precise luminosity measurement analysis for Run 3 in the CMS experiment of LHC, together with the rest of the luminometers  for a final publication that presents all these final results.

### 2023-06-16 tesis_Ashish/compile.sh

@@ -1,0 +1,42 @@
+#!/bin/bash
+
+thesis="thesis";
+
+if [ $1 = "clean" ]
+then
+	echo "Cleaning please wait ..."
+	rm -f *~
+	rm -rf *.aux
+	rm -rf ./*/*.aux
+	rm -rf *.bbl
+	rm -rf *.blg
+	rm -rf *.d
+	rm -rf *.fls
+	rm -rf *.ilg
+	rm -rf *.ind
+	rm -rf *.toc*
+	rm -rf *.lot*
+	rm -rf *.lof*
+	rm -rf *.log
+	rm -rf *.idx
+	rm -rf *.out*
+	rm -rf *.nlo
+	rm -rf *.nls
+	rm -rf $thesis.pdf
+	rm -rf $thesis.ps
+	rm -rf $thesis.dvi
+	rm -rf $thesis.spl
+	rm -rf *#* 
+	echo "Cleaning complete!"
+else
+	echo "Compiling ...!"
+	pdflatex -interaction=nonstopmode $thesis.tex
+	bibtex $thesis.aux 	
+	makeindex $thesis.aux
+	makeindex $thesis.idx
+	makeindex $thesis.nlo -s nomencl.ist -o $thesis.nls
+	pdflatex -interaction=nonstopmode $thesis.tex
+	makeindex $thesis.nlo -s nomencl.ist -o $thesis.nls
+	pdflatex -interaction=nonstopmode $thesis.tex
+	echo "Success!"
+fi

### 2023-07-05 tesis_Ashish/Abstract/abstract.tex
AS thesis update

@@
 
-The Pixel Cluster Counting (PCC) luminosity measurement method has emerged as a reliable offline technique for luminosity measurement during LHC run periods.
-The PCC method is based on the rate of pixel clusters in the CMS pixel detector, which is the innermost part of the CMS tracker.
-PCC is studied for its stability and accuracy in luminosity measurements using 2018 AlCa Reco datasets.
-The results of these studies demonstrate that the PCC luminosity measurement method is stable and accurate, able to achieve ??\% systematic uncertainty on the final luminosity measurement for Run 2 data.
-Moreover, the algorithms and optimization for the Phase II High Luminosity LHC (HL-LHC) luminosity measurement are also developed, using the Tracker Endcap Pixel Detector (TEPX).
-This detector is expected to provide excellent statistical and linearity performance, which is essential for accurate luminosity measurements at the HL-LHC.
-The TEPX detector will replace the upgraded Phase I pixel detector and is expected to provide even higher precision luminosity measurement.
+The Pixel Cluster Counting (PCC) luminosity measurement method has emerged as a reliable offline technique for luminosity measurement.
+%The PCC method is based on the rate of pixel clusters in the CMS pixel detector, which is the innermost part of the CMS tracker.
+PCC method is studied for its precision in luminosity measurement using 2018 AlCa Reco datasets.
+The results of these studies demonstrate that the PCC luminosity measurement method is stable and linear, able to achieve 1\% systematic uncertainty on the final luminosity measurement.
+Moreover, the clusters and coincidences counting algorithms and their optimization for the Phase II High Luminosity LHC (HL-LHC) luminosity measurement are also developed, using simulated datasets for the proposed Phase II pixel detector.
+%This new pixel detector will replace the Run 2 pixel detector.
+Linearity of the TEPX and D4R1 luminometers are expected to be within 1\% (offline) up to a pileup of 200 and their statistical precision per second is about 0.1\% at <PU>=200.
+%It is expected to provide excellent statistical precision and linearity performance, which is essential for precision luminosity measurements at the HL-LHC.
 

### 2023-07-05 tesis_Ashish/Chapter1/chapter1.tex
new thesis
AS thesis update

@@
 Collider experiments have played a crucial role in advancing our understanding of particle physics and continue to be a vital tool for scientific exploration.
+Two important parameters in the collider experiments are energy and luminosity.
 
@@
 
-Luminosity is a measure of the number of particle collisions that occur per unit time and per unit area.
-In particle physics, luminosity is a crucial parameter that determines the rate at which particles are produced in a collider experiment.
+Luminosity is a measure of the number of particle collisions that occur per unit area per unit area.
+In particle physics, luminosity is a crucial parameter that determines the rate at which particles are produced in a collider experiment \cite{Herr:941318}.
 
@@
 The importance of luminosity in particle physics lies in its direct relationship with the production rate of particles of interest.
-The production rate of a given particle is proportional to the product of the luminosity and the cross-section of the process.
+The production rate of a given particle is the product of the luminosity and the cross-section of the process.
 Thus, luminosity directly affects the ability to detect rare events and make precise measurements.
@@
 Another technique is to use radio frequency cavities to accelerate the particles to higher energies increasing the frequency of bunch crossings.
-Increasing the number of particles in each bunch is another way to increase luminosity.
 In high-energy particle accelerators, such as the Large Hadron Collider (LHC) at CERN, the luminosity is typically measured in units of inverse femtobarns ($fb^{-1}$), which is a measure of the total number of collisions per unit area during the course of an experiment.
-For example, the LHC has a design luminosity of $10^{34} cm^{-2}s^{-1}$, which means that there are $10^{34}$ proton-proton collisions per second per square centimeter of the detector.
-The importance of luminosity can be seen in the many discoveries that have been made in particle physics due to high-luminosity experiments.
+For example, the LHC has a design luminosity of $10^{34} cm^{-2}s^{-1}$, which means that there are $10^{34}$ proton-proton collisions per square centimeter per second.
+The importance of luminosity can be seen in the many discoveries that have been made in particle physics due to high luminosity experiments.
 For example, the discovery of the Higgs boson at the LHC was made possible by the high luminosity of the collider, which allowed physicists to observe the rare Higgs boson signal over the background noise of other particles.
@@
 In particle physics, the luminosity of colliding beams is a crucial measurement as it provides information about the rate at which rare processes occur and enables precise measurements of particle properties such as cross sections and couplings to fermions, bosons.
-Cross sections are fundamental quantities in particle physics, used to predict the number of events a certain process will produce.
 Luminosity depends on several variables, including the number of protons in each beam, the size and shape of the beams, and their relative positioning.
@@
 As such, the uncertainty in cross-section and coupling measurements cannot be better than the uncertainty in luminosity measurement.
-Therefore, ongoing efforts are focused on improving the accuracy of luminosity measurements, with the pixel detector at CMS being a key component of this effort.
+Therefore, ongoing efforts are focused on improving the precision of luminosity measurements, with the pixel detector at CMS being a key component of this effort.
 By reducing the luminosity uncertainty, physicists can make more precise measurements of particle properties and potentially discover new physics beyond the Standard Model.
@@
 \centering
-\includegraphics[width=0.42\textwidth]{ashish_thesis/lumi_precision.png}
-\caption{%
+\includegraphics[width=0.8\textwidth]{ashish_thesis/lumi_precision.png}
+\caption[Phase II uncertainty projections]{ %
    Higgs boson production processes cross section projected uncertainty.
-In the most precisely measured Higgs boson production process, gluon fusion (ggH), luminosity uncertainty will dominate the experimental systematic uncertainty at the High Luminosity (HL)-LHC.
+In the most precisely measured Higgs boson production process, gluon fusion (ggH), luminosity uncertainty will dominate other experimental systematic uncertainty at the High Luminosity (HL)-LHC.
+\cite{Dainese:2703572}
 }
@@
 \end{figure}
+
+%\begin{center}
+ % \begin{figure}[h]
+  %  \centering
+   % \includegraphics[scale=.35]{ashish_thesis/lumi_precision.png}
+    %\caption[Phase II uncertainty projections]{Higgs boson production processes cross section projected uncertainty.
+In the most precisely measured Higgs boson production process, gluon fusion (ggH), luminosity uncertainty will dominate the experimental systematic uncertainty at the High Luminosity (HL)-LHC.}
+    %\label{fig:lum_unc}
+  %\end{figure}
+%\end{center}
 
@@
 \centering
-\includegraphics[width=0.6\textwidth]{ashish_thesis/lhc_schematic.png}
-\caption{%
+\includegraphics[width=0.9\textwidth]{ashish_thesis/lhc_schematic.png}
+\caption[CERN accelerator complex]{%
     CERN accelerator complex consists of Linac 2, Proton Synchrotron Booster (PSB), Proton Synchrotron (PS), Super Proton Synchrotron (SPS) and Large Hadron Collider (LHC).
-LHC ring showing four interaction points where the ALICE, ATLAS, LHCb and CMS detectors are stationed.
+LHC ring showing four interaction points where the ALICE, ATLAS, LHCb and CMS detectors are stationed \cite{lhc_complex}.
 }
@@
 \centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/cms_exp.png}
-\caption{%
-   Compact muon solenoid (CMS) detector with all of the sub detectors showing silicon tracker, electromagnetic and hadron calorimeters and muon chambers. 
+\includegraphics[width=0.75\textwidth]{ashish_thesis/cms_exp.png}
+\caption[CMS Experiment]{%
+   Compact muon solenoid (CMS) detector with all of the sub detectors showing silicon tracker, electromagnetic and hadron calorimeters and muon chambers \cite{CMS:2008xjf}. 
 }
@@
 During the operation of the CMS experiment, two main data-taking periods were conducted: Run 1, which spanned from 2010 to 2013, and Run 2, which took place from 2015 to 2018.
-During these periods, the CMS experiment measured the instantaneous and integrated luminosity of the proton-proton collisions produced by the Large Hadron Collider (LHC) shown in Fig.~\ref{fig:lumi}.
+During these periods, the CMS experiment measured the instantaneous and integrated luminosity of the proton-proton collisions produced by the Large Hadron Collider (LHC) where the integrated luminosity for each year is shown in Fig.~\ref{fig:lumi}.
 During Run 1, the CMS experiment achieved a peak instantaneous luminosity of up to $5 \times 10^{33} cm^{-2} s^{-1}$, while during Run 2, the luminosity reached a peak value of up to $2 \times 10^{34} cm^{-2} s^{-1}$.
-The luminosity measurements during both runs were accompanied by careful assessments of the systematic uncertainties to ensure accurate and reliable results as shown in Table.
+The luminosity measurements during both runs were accompanied by careful assessments of the systematic uncertainties to ensure accurate and reliable results \cite{CMS-PAS-EWK-10-004}\cite{CMS-PAS-EWK-11-001} \cite{CMS-PAS-SMP-12-008} \cite{CMS-PAS-LUM-13-001} \cite{Sirunyan:2759951} \cite{pas_17}\cite{pas_18} as shown in Table.
 \ref{tab:lumi}.
@@
 \centering
-\caption{Summary of center of mass energy, integrated luminosity, and systematic uncertainty per year during the CMS luminosity measurement.}
+\caption[Run 1, Run 2 Integrated luminosity and its precision]{Summary of center of mass energy, integrated luminosity, and systematic uncertainty per year during the CMS luminosity measurement.}
 \begin{tabular}{c c c c}
@@
 2010 & 7 & 0.045 & 11 \\
-2011 & 7 and 8 & 6.1 & 4.5 \\
+2011 & 7 and 8 & 6.1 & 2.2 \\
 2012 & 8 & 23.3 & 2.5 \\
-2015 & 13 & 4.3 & 2.3 \\
-2016 & 13 & 41.6 & 2.5 \\
+2015 & 13 & 4.3 & 1.6 \\
+2016 & 13 & 41.6 & 1.2 \\
 2017 & 13 & 49.8 & 2.3 \\
@@
 \centering
-\includegraphics[width=0.8\textwidth]{ashish_thesis/CMS_luminosity.png}
-\caption{%
-    Delivered luminosity versus time for Run 1 and Run 2 of the CMS experiment.
+\includegraphics[width=0.9\textwidth]{ashish_thesis/CMS_luminosity.png}
+\caption[Integrated luminosity per year]{%
+    Delivered luminosity versus time for Run 1, Run 2 and Run 3 of the CMS Experiment \cite{wikicern_cc}.
 }

### 2023-07-05 tesis_Ashish/Chapter2/chapter2.tex
AS thesis update

@@
 
-Luminosity measurement is a crucial aspect of particle physics experiments such as the Compact Muon Solenoid (CMS) experiment at the Large Hadron Collider (LHC).
+%Luminosity measurement is a crucial aspect of particle physics experiments such as the Compact Muon Solenoid (CMS) experiment at the Large Hadron Collider (LHC).
 Luminosity refers to the rate at which particles collide within the detector, and accurate measurement of luminosity is essential for precise determination of particle collision rates and cross-sections.
@@
 In addition, the Pixel Cluster Counting (PCC) and zero counting method are a commonly used techniques for luminosity measurement at the CMS experiment.
+
+Luminosity measurement is a crucial aspect of particle physics experiments such as the Compact Muon Solenoid (CMS) at the Large Hadron Collider (LHC).
+Luminosity signifies the rate at which particles collide per unit area per second, making its precision measurement vital for the precise determination of particle collision rates and cross-sections.
+The CMS experiment employs several devices to measure luminosity, each covering specific pseudorapidity ranges and regions within the CMS detector \cite{CMS-PAS-LUM-18-002}.
+The use of several luminometers as shown in Fig.~\ref{fig:lumino_cms} offers a multitude of advantages.
+Primarily, it ensures redundancy and acts as a backup for potential device failures, ensuring that data collection can proceed without interruption.
+Additionally, having multiple luminometers allows for cross-checking, providing greater consistency in results and allowing for more reliable data interpretation.
+These different devices enable better control over systematic uncertainties, as any discrepancies can be identified and adjusted for.
+Moreover, each device employs different method to measure luminosity, providing complementary information that enriches the overall understanding of particle interactions.
+Some luminometers recording low rates can be calibrated using others, enhancing their accuracy and utility.
+This holistic approach to luminosity measurement significantly improves the robustness and reliability of the data collected.
+In the central region, The Muon Drift Tubes (DT) luminometer is used covering a pseudorapidity range from 0 to 1.2.
+The Pixel Cluster Counting (PCC) luminometer also operates in this region and extends into the forward region covering a range from 0 to 2.5.
+In the forward region, several devices are utilized.
+The Pixel Luminosity Telescope (PLT) covers the pseudorapidity range from 2.8 to 4.7.
+The Fast Beam Condition Monitor (BCM1F) functions in a range from 3.1 to 4.7.
+The Radiation Monitoring System for Environment and Safety (RAMSES) operates in the pseudorapidity range from 4 to 5.
+In the most Forward Region, The Hadron forward (HF) luminometer caters to the most forward region of the CMS detector \cite{Sirunyan:2759951}, functioning in the pseudorapidity range from 3 to 5  as shown in Fig.~\ref{fig:lumino_cms_pseudo}.
+
+%In addition to these devices, two common techniques used for luminosity measurement at the CMS experiment are the Pixel Cluster Counting (PCC) and zero counting method.
+Please refer to Figures 1.1 and 1.2 for further visual information about these devices and their respective coverage within the CMS detector.
 
@@
 The third layer is located 4.9 cm from the interaction point.
-The outermost layer is located 10.2 cm from the interaction point.
+The outermost layer is located 10.2 cm from the interaction point \cite{Ayala:2861814}.
 The pixel sensors are designed to detect charged particles produced in the collisions as they pass through the detector layers.
@@
 This is done by analyzing the signals from the individual pixels and using algorithms to determine the path of the particle through the detector.
-To measure the luminosity of the collisions, the PLT counts the number of charged particles produced in each bunch crossing, and uses this information to calculate the rate of collisions.
+  %To measure the luminosity of the collisions, the PLT counts the number of charged particles produced in each bunch crossing, and uses this information to calculate the rate of collisions.
 The luminosity is then calculated by dividing the collision rate by the cross-section of the proton-proton interactions.
-The PLT uses a specialized algorithm called the "triple coincidence filter" to identify charged particles that are produced in the collisions and to reject background noise.
-The filter requires a charged particle to be detected in at least three of the four detector planes, which corresponds to a "triple coincidence" detection.
-This helps to reduce the contribution of background noise and improve the precision of the luminosity measurement.
+  The PLT uses a specialized algorithm called the "triple coincidence" to identify charged particles that are produced in the collisions and to reject background noise.
+It requires a charged particle to be detected in at least three of the four detector planes, which corresponds to a "triple coincidence" detection.
+The rate of triple coincidences is proportional to the luminosity.
+This helps to reduce the contribution of background noise and improve the precision of the luminosity measurement \cite{Lujan:2017kvh}.
 
-\item Fast Beam Conditions Monitor (BCM1F) : The BCM1F is a device used in the CMS (Compact Muon Solenoid) experiment at CERN's Large Hadron Collider (LHC) to measure the luminosity of proton-proton collisions.
-The luminosity is a measure of the rate of collision events per unit time and per unit area of the beam.
-The BCM1F is specifically designed to detect the ionization produced by charged particles passing through its diamond sensors, and to convert this signal into a measurement of the beam intensity and luminosity.
+\item Fast Beam Conditions Monitor (BCM1F) : The BCM1F is specifically designed to detect the ionization produced by charged particles passing through its diamond sensors, and to convert this signal into a measurement of the beam intensity and luminosity.
 The BCM1F consists of 24 diamond sensors, each with an active area of 1 cm², arranged in six rings around the beam pipe.
@@
 The number of charged particles per bunch is determined by calibrating the BCM1F with data from other detectors in the CMS experiment, such as the silicon pixel detector and the pixel luminosity telescope.
-These detectors are used to measure the total number of charged particles produced by the proton-proton collisions, which is then used to calibrate the BCM1F.
+These detectors are used to measure the total number of charged particles produced by the proton-proton collisions, which is then used to calibrate the BCM1F \cite{CMS-DP-2013-003}.
 
@@
 \item Hadron Forward Calorimeter: The Hadron Forward (HF) Calorimeter is a critical component of the Compact Muon Solenoid (CMS) experiment at the Large Hadron Collider (LHC) at CERN.
-It is a subdetector that measures the energy and position of particles produced during proton-proton collisions in the LHC.
-The HF Calorimeter is designed specifically to measure hadronic particles, which are particles made up of quarks and gluons, in the forward region (i.e., close to the beamline) of the CMS detector.
+It is a subdetector that measures the energy, position and arrival time of particles produced during proton-proton collisions in the LHC.
+The HF Calorimeter is designed specifically to measure hadron particles, which are particles made up of quarks and gluons, in the forward region (i.e., close to the beamline) of the CMS detector.
 The HF Calorimeter is located at the very front and back of the CMS detector, at a distance of about 11.2 meters from the interaction point.
@@
 The active material, in this case, is scintillating quartz fibers, which emit light when they interact with charged particles.
-The passive material is steel absorber plates, which serve to initiate hadronic showers, causing the incident hadronic particles to interact and create secondary particles.
+The passive material is steel absorber plates, which serve to initiate hadron showers, causing the incident hadron to interact and create secondary particles.
 As these secondary particles pass through the scintillating fibers, they produce light, which is collected by photodetectors and converted into an electrical signal proportional to the particle's energy.
-Two of the methods used for luminosity measurement in the HF Calorimeter are the Zero Counting (ZC) method and the Missing Energy (ME) method.
+Two separate algorithm are used for luminosity measurement in the HF Calorimeter, HFOC and HFET based on the Zero Counting (ZC) method and the Missing Transverse Energy (MET) methods respectively \cite{CMS-PAS-LUM-15-001}.
 
@@
 However, it may be affected by detector noise and other background processes that can lead to a non-zero energy deposition.
-The zero counting method is another method used by particle colliders to measure the luminosity of collisions.
+The zero counting method is used by particle colliders to measure the luminosity.
 In this method, the luminosity is estimated by counting the number of events with zero particles detected in a specific region of the detector.
@@
 
-where L is the luminosity, N is the number of events with zero particles detected in the region of interest, $N_0$ is the total number of events, $\sigma_{vis}$ is the visible cross-section.One advantage is that it is a simple and robust method that does not require sophisticated detectors or calibration procedures.
+where L is the luminosity, N is the number of events with zero particles detected in the region of interest, $N_0$ is the total number of events, $\sigma_{vis}$ is the visible cross-section.
+One advantage is that it is a simple and robust method that does not require sophisticated detectors or calibration procedures.
 However, it can be affected by background events, such as cosmic rays or beam-gas interactions, which can produce zero particles in the region of interest and increase the uncertainty in the luminosity measurement.
+\\
 The Missing Energy method is an alternative approach for luminosity measurement in the HF Calorimeter.
@@
 The ME method is sensitive to the energy scale calibration of the detector and the modeling of background processes.
-However, it provides an independent and complementary measurement to the ZC method, which helps to reduce systematic uncertainties in the luminosity determination.
+However, it provides an independent and complementary measurement to the ZC method, which helps to reduce systematic uncertainties in the luminosity determination \cite{Sirunyan:2759951}.
 
@@
 This approach would require careful control of various experimental factors, such as the efficiency and acceptance of the DT system, the precise determination of the production cross-sections, and corrections for pile-up and background processes.
-It is important to note that this would not be a primary luminosity measurement technique, but it could provide a complementary cross-check to the main methods used in the CMS experiment.
+It is important to note that this would not be a primary luminosity measurement technique, but it could provide a complementary cross-check to the main methods used in the CMS experiment \cite{Chatrchyan:2013sba}.
 
@@
 The total number of clusters detected over a certain period of time is used to estimate the luminosity.
-The PCC provides a precise measurement of the luminosity and is particularly useful when the collision rate is high.
+The PCC provides a precise measurement of the luminosity and is particularly useful when the collision rate is high \cite{CMS-PAS-LUM-13-001}.
 
@@
 \centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/luminometer_cms.png}
-\caption{%
+\includegraphics[width=0.9\textwidth]{ashish_thesis/luminometer_cms.png}
+\caption[CMS luminometers]{%
    Compact muon solenoid (CMS) detector with all of the luminosity measurement devices showing PLT, BCM1F, HF, DT, PCC and RAMSES. 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{ashish_thesis/luminometer_cms_pseudo.png}
-\caption{%
+\includegraphics[width=0.9\textwidth]{ashish_thesis/luminometer_cms_pseudo.png}
+\caption[Location of CMS luminometers]{%
     Cross section of the CMS detector in the r-z plane showing all Run 2 luminometer PLT, BCM1F, DTs, and HF location.
@@
 It consists of four barrel layers (L1-L4) at radii of 29, 68, 109 and 160 mm and three forward disks (D1-D3) on each end at distances of 291, 396, and 516 mm of pixel sensors from the center of the detector as shown in Fig.~\ref{fig:phaseI_upgrade}.
-It is built from 1856 silicon sensor modules, 1184 modules in the barrel layers (BPIX) and 672 modules for the forward disks (FPIX).
+It is built from 1856 silicon sensor modules, 1184 modules in the barrel layers (BPIX) and 672 modules for the forward disks (FPIX) \cite{Adam:2748381}.
 Modules for barrel layers and forward disks are shown in Fig.~\ref{fig:pixelmodule}.
+Table~\ref{tab:modpix} shows the number of modules in each pixel layer and disk.
 The modules in BPIX L1 are designed to handle high particle densities and radiation levels.
@@
 Another challenge is the non-linearity of the pixel detector response, which can lead to inaccuracies in the luminosity measurement.
-Therefore, the motivation of this work is to develop and test more precise techniques for measuring the luminosity with the pixel detector, in order to improve the accuracy of the luminosity measurement and to better understand the effects of detector response on the measurement.
+Therefore, the motivation of this research work is to develop and test more precise techniques for measuring the luminosity with the pixel detector, in order to improve the precision of the luminosity measurement and to better understand the effects of detector response on the measurement.
 
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/phaseI_upgrade_pixel_detector.png}
-\caption{%
-   Layout of the CMS Phase-1 pixel detector in longitudinal view. 
+\caption[Pixel detector layout]{%
+   Layout of the CMS Phase-1 upgraded pixel detector in longitudinal view. 
 }
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/silicon_pixel_module.png}
-\caption{%
+\caption[Design of pixel module]{%
    Pixel detector modules for BPIX L1 (left), BPIX L2-4 (middle), and
@@
       \end{tabular}
-    \caption{Number of pixel detector modules in each layer and disk}
+    \caption[\# modules in pixel layers and disks]{Number of pixel detector modules in each layer and disk.}
     \label{tab:modpix}
@@
 
-The Pixel Cluster Counting (PCC) method is one of the two primary luminosity measurement methods used at the CMS experiment.
+The Pixel Cluster Counting (PCC) method is one of the main luminosity measurement methods used at the CMS experiment.
 The PCC method is based on counting the number of pixel clusters produced by the collisions in the CMS pixel detector, which is a high-resolution silicon detector located close to the collision point.
@@
 The PCC method is based on the assumption that the number of pixel clusters produced is proportional to the number of collisions, and therefore to the luminosity.
-The proportionality constant is called the pixel cluster visible cross section, and it can be determined from a calibration measurement.
+The proportionality constant is called the pixel detector visible cross section, and it can be determined from a calibration measurement.
 The PCC method is implemented in two stages: the online and offline stages.
@@
 The offline luminosity measurement is more accurate than the online measurement, as it takes into account various corrections and calibrations that are not possible in real time.
-The offline luminosity measurement is also used to determine the luminosity scale and the absolute luminosity, which is the total number of collisions per unit time and per unit area.
-Steps involved in the PCC method for measuring luminosity are as follows,
+The offline luminosity measurement is also used to determine the absolute luminosity scale, which is obtained from beam parameters.
+There are several steps involved in the PCC method for measuring luminosity as described below.
 
@@
 This is typically done using trigger systems that select events that are likely to be of interest based on their energy, particle multiplicity, or other criteria.
-Once the events of interest have been selected, the next step is to reconstruct the pixel clusters in each event using the algorithm described in the previous answer.
+Once the events of interest have been selected, the next step is to reconstruct the pixel clusters in each event using the algorithm described in the previous bullet point.
 This involves identifying individual pixel hits, identifying seed pixels, building pixel clusters around each seed pixel, and parameterizing the clusters.
@@
 One advantage is its high precision and stability, as it is based on a well-understood physical process and has a small systematic uncertainty.
-Another advantage is its independence from the beam conditions, as the pixel detector is insensitive to the beam halo and the beam-gas interactions.
+%Another advantage is its independence from the beam conditions, as the pixel detector is insensitive to the beam halo and the beam-gas interactions.
 The PCC method is also robust against pile-up, which is the presence of multiple proton-proton interactions in a single bunch crossing, as it can distinguish between pixel clusters produced by different collisions.
@@
 The PCC method has been extensively tested and validated by the CMS during the LHC Run 1 and Run 2, which corresponded to proton-proton collisions at center-of-mass energies of 7-8 TeV and 13 TeV, respectively.
-The PCC method has achieved a relative luminosity precision of about 2-3 \%, which is well within the design goals of the CMS.
+The PCC method has achieved a relative luminosity precision of about 2-3 \%, which is well within the design goals of the CMS \cite{CMS-PAS-LUM-18-002}.
 In the future, the PCC method will continue to be a key component of the CMS luminosity measurement strategy, as it provides a precise and robust measurement of the luminosity ratio between different datasets and periods.
@@
 
-\section{Previous studies related to PCC luminosity measurement}
+\newpage
+\section{Previous studies on PCC luminosity measurement}
+
+The Pixel Cluster Count (PCC) of various layers and disks, normalized to the total PCC, as a function of luminosity section can provide crucial insights into the detector's performance and stability over time and under different conditions \cite{CMS-PAS-LUM-15-001}\cite{CMS-PAS-LUM-16-001}.
+A luminosity section is a unit of data-taking time in the LHC, typically lasting about 23.36 seconds, during which the beam conditions are assumed to be stable.
+The luminosity delivered during each of these sections can vary, leading to different levels of activity in the detector.
+
+When these ratios are plotted against lumi sections, several key aspects can be studied:
+
+\begin{itemize}
+\item Detector Stability: Stable ratios across lumi sections suggest that the detector is functioning consistently and reliably under varying luminosity conditions.
+Abrupt spikes or drops could be indicative of potential problems such as radiation damage, electronic noise, or other instabilities in the detector.
+
+\item Long-Term Performance: By tracking these ratios over multiple lumi sections, one can monitor the long-term performance of the detector.
+This approach allows for the detection of gradual changes or trends, which could suggest a slow degradation of the detector components.
+
+\item Layer/Disk-Specific Analysis: This type of plot can reveal layer or disk-specific issues.
+For instance, if one layer's PCC ratio deviates significantly from the norm in high luminosity sections, it might suggest that this layer is particularly sensitive to high luminosity or is underperforming.
+
+\item Operational Adjustments: Observations from these plots can guide operational adjustments.
+If the PCC ratios for certain layers or disks consistently deviate under specific luminosity conditions, adjustments could be made in the detector operation to account for these variations.
+\end{itemize}
+
+The stability plots of the pixel detector for Run2018A, Run2018B and Run2018C are shown in Fig.~\ref{fig:RunA_PCC_ratios}, Fig.~\ref{fig:RunB_PCC_ratios}, Fig.~\ref{fig:RunC_PCC_ratios} respectively where the PCC ratios are not stable for some layers and disks with time.
+These PCC ratios as a function of luminosity sections, where each section represents about 23.36 seconds of data collection, allows physicists to conduct a nuanced evaluation of the pixel detector's performance and stability, identify potential issues, and make necessary operational modifications to ensure the detector's efficiency.
 
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/Run2018A_old.png}
-\caption{%
+\caption[PCC ratios for period 2018A]{%
+Left: Luminosity ratios for various sub detectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018A.
+Right: X Profile of luminosity ratios vs lumi section graph for various sub detectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section for Run2018A.
 
 }
-\label{fig:pixelmodule}
+\label{fig:RunA_PCC_ratios}
 \end{figure}
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/Run2018B_old.png}
-\caption{%
-
+\caption[PCC ratios for period 2018B]{%
+Left: Luminosity ratios for various sub detectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018B.
+Right: X Profile of luminosity ratios vs lumi section graph for various sub detectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section for Run2018B.
 }
-\label{fig:pixelmodule}
+\label{fig:RunB_PCC_ratios}
 \end{figure}
@@
 \centering
-\includegraphics[width=1\textwidth]{ashish_thesis/Run2018B_old.png}
-\caption{%
-
+\includegraphics[width=1\textwidth]{ashish_thesis/Run2018C_old.png}
+\caption[PCC ratios for period 2018C]{%
+Left: Luminosity ratios for various sub detectors L2, L3, L4, D1, D2, D3 of pixel detector as a function of lumi section for Run2018C.
+Right: X Profile of luminosity ratios vs lumi section graph for various sub detectors L2, L3, L4, D1, D2, D3 of pixel detector showing luminosity fraction as a function of lumi section for Run2018C.
 }
-\label{fig:pixelmodule}
+\label{fig:RunC_PCC_ratios}
 \end{figure}

### 2023-07-05 tesis_Ashish/Chapter3/chapter3.tex
AS thesis update

@@
 
-One widely used method for the calibration of luminosity measurement devices is the van der Meer (VdM) scan.
+%One of the widely used method for the calibration of luminosity measurement devices is the van der Meer (VdM) scan method.
+A prevalent technique for calibrating luminosity measurement devices is the van der Meer (VdM) scan method.
 This method is named after Simon van der Meer, a Dutch physicist and Nobel laureate, who developed the technique in the 1960s.
-van der Meer calibration is a technique used to determine the absolute luminosity of colliding beams in particle accelerators.
+These scans are performed to relate the collision rate of a given luminometer to the absolute luminosity determined from the measured beam parameters.
+The proportionality constant is called the visible cross section.
 It involves scanning the beams across each other in the horizontal and vertical planes to measure the beam overlap integral, which is proportional to the luminosity.
 The first step in the VdM calibration is to scan the colliding beams across each other.
-This is done by displacing the beams in the horizontal (x) and vertical (y) planes independently while keeping the other direction fixed.
+This is done by displacing the beams in the horizontal (x) and vertical (y) planes independently while keeping the other direction fixed as shown in left part of Fig.
+\ref{fig:vdm_scan_method}.
 The scans are performed at several different positions along the collision point, creating a series of data points for each plane.
-The data points collected during the scans are then fitted with Gaussian function or other suitable function like double gaussian, Poly2G, Poly4G, etc to determine the beam overlap integrals in the x and y directions.
+The data points collected during the scans are then fitted with Gaussian function or other suitable function like double gaussian, Poly2G, Poly4G, etc as shown in right part of Fig.
+\ref{fig:vdm_scan_method}  to determine the beam overlap integrals in the x and y directions.
 The product of the integrals in the two planes yields the total beam overlap integral.
 %The event rate is proportional to the luminosity and is given by the product of the cross-section ($\sigma$) and luminosity.
-The beam overlap integral is the integral of the product of the beam overlap width in the horizontal and vertical planes over the entire interaction region.
+The beam overlap integral is the integral of the product of the beam overlap width in the horizontal and vertical planes over the entire interaction region \cite{vanderMeer1968}.
 It is an essential parameter in determining the absolute luminosity.
 
-\section{van der Meer (vdM) calibration}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1\textwidth]{ashish_thesis/vdm_method.png}
+    \caption[Schematic of van der Meer scan]{Left: Scanning the beams across each other (±3$\sigma$) in the transverse plane, horizontal (x-scan) and vertical (y-scan) directions.
+Right: Rate is measured as a function of beam separation}
+    \label{fig:vdm_scan_method}
+\end{figure}
 
-van der Meer (vdM) scans are done to measure change in rate as a function of beam overlap that is used to determine the visible cross section $\sigma_{vis}$ of the pixel detector which is a calibration constant in the relation between rate of a quantity (clusters, coincidences) read out by the detector and the instantaneous luminosity.
+\section{van der Meer (vdM) method}
+
+In the van der Meer (vdM) scans,  rate is plotted as a function of beam overlap widths along x and y directions that is used to determine the visible cross section $\sigma_{vis}$ of the pixel detector which is a calibration constant in the relation between rate of a quantity (clusters, coincidences) read out by the detector and the instantaneous luminosity.
 
@@
 
-where $N_1, N_2$ are the number of protons in the colliding bunches, f is the LHC orbit frequency whose value is 11246Hz,  $\rho_1(x,y)$ and $\rho_2(x+\Delta x,y+\Delta y)$ are the two dimensional particle density distribution functions for each colliding bunch separated by $\Delta x$ and $\Delta y$ in x and y directions.
+where $N_1, N_2$ are the number of protons in the colliding bunches, f is the LHC orbit frequency whose value is 11246Hz,  $\rho_1(x,y)$ and $\rho_2(x+\Delta x,y+\Delta y)$ are the two dimensional particle density distribution functions for each colliding bunch separated by $\Delta x$ and $\Delta y$ in x and y directions  \cite{CMS-PAS-LUM-17-004}.
 
@@
 
+The calibration of luminosity measurement by the CMS experiment in the 2018 proton-proton data taking at √s = 13 TeV was performed during
+
+LHC fill 6868 on June 30 and July 1, 2018 at √s = 13 TeV
+
+Zero-bias triggers on 5 bunch pairs (BCIDs 265, 865, 1780, 2192, and 3380)
+
+recorded events rate is 27.7 kHz.
+
+vdM scans are typically conducted at least once a year to ensure the luminometer is correctly calibrated.
+Results of these scans are used to normalize the data collected by the experiments during physics run.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1\textwidth]{ashish_thesis/vdm_program_2018.png}
+    \caption[2018 vdM program]{Beam position along x and y is plotted as a function of time showing different types of scans.
+#3 and #10 are vdM scans, #4 and #9 are offset scans, #5, #7 and #8 are beam imaging scans, #6 is emittance scan.
+}
+    \label{fig:vdm_prog_2018}
+\end{figure}
+
 \section{Background Estimation}
@@
 These contributions can affect the precision of the luminosity measurement and lead to systematic uncertainties in the calibration.
-Beam-separation scans can be performed with increased beam separations (i.e., with the beams not fully overlapped).
+Beam-separation scans are performed with increased beam separations (i.e., with the beams not fully overlapped).
 These scans can provide an estimate of the background contributions when the beams are not colliding.
-Sources of machine induced backgrounds are as follows,
+Sources of machine induced backgrounds are described below.
 
@@
 
-The poly2G model, or the "polynomial plus two Gaussians" model, is a fitting function that combines a second-order polynomial function and two Gaussian functions.
+The poly2G model, or the "Gaussian function with a polynomial term" model, is a fitting function that combines a second-order polynomial function and a Gaussian function.
 It is a versatile and flexible model that can be used to fit various types of data, including the PCC rate plot in the context of the Van der Meer (VdM) calibration process.
 In a PCC rate plot, the event rate is plotted as a function of the beam separation.
-The poly2G model can be employed to fit the PCC rate plot to extract the beam parameters, such as the beam widths and the center positions, which are essential for the luminosity measurement.
-The general form of the poly2G model is as follows,
+The poly2G model can be employed to fit the PCC rate plot to extract the beam parameters, such as the beam overlap widths and the center positions, which are essential for the luminosity measurement \cite{Cekmecelioglu:2775639}.
+The general form of the poly2G model is
 
@@
 
+\begin{comment}
+
 The background estimation for the PCC rate is done with two super-separation scans SS1 and SS2.
@@
       \end{tabular}
-    \caption{Mean for the background estimated with the SS1 and SS2 data, separately for all five BCIDs and averaged.}
+    \caption[Background in PCC rate]{Mean for the background estimated with the SS1 and SS2 data, separately for all five BCIDs and averaged.}
     \label{tab:vdm:SS1_SS2}
@@
 \ref{fig:fitquality} shows chi2/ndof for vdM and imaging scans with an average value of 0.4514 where the Poly2G fit model converges for all BCIDs.
-Peak value and beam overlap along X and Y are extracted from fit to calculate PCC visible cross section $\sigma_{vis}$.
+Peak value and beam overlap along X and Y are extracted from fit to calculate PCC visible cross section.
 PCC visible cross section for $2\%$ rms common module vetolist is 960.601 $\pm$ 0.851(stat.) mb.
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{ashish_thesis/vdM_fit_cveto.png}
-    \caption{vdM fit 2\% rms common veto.}
+    \includegraphics[width=1\textwidth]{ashish_thesis/vdM_fit_cveto.png}
+    \caption[PCC rate fit]{Normalized rates and the resulting fitted poly2G scan curves as a function of the beam separation for a single bunch (BCID 865) as recorded by PCC for a scan in the x (left) and y direction (right).
+Background subtraction and the corrections  have been applied to the raw data before the fit.}
     \label{fig:fitquality}
@@
     \centering
-    \includegraphics[width=0.6\textwidth]{ashish_thesis/fit_quality_chisquare.png}
-    \caption{chi2/ndof for all vdM and imaging scans.}
+    \includegraphics[width=1\textwidth]{ashish_thesis/fit_quality_chisquare.png}
+    \caption[Fit quality]{chi2/ndof for all vdM and imaging scans.}
     \label{fig:fitquality}
@@
     \centering
-    \includegraphics[width=0.7\textwidth]{ashish_thesis/sigma_vis_per_scan.png}
-    \caption{$\sigma_{vis}$ per scan where red line shows the average value.}
+    \includegraphics[width=1\textwidth]{ashish_thesis/sigma_vis_per_scan.png}
+    \caption[PCC visible cross section]{Visible cross section per scan where red line shows the average value.}
     \label{fig:sigmaperscan}
 \end{figure}
+
+\end{comment}
 

### 2023-07-05 tesis_Ashish/Chapter4/chapter4.tex
AS thesis update

@@
-\chapter{Methodology}  %Title of the First Chapter
+\chapter{Run 2 Luminosity Measurement}  %Title of the First Chapter
 
@@
 
+%Chapter 4: Run 2 Luminosity Measurement
+
+%Detector Module selection
+%Afterglow Model
+%vdM Calibration Results
+%Luminosity for Physics Fills
+%Systematic Uncertainties
+
 \section{Datasets}
 
-2018 luminosity data taking is divided into seven periods namely A, B, C, D1, D2, D3 and D4 as shown in Fig.
-\ref{fig:period_bound}.
-vdM data is shown during period B corresponding to Fill 6868.
+For studying 2018 PCC dataset, we have divided CMS luminosity data taking into seven periods: A, B, C, D1, D2, D3, and D4, as depicted in % 2018 CMS luminosity data taking is divided into seven periods namely A, B, C, D1, D2, D3 and D4
+as shown in Fig. \ref{fig:period_bound}. During period B, specifically corresponding to Fill 6868, van der Meer (vdM) scans were conducted for calibrating the luminometer.
+%vdM data is shown during period B corresponding to Fill 6868.
 Run range for each period is shown in Table \ref{tab:period run ranges}.
@@
 \begin{itemize}
+
 \item CMSSW: The CMS Software (CMSSW) is a comprehensive software framework developed for the Compact Muon Solenoid (CMS) experiment at the Large Hadron Collider (LHC) at CERN.
@@
 
-\section{Pixel module veto list}
+\section{Module Selection}
 
@@
 
-\section{Afterglow corrections}
+\section{Afterglow Model}
 
@@
 \end{figure}
+
+\section{vdM Calibration Results}
+
+The background estimation for the PCC rate is done with two super-separation scans SS1 and SS2.
+The mean and error are obtained from the $y$ projection of PCC per NB4 plotted as a function of time.
+The results for five different BCIDs are shown in Table~\ref{tab:vdm:SS1_SS2}, using the reprocessed PCC data for Fill 6868.
+The overall background correction applied to raw PCC rate is $0.02757\pm0.01987$, which is calculated by taking the average of the mean values of SS1 and SS2.
+
+\begin{table}
+  \begin{center}
+    \begin{tabular}{ccccc}
+    \textbf{BCID}   & \textbf{Mean (SS1)} & \textbf{Mean (SS2)} \\ \hline
+      265     &  0.02902    &  0.02743    \\
+        865  &    0.02572  &     0.0281  \\
+       1780    &  0.02862   &     0.0286  \\
+       2192   &  0.02729  &     0.02323  \\
+        3380  &  0.02882  &    0.02896   \\
+      \end{tabular}
+    \caption[Background in PCC rate]{Mean for the background estimated with the SS1 and SS2 data, separately for all five BCIDs and averaged.}
+    \label{tab:vdm:SS1_SS2}
+  \end{center}
+\end{table}
+
+Fig.
+\ref{fig:fitquality} shows chi2/ndof for vdM and imaging scans with an average value of 0.4514 where the Poly2G fit model converges for all BCIDs.
+Peak value and beam overlap along X and Y are extracted from fit to calculate PCC visible cross section.
+PCC visible cross section for $2\%$ rms common module vetolist is 960.601 $\pm$ 0.851(stat.) mb.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1\textwidth]{ashish_thesis/vdM_fit_cveto.png}
+    \caption[PCC rate fit]{Normalized rates and the resulting fitted poly2G scan curves as a function of the beam separation for a single bunch (BCID 865) as recorded by PCC for a scan in the x (left) and y direction (right).
+Background subtraction and the corrections  have been applied to the raw data before the fit.}
+    \label{fig:fitquality}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1\textwidth]{ashish_thesis/fit_quality_chisquare.png}
+    \caption[Fit quality]{chi2/ndof for all vdM and imaging scans.}
+    \label{fig:fitquality}
+\end{figure}
+
+The visible cross section per scan is averaged over all BCIDs and its scan to scan variation is shown in Fig. \ref{fig:sigmaperscan}.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1\textwidth]{ashish_thesis/sigma_vis_per_scan.png}
+    \caption[PCC visible cross section]{Visible cross section per scan where red line shows the average value.}
+    \label{fig:sigmaperscan}
+\end{figure}
+
+%\newpage
+
+\section{Luminosity for Physics Fills}
+
+\section{Systematic Uncertainties}
+
+\subsection{Uncertainties associated with the Van der Meer calibration}
+
+\begin{itemize}
+
+ \item  Orbit Drift: Refers to the gradual displacement of the beam orbit from its ideal trajectory due to various effects such as ground motion, magnetic field fluctuations, and thermal expansion.
+This can result in reduced beam intensity and beam quality.
+
+ \item  X-Y Nonfactorization: Refers to the failure of the x and y coordinates of a particle beam to factorize, meaning that the beam profile cannot be expressed as a product of independent x and y profiles.
+This can result in beam asymmetries and other effects.
+
+ \item Beam-Beam Deflection: Refers to the mutual interaction of two colliding particle beams, resulting in the deflection of the individual beams due to the electromagnetic fields generated by the other beam.
+This effect can lead to beam losses and reduced luminosity.
+
+ \item Dynamic $\beta$: Refers to the time-varying beta function of a particle beam, which describes the rate at which the beam diverges or converges as it propagates.
+This effect can be important for beam stability and the control of beam emittance.
+
+\item Beam Current Calibration: Refers to the process of accurately measuring the current of a particle beam, which is essential for many beam diagnostics and control systems.
+
+\item Ghosts and Satellites: Refers to unwanted signals in a detector or measurement system that can arise from various sources such as scattered radiation, electronic noise, or interference from other particles.
+These can lead to inaccurate measurements and reduced data quality.
+
+\item Scan to Scan Variation: Refers to the variation in experimental results obtained from different scans or measurements, which can arise from various sources such as statistical fluctuations, instrument drift, or systematic errors.
+
+\item Bunch to Bunch Variation: Refers to the variation in the properties of individual particle bunches within a beam, such as their intensity, energy spread, or emittance.
+This effect can be important for beam tuning and optimization.
+
+\item Cross-Detector Consistency: Refers to the agreement between measurements obtained from different detectors or measurement systems.
+This is important for verifying the accuracy and reliability of experimental results.
+
+\item Background Subtraction: Refers to the process of removing unwanted signals from a measurement or detector system that arise from sources other than the physical phenomenon of interest, such as noise, cosmic rays, or other particles.
+This is essential for obtaining accurate measurements of the physical signal.
+
+  \end{itemize}
+
+\subsection{Uncertainties associated with physics data taking}
+
+\begin{itemize}
+
+\item Stability: The CMS pixel detector is a complex instrument with many components, including silicon sensors and readout electronics, that must operate consistently and with high precision over long periods.
+Any variations in the performance of the detector can affect the efficiency of the pixel cluster counting method and lead to uncertainties in the luminosity measurement.
+
+  One example of how the stability of the detector can affect the luminosity measurement is through changes in the detector's noise level.
+The noise level refers to the level of electronic noise present in the detector, which can interfere with the detection of pixel clusters produced by proton-proton collisions.
+If the noise level increases, the efficiency of the pixel cluster counting method may decrease, leading to an underestimation of the luminosity.
+Conversely, if the noise level decreases, the efficiency of the method may increase, leading to an overestimation of the luminosity.
+
+  Another example is changes in the efficiency of the pixel detector.
+The efficiency of the detector refers to the fraction of proton-proton collisions that produce pixel clusters that can be detected and counted by the method.
+Any changes in the efficiency of the detector, for example due to changes in the gain or response of the silicon sensors, can lead to uncertainties in the luminosity measurement.
+
+  To mitigate these uncertainties, the CMS collaboration performs regular calibrations and monitoring of the detector performance, as well as cross-checks with other luminosity measurement techniques
+
+  Systematic uncertainties due to stability in the detector itself for the pixel cluster counting method are typically estimated by studying the performance of the method over time and comparing it to simulations or other measurements.
+Uncertainties due to changes in the noise level and detector efficiency are typically estimated separately and combined to obtain the total systematic uncertainty
+
+\item Linearity: the luminosity obtained from the PCC method is compared to that obtained from the HFOC method for a given set of collisions.
+Any deviations between the two measurements are used to estimate the linearity uncertainty in the PCC method.
+
+  The linearity uncertainty is typically quantified as a systematic uncertainty in the luminosity measurement, expressed as a percentage of the measured luminosity.
+This uncertainty can be estimated by fitting the PCC and HFOC measurements to a linear function and calculating the deviation of the PCC measurement from the linear fit.
+
+\item Type 1 afterglow refers to the persistence of charge in the pixels of the detector after a collision event.
+This charge can be produced by various sources, such as ionization due to the passage of charged particles, or leakage currents in the readout electronics.
+If this charge is not properly accounted for, it can be mistakenly counted as pixel clusters produced by subsequent collision events, leading to an overestimation of the luminosity.
+
+  Type 2 afterglow refers to the persistence of noise in the detector after a collision event.
+This noise can be produced by various sources, such as thermal or radiation-induced effects, and can also interfere with subsequent collisions.
+If this noise is not properly accounted for, it can lead to a reduction in the efficiency of the pixel cluster counting method and an underestimation of the luminosity.
+
+\end{itemize}

### 2023-07-10 tesis_Ashish/Chapter2/chapter2.tex
update

@@
 \item Layer/Disk-Specific Analysis: This type of plot can reveal layer or disk-specific issues.
-For instance, if one layer's PCC ratio deviates significantly from the norm in high luminosity sections, it might suggest that this layer is particularly sensitive to high luminosity or is underperforming.
+For instance, if one layer's PCC ratio deviates significantly from the norm in high lumi sections, it might suggest that this layer is particularly sensitive to low luminosity or is underperforming.
 

### 2023-07-10 tesis_Ashish/Chapter4/chapter4.tex
update

@@
 
-\section{Datasets}
-
-For studying 2018 PCC dataset, we have divided CMS luminosity data taking into seven periods: A, B, C, D1, D2, D3, and D4, as depicted in % 2018 CMS luminosity data taking is divided into seven periods namely A, B, C, D1, D2, D3 and D4
-as shown in Fig. \ref{fig:period_bound}. During period B, specifically corresponding to Fill 6868, van der Meer (vdM) scans were conducted for calibrating the luminometer.
+\section{Dataset}
+
+For studying the performance of PCC luminometer during 2018 data taking, we have divided CMS luminosity data taking into seven periods: A, B, C, D1, D2, D3, and D4, as depicted in % 2018 CMS luminosity data taking is divided into seven periods namely A, B, C, D1, D2, D3 and D4
+Fig. \ref{fig:period_bound}. Run ranges for each period are shown in Table \ref{tab:period_run_ranges}.
+During period B, specifically corresponding to Fill 6868, van der Meer (vdM) scans were conducted for calibrating the luminometer.
 %vdM data is shown during period B corresponding to Fill 6868.
-Run range for each period is shown in Table \ref{tab:period run ranges}.
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.8\textwidth]{ashish_thesis/period_boundary.png}
-\caption{%
-   2018 luminosity data taking periods showing data taking period boundaries and vdM calibration data.
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.9\textwidth]{ashish_thesis/period_boundary.png}
+\caption[2018 CMS luminosity data taking periods.]{%
+   2018 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
 }
@@
 \end{figure}
+
+\begin{table}
+  \begin{center}
+    \begin{tabular}{ccccc}
+    \textbf{Period}   & \textbf{Run range} \\ \hline
+     2018A      &        315252-316995         \\
+     2018B      &        317080-319311         \\
+     2018C      &        319337-320065         \\
+     2018D1     &        320500-321665        \\
+     2018D2     &        321710-322964         \\
+     2018D3     &        323363-324420         \\
+     2018D4     &        324564-325175        \\
+      \end{tabular}
+    \caption[Run ranges]{2018 luminosity data periods with run ranges.}
+    \label{tab:period_run_ranges}
+  \end{center}
+\end{table}
+
+In the study under consideration, we have utilized a series of datasets corresponding to the data-taking periods of 2018, namely 2018A, 2018B, 2018C, and 2018D as shown in Table \ref{tab:datasets}.
+These datasets have been drawn from the Alignment and Calibration (AlCa) project, an integral component of the Compact Muon Solenoid (CMS) experiment conducted at the Large Hadron Collider.
+The dataset selection includes two subsets denoted as AlCaPCCRandom and AlCaPCCZeroBias.
+The AlCaPCCRandom dataset comprises of data where trigger is applied on both colliding and non-colliding bunches, thereby providing a holistic and representative view of the whole dataset.
+On the other hand, the AlCaPCCZeroBias dataset encapsulates events that have passed the trigger system with no bias where trigger is applied on only colliding bunches, thereby serving as an unbiased reference dataset.
+In terms of processing, the selected datasets have undergone an Express processing pathway.
+This rapid processing approach, while less detailed than the full reprocessing, provides valuable and timely insights into the data quality and physics performance.
+The datasets fall within the ALCARECO (ALignment, CALibration, and REConstruction objects) data tier, which specifically encompasses information pertinent to detector alignment and calibration, forming a crucial resource in our analysis.
+The timestamps associated with these datasets (e.g., $'13Mar2023\_UL2018\_PCC'$) indicate that they have undergone a reprocessing or update post their initial collection in 2018.
+%This reprocessing phase enhances the scientific value of these datasets, by incorporating improved calibrations and alignment, and updates to the data reconstruction algorithms.
+Consequently, the reprocessed datasets used in this thesis afford a more accurate and comprehensive representation of the physics events under investigation.
+
+\begin{table}[htbp]
+  \centering
+  \begin{tabular}{@{}c@{\hspace{0.5cm}}p{6.5cm}p{6.5cm}@{}}
+    \textbf{Period} & \textbf{Random Trigger Dataset} & \textbf{Zero Bias Dataset} \\
+    2018A & /AlCaLumiPixels/Run2018A-\newline AlCaPCCRandom-15Apr2023\_UL2018\_\newline 315252\_316062\_PCCRandom\_-v1/ALCARECO, \newline /StreamALCALUMIPIXELSEXPRESS/\newline Run2018A-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018A-\newline AlCaPCCZeroBias-\newline 13Mar2023\_UL2018\_PCC-v1/ALCARECO \\
+    2018B & /StreamALCALUMIPIXELSEXPRESS/\newline Run2018B-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018B-\newline AlCaPCCZeroBias-\newline 13Mar2023\_UL2018\_PCC-v1/ALCARECO \\
+    2018C & /StreamALCALUMIPIXELSEXPRESS/\newline Run2018C-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018C-\newline AlCaPCCZeroBias-\newline 13Mar2023\_UL2018\_PCC-v1/ALCARECO \\
+    2018D & /StreamALCALUMIPIXELSEXPRESS/\newline Run2018D-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018D-\newline AlCaPCCZeroBias-\newline 13Mar2023\_UL2018\_PCC-v1/ALCARECO \\
+  \end{tabular}
+  \caption[PCC datasets]{Datasets used for studying performance of PCC luminometer \cite{CERNDAS}}
+  \label{tab:datasets}
+\end{table}
+
+\begin{comment}
+
+\begin{table}[htbp]
+  \centering
+  \begin{tabular}{@{}c@{\hspace{0.5cm}}p{6.5cm}p{6.5cm}@{}}
+    \textbf{Period} & \textbf{Random Trigger Dataset} & \textbf{Zero Bias Dataset} \\[1em]
+    2018A & /AlCaLumiPixels/Run2018A-\newline AlCaPCCRandom-15Apr2023\_UL2018\_\newline 315252\_316062\_PCCRandom\_-v1/ALCARECO, \newline /StreamALCALUMIPIXELSEXPRESS/\newline Run2018A-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018A-\newline AlCaPCCZeroBias-\newline 13Mar2023\_UL2018\_PCC-v1/ALCARECO \\[1em]
+    2018B & /StreamALCALUMIPIXELSEXPRESS/\newline Run2018B-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018B-\newline AlCaPCCZeroBias-\newline 13Mar2023\_UL2018\_PCC-v1/ALCARECO \\[1em]
+    2018C & /StreamALCALUMIPIXELSEXPRESS/\newline Run2018C-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018C-\newline AlCaPCCZeroBias-\newline 13Mar2023\_UL2018\_PCC-v1/ALCARECO \\[1em]
+    2018D & /StreamALCALUMIPIXELSEXPRESS/\newline Run2018D-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018D-\newline AlCaPCCZeroBias-\newline 13Mar2023\_UL2018\_PCC-v1/ALCARECO \\[1em]
+  \end{tabular}
+  \caption{Datasets used for studying performance of PCC luminometer}
+  \label{tab:datasets}
+\end{table}
 
@@
     2018C & /StreamALCALUMIPIXELSEXPRESS/Run2018C-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018C-AlCaPCCZeroBias-13Mar2023\_UL2018\_PCC-v1/ALCARECO \\
-    2018D & /StreamALCALUMIPIXELSEXPRESS/Run2018D-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018D-AlCaPCCZeroBias-PromptReco-v2/ALCARECO \\
+    2018D & /StreamALCALUMIPIXELSEXPRESS/Run2018D-AlCaPCCRandom-Express-v1/ALCARECO & /AlCaLumiPixels/Run2018D-AlCaPCCZeroBias-13Mar2023_UL2018_PCC-v1/ALCARECO \\
   \end{tabular}
-  \caption{Dataset Information}
+  \caption{Datasets used for studying performance of PCC luminometer}
   \label{tab:datasets}
@@
 
-\textbf{/AlCaLumiPixels/Run2018A-AlCaPCCRandom15Apr2023\_UL2018\_315252\_316062\_PCCRandom\_-v1/ALCARECO}
-
+\end{comment}
+
+%\textbf{/AlCaLumiPixels/Run2018A-AlCaPCCRandom15Apr2023\_UL2018\_315252\_316062\_PCCRandom\_-v1/ALCARECO}
+
+\textbf{\url{/AlCaLumiPixels/Run2018A-AlCaPCCRandom15Apr2023_UL2018_315252_316062_PCCRandom_-v1/ALCARECO}}
 %\textbf{/AlCaLumiPixels/Run2018A-AlCaPCCRandom15Apr2023_UL2018_315252_316062_PCCRandom_-v1/ALCARECO}
@@
 
-\item $15Apr2023_UL2018_315252_316062_PCCRandom_-v1$: This part represents the processing version, date, and run range of the dataset.
+\item $15Apr2023\_UL2018\_315252\_316062\_PCCRandom\_-v1$: This part represents the processing version, date, and run range of the dataset.
 "15Apr2023" is the date when this specific version of the dataset was created.
@@
 
-$\textbf{/StreamALCALUMIPIXELSEXPRESS/Run2018A-AlCaPCCRandom-Express-v1/ALCARECO}$
+%$\textbf{/StreamALCALUMIPIXELSEXPRESS/Run2018A-AlCaPCCRandom-Express-v1/ALCARECO}$
+
+\textbf{\url{/StreamALCALUMIPIXELSEXPRESS/Run2018A-AlCaPCCRandom-Express-v1/ALCARECO}}
 
@@
 
-$\textbf{/AlCaLumiPixels/Run2018A-AlCaPCCZeroBias-13Mar2023\_UL2018\_PCC-v1/ALCARECO}$
+%$\textbf{/AlCaLumiPixels/Run2018A-AlCaPCCZeroBias-13Mar2023\_UL2018\_PCC-v1/ALCARECO}$
+
+\textbf{\url{/AlCaLumiPixels/Run2018A-AlCaPCCZeroBias-13Mar2023_UL2018_PCC-v1/ALCARECO}}
 
@@
 
-$\textbf{/AlCaLumiPixels/Run2018D-AlCaPCCZeroBias-PromptReco-v2/ALCARECO}$
+%$\textbf{/AlCaLumiPixels/Run2018D-AlCaPCCZeroBias-PromptReco-v2/ALCARECO}$
+
+\begin{comment}
+
+\textbf{\url{/AlCaLumiPixels/Run2018D-AlCaPCCZeroBias-PromptReco-v2/ALCARECO}}
 
@@
 \end{itemize}
+
+\end{comment}
 
@@
 
-The calibration of luminosity measurement by the CMS experiment in the 2018 proton-proton data taking at $\sqrt{s}$ = 13 TeV was performed during
+The calibration of luminosity measurement by the CMS experiment luminometers in the 2018 proton-proton data taking at $\sqrt{s}$ = 13 TeV \cite{CMS-PAS-LUM-18-002} was performed during
 
@@
 
-To measure the luminosity using the pixel cluster counting method, pixel detector is divided into modules, each consisting of a number of pixels arranged in a grid.
-The number of pixel clusters produced in each module per unit time is proportional to the instantaneous luminosity of the collider.
-To implement this method, the pixel detector is operated in an integrated mode, where the detector is read out at a fixed time interval called a "lumi section".
-During each lumi section, the number of pixel clusters produced in each module is recorded, the rate of number of pixel clusters and visible cross section is used to determine the instantaneous luminosity of the collider.
-CMS software (CMSSW) version $10{\_}2{\_}2$  and $10{\_}6{\_}30$ are used for reprocessing PCC data.
+To measure the luminosity using the pixel detector, pixel cluster count is studied for each module, where a module consists of a number of pixels arranged in a grid.
+The number of pixel clusters recorded in each module per unit time is proportional to the instantaneous luminosity of the collider.
+To implement PCC method, the pixel detector is operated in an integrated mode, where the detector is read out at a fixed time interval called a "lumi section".
+During each lumi section, the number of pixel clusters produced in each module is recorded, the rate of pixel clusters and visible cross section of the detector is used to determine the instantaneous luminosity of the collider.
+PCC data is reprocessed, a procedure that involves the re-analysis of the data using refined or updated algorithms, calibrations, or detector conditions.
+
+\newpage
+The purpose of reprocessing can be multifold:
+
+\begin{itemize}
+
+\item Improved Algorithms or Calibration: As experiments progress, there can be improvements in algorithms or calibration techniques used to process the raw data.
+This can lead to a more accurate or efficient representation of the collected data.
+Reprocessing allows these improvements to be applied to previously collected data.
+
+\item Changes in Detector Conditions: Detector conditions might change over time due to factors like aging or upgrades.
+These changes can affect the interpretation of the data.
+By reprocessing, the data can be reinterpreted to account for these changes.
+
+\item Discovery of Issues or Errors: Sometimes, errors or issues in the original data processing might be discovered. Reprocessing the data allows these errors to be corrected.
+
+\end{itemize}
+
+In the context of PCC data, reprocessing can lead to a more accurate luminosity measurement, which in turn can affect the interpretation of the physics results derived from the LHC data.
+The luminosity measurement is crucial because it is directly linked to the determination of cross-sections, a fundamental quantity in the interpretation of the outcomes of high-energy particle physics experiments.
+
+CMS software (CMSSW) version $10{\_}2{\_}2$ is used for reprocessing random trigger PCC dataset and $10{\_}6{\_}30$  \cite{CMSReleaseNotes} is used for reprocessing zero bias PCC datasets.
 Datasets can be obtained by applying triggers on all bunches (colliding and non colliding) and only on colliding bunches to get random trigger and zero bias data respectively as described in previous section.
@@
 This is achieved through careful calibration of the detector and by using dedicated algorithms to estimate the contribution of pileup to the observed pixel cluster counts.
+
+\begin{comment}
 
@@
 \end{table}
+
+\end{comment}
 
@@
 Data storage and management: CMSSW uses the ROOT data format for the storage and management of data objects.
-ROOT is a powerful and flexible data storage and processing framework developed at CERN, which provides efficient data handling, advanced statistical analysis tools, and extensive data visualization capabilities.
+ROOT is a powerful and flexible data storage and processing framework developed at CERN, which provides efficient data handling, advanced statistical analysis tools, and extensive data visualization capabilities \cite{CMSWorkBook}.
 
@@
 The tool can generate plots and graphs to visualize the luminosity data, making it easier for researchers to interpret the results and identify trends or anomalies.
-Brilcalc is designed to be extensible, allowing users to develop custom plugins and scripts for advanced data analysis and visualization tasks.
+Brilcalc is designed to be extensible, allowing users to develop custom plugins and scripts for advanced data analysis and visualization tasks \cite{CMSLuminosityCalculationGuide}.
 
@@
 ROOT offers a rich set of tools for data processing, statistical analysis, and visualization.
-In the context of PCC luminosity measurement, ROOT is employed to analyze and process the output data from CMSSW, perform statistical analyses, and generate plots for data visualization.
+In the context of PCC luminosity measurement, ROOT is employed to analyze and process the output data from CMSSW, perform statistical analyses, and generate plots for data visualization \cite{ROOT}.
 
@@
 It offers researchers an alternative method for accessing various CMS data services without using the web-based DAS interface.
-The DASgoclient allows users to query and retrieve data in a more scriptable and automated manner, making it an essential tool for managing datasets and streamlining the data retrieval process for PCC luminosity measurements.
-
-\end{itemize}
+The DASgoclient allows users to query and retrieve data in a more scriptable and automated manner, making it an essential tool for managing datasets and streamlining the data retrieval process for PCC luminosity measurement.
+
+\end{itemize}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.8\textwidth]{ashish_thesis/pcc_stability_begin.png}
+\caption{%
+   Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
+}
+\label{fig:PCC_stab_begin}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.8\textwidth]{ashish_thesis/pixel_layer_disk_noveto_noselection.png}
+\caption{%
+   Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
+}
+\label{fig:PCC_stab_begin}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.8\textwidth]{ashish_thesis/pcc_frac_L0_veto.png}
+\caption{%
+   Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
+}
+\label{fig:PCC_stab_L0_veto}
+\end{figure}
 
@@
 \begin{itemize}
+
 \item Lumi section duration: The data collected for luminosity measurements are divided into lumi sections, each lasting for 23.36 seconds.
@@
 \item Selection criteria: Only pixel modules that demonstrate consistent and reliable performance throughout the entire 2018 year are considered good and included in the analysis.
-Modules that do not meet these criteria are classified as bad and excluded from the luminosity measurements.
-\end{itemize}
-
-By carefully analyzing the module weights and excluding the bad modules from the analysis, the instabilities in PCC luminosity measurements can be minimized.
-This process ensures that the data used for luminosity measurements are of high quality and can produce accurate results.
+Modules that do not meet these criteria are classified as bad and excluded from the luminosity measurement.
+
+\end{itemize}
+
+By carefully analyzing the module weights and excluding the bad modules from the analysis, the instabilities in PCC luminosity measurement can be minimized.
+This process ensures that the data used for luminosity measurement is of high quality and can produce precise results.
 
@@
 \centering
-\includegraphics[width=0.9\textwidth]{ashish_thesis/Module_weight.png}
-\caption{%
+\includegraphics[width=1\textwidth]{ashish_thesis/Module_weight.png}
+\caption[Steps involved to obtain module weights]{%
    Method to obtain module weights as a function of lumi section for categorizing good and bad modules.
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/good_bad_modules.png}
-\caption{%
-   Variation of normalized module weight with time. Modules showing significant change in module weight (shown in right figure) over time having large rms/mean values are used to make module vetolist.
+\caption[Good and bad module weights]{%
+   Change in normalized module weight with time. Modules showing significant change in module weight (shown in right figure) over time having large RMS/mean values are used to make module veto list.
 }
@@
 
-Module vetolist is first created for period B, vdM Fill and then for other periods A, C, D1, D2, D3 and D4 as follows,
+\newpage
+The module veto list is a list of detector modules that are excluded from the analysis of data due to their known or suspected high rate of background events or other issues that could affect the accuracy of the measurement.
+The inclusion of certain modules in the veto list is based on various factors, including:
+
+\begin{itemize}
+
+\item Radiation damage: The harsh radiation environment in the LHC can cause damage to the silicon pixel sensors over time, leading to increased leakage currents, noise, or reduced charge collection efficiency.
+
+\item Manufacturing defects: Defects in the silicon material or issues during the manufacturing process can result in poorly performing pixel modules.
+These defects may not be immediately evident but can become more pronounced overtime.
+
+\item Electronic noise: Noisy electronic components or crosstalk between channels can lead to an increased number of false signals or noise in the pixel module data.
+
+\item Temperature variations: Temperature fluctuations can affect the performance of the pixel modules, leading to changes in their noise levels, gain, or charge collection efficiency.
+
+\item High voltage issues: Problems with the high voltage supply to the pixel modules can result in unstable operation, leading to erratic behavior or complete module failure.
+
+\item Partial module failure: A pixel module may suffer from partial failure, with some pixels or readout channels not functioning properly.
+This can lead to an increased number of dead or noisy pixels in the module.
+
+\item Readout or data acquisition issues: Errors in the readout electronics or data acquisition system can lead to data corruption or loss, affecting the performance of the pixel modules.
+
+\item Calibration issues: Inaccurate or outdated calibration parameters can result in incorrect measurements, leading to the appearance of abnormal behavior in the pixel module data.
+
+\item Firmware or software issues: Bugs in the firmware or software responsible for controlling and reading out the pixel modules can lead to abnormal behavior or incorrect measurements.
+
+\item Mechanical or alignment issues: Mechanical stresses or misalignments during the installation or operation of the pixel detector can affect the performance of the pixel modules or cause them to fail.
+
+\item Contamination or environmental factors: Contamination of the pixel modules by dust, moisture, or other substances can affect their performance or cause them to fail.
+Similarly, external environmental factors, such as magneticfields or vibrations, can impact the operation of the pixel modules.
+
+\end{itemize}
+
+The inclusion of certain modules in the veto list is based on a careful analysis of the detector performance and the expected background rates in a given experiment.
+By excluding modules with high background rates or other issues, the analysis can be improved and the accuracy of the measurement can be increased.
+
+Module veto list consisting of bad modules is first created for period B, vdM Fill and then for other periods A, C, D1, D2, D3 and D4 as follows,
 
@@
 
-\item Poor statistics lumi sections are removed by applying selection on total PCC Fig. \ref{fig:PCC_cut} and \ref{fig:f_it}.
-
-\item All barrel layer 1 modules are removed as these modules are significantly affected by dynamic inefficiency effects, where the hit efficiency decreases at higher $L_{inst}$ due to the readout chip not being able to process all of the hits.
-\item A loose selection of 7\% based on rms/mean of module weight profile is applied where mean and rms values are obtained from y projection of module weight profile.
-Modules with significantly large rms/mean are removed with this loose selection as shown in Fig.
+\item Poor statistics lumi sections are removed by applying selection on total PCC Fig. \ref{fig:PCC_cut}. % and \ref{fig:f_it}.
+
+\item All barrel layer 1 modules are removed as these modules are significantly affected by dynamic inefficiency effects, where the hit efficiency decreases at higher instantaneous luminosity due to the readout chip not being able to process all of the hits.
+
+\item A loose selection of 7\% based on RMS/mean of module weight profile is applied where mean and rms values are obtained from y projection of module weight profile.
+Modules with significantly large RMS/mean are removed with this loose selection as shown in Fig.
 \ref{fig:outliermodules}.
 
-\item Module stability is re-evaluated based on rms/mean values using an iterative method where in each step, appropriate selections are applied to remove bad modules until stable luminosity is attained as sshown in Fig.
+\item Module stability is re-evaluated based on RMS/mean values using an iterative method where in each step, appropriate selections are applied to remove bad modules until stable luminosity is attained as sshown in Fig.
 \ref{fig:sec_it_cut}.
@@
 
-\item Period B module veto list is applied to these periods to determine remaining bad modules.
+\item Period B module vetolist is applied to these periods to determine remaining bad modules.
 
@@
 
-\item module weight comparisons between period B and these periods is done and modules with more than 3 sigma change in module weights are removed as shown in Fig.
-\ref{fig:mod_w_com} and Fig \ref{fig:mod_w_com_1}.
-.
-\end{itemize}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/Run2018B_totalPCC_cut.png}
-\caption{%
- Total PCC as a function of lumi section for period 2018B.  Appropriate selection on total PCC is applied to remove low statistics lumi sections.
+\item module weight comparisons between period B and these periods is done and modules with more than 3 sigma change in module weights are removed as shown in %Fig. \ref{fig:mod_w_com} and
+  Fig \ref{fig:mod_w_com_1}.                                                                              
+\end{itemize}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/Run2018B_totalPCC_cut.png}
+\caption[Selection to remove low statistics lumi sections]{%
+ Total PCC as a function of lumi section for period 2018B.  Appropriate selection on total PCC shown by the red line is applied to remove low statistics lumi sections.
 }
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/first_iteration.png}
-\caption{%
-   A loose cut of 7\% is applied on rms/mean values of module stability profile to remove outlier modules.
-}
-\label{fig:f_it}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.8\textwidth]{ashish_thesis/cut_selection.png}
-\caption{%
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=0.7\textwidth]{ashish_thesis/first_iteration.png}
+%\caption{%
+%   A loose cut of 7\% is applied on rms/mean values of module stability profile to remove outlier modules.
+%}
+%\label{fig:f_it}
+%\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/cut_selection.png}
+\caption[First iteration to remove outlier modules]{%
    RMS/mean of module weight profile for all modules. A loose selection of 7\% is applied to remove bad modules. Appropriate selections are applied in each iterative step to remove other bad modules.
@@
 \centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/second_iteration_cut.png}
-\caption{%
+\includegraphics[width=1\textwidth]{ashish_thesis/second_iteration_cut.png}
+\caption[Final iteration to remove outlier modules]{%
  Final selection on RMS/mean of 2\% is applied to obtain module veto list for each period.
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/mod_weight_comparison.png}
-\caption{%
-   Change in module weights between period A and B for all modules left after applying 2\% rms module vetolist.
-}
-\label{fig:mod_w_com}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.8\textwidth]{ashish_thesis/mod_weight_comp_1.png}
-\caption{%
-   Projection of change in module weights between period A and B. Modules showing more than 3 sigma change are added to the module vetolist.
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/mod_weight_comparison.png}
+%\caption{%
+%   Change in module weights between period A and B for all modules left after applying 2\% rms module vetolist.
+%}
+%\label{fig:mod_w_com}
+%\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/mod_weight_comp_1.png}
+\caption[Selection to remove modules due to change in module weights across period]{%
+   Projection of change in module weights between period A and B. Modules showing more than 3 sigma change in module weights are added to the module veto list.
 }
@@
 
- 2\% selection on rms/mean of module weight profile gives the best stability for all pixel detector barrel layers and forward disks.
+ 2\% selection on RMS/mean of module weight profile gives the best stability for all pixel detector barrel layers and forward disks.
 Bad modules found after applying this 2\% selection in the final iterative step are used to constitute a 2 $\%$ rms module veto list for each period as shown in Table \ref{tab:per period veto}.
@@
       \end{tabular}
-    \caption{2 \% rms module vetolist for each period showing number of good and bad modules.}
+    \caption[Module veto list for each period]{2 \% rms module vetolist for each period showing number of good and bad modules.}
     \label{tab:per period veto}
@@
 \end{table}
+
+\begin{table}[!ht]
+\centering
+\topcaption{%
+    PCC/ HFOC luminosity mean and rms values for new per period vetolist showing variation in mean values across period.
+}
+\begin{tabular}{ccccc}
+    \textbf{Period} & \textbf{mean} & \textbf{rms} &  \textbf{rms/mean} \\ \hline
+    A & 1.006 & 0.004183 & 0.004158 \\
+    B & 0.9981  & 0.003133 & 0.0031389 \\
+    C & 0.9989  & 0.003009 & 0.003012\\
+    D1 & 1.003  & 0.002441 & 0.002433 \\
+    D2 & 1.001  & 0.0029 & 0.00289 \\
+   D3  & 1  & 0.002115 & 0.002115 \\
+   D4  & 1.002  & 0.003673 & 0.003666 \\ 
+\end{tabular}
+\label{tab:pccvis_diffveto}
+\end{table}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.8\textwidth]{ashish_thesis/old_new_veto.png}
+\caption{%
+   klm
+}
+\label{fig:old_new_vetolist}
+\end{figure}
 
@@
       \end{tabular}
-    \caption{2\% rms common module vetolist. This vetolist is created by combining module vetolists for each period.}
+    \caption[Common module veto list for all periods]{2\% rms common module vetolist. This veto list is created by combining module veto lists for each period.}
     \label{tab:2commonveto}
@@
 
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/before_after_vdm_stability.png}
+\caption{%
+   Luminosity fraction (stability plots) before and after applying 2\% rms module vetolist.
+}
+\label{fig:b_a_stability_vdm}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/pcc_layer_disk_mean_rms.png}
+\caption{%
+pcc layer disk mean rms
+}
+\label{fig:pixellalyerdiskmeanrms}
+\end{figure}
+
 The relative contribution to PCC luminosity from each pixel detector layer and disk after removing low statistics lumi sections and applying 2\% rms common module vetolist is shown in Fig.
@@
 \centering
-\includegraphics[width=0.8\textwidth]{ashish_thesis/ProfileX_combined_testing_LUM_20-001.png}
-\caption{%
-   Stability profiles of pixel detector layer and disk modules for 2\% rms common module vetolist.
+\includegraphics[width=0.8\textwidth]{ashish_thesis/2percentcommonveto_pixellayerdisk.png}
+\caption[Pixel layer/disk stability]{%
+   Stability profiles of pixel detector layer and disk modules for 2\% rms common module veto list.
 }
@@
 %\subsection{Reasons for the inclusion of certain modules in the veto list}
+
+\begin{comment}
 
@@
 
+\end{comment}
+
 \section{Afterglow Model}
 
-Type 1 and Type 2 afterglow corrections are essential for obtaining accurate PCC measurements.
+Type 1 and Type 2 afterglow corrections are very important for precise PCC luminosity measurement.
+Type 1 afterglow noise, or electronic spillover, arises due to the lingering signal waveform within silicon.
+Contrarily, Type 2 afterglow noise emanates from the exponentially diminishing activation of the detector caused by the creation of secondary particles when the detector material encounters high-energy particles \cite{CMS-PAS-SMP-12-008}(as depicted in Fig.
+\ref{fig:pcc_afterglow}).
+
+The rectification of afterglow noise is achieved by constructing a model that replicates the tail of the afterglow from a single collision event.
+This model is then adjusted according to the luminosity of the event.
+In an ongoing process of correction, a histogram representing the collision events and containing bunch trains is adjusted, whereby the afterglow model is multiplied by the luminosity of each colliding pair and subsequently deducted from all subsequent collision events.
+This iterative process is repeated for all colliding pairs, ensuring each event is completely rectified prior to being used for further correction.
+
+The afterglow correction, or the scale factor, is determined by calculating the ratio of the corrected to uncorrected PCC.
+This factor is then implemented into individual event histograms within the zero bias data.
+
+Apart from afterglow corrections, pedestal correction is another critical component.
+It signifies the adjustment of baseline values in the detector readout to account for any systematic biases or drifts.
+The pedestal correction involves monitoring the detector's output in the absence of a signal, and then subtracting this baseline value from the signal collected during data capture.
+The application of pedestal correction significantly enhances the accuracy and stability of the detector's readings, thereby leading to precision measurement of PCC luminosity.
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/veto_change_same_af.png}
+\caption{%
+    ratio of scale factor for new and old veto.
+}
+\label{fig:af_change_veto}
+\end{figure}
+
+%Type 1 and Type 2 afterglow corrections are essential for obtaining accurate PCC measurements.
 Type 1 afterglow noise, also known as electronic spillover, is caused by the long waveform of the signal in silicon.
@@
 
-\item Pedestal afterglow correction: The pedestal afterglow refers to the baseline noise level in the detector, which can be influenced by factors such as temperature fluctuations, electronic noise, and radiation damage.
+\item Pedestal correction: The pedestal correction refers to the baseline noise level in the detector, which can be influenced by factors such as temperature fluctuations, electronic noise, and radiation damage.
 This noise can cause an over- or underestimation of the actual number of pixel clusters.
@@
 \centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/afterglow_type1_type2.png}
-\caption{%
+\includegraphics[width=1\textwidth]{ashish_thesis/af_t1_t2.png}
+\caption[Type 1 and type 2 afterglow effect for single colliding bunch]{%
 Afterglow corrections are calculated from cluster rate measurements in empty bunches.
@@
 
-\section{vdM Calibration Results}
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/fill_7036_pattern.png}
+\caption[]{%                                                                                                                                                                                         
+  Afterglow fit model.
+}
+\label{fig:af_fit}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/af_model_fit.png}
+\caption[]{%
+  Afterglow fit model.
+}
+\label{fig:af_fit}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/bunch_train.png}
+\caption[]{%
+
+  Afterglow fit model.
+}
+\label{fig:af_fit}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2wagon_af.png}
+\caption[]{%
+
+  Afterglow fit model.
+}
+\label{fig:af_fit}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2wagon_fit.png}
+\caption[]{%
+
+  Afterglow fit model.
+}
+\label{fig:af_fit}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/3wagon_af.png}
+\caption[]{%
+
+  Afterglow fit model.
+}
+\label{fig:af_fit}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/3wagon_fit.png}
+\caption[]{%                                                                          
+  Afterglow fit model.
+}
+\label{fig:af_fit}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/type2_af_parameters.png}
+\caption[]{%                                                                                
+  Afterglow fit model.
+}
+\label{fig:af_fit}
+\end{figure}
+
+\section{vdM calibration results}
 
@@
 
-\section{Systematic Uncertainties}
-
-\subsection{Uncertainties associated with the Van der Meer calibration}
+\section{Systematic uncertainties}
+
+\subsection{van der Meer calibration uncertainties}
 
@@
 
-\item Scan to Scan Variation: Refers to the variation in experimental results obtained from different scans or measurements, which can arise from various sources such as statistical fluctuations, instrument drift, or systematic errors.
+\item Scan to Scan Variation: Refers to the variation in experimental results obtained from different scans or measurements, which can arise from various sources such as statistical fluctuations, instrument drift, or systematic errors as shown in Fig.
+\ref{fig:sigmaperscan}.
 
@@
 
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/sigma_vis_btob_var.png}
+\caption[]{%                                                                                                                                                                            
+ Bunch to bunch variation of PCC visible cross section.  
+}
+\label{fig:sigmavis_btob_variation}
+\end{figure}
+
+\begin{tabular}{cccccc}
+\textbf{Scan} & \textbf{Mean} & \textbf{SEM} & \textbf{Standard Deviation} & \textbf{(Standard Deviation/Mean) $\times$ 100} \\
+\hline
+vdm1 & 953621.33 & 2148.68 & 1334.83 & 0.14\% \\
+Img1 & 959386.63 & 2050.61 & 559.37 & 0.058\% \\
+Img3 & 964376.43 & 2213.15 & 2502.04 & 0.26\% \\
+Img4 & 960386.85 & 2163.92 & 2936.50 & 0.31\% \\
+vdm2 & 960566.04 & 2425.60 & 4320.81 & 0.45\% \\
+vdm3 & 964566.94 & 2456.97 & 3928.54 & 0.41\% \\
+vdm4 & 962586.52 & 2419.86 & 3943.24 & 0.41\% \\
+\end{tabular}
+
 \item Cross-Detector Consistency: Refers to the agreement between measurements obtained from different detectors or measurement systems.
@@
 
-  \end{itemize}
-
-\subsection{Uncertainties associated with physics data taking}
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/SS_background.png}
+\caption[]{%
+}
+\label{fig:sigmavis_btob_variation}
+\end{figure}
+
+\begin{table}[ht]
+  \begin{subtable}{0.5\linewidth}
+    \centering
+    \begin{tabular}{cc}
+      \textbf{BCID} & \textbf{Mean} \\
+      \hline
+      265 & 0.02902 \\
+      865 & 0.02572 \\
+      1780 & 0.02862 \\
+      2192 & 0.02729 \\
+      3380 & 0.02882 \\
+    \end{tabular}
+    \caption{SS1_{avg}= 0.027894 \pm 0.01249}
+  \end{subtable}%
+  \begin{subtable}{0.5\linewidth}
+    \centering
+    \begin{tabular}{cc}
+      \textbf{BCID} & \textbf{Mean} \\
+      \hline
+      265 & 0.02743 \\
+      865 & 0.0281 \\
+      1780 & 0.0286 \\
+      2192 & 0.02323 \\
+      3380 & 0.02896 \\
+    \end{tabular}
+    \caption{SS2_{avg}= 0.027264 \pm 0.00049}
+  \end{subtable}
+  \caption{SS bkg= 0.02757 +- 0.01987}
+\end{table}
+
+%c_rate = r_rate - b_rate
+%d(c_rate)square = d(r_rate)square + d(b_rate)square
+%d(c_rate)/c = sqrt[d(r_rate)square + d(b_rate)square] /c
+%d(c_rate)/c= d(b_rate)/c
+%= 0.00049/4.6 = 0.000106 (0.01%)
+%(delta sigma/sigma)square = (delta R/R) square
+
+%\begin{equation}
+%c_{rate} = r_{rate} - b_{rate}
+%(dc_{rate})^2 = (dr_{rate})^2 + (db_{rate})^2
+%\end{equation}
+
+%\begin{equation}
+%dc_{rate} = \sqrt{(dr_{\text{rate}})^2 + (db_{\text{rate}})^2}
+%\end{equation}
+
+%\begin{equation}
+%$\frac{dc_{rate}}{c_{peak}}$ =$\frac{\sqrt{(dr_{\text{rate}})^2 + (db_{\text{rate}})^2}}{c_{peak}}$
+%\end{equation}
+
+%\begin{equation}
+%$\frac{d(c_{\text{rate}})}{c_{peak}}$ = $\frac{d(b_{\text{rate}})}{c_{peak}}$
+%\frac{0.00049}{4.6} = 0.000106 \text{ (0.01\%)}
+%(\frac{\delta \sigma}{\sigma})^2 = (\frac{\delta R}{R})^2
+%\end{equation}
+
+\end{itemize}
+
+\begin{equation}
+c_{rate} = r_{rate} - b_{rate}
+\end{equation}
+
+\begin{equation}
+(dc_{rate})^2 = (dr_{rate})^2 + (db_{rate})^2
+\end{equation}
+
+\begin{equation}
+dc_{rate} = \sqrt{(dr_{\text{rate}})^2 + (db_{\text{rate}})^2}
+\end{equation}
+
+\begin{equation}
+
+$\frac{dc_{rate}}{c_{peak}}$ =$\frac{\sqrt{(dr_{\text{rate}})^2 + (db_{\text{rate}})^2}}{c_{peak}}$
+\end{equation}
+
+\begin{equation}
+
+$\frac{dc_{rate}}{c_{peak}}$ = $\frac{d(b_{rate})}{c_{peak}}$
+
+%\frac{0.00049}{4.6} = 0.000106 \text{ (0.01\%)}
+%(\frac{\delta \sigma}{\sigma})^2 = (\frac{\delta R}{R})^2
+\end{equation}
+
+\subsection{Physics data taking uncertainties}
 
@@
 
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/stability_sys.png}
+\caption[]{%
+  Stability systematic uncertainty.
+}
+\label{fig:af_fit}
+\end{figure}
+
 \item Linearity: the luminosity obtained from the PCC method is compared to that obtained from the HFOC method for a given set of collisions.
@@
 
-\item Type 1 afterglow refers to the persistence of charge in the pixels of the detector after a collision event.
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/linearity_sys.png}
+\caption[]{%                                                                                                                                                                                                                \
+
+  Linearity systematic uncertainty.
+}
+\label{fig:af_fit}
+\end{figure}
+
+FCN=11192 FROM MIGRAD    STATUS=CONVERGED      40 CALLS          41 TOTAL
+                     EDM=3.66412e-15    STRATEGY= 1      ERROR MATRIX ACCURATE 
+  EXT PARAMETER                                   STEP         FIRST   
+  NO.   NAME      VALUE            ERROR          SIZE      DERIVATIVE 
+   1  p0           2.34306e-07   2.04110e-09   3.00000e-06  -1.82768e+02
+   2  p1           9.92659e-01   2.73960e-05   3.00000e-06  -1.37960e-02
+
+ \item Afterglow:
+
+  %Type 1 afterglow refers to the persistence of charge in the pixels of the detector after a collision event.
 This charge can be produced by various sources, such as ionization due to the passage of charged particles, or leakage currents in the readout electronics.
@@
 
-  Type 2 afterglow refers to the persistence of noise in the detector after a collision event.
+  %Type 2 afterglow refers to the persistence of noise in the detector after a collision event.
 This noise can be produced by various sources, such as thermal or radiation-induced effects, and can also interfere with subsequent collisions.
@@
 
-\end{itemize}
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/type1_res.png}
+\caption[]{%
+   Type 1 residual.
+}
+\label{fig:type1}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/type2_res.png}
+\caption[]{%
+
+  Type 2 residuals.
+}
+\label{fig:type2}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/type1res_frac.png}
+\caption[]{%
+   Type 1 residual fraction.
+}
+\label{fig:type2}
+\end{figure}
+
+\end{itemize}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/h_ProfileX_PCC_HFOCvsHFOC_all.png}
+%\caption[]{%
+
+ %  Type 1 residual fraction.
+
+%}
+%\label{fig:type2}
+%\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/PCC_HFOCvsHFOC_ProfileX_all.png}
+\caption[]{%                                                                                                                                                          
+   Type 1 residual fraction.
+
+}
+\label{fig:type2}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/PCC_HFOCvsHFOC_ProfileX_residuals_all.png}
+\caption[]{%                                                                                                                                                         
+   Type 1 residual fraction.
+
+}
+\label{fig:type2}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/PCC_HFOCvsls_all.png}
+\caption[]{%                                                                                                                                                         
+   Type 1 residual fraction.
+
+}
+\label{fig:type2}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/PCC_HFOCvsls_ProfileX_all.png}
+\caption[]{%                                                                                                                                                         
+   Type 1 residual fraction.
+
+}
+\label{fig:type2}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/PCCvsHFOC_all.png}
+\caption[]{%
+
+   Type 1 residual fraction.
+
+}
+\label{fig:type2}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/PCCvsHFOC_ProfileX_all.png}
+\caption[]{%
+
+   Type 1 residual fraction.
+
+}
+\label{fig:type2}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/PCCvsHFOC_ProfileX_residuals_all.png}
+\caption[]{%                                                                                                                                                         
+   Type 1 residual fraction.
+
+}
+\label{fig:type2}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/PCCvsHFOC_ProjectionY_all.png}
+\caption[]{%
+
+   Type 1 residual fraction.
+
+}
+\label{fig:type2}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/ProjY_ProfileX_h_ratio_all.png}
+\caption[]{%
+
+   Type 1 residual fraction.
+
+}
+\label{fig:type2}
+\end{figure}

### 2023-07-10 tesis_Ashish/Chapter5/chapter5.tex
AS thesis update
update

@@
-\chapter{Systematic uncertainty in PCC luminosity measurement}  %Title of the First Chapter
+\chapter{Run 3 Luminosity Measurement}  %Title of the First Chapter
 
@@
 %\label{sec:sysunc}
+
+%Please ask Luis for latest 2022 calibration plots
+
+%module veto plots are in slides from Antonio in December PCC meeting
+
+%Afterglow residuals are in my slides in PCC meeting  January , February
+
+%Chapter 5: Run 3 Luminosity Measurement
+
+%Detector Module selection
+%Afterglow Model- Detector Module selection
+%vdM Calibration Results
+%Luminosity for Physics Fills
+%Systematic Uncertainties
+
+\section{Detector Module selection}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_dataset.png}
+\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                              
+   2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
+}
+\label{fig:period_bound}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_periodC_first_iteration}
+\caption[2018 CMS luminosity data taking periods.]{%
+  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
+}
+\label{fig:period_bound}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_periodC_final_iteration.png}
+\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                              
+  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
+}
+\label{fig:period_bound}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_per_period_veto.png}
+\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                         
+  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
+}
+\label{fig:period_bound}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_common_veto.png}
+\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                             
+  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
+}
+\label{fig:period_bound}
+\end{figure}
+
+\section{Afterglow Model}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_type1res.png}
+\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                             
+  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
+}
+\label{fig:period_bound}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_type2res.png}
+\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                             
+  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
+}
+\label{fig:period_bound}
+\end{figure}
+
+\section{vdM Calibration Results}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_vdM.png}
+\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                             
+  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
+}
+\label{fig:period_bound}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_vdM_fit.png}
+\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                              
+  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
+}
+\label{fig:period_bound}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_vdM_fit_quality-png.png}
+\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                             
+  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
+}
+\label{fig:period_bound}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_capsigma.png}
+\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                             
+  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
+}
+\label{fig:period_bound}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_peak.png}
+\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                             
+  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
+}
+\label{fig:period_bound}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_sigma_vis_btob_variation.png}
+\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                             
+  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
+}
+\label{fig:period_bound}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_sigma_vis_per_scan.png}
+\caption[2018 CMS luminosity data taking periods.]{%                                                                                              
+  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
+}
+\label{fig:period_bound}
+\end{figure}
+
+Sigma Vis =  4.1694 +- 0.002 (stat) Barns
+0.06\% statistical error
+
+\section{Luminosity for Physics Fills}
+
+\section{Systematic uncertainties}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_SS_scan.png}
+\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                              
+  2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
+}
+\label{fig:period_bound}
+\end{figure}
+
+\begin{table}[h]
+    \centering
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \caption{SS1   SS1_avg= 0.76804 +- 0.002478}
+        \begin{tabular}{ccc}
+        \textbf{BCID} & \textbf{Mean} & \textbf{SEM} \\ 
+        \hline
+        282 & .7734 & .00570 \\ 
+        822 & .7756 & .00578 \\ 
+        2944 & .7703 & .00599 \\ 
+        3123 & .7478 & .00505 \\ 
+        3302 & .7731 & .00521 \\ 
+        \end{tabular}
+    \end{minipage}
+    \hfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \caption{SS2.  SS2_avg= 0.72026 -+0.002888}
+        \begin{tabular}{ccc}
+        \textbf{BCID} & \textbf{Mean} & \textbf{SEM} \\ 
+        \hline
+        282 & .7207 & .00521 \\ 
+        822 & .7247 & .00898 \\ 
+        2944 & .7306 & .00616 \\ 
+        3123 & .7038 & .00563 \\ 
+        3302 & .7215 & .00560 \\ 
+        \end{tabular}
+    \end{minipage}
+\end{table}
+
+SS bkg= 0.74415 +- 0.002683
+
+\begin{comment}
 
@@
 \section{Comparison of PCC with HFOC luminosity}
+
+\end{comment}

### 2023-07-10 tesis_Ashish/Chapter6/chapter6.tex
AS thesis update
update

@@
 \centering
+\includegraphics[width=0.8\textwidth]{ashish_thesis/pixel_layer_disk_noveto_noselection.png}
+\caption{%
+   Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
+}
+\label{fig:PCC_stab_begin}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
 \includegraphics[width=0.8\textwidth]{ashish_thesis/pcc_stability_begin.png}
@@
 \label{fig:PCC_stab_begin}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.8\textwidth]{ashish_thesis/pcc_frac_L0_veto.png}
+\caption{%
+   Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
+}
+\label{fig:PCC_stab_L0_veto}
 \end{figure}
@@
 }
-\label{fig:stability_D4}
+\label{fig:stability_D5}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/veto_change_same_af.png}
+\caption{%
+    ratio of scale factor for new and old veto.
+}
+\label{fig:af_change_veto}
 \end{figure}
@@
 
-\begin{comment}
-
 \begin{figure}[!htp]
 \centering
-\includegraphics[width=|\textwidth]{ashish_thesis/new_framework_vdm.png}
+\includegraphics[width=1\textwidth]{ashish_thesis/new_framework_vdm.png}
 \caption{%
@@
 \end{figure}
+
+%\begin{comment}
 
@@
     \textbf{Module veto list} & \textbf{PCC visible cross section values (mb)} & \textbf{Uncertainty} \\ \hline
-    Old veto (LUM PAS 2018) & 5982 & 37 (0.08%) stat+syst \\
-    New per period veto (Period B) & 9229.4  & 7.7 (0.08%) stat \\
-    4\% rms common veto & 1673.49  & 0.93 (0.05%) stat \\
-    2\% rms common veto & 959.94  & 0.92 (0.09%) stst \\
+    Old veto (LUM PAS 2018) & 5982 & 37 (0.08\%) stat+syst \\
+    New per period veto (Period B) & 9229.4  & 7.7 (0.08\%) stat \\
+    4\% rms common veto & 1673.49  & 0.93 (0.05\%) stat \\
+    2\% rms common veto & 959.94  & 0.92 (0.09\%) stst \\
 \end{tabular}
@@
 \caption{%
-kjbhgjklh
+stability uncertainty all vetoes
 }
@@
 \caption{%
-kjbhgjklh
+linearity systematic uncertainty
 }
@@
 \caption{%
-kjbhgjklh
+old new veto linearity
 }
-\label{fig:linearitypcchfoc}
+\label{fig:pcc_hf_new_lin}
 \end{figure}
@@
 \caption{%
-kjbhgjklh
+linearity 2 percent veto
 }
-\label{fig:linearitypcchfoc}
+\label{fig:linearity2perveto}
 \end{figure}
@@
 \caption{%
-kjbhgjklh
+all veto linearity sys uncertainty
 }
-\label{fig:linearitypcchfoc}
+\label{fig:linearitysys}
 \end{figure}
@@
 \caption{%
-kjbhgjklh
+4 percent veto
 }
-\label{fig:linearitypcchfoc}
+\label{fig:4perdisklayerstab}
 \end{figure}
@@
 \caption{%
-kjbhgjklh
+pcc layer disk mean rms
 }
-\label{fig:linearitypcchfoc}
+\label{fig:pixellalyerdiskmeanrms}
 \end{figure}
@@
 \caption{%
-kjbhgjklh
+linearity all period
 }
-\label{fig:linearitypcchfoc}
+\label{fig:linearityperperiod}
 \end{figure}
@@
 \caption{%
-kjbhgjklh
+residuals af
 }
-\label{fig:linearitypcchfoc}
+\label{fig:afres}
 \end{figure}
 
-\end{comment}
+%\end{comment}

### 2023-07-11 tesis_Ashish/Chapter4/chapter4.tex
thesis version 11 Jul

@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.8\textwidth]{ashish_thesis/pcc_stability_begin.png}
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=0.8\textwidth]{ashish_thesis/pcc_stability_begin.png}
+%\caption{%                                                                                                                                                                                          
+ %  Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
+%}
+%\label{fig:PCC_stab_begin}
+%\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=0.8\textwidth]{ashish_thesis/pixel_layer_disk_noveto_noselection.png}
+%\caption{%
+ %  Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
+%}
+%\label{fig:PCC_stab_begin}
+%\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.8\textwidth]{ashish_thesis/pixel_layer_disk_noveto.png}
 \caption{%                                                                                                                                                                
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.8\textwidth]{ashish_thesis/pixel_layer_disk_noveto_noselection.png}
-\caption{%
-   Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
-}
-\label{fig:PCC_stab_begin}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.8\textwidth]{ashish_thesis/pcc_frac_L0_veto.png}
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=0.8\textwidth]{ashish_thesis/pcc_frac_L0_veto.png}
+%\caption{%                                                                                                                                                                           
+ %  Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
+%}
+%\label{fig:PCC_stab_L0_veto}
+%\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.8\textwidth]{ashish_thesis/pixel_layer_disk_B0_veto.png}
 \caption{%                                                                                                                                                                           
@@
 \centering
-\topcaption{%
-    PCC/ HFOC luminosity mean and rms values for new per period vetolist showing variation in mean values across period.
-}
+%\topcaption{%
+ %PCC/ HFOC luminosity mean and rms values for new per period vetolist showing variation in mean values across period.
+%}
 \begin{tabular}{ccccc}
@@
 \end{tabular}
+\caption{%                                                                                                                                                                                              
+ PCC/ HFOC luminosity mean and rms values for new per period vetolist showing variation in mean values across period.
+}
 \label{tab:pccvis_diffveto}
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.8\textwidth]{ashish_thesis/old_new_veto.png}
-\caption{%
-   klm
-}
-\label{fig:old_new_vetolist}
-\end{figure}
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=0.8\textwidth]{ashish_thesis/old_new_veto.png}
+%\caption{%
+ %  klm
+%}
+%\label{fig:old_new_vetolist}
+%\end{figure}
+
+\begin{table}[htbp]
+\centering
+\label{tab:run-period}
+\begin{tabular}{cccc}
+\textbf{Run period (Old Veto)} & \textbf{Good modules} & \textbf{Run period (New Veto)} & \textbf{Good modules} \\
+\hline
+A & 787 & A & 580 \\
+B & 787 & B & 1054 \\
+C & 787 & C & 780 \\
+D early & 787 & D1 & 687 \\
+ & & D2 & 672 \\
+ & 775 & D3 (323363-323699)  & \\
+D late & 469 & D3 (323700-324420) & 775 \\
+ & 824 & D4 & \\
+\end{tabular}
+\caption{Run Period and Good Modules}
+\end{table}
 
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/pcc_layer_disk_mean_rms.png}
-\caption{%
-pcc layer disk mean rms
-}
-\label{fig:pixellalyerdiskmeanrms}
-\end{figure}
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/pcc_layer_disk_mean_rms.png}
+%\caption{%
+%pcc layer disk mean rms
+%}
+%\label{fig:pixellalyerdiskmeanrms}
+%\end{figure}
+
+\begin{table}[htbp]
+\centering
+%\caption{Layer/Disk Statistics}
+\label{tab:layer-disk}
+\begin{tabular}{cccccc}
+\textbf{Layer/Disk} & \textbf{Good modules} & \textbf{mean} & \textbf{rms} & \textbf{rms/mean} \\
+\hline
+Layer 2 & 0 & 0 & 0 & 0 \\
+Layer 3 & 48 & 0.374681 & 0.000663165 & 0.00176995 \\
+Layer 4 & 79 & 0.356424 & 0.000724235 & 0.00203195 \\
+Disk 1 & 10 & 0.102687 & 0.000535149 & 0.00521144 \\
+Disk 2 & 12 & 0.112508 & 0.000460595 & 0.00409389 \\
+Disk 3 & 6 & 0.0537002 & 0.000282446 & 0.00525967 \\
+Total  & 155 & & \\
+%\multicolumn{2}{c}{} & \multicolumn{2}{r}{155} \\
+\end{tabular}
+\caption{Layer/Disk Statistics}
+\end{table}
 
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/type2_af_parameters.png}
-\caption[]{%                                                                                
-  Afterglow fit model.
-}
-\label{fig:af_fit}
-\end{figure}
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/type2_af_parameters.png}
+%\caption[]{%                                                                                
+ % Afterglow fit model.
+%}
+%\label{fig:af_fit}
+%\end{figure}
+
+\begin{table}
+  \centering
+  \begin{tabular}{ccc}
+    \textbf{\# of wagon} & \textbf{a} & \textbf{b} \\
+     \hline
+   1-wagon train  & 0.001246  & 0.01261 \\
+   2-wagon train  & 0.000813 &  0.01219\\
+   3-wagon train  & 0.0008265 &  0.01231\\
+  \end{tabular}
+  \caption{type 2  af parameters}
+\end{table}
 
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/stability_sys.png}
-\caption[]{%
-  Stability systematic uncertainty.
-}
-\label{fig:af_fit}
-\end{figure}
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/stability_sys.png}
+%\caption[]{%
+ % Stability systematic uncertainty.
+%}
+%\label{fig:af_fit}
+%\end{figure}
 
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/linearity_sys.png}
-\caption[]{%                                                                                                                                                                                                                \
-
-  Linearity systematic uncertainty.
-}
-\label{fig:af_fit}
-\end{figure}
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/linearity_sys.png}
+%\caption[]{%                                                                                                                                                                                               %                 \
+
+ % Linearity systematic uncertainty.
+%}
+%\label{fig:af_fit}
+%\end{figure}
 
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/type1_res.png}
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/type1_res.png}
+%\caption[]{%
+ %  Type 1 residual.
+%}
+%\label{fig:type1}
+%\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/type1res_gr0p5.png}
 \caption[]{%
    Type 1 residual.
+
 }
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/type2_res.png}
-\caption[]{%
-
-  Type 2 residuals.
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/type2_res.png}
+%\caption[]{%
+
+ % Type 2 residuals.
+%}
+%\label{fig:type2}
+%\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/type2res_gr0.5.png}
+%\caption[]{%
+
+ % Type 2 residuals.
+%}
+%\label{fig:type2}
+%\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/type2res_gr0.5_rangefixed.png}
+\caption[]{%
+  Type 2 residuals.  Mean value is 0.00267652.
  }
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/type1res_frac.png}
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/type1res_frac.png}
+%\caption[]{%
+ %  Type 1 residual fraction.
+%}
+%\label{fig:type2}
+%\end{figure}
+
+\end{itemize}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/type1frac_gr0p5.png}
 \caption[]{%
@@
 \end{figure}
+
+\begin{table}[htbp]
+\centering
+\caption{Systematic Uncertainty}
+\label{tab:systematic-uncertainty}
+\begin{tabular}{cccc}
+\textbf{N/I} & \textbf{Systematic names} & \textbf{Uncertainty (PAS) [\%]} & \textbf{Uncertainty (Final veto) [\%]} \\
+\hline
+Normalization & length scale & &  \\
+ & Orbit drift &  &  \\
+ & X-Y nonfactorization & 2 & 0.4 \\
+ & Beam-beam deflection & -- & -- \\
+ & Dynamic beta & -- & -- \\
+ & Beam current calibration & -- & -- \\
+ & Ghost and satellite & -- & -- \\
+ & Scan to scan variation & 0.3 & 0.3 \\
+ & Bunch to bunch variation & 0.3 & 0.1 \\
+ & Cross detector consistency & -- & -- \\
+ & Background subtraction & 0.1 & 0.06 \\
+Integration & Afterglow & 0.5 & 0.3 \\
+ & Cross detector stability & 0.6 & 0.24 \\
+ & Linearity & 1.1 & 0.35 \\
+Total & -- & 2.47 & 0.813 \\
+\end{tabular}
+\end{table}

### 2023-07-16 tesis_Luis/Chapter4/chapter4.tex
updated

@@
 \section{2022 vdM scan program}
-
-In 2022, the main vdM scan program for the CMS experiment was conducted during LHC fills 8379 and 8381 on 10 and 11 November.
+\label{2022 vdM scan program}
+In 2022, the main vdM scan program for the CMS experiment was conducted during LHC fills 8379 and 8381 on November 10 and 11.
 During fill 8381, a total of 144 bunch pairs were collided head-on , with a proton-proton collision energy $\sqrt{s}$ of 13.6 TeV.
@@
 
-The calibration program included four scan pairs, vdM1,vdM2, vdM3 and vdM4, these are considered the standard vdM scans in the program, used specifically to compute $\sigma_{vis}$.
+The calibration program included four vdM scan pairs, vdM1,vdM2, vdM3 and vdM4, these are considered the standard vdM scans in the program, used specifically to compute $\sigma_{vis}$.
 In this type of scan the two beams are separated by $6\sigma_{b} \thickapprox 578\mu m$, where $\sigma_{b}$ represents the transverse bunch size.
@@
 The calibration program also included two beam-imaging scan pairs, BI1 and BI2 .
-These scans were developed for studies on beam shapes, estimating the uncertainty caused by the not strictly valid assumption seen in previous sections that the bunch proton density function is factorizable into independent $x$ and $y$ densitys, this correction is called  ($x$-$y$ nonfactorization).
-BI acans also are used to compute of $\sigma_{vis}$, independent of the standard vdM's scans.
+These scans were developed for studies on beam shapes, estimating the uncertainty caused by the not strictly valid assumption seen in previous sections that the bunch proton density function is factorizable into independent $x$ and $y$ densities, this correction is called  ($x$-$y$ nonfactorization).
+BI scans also are used to compute of $\sigma_{vis}$, independent of the standard vdM's scans.
 During the BI scans, one beam is kept fixed at its nominal head-on position, while the other beam is separated and scanned in 19 steps, each step lasts 46 seconds and covers a range from $-4.5\sigma_{b}$ to $+4.5\sigma_{b} \thickapprox 433 \mu m$.\\
 
-Two length scale LS scans were conducted, one during fill 8381 and another during fill 8379.
+Two length scale (LS) scans were conducted, one during fill 8381 and another during fill 8379.
 The LS scan is a special scan designed to apply a correction to the results of  $\sigma_{vis}$ obtained from the vdM scan program, this correction will be described further in this section.
@@
 
-Finally two super separation periods SS1 and SS2 were performed for the background estimation, here the two beams were sepated at a distance of $6\sigma_{b}$ during 5 minutes, at this distance the overlap of the beams is minimal and the contribution of collision is negligible.
+Finally two super separation periods, SS1 and SS2, were performed for the background estimation, here the two beams were sepated at a distance of $6\sigma_{b}$ during 5 minutes, at this distance the overlap of the beams is minimal and the contribution of collision is negligible.
 %23:31-23:36 11:47-11:52
@@
 
-\section{Data aquisition and processing}
+\section{Data acquisition and processing}
 \label{data}
-In order to achieve a high statistical precision in data for each colliding bunch pairs the system trigger  bandwidth  limitations do not allow the use of all of them, beacause this, CMS implemented a zero-bias triggers only on five Bunch crossing id (BCID): 282, 822, 2944, 3123, and 3302.
-This data is saved randomly with the highest possible rate of 27.23 kHz using the High Level Trigger (HLT) through the CMS data acquisition (DAQ) system.
+In order to achieve a high statistical precision in data for each colliding bunch pairs, the system trigger  bandwidth  limitations do not allow the use of all of bunches, because of this, CMS implemented a zero-bias triggers (defined in section \ref{Luminometers}) only on five Bunch crossing id (BCID): 282, 822, 2944, 3123, and 3302.
+This data is saved randomly with the highest possible rate of 27.2 kHz (5.4 kHz per BCID) using the High Level Trigger (HLT) through the CMS data acquisition (DAQ) system.
 Due to the weight of the events, 16 different streams are required to save the full data.
-Here the datasets are in their RAW format, which contains information per event (bunch crossing) and the amount of charge deposited in each pixel.\\
+Here the datasets are in the CMS RAW format, which contains information per event (bunch crossing) and the amount of charge deposited in each pixel.\\
 During the vdM2 scan pair, the central CMS data taking was not operational, so no data was recorded for PCC, and this scan pair was skipped from the full calibration.\\
@@
 The ALCARECO samples are processed using CMSSW software (written in Python and C++) to extract the clusters per module.
-Due to the large size of the datasets, all the datasets were sent for reprocessing through The Worldwide LHC Computing Grid (WLCG), wish consists of a grid-based computer network infrastructure,designed by CERN to handle the big volume of data produced by LHC experiments.
-In this  process, we obtained the required cluster counts, which was saved in a dataset with a ROOT format.
+Due to the large size of the datasets, all the datasets were sent for reprocessing through The Worldwide LHC Computing Grid (WLCG), which consists of a grid-based computer network infrastructure,designed by CERN to handle the big volume of data produced by LHC experiments.
+In this  process, we obtained the required cluster counts, which were saved in a dataset with a ROOT format (an open-source data analysis framework used by high energy physics) \cite{ROOT}.
 This format uses TTrees and TBranches, that are containers to maintain the information in a hierarchical and organized manner.
@@
 In order to maintain full statistical precision despite the limitations of the vdM framework (vdMFW), which was utilized for the final fit of our data, the rates were stored  each 1.32 s (NB4) time that corresponding to 4 LN, this was done making  an average  between clusters and the number of events that fall within this time span.
-During this process, the module veto list mentioned in the previous section is introduced and the modules detected in these list were removed.
-In this phase, the information is merged into a single file using a hierarchical data format (hd5) that organizes the data into tables, this final format is the required by the vdMFW.
-All the  process is carried out using lxbatch, a cluster of computers located within CERN.\\
+During this process, the module veto list mentioned in the previous section is introduced and the modules detected in this list were removed.
+In this phase, the information is merged into a single file using a hierarchical data format (HD5) \cite{HD5} that organizes the data into tables, this final format is the required by the vdMFW.
+All the  process is carried out using LxBatch, a cluster of computers located within CERN.\\
 
-Finally the hd5 file containing the rates collected during the vdM scans  is analyzed using the vdMFW, which is written in Python and uses the ROOT data analysis package through the PyRoot library.
+Finally the HD5 file containing the rates collected during the vdM scans  is analyzed using the vdMFW, which is written in Python and uses the ROOT data analysis package through the PyRoot \cite{PyROOT} library.
 The vdMFW  extracts the necessary information using its analysis tools.
@@
 
-\item Beam Gas Elastic (BGE).
-The elastic beam gas contribution are all coherent and quasi-elastic, nuclear elastic and coulomb scattering for multi-turn beam-gas interactions around the ring.
-Typically the interaction of the primary beam proton and the takes place at the tertiary TCT collimator jaw \cite{bkg_source}.
+\item Beam Halo (BH): This component occurs when the secondary particles reach the experimental cavern from the LHC tunnel.
+The primary beam halo is  the population of beam protons characterized by offsets in the transverse coordinates, travelling in  radial amplitude around the beam axis and being captured mostly by the LHC collimation system.
+In every step of the multi-stage cleaning system of the LHC, more halo particles are captured but also secondary showers are created by the interaction of the beam particles with the collimator material.
+The largest contribution of the  beam halo to the background consist of secondary particles  that stem from the interactions of the beam halo particles at the tertiary collimators and arrive in large radius into the CMS cavern \cite{beam_halo}.
 
-\item Beam Gas Inelastic (BGI).
-These are all inelastic interactions of primary beam protons with rest gas in the beam pipe.
-The interaction rate is dominated by the vacuum quality in the various beam line elements upstream CMS.
-Therefore the origin of this contribution is distributed all along the long straight section \cite{bkg_source}.
+\item  Beam Gas Inelastic (BGI): This component arises from all inelastic interactions between primary beam protons and residual gas in the beam pipe.
+The interaction rate is largely influenced by the quality of the vacuum in the various beam line elements upstream of CMS, so the source of this contribution is distributed throughout the long straight section \cite{bkg_source}.
 
-\item Beam Halo (BH).
-This component of the machine induced background is caused by the inefficiency of the main collimation system.
-Protons can escape from one collimator and being intercepted by another collimator \cite{bkg_source}.
+\item Beam Gas Elastic (BGE): The elastic beam gas contribution is made up of all the coherent and quasi-elastic, nuclear elastic, and Coulomb scattering for multi-turn beam-gas interactions around the ring.
+\cite{bkg_source}.
+
 \end{itemize}
 
-In order to illustrate the two SS periods for this analisys, Figure \ref{ssp_wide_bx282} displays the PCC per NB4 versus time for BCID 282.
+In order to illustrate a SS period for this analisys, the Fig.
+\ref{ssp_wide_bx282}, correspnding to the BCID 282, displays the $<\text{PCC}>$  that is the average of pixel clusters per event in a time of 1.32s (NB4).
 The lower regions of the plot correspond to a time window of 5 minutes during which the beams were separated by a distance of $6\sigma_{b}$.\\
@@
 \centering
-\includegraphics[width=.49\textwidth]{Chapter4/BX_282_Rates_SS1.png}
-\includegraphics[width=.49\textwidth]{Chapter4/BX_282_Rates_SS2.png}
-\caption[Super Separation periods for BCID 282]{PCC per NB4 versus time for BCID 282. The lower regions corresponds to the super separation period I (left) and II (right).}
+\includegraphics[width=.80\textwidth]{Chapter4/BX_282_Rates_SS1.png}
+\caption[Super Separation period I for BCID 282]{Background  level for BCID 282, where $<\text{PCC}>$ is the average of pixel clusters per event in a time of 1.32s (NB4)  .
+The lower region correspond to the super separation period I.}
 \label{ssp_wide_bx282}
@@
 
-To estimate the background value in each BCID, the mean value of the PCC per NB4 rates distribution is computed.
-The mean and error per super separation (SS) period are obtained by plotting the PCC per NB4 as a function of time and then taking the $y$ projection.
-The error is calculated using the formula $AvgErr = \sqrt{SEM_1^2 + SEM_2^2 + \cdots + SEM_N}/N$.
-To illustrate this process for each BCID, the distribution or profile of PCC per NB4 for each SS period is plotted.
-Figure \ref{ss1_hist_282} displays the PCC per NB4 distribution for SS period I, specifically for BCID 282, but the same plot is created for every BCID.\\
+To estimate the background value and its conrresponding statistical error (SEM) for each super separation period, the mean value and the standard deviation are taken from the distribution resulting  by making a Y-projection from the rates of $<\text{PCC}>$ shown in the Fig \ref{ssp_wide_bx282}.
+To illustrate this process Fig. \ref{ss1_hist_282} displays a distribution for these values for the SS period I, specifically for BCID 282. The same plot and analysis were done  for each BCID.\\
 
@@
     \centering
-    \includegraphics[scale=.30]{Chapter4/ss1_histo_bx282.png}
-    \caption[PCC per NB4 profile for BCID 282 from SS period I]{ PCC per NB4 profile for BCID 282 from SS period I.} 
+    \includegraphics[scale=.27]{Chapter4/ss1_histo_bx282.png}
+    \caption[$<\text{PCC}>$ profile for BCID 282 from SS period I]{profile of the $<\text{PCC}>$  for BCID 282 from SS period I.} 
     \label{ss1_hist_282}
@@
      \hline %\midrule[1.1pt]
-      282 & 0.7712 & 0.0054\\
+      282 & 0.7734 & 0.0057\\
       \hline
-      822 & 0.7744 & 0.0055\\ 
+      822 & 0.7756 & 0.0055\\ 
       \hline
-      2944 & 0.7695 & 0.0057\\ 
+      2944 & 0.7708 & 0.0060\\ 
       \hline
-      3123 & 0.7469 & 0.0049\\ 
+      3123 & 0.7478 & 0.0050\\ 
       \hline
-      3302 & 0.7708 & 0.0049\\ 
+      3302 & 0.7731 & 0.0052\\ 
       \hline
       \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}\\
-      \multicolumn{1}{c}{$\text{SSI}_{\text{Avg}}=$} & \multicolumn{1}{l}{$0.7665 \pm 0.0023$} & \multicolumn{1}{c}{}\\
+      \multicolumn{1}{c}{$\text{SSI}_{\text{Avg}}=$} & \multicolumn{1}{l}{$0.7680 \pm 0.0025$} & \multicolumn{1}{c}{}\\
 %      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}
@@
      \hline %\midrule[1.1pt]
-      282 & 0.7192 & 0.0048\\
+      282 & 0.7207 & 0.0052\\
       \hline
-      822 & 0.7257 & 0.0057\\ 
+      822 & 0.7247 & 0.0090\\ 
       \hline
-      2944 & 0.7292 & 0.0058\\ 
+      2944 & 0.7306 & 0.0061\\ 
       \hline
-      3123 & 0.7028 & 0.0052\\ 
+      3123 & 0.7038 & 0.0056\\ 
       \hline
-      3302 & 0.7208 & 0.0053\\ 
+      3302 & 0.7215 & 0.0056\\ 
       \hline
       \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}\\
-      \multicolumn{1}{c}{$\text{SSII}_{\text{Avg}}=$} & \multicolumn{1}{l}{$ 0.7195 \pm 0.0024$} & \multicolumn{1}{c}{}
+      \multicolumn{1}{c}{$\text{SSII}_{\text{Avg}}=$} & \multicolumn{1}{l}{$ 0.7203 \pm 0.0029$} & \multicolumn{1}{c}{}
     \end{tabular}   
@@
 
-Table  \ref{ss_per_bx} shows the results for five different BCIDs, using the reprocessed PCC data for Fill 8381.
-This analysis reveals notable inconsistencies in the background values obtained from the two Super Separation (SS) periods.
-As a result, the quality of the fit was affected, and thus, this data was excluded from subsequent analyses.
-Further details on this matter will be discussed in a later section.
+Table  \ref{ss_per_bx} shows the results for five different BCIDs, using the reprocessed PCC data for Fill 8381, where the error is calculated as $AvgErr=\sqrt{SEM_1^2 + \cdots + SEM_N}/N$.
+This analysis reveals notable inconsistencies in the background values obtained from the two Super Separation (SS) periods and the utilization of an average background value for all scans affected the quality of the fit.\\
+
+This circumstance prompted the implementation of a specific background value for each scan, corresponding to the time at which the scan was taken.
+This was achieved through an interpolation between the two background values from the SS periods.
+Figure \ref{interpolation} shows this procedure and the corresponding values for each scan, where the scan  times is taken from the  mean of the full scan (x and y scans) and the error asigned to these values is the mean of the two SS background errors divided by $\sqrt{2}$ assuming that there are not correlation between them.
+These values will be applied to each respective scan, resulting in a more consistent analysis aligned with the behavior of the background.
+
+  \begin{figure}[!h]
+  \label{interpolation}
+  \begin{minipage}{1cm}
+ % \label{int1}
+    \begin{center}
+    \includegraphics[scale=.3]{Chapter4/interpolation2.png}
+   % \caption[Background interpolation]{ Interpolation of SS background values and time  intersection for the different scans} 
+   % \label{bkg_interpolation}
+    \end{center}
+  \end{minipage}
+  \hfill
+\begin{minipage}{6cm}
+%\label{int2}
+\centering
+    \begin{center}
+%\caption[Systematic Uncertainties]{Total systematic uncertainties for the calibration.}
+%\label{systematics}
+\begin{tabular}{lc}
+                               & \multicolumn{1}{l}{}       \\
+                               & \multicolumn{1}{l}{}       \\
+\textbf{Scan}            & \textbf{Background value}  \\ 
+\toprule
+SS1           & 0.768$\pm$0.002               \\
+vdM1          & 0.766$\pm$0.007              \\
+BI1          & 0.763$\pm$0.007              \\
+BI2          & 0.760$\pm$0.007              \\
+vdM3          & 0.730$\pm$0.007              \\
+vdM           & 0.723$\pm$0.007              \\
+SS2           & 0.720$\pm$0.007      
+\end{tabular}
+   \end{center}
+  \end{minipage}
+   \caption[Background interpolation]{Interpolation between the Background values ​​of the two SS periods, in red the SS values ​​are shown with their respective error, the blue line represents the interpolation and the green marks represent  the background values ​for each scan, here they follow the same order in time that has already been seen (vdM1, BI1, BI2, vdM3 and vdM4).
+On the right side the table is shown with the background values ​​corresponding to each of these scans}
+  \label{interpolation}
+\end{figure}
 
 \section{Beam Corrections}
-
+\label{bbcorrections}
+%https://cms.cern.ch/iCMS/analysisadmin/cadilines?line=LUM-22-001
 There are several systematic effects that affect the measurement of beam overlap width and therefore the extraction of $\sigma_{vis}$ from the vdM scan procedure.
@@
 Corrects the presence of spurious charges, which affect bunch currents.
-Satellite charges refer to additional charges outside the actual colliding bunch, while ghost charges refer to charge not in any nominally filled bunch slot, these results in corrections of up to 0.5\% to $\sigma_{vis}$.
-The overall uncertaintys estimate the bunch current measurement  to be 0.4\%.
+Satellite charges refer to additional charges outside the actual colliding bunch, while ghost charges refer to charge not in any nominally filled bunch slot.
+The charges are measured by Longitudinal Density Monitors (LDMs) \cite{ghost_charge} and are corrected for with the procedure described in Ref.
+\cite{lumi_precise_2015_2016}.%These results in corrections of up to 0.5\% to $\sigma_{vis}$.
+The overall uncertaintys estimate for this  correction is 0.1\%.
 
@@
 This correction accounts for potential movement of the LHC orbit during the vdM scans.
-Time-dependent changes of the transverse beam positions for fixed machine parameters can alter the beam separation, this correction is composed of two independent corrections:
-
-Orbit drift separation "ODS", correction that aims to correct for the orbit drift in the scanning direction and only affects beam separation and  Orbit drift rate "ODR", correction that aims to correct for the orbit drift in the direction orthogonal to the scanning direction and only affects the luminometer rate.
+Time-dependent changes of the transverse beam positions for fixed machine parameters can alter the beam separation, this correction is composed of two independent corrections: Orbit drift separation "ODS", correction that aims to correct for the orbit drift in the scanning direction and only affects beam separation and  Orbit drift rate "ODR", correction that aims to correct for the orbit drift in the direction orthogonal to the scanning direction and only affects the luminometer rate.
 %The derived correction assumes that the beam overlap has a single Gaussian shape. The correction reads the $\sigma_{vis}$ in the orthogonal direction from the previous correction. 
-
-Applying this correction improves the agreement between the $\sigma_{vis}$ values derived with different scan pairs and changes the average $\sigma_{vis}$ by about 0.3\%, considering the full size of the correction is as uncertainty.
+%Applying this correction improves the agreement between the $\sigma_{vis}$ values derived with different scan pairs and changes the average $\sigma_{vis}$ by about 0.3\%, considering the full size of the correction is as uncertainty.
 
@@
 As a result, the non-linear change during separation steps in transverse bunch profiles is observed, and can described by the effective change of the $\beta^{*}$  value.
-
-The corrections are calculated for each proton bunch pair individually, and the combined effect of the two corrections is an increase of $\sigma_{vis}$ by 1.0\%, with an uncertainty of 0.5\%.
+%The corrections are calculated for each proton bunch pair individually, and the combined effect of the two corrections is an increase of $\sigma_{vis}$ by 1.0\%, with an uncertainty of 0.5\%.
 
 \item Length Scale. 
-It applies a linear scaling to the beam separation to convert it from the "CMS scale" to the actual "physics scale".
-This is  calibrated by analyzing pp collision vertices reconstruced by the CMS tracker using data from the five length scale scan pairs performed in fills 8178, 8379, and 8381.This correction reduces $\sigma_{vis}$ by 1.0\% and results in an uncertainty of 0.12\%.
+During beam separation scans, the beam positions are controlled by LHC dipole magnets and the separation is determined based on the magnet currents.
+To accurately calibrate the absolute scale of these "nominal" positions, dedicated length scale calibration scans are conducted.
+These scans involve analyzing the reconstructed pp collision vertices obtained from the CMS tracker using data from five length scale scan pairs performed in fills 8178, 8379, and 8381.
+The method applied here is based on the procedure described in Ref.
+\cite{lumi_precise_2015_2016}
+
+%https://indico.cern.ch/event/1244981/contributions/5230942/attachments/2581191/4452030/POG_pres.pdf
+\item Residual beam positions.
+To investigate additional deviations of the beams, a fit model is created by combining the nominal beam positions, the orbit drift correction, and the beam-beam deflection.
+In order to accommodate the unknown response of the Beam Position Monitors (BPM) to the beam-beam deflection, the beam-beam deflection is scaled using a parameter that is allowed to freely vary \cite{lumi_precise_2015_2016}.
+Moreover, length scale factors are also included as freely floating parameters.
+
+In general, the residual deviations are less than 2 $\mum$.
+The primary source of uncertainty here is from the scale of the beam-beam deflection.
+Varying the scale parameter within the range of values found by the fit results in a change of $\sigma_{vis}$ of up to 1.0\%.
+This value is assigned as an uncertainty.\\
+
+%\item Factorization bias.
+As we mentioned in section \ref{2022 vdM scan program} the vdM method assumes that the bunch proton density function is factorizable into dependent $x$ and $y$ distributions and this can lead to a biased estimate of the beam overlap area.
+For this, the special beam imaging scans are used.
+Wherein the measured vertex\footnote{A vertex is a hit recontruction that allow measure the location and the associated uncertainty, of all proton-proton interaction in each event \cite{vertex}} position distributions for $x$ and $y$ scans are fitted using aDouble Gaussian function \cite{BI_calibration,Measuring_luminosity}.
+
+%\noindent For each fit result, the factorization bias is evaluated by comparing the luminous area ($2\pi\Sigma_{x}\Sigma_{y}$) with a simulation of a vdM scan pair that uses the fitted transverse proton bunch densities.
+This simulation is repeated several times to evaluate the impact of statistical fluctuations on the factorization bias.
+The  fit model results in a predicted factorization bias of about 0.7\% in $\sigma_{vis}$ .
+To account for potential additional contributions from higher order x-y correlations , twice the bias value is assigned as uncertainty.\\
+
+%to estimate the rate at each scan step
+%in the transverse bunch proton densities
+\item Bunch current measurement.
+The number of protons per bunch are estimated from the bunch currents measured with the Fast Bunch Current Transformers \cite{LHC_bunch_populations}.
+A precise measurement of the total beam current is provided by the Direct Current Current Transformers (DCCTs) with a relative precision of 0.2\%, this quantity is assigned directly as systematic uncertainty \cite{DCCT_calibration_studies}.
+\\
 
@@
 
-As we have seen in previous sections, the points generated for each step of the scan need to be fitted using a mathematical function.
+As we have seen in previous sections, the averaged cluster rates generated for each step of the scan need to be fitted using a mathematical function.
 This allows us to extract the parameters we need, such as $\Sigma_{x,y}$ and peak values for all the bunches in the scan, in order to finally compute $\sigma_{\text{vis}}$.
@@
 These functions include Double Gaussian (DG), Single Gaussian (SG), Poly Gaussians (PG), among others.
-All of the above functions exist in versions with an additive constant to the entire function, typically used to fit to the background levels.\\
+All of the above functions exist in versions with an additive constant to the entire function, typically used to fit to the background levels as a separate method to the SS data.\\
 
@@
 
-After testing several mathematical fit models, those requiring background subtraction from SS periods analysis were ultimately discarded due to the unacceptably high chi-square values obtained, this was due to the inconsistencies mentioned the section \ref{bkg}.
-Therefore, it was decided to use functions that include a constant to model the background in the fit.
-The chosen model with the best fit quality and after applying all the corrections mentioned earlier, was a double Gaussian function plus a constant:
+After testing several mathematical fit models, the chosen model with the best fit quality and after applying all the corrections mentioned earlier, was a double Gaussian function:
 %https://gitlab.cern.ch/bril/VdMFramework/-/blob/main/src/plotting/capsigma_over_time.py#L90
@@
 \begin{equation}
-f(x)= C+P \cdot \Biggl[ F \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2(\frac{\Sigma\cdot R}{F \cdot R+1-F} )^{2} } \Biggr) + (1-F) \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 (\frac{\Sigma}{F \cdot R+1-F} )^{2} } \Biggr) \Biggr]
+f(x)= P \cdot \Biggl[ F \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2(\frac{\Sigma\cdot R}{F \cdot R+1-F} )^{2} } \Biggr) + (1-F) \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 (\frac{\Sigma}{F \cdot R+1-F} )^{2} } \Biggr) \Biggr]
 \end{equation}
@@
 \begin{itemize}
-\item $C$ is the constant value.
+%\item $C$ is the constant value.
 \item $P$ the $peak$ rate.
@@
 \item $\bar{x}$ is the mean.
-\item $\Sigma$ is the overllap between the beams.
+\item $\Sigma$ is the overlap between the beams.
 \item $R$ is the ratio between the standard deviations of the  Gaussians (first over the second).
@@
 
-Figure \ref{vdM1_282_XYscan} shows the fit graphs of the first vdM scan pair for BCID 282 where  all the corrections described in the previous section have been applied and where  rates are normalized by the beam currents ($N_{1}N_{2}$), which is according of Eq.
-\ref{sigmavis_eq}.
+Figure \ref{vdM1_282_XYscan} shows the fit graphs of the first vdM scan pair for BCID 282 where  all the corrections described in the previous section have been applied and where  rates are normalized by the beam currents ($N_{1}N_{2}$).
 
@@
     \centering
-    \includegraphics[scale=.030]{Chapter4/DGConst_chi2.png}
+    \includegraphics[scale=.30]{Chapter4/DGConst_chi2.png}
     \caption[$\chi^{2}$/ndof per BCID for all scan pairs]{ chi2/ndof for all the scan pairs.
@@
 
-The values of $\Sigma_{x,y}$ wish provide a direct measurement of the beam shape show a decrease in both the $x$ and $y$ directions during the fill time, this is due to a phenomenon called "damping", which occurs due to the interaction between the particles in the beam and the electromagnetic fields in the LHC ring, these fields exert a force on the particles, causing them to lose energy and amplitude, which causes the beam to gradually focus with time.
-On the other hand the values ​​for the $peak$ are then a direct consequence of this effect, since a more focused beam means more collisions and thus a higher rate.\\
+The values of $\Sigma_{x,y}$ which provide a direct measurement of the beam shape show a decrease in both the $x$ and $y$ directions during the fill time, this is due to a phenomenon called "damping", which occurs due to the interaction between the particles in the beam and the electromagnetic fields in the LHC ring, these fields exert a force on the particles, causing them to lose energy and amplitude, which causes the beam to gradually focus with time.
+On the other hand the values ​​for the $peak$ that are the rates on head-on normalized by the bunch currents ($R(0,0)/N_{1}N_{2}$) are then a direct consequence of the same effect, since a more focused beam means more collisions and thus a higher rate.\\
 
@@
 
-The $\sigma_{vis}$ for all BCIDs (vdM and BI scans) is then computed from the fit results $\Sigma_{x,y}$ and $peak_{x,y}$ shown above, this is done using the Eq.
+The $\sigma_{vis}$ for each BCID (vdM and BI scans) is then computed from the fit results $\Sigma_{x,y}$ and $peak_{x,y}$ shown above, where the final $peak$ value to use  is obtained by taking the average of the peaks in the $x$ and $y$ scans.
+For each bunch crossing the visible cross sections are then measured using Eq.
 \ref{sigmavis_eq}.
-The value of $R(0,0)$ is obtained is obtained by taking the average of the peaks in the $x$ and $y$ scans, which has already been normalized.
-As a result, Equation \ref{sigmavis_eq} is rewritten as:
 
 \begin{equation}
- \sigma_{vis}= 2\pi \Sigma_{x} \Sigma_{y} \Biggl( \frac{peak_{x}+peak_{y}}{2} \Biggr)
+ \sigma_{vis}= \pi \Sigma_{x} \Sigma_{y}(peak_{x}+peak_{y})
  \end{equation}
 
-Figure \ref{sigmavis_perbcid} shows the  value of $\sigma_{vis}$ per BCID for all the scans where the error on $\sigma_{vis}$ is assigned as:
+Figure \ref{sigmavis_perbcid} depicts the  value of $\sigma_{vis}$ per BCID for all the scans, where the error on $\sigma_{vis}$ is assigned as shown in Eq.
+\ref{sigma_err}, where $P=(peak_{x}+peak_{y})/2$
 
@@
 \sigma_{vis\text{Err}}= 2 \pi \sqrt{ (\Sigma_{y} \cdot P \cdot \Sigma_{x\text{Err}})^{2} + (\Sigma_{x} \cdot P \cdot \Sigma_{y \text{Err}})^{2} + (\Sigma_{x} \Sigma_{y} P_{\text{Err}})^{2} }
+\label{sigma_err}
 \end{equation}
@@
     \centering
-    \includegraphics[scale=.22]{Chapter4/DGConst_xsec.png}
+    \includegraphics[scale=.30]{Chapter4/DGConst_xsec.png}
     \caption[$\sigma_{vis}$ per BCID for all scans]{ $\sigma_{vis}$ per BCID for all the scans,  in each scan, the BCIDs follow the same order, which is 282, 822, 2944, 3123, and 3302.}
@@
 
-To obtain the final value of sigma visible , we first perform a weighted average using 5 BCIDs for each scan as shown in Figure \ref{sigmavis_perscan} with blue dots.
+To obtain the final value of $\sigma_{vis}$, we first perform a weighted average using 5 BCIDs for each scan as shown in Figure \ref{sigmavis_perscan} with blue dots.
 Subsequently, we perform another weighted average among the results of these 5 scans, this final value is represented by the red line in Figure \ref{sigmavis_perscan}.
-In both calcuation, it is assumed that there is no correlation between the BCIDs and the scans.
+In both calculation, it is assumed that there is no correlation between the BCIDs and the scans.
 Therefore, the computation of the weighted average and the total error  follows Equations \ref{average} and \ref{error} respectively, where the weight is assigned as $w_{i} = 1/\sigma_{visErr}^{2}$.
@@
     \centering
-    \includegraphics[scale=0.45]{Chapter4/xsec_perscan_v2.png}
+    \includegraphics[scale=0.40]{Chapter4/xsec_perscan_v2.png}
     \caption[$\sigma_{vis}$ average per scan and final result]{ $\sigma_{vis}$  per scan.} 
@@
 
-As depicted in Figure \ref{sigmavis_perscan}, the scans demonstrate an RMS of $12.8 \text{ mb}$ for the $\sigma_{vis}$ values, which is larger than the statistical uncertainty.
+%As depicted in Figure \ref{sigmavis_perscan}, the scans demonstrate an RMS of $12.8 \text{ mb}$ for the $\sigma_{vis}$ values, which is larger than the statistical uncertainty.
 Notably, vdM1 and vdM3 exhibit the largest variations, deviating by approximately 2 standard deviations from the mean.
@@
 In this work, we assign the RMS value as an estimate of the systematic uncertainty.
+
+\section{Systematic Uncertainties}
+%https://cms.cern.ch/iCMS/analysisadmin/cadilines?line=LUM-22-001
+As depicted in Fig.
+\ref{sigmavis_perscan} and Fig.
+\ref{sigmavis_perbcid}, some variations in the visible cross sections from scan-to-scan and bunch-to-bunch are observed.
+Notably vdM3 scan exhibit the largest variation, deviating by approximately 2 standard deviations from the mean.
+These discrepancies are attributed to systematic effects in the detector during the scans, which, along with the uncertainty generated by the background, contribute to the final systematic error.
+The method for assigning an uncertainty value to these sources is described below.\\
+
+\textbf{Scan-to-scan variation}: To cover the possibility of systematic differences between the scans, the standard deviation of $\sigma_{vis}$ for the five  scans is taken as uncertainty, resulting in a value of  0.26\% ($10.8 \text{ mb}$).\\
+
+\textbf{Bunch-to-bunch variation}: The systematic of each scan is assigned as the standard deviation divided by the mean of its 5 BCIDs.
+Afterwards, this value is divided by the square root of the number of bunches due to the non-correlation between the bunches, as shown in table \ref{bunch-to-bunch}.
+The final uncertainty is assigned as the average of the systematic uncertainties from all the scans.
+This results in a total uncertainty of 0.1\% (3.73 mb).\\
+
+\begin{table}[h!]
+\centering
+\caption[Bunch-to-Bunch Uncertinties]{Systematic uncertainties corresponding to Bunch-to-Bunch variations.}
+\label{bunch-to-bunch}
+\begin{tabular}{lccc}
+\multicolumn{1}{c}{\textbf{Scan}} & \textbf{$\sigma_{\textbf{vis}}$ (mb)} & \begin{tabular}[c]{@{}c@{}}\textbf{Standar}\\\textbf{Deviation~(STD) }\end{tabular} & \begin{tabular}[c]{@{}c@{}}\textbf{Syst.
+error}\\\textbf{$\text{STD/}(\sigma_{\textbf{vis}}*\sqrt{5})$}\end{tabular}  \\
+\toprule
+vdM1                              & 4147.71               & 12.56                                                                       & 0.13                                                                              \\
+BI1                              & 4151.50               & 12.22                                                                       & 0.13                                                                              \\
+BI2                              & 4146.04               & 5.39                                                                       & 0.05                                                                              \\
+vdM3                              & 4174.31               & 9.18                                                                        & 0.10                                                                              \\
+vdM4                              & 4145.64               & 6.96                                                                      & 0.08                                                                              \\
+\hline
+\textbf{Total}                    &                          &                                                                                & \textbf{0.1}
+\end{tabular}
+\end{table}
+%& \begin{tabular}[c]{@{}c@{}}\textbf{$STD/(\sigma_{vis}*\sqrt{5})}\\\textbf{[\%]}\end{tabular}  \\ 
+\textbf{Background}: The value of the background systematic  is assigned as the  difference between the sigma visible value obtained with a DG+Constant Fit model (4163.3 mb) and our current DG fit model with background subtraction (4153.3 mb).
+This revealed a difference in the $\sigma_{vis}$ of 10.0 mb, corresponding to an assigned uncertainty of 0.24\%.\\
+
+Additionally, the beam corrections described in section \ref{bbcorrections} are taken into account, and the corresponding uncertainties have been estimated.
+Table \ref{systematics} displays their assigned values for the systematic error contributions.
+These analyses and results were obtained through independent studies conducted by the CMS team responsible for luminosity calibration.
+
+\begin{table}[h!]
+\centering
+\caption[Systematic Uncertainties]{Total systematic uncertainties for the calibration.}
+\label{systematics}
+\begin{tabular}{lc}
+                               & \multicolumn{1}{l}{}       \\
+                               & \multicolumn{1}{l}{}       \\
+            & \textbf{Systematic Uncertainty [\%]}  \\ 
+\toprule
+Length scale                   & 0.12                        \\
+Orbit drift                    & 0.3                        \\
+%Residual beam positions & 1.0                \\
+%Factorization bias & 1.4                        \\
+Beam-beam effects              & 0.5                        \\
+Beam current calibration       & 0.2                        \\
+Ghost and satellite            & 0.1                        \\
+Scan to scan variation         & 0.26                        \\
+Bunch to bunch variation       & 0.1                        \\
+%Cross detector consistency     & -                          \\
+Background subtraction         & 0.24                          \\ 
+\hline
+\textbf{Total}                 & \textbf{0.73}               
+\end{tabular}
+\end{table}
+
+Taking into account the above considerations, the total systematic uncertainty is found to be 0.73\% ($77.8 \text{ mb}$). Therefore, the final value for $\sigma_{vis}$ is determined as:
+
+\begin{equation}
+\sigma_{vis} = 4153.3 \pm 2.7 \text{(stat.)} \pm 30.3 \text{(syst.) mb}
+\end{equation}

### 2023-08-07 tesis_Luis/Chapter4/chapter4.tex
updated

@@
 The evaluation of the goodness of fit is shown in Fig.
-\ref{chi2/ndof} where displays a plot of the $\chi^{2}/ndof$ for all the five scan pairs, which has a mean value of 1.88.
+\ref{chi2/ndof} where displays a plot of the $\chi^{2}/ndof$ for all the five scan pairs, which has a mean value of 1.98.
 
@@
 \begin{equation}
-\sigma_{vis}=4163.3 \pm 3.3 \text{ (stat)  mb}
+\sigma_{vis}=4153.3 \pm 2.7 \text{ (stat)  mb}
 \end{equation}
@@
 \hline
-\textbf{Total}                    &                          &                                                                                & \textbf{0.1}
+\textbf{Average}                    &                          &                                                                                & \textbf{0.1}
 \end{tabular}
@@
 
-\begin{table}[h!]
+Taking into account the above considerations, the total systematic uncertainty is found to be 0.73\% ($30.3 \text{ mb}$).
+\newpage
+\begin{table}[!ht]
 \centering
@@
 
-Taking into account the above considerations, the total systematic uncertainty is found to be 0.73\% ($77.8 \text{ mb}$). Therefore, the final value for $\sigma_{vis}$ is determined as:
+ %Therefore, the final value for $\sigma_{vis}$ is determined as:
 
-\begin{equation}
-\sigma_{vis} = 4153.3 \pm 2.7 \text{(stat.)} \pm 30.3 \text{(syst.) mb}
-\end{equation}
+%\begin{equation}
+%\sigma_{vis} = 4153.3 \pm 2.7 \text{(stat.)} \pm 30.3 \text{(syst.) mb}
+%\end{equation}

### 2023-08-23 project_Luis_PhD/paper.tex
updated

--- 2021-05-02 project_ashish_lumi/paper.tex
@@
 
-\def\Student{Ashish Sehrawat}
+\def\Student{Luis Enrique Cuevas  Picos}
 \def\Title{THESIS PROJECT PROPOSAL}
@@
 \def\ProjectTitle{Measurement of the luminosity in proton-proton collisions at the CMS experiment of the Large Hadron Collider}
-\def\ResearchLine{Astrof\'{i}sica, Cosmolog\'{i}a y F\'{i}sica de Part\'{i}culas}
+\def\ResearchLine{F\'{i}sica de Part\'{i}culas}
 
@@
 {\scshape\Large \Title \par}
-project revised 2021-1
+project revised 2023-2
 
@@
 
-  This research project proposes to determine precise value and corresponding uncertainity of luminosity delivered to Compact Muon Solenoid (CMS) experiment at CERN during 2017-2018 period using Pixel Cluster Counting (PCC) method and construction of luminosity measurement device using Tracker Endcap Pixel Detector (TEPX) for High Luminosity (HL)-LHC which will be able to withstand luminosities of up to 3000 $fb^{-1}$.
-Luminosity plays a vital role in determination of cross section for various production and decay processes of elementary particles and its accurate determination will assist in precise calculation of SM quantities like cross section, couplings and exploring physics beyond SM.
+  This research project proposes...
 
@@
 
-This project has two main parts, in the first part we propose to perform an analysis of the LHC luminosity data  recorded by the CMS experiment during 2017 and 2018 using Pixel Cluster Counting (PCC) method.
-In the second part we develop an upgraded luminosity measurement system for the HL-LHC phase (2026-2038).
+This project propose...
 
@@
 
-The main objective of this work is to perform a measurement of the 2017-2018 LHC delivered luminosity with a precision at the level of 2\% or less using the CMS Pixel detector.
-This precision is necesary for testing SM of elementary particles and identifying possible new physics which could elucidate the nature of Dark Matter in our universe.
-
-The second objective is to develop an upgraded luminosity measurement system for the HL-LHC phase using Tracker Endcap Pixel detector (TEPX).
-TEPX is a part of new tracker detector proposed by the CMS collaboration which will replace the current one during LS3 (2024-2026).
+The main objective of this work is to perform...
 
@@
 
-As mentioned in the introduction, precision achieved in the measurement of integrated luminosity during Run 1 was about 2.5\% using  methods developed for the first time.
-In 2015 and 2016 the uncertainty achieved was 1.6\% and 1.2\%, respectively, for datasets corresponding to \lumi{2.5} and \lumi{36}  \cite{Sirunyan:2021qkt}.
-The methods used for the 2015 and 2016 data are similar to the strategy we propose in this project.
-We expect that the final uncertainties for the 2017 and 2018 datasets to be similar, but the ultimate goal of the CMS collaboration is to reduce these uncertainties to below 1\%  \cite{Dainese:2019rgk}.
-
-For the upgrade part of this project, we must consider that in the HL-LHC phase the higher expected pileup (number of proton collisions per bunch crossing) will lead to more difficult scenarios for the luminosity measurement due to increased detector occupancy and larger irradiation of the detector components.
-However, we expect that new methods to be introduced between now and the start of the HL-LHC phase will improve the measurement precision and compensate the higher backgrounds and detector aging.
+As mentioned in the introduction...
 
@@
 
-\item {\bf Semester 1 (2019-2)}:
+\item {\bf Semester 1 (2023-2)}:
   \SubItem{ Readings on Standard Model of particle physics theory}
@@
 
-\item {\bf Semester 2 (2020-1)}:
+\item {\bf Semester 2 (2024-1)}:
   \SubItem{ Course I on particle physics, particle detection, or data analysis}
@@
 
-\item {\bf Semester 3 (2020-2)}:
+\item {\bf Semester 3 (2024-2)}:
   \SubItem{ Course II on particle physics, particle detection, or  data analysis}
@@
 
-\item {\bf Semester 4 (2021-1)}:
+\item {\bf Semester 4 (2025-1)}:
   \SubItem{ Completion of the TEPX luminometer studies for the TDR document}
@@
 
-\item {\bf Semester 5 (2021-2)}:
+\item {\bf Semester 5 (2025-2)}:
   \SubItem{ Publication of the TDR document in CDS and submission to the LHCC for review}
@@
 
-\item {\bf Semester 6 (2022-1)}:
+\item {\bf Semester 6 (2026-1)}:
   \SubItem{ Completion of the studies of the Run 2 data luminosity measurement}
@@
 
-\item {\bf Semester 7 (2022-2)}:
+\item {\bf Semester 7 (2026-2)}:
   \SubItem{ Publication of the Run 2 data luminosity measurement in a peer reviewed journal}
 
-\item {\bf Semester 8 (2023-1)}: 
+\item {\bf Semester 8 (2027-1)}: 
   \SubItem{ Presentations at national or international conferences for both the Run 2 luminosity measurement and TEPX luminometer for HL-LHC}

### 2023-09-13 project_Luis_PhD/paper.tex
project update

@@
 \def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
-\def\ProjectTitle{Measurement of the luminosity in proton-proton collisions at the CMS experiment of the Large Hadron Collider}
+\def\ProjectTitle{Luminosity measurement using Pixel Cluster Counting in the CMS experiment}
 \def\ResearchLine{F\'{i}sica de Part\'{i}culas}
@@
 %%header and footer
-\lhead{\Student\ / \ \Dept}
+\lhead{\Student\ / \Prog}
 \rhead{\Title}
@@
 {\scshape\Large \Title \par}
-project revised 2023-2
+%project revised 2023-2
 
@@
 
-  \vspace{1 cm}
+  \vspace{0.5cm}
 
@@
 $L$ is one of the  main figures of merit that quantify the potential for observing new particles and measuring their properties.
-The instantaneous luminosity $L(t)$ is the process-independent ratio between the rate $R(t)$ of events produced per unit time and the cross section for a given process $\sigma$: $L(t) = R(t)/\sigma$.
+The instantaneous luminosity $L(t)$ is the process-independent ratio between the rate $R(t)$ of events produced per unit time and the cross section for a given process $\sigma$:  $R(t) = \sigma L(t)$.
 During Run 1 (2011-2012) LHC reached a peak instantaneous luminosity of \instlumi{0.77} and delivered an integrated luminosity of about \lumi{25} with a precision of about 2.0\% 
@@
 In the first part of Run 2 (2015-2016), the delivered luminosity has been measured to be \lumi{38.4} with an unprecedented precision of 1.3\% \cite{Sirunyan:2021qkt}.
-For the second part of Run 2 (2017-2018), the integrated luminosity is about \lumi{78}, but its precise value and uncertainty remain to be determined and is one of the main objectives of this thesis project \cite{CMS:2018elu}.
+For the second part of Run 2 (2017-2018), the integrated luminosity is about \lumi{78}, but its precise value and uncertainty remain to be determined \cite{CMS:2018elu}.
+The plan of the LHC till year 2038 is to obtain datasets with up to 10 times higher values of instanteneous luminosities in the final phase.
+The LHC Run 3 began in 2022 and will last until 2024, with an expected integrated luminosity of about \lumi{300}.
 
-The plan of the LHC till year 2038 is to obtain datasets with up to 10 times higher values of instanteneous luminosities in the final phase, the  High Luminosity LHC (HL-LHC), and corresponding integrated luminosities of order \lumi{3000} as shown in Figure~\ref{figure6}.
-These final datasets will provide  precise measurements of the properties of the Higgs boson and other SM particles as shown in Fig. ~\ref{figureKappasUncs}.
+The  High Luminosity LHC (HL-LHC), and corresponding integrated luminosities of order \lumi{3000} as shown in Figure~\ref{figure6}.
+These datasets will provide  precise measurements of the properties of the Higgs boson and other SM particles as shown in Fig. ~\ref{figureKappasUncs}.
 This figure shows that one of the dominant uncertainties which remain to be determined is due to the luminosity measurement.
-In this project, we also perform studies for the design and construction of an upgraded luminosity measurement system to be installed for CMS in the HL-LHC phase}\cite{Collaboration:2706512}.
 
@@
   \centering
-  \includegraphics[width=0.7\columnwidth]{./LHCcomplex.png}
-  \caption{Diagram of the LHC accelerator complex located near Geneva, Switzerland.
+  \includegraphics[width=0.6\columnwidth]{./LHCcomplex.png}
+  \caption{
+    Diagram of the LHC accelerator complex located near Geneva, Switzerland.
 The complex consists of three accelerator stages: the proton (p) or lead (Pb) source, the Proton Synchrotron (PS), the Super Proton Synchrotron (SPS), and the 27 km LHC ring.
@@
   \includegraphics[width=0.8\columnwidth]{./HLLHCLumi.png}
-  \caption{Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities.
-Points show instantaneous luminosity while the line shows luminosity accumulated \cite{collaborations2019report}.}
+  \caption{
+    Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities.
+Points show instantaneous luminosity while the line shows luminosity accumulated \cite{collaborations2019report}.
+  }
   \label{figure6}
@@
 
-This project propose...
+In this project, we aim to make the most precise measurements of the luminosity for the Run 2 (2017-2018) as well as for the Run 3 data taking period (2022-2024).
+In addition we expect to perform studies for the design and construction of an upgraded luminosity measurement system to be installed for CMS in the HL-LHC phase \cite{Collaboration:2706512}.
 
@@
 
-The main objective of this work is to perform...
+The main objective of this work is to improve on the precision of the preliminary luminosity measurements for the different datasets with the aim to provide a final precision at the level of 1\%.
+This precision is needed for the measurement of many important physics processes, like the Higgs boson production crossection, which define the Standard Model of particle physics.
 
@@
 
-As mentioned in the introduction...
-
-\section{SPECIFIC OBJECTIVES}
-
-For the Run 2 luminosity measurement:
-\begin{itemize}
-\item understand the CMS pixel detector layout including the barrel layers and endcap disks and their constituent modules,
-\item study the stability of the modules in the different layers or disks of the pixel detector and select the stable components,
-\item calculate the visible cross section corresponding to the PCC rate for proton-proton colisions at 13 TeV using the selected pixel detector components,
-\item study the stability and linearity of the PCC luminosity measurement by comparing to other CMS luminometers as a measurement of the systematic uncertainties,
-\item determine the delivered luminosity per lumisection (23 second intervals) and the total integrated luminosity and determine the corresponding uncertainty.
-\end{itemize}
-
-\par
-For the development of the HL-LHC upgrade system:
-\begin{itemize}
-\item study the different parts of the TEPX detector.
-\item study the pixel cluster counting at the HL-LHC conditions using simulations of the TEPX detector.
-\item develop an algorithm for counting cluster coincidences using sensor layers of the same disk in the TEPX detector in order to reduce backgrounds.
-\item determine the linearity and statistical precision of the PCC method and coincidence counting method for the TEPX detector and its constituent parts (disks and rings).
-\end{itemize}
+Based on the previous work on the Run 2 (2015-2016) datasets which have achieved a precision at the level of 1.3\%, we expect that a precision at this level or lower will be possible due to the improved methods we are developing.
+For reference, the current precision on the Run 2 (2017-2018) and Run 3 (2022) datasets is above 2\%~\cite{Sirunyan:2021qkt}.
 
@@
 
-The CMS experiment is located at one of the four interaction points of LHC.
+The CMS experiment is located at one of the four interaction points of the LHC.
 The CMS detector has the form of a cylindrical onion, with several concentric layers of components.
@@
 
-The PCC method consists of the reconstruction of track clusters produced by charged particle tracks as shown in Figure~\ref{fig:trackcluster}.
+The PCC method consists of the reconstruction of track clusters produced by charged particle tracks as shown in Figure~\ref{fig:bunchcrossing}.
 Due to the fine granularity of the pixel sensors and the large number of total pixels, the hit occupancy in the sensors remains very small, order of 1\%, during normal collisions.
@@
 The linearity of the cluster counting algorithm will be studied.
-In addition, a new algorithm will be developed to detect cluster coincidences between consecutive layers of a disk.
-It is expected that coincidences will be less sensitive to backgrounds in HL-LHC pileup conditions and therefore a more robust luminosity measurement can be performed.
+In addition, a new algorithm may be developed to detect cluster coincidences between consecutive layers of a disk.
+%It is expected that coincidences will be less sensitive to backgrounds in HL-LHC pileup conditions and therefore a more robust luminosity measurement can be performed.
 
@@
   \centering
-  \includegraphics[width=0.7\columnwidth]{./cms12.png}
+  \includegraphics[width=0.65\columnwidth]{./cms12.png}
   \caption{Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimeter, superconducting solenoid and muon chambers \cite{Chatrchyan:2008aa}.}
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{./bunchcrossing.jpg}
-  \includegraphics[width=0.4\columnwidth]{./vectorhit1.jpg}
+  \includegraphics[width=0.48\columnwidth]{./bunchcrossing.jpg}
+  \includegraphics[width=0.48\columnwidth]{./vectorhit1.jpg}
   \caption{
-    Left: Diagram showing the collision of two proton bunches at LHC, bunches contain about $10^{11}$ protons  \cite{deMaria:2008zzb}.
-    Right: diagram showing example tracks originating from the collision at the beamspot and producing clusters at the pixel sensors in two detector layers.
+    Left: Dagram showing the collision of two proton bunches at LHC, bunches contain about $10^{11}$ protons  \cite{deMaria:2008zzb}.
+    Right: diagram showing example tracks originating from the collision and producing hits in the pixel detector layers.
   }
-  \label{fig:trackcluster}
+  \label{fig:bunchcrossing}
 \end{figure}
@@
 
+\section{SPECIFIC OBJECTIVES}
+
+For the Run 2 and Run 3 luminosity measurements:
+\begin{itemize}
+\item understand the CMS pixel detector layout including the barrel layers and endcap disks and their constituent modules,
+\item study the stability of the modules in the different layers or disks of the pixel detector and select the stable components,
+\item calculate the calibration constant (visible crossection) corresponding to 13 TeV proton-proton collision data,
+\item study the stability and linearity of the PCC luminosity measurement by comparing to other CMS luminometers,
+\item determine the instantaneous and the total integrated luminosity,
+\item determine the systematic uncertainties on the calibration constant and on the integrated luminosity.
+\end{itemize}
+
+\par
+For the development of the HL-LHC upgrade system:
+\begin{itemize}
+\item study the different parts of the TEPX detector,
+\item study the pixel cluster counting at the HL-LHC conditions using simulations of the TEPX detector,
+\item develop algorithms for pixel  cluster counting and coincidence counting,
+\item determine the linearity and  precision of the different methods.
+\end{itemize}
+
 \section{EXPECTED RESULTS}
@@
 \begin{itemize}
-\item
-For the Run 2 luminosity mesurement, the student will perform the studies for the selection of good modules for calculating luminosity using the PCC method.
-From past performance of this algorithm it is expected that this measurement will give one of the best linearity and stability systematic uncertainties for the integrated luminosity value.
+\item For the Run 2 luminosity mesurement, studies of the selection of good detector modules, calibration, background estimation, and calculation of the integrated luminosity, including the systematic uncertainties will be completed.
 The results of these studies will be published in a peer-reviewed scientific journal.
-\item
-For the development of the HL-LHC upgrade system, we expect to produce a Technical Design Report (TDR) with the proposed design and algorithms to use the TEPX detector.
-This document will be published in the CERN document server (CDS) and submitted to the LHC committee for approval of required funding for the construction and operation of the system.
+\item For the Run 3 luminosity measurement, no measurement of the luminosity precision has been performed at this moment.
+Similar studies as for the Run 2 dataset will be performed completed and a preliminary result of the luminosity measurement will be published.
+\item For the development of the HL-LHC upgrade system, the work  will be based on the previously published Technical Design Report (TDR) with the proposed design and algorithms to use the TEPX detector.
+It is expected that this work will be presented at conferences and used for the final design and construction of the system to be installed in the LS3 (2025-2027).  
 \end{itemize}
@@
 \item {\bf Semester 1 (2023-2)}:
-  \SubItem{ Readings on Standard Model of particle physics theory}
-  \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
-  \SubItem{ Initial planning of the analysis strategy}
+  \SubItem{ Readings on Standard Model of physics theory, LHC, and CMS experiments}
+  \SubItem{ Review of the literature.}
+  \SubItem{ Master Linux computing and data analysis  skills (\textsc{Bash, Emacs, Root, HTCondor parallel processing})}
+  \SubItem{ Complete work on the 2022 luminosity measurement for a preliminary  publication.}
 
@@
   \SubItem{ Course I on particle physics, particle detection, or data analysis}
-  \SubItem{ Readings on the LHC and CMS experiments}
-  \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
-  \SubItem{ Computing accounts at CERN and Fermilab}
-  \SubItem{ Studies of the TEPX luminometer upgrade}
+  \SubItem{ Continue readings on Standard Model of physics theory, LHC, and CMS experiments}
+  \SubItem{ Master Linux computing and data analysis  skills (\textsc{Bash, Emacs, Root, HTCondor parallel processing})}
+  \SubItem{ Complete work on the Run 2 luminosity measurement for a final  publication.}
+  \SubItem{ Start work on the 2023 dataset luminosity measurement. }
 
@@
   \SubItem{ Course II on particle physics, particle detection, or  data analysis}
-  \SubItem{ Studies of the TEPX luminometer upgrade}
+  \SubItem{ Complete work on the 2023 dataset luminosity measurement. }
+  \SubItem{ Start work on the 2024 dataset luminosity measurement. }
 
 \item {\bf Semester 4 (2025-1)}:
-  \SubItem{ Completion of the TEPX luminometer studies for the TDR document}
-  \SubItem{ Studies of the LHC Run 2 data using the PCC method}
+  \SubItem{ Continue work on the 2024 dataset luminosity measurement. }
+  \SubItem{ Start studies on the TEPX luminometer for the HL-LHC}
   \SubItem{ Writing of the monograph}
@@
 \item {\bf Semester 5 (2025-2)}:
-  \SubItem{ Publication of the TDR document in CDS and submission to the LHCC for review}
+  \SubItem{ Complete work on the 2024 dataset luminosity measurement. }
+  \SubItem{ Complete studies on the TEPX luminometer for the HL-LHC}
   \SubItem{ Presentation at national or international conferences of the TEPX upgrade studies}
-  \SubItem{ Studies of the LHC Run 2 data using the PCC method}
 
 \item {\bf Semester 6 (2026-1)}:
-  \SubItem{ Completion of the studies of the Run 2 data luminosity measurement}
-  \SubItem{ Writing of the Run 2 data luminosity measurement publication and review within the CMS collaboration}
+  \SubItem{ Start final studies of the Run 3 data luminosity measurement for publication in a peer reviewed journal}
 
 \item {\bf Semester 7 (2026-2)}:
-  \SubItem{ Publication of the Run 2 data luminosity measurement in a peer reviewed journal}
+  \SubItem{ Completion of the studies of the Run 3 data luminosity measurement for publication in a peer reviewed journal}
+  \SubItem{ Presentations at national or international conferences of the luminosity measurements and TEPX luminometer for HL-LHC}
+  \SubItem{ Writing of the Ph.D thesis}
 
 \item {\bf Semester 8 (2027-1)}: 
-  \SubItem{ Presentations at national or international conferences for both the Run 2 luminosity measurement and TEPX luminometer for HL-LHC}
-  \SubItem{ Writing of the Ph.D thesis}
+  \SubItem{ Publication of the Run 3 data luminosity measurement in a peer reviewed journal}
+  \SubItem{ Presentations at national or international conferences of the luminosity measurements and TEPX luminometer for HL-LHC}
+  \SubItem{ Defense of the Ph.D thesis}
 

### 2023-09-14 project_Luis_PhD/paper.tex
abstract added

@@
 
-  This research project proposes...
+This research project proposes to enhance the precision of luminosity measurements at the LHC during Run 2 and Run 3, while also developing an upgraded luminosity measurement system for the HL-LHC phase.
+Accurate luminosity measurements are crucial for understanding particle physics, including Higgs boson production.
+The research involves analyzing the CMS pixel detector, calibrating it for 13.6 TeV collisions, and addressing systematic uncertainties.
+Additionally, it explores the Tracker Endcap
+Pixel Detector's (TEPX) performance for HL-LHC conditions and develops new cluster counting algorithms.
+The project contributes to high-precision particle physics and will result in peer-reviewed publications and conference presentations.
 

### 2023-09-14 tesis_Luis/Portada/Portada.tex
Add files via upload
updated
abstract added

--- 2022-12-29 tesis_Rodolfo/Portada/Portada.tex
@@
         \vspace{.4cm}   %% DEFINE EL ESPACIO ENTRE LA DOBLE LINEA Y EL NOMBRE DE LA DIVISIÓN
-        {\scshape \large Divisi\'on de Ciencias Exactas y Naturales}
+        {\scshape \large Facultad Interdisciplinaria de Ciencias Exactas y Naturales}
         {\scshape Departamento de Investigaci\'on en F\'isica} %% NOMBRE DE LA DIVISIÓN
@@
       \vspace{2cm}
-        {\Large \scshape {Measurements of the Large Hadron Collider luminosity using the CMS silicon pixel detector}}
+        {\Large \scshape {Development and calibration of the luminosity measurement system CMS Silicon Pixel Detector}}
 
@@
         By:\\[12pt]
-        \textbf{  {\large Jesus Rodolfo MORENO CHAVEZ}}
+        \textbf{  {\large Luis Enrique CUEVAS PICOS}}
 
@@
 
-        { Hermosillo, Sonora} \hskip2.5cm {December 08, 2022}
+        { Hermosillo, Sonora} \hskip2.5cm {August 15, 2023}
       \end{center}

### 2023-09-14 project_Luis_PhD/paper.tex
add cites, corrections and abstract

@@
 The plan of the LHC till year 2038 is to obtain datasets with up to 10 times higher values of instanteneous luminosities in the final phase.
-The LHC Run 3 began in 2022 and will last until 2024, with an expected integrated luminosity of about \lumi{300}.
+The LHC Run 3 began in 2022 and will last until 2024, with an expected integrated luminosity of about \lumi{450} \cite{lumi-run3}.
 
@@
 
-The PCC method for measuring luminosity uses the Pixel detector of the CMS tracker, the layout of the  detector used for recording the data during 2016-2018 is shown in Figure~\ref{fig:pixeldet}.
-The Pixel detector consists of 4 concentric cylindrical layers in the barrel and 2 disks in each endcap.
+The PCC method for measuring luminosity uses the Pixel detector of the CMS tracker, the layout of the  detector used for recording the data during 2016-2018 is shown in Figure~\ref{fig:pixeldet},  this detector is expected to deliver high-quality data until the end of LHC Run 3 (currently expected for 2024).
+The Pixel detector consists of 4 concentric cylindrical layers in the barrel and 3 disks in each endcap.
 Each detector part is composed of pixel sensors, a schematic of one sensor is shown in Figure~\ref{fig:pixeldet}.
-The entire Pixel detector contains 1856 sensor modules and a total of 65 million pixels.
+The entire Pixel detector contains 1856 sensor modules and a total of 124 million pixels \cite{TrackerGroupoftheCMS:2020bgg}.
 

### 2023-09-14 project_Luis_PhD/paper.tex
add cites, abstract and corrections

@@
 Due to the fine granularity of the pixel sensors and the large number of total pixels, the hit occupancy in the sensors remains very small, order of 1\%, during normal collisions.
-This low occupancy makes the PCC  very linear as a function of pileup, an essential property of a good luminometer.
+This low occupancy makes the PCC  very linear as a function of pileup, an essential property of a good luminometer \cite{Sirunyan:2021qkt}.
 
 The calibration of the luminometer consists of a van der Meer (vdM) scan performed in a special LHC run usually at the beginning of the run period (year).
-In this calibration setup, proton beams are moved across each other in separation steps of about 100 micrometers, by measuring the rates of clusters with the PCC algorithm and knowledge of the beam parameters during the vdM conditions, the calibration constant ($\sigma_{vis}$) is determined.
-This calibration constant is then used to normalize the measured PCC rates during normal running throughout the data-taking year.
+These scans are performed by varying the separation between the beams in each direction ($x$ and $y$) at a fixed number of separation steps of about 100 micrometers.
+Then these rates are fitted by a Gaussian function to obtain the beam overlaps $\Sigma_{x,y}$ and the peak rate of clusters $R(0,0)$ \cite{CMS:2018}.
+A schematic view of this methos is shown in Fig.
+\ref{vdMSketch}.
+Finally the calibration constant ($\sigma_{vis}$) is determined as Eq.\ref{sigmavis_eq}.
+
+\begin{equation}
+  \sigma_{vis}=\frac{2\pi \Sigma_{x} \Sigma_{y} R(0, 0)}{N_{1}N_{2} f}
+  \label{sigmavis_eq}
+\end{equation}
+Where $f$  is the LHC frecuency and $N_{1},N_{2}$ are the buch current used to normalize  the rates.
+This calibration constant is then used to determine the luminosity during a normal running throughout the data-taking year \cite{CMS:2018}.
 
@@
 The current design of the this tracker is shown in Figure~\ref{fig:tepx}, where the TEPX part consists of the last 4 disks at $|z|>170$ cm.
-In the same figure a transverse view of one disk is shown, and shows the layout of the sensor modules along phi for each ring in the disk.
+In the same figure a transverse view of one disk is shown, and shows the layout of the sensor modules along phi for each ring in the disk \cite{Klein:2017nke}.
 Studies will be performed using simulated samples with HL-LHC beam conditions, currently the expected pileup for these conditions is about 200 proton collisions per bunch crossing.
@@
   \label{fig:bunchcrossing}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.7\columnwidth]{./vdm_sketch.png}
+  \caption{
+   Sketch of a vdM scan in x and y planes. The sketch is an example of
+the fit of the resulting cluster rates \cite{vdMSketch}.
+  }
+  \label{vdMSketch}
 \end{figure}

### 2023-09-14 project_Luis_PhD/paper.tex
add abstract, correcions,  cites review

@@
 \begin{itemize}
-\item understand the CMS pixel detector layout including the barrel layers and endcap disks and their constituent modules,
-\item study the stability of the modules in the different layers or disks of the pixel detector and select the stable components,
-\item calculate the calibration constant (visible crossection) corresponding to 13 TeV proton-proton collision data,
-\item study the stability and linearity of the PCC luminosity measurement by comparing to other CMS luminometers,
-\item determine the instantaneous and the total integrated luminosity,
-\item determine the systematic uncertainties on the calibration constant and on the integrated luminosity.
+\item Understand the CMS pixel detector layout including the barrel layers and endcap disks and their constituent modules.
+\item Study the stability of the modules in the different layers or disks of the pixel detector and select the stable components.
+\item Calculate the calibration constant (visible crossection) corresponding to 13.6 TeV proton-proton collision data.
+\item Study the stability and linearity of the PCC luminosity measurement by comparing to other CMS luminometers.
+\item Determine the instantaneous and the total integrated luminosity.
+\item Determine the systematic uncertainties on the calibration constant and on the integrated luminosity.
 \end{itemize}
@@
 \begin{itemize}
-\item study the different parts of the TEPX detector,
-\item study the pixel cluster counting at the HL-LHC conditions using simulations of the TEPX detector,
-\item develop algorithms for pixel  cluster counting and coincidence counting,
+\item Study the different parts of the TEPX detector.
+\item Study the pixel cluster counting at the HL-LHC conditions using simulations of the TEPX detector.
+\item Develop algorithms for pixel  cluster counting and coincidence counting.
 \item determine the linearity and  precision of the different methods.
@@
 \item {\bf Semester 1 (2023-2)}:
-  \SubItem{ Readings on Standard Model of physics theory, LHC, and CMS experiments}
+  \SubItem{ Readings on Standard Model of physics theory, LHC, and CMS experiments.}
   \SubItem{ Review of the literature.}
-  \SubItem{ Master Linux computing and data analysis  skills (\textsc{Bash, Emacs, Root, HTCondor parallel processing})}
+  \SubItem{ Master Linux computing and data analysis  skills (\textsc{Bash, Emacs, Root, HTCondor parallel processing.})}
   \SubItem{ Complete work on the 2022 luminosity measurement for a preliminary  publication.}
@@
 \item {\bf Semester 2 (2024-1)}:
-  \SubItem{ Course I on particle physics, particle detection, or data analysis}
-  \SubItem{ Continue readings on Standard Model of physics theory, LHC, and CMS experiments}
-  \SubItem{ Master Linux computing and data analysis  skills (\textsc{Bash, Emacs, Root, HTCondor parallel processing})}
+  \SubItem{ Course I on particle physics, particle detection, or data analysis.}
+  \SubItem{ Continue readings on Standard Model of physics theory, LHC, and CMS experiments.}
+  \SubItem{ Master Linux computing and data analysis  skills (\textsc{Bash, Emacs, Root, HTCondor parallel processing.})}
   \SubItem{ Complete work on the Run 2 luminosity measurement for a final  publication.}
@@
 \item {\bf Semester 3 (2024-2)}:
-  \SubItem{ Course II on particle physics, particle detection, or  data analysis}
-  \SubItem{ Complete work on the 2023 dataset luminosity measurement. }
+  \SubItem{ Course II on particle physics, particle detection, or  data analysis.}
+  \SubItem{ Complete work on the 2023 dataset luminosity measurement.}
   \SubItem{ Start work on the 2024 dataset luminosity measurement. }
@@
   \SubItem{ Continue work on the 2024 dataset luminosity measurement. }
-  \SubItem{ Start studies on the TEPX luminometer for the HL-LHC}
-  \SubItem{ Writing of the monograph}
+  \SubItem{ Start studies on the TEPX luminometer for the HL-LHC.}
+  \SubItem{ Writing of the monograph.}
 
@@
   \SubItem{ Complete work on the 2024 dataset luminosity measurement. }
-  \SubItem{ Complete studies on the TEPX luminometer for the HL-LHC}
-  \SubItem{ Presentation at national or international conferences of the TEPX upgrade studies}
+  \SubItem{ Complete studies on the TEPX luminometer for the HL-LHC.}
+  \SubItem{ Presentation at national or international conferences of the TEPX upgrade studies.}
 
 \item {\bf Semester 6 (2026-1)}:
-  \SubItem{ Start final studies of the Run 3 data luminosity measurement for publication in a peer reviewed journal}
+  \SubItem{ Start final studies of the Run 3 data luminosity measurement for publication in a peer reviewed journal.}
 
 \item {\bf Semester 7 (2026-2)}:
-  \SubItem{ Completion of the studies of the Run 3 data luminosity measurement for publication in a peer reviewed journal}
-  \SubItem{ Presentations at national or international conferences of the luminosity measurements and TEPX luminometer for HL-LHC}
-  \SubItem{ Writing of the Ph.D thesis}
+  \SubItem{ Completion of the studies of the Run 3 data luminosity measurement for publication in a peer reviewed journal.}
+  \SubItem{ Presentations at national or international conferences of the luminosity measurements and TEPX luminometer for HL-LHC.}
+  \SubItem{ Writing of the Ph.D thesis.}
 
 \item {\bf Semester 8 (2027-1)}: 
-  \SubItem{ Publication of the Run 3 data luminosity measurement in a peer reviewed journal}
-  \SubItem{ Presentations at national or international conferences of the luminosity measurements and TEPX luminometer for HL-LHC}
-  \SubItem{ Defense of the Ph.D thesis}
+  \SubItem{ Publication of the Run 3 data luminosity measurement in a peer reviewed journal.}
+  \SubItem{ Presentations at national or international conferences of the luminosity measurements and TEPX luminometer for HL-LHC.}
+  \SubItem{ Defense of the Ph.D thesis.}
 

### 2023-09-15 project_Luis_PhD/paper.tex
anteproyecto v1

@@
 \def\Student{Luis Enrique Cuevas  Picos}
-\def\Title{THESIS PROJECT PROPOSAL}
+\def\Title{ANTEPROYECTO}
 \def\Prog{Doctorado en Ciencias (F\'{i}sica) }
@@
 \def\ProjectTitle{Luminosity measurement using Pixel Cluster Counting in the CMS experiment}
-\def\ResearchLine{F\'{i}sica de Part\'{i}culas}
+\def\ResearchLine{Experimental Particle Physics}
 
@@
 
+\newpage
 \section{EXPECTED RESULTS}
@@
 \item For the development of the HL-LHC upgrade system, the work  will be based on the previously published Technical Design Report (TDR) with the proposed design and algorithms to use the TEPX detector.
-It is expected that this work will be presented at conferences and used for the final design and construction of the system to be installed in the LS3 (2025-2027).  
+It is expected that this work will be used for the final design and construction of the system to be installed in the LS3 (2025-2027).  
 \end{itemize}
 
-Also, the student will become a part of an international experiment and is expected to present his results at national or international scientific conferences.
+The student will become parto of an international collaboration and is expected to present his results at national or international scientific conferences.
 
 \section{CALENDAR OF ACTIVITIES}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=\columnwidth]{./calendario.pdf}
+  \caption{ Calendar of activities }
+  \label{fig:calendario}
+\end{figure}
 
-\begin{itemize}
+%\begin{itemize}
+%
+%\item {\bf Semester 1 (2023-2)}:
+%  \SubItem{ Readings on Standard Model of physics theory, LHC, and CMS experiments.}
+%  \SubItem{ Review of the literature.}
+%  \SubItem{ Master Linux computing and data analysis  skills (\textsc{Bash, Emacs, Root, HTCondor parallel processing.})}
+%  \SubItem{ Complete work on the 2022 luminosity measurement for a preliminary  publication.}
+%
+%\item {\bf Semester 2 (2024-1)}:
+%  \SubItem{ Course I on particle physics, particle detection, or data analysis.}
+%  \SubItem{ Continue readings on Standard Model of physics theory, LHC, and CMS experiments.}
+%  \SubItem{ Master Linux computing and data analysis  skills (\textsc{Bash, Emacs, Root, HTCondor parallel processing.})}
+%  \SubItem{ Complete work on the Run 2 luminosity measurement for a final  publication.}
+%  \SubItem{ Start work on the 2023 dataset luminosity measurement. }
+%  
+%\item {\bf Semester 3 (2024-2)}:
+%  \SubItem{ Course II on particle physics, particle detection, or  data analysis.}
+%  \SubItem{ Complete work on the 2023 dataset luminosity measurement.}
+%  \SubItem{ Start work on the 2024 dataset luminosity measurement. }
+%  
+%\item {\bf Semester 4 (2025-1)}:
+%  \SubItem{ Continue work on the 2024 dataset luminosity measurement. }
+%  \SubItem{ Start studies on the TEPX luminometer for the HL-LHC.}
+%  \SubItem{ Writing of the monograph.}
+%
+%\item {\bf Semester 5 (2025-2)}:
+%  \SubItem{ Complete work on the 2024 dataset luminosity measurement. }
+%  \SubItem{ Complete studies on the TEPX luminometer for the HL-LHC.}
+%  \SubItem{ Presentation at national or international conferences of the TEPX upgrade studies.}
+%  
+%\item {\bf Semester 6 (2026-1)}:
+%  \SubItem{ Start final studies of the Run 3 data luminosity measurement for publication in a peer reviewed journal.}
+%
+%\item {\bf Semester 7 (2026-2)}:
+%  \SubItem{ Completion of the studies of the Run 3 data luminosity measurement for publication in a peer reviewed journal.}
+%  \SubItem{ Presentations at national or international conferences of the luminosity measurements and TEPX luminometer for HL-LHC.}
+%  \SubItem{ Writing of the Ph.D thesis.}
+%  
+%\item {\bf Semester 8 (2027-1)}: 
+%  \SubItem{ Publication of the Run 3 data luminosity measurement in a peer reviewed journal.}
+%  \SubItem{ Presentations at national or international conferences of the luminosity measurements and TEPX luminometer for HL-LHC.}
+%  \SubItem{ Defense of the Ph.D thesis.}
+%  
+%\end{itemize}
 
-\item {\bf Semester 1 (2023-2)}:
-  \SubItem{ Readings on Standard Model of physics theory, LHC, and CMS experiments.}
-  \SubItem{ Review of the literature.}
-  \SubItem{ Master Linux computing and data analysis  skills (\textsc{Bash, Emacs, Root, HTCondor parallel processing.})}
-  \SubItem{ Complete work on the 2022 luminosity measurement for a preliminary  publication.}
-
-\item {\bf Semester 2 (2024-1)}:
-  \SubItem{ Course I on particle physics, particle detection, or data analysis.}
-  \SubItem{ Continue readings on Standard Model of physics theory, LHC, and CMS experiments.}
-  \SubItem{ Master Linux computing and data analysis  skills (\textsc{Bash, Emacs, Root, HTCondor parallel processing.})}
-  \SubItem{ Complete work on the Run 2 luminosity measurement for a final  publication.}
-  \SubItem{ Start work on the 2023 dataset luminosity measurement. }
-
-\item {\bf Semester 3 (2024-2)}:
-  \SubItem{ Course II on particle physics, particle detection, or  data analysis.}
-  \SubItem{ Complete work on the 2023 dataset luminosity measurement.}
-  \SubItem{ Start work on the 2024 dataset luminosity measurement. }
-
-\item {\bf Semester 4 (2025-1)}:
-  \SubItem{ Continue work on the 2024 dataset luminosity measurement. }
-  \SubItem{ Start studies on the TEPX luminometer for the HL-LHC.}
-  \SubItem{ Writing of the monograph.}
-
-\item {\bf Semester 5 (2025-2)}:
-  \SubItem{ Complete work on the 2024 dataset luminosity measurement. }
-  \SubItem{ Complete studies on the TEPX luminometer for the HL-LHC.}
-  \SubItem{ Presentation at national or international conferences of the TEPX upgrade studies.}
-
-\item {\bf Semester 6 (2026-1)}:
-  \SubItem{ Start final studies of the Run 3 data luminosity measurement for publication in a peer reviewed journal.}
-
-\item {\bf Semester 7 (2026-2)}:
-  \SubItem{ Completion of the studies of the Run 3 data luminosity measurement for publication in a peer reviewed journal.}
-  \SubItem{ Presentations at national or international conferences of the luminosity measurements and TEPX luminometer for HL-LHC.}
-  \SubItem{ Writing of the Ph.D thesis.}
-
-\item {\bf Semester 8 (2027-1)}: 
-  \SubItem{ Publication of the Run 3 data luminosity measurement in a peer reviewed journal.}
-  \SubItem{ Presentations at national or international conferences of the luminosity measurements and TEPX luminometer for HL-LHC.}
-  \SubItem{ Defense of the Ph.D thesis.}
-
-\end{itemize}
-
+\newpage
 \onehalfspacing

### 2023-11-14 project_Luis_PhD/paper.tex
updated

@@
 Then these rates are fitted by a Gaussian function to obtain the beam overlaps $\Sigma_{x,y}$ and the peak rate of clusters $R(0,0)$ \cite{CMS:2018}.
-A schematic view of this methos is shown in Fig.
+A schematic view of this method is shown in Fig.
 \ref{vdMSketch}.
@@
   \includegraphics[width=0.48\columnwidth]{./bunchcrossing.jpg}
-  \includegraphics[width=0.48\columnwidth]{./vectorhit1.jpg}
+  \includegraphics[width=0.42\columnwidth]{./vectorhit1.jpg}
   \caption{
     Left: Dagram showing the collision of two proton bunches at LHC, bunches contain about $10^{11}$ protons  \cite{deMaria:2008zzb}.
-    Right: diagram showing example tracks originating from the collision and producing hits in the pixel detector layers.
+    Right: diagram showing example tracks originating from the collision and producing hits in the pixel detector layers \cite{Thomsom}.
   }
@@
 
-The student will become parto of an international collaboration and is expected to present his results at national or international scientific conferences.
+Additional benefits entail becoming a member of the CMS collaboration, presenting results at international and national scientific conferences, and contributing to the development of new technology for the HL-LHC project.
 

### 2023-12-17 tesis_Ashish/Abstract/abstract.tex
Sehrawat A thesis 17 Dec 2023

@@
 
-The Pixel Cluster Counting (PCC) luminosity measurement method has emerged as a reliable offline technique for luminosity measurement.
+The Pixel Cluster Counting (PCC) luminosity measurement method has emerged as a reliable offline technique for luminosity measurement developed for the CMS experiment.
 %The PCC method is based on the rate of pixel clusters in the CMS pixel detector, which is the innermost part of the CMS tracker.
-PCC method is studied for its precision in luminosity measurement using 2018 AlCa Reco datasets.
-The results of these studies demonstrate that the PCC luminosity measurement method is stable and linear, able to achieve 1\% systematic uncertainty on the final luminosity measurement.
+The PCC method is studied for its precision in luminosity measurement using 2017, 2018 and 2022  datasets.
+The results of these studies demonstrate that the PCC luminosity measurement method is stable and linear, able to achieve final uncertainty on the luminosity measurement at the level of 1\% or better.
+Final systematic uncertainty achieved on luminosity measurement for 2018 and 2022 datasets are 1.08\% and 1.5\% respectively.
+%1\% systematic uncertainty on the final luminosity measurement.
 Moreover, the clusters and coincidences counting algorithms and their optimization for the Phase II High Luminosity LHC (HL-LHC) luminosity measurement are also developed, using simulated datasets for the proposed Phase II pixel detector.
 %This new pixel detector will replace the Run 2 pixel detector.
-Linearity of the TEPX and D4R1 luminometers are expected to be within 1\% (offline) up to a pileup of 200 and their statistical precision per second is about 0.1\% at <PU>=200.
+Linearity of the Tracker endcap pixel (TEPX) and Disk 4 Ring 1 luminometers are expected to be within 1\% (offline) up to a pileup of 200 and their statistical precision per second is about 0.1\% at pileup 200.
 %It is expected to provide excellent statistical precision and linearity performance, which is essential for precision luminosity measurements at the HL-LHC.

### 2023-12-17 tesis_Ashish/Chapter1/chapter1.tex
Sehrawat A thesis 17 Dec 2023

@@
 
-Collider experiments are a type of particle physics experiment that involve colliding particles, typically protons or electrons, at very high energies.
+Collider experiments are a type of particle physics experiment that involve that typically involve high energy collisions of electrons or protons.
+%colliding particles, typically protons or electrons, at very high energies.
 These collisions can lead to the creation of new particles or the detection of new phenomena, providing insight into the fundamental nature of matter.
 Colliders are designed to accelerate particles to nearly the speed of light and guide them along a circular or linear path using magnetic fields.
-By colliding particles head-on or at oblique angles, physicists can study the resulting particle showers and detect the products of the collision using complex detectors.
+By colliding particles, physicists can study the resulting particle showers and detect the products of the collision using complex detectors.
+Two important parameters in the collider experiments are energy and luminosity.
 Collider experiments have played a crucial role in advancing our understanding of particle physics and continue to be a vital tool for scientific exploration.
-Two important parameters in the collider experiments are energy and luminosity.
 
@@
 
-Luminosity is a measure of the number of particle collisions that occur per unit area per unit area.
-In particle physics, luminosity is a crucial parameter that determines the rate at which particles are produced in a collider experiment \cite{Herr:941318}.
+Luminosity is a measure of the number of particle collisions that occur per unit area per unit time.
+In particle physics, luminosity is a crucial parameter that determines the rate at which interesting particles may be produced in an collider experiment \cite{Herr:941318}.
 
@@
 Thus, luminosity directly affects the ability to detect rare events and make precise measurements.
-The more collisions that occur, the higher the probability of rare events happening, such as the creation of new particles or the detection of new phenomena.
+%The more collisions that occur, the higher the probability of rare events happening, such as the creation of new particles or the detection of new phenomena.
 Additionally, precise measurements require a large number of collisions to be able to statistically determine the properties of the particles being studied.
 
-The production rate of a given particle can be expressed as:
+The rate (R) of a given particle can be expressed as:
 
@@
 
-where R is the production rate, L is the luminosity, and $\sigma$ is the cross-section of the process that produces the particle.
-The cross-section is a measure of the probability that a given process will occur, and it is typically a very small number, on the order of picobarns ($10^{-36} m^2$).
+where %R is the production rate,
+L is the luminosity, and $\sigma$ is the cross-section of the process that produces the particle.
+The cross-section is a measure of the probability that a given process will occur, and it is typically a very small number, on the order of picobarns ($10^{-36} cm^2$).
 In order to achieve high luminosity, particle accelerators use various techniques to increase the number of particles in the beams and focus them to a small cross-sectional area.
@@
 In high-energy particle accelerators, such as the Large Hadron Collider (LHC) at CERN, the luminosity is typically measured in units of inverse femtobarns ($fb^{-1}$), which is a measure of the total number of collisions per unit area during the course of an experiment.
-For example, the LHC has a design luminosity of $10^{34} cm^{-2}s^{-1}$, which means that there are $10^{34}$ proton-proton collisions per square centimeter per second.
+%For example, the LHC has a design luminosity of $10^{34} cm^{-2}s^{-1}$, which means that there are $10^{34}$ proton-proton collisions per square centimeter area per second.
 The importance of luminosity can be seen in the many discoveries that have been made in particle physics due to high luminosity experiments.
@@
 
-In particle physics, the luminosity of colliding beams is a crucial measurement as it provides information about the rate at which rare processes occur and enables precise measurements of particle properties such as cross sections and couplings to fermions, bosons.
+In particle physics, the luminosity of colliding beams is a crucial measurement as it provides information about the rate at which rare processes occur and enables precise measurements of particle properties such as cross-section and couplings to fermions and bosons.
 Luminosity depends on several variables, including the number of protons in each beam, the size and shape of the beams, and their relative positioning.
-A slight change in any of these variables can significantly alter the luminosity, which in turn affects the interpretation of collision data.
+A slight change in any of these variables can significantly alter the luminosity.
+%which in turn affects the interpretation of collision data.
 Therefore, it is crucial to measure the luminosity with high precision.
@@
 This information is then used to calculate the luminosity.
-Improving the uncertainty in luminosity measurements is essential for many physics analyses, including searches for new particles and measurements of the properties of known particles.
+Improving the uncertainty in luminosity measurements is essential for many physics analyses.
+%including searches for new particles and measurements of the properties of known particles.
 It is a dominant factor in the measurement of Higgs Boson cross sections and couplings to other gauge bosons and fermions, as shown in Fig~\ref{fig:lum_unc}.
@@
 \includegraphics[width=0.8\textwidth]{ashish_thesis/lumi_precision.png}
-\caption[Phase II uncertainty projections]{ %
+\caption[Phase II Uncertainty Projection]{ %
    Higgs boson production processes cross section projected uncertainty.
-In the most precisely measured Higgs boson production process, gluon fusion (ggH), luminosity uncertainty will dominate other experimental systematic uncertainty at the High Luminosity (HL)-LHC.
-\cite{Dainese:2703572}
+In the most precisely measured Higgs boson production process, gluon fusion (ggH), luminosity uncertainty will dominate other experimental systematic uncertainty at the High Luminosity (HL)-LHC \cite{Dainese:2703572}.
 }
@@
 Finally, the proton beams are sent to the LHC, where they are accelerated to their maximum energy of 6.5 TeV per proton.
-LHC consists of a 27-kilometer ring of superconducting magnets, which guide two counter-rotating beams of protons to collide at four different locations around the ring, where four major experiments, ATLAS, the CMS (Compact Muon Solenoid) experiment, ALICE and LHCb are located as shown in Fig.~\ref{fig:lhc}.
+
+LHC consists of a 27-kilometer ring of superconducting magnets, which guide two counter-rotating beams of protons to collide at four different locations around the ring, where four major experiments, ATLAS, the Compact Muon Solenoid (CMS) experiment, ALICE and LHCb are located as shown in Fig.~\ref{fig:lhc}.
 The protons are organized into "bunches," with each bunch containing around 100 billion protons.
 The bunches are spaced apart by 25 nanoseconds, and the LHC can contain up to 2,808 bunches per beam.
-The bunches in the LHC are designed to have a "bunch current" of 0.55 amperes.
+The bunches in the LHC are designed to have a beam current of 0.55 amperes.
 It uses radiofrequency (RF) cavities to accelerate the proton beams.
@@
 The dipole magnets are cooled to a temperature of 1.9 Kelvin (-271.3°C) using liquid helium, and are capable of producing a magnetic field of up to 8.3 tesla.
-The LHC's detectors record data from proton-proton collisions at a rate of around 40 million collisions per second, but only a tiny fraction of these are actually recorded for analysis.
+The LHC's detectors record data from proton-proton collisions at a rate of around 40 million bunch crossings per second, but only a tiny fraction of these are actually recorded for analysis.
 The LHC operates at a vacuum pressure of around $10^{-13}$ atmospheres, which is lower than the pressure on the surface of the moon.
@@
 \includegraphics[width=0.9\textwidth]{ashish_thesis/lhc_schematic.png}
-\caption[CERN accelerator complex]{%
+\caption[CERN Accelerator Complex]{%
     CERN accelerator complex consists of Linac 2, Proton Synchrotron Booster (PSB), Proton Synchrotron (PS), Super Proton Synchrotron (SPS) and Large Hadron Collider (LHC).
@@
 The CMS detector is a complex instrument that consists of several layers of sub-detectors, each designed to detect different types of particles and measure different properties of the particles.
+The CMS detector consists of a tracker, an electromagnetic calorimeter, hadron calorimeter and muon detector.
 
@@
 
-\item The tracker is a cylindrical-shaped detector designed to reconstruct the trajectories of charged particles with high precision.
+\item The tracker is a cylindrical detector made up of two main subsystems: the pixel detector and the silicon strip detector.
+The pixel detector, the innermost subsystem near the interaction point, is crucial for precise track reconstruction and vertex identification.
+It includes four barrel layers and two endcap regions with hybrid pixel detector modules.
+These modules consist of a silicon sensor, segmented into roughly 100x150 $\mu$m² pixels, and readout electronics.
+When charged particles pass through the sensor, they create electron-hole pairs that induce a current, which is amplified, shaped, and digitized.
+The upgraded pixel detector used in Run2 contained over 120 million pixels, ensuring high granularity and hit efficiency.
+The pixel detector has a 4.8 $\mu$m  and 7.99 $\mu$m  spatial resolution along 100 $\mu$m and 150 $\mu$m pixel pitch respectively.
+The silicon strip detector surrounding the pixel detector provides extra tracking points for improved track reconstruction.
+It comprises of the Tracker Inner Barrel and Disks (TIB/TID) and the Tracker Outer Barrel and Endcaps (TOB/TEC).
+Silicon strip sensors, segmented into strips with a pitch of 80 to 205 $\mu$m, generate electron-hole pairs like the pixel detector.
+The signals are then processed by the readout electronics.
+  %The silicon strip detector has a spatial resolution of 20-30 $\mu$m in the barrel region and 30-45 $\mu$m in the endcap region.
+
+  %The tracker is a cylindrical-shaped detector designed to reconstruct the trajectories of charged particles with high precision.
 The tracker is composed of two main subsystems: the pixel detector, located closest to the interaction point, and the silicon strip detector, surrounding the pixel detector.
 The pixel detector is the innermost subsystem of the CMS tracker, providing high-resolution spatial measurements essential for precise track reconstruction and vertex identification.
-The pixel detector consists of four barrel layers (BPIX) and two endcap regions, each with three disks (FPIX).
+The pixel detector consists of four barrel layers and two endcap regions, each with three disks.
 The pixel detector is built from hybrid pixel detector modules, which consist of a silicon sensor and readout electronics.
@@
 
-\item The Electromagnetic Calorimeter (ECAL) is an important component of the Compact Muon Solenoid (CMS) detector located inside the solenoid magnet of the Compact Muon Solenoid (CMS) detector.
+\item The Electromagnetic Calorimeter (ECAL), a part of the CMS detector, is crucial for measuring the energy of photons and electrons from collisions.
+The ECAL contains over 75,000 lead tungstate (PbWO4) crystals arranged cylindrically around the interaction point.
+When photons or electrons hit the crystals, they generate a secondary particle shower, producing scintillation light proportional to the energy of the incoming particle.
+By assessing this light in each crystal, the ECAL can precisely determine the energy of the incoming particle.
+The ECAL covers a pseudorapidity range $|\eta| < 3.0$ \footnote{The pseudorapidity $\eta$ is calculated as $\eta = - \ln(\tan(\frac{\theta}{2}))$ and ranges from $-\infty$ to $+\infty$.}, facilitating measurement of particles at various angles to the beam axis.
+Its arrangement includes a barrel region and two endcap regions.
+The PbWO4 crystals vary in size and orientation in these regions to match particle trajectories.
+They are sufficiently long to absorb incoming particle energy.
+The ECAL boasts an energy resolution of less than 0.5\% for 50 GeV electrons and less than 1\% for 100 GeV photons.
+This precision results from the small crystal size, the PbWO4 crystals' high light yield, and advanced calibration procedures.
+Moreover, it has excellent timing resolution, crucial for differentiating between particles from the same collision and rejecting background events.
+
+  %The Electromagnetic Calorimeter (ECAL) is an important component of the Compact Muon Solenoid (CMS) detector located inside the solenoid magnet of the Compact Muon Solenoid (CMS) detector.
 Its main function is to measure the energy of photons and electrons that are produced in collisions.
@@
 
-\item The Hadron Calorimeter (HCAL) is a crucial component of the Compact Muon Solenoid (CMS) detector, located outside of the Electromagnetic Calorimeter (ECAL).
+\item The Hadron Calorimeter (HCAL) in the CMS detector, positioned outside of the Electromagnetic Calorimeter (ECAL), measures the energy of hadrons—particles comprised of quarks bound by the strong nuclear force.
+Since hadrons are abundantly produced in high-energy LHC collisions, the HCAL's design focuses on absorbing their energy for measurement.
+It is composed of alternating layers of brass, for energy absorption, and plastic scintillator, for light emission when particles pass through.
+Photodetectors convert this light into a measurable electrical signal.
+The Barrel HCAL, also known as HB in CMS, is the main part of the HCAL that is centered around the beam pipe and extends outwards.
+The pseudorapidity range for this section of the calorimeter is $|\eta|$ < 1.3.
+The Endcap HCAL, or HE, is designed to capture particles emitted at larger angles from the beam pipe, extending the coverage of the barrel region.
+The pseudorapidity range of the Endcap HCAL is 1.3 < $|\eta|$ < 3.0.
+The Forward HCAL, or HF, is situated at both ends of the detector to capture particles produced at the smallest angles to the beam direction.
+The pseudorapidity range of the Forward HCAL in the CMS experiment is 3.0 < $|\eta|$ < 5.2.
+
+  %The HCAL, divided into a central barrel region and endcap regions, ensures coverage for particles produced at angles up to $|\eta| < 5.2$, accommodating a broad range of angles and energies up to several hundred GeV.
+
+  %The Hadron Calorimeter (HCAL) is a crucial component of the Compact Muon Solenoid (CMS) detector, located outside of the Electromagnetic Calorimeter (ECAL).
 The HCAL is responsible for measuring the energy of hadrons, which are particles made up of quarks bound together by the strong nuclear force.
@@
 
-\item The Muon Chambers are an essential component of the Compact Muon Solenoid (CMS) detector, which is one of the four main particle detectors at the Large Hadron Collider (LHC) at CERN.
+\item The Muon Chambers are a vital part of the CMS detector.
+Designed to detect a variety of particles from high-energy collisions, the CMS is particularly equipped for detecting muons, highly penetrative charged particles that often evade other detection methods.
+Positioned on the outermost layer of the CMS detector, the muon chambers comprise three types of detectors: drift tubes (DTs), cathode strip chambers (CSCs), and resistive plate chambers (RPCs).
+The DTs are centrally located in the barrel region, while CSCs cover the forward and backward endcap regions.
+The RPCs, offering a quick trigger signal for muon detection, are found in both the barrel and endcap regions.
+These chambers detect muons by observing the ionization when a muon travels through the detector gas.
+By tracking muon trajectories, scientists can investigate the properties of these particles and explore physics beyond the Standard Model.
+
+  %The Muon Chambers are an essential component of the Compact Muon Solenoid (CMS) detector, which is one of the four main particle detectors at the Large Hadron Collider (LHC) at CERN.
 The CMS detector is designed to detect a wide range of particles produced in high-energy collisions at the LHC, including muons, which are charged particles that pass through most materials easily and are difficult to detect using other methods.
@@
 
-\item The Compact Muon Solenoid (CMS) experiment at the Large Hadron Collider (LHC) at CERN uses a powerful superconducting solenoid magnet to produce a strong and uniform magnetic field, which is essential for detecting and measuring the properties of charged particles produced in high-energy collisions.
+\item The CMS experiment employs a powerful superconducting solenoid magnet, composed of niobium-titanium (NbTi) wire, to generate a strong, uniform magnetic field crucial for detecting and measuring charged particles from high-energy collisions.
+The wire, cooled to -268.5°C with liquid helium, becomes superconducting, carrying substantial electrical currents without heat generation.
+The cylindrical magnet, among the largest of its kind at 13 meters long and 6 meters in diameter, produces a 3.8 Tesla magnetic field—approximately 100,000 times stronger than Earth's magnetic field.
+This field bends the trajectories of charged particles as shown in Fig.~\ref{fig:cms}, facilitating momentum measurement and aiding physicists in studying the properties of various particles.
+  %such as the 2012-discovered Higgs boson. In conjunction with other CMS detector components, the solenoid magnet enables comprehensive reconstruction of particle properties.
+
+  %The Compact Muon Solenoid (CMS) experiment  uses a powerful superconducting solenoid magnet to produce a strong and uniform magnetic field, which is essential for detecting and measuring the properties of charged particles produced in high-energy collisions.
 The CMS solenoid magnet is made of niobium-titanium (NbTi) superconducting wire, which is cooled to a temperature of -268.5°C using liquid helium.
@@
 \includegraphics[width=0.75\textwidth]{ashish_thesis/cms_exp.png}
-\caption[CMS Experiment]{%
-   Compact muon solenoid (CMS) detector with all of the sub detectors showing silicon tracker, electromagnetic and hadron calorimeters and muon chambers \cite{CMS:2008xjf}. 
+\caption[CMS Experiment Design]{%
+   CMS detector with all of the sub detectors showing silicon tracker, electromagnetic and hadron calorimeters and muon chambers \cite{CMS:2008xjf}. 
 }
@@
 
-\section{Run 1 and Run 2 luminosity measurement}
+\section{Run 1, Run 2 and Run 3 luminosity measurement}
 
 During the operation of the CMS experiment, two main data-taking periods were conducted: Run 1, which spanned from 2010 to 2013, and Run 2, which took place from 2015 to 2018.
-During these periods, the CMS experiment measured the instantaneous and integrated luminosity of the proton-proton collisions produced by the Large Hadron Collider (LHC) where the integrated luminosity for each year is shown in Fig.~\ref{fig:lumi}.
+During these periods, the CMS experiment measured the instantaneous and integrated luminosity of the proton-proton collisions produced by the LHC where the integrated luminosity for each year is shown in Fig.~\ref{fig:lumi}.
 During Run 1, the CMS experiment achieved a peak instantaneous luminosity of up to $5 \times 10^{33} cm^{-2} s^{-1}$, while during Run 2, the luminosity reached a peak value of up to $2 \times 10^{34} cm^{-2} s^{-1}$.
-The luminosity measurements during both runs were accompanied by careful assessments of the systematic uncertainties to ensure accurate and reliable results \cite{CMS-PAS-EWK-10-004}\cite{CMS-PAS-EWK-11-001} \cite{CMS-PAS-SMP-12-008} \cite{CMS-PAS-LUM-13-001} \cite{Sirunyan:2759951} \cite{pas_17}\cite{pas_18} as shown in Table.
+The luminosity measurements during both runs were accompanied by careful assessments of the systematic uncertainties to ensure accurate and reliable results \cite{CMS-PAS-EWK-10-004, CMS-PAS-EWK-11-001, CMS-PAS-SMP-12-008, CMS-PAS-LUM-13-001, Sirunyan:2759951, pas_17, pas_18} as shown in Table.
 \ref{tab:lumi}.
@@
   \centering
-\caption[Run 1, Run 2 Integrated luminosity and its precision]{Summary of center of mass energy, integrated luminosity, and systematic uncertainty per year during the CMS luminosity measurement.}
+  \caption[Integrated luminosity and its precision for Run1 and Run2]{Summary of center of mass energy, integrated luminosity, and systematic uncertainty per year during the CMS luminosity measurement.}
 \begin{tabular}{c c c c}
-Year & Center of Mass Energy (TeV) & Integrated Luminosity (fb$^{-1}$) & Systematic Uncertainty (\%) \\
+  Year & Center of Mass Energy & Integrated Luminosity & Systematic Uncertainty \\
+  & (TeV) & (fb$^{-1}$) & (\%) \\
 \hline
@@
 \includegraphics[width=0.9\textwidth]{ashish_thesis/CMS_luminosity.png}
-\caption[Integrated luminosity per year]{%
+\caption[CMS Integrated luminosity]{%
     Delivered luminosity versus time for Run 1, Run 2 and Run 3 of the CMS Experiment \cite{wikicern_cc}.

### 2023-12-17 tesis_Ashish/Chapter2/chapter2.tex
Sehrawat A thesis 17 Dec 2023

@@
 
-Luminosity measurement is a crucial aspect of particle physics experiments such as the Compact Muon Solenoid (CMS) at the Large Hadron Collider (LHC).
+%Luminosity measurement is a crucial aspect of particle physics experiments such as the Compact Muon Solenoid (CMS) at the Large Hadron Collider (LHC).
 Luminosity signifies the rate at which particles collide per unit area per second, making its precision measurement vital for the precise determination of particle collision rates and cross-sections.
+
 The CMS experiment employs several devices to measure luminosity, each covering specific pseudorapidity ranges and regions within the CMS detector \cite{CMS-PAS-LUM-18-002}.
@@
 This holistic approach to luminosity measurement significantly improves the robustness and reliability of the data collected.
-In the central region, The Muon Drift Tubes (DT) luminometer is used covering a pseudorapidity range from 0 to 1.2.
+In the central region, the Muon Drift Tubes (DT) luminometer is used covering a $\eta$ range from 0 to 1.2.
 The Pixel Cluster Counting (PCC) luminometer also operates in this region and extends into the forward region covering a range from 0 to 2.5.
@@
 The Fast Beam Condition Monitor (BCM1F) functions in a range from 3.1 to 4.7.
-The Radiation Monitoring System for Environment and Safety (RAMSES) operates in the pseudorapidity range from 4 to 5.
-In the most Forward Region, The Hadron forward (HF) luminometer caters to the most forward region of the CMS detector \cite{Sirunyan:2759951}, functioning in the pseudorapidity range from 3 to 5  as shown in Fig.~\ref{fig:lumino_cms_pseudo}.
+The Radiation Monitoring System for Environment and Safety (RAMSES) are located directly behind HF.
+The Hadron forward (HF) luminometer caters to the most forward region of the CMS detector \cite{Sirunyan:2759951}, functioning in the pseudorapidity range from 2.9 to 5.2 as shown in Fig.~\ref{fig:lumino_cms_pseudo}.
 
@@
 
-\item Pixel Luminosity Telescope (PLT) : The PLT consists of four layers of silicon pixel sensors arranged in a stack, with each layer containing over 8 million individual pixels.
+\item Pixel Luminosity Telescope (PLT) : PLT is positioned 1.75 meters away from the interaction point, the PLT is an ensemble of 16 "telescopes." These are symmetrically distributed around the beam pipe at both extremities of the detector, with each telescope being composed of three individual silicon sensor planes.
+A defining feature of the PLT's functionality is the measurement of per-bunch instantaneous luminosity.
+This is accomplished by enumerating events in which all three sensor planes in a given telescope simultaneously register a hit.
+A specialized readout mechanism operating at the LHC's full bunch-crossing frequency of 40 MHz is employed to carry out this task.
+The PLT has provisions for reading out full pixel data, albeit at lower frequencies.
+This less frequent, yet detailed data readout serves multiple purposes.
+It is instrumental in determining calibrations, implementing corrections, and evaluating systematic uncertainties associated with both online and offline measurements.
+The PLT operates in what is called the "fast-OR" mode, which detects charged particles produced in a single bunch crossing of the proton beams.
+In this mode, the PLT triggers on any pixel in the detector that registers a signal above a certain threshold.
+This signal is called the "fast-OR signal" and indicates that a charged particle has passed through the detector.
+The PLT uses the information from all three detector planes to reconstruct the trajectories of the charged particles produced in the collisions.
+This is done by analyzing the signals from the individual pixels and using algorithms to determine the path of the particle through the detector.
+  %The PLT consists of four layers of silicon pixel sensors arranged in a stack, with each layer containing over 8 million individual pixels.
 The first three layers are located very close to the interaction point where the proton beams collide, and the fourth layer is located further away.
@@
   The PLT uses a specialized algorithm called the "triple coincidence" to identify charged particles that are produced in the collisions and to reject background noise.
-It requires a charged particle to be detected in at least three of the four detector planes, which corresponds to a "triple coincidence" detection.
+It requires a charged particle to be detected in all three planes, which corresponds to a "triple coincidence" detection.
 The rate of triple coincidences is proportional to the luminosity.
@@
 The integrated signal is then converted into a measure of the instantaneous luminosity, which is proportional to the product of the number of charged particles per bunch and the collision frequency.
-The number of charged particles per bunch is determined by calibrating the BCM1F with data from other detectors in the CMS experiment, such as the silicon pixel detector and the pixel luminosity telescope.
+
+  %The number of charged particles per bunch is determined by calibrating the BCM1F with data from other detectors in the CMS experiment, such as the silicon pixel detector and the pixel luminosity telescope.
 These detectors are used to measure the total number of charged particles produced by the proton-proton collisions, which is then used to calibrate the BCM1F \cite{CMS-DP-2013-003}.
@@
 
-\item Beam Halo Monitor (BHM):  The Beam Halo Monitor (BHM) is a device used in particle accelerators to measure the halo of particles that surround the main beam.
+%\item Beam Halo Monitor (BHM):  The Beam Halo Monitor (BHM) is a device used in particle accelerators to measure the halo of particles that surround the main beam.
 The halo is a region of low-density particles that surrounds the main beam and can cause damage to accelerator components or experimental detectors.
@@
 
-\item Hadron Forward Calorimeter: The Hadron Forward (HF) Calorimeter is a critical component of the Compact Muon Solenoid (CMS) experiment at the Large Hadron Collider (LHC) at CERN.
-It is a subdetector that measures the energy, position and arrival time of particles produced during proton-proton collisions in the LHC.
+\item Hadron Forward Calorimeter: The Hadron Forward (HF) Calorimeter is a critical component of the CMS experiment.
+It is a subdetector that measures the energy, position and arrival time of particles produced during proton-proton collisions.
 The HF Calorimeter is designed specifically to measure hadron particles, which are particles made up of quarks and gluons, in the forward region (i.e., close to the beamline) of the CMS detector.
@@
 This method relies on measuring the total transverse energy (Et) deposited in the calorimeter and comparing it with the expected average transverse energy for inelastic collisions.
-The idea behind the ME method is that the total transverse energy should be conserved in a collision event.
+The idea behind the MET method is that the total transverse energy should be conserved in a collision event.
 Inelastic collisions are expected to produce a certain amount of transverse energy on average, which can be estimated from simulations and theoretical calculations.
@@
 This distribution is then fitted to a functional form, which includes a term for the inelastic collisions and terms for various background processes (e.g., detector noise, beam-gas interactions).
-The fit allows extracting the number of inelastic collisions, which can then be used to calculate the luminosity by dividing it by the integrated time and the inelastic cross-section.
-The ME method is sensitive to the energy scale calibration of the detector and the modeling of background processes.
+The fit allows extracting the number of inelastic collisions, which can then be used to calculate the luminosity.
+The MET method is sensitive to the energy scale calibration of the detector and the modeling of background processes.
 However, it provides an independent and complementary measurement to the ZC method, which helps to reduce systematic uncertainties in the luminosity determination \cite{Sirunyan:2759951}.
@@
 
-\item Muon drift tubes: The DT system is part of the CMS muon system, which also includes the Resistive Plate Chambers (RPCs) and the Cathode Strip Chambers (CSCs).
+\item Muon drift tubes: The DT system is part of the CMS muon system, %which also includes the Resistive Plate Chambers (RPCs) and the Cathode Strip Chambers (CSCs).
   Drift Tubes (DTs) in the CMS experiment are designed to accurately measure the trajectory and momentum of muons produced in proton-proton collisions at the LHC.
-The DT system is located in the barrel region of the CMS detector, covering the pseudorapidity range of $|\eta| < 1.2$.
-The CMS Drift Tubes consist of rectangular drift cells filled with a gas mixture, typically of argon and carbon dioxide.
-Each drift cell contains a thin anode wire held at a high voltage relative to the cell walls, which act as the cathode.
+  %The DT system is located in the barrel region of the CMS detector, covering the pseudorapidity range of $|\eta| < 1.2$.
+  The DT system consist of rectangular drift cells filled with a gas mixture, typically of argon and carbon dioxide.
+The use of DT muon rates for luminosity measurement is based on the idea that the rate of single muon production is proportional to the instantaneous luminosity.
+Single muons comes from decay of inclusive, Z, W, top and jets.
+%The DT system in the CMS detector is used for muon detection and precise position measurement.
+Drift Tubes are essentially gas-filled detectors.
+When muons pass through these tubes, they ionize the gas.
+The resulting ions and electrons drift under the influence of an electric field to anode wires located in the center of the tubes, producing a signal.
+By measuring the drift time, one can infer the position of the muon's trajectory.
+To use the DT muon rates as a luminometer, one would need to count the rate of detected muons as a function of the delivered luminosity.
+However, the DT muon rate luminometer is not independently calibrated during the Van der Meer (vdM) scan due to low measured rate.
+It is cross calibrated with PCC or HF.
+
+  %Each drift cell contains a thin anode wire held at a high voltage relative to the cell walls, which act as the cathode.
 When a charged particle like a muon passes through the gas-filled cell, it ionizes the gas molecules, producing free electrons and positively charged ions.
@@
 \includegraphics[width=0.9\textwidth]{ashish_thesis/luminometer_cms.png}
-\caption[CMS luminometers]{%
-   Compact muon solenoid (CMS) detector with all of the luminosity measurement devices showing PLT, BCM1F, HF, DT, PCC and RAMSES. 
+\caption[CMS Luminometers]{%
+   CMS detector with all of the luminosity measurement devices showing PLT, BCM1F, HF, DT, PCC and RAMSES \cite{meyer2021luminosity}. 
 }
@@
 \includegraphics[width=0.9\textwidth]{ashish_thesis/luminometer_cms_pseudo.png}
-\caption[Location of CMS luminometers]{%
+\caption[CMS luminometers Location]{%
     Cross section of the CMS detector in the r-z plane showing all Run 2 luminometer PLT, BCM1F, DTs, and HF location.
-The two RAMSES monitors used as a luminometer in Run 2 are located directly behind HF.
+The two RAMSES monitors used as a luminometer in Run 2 are located directly behind HF \cite{Sirunyan:2759951}.
 }
@@
 The FPIX modules are also designed to handle high particle densities and radiation levels.
-Each module in the FPIX consists of a matrix of 16128 pixels, arranged in 160 rows and 101 columns.
-The pixel size in the FPIX is approximately 100x150 µm².
-It provide high-precision position measurements of the charged particles produced in the collisions.
+Each module in the FPIX consists of a matrix of 16128 pixels, arranged in 160 rows and 101 columns with same pixel size as layer pixels.
+%It provide high-precision position measurements of the charged particles produced in the collisions.
 These position measurements are used to reconstruct the trajectories of the particles and to identify the particles themselves.
-The pixel detector has a high position resolution, with a spatial resolution of 10-20 microns in the transverse direction and 20-30 microns in the longitudinal direction.
+The pixel detector has a high position resolution, with a spatial resolution of 4.8  microns in the transverse direction and 7.99 microns in the longitudinal direction.
 The pixel detector also has a high time resolution, with a readout time of 25 nanoseconds.
@@
 The pixel detector is able to operate at very high particle fluxes, with a hit rate of up to $100 MHz/cm^2$.
-To achieve this high rate capability, the pixel detector uses fast readout electronics, which can read out the signals from the pixels in a few microseconds.
+To achieve this high rate capability, the pixel detector uses fast readout electronics.
+%which can read out the signals from the pixels in a few microseconds.
 The pixel detector is also designed to operate at a high radiation level, with a dose of up to $5 \times 10^{14} neutrons/cm^2$ expected over the lifetime of the detector.
 To mitigate the effects of radiation damage, the pixel detector uses sensors made of high-purity silicon and a cooling system that keeps the detector at a temperature of -20°C.
-The pixel detector is also used for the measurement of the luminosity at the CMS experiment.
+The pixel detector is  used as a primary luminometer.
 The luminosity measurement is based on counting the number of pixel clusters produced in the detector by the proton-proton collisions.
-The higher the collision rate, the more clusters are produced in the pixel detector.
 However, there are several challenges to accurately measure the luminosity with the pixel detector.
-One challenge is the high rate of particles that pass through the detector, which can cause pileup (multiple particles passing through the detector at the same time).
+One challange is the multiple proton-proton collisions per bunch crossing (pileup).
 Another challenge is the non-linearity of the pixel detector response, which can lead to inaccuracies in the luminosity measurement.
-Therefore, the motivation of this research work is to develop and test more precise techniques for measuring the luminosity with the pixel detector, in order to improve the precision of the luminosity measurement and to better understand the effects of detector response on the measurement.
+Therefore, the motivation of this research work is to develop and test more precise techniques for measuring the luminosity with the pixel detector.
 
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/phaseI_upgrade_pixel_detector.png}
-\caption[Pixel detector layout]{%
-   Layout of the CMS Phase-1 upgraded pixel detector in longitudinal view. 
+\caption[Pixel Detector Layout]{%
+   Layout of the CMS Phase-1 upgraded pixel detector in longitudinal view \cite{Adam:2748381}. 
 }
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/silicon_pixel_module.png}
-\caption[Design of pixel module]{%
+\caption[Pixel Module Design]{%
    Pixel detector modules for BPIX L1 (left), BPIX L2-4 (middle), and
-the FPIX detector (right). 
+the FPIX detector (right) \cite{Adam:2748381}. 
 }
@@
   \begin{center}
+    \caption[Number of modules in pixel layers and disks]{Number of pixel detector modules in each layer and disk.}
     \begin{tabular}{ccccc}  
@@
       \end{tabular}
-    \caption[\# modules in pixel layers and disks]{Number of pixel detector modules in each layer and disk.}
+    %\caption[Number of modules in pixel layers and disks]{Number of pixel detector modules in each layer and disk.}
     \label{tab:modpix}
@@
 
-The Pixel Cluster Counting (PCC) method is one of the main luminosity measurement methods used at the CMS experiment.
+The Pixel Cluster Counting (PCC) method is one of the main luminosity measurement technique used at the CMS experiment.
 The PCC method is based on counting the number of pixel clusters produced by the collisions in the CMS pixel detector, which is a high-resolution silicon detector located close to the collision point.
-The pixel detector is made up of more than 65 million pixels, each of which is 100 micrometers by 150 micrometers in size.
+The pixel detector is made up of more than 124 million pixels.
 The detector is designed to detect charged particles produced in the collisions, and the pixel clusters are formed when several neighboring pixels are hit by a single particle.
 The PCC method is based on the assumption that the number of pixel clusters produced is proportional to the number of collisions, and therefore to the luminosity.
-The proportionality constant is called the pixel detector visible cross section, and it can be determined from a calibration measurement.
+The proportionality constant is called the pixel detector visible cross section, and it can be determined with a calibration method described in section 3.1.
 The PCC method is implemented in two stages: the online and offline stages.
 In the online stage, the pixel clusters are counted in real time by the CMS data acquisition system, which uses a custom-designed ASIC chip to process the pixel detector signals.
-The online luminosity measurement is therefore available within seconds of the collisions, and it is used to monitor the stability of the detector and to provide feedback to the LHC operators.
+%The online luminosity measurement is therefore available within seconds of the collisions, and it is used to monitor the stability of the detector and to provide feedback to the LHC operators.
 In the offline stage, the raw data from the pixel detector is analyzed using dedicated software to determine the pixel clusters and to calculate the luminosity.
 The offline luminosity measurement is more accurate than the online measurement, as it takes into account various corrections and calibrations that are not possible in real time.
-The offline luminosity measurement is also used to determine the absolute luminosity scale, which is obtained from beam parameters.
-There are several steps involved in the PCC method for measuring luminosity as described below.
+%The offline luminosity measurement is also used to determine the absolute luminosity scale, which is obtained from beam parameters.
+There are several steps involved in the PCC method for measuring luminosity like data acquisition, pixel cluster reconstruction, pixel cluster counting as described below.
 
@@
 The data is sent in packets, called data frames, which contain information about the event, such as the time of the event, the position of the particle, and the amount of charge deposited in the pixel sensor.
-The data acquisition system processes the data frames to reconstruct the particle tracks and identify the types of particles that passed through the pixel detector.
+%The data acquisition system processes the data frames to reconstruct the particle tracks and identify the types of particles that passed through the pixel detector.
 The data is then stored in a format that can be used for further analysis.
@@
 
-\item The number of pixel clusters is counted for a given time interval, known as lumi section.
+\item The number of pixel clusters is counted over a fixed time intervals, known as lumi section.
 One lumi section is 23.36 seconds time interval.
-The first step in the pixel cluster counting process is to select events of interest from the large dataset obtained from the CMS experiment.
-This is typically done using trigger systems that select events that are likely to be of interest based on their energy, particle multiplicity, or other criteria.
-Once the events of interest have been selected, the next step is to reconstruct the pixel clusters in each event using the algorithm described in the previous bullet point.
-This involves identifying individual pixel hits, identifying seed pixels, building pixel clusters around each seed pixel, and parameterizing the clusters.
+In the pixel cluster counting process, events of interest are selected from the large dataset obtained from the CMS experiment.
+This is typically done using zero bias triggers that select events that are coming from filled bunch crossing.
+  %Once the events of interest have been selected, reconstruction the pixel clusters in each event is done using the steps described in the previous bullet point.
+  %This involves identifying individual pixel hits, identifying seed pixels, building pixel clusters around each seed pixel, and parameterizing the clusters.
   After the pixel clusters have been reconstructed in each event, the next step is to count the number of clusters in each event.
-This can be done using simple counting algorithms that count the number of clusters above a certain energy threshold, or more sophisticated algorithms that use machine learning techniques to identify and count clusters.
-The number of pixel clusters in each event is affected by various sources of background noise, such as electronic noise and cosmic ray background.
+This can be done using simple counting algorithms that count the number of clusters above a certain energy threshold.
+%or more sophisticated algorithms that use machine learning techniques to identify and count clusters.
+  The number of pixel clusters in each event is affected by various sources of background noise. %such as electronic noise and cosmic ray background.
   To accurately measure the number of signal clusters in each event, these background sources must be subtracted from the total cluster count.
-This can be done using techniques such as sideband subtraction or template fitting.
-Finally, to obtain an accurate measurement of the number of particles that passed through the pixel detector, the cluster counts must be corrected for the inefficiencies in the cluster reconstruction process.
+ %This can be done using techniques such as sideband subtraction or template fitting.
+%Finally, to obtain an accurate measurement of the number of particles that passed through the pixel detector, the cluster counts must be corrected for the inefficiencies in the cluster reconstruction process.
 This can be done using simulation or other techniques to estimate the efficiency of the cluster finding algorithm as a function of the particle energy, position, and type.
 
-\item The number of pixel clusters is calibrated to account for various factors that affect the luminosity measurement, such as the efficiency of the pixel detector and the beam intensity.
+%\item The number of pixel clusters is calibrated to account for various factors that affect the luminosity measurement, such as the efficiency of the pixel detector and the beam intensity.
 The calibration step is an important part of the PCC (Pixel Cluster Counting) method for measuring luminosity at the CMS experiment.
@@
 \begin{equation}
- L = \frac{N_{cl} f_{rev} } {\sigma_{vis}}   
+ L_b = \frac{N_{cl} f_{rev} } {\sigma_{vis}}   
 \end{equation}
 
-where L is the luminosity, $N_{cl}$ is the number of clusters, $f_{rev}$ is the revolution frequency of the LHC, and $\sigma_{vis}$ is the visible cross section of the interaction region.
+where $L_b$ is the bunch luminosity, $N_{cl}$ is the number of clusters per bunch crossing, $f_{rev}$ is the revolution frequency of the LHC, and $\sigma_{vis}$ is the visible cross section of the pixel detector obtained from calibration.
 
@@
 
-\section{Advantages of the pixel cluster counting method}
-
 The PCC method has several advantages over the other luminosity measurement methods used by the CMS experiment.
-One advantage is its high precision and stability, as it is based on a well-understood physical process and has a small systematic uncertainty.
+The PCC method is based on the pixel detector, which has a high spatial resolution and can accurately measure the position and energy of charged particles.
+Another advantage is its high precision and stability, as it is based on a well-understood physical process and has a small systematic uncertainty.
 %Another advantage is its independence from the beam conditions, as the pixel detector is insensitive to the beam halo and the beam-gas interactions.
 The PCC method is also robust against pile-up, which is the presence of multiple proton-proton interactions in a single bunch crossing, as it can distinguish between pixel clusters produced by different collisions.
-The PCC method is based on the pixel detector, which has a high spatial resolution and can accurately measure the position and energy of charged particles.
+%The PCC method is based on the pixel detector, which has a high spatial resolution and can accurately measure the position and energy of charged particles.
 This allows for precise measurements of the luminosity, even when the particle collision rate is high.
+The pixel detector has a high detection efficiency, meaning that it can detect a large fraction of the particles produced in the collisions.
+The pixel detector's high granularity enables precise detection of individual particles.
+%The pixel cluster counting method is relatively insensitive to pileup, allowing accurate luminosity measurements even when pileup is high,
+It has a wide dynamic range, capable of measuring luminosities from low to high due to the large number of pixels.
+
+\begin{comment}
+
 Advantages of the PCC method are described below,
@@
 \item High precision: The pixel detector has a high granularity and can detect individual particles with high precision.
-This allows for a precise measurement of the luminosity, with uncertainties typically below 2\%.
+%This allows for a precise measurement of the luminosity, with uncertainties typically below 2\%.
 
 \item High efficiency: The pixel detector has a high detection efficiency, meaning that it can detect a large fraction of the particles produced in the collisions.
-This allows for a high signal-to-noise ratio and a low level of background noise, resulting in a more accurate measurement of the luminosity.
+%This allows for a high signal-to-noise ratio and a low level of background noise, resulting in a more accurate measurement of the luminosity.
 
@@
 The pixel cluster counting method is relatively insensitive to pileup, meaning that it can still provide accurate luminosity measurements even when pileup is high.
+Thus, PCC is a linear luminometer.
 
-\item Wide dynamic range: The pixel cluster counting method has a wide dynamic range, meaning that it can measure luminosities over a wide range of values, from low to high.
-This is important for experiments that need to measure luminosities over different energy ranges.
+\item Wide dynamic range: The pixel cluster counting method has a wide dynamic range, meaning that it can measure luminosities over a wide range of values, from low to high because of large number of pixels.
 
-\item Insensitivity to beam conditions: The pixel cluster counting method is relatively insensitive to beam conditions such as beam intensity and beam size.
+%This is important for experiments that need to measure luminosities over different energy ranges.
+
+%\item Insensitivity to beam conditions: The pixel cluster counting method is relatively insensitive to beam conditions such as beam intensity and beam size.
 This makes it a reliable technique for luminosity measurement, even when the beam conditions vary.
 
-\item Independent of beam crossing angle: The pixel cluster counting method is independent of the beam crossing angle, which is the angle at which the beams intersect.
+%\item Independent of beam crossing angle: The pixel cluster counting method is independent of the beam crossing angle, which is the angle at which the beams intersect.
 This makes it easier to compare results obtained under different beam crossing angles.
 
-\item Independence from trigger systems: The PCC method operates independently of the CMS experiment's trigger systems, which means it is not affected by any biases or inefficiencies that might be present in the trigger.
+%\item Independence from trigger systems: The PCC method operates independently of the CMS experiment's trigger systems, which means it is not affected by any biases or inefficiencies that might be present in the trigger.
 
 \end{itemize}
+
+\end{comment}
 
@@
 The PCC method has been extensively tested and validated by the CMS during the LHC Run 1 and Run 2, which corresponded to proton-proton collisions at center-of-mass energies of 7-8 TeV and 13 TeV, respectively.
-The PCC method has achieved a relative luminosity precision of about 2-3 \%, which is well within the design goals of the CMS \cite{CMS-PAS-LUM-18-002}.
+The PCC method has achieved a relative luminosity precision of about 1.5 \%, which is well within the design goals of the CMS \cite{CMS-PAS-LUM-18-002}.
 In the future, the PCC method will continue to be a key component of the CMS luminosity measurement strategy, as it provides a precise and robust measurement of the luminosity ratio between different datasets and periods.
@@
 
-\newpage
-\section{Previous studies on PCC luminosity measurement}
+%\section{Previous studies on PCC luminosity measurement}
 
-The Pixel Cluster Count (PCC) of various layers and disks, normalized to the total PCC, as a function of luminosity section can provide crucial insights into the detector's performance and stability over time and under different conditions \cite{CMS-PAS-LUM-15-001}\cite{CMS-PAS-LUM-16-001}.
-A luminosity section is a unit of data-taking time in the LHC, typically lasting about 23.36 seconds, during which the beam conditions are assumed to be stable.
-The luminosity delivered during each of these sections can vary, leading to different levels of activity in the detector.
+The PCC of various layers and disks, normalized to the total PCC, as a function of lumi section can provide crucial insights into the detector's performance and stability over time and under different conditions \cite{CMS-PAS-LUM-15-001}\cite{CMS-PAS-LUM-16-001}.
+A lumi section is a unit of data-taking time in the LHC, typically lasting about 23.36 seconds, during which the beam conditions are assumed to be stable.
+The luminosity delivered during each of these lumi sections can vary, leading to different levels of activity in the detector.
 
@@
 
-\item Operational Adjustments: Observations from these plots can guide operational adjustments.
+%\item Operational Adjustments: Observations from these plots can guide operational adjustments.
 If the PCC ratios for certain layers or disks consistently deviate under specific luminosity conditions, adjustments could be made in the detector operation to account for these variations.
 \end{itemize}
+
+\begin{comment}
 
@@
 \end{figure}
+
+\end{comment}

### 2023-12-17 tesis_Ashish/Chapter3/chapter3.tex
update
thesis version 11 Jul
Sehrawat A thesis 17 Dec 2023

@@
-\chapter{PCC luminometer calibration}  %Title of the First Chapter
+\chapter{Luminometer calibration}  %Title of the First Chapter
 
@@
 %One of the widely used method for the calibration of luminosity measurement devices is the van der Meer (VdM) scan method.
-A prevalent technique for calibrating luminosity measurement devices is the van der Meer (VdM) scan method.
+A prevalent technique for calibrating luminosity measurement devices is the van der Meer (vdM) scan method.
 This method is named after Simon van der Meer, a Dutch physicist and Nobel laureate, who developed the technique in the 1960s.
-These scans are performed to relate the collision rate of a given luminometer to the absolute luminosity determined from the measured beam parameters.
+These scans are performed to relate the detection rate of a given luminometer to the absolute luminosity determined from the measured beam parameters.
 The proportionality constant is called the visible cross section.
 It involves scanning the beams across each other in the horizontal and vertical planes to measure the beam overlap integral, which is proportional to the luminosity.
-The first step in the VdM calibration is to scan the colliding beams across each other.
+The first step in the vdM calibration is to scan the colliding beams across each other.
 This is done by displacing the beams in the horizontal (x) and vertical (y) planes independently while keeping the other direction fixed as shown in left part of Fig.
@@
 The scans are performed at several different positions along the collision point, creating a series of data points for each plane.
-The data points collected during the scans are then fitted with Gaussian function or other suitable function like double gaussian, Poly2G, Poly4G, etc as shown in right part of Fig.
+The data points collected during the scans are then fitted with  suitable function like single, double gaussian as shown in right part of Fig.
 \ref{fig:vdm_scan_method}  to determine the beam overlap integrals in the x and y directions.
-The product of the integrals in the two planes yields the total beam overlap integral.
-%The event rate is proportional to the luminosity and is given by the product of the cross-section ($\sigma$) and luminosity.
-The beam overlap integral is the integral of the product of the beam overlap width in the horizontal and vertical planes over the entire interaction region \cite{vanderMeer1968}.
-It is an essential parameter in determining the absolute luminosity.
+%The product of the integrals in the two planes yields the total beam overlap integral.
+The event rate is proportional to the luminosity and is given by the product of the cross-section ($\sigma$) and luminosity.
+The total beam overlap is the product of beam overlap width in the horizontal and vertical planes over the entire interaction region \cite{vanderMeer1968}.
+It is an essential parameter in determining the absolute luminosity to calculate visible cross section.
 
@@
     \includegraphics[width=1\textwidth]{ashish_thesis/vdm_method.png}
-    \caption[Schematic of van der Meer scan]{Left: Scanning the beams across each other (±3$\sigma$) in the transverse plane, horizontal (x-scan) and vertical (y-scan) directions.
-Right: Rate is measured as a function of beam separation}
+    \caption[vdM Scan Schematic]{Left: Scanning the beams across each other (±3$\sigma$) in the transverse plane, horizontal (x-scan) and vertical (y-scan) directions.
+Right: Rate is measured as a function of beam separation \cite{karacheban2017luminosity}.}
     \label{fig:vdm_scan_method}
@@
 
-In the van der Meer (vdM) scans,  rate is plotted as a function of beam overlap widths along x and y directions that is used to determine the visible cross section $\sigma_{vis}$ of the pixel detector which is a calibration constant in the relation between rate of a quantity (clusters, coincidences) read out by the detector and the instantaneous luminosity.
+In the van der Meer (vdM) scans,  rate is plotted as a function of beam separation along x and y directions that is used to determine the visible cross section $\sigma_{vis}$.
+%of the pixel detector which is a calibration constant in the relation between rate of a quantity (clusters, coincidences) read out by the detector and the instantaneous luminosity.
 
@@
 \begin{equation}
-L_{b} = N_1 N_2 f \int^{+\infty}_{-\infty} \rho_1(x,y) \rho_2(x+\Delta x, y+\Delta y) dx dy 
+L_{b} = N_1 N_2 f \int^{+\infty}_{-\infty} \rho_1(x,y) \rho_2(x, y) dx dy 
 \end{equation}
 
-where $N_1, N_2$ are the number of protons in the colliding bunches, f is the LHC orbit frequency whose value is 11246Hz,  $\rho_1(x,y)$ and $\rho_2(x+\Delta x,y+\Delta y)$ are the two dimensional particle density distribution functions for each colliding bunch separated by $\Delta x$ and $\Delta y$ in x and y directions  \cite{CMS-PAS-LUM-17-004}.
+where $N_1, N_2$ are the number of protons in the colliding bunches, f is the LHC orbit frequency whose value is 11246 Hz,  $\rho_1(x,y)$ and $\rho_2(x,y)$ are the two dimensional particle density distribution functions for each colliding bunch in x and y directions  \cite{CMS-PAS-LUM-17-004}.
 
@@
 \begin{equation}
-L_{b} = N_1 N_2 f \int^{+\infty}_{-\infty} \rho_{1x}(x) \rho_{2x}(x+\Delta x)  dx   \int^{+\infty}_{-\infty} \rho_{1y}(y) \rho_{2y}(y+\Delta y)  dy 
+L_{b} = N_1 N_2 f \int^{+\infty}_{-\infty} \rho_{1x}(x) \rho_{2x}(x)  dx   \int^{+\infty}_{-\infty} \rho_{1y}(y) \rho_{2y}(y)  dy 
 \end{equation}
 
-where $\rho_1(x,y) = \rho_{1x}(x) \rho_{1y} (y)$ and $\rho_2(x,y) = \rho_{2x}(x+\Delta x) \rho_{2y} (y+\Delta y)$
+where $\rho_1(x,y) = \rho_{1x}(x) \rho_{1y} (y)$ and $\rho_2(x,y) = \rho_{2x}(x) \rho_{2y} (y)$
 
-The vdM scan determines the bunch  overlap integrals $\int \rho_{x1} (x) \rho_{x2} (x+\Delta x) dx$ and  $\int \rho_{y1}(y) \rho_{y2} (y+\Delta y) dy$ by measuring pixel clusters rate as a function of bunch separation $\Delta x$ and $\Delta y$ along x and y directions as shown in Fig.
-14.
+The vdM scan determines the bunch  overlap integrals $\int \rho_{1x} (x) \rho_{2x} (x) dx$ and  $\int \rho_{1y}(y) \rho_{2y} (y) dy$ by measuring pixel clusters rate as a function of beam separation $\Delta x$ and $\Delta y$ along x and y directions.
 
 \begin{equation}
-\int \rho_{x1} (x) \rho_{x2} (x+\Delta x) dx = \frac{R_x(0)}{\int R_x(\Delta x)dx} 
+\int \rho_{1x} (x) \rho_{2x} (x) dx = \frac{R_x(0)}{\int R_x(\Delta x)d \Delta x} 
 \end{equation}
@@
 \begin{equation}
-\int \rho_{y1} (y) \rho_{y2} (y+\Delta y) dy = \frac{R_y(0)}{\int R_y(\Delta y)dy} 
+\int \rho_{1y} (y) \rho_{2y} (y) dy = \frac{R_y(0)}{\int R_y(\Delta y)d \Delta y} 
 \end{equation}
 
-where $R_x(0)$ is the measured cluster rate along x direction when the bunch separation is zero and $R_x(\Delta x)$ is the measured cluster rate when bunches are separated by distance $\Delta x$ and $R_y(0)$ is the measured cluster rate along y direction when the bunch separation is zero and $R_y(\Delta y)$ is the measured cluster rate when bunches are separated by distance $\Delta y$.
+where $R_x(0)$ is the measured cluster rate along x direction when the beam separation is zero and $R_x(\Delta x)$ is the measured cluster rate when beams are separated by distance $\Delta x$ and $R_y(0)$ is the measured cluster rate along y direction when the beam separation is zero and $R_y(\Delta y)$ is the measured cluster rate when beams are separated by distance $\Delta y$.
 
-Bunch overlap widths $\Sigma_x$ and $\Sigma_y$ along x and y directions are defined as
+We define the quantities $\Sigma_x$ and $\Sigma_y$:
+
+%Bunch overlap widths $\Sigma_x$ and $\Sigma_y$ along x and y directions are defined as \cite{White:1308187}
 
 \begin{equation}
-\Sigma_x = \frac{1}{\sqrt{2 \pi}} \frac{\int R_x(\Delta x)dx}{R_x(0)} 
+\Sigma_x = \frac{1}{\sqrt{2 \pi}} \frac{\int R_x(\Delta x)d \Delta x}{R_x(0)} 
 \end{equation}
@@
 \begin{equation}
-\Sigma_y =  \frac{1}{\sqrt{2 \pi}} \frac{\int R_y(\Delta y)dy}{R_y(0)} 
+\Sigma_y =  \frac{1}{\sqrt{2 \pi}} \frac{\int R_y(\Delta y)d \Delta y}{R_y(0)} 
 \end{equation}
@@
 
-where R(0) is the peak cluster rate measured by the pixel detector after applying appropriate stability module selection.
+where R(0) is the peak cluster rate. % measured by the pixel detector after applying appropriate stability module selection.
 
@@
 
+\begin{comment}
 The calibration of luminosity measurement by the CMS experiment in the 2018 proton-proton data taking at √s = 13 TeV was performed during
 
-LHC fill 6868 on June 30 and July 1, 2018 at √s = 13 TeV
+\begin{itemize}
+\item LHC fill 6868 on June 30 and July 1, 2018 at √s = 13 TeV
 
-Zero-bias triggers on 5 bunch pairs (BCIDs 265, 865, 1780, 2192, and 3380)
+\item Zero-bias triggers on 5 bunch pairs (BCIDs 265, 865, 1780, 2192, and 3380)
 
-recorded events rate is 27.7 kHz.
+\item recorded events rate is 27.7 kHz. 
+\end{itemize}
 
 vdM scans are typically conducted at least once a year to ensure the luminometer is correctly calibrated.
-Results of these scans are used to normalize the data collected by the experiments during physics run.
+Results of these scans that is the visible cross section is used to normalize the data collected by the experiments during physics run.
 
@@
 
-\section{Background Estimation}
+\end{comment}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/new_framework_vdm.png}
+%\caption{%
+%   klm
+%}
+%\label{fig:vdm_new_f}
+%\end{figure}
+
+\section{Background estimation}
 
@@
 
-\section{vdM fit model}
+\section{Fit model}
 
 The poly2G model, or the "Gaussian function with a polynomial term" model, is a fitting function that combines a second-order polynomial function and a Gaussian function.
-It is a versatile and flexible model that can be used to fit various types of data, including the PCC rate plot in the context of the Van der Meer (VdM) calibration process.
-In a PCC rate plot, the event rate is plotted as a function of the beam separation.
-The poly2G model can be employed to fit the PCC rate plot to extract the beam parameters, such as the beam overlap widths and the center positions, which are essential for the luminosity measurement \cite{Cekmecelioglu:2775639}.
-The general form of the poly2G model is
+It is a versatile and flexible model that can be used to fit various types of data, including the PCC data in the context of the vdM calibration.
+%In a PCC rate plot, the rate is plotted as a function of the beam separation.
+The Poly2G model can be employed to fit the PCC rates %to display data and fit model in the plot
+and extract the beam parameters, beam overlap integrals and peak rates  needed for the determination of the calibration constant  %such as the beam overlap widths and the beam center positions, which are essential for the luminosity measurement
+\cite{Cekmecelioglu:2775639}.
+The Poly2G function has additional degrees of freedom compared to a single Gaussian but fewer than a DG (Double Gaussian), allowing for better convergence.
+The general form of the Poly2G model is
 
@@
 \begin{equation}
-Poly2G = Peak  \left [1+r2 \left(\frac{x-\mu} {\frac{\sigma}{1+r2}}\right)^2 \right] exp \left[-\frac{1}{2}\left(\frac{x-\mu}{\frac{\sigma}{1+r2}}\right)^2\right]
+F(x) = Peak  \left [1+r_2 \left(\frac{\Delta x-\mu} {\frac{\sigma}{1+r_2}}\right)^2 \right] exp \left[-\frac{1}{2}\left(\frac{\Delta x-\mu}{\frac{\sigma}{1+r_2}}\right)^2\right]
 \end{equation}
 
-where Peak is the maximum PCC rate, $\mu$ is the mean, $\sigma$ and r2 are the fit parameters.
+where Peak is the maximum PCC rate, $\mu$ is the mean, $\sigma$ and $r_2$ are the fit parameters.
+
+To determine the beam overlap $\Sigma$ in this model, we calculate the area under the Poly2G curve between $-\infty$ and  +$\infty$ and divide by its peak value. We integrate the poly2G function
+%\[
+%F(x) = \text{Peak} \left[ 1 + r_2 \left( \frac{x - \mu}{\frac{\sigma}{1 + r_2}} \right)^2 \right] \exp \left[ -\frac{1}{2} \left( \frac{x - \mu}{\frac{\sigma}{1 + r_2}} \right)^2 \right]
+%\]
+from \(-\infty\) to \(+\infty\) using the substitution method.
+
+\begin{equation}
+z = \frac{x - \mu}{\frac{\sigma}{1 + r_2}} ,   dx = \frac{\sigma}{1 + r_2} dz 
+\end{equation}
+
+With this substitution, the function becomes:
+
+\begin{equation}
+F(z) = \text{Peak} \left[ 1 + r_2 z^2 \right] \exp\left(-\frac{1}{2} z^2\right)
+\end{equation}
+
+The integral is then:
+
+\begin{equation}
+I = \text{Peak} \int_{-\infty}^{\infty} \left[ 1 + r_2 z^2 \right] \exp\left(-\frac{1}{2} z^2\right) \frac{\sigma}{1 + r_2} dz
+\end{equation}
+
+%Breaking this into two parts:
+
+%\begin{equation}  
+%I_1 & = \text{Peak} \int_{-\infty}^{\infty} \exp\left(-\frac{1}{2} z^2\right) \frac{\sigma}{1 + r_2} dz = \text{Peak} \sqrt{2\pi} \frac{\sigma}{1 + r_2} \\
+%\end{equation}
+
+%\begin{equation}
+%I_2 & = \text{Peak} r_2 \int_{-\infty}^{\infty} z^2 \exp\left(-\frac{1}{2} z^2\right) \frac{\sigma}{1 + r_2} dz = \text{Peak} r_2 \sqrt{2\pi} \frac{\sigma}{1 + r_2}
+%\end{equation}
+
+Thus:
+\[ I = \frac{\text{Peak} \sqrt{2\pi} \sigma (1 + r_2) }{1+r_2} = \text{Peak} \sqrt{2\pi} \sigma \]
+
+Dividing by the \(\text{Peak}\) value:
+\[ \frac{I}{\text{Peak}} = \sqrt{2\pi} \sigma  \]
+
+Beam overlap width for Poly2G fit function is
+\begin{equation}
+ \Sigma = \frac{ \sqrt{2\pi} \sigma}{\sqrt{2 \pi}} = \sigma 
+\end{equation}
 

### 2023-12-17 tesis_Ashish/Chapter4/chapter4.tex
Sehrawat A thesis 17 Dec 2023

@@
 Fig. \ref{fig:period_bound}. Run ranges for each period are shown in Table \ref{tab:period_run_ranges}.
-During period B, specifically corresponding to Fill 6868, van der Meer (vdM) scans were conducted for calibrating the luminometer.
+During period B, specifically corresponding to Fill 6868, van der Meer (vdM) scans were conducted for calibrating the PCC luminometer.
 %vdM data is shown during period B corresponding to Fill 6868.
@@
 \includegraphics[width=0.9\textwidth]{ashish_thesis/period_boundary.png}
-\caption[2018 CMS luminosity data taking periods.]{%
-   2018 luminosity data taking periods showing data taking period boundaries and vdM calibration data  \cite{CERNLumiPublicResults}.
+\caption[2018 CMS Luminosity Data Period]{%
+   2018 luminosity data taking periods showing data taking period boundaries and vdM calibration data (1 July in period B)  \cite{CERNLumiPublicResults}.
 }
@@
   \begin{center}
+    \caption[Run ranges for 2022 periods]{2018 luminosity data periods with run ranges.}
     \begin{tabular}{ccccc}
@@
       \end{tabular}
-    \caption[Run ranges]{2018 luminosity data periods with run ranges.}
+    %\caption[Run ranges]{2018 luminosity data periods with run ranges.}
     \label{tab:period_run_ranges}
@@
 
-In the study under consideration, we have utilized a series of datasets corresponding to the data-taking periods of 2018, namely 2018A, 2018B, 2018C, and 2018D as shown in Table \ref{tab:datasets}.
-These datasets have been drawn from the Alignment and Calibration (AlCa) project, an integral component of the Compact Muon Solenoid (CMS) experiment conducted at the Large Hadron Collider.
-The dataset selection includes two subsets denoted as AlCaPCCRandom and AlCaPCCZeroBias.
-The AlCaPCCRandom dataset comprises of data where trigger is applied on both colliding and non-colliding bunches, thereby providing a holistic and representative view of the whole dataset.
-On the other hand, the AlCaPCCZeroBias dataset encapsulates events that have passed the trigger system with no bias where trigger is applied on only colliding bunches, thereby serving as an unbiased reference dataset.
-In terms of processing, the selected datasets have undergone an Express processing pathway.
-This rapid processing approach, while less detailed than the full reprocessing, provides valuable and timely insights into the data quality and physics performance.
-The datasets fall within the ALCARECO (ALignment, CALibration, and REConstruction objects) data tier, which specifically encompasses information pertinent to detector alignment and calibration, forming a crucial resource in our analysis.
-The timestamps associated with these datasets (e.g., $'13Mar2023\_UL2018\_PCC'$) indicate that they have undergone a reprocessing or update post their initial collection in 2018.
-%This reprocessing phase enhances the scientific value of these datasets, by incorporating improved calibrations and alignment, and updates to the data reconstruction algorithms.
-Consequently, the reprocessed datasets used in this thesis afford a more accurate and comprehensive representation of the physics events under investigation.
+In the study under consideration, the datasets have been drawn from the Alignment and Calibration (AlCa) project, an integral component of the CMS experiment.
+The dataset selection includes two subsets: Random trigger and Zero-Bias.
+The Random trigger dataset comprises of data where trigger is applied on both colliding and non-colliding bunches.
+On the other hand, the Zero-Bias dataset encapsulates events that have passed the trigger system with no bias which means the colliding bunches are randomly triggered without the use of any CMS detector signal.
+The list of colliding bunches is detected by an independent system Beam Pick-up Timing system (BPTX) for Experiments.
+CMS software (CMSSW) version $10{\_}2{\_}2$ is used for reprocessing random trigger PCC dataset and $10{\_}6{\_}30$  \cite{CMSReleaseNotes} is used for reprocessing zero bias PCC datasets.
+
+\begin{comment}
 
@@
 
-\begin{comment}
-
 \begin{table}[htbp]
@@
 
-%\textbf{/AlCaLumiPixels/Run2018A-AlCaPCCRandom15Apr2023\_UL2018\_315252\_316062\_PCCRandom\_-v1/ALCARECO}
-
-\textbf{\url{/AlCaLumiPixels/Run2018A-AlCaPCCRandom15Apr2023_UL2018_315252_316062_PCCRandom_-v1/ALCARECO}}
-%\textbf{/AlCaLumiPixels/Run2018A-AlCaPCCRandom15Apr2023_UL2018_315252_316062_PCCRandom_-v1/ALCARECO}
-
-\begin{itemize}
-
-\item /AlCaLumiPixels/Run2018A: This indicates that the dataset is related to the "AlCa" (ALignment and CALibration) stream, specifically for the "LumiPixels" subdetector.
-The data corresponds to the Run2018A period, which means it was collected during the first run period in 2018.
-
-\item AlCaPCCRandom: This tag represents the primary dataset and the trigger path used to collect the data.
-"PCC" stands for "Pixel Cluster Counting" and is a method for luminosity measurement.
-"Random" indicates that this dataset was collected using a random trigger, which is a method to sample a fraction of the events by applying trigger on both colliding and non-colliding bunch crossings.
-
-\item $15Apr2023\_UL2018\_315252\_316062\_PCCRandom\_-v1$: This part represents the processing version, date, and run range of the dataset.
-"15Apr2023" is the date when this specific version of the dataset was created.
-"UL2018" indicates that this data has been processed using the "Ultra Legacy" (UL) campaign for the 2018 dataset, which aims to provide the highest quality data for physics analysis.
-The numbers $"315252_316062"$ represent the range of run numbers included in the dataset.
-$"PCCRandom_"$ is a reference to the Pixel Cluster Counting method used for luminosity measurement and the random trigger.
-"v1" denotes the version number of this processed dataset.
-
-\item ALCARECO:
-This acronym stands for "ALignment and CALibration RECOstruction." It is a data tier representing the output of specific reconstruction algorithms applied to the raw data to produce high-level objects needed for the alignment and calibration tasks.
-
-\end{itemize}
-
-%To summarize, this dataset is a collection of events from the CMS experiment during the Run2018A period, sampled using a random trigger.
-It is specifically related to the luminosity measurement using the Pixel Cluster Counting method.
-The dataset has been processed using the Ultra Legacy campaign, and the output contains high-level objects required for alignment and calibration tasks.
-
-%$\textbf{/StreamALCALUMIPIXELSEXPRESS/Run2018A-AlCaPCCRandom-Express-v1/ALCARECO}$
-
-\textbf{\url{/StreamALCALUMIPIXELSEXPRESS/Run2018A-AlCaPCCRandom-Express-v1/ALCARECO}}
-
-\begin{itemize}
-
-\item /StreamALCALUMIPIXELSEXPRESS/Run2018A:
-This indicates that the dataset is related to the "AlCa" (ALignment and CALibration) stream, specifically for the "LumiPixels" subdetector, and is part of the "Express" data processing tier.
-The data corresponds to the Run2018A period, which means it was collected during the first run period in 2018.
-
-\item AlCaPCCRandom:
-This tag represents the primary dataset and the trigger path used to collect the data.
-"PCC" stands for "Pixel Cluster Counting" and is a method for luminosity measurement.
-"Random" indicates that this dataset was collected using a random trigger, which is a method to sample a fraction of the events without specific selection criteria (i.e., unbiased events).
-
-\item Express-v1:
-This part represents the processing version and the type of data processing.
-"Express" indicates that this data has been processed using the "Express" campaign, which is a near-real-time processing of the data as it is collected.
-This type of processing is essential for providing timely feedback to the experiments and enabling rapid identification of any issues.
-"v1" denotes the version number of this processed dataset.
-
-\item ALCARECO:
-This acronym stands for "ALignment and CALibration RECOstruction." It is a data tier representing the output of specific reconstruction algorithms applied to the raw data to produce high-level objects needed for the alignment and calibration tasks.
-
-\end{itemize}
-
-%In summary, this dataset is a collection of events from the CMS experiment during the Run2018A period, sampled using a random trigger.
-It is specifically related to the luminosity measurement using the Pixel Cluster Counting method.
-The dataset has been processed using the Express campaign, and the output contains high-level objects required for alignment and calibration tasks.
-
-%$\textbf{/AlCaLumiPixels/Run2018A-AlCaPCCZeroBias-13Mar2023_UL2018_PCC-v1/ALCARECO}$
-
-%$\textbf{/AlCaLumiPixels/Run2018A-AlCaPCCZeroBias-13Mar2023\_UL2018\_PCC-v1/ALCARECO}$
-
-\textbf{\url{/AlCaLumiPixels/Run2018A-AlCaPCCZeroBias-13Mar2023_UL2018_PCC-v1/ALCARECO}}
-
-\begin{itemize}
-
-\item /AlCaLumiPixels/Run2018A:
-This indicates that the dataset is related to the "AlCa" (ALignment and CALibration) stream, specifically for the "LumiPixels" subdetector.
-The data corresponds to the Run2018A period, which means it was collected during the first run period in 2018.
-
-\item AlCaPCCZeroBias:
-This tag represents the primary dataset and the trigger path used to collect the data.
-"PCC" stands for "Pixel Cluster Counting" and is a method for luminosity measurement.
-"ZeroBias" indicates that this dataset was collected using a trigger with no specific selection criteria (i.e., unbiased events).
-
-\item $13Mar2023_UL2018_PCC-v1$:
-This part represents the processing version and the date of the dataset.
-"13Mar2023" is the date when this specific version of the dataset was created.
-"UL2018" indicates that this data has been processed using the "Ultra Legacy" (UL) campaign for the 2018 dataset, which aims to provide the highest quality data for physics analysis.
-"PCC" is again a reference to the Pixel Cluster Counting method used for luminosity measurement.
-"v1" denotes the version number of this processed dataset.
-
-\item ALCARECO:
-This acronym stands for "ALignment and CALibration RECOstruction." It is a data tier representing the output of specific reconstruction algorithms applied to the raw data to produce high-level objects needed for the alignment and calibration tasks.
-
-\end{itemize}
-
-%So, to summarize, this dataset is a collection of unbiased events from the CMS experiment during the Run2018A period.
-It is specifically related to the luminosity measurement using the Pixel Cluster Counting method.
-The dataset has been processed using the Ultra Legacy campaign, and the output contains high-level objects required for alignment and calibration tasks.
-
-%$\textbf{/AlCaLumiPixels/Run2018D-AlCaPCCZeroBias-PromptReco-v2/ALCARECO}$
-
 \begin{comment}
 
-\textbf{\url{/AlCaLumiPixels/Run2018D-AlCaPCCZeroBias-PromptReco-v2/ALCARECO}}
-
-\begin{itemize}
-
-\item /AlCaLumiPixels/Run2018D:
-This indicates that the dataset is related to the "AlCa" (ALignment and CALibration) stream, specifically for the "LumiPixels" subdetector.
-The data corresponds to the Run2018D period, which means it was collected during the fourth run period in 2018.
-
-\item AlCaPCCZeroBias:
-This tag represents the primary dataset and the trigger path used to collect the data.
-"PCC" stands for "Pixel Cluster Counting" and is a method for luminosity measurement.
-"ZeroBias" indicates that this dataset was collected using a trigger with no specific selection criteria (i.e., unbiased events).
-
-\item PromptReco-v2:
-This part represents the processing version and the type of data processing.
-"PromptReco" indicates that this data has been processed using the "Prompt Reconstruction" campaign, which is a near-real-time processing of the data as it is collected.
-This type of processing is essential for providing timely feedback to the experiments and enabling rapid identification of any issues.
-"v2" denotes the version number of this processed dataset.
-
-\item ALCARECO:
-This acronym stands for "ALignment and CALibration RECOstruction." It is a data tier representing the output of specific reconstruction algorithms applied to the raw data to produce high-level objects needed for the alignment and calibration tasks.
-
-\end{itemize}
+The calibration of luminosity measurement by the CMS experiment luminometers in the 2018 proton-proton data taking at $\sqrt{s}$ = 13 TeV \cite{CMS-PAS-LUM-18-002} was performed during LHC fill 6868 on June 30 and July 1, 2018 at $\sqrt{s}$ = 13 TeV.
+Zero-bias triggers on 5 bunch pairs (BCIDs 265, 865, 1780, 2192, and 3380) recorded events rate is 27.7 kHz.
+Trigger is applied on five colliding bunches due to limitation of the recording bandwidth.
+
+%\item "lsc1", was the "constant separation" scan, two beams were separated by 1.4 $\sigma$ and moved together in steps of 1 $\sigma$ across and back.
+%\item "lsc2", was the "variable separation" scan method, one beam (starting with beam 1) is moved to -2.5 $\sigma$ and then a three-point scan (a "miniscan") is performed with the other beam.
+%a normal VdM scan pair "norm4" and two short emittance scan pairs "emit4" and "emit5" were also performed.
+
+%The 2018 CMS VdM scan program was conducted in two segments, interrupted by an alarm.
+The first segment involved six x-y scan pairs.
+Two were short ``emittance'' scans, named ``emit1'' and ``emit2,'' where the beams were separated by $ \(4\sigma_b\) $ over 9 steps with a 10 second integration time at each step.
+A standard VdM scan, named ``norm1,'' separated the beams by $\(6\sigma_b \approx 600\)~\mu m$ in 25 steps, with a 30-second duration per step.
+The ``offset1'' scan followed the same procedure as the standard scans but with a $\(\pm 1.5\sigma_b\)$ separation in the non-scanning direction.
+Lastly, two sets of ``beam imaging'' scans were conducted, where one beam remained fixed while the other was moved in 19 steps between $\(+4.5\sigma_b\)$ and $\(-4.5\sigma_b\)$, each lasting 46 seconds per step.
+
+The 2018 CMS VdM scan program (shown in Fig.
+\ref{fig:vdm_prog_2018}) was conducted in two segments, interrupted by an alarm.
+The first segment involved six x-y scan pairs.
+Two were short ``emittance'' scans, named ``emit1'' and ``emit2,'' where the beams were separated by \(4\sigma_b\) over 9 steps with a 10-second integration time at each step.
+A standard vdM scan (described in section 3.1), named ``norm1,'' separated the beams by \(6\sigma_b \approx 600\)~$\mu$m in 25 steps, with a 30-second duration per step.
+The ``offset1'' scan followed the same procedure as the standard scans but with a \(\pm 1.5\sigma_b\) separation in the non-scanning direction.
+Lastly, two sets of ``beam imaging'' scans were conducted, where one beam remained fixed while the other was moved in 19 steps between \(+4.5\sigma_b\) and \(-4.5\sigma_b\), each lasting 46 seconds per step.
+The second part of the scan program was conducted in the same fill, approximately 7.5 hours later, and consisted of twelve scan pairs.
+This included a short emittance scan, ``emit3''; beam imaging scan pairs, ``imag2'' and ``imag3''; an offset scan pair, ``offset2''; and two standard VdM scan pairs, ``norm2'' and ``norm3''.
+
+Beam Imaging Scans: Beam imaging scans are designed to measure the transverse profile of the beam.
+They involve moving one beam across the other in steps and measuring the interaction rate (or event rate) at each step.
+By doing this, the shape or "profile" of the beam in the transverse plane can be obtained.
+These scans allow for a detailed analysis of the beam shape, which is essential for understanding the beam properties.
+In a perfect scenario, the density distributions of protons in a bunch would factorize into separate X (horizontal) and Y (vertical) components.
+However, real beams can have correlations between X and Y (non-factorization).
+Beam imaging scans help map the 2D profile of the beam and are thus essential for diagnosing and understanding any such correlations.
+Knowing the 2D profile of the beams is crucial when calculating luminosity, as assumptions made about the factorization of the beam profiles feed into these calculations.
+By using beam imaging scans, experimenters can assess the validity of the factorization assumption or correct for any observed non-factorization.
+
+Offset Scans: Offset scans are performed to check for systematic errors in the luminosity measurement, which may arise from various sources.
+They are similar to standard VdM scans but involve an intentional offset in the non-scanning direction.
+By comparing the results of offset scans with the results of regular scans, one can identify and correct for any systematic discrepancies that are present.
+Offset scans can help to assess the sensitivity of the luminosity measurement to non-factorization in the transverse plane.
+For example, if there are correlations between the X and Y distributions of protons (i.e., non-factorization), this could in principle affect the shape of the beam overlap region in the collision point.
+Offset scans, by changing the relative position of the beams, can help to assess whether such non-factorization has a significant effect on the measured luminosity.
+
+%The second part of the scan program was conducted in the same fill, approximately 7.5 hours later, and consisted of twelve scan pairs.
+This included a short emittance scan, ``emit3''; beam imaging scan pairs, ``imag2'' and ``imag3''; an offset scan pair, ``offset2''; and two standard VdM scan pairs, ``norm2'' and ``norm3''.
+
+vdM scans are typically conducted at least once a year to ensure the luminometer is correctly calibrated.
+Results of these scans that is the visible cross section is used to normalize the data collected by the experiments during physics run.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1\textwidth]{ashish_thesis/vdm_program_2018.png}
+    \caption[2018 vdM program]{Beam position along x and y is plotted as a function of time showing different types of scans.
+#3 and #10 are vdM scans, #4 and #9 are offset scans, #5, #7 and #8 are beam imaging scans, #6 is emittance scan.
+}
+    \label{fig:vdm_prog_2018}
+\end{figure}
 
@@
 
-%In summary, this dataset is a collection of unbiased events from the CMS experiment during the Run2018D period, specifically related to the luminosity measurement using the Pixel Cluster Counting method.
-The dataset has been processed using the Prompt Reconstruction campaign, and the output contains high-level objects required for alignment and calibration tasks.
-
-\begin{comment}
-
-The dataset /StreamALCALUMIPIXELSEXPRESS/Run2018A-AlCaPCCRandom-Express-v1/ALCARECO, is a dataset from the CMS experiment at CERN's Large Hadron Collider (LHC).
-This dataset is specifically collected for luminosity measurements using pixel cluster counting (PCC) in the CMS detector by applying trigger on colliding and non-colliding bunches.
-
-\begin{itemize}
-
-\item StreamALCALUMIPIXELSEXPRESS: This indicates that the dataset is related to the "AlCa" (Alignment and Calibration) sub-system of the CMS detector, specifically focused on luminosity measurements using the pixel detector.
-The "EXPRESS" in the name signifies that this dataset is processed using the Express Stream, which is a fast data processing system for near real-time analysis of CMS data.
-
-\item Run2018A: This represents the run period during which the data was collected. In this case, it refers to the 2018 data-taking period, specifically the "A" run.
-
-\item AlCaPCCRandom: This indicates that the dataset is related to the "PCC" (Pixel Cluster Counting) method of luminosity measurement, and "Random" refers to the trigger used for data collection.
-In this case, a random trigger is used, selecting events without any specific bias.
-
-\item Express-v1: This signifies that the dataset has been processed using the Express Stream system. The "-v1" indicates the version of the processing.
-
-\item ALCARECO: This is the final data format of the dataset, specifically designed for alignment and calibration tasks.
-
-%\item Data collection: The CMS detector collects data from proton-proton collisions at the LHC.
-For this dataset, a random trigger is used , ensuring a representative sample of events for luminosity measurements.
-
-%\item Data processing: The raw data is processed using the Express Stream system.
-This is a fast processing system used for near real-time analysis of CMS data.
-During this process, the raw data is converted into higher-level objects, such as tracks and vertices, which are more convenient for analysis.
-
-%\item Data filtering: ALCARECO datasets are created by applying specific filters and selections to the processed data.
-In this case, the filters are chosen to focus on pixel cluster counting for luminosity measurements.
-
-%\item Dataset storage: The final ALCARECO dataset is stored and made available for analysis by researchers working on alignment, calibration, and luminosity-related studies.
-
-\end{itemize}
-
- The dataset /AlCaLumiPixels/Run2018D-AlCaPCCZeroBias-PromptReco-v2/ALCARECO, is specifically collected for luminosity measurements using pixel cluster counting (PCC) in the CMS detector by applying trigger on only colliding bunches.
-
-\begin{itemize}
-
-\item AlCaLumiPixels: This indicates that the dataset is related to the "AlCa" (Alignment and Calibration) sub-system of the CMS detector, specifically focused on luminosity measurements using the pixel detector.
-
-\item Run2018A: This represents the run period during which the data was collected. In this case, it refers to the 2018 data-taking period, specifically the "A" run.
-
-\item AlCaPCCZeroBias: This indicates that the dataset is related to the "PCC" (Pixel Cluster Counting) method of luminosity measurement, and "ZeroBias" refers to the trigger used for data collection.
-ZeroBias triggers are unbiased, meaning they are randomly triggered and do not rely on any specific event characteristics.
-
-\item PromptReco-v2: This signifies that the dataset has been processed using the "PromptReco" (Prompt Reconstruction) system, which is a fast processing system for real-time analysis of CMS data.
-The "-v2" indicates the version of the processing.
-
-\item ALCARECO: This is the final data format of the dataset, specifically designed for alignment and calibration tasks.
-
-%\item Data collection: The CMS detector collects data from proton-proton collisions at the LHC.
-For this dataset, the ZeroBias trigger is used, ensuring an unbiased sample of events for luminosity measurements.
-
-%\item Data processing: The raw data is processed using the Prompt Reconstruction system.
-During this process, the raw data is converted into higher-level objects, such as tracks and vertices, which are more convenient for analysis.
-
-%\item Data filtering: ALCARECO datasets are created by applying specific filters and selections to the processed data.
-In this case, the filters are chosen to focus on pixel cluster counting for luminosity measurements.
-
-%\item Dataset storage: The final ALCARECO dataset is stored and made available for analysis by researchers working on alignment, calibration, and luminosity-related studies.
-
-\end{itemize}
-
-The dataset "AlCaLumiPixels/Run2018D-AlCaPCCZeroBias-PromptReco-v2/ALCARECO" dataset is a specialized dataset that provides information related to luminosity measurements using pixel detectors.
-
-\begin{itemize}
-
-\item AlCaLumiPixels: The term "AlCaLumiPixels" indicates that the dataset focuses on luminosity measurements obtained from the pixel detectors.
-The pixel detectors are part of the CMS experiment's innermost layers and are designed to precisely track the paths of charged particles produced in proton-proton collisions.
-
-\item Run2018D: The "Run2018D" refers to a specific data-taking period or run period of the CMS experiment.
-The LHC operates in cycles of data-taking known as runs, which are typically identified by a year and a letter.
-In this case, "2018D" corresponds to a particular period of data collection in 2018.
-
-\item AlCaPCCZeroBias: "AlCaPCCZeroBias" is a term that likely indicates the specific algorithm and event type used for luminosity measurement.
-The "PCC" stands for "Pixel Cluster Counting," which is an algorithm employed to estimate the instantaneous luminosity based on the information recorded by the pixel detectors.
-The "ZeroBias" events represent a special category of collisions where all the CMS detector systems trigger, regardless of the specific physics processes involved.
-These events are particularly useful for luminosity measurements.
-
-\item PromptReco-v2: "PromptReco" refers to the reconstruction process for the prompt data.
-Prompt reconstruction involves the real-time processing and calibration of the recorded data immediately after it is taken.
-The "-v2" indicates a specific version or iteration of the prompt reconstruction process.
-
-\item ALCARECO: "ALCARECO" stands for "ALignment CALibration RECOnditioned" data.
-It is a category of specialized reconstructed datasets produced with specific requirements for alignment and calibration studies.
-These datasets are carefully processed and conditioned to ensure accurate alignment of the CMS detector elements and precise calibration of the recorded data.
-
-\end{itemize}
-
-PromptReco (Prompt Reconstruction) and AlCaReco (ALignment and CALibration REConstructed Objects) are two different data processing and formatting systems used in the CMS experiment at CERN's Large Hadron Collider (LHC).
-While both systems are related to the processing of data collected by the CMS detector, they serve different purposes and have distinct features.
-Here is a comparison of the two systems:
-
-Purpose: \\ 
-PromptReco: The primary goal of the PromptReco system is to rapidly convert the raw data collected by the CMS detector into a format more suitable for physics analysis.
-It reconstructs the raw data into higher-level objects like tracks, vertices, and calorimeter clusters, which are then used by researchers to study various aspects of the particle collisions.
-
-AlCaReco: The main purpose of the AlCaReco system is to provide specialized datasets for detector alignment, calibration, and other related tasks.
-AlCaReco datasets are generated by applying specific filters and selections to the reconstructed data (RECO), focusing on events and information that are particularly useful for alignment, calibration, and performance monitoring.
-
-Data format: \\
-PromptReco: The output of the PromptReco system is the RECO (REConstructed Objects) data format.
-This is the primary data format used for physics analysis in the CMS experiment, containing reconstructed objects such as tracks, vertices, and calorimeter clusters.
-
-AlCaReco: The AlCaReco data format is designed specifically for alignment, calibration, and performance monitoring tasks.
-It is a more focused and compact data format, containing only the events and information relevant to the specific task, resulting in reduced data volume compared to the full RECO data.
-
-Data processing:\\
-PromptReco: The PromptReco system processes the raw data at Tier-0 of the Worldwide LHC Computing Grid (WLCG), using a series of algorithms to reconstruct the detector information into higher-level physics objects.
-
-AlCaReco: The AlCaReco processing stream is applied after the PromptReco system, using the reconstructed data (RECO) as input.
-AlCaReco datasets are generated by applying specific filters and selections tailored to the needs of the alignment, calibration, and performance monitoring tasks.
-
-%The main difference between PromptReco and AlCaReco is their purpose and the type of data they produce.
-PromptReco is focused on the rapid reconstruction of raw data into a format suitable for physics analysis, while AlCaReco is designed to provide specialized datasets for detector alignment, calibration, and performance monitoring tasks.
-Both systems play a crucial role in the overall data processing and analysis pipeline of the CMS experiment.
-
-%AlCaReco stands for "ALignment and CALibration REConstructed Objects." It is a specific data format and processing stream used by the CMS experiment at CERN's Large Hadron Collider (LHC) for the purpose of detector alignment, calibration, and other specialized tasks.
-AlCaReco datasets are designed to be smaller and more focused compared to the primary reconstructed data (RECO), making them suitable for specialized analyses that require a specific set of event characteristics or detector information.
-The AlCaReco data format and processing stream serve several important functions: Customized event selection: AlCaReco datasets are generated by applying specific filters and selections to the reconstructed data (RECO).
-These filters are tailored to select events that are particularly useful for alignment, calibration, and other specialized tasks.
-For example, certain triggers or event topologies might be more suitable for studying the performance of a specific detector subsystem or measuring certain quantities.
-By selecting events with these specific characteristics, the AlCaReco datasets provide a more focused sample for the targeted analyses.
-Reduced data volume: One of the main advantages of AlCaReco datasets is their reduced data volume compared to the full RECO data.
-By selecting only the events and information relevant to the specific task, the AlCaReco data format helps save storage space and computational resources, making the data processing and analysis more efficient.
-Detector performance monitoring: AlCaReco datasets are used to monitor the performance of the CMS detector and its subsystems.
-By analyzing the data in these specialized datasets, researchers can track the detector's performance over time and identify any potential issues or areas for improvement.
-This information can then be used to optimize the detector's operation and ensure accurate data collection.
-Alignment and calibration: Accurate detector alignment and calibration are crucial for the overall performance of the CMS experiment.
-AlCaReco datasets provide the necessary information to perform these tasks, allowing researchers to refine the detector's geometry, timing, and energy response.
-This, in turn, improves the quality of the data collected by the CMS detector and increases the accuracy of the physics analyses.
-In summary, AlCaReco is a specialized data format and processing stream used by the CMS experiment for tasks related to detector alignment, calibration, and performance monitoring.
-By providing focused datasets with reduced data volume, AlCaReco enables efficient and accurate analysis of the data needed to maintain and optimize the performance of the CMS detector.
-AlCaReco: The main purpose of the AlCaReco system is to provide specialized datasets for detector alignment, calibration, and other related tasks.
-AlCaReco datasets are generated by applying specific filters and selections to the reconstructed data (RECO), focusing on events and information that are particularly useful for alignment, calibration, and performance monitoring.
-AlCaReco: The AlCaReco data format is designed specifically for alignment, calibration, and performance monitoring tasks.
-It is a more focused and compact data format, containing only the events and information relevant to the specific task, resulting in reduced data volume compared to the full RECO data.
-AlCaReco: The AlCaReco processing stream is applied after the PromptReco system, using the reconstructed data (RECO) as input.
-AlCaReco datasets are generated by applying specific filters and selections tailored to the needs of the alignment, calibration, and performance monitoring tasks.
-
-\end{comment}
-
-The calibration of luminosity measurement by the CMS experiment luminometers in the 2018 proton-proton data taking at $\sqrt{s}$ = 13 TeV \cite{CMS-PAS-LUM-18-002} was performed during
-
-\begin{itemize}
-\item LHC fill 6868 on June 30 and July 1, 2018 at $\sqrt{s}$ = 13 TeV
-\item Zero-bias triggers on 5 bunch pairs (BCIDs 265, 865, 1780, 2192, and 3380)
-recorded events rate is 27.7 kHz. 
-\item "lsc1", was the "constant separation" scan, two beams were separated by 1.4 $\sigma$ and moved together in steps of 1 $\sigma$ across and back.
-\item "lsc2", was the "variable separation" scan method, one beam (starting with beam 1) is moved to -2.5 $\sigma$ and then a three-point scan (a "miniscan") is performed with the other beam.
-\item a normal VdM scan pair "norm4" and two short emittance scan pairs "emit4" and "emit5" were also performed.
-\end{itemize}
-
-To measure the luminosity using the pixel detector, pixel cluster count is studied for each module, where a module consists of a number of pixels arranged in a grid.
+%In order to measure luminosity using a pixel detector, the count of pixel clusters is studied for each module, with each module being composed of numerous pixels arranged in a grid.
+The number of pixel clusters recorded per unit time in each module is proportional to the instantaneous luminosity of the collider.
+The Pixel Cluster Counting (PCC) method is implemented by operating the pixel detector in an integrated mode.
+The Pixel detector is read out at a fixed interval termed a "lumi section", each lasting for 23.36 seconds.
+
+The pixel detector records data for each bunch-crossing, though the readout rate is constrained by the trigger.
+During subsequent data processing,  these events are consolidated into lumi sections.
+During each lumi section, the number of pixel clusters produced in each module is recorded and the module weights for all pixel modules are studied to track their performance over time.
+This helps in identifying good and bad modules, as shown in Fig.
+\ref{fig:goodbadmodules}.
+Only pixel modules that demonstrate consistent and reliable performance throughout the entire 2018 year are considered good and included in the analysis.
+The pixel cluster rate, along with the visible cross section of the detector, is used to determine the instantaneous luminosity of the collider.
+PCC data is subsequently reprocessed.
+This involves the re-analysis of the data using updated or refined algorithms, calibrations, and detector conditions.
+
+%To measure the luminosity using the pixel detector, pixel cluster count is studied for each module, where a module consists of a number of pixels arranged in a grid.
 The number of pixel clusters recorded in each module per unit time is proportional to the instantaneous luminosity of the collider.
@@
 
-\newpage
 The purpose of reprocessing can be multifold:
@@
 This can lead to a more accurate or efficient representation of the collected data.
-Reprocessing allows these improvements to be applied to previously collected data.
-
-\item Changes in Detector Conditions: Detector conditions might change over time due to factors like aging or upgrades.
-These changes can affect the interpretation of the data.
-By reprocessing, the data can be reinterpreted to account for these changes.
-
-\item Discovery of Issues or Errors: Sometimes, errors or issues in the original data processing might be discovered. Reprocessing the data allows these errors to be corrected.
+
+\item Changes in Detector Conditions: Detector conditions might change over time due to factors like aging or upgrades. These changes can affect the interpretation of the data.
+
+\item Discovery of Issues or Errors: Sometimes, errors or issues in the original data processing might be discovered.
 
@@
 In the context of PCC data, reprocessing can lead to a more accurate luminosity measurement, which in turn can affect the interpretation of the physics results derived from the LHC data.
-The luminosity measurement is crucial because it is directly linked to the determination of cross-sections, a fundamental quantity in the interpretation of the outcomes of high-energy particle physics experiments.
-
-CMS software (CMSSW) version $10{\_}2{\_}2$ is used for reprocessing random trigger PCC dataset and $10{\_}6{\_}30$  \cite{CMSReleaseNotes} is used for reprocessing zero bias PCC datasets.
-Datasets can be obtained by applying triggers on all bunches (colliding and non colliding) and only on colliding bunches to get random trigger and zero bias data respectively as described in previous section.
-Random trigger PCC dataset is reprocessed with new module vetolist to obtain afterglow corrections with improved module stability selections.
-Zero bias dataset is reprocessed after applying afterglow corrections using same module vetolist with more stringent selections on module stability to obtain PCC luminosity.
-
+Random trigger PCC dataset is reprocessed with new module veto list (described in section 4.2) to obtain afterglow corrections with improved module stability selections.
+Zero-bias dataset is reprocessed after applying afterglow corrections using same module veto list with more stringent selections on module stability to obtain PCC luminosity.
+
+%CMS software (CMSSW) version $10{\_}2{\_}2$ is used for reprocessing random trigger PCC dataset and $10{\_}6{\_}30$  \cite{CMSReleaseNotes} is used for reprocessing zero bias PCC datasets.
+%Datasets can be obtained by applying triggers on all bunches (colliding and non colliding) and only on colliding bunches to get random trigger and zero bias data respectively as described in previous section.
+%Random trigger PCC dataset is reprocessed with new module veto list (described in section 4.2) to obtain afterglow corrections with improved module stability selections.
+Zero-bias dataset is reprocessed after applying afterglow corrections using same module veto list with more stringent selections on module stability to obtain PCC luminosity.
 %To ensure accurate luminosity measurements, it is necessary to correct for various effects, such as detector inefficiencies and pileup (the presence of additional proton-proton collisions in the same bunch crossing).
@@
 \end{table}
-
-\end{comment}
 
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.8\textwidth]{ashish_thesis/pixel_layer_disk_noveto.png}
-\caption{%                                                                                                                                                                
-   Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
-}
-\label{fig:PCC_stab_begin}
-\end{figure}
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=0.8\textwidth]{ashish_thesis/pixel_layer_disk_noveto.png}
+%\caption{%                                                                                                                                                                
+ %  Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
+%}
+%\label{fig:PCC_stab_begin}
+%\end{figure}
 
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.8\textwidth]{ashish_thesis/pixel_layer_disk_B0_veto.png}
-\caption{%                                                                                                                                                                           
-   Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section.
-}
-\label{fig:PCC_stab_L0_veto}
-\end{figure}
-
-\section{Module Selection}
-
-The goal of minimizing instabilities in PCC (Pixel Cluster Counting) luminosity measurement is to ensure accurate and consistent results.
-To achieve this, a pixel module vetolist is created for each run period to keep track of good and bad modules.
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=0.8\textwidth]{ashish_thesis/pixel_layer_disk_B0_veto.png}
+%\caption{%                                                                                                                                                                           
+ %  Luminosity fraction of pixel detector for various layer and disks as a function of lumi section after removing low statistics lumi section and all modules in Layer 1.
+%}
+%\label{fig:PCC_stab_L0_veto}
+%\end{figure}
+
+\end{comment}
+
+\section{Detector module selection}
+
+The goal of minimizing instabilities in PCC luminosity measurement is to ensure precise and consistent results.
+To achieve this, a pixel module veto list is created for each period to keep track of  bad modules.
 The stability of each module is determined based on the change in the ratio of module PCC and total PCC, referred to as the module weight as shown in Fig.
@@
 
-\begin{itemize}
-
-\item Lumi section duration: The data collected for luminosity measurements are divided into lumi sections, each lasting for 23.36 seconds.
-
-\item Analyzing module weights: During each lumi section, the module weights for all pixel modules are studied to track their performance over time.
+%\begin{itemize}
+
+%\item Lumi section duration: The data collected for luminosity measurements are divided into lumi sections, each lasting for 23.36 seconds.
+
+%\item Analyzing module weights: During each lumi section, the module weights for all pixel modules are studied to track their performance over time.
 This helps in identifying good and bad modules, as shown in Fig.
@@
 
-\item Pixel detector composition: The pixel detector used for the 2018 luminosity measurement comprises two main components - the BPIX (barrel pixel detector) with 4 barrel layers, and the FPIX (forward pixel detector) with three forward disks.
+%\item Pixel detector composition: The pixel detector used for the 2018 luminosity measurement comprises two main components - the BPIX (barrel pixel detector) with 4 barrel layers, and the FPIX (forward pixel detector) with three forward disks.
 These two components consist of 1184 and 672 pixel modules, respectively.
 
-\item Selection criteria: Only pixel modules that demonstrate consistent and reliable performance throughout the entire 2018 year are considered good and included in the analysis.
-Modules that do not meet these criteria are classified as bad and excluded from the luminosity measurement.
-
-\end{itemize}
+%\item Selection criteria: Only pixel modules that demonstrate consistent and reliable performance throughout the entire 2018 year are considered good and included in the analysis.
+%Modules that do not meet these criteria are classified as bad and excluded from the luminosity measurement.
+
+%\end{itemize}
 
@@
 \centering
-\includegraphics[width=1\textwidth]{ashish_thesis/Module_weight.png}
-\caption[Steps involved to obtain module weights]{%
+\includegraphics[width=1\textwidth]{ashish_thesis/Module_weight_2.png}
+\caption[Module Weight]{%
    Method to obtain module weights as a function of lumi section for categorizing good and bad modules.
@@
 \centering
-\includegraphics[width=1\textwidth]{ashish_thesis/good_bad_modules.png}
-\caption[Good and bad module weights]{%
+\includegraphics[width=1\textwidth]{ashish_thesis/good_bad_modules_1.png}
+\caption[Good/Bad Module Weights]{%
    Change in normalized module weight with time. Modules showing significant change in module weight (shown in right figure) over time having large RMS/mean values are used to make module veto list.
@@
 
-\newpage
 The module veto list is a list of detector modules that are excluded from the analysis of data due to their known or suspected high rate of background events or other issues that could affect the accuracy of the measurement.
-The inclusion of certain modules in the veto list is based on various factors, including:
+The following factors lead to unstable modules:
 
@@
 
-The inclusion of certain modules in the veto list is based on a careful analysis of the detector performance and the expected background rates in a given experiment.
+%The inclusion of certain modules in the veto list is based on a careful analysis of the detector performance and the expected background rates in a given experiment.
 By excluding modules with high background rates or other issues, the analysis can be improved and the accuracy of the measurement can be increased.
@@
 
-\item Poor statistics lumi sections are removed by applying selection on total PCC Fig. \ref{fig:PCC_cut}. % and \ref{fig:f_it}.
+\item Poor statistics lumi sections are removed by applying selection on total PCC. %Fig. \ref{fig:PCC_cut}. % and \ref{fig:f_it}.
 
@@
 
-\item A loose selection of 7\% based on RMS/mean of module weight profile is applied where mean and rms values are obtained from y projection of module weight profile.
+\item A loose selection of 7\% based on RMS/mean of module weight profile is applied where mean and RMS values are obtained from y projection of module weight profile.
 Modules with significantly large RMS/mean are removed with this loose selection as shown in Fig.
@@
 
-\item Module stability is re-evaluated based on RMS/mean values using an iterative method where in each step, appropriate selections are applied to remove bad modules until stable luminosity is attained as sshown in Fig.
-\ref{fig:sec_it_cut}.
+\item Module stability is re-evaluated based on RMS/mean values using an iterative method where in each step, appropriate selections are applied to remove bad modules (shown in Fig.
+\ref{fig:sec_it_cut}) until stable luminosity is attained.
 \end{itemize}
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/Run2018B_totalPCC_cut.png}
-\caption[Selection to remove low statistics lumi sections]{%
- Total PCC as a function of lumi section for period 2018B.  Appropriate selection on total PCC shown by the red line is applied to remove low statistics lumi sections.
-}
-\label{fig:PCC_cut}
-\end{figure}
+%\begin{figure}[t]
+%\centering
+%\includegraphics[width=0.7\textwidth]{ashish_thesis/Run2018B_totalPCC_cut.png}
+%\caption[Low Statistics Lumi section Filtering]{%
+% Total PCC as a function of lumi section for period 2018B. Appropriate selection on total PCC shown by the red line is applied to remove low statistics lumi sections.
+%}
+%\label{fig:PCC_cut}
+%\end{figure}
 
@@
 \centering
-\includegraphics[width=1\textwidth]{ashish_thesis/cut_selection.png}
-\caption[First iteration to remove outlier modules]{%
-   RMS/mean of module weight profile for all modules. A loose selection of 7\% is applied to remove bad modules. Appropriate selections are applied in each iterative step to remove other bad modules.
+\includegraphics[width=0.8\textwidth]{ashish_thesis/cut_selection_1.png}
+\caption[First Iteration For Outlier Module Removal]{%
+   A loose selection of 7\% is applied to remove bad modules. Appropriate selections are applied in each iterative step to remove other bad modules.
 }
@@
     \centering
-\includegraphics[width=1\textwidth]{ashish_thesis/second_iteration_cut.png}
-\caption[Final iteration to remove outlier modules]{%
+    %\begin{minipage}{0.45\textwidth}
+        \centering
+        \includegraphics[width=1.0\linewidth]{ashish_thesis/3percent_cut_1.png}
+    %\end{minipage}
+    %\hfill
+    %\begin{minipage}{0.45\textwidth}
+     %   \centering
+      %  \includegraphics[width=1.0\linewidth]{ashish_thesis/second_iteration_cut.png}
+    %\end{minipage}
+
+    \caption[Second and Final Iteration For Outlier Module Removal]{%
+        Left: Second iteration on RMS/mean of 3\% is applied to remove more bad modules. 
+        Right: Final iteration on RMS/mean of 2\% is applied to obtain module veto list for each period.
+    }
+    \label{fig:sec_it_cut}
+\end{figure}
+
+\begin{comment}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.6\textwidth]{ashish_thesis/3percent_cut.png}
+\caption[Second Iteration For Outlier Module Removal]{%
+ Second selection on RMS/mean of 3\% is applied to obtain module veto list for each period.
+}
+\label{fig:second_it_cut}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.6\textwidth]{ashish_thesis/second_iteration_cut.png}
+\caption[Final Iteration For Outlier Module Removal]{%
  Final selection on RMS/mean of 2\% is applied to obtain module veto list for each period.
@@
 
+\end{comment}
+
 %\begin{figure}[!htp]
@@
 \centering
-\includegraphics[width=1\textwidth]{ashish_thesis/mod_weight_comp_1.png}
-\caption[Selection to remove modules due to change in module weights across period]{%
+\includegraphics[width=0.7\textwidth]{ashish_thesis/mod_weight_comp_2.png}
+\caption[Module Weights Change Removal]{%
    Projection of change in module weights between period A and B. Modules showing more than 3 sigma change in module weights are added to the module veto list.
@@
 
- 2\% selection on RMS/mean of module weight profile gives the best stability for all pixel detector barrel layers and forward disks.
-Bad modules found after applying this 2\% selection in the final iterative step are used to constitute a 2 $\%$ rms module veto list for each period as shown in Table \ref{tab:per period veto}.
+ 2\% selection on RMS/mean of module weights gives the best stability for all pixel detector barrel layers and forward disks.
+Number of good and bad modules after this selection is shown in Table \ref{tab:per period veto}.
+% Bad modules found after applying this 2\% selection in the final iterative step are used to constitute a 2 $\%$ rms module veto list for each period as shown in Table \ref{tab:per period veto}.
 
@@
    \begin{center}
+     \caption[Good/bad modules for each period]{2 \% rms module veto list for each period showing number of good and bad modules.}
     \begin{tabular}{ccccc}  
     \textbf{Period}   & \textbf{\# bad modules} & \textbf{\# good modules} \\ \hline
-     2018A      &   1276   &  580    \\  
-     2018B      &    802  &     1054  \\ 
-     2018C      &   1076  &    780   \\ 
-     2018D1     &  1169  &     687  \\ 
-     2018D2     &  1184  &    672   \\ 
-     2018D3     &  1081  &    775   \\ 
-     2018D4     &  1032  &     824  \\ 
+     A      &   1276   &  580    \\  
+     B      &    802  &     1054  \\ 
+     C      &   1076  &    780   \\ 
+     D1     &  1169  &     687  \\ 
+     D2     &  1184  &    672   \\ 
+     D3     &  1081  &    775   \\ 
+     D4     &  1032  &     824  \\ 
       \end{tabular}
-    \caption[Module veto list for each period]{2 \% rms module vetolist for each period showing number of good and bad modules.}
+    %\caption[Good and bad modules during each period]{2 \% rms module veto list for each period showing number of good and bad modules.}
     \label{tab:per period veto}
@@
 \end{table}
+
+\begin{comment}
+
+Table \ref{tab:pccvis_diffveto} depicts the mean and RMS values of PCC/HFOC luminosity for each period using per period veto list.
+The mean values are demonstrated for periods A, B, C, D1, D2, D3, and D4, with 'A' having a mean value of 1.006 and the other periods ranging from 0.9981 to 1.003.
+The RMS values range from 0.002115 to 0.004183, showing a degree of variation.
+The table also provides the ratio of RMS to mean, which offers a perspective on relative fluctuations.
+The calculated ratios are close to their corresponding RMS values, indicating relatively consistent variability across periods.
+The table effectively illustrates a nuanced variation in mean luminosity values across different periods.
 
@@
 \end{tabular}
-\caption{%                                                                                                                                                                                              
- PCC/ HFOC luminosity mean and rms values for new per period vetolist showing variation in mean values across period.
+\caption[Mean value change for PCC/HFOC across period.]{%                                                                                                                                       
+ PCC/ HFOC luminosity mean and rms values for  per period veto list showing variation in mean values across period.
 }
@@
 
+\end{comment}
+
+Figure \ref{fig:b_a_stability_vdm} shows the stability plots of the relative contribution to luminosity from pixel layers/disks before and after applying the module veto in the vdM calibration period.
+%This veto list application is essential for maintaining data quality as it helps to filter out data from modules showing more than 2\% variability in their RMS/mean, considered potentially large.
+The plots provide a comparative view of how the luminosity fraction has been impacted by the application of this veto list.
+The 'before' plot shows greater variability, reflecting the natural fluctuations in luminosity across different layers or disks  during each lumi section.
+In contrast, the 'after' plot  display a more stable profile, indicating that the module selection has effectively reduced the variance in luminosity fraction readings, enhancing data stability.
+%This figure plays a crucial role in visualizing the impact of implementing stringent data vetting procedures in the analysis of luminosity measurement.
+%An improvement in the stability of various PCC layer and disk for the whole Period B after applying new veto list shown in Fig. \ref{fig:old_new_periodB}.
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/before_after_vdm_stability_1.png}
+\caption[PCC vdM Stability]{%                                                                                                                                                                      
+   Luminosity fraction per layer or disk (stability plots) before (no veto) and after applying the final module veto with 2\% RMS/mean selection for the vdM fill data.
+}
+\label{fig:b_a_stability_vdm}
+\end{figure}
+
 %\begin{figure}[!htp]
@@
 
-\begin{table}[htbp]
-\centering
-\label{tab:run-period}
+\begin{comment}
+
+Table \ref{tab:runperiod_oldnew} details the number of "Good Modules" across different run periods under both old and new veto conditions.
+The periods under consideration are A, B, C, and D, with D further subdivided into "early" and "late" phases for the old veto.
+In the new veto, period D is segmented into D1, D2, D3 (split into two specific run ranges), and D4.
+Under the "Old Veto" condition, periods A, B, C, and "D early" each have a consistent count of 787 good modules.
+However, for the "D late" phase, there are 469 good modules, suggesting a notable reduction from the earlier phase of period D.
+Moving to the "New Veto" scenario, the good modules count shows considerable variability across periods.
+Period A records 580 good modules, B has the highest number with 1054, and C presents 780 good modules.
+For the D period under the new veto, D1 and D2 show 687 and 672 good modules respectively.
+Period D3, divided into two separate run ranges (323363-323699 and 323700-324420), maintains a consistent count of 775 good modules for both ranges.
+Finally, for period D4, there are 824 good modules.
+
+\begin{table}
+  \centering
+  \caption{Run Period and Good Modules}
 \begin{tabular}{cccc}
@@
  & & D2 & 672 \\
- & 775 & D3 (323363-323699)  & \\
+ &  & D3 (323363-323699)  &  775\\
 D late & 469 & D3 (323700-324420) & 775 \\
- & 824 & D4 & \\
+&  & D4 & 824\\
 \end{tabular}
-\caption{Run Period and Good Modules}
+%\caption{Run Period and Good Modules}
+\label{tab:runperiod_oldnew}
 \end{table}
 
-To further improve the stability of PCC luminometer, $2\%$ rms common module vetolist is created as shown in Table \ref{tab:2commonveto}.
+\end{comment}
+
+%An improvement in the stability of various PCC layer and disk is shown in Fig. \ref{fig:old_new_periodB} after applying new veto list.
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/old_new_veto_periodB.png}
+%\caption[Old new veto period B per layer/disk stability]{Comparison of PCC layer and disk stability for old and new module veto.}
+%\label{fig:old_new_periodB}
+%\end{figure}
+
+%To reduce the variation in mean values across periods thereby improving the stability of PCC luminometer, a common module veto list is created using the 2\% RMS/mean selection as shown in Table \ref{tab:2commonveto}.
+
+Table \ref{tab:2commonveto} shows the number of modules for a common selection over the entire year.
 Common module veto list is a combination of module veto list of all run periods A, B, C, D1, D2, D3 and D4.
@@
 Less than $9\%$ of the pixel modules remain after applying module stability selections to be used for final luminosity measurement.
+The total number of good modules across all layers and disks is 155.
 
@@
   \begin{center}
+    \caption[Common module veto list]{Final module veto list. This veto list is created by combining module veto lists for each period.}
     \begin{tabular}{ccccc}  
       \textbf{Period}   & \textbf{\# bad modules} & \textbf{\# good modules} \\  \hline
-     2018A + B + C      &  1417   &  439    \\  
-     2018A + B + C + D1      &   1534  &   322    \\ 
-     2018A + B + C + D1 + D2      &   1629 &    227   \\ 
-     2018A + B + C + D1 + D2 + D3     &   1668 &   188    \\ 
-     2018A + B + C + D1 + D2 + D3 + D4     &  1701 &     155  \\ 
+      A + B  & 1276 & 580 \\
+     A + B + C      &  1417   &  439    \\  
+     A + B + C + D1      &   1534  &   322    \\ 
+     A + B + C + D1 + D2      &   1629 &    227   \\ 
+     A + B + C + D1 + D2 + D3     &   1668 &   188    \\ 
+     A + B + C + D1 + D2 + D3 + D4     &  1701 &     155  \\ 
       \end{tabular}
-    \caption[Common module veto list for all periods]{2\% rms common module vetolist. This veto list is created by combining module veto lists for each period.}
+    %\caption[Common module veto list for all periods]{Final module veto list. This veto list is created by combining module veto lists for each period.}
     \label{tab:2commonveto}
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/before_after_vdm_stability.png}
-\caption{%
-   Luminosity fraction (stability plots) before and after applying 2\% rms module vetolist.
-}
-\label{fig:b_a_stability_vdm}
-\end{figure}
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/before_after_vdm_stability.png}
+%\caption[]{%
+ %  Luminosity fraction (stability plots) before and after applying 2\% rms module vetolist.
+%}
+%\label{fig:b_a_stability_vdm}
+%\end{figure}
 
@@
 
-\begin{table}[htbp]
-\centering
+%\begin{table}[htbp]
+%\centering
 %\caption{Layer/Disk Statistics}
-\label{tab:layer-disk}
+%\label{tab:layer-disk}
+%\begin{tabular}{cccccc}
+%\textbf{Layer/Disk} & \textbf{Good modules} & \textbf{mean} & \textbf{rms} & \textbf{rms/mean} \\
+%\hline
+%Layer 2 & 0 & 0 & 0 & 0 \\
+%Layer 3 & 48 & 0.374681 & 0.000663165 & 0.00176995 \\
+%Layer 4 & 79 & 0.356424 & 0.000724235 & 0.00203195 \\
+%Disk 1 & 10 & 0.102687 & 0.000535149 & 0.00521144 \\
+%Disk 2 & 12 & 0.112508 & 0.000460595 & 0.00409389 \\
+%Disk 3 & 6 & 0.0537002 & 0.000282446 & 0.00525967 \\
+%Total  & 155 & & \\
+%\multicolumn{2}{c}{} & \multicolumn{2}{r}{155} \\
+%\end{tabular}
+%\caption{Layer/Disk Statistics}
+%\end{table}
+
+The relative contribution to PCC luminosity from each pixel detector layer and disk without and with final module veto list is shown in Fig. \ref{fig:stabprof_4333}.
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=0.8\textwidth]{ashish_thesis/2percentcommonveto_pixellayerdisk.png}
+%\caption[Pixel layer/disk stability]{%
+ %  Stability profiles of pixel detector layer and disk modules for 2\% rms common module veto list.
+%}
+%\label{fig:stabprof}
+%\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=\textwidth]{ashish_thesis/2percentcommonveto_pixellayerdisk_1.png}
+\caption[PCC Stability For Physics Runs]{Left: Luminosity fraction of pixel detector for various layer and disks as a function of lumi section for a module selection excluding only the BPIX Layer 0 for the full 2018 zero-bias dataset.
+Right: Stability profiles of pixel detector layer and disk for final module veto list.}
+\label{fig:stabprof_4333}
+\end{figure}
+
+%\begin{figure}[!htp]
+ % \centering
+  %\begin{subfigure}[b]{0.49\textwidth}
+   % \includegraphics[width=\textwidth]{ashish_thesis/pixel_layer_disk_B0_veto.png}
+    %\caption{Image 1}
+  %\end{subfigure}
+  %\hfill % or \hspace{5mm} for a specific horizontal space
+  %\begin{subfigure}[b]{0.49\textwidth}
+   % \includegraphics[width=\textwidth]{ashish_thesis/2percentcommonveto_pixellayerdisk.png}
+    %\caption{Image 2}
+  %\end{subfigure}
+  %%\caption[PCC Stability For Physics Runs]{Left: Luminosity fraction of pixel detector for various layer and disks as a function of lumi section for a module selection excluding only the BPIX Layer 0 for the full 2018 zero-bias dataset.
+Right: Stability profiles of pixel detector layer and disk for final module veto list.}
+  %\label{fig:stabprof_4333}
+%\end{figure}
+
+Table \ref{tab:layer-disk} presents the statistics of good modules across different layers and disks for final module veto list.
+The layers and disks are divided into five categories: Layer 3, Layer 4, Disk 1, Disk 2, and Disk 3.
+For each of these categories, the number of good modules, mean, RMS, and the ratio of RMS to mean are provided.
+Layer 2 has no good modules and all statistical parameters are zero.
+Layer 3, on the other hand, has 48 good modules with a mean value of 0.374681, an RMS of 0.000663165 and an RMS-to-mean ratio of 0.00176995, indicating low variability.
+Layer 4 shows a slightly larger count of good modules with 79, and similar statistical parameters to Layer 3, albeit with a slightly higher RMS and RMS-to-mean ratio, suggesting slightly greater variability.
+When it comes to the disk categories, Disk 1 and Disk 2 each have 10 and 12 good modules respectively.
+Their mean values are lower than those of the layers, as are their RMS values, although their RMS-to-mean ratios are higher, suggesting greater relative variability in these categories.
+Disk 3 has the fewest good modules with only 6, and it presents the highest RMS-to-mean ratio among all categories, indicating the highest relative variability.
+%The total number of good modules across all layers and disks is 155.
+%It's noteworthy that the table does not provide an aggregated mean, RMS, or RMS-to-mean ratio across all categories.
+
+\begin{table}[!htp]
+  \centering
+  \caption[Final module veto statistics]{Layer/Disk good modules and statistics for final module veto list.}
+%\caption{Layer/Disk Statistics}                                                                                                                                                                       
+%\label{tab:layer-disk}
 \begin{tabular}{cccccc}
-\textbf{Layer/Disk} & \textbf{Good modules} & \textbf{mean} & \textbf{rms} & \textbf{rms/mean} \\
+\textbf{Layer/Disk} & \textbf{Good modules} & \textbf{mean} & \textbf{rms} & \textbf{rms/mean} (\%) \\
 \hline
-Layer 2 & 0 & 0 & 0 & 0 \\
-Layer 3 & 48 & 0.374681 & 0.000663165 & 0.00176995 \\
-Layer 4 & 79 & 0.356424 & 0.000724235 & 0.00203195 \\
-Disk 1 & 10 & 0.102687 & 0.000535149 & 0.00521144 \\
-Disk 2 & 12 & 0.112508 & 0.000460595 & 0.00409389 \\
-Disk 3 & 6 & 0.0537002 & 0.000282446 & 0.00525967 \\
+Layer 3 & 48 & 0.374681 & 0.000663165 & 0.176995 \\
+Layer 4 & 79 & 0.356424 & 0.000724235 & 0.203195 \\
+Disk 1 & 10 & 0.102687 & 0.000535149 & 0.521144 \\
+Disk 2 & 12 & 0.112508 & 0.000460595 & 0.409389 \\
+Disk 3 & 6 & 0.0537002 & 0.000282446 & 0.525967 \\
 Total  & 155 & & \\
@@
 \end{tabular}
-\caption{Layer/Disk Statistics}
+%\caption[Final veto statistics]{Layer/Disk good modules and statistics for final module veto list.}
+\label{tab:layer-disk}
 \end{table}
 
-The relative contribution to PCC luminosity from each pixel detector layer and disk after removing low statistics lumi sections and applying 2\% rms common module vetolist is shown in Fig.
-\ref{fig:stabprof}.
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.8\textwidth]{ashish_thesis/2percentcommonveto_pixellayerdisk.png}
-\caption[Pixel layer/disk stability]{%
-   Stability profiles of pixel detector layer and disk modules for 2\% rms common module veto list.
-}
-\label{fig:stabprof}
-\end{figure}
-
-%\subsection{Reasons for the inclusion of certain modules in the veto list}
+\section{vdM calibration results}
+
+The calibration of luminosity measurement by the CMS experiment luminometers in the 2018 proton-proton data taking at $\sqrt{s}$ = 13 TeV \cite{CMS-PAS-LUM-18-002} was performed during LHC fill 6868 on June 30 and July 1, 2018 at $\sqrt{s}$ = 13 TeV.
+Zero-bias triggers on 5 bunch pairs (BCIDs 265, 865, 1780, 2192, and 3380) recorded events rate is 27.7 kHz.
+Trigger is applied on five colliding bunches due to limitation of the recording bandwidth.
+
+%\item "lsc1", was the "constant separation" scan, two beams were separated by 1.4 $\sigma$ and moved together in steps of 1 $\sigma$ across and back.
+%\item "lsc2", was the "variable separation" scan method, one beam (starting with beam 1) is moved to -2.5 $\sigma$ and then a three-point scan (a "miniscan") is performed with the other beam.
+%a normal VdM scan pair "norm4" and two short emittance scan pairs "emit4" and "emit5" were also performed.
+%The 2018 CMS VdM scan program was conducted in two segments, interrupted by an alarm.
+The first segment involved six x-y scan pairs.
+Two were short ``emittance'' scans, named ``emit1'' and ``emit2,'' where the beamswere separated by $ \(4\sigma_b\) $ over 9 steps with a 10 second integration time at each step.
+A standard VdM scan, named ``norm1,'' separated the beams by $\(6\sigma_b \approx 600\)~\mu m$ in 25 steps, with a 30-second duration per step.
+The ``offset1'' scan followed the same procedure as the standard scans but with a $\(\pm 1.5\sigma_b\)$ separation in the non-scanning direction.
+Lastly, two sets of ``beam imaging'' scans wereconducted, where one beam remained fixed while the other was moved in 19 steps between $\(+4.5\sigma_b\)$ and $\(-4.5\sigma_b\)$, each lasting 46 seconds per step.
+The 2018 CMS vdM scan program (shown in Fig.
+\ref{fig:vdm_prog_2018}) was conducted in two segments, interrupted by an alarm.
+The first segment involved six x-y scan pairs.
+Two were short ``emittance'' scans, named ``emit1'' and ``emit2,'' where the beams were separated by \(4\sigma_b\) over 9 steps with a 10-second integration time at each step.
+A standard vdM scan (described in section 3.1), named ``vdM1,'' separated the beams by \(6\sigma_b \approx 600\)~$\mu$m in 25 steps, with a 30-second duration per step.
+The ``offset1'' scan followed the same procedure as the standard scans but with a \(\pm 1.5\sigma_b\) separation in the non-scanningdirection.
+Lastly, two sets of ``beam imaging'' scans were conducted, where one beam remained fixed while the other was moved in 19 steps between \(+4.5\sigma_b\) and \(-4.5\sigma_b\), each lasting 46 seconds per step.
+The second part of the scan program was conducted in the same fill, approximately 7.5 hours later, and consisted of twelve scan pairs.
+This included a short emittance scan, ``emit3''; beam imaging scan pairs, ``imag2'' and``imag3''; an offset scan pair, ``offset2''; and two standard vdM scan pairs, ``vdM2'' and ``vdM3''.
+
+Beam Imaging Scans: Beam imaging scans are designed to measure the transverse profile of the beam.
+They involve moving one beam across the other in steps and measuring the interaction rate (or event rate) at each step.
+By doing this, the shape or "profile" of the beam in the transverse plane can be obtained.
+These scans allow for a detailed analysis of the beam shape, which is essential for understanding the beam properties.
+In a perfect scenario, the density distributions of protons in a bunch would factorize into separate X (horizontal) and Y (vertical) components.
+However, real beams can have correlations between X and Y (non-factorization).
+Beam imaging scans help map the 2D profile of the beam and are thus essential for diagnosing and understanding any such correlations.
+Knowing the 2D profile of the beams is crucial when calculating luminosity, as assumptions made about the factorization of the beam profiles feed into these calculations.
+By using beam imaging scans, experimenters can assess the validity of the factorization assumption or correct for any observed non-factorization.
+
+Offset Scans: %Offset scans are performed to check for systematic errors in the luminosity measurement, which may arise from various sources.
+They are similar to standard VdM scans but involve an intentional offset in the non-scanning direction.
+By comparing the results of offset scans with the results of regular scans, one can identify and correct for any systematic discrepancies that are present.
+Offset scans can help to assess the sensitivity of the luminosity measurement to non-factorization in the transverse plane.
+For example, if there are correlations between the X and Y distributions of protons (i.e., non-factorization), this could in principle affect the shape of the beam overlap region in the collision point.
+Offset scans, by changing the relative position of the beams, can help to assess whether such non-factorization has a significant effect on the measured luminosity.
+
+vdM scans are typically conducted at least once a year to ensure the luminometer is correctly calibrated.
+Results of these scans that is the visible cross section is used to normalize the data collected by the experiments during physics run.
+
+\begin{figure}[!htp]
+    \centering
+    \includegraphics[width=1\textwidth]{ashish_thesis/vdm_program_2018.png}
+    \caption[2018 vdM Program]{Beam position along x and y is plotted as a function of time showing different types of scans.
+#3 and #10 are vdM scans, #4 and #9 are offset scans, #5, #7 and #8 are beam imaging scans, #6 is emittance scan.}
+    \label{fig:vdm_prog_2018}
+\end{figure}
+
+The vdM data (LHC fill 6868) is processed using the final module selection.
+The background estimation for the PCC rate is done with two super-separation scans SS1 and SS2.
+The mean and error are obtained from the $y$ projection of PCC per NB4 plotted as a function of time as shown in Fig.
+\ref{fig:sigmavis_ss_backg}.
+The results for five different BCIDs are shown in Table \ref{tab:vdm:SS1_SS2}, using the reprocessed PCC data for Fill 6868.
+The overall background correction applied to raw PCC rate is $0.02757\pm0.01987$, which is calculated by taking the average of the mean values of SS1 and SS2.
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/SS1_SS2_bkg_pcc_1.png}
+\caption[Background estimation]{2D histogram filled with the Avg. PCC evaluated per NB4, during head-on collisions (high part) and during the Super-Separation window (low part).}
+\label{fig:sigmavis_ss_backg}
+\end{figure}
+
+\begin{table}
+  \begin{center}
+    \caption[2018 PCC Background]{Mean for the background estimated with the SS1 and SS2 data, separately for all five BCIDs and averaged.}
+    \begin{tabular}{ccccc}
+    \textbf{BCID}   & \textbf{Mean (SS1)} & \textbf{Mean (SS2)} \\ \hline
+      265     &  0.02902    &  0.02743    \\
+        865  &    0.02572  &     0.0281  \\
+       1780    &  0.02862   &     0.0286  \\
+       2192   &  0.02729  &     0.02323  \\
+        3380  &  0.02882  &    0.02896   \\
+      \end{tabular}
+    %\caption[Background in PCC rate]{Mean for the background estimated with the SS1 and SS2 data, separately for all five BCIDs and averaged.}
+    \label{tab:vdm:SS1_SS2}
+  \end{center}
+\end{table}
+
+Figure \ref{fig:fitquality} displays the collision rates for a specific particle bunch as one beam is moved across another, with all necessary corrections applied.
+$\chi^2/ndof$ for vdM and imaging scans has an average value of 0.4514 where the Poly2G fit model converges for all BCIDs.
+Peak value and beam overlap $\Sigma_x$ and $\Sigma_y$ along X and Y are extracted from fit to calculate $\sigma_{vis}$.
+%The $\sigma_{vis}$ per scan is averaged over all BCIDs and its scan to scan variation is shown in Fig.
+\ref{fig:sigmaperscan}.
+The $\sigma_{vis}$ value obtained by averaging all scans is for final module veto list is 960.54 $\pm$ 0.85(stat.) mb.
+
+\begin{figure}[!htp]
+    \centering
+    \includegraphics[width=1\textwidth]{ashish_thesis/vdM_fit_cveto_1.png}
+    \caption[PCC Rate Fit]{Rates and the resulting fitted Poly2G scan curves as a function of the beam separation for a single bunch (BCID 265) as recorded by PCC for vdM1 scan in the x (left) and y direction (right).
+Background subtraction and the beam corrections have been applied to the raw data before the fit.}
+    \label{fig:fitquality}
+\end{figure}
+
+%\begin{figure}[!htp]
+ %   \centering
+  %  \includegraphics[width=0.8\textwidth]{ashish_thesis/sigma_vis_per_scan.png}
+  %  \caption[PCC Visible Cross Section]{Visible cross section per scan where red line shows the average value.}
+   % \label{fig:sigmaperscan}
+%\end{figure}
+
+\newpage
+\section{Luminosity for physics fill}
+
+The LHC operates in cycles known as "fills." A fill is a period during which the LHC is filled with protons and provides collisions for its experiments.
+The luminosity profile of a fill is a graphical representation of the instantaneous luminosity as a function of time for the entire duration of that fill.
+Before the actual data taking begins, there is a phase of beam injection, acceleration, and stabilization.
+During this period, no collisions are taking place, so the luminosity is zero.
+Once the beams are accelerated to their maximum energy and brought into collision, there is a rapid rise in luminosity.
+This is the point where the luminosity reaches its highest value, known as the peak luminosity.
+After the peak, the luminosity starts to decrease.
+This period, known as "stable beams", is when most of the data is collected.
+The reason for the decrease in luminosity over time is the reduction in the number of protons in the beams due to collisions.
+As the protons in the beams collide, the number of protons, and hence the luminosity, diminishes.
+The rate of this decrease can be influenced by various factors, including beam dynamics, losses, and the efficiency of the collider's operation.
+The fill concludes when the number of protons is too low to provide useful data, or if there's a technical issue, leading to a beam dump.
+At this point, the luminosity drops to zero.
+The total duration of a fill can vary.
+Some fills last only a few hours, while others can extend for over a day, depending on operational efficiency and the goals for that specific fill.
+Fill profile for Fill 6961 during 2018 data taking is shown in Fig.
+\ref{fig:Fill6961} with
+
+\begin{itemize}
+
+\item Peak luminosity = $1.85 \times 10^{34} cm^{-2} s^{-1}$
+\item End luminosity = $0.9 \times 10^{34} cm^{-2} s^{-1}$ 
+\item Number of colliding bunches = 2556
+\item Number of lumi sections = 1400
+\item Integrated luminosity = 0.418 $fb^{-1}$
+
+\end{itemize}
+
+\begin{figure}[!htp]
+    \centering
+    \includegraphics[width=0.9\textwidth]{ashish_thesis/Fill_profile_6961_1.png}
+    \caption[Fill 6961 Profile]{Typical lumi profile for LHC Fill during 2018 data taking period for Fill 6961.}
+    \label{fig:Fill6961}
+\end{figure}
+
+\newpage
+\subsection{Afterglow backgrounds}
+
+In the precision PCC luminosity measurement, understanding and rectifying the effects of afterglow is crucial.
+When estimating afterglow corrections, it's paramount to utilize raw PCC data obtained from both colliding and non-colliding bunches.
+The colliding bunches yield genuine signals representative of particle interactions, while the non-colliding bunches illuminate the background noise inherent in the system, simultaneously capturing any lingering afterglow from prior collisions.
+Two primary types of afterglow noise have been identified:
+
+Type 1 Afterglow (Electronic Spillover): This noise arises due to the lingering signal waveform in silicon after an actual collision event.
+
+Type 2 Afterglow (Activation-Induced Background): This noise is a consequence of the gradually diminishing activation of the detector.
+It occurs when the detector material encounters high-energy particles, leading to the creation and decay of radioactive isotopes \cite{CMS-PAS-SMP-12-008} %(as depicted in Fig.
+\ref{fig:pcc_afterglow}).
+
+The afterglow correction process seeks to adjust for these residual signals, which result in background added to the cluster count.
+The concept of 'afterglow' is intrinsically tied to the detector and the events it records, independent of the specific modules used for data collection.
+Thus, regardless of any module's performance or operational state, the need for consistent afterglow correction remains.
+
+In the afterglow correction process, following steps are involved.
+
+\begin{itemize}
+\item A model is constructed to mirror the afterglow tail from a single colliding bunch using the random trigger data.
+\item The model is then fine-tuned according to the luminosity associated with that bunch.
+\item In the ongoing correction process, a histogram representing the collision events and containing bunch trains is adjusted whereby the afterglow model, multiplied by the luminosity of each colliding pair, is subtracted from all subsequent collision events.
+This step ensures each bunch is comprehensively corrected.
+\item Finally, the scale factor for correction is defined by the ratio of the corrected to the uncorrected PCC.
+This factor is then implemented in the final PCC for the ZB data.
+%An example plot of the scale factor is shown in Fig.
+\ref{fig:af_change_veto}.
+\end{itemize}
+
+Moreover, pedestal correction is essential.
+It signifies the adjustment of baseline values in the detector due to electronics noise.
+This procedure ensures accurate and stable readings from the pixel detector, culminating in precision PCC luminosity measurements.
+%An example of the afterglow correction factor including type 1, type 2 and pedestal corrections is shown in Fig.
+\ref{fig:af_change_veto}.
+
+For accurately modeling the afterglow effect in raw data, a composite function is utilized.
+It includes parameters for the Type 1 afterglow and an exponentially decaying model for Type 2, taking both amplitude and decay width into account.
+The model is summed over all bunch crossings.
+Fill 9036, shown in \ref{fig:af_fit40} and encompassing 900 colliding bunches, serves as the foundation for estimating the Type 2 afterglow parameters.
+A fit is performed to one wagon train, then two, and finally three, refining the parameters for Type 2 afterglow and minimizing the residuals of both afterglow types.
+Fit plots for single colliding bunch is shown in \ref{fig:af_fit99}.
+The values of type 2 afterglow parameter amplitude (a) and decay width (b) for different wagon trains are shown in Table \ref{fig:af_fit4000}.
 
@@
 
-The module veto list in particle physics experiments is a list of detector modules that are excluded from the analysis of data due to their known or suspected high rate of background events or other issues that could affect the accuracy of the measurement.
-The inclusion of certain modules in the veto list is based on various factors, including:
-
-\begin{itemize}
-
-\item Radiation damage: The harsh radiation environment in the LHC can cause damage to the silicon pixel sensors over time, leading to increased leakage currents, noise, or reduced charge collection efficiency.
-
-\item Manufacturing defects: Defects in the silicon material or issues during the manufacturing process can result in poorly performing pixel modules.
-These defects may not be immediately evident but can become more pronounced over time.
-
-\item Electronic noise: Noisy electronic components or crosstalk between channels can lead to an increased number of false signals or noise in the pixel module data.
-
-\item Temperature variations: Temperature fluctuations can affect the performance of the pixel modules, leading to changes in their noise levels, gain, or charge collection efficiency.
-
-\item High voltage issues: Problems with the high voltage supply to the pixel modules can result in unstable operation, leading to erratic behavior or complete module failure.
-
-\item Partial module failure: A pixel module may suffer from partial failure, with some pixels or readout channels not functioning properly.
-This can lead to an increased number of dead or noisy pixels in the module.
-
-\item Readout or data acquisition issues: Errors in the readout electronics or data acquisition system can lead to data corruption or loss, affecting the performance of the pixel modules.
-
-\item Calibration issues: Inaccurate or outdated calibration parameters can result in incorrect measurements, leading to the appearance of abnormal behavior in the pixel module data.
-
-\item Firmware or software issues: Bugs in the firmware or software responsible for controlling and reading out the pixel modules can lead to abnormal behavior or incorrect measurements.
-
-\item Mechanical or alignment issues: Mechanical stresses or misalignments during the installation or operation of the pixel detector can affect the performance of the pixel modules or cause them to fail.
-
-\item Contamination or environmental factors: Contamination of the pixel modules by dust, moisture, or other substances can affect their performance or cause them to fail.
-Similarly, external environmental factors, such as magnetic fields or vibrations, can impact the operation of the pixel modules.
-
-\end{itemize}
-
-The inclusion of certain modules in the veto list is based on a careful analysis of the detector performance and the expected background rates in a given experiment.
-By excluding modules with high background rates or other issues, the analysis can be improved and the accuracy of the measurement can be increased.
-
-\end{comment}
-
-\section{Afterglow Model}
-
 Type 1 and Type 2 afterglow corrections are very important for precise PCC luminosity measurement.
-Type 1 afterglow noise, or electronic spillover, arises due to the lingering signal waveform within silicon.
-Contrarily, Type 2 afterglow noise emanates from the exponentially diminishing activation of the detector caused by the creation of secondary particles when the detector material encounters high-energy particles \cite{CMS-PAS-SMP-12-008}(as depicted in Fig.
+Type 1 afterglow noise, or electronic spillover, arises due to the lingering signal waveform within silicon after actual collision event.
+Contrarily, Type 2 afterglow noise emanates from the exponentially diminishing activation of the detector caused by the creation of secondary particles when the detector material encounters high-energy particles \cite{CMS-PAS-SMP-12-008} (as depicted in Fig.
 \ref{fig:pcc_afterglow}).
@@
 
+%The afterglow correction is independent of the module veto list as shown in Fig.
+\ref{fig:af_change_veto} , meaning the correction is applied universally across all modules irrespective of whether a module is on the veto list or not.
+This is because afterglow is a characteristic of the detector material and particle interactions, not of the specific modules.
+Thus, even when the module veto list changes, the afterglow corrections remain consistent, ensuring accurate luminosity measurement.
+
+The afterglow correction in PCC luminosity measurement is a compensatory procedure that's designed to adjust for the lingering effects of prior particle collisions, which may otherwise skew the accuracy of the luminosity calculations.
+The concept of 'afterglow' is related to these residual signals, identified as Type 1 and Type 2, that originate from the detector material and the physical processes associated with the particle interactions.
+Importantly, the presence and extent of afterglow are influenced by these fundamental factors and are not dictated by the operational state or quality of any individual detector module as shown in Fig.
+\ref{fig:af_change_veto}.
+That is, the afterglow is an inherent characteristic tied to the detector and the physical event, and it is independent of the specific modules being used to collect the data.
+A module veto list is a register of detector modules that are excluded from data collection and analysis for various reasons, such as suboptimal performance, high noise levels, or other technical issues.
+When a module is added to or removed from the veto list, it can affect the raw data that's being gathered, but it doesn't influence the underlying afterglow characteristics that are tied to the detector material and the particle collisions.
+Therefore, changes to the veto list do not alter the need for, or the application of, the afterglow correction.
+Consequently, the afterglow correction process remains consistent and is applied across all modules, irrespective of their veto list status.
+This ensures that the measured luminosity accurately represents the actual particle collision events, providing reliable data for subsequent analysis and interpretation, regardless of the specific module configuration at any given time.
+
 Apart from afterglow corrections, pedestal correction is another critical component.
@@
 The pedestal correction involves monitoring the detector's output in the absence of a signal, and then subtracting this baseline value from the signal collected during data capture.
-The application of pedestal correction significantly enhances the accuracy and stability of the detector's readings, thereby leading to precision measurement of PCC luminosity.
+The application of pedestal correction significantly enhances the accuracy and stability of the pixel detector's readings, thereby leading to precision measurement of PCC luminosity.
 
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/veto_change_same_af.png}
-\caption{%
-    ratio of scale factor for new and old veto.
+\caption[Afterglow background ratio]{%
+    Ratio of afterglow scale factor for new per period veto and old veto.
 }
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/af_t1_t2.png}
-\caption[Type 1 and type 2 afterglow effect for single colliding bunch]{%
-Afterglow corrections are calculated from cluster rate measurements in empty bunches.
+\end{comment}
+
+%The scale factor for one 50 lumi section block in run number 315690 is shown in Fig.
+\ref{fig:af_change_veto}.
+It provides an overview of the afterglow scale factor applied to the raw PCC.
+On the left, both the raw and corrected PCC for all bunch crossings are displayed, showing the variations between the initial data and the adjusted counts.
+The right side specifically highlights the afterglow scale factor for a single 50 lumi section block, representing the afterglow correction applied for final module veto.
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=0.7\textwidth]{ashish_thesis/af_t1_t2.png}
+%\caption[Afterglow Effect Single Bunch]{%
+%Afterglow corrections are calculated from cluster rate measurements in empty bunches.
 Electronic spillover (“Type-1”).
@@
 All empty bunches after bunch train are used to calculate it.
+%}
+%\label{fig:pcc_afterglow}
+%\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/afterglow_correction_factor_1lsblock_315690.png}
+%\caption[Afterglow background]{%
+% Left: Raw and corrected PCC for all bunch crossings. Right: Afterglow scale factor for one 50 lumi section block in run 315690 for the final module veto.
+%}
+%\label{fig:af_change_veto}
+%\end{figure}
+
+\begin{comment}
+
+The model used for fitting the afterglow in PCC raw data consists of a parameter for type 1 afterglow correction and exponentially decaying model with two parameters for type 2 afterglow correction taking into account amplitude and decay width.
+The fit function is summed over all bunch crossings.
+Fill 9036 (shown in Fig.
+\ref{fig:af_fit40}) consisting of 900 colliding bunches is used for the estimation of type 2 afterglow parameters.
+We start by fitting a single 50 lumi section block, then fit one wagon train, two wagon train and three wagon train to get better estimation of type 2 afterglow parameters to obtain least type 1 and type 2 afterglow residuals.
+
+\end{comment}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/fill_7036_pattern_2.png}
+\caption[7036 Fill Patern]{%
+  Fill 7036 pattern (900 b fill).
 }
-\label{fig:pcc_afterglow}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/fill_7036_pattern.png}
-\caption[]{%                                                                                                                                                                                         
-  Afterglow fit model.
-}
-\label{fig:af_fit}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/af_model_fit.png}
-\caption[]{%
-  Afterglow fit model.
-}
-\label{fig:af_fit}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/bunch_train.png}
-\caption[]{%
-
-  Afterglow fit model.
-}
-\label{fig:af_fit}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/2wagon_af.png}
-\caption[]{%
-
-  Afterglow fit model.
-}
-\label{fig:af_fit}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/2wagon_fit.png}
-\caption[]{%
-
-  Afterglow fit model.
-}
-\label{fig:af_fit}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/3wagon_af.png}
-\caption[]{%
-
-  Afterglow fit model.
-}
-\label{fig:af_fit}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/3wagon_fit.png}
-\caption[]{%                                                                          
-  Afterglow fit model.
-}
-\label{fig:af_fit}
+\label{fig:af_fit40}
+\end{figure}
+
+%Fit plots for single 50 lumi section block, 2 wagon and 3 wagon trains are shown in Fig. \ref{fig:af_fit41}, \ref{fig:af_fit} and \ref{fig:af_fit99}.
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/af_model_fit.png}
+%\caption[]{%
+ % Afterglow fit model for single 50 lumi section block.
+%}
+%\label{fig:af_fit41}
+%\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/bunch_train.png}
+%\caption[]{%
+
+  %Afterglow fit model.
+%}
+%\label{fig:af_fit}
+%\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/2wagon_af.png}
+%\caption[]{%
+
+ % Afterglow fit model.
+%}
+%\label{fig:af_fit}
+%\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/2wagon_fit.png}
+%\caption[]{%                                                                                                                                 
+ % Afterglow fit model for 2 wagon train.
+%}
+%\label{fig:af_fit}
+%\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/3wagon_af.png}
+%\caption[]{%
+
+ % Afterglow fit model.
+%}
+%\label{fig:af_fit}
+%\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/3wagon_fit.png}
+%\caption[Afterglow Fit]{%                                                                          
+ % Afterglow fit model for 3 wagon train.
+%}
+%\label{fig:af_fit99}
+%\end{figure}
+
+\begin{figure}[!htp]
+  \centering
+    \includegraphics[width=\textwidth]{ashish_thesis/2018_af_fit_1.png} 
+  %\hfill % or \hspace{5mm} for a specific horizontal space                                                                                                  
+  %\begin{subfigure}[b]{0.49\textwidth}
+   % \includegraphics[width=\textwidth]{ashish_thesis/2018_af_fit_residuals.png}                                                                                     
+  %\end{subfigure}
+  \caption[Afterglow Effect Fit]{Fit to single train to estimate afterglow parameters.}
+  \label{fig:af_fit99}
 \end{figure}
@@
 
+%The values of type 2 afterglow parameter amplitude (a) and decay width (b) for different wagon trains are shown in Table \ref{fig:af_fit4000}.
+
+\newpage
 \begin{table}
   \centering
+  \caption[Type 2 afterglow parameters estimation]{Type 2 afterglow parameters obtained from fit to raw pcc data}
   \begin{tabular}{ccc}
@@
      \hline
-   1-wagon train  & 0.001246  & 0.01261 \\
+   %1-wagon train  & 0.001246  & 0.01261 \\
    2-wagon train  & 0.000813 &  0.01219\\
@@
   \end{tabular}
-  \caption{type 2  af parameters}
+  %\caption{Type 2 afterglow parameters obtained from fit to raw pcc data}
+  \label{fig:af_fit4000}
 \end{table}
 
-\section{vdM calibration results}
-
-The background estimation for the PCC rate is done with two super-separation scans SS1 and SS2.
-The mean and error are obtained from the $y$ projection of PCC per NB4 plotted as a function of time.
-The results for five different BCIDs are shown in Table~\ref{tab:vdm:SS1_SS2}, using the reprocessed PCC data for Fill 6868.
-The overall background correction applied to raw PCC rate is $0.02757\pm0.01987$, which is calculated by taking the average of the mean values of SS1 and SS2.
-
-\begin{table}
-  \begin{center}
-    \begin{tabular}{ccccc}
-    \textbf{BCID}   & \textbf{Mean (SS1)} & \textbf{Mean (SS2)} \\ \hline
-      265     &  0.02902    &  0.02743    \\
-        865  &    0.02572  &     0.0281  \\
-       1780    &  0.02862   &     0.0286  \\
-       2192   &  0.02729  &     0.02323  \\
-        3380  &  0.02882  &    0.02896   \\
-      \end{tabular}
-    \caption[Background in PCC rate]{Mean for the background estimated with the SS1 and SS2 data, separately for all five BCIDs and averaged.}
-    \label{tab:vdm:SS1_SS2}
-  \end{center}
-\end{table}
-
-Fig.
-\ref{fig:fitquality} shows chi2/ndof for vdM and imaging scans with an average value of 0.4514 where the Poly2G fit model converges for all BCIDs.
-Peak value and beam overlap along X and Y are extracted from fit to calculate PCC visible cross section.
-PCC visible cross section for $2\%$ rms common module vetolist is 960.601 $\pm$ 0.851(stat.) mb.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=1\textwidth]{ashish_thesis/vdM_fit_cveto.png}
-    \caption[PCC rate fit]{Normalized rates and the resulting fitted poly2G scan curves as a function of the beam separation for a single bunch (BCID 865) as recorded by PCC for a scan in the x (left) and y direction (right).
-Background subtraction and the corrections  have been applied to the raw data before the fit.}
-    \label{fig:fitquality}
-\end{figure}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=1\textwidth]{ashish_thesis/fit_quality_chisquare.png}
-    \caption[Fit quality]{chi2/ndof for all vdM and imaging scans.}
-    \label{fig:fitquality}
-\end{figure}
-
-The visible cross section per scan is averaged over all BCIDs and its scan to scan variation is shown in Fig. \ref{fig:sigmaperscan}.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=1\textwidth]{ashish_thesis/sigma_vis_per_scan.png}
-    \caption[PCC visible cross section]{Visible cross section per scan where red line shows the average value.}
-    \label{fig:sigmaperscan}
-\end{figure}
-
-%\newpage
-
-\section{Luminosity for Physics Fills}
-
+The scale factor for one 50 lumi section block in run number 315690 is shown in Fig.
+\ref{fig:af_change_veto}.
+It provides an overview of the afterglow scale factor applied to the raw PCC.
+On the left, both the raw and corrected PCC for all bunch crossings are displayed, showing the variations between the initial data and the adjusted counts.
+The right side specifically highlights the afterglow scale factor for a single 50 lumi section block, representing the afterglow correction applied for final module veto.
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/afterglow_correction_factor_1lsblock_315690_1.png}
+\caption[Run 315690 Afterglow Background]{%
+ Left: Raw and corrected PCC for all bunch crossings. Right: Afterglow scale factor for one 50 lumi section block in run 315690 for the final module veto.
+}
+\label{fig:af_change_veto}
+\end{figure}
+
+\section{PCC instantaneous and integrated luminosity}
+
+Instantaneous luminosity refers to the rate of collisions at any given moment in time.
+It is a snapshot of the experiment's performance and is represented as \( L_{\text{inst}} \).
+The unit of instantaneous luminosity is often Hertz per micro barn $(Hz/ub)$.
+Integrated luminosity is the accumulation of instantaneous luminosity over a specific time period.
+Mathematically, it is defined as:
+\[
+\text{Integrated Luminosity} = \int (\text{Instantaneous Luminosity}) \, dt
+\]
+The unit of integrated luminosity is typically inverse femtobarns (\( \text{fb}^{-1} \)).
+Integrated luminosity can be understood as the sum of all instantaneous luminosities over the duration of the experiment, enhancing the statistical significance of the data collected.
+It serves as a measure of the total number of events recorded by the experiment, crucial for robust statistical analysis.
+When plotted as a function of lumi sections, PCC instantaneous and integrated luminosity offer distinct yet complementary insights into the experiment's performance.
+In plots that feature luminosity as a function of these lumi sections, the x-axis enumerates the lumi sections while the y-axis presents the luminosity values.
+For instantaneous luminosity, discrete data points are plotted for each lumi section, providing immediate, lumi section specific measurements of the collision rate as shown in Fig.
+\ref{fig:PCC_inst_2018}.
+These points can fluctuate based on a variety of factors, such as beam conditions or adjustments to the accelerator.
+On the other hand, integrated luminosity is represented by a continuously ascending curve.
+Each point on this curve accumulates the instantaneous luminosity values up to that specific lumi section.
+The integrated luminosity for entire 2018 is calculated to be 60.47 fb^{-1}.
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/PCClumivslumisection_2018_1.png}
+\caption[2018 PCC Inst. Luminosity]{%                                                                                                                                                                   
+ 2018 PCC instantaneous luminosity as a function of lumi section.
+}
+\label{fig:PCC_inst_2018}
+\end{figure}
+
+\newpage
 \section{Systematic uncertainties}
 
-\subsection{van der Meer calibration uncertainties}
+The luminosity measurement at CMS experiment is influenced by various systematic uncertainties.
+Systematic uncertainty originates from inherent biases in experimental design, instrumentation, or methodologies, consistently skewing results away from the true value.
+These include effects from orbit drifts, xy non-factorization, beam-beam interactions, stability issues, non-linearity of the detector response, afterglow from preceding collisions, and CMS deadtime.
+Each of these sources can impact the precision of the luminosity determination and requires careful consideration in the luminosity's data analysis.
+
+\subsection{vdM calibration uncertainties}
 
@@
 
- \item  Orbit Drift: Refers to the gradual displacement of the beam orbit from its ideal trajectory due to various effects such as ground motion, magnetic field fluctuations, and thermal expansion.
-This can result in reduced beam intensity and beam quality.
-
- \item  X-Y Nonfactorization: Refers to the failure of the x and y coordinates of a particle beam to factorize, meaning that the beam profile cannot be expressed as a product of independent x and y profiles.
-This can result in beam asymmetries and other effects.
-
- \item Beam-Beam Deflection: Refers to the mutual interaction of two colliding particle beams, resulting in the deflection of the individual beams due to the electromagnetic fields generated by the other beam.
-This effect can lead to beam losses and reduced luminosity.
-
- \item Dynamic $\beta$: Refers to the time-varying beta function of a particle beam, which describes the rate at which the beam diverges or converges as it propagates.
-This effect can be important for beam stability and the control of beam emittance.
-
-\item Beam Current Calibration: Refers to the process of accurately measuring the current of a particle beam, which is essential for many beam diagnostics and control systems.
-
-\item Ghosts and Satellites: Refers to unwanted signals in a detector or measurement system that can arise from various sources such as scattered radiation, electronic noise, or interference from other particles.
-These can lead to inaccurate measurements and reduced data quality.
-
-\item Scan to Scan Variation: Refers to the variation in experimental results obtained from different scans or measurements, which can arise from various sources such as statistical fluctuations, instrument drift, or systematic errors as shown in Fig.
-\ref{fig:sigmaperscan}.
-
-\item Bunch to Bunch Variation: Refers to the variation in the properties of individual particle bunches within a beam, such as their intensity, energy spread, or emittance.
-This effect can be important for beam tuning and optimization.
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/sigma_vis_btob_var.png}
-\caption[]{%                                                                                                                                                                            
+\item Orbit Drift: Orbit drift in particle accelerators refers to the slight deviation or shift in the trajectory of circulating particle beams from their intended path.
+This drift can be caused by a myriad of factors, including imperfections in the magnetic fields guiding the beams, external disturbances, and even minute ground movements or temperature fluctuations affecting the accelerator components.
+The precision with which beams are aligned in colliders like the LHC is crucial for maximizing the number of particle collisions, and hence the luminosity.
+When an orbit drift occurs, the overlap of the colliding beams may become suboptimal, leading to a reduced instantaneous luminosity.
+This reduction can influence the effectiveness of the experiments conducted, potentially introducing uncertainties in the luminosity measurement \cite{CERNOribLumi}.
+
+\begin{comment}
+
+Orbit drift refers to the changes in the orbit of the proton beams in the Large Hadron Collider (LHC) \cite{CERNOribLumi}.
+These beams are accelerated to near the speed of light, and any minor variations in the beam's path can lead to discrepancies in the observed data.
+This drift becomes particularly significant for precision measurements, such as those required for calculating the luminosity of collisions in the CMS experiment.
+
+%Luminosity at CMS is a crucial quantity as it directly correlates to the number of potential collision events.
+The higher the luminosity, the more data available for scientists to analyze.
+Thus, the accurate measurement of luminosity is of paramount importance.
+
+Orbit drift in the LHC can contribute to systematic uncertainties in the luminosity measurement in several ways:
+
+Beam Position: Orbit drift can change the beam's position in the detector, which could affect the interaction rate and thus the measured luminosity.
+The systematic uncertainty in the luminosity due to orbit drift is associated with the precision of the correction techniques used to compensate for this drift.
+
+Beam Size: Orbit drift can also alter the size and shape of the beam, which affects the beam's cross-sectional area.
+As the luminosity is inversely proportional to the cross-sectional area, changes in this parameter can lead to a systematic uncertainty in the luminosity.
+
+Beam Angle: If the orbit drift changes the angle at which the beams collide, it could affect the effective overlap of the beams, again influencing the measured luminosity.
+
+A high degree of precision in luminosity measurement requires a similarly precise knowledge of the beam's position and path.
+Orbit drift, therefore, poses a challenge.
+One common cause of orbit drift is the natural degradation of the magnetic field in the LHC's dipole magnets, which are responsible for steering the protons around the LHC ring.
+
+Orbit drift correction in luminosity measurements at CMS is typically addressed by using a combination of real-time monitoring and post-experiment data corrections.
+
+Real-time corrections: The LHC includes a Beam Position Monitor (BPM) system, which continuously tracks the position of the beams.
+If a drift is detected, the LHC's steering magnets can be adjusted to correct the orbit in real time.
+This adjustment is automated and relies on feedback loops.
+
+Post-experiment corrections: After the data are collected, a detailed analysis of the recorded beam positions and luminosity is carried out.
+This analysis can detect and correct for any residual orbit drift that wasn't addressed in real time.
+This post-processing step involves detailed statistical analyses and machine learning algorithms to optimize the precision of the luminosity measurement.
+
+\end{comment}
+
+%Furthermore, simulations of the LHC beam dynamics are used to better understand the causes and effects of orbit drift, allowing the CMS experiment team to continuously improve their correction methods and achieve the best possible precision in their luminosity measurements.
+
+%As the LHC continues to upgrade its hardware, including the upgrade to the High-Luminosity LHC, orbit drift will continue to be an important aspect to monitor and correct to ensure accurate and reliable results from the CMS and other experiments at CERN.
+
+  %Refers to the gradual displacement of the beam orbit from its ideal trajectory due to various effects such as ground motion, magnetic field fluctuations, and thermal expansion.
+This can result in reduced beam intensity and beam quality
+
+ %\cite{CERNOribLumi}.
+
+\item  X-Y nonfactorization: The luminosity calibration often relies on methods that factorize the beam overlap integral into two separate integrals in the horizontal (X) and vertical (Y) directions.
+When this factorization is not valid or precise, the XY non-factorization comes into play.
+It essentially refers to the systematic uncertainty arising from the inability to perfectly separate or factorize the beam profiles in the horizontal and vertical dimensions.
+A variety of reasons can lead to XY non-factorization.
+One of the main causes is the complex shape and dynamics of the colliding beams.
+While in an ideal scenario, the beams might be perfectly Gaussian in shape and independent in X and Y dimensions, real-world effects such as beam-beam interactions, intrabeam scattering, or external perturbations can introduce correlations between the two dimensions.
+This means that the actual overlap of the beams cannot be simply represented as a product of their profiles in X and Y.
+The luminosity is a direct measure of how many collisions are happening per unit of time and area, and it depends on the overlap of the colliding beams.
+If the beams' profiles in the X and Y dimensions are not factorized correctly, it can lead to an inaccurate representation of their overlap, thus introducing a systematic uncertainty in the luminosity measurement \cite{CERNLUMPOG}.
+
+%This is crucial because any error in luminosity calibration directly impacts the normalization of the cross-section measurements and, thus, the results and interpretations of the physics processes under study \cite{CERNLUMPOG}.
+
+\begin{comment}
+
+The nonfactorization of proton density distribution in the X-Y plane (i.e., the plane transverse to the direction of the beam in the accelerator) can introduce uncertainties in the measurement of luminosity \cite{CERNLUMPOG}.
+
+In ideal conditions, the density distribution of the protons in each beam would be a perfect Gaussian distribution that is factorizable in the X and Y directions.
+That is, the distribution in the X direction would not depend on the position in the Y direction, and vice versa.
+However, in reality, this is often not the case due to various factors such as the design of the beam optics, beam-beam interactions.
+
+The nonfactorizability of the proton density distribution means that the actual distribution of the protons in the beam deviates from the ideal Gaussian shape.
+The distribution can become asymmetric, or develop tails or other deformations.
+These deviations can lead to uncertainties in the luminosity measurement in several ways:
+
+Interaction Rate: The luminosity is directly proportional to the overlap of the two beams at the collision point.
+If the density distribution is nonfactorizable, the overlap of the beams can be less (or more) than what would be predicted by assuming a factorizable distribution.
+
+The nonfactorizability of the density distribution can also affect the effective size of the beam at the collision point.
+
+%Beam Shape: The shape of the beam, which is determined by the density distribution of the protons, can also affect the luminosity.
+For example, a non-Gaussian beam shape can lead to a non-uniform spatial distribution of collision events in the detector, which can introduce uncertainties in the luminosity measurement.
+
+%Refers to the failure of the x and y coordinates of a particle beam to factorize, meaning that the beam profile cannot be expressed as a product of independent x and y profiles.
+This can result in beam asymmetries and other effects
+%\cite{CERNLUMPOG}.
+
+\end{comment}
+
+\item Beam-Beam Deflection: refers to the change in trajectory of the individual particles in the beam as they pass near each other in the interaction point, due to their electromagnetic interaction \cite{Herr:1982430}.
+In a perfect scenario, each beam of protons would stay focused and keep their trajectory constant throughout the process.
+However, when two beams cross each other, the electromagnetic fields of the protons in one beam can exert forces on the protons in the other beam, causing them to deviate from their initial trajectory \cite{babaev2023impact}.
+
+%Refers to the mutual interaction of two colliding particle beams, resulting in the deflection of the individual beams due to the electromagnetic fields generated by the other beam.
+This effect can lead to beam losses and reduced luminosity \cite{CERNBeamBeam}
+%\cite{Herr:1982430} \cite{babaev2023impact}.
+
+\item Dynamic $\beta$: The beta function ($\beta$*) in the context of particle accelerators like the Large Hadron Collider (LHC) is a measure of the beam size at the collision point \cite{CERNVdMOMC}, and it plays a crucial role in determining the luminosity of the collisions.
+Lower values of $\beta$* lead to smaller beam sizes at the interaction point and thus higher luminosity, as the probability of proton-proton collisions is increased.
+However, $\beta$* is not necessarily constant during the operation of the LHC.
+It can vary due to factors such as changes in the accelerator's operating conditions, beam-beam interactions.
+%This variability, often referred to as "dynamic beta", can contribute to uncertainties in the luminosity measurement.
+ When $\beta$* changes, it can alter the size of the proton beams at the interaction point.
+As the luminosity is inversely proportional to the square of the beam size, a small change in $\beta$* can lead to a significant change in luminosity.
+If these changes in $\beta$* are not accurately tracked and accounted for, they can introduce uncertainties in the luminosity measurement.
+The challenge is that $\beta$* is not directly observable, so its value and any changes in it have to be inferred from other measurements, such as the beam size and position, the orbit drift.
+ %and so on. These measurements have their own uncertainties, which can further contribute to the uncertainty in β* and thus the luminosity.
+  %Refers to the time-varying beta function of a particle beam, which describes the rate at which the beam diverges or converges as it propagates.
+This effect can be important for beam stability and the control of beam emittance
+ % \cite{CERNVdMOMC}.
+
+\item Beam Current Calibration:  Beam current calibration ensures that the \( N \) value (number of particles per bunch) used in the luminosity equation is accurate.
+If the calibration is off, the derived value of \( N \) from the instruments like beam current transformers will be inaccurate, leading to errors in the calculated luminosity \( L \).
+As the luminosity dependence on number of particles per bunch is \( N^2 \), even small errors in beam current calibration can significantly affect the accuracy of \( L \) \cite{CERNLumiDays}.
+
+%Refers to the process of accurately measuring the current of a particle beam, which is essential for many beam diagnostics and control systems \cite{CERNLumiDays}.
+
+\item Ghosts and Satellites: The ghost charge refers to the unintended or unexpected particles present in slots within the LHC beam that are nominally supposed to be empty.
+This term encapsulates the stray particles that aren't part of the primary, intended bunch structure of the beam.
+Ghost charges can originate from remnants of previous fills or injections into the LHC.
+When protons are injected and circulated within the accelerator, not all of them are perfectly grouped into the designated bunch structures.
+Some can linger outside the primary bunches, leading to these unintended ghost charges.
+The presence of ghost charges can significantly impact the luminosity measurement.
+Ghost charges can lead to additional, unexpected collisions when they interact with particles from the opposing beam.
+If these ghost-induced collisions are not accounted for, the luminosity can be overestimated.
+In the LHC, with its 400 MHz RF, there are 35640 RF bins, each about 2.5 ns long.
+Though only every tenth bin is typically filled with a particle bunch, stray particles are found in neighboring bins.
+These stray bunches within a \(\pm 12.5 \) ns range of a filled RF bin are termed \textit{"satellite bunches"}, distinct from main bunches and can influence precision luminosity measurement.
+ \cite{Alici:1427728}.
+
+  %Refers to unwanted signals in a detector or measurement system that can arise from various sources such as scattered radiation, electronic noise, or interference from other particles.
+These can lead to inaccurate measurements and reduced data quality \cite{Alici:1427728}.
+
+\item Scan to Scan Variation: Refers to the variation in experimental results obtained from different scans or measurements, which can arise from various sources such as statistical fluctuations, instrument drift, or systematic errors.
+
+\item Bunch to Bunch Variation: It means the $\sigma_{vis}$  varies from one bunch to another bunch.
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.7\textwidth]{ashish_thesis/sigma_vis_btob_var_1.png}
+\caption[$\sigma_{vis}$ Bunch Variation]{%
  Bunch to bunch variation of PCC visible cross section.  
@@
 
+%\begin{tabular}{cccccc}
+%\textbf{Scan} & \textbf{Mean} & \textbf{SEM} & \textbf{Standard Deviation} & \textbf{(Standard Deviation/Mean) $\times$ 100} \\
+%\hline
+%vdm1 & 953621.33 & 2148.68 & 1334.83 & 0.14\% \\
+%Img1 & 959386.63 & 2050.61 & 559.37 & 0.058\% \\
+%Img3 & 964376.43 & 2213.15 & 2502.04 & 0.26\% \\
+%Img4 & 960386.85 & 2163.92 & 2936.50 & 0.31\% \\
+%vdm2 & 960566.04 & 2425.60 & 4320.81 & 0.45\% \\
+%vdm3 & 964566.94 & 2456.97 & 3928.54 & 0.41\% \\
+%vdm4 & 962586.52 & 2419.86 & 3943.24 & 0.41\% \\
+%\end{tabular}
+%\caption[]{Scan to scan variation of PCC visible cross section.
+The “bunch spread” is determined from the standard deviation of the individual bunch-to-bunch uncertainty, averaged over all scans.
+The “bunch uncertainty” equal to the spread divided by the square root of the number of bunches.
+%}
+
+Table \ref{tab:sigmavis_btob_values} provides statistical data of the PCC visible cross-section for different scans.
+These scans represent different data-taking periods under slightly different experimental conditions.
+We observe that the 'Img1' scan has the smallest relative standard deviation, implying the least variability in the measured visible cross-section compared to its mean.
+On the other hand, the 'vdM2', 'vdM3', and 'vdM4' scans have higher relative standard deviations, indicating greater variability.
+
+\begin{table}[h]
+  \centering
+  \caption[$\sigma_{vis}$ bunch variation uncertainty]{Bunch to bunch variation of PCC visible cross section.
+The “bunch spread” is determined as the standard deviation (STD) of the bunches divided by the mean.}
 \begin{tabular}{cccccc}
-\textbf{Scan} & \textbf{Mean} & \textbf{SEM} & \textbf{Standard Deviation} & \textbf{(Standard Deviation/Mean) $\times$ 100} \\
+\textbf{Scan} & \textbf{Mean} & \textbf{STD} & \textbf{(STD/Mean) [\%]} \\
 \hline
-vdm1 & 953621.33 & 2148.68 & 1334.83 & 0.14\% \\
-Img1 & 959386.63 & 2050.61 & 559.37 & 0.058\% \\
-Img3 & 964376.43 & 2213.15 & 2502.04 & 0.26\% \\
-Img4 & 960386.85 & 2163.92 & 2936.50 & 0.31\% \\
-vdm2 & 960566.04 & 2425.60 & 4320.81 & 0.45\% \\
-vdm3 & 964566.94 & 2456.97 & 3928.54 & 0.41\% \\
-vdm4 & 962586.52 & 2419.86 & 3943.24 & 0.41\% \\
+vdM1 & 953621.33 & 1334.83 & 0.14 \\
+Img1 & 959386.63 & 559.37 & 0.058 \\
+Img3 & 964376.43 & 2502.04 & 0.26 \\
+Img4 & 960386.85 & 2936.50 & 0.31 \\
+vdM2 & 960566.04 & 4320.81 & 0.45 \\
+vdM3 & 964566.94 & 3928.54 & 0.41 \\
+vdM4 & 962586.52 & 3943.24 & 0.41 \\
 \end{tabular}
+%\caption[Uncertainty due to bunch to bunch variation]{Bunch to bunch variation of PCC visible cross section.
+The “bunch spread” is determined as the standard deviation (STD) of the bunches divided by the mean.} %from the standard deviation of the individual bunch-to-bunch uncertainty, averaged over all scans.
+The “bunch uncertainty” equals the spread divided by the square root of the number of bunches.}
+\label{tab:sigmavis_btob_values}
+\end{table}
 
@@
 This is important for verifying the accuracy and reliability of experimental results.
+A head-on lumi phase during vdm fill is used.
 
 \item Background Subtraction: Refers to the process of removing unwanted signals from a measurement or detector system that arise from sources other than the physical phenomenon of interest, such as noise, cosmic rays, or other particles.
-This is essential for obtaining accurate measurements of the physical signal.
+Machine induced backgrounds are subtracted from raw PCC rate as described in section 4.3.
+%Corrected rate is given by the difference between the raw rate and the background rate.
+Uncertainty in the background propagate to uncertainty in the rate as follows,
+
+\begin{comment}
 
@@
 }
-\label{fig:sigmavis_btob_variation}
+\label{fig:sigmavis_ss_backg}
 \end{figure}
@@
 
+\end{comment}
+
 %c_rate = r_rate - b_rate
@@
 
+\begin{comment}
+
 \begin{equation}
@@
 $\frac{dc_{rate}}{c_{peak}}$ =$\frac{\sqrt{(dr_{\text{rate}})^2 + (db_{\text{rate}})^2}}{c_{peak}}$
+
 \end{equation}
@@
 
-\subsection{Physics data taking uncertainties}
+%\end{comment}
+
+\begin{equation}
+c_{\text{rate}} = r_{\text{rate}} - b_{\text{rate}}
+\end{equation}
+
+\begin{equation}
+(dc_{\text{rate}})^2 = (dr_{\text{rate}})^2 + (db_{\text{rate}})^2
+\end{equation}
+
+\begin{equation}
+dc_{\text{rate}} = \sqrt{(dr_{\text{rate}})^2 + (db_{\text{rate}})^2}
+\end{equation}
+
+\begin{equation}
+\frac{dc_{\text{rate}}}{c_{\text{peak}}} = \frac{\sqrt{(dr_{\text{rate}})^2 + (db_{\text{rate}})^2}}{c_{\text{peak}}}
+\end{equation}
+
+\begin{equation}
+\frac{dc_{\text{rate}}}{c_{\text{peak}}} = \frac{db_{\text{rate}}}{c_{\text{peak}}}
+\end{equation}
+
+\end{comment}
+
+\subsection{Integration uncertainties}
 
@@
 
-\item Stability: The CMS pixel detector is a complex instrument with many components, including silicon sensors and readout electronics, that must operate consistently and with high precision over long periods.
+\item Stability: Systematic uncertainties can be introduced due to time-dependent changes in detector performance and environmental conditions.
+These changes can be influenced by various factors, including detector aging, radiation damage, and fluctuations in noise.
+A comparison of PCC luminosity with HFOC luminosity as a function of time is shown in Fig.
+\ref{fig:stabprof} depicting slight instabilities in PCC luminosity over time.
+%Detector Aging and Radiation Damage Detectors used in high-energy physics experiments are subject to aging and radiation damage due to the high-intensity radiation environment they operate in.
+Detector aging can result in time-dependent changes in the detector's performance.
+For example, as the detector ages or sustains radiation damage, its efficiency may decrease, leading to a reduction in the number of detected events for a given luminosity.
+%This effect is typically modeled and accounted for in the data analysis, but any inaccuracies in the modeling can introduce a systematic uncertainty.
+Fluctuation in the  noise level in the detector can also fluctuate over time due to changes in the experimental conditions.
+Noise can lead to spurious signals that can be misinterpreted as genuine events, leading to an overestimate of the luminosity.
+Conversely, high noise levels can also mask genuine events, leading to an overestimate of the luminosity.
+%Noise can be suppressed using data analysis techniques, but this is not always perfect, and residual noise can introduce a systematic uncertainty.
+The standard deviation of ratio of luminosity from best and second best luminometer is used as stability systematic uncertainty as shown in Fig.
+\ref{fig:stabprof1}.
+The standard deviation provides a measure of the spread or dispersion of the measurements.
+If the measurements are stable, the spread will be small, and the standard deviation will be low.
+Conversely, if there are time-dependent changes in the detector performance or environmental conditions, the measurements will vary more, and the standard deviation will be higher.
+
+  %It arises from time-dependent changes in detector performance or environmental conditions, Detector aging, radiation damage, fluctuation in noise.
+The standard deviation of ratio of luminosity from first and second best luminometeris used as stability systematic uncertainty.
+
+  %The CMS pixel detector is a complex instrument with many components, including silicon sensors and readout electronics, that must operate consistently and with high precision over long periods.
 Any variations in the performance of the detector can affect the efficiency of the pixel cluster counting method and lead to uncertainties in the luminosity measurement.
 
-  One example of how the stability of the detector can affect the luminosity measurement is through changes in the detector's noise level.
+  %One example of how the stability of the detector can affect the luminosity measurement is through changes in the detector's noise level.
 The noise level refers to the level of electronic noise present in the detector, which can interfere with the detection of pixel clusters produced by proton-proton collisions.
@@
 
-  Another example is changes in the efficiency of the pixel detector.
+  %Another example is changes in the efficiency of the pixel detector.
 The efficiency of the detector refers to the fraction of proton-proton collisions that produce pixel clusters that can be detected and counted by the method.
@@
 
-  To mitigate these uncertainties, the CMS collaboration performs regular calibrations and monitoring of the detector performance, as well as cross-checks with other luminosity measurement techniques
-
-  Systematic uncertainties due to stability in the detector itself for the pixel cluster counting method are typically estimated by studying the performance of the method over time and comparing it to simulations or other measurements.
+  %To mitigate these uncertainties, the CMS collaboration performs regular calibrations and monitoring of the detector performance, as well as cross-checks with other luminosity measurement techniques
+
+  %Systematic uncertainties due to stability in the detector itself for the pixel cluster counting method are typically estimated by studying the performance of the method over time and comparing it to simulations or other measurements.
 Uncertainties due to changes in the noise level and detector efficiency are typically estimated separately and combined to obtain the total systematic uncertainty
 
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.8\textwidth]{ashish_thesis/PCC_HFOCvsls_ProfileX_all_1.png}
+\caption[Luminosity Ratio Profile]{Profile of the PCC/HFOC luminosity as a function of lumi section.}
+\label{fig:stabprof1}
+\end{figure}
+
+%\begin{figure}[h]
+ % \centering
+  %\begin{subfigure}[b]{0.49\textwidth}
+   % \includegraphics[width=\textwidth]{ashish_thesis/PCC_HFOCvsls_ProfileX_all.png}
+    %\caption{Image 1}                                                                                                                                                                  
+  %\end{subfigure}
+  %\hfill % or \hspace{5mm} for a specific horizontal space                                                                                                                              
+  %\begin{subfigure}[b]{0.49\textwidth}
+   % \includegraphics[width=\textwidth]{ashish_thesis/PCCvsHFOC_ProjectionY_all.png}
+    %\caption{Image 2}                                                                                                                                                                  
+  %\end{subfigure}
+  %\caption[Stability of PCC luminosity compared to HFOC]{Left: Profile of the PCC/HFOC luminosity as a function of lumi section.
+Right: Histogram filled with the ratio of PCC/HFOC luminosity per lumi section.}
+%\label{fig:stabprof}
+%\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.8\textwidth]{ashish_thesis/ProjY_ProfileX_h_ratio_all_1.png}
+\caption[Projection Of Luminosity Ratio Profile]{%
+Distribution of the ratio of PCC/HFOC luminosity evaluated per 50 lumi section blocks. 
+}
+\label{fig:stabprof1}
+\end{figure}
+
 %\begin{figure}[!htp]
@@
 
-\item Linearity: the luminosity obtained from the PCC method is compared to that obtained from the HFOC method for a given set of collisions.
+\newpage
+\item Linearity: The response of a detector might not always be the same at different luminosity levels.
+In other words, a detector might respond differently when there are more particles passing through it per unit of time (higher luminosity) compared to when there are fewer particles (lower luminosity).
+This is particularly relevant at the high luminosities achieved.
+Linearity of PCC luminosity with HFOC luminosity is shown in Fig.
+\ref{fig:stabprof2}.
+%Pileup Conditions Affect the Linearity of Luminosity Measurement
+Pileup events are common at high luminosities and can affect the linearity of the luminosity measurement.
+If the detector or the counting system is unable to accurately count the number of pileup events, the count rate might not increase linearly with the actual luminosity, leading to a non-linear response.
+%This could introduce a systematic bias in the luminosity measurement, especially at high luminosities.
+%High Pileup Can Cause Over- or Underestimation of Luminosity
+%At high pileup conditions, the counting system may fail to distinguish between individual particle events and hence underestimate the actual number of particles, leading to an underestimation of the luminosity.
+Conversely, pileup can also potentially lead to overestimation of the luminosity if multiple particles are mistakenly counted as a single, more energetic particle.
+%The Product of Slope and Luminosity Range is a Measure of Linearity Systematic Uncertainty
+%In a perfect scenario, the  rate should increase linearly with the luminosity, and the slope of this relationship should be constant.
+However, due to non-linearities in the detector response, the slope can vary depending on the luminosity level as shown in Fig.
+\ref{fig:lin_unc}.
+This variability in the slope can be used to quantify the linearity systematic uncertainty.
+
+A linear fit is done to study change in detector response at different luminosity levels.
+By multiplying the slope by the luminosity range (the difference between the highest and lowest luminosity levels), we obtain a measure of how much the  rate is expected to vary due to non-linearity over that luminosity range.
+This product can be used as an estimate of the linearity systematic uncertainty in the luminosity measurement.
+
+  %the luminosity obtained from the PCC method is compared to that obtained from the HFOC method for a given set of collisions.
 Any deviations between the two measurements are used to estimate the linearity uncertainty in the PCC method.
 
-  The linearity uncertainty is typically quantified as a systematic uncertainty in the luminosity measurement, expressed as a percentage of the measured luminosity.
+  %The linearity uncertainty is typically quantified as a systematic uncertainty in the luminosity measurement, expressed as a percentage of the measured luminosity.
 This uncertainty can be estimated by fitting the PCC and HFOC measurements to a linear function and calculating the deviation of the PCC measurement from the linear fit.
@@
 
-FCN=11192 FROM MIGRAD    STATUS=CONVERGED      40 CALLS          41 TOTAL
-                     EDM=3.66412e-15    STRATEGY= 1      ERROR MATRIX ACCURATE 
-  EXT PARAMETER                                   STEP         FIRST   
-  NO.   NAME      VALUE            ERROR          SIZE      DERIVATIVE 
-   1  p0           2.34306e-07   2.04110e-09   3.00000e-06  -1.82768e+02
-   2  p1           9.92659e-01   2.73960e-05   3.00000e-06  -1.37960e-02
-
- \item Afterglow:
+%\begin{figure}[!htp]                                                                                                                                                                   
+%\centering                                                                                                                                                                             
+%\includegraphics[width=0.6\textwidth]{ashish_thesis/PCC_HFOCvsHFOC_ProfileX_all.png}                                                                                                     
+%\caption[]{%                                                                                                                                                                           
+ %  Ratio of PCC/HFOC luminosity plotted as a function of HFOC luminosity to determine change in detector response over different luminosity levels.
+Slope of the linear fit is 2.34306e-07.
+%}
+%\label{fig:lin_unc}
+%\end{figure}
+
+%%\begin{table}[h]
+ % \centering
+  % \caption[Fit PCC luminosity]{Parameter values from fit}
+   % \begin{tabular}{ccccc}
+    %     Parameter Name & Value & Error \\
+     %   \hline
+      %   Slope &  7.21854e-07 & 7.61113e-09  \\
+       %  Intercept & 9.86768e-01 & 1.17605e-05  \\
+    %\end{tabular}
+    %\caption{Parameter values from fit}
+    %\label{tab:lin_fit}
+%\end{table}
+
+%\begin{figure}[h]
+%  \centering
+ % \begin{subfigure}[b]{0.49\textwidth}
+  %  \includegraphics[width=\textwidth]{ashish_thesis/PCCvsHFOC_ProfileX_Fill6961_1.png}
+    %\caption{Image 1}                                                                                                                                                                 
+  %\end{subfigure}
+  %\hfill % or \hspace{5mm} for a specific horizontal space                                                                                                                             
+ % \begin{subfigure}[b]{0.49\textwidth}
+  %  \includegraphics[width=\textwidth]{ashish_thesis/PCC_HFOCvsHFOC_ProfileX_Fill6961_1.png}
+    %\caption{Image 2}                                                                                                                                                                 
+  %\end{subfigure}
+  %\caption[2018 PCC linearity]{Left: Linearity of PCC compared to HFOC for fill 6961.
+Right: Ratio of PCC/HFOC luminosity plotted as a function of HFOC luminosity to determine change in detector response over different luminosity levels.
+Slope of the linear fit is 7.2e^{-7} $in units of$ (Hz/ub)^{-1}.}
+%\label{fig:stabprof2}
+%\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=1\textwidth]{ashish_thesis/PCCvsHFOC_ProfileX_Fill6961_2.png}
+  \caption[2018 PCC linearity]{Left: Linearity of PCC compared to HFOC for fill 6961. Right: Ratio of PCC/HFOC luminosity plotted as a function of HFOC luminosity to determ\
+ine change in detector response over different luminosity levels. Slope of the linear fit is 7.2e^{-7} $in units of$ (Hz/ub)^{-1}.}
+  \label{fig:stabprof2}
+\end{figure}
+
+\newpage
+\item Afterglow: Systematic uncertainty due to afterglow background are determined by calculating the mean of the type 1 and type 2 afterglow residuals that are defined as the ratio of the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch and ratio of the luminosity of the second and following empty bunches after a colliding bunch to the luminosity of the colliding bunch respectively.
 
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/type1res_gr0p5.png}
-\caption[]{%
-   Type 1 residual.
-
+%\begin{figure}[h]
+ % \centering
+  %\begin{subfigure}[b]{0.49\textwidth}
+   % \includegraphics[width=\textwidth]{ashish_thesis/type1res_gr0p5.png}
+    %\caption{Image 1}                                                                                                                                                                  
+  %\end{subfigure}
+  %\hfill % or \hspace{5mm} for a specific horizontal space                                                                                                                              
+  %\begin{subfigure}[b]{0.49\textwidth}
+   % \includegraphics[width=\textwidth]{ashish_thesis/type2res_gr0.5_rangefixed.png}
+    %\caption{Image 2}                                                                                                                                                                 
+  %\end{subfigure}
+  %\caption[PCC Afterglow Residuals]{Left: PCC afterglow correction type 1 residual as a function of instantaneous luminosity.
+The residual fraction is given by the ratio of the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch.
+Right: Type 2 residual as a function of instantaneous luminosity.
+These are given by the ratio of the luminosity of the second and following empty bunches after a colliding bunch to the luminosity of the colliding bunch.
+Random trigger PCC dataset for all periods are used to make these plots \cite{Sehrawat2023}.}
+%\label{fig:stabprof}
+%\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=1\textwidth]{ashish_thesis/type1res_gr0p5_1.png}
+  \caption[PCC Afterglow Residuals]{Left: PCC afterglow correction type 1 residual as a function of instantaneous luminosity. The residual fraction is given by the ratio of\
+ the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch. Right: Type 2 residual as a function of instantane\
+ous luminosity. These are given by the ratio of the luminosity of the second and following empty bunches after a colliding bunch to the luminosity of the colliding bunch. Ra\
+ndom trigger PCC dataset for all periods are used to make these plots \cite{Sehrawat2023}.}
+  \label{fig:stabprof}
+\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/type1res_gr0p5.png}
+%\caption[]{%
+ %  Type 1 residual.
+
+%}
+%\label{fig:type1}
+%\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/type2res_gr0.5_rangefixed.png}
+%\caption[]{%
+ % Type 2 residuals.  Mean value is 0.00267652.
+ %}
+%\label{fig:type2}
+%\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/type1res_frac.png}
+%\caption[]{%
+ %  Type 1 residual fraction.
+%}
+%\label{fig:type2}
+%\end{figure}
+
+\end{itemize}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=0.6\textwidth]{ashish_thesis/type1frac_gr0p5.png}
+%\caption[]{%
+ %  Type 1 afterglow fraction as a function of single-bunch instantaneous luminosity.
+Random trigger PCC dataset for all periods are used to make this plot.
 }
-\label{fig:type1}
-\end{figure}
-
-%\begin{figure}[!htp]
-%\centering
-%\includegraphics[width=1\textwidth]{ashish_thesis/type2_res.png}
-%\caption[]{%
-
- % Type 2 residuals.
-%}
 %\label{fig:type2}
@@
 
-%\begin{figure}[!htp]
-%\centering
-%\includegraphics[width=1\textwidth]{ashish_thesis/type2res_gr0.5.png}
-%\caption[]{%
-
- % Type 2 residuals.
+\end{itemize}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/h_ProfileX_PCC_HFOCvsHFOC_all.png}
+%\caption[]{%
+
+ %  Type 1 residual fraction.
+
 %}
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/type2res_gr0.5_rangefixed.png}
-\caption[]{%
-  Type 2 residuals.  Mean value is 0.00267652.
- }
-\label{fig:type2}
-\end{figure}
-
-%\begin{figure}[!htp]
-%\centering
-%\includegraphics[width=1\textwidth]{ashish_thesis/type1res_frac.png}
+%\begin{figure}[h]
+ % \centering
+  %\begin{subfigure}[b]{0.49\textwidth}
+   % \includegraphics[width=\textwidth]{ashish_thesis/PCC_HFOCvsls_ProfileX_all.png}
+    %\caption{Image 1}
+  %\end{subfigure}
+  %\hfill % or \hspace{5mm} for a specific horizontal space
+  %\begin{subfigure}[b]{0.49\textwidth}
+   % \includegraphics[width=\textwidth]{ashish_thesis/PCCvsHFOC_ProjectionY_all.png}
+    %\caption{Image 2}
+  %\end{subfigure}
+  %\caption{Left: }
+%\label{fig:stabprof}
+%\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=0.6\textwidth]{ashish_thesis/ProjY_ProfileX_h_ratio_all.png}
 %\caption[]{%                                                                                                                                                                         
@@
 
-\end{itemize}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/type1frac_gr0p5.png}
-\caption[]{%
-   Type 1 residual fraction.
-}
-\label{fig:type2}
-\end{figure}
-
-\end{itemize}
-
-%\begin{figure}[!htp]
-%\centering
-%\includegraphics[width=1\textwidth]{ashish_thesis/h_ProfileX_PCC_HFOCvsHFOC_all.png}
-%\caption[]{%
-
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/PCC_HFOCvsHFOC_ProfileX_all.png}
+%\caption[]{%                                                                                                                                                          
  %  Type 1 residual fraction.
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/PCC_HFOCvsHFOC_ProfileX_all.png}
-\caption[]{%                                                                                                                                                          
-   Type 1 residual fraction.
-
-}
-\label{fig:type2}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/PCC_HFOCvsHFOC_ProfileX_residuals_all.png}
-\caption[]{%                                                                                                                                                         
-   Type 1 residual fraction.
-
-}
-\label{fig:type2}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/PCC_HFOCvsls_all.png}
-\caption[]{%                                                                                                                                                         
-   Type 1 residual fraction.
-
-}
-\label{fig:type2}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/PCC_HFOCvsls_ProfileX_all.png}
-\caption[]{%                                                                                                                                                         
-   Type 1 residual fraction.
-
-}
-\label{fig:type2}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/PCCvsHFOC_all.png}
-\caption[]{%
-
-   Type 1 residual fraction.
-
-}
-\label{fig:type2}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/PCCvsHFOC_ProfileX_all.png}
-\caption[]{%
-
-   Type 1 residual fraction.
-
-}
-\label{fig:type2}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/PCCvsHFOC_ProfileX_residuals_all.png}
-\caption[]{%                                                                                                                                                         
-   Type 1 residual fraction.
-
-}
-\label{fig:type2}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/PCCvsHFOC_ProjectionY_all.png}
-\caption[]{%
-
-   Type 1 residual fraction.
-
-}
-\label{fig:type2}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/ProjY_ProfileX_h_ratio_all.png}
-\caption[]{%
-
-   Type 1 residual fraction.
-
-}
-\label{fig:type2}
-\end{figure}
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/PCC_HFOCvsHFOC_ProfileX_residuals_all.png}
+%\caption[]{%                                                                                                                                                         
+ %  Type 1 residual fraction.
+
+%}
+%\label{fig:type2}
+%\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/PCC_HFOCvsls_all.png}
+%\caption[]{%                                                                                                                                                         
+ %  Type 1 residual fraction.
+
+%}
+%\label{fig:type2}
+%\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/PCC_HFOCvsls_ProfileX_all.png}
+%\caption[]{%                                                                                                                                                         
+ %  Type 1 residual fraction.
+
+%}
+%\label{fig:type2}
+%\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/PCCvsHFOC_all.png}
+%\caption[]{%
+
+ %  Type 1 residual fraction.
+
+%}
+%\label{fig:type2}
+%\end{figure}
+
+%\begin{figure}[h]
+%  \centering
+ % \begin{subfigure}[b]{0.49\textwidth}
+  %  \includegraphics[width=\textwidth]{ashish_thesis/PCCvsHFOC_ProfileX_all.png}
+    %\caption{Image 1}                                                                                                                                                                
+  %\end{subfigure}
+  %\hfill % or \hspace{5mm} for a specific horizontal space                                                                                                                            
+  %\begin{subfigure}[b]{0.49\textwidth}
+   % \includegraphics[width=\textwidth]{ashish_thesis/PCCvsHFOC_ProfileX_residuals_all.png}
+    %\caption{Image 2}                                                                                                                                                                
+  %\end{subfigure}
+  %\caption{Left: }
+%\label{fig:stabprof}
+%\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/PCCvsHFOC_ProfileX_all.png}
+%\caption[]{%
+
+ %  Type 1 residual fraction.
+
+%}
+%\label{fig:type2}
+%\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/PCCvsHFOC_ProfileX_residuals_all.png}
+%\caption[]{%                                                                                                                                                         
+ %  Type 1 residual fraction.
+
+%}
+%\label{fig:type2}
+%\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/PCCvsHFOC_ProjectionY_all.png}
+%\caption[]{%
+
+ %  Type 1 residual fraction.
+
+%}
+%\label{fig:type2}
+%\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/ProjY_ProfileX_h_ratio_all.png}
+%\caption[]{%                                                                                                                                                         
+ %  Type 1 residual fraction.
+%}
+%\label{fig:type2}
+%\end{figure}
+
+The systematic uncertainty during 2018 luminosity measurement for final veto is shown in Table \ref{tab:systematic-uncertainty}.
+
+\begin{comment}
+X-Y Nonfactorization: The uncertainty associated with the assumption of independent proton distributions in the X and Y dimensions decreases from 2\% under the PAS veto to 0.4\% under the final veto.
+
+Bunch to Bunch Variation: The uncertainty related to variability between different bunches of protons reduces from 0.3\% under the PAS veto to 0.1\% under the final veto.
+
+Background Subtraction: The uncertainty from the process of estimating and subtracting background noise reduces from 0.1\% under the PAS veto to 0.06\% under the final veto.
+
+Afterglow: The uncertainty related to the lingering signal (afterglow) following a high-intensity bunch significantly drops from 0.5\% under the PAS veto to 0.003\% for Type 1 afterglow and 0.27\% for Type 2 afterglow under the final veto.
+
+Cross Detector Stability: The uncertainty due to changes in detector stability reduces from 0.6\% under the PAS veto to 0.2952\% under the final veto.
+
+Linearity: The uncertainty from non-linear detector responses decreases from 1.1\% under the PAS veto to 0.35\% under the final veto.
+
+%\begin{comment}
 
@@
 \centering
-\caption{Systematic Uncertainty}
 \label{tab:systematic-uncertainty}
 \begin{tabular}{cccc}
-\textbf{N/I} & \textbf{Systematic names} & \textbf{Uncertainty (PAS) [\%]} & \textbf{Uncertainty (Final veto) [\%]} \\
+  \textbf{}&\textbf{Systematics} &\textbf{Uncertainty(PAS)[\%]}&\textbf{Uncertainty(Finalveto)[\%]} \\
 \hline
@@
  & Background subtraction & 0.1 & 0.06 \\
-Integration & Afterglow & 0.5 & 0.3 \\
- & Cross detector stability & 0.6 & 0.24 \\
+Integration & Afterglow & 0.5 & 0.003 \bigoplus$ 0.27 \\
+ & Cross detector stability & 0.6 & 0.2952 \\
  & Linearity & 1.1 & 0.35 \\
-Total & -- & 2.47 & 0.813 \\
+Total & -- & 2.47 & 0.739 \\
 \end{tabular}
+\caption[Systematic uncertainty]{Systematic uncertainty during calibration and physics data taking for PAS and final veto.}
+\label{tab:systematic-uncertainty}
 \end{table}
+
+\end{comment}
+
+\begin{table}[htbp]
+  \centering
+  \caption[2018 Luminosity systematic uncertainty]{Systematic uncertainty during calibration and physics data taking for the final veto.}
+\label{tab:systematic-uncertainty}
+\begin{tabular}{cccc}
+  \textbf{}&\textbf{Systematics} &\textbf{Uncertainty [\%]} \\
+\hline
+Normalization & Length scale & 0.2  \\
+ & Orbit drift &  0.2  \\
+ & x-y nonfactorization & 0.6 \\
+ & Beam-beam deflection + Dynamic $\beta^{*}$  & 0.2 \\
+ & Beam current calibration  & 0.2 \\
+ & Ghost and satellite & 0.1 \\
+ & Scan to scan variation & 0.3 \\
+ & Bunch to bunch variation & 0.1 \\
+ & Cross detector consistency  & 0.5 \\
+ & Background subtraction  & 0.1 \\
+Integration & Afterglow  &  0.3 \\
+ & Cross detector stability & 0.3 \\
+ & Linearity  & 0.4 \\
+Total &  &  1.08 \\
+\end{tabular}
+%\caption[Systematic uncertainty]{Systematic uncertainty during calibration and physics data taking for PAS and final veto.}
+\label{tab:systematic-uncertainty}
+\end{table}

### 2023-12-17 tesis_Ashish/Chapter5/chapter5.tex
Sehrawat A thesis 17 Dec 2023

--- 2023-06-16 tesis_Ashish/Chapter5/chapter5.tex
@@
 %\label{sec:sysunc}
+
+%Please ask Luis for latest 2022 calibration plots
+
+%module veto plots are in slides from Antonio in December PCC meeting
+
+%Afterglow residuals are in my slides in PCC meeting  January , February
+
+%Chapter 5: Run 3 Luminosity Measurement
+
+%Detector Module selection
+%Afterglow Model- Detector Module selection
+%vdM Calibration Results
+%Luminosity for Physics Fills
+%Systematic Uncertainties
+
+\section{Dataset}
+
+To investigate the performance of the PCC luminometer during the 2022 data collection period, we segment CMS luminosity data into five distinct periods:  C, D, E, F, and G, as illustrated in Figure \ref{fig:period_bound_1}.
+The run ranges associated with each of these periods are outlined in Fig.
+\ref{fig:period_bound_1}.
+Notably, during period F, specifically during Fill 8381, van der Meer (vdM) scans were implemented to calibrate the PCC luminometer.
+For our current analysis, we employ dataset that align with the 2022 luminosity measurement periods, specifically 2022C, 2022D, 2022E, and 2022F, Run 2022G as highlighted in Table \ref{tab:my_label_1}.
+We extracted these datasets from the Alignment and Calibration (AlCa) project, a critical aspect of the CMS experiment.
+The selected datasets encompass two subcategories, namely Random trigger and Zero Bias similar to Run 2 PCC dataset.
+%The Random trigger dataset includes data where triggers are applied to both colliding and non-colliding bunches and the Zero Bias dataset consists of events that have successfully navigated the trigger system without any bias (no use of CMS detector signal), in this case, the trigger is applied exclusively to the colliding bunches.
+
+\begin{figure}[!htp]
+  \centering
+  %\caption[2018 CMS luminosity data taking periods]{ 2022 luminosity data taking periods showing data taking period boundaries.}
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_lumi_datasets.png}
+\caption[2022 CMS Luminosity Data Periods]{%                                                                                                                                              
+   2022 luminosity data taking periods showing data taking period boundaries.
+}
+\label{fig:period_bound_1}
+\end{figure}
+
+\begin{table}[h]
+  \centering
+  \caption[2022 run ranges]{Run periods, run number ranges and dates.}
+\begin{tabular}{ccc}
+%\hline
+\textbf{Run Period} & \textbf{Run Number Range} & \textbf{Date} \\
+\hline
+C & 355862 - 357401 & 2022-07-19 to 2022-08-12 \\
+%\hline
+D & 357538 - 357900 & 2022-08-15 to 2022-08-23 \\
+%\hline
+E & 359268 - 360327 & 2022-09-23 to 2022-10-14 \\
+%\hline
+F & 360390 - 362167 & 2022-10-14 to 2022-11-17 \\
+%\hline
+G & 362433 - 362760 & 2022-11-21 to 2022-11-28 \\
+%\hline
+\end{tabular}
+%\caption[Run period details]{Run periods, run number ranges and dates.}
+\label{tab:my_label_1}
+\end{table}
+
+\section{Detector module selection}
+
+%The primary goal of PCC is to measure luminosity by counting charged particle clusters detected in the pixel detector, comprised of 1856 pixel modules.
+However, some modules are inconsistent due to issues like radiation damage or electronic malfunctions.
+To ensure accurate luminosity measurement, the performance of each module is continually assessed using a metric called the 'module weight', which is the ratio of a module's PCC to the total PCC as shown in Fig.
+\ref{fig:test}.
+If this weight shows significant fluctuations over time, the module might be unreliable.
+During each 23.36-second interval, termed a lumi section, an extensive analysis of these module weights is conducted.
+
+The method for selecting reliable modules based on their performance, using the module weight, is detailed in section 4.2.
+Its significance in identifying consistent modules are illustrated in Fig.
+\ref{fig:test}.
+Evaluations are undertaken in lumi sections.
+Modules with consistent performance throughout 2022 are focused upon.
+Unreliable modules are added to a "module veto list", ensuring their data is excluded from luminosity calculation, thus preserving data accuracy.
+While all modules can be part of the luminosity measurement, only around 10\% withstand the rigorous selection criteria.
+The selection focuses on evaluating each module's stability using zero-bias dataset.
+
+\begin{figure}[ht]
+  \centering
+  %\caption[Good and bad module weight profile]{Module weight profile showing good and bad module during Run 2022F.}
+\begin{subfigure}{0.49\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{ashish_thesis/2022_good_module_1.png}
+  %\caption{}                                                                                                                                                                 
+  \label{fig:sub1}
+\end{subfigure}%                                                                                                                                                              
+\begin{subfigure}{0.49\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{ashish_thesis/2022_bad_module_1.png}
+  %\caption{}                                                                                                                                                                 
+  \label{fig:sub2}
+\end{subfigure}
+\caption[Good/Bad Module Weight Profile]{Module weight profile as a function of lumi section showing good (left) and bad (right) module during Run 2022F.
+The horizontal red line is the mean of the module weight.}
+\label{fig:test}
+\end{figure}
+
+%\begin{itemize}
+ %   \item \textbf{Stability over Time:} Modules maintaining consistent relative contributions during standard physics runs are retained.
+If they deviate beyond an initial 5-10\% range, as gauged by the RMS-to-Mean distribution of cluster counts, they're excluded.
+This exclusion process is repeated two or three times, removing outliers with each iteration as shown in Fig.
+\ref{fig:stab_deviation_2022}.
+
+  %  \item \textbf{Linearity:} The analysis centers on a module's response to instantaneous luminosity, measured by the average Pixel Cluster Count (PCC) per module.
+Two figures elucidate this: one detailing an individual module's response and another offering a cumulative histogram for all modules as shown in Fig.
+\ref{fig:lin_deviation_2022}.
+%\end{itemize}
+
+For module evaluation, the steps include:
+\begin{enumerate}
+    \item Lumi sections with low statistics are removed based on total PCC.
+    \item All barrel Layer-0 modules are sidestepped due to their vulnerability to dynamic inefficiency.
+    \item An intial filtering removes modules with 7\% average deviation of the module weight from its mean (shown in Fig.
+\ref{fig:stab_deviation_2022}).
+%Subsequent adjustments tighten this criterion, illustrated by further refinements to 2\% and 0.8\% respectively.
+
+    \item Module stability is reviewed using an iterative method.
+In the case of the 2022F dataset, we introduce additional criteria at 2\% and 0.8\%.
+For different data periods, the specific values used depend on how good the initial module list is.
+
+    \item The selection of modules based on their linearity relies on assessing the average deviation of the module weight v.s.
+the average PCC per module (shown in Fig.
+\ref{fig:lin_deviation_2022}).
+This process typically requires either one or two iterations.
+To illustrate, during the 2022F period, we first apply a 0.4\% selection criterion, followed by a more stringent 0.25\% selection.
+
+\end{enumerate}
+
+%The quality of the initial module list determines the precision in ensuing data periods.
+For periods C, D, E, and G, the Run 2022F module veto list is used as a starting point.
+During the vdM fill, modules evincing instability or high noise are dismissed.
+%Table \ref{tab:bad_modules} delivers a comprehensive rundown of omitted modules for the 2022 datasets.
+
+\begin{figure}[!htp]
+  \centering
+  %\caption[2018 CMS luminosity data taking periods]{ 2022 luminosity data taking periods showing data taking period boundaries.}
+\includegraphics[width=1\textwidth]{ashish_thesis/stability_deviation_2022_1.png}
+\caption[Module Weight Standard Deviation]{%
+  During Run 2022F, the distribution illustrates the average deviation of the module weight over it's mean for all modules.
+}
+\label{fig:stab_deviation_2022}
+\end{figure}
+
+\begin{figure}[!htp]
+  \centering
+  %\caption[2018 CMS luminosity data taking periods]{ 2022 luminosity data taking periods showing data taking period boundaries.}
+\includegraphics[width=1\textwidth]{ashish_thesis/linearity_deviation_2022_1.png}
+\caption[Module Linearity & Linearity Deviation Distribution]{%
+ Left: Linearity profile, module weight as a function of average PCC per module for one module in Run 2022F.
+Right: For all modules in Run 2022F, the distribution displays average deviations of the module weight divided by their mean derived from their linearity profiles.
+}
+\label{fig:lin_deviation_2022}
+\end{figure}
+
+%The objective of reducing fluctuations in the PCC luminosity measurement is to guarantee accurate and reliable results.
+This is accomplished by creating a pixel module veto list for each time period to monitor and exclude problematic modules.
+The stability of each module is assessed by tracking the fluctuation in the ratio of the module's PCC to the total PCC, a value termed as the module weight, as demonstrated in Fig.
+\ref{fig:test}.
+The data acquired for luminosity measurements is partitioned into sections referred to as lumi sections, each spanning a duration of 23.36 seconds.
+During each lumi section, an in-depth analysis of the module weights for all pixel modules is carried out to monitor their performance progression over time.
+This critical step aids in the distinction between efficient and inefficient modules.
+The pixel modules selected for consideration are those that demonstrate a consistently reliable performance throughout the entirety of 2022.
+%Any modules failing to meet these standards are deemed inefficient and are hence excluded from the luminosity measurement.
+Through meticulous examination of the module weights and the strategic exclusion of inefficient modules from the study, we can substantially reduce instabilities in PCC luminosity measurement.
+This rigorous process assures the high quality of data used for luminosity measurement, paving the way for precision in the obtained results.
+
+\begin{comment}
+
+\begin{figure}[ht]
+\centering
+\begin{subfigure}{0.49\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{ashish_thesis/2022_good_module.png}
+  %\caption{}
+  \label{fig:sub1}
+\end{subfigure}%
+\begin{subfigure}{0.49\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{ashish_thesis/2022_bad_module.png}
+  %\caption{}
+  \label{fig:sub2}
+\end{subfigure}
+\caption[Good and bad module weight profile]{Module weight profile showing good and bad module during Run 2022F.}
+\label{fig:test}
+\end{figure}
+
+\end{comment}
+
+%The basic premise of PCC is to count the number of clusters of charged particles detected in the pixel detector, and use this count to calculate the luminosity.
+The pixel detector is composed of thousands of small, sensitive components known as pixel modules.
+These pixel modules detect and measure particles passing through them, which provides the raw data used to calculate luminosity.
+However, not all pixel modules perform consistently.
+Factors like radiation damage, aging, or electronic faults can cause a module to give incorrect or inconsistent readings.
+When a module isn't working correctly, its data can introduce significant errors into the luminosity measurement.
+If a module is found to be performing poorly or inconsistently, it is added to a "module veto list." This list is a record of all the pixel modules that have been identified as unreliable.
+The 'veto' in the module veto list refers to the act of explicitly excluding or disregarding the data from the listed modules in the luminosity calculation to prevent them from skewing the results.
+%Creating and maintaining the module veto list is a complex process that requires continual monitoring and analysis.
+%For each data-taking period, the module weight, which is the ratio of a module's PCC to the total PCC, is computed and tracked.
+If the module weight shows significant or unexplained variations, that could be a sign that the module is not performing correctly, and it may be added to the veto list.
+By doing so, the impact of these 'bad' modules is eliminated, and the luminosity measurement is improved, leading to more reliable and accurate data.
+%In essence, the module veto list is an important quality control tool used in the CMS experiment to ensure the highest possible accuracy and precision in their luminosity measurement.
+
+%Figure \ref{fig:period_bound_3} describes the distribution of the ratio of Root Mean Square (RMS) to the mean of the module weight profile for all modules.
+The module weight is a representation of each module's performance.
+The RMS over the mean provides a measure of the variation in the module weights.
+In this figure, a preliminary selection criterion of 7\% is used to identify and exclude 'bad' or poorly performing modules, i.e., modules whose RMS to mean ratio exceeds 7\% are considered bad and removed.
+
+%This process is iterative, employing different selection thresholds at each stage to systematically identify and exclude bad modules.
+Figure \ref{fig:period_bound_4} illustrates the RMS over mean module weight distribution, after second iterative selection step have been completed.
+Here, a stricter selection criterion of 4\% is applied.
+This means that any modules with an RMS to mean ratio exceeding 4\%, even after all previous selection stages, are added to the veto list for each period.
+These modules' data are excluded from the luminosity measurements for their respective period.
+Table \ref{tab:bad_modules} delivers a comprehensive rundown of omitted modules for the 2022 dataset.
+%The entire process, as depicted in these figures, is intended to ensure that the PCC luminosity measurement rely solely on data from the most stable and reliable modules, thereby enhancing the accuracy and precision of these measurement.
+
+Table \ref{tab:bad_modules} presents a quantitative summary of malfunctioning or "bad" modules across various periods.
+BPIX Layer0 has 96 bad modules.
+As we progress through the various periods in 2022 (from F to D), there is a general trend of increasing bad modules, both for stability and linearity considerations.
+This suggests that as time progresses, the number of malfunctioning modules tends to grow.
+The highest number of bad modules for stability is observed in the 2022D period with 1653 bad modules.
+On the other hand, the 2022D period also has the highest for linearity with 1677 bad modules.
+The vdM fill has 1693 bad modules, which is slightly higher than those in the 2022D period for stability but slightly less for linearity.
+There seems to be a consistent observation that for each given period, the number of bad modules under linearity considerations is either equal to or slightly higher than those under stability considerations \cite{bril2023moduleveto}.
+
+\begin{table}[h]
+  \centering
+  \caption[Bad modules per period]{Number of bad modules for selection on stability and linearity for various periods.}
+\begin{tabular}{lr}
+\textbf{Type Or Period/Step} & \textbf{\# of bad modules} \\
+\hline
+BPIX Layer0 & 96 \\
+2022F Stability & 983 \\
+2022F Linearity & 1195 \\
+2022C Stability & 1364 \\
+2022C Linearity & 1484 \\
+2022E Stability & 1553 \\
+2022E Linearity & 1570 \\
+2022G Stability & 1604 \\
+2022G Linearity & 1628 \\
+2022D Stability & 1653 \\
+2022D Linearity & 1677 \\
+vdM fill & 1693 \\
+\end{tabular}
+%\caption{Number of bad modules for selection on stability and linearity for various periods.}
+\label{tab:bad_modules}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Number of good modules in each layer/disk}
+\label{tab:2022ldmodules}
+\begin{tabular}{cc}
+\textbf{Layer/Disk} & \textbf{Number of Good Modules} \\
+\hline
+Layer 3 & 39 \\
+Layer 4 & 88 \\
+Disk 1 & 13 \\
+Disk 2 &  19\\
+Disk 3 &  4\\
+Total & 163\\
+% Add more empty rows as needed
+\end{tabular}
+\end{table}
+
+Table \ref{tab:2022ldmodules} presents the number of good modules in various layers and disks of the pixel detector after a final selection process.
+Layer 3 has 39 good modules, Layer 4 has 88, Disk 1 has 13, Disk 2 has 19, and Disk 3 has 4, totaling 163 modules.
+The stability of various pixel layers and disks after removing all modules in Layer 0 and for final veto are shown in Fig.
+\ref{fig:stabprof_69a}  and Fig.
+\ref{fig:stabprof_69b} respectively.
+
+\begin{comment}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_periodC_first_iteration}
+\caption[First Iteration to Remove Outlier Modules]{%
+  RMS/mean of module weight profile for all modules. A loose selection of 7\% is applied to remove bad modules. Appropriate selections are applied in each iterative step to remove other bad modules.
+}
+\label{fig:period_bound_3}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_periodC_final_iteration.png}
+\caption[Final Iteration To Remove Outlier Modules]{%
+ Second selection on RMS/mean of 4\% is applied.}
+}
+\label{fig:period_bound_4}
+\end{figure}
+
+\end{comment}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/2022_per_period_veto.png}
+%\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                         
+ % 2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data .
+%}
+%\label{fig:period_bound}
+%\end{figure}
+
+\begin{comment}
+
+Table \ref{table:1_2022} presents a summary of the number of good and bad pixel modules identified for different periods (C, D, E, F, and G) during the 2022 PCC luminosity measurement.
+It is structured into three columns: 'Period', 'Good Modules', and 'Bad Modules'.
+The 'Period' column lists the periods during which the luminosity measurements were taken.
+These are represented as C, D, E, F, and G.
+The 'Good Modules' column shows the count of pixel modules that consistently performed well and provided reliable data for each respective period.
+For instance, there are 1198 good modules in period C, 1289 in period D, and so on.
+The 'Bad Modules' column displays the number of pixel modules that were identified as problematic or unreliable during each period.
+These modules have shown signs of inconsistent performance, thereby added to the veto list.
+For example, there are 658 bad modules during period C, 567 in period D.
+It allows a clear comparison between the periods in terms of the quality of modules used in the luminosity measurements, highlighting the different counts of good and bad modules identified during each period.
+
+\begin{table}[h!]
+  \centering
+  \caption[2022 period veto]{Good and bad modules for each period using per period veto.}
+\begin{tabular}{ccc}
+\textbf{Period} & \textbf{Good Modules} & \textbf{Bad Modules} \\
+\hline
+C & 1198 & 658 \\
+D & 1289 & 567 \\
+E & 1274 & 582 \\
+F & 827 & 1029 \\
+G & 1347 & 509 \\
+\end{tabular}
+%\caption[2022 per period veto]{Good and bad modules for each period using per period veto.}
+\label{table:1_2022}
+\end{table}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/2022_common_veto.png}
+%\caption[2018 CMS luminosity data taking periods.]{%                                                                                                                                             
+ % 2022 luminosity data taking periods showing data taking period boundaries and vdM calibration data .
+%}
+%\label{fig:period_bound}
+%\end{figure}
+
+Table \ref{table:12_2022} provides a summary of the number of bad pixel modules identified over different combinations of periods (CD, CDE, CDEF, and CDEFG).
+The results are achieved using a 4\% rms common module veto list.
+The table is organized into two columns: 'Periods' and 'Bad Modules'.
+In the 'Periods' column, various combinations of periods are listed, which denote the time intervals during which the luminosity measurements are conducted.
+The listed combinations - CD, CDE, CDEF, and CDEFG - indicate that the analysis was done over expanding time frames, starting with periods C and D, then extending to include E, followed by F, and finally G.
+The 'Bad Modules' column provides the total number of bad or unreliable pixel modules identified across the listed combination of periods.
+For example, 886 bad modules are found over periods C and D, 1106 bad modules over periods C, D, and E \cite{bril2023moduleveto_1}.
+
+\begin{table}[h!]
+  \centering
+  \caption[Common module veto list]{4\% rms common module veto list. This veto list is created by combining module veto lists of each period.}
+\begin{tabular}{ccc}
+\textbf{Periods} &  \textbf{Bad Modules} \\
+\hline
+CD & 886 \\
+CDE & 1106 \\
+CDEF & 1307 \\
+CDEFG & 1411 \\
+\end{tabular}
+%\caption[Common module veto list]{4\% rms common module veto list. This veto list is created by combining module veto lists of each period.}
+\label{table:12_2022}
+\end{table}
+
+%\end{comment}
+
+%In a pixel system with 1856 modules, a module veto list filters out unstable modules for luminosity measurement. Only about 10\% pass strict criteria.
+
+%Modules are evaluated based on:
+
+%Stability: Modules with consistent contributions during standard physics runs are retained.
+Those deviating by initially 5-10\% from the average are excluded.
+This assessment, rooted in the RMS-to-Mean distribution of cluster counts, is iteratively refined.
+
+%Linearity: Modules are tested for response stability against effective instantaneous luminosity, gauged by the average PCC.
+
+%Using the Run 2022F veto list as a baseline for periods C, D, E, and G, additional unstable or noisy modules are identified and removed, especially during the vdM fill data phase.
+A summary of exclusions is provided in Table \ref{tab:bad_modules}.
+
+\begin{table}[h]
+  \centering
+  \caption{Number of bad modules for selection on stability and linearity for various periods.}
+\begin{tabular}{lr}
+\textbf{Type Or Period/Step} & \textbf{\# of bad modules} \\
+\hline
+BPIX Layer0 & 96 \\
+2022F Stability & 983 \\
+2022F Linearity & 1195 \\
+2022C Stability & 1364 \\
+2022C Linearity & 1484 \\
+2022E Stability & 1553 \\
+2022E Linearity & 1570 \\
+2022G Stability & 1604 \\
+2022G Linearity & 1628 \\
+2022D Stability & 1653 \\
+2022D Linearity & 1677 \\
+vdM fill & 1693 \\
+\end{tabular}
+%\caption{Number of bad modules for selection on stability and linearity for various periods.}
+\label{tab:bad_modules}
+\end{table}
+
+\end{comment}
+
+%A comprehensive examination of the performance and stability of the pixel detector layers and disks for each lumi section throughout the 2022 data-taking period is shown in Fig.
+\ref{fig:stabprof_69}.
+The figure on the left illustrates the proportional contribution to the total detected luminosity from different layers and disks of the pixel detector as a function of lumi section, with only Layer 1 modules vetoed.
+This plot essentially shows how the luminosity fraction, that is, the relative contribution to the total detected luminosity from each layer and disk, evolves over the course of the data-taking period.
+The layer 1 module veto indicates that malfunctioning or underperforming modules in Layer 1 of the pixel detector have been systematically excluded from the measurement.
+The figure on the right presents stability profiles of the pixel detector's layers and disks, taking into account a 4\% RMS common module veto list.
+%The stability of a module, determined in terms of its consistent response to incoming particles and reliability in data recording, is crucial for accurate measurements.
+The "4\% RMS common module veto list" refers to modules that have been omitted from data analysis due to their performance deviation - in terms of variability or RMS - exceeding 4\% from an expected value.
+
+\begin{figure}[!htp]
+  \centering
+  \includegraphics[width=0.7\textwidth]{ashish_thesis/PCC_stability_2022_L0veto_4.png}
+  \caption[Luminosity Fractions w/o Layer 0 Modules]{Luminosity fraction of pixel detector for various layer and disks as a function of lumi section for the entire 2022 data with all Layer 0 modules vetoed.}
+  \label{fig:stabprof_69a}
+\end{figure}
+
+\begin{figure}[!htp]
+  \centering
+  \includegraphics[width=0.7\textwidth]{ashish_thesis/2022_pcc_stability_2.png}
+  \caption[Stability Profiles For Final Veto]{Stability profiles of pixel detector layer and disk modules for the final module veto list.}
+  \label{fig:stabprof_69b}
+\end{figure}
+
+\begin{comment}
+
+\begin{figure}[!htp]
+  \centering
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{ashish_thesis/PCC_stability_2022_L0veto.png}
+    %\caption{Image 1}                                                                                                                                                                           
+  \end{subfigure}
+  \hfill % or \hspace{5mm} for a specific horizontal space                                                                                                                                      
+  \begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=\textwidth]{ashish_thesis/2022_pcc_stability.png}
+    %\caption{Image 2}                                                                                                                                                                           
+  \end{subfigure}
+  \caption[Pixel detector stability plots without and with veto list]{Left: Luminosity fraction of pixel detector for various layer and disks as a function of lumi section for the entire 2022 data  with all Layer 0 modules vetoed.
+Right: Stability profiles of pixel detector layer and disk modules for the final module veto list.}
+  \label{fig:stabprof_69}
+\end{figure}
+
+\end{comment}
+
+\newpage
+\section{vdM calibration results}
+
+The vdM calibration involves varying the position of the colliding proton beams horizontally and vertically and observing the changes in the event rate resulting from these shifts as a function of beam separation.
+This procedure allows us to determine the overlap integral of the beam profiles, which is an essential part of the absolute luminosity calculation.
+In the context of PCC, the event rate corresponds to the number of pixel clusters detected per unit time.
+Therefore, by observing how this rate changes with the beam positions, the calibration constant of the PCC luminometer can be determined.
+% the efficiency and response of the pixel detector.
+
+%The key steps of the vdM calibration procedure: Beam Separation Scans: Two beams are made to collide, and the number of collisions (events) is counted.
+The beam separation in either the horizontal or vertical direction is then progressively increased, and the change in the number of events is measured.
+This procedure allows for the determination of the spatial distribution of each beam, referred to as the beam profile.
+Fitting of Scan Data: The beam profiles obtained from the scans are then used to fit a function to the event rate as a function of beam separation.
+The maximum of this function gives the event rate when the beams are perfectly overlapped.
+Calculation of Luminosity: The luminosity is directly proportional to the event rate at perfect overlap and inversely proportional to the area of the beam profiles.
+Using these relationships, the absolute luminosity can be calculated.
+Calibration of the Detector: The calibration constant or visible cross section obtained from absolute luminosity and peak rate during vdM calibration is then used to calibrate the detector.
+
+van der Meer (vdM) scan was performed in November 2022, during the LHC fills 8379 and 8381.
+In fill 8381 on 10–11 Nov 2022, data was collected when 144 paired bunches of particles were colliding, with additional unpaired bunches also present, various scan pairs were conducted, including four vdM scans, two Beam Imaging (BI) scans, and one length scale scan.
+Each of these scans consists of two examinations in the x and y transverse planes.
+In the vdM scan, beams were separated by a distance correlating to six times transverse beam size and then moved across each other in 25 steps.
+Each step lasted 30 seconds and moved the beams by half of their transverse size.
+For the BI scans, one beam remained fixed while the other moved in 19 steps, over a distance of up to 4.5 times its transverse size.
+The length scale scan involved beams being separated by a constant distance and moved in both directions in five steps.
+The scan program during Fill 8381 is shown in Fig.
+\ref{fig:2022_vdM_program}.
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_vdM.png}
+\caption[2022 vdM Program]{%                                                                                                                                             
+  2022 vdM calibration program. In LHC fill 8381, proton beam positions were recorded, including four vdM scans, two BI scans, one LS scan, and two SS periods.
+}
+\label{fig:2022_vdM_program}
+\end{figure}
+
+%On November 10, 2022, during the LHC fill 8370, 58 paired bunches were colliding at the CMS Interaction Point (IP), with 12 extra unpaired bunches in each beam.
+An extra length scale scan pair was conducted during this fill.
+%Moreover, a secondary scan program occurred during LHC fill 8178 from September 24-26, 2022, focusing on data collection for the LHCf experiment.
+At the CMS IP, 144 bunch pairs were colliding with two additional unpaired bunches in each beam.
+%Several scans took place, but only results from three length scale scan pairs are mentioned here, one of which had nine steps per direction rather than the typical five.
+
+The result of the calibration is described in
+%Normalized Rates and Resulting Fitted Double Gaussian Scan Curves for Single Bunch in X and Y Directions:
+Figure \ref{fig:period_bound_50} which depict how the detected event rate varies as the beams are scanned across each other in the horizontal (X) and vertical (Y) directions.The rates have been fitted to a double Gaussian curve, which reflects the bell-shaped spatial distribution of the proton bunches.
+The peaks of these curves correspond to the maximum event rate, which occurs when the beams are perfectly overlapped.
+The width of the curve gives an indication of the spread of the beam in the respective direction.
+In the final analysis.
+a floating constant is used in the fit for the background because the background from the SS1 and SS2 give inconsistent values as shown in Table \ref{table:side_by_side}.
+
+\begin{table}[!htp]
+  \centering
+  \caption[2022 PCC background rate]{PCC background rate for five BCIDs during super separation scans 1 and 2. Average PCC background rate is calculated by averaging over all five BCIDs.}
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \begin{tabular}{ccc}
+          \hline
+            \multicolumn{3}{|c|}{SS 1} \\
+            \hline
+            BCID & Mean & SEM \\
+            \hline
+            282 & 0.03917 & 0.00147 \\
+            822 & 0.03896 & 0.00130 \\
+            2944 & 0.03979 & 0.00145 \\
+            3123 & 0.03788 & 0.00132 \\
+            3302 & 0.03931 & 0.00130 \\
+        \end{tabular}
+        \subcaption{SS1_{avg}= 0.039022 +- 0.000613}
+    \end{minipage}%
+    \hfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \begin{tabular}{ccc}
+            \hline
+            \multicolumn{3}{|c|}{SS 2} \\
+            \hline
+            BCID & Mean & SEM \\
+            \hline
+            282 & 0.07682 & 0.00128 \\
+            822 & 0.077513 & 0.00137 \\
+            2944 & 0.082114 & 0.00178 \\
+            3123 & 0.075385 & 0.00127 \\
+            3302 & 0.077605 & 0.00139 \\
+        \end{tabular}
+        \subcaption{SS2_{avg}= 0.0779018 -+ 0.00060436}
+    \end{minipage}
+    %\caption{PCC background rate for five BCIDs during super separation scans 1 and 2.
+Average PCC background rate is calculated by averaging over all five BCIDs.}
+    \label{table:side_by_side}
+\end{table}
+
+%Background subtraction and beam corrections have been applied to the raw data to account for noise.
+%Chi2/ndof for all vdM and Imaging Scans:
+%Figure \ref{fig:period_bound_51} provide an indication of the quality of the fits to the scan data.
+The $\chi^2$ statistic measures the discrepancy between the observed event rates and the values predicted by the double Gaussian fit, while ndof (number of degrees of freedom) accounts for the complexity of the fit.
+A value of  $\chi^2$/ndof close to 1 can be seen in the statistics box which signifies a good fit.
+PCC visible cross section is 1076 $\pm$ 0.9 (stat) mb as shown in Fig.
+\ref{fig:period_bound_105} \cite{bril2023vdmrecalibration}.
+
+%Beam Overlap Widths for each vdM and Imaging Scans:
+%Figure \ref{fig:period_bound_52} show the beam overlap widths, or the widths of the double gaussian fit, for each scan.
+%The overlap width essentially gives the size of the beam at the interaction point and is used to calculate the absolute luminosity.
+Comparison of these widths across different scans can reveal variations in the beam size over time.
+%Figure \ref{fig:period_bound_53} show the maximum event rate for each scan, which corresponds to the peak of the double gaussian fit.
+This peak rate is achieved when the beams are perfectly overlapped.
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_vdM_fit_1.png}
+\caption[2022 PCC vdM Fit]{%                                                                                                                                              
+  Rates and the resulting fitted double Gaussian scan curves as a function of the beam separation for a single bunch (BCID 282) as recorded by PCC for a vdM1 scan in the x (left) and y direction (right).
+Beam corrections have been applied to the raw data before the fit.
+}
+\label{fig:period_bound_50}
+\end{figure}
+
+\begin{comment}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.6\textwidth]{ashish_thesis/2022_vdM_fit_quality-png.png}
+\caption{%                                                                                                                                             
+  $\chi^2$/ndof for all vdM and imaging scans.
+}
+\label{fig:period_bound_51}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.6\textwidth]{ashish_thesis/2022_capsigma.png}
+\caption[Beam overlap widths]{%                                                                                                                                             
+  Beam overlap widths for each vdM and imaging scans.
+}
+\label{fig:period_bound_52}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.6\textwidth]{ashish_thesis/2022_peak.png}
+\caption[Peak PCC rate]{%                                                                                                                                             
+  Peak PCC rate for each vdM and imaging scans.
+}
+\label{fig:period_bound_53}
+\end{figure}
+
+\end{comment}
+
+%PCC visible cross section is 1076 $\pm$ 0.9 (stat) mb as shown in Fig. \ref{fig:period_bound_105}.
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.8\textwidth]{ashish_thesis/2022_sigma_vis_per_scan.png}
+\caption[2022 PCC Visible Cross Section]{%
+  Visible cross section per scan where red line shows the average value. Red band depicts the RMS of the values.
+}
+\label{fig:period_bound_105}
+\end{figure}
+
+\newpage
+\section{Luminosity for physics fills}
+
+The Fill cycle in Run 3 includes a leveling part in order to control the very high pileup achieved with upgraded LHC beam optics.
+The Fill luminosity profile for Fill 8274 during 2022 data taking is shown in Fig.
+\ref{fig:period_bound_111}.
+This Fill consists of
+
+\begin{itemize}
+
+\item 2450 colliding bunches
+
+\item 2600 lumi sections
+
+\item peak luminosity of $19000 \text{Hz} / \text{ub}$
+
+%\item minimum luminosity of 8.5 \times 10^{33} \, \text{cm}^{-2} \, \text{s}^{-1}
+
+\end{itemize}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/Fill_profile_8274_1.png}
+\caption[Fill 8274 Luminosity Profile]{%
+  PCC luminosity profile for Fill 8395.
+}
+\label{fig:period_bound_111}
+\end{figure}
+
+\newpage
+\subsection{Afterglow background corrections}
+
+%Figure \ref{fig:period_bound_44} and  \ref{fig:period_bound_45} describe the residuals of the PCC afterglow correction model fit as a function of instantaneous luminosity.
+The afterglow effect in PCC luminosity measurement refers to the lingering response of the detector to a previous collision event, which could lead to a systematic overestimate of the luminosity in subsequent bunch crossings.
+
+Corrections are introduced to the PCC measurement to mitigate background effects. The considered background contributions for physics fills are:
+
+\begin{itemize}
+    \item \textbf{Pedestal}: Represents a consistent noise in the pixel cluster count.
+
+    \item \textbf{Afterglow (Out-of-time counts)}:
+    \begin{itemize}
+        \item \textbf{Type 1}: Activations from the preceding bunch's pixels. Rectified by observing subsequent bunch clusters.
+
+        \item \textbf{Type 2}: Due to the detector's material activation, modeled using an exponential decay function for non-colliding bunches post-train.
+    \end{itemize}
+\end{itemize}
+
+Both pedestal and type-1 parameters are determined in each 50 LS blocks.
+
+Type-2 parameters, derived from a preceding study using Random trigger data, are presumed to remain constant during the year. The fitting template is given by:
+\begin{equation}
+F(x) = \Sigma_{k=0}^{N_{bcid}} N_k \left[(x-k==0)+\alpha\cdot(x-k==1)+A \cdot e^{-\tau\cdot(x-k-1)}(x-k>=1) \right]
+\end{equation}
+with $k$ denoting the colliding bunch crossing and $x$ indicating the histogram bin.
+2022 PCC afterglow model uses run number 361957 for doing fit to type 1 and type 2 afterglow effect in the PCC raw data as shown in Fig.
+\ref{fig:period_bound_101}.
+Model consist of a parameter for type 1 afterglow correcton and exponentially decaying function with two parameters amplitude and decay width to model type 2 afterglow correction.
+Fit function is summed over all bunch crossings.
+Fit perfomed for 4 wagon train is shown in Fig.
+\ref{fig:period_bound_102} in run 361957 to compute type 2 afterglow amplitude and decay width.
+The values obtained for type 2 afterglow amplitude and decay parameters are 0.0007915 and 0.00918 respectively \cite{bril2023afterglow}.
+%as shown in Table. \ref{table:trains_data}.
+
+%Type 1 Afterglow Effect: This effect pertains to the first empty bunch crossing immediately following a colliding bunch.
+Fig.
+\ref{fig:period_bound_44} visualizes the Type 1 residual as a function of instantaneous luminosity.
+The residual fraction is computed as the ratio of the luminosity measured in the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch itself.
+If the afterglow effect is significant, this ratio will be higher than expected, indicating that some of the signals attributed to the empty bunch actually originate from the preceding colliding bunch due to the afterglow effect.
+The objective of the Type 1 correction is to account for this lingering response and adjust the measured luminosity appropriately.
+%Type 2 Afterglow Effect: This effect pertains to the second and following empty bunch crossings after a colliding bunch.
+Fig.
+\ref{fig:period_bound_45} illustrates the Type 2 residual as a function of instantaneous luminosity.
+These residuals are calculated similarly to Type 1, but they use the luminosity measurements from the second and subsequent empty bunches after a colliding bunch.
+The ratio of these measurements to the luminosity of the colliding bunch provides an estimate of the extent of the afterglow effect beyond the immediate aftermath of a collision.
+The aim of the Type 2 correction is to account for any persistent afterglow effects that affect more than just the immediately following empty bunch.
+%The afterglow effect in PCC luminosity measurement could lead to a systematic overestimate of the luminosity in subsequent bunch crossings.
+%Figure \ref{fig:period_bound_44} and  \ref{fig:period_bound_45} describe the residuals of the PCC afterglow correction model fit as a function of instantaneous luminosity.
+The afterglow effect in PCC luminosity measurement refersto the lingering response of the detector to a previous collision event, which could lead to a systematic overestimate of the luminosity in subsequent bunch crossings.
+%The PCC afterglow model is designed to correct for these effects and thereby improve the accuracy of the luminosity measurement.
+The model calculates the residuals, evaluates their dependence on instantaneous luminosity, and applies correction factors to the luminosity measurements of both colliding and empty bunches.
+By doing so, it ensures that the measured luminosity is not artificially inflated due to the lingering detector response from previous collisions.
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.8\textwidth]{ashish_thesis/run_361957_ls_block_1.png}
+\caption[Raw PCC Run 361957]{%                                                                                                                                           
+ PCC per bx for fill 8307 for one 50 LS block. The first and ninth train are used to fit the afterglow tail.
+}
+\label{fig:period_bound_101}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.8\textwidth]{ashish_thesis/afterglow_fit_2022_1.png}
+\caption[Afterglow Fit 4-wagon]{%
+ Fit to 4-wagon train.
+}
+\label{fig:period_bound_102}
+\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/Run2022_af_model_run.png}
+%\caption[Raw PCC run 366800]{%                                                                                                                         
+% PCC per bunch crossing for run number 366800. Red circles are the trains that are fit.
+%}
+%\label{fig:period_bound_101}
+%\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/2022_four_wagon_fit.png}
+%\caption[Four wagon fit]{%                                                                                                                         
+% Fit for four wagon train using PCC raw data.
+%}
+%\label{fig:period_bound_102}
+%\end{figure}
+
+%\begin{table}[ht]
+ % \centering
+  %\caption[Type 2 parameters]{Type 2 afterglow parameters for increasing number of trains.}
+%\begin{tabular}{cccc}
+%\textbf{Train} & \textbf{Type1 f} & \textbf{Type2 a} & \textbf{Type2 b}\\
+%\hline
+%Train 1 & $1.98 \times 10^{-2} \pm 1.3 \times 10^{-3}$ & $7.58 \times 10^{-4} \pm 1.2 \times 10^{-5}$ & $1.53 \times 10^{-2} \pm 3.6 \times 10^{-4}$\\
+%Train 2 & $1.35 \times 10^{-2} \pm 1.7 \times 10^{-3}$ & $8.35 \times 10^{-4} \pm 1.5 \times 10^{-5}$ & $1.46 \times 10^{-2} \pm 4.0 \times 10^{-4}$\\
+%Train 3 & $2.25 \times 10^{-2} \pm 1.5 \times 10^{-3}$ & $7.76 \times 10^{-4} \pm 1.2 \times 10^{-5}$ & $1.55 \times 10^{-2} \pm 3.6 \times 10^{-4}$\\
+%Train 4 & $2.36 \times 10^{-2} \pm 1.3 \times 10^{-3}$ & $7.53 \times 10^{-4} \pm 1.2 \times 10^{-5}$ & $1.48 \times 10^{-2} \pm 3.6 \times 10^{-4}$\\
+%\end{tabular}
+%\caption[Type 2 parameters]{Type 2 afterglow parameters for increasing number of trains.}
+%\label{table:trains_data}
+%\end{table}
+
+\begin{comment}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/afterglow_t1f_vsinstlumi.png}
+\caption[2022 PCC type 1 afterglow fraction]{%                                                                                                                             
+  PCC afterglow correction type 1 fraction as a function of instantaneous luminosity for period Run 2022F.
+The residual fraction is given by the ratio of the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch.
+
+}
+\label{fig:period_bound_44}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/afterglow_t1res_vsinstlumi.png}
+\caption[2022 PCC Type 1 Afterglow Residuals]{%                                                                                                                                             
+ PCC afterglow correction type 1 residual as a function of instantaneous luminosity for period Run 2022F.
+The residual fraction is given by the ratio of the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch.
+
+}
+\label{fig:period_bound_44}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/afterglow_t2res_vsinstlumi.png}
+\caption[2022 PCC Type 2 Afterglow Residuals]{%                                                                                                                                             
+Type 2 residual as a function of instantaneous luminosity for period 2022F.
+These are given by the ratio of the luminosity of the second and following empty bunches after a colliding bunch to the luminosity of the colliding bunch.
+}
+\label{fig:period_bound_45}
+\end{figure}
+
+\end{comment}
+
+\begin{comment}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/PCC_stability_2022_L0veto.png}
+\caption[Pixel detector stability plots without veto list]{%                                                                                                                                      
+  Luminosity fraction of pixel detector for various layer and disks as a function of lumi section for Layer 1 module veto. 
+}
+\label{fig:period_bound}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_pcc_stability.png}
+\caption[Pixel detector stability plots with veto list]{%                                                                                                                                              
+  Stability profiles of pixel detector layer and disk modules for 4\% rms common module veto list.
+}
+\label{fig:period_bound}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \begin{subfigure}[b]{0.8\textwidth}
+    \includegraphics[width=\textwidth]{ashish_thesis/PCC_stability_2022_L0veto.png}
+    %\caption{Image 1}                                                                                                                                                                     
+  \end{subfigure}
+  %\hfill % or \hspace{5mm} for a specific horizontal space                                                                                                                                 
+  %\begin{subfigure}[b]{0.49\textwidth}
+   % \includegraphics[width=\textwidth]{ashish_thesis/2022_pcc_stability.png}
+    %\caption{Image 2}                                                                                                                                                                     
+  %\end{subfigure}
+  \caption[Pixel detector stability plots without and with common veto list]{Luminosity fraction of pixel detector for various layer and disks as a function of lumi section for Layer 1 module veto.} %Right: Stability profiles of pixel detector layer and disk modules for 4\% rms common module veto list.}
+  \label{fig:stabprof}
+\end{figure}
+
+\end{comment}
+
+\newpage
+Background estimations are obtained from the Random trigger datasets, processed in 50 LS blocks.
+The corrections, determined from these backgrounds, are subsequently applied to the zero-bias data.
+%Post-fitting residuals help in verifying the accuracy of the process.
+While Type 1 residuals are minimal, Type 2 shows a slight deviation of around 0.2\%.
+
+Comparable patterns are observed for 2022 periods E, F and G.
+During periods C and D, data was limited to the "AlCALumiPixelsEXPRESS" stream with an outdated module selection.
+Consequently, direct re-evaluation became unfeasible.
+As a solution, stored afterglow corrections, bolstered by a 1.008 factor from period E data, were applied.
+
+\section{PCC instantaneous and integrated luminosity}
+
+PCC instantaneous luminosity provides a measure of the collider's performance and is graphically represented in Fig.
+\ref{fig:period_bound_1000045}.
+Each fill in the graph consistently displays a sequence of characteristics related to luminosity.
+The process initiates with ramp-up periods, where a swift increase in luminosity is evident.
+This surge is subsequently followed by leveling parts, where luminosity stabilizes and plateaus.
+As the fill progresses, burn-off parts emerge, marked by a gradual decline in luminosity.
+Interspersed within the graph are notable, sharp drops to lower luminosity levels, characteristic of emittance scans.
+As each fill reaches its culmination, pronounced drops are observable, signifying the end of fill events.
+This cyclical pattern is evident across all fills, underscoring the systematic nature of the process.
+Integrated luminosity accumulates this data over time.
+For 2022, the total PCC integrated luminosity is calculated to be 38.61 $fb^{-1}$ \cite{bril2023randomzerobias}.
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/PCClumivslumisection_2022.png}
+\caption[2022 PCC Inst. Luminosity]{%
+  PCC instantaneous luminosity as a function of lumi section for entire 2022 year.
+
+}
+\label{fig:period_bound_1000045}
+\end{figure}
+
+\newpage
+\section{Systematic uncertainties}
+
+Various sources of systematic uncertainty come into play, affecting the precision of the results.
+These uncertainties arise from factors such as detector calibrations, alignment, temporal drifts in the detector response, modeling of the beam conditions, and potential nonlinearities in the detector response.
+Each of these factors necessitates careful calibration, modeling, and validation processes to ensure the highest accuracy in the luminosity measurement.
+%Addressing these systematic uncertainties is pivotal for the CMS collaboration to draw meaningful and reliable conclusions from its data.
+
+\subsection{vdM calibration uncertainties}
+
+\begin{itemize}
+
+\item XY-factorization: In the vdM calibration, the luminous area estimation, based on beam shapes, can lead to the "factorization bias." Methods to study factorization bias are
+
+\begin{itemize}
+
+\item \textbf{Beam-Imaging Method:} By using reconstructed collision vertices, this method estimates actual beam densities, which helps in refining the vdM-based luminous area.
+The following equation describes the relationship between the number of interaction points (vertices) and the proton densities of two beams at specific positions.
+
+\begin{equation}
+N_{\text{vertices}}(x, y; \Delta x) \propto \rho_1(x + \Delta x, y) \cdot \rho_2(x, y) \bigotimes V
+\end{equation}
+
+where
+\begin{itemize}
+  \item \(N_{\text{vertices}}(x, y; \Delta x)\): Represents the number of vertices or interaction points at a given beam separation in the x and y directions.
+The term \(\Delta x\) indicates the change or step in the x-direction.
+
+  \item \(\rho_1(x + \Delta x, y)\) and \(\rho_2(x, y)\): Represent the proton density distributions of the two beams at specific positions.
+The densities indicate how many protons are present at a particular point in space.
+
+  \item \(\bigotimes V\): Represents a convolution operation with \(V\), the vertex resolution.
+It's a mathematical way to combine two functions to produce a third function, used here to account for the limitations in measuring the exact position of the vertices due to the resolution of the detectors.
+\end{itemize}
+
+Combining all steps, we get
+
+\begin{align}
+\sum_{\Delta x} N_{\text{vertices}}(x, y; \Delta x) &\propto \sum_{\Delta x} \left[ \rho_1(x + \Delta x, y) \cdot \rho_2(x, y) \right] \otimes V \nonumber \\
+&\approx \int_{\Delta x} \left[ \rho_1(x + \Delta x, y) \cdot \rho_2(x, y) \right] \otimes V d\Delta x
+\end{align}
+
+The number of interaction points (vertices) observed depends on the proton densities of the two beams at specific positions, the separation between the beams in the x and y directions, and the precision with which these interaction points can be measured.
+By studying the change in the number of interaction points as the beams are moved closer or further apart, we can know about the proton densities of the beams and their distribution in space.
+The convolution with \(V\) ensures that the measurements are adjusted for the limitations of the detectors.
+
+%Data from four LHC scans are compiled into histograms and fitted using models describing beam shapes.
+Three fit models are employed: single-Gaussian (SG), double-Gaussian (DG), and super-Gaussian (SupG), each defining the beam shape differently based on beam widths and correlation parameters.
+The DG and SupG models involve combinations of "narrow" and "wide" components with specific parameter restrictions.
+The super-Gaussian fit most accurately describes the beam-imaging scan data, showing consistent results across all BCIDs.
+
+\item \textbf{Diagonal Scans:} Moving the beams at a 45° angle to the standard vdM direction in diagonal scans captures data across both x and y dimensions at the same time.
+This approach provides a unique view of how protons overlap and distribute in a two-dimensional plane.
+Instead of just seeing a linear view from one direction, the diagonal movement offers a comprehensive picture of the spread and patterns of protons in 2D.
+
+\item \textbf{Offset Scans:} In offset scans, the added separation in the direction not being actively scanned gives additional data points that wouldn't be captured in a standard vdM scan.
+This added separation means that the scan captures proton densities at slightly shifted positions.
+When combined with the regular vdM scan data, it offers a more detailed view of the proton distribution in two dimensions, helping to understand variations and potential irregularities in the 2D proton density.
+
+  %\item \textbf{Diagonal and Offset scans:} In diagonal scans, beams are moved simultaneously in x and y, at a 45° angle to the standard vdM direction offering a different perspective of overlap.
+In offset scans, along with the regular vdM scan movement, there's an added separation in the direction not being actively scanned.
+Luminometers like BCM1F, BCM1FUTCA, PLT were analyzed.
+   % Background, orbit drift, beam-beam corrections are applied.
+An extra orbit drift correction came from rate matching and 1D vdM fits.
+Data is saved as 2D graphs while VdMFramework uses less precise 1D graphs.
+2D fit functions include Single Gaussian, Super Gaussian, q-Gaussian, and variations of Double Gaussian.
+2D fitting involved pairing on-axis and off-axis scans.
+Off-axis scans were matched to the nearest vdM scans, combining rate values for clearer 2D shapes.
+
+%BCID dependence patterns correlate with LHC experiment collisions as there is periodic structure every fourth bunch, influenced by PS Booster effects.
+Averaged correction across off-axis+on-axis scan pairs is \(0.98 \pm 0.35\).
+Detectors' predictions align well.
+Data encoding reflects types and directions of shifts.
+Some evidence of an ellipsoidal shape tilted relative to the XY frame.
+Including all models modifies correction and RMS significantly.
+Largest contributors to corrections are BCID, model dependence, and OD systematics, yielding a combined RMS of \(0.35\%\).
+Considering all model uncertainties, this increases to \(0.45\%\).
+
+\end{itemize}
+
+%Factorization bias in VdM calibration is due to the assumption of factorizable beam shapes.
+This can be addressed by reconstructing transverse proton densities during a VdM fill, enabling a comparison of the luminous area to expected outcomes.
+The beam-imaging method, applied by CMS, uses reconstructed vertices to extract proton densities.
+Other methods, like diagonal and offset scans, examine different luminous area sections to understand factorization biases.
+CMS has explored these methods, with recent studies ongoing from 2022 data.
+
+\item Bunch to bunch uncertainty: The "bunch to bunch variation of PCC visible cross section" refer to how much the measured visible cross-section (and thus, the measured luminosity) changes from one bunch crossing to another as shown in Fig.
+\ref{fig:period_bound_99}.
+Variations could arise from different factors such as varying numbers of protons per bunch, spatial distribution of protons within the bunches, and the specific conditions of the pixel detector at the time of each bunch crossing.
+%These variations are important to monitor as they can impact the precision of the luminosity measurement, which in turn affects the accuracy of the results obtained from the physics analyses conducted with the data.
+If significant variations are observed, it may be necessary to adjust the analysis to account for these differences.
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.8\textwidth]{ashish_thesis/2022_sigma_vis_btob_variation.png}
+\caption[$\sigma_{vis}$ Bunch Variation]{%                                                                                                                                             
+  Bunch to bunch variation of PCC visible cross section where the red line is the average value. Red band depicts the $\pm$ one RMS of the values.
+}
+\label{fig:period_bound_99}
+\end{figure}
+
+%\begin{table}[!htp]
+ % \centering
+  %\caption[$\sigma_{vis}$ bunch uncertainty]{Bunch to bunch variation of visible cross section. $N_b$ is the number of bunches in the vdM scan.}
+%\begin{tabular}{ccccc}
+ %& \textbf{Scan} & \textbf{$\sigma_{vis}$ [mb]} & \textbf{RMS [mb]} & $\frac{\frac{\textbf{RMS}}{\sqrt{N_b}}}{\sigma_{\textbf{vis}}}$  [\%]} \\
+%\hline
+%1 & vdM1 & 4147.71 & 12.56 & 0.13 \\
+%2 & Img1 & 4151.50 & 12.22 & 0.13 \\
+%3 & Img2 & 4146.04 & 5.39 & 0.05 \\
+%4 & vdM3 & 4174.31 & 9.18 & 0.10 \\
+%5 & vdM4 & 4145.64 & 6.96 & 0.08 \\
+%\end{tabular}
+%\label{tab:my_label}
+%\end{table}
+
+\begin{table}[!htp]
+  \centering
+  \caption{Bunch to bunch variation of visible cross section. $N_b$ is the number of bunches in the vdM scan.}
+\begin{tabular}{cccc}
+\textbf{Scan} & \textbf{$\sigma_{vis}$ [mb]} & \textbf{RMS [mb]} & $\frac{\frac{\textbf{RMS}}{\sqrt{N_b}}}{\sigma_{\textbf{vis}}}$ [\%] \\
+\hline
+vdM1 & 1065.09 & 2.89 & 0.1286 \\
+Img1 & 1070.14 & 3.94 & 0.1746 \\
+Img2 & 1075.38 & 2.35 & 0.1040 \\
+vdM3 & 1083.58 & 3.70 & 0.1616 \\
+vdM4 & 1080.37 & 2.09 & 0.0920 \\
+\end{tabular}
+\label{tab:my_label}
+%\caption{Bunch to bunch variation of visible cross section. $N_b$ is the number of bunches in the vdM scan.}
+\end{table}
+
+\newpage
+\item Scan to scan uncertainty: PCC visible cross section can exhibit change from one scan to the next.
+These variations could be due to slight changes in the experimental conditions.
+The results for each scan are plotted after averaging over five BCIDs.
+Each point on this graph represent the result from one scan.
+A red line is drawn to indicate the average value of the visible cross-section over all the scans.
+This average value provide a useful comparison point to evaluate the consistency of the individual scan results and identify any potential anomalies or systematic errors.
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=0.6\textwidth]{ashish_thesis/2022_sigma_vis_per_scan.png}
+%\caption[2022 PCC visible cross section]{%                                                                                              
+ % Visible cross section per scan where red line shows the average value.
+%}
+%\label{fig:period_bound_105}
+%\end{figure}
+
+%Sigma Vis =  4.1694 +- 0.002 (stat) Barns
+%0.06\% statistical error
+%\section{Systematic uncertainties}
+
+\item Background subtraction: %The process of PCC correction involves eliminating undesired signals from a detector system that are not relevant to the physical phenomenon under study, such as noise or cosmic rays.
+  Machine-induced backgrounds are studied using two super separation scans 1 and 2.
+A floating constant is used in each fit and the uncertainty due to the background level is directly propagated to the result in the visible cross section values.
+
+\begin{comment}
+  The results from these scans show significant interpolation, leading to using floating background parameter in the fit which is a constant term to mimic machine induced backgrounds.
+Any uncertainty in the background rate directly contributes to the uncertainty in the final, corrected rate and thus luminosity.
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/SS_bkg_2022.png}
+\caption[2022 Backgound Estimation]{%                                                                                                                                              
+  2D histogram filled with the Avg. PCC evaluated per NB4, during the Super-Separation window.
+}
+\label{fig:ssbkg_2022}
+\end{figure}
+
+%\begin{comment}
+
+\begin{table}[!htp]
+  \centering
+  \caption[2022 PCC background rate]{PCC background rate for five BCIDs during super separation scans 1 and 2. Average PCC background rate is calculated by averaging over all five BCIDs.}
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \begin{tabular}{ccc}
+          \hline
+            \multicolumn{3}{|c|}{SS 1} \\
+            \hline
+            BCID & Mean & SEM \\
+            \hline
+            282 & 0.03917 & 0.00147 \\
+            822 & 0.03896 & 0.00130 \\
+            2944 & 0.03979 & 0.00145 \\
+            3123 & 0.03788 & 0.00132 \\
+            3302 & 0.03931 & 0.00130 \\
+        \end{tabular}
+        \subcaption{SS1_{avg}= 0.039022 +- 0.000613}
+    \end{minipage}%
+    \hfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \begin{tabular}{ccc}
+            \hline
+            \multicolumn{3}{|c|}{SS 2} \\
+            \hline
+            BCID & Mean & SEM \\
+            \hline
+            282 & 0.07682 & 0.00128 \\
+            822 & 0.077513 & 0.00137 \\
+            2944 & 0.082114 & 0.00178 \\
+            3123 & 0.075385 & 0.00127 \\
+            3302 & 0.077605 & 0.00139 \\
+        \end{tabular}
+        \subcaption{SS2_{avg}= 0.0779018 -+ 0.00060436}
+    \end{minipage}
+    %\caption{PCC background rate for five BCIDs during super separation scans 1 and 2. Average PCC background rate is calculated by averaging over all five BCIDs.}
+    \label{table:side_by_side}
+\end{table}
+
+%\begin{comment}
+
+\begin{table}[h]
+    \centering
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        %\caption{SS1   SS1_{avg}= 0.76804 +- 0.002478}
+        \begin{tabular}{ccc}
+        \textbf{BCID} & \textbf{Mean} & \textbf{SEM} \\ 
+        \hline
+        282 & .7734 & .00570 \\ 
+        822 & .7756 & .00578 \\ 
+        2944 & .7703 & .00599 \\ 
+        3123 & .7478 & .00505 \\ 
+        3302 & .7731 & .00521 \\ 
+        \end{tabular}
+        \caption[Super separation scan SS1]{SS1_{avg}= 0.76804 +- 0.002478}
+    \end{minipage}
+    \hfill
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        %\caption{SS2.  SS2_{avg}= 0.72026 -+0.002888}
+        \begin{tabular}{ccc}
+        \textbf{BCID} & \textbf{Mean} & \textbf{SEM} \\ 
+        \hline
+        282 & .7207 & .00521 \\ 
+        822 & .7247 & .00898 \\ 
+        2944 & .7306 & .00616 \\ 
+        3123 & .7038 & .00563 \\ 
+        3302 & .7215 & .00560 \\ 
+        \end{tabular}
+        \caption[Super separation scan SS2]{SS2_{avg}= 0.72026 -+0.002888}
+    \end{minipage}
+\end{table}
+
+\end{comment}
+
+%Super separation background flag applied is SS bkg= 0.058461 +- 0.00042725
+
+\end{itemize}
+
+\subsection{Integration uncertainties}
+
+\begin{itemize}
+
+\item Stability: Stability systematic uncertainties, often stem from time-variable factors such as detector aging, radiation damage, and noise fluctuations.
+Detectors used in high-energy physics are subject to a harsh radiation environment which can cause performance degradation over time.
+This degradation, if not accurately accounted for in the models, can introduce systematic uncertainties.
+%Furthermore, changes in noise levels can lead to overestimation or underestimation of luminosity due to false or missed signals.
+While data analysis techniques can suppress noise, any residual noise can introduce additional systematic uncertainty.
+  The stability systematic uncertainty is quantified by the standard deviation of the luminosity ratio from the best and second-best luminometer.
+A larger spread in measurements, indicated by a higher standard deviation, represents a greater systematic uncertainty due to temporal shifts in detector performance or environmental conditions.
+Fig.
+\ref{fig:stabprof_78} depicts the time evolution of ratio of luminosity values obtained from the PCC and the HFET luminometer.
+Each point on the x-axis represents a lumi section - a discrete time interval of data collection.
+The plot shows the variation in luminosity measurements across the data-taking period.
+This is crucial in calculating the systematic uncertainty related to stability, as any temporal fluctuations in luminosity could potentially indicate a source of uncertainty in the measurements.
+%The projection of the luminosity ratio.
+This projection, by condensing the two-dimensional information along the x axis and displaying the distribution of the luminosity measurements, can help identify any variations in the luminosity data that could contribute to systematic uncertainty.
+A uniform distribution would suggest good stability, while any deviations might point towards potential sources of systematic uncertainty.
+Fig.
+\ref{fig:stabprof1_79} shows the projection of the luminosity ratio using 50 lumi section binning strategy.
+%By grouping the lumi sections into larger bins, this visualization enables an aggregated view of luminosity data over broader intervals of the data-taking period.
+
+%Again, by studying the distribution and looking for any significant fluctuations, physicists can identify potential sources of systematic uncertainty due to instability in the measurements.
+
+\begin{figure}[!htp]
+  \centering
+  \begin{subfigure}[b]{1\textwidth}
+    \includegraphics[width=\textwidth]{ashish_thesis/PCC_HFOCvsls_ProfileX_all_2022_1.png}
+    %\caption{Image 1}                                                                                                                                                                                 
+  \end{subfigure}
+  \hfill % or \hspace{5mm} for a specific horizontal space
+  %\begin{subfigure}[b]{0.49\textwidth}
+   % \includegraphics[width=\textwidth]{ashish_thesis/PCCvsHFOC_ProjectionY_all_2022.png}
+    %\caption{Image 2}                                                                                                                                                             
+  %\end{subfigure}
+  \caption[Luminosity Ratio Profile]{Profile of the PCC/HFET luminosity as a function of integrated luminosity.} %Right: Histogram filled with the ratio of PCC/HFET luminosity per lumi section.}
+\label{fig:stabprof_78}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/ProjY_ProfileX_h_ratio_all_2022_1.png}
+\caption[Projection of Luminosity Ratio Profile]{%
+ Distribution of the ratio of PCC/HFET luminosity evaluated per 50 lumi section blocks.
+}
+\label{fig:stabprof1_79}
+\end{figure}
+
+\newpage
+\item Linearity: Detectors in high-energy physics experiments can display varying responses at different luminosity levels, leading to non-linear behavior, especially at high luminosities.
+%This variability is observable in the residuals of PCC luminosity compared to HFOC luminosity.
+To quantify the linearity systematic uncertainty, the slope variability of the detector response against luminosity levels can be analyzed.
+This, combined with the luminosity range, provides a measure of the expected rate variability due to non-linearity, representing the linearity systematic uncertainty.
+%Non-linear response during fill 8274 and three consecutive fill 8274, 8275 and 8276 is shown in Fig.
+\ref{fig:kinknon1_} and \ref{fig:kinknon_}.
+
+%"Kink" non-linearity is a specific type of response variation that we observed during 2022 fill  \cite{calibratedRunIIIPCC_AN-22-148}.
+This phenomenon is characterized by a sudden drop or "kink" in luminosity measurement in the middle of the fill, rather than a gradual or linear change as shown in Fig.
+\ref{fig:kinknon1_}.
+This behavior represents a distinct form of non-linearity where the detector's response to particle flow isn't consistent throughout the fill.
+Instead of maintaining a steady response, the detector experiences an abrupt change, causing a sudden decrease in the measured luminosity.
+This behaviour is not confined to a particular Fill but can be seen in three consecutive Fill in Fig.
+\ref{fig:kinknon_}.
+The root causes of this type of non-linearity is still unknown, potentially could be linked to changes in detector conditions, particle flux inconsistencies, or other experimental variables.
+A different approach to vetoing modules was able to fix this issue.
+%Efforts are ongoing to  understand and correct for kink non-linearity to achieve accurate luminosity measurement and reduce systematic uncertainty.
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=0.6\textwidth]{ashish_thesis/Kink_nonlinearity_oneFill.png}
+%\caption[]{%
+%Non-linearity during Fill 8274.
+%}
+%\label{fig:kinknon1_}
+%\end{figure}
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=0.6\textwidth]{ashish_thesis/2022_PCC_hfet_nonlinearity.png}
+%\caption[]{%
+%Non-linearity during 3 consecutive Fill 8274, 8275, 8276.
+%}
+%\label{fig:kinknon_}
+%\end{figure}
+
+The left plot in figure \ref{fig:stabprof2_2000} provides a comparison of the linearity of PCC luminosity in relation to HFET luminosity.
+A perfectly linear relationship would imply same luminosity measured by both the luminometers, suggesting an absence of non-linearity in the detector response.
+The plot on the right in \ref{fig:stabprof2_2000} shows the ratio of luminosity values obtained using the PCC method to those from the HFET luminometer.
+The values are plotted as a function of HFET luminosity.
+The goal of this graph is to examine potential changes in the detector's response across different luminosity levels.
+If the detector's response was perfectly linear, we do expect the ratio to remain constant across the range of HFET luminosity values.
+Deviations from a constant ratio indicate non-linearity in the detector response, thereby contributing to systematic uncertainties.
+
+%Linearity of PCC Compared to HFET and Residuals Obtained After Doing a Linear Fit: The left plot in figure \ref{fig:stabprof2_99} provides a visual comparison of the linearity of PCC luminosity in relation to HFET luminosity.
+A perfectly linear relationship would imply a constant ratio across all luminosity levels, suggesting an absence of non-linearity in the detector response.
+On the right, the residuals, i.e., the differences between the observed values (PCC/HFET ratio) and the values predicted by a linear fit, are plotted.
+If the residuals are randomly scattered around zero across all HFET luminosity values, this would support the assumption of linearity.
+However, if there's a systematic pattern in the residuals, it would suggest non-linearity, indicating potential sources of systematic uncertainty.
+
+\begin{comment}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.6\textwidth]{ashish_thesis/PCC_HFOCvsHFOC_ProfileX_all_2022_1.png}
+\caption[PCC Response To Luminosity]{%                                                                                                                                                                
+   Ratio of PCC/HFET luminosity plotted as a function of HFET luminosity to determine change in detector response over different luminosity levels.                                                    
+}
+\label{fig:lin_unc}
+\end{figure}
+
+\end{comment}
+
+%\begin{table}[h]
+ % \centering
+ % \caption{Parameter values from fit}
+  %  \begin{tabular}{ccccc}
+   %      Parameter Name & Value & Error \\
+    %    \hline
+     %    Slope & 2.76132e-07 & 2.97602e-09 \\
+      %   Intercept & 9.90718e-01 & 4.73417e-05 \\
+    %\end{tabular}
+    %\caption{Parameter values from fit}
+    %\label{tab:lin_fit_47}
+%\end{table}
+
+\begin{figure}[H]
+  \centering
+  %\begin{subfigure}[b]{0.49\textwidth}
+   % \includegraphics[width=\textwidth]{ashish_thesis/PCCvsHFOC_ProfileX_all_2022.png}
+    %\caption{Image 1}                                                                                                                                                                           
+  %\end{subfigure}
+  %\hfill % or \hspace{5mm} for a specific horizontal space                                                                                                                            
+  %\begin{subfigure}[b]{0.49\textwidth}
+    \includegraphics[width=0.7\textwidth]{ashish_thesis/PCC_HFOCvsHFOC_ProfileX_all_2022_1.png}
+    %\caption{Image 2}                                                                                                                                                                           
+  %\end{subfigure}
+    \caption[2022 PCC linearity]{%Left: Linearity of PCC compared to HFET.
+      Ratio of PCC/HFET luminosity plotted as a function of HFET luminosity to determine change in detector response over different luminosity levels.
+Slope is 0.00114 ub/Hz.
+% $ PCC and HFET iovtags used are pcc22v2 and hfet22v10.$
+  }
+
+\label{fig:stabprof2_2000}
+\end{figure}
+
+\item Afterglow: Systematic uncertainties from afterglow backgrounds are derived from the means of type 1 and type 2 afterglow residuals.
+These are determined by comparing the luminosity of the immediate empty bunch after a collision to the colliding bunch luminosity and comparing subsequent empty bunches' luminosity to the colliding bunch, respectively.
+
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/afterglow_t1f_vsinstlumi.png}
+%\caption[2022 PCC type 1 afterglow fraction]{%
+ % PCC afterglow correction type 1 fraction as a function of instantaneous luminosity for period Run 2022F.
+The residual fraction is given by the ratio of the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch.
+
+%}
+%\label{fig:period_bound_44}
+%\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/afterglow_t1res_vsinstlumi_1.png}
+\caption[2022 PCC Type 1 Afterglow Residuals]{%
+ PCC afterglow correction type 1 residual as a function of instantaneous luminosity for period Run 2022F.
+The residual fraction is given by the ratio of the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch.
+
+}
+\label{fig:period_bound_44}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/afterglow_t2res_vsinstlumi_1.png}
+\caption[2022 PCC Type 2 Afterglow Residuals]{%
+  Type 2 residual as a function of instantaneous luminosity for period 2022F.
+These are given by the ratio of the luminosity of the second and following empty bunches after a colliding bunch to the luminosity of the colliding bunch.
+}
+\label{fig:period_bound_45}
+\end{figure}
+
+\end{itemize}
+
+\newpage
+Table \ref{table:correction_uncertainties} provides a detailed breakdown of the systematic uncertainties associated with the luminosity measurement for the year 2022.
+Each row represents a specific correction factor, while the corresponding column indicates its associated uncertainty as a percentage.
+
+\begin{table}[H]
+  \centering
+  \caption{Systematic uncertainty in luminosity measurement (\%)}
+    \begin{tabular}{l|c}
+        \textbf{Source} & \textbf{Uncertainty (\%)} \\
+        \hline
+        \multicolumn{2}{c}{\textbf{Calibration}} \\
+        \hline
+        Beam current & 0.2 \\
+        Ghosts \& satellites & 0.15 \\
+        Orbit drift & 0.3 \\
+        Residual beam positions & 0.33 \\
+        Beam-beam effects & 0.37 \\
+        Length scale & 0.12 \\
+        Factorization bias & 0.8 \\
+        Scan-to-scan variation & 0.2 \\
+        Bunch-to-bunch variation & 0.1 \\
+        Cross-detector consistency & 0.7 \\
+        \hline
+        \multicolumn{2}{c}{\textbf{Integration}} \\
+        \hline
+        Afterglow corrections & 0.2 \\
+        Cross-detector stability & 0.5 \\
+        Cross-detector linearity & 0.54 \\
+        \hline
+        Calibration & 1.3 \\
+        Integration & 0.8 \\
+        \hline
+        \textbf{Total} & 1.5 \\
+    \end{tabular}
+    \label{table:correction_uncertainties}
+    %\caption{Systematic uncertainty in luminosity measurement (\%)}
+\end{table}
+
+\begin{comment}
 

### 2023-12-17 tesis_Ashish/Chapter7/chapter7.tex
update
Sehrawat A thesis 17 Dec 2023

@@
-\chapter{Phase II upgrade of the CMS Tracker}  %Title of the First Chapter
+\chapter{TEPX luminometer for HL-LHC}  %Title of the First Chapter
 
@@
 
-%\section{Overview of the Phase II upgrade of the CMS Tracker}
-%\label{sec:PhaseIItracker}
-
 The Phase II upgrade of the CMS Tracker is a crucial project undertaken to maintain the effectiveness of the CMS experiment during the High Luminosity LHC (HL-LHC) run, which is expected to start in 2027.
 The HL-LHC will significantly increase the instantaneous luminosity, leading to a higher number of proton-proton collisions per bunch crossing.
+Instantaneous luminosity will increase to an unprecedented value of $7.5 \times 10^{34} cm^{-2} s^{-1}$ which corresponds to 200 proton-proton collisions per bunch crossing.
 This higher collision rate poses several challenges, including increased radiation levels, higher data rates, and more complex event environments.
-The Phase II upgrade of the CMS tracker comprises two main components: the Inner Tracker (IT) and the Outer Tracker (OT).
-The Inner Tracker consists of three main sub-components: the TEPX (Tracker Endcap Pixel), the TFPX (Tracker Forward Pixel), and the TBPX (Tracker Barrel Pixel) detectors.
-These sub-components are designed to handle the increased radiation levels and data rates in the HL-LHC environment.
+Run 2 pixel detector will not be able to handle these extreme radiation environment, resolve nearby particle tracks and operate properly to give a reliable estimate of the instantaneous luminosity for such a high pileup.
+That is why it will be replaced by a new pixel detector.
+The Phase II upgrade of the CMS tracker comprises of two main components: the Inner Tracker (IT) and the Outer Tracker (OT) \cite{collaboration:2759074}.
+The Inner Tracker consists of three main sub-components: the TEPX (Tracker Endcap Pixel), the TFPX (Tracker Forward Pixel), and the TBPX (Tracker Barrel Pixel) detectors as shown in Fig.
+\ref{fig:Innertracker}.
+TEPX will have better radiation tolerance, increased granularity, improved two-track separation, improved estimation of hit rate and statistical precision, extended tracking acceptance $|\eta|=4$ with Disk 4 Ring 1 operating as an independent luminosity measurement device \cite{Collaboration:2706512}.
 The Outer Tracker is responsible for detecting charged particles in the outer region of the CMS detector.
-It consists of two key subsystems: the silicon strip tracker and the silicon macro pixel tracker.
-
-%The Phase II upgrade of the CMS tracker is a major upgrade of the tracking system of the Compact Muon Solenoid (CMS) experiment at the Large Hadron Collider (LHC) at CERN.
-The upgrade is designed to improve the performance of the CMS tracker, enabling more precise measurements of the properties of particles produced in proton-proton collisions at the LHC.
+It consists of two key subsystems: the silicon strip tracker and the silicon macro pixel tracker \cite{RoyChowdhury:2729279}.
 
@@
 The Inner Tracker is crucial for the precise determination of the primary and secondary vertices (interaction points) and the accurate reconstruction of decay paths of short-lived particles.
-The Inner Tracker of the CMS experiment during the Phase II Upgrade will consist of three main subcomponents: TEPX (Tracker Endcap Pixel), TFPX (Tracker Forward Pixel), and TBPX (Tracker Barrel Pixel).
+The Inner Tracker of the CMS experiment during the Phase II Upgrade will consist of three main subcomponents: TEPX (Tracker Endcap Pixel), TFPX (Tracker Forward Pixel), and TBPX (Tracker Barrel Pixel) \cite{CERN-LHCC-2017-009}.
 These subsystems together form the new high-resolution, highly granular, and radiation-tolerant pixel tracking system.
@@
 
-%The TBPX, TFPX, and TEPX subsystems will form a highly efficient, high-resolution Inner Tracker capable of providing precise position measurements for charged particles produced in proton-proton collisions at the LHC.
-The upgraded pixel-based Inner Tracker will be crucial for maintaining the CMS experiment's excellent performance during the high-luminosity and high-radiation environment expected during the HL-LHC era.
-
 \item Outer Tracker: The Outer Tracker is designed to provide additional tracking points for charged particles as they traverse through the CMS detector.
@@
 
-%\end{enumerate}
-
-%\item Pixel Detector: The new pixel detector will have smaller pixels than the existing one, which will improve the spatial resolution of the detector.
-The new pixels will be 50 x 50 micrometers in size, compared to 100 x 150 micrometers in the existing detector.
-The new detector will also be more radiation tolerant, which means that it will be able to withstand the high radiation levels near the LHC beamline without losing performance.
-The new detector will consist of four barrel layers and six forward disks, providing coverage out to a pseudorapidity of 4.
-
-%\begin{enumerate}
-%\renewcommand{\labelenumi}{\roman{enumi})}
- %\item Tracker Endcap Pixel detector (TEPX): TEPX is a specialized pixel detector that will be added to the endcap region of the CMS tracker.
-It will be located in the forward region of the detector, covering a pseudorapidity range of 1.8 to 2.9.
-TEPX will consist of two disks on each side of the detector, with each disk containing 96 modules of pixel sensors.
-
-%\item Tracker Forward Pixel detector (TFPX): TFPX is a specialized pixel detector that will be added to the forward region of the CMS tracker.
-It will be located in front of the existing pixel detector and will cover a pseudorapidity range of 2.5 to 4.0.
-TFPX will consist of four disks on each side of the detector, with each disk containing 24 modules of pixel sensors.
-
-%\item Tracker Barrel Pixel detector (TBPX): TBPIX is a specialized pixel detector that will be added to the barrel region of the CMS tracker.
-It will be located in between the existing pixel detector layers and will cover a pseudorapidity range of 0 to 2.5.
-TBPIX will consist of four layers of pixel sensors, each layer containing 192 modules.
-
-%\end{enumerate}
-
-%\item Strip Detector: The new strip detector will have larger and thinner silicon sensors, which will improve the spatial resolution of the detector.
-The new sensors will be 100 micrometers thick, compared to 320 micrometers in the existing detector, and they will be up to 12 centimeters long, compared to 10 centimeters in the existing detector.
-The new readout electronics will be faster and more radiation tolerant than the existing ones.
-The new strip detector will have a total of 10 layers, providing coverage out to a pseudorapidity of 2.7.
-
-\item Timing layer is a new addition to the CMS Tracker during the Phase II upgrade, designed to provide precise time measurements of charged particles passing through the detector.
+\item The CMS Tracker's Phase II upgrade includes the Timing Layer, equipped with Low Gain Avalanche Detectors (LGAD) to improve time measurement of charged particles.
+This enhancement helps distinguish particles from different vertices, reducing pileup in event reconstruction.
+LGADs, with their charge amplification capability, offer superior time resolution.
+Charged particles generate electron-hole pairs in the LGAD sensor, which are then amplified and collected quickly for improved timing accuracy.
+The system aims for a 30-40 picosecond time resolution, enhancing particle identification and handling pileup effects.
+Covering a pseudorapidity range of $|\eta|$ < 2.5, the Timing Layer has a lightweight, radiation-tolerant support structure with efficient cooling, ensuring reliable performance.
+
+  %Timing layer is a new addition to the CMS Tracker during the Phase II upgrade, designed to provide precise time measurements of charged particles passing through the detector.
 These measurements help in distinguishing between particles originating from different vertices in the same event and reducing the impact of pileup on event reconstruction.
@@
 
-%\item Timing Layer: The new timing layer will consist of small, fast silicon sensors that will provide precise timing information for particles passing through the detector.
-The sensors will have a time resolution of less than 50 picoseconds, which will enable the separation of particles that are produced close together in time.
-The timing layer will be located in the forward region of the detector, where the particle flux is highest.
-
-%\item Mechanical Support: The new tracker will be supported by a new lightweight, carbon-fiber support structure, which will reduce the amount of material in front of the detector and improve its performance.
-The new support structure will also be more compact than the existing one, which will allow more space for other detector components.
-
-%\item Data Acquisition: The data acquisition system of the CMS tracker will be upgraded to handle the increased data rates and provide faster readout times.
-The upgraded system will use new custom-designed ASICs (Application-Specific Integrated Circuits) that will be able to process the data from the tracker at a rate of 320 gigabits per second.
-
 \item Data Acquisition (DAQ) system for the Phase II CMS Tracker must handle the increased data rates and complexity associated with the high-luminosity phase of the LHC (HL-LHC).
@@
 This increased luminosity leads to a higher collision rate and more complex events, which the DAQ system must handle.
-Data Rates: The upgraded CMS Tracker will generate a large amount of data due to the increased granularity of the pixel and strip sensors.
+
+\begin{itemize}
+
+ \item Data Rates: The upgraded CMS Tracker will generate a large amount of data due to the increased granularity of the pixel and strip sensors.
 The data rates from the tracker modules are expected to be several terabits per second (Tbps) during the HL-LHC operation.
-Trigger Rate: The Level-1 Trigger system in the Phase II Upgrade is designed to accept events at a rate of up to 750 kHz.
+
+ \item Trigger Rate: The Level-1 Trigger system in the Phase II Upgrade is designed to accept events at a rate of up to 750 kHz.
 The DAQ system must handle the transmission of trigger primitives to the Level-1 Trigger system and buffer the full event data until the trigger decision is made.
-Optical Links: The high-speed optical links used for data transmission between the Front-End Electronics (FEE) and off-detector electronics are expected to operate at data rates of 10-25 Gbps or higher to handle the large data volumes generated by the upgraded tracker.
-Buffering and Storage: The off-detector electronics must be able to buffer and store the full event data generated by the tracker modules until the Level-1 Trigger decision is made.
+
+  \item Optical Links: The high-speed optical links used for data transmission between the Front-End Electronics (FEE) and off-detector electronics are expected to operate at data rates of 10-25 Gbps or higher to handle the large data volumes generated by the upgraded tracker.
+
+  \item Buffering and Storage: The off-detector electronics must be able to buffer and store the full event data generated by the tracker modules until the Level-1 Trigger decision is made.
 The required buffering capacity depends on the trigger rate and the average event size but is expected to be in the order of several terabytes to accommodate the high data rates and trigger latencies.
-Processing Latency: The DAQ system must process the raw detector data and form trigger primitives within a very tight time constraint.
+
+  \item Processing Latency: The DAQ system must process the raw detector data and form trigger primitives within a very tight time constraint.
 The processing latency budget for the formation of trigger primitives in the Outer Tracker is expected to be around a few microseconds.
 
+\end{itemize}
+
 \end{enumerate}
 
-\section{New Inner tracker and its features}
-\label{sec:tepx}
-
-The High Luminosity (HL)-LHC will increase instantaneous luminosity to unprecedented value of $7.5 \times 10^{34} cm^{-2} s^{-1}$ which corresponds to 200 proton-proton collisions per bunch crossing (pileup).
-Run 2 pixel detector will not be able to handle the extreme radiation environment, resolve nearby particle tracks and operate properly to give a reliable estimate of the instantaneous luminosity for high pileup values.
-That is why it will be replaced by a new pixel detector which will be composed of three subdetectors: tracker barrel pixel detector (TBPX), tracker forward pixel detector (TFPX) and tracker endcap pixel detector (TEPX).
-TEPX will have better radiation tolerance, increased granularity, improved two-track separation, improved estimation of hit rate and statistical precision, extended tracking acceptance $|\eta|=4$ with Disk 4 Ring 1 operating as an independent luminometer \cite{Klein:2017nke}.
-\\
-
-\section{Phase II TEPX detector}
-
-Tracker endcap pixel detector (TEPX) consists of four double disks per side (-Z and +Z) with each double disk containing five rings as shown in Fig.
-25 having 20, 28, 36, 44 and 48 modules respectively.
-One double disk has four surfaces with +Z side containing modules with even module number in front layers (L1 $\&$ L2) and modules with odd module number in back layers (L3 $\&$ L4) from Ring 1 to Ring 4 and for Ring 5, modules with odd module number in front layers and modules with even module number in back layers as shown in Fig.
-26.
+\section{Tracker Endcap Pixel (TEPX) detector}
+
+Tracker endcap pixel detector (TEPX) consists of four double disks per side (-Z and +Z) (shown in left part of Fig.
+\ref{fig:Innertracker}) with each double disk consisting of five rings as shown in right part of Fig.
+\ref{fig:Innertracker} having 20, 28, 36, 44 and 48 modules respectively.
+One double disk has four surfaces with +Z side consisting of modules with even module number in front layers (L1 $\&$ L2) and modules with odd module number in back layers (L3 $\&$ L4) from Ring 1 to Ring 4 and for Ring 5, modules with odd module number in front layers and modules with even module number in back layers.
+%as shown in Fig.
+\ref{fig:CMS1_49}.
 For -Z side, four surfaces contain modules with odd module number in front layer and modules with even module number in back layer from Ring 1 to Ring 4 and for Ring 5, modules with even module number in front layer and modules with odd module number in back layer.
@@
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1 \columnwidth]{./tepx_tt.png}
-  \caption{ \onehalfspacing Left: A layout of the CMS Phase II inner tracker showing four TEPX disks, eight TFPX disks and four barrel layers.
-Right: Diagram showing one double disk of TEPX with five rings \cite{Klein:2017nke}.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1 \columnwidth]{./fourlayers.png}
-  \caption{ \onehalfspacing Fours layers of one double disk of TEPX showing module arrangement in rings for each layer. Ring 1, 2, 3, 4 and 5 consists of 20, 28, 36, 44 and 48 modules respectively. }
-  \label{fig:CMS}
-\end{figure}
-
-%\subsection{Expected improvements in luminosity measurement with the new TEPX detector}
-\subsection{Phase II CMS simulation samples}
-
- Simulated data samples for Phase II include full CMS detector description and uses official CMS software (CMSSW) version $10-6-0-patch2$ which calls GEANT4 for particle and energy deposit simulation as well as for reconstruction \cite{Agostinelli:2002hh}.
+\begin{figure}[!htp]
+  \centering
+  \includegraphics[width=1 \columnwidth]{ashish_thesis/tepx_tt.png}
+  \caption[Phase II CMS Inner Tracker]{ \onehalfspacing Left: A layout of the CMS Phase II inner tracker showing four TEPX disks, eight TFPX disks and four barrel layers.
+Right: Diagram showing one double disk of TEPX with five rings.}
+  \label{fig:Innertracker}
+\end{figure}
+
+%\begin{figure}[!htp]
+%  \centering
+ % \includegraphics[width=1 \columnwidth]{ashish_thesis/fourlayers.png}
+  %\caption[TEPX One Double Disk]{ \onehalfspacing Fours layers of one double disk of TEPX showing module arrangement in rings for each layer.
+Ring 1, 2, 3, 4 and 5 consists of 20, 28, 36, 44 and 48 modules respectively.
+}
+  %\label{fig:CMS1_49}
+%\end{figure}
+
+\section{Phase II CMS tracker simulation samples}
+
+ Simulated data samples for Phase II include full CMS detector description and uses official CMS software (version $\texttt{CMSSW\_10\_6\_0\_patch2}$) which calls GEANT4 for particle and energy deposit simulation as well as for reconstruction \cite{GEANT4:2002zbu}.
 These samples contain single-neutrino event overlaid with a variable number of minimum-bias events (events with any amount of real energy detected in CMS) to simulate different pileup values.
-The statistics for samples with average pileup values from 0.5 to 2 is 500000 events per step and for average pileup values between 10 and 200, statistics is 100000.
-
-\begin{table}[htbp]
-  \centering
-  \caption{Phase II upgrade of CMS tracker datasets}
-  \label{tab:sample}
-  \begin{tabular}{ccc}
-    \hline
-    \textbf{pileup} & \textbf{Total number of events} & \textbf{Dataset name} \\
-    \hline
-    noPU  & 500000 & /RelValNuGun/CMSSW_10_6_0_patch2-106X_upgrade2023_realistic_v3_2023D42noPU-v1/GEN-SIM-RECO \\
-     0.5& 500000 &  /RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU0p5-v1/GEN-SIM-RECO\\
-     1&  & 500000 &   /RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU1-v1/GEN-SIM-RECO\\
-     1.5 & 500000 &   /RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU1p5-v1/GEN-SIM-RECO\\
-     2&  &  500000 &   /RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU2-v1/GEN-SIM-RECO\\
-     10&  &  100000&   /RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU10-v1/GEN-SIM-RECO\\
-      30&  &  100000&   /RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU30-v1/GEN-SIM-RECO\\
-     50&  &  100000&   /RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU50-v1/GEN-SIM-RECO \\
-     100&  & 100000 & /RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU100-v2/GEN-SIM-RECO\\
-      140&  &  99600&  /RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU140-v2/GEN-SIM-RECO\\
-     200&  &  100000&  /RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU200-v1/GEN-SIM-RECO\\
-    %\hline
-  \end{tabular}
-\end{table}
-
-$/RelValNuGun/CMSSW_10_6_0_patch2-PU25ns_106X_upgrade2023_realistic_v3_2023D42PU200-v1/GEN-SIM-RECO$
-This dataset represents a simulated event sample generated using the CMS software framework, CMSSW, for the phase-2 upgrade of the CMS detector at the Large Hadron Collider (LHC).
-
-\begin{itemize}
-
-\item RelValNuGun: This refers to the type of generated events in this dataset.
-"RelVal" is short for "Release Validation," meaning that this sample is used for validating the performance of the CMS software release.
-"NuGun" refers to the specific event generator setup used for this dataset, which is a neutrino gun.
-In this setup, neutrinos are produced uniformly throughout the detector, providing a simple event topology for testing the software and detector response.
-
-\item $CMSSW_10_6_0_patch2$: This refers to the version of the CMS Software (CMSSW) used to generate and process the dataset.
-In this case, it is version 10.6.0 with patch 2 applied, containing specific software improvements or bug fixes.
-
-\item $PU25ns_106X_upgrade2023_realistic_v3_2023D42PU200$: This part contains several details about the dataset conditions:
-
-\item PU25ns: This indicates that the dataset includes simulated pileup events with an average of 25 collisions per bunch crossing, separated by 25 nanoseconds.
-\item 106X: This refers to the software release cycle (10.6.X) used for this dataset.
-\item $upgrade2023_realistic_v3$: This specifies that the dataset is for the planned 2023 upgrade of the CMS detector, using a "realistic" geometry and conditions version 3, which simulates the expected detector performance and environment.
-\item 2023D42PU200: This is a specific identifier for the simulated detector layout (D42) and conditions for the 2023 upgrade, with an emphasis on the 200 pileup events included in the simulation.
-GEN-SIM-RECO: These are the processing steps applied to the dataset:
-
-\item GEN: The "Generator" step, where the initial particle-level events are generated using Monte Carlo methods.
-\item SIM: The "Simulation" step, where the detector's response to the generated particles is simulated, taking into account the detector geometry, materials, and electronics.
-\item RECO: The "Reconstruction" step, where the simulated detector hits are processed to reconstruct the physics objects (e.g., particles and their trajectories), which are then used for further analysis.
-
-This dataset represents a set of simulated neutrino gun events, generated and processed with the CMS software version $10.6.0_patch2$, for the phase-2 upgrade of the CMS detector in 2023.
-The dataset includes realistic detector geometry and conditions, and 25ns pileup events, with an emphasis on 200 pileup events.
-The dataset has undergone the generation, simulation, and reconstruction steps, making it suitable for validation and analysis tasks.
-
-\end{itemize}
-
-\begin{table}[htbp]
+The statistics for samples with average pileup values from 0.5 to 2 is 500000 events per step and for average pileup values between 10 and 200, statistics is 100000 as shown in Table \ref{tab:sample_12}.
+The number of event processed in this study for each pileup is shown in Table \ref{tab:sample_2}.
+
+\begin{table}[ht]
+  \centering
+  \caption[Phase II simulated samples]{Total number of events in Phase II CMS tracker simulated samples}
+  \begin{tabular}{cc}
+    \textbf{pileup} & \textbf{Total number of events} \\
+    \hline
+    noPU  & 500000 \\
+    0.5 & 500000 \\
+    1 & 500000 \\
+    1.5 & 500000 \\
+    2 & 500000 \\
+    10 & 100000 \\
+    30 & 100000 \\
+    50 & 100000 \\
+    100 & 100000 \\
+    140 & 99600 \\
+    200 & 100000 \\
+  \end{tabular}
+  \label{tab:sample_12}
+\end{table}
+
+%The dataset is a simulated sample designed to evaluate the phase-2 upgrade of the CMS tracker.
+It includes a range of pileup conditions, from zero to 200 collisions per bunch crossing.
+Generated using a neutrino gun for events and version 10.6.0 of the CMS Software, the dataset aims to replicate conditions expected for the 2023 CMS upgrade.
+The data goes through a three-step process that consists of generating initial events, simulating the detector's response, and reconstructing physics objects for further study.
+%Table \ref{tab:sample_1} provides information about the number of events per file in relation to  pileup.
+Pileup is used to denote the number of pp collisions per bunch crossing.
+In the table, the pileup ranges from 'noPU' (no pileup) to a pileup of 200.
+As the pileup increases, the number of events per file generally decreases.
+For example, with no pileup, there are 2000 events per file.
+At a pileup of 0.5, this remains the same.
+However, as the pileup increases to 1, the number of events drops to 1800.
+The decrease continues progressively until a pileup of 2, where there are 1400 events per file.
+Beyond a pileup of 10, the number of events per file dramatically drops and stays constant at 100 events per file for pileups from 50 to 200.
+The number of event processed in this study for each pileup is shown in Table \ref{tab:sample_2}.
+
+\begin{comment}
+\begin{table}[ht]
   \centering
   \caption{Events per file for each pileup}
-  \label{tab:sample}
   \begin{tabular}{ccc}
@@
   \end{tabular}
-\end{table}
-
-\begin{table}[htbp]
+  \label{tab:sample_1}
+\end{table}
+
+\end{comment}
+
+\begin{table}[ht]
   \centering
   \caption{Events processed for each pileup}
-  \label{tab:sample}
   \begin{tabular}{ccc}
@@
      \hline
-     noPU & 10000  \\
+     noPU & 100000  \\
      0.5 &  100600 \\
@@
   \end{tabular}
-\end{table}
-
-\section{Luminosity determination using TEPX - counting clusters/coincidences}
-
-Luminosity determination using PCC method for Phase II HL-LHC will be based on counting the number of clusters in TEPX Disk 4 Ring 1.
-The innermost ring of the last disk of TEPX (D4R1) is located at 2.65 m away from the interaction point that is beyond the tracking acceptance ($|\eta| = 4$) and as this region has few tracking points, it can be solely used for the purpose of luminosity measurement by using the full available trigger rate and bandwidth.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{ashish_thesis/tepx_clusters.png}
-  \caption{TEPX cluster map in the XY plane for pileup 200 simulated sample.
+  %\caption{Events processed for each pileup}
+  \label{tab:sample_2}
+\end{table}
+
+\section{Luminosity measurement using TEPX}
+
+%Luminosity measurement for Phase II HL-LHC pixel detector will be done using two different systems: TEPX and D4R1 \cite{Haranko2023}.
+TEPX will be used in physics for tracking but will also get a dedicated trigger generated by the BRIL trigger board, data will be only processed by luminosity hardware of TEPX and send to BRILDAQ.
+D4R1 will be a dedicated luminometer with dedicated triggers fully independent of the CMS DAQ system for data analysis.
+Luminosity measurement using TEPX will be based on real time pixel cluster/coincidences counting (PCC) on FPGA, a method which involve counting the number of pixel clusters in the pixel detector (innermost part of the CMS tracker) per bunch crossing in minimum bias events.
+The innermost ring of the last disk of TEPX (D4R1) is located at 2.65 m away from the interaction point that is beyond the tracking acceptance ($|\eta| = 4$) and as this region has few tracking points, it can be solely used for the purpose of luminosity measurement by using the full available trigger rate and bandwidth \cite{Collaboration:2706512}.
+D4R1 will have dual purpose, luminosity and beam induced background (beam gas & beam halo) measurements.
+It will be operated during LHC ramp when beams are not colliding for measuring beam induced backgrounds.
+First bunch in a train or noncolliding bunches will be used for beam-induced background measurements.
+
+During Phase II HL-LHC, the pixel detector's luminosity will be measured using two systems: TEPX and D4R1  \cite{Haranko2023}.
+TEPX, primarily for tracking in physics, will also have a dedicated BRIL trigger for luminosity data, processed and sent to BRILDAQ.
+D4R1, a separate luminometer, operates independently of the CMS DAQ system  \cite{Collaboration:2706512}.
+TEPX's luminosity measurement uses real-time pixel cluster counting (PCC) on FPGA, tracking clusters per bunch crossing in minimum bias events.
+D4R1, located at 2.65 m from the interaction point and beyond tracking acceptance, focuses on luminosity and beam-induced background measurements, including during non-colliding LHC ramps.
+
+Expected CMS L1 trigger rate is around 750 kHz at pileup 200.
+500 kHz trigger rate during van der meer scans (pileup 0.5) and 75 kHz (10\% of expected CMS L1 trigger rate) trigger rate will be used for TEPX luminosity measurement at pileup 200.
+1000 kHz trigger rate during van der meer scans (pileup 0.5) and 825 kHz trigger rate will be used for D4R1 luminosity measurement at average pileup 200.
+
+The TEPX and D4R1 detectors will utilize an independent BRIL trigger board (BTB) for luminosity measurement, separate from the CMS L1 trigger system.
+This setup includes a local control stream synchronized with the LHC clock.
+Data from TEPX will be transmitted via high-speed links and processed by an FPGA for pixel clustering and histogramming, ensuring synchronization with CMS's overall timing and control system.
+
+\begin{comment}
+TEPX and D4R1 will require BRIL trigger board (BTB) independent of CMS L1 trigger system to have full control over luminosity triggers, local TCDS2-like control stream for D4R1 synchronised to LHC clock, luminosity local L1 triggers, encoding of beam 1 & beam 2 logical signals.
+CMS Timing and Control Distribution System (TCDS) receives LHC Clock and Orbit signals that are generated by the LHC RF system and uses them for generating the CMS Clock and commands.
+Measurement of beam induced background with D4R1 during the LHC ramp will need to be independent but synchronized to the rest of CMS and the central services like TCDS2 and data acquisition will be implemented using special clocking scheme.
+Trigger and timing subsystem for D4R1 will receive a dedicated “TCDS2-like” control stream from the BRIL trigger board (BTB) that is based on the LHC clock.
+
+Data accepted by CMS L1 trigger (750 kHz) will be collected by the end column of the pixel chip in TEPX and sent through electrical links (eLinks) at 1.28 Gb/s to LpGBT ASICs for optical transmission.
+Backend system DTC will be connected to frontend TEPX electronics via low-power Gigabit Transceiver (LpGBT) optical links.
+Optical down-links at 2.5 Gb/s will be used for clock, trigger, commands, and configuration data to the pixel modules.
+Optical up-links at 10 Gb/s will carry readout data from L1 accept and monitoring information to the DAQ and control system.
+TEPX luminosity processing will be performed by a separate luminosity processor board to which the DTC backend will send data over $~$ 4 x 25 Gb/s optical links.
+
+TEPX luminosity processing FPGA will consist of pixel clustering and histogramming instances.
+Clustering firmware will consists of
+Stream decoder: It will receives TEPX chip data, separate it from data appended by DTC and decode it.
+Quarter core processor: It will be used to identify up to four possible clusters within a quarter core. Two hits form a cluster if they touch horizontally, vertically or diagonally.
+Quarter core distributor: The quarter core distributor will check a given quarter core for isolation and decides whether it has to be sent to the row merger or counted internally.
+Count accumulator: It will receive final data bit and increment cluster count.
+
+\end{comment}
+
+Fig.
+\ref{fig:tepx_cl} shows the location of TEPX clusters in Disk 4 in the XY plane (Z is the direction of the beam) from a simulated sample with a pileup of 200.
+Clusters refer to groups of hits in the pixel detector.
+The TEPX disk in this map consists of 5 rings which are concentric rings of pixel modules at different radial distances from the beamline.
+
+\begin{figure}[!htp]
+  \centering
+  \includegraphics[width=0.9\columnwidth]{ashish_thesis/tepx_clusters_1.png}
+  \caption[TEPX Cluster Map]{TEPX cluster map in the XY plane for pileup 200 simulated sample.
 Map showing coordinates of TEPX clusters in CMS global coordinate system.
@@
 Hot regions are showing the module overlap for all rings (red, orange, green, yellow).
-Number of x bins is 1000, x bins range from -50 to 50.
+Number of x bins is 1000, x bins range from -40 to 40.
 x bin size is 0.1 cm.
-Number of y bins is 1000, y bins range from -50 to 50.
+Number of y bins is 1000, y bins range from -40 to 40.
 y bin size is 0.1 cm.}
@@
 
+The number of clusters per pp collision in Disk 4 Ring 1 varies from 0 to 2600 as a function of pileup.
+At pileup 200, mean number of cluster per pp collision is 2200 as shown in Fig.
+\ref{fig:tepx_cl_allPU}.
+The peak of the distribution drops as pileup increases because we have processed different number of events for different pileup values.
+Under low pileup conditions which is crucial for vdM calibration, number of clusters varies from 0 to 35.
+For average pileup value of 0.5 (vdM conditions), number of clusters varies between 0 and 12.
+
+\begin{figure}[!htp]
+  \centering
+  \includegraphics[width=1\columnwidth]{ashish_thesis/tepx_D4R!_clusters._allpu_1.png}
+  \caption[D4R1 Clusters All Pileup]{Distribution of number of clusters for TEPX Disk 4 Ring 1 for all pileup values.}
+  \label{fig:tepx_cl_allPU}
+\end{figure}
+
+Linearity is one of the systematic uncertainty in the calculation of instantaneous luminosity and PCC visible cross section $\sigma_{vis}$.
+A linear relation between the number of clusters and pileup (PU) imply that \\
+
+$<N_{cl/pp}> = \frac{<N_{cl}>}{\mu} = \frac{\sigma_{vis}}{\sigma_{pp}}$ \\
+
+$<N_{cl}> =  \frac{\sigma_{vis}}{\sigma_{pp}} \mu $ \\
+
+Linearity indicates that the PCC visible cross section $\sigma_{vis}$ does not depend on the per bunch instantaneous luminosity (ideal luminometer).
+In ideal scenario, $\sigma_{vis}$ is not dependent on pileup, but this a potential problem with the luminometer.
+Linearity results for simulated TEPX clusters from low to high pileup values are shown from Fig.
+\ref{fig:CMS_420} to Fig.
+\ref{fig:CMS_005}.
+TEPX luminometer proposed for Phase II shows excellent linearity over entire pileup range.
+A non-linear relation $<N_{cluster}> = \alpha (PU)^{\gamma}, \gamma \neq 1$ would add non-linear terms in the rate equation $R = \sigma_{vis} L_{inst}$  and cause $\sigma_{vis}$ to vary with the per bunch instantaneous luminosity and pileup values.
+
 \begin{figure}[H]
   \centering
-  \includegraphics[width=1\columnwidth]{ashish_thesis/tepx_D4R!_clusters._allpupng.png}
-  \caption{Left: Distribution of number of clusters for TEPX Disk 4 Ring 1 for all pileup values. Right: Distribution of number of clusters for TEPX Disk 4 Ring 1 for all low pileup values. }
-  \label{fig:tepx_cl_allPU}
+  \includegraphics[width=1\columnwidth]{ashish_thesis/totalclusters.png}
+  \caption[TEPX Clusters Fit And Residuals]{\onehalfspacing Left: Simulated mean number of clusters for all entire TEPX detector as a function of pileup.
+A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.
+Right: Deviation from linearity for clusters for entire TEPX detector.
+The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.
+Non-linearity is within 1 \% for entire pileup range.
+Pileup 200 corresponds to High Luminosity (HL)-LHC environment.}
+  \label{fig:CMS_420}
 \end{figure}
@@
   \centering
-  \includegraphics[width=1\columnwidth]{ashish_thesis/tepx_coincidences.png}
-  \caption{Left: TEPX coincidences in phi map in the XY plane for pileup 200 simulated sample.
-Right:TEPX coincidences in R map in the XY plane for pileup 200 simulated sample.
-Number of x bins is 1000, x bins range from -50 to 50.
-x bin size is 0.1 cm and Number of y bins is 1000, y bins range from -50 to 50.
-y bin size is 0.1 cm.}
-  \label{fig:tepx_coinc}
+  \includegraphics[width=1\columnwidth]{ashish_thesis/clustersD4R1.png}
+  \caption[Disk 4 Ring 1 Clusters Fit And Residual]{\onehalfspacing Left: Simulated mean number of clusters for TEPX Disk 4 Ring 1 as a function of pileup.
+Right: Deviation from linearity for clusters for TEPX Disk 4 Ring 1.
+The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
+  \label{fig:CMS_003}
 \end{figure}
@@
   \centering
-  \includegraphics[width=1\columnwidth]{ashish_thesis/tepx_D4R1_coin_allpu.png}
-  \caption{Left: Distribution of number of two fold coincidences for TEPX Disk 4 Ring 1 for all pileup values.
-Right: Distribution of number of two fold coincidences for TEPX Disk 4 Ring 1 for all low pileup values.}
-  \label{fig:tepx_coin_allPU}
+  \includegraphics[width=1 \columnwidth]{ashish_thesis/clustersperdisk+z.png}
+  \caption[Clusters Per disk Fit And Residual]{Left: Simulated mean number of clusters for +z side TEPX disks as a function of pileup.
+Right: Deviation from linearity for clusters for +z side TEPX disks.}
+  \label{fig:CMS_004}
 \end{figure}
@@
   \centering
-  \includegraphics[width=1\columnwidth]{ashish_thesis/tepx_D4_3foldcoin_allpu.png}
-  \caption{Distribution of number of three fold coincidences for TEPX Disk 4 all rings for all pileup values.}
-  \label{fig:tepx_3foldcoin_allPU}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{ashish_thesis/tepx_D4_3foldcoin_lowpu.png}
-  \caption{Distribution of number of three fold coincidences for TEPX Disk 4 all rings for low pileup values.}
-  \label{fig:tepx_3foldcoin_allPU}
-\end{figure}
-
-\subsubsection{Old algorithm for counting TEPX two fold coincidences}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/oldvariable_xy.png}
-\caption{%
-   Old X, Y variables used for defining two fold coincidences clusters in phi.
-}
-\label{fig:oldvar_xy}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/overlap_modules2_Ring1.png}
-\caption{%
- XY cluster map showing module overlap within the same ring in a disk that gives rise to two fold coincidences in phi.
-}
-\label{fig:overlap_2foldinphi}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/twofoldcoin_inphi_PU0p5_200.png}
-\caption{%
- Separation between X coordinates of two clusters for pileup 0.5 and 200 showing distribution total, true and fake two fold coincidences in phi.
-}
-\label{fig:dx_twofold}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/twofoldcoin_cluster_y.png}
-\caption{%
-    Separation between Y coordinates of two clusters for pileup 0.5 and 200 showing distribution total, true and fake two fold coincidences in phi.
-}
-\label{fig:dy_twofold}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/cut_optimization_twofoldcoin.png}
-\caption{%
- Cut optimization for two fold coincidences based on x, y variables to compute coincidence cluster separation.
-}
-\label{fig:cutopdxdy}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/cut_optimization_residual.png}
-\caption{%
-  Residual obtained after doing linear fit for different values of dx and dy.
-Two fold coincidences does not show decrement for high pileup when more stringent selections are applied on dx, dy variables.
-}
-\label{fig:res_dxdycut}
-\end{figure}
-
-\subsection{New algorithm for counting TEPX two fold coincidences}
-
-\subsection{TEPX two fold coincidences in phi}
-
-A new algorithm for luminosity determination based on counting two fold coincidences is proposed that applies selections using dr and $d\phi$ variables to minimize non-linearity for high pileup values as these variables take into account track angle and its curvature.
-Two fold coincidences are those hits which are created by the module overlap regions between various layers of one TEPX double disk.
+  \includegraphics[width=1\columnwidth]{ashish_thesis/clustersperringD+4.png}
+  \caption[Clusters Per Ring For Disk 4 Fit And Residual]{Left: Simulated mean number of clusters for +z side TEPX Disk 4 all rings as a function of pileup.
+Ring 1 has highest slope and Ring 5 has least slope.
+Right: Deviation from linearity for clusters for TEPX Disk +4 all rings.
+Non-linearity is within $1\%$ for all rings over entire pileup range.}
+  \label{fig:CMS_005}
+\end{figure}
+
+Two fold coincidences are clusters in modules overlap regions formed by modules in front and back layers of TEPX disk.
+There are two types of two fold coincidences namely in phi and r.
+Two fold coincidence in phi involve modules overlap in the same ring  of one double disk and two fold coincidence in r require modules overlap between successive rings of one double disk.
+wo fold coincidences are better way to distinguish between a real hit and random electrical noise.
+They are more likely to be real hit than random electrical noise.
+Luminosity determination based on counting coincidences has an advantage over clusters that afterglow effects are tiny in the case of coincidences.
+%as shown in Fig.
+\ref{fig:cluster_ring_4000}.
+ %(shown in Fig. \ref{fig:cluster_ring_73})
+  %as depicted in Fig. \ref{fig:cluster_ring_74}. 
+ %Overlap between L1 L3 and L2 L4 layers also possible but we havent considered them in this simulation.
+L1L2 two fold coincidences in r are clusters in module overlaps between adjacent rings in first two layers.
+L3L4 two fold coincidences in r are modules overlaps in the last two layers between adjacent rings.
+All types of two fold coincidences in r are shown in Table \ref{tab:twofoldinr}.
+Module overlap between different rings for all types of two fold coincidences in r are shown in Fig.
+\ref{tab:twofoldinr}.
 Two fold coincidences are better way to distinguish between a real hit and random electrical noise.
 They are more likely to be real hit than random electrical noise.
-Two fold coincidence in $\phi$ will involve modules overlapping in the same ring in front and back layers of one double disk as shown in top part of Fig.
-27 and Fig.
-28 while two fold coincidence in r will require modules overlapping between successive rings in the front (L1 $\&$ L2) and back layers (L3 $\&$ L4) of one double disk as shown in bottom part of Fig.
-27.
-Luminosity calculated based on counting coincidences has an advantage over clusters that afterglow effects are tiny in the case of coincidences  %\cite{Collaboration:2706512} \cite{brilsim} \cite{brilsim1}\cite{brilsim2}.
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/dr_dphi_variables.png}
-\caption{%
+Luminosity determination based on counting coincidences has an advantage over clusters that afterglow effects are tiny in the case of coincidences.
+
+\begin{comment}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.6\textwidth]{ashish_thesis/twofoldinphi.png}
+\caption[Module Overlap Two Fold Coincidences in phi]{%                                                                                                                                     
+  Example of module overlap between same ring modules that can give rise to two fold coincidences in phi.
+}
+\label{fig:cluster_ring_4000}
+\end{figure}
+
+\begin{table}[ht]
+  \centering
+  \caption{Location of four layers in Disk 4}
+\begin{tabular}{cc}
+\textbf{Layer} & \textbf{z coordinate} \\ 
+\hline
+Layer 1 (L1) & 264.4 \\ 
+Layer 2 (L2) & 264.8 \\ 
+Layer 3 (L3) & 265.2 \\ 
+Layer 4 (L4) & 265.6 \\ 
+\end{tabular}
+\label{tab:alllayerz}
+\end{table}
+
+\begin{table}[ht]
+  \centering
+  \caption{Types of two fold coincidences in r}
+\begin{tabular}{ccc}
+\textbf{Type of two fold coincidences in r} & \textbf{Module overlap} & \textbf{dz} \\ 
+\hline
+A & R1L1-R2L2 & 0.4 \\ 
+B & R1L1-R2L4 & 1.2 \\ 
+C & R1L3-R2L4 & 0.4 \\ 
+D & R2L2-R3L3 & 0.4 \\
+E & R3L1-R2L2 & 0.4 \\ 
+F & R3L3-R2L4 & 0.4 \\ 
+G & R3L1-R4L2 & 0.4 \\ 
+H & R3L1-R4L4 & 1.2 \\ 
+I & R3L3-R4L4 & 0.4 \\ 
+J & R5L1-R4L2 & 0.4 \\ 
+K & R4L2-R5L3 & 0.4 \\ 
+L & R5L3-R4L4 & 0.4 \\ 
+\end{tabular}
+\label{tab:twofoldinr}
+\end{table}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/moduleoverlapinR_1.png}
+\caption[Module Overlap Two Fold Coincidences in r]{%
+  Example of module overlap between different ring modules that can give rise to two fold coincidences in r.
+}
+\label{fig:cluster_ring_73}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/twofoldinRmethod.png}
+\caption[Few types Of Two Fold Coincidences in r]{%
+  Example of module overlap between different ring modules in the first two and last two layers of one tepx double disk that can give rise to two fold coincidences in r.
+}
+\label{fig:cluster_ring_74}
+\end{figure}
+
+\end{comment}
+
+%\begin{figure}[!htp]
+ % \centering
+  %\includegraphics[width=1\columnwidth]{ashish_thesis/tepx_D4_3foldcoin_lowpu.png}
+  %\caption[TEPX D4 All Rings Three Fold Coincidences Low Pileup]{Distribution of number of three fold coincidences for TEPX Disk 4 all rings for low pileup values.}
+  %\label{fig:tepx_3foldcoin_lowPU}
+%\end{figure}
+
+\begin{comment}
+
+The old algorithm for defining two fold coincidence employ x and y global position coordinates of clusters \cite{dabrowski2020}.
+Separation between x and y coordinate of original and coincidence cluster with proper selection and z coordinate selection in accordance with the separation between different layers in tepx disk is used as shown in Fig.
+\ref{fig:oldvar_xy}.
+
+dx=x2-x1, dy=y2-y1
+
+\begin{itemize}
+
+\item Two fold coincidence in this algorithm is defined as the pair of hits in the module overlap region within TEPX disk satisfying dx and dy selections of 0.1 and separated by z coordinate of 0.9.
+
+\item True coincidences are hits in module overlap region satisfying dx, dy selections of 0.1 and generated by same simulated track id.
+
+\item Fake coincidences are hits in module overlap region satisfying same dx, dy selections of 0.1 but not generated by same simulated track id.
+
+\end{itemize}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/oldvariable_xy.png}
+\caption[Old Definition Of Two Fold Coincidences]{%
+   Old x, y variables used for defining two fold coincidences clusters in phi.
+}
+\label{fig:oldvar_xy}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/twofoldcoin_inphi_PU0p5_200.png}
+\caption[Total, True and Fake Two Fold coincidences in phi (old x variables)]{%
+ Separation between x coordinates of clusters in module overlap region for pileup 0.5 and 200 showing distribution total, true and fake two fold coincidences in phi.
+}
+\label{fig:dx_twofold}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/twofoldcoin_cluster_y.png}
+\caption[Total, True and Fake Two Fold Coincidences in phi (old y variables)]{%
+    Separation between y coordinates of clusters in module overlap region for pileup 0.5 and 200 showing distribution total, true and fake two fold coincidences in phi.
+}
+\label{fig:dy_twofold}
+\end{figure}
+
+In order to reduce fake two fold coincidences for high pileup, we tried more stringent selections on separation of x, y variables for original and coincidence clusters as depicted in Fig.
+\ref{fig:cutopdxdy} to select dx, dy distribution (shown in Fig.
+\ref{fig:dx_twofold} and Fig.
+\ref{fig:dy_twofold}) only close to the peak cluster count but were unable to improve the residuals at high pileup to suppress physics noise.
+With this algorithm, we obtain residual upto 3\% even with smallest possible selection on dx and dy.
+Residuals obtained using different value of dx, dy selections are shown in Fig.
+\ref{fig:res_dxdycut}.
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/cut_optimization_twofoldcoin.png}
+\caption[Cut Optimization  Old variables]{%
+ Cut optimization for two fold coincidences based on x, y variables to compute coincidence cluster separation.
+}
+\label{fig:cutopdxdy}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/cut_optimization_residual.png}
+\caption[Residuals Different Cut Values]{%
+  Residual obtained after doing linear fit for different values of dx and dy.
+Fake two fold coincidences does not show decrement for high pileup when more stringent selections are applied on dx, dy variables.
+}
+\label{fig:res_dxdycut}
+\end{figure}
+
+\end{comment}
+
+\newpage
+A new algorithm for luminosity measurement based on counting two fold coincidences is proposed that applies selections using dr and $d\phi$ variables (shown in Fig.
+\ref{fig:drdphi_diagram}) to minimize non-linearity for high pileup as these variables take into account track angle and its curvature \cite{sehrawat2020}.
+Proper selections are applied for each TEPX disk based on these variables using low pileup simulated samples and then these selections are extrapolated to high pileup samples for suppressing fake coincidences.
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.7\textwidth]{ashish_thesis/dr_dphi_variables1_1.png}
+\caption[New Variables For Two Fold Coincidences]{%
   New r, phi variables used to define coincidence clusters. These variables take into account track angle and curvature.
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/new_variables.png}
-\caption{%
-   Possible new variable to replace x, y variable for defining coincidence clusters.
-}
-\label{fig:newvar}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/deltaR.png}
-\caption{%
- dR
-}
-\label{fig:dR}
-\end{figure}
+\begin{comment}
 
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/delta_r.png}
-\caption{%
-  dr
+\caption[Total, True & Fake Cluster Counts vs. dr (PU 0.5)]{%
+  Distribution of total, true and fake coincidence cluster count as a function of dr variable for pileup 0.5.
 }
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/dphi.png}
-\caption{%
- dphi 
+\caption[Total, True & Fake Cluster Counts vs. dphi (PU 0.5)]{%
+ Distribution of total, true and fake coincidence cluster count as a function of dphi variable for pileup 0.5.
 }
@@
 
+\end{comment}
+
+We study the two fold coincidences in phi for all TEPX Disk and rings using dr, dphi variable for pileup 0.5 and apply nominal selection of 0.15 cm on dr and 0.04 on dphi variable in order to remove fake coincidences.
+After obtaining these distributions for all TEPX disks and rings, we carry out fit of the distribution to obtain mean and standard deviation of these distributions.
+The dr, dphi distribution showing true, fake, total two fold coincidences for Disk 4 Ring 1 for pileup 0.5 is shown in Fig.
+\ref{fig:cluster_dr_dphi_dist}.
+%Example fits are shown in Fig.
+\ref{fig:cluster_ring_1003}, \ref{fig:cluster_ring_70}, \ref{fig:cluster_ring_71}.
+While doing the fit, mean value for dphi variable is set to zero.
+%The mean is taken as the offset value and standard deviation is used as the selection on dr, dphi variables as shown in Table \ref{tab:disk_values}, \ref{tab:mdphi_cuts_values} and \ref{tab:mdr_cuts_offset_values}.
+The mean of the fit is taken as the offset value and standard deviation is used as the selection on dr, dphi variables as shown in Table \ref{tab:disk_values}, \ref{tab:mdphi_cuts_values} and \ref{tab:mdr_cuts_offset_values}.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/D4R1_S2_drdphi_cut_1.png}
+\caption[Pileup 0.5 Cluster Count in D4R1 (+Z) vs. dr & dphi]{%
+  Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 1 (+Z). Appropriate selection on dr, dphi are used to minimize fake two fold coincidences.
+}
+\label{fig:cluster_dr_dphi_dist}
+\end{figure}
+
+\begin{comment}
+
 \begin{figure}[!htp]
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/D4R1_S2_drdphi_cut.png}
-\caption{%
-  Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 1 (+Z). Appropriate selection on dr, dphi are used to minimize fake two fold coincidence clusters.
+\caption[Pileup 0.5 Cluster Count in D4R1 (+Z) vs. dr & dphi]{%
+  Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 1 (+Z). Appropriate selection on dr, dphi are used to minimize fake two fold coincidences.
 }
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/D4R2_S2_drdphicut.png}
-\caption{%
+\caption[Pileup 0.5 Cluster Count in D4R2 (+Z) vs. dr & dphi]{%
+   Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 2 (+Z). Appropriate selection on dr, dphi are used to minimize fake two fold coincidences.
+}
+\label{fig:cluster_ring_1000}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/D4R3_S2_drdphi_cut.png}
+\caption[Pileup 0.5 Cluster Count in D4R3 (+Z) vs. dr & dphi]{%
+  Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 3 (+Z). Appropriate selection on dr, dphi are used to minimize fake two fold coincidences.
+}
+\label{fig:cluster_ring_10001}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/D4R5_drdphicut.png}
+\caption[Pileup 0.5 Cluster Count in D4R5 (+Z) vs. dr & dphi]{%
+  Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 5 (+Z). Appropriate selection on dr, dphi are used to minimize fake two fold coincidences.
+}
+\label{fig:cluster_ring_1002}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/D4R1S2_fit.png}
+\caption[Disk 4 Ring 1 Clusters Fit]{%
+   Example fit using single gaussian function of cluster count as a function of dr variable for Disk 4 Ring 1 (+Z).
+}
+\label{fig:cluster_ring_1003}
+\end{figure}
+
+\begin{comment}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/D4R1S2_dr_dphi_cut.png}
+\caption[New dr selection value]{%
+ Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 1 (+Z).
+1 sigma selection on dr and dphi equal to 0.04 are used to minimize fake two fold coincidence.
+}
+\label{fig:cluster_ring_1004}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/D4R2S2_dr_dphi_cut.png}
+\caption[New dphi selection value]{%
    Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 2 (+Z).
-Appropriate selection on dr, dphi are used to minimize fake two fold coincidence clusters.
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/D4R3_S2_drdphi_cut.png}
-\caption{%
-  Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 3 (+Z). Appropriate selection on dr, dphi are used to minimize fake two fold coincidence clusters.
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/D4R5_drdphicut.png}
-\caption{%
-  Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 5 (+Z). Appropriate selection on dr, dphi are used to minimize fake two fold coincidence clusters.
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/D4R1S2_fit.png}
-\caption{%
-   Example fit using single gaussian function of cluster count as a function of dr variable for Disk 4 Ring 1 (+Z).
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/D4R1S2_dr_dphi_cut.png}
-\caption{%
- Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 1 (+Z).
-1 sigma selection on dr and dphi equal to 0.04 are used to minimize fake two fold coincidence clusters.
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/D4R2S2_dr_dphi_cut.png}
-\caption{%
-   Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 2 (+Z).
-1 sigma selection on dr and dphi equal to 0.04 are used to minimize fake two fold coincidence clusters.
-}
-\label{fig:cluster_ring}
+1 sigma selection on dr and dphi equal to 0.04 are used to minimize fake two fold coincidences.
+}
+\label{fig:cluster_ring_1005}
 \end{figure}
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/D4R3S2_dr_dphi_cut.png}
-\caption{%
+\caption[Cluster count as function of new variables with selection for PU 0.5 D4R3S2]{%
     Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 3 (+Z).
-1 sigma selection on dr and dphi equal to 0.04 are used to minimize fake two fold coincidence clusters.
-}
-\label{fig:cluster_ring}
+1 sigma selection on dr and dphi equal to 0.04 are used to minimize fake two fold coincidences.
+}
+\label{fig:cluster_ring_1006}
 \end{figure}
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/D4R4S2_dr_dphi_cut.png}
-\caption{%
+\caption[Cluster count as function of new variables with selection for PU 0.5 D4R4S2]{%
   Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 4 (+Z).
-1 sigma selection on dr and dphi equal to 0.04 are used to minimize fake two fold coincidence clusters.
-}
-\label{fig:cluster_ring}
+1 sigma selection on dr and dphi equal to 0.04 are used to minimize fake two fold coincidences.
+}
+\label{fig:cluster_ring_68}
 \end{figure}
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/D4R5S2_dr_dphi_cut.png}
-\caption{%
+\caption[Cluster count as function of new variables with selection for PU 0.5 D4R5S2]{%
   Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 5 (+Z).
@@
 }
-\label{fig:cluster_ring}
-\end{figure}
+\label{fig:cluster_ring_69}
+\end{figure}
+
+%\end{comment}
 
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/D4R1S2_fit_PU0p5.png}
-\caption{%
-  Example fit using single Gaussian function of cluster count as a function of dr variable for pileup 0.5 Disk 4 Ring 1 (+Z).
-}
-\label{fig:cluster_ring}
+\caption[Fit Disk 4 Ring 1 (+Z) Cluster Distribution]{%
+  Example fit using single Gaussian function of cluster count as a function of dphi variable for pileup 0.5 Disk 4 Ring 1 (+Z).
+}
+\label{fig:cluster_ring_70}
 \end{figure}
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/D4R5_fit_PU0p5.png}
-\caption{%
- Example fit using single Gaussian function of cluster count as a function of dr variable for pileup 0.5 Disk 4 Ring 5 (+Z). 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{table}[htbp]
-  \centering
-  \caption{dr cut values for two fold coincidences in phi for all disks and rings}
-  \label{tab:disk_values}
+\caption[Fit Disk 4 Ring 5 (+Z) Cluster Distribution]{%
+ Example fit using single Gaussian function of cluster count as a function of dphi variable for pileup 0.5 Disk 4 Ring 5 (+Z). 
+}
+\label{fig:cluster_ring_71}
+\end{figure}
+
+\end{comment}
+
+%The mean of the fit is taken as the offset value and standard deviation is used as the selection on dr, dphi variables as shown in Table \ref{tab:disk_values}, \ref{tab:mdphi_cuts_values} and \ref{tab:mdr_cuts_offset_values}.
+
+\begin{table}[h]
+  \centering
+  \caption[dr cut values]{dr cut values for two fold coincidences in phi for all disks and rings}
   \begin{tabular}{cccccc}
@@
     \hline
-    -1 & 0.00633554 & 0.00709231 & 0.00757662 & 0.008659   & 0.00872148 \\
-    -2 & 0.00594206 & 0.00663493 & 0.00718173 & 0.00766371 & 0.00797059 \\
-    -3 & 0.00594206 & 0.00663493 & 0.00660603 & 0.00713035 & 0.00679445 \\
-    -4 & 0.00530235 & 0.00587692 & 0.00616465 & 0.00661972 & 0.00660599 \\
-    1  & 0.00635769 & 0.0071538  & 0.00780034 & 0.00863764 & 0.00883121 \\
-    2  & 0.00587583 & 0.00656126 & 0.00700576 & 0.00773345 & 0.00786885 \\
-    3  & 0.00557387 & 0.00617934 & 0.00664346 & 0.0070085  & 0.00727192 \\
-    4  & 0.0053299  & 0.00586655 & 0.0061499  & 0.00667791 & 0.00678366 \\
-  \end{tabular}
-\end{table}
-
-\begin{table}[htbp]
-  \centering
-  \caption{dphi cut values for two fold coincidences in phi for all disks and rings}
-  \label{tab:mdphi_cuts_values}
+    %-1 & 0.00633554 & 0.00709231 & 0.00757662 & 0.008659   & 0.00872148 \\
+    %-2 & 0.00594206 & 0.00663493 & 0.00718173 & 0.00766371 & 0.00797059 \\
+    %-3 & 0.00594206 & 0.00663493 & 0.00660603 & 0.00713035 & 0.00679445 \\
+    %-4 & 0.00530235 & 0.00587692 & 0.00616465 & 0.00661972 & 0.00660599 \\
+    1  & 0.0064 & 0.0072  & 0.0078 & 0.0086 & 0.0088 \\
+    2  & 0.0059 & 0.0066 & 0.0070 & 0.0077 & 0.0079 \\
+    3  & 0.0056 & 0.0062 & 0.0066 & 0.0070  & 0.0073 \\
+    4  & 0.0053  & 0.0059 & 0.0061  & 0.0067 & 0.0068 \\
+  \end{tabular}
+  \label{tab:disk_values}
+\end{table}
+
+\begin{table}[h]
+  \centering
+  \caption[dphi cut values]{dphi cut values for two fold coincidences in phi for all disks and rings}
   \begin{tabular}{cccccc}
@@
     \hline
-    -1 & 0.000856727  & 0.00128078   & 0.00151297   & 0.00151297   & 0.0016561    \\
-    -2 & 0.000765842  & 0.00110698   & 0.00131104   & 0.00143555   & 0.00150265   \\
-    -3 & 0.000684645  & 0.000975385  & 0.00115899   & 0.00126858   & 0.00131598   \\
-    -4 & 0.000598839  & 0.000862728  & 0.00104327   & 0.00112621   & 0.00115609   \\
-    1  & 0.000877912  & 0.00125898   & 0.0015378    & 0.00164165   & 0.00173015   \\
-    2  & 0.00076339   & 0.00110755   & 0.00132174   & 0.00144755   & 0.00150547   \\
-    3  & 0.000679543  & 0.000972429  & 0.00116735   & 0.00125955   & 0.00132885   \\
-    4  & 0.000609859  & 0.000881345  & 0.00101584   & 0.00112554   & 0.00118477   \\
-  \end{tabular}
-\end{table}
-
-\begin{table}[htbp]
-  \centering
-  \caption{dr mean values obtained from fit for two fold coincidences in phi for all disks and rings}
-  \label{tab:mdr_cuts_offset_values}
+    %-1 & 0.000856727  & 0.00128078   & 0.00151297   & 0.00151297   & 0.0016561    \\
+    %-2 & 0.000765842  & 0.00110698   & 0.00131104   & 0.00143555   & 0.00150265   \\
+    %-3 & 0.000684645  & 0.000975385  & 0.00115899   & 0.00126858   & 0.00131598   \\
+    %-4 & 0.000598839  & 0.000862728  & 0.00104327   & 0.00112621   & 0.00115609   \\
+    1  & 0.00088  & 0.0013   & 0.0015    & 0.0016   & 0.0017   \\
+    2  & 0.00076   & 0.0011   & 0.0013   & 0.0014   & 0.0015   \\
+    3  & 0.00068  & 0.00097  & 0.0012   & 0.0013   & 0.0013   \\
+    4  & 0.00061  & 0.00088  & 0.0010   & 0.0011   & 0.0012   \\
+  \end{tabular}
+  \label{tab:mdphi_cuts_values}
+\end{table}
+
+\begin{table}[h]
+  \centering
+  \caption[dr offset values]{dr mean values obtained from fit for two fold coincidences in phi for all disks and rings}
   \begin{tabular}{cccccc}
@@
     \hline
-    -1 & 0.0342041  & 0.0511416 & 0.0676943 & 0.0834355 & 0.0984932 \\
-    -2 & 0.0298276  & 0.0445398 & 0.0589828 & 0.0727454 & 0.0853587 \\
-    -3 & 0.0260326  & 0.0386608 & 0.05122   & 0.0632478 & 0.0746467 \\
-    -4 & 0.0227089  & 0.0336467 & 0.044476  & 0.0551065 & 0.06484   \\
-    1  & 0.0341565  & 0.0511018 & 0.0676485 & 0.0835835 & 0.0984028 \\
-    2  & 0.0298515  & 0.0444016 & 0.0589681 & 0.0727789 & 0.0854843 \\
-    3  & 0.0260239  & 0.0387303 & 0.0511824 & 0.0633755 & 0.0742994 \\
-    4  & 0.022729   & 0.0336624 & 0.0445526 & 0.0550466 & 0.0644863 \\
-  \end{tabular}
-\end{table}
-
-\subsection{TEPX two fold coincidences in R}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.5\textwidth]{ashish_thesis/2foldinR.png}
-\caption{%
-  All possible module overlaps between different rings that can give rise to two fold coincidences in R.
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{table}[htbp]
-\centering
-\caption{Various types of two fold coincidences in R in one TEPX double disk with module overlaps and z separation is shown in the table.}
-\label{tab:module_connections}
+    %-1 & 0.0342041  & 0.0511416 & 0.0676943 & 0.0834355 & 0.0984932 \\
+    %-2 & 0.0298276  & 0.0445398 & 0.0589828 & 0.0727454 & 0.0853587 \\
+    %-3 & 0.0260326  & 0.0386608 & 0.05122   & 0.0632478 & 0.0746467 \\
+    %-4 & 0.0227089  & 0.0336467 & 0.044476  & 0.0551065 & 0.06484   \\
+    1  & 0.034  & 0.051 & 0.068 & 0.084 & 0.098 \\
+    2  & 0.030  & 0.044 & 0.059 & 0.073 & 0.085 \\
+    3  & 0.026  & 0.039 & 0.051 & 0.063 & 0.074 \\
+    4  & 0.023   & 0.034 & 0.045 & 0.055 & 0.064 \\
+  \end{tabular}
+  \label{tab:mdr_cuts_offset_values}
+\end{table}
+
+\newpage
+The final plot of two fold coincidences in phi after applying all selection based on standard deviation values of all tepx disks and rings is shown in Fig. \ref{fig:cluster_ring_720}.
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/twofoldinphi_sch.png}
+\caption[Map Of Two Fold Coincidences in phi]{%                                                                                                                                                       
+  Map of two fold coincidences in phi showing all module overlap regions.
+}
+\label{fig:cluster_ring_720}
+\end{figure}
+
+\newpage
+Simlarly, we also studied two fold coincidences in r which arise from module overlaps between successive rings by only considering one to one module overlap between first two and last two layers in one TEPX double disk.
+%Table \ref{table:two_fold_coincidences} categorizes various types of two-fold coincidences in r, observed in the TEPX detector.
+These coincidences are labeled from A to L and arise due to the module overlap in different layers within a single TEPX double disk.
+The 'dz' column quantifies the spatial separation along beam axis between the coinciding layers,  the z coordinates for Layers L1 to L4 within the TEPX detector is also mentioned.
+These coordinates provide a precise location for each layer, contributing to the understanding of where these two fold coincidences are likely to occur.
+The two fold coincidence in r map showing module overlap regions for different types is shown in Fig.
+\ref{fig:cluster_ring_770}.
+ A one-to-one overlapping of modules is considered between L1L2 and L3L4 module overlap. %as shown in Fig. \ref{tab:my_label2}. 
+ %The distributions for dr, dphi distribution depicting fake, true, total two fold coincidence in r for pileup 0.5 and 200 are shown in Fig.
+\ref{fig:cluster_ring_81} and \ref{fig:cluster_ring_82} respectively.
+ Fit is done to pileup 0.5 distribution of true coincidences for both L1L2 and L3L4 coincidences in r .%as shown in Fig. \ref{fig:cluster_ring_83} and \ref{fig:cluster_ring_84}. 
+ Fit results for all disks and rings are shown from  Table \ref{tab:my_label_55} to \ref{tab:my_label_50}.
+After applying all selections obtained from the fits, we plotted the XY map of two fold coincidences in r for L1L2 and L3L4 combined as shown in \ref{fig:cluster_ring_79}.
+
+\begin{comment}
+
+\begin{table}[H]
+  \centering
+  \caption[Two fold coincidences in r types]{Left: All type of two fold coincidences in r. Right: z coordinates for Layers L1 to L4.}
+\begin{minipage}{0.45\textwidth}
+    \centering
     \begin{tabular}{ccc}
-\textbf{Two fold in R types} & \textbf{Module overlaps} & \textbf{dz} \\ \hline
-A & R1L3-R2L4 & 0.4 \\
+    Modules & Type of Two Fold Coincidences & dz \\
+    \hline
+    A & R1L1-R2L2 & 0.4 \\
     B & R1L1-R2L4 & 1.2 \\
-C & R1L1-R2L2 & 0.4 \\
-D & R3L3-R2L4 & 0.4 \\
-E & R2L2-R3L3 & 0.4 \\
-F & R3L1-R2L2 & 0.4 \\
-G & R3L3-R4L4 & 0.4 \\
+    C & R1L3-R2L4 & 0.4 \\
+    D & R2L2-R3L3 & 0.4 \\
+    E & R3L1-R2L2 & 0.4 \\
+    F & R3L3-R2L4 & 0.4 \\
+    G & R3L1-R4L2 & 0.4 \\
     H & R3L1-R4L4 & 1.2 \\
-I & R3L1-R4L2 & 0.4 \\
-J & R5L3-R4L4 & 0.4 \\
+    I & R3L3-R4L4 & 0.4 \\
+    J & R5L1-R4L2 & 0.4 \\
     K & R4L2-R5L3 & 0.4 \\
-L & R5L1-R4L2 & 0.4 \\ 
-\end{tabular}
-\end{table}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/moduleoverlapinR_1.png}
-\caption{%
-  Example of module overlap between different ring modules that can give rise to two fold coincidences in R.
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/twofoldinRmethod.png}
-\caption{%
-  Example of module overlap between different ring modules in the first two and last two layers of one tepx double disk that can give rise to two fold coincidences in R.
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/moduleoverlapfortwofoldinR.png}
-\caption{%
-   Module overlap between different ring modules that can give rise to two fold coincidences in R.
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/onetoonemoduleoverlap2xinR_table.png}
-\caption{%
-   Module overlap between different ring modules that can give rise to two fold coincidences in R.
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/l1l2_2xinr.png}
-\caption{%
-   Module overlap between different ring modules that can give rise to two fold coincidences in R.
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/l3l4_2xinr.png}
-\caption{%
-   Module overlap between different ring modules that can give rise to two fold coincidences in R.
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/l1l2_l3l4_2xinr.png}
-\caption{%
-   Module overlap between different ring modules that can give rise to two fold coincidences in R.
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/XY_map_2xinphi_2xinr.png}
-\caption{%
-   Module overlap between different ring modules that can give rise to two fold coincidences in R.
-}
-\label{fig:cluster_ring}
-\end{figure}
+    L & R5L3-R4L4 & 0.4 \\
+    \end{tabular}
+\end{minipage}%
+\hfill
+\begin{minipage}{0.45\textwidth}
+    \centering
+    \begin{tabular}{cc}
+    Layer & z-coordinate \\
+    \hline
+    Layer 1 (L1) & 264.4 \\
+    Layer 2 (L2) & 264.8 \\
+    Layer 3 (L3) & 265.2 \\
+    Layer 4 (L4) & 265.6 \\
+    \end{tabular}
+\end{minipage}
+\label{table:two_fold_coincidences}
+\end{table}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/twofoldinr_alltypes_diag.png}
+\caption[Two Fold Coincidences in r types]{%
+  Types of module overlap between different ring modules that can give rise to two fold coincidences in r.
+}
+\label{fig:cluster_ring_770}
+\end{figure}
+
+\begin{table}[H]
+  \caption[Module mapping for two fold coincidenes in r]{Left: One to one module mapping in L1L2. Right: One to one module mapping in L3L4.}
+  \begin{minipage}{0.45\linewidth}
+    \centering
+    %\caption{Left: One to one module mapping in L1L2. Right: One to one module mapping in L3L4}
+    \begin{tabular}{cc}
+      \textbf{R1L1} & \textbf{R2L2} \\
+      \hline
+      2 & 2 \\
+      4 & 6 \\
+      6 & 8 \\
+      8 & 12 \\
+      10 & 14 \\
+      12 & 16 \\
+      14 & 20 \\
+      16 & 22 \\
+      18 & 24 \\
+      20 & 28 \\
+    \end{tabular}
+    %\label{tab:my_label1}
+  \end{minipage}
+  \hfill
+  \begin{minipage}{0.45\linewidth}
+    \centering
+    %\caption{One to one module mapping in L3L4}
+    \begin{tabular}{cc}
+      \textbf{R1L3} & \textbf{R2L4} \\
+      \hline
+      1 & 1 \\
+      3 & 5 \\
+      5 & 7 \\
+      7 & 9 \\
+      9 & 13 \\
+      11 & 15 \\
+      13 & 19 \\
+      15 & 21 \\
+      17 & 23 \\
+      19 & 27 \\
+    \end{tabular}
+    %\label{tab:my_label2}
+  \end{minipage}
+  \label{tab:my_label2}
+\end{table}
+
+\end{comment}
+
+\begin{comment}
 
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/l1l2_dr_dphi_D4R1S2.png}
-\caption{%
-   Module overlap between different ring modules that can give rise to two fold coincidences in R.
-}
-\label{fig:cluster_ring}
+\caption[D4R1 Two-Fold Coincidences vs. dr & dphi (PU 0.5)]{%
+   PU 0.5 D4R1 total, true, fake two fold coincidences  in r as a function of dr, dphi variables.
+}
+\label{fig:cluster_ring_81}
 \end{figure}
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/l1l2_drdphi_2xinr_PU200.png}
-\caption{%
-   Module overlap between different ring modules that can give rise to two fold coincidences in R.
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/l1l2_drdphi_2xinr_PU200.png}
-\caption{%
-   Module overlap between different ring modules that can give rise to two fold coincidences in R.
-}
-\label{fig:cluster_ring}
-\end{figure}
+\caption[D4R1 Two-Fold Coincidences vs. dr & dphi (PU 200)]{%
+   PU 200 D4R1 total, true, fake two fold coincidences  in r as a function of dr, dphi variables.
+}
+\label{fig:cluster_ring_82}
+\end{figure}
+
+\endn{comment}
+
+\begin{comment}
 
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/fit_l1l2_dr_2xinr.png}
-\caption{%
-   Module overlap between different ring modules that can give rise to two fold coincidences in R.
-}
-\label{fig:cluster_ring}
-\end{figure}
+\caption[Fit L1L2 Two Fold Coincidences in r]{%
+   Fit L1L2 two fold coincidences in R.
+}
+\label{fig:cluster_ring_83}
+\end{figure}
+
+\begin{table}[H]
+  \centering
+  \caption{Fit parameters for dr}
+\begin{tabular}{ccc}
+\textbf{Parameter Name} & \textbf{Value} & \textbf{Error} \\ 
+\hline
+p0 & 8.25e+02 & 1.40e+01 \\ 
+p1 & 1.49e-02 & 6.52e-05 \\ 
+p2 & 4.44e-03 & 5.61e-05 \\ 
+p3 & 4.94e+01 & 1.18e+00 \\ 
+p4 & 2.04e-02 & 9.87e-04 \\ 
+p5 & 6.35e-02 & 1.14e-03 \\ 
+\end{tabular}
+\label{tab:my_label3}
+\end{table}
 
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/fit_l3l4_dr_2xinr.png}
-\caption{%
-   Module overlap between different ring modules that can give rise to two fold coincidences in R.
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/residuaL_L1L2_L3L4_2xinr.png}
-\caption{%
-   Module overlap between different ring modules that can give rise to two fold coincidences in R.
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{comment}
-
-\begin{table}[htbp]
-  \centering
-  \caption{m\_dr\_cuts\_offset\_InR\_f Values}
-  \label{tab:mdr_cuts_offset_InR_f_values}
-  \begin{tabular}{cccc}
-    \hline
-    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} &  \textbf{Ring 4}\\
-    \hline
-    -1 & 0.0230881 & 0.0309854 & 0.0387241 & 0.0464962 \\
-    -2 & 0.0199761 & 0.0270206 & 0.0338467 & 0.0403068 \\
-    -3 & 0.017385  & 0.0233397 & 0.0294101 & 0.0348779 \\
-    -4 & 0.0150614 & 0.0202725 & 0.0255259 & 0.0303849 \\
+\caption[Fit L3L4 Two Fold Coincidences in r]{%
+   Fit L3L4 two fold coincidences in r.
+}
+\label{fig:cluster_ring_84}
+\end{figure}
+
+\begin{table}[H]
+  \centering
+  \caption{Fit parameters for dr}
+\begin{tabular}{ccc}
+\textbf{Parameter Name} & \textbf{Value} & \textbf{Error} \\ 
+\hline
+p0 & 8.33e+02 & 1.43e+01 \\ 
+p1 & 1.50e-02 & 6.56e-05  \\ 
+p2 & 4.57e-03  & 6.01e-05 \\
+p3 & 4.95e+01 & 1.17e+00 \\
+p4 & 2.02e-02 & 1.04e-03  \\  
+p5 & 6.68e-02 & 1.24e-03  \\ 
+\end{tabular}
+\label{tab:my_label6}
+\end{table}
+
+\end{comment}
+
+%\begin{table}[h]
+ % \centering
+  %\caption{Fit parameters for dphi}
+%\begin{tabular}{ccc}
+%\textbf{Parameter Name} & \textbf{Value} & \textbf{Error} \\ 
+%\hline
+%p0 & 1.263e+03 & 2.52e+01 \\ 
+%p1 & 0.00e+00 & fixed \\ 
+%p2 & 4.510e-04 & 7.25e-06 \\
+%\end{tabular}
+%\label{tab:my_label10}
+%\end{table}
+
+\begin{table}[H]
+  \centering
+  \caption[dr mean values (L1L2)]{dr mean values obtained from fit for all disks and rings for coincidences in r in layers L1L2}
+\begin{tabular}{ccccc}
+ & \multicolumn{4}{c}{\textbf{Ring}} \\
+\textbf{Disk} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} \\
+\hline
+%-4 & 0.0230881 & 0.0309854 & 0.0387241 & 0.0464962 \\ 
+%-3 & 0.0199761 & 0.0270206 & 0.0338467 & 0.0403068 \\ 
+%-2 & 0.017385  & 0.0233397 & 0.0294101 & 0.0348779 \\ 
+%-1 & 0.0150614 & 0.0202725 & 0.0255259 & 0.0303849 \\
 1 & 0.0229736 & 0.0311421 & 0.0390871 & 0.0468038 \\
@@
 4 & 0.0149661 & 0.020194  & 0.0255051 & 0.0305483 \\
-    \hline
-  \end{tabular}
-\end{table}
-
-\begin{table}[htbp]
-  \centering
-  \caption{m\_dphi\_cuts\_InR\_f Values}
-  \label{tab:mdphi_cuts_InR_f_values}
-  \begin{tabular}{cccc}
-    \hline
-    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} \\
-    \hline
-    -1 & 0.000628313 & 0.000828659 & 0.000975585 & 0.00101984  \\
-    -2 & 0.000545699 & 0.000722289 & 0.00081899  & 0.000918094 \\
-    -3 & 0.000495422 & 0.000649127 & 0.000754224 & 0.000839347 \\
-    -4 & 0.000451069 & 0.000604104 & 0.000689508 & 0.000755603 \\
+\end{tabular}
+\label{tab:my_label_55}
+\end{table}
+
+\begin{table}[H]
+  \centering
+  \caption[dphi cut values (L1L2)]{dphi standard deviation values obtained from fit for all disks and rings for coincidences in r in layers L1L2}
+\begin{tabular}{ccccc}
+ & \multicolumn{4}{c}{\textbf{Ring}} \\
+\textbf{Disk} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} \\
+\hline
+%-4 & 0.000628313 & 0.000828659 & 0.000975585 & 0.00101984 \\ 
+%-3 & 0.000545699 & 0.000722289 & 0.00081899 & 0.000918094 \\ 
+%-2 & 0.000495422 & 0.000649127 & 0.000754224 & 0.000839347 \\ 
+%-1 & 0.000451069 & 0.000604104 & 0.000689508 & 0.000755603 \\
 1 & 0.000627781 & 0.000814669 & 0.000941641 & 0.0010221 \\
@@
 4 & 0.000471669 & 0.000589938 & 0.000692007 & 0.000750302 \\
-    \hline
-  \end{tabular}
-\end{table}
-
-\begin{table}[htbp]
-  \centering
-  \caption{m\_dr\_cuts\_InR\_f Values}
-  \label{tab:mdr_cuts_InR_f_values}
-  \begin{tabular}{cccc}
-    \hline
-    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} \\
-    \hline
-    -1 & 0.00458531 & 0.00466448 & 0.00486059 & 0.0052905  \\
-    -2 & 0.00444971 & 0.0046465  & 0.00472138 & 0.00490022 \\
-    -3 & 0.00453556 & 0.00471864 & 0.00465781 & 0.00503102 \\
-    -4 & 0.00457346 & 0.00458345 & 0.00478342 & 0.00497171 \\
+\end{tabular}
+\label{tab:my_label_54}
+\end{table}
+
+\begin{table}[H]
+  \centering
+  \caption[dr cut values (L1L2)]{dr standard deviation values obtained from fit for all disks and rings for coincidences in r in layers L1L2}
+\begin{tabular}{ccccc}
+ & \multicolumn{4}{c}{\textbf{Ring}} \\
+\textbf{Disk} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} \\
+\hline
+%-4 & 0.00458531 & 0.00466448 & 0.00486059 & 0.0052905 \\ 
+%-3 & 0.00444971 & 0.0046465 & 0.00472138 & 0.00490022 \\ 
+%-2 & 0.00453556 & 0.00471864 & 0.00465781 & 0.00503102 \\ 
+%-1 & 0.00457346 & 0.00458345 & 0.00478342 & 0.00497171 \\
 1 & 0.00448255 & 0.00445856 & 0.00474102 & 0.0051553 \\
@@
 4 & 0.00444657 & 0.00468584 & 0.00493828 & 0.00488064 \\
-    \hline
-  \end{tabular}
-\end{table}
-
-\begin{table}[htbp]
-  \centering
-  \caption{m\_dr\_cuts\_InR\_S Values}
-  \label{tab:mdr_cuts_InR_S_values}
-  \begin{tabular}{cccc}
-    \hline
-    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} \\
-    \hline
-    -1 & 0.00448255 & 0.00445856 & 0.00474102 & 0.0051553  \\
-    -2 & 0.00442349 & 0.00472485 & 0.00474663 & 0.0050426  \\
-    -3 & 0.00450002 & 0.0045179  & 0.00492058 & 0.00494887 \\
-    -4 & 0.00444657 & 0.00468584 & 0.00493828 & 0.00488064 \\
+\end{tabular}
+\label{tab:my_label_53}
+\end{table}
+
+\begin{table}[H]
+  \centering
+  \caption[dphi cut values (L3L4)]{dphi standard deviation values obtained from fit for all disks and rings for coincidences in r in layers L3L4}
+\begin{tabular}{ccccc}
+ & \multicolumn{4}{c}{\textbf{Ring}} \\
+\textbf{Disk} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} \\
+\hline
+%-4 & 0.00448255 & 0.00445856 & 0.00474102 & 0.0051553 \\ 
+%-3 & 0.00442349 & 0.00472485 & 0.00474663 & 0.0050426 \\ 
+%-2 & 0.00450002 & 0.0045179 & 0.00492058 & 0.00494887 \\ 
+%-1 & 0.00444657 & 0.00468584 & 0.00493828 & 0.00488064 \\
 1 & 0.00458531 & 0.00466448 & 0.00486059 & 0.0052905 \\
@@
 4 & 0.00457346 & 0.00458345 & 0.00478342 & 0.00497171 \\
-    \hline
-  \end{tabular}
-\end{table}
-
-\begin{table}[htbp]
-  \centering
-  \caption{m\_dphi\_cuts\_InR\_S Values}
-  \label{tab:mdphi_cuts_InR_S_values}
-  \begin{tabular}{cccc}
-    \hline
-    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} \\
-    \hline
-    -1 & 0.000627781 & 0.000814669 & 0.000941641 & 0.0010221   \\
-    -2 & 0.000573352 & 0.000761853 & 0.000851161 & 0.000901014 \\
-    -3 & 0.000523361 & 0.000662691 & 0.000778358 & 0.000834924 \\
-    -4 & 0.000471669 & 0.000589938 & 0.000692007 & 0.000750302 \\
+\end{tabular}
+\label{tab:my_label_52}
+\end{table}
+
+\begin{table}[H]
+  \centering
+  \caption[dphi cut values (L3L4)]{dphi standard deviation values obtained from fit for all disks and rings for coincidences in r in layers L3L4}
+\begin{tabular}{ccccc}
+ & \multicolumn{4}{c}{\textbf{Ring}} \\
+\textbf{Disk} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} \\
+\hline
+%-4 & 0.000627781 & 0.000814669 & 0.000941641 & 0.0010221 \\ 
+%-3 & 0.000573352 & 0.000761853 & 0.000851161 & 0.000901014 \\ 
+%-2 & 0.000523361 & 0.000662691 & 0.000778358 & 0.000834924 \\ 
+%-1 & 0.000471669 & 0.000589938 & 0.000692007 & 0.000750302 \\
 1 & 0.000628313 & 0.000828659 & 0.000975585 & 0.00101984 \\
@@
 4 & 0.000451069 & 0.000604104 & 0.000689508 & 0.000755603 \\
-    \hline
-  \end{tabular}
-\end{table}
-
-\begin{table}[htbp]
-  \centering
-  \caption{m\_dr\_cuts\_offset\_InR\_S Values}
-  \label{tab:mdr_cuts_offset_InR_S_values}
-  \begin{tabular}{cccc}
-    \hline
-    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} \\
-    \hline
-    -1 & 0.0229736 & 0.0311421 & 0.0390871 & 0.0468038 \\
-    -2 & 0.0202136 & 0.0268963 & 0.0337796 & 0.040398  \\
-    -3 & 0.0174894 & 0.0233893 & 0.0293971 & 0.0351501 \\
-    -4 & 0.0149661 & 0.020194  & 0.0255051 & 0.0305483 \\
+\end{tabular}
+\label{tab:my_label_51}
+\end{table}
+
+\begin{table}[H]
+  \centering
+  \caption[dr mean values (L3L4)]{dr mean values obtained from fit for all disks and rings for coincidences in r in layers L3L4}
+\begin{tabular}{ccccc}
+ & \multicolumn{4}{c}{\textbf{Ring}} \\
+\textbf{Disk} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} \\
+\hline
+%-4 & 0.0229736 & 0.0311421 & 0.0390871 & 0.0468038 \\ 
+%-3 & 0.0202136 & 0.0268963 & 0.0337796 & 0.040398 \\ 
+%-2 & 0.0174894 & 0.0233893 & 0.0293971 & 0.0351501 \\ 
+%-1 & 0.0149661 & 0.020194 & 0.0255051 & 0.0305483 \\
 1 & 0.0230881 & 0.0309854 & 0.0387241 & 0.0464962 \\
@@
 4 & 0.0150614 & 0.0202725 & 0.0255259 & 0.0303849 \\
-    \hline
-  \end{tabular}
-\end{table}
+\end{tabular}
+\label{tab:my_label_50}
+\end{table}
+
+\begin{comment}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/l1l2_2xinr.png}
+\caption[L1L2 Module Overlap Map for Two Fold Coincidences in r]{%                                                                                                                                   
+   Module overlap map in L1L2 layers for two fold coincidences in r.
+}
+\label{fig:cluster_ring_77}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/l3l4_2xinr.png}
+\caption[L3L4 Module Overlap Map for Two Fold Coincidences in r]{%
+   Module overlap map in L3L4 layers for two fold coincidences in r.
+}
+\label{fig:cluster_ring_78}
+\end{figure}
 
@@
 
-%\begin{figure}[!htp]
-%\centering
-%\includegraphics[width=0.7\textwidth]%{ashish_thesis/events_processed_twofoldcoin_newcuts.png}
-%\caption{%
-
-%}
-%\label{fig:cluster_ring}
-%\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/D4R1S2_linear_fit_twofoldcoin.png}
-\caption{%
-  Fit two fold coincidences Disk 4 Ring 1 side 2
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/Alldisk_S1_twofoldcoin_residuals.png}
-\caption{%
-   fit residual two fold coincidences 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/Alldisk_S2_twofoldcoin_residuals.png}
-\caption{%
-  fit residual two fold coincidences all disk.
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/D4R1_z_dr_dphi_total_fake_twofold.png}
-\caption{%
-  jhgil
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/D4R5_z_dr_dphi_twofoldcoin_total_fake.png}
-\caption{%
-   klbjihvb
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/fake_rate_D4allring.png}
-\caption{%
-  lhivbhiv
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{table}[htbp]
-  \centering
-  \caption{Sample Table}
-  \label{tab:sample}
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/l1l2_l3l4_2xinr.png}
+\caption[L1L2 and L3L4 Module Overlap Map for Two Fold Coincidences in r]{%
+   Module overlap map in L1L2 and L3L4 layers for two fold coincidences in r.
+}
+\label{fig:cluster_ring_79}
+\end{figure}
+
+\newpage
+The new algorithm is able to remove physics noise at high pileup as can be seen from the high efficiency values and low fake rates for Disk 4 all rings and all pileup samples as shown in Table \ref{tab:sample}, \ref{tab:sample_1} and \ref{tab:sample_2}.
+
+\begin{table}[H]
+  \centering
+  \caption{Fake rate for Disk 4 all rings}
   \begin{tabular}{cc}
@@
   \end{tabular}
-\end{table}
-
-\begin{table}[htbp]
-  \centering
-  \caption{Sample Table}
   \label{tab:sample}
+\end{table}
+
+\begin{table}[H]
+  \centering
+  \caption{TEPX two fold coincidences fake rate}
 \begin{tabular}{cccc}
-    \textbf{Pileup} & \textbf{Fake two fold coincidence in phi rate ()} & \textbf{Fake two fold coincidence in R rate ()} & \textbf{Fake two fold coincidence rate ()} \\
+\textbf{Pileup} & \textbf{Fake two fold} & \textbf{Fake two fold} & \textbf{Fake two} \\
+\textbf{} & \textbf{coincidence in phi} & \textbf{coincidence in R} & \textbf{fold coincidence} \\
 \hline
@@
 \end{tabular}
-\end{table}
-
-\begin{table}[htbp]
-  \centering
-  \caption{Sample Table}
-  \label{tab:sample}
+\label{tab:sample_1}
+\end{table}
+
+\begin{table}[H]
+  \centering
+  \caption{TEPX two coincidences efficiency}
 \begin{tabular}{cccc}
-    \textbf{Pileup} & \textbf{efficiency for two fold coincidence in phi} & \textbf{Efficiency for Fake two fold coincidence in R} & \textbf{Efficiency for two fold coincidence ()} \\
+\textbf{Pileup} & \textbf{Efficiency for two} & \textbf{Efficiency for Fake} & \textbf{Efficiency for two} \\
+& \textbf{fold coincidence in phi} & \textbf{two fold coincidence in R} & \textbf{fold coincidence} \\
 \hline
@@
 \end{tabular}
-\end{table}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/D4R1_fake_true_ratio.png}
-\caption{%
-  Ratio of fake and total two fold coincidences for disk 4 ring 1.
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/D4R5_fake_true_ratio.png}
-\caption{%
-  Ratio of fake and total two fold coincidences for disk 4 ring 5.
-}
-\label{fig:cluster_ring}
-\end{figure}
+\label{tab:sample_2}
+\end{table}
+
+%Ratio of the integrals for fake & total coincidence for dr & dphi distributions is 3454/145988 = 0.023
+
+It is important to study how the number of two fold coincidences after final selections change with pileup for precise luminosity measurement.
+Number of two fold coincidences increases with pileup.
+Distribution of two fold coincidences for TEPX Disk 4 Ring 1 for all pileup values is shown in Fig.
+\ref{fig:tepx_coin_allPU}.
+For pileup 200, mean two fold coincidences is around 270.
+Under vdM conditions, it range from 0 to 13.
+The new algorithm is able to suppress non-linearity at high pileup values as shown from Fig.
+1.17 to Fig.
+1.24.
 
@@
   \centering
-  \includegraphics[width=0.7\columnwidth]{./2foldinrphi.png}
-  \caption{ \onehalfspacing Diagram showing modules overlap between the front (L1 \& L2) and back (L3 \& L4) layers of one double disk of TEPX that creates two fold coincidences in $\phi$ and r.}
-  \label{fig:CMS}
+  \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_D4R1_coin_allpu_1.png}
+  \caption[TEPX D4R1 Two Fold Coincidences All Pileup]{Distribution of number of two fold coincidences for TEPX Disk 4 Ring 1 for all pileup values.}
+  \label{fig:tepx_coin_allPU}
 \end{figure}
@@
   \centering
-  \includegraphics[width=0.6\columnwidth]{./23coin.png}
-  \caption{\onehalfspacing Example of two and threefold coincidence regions on a portion of a single TEPX disk.}
-  \label{fig:CMS}
-\end{figure}
-
-\subsection{TEPX linearity}
-
-Linearity is one of the systematic uncertainty in the calculation of instantaneous luminosity and PCC visible cross section $\sigma_{vis}$.
-A linear relation between the number of clusters and pileup (PU) imply that \\
-
-$<N_{cl/pp}> = \frac{<N_{cl}>}{\mu} = \frac{\sigma_{vis}}{\sigma_{pp}}$ \\
-
-$<N_{cl}> =  \frac{\sigma_{vis}}{\sigma_{pp}} \mu $ \\
-
-Linearity indicates that the PCC visible cross section $\sigma_{vis}$ does not depend on the per bunch instantaneous luminosity (ideal luminometer).
-In ideal scenario, $\sigma_{vis}$ is not dependent on pileup, but this a potential problem with the luminometer.
-Linearity results for simulated TEPX clusters and coincidences from low to high pileup values are shown from Fig.
-29 to Fig.
-40.
-TEPX luminometer proposed for Phase II shows excellent linearity over entire pileup range.
-A non-linear relation $<N_{cluster}> = \alpha (PU)^{\gamma}, \gamma \neq 1$ would add non-linear terms in the rate equation $R = \sigma_{vis} L_{inst}$  and cause $\sigma_{vis}$ to vary with the per bunch instantaneous luminosity and pileup values.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{./totalclusters.png}
-  \caption{\onehalfspacing Left: Simulated mean number of clusters for all entire TEPX detector as a function of pileup.
-A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.
-Right: Deviation from linearity for clusters for entire TEPX detector.
-The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.
-Non-linearity is within 1 \% for entire pileup range.
-Pileup 200 corresponds to High Luminosity (HL)-LHC environment.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{./clustersD4R1.png}
-  \caption{\onehalfspacing Left: Simulated mean number of clusters for TEPX Disk 4 Ring 1 as a function of pileup.
-Right: Deviation from linearity for clusters for TEPX Disk 4 Ring 1.
-The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1 \columnwidth]{./clustersperdisk+z.png}
-  \caption{Left: Simulated mean number of clusters for +z side TEPX disks as a function of pileup. Right: Deviation from linearity for clusters for +z side TEPX disks.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{./clustersperringD+4.png}
-  \caption{Left: Simulated mean number of clusters for +z side TEPX Disk 4 all rings as a function of pileup.
-Ring 1 has highest slope and Ring 5 has least slope.
-Right: Deviation from linearity for clusters for TEPX Disk +4 all rings.
-Non-linearity is within $1\%$ for all rings over entire pileup range.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1 \columnwidth]{./totalcoincidences.png}
-  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for all entire TEPX detector as a function of pileup.
+  \includegraphics[width=1 \columnwidth]{ashish_thesis/totalcoincidences.png}
+  \caption[TEPX Two Fold Coincidences Fit And Residual]{Left: Simulated mean number of coincidences in $\phi$ and r for all entire TEPX detector as a function of pileup.
 A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.
@@
   \centering
-  \includegraphics[width=1\columnwidth]{./totalcoincidencesD4R1.png}
-  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for TEPX Disk 4 Ring 1 as a function of pileup.
+  \includegraphics[width=1\columnwidth]{ashish_thesis/totalcoincidencesD4R1.png}
+  \caption[Two Fold Coincidences for Disk 4 Ring 1 Fit And Residual]{Left: Simulated mean number of coincidences in $\phi$ and r for TEPX Disk 4 Ring 1 as a function of pileup.
 Right: Deviation from linearity for coincidences in $\phi$ and r for TEPX Disk 4 Ring 1.
@@
   \centering
-  \includegraphics[width=1\columnwidth]{./coincidencesperdisk+z.png}
-  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for +z side TEPX disks as a function of pileup.
+  \includegraphics[width=1\columnwidth]{ashish_thesis/coincidencesperdisk+z.png}
+  \caption[Two Fold Coincidences Per Disk Fit And Residual]{Left: Simulated mean number of coincidences in $\phi$ and r for +z side TEPX disks as a function of pileup.
 Right: Deviation from linearity for coincidences in $\phi$ and r for +z side TEPX disks.}
@@
   \centering
-  \includegraphics[width=1\columnwidth]{./coincidencesinphiD4R1z+.png}
-  \caption{Left: Simulated mean number of coincidences in $\phi$ for TEPX +z side Disk 4 Ring 1 as a function of pileup.
+  \includegraphics[width=1\columnwidth]{ashish_thesis/coincidencesinphiD4R1z+.png}
+  \caption[Two Fold Coincidences in phi for Disk 4 Ring 1 Fit And Residual]{Left: Simulated mean number of coincidences in $\phi$ for TEPX +z side Disk 4 Ring 1 as a function of pileup.
 Right: Deviation from linearity for coincidences in $\phi$ for TEPX +z side Disk 4 Ring 1.
@@
   \centering
-  \includegraphics[width=1\columnwidth]{./coincidencesinrD4R1z+.png}
-  \caption{Left: Simulated mean number of coincidences in r for TEPX +z side Disk 4 Ring 1 as a function of pileup.
+  \includegraphics[width=1\columnwidth]{ashish_thesis/coincidencesinphiperringD+4.png}
+  \caption[Two fold coincidences in phi per ring Fit And Residual]{Left: Simulated mean number of coincidences in $\phi$ for +z side TEPX Disk 4 per ring as a function of pileup.
+Ring 1 has highest slope and Ring 5 has least slope.
+Right: Deviation from linearity for coincidences in $\phi$ for +z side TEPX Disk 4 per ring.
+Non-linearity is within 1\% for all rings over entire pileup range.}
+  \label{fig:CMS}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{ashish_thesis/coincidencesinrperringD+4.png}
+  \caption[Two Fold Coincidences in r Per Ring Fit And Residual]{Left: Simulated mean number of coincidences in r for +z side TEPX Disk 4 per ring as a function of pileup.
+Ring 1 has highest slope and Ring 5 has least slope.
+Right: Deviation from linearity for coincidences in r for +z side TEPX Disk 4 per ring.
+Non-linearity is within $1\%$ for all rings over entire pileup range.}
+  \label{fig:CMS_999}
+\end{figure}
+
+\begin{comment}
+
+For Disk 4 Ring 1, fake coincidences are randomly distributed and true coincidences are localized in the middle of the distribution as shown in Fig.
+\ref{fig:cluster_ring_20}.
+For Disk 4 Ring 5, fake coincidence are randomly distributed.
+True coincidences are localized in the middle of the distribution.
+Compared to Ring 1, there are less true coincidences in the middle part of the distribution as shown in Fig.
+\ref{fig:cluster_ring_21}.
+
+\begin{figure}[!htp]
+  \centering
+  \includegraphics[width=1\columnwidth]{ashish_thesis/coincidencesinrD4R1z+.png}
+  \caption[Two Fold Coincidences in r Disk 4 Ring 1 Fit And Residual]{Left: Simulated mean number of coincidences in r for TEPX +z side Disk 4 Ring 1 as a function of pileup.
 Right: Deviation from linearity for coincidences in r for TEPX +z side Disk 4 Ring 1.
@@
   \centering
-  \includegraphics[width=1\columnwidth]{./coincidencesperringD+4.png}
-  \caption{Left: Simulated mean number of coincidences in $\phi$ and r for +z side TEPX Disk 4 per ring as a function of pileup.
+  \includegraphics[width=1\columnwidth]{ashish_thesis/coincidencesperringD+4.png}
+  \caption[Two fold coincidences per ring Fit And Residual]{Left: Simulated mean number of coincidences in $\phi$ and r for +z side TEPX Disk 4 per ring as a function of pileup.
 Ring 1 has highest slope and Ring 5 has least slope.
@@
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{./coincidencesinphiperringD+4.png}
-  \caption{Left: Simulated mean number of coincidences in $\phi$ for +z side TEPX Disk 4 per ring as a function of pileup.
-Ring 1 has highest slope and Ring 5 has least slope.
-Right: Deviation from linearity for coincidences in $\phi$ for +z side TEPX Disk 4 per ring.
-Non-linearity is within 1\% for all rings over entire pileup range.}
-  \label{fig:CMS}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=1\columnwidth]{./coincidencesinrperringD+4.png}
-  \caption{Left: Simulated mean number of coincidences in r for +z side TEPX Disk 4 per ring as a function of pileup.
-Ring 1 has highest slope and Ring 5 has least slope.
-Right: Deviation from linearity for coincidences in r for +z side TEPX Disk 4 per ring.
-Non-linearity is within $1\%$ for all rings over entire pileup range.}
-  \label{fig:CMS}
-\end{figure}
-
-\subsection{Statistical precision for TEPX luminometer}
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/D4R1_fake_true_ratio.png}
+\caption[Disk 4 Ring 1 Fake/Total coincidences]{%
+  Ratio of fake and total two fold coincidences for disk 4 ring 1.
+}
+\label{fig:cluster_ring_20}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/D4R5_fake_true_ratio.png}
+\caption[Disk 4 Ring 5 Fake/Total coincidences]{%
+  Ratio of fake and total two fold coincidences for disk 4 ring 5.
+}
+\label{fig:cluster_ring_21}
+\end{figure}
+
+\end{comment}
+
+It is possible to have three fold coincidences in TEPX detector.
+A three-fold coincidence cluster refers to a situation where three hits are detected simultaneously within a tepx disk.
+The XY map of three fold coincidences is shown in Fig.
+\ref{fig:tepx_3foldcoin_allPU_1}.
+When particles pass through the TEPX detector, they can leave behind 'traces' by interacting with the detector.
+These interactions are detected and measured as electrical signals.
+Each interaction might be seen as a 'hit' in the detector.
+When three of these hits occur nearly simultaneously and in a close spatial arrangement, they can form what is known as a three-fold coincidence hit originating from the same underlying event, for instance, the passage of a single particle or a single collision event.
+Three fold coincidences under all pileup conditions is shown in Fig.
+\ref{fig:tepx_3foldcoin_allPU_2}.
+With the current algorithm, three fold coincidences shows non-linearity at high pileup as shown in Fig.
+\ref{fig:tepx_3foldcoin_allPU_3} % and Fig.
+\ref{fig:tepx_3foldcoin_lowPU}.
+
+\begin{figure}[!htp]
+  \centering
+  \includegraphics[width=1\columnwidth]{ashish_thesis/tepx_threefold_coincidences.png}
+  \caption[Regions in XY plane showing three fold coincidences]{X vs Y map of three fold coincidences.}
+  \label{fig:tepx_3foldcoin_allPU_1}
+\end{figure}
+
+\begin{figure}[!htp]
+  \centering
+  \includegraphics[width=1\columnwidth]{ashish_thesis/tepx_threefold_allpu.png}
+  \caption[TEPX Disk 4 Ring 2 Three Fold Coincidences]{Distribution of number of three fold coincidences for TEPX Disk 4 Ring 2 for all pileup values.}
+  \label{fig:tepx_3foldcoin_allPU_2}
+\end{figure}
+
+%\begin{figure}[!htp]
+ % \centering
+  %\includegraphics[width=1\columnwidth]{ashish_thesis/tepx_D4_3foldcoin_allpu.png}
+  %\caption[TEPX D4 All Rings Three Fold Coincidences]{Distribution of number of three fold coincidences for TEPX Disk 4 all rings for all pileup values.}
+  %\label{fig:tepx_3foldcoin_allPU}
+%\end{figure}
+
+\begin{figure}[!htp]
+  \centering
+  \includegraphics[width=1\columnwidth]{ashish_thesis/TEPX_threefold_linearity.png}
+  \caption[Disk 4 Ring 2 three Fold Coincidences Linearity]{Left: Simulated mean number of three fold coincidences for all Disk 4 all rings as a function
+    of pileup. Right: Deviation from linearity for Disk 4 all rings.}
+  \label{fig:tepx_3foldcoin_allPU_3}
+\end{figure}
+
+\section{Statistical precision for TEPX luminometer}
 Statistical precision is another uncertainty that need to be considered for precise luminosity measurement. It must be kept minimal to achieve 1 $\%$ accuracy for HL-LHC luminosity measurement.
@@
 
-\newpage
-\begin{flushleft} 
-Table 1: Expected statistical precision (in $\%$) in head-on collisions during typical vdM conditions with pileup of 0.5 for TEPX clusters and two fold coincidences over different integration time period.
-\end{flushleft} 
-\begin{center}
-\scalebox{1}{
-\begin{tabular}{|l | c | c | c |c|}
-\hline
- vdM (PU 0.5) & Readout Rate (kHz) &1 bx, 1s & 1 bx, 30s & 100 bx, 30s\\
+\begin{table}[htbp]
+  \centering
+  \caption[Expected stat.
+precision of TEPX under low pileup] {Expected statistical precision (in $\%$) in head-on collisions during typical vdM conditions with pileup of 0.5 for TEPX clusters and two fold coincidences over different integration time period.}
+\begin{tabular}{lcccc}
+vdM (PU 0.5) & Readout Rate (kHz) & 1 bx, 1s & 1 bx, 30s & 100 bx, 30s\\
 \hline
 TEPXD4R1 Clusters&1000&1.82&0.332 & 0.0332\\
-\hline
 TEPXD4R1 2x Coincidences in phi &1000&5.98&1.09 & 0.109\\
-\hline
 TEPXD4R1 2x Coincidences in r &1000&11.1&2.02 & 0.202\\
-\hline
 TEPXD4R1 2x Coincidences &1000&5.27&0.962 & 0.0962\\
-\hline
 TEPX Clusters&500&0.709&0.129 & 0.0129\\
-\hline
 TEPX 2x Coincidences in phi &500&2.65&0.485 & 0.0485\\
-\hline
 TEPX 2x Coincidences in r &500&4.59&0.838 & 0.0838\\
-\hline
 TEPX 2x Coincidences &500&2.3&0.42 & 0.042\\
-\hline
-\end{tabular}}
-\end{center}
-
-\begin{flushleft} 
-  Table 2: Expected statistical precision (in $\%$) in head-on collisions during physics conditions with pileup of 200 for TEPX clusters and two fold coincidences over different integration time period.
-  \end{flushleft} 
-\begin{center}
-\scalebox{1}{
-\begin{tabular}{|l | c | c | c |c |}
-\hline
-Algorithm & Readout Rate (kHz)& 1 bx, 1s &2500 bx, 1s   & 2500 bx, 1 LS \\
-\hline
-TEPXD4R1 Clusters&825&0.1&0.002&0.000414\\
-\hline
-TEPXD4R1 2x Coincidences in phi &825&0.329&0.00659&0.00136\\
-\hline
-TEPXD4R1 2x Coincidences in r &825&0.61&0.0122&0.00252\\
-\hline
-TEPXD4R1 2x Coincidences  &825&0.29&0.0058&0.0012\\
-\hline
-TEPX Clusters &75&0.0915&0.00183&0.000379\\
-\hline
-TEPX 2x Coincidences in phi &75&0.343&0.00685&0.00142\\
-\hline
-TEPX 2x Coincidences in r &75&0.593&0.0119&0.00245\\
-\hline
-TEPX 2x Coincidences &75&0.297&0.00594&0.00123\\
-\hline
-\end{tabular}}
-\end{center}
+\end{tabular}
+\end{table}
+
+\begin{table}[htbp]
+\centering
+\caption[Expected stat.
+precision of TEPX under high pileup]{Expected statistical precision (in $\%$) in head-on collisions during physics conditions with pileup of 200 for TEPX clusters and two fold coincidences over different integration time period.}
+\begin{small} % this command will decrease the font size
+\begin{tabular}{lcccc}
+Algorithm & Readout Rate (kHz) & 1 bx, 1s & 2500 bx, 1s & 2500 bx, 1 LS \\
+\hline
+TEPXD4R1 Clusters & 825 & 0.1 & 0.002 & 0.000414 \\
+TEPXD4R1 2x Coincidences in phi & 825 & 0.329 & 0.00659 & 0.00136 \\
+TEPXD4R1 2x Coincidences in r & 825 & 0.61 & 0.0122 & 0.00252 \\
+TEPXD4R1 2x Coincidences & 825 & 0.29 & 0.0058 & 0.0012 \\
+TEPX Clusters & 75 & 0.0915 & 0.00183 & 0.000379 \\
+TEPX 2x Coincidences in phi & 75 & 0.343 & 0.00685 & 0.00142 \\
+TEPX 2x Coincidences in r & 75 & 0.593 & 0.0119 & 0.00245 \\
+TEPX 2x Coincidences & 75 & 0.297 & 0.00594 & 0.00123 \\
+\end{tabular}
+\end{small}
+\end{table}
 
@@
 
-\item 2023-2025: Installation of the new detectors and electronics in the CMS detector, including the pixel and strip detectors, timing layer, and data acquisition system.
-
-\item 2025-2026: Commissioning and testing of the upgraded detector.
-
-\item 2026: Full operation of the upgraded CMS detector.
+\item 2024-2026: Installation of the new detectors and electronics in the CMS detector, including the pixel and strip detectors, timing layer, and data acquisition system.
+
+\item 2027-2028: Commissioning and testing of the upgraded detector.
+
+\item 2029: Full operation of the upgraded CMS detector.
 
 \end{itemize}
-
-\begin{comment}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/xvsy_cluster.png}
-\caption{%
-  cluster map tepx 
-}
-\label{fig:cluster_xvsy}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/cluster_ring.png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/tepx_dataset.png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/tepx_events_processed.png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/tepx_cluster_pu100.png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/clusters_tepx_disk4.png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/clusters_tepx_pu10_allrings.png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/lowpu_clusters_fit_D4R1.png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/fit_extrapol_D4R1.png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/twofoldcoin_D4_allring (1).png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/twofold_geometry_pu30.png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/lowpufit_twofold_D4R1.png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/twofoldcoincidences_extrapolation_D4R1.png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/twofold_residual_D4R1.png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/events_per_file_tepx_sim.png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/clusters_D4R1_low_allPU.png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/twofoldcoin_low_allpu_D4R1.png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/threefoldcoin_D4_PU100.png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/threefoldcoin_D4_allpu.png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/threefoldcoin_D4_lowPU.png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/stat_prec_d4r1.png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/cut_optimization_twofold.png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/cut_optimization_twofold.png}
-\caption{%
-  cluster per event ring tepx 
-}
-\label{fig:cluster_ring}
-\end{figure}
-
-\end{comment}

### 2023-12-17 tesis_Ashish/Portada/Portada.tex
Sehrawat A thesis 17 Dec 2023

@@
       \vspace{2cm}
-        {\Large \scshape {Luminosity measurement with the Pixel detector at the CMS experiment of the Large Hadron Collider}
+        {\Large \scshape {Measurement of the luminosity in proton-proton collisions at the CMS experiment of the Large Hadron Collider}
 
         \vspace{3cm}
+%\end{minipage}
+%\begin{minipage}[c][0.5\textheight][t]{0.5\textwidth}
+{ \fontsize{10pt}{12pt}\selectfont
+        \makebox[5cm][c]{\textbf{THESIS}}  \\[10pt]
+         in partial fulfillment of the
+requirements for the degree of:\\[3pt]
+        {\textbf{{Doctorado en Ciencias (F\'isica)}}}\\[20pt]
+        By:\\[6pt]
+        \textbf{  {Ashish Sehrawat}}
 
-        \makebox[5cm][c]{\LARGE THESIS}  \\[20pt]
-         in partial fulfillment of the
-requirements for the degree of:\\[5pt]
-        {\Large \textbf{{Doctorado en Ciencias (F\'isica)}}}\\[40pt]
-        By:\\[12pt]
-        \textbf{  {\large Ashish Sehrawat}}
+        \vspace{1cm}
 
+        { Director}:\\Dr. Jose Feliciano BENITEZ RUBIO \\
         \vspace{2cm}
-
-        { \large Director}:\\Dr. Jose Feliciano BENITEZ RUBIO
-
-        \vspace{2.5cm}
-
-        { Hermosillo, Sonora} \hskip2.5cm {June, 2023}
+        %{ Hermosillo, Sonora} \\ \hskip1.25cm  \\ 28 November, 2023 \\
+        { Hermosillo, Sonora} \\[1.25cm]
+        \mydateformat\today \\
+        }
       \end{center}

### 2023-12-22 tesis_Ashish/Chapter7/chapter7.tex
Updated 22Dec2023

@@
 
-The Phase II upgrade of the CMS Tracker is a crucial project undertaken to maintain the effectiveness of the CMS experiment during the High Luminosity LHC (HL-LHC) run, which is expected to start in 2027.
+The Phase II upgrade of the CMS Tracker is a crucial project undertaken to maintain the effectiveness of the CMS experiment during the High Luminosity LHC (HL-LHC) phase, which is expected to start in 2029.
 The HL-LHC will significantly increase the instantaneous luminosity, leading to a higher number of proton-proton collisions per bunch crossing.
-Instantaneous luminosity will increase to an unprecedented value of $7.5 \times 10^{34} cm^{-2} s^{-1}$ which corresponds to 200 proton-proton collisions per bunch crossing.
-This higher collision rate poses several challenges, including increased radiation levels, higher data rates, and more complex event environments.
+Instantaneous luminosity will increase to an unprecedented value of $7.5 \times 10^{34} cm^{-2} \: s^{-1}$ which corresponds to 200 proton-proton collisions per bunch crossing.
+This higher collision rate poses several challenges, including increased radiation levels, higher data rates, and more complex event environment.
 Run 2 pixel detector will not be able to handle these extreme radiation environment, resolve nearby particle tracks and operate properly to give a reliable estimate of the instantaneous luminosity for such a high pileup.
@@
 The Phase II upgrade of the CMS tracker comprises of two main components: the Inner Tracker (IT) and the Outer Tracker (OT) \cite{collaboration:2759074}.
-The Inner Tracker consists of three main sub-components: the TEPX (Tracker Endcap Pixel), the TFPX (Tracker Forward Pixel), and the TBPX (Tracker Barrel Pixel) detectors as shown in Fig.
+The Inner Tracker consists of three main sub-components: the Tracker Endcap Pixel detector (TEPX), the Tracker Forward Pixel detector (TFPX), and the Tracker Barrel Pixel (TBPX) detector as shown in Fig.
 \ref{fig:Innertracker}.
-TEPX will have better radiation tolerance, increased granularity, improved two-track separation, improved estimation of hit rate and statistical precision, extended tracking acceptance $|\eta|=4$ with Disk 4 Ring 1 operating as an independent luminosity measurement device \cite{Collaboration:2706512}.
 The Outer Tracker is responsible for detecting charged particles in the outer region of the CMS detector.
@@
 
+The TBPX occupies the central region along the \( z \)-axis from 0 to just below 300~mm, employing 360 units of \( 1 \times 2 \) modules and 504 units of \( 2 \times 2 \) modules.
+The TFPX extends from approximately 300~mm to 600~mm in the \( z \)-direction, with 832 units of \( 1 \times 2 \) and 896 units of \( 2 \times 2 \) modules.
+The TEPX covers a broader range from about 600~mm to over 2500~mm and includes 768 units of \( 1 \times 2 \) and 992 units of \( 2 \times 2 \) modules.
+TEPX consists of four double disks per side with each double disk consisting of five rings as shown in Fig.
+\ref{fig:Innertracker_40} having 20, 28, 36, 44 and 48 modules respectively.
+One double disk has four surfaces with +Z side consisting of modules with even module number in front layers (L1 $\&$ L2) and modules with odd module number in back layers (L3 $\&$ L4) from Ring 1 to Ring 4 and for Ring 5, modules with odd module number in front layers and modules with even module number in back layers as shown in Fig.
+\ref{fig:Innertracker_41}.
+For -Z side, four surfaces contain modules with odd module number in front layer and modules with even module number in back layer from Ring 1 to Ring 4 and for Ring 5, modules with even module number in front layer and modules with odd module number in back layer.
+TEPX will have better radiation tolerance, increased granularity, improved two-track separation, improved estimation of hit rate and statistical precision, extending tracking acceptance beyond $|\eta|=4$.
+Collectively, these sub-detectors boast around 1.947 billion pixels across 13,488 pixel chips, spanning a silicon area of 4.87 square meters.
+
+The Outer Tracker is designed for tracking particles over extended radii with six "barrel" layers for \( |z| < 1200 \)~mm and five "endcap" double-discs for \( 1200 \text{~mm} < |z| < 2700 \)~mm.
+The modules are radially placed from about 21~cm to 112~cm.
+It features 2S modules with 2032 strips each and PS modules with 1920 strips and 30,720 macro-pixels of about 1.5~mm size.
+The PS modules are located in the innermost three layers (200--600~mm radial distance) for precise \( z \)-coordinate measurement, while the 2S modules are positioned in the outer layers beyond 600~mm, with various strip lengths to cater to different tracking requirements.
+
+\begin{figure}[!htp]
+  \centering
+  \includegraphics[width=1 \columnwidth]{ashish_thesis/tepx_tt_1.png}
+  \caption[Phase II CMS Inner Tracker]{ \onehalfspacing A layout of the CMS Phase II inner tracker showing four TEPX disks, eight TFPX disks and four barrel layers.}
+  \label{fig:Innertracker}
+\end{figure}
+
+\begin{figure}[!htp]
+  \centering
+  \includegraphics[width=0.6 \columnwidth]{ashish_thesis/tepx_DD.png}
+  \caption[TEPX double disk]{ \onehalfspacing View of one TEPX disk in the $r-\phi$ plane; individual pixel modules on two planes (double-disk) and five rings are outlined by yellow rectangles.
+The planes are separated in z by about 1 cm.
+The first plane holds modules on both front and back faces, with alternating rings to cover the gaps in r; the second plane holds modules in the same way as the first plane, but with an offset in phi to cover the gaps in phi.}
+  \label{fig:Innertracker_40}
+\end{figure}
+
+\begin{figure}[!htp]
+  \centering
+  \includegraphics[width=0.3 \columnwidth]{ashish_thesis/tepx_alllayer.png}
+  \caption[TEPX double disk]{ \onehalfspacing R-Z view of the TEPX one double disk showing all four layers L1, L2, L3 and L4.
+Layer 1 and 3 has Ring 1, 2 and 3 modules, Layer 2 and 4 has Ring 2 and Ring 5 modules.}
+  \label{fig:Innertracker_41}
+\end{figure}
+
+\newpage
+\section{Tracker as a Luminometer}
+
+TEPX is designed to function as a high-precision online bunch-by-bunch luminometer, primarily uses pixel cluster counting for luminosity measurement, a method involving the detection and counting of pixel clusters formed due to particle interactions.
+Additionally, TEPX benefits from coincidence counting in overlapping modules for enhanced accuracy and systematic studies.
+Positioned as part of the forward extension of the Inner Tracker detector, TEPX features a sophisticated dedicated trigger system for sampling all relevant bunch crossings in an unbiased manner.
+This system operates at a baseline trigger rate of 75 kHz, which is 10$\%$  of the 750 kHz allocated for physics.
+In terms of data acquisition, TEPX adapts to different operational conditions: during standard physics runs, it maintains a baseline luminosity trigger rate of 75 kHz, while during van der Meer (vdM) scans, this rate can significantly increase, potentially up to 1 MHz.
+The DAQ system of TEPX is designed to handle substantial data rates, with link bandwidth requirements varying from about 79.2 Gb/s at a trigger rate of 825 kHz during nominal physics operations to up to 24 Gb/s at the standard rate of 75 kHz  \cite{Collaboration:2706512}.
+
+TEPX Disk 4 Ring 1 (D4R1), located in the innermost ring of the last disk of the Inner Tracker Endcap Pixel Detector, is uniquely designed for measuring luminosity and beam-induced background (BIB).
+D4R1 is optimally placed due to its low radius, large active area, and high z position, making it highly sensitive and efficient for these measurements.
+D4R1's operational model is distinct from the rest of TEPX.
+It employs the entire available trigger rate and readout bandwidth, which varies based on operational mode (binary readout or Time-over-Threshold information).
+This capability ranges from a trigger rate of 825 kHz (similar to the rest of TEPX) up to several MHz, limited by readout bandwidth and the available e-link capacity.
+In nominal physics conditions, the baseline trigger rate for D4R1 is 825 kHz, while in van der Meer (vdM) conditions, it is 2 MHz, with the potential to reach between 5 and 10 MHz in certain scenarios.
+
+%A significant advantage of D4R1 is its independence from the CMS central services, particularly during special beam conditions like machine development and LHC ramp.
+This independence allows for luminosity measurements and BIB analysis even outside stable beams, providing vital data to improve accelerator performance.
+D4R1 operates on the LHC clock, enabling it to measure BIB throughout the full LHC machine cycle, including during ramp phases when the radio frequency clock, and consequently the bunch clock, increases significantly.
+To maintain this independent yet synchronized operation with the rest of CMS, a special clocking scheme is employed.
+This scheme involves the BRIL trigger board (BTB) and a Data Transmission Hub (DTH), which interfaces with the central TCDS2 system to receive all necessary signals, including clocks, triggers, and synchronization commands.
+This setup ensures that D4R1 can operate on the LHC clock while remaining synchronized with CMS during various operational phases, including the ramp and stable beams.
+
+The Outer Tracker (OT) Layer 6 of the CMS will play a pivotal role in luminosity measurement, trigger, and data acquisition for the CMS experiment.
+It is designed to perform bunch-by-bunch measurements.
+This is achieved by utilizing a technique called "coincidence counting," which involves detecting two-hit coincidences on two closely spaced silicon sensors, also known as "stubs." This system operates at the full 40 MHz bunch-crossing frequency, which is essential for capturing the high-frequency data required for accurate and timely analysis.
+
+%As part of the forward extension of the Inner Tracker detector, TEPX features an advanced dedicated trigger system.
+This system is crucial for sampling all relevant bunch crossings in an unbiased manner, operating at a trigger rate of 75 kHz, which constitutes 10$\%$ of the 750 kHz allocated for physics.
+For luminosity measurements, TEPX primarily employs pixel cluster counting, a technique that counts the number of pixel clusters formed due to particle interactions within the detector.
+Additionally, TEPX is capable of coincidence counting in overlapping modules, enhancing measurement accuracy and aiding in systematic studies.
+This method counts coincident events in neighboring modules.
+In terms of data acquisition, TEPX adapts to varying operational conditions: during standard physics runs, it manages a baseline luminosity trigger rate of 75 kHz, while during van der Meer (vdM) scans, this rate can increase considerably, potentially up to 1 MHz.
+The DAQ system of TEPX is designed to handle substantial data rates, with link bandwidth requirements varying from about 79.2 Gb/s at a trigger rate of 825 kHz during nominal physics operations to up to 24 Gb/s at the standard rate of 75 kHz.
+This sophisticated combination of trigger systems, pixel cluster counting, and adaptable DAQ capabilities highlights TEPX's vital role in accurate luminosity measurement across different CMS operational scenarios.
+
+\begin{comment}
+
+ with Disk 4 Ring 1 operating as an independent luminosity measurement device \cite{Collaboration:2706512}. 
 \begin{enumerate}
@@
 
-\item Data Acquisition (DAQ) system for the Phase II CMS Tracker must handle the increased data rates and complexity associated with the high-luminosity phase of the LHC (HL-LHC).
-The HL-LHC is expected to achieve a peak luminosity of about $5-7.5 \times 10^{34} cm^{-2}s^{-1}$, which is around 5-7 times higher than the initial LHC design luminosity.
-This increased luminosity leads to a higher collision rate and more complex events, which the DAQ system must handle.
-
-\begin{itemize}
-
- \item Data Rates: The upgraded CMS Tracker will generate a large amount of data due to the increased granularity of the pixel and strip sensors.
+\end{comment}
+
+Data Acquisition (DAQ) system for the Phase II CMS Tracker must handle the increased data rates and complexity associated with the high-luminosity phase of the LHC (HL-LHC).
+The HL-LHC is expected to achieve a peak luminosity which is around 5-7 times higher than the current LHC design luminosity which the DAQ system must handle.
+The upgraded CMS Tracker will generate a large amount of data due to the increased granularity of the pixel and strip sensors.
 The data rates from the tracker modules are expected to be several terabits per second (Tbps) during the HL-LHC operation.
-
- \item Trigger Rate: The Level-1 Trigger system in the Phase II Upgrade is designed to accept events at a rate of up to 750 kHz.
+The Level-1 Trigger system in the Phase II Upgrade is designed to accept events at a rate of up to 750 kHz.
 The DAQ system must handle the transmission of trigger primitives to the Level-1 Trigger system and buffer the full event data until the trigger decision is made.
-
-  \item Optical Links: The high-speed optical links used for data transmission between the Front-End Electronics (FEE) and off-detector electronics are expected to operate at data rates of 10-25 Gbps or higher to handle the large data volumes generated by the upgraded tracker.
-
-  \item Buffering and Storage: The off-detector electronics must be able to buffer and store the full event data generated by the tracker modules until the Level-1 Trigger decision is made.
-The required buffering capacity depends on the trigger rate and the average event size but is expected to be in the order of several terabytes to accommodate the high data rates and trigger latencies.
-
-  \item Processing Latency: The DAQ system must process the raw detector data and form trigger primitives within a very tight time constraint.
-The processing latency budget for the formation of trigger primitives in the Outer Tracker is expected to be around a few microseconds.
-
-\end{itemize}
-
-\end{enumerate}
-
-\section{Tracker Endcap Pixel (TEPX) detector}
-
-Tracker endcap pixel detector (TEPX) consists of four double disks per side (-Z and +Z) (shown in left part of Fig.
-\ref{fig:Innertracker}) with each double disk consisting of five rings as shown in right part of Fig.
-\ref{fig:Innertracker} having 20, 28, 36, 44 and 48 modules respectively.
-One double disk has four surfaces with +Z side consisting of modules with even module number in front layers (L1 $\&$ L2) and modules with odd module number in back layers (L3 $\&$ L4) from Ring 1 to Ring 4 and for Ring 5, modules with odd module number in front layers and modules with even module number in back layers.
-%as shown in Fig.
-\ref{fig:CMS1_49}.
-For -Z side, four surfaces contain modules with odd module number in front layer and modules with even module number in back layer from Ring 1 to Ring 4 and for Ring 5, modules with even module number in front layer and modules with odd module number in back layer.
-\\
-
-\begin{figure}[!htp]
-  \centering
-  \includegraphics[width=1 \columnwidth]{ashish_thesis/tepx_tt.png}
-  \caption[Phase II CMS Inner Tracker]{ \onehalfspacing Left: A layout of the CMS Phase II inner tracker showing four TEPX disks, eight TFPX disks and four barrel layers.
-Right: Diagram showing one double disk of TEPX with five rings.}
-  \label{fig:Innertracker}
-\end{figure}
+The high-speed optical links used for data transmission between the Front-End Electronics (FEE) and off-detector electronics are expected to operate at data rates of 10-25 Gbps or higher to handle the large data volumes generated by the upgraded tracker.
+
+%\section{Tracker Endcap Pixel (TEPX) detector}
 
@@
 
-\section{Phase II CMS tracker simulation samples}
-
- Simulated data samples for Phase II include full CMS detector description and uses official CMS software (version $\texttt{CMSSW\_10\_6\_0\_patch2}$) which calls GEANT4 for particle and energy deposit simulation as well as for reconstruction \cite{GEANT4:2002zbu}.
-These samples contain single-neutrino event overlaid with a variable number of minimum-bias events (events with any amount of real energy detected in CMS) to simulate different pileup values.
-The statistics for samples with average pileup values from 0.5 to 2 is 500000 events per step and for average pileup values between 10 and 200, statistics is 100000 as shown in Table \ref{tab:sample_12}.
-The number of event processed in this study for each pileup is shown in Table \ref{tab:sample_2}.
+\section{TEPX Luminomter Simulation}
+
+ Simulated data samples for Phase II include full CMS detector description and uses official CMS software (version $\texttt{CMSSW\_10\_6\_0\_patch2}$) which calls GEANT4 for detector simulation \cite{GEANT4:2002zbu}.
+Pixel cluster reconstruction is done by converting raw data to digi format (row, column, charge) and then form clusters from digis.
+The samples used in simulation contain single-neutrino event overlaid with a variable number of minimum-bias events (events with any amount of real energy detected in CMS) to simulate different pileup values.
+The number of simulated events used in this analysis for each pileup value is shown in Table \ref{tab:12}.
+
+\begin{comment}
 
@@
   \end{tabular}
-  \label{tab:sample_12}
-\end{table}
+  \label{tab:12}
+\end{table}
+
+\end{comment}
 
@@
 \begin{comment}
+
 \begin{table}[ht]
@@
   %\caption{Events processed for each pileup}
-  \label{tab:sample_2}
-\end{table}
+  \label{tab:12}
+\end{table}
+
+\begin{comment}
 
@@
 
+\end{comment}
+
 Fig.
 \ref{fig:tepx_cl} shows the location of TEPX clusters in Disk 4 in the XY plane (Z is the direction of the beam) from a simulated sample with a pileup of 200.
-Clusters refer to groups of hits in the pixel detector.
+%Clusters refer to groups of hits in the pixel detector.
 The TEPX disk in this map consists of 5 rings which are concentric rings of pixel modules at different radial distances from the beamline.
@@
 
+\subsection{Linearity of TEPX clusters}
+
+Linearity is one of the systematic uncertainty in the calculation of instantaneous luminosity and PCC visible cross section $\sigma_{vis}$.
+A linear relation between the number of clusters and pileup (PU) imply that \\
+
+$<N_{cl/pp}> = \frac{<N_{cl}>}{\mu} = \frac{\sigma_{vis}}{\sigma_{pp}}$ \\
+
+$<N_{cl}> =  \frac{\sigma_{vis}}{\sigma_{pp}} \mu $ \\
+
+Linearity indicates that the PCC visible cross section $\sigma_{vis}$ does not depend on the per bunch instantaneous luminosity (ideal luminometer).
+In ideal scenario, $\sigma_{vis}$ is not dependent on pileup, but this a potential problem with the luminometer.
+TEPX luminometer proposed for Phase II shows excellent linearity over entire pileup range.
+A non-linear relation $<N_{cluster}> = \alpha (PU)^{\gamma}, \gamma \neq 1$ would add non-linear terms in the rate equation $R = \sigma_{vis} L_{inst}$  and cause $\sigma_{vis}$ to vary with the per bunch instantaneous luminosity and pileup values.
+
 The number of clusters per pp collision in Disk 4 Ring 1 varies from 0 to 2600 as a function of pileup.
@@
 For average pileup value of 0.5 (vdM conditions), number of clusters varies between 0 and 12.
+Linearity results for simulated TEPX clusters from low to high pileup values are shown in  Fig.
+\ref{fig:CMS_4205} and  \ref{fig:CMS_4206}.
+Non-linearity is within 1 \% for entire pileup range.
 
@@
 
-Linearity is one of the systematic uncertainty in the calculation of instantaneous luminosity and PCC visible cross section $\sigma_{vis}$.
-A linear relation between the number of clusters and pileup (PU) imply that \\
-
-$<N_{cl/pp}> = \frac{<N_{cl}>}{\mu} = \frac{\sigma_{vis}}{\sigma_{pp}}$ \\
-
-$<N_{cl}> =  \frac{\sigma_{vis}}{\sigma_{pp}} \mu $ \\
-
-Linearity indicates that the PCC visible cross section $\sigma_{vis}$ does not depend on the per bunch instantaneous luminosity (ideal luminometer).
-In ideal scenario, $\sigma_{vis}$ is not dependent on pileup, but this a potential problem with the luminometer.
-Linearity results for simulated TEPX clusters from low to high pileup values are shown from Fig.
-\ref{fig:CMS_420} to Fig.
-\ref{fig:CMS_005}.
-TEPX luminometer proposed for Phase II shows excellent linearity over entire pileup range.
-A non-linear relation $<N_{cluster}> = \alpha (PU)^{\gamma}, \gamma \neq 1$ would add non-linear terms in the rate equation $R = \sigma_{vis} L_{inst}$  and cause $\sigma_{vis}$ to vary with the per bunch instantaneous luminosity and pileup values.
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_2.png}
+  \caption[TEPX Clusters Fit And Residuals]{\onehalfspacing Left: Simulated mean number of clusters for TEPX disks as a function of pileup.
+A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.
+Right: Deviation from linearity for clusters for  TEPX disks.
+The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.
+}
+  \label{fig:CMS_4205}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_3.png}
+  \caption[TEPX Clusters Fit And Residuals]{\onehalfspacing Left: Simulated mean number of clusters for  TEPX Disk 4 Ring 1 as a function of pileup.
+A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.
+Right: Deviation from linearity for clusters for TEPX Disk 4 Ring 1.
+The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.
+}
+  \label{fig:CMS_4206}
+\end{figure}
+
+\begin{comment}
 
@@
 
+\end{comment}
+
+\subsection{TEPX two fold coincidences}
+
 Two fold coincidences are clusters in modules overlap regions formed by modules in front and back layers of TEPX disk.
@@
 Luminosity determination based on counting coincidences has an advantage over clusters that afterglow effects are tiny in the case of coincidences.
-%as shown in Fig.
-\ref{fig:cluster_ring_4000}.
+%as shown in Fig. \ref{fig:cluster_ring_4000}. 
  %(shown in Fig. \ref{fig:cluster_ring_73})
@@
 
-\newpage
 A new algorithm for luminosity measurement based on counting two fold coincidences is proposed that applies selections using dr and $d\phi$ variables (shown in Fig.
@@
 We study the two fold coincidences in phi for all TEPX Disk and rings using dr, dphi variable for pileup 0.5 and apply nominal selection of 0.15 cm on dr and 0.04 on dphi variable in order to remove fake coincidences.
-After obtaining these distributions for all TEPX disks and rings, we carry out fit of the distribution to obtain mean and standard deviation of these distributions.
+
 The dr, dphi distribution showing true, fake, total two fold coincidences for Disk 4 Ring 1 for pileup 0.5 is shown in Fig.
 \ref{fig:cluster_dr_dphi_dist}.
+After obtaining these distributions for all TEPX disks and rings, we carry out fit of the true coincidences distribution (shown in red  color) to obtain mean and standard deviation of these distributions.
+Two standard deviation cut is applied on the dr variable.
+The mean values are shown in Table \ref{tab:mdr_cuts_offset_values}.
+The  standard deviation values of the fit to true coincidences for all disks and rings are shown in Table \ref{tab:disk_values}.
 %Example fits are shown in Fig.
 \ref{fig:cluster_ring_1003}, \ref{fig:cluster_ring_70}, \ref{fig:cluster_ring_71}.
+Similarly, two sigma cut is applied on the dphi variable as well.
+The standard deviation values for dphi variable are shown in Table \ref{tab:mdphi_cuts_values}.
 While doing the fit, mean value for dphi variable is set to zero.
 %The mean is taken as the offset value and standard deviation is used as the selection on dr, dphi variables as shown in Table \ref{tab:disk_values}, \ref{tab:mdphi_cuts_values} and \ref{tab:mdr_cuts_offset_values}.
-The mean of the fit is taken as the offset value and standard deviation is used as the selection on dr, dphi variables as shown in Table \ref{tab:disk_values}, \ref{tab:mdphi_cuts_values} and \ref{tab:mdr_cuts_offset_values}.
+The mean of the fit is taken as the offset value and standard deviation is used as the cut on dr, dphi variables.
 
@@
 %The mean of the fit is taken as the offset value and standard deviation is used as the selection on dr, dphi variables as shown in Table \ref{tab:disk_values}, \ref{tab:mdphi_cuts_values} and \ref{tab:mdr_cuts_offset_values}.
+
+\begin{table}[h]
+  \centering
+  \caption[dr offset values]{dr mean values obtained from fit for two fold coincidences in phi for all disks and rings}
+  \begin{tabular}{cccccc}
+    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} & \textbf{Ring 4} & \textbf{Ring 5} \\
+    \hline
+    %-1 & 0.0342041  & 0.0511416 & 0.0676943 & 0.0834355 & 0.0984932 \\
+    %-2 & 0.0298276  & 0.0445398 & 0.0589828 & 0.0727454 & 0.0853587 \\
+    %-3 & 0.0260326  & 0.0386608 & 0.05122   & 0.0632478 & 0.0746467 \\
+    %-4 & 0.0227089  & 0.0336467 & 0.044476  & 0.0551065 & 0.06484   \\
+    1  & 0.034  & 0.051 & 0.068 & 0.084 & 0.098 \\
+    2  & 0.030  & 0.044 & 0.059 & 0.073 & 0.085 \\
+    3  & 0.026  & 0.039 & 0.051 & 0.063 & 0.074 \\
+    4  & 0.023   & 0.034 & 0.045 & 0.055 & 0.064 \\
+  \end{tabular}
+  \label{tab:mdr_cuts_offset_values}
+\end{table}
 
@@
 
-\begin{table}[h]
-  \centering
-  \caption[dr offset values]{dr mean values obtained from fit for two fold coincidences in phi for all disks and rings}
-  \begin{tabular}{cccccc}
-    \textbf{Disk} & \textbf{Ring 1} & \textbf{Ring 2} & \textbf{Ring 3} & \textbf{Ring 4} & \textbf{Ring 5} \\
-    \hline
-    %-1 & 0.0342041  & 0.0511416 & 0.0676943 & 0.0834355 & 0.0984932 \\
-    %-2 & 0.0298276  & 0.0445398 & 0.0589828 & 0.0727454 & 0.0853587 \\
-    %-3 & 0.0260326  & 0.0386608 & 0.05122   & 0.0632478 & 0.0746467 \\
-    %-4 & 0.0227089  & 0.0336467 & 0.044476  & 0.0551065 & 0.06484   \\
-    1  & 0.034  & 0.051 & 0.068 & 0.084 & 0.098 \\
-    2  & 0.030  & 0.044 & 0.059 & 0.073 & 0.085 \\
-    3  & 0.026  & 0.039 & 0.051 & 0.063 & 0.074 \\
-    4  & 0.023   & 0.034 & 0.045 & 0.055 & 0.064 \\
-  \end{tabular}
-  \label{tab:mdr_cuts_offset_values}
-\end{table}
-
 \newpage
-The final plot of two fold coincidences in phi after applying all selection based on standard deviation values of all tepx disks and rings is shown in Fig. \ref{fig:cluster_ring_720}.
+A plot of two fold coincidences in phi after applying all selection based on standard deviation values of all TEPX disks and rings is shown in Fig. \ref{fig:cluster_ring_720}.
 
@@
 
-\newpage
 Simlarly, we also studied two fold coincidences in r which arise from module overlaps between successive rings by only considering one to one module overlap between first two and last two layers in one TEPX double disk.
@@
 \ref{fig:cluster_ring_770}.
- A one-to-one overlapping of modules is considered between L1L2 and L3L4 module overlap. %as shown in Fig. \ref{tab:my_label2}. 
+ A one-to-one overlapping of modules is considered between L1L2 and L3L4 module overlap as shown in Fig. \ref{fig:cluster_ring_72034}. %as shown in Fig. \ref{tab:my_label2}. 
  %The distributions for dr, dphi distribution depicting fake, true, total two fold coincidence in r for pileup 0.5 and 200 are shown in Fig.
 \ref{fig:cluster_ring_81} and \ref{fig:cluster_ring_82} respectively.
- Fit is done to pileup 0.5 distribution of true coincidences for both L1L2 and L3L4 coincidences in r .%as shown in Fig. \ref{fig:cluster_ring_83} and \ref{fig:cluster_ring_84}. 
- Fit results for all disks and rings are shown from  Table \ref{tab:my_label_55} to \ref{tab:my_label_50}.
+ Fit is done to pileup 0.5 distribution of true coincidences for both L1L2 and L3L4 coincidences in r. %as shown in Fig. \ref{fig:cluster_ring_83} and \ref{fig:cluster_ring_84}. 
+  Fit results for all disks and rings are shown from  Table \ref{tab:my_label_55} to \ref{tab:my_label_54}.
+Two standard deviation selections are applied on dr, dphi variables.
 After applying all selections obtained from the fits, we plotted the XY map of two fold coincidences in r for L1L2 and L3L4 combined as shown in \ref{fig:cluster_ring_79}.
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.3\textwidth]{ashish_thesis/twofoldinr_exam.png}
+\caption[Examples of two fold coincidences in r]{%
+  Map of two fold coincidences in r showing all module overlap regions.
+}
+\label{fig:cluster_ring_72034}
+\end{figure}
 
@@
   \centering
-  \caption[dr mean values (L1L2)]{dr mean values obtained from fit for all disks and rings for coincidences in r in layers L1L2}
+  \caption[dr mean values (L1L2)]{dr mean values obtained from fit for all disks and rings for coincidences in r}
 \begin{tabular}{ccccc}
@@
 %-1 & 0.0150614 & 0.0202725 & 0.0255259 & 0.0303849 \\
-1 & 0.0229736 & 0.0311421 & 0.0390871 & 0.0468038 \\
-2 & 0.0202136 & 0.0268963 & 0.0337796 & 0.040398 \\
-3 & 0.0174894 & 0.0233893 & 0.0293971 & 0.0351501 \\
-4 & 0.0149661 & 0.020194  & 0.0255051 & 0.0305483 \\
+1 & 0.023 & 0.031 & 0.039 & 0.047 \\
+2 & 0.020 & 0.027 & 0.034 & 0.040 \\
+3 & 0.018 & 0.023 & 0.029 & 0.035 \\
+4 & 0.015 & 0.020  & 0.026 & 0.031 \\
 \end{tabular}
@@
   \centering
-  \caption[dphi cut values (L1L2)]{dphi standard deviation values obtained from fit for all disks and rings for coincidences in r in layers L1L2}
+  \caption[dr cut values (L1L2)]{dr standard deviation values obtained from fit for all disks and rings for coincidences in r}
+\begin{tabular}{ccccc}
+ & \multicolumn{4}{c}{\textbf{Ring}} \\
+\textbf{Disk} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} \\
+\hline
+%-4 & 0.00458531 & 0.00466448 & 0.00486059 & 0.0052905 \\ 
+%-3 & 0.00444971 & 0.0046465 & 0.00472138 & 0.00490022 \\ 
+%-2 & 0.00453556 & 0.00471864 & 0.00465781 & 0.00503102 \\ 
+%-1 & 0.00457346 & 0.00458345 & 0.00478342 & 0.00497171 \\
+1 & 0.0045 & 0.0045 & 0.0047 & 0.0052 \\
+2 & 0.00442 & 0.0047 & 0.0048 & 0.0050 \\
+3 & 0.0045 & 0.0045 & 0.0049 & 0.0049 \\
+4 & 0.0045 & 0.0047 & 0.0049 & 0.0049 \\
+\end{tabular}
+\label{tab:my_label_53}
+\end{table}
+
+\begin{table}[H]
+  \centering
+  \caption[dphi cut values (L1L2)]{dphi standard deviation values obtained from fit for all disks and rings for coincidences in r}
 \begin{tabular}{ccccc}
@@
 %-1 & 0.000451069 & 0.000604104 & 0.000689508 & 0.000755603 \\
-1 & 0.000627781 & 0.000814669 & 0.000941641 & 0.0010221 \\
-2 & 0.000573352 & 0.000761853 & 0.000851161 & 0.000901014 \\
-3 & 0.000523361 & 0.000662691 & 0.000778358 & 0.000834924 \\
-4 & 0.000471669 & 0.000589938 & 0.000692007 & 0.000750302 \\
+1 & 0.00063 & 0.00082 & 0.00094 & 0.0010 \\
+2 & 0.00057 & 0.00076 & 0.00085 & 0.00090 \\
+3 & 0.00052 & 0.00066 & 0.00077 & 0.00083 \\
+4 & 0.00047 & 0.00059 & 0.00069 & 0.00075 \\
 \end{tabular}
@@
 
-\begin{table}[H]
-  \centering
-  \caption[dr cut values (L1L2)]{dr standard deviation values obtained from fit for all disks and rings for coincidences in r in layers L1L2}
-\begin{tabular}{ccccc}
- & \multicolumn{4}{c}{\textbf{Ring}} \\
-\textbf{Disk} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} \\
-\hline
-%-4 & 0.00458531 & 0.00466448 & 0.00486059 & 0.0052905 \\ 
-%-3 & 0.00444971 & 0.0046465 & 0.00472138 & 0.00490022 \\ 
-%-2 & 0.00453556 & 0.00471864 & 0.00465781 & 0.00503102 \\ 
-%-1 & 0.00457346 & 0.00458345 & 0.00478342 & 0.00497171 \\
-1 & 0.00448255 & 0.00445856 & 0.00474102 & 0.0051553 \\
-2 & 0.00442349 & 0.00472485 & 0.00474663 & 0.0050426 \\
-3 & 0.00450002 & 0.0045179 & 0.00492058 & 0.00494887 \\
-4 & 0.00444657 & 0.00468584 & 0.00493828 & 0.00488064 \\
-\end{tabular}
-\label{tab:my_label_53}
-\end{table}
+\begin{comment}
 
@@
 
+\end{comment}
+
 \begin{comment}
@@
 \newpage
-The new algorithm is able to remove physics noise at high pileup as can be seen from the high efficiency values and low fake rates for Disk 4 all rings and all pileup samples as shown in Table \ref{tab:sample}, \ref{tab:sample_1} and \ref{tab:sample_2}.
+The new algorithm is able to remove physics noise at high pileup as can be seen from the high efficiency values and low fake rates for Disk 4 all rings and all pileup samples as shown in Table  \ref{tab:sample} and \ref{tab:combined_sample}.
+
+\begin{equation}
+\text{Fake rate} = \frac{\text{Number of fake coincidences (Area under the green curve)}}{\text{Total number of coincidences (Area under the black curve)}}
+\end{equation}
 
@@
   \centering
-  \caption{Fake rate for Disk 4 all rings}
+  \caption{Fake rate for Disk 4 for pileup 200}
   \begin{tabular}{cc}
@@
 \end{table}
+
+\begin{table}[H]
+  \centering
+  \caption{TEPX two fold coincidences fake rate and efficiency}
+  \begin{tabular}{ccccc}
+    \textbf{Pileup} & \textbf{Fake 2xinphi (\%)} & \textbf{Fake 2xinr (\%)} & \textbf{Efficiency 2xinphi (\%)} & \textbf{Efficiency 2xinr (\%)} \\
+    \hline
+    0.5  & 0.78 & 0.99 & 99.21 & 99.00 \\
+    1    & 0.79 & 1.01 & 99.20 & 98.98 \\
+    1.5  & 0.80 & 1.02 & 99.19 & 98.97 \\
+    2    & 0.79 & 1.02 & 99.20 & 98.97 \\
+    10   & 0.83 & 1.04 & 99.16 & 98.95 \\
+    30   & 0.94 & 1.09 & 99.05 & 98.90 \\
+    50   & 1.04 & 1.14 & 98.95 & 98.85 \\
+    100  & 1.31 & 1.29 & 98.68 & 98.70 \\
+    140  & 1.53 & 1.41 & 98.46 & 98.58 \\
+    200  & 1.85 & 1.57 & 98.14 & 98.42 \\
+  \end{tabular}
+  \label{tab:combined_sample}
+\end{table}
+
+\begin{comment}
 
@@
 
+\end{comment}
+
 %Ratio of the integrals for fake & total coincidence for dr & dphi distributions is 3454/145988 = 0.023
@@
 Under vdM conditions, it range from 0 to 13.
-The new algorithm is able to suppress non-linearity at high pileup values as shown from Fig.
-1.17 to Fig.
-1.24.
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_D4R1_coin_allpu_1.png}
+The new algorithm is able to suppress non-linearity at high pileup values as shown in Fig.
+\ref{fig:CMS_420}  and \ref{fig:CMS_4207}.
+Non-linearity is within 1 \% for entire pileup range.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{ashish_thesis/tepx_D4R1_coin_allpu_1.png}
   \caption[TEPX D4R1 Two Fold Coincidences All Pileup]{Distribution of number of two fold coincidences for TEPX Disk 4 Ring 1 for all pileup values.}
@@
 \end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_1.png}
+  \caption[TEPX two fold coincidences fit And residuals]{\onehalfspacing Left: Simulated mean number of two fold coincidences for TEPX disks as a function of pileup.
+A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.
+Right: Deviation from linearity for two fold coincidences for TEPX disks.
+The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
+  \label{fig:CMS_420}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_4.png}
+  \caption[TEPX two fold coincidences fit And residuals]{\onehalfspacing Left: Simulated mean number of two fold coincidences in phi for TEPX Disk 4 Ring 1 as a function of pileup.
+A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.
+Right: Deviation from linearity for two fold coincidences in phi for TEPX Disk 4 Ring 1.
+The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
+  \label{fig:CMS_4207}
+\end{figure}
+
+\begin{comment}
 
@@
 
+\section{TEPX three fold coincidences}
+
 It is possible to have three fold coincidences in TEPX detector.
-A three-fold coincidence cluster refers to a situation where three hits are detected simultaneously within a tepx disk.
+A three-fold coincidence refers to a situation where three hits occur nearly simultaneously and in a close spatial arrangement originating from the same underlying event.
+In the current algorithm, we look for another cluster in the lower ring after a two fold coincidence cluster is found.
 The XY map of three fold coincidences is shown in Fig.
 \ref{fig:tepx_3foldcoin_allPU_1}.
-When particles pass through the TEPX detector, they can leave behind 'traces' by interacting with the detector.
-These interactions are detected and measured as electrical signals.
-Each interaction might be seen as a 'hit' in the detector.
-When three of these hits occur nearly simultaneously and in a close spatial arrangement, they can form what is known as a three-fold coincidence hit originating from the same underlying event, for instance, the passage of a single particle or a single collision event.
 Three fold coincidences under all pileup conditions is shown in Fig.
@@
 With the current algorithm, three fold coincidences shows non-linearity at high pileup as shown in Fig.
-\ref{fig:tepx_3foldcoin_allPU_3} % and Fig.
+\ref{fig:tepx_3foldcoin_allPU_3}.
+% and Fig.
 \ref{fig:tepx_3foldcoin_lowPU}.
@@
 
+\newpage
 \section{Statistical precision for TEPX luminometer}
@@
 
+\begin{comment}
+
 \section{Summary of the planned upgrade schedule}
@@
 \end{itemize}
+
+\end{comment}

### 2023-12-22 tesis_Ashish/Chapter7/chapter7.tex
Updated 23Dec2023

@@
 \end{comment}
+
+\newpage
+
+\section{Conclusion}
+
+The research presented in this thesis on the PCC luminometer offers profound insights and advancements in luminosity measurement.
+The meticulous analysis and improvement in PCC luminosity analysis, including the development of a comprehensive module veto list and innovative calibration techniques, have significantly enhanced the precision of luminosity measurement.
+The implementation of afterglow correction methodologies addresses residual signals, ensuring the accuracy of the PCC data.
+
+Alongside these achievements, this thesis also contributes substantially to the Phase II upgrade of the CMS detector.
+The Phase II upgrade is a major, multi-year project, currently in its design and development phase, with full operation expected to commence in 2029.
+This upgrade encompasses the installation of new pixel and strip detectors, a timing layer, and an advanced data acquisition system.
+The new carbon-fiber support structure for the upgraded tracker, scheduled for installation between 2022 and 2023, is part of this extensive revamp.
+The period from 2024 to 2026 will see the installation of these new detectors and electronics, followed by a crucial phase of commissioning and testing from 2027 to 2028 to ensure optimal functionality.
+
+The advancements in the PCC luminometer, combined with the upcoming Phase II upgrades, position the CMS detector at the forefront of particle physics research.
+The improvements in luminosity measurement techniques and detector capabilities will enable more precise and accurate experiments, paving the way for groundbreaking discoveries in understanding the fundamental forces and particles of our universe.
+The comprehensive approach and innovative methodologies developed in this thesis are pivotal contributions to the field, enhancing not only current research capabilities but also setting a solid foundation for future explorations in high-energy particle physics.

### 2023-12-23 tesis_Ashish/Chapter7/chapter7.tex
Updated 23Dec2023
update 24Dec2023

@@
   \centering
-  \includegraphics[width=0.3 \columnwidth]{ashish_thesis/tepx_alllayer.png}
+  \includegraphics[width=0.2 \columnwidth]{ashish_thesis/tepx_alllayer.png}
   \caption[TEPX double disk]{ \onehalfspacing R-Z view of the TEPX one double disk showing all four layers L1, L2, L3 and L4.
-Layer 1 and 3 has Ring 1, 2 and 3 modules, Layer 2 and 4 has Ring 2 and Ring 5 modules.}
+Layer 1 and 3 has Ring 1, 3 and 5 modules, Layer 2 and 4 has Ring 2 and Ring 4 modules.}
   \label{fig:Innertracker_41}
@@
 
-\section{TEPX three fold coincidences}
+\subsection{TEPX three fold coincidences}
 
@@
   \includegraphics[width=1\columnwidth]{ashish_thesis/TEPX_threefold_linearity.png}
-  \caption[Disk 4 Ring 2 three Fold Coincidences Linearity]{Left: Simulated mean number of three fold coincidences for all Disk 4 all rings as a function
+  \caption[Disk 4 all rings three Fold Coincidences Linearity]{Left: Simulated mean number of three fold coincidences for all Disk 4 all rings as a function
     of pileup. Right: Deviation from linearity for Disk 4 all rings.}

### 2023-12-29 tesis_Ashish/Chapter7/chapter7.tex
Updated thesis 29 Dec 2023

@@
 \ref{fig:Innertracker}.
-The Outer Tracker is responsible for detecting charged particles in the outer region of the CMS detector.
+%The Outer Tracker is responsible for detecting charged particles in the outer region of the CMS detector.
 It consists of two key subsystems: the silicon strip tracker and the silicon macro pixel tracker \cite{RoyChowdhury:2729279}.
 
-The TBPX occupies the central region along the \( z \)-axis from 0 to just below 300~mm, employing 360 units of \( 1 \times 2 \) modules and 504 units of \( 2 \times 2 \) modules.
+Data Acquisition (DAQ) system for the Phase II CMS Tracker must handle the increased data rates and complexity associated with the high-luminosity phase of the LHC (HL-LHC).
+The HL-LHC is expected to achieve a peak luminosity which is around 5-7 times higher than the current LHC design luminosity which the DAQ system must handle.
+The upgraded CMS Tracker will generate a large amount of data due to the increased granularity of the pixel and strip sensors.
+The data rates from the tracker modules are expected to be several terabits per second (Tbps) during the HL-LHC operation.
+The Level-1 Trigger system in the PhaseII Upgrade is designed to accept events at a rate of up to 750 kHz.
+The DAQ system must handle the transmission of trigger primitives to the Level-1 Trigger system and buffer the full event data until the t\
+rigger decision is made.
+The high-speed optical links used for data transmission between the Front-End Electronics (FEE) and off-detector electronics are expected to operate at data rates of 10-25 Gbps or higher to handle the large data volumes generated by the upgraded tracker.
+
+The TBPX occupies the central region along the \( z \)-axis from 0 to just below 300~mm, employing 360 units of \( 1 \times 2 \) modules (modules with two readout chips) and 504 units of \( 2 \times 2 \) modules (modules with four readout chips).
 The TFPX extends from approximately 300~mm to 600~mm in the \( z \)-direction, with 832 units of \( 1 \times 2 \) and 896 units of \( 2 \times 2 \) modules.
 The TEPX covers a broader range from about 600~mm to over 2500~mm and includes 768 units of \( 1 \times 2 \) and 992 units of \( 2 \times 2 \) modules.
-TEPX consists of four double disks per side with each double disk consisting of five rings as shown in Fig.
-\ref{fig:Innertracker_40} having 20, 28, 36, 44 and 48 modules respectively.
-One double disk has four surfaces with +Z side consisting of modules with even module number in front layers (L1 $\&$ L2) and modules with odd module number in back layers (L3 $\&$ L4) from Ring 1 to Ring 4 and for Ring 5, modules with odd module number in front layers and modules with even module number in back layers as shown in Fig.
+
+The TEPX consists of four double disks per side with each double disk consisting of five rings of modules as shown in Fig.
+\ref{fig:Innertracker_40}.
+The rings have 20, 28, 36, 44 and 48 modules respectively.
+The first two inner rings are equipped with \(1 \times 2\) modules, while the more extensive \(2 \times 2\) modules are mounted on the three outer rings.
+This design is further enhanced by the unique arrangement of modules in four layers as shown in Fig.
 \ref{fig:Innertracker_41}.
-For -Z side, four surfaces contain modules with odd module number in front layer and modules with even module number in back layer from Ring 1 to Ring 4 and for Ring 5, modules with even module number in front layer and modules with odd module number in back layer.
+This allows for modules to be mounted on both the front and back sides of a disk, creating an overlap in the r-\(\phi\) direction.
+Additionally, by mounting modules at varying radii on the two disk that form each double-disk, overlap in the radial direction (r) is also accomplished.
+
+%One double disk has four surfaces with +Z side consisting of modules with even module number in front layers (L1 $\&$ L2) and modules with odd module number in back layers (L3 $\&$ L4) from Ring 1 to Ring 4 and for Ring 5, modules with odd module number in front layers and modules with even module number in back layers as shown in Fig.
+\ref{fig:Innertracker_41}.
+
+%For -Z side, four surfaces contain modules with odd module number in front layer and modules with even module number in back layer from Ring 1 to Ring 4 and for Ring 5, modules with even module number in front layer and modules with odd module number in back layer.
+
 TEPX will have better radiation tolerance, increased granularity, improved two-track separation, improved estimation of hit rate and statistical precision, extending tracking acceptance beyond $|\eta|=4$.
@@
 
-The Outer Tracker is designed for tracking particles over extended radii with six "barrel" layers for \( |z| < 1200 \)~mm and five "endcap" double-discs for \( 1200 \text{~mm} < |z| < 2700 \)~mm.
+%The Outer Tracker is designed for tracking particles over extended radii with six "barrel" layers for \( |z| < 1200 \)~mm and five "endcap" double-discs for \( 1200 \text{~mm} < |z| < 2700 \)~mm.
 The modules are radially placed from about 21~cm to 112~cm.
@@
   \includegraphics[width=1 \columnwidth]{ashish_thesis/tepx_tt_1.png}
-  \caption[Phase II CMS Inner Tracker]{ \onehalfspacing A layout of the CMS Phase II inner tracker showing four TEPX disks, eight TFPX disks and four barrel layers.}
+  \caption[Phase II CMS Inner Tracker]{ \onehalfspacing A layout of the CMS Phase II Inner Tracker showing four TEPX disks, eight TFPX disks and four TBPX layers.}
   \label{fig:Innertracker}
@@
 
-\begin{figure}[!htp]
-  \centering
-  \includegraphics[width=0.6 \columnwidth]{ashish_thesis/tepx_DD.png}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5 \columnwidth]{ashish_thesis/tepx_DD.png}
   \caption[TEPX double disk]{ \onehalfspacing View of one TEPX disk in the $r-\phi$ plane; individual pixel modules on two planes (double-disk) and five rings are outlined by yellow rectangles.
 The planes are separated in z by about 1 cm.
-The first plane holds modules on both front and back faces, with alternating rings to cover the gaps in r; the second plane holds modules in the same way as the first plane, but with an offset in phi to cover the gaps in phi.}
+The first plane holds modules on both front and back faces, with alternating rings to cover the gaps in r; the second plane holds modules in the same way as the first plane, but with an offset in $\phi$ to cover the gaps in $\phi$.}
   \label{fig:Innertracker_40}
@@
 
-\begin{figure}[!htp]
-  \centering
-  \includegraphics[width=0.2 \columnwidth]{ashish_thesis/tepx_alllayer.png}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.1 \columnwidth]{ashish_thesis/tepx_alllayer.png}
   \caption[TEPX double disk]{ \onehalfspacing R-Z view of the TEPX one double disk showing all four layers L1, L2, L3 and L4.
@@
 \newpage
-\section{Tracker as a Luminometer}
-
-TEPX is designed to function as a high-precision online bunch-by-bunch luminometer, primarily uses pixel cluster counting for luminosity measurement, a method involving the detection and counting of pixel clusters formed due to particle interactions.
-Additionally, TEPX benefits from coincidence counting in overlapping modules for enhanced accuracy and systematic studies.
-Positioned as part of the forward extension of the Inner Tracker detector, TEPX features a sophisticated dedicated trigger system for sampling all relevant bunch crossings in an unbiased manner.
-This system operates at a baseline trigger rate of 75 kHz, which is 10$\%$  of the 750 kHz allocated for physics.
-In terms of data acquisition, TEPX adapts to different operational conditions: during standard physics runs, it maintains a baseline luminosity trigger rate of 75 kHz, while during van der Meer (vdM) scans, this rate can significantly increase, potentially up to 1 MHz.
-The DAQ system of TEPX is designed to handle substantial data rates, with link bandwidth requirements varying from about 79.2 Gb/s at a trigger rate of 825 kHz during nominal physics operations to up to 24 Gb/s at the standard rate of 75 kHz  \cite{Collaboration:2706512}.
-
-TEPX Disk 4 Ring 1 (D4R1), located in the innermost ring of the last disk of the Inner Tracker Endcap Pixel Detector, is uniquely designed for measuring luminosity and beam-induced background (BIB).
+\section{TEPX Luminometer}
+
+TEPX is designed to function as a high-precision online bunch-by-bunch luminometer, primarily uses pixel cluster counting for luminosity measurement, a method involving the detection and counting of pixel clusters formed by charged particles from the proton collisions.
+Additionally, TEPX benefits from coincidence counting due to overlapping modules which enhances accuracy and enables systematic studies.
+%Positioned as part of the forward extension of the Inner Tracker detector,
+TEPX features a sophisticated dedicated trigger system for sampling all relevant bunch crossings in an unbiased manner.
+This system operates at a baseline trigger rate of 75 kHz, which is 10$\%$  of the 750 kHz allocated for physics data.
+%In terms of data acquisition,
+TEPX adapts to different operational conditions: during standard physics runs, it maintains a baseline luminosity trigger rate of 75 kHz, while during van der Meer (vdM) scans, this rate can significantly increase, potentially up to 1 MHz.
+TEPX readout rate (E-link speed) is estimated to be approximately 1330 Gbps at a pileup of 200  \cite{Collaboration:2706512}.
+%The DAQ system of TEPX is designed to handle substantial data rates, with link bandwidth requirements varying from about 79.2 Gb/s at a trigger rate of 825 kHz during nominal physics operations to up to 24 Gb/s at the standard rate of 75 kHz  \cite{Collaboration:2706512}.
+
+TEPX Disk 4 Ring 1 (D4R1) is located in the innermost ring of the last double-disk of the TEPX, is uniquely designed for measuring luminosity and beam-induced background (BIB).
 D4R1 is optimally placed due to its low radius, large active area, and high z position, making it highly sensitive and efficient for these measurements.
-D4R1's operational model is distinct from the rest of TEPX.
+The D4R1 operational model is distinct from the rest of TEPX.
 It employs the entire available trigger rate and readout bandwidth, which varies based on operational mode (binary readout or Time-over-Threshold information).
@@
 
-The Outer Tracker (OT) Layer 6 of the CMS will play a pivotal role in luminosity measurement, trigger, and data acquisition for the CMS experiment.
+%The Outer Tracker (OT) Layer 6 of the CMS will play a pivotal role in luminosity measurement, trigger, and data acquisition for the CMS experiment.
 It is designed to perform bunch-by-bunch measurements.
@@
 
-Data Acquisition (DAQ) system for the Phase II CMS Tracker must handle the increased data rates and complexity associated with the high-luminosity phase of the LHC (HL-LHC).
+%Data Acquisition (DAQ) system for the Phase II CMS Tracker must handle the increased data rates and complexity associated with the high-luminosity phase of the LHC (HL-LHC).
 The HL-LHC is expected to achieve a peak luminosity which is around 5-7 times higher than the current LHC design luminosity which the DAQ system must handle.
@@
      \hline
-     noPU & 100000  \\
+     %noPU & 100000  \\
      0.5 &  100600 \\
@@
 %Clusters refer to groups of hits in the pixel detector.
-The TEPX disk in this map consists of 5 rings which are concentric rings of pixel modules at different radial distances from the beamline.
-
-\begin{figure}[!htp]
-  \centering
-  \includegraphics[width=0.9\columnwidth]{ashish_thesis/tepx_clusters_1.png}
-  \caption[TEPX Cluster Map]{TEPX cluster map in the XY plane for pileup 200 simulated sample.
-Map showing coordinates of TEPX clusters in CMS global coordinate system.
+It consists of five concentric rings that are color-coded to indicate the density of clusters within the detector.
+It is transitioning from blue (low density) to red (high density), with the hottest regions indicating the overlap modules within the rings.
+The granularity of the data is high, with the number of bins set to 1000 for both axes and a bin size of 0.1 cm, allowing for a detailed visualization of the clusters across the disk.
+%The TEPX disk in this map consists of 5 rings which are concentric rings of pixel modules at different radial distances from the beamline.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_clusters_1.png}
+  \caption[TEPX Cluster Map]{TEPX cluster map in the XY plane for pileup 200 simulated sample. %Map showing coordinates of TEPX clusters in CMS global coordinate system.
     It shows clusters in one TEPX disk consisting of 5 rings.
-Hot regions are showing the module overlap for all rings (red, orange, green, yellow).
+Hot regions are showing the module overlap.
+%for all rings (red, orange, green, yellow).
 Number of x bins is 1000, x bins range from -40 to 40.
-x bin size is 0.1 cm.
-Number of y bins is 1000, y bins range from -40 to 40.
+    x bin size is 0.1 cm and %Number of y bins is 1000, y bins range from -40 to 40.
     y bin size is 0.1 cm.}
@@
 
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_D4R!_clusters._allpu_1.png}
+  \caption[D4R1 Clusters All Pileup]{Distribution of number of clusters for TEPX Disk 4 Ring 1 for all pileup samples.}
+  \label{fig:tepx_cl_allPU}
+\end{figure}
+
+\newpage
 \subsection{Linearity of TEPX clusters}
@@
 
-\begin{figure}[!htp]
-  \centering
-  \includegraphics[width=1\columnwidth]{ashish_thesis/tepx_D4R!_clusters._allpu_1.png}
-  \caption[D4R1 Clusters All Pileup]{Distribution of number of clusters for TEPX Disk 4 Ring 1 for all pileup values.}
-  \label{fig:tepx_cl_allPU}
-\end{figure}
+%\begin{figure}[!htp]
+ % \centering
+  %\includegraphics[width=0.6\columnwidth]{ashish_thesis/tepx_D4R!_clusters._allpu_1.png}
+  %\caption[D4R1 Clusters All Pileup]{Distribution of number of clusters for TEPX Disk 4 Ring 1 for all pileup values.}
+  %\label{fig:tepx_cl_allPU}
+%\end{figure}
 
@@
 
-\subsection{TEPX two fold coincidences}
-
-Two fold coincidences are clusters in modules overlap regions formed by modules in front and back layers of TEPX disk.
-There are two types of two fold coincidences namely in phi and r.
-Two fold coincidence in phi involve modules overlap in the same ring  of one double disk and two fold coincidence in r require modules overlap between successive rings of one double disk.
-wo fold coincidences are better way to distinguish between a real hit and random electrical noise.
+\subsection{TEPX two-fold coincidences}
+
+Two-fold coincidences are clusters in modules overlap regions formed by modules in front and back layers of TEPX disk.
+There are two types of two-fold coincidences namely in $\phi$ and r.
+Two-fold coincidence in $\phi$ involve modules overlap in the same ring  of one double disk and two-fold coincidence in r require modules overlap between successive rings of one double disk.
+Two-fold coincidences are better way to distinguish between a real hit and random electrical noise.
 They are more likely to be real hit than random electrical noise.
@@
 
-A new algorithm for luminosity measurement based on counting two fold coincidences is proposed that applies selections using dr and $d\phi$ variables (shown in Fig.
+A new algorithm for luminosity measurement based on counting two-fold coincidences is proposed that applies selections using dr and $d\phi$ variables (shown in Fig.
 \ref{fig:drdphi_diagram}) to minimize non-linearity for high pileup as these variables take into account track angle and its curvature \cite{sehrawat2020}.
@@
 
-We study the two fold coincidences in phi for all TEPX Disk and rings using dr, dphi variable for pileup 0.5 and apply nominal selection of 0.15 cm on dr and 0.04 on dphi variable in order to remove fake coincidences.
-
-The dr, dphi distribution showing true, fake, total two fold coincidences for Disk 4 Ring 1 for pileup 0.5 is shown in Fig.
+We study the two-fold coincidences in phi for all TEPX Disk and rings using dr, dphi variable for pileup 0.5 and apply pre-selection of 0.15 cm on dr and 0.04 on dphi variable in order to remove fake coincidences.
+
+The dr, dphi distribution showing true, fake, total two-fold coincidences for Disk 4 Ring 1 for pileup 0.5 is shown in Fig.
 \ref{fig:cluster_dr_dphi_dist}.
 After obtaining these distributions for all TEPX disks and rings, we carry out fit of the true coincidences distribution (shown in red color) to obtain mean and standard deviation of these distributions.
-Two standard deviation cut is applied on the dr variable.
+A two-standard-deviation selection is applied on the dr value about the mean.
 The mean values are shown in Table \ref{tab:mdr_cuts_offset_values}.
@@
 \ref{fig:cluster_ring_1003}, \ref{fig:cluster_ring_70}, \ref{fig:cluster_ring_71}.
-Similarly, two sigma cut is applied on the dphi variable as well.
+Similarly, two-sigma cut is applied on the dphi variable as well.
 The standard deviation values for dphi variable are shown in Table \ref{tab:mdphi_cuts_values}.
@@
 %The mean is taken as the offset value and standard deviation is used as the selection on dr, dphi variables as shown in Table \ref{tab:disk_values}, \ref{tab:mdphi_cuts_values} and \ref{tab:mdr_cuts_offset_values}.
-The mean of the fit is taken as the offset value and standard deviation is used as the cut on dr, dphi variables.
+%The mean of the fit is taken as the offset value and standard deviation is used as the cut on dr, dphi variables.
 
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/D4R1_S2_drdphi_cut_1.png}
-\caption[Pileup 0.5 Cluster Count in D4R1 (+Z) vs. dr & dphi]{%
-  Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 1 (+Z). Appropriate selection on dr, dphi are used to minimize fake two fold coincidences.
+\caption[Pileup 0.5 Cluster Count in D4R1 vs. dr & dphi]{%
+  Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for Disk 4 Ring 1.
+The black curve represents the total two-fold coincidence counts, the red curve depicts the true two-fold coincidence counts, and the green curve indicates the fake two-fold coincidence counts.
 }
@@
 \newpage
-A plot of two fold coincidences in phi after applying all selection based on standard deviation values of all TEPX disks and rings is shown in Fig. \ref{fig:cluster_ring_720}.
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/twofoldinphi_sch.png}
+A plot of two-fold coincidences in phi after applying all selection based on standard deviation values of all TEPX disks and rings is shown in Fig. \ref{fig:cluster_ring_720}.
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.6\textwidth]{ashish_thesis/twofoldinphi_sch.png}
 \caption[Map Of Two Fold Coincidences in phi]{%                                                                                                                                                       
@@
 
-Simlarly, we also studied two fold coincidences in r which arise from module overlaps between successive rings by only considering one to one module overlap between first two and last two layers in one TEPX double disk.
+Simlarly, we also studied two-fold coincidences in r which arise from module overlaps between successive rings by only considering one to one module overlap between first two and last two layers in one TEPX double disk.
 %Table \ref{table:two_fold_coincidences} categorizes various types of two-fold coincidences in r, observed in the TEPX detector.
@@
   Fit results for all disks and rings are shown from  Table \ref{tab:my_label_55} to \ref{tab:my_label_54}.
-Two standard deviation selections are applied on dr, dphi variables.
-After applying all selections obtained from the fits, we plotted the XY map of two fold coincidences in r for L1L2 and L3L4 combined as shown in \ref{fig:cluster_ring_79}.
+Similarly, two-sigma standard deviation selections are applied on dr, dphi variables.
+After applying all selections, the XY map of two-fold coincidences in r for L1L2 and L3L4 combined as shown in \ref{fig:cluster_ring_79}.
 
@@
 \caption[Examples of two fold coincidences in r]{%
-  Map of two fold coincidences in r showing all module overlap regions.
+  Definition of two-fold coincidences in r from the module overlap regions.
 }
@@
   \centering
-  \caption[dr mean values (L1L2)]{dr mean values obtained from fit for all disks and rings for coincidences in r}
+  \caption[dr mean values]{dr mean values (cm) obtained from fit for all disks and rings for coincidences in r}
 \begin{tabular}{ccccc}
  & \multicolumn{4}{c}{\textbf{Ring}} \\
-\textbf{Disk} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} \\
+\textbf{Disk} & \textbf{1-2} & \textbf{2-3} & \textbf{3-4} & \textbf{4-5} \\
 \hline
@@
   \centering
-  \caption[dr cut values (L1L2)]{dr standard deviation values obtained from fit for all disks and rings for coincidences in r}
+  \caption[dr cut values]{dr standard deviation (sigma) values obtained from fit for all disks and rings for coincidences in r}
 \begin{tabular}{ccccc}
  & \multicolumn{4}{c}{\textbf{Ring}} \\
-\textbf{Disk} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} \\
+\textbf{Disk} & \textbf{1-2} & \textbf{2-3} & \textbf{3-4} & \textbf{4-5} \\
 \hline
@@
   \centering
-  \caption[dphi cut values (L1L2)]{dphi standard deviation values obtained from fit for all disks and rings for coincidences in r}
+  \caption[dphi cut values]{dphi standard deviation values obtained from fit for all disks and rings for coincidences in r}
 \begin{tabular}{ccccc}
  & \multicolumn{4}{c}{\textbf{Ring}} \\
-\textbf{Disk} & \textbf{1} & \textbf{2} & \textbf{3} & \textbf{4} \\
+\textbf{Disk} & \textbf{1-2} & \textbf{2-3} & \textbf{3-4} & \textbf{4-5} \\
 \hline
@@
   \begin{tabular}{cc}
-    \textbf{Disk 4} & \textbf{Fake two fold coincidence rate (\%)} \\
+    \textbf{Disk 4} & \textbf{Fake two-fold coincidence rate (\%)} \\
     \hline
@@
 
+\begin{comment}
+
 \begin{table}[H]
   \centering
-  \caption{TEPX two fold coincidences fake rate and efficiency}
+  \caption{TEPX two-fold coincidences fake rate and efficiency}
   \begin{tabular}{ccccc}
-    \textbf{Pileup} & \textbf{Fake 2xinphi (\%)} & \textbf{Fake 2xinr (\%)} & \textbf{Efficiency 2xinphi (\%)} & \textbf{Efficiency 2xinr (\%)} \\
+    \textbf{Pileup} & \textbf{Fake rate 2-fold in phi (\%)} & \textbf{Fake rate 2-fold in r (\%)} & \textbf{Efficiency 2-fold in phi (\%)} & \textbf{Efficiency 2-fold in r (\%)} \\
     \hline
@@
 
+\end{comment}
+
+\begin{table}[H]
+  \centering
+  \caption{TEPX two-fold coincidences fake rate and efficiency}
+  \begin{tabular}{ccccc}
+    & \multicolumn{2}{c}{\textbf{Fake rate (\%)}} & \multicolumn{2}{c}{\textbf{Efficiency (\%)}} \\
+    %\cline{2-5}
+    \textbf{Pileup}  & \textbf{2-fold in phi} & \textbf{2-fold in r} & \textbf{2-fold in phi} & \textbf{2-fold in r} \\
+    \hline
+    0.5  & 0.78 & 0.99 & 99.21 & 99.00 \\
+    1    & 0.79 & 1.01 & 99.20 & 98.98 \\
+    1.5  & 0.80 & 1.02 & 99.19 & 98.97 \\
+    2    & 0.79 & 1.02 & 99.20 & 98.97 \\
+    10   & 0.83 & 1.04 & 99.16 & 98.95 \\
+    30   & 0.94 & 1.09 & 99.05 & 98.90 \\
+    50   & 1.04 & 1.14 & 98.95 & 98.85 \\
+    100  & 1.31 & 1.29 & 98.68 & 98.70 \\
+    140  & 1.53 & 1.41 & 98.46 & 98.58 \\
+    200  & 1.85 & 1.57 & 98.14 & 98.42 \\
+  \end{tabular}
+  \label{tab:combined_sample}
+\end{table}
+
 \begin{comment}
@@
 
-It is important to study how the number of two fold coincidences after final selections change with pileup for precise luminosity measurement.
-Number of two fold coincidences increases with pileup.
-Distribution of two fold coincidences for TEPX Disk 4 Ring 1 for all pileup values is shown in Fig.
+It is important to study how the number of two-fold coincidences after final selections change with pileup for precise luminosity measurement.
+Distribution of two-fold coincidences for TEPX Disk 4 Ring 1 for all pileup values is shown in Fig.
 \ref{fig:tepx_coin_allPU}.
-For pileup 200, mean two fold coincidences is around 270.
+For pileup 200, mean two-fold coincidences is around 270.
 Under vdM conditions, it range from 0 to 13.
@@
   \centering
-  \includegraphics[width=1\columnwidth]{ashish_thesis/tepx_D4R1_coin_allpu_1.png}
-  \caption[TEPX D4R1 Two Fold Coincidences All Pileup]{Distribution of number of two fold coincidences for TEPX Disk 4 Ring 1 for all pileup values.}
+  \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_D4R1_coin_allpu_1.png}
+  \caption[TEPX D4R1 Two-Fold Coincidences All Pileup]{Distribution of number of two-fold coincidences for TEPX Disk 4 Ring 1 for all pileup values.}
   \label{fig:tepx_coin_allPU}
@@
   \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_1.png}
-  \caption[TEPX two fold coincidences fit And residuals]{\onehalfspacing Left: Simulated mean number of two fold coincidences for TEPX disks as a function of pileup.
+  \caption[TEPX two-fold coincidences fit And residuals]{\onehalfspacing Left: Simulated mean number of two-fold coincidences for TEPX disks as a function of pileup.
 A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.
-Right: Deviation from linearity for two fold coincidences for TEPX disks.
-The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
+Right: The relative difference between the data points and the values of the fit function at the respective pileup value.}
   \label{fig:CMS_420}
@@
   \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_4.png}
-  \caption[TEPX two fold coincidences fit And residuals]{\onehalfspacing Left: Simulated mean number of two fold coincidences in phi for TEPX Disk 4 Ring 1 as a function of pileup.
+  \caption[TEPX two-fold coincidences fit And residuals]{\onehalfspacing Left: Simulated mean number of two-fold coincidences in phi for TEPX Disk 4 Ring 1 as a function of pileup.
 A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.
-Right: Deviation from linearity for two fold coincidences in phi for TEPX Disk 4 Ring 1.
-The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.}
+Right: The relative difference between the data points and the values of the fit function at the respective pileup value.}
   \label{fig:CMS_4207}
@@
 
-\subsection{TEPX three fold coincidences}
+\subsection{TEPX three-fold coincidences}
 
@@
 A three-fold coincidence refers to a situation where three hits occur nearly simultaneously and in a close spatial arrangement originating from the same underlying event.
-In the current algorithm, we look for another cluster in the lower ring after a two fold coincidence cluster is found.
-The XY map of three fold coincidences is shown in Fig.
+In the current algorithm, we look for another cluster in the lower ring after a two fold coincidence cluster in phi or r is found.
+The XY map of three-fold coincidences is shown in Fig.
 \ref{fig:tepx_3foldcoin_allPU_1}.
-Three fold coincidences under all pileup conditions is shown in Fig.
+Three-fold coincidences under all pileup conditions is shown in Fig.
 \ref{fig:tepx_3foldcoin_allPU_2}.
-With the current algorithm, three fold coincidences shows non-linearity at high pileup as shown in Fig.
+With the current algorithm, three-fold coincidences shows non-linearity at high pileup as shown in Fig.
 \ref{fig:tepx_3foldcoin_allPU_3}.
@@
 
-\begin{figure}[!htp]
-  \centering
-  \includegraphics[width=1\columnwidth]{ashish_thesis/tepx_threefold_coincidences.png}
-  \caption[Regions in XY plane showing three fold coincidences]{X vs Y map of three fold coincidences.}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.5\columnwidth]{ashish_thesis/tepx_threefold_coincidences.png}
+  \caption[Regions in XY plane showing three-fold coincidences]{X vs Y map of three fold coincidences.}
   \label{fig:tepx_3foldcoin_allPU_1}
@@
 
-\begin{figure}[!htp]
-  \centering
-  \includegraphics[width=1\columnwidth]{ashish_thesis/tepx_threefold_allpu.png}
+\newpage
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_threefold_allpu.png}
   \caption[TEPX Disk 4 Ring 2 Three Fold Coincidences]{Distribution of number of three fold coincidences for TEPX Disk 4 Ring 2 for all pileup values.}
@@
 
-\begin{figure}[!htp]
+\begin{figure}[H]
   \centering
   \includegraphics[width=1\columnwidth]{ashish_thesis/TEPX_threefold_linearity.png}
-  \caption[Disk 4 all rings three Fold Coincidences Linearity]{Left: Simulated mean number of three fold coincidences for all Disk 4 all rings as a function
-    of pileup. Right: Deviation from linearity for Disk 4 all rings.}
+  \caption[Disk 4 all rings Three-Fold Coincidences Linearity]{Left: Simulated mean number of three-fold coincidences for all Disk 4 all rings as a function
+    of pileup. Right: Deviation from linearity for Disk 4 all rings, the relative difference between the data points and the values of the fit function at the respective pileup value.}
   \label{fig:tepx_3foldcoin_allPU_3}
@@
 \section{Statistical precision for TEPX luminometer}
+
 Statistical precision is another uncertainty that need to be considered for precise luminosity measurement. It must be kept minimal to achieve 1 $\%$ accuracy for HL-LHC luminosity measurement.
@@
   \caption[Expected stat.
-precision of TEPX under low pileup] {Expected statistical precision (in $\%$) in head-on collisions during typical vdM conditions with pileup of 0.5 for TEPX clusters and two fold coincidences over different integration time period.}
+precision of TEPX under low pileup] {Expected statistical precision (in $\%$) in head-on collisions during typical vdM conditions with pileup of 0.5 for TEPX clusters and two-fold coincidences over different integration time period.}
 \begin{tabular}{lcccc}
-vdM (PU 0.5) & Readout Rate (kHz) & 1 bx, 1s & 1 bx, 30s & 100 bx, 30s\\
-\hline
-TEPXD4R1 Clusters&1000&1.82&0.332 & 0.0332\\
-TEPXD4R1 2x Coincidences in phi &1000&5.98&1.09 & 0.109\\
-TEPXD4R1 2x Coincidences in r &1000&11.1&2.02 & 0.202\\
-TEPXD4R1 2x Coincidences &1000&5.27&0.962 & 0.0962\\
-TEPX Clusters&500&0.709&0.129 & 0.0129\\
-TEPX 2x Coincidences in phi &500&2.65&0.485 & 0.0485\\
-TEPX 2x Coincidences in r &500&4.59&0.838 & 0.0838\\
-TEPX 2x Coincidences &500&2.3&0.42 & 0.042\\
+vdM (PU 0.5) & Trigger Rate (kHz) & 1 bx, 1s & 1 bx, 30s\\
+\hline
+TEPXD4R1 Clusters&1000&1.82&0.332\\
+TEPXD4R1 2x Coincidences in phi &1000&5.98&1.09\\
+TEPXD4R1 2x Coincidences in r &1000&11.1&2.02\\
+TEPXD4R1 2x Coincidences &1000&5.27&0.962\\
+TEPX Clusters&500&0.709&0.129\\
+TEPX 2x Coincidences in phi &500&2.65&0.485\\
+TEPX 2x Coincidences in r &500&4.59&0.838\\
+TEPX 2x Coincidences &500&2.3&0.42\\
 \end{tabular}
@@
 \caption[Expected stat.
-precision of TEPX under high pileup]{Expected statistical precision (in $\%$) in head-on collisions during physics conditions with pileup of 200 for TEPX clusters and two fold coincidences over different integration time period.}
+precision of TEPX under high pileup]{Expected statistical precision (in $\%$) in head-on collisions during physics conditions with pileup of 200 for TEPX clusters and two-fold coincidences over different integration time period.}
 \begin{small} % this command will decrease the font size
 \begin{tabular}{lcccc}
-Algorithm & Readout Rate (kHz) & 1 bx, 1s & 2500 bx, 1s & 2500 bx, 1 LS \\
-\hline
-TEPXD4R1 Clusters & 825 & 0.1 & 0.002 & 0.000414 \\
-TEPXD4R1 2x Coincidences in phi & 825 & 0.329 & 0.00659 & 0.00136 \\
-TEPXD4R1 2x Coincidences in r & 825 & 0.61 & 0.0122 & 0.00252 \\
-TEPXD4R1 2x Coincidences & 825 & 0.29 & 0.0058 & 0.0012 \\
-TEPX Clusters & 75 & 0.0915 & 0.00183 & 0.000379 \\
-TEPX 2x Coincidences in phi & 75 & 0.343 & 0.00685 & 0.00142 \\
-TEPX 2x Coincidences in r & 75 & 0.593 & 0.0119 & 0.00245 \\
-TEPX 2x Coincidences & 75 & 0.297 & 0.00594 & 0.00123 \\
+Algorithm & Trigger Rate (kHz) & 1 bx, 1s & 2500 bx, 1s\\
+\hline
+TEPXD4R1 Clusters & 825 & 0.1 & 0.002  \\
+TEPXD4R1 2x Coincidences in phi & 825 & 0.329 & 0.00659 \\
+TEPXD4R1 2x Coincidences in r & 825 & 0.61 & 0.0122  \\
+TEPXD4R1 2x Coincidences & 825 & 0.29 & 0.0058  \\
+TEPX Clusters & 75 & 0.0915 & 0.00183  \\
+TEPX 2x Coincidences in phi & 75 & 0.343 & 0.00685 \\
+TEPX 2x Coincidences in r & 75 & 0.593 & 0.0119  \\
+TEPX 2x Coincidences & 75 & 0.297 & 0.00594  \\
 \end{tabular}

### 2023-12-29 tesis_Ashish/Chapter7/chapter7.tex
Updated thesis 29 Dec 2023

@@
 
-Statistical precision is another uncertainty that need to be considered for precise luminosity measurement. It must be kept minimal to achieve 1 $\%$ accuracy for HL-LHC luminosity measurement.
-
-Relative statistical uncertainty in $\%$ = $\frac{\sqrt{N}}{N} \times 100$ \\
-
-where N = (Number of counts per event)$\times$(Trigger Frequency)$\times$(Time Integration period).
+Statistical precision is another uncertainty that need to be considered for precise luminosity measurement.
+It must be kept minimal to achieve 1 $\%$ accuracy for HL-LHC luminosity measurement.
+Relative statistical uncertainty in $\%$ = $\frac{\sqrt{N}}{N} \times 100$ where N is the product of the number of counts per event, the trigger frequency and the time integration period.\\
 
@@
 
-\section{Conclusion}
+\section{Summmary}
 
@@
 The comprehensive approach and innovative methodologies developed in this thesis are pivotal contributions to the field, enhancing not only current research capabilities but also setting a solid foundation for future explorations in high-energy particle physics.
+
+Chapter 1 of the thesis lays the groundwork for understanding collider experiments, focusing on the critical role of luminosity in particle physics, particularly in the Large Hadron Collider (LHC).
+Collider experiments, crucial for probing the fundamental nature of matter, involve high-energy collisions, such as those between protons or electrons.
+Luminosity, indicating the collision rate, is essential for determining particle production rates and detecting rare events.
+Accurate luminosity measurement is imperative as it directly influences the rate of particle production, crucial for significant discoveries like the Higgs boson and precise measurements of particles like the top quark.
+The chapter highlights ongoing advancements in enhancing luminosity measurement precision, notably through the CMS's pixel detector, which is key to improving particle property measurements and discovering new physics beyond the Standard Model.
+
+In Chapter 2, we delves into the comprehensive strategies and methodologies adopted in the CMS experiment for luminosity measurement.
+We elaborates on the Pixel Cluster Counting (PCC) method's precision and how it is optimized for high luminosity scenarios anticipated in future LHC runs.
+The chapter also discusses the advancements in the PCC technique, including the development of algorithms and the calibration processes that will be imperative for maintaining measurement accuracy in the High-Luminosity LHC (HL-LHC) phase.
+The innovations in the detector technology, data processing, and analysis underscore the ongoing evolution of the CMS experiment's capabilities to achieve precise and reliable luminosity measurements.
+
+In Chapter 3, we discuss the calibration of luminosity measurement devices using the van der Meer (vdM) scan method.
+It explains the technique developed by Simon van der Meer for relating the detection rate of a luminometer to absolute luminosity.
+This involves scanning colliding beams across each other and measuring the beam overlap integral, which is proportional to luminosity.
+The chapter also covers background estimation to account for various sources of noise and the Poly2G model, a fitting function used in the vdM calibration process.
+
+In Chapter 4, the results from the CMS experiment at the Large Hadron Collider's Run 2 are comprehensively detailed.
+For the year 2018, the integrated luminosity was calculated to be \(60.47 \, \text{fb}^{-1}\).
+The visible cross section was accurately determined as \(960.54 \pm 0.85 \, (\text{stat.}) \, \text{mb}\).
+A total of 155 good pixel modules were selected for the final luminosity measurement.
+Systematic uncertainties were meticulously quantified, including afterglow (\(0.3\%\)), linearity (\(0.4\%\)), and cross detector stability (\(0.3\%\)), contributing to a total uncertainty of \(1.08\%\).
+
+In Chapter 5, significant results from the PCC luminosity measurement during its third run are outlined.
+The chapter reports that the PCC integrated luminosity for 2022 was computed to be \(38.61 \, \text{fb}^{-1}\) .
+Furthermore, a comprehensive analysis of systematic uncertainties in the luminosity measurement for the year 2022 is presented.
+These uncertainties encompass a range of factors including calibration (1.3\%), integration (0.8\%), and other specific sources such as beam current (0.2\%), orbit drift (0.3\%), and cross-detector linearity (0.54\%), culminating in a total uncertainty of \(1.5\%\).
+
+Chapter 6 of the thesis on the TEPX luminometer for the High Luminosity Large Hadron Collider (HL-LHC) addresses the challenges and solutions in luminosity measurement for the anticipated HL-LHC phase starting in 2029.
+With the HL-LHC set to increase instantaneous luminosity to up to 200 proton-proton collisions per bunch crossing, the TEPX luminometer is designed for high-precision, real-time measurement using pixel cluster counting and coincidence counting.
+This setup enhances accuracy and handles the expected increase in radiation levels, data rates, and event complexity.
+The TEPX system is noted for its linearity, indicating its effectiveness as a luminometer as the PCC visible cross section remains constant across various luminosity levels.
+Advanced algorithms using dr and $d\phi$ variables effectively manage non-linearity and suppress fake coincidences at high pileup levels, maintaining non-linearity within 1\% across the pileup range.
+Furthermore, the system achieves high efficiency and low fake rates in complex luminosity conditions.
+Statistical precision is also emphasized as a critical factor for achieving the targeted 0.1\% accuracy in HL-LHC luminosity measurements.

### 2023-12-29 tesis_Ashish/Chapter7/chapter7.tex
Updated thesis 29 Dec 2023

@@
 
-\section{Summmary}
+\section{Summary}
 
@@
 
-In Chapter 2, we delves into the comprehensive strategies and methodologies adopted in the CMS experiment for luminosity measurement.
-We elaborates on the Pixel Cluster Counting (PCC) method's precision and how it is optimized for high luminosity scenarios anticipated in future LHC runs.
-The chapter also discusses the advancements in the PCC technique, including the development of algorithms and the calibration processes that will be imperative for maintaining measurement accuracy in the High-Luminosity LHC (HL-LHC) phase.
-The innovations in the detector technology, data processing, and analysis underscore the ongoing evolution of the CMS experiment's capabilities to achieve precise and reliable luminosity measurements.
+In Chapter 2, we provide a comprehensive overview of the methods and technologies used to measure luminosity at the CMS detector.
+It focuses on various luminosity measurement methods, the role of the pixel detector, and the pixel cluster counting (PCC) method.
+It details the importance of precise luminosity measurement for understanding particle interactions, the challenges involved, and the advancements made in this field, particularly with the PCC method's implementation and its impact on enhancing the accuracy of luminosity measurements.
 
@@
 Furthermore, the system achieves high efficiency and low fake rates in complex luminosity conditions.
-Statistical precision is also emphasized as a critical factor for achieving the targeted 0.1\% accuracy in HL-LHC luminosity measurements.
+Statistical precision is also emphasized as a critical factor for achieving the targeted 0.1\% accuracy in HL-LHC luminosity measurement.

### 2023-12-29 tesis_Ashish/Chapter7/chapter7.tex
Updated thesis 29 Dec 2023

@@
 The Level-1 Trigger system in the PhaseII Upgrade is designed to accept events at a rate of up to 750 kHz.
-The DAQ system must handle the transmission of trigger primitives to the Level-1 Trigger system and buffer the full event data until the t\
-rigger decision is made.
+The DAQ system must handle the transmission of trigger primitives to the Level-1 Trigger system and buffer the full event data until the trigger decision is made.
 The high-speed optical links used for data transmission between the Front-End Electronics (FEE) and off-detector electronics are expected to operate at data rates of 10-25 Gbps or higher to handle the large data volumes generated by the upgraded tracker.

### 2023-12-29 tesis_Ashish/Chapter7/chapter7.tex
Updated thesis 29 Dec 2023

@@
 The Inner Tracker consists of three main sub-components: the Tracker Endcap Pixel detector (TEPX), the Tracker Forward Pixel detector (TFPX), and the Tracker Barrel Pixel (TBPX) detector as shown in Fig.
-\ref{fig:Innertracker}.
+\ref{fig:Innertracker} \cite{CERN-LHCC-2017-009}.
 %The Outer Tracker is responsible for detecting charged particles in the outer region of the CMS detector.
@@
 D4R1 is optimally placed due to its low radius, large active area, and high z position, making it highly sensitive and efficient for these measurements.
-The D4R1 operational model is distinct from the rest of TEPX.
+The D4R1 operational model is distinct from the rest of TEPX \cite{Haranko2023}.
 It employs the entire available trigger rate and readout bandwidth, which varies based on operational mode (binary readout or Time-over-Threshold information).
@@
 Fig.
-\ref{fig:tepx_cl} shows the location of TEPX clusters in Disk 4 in the XY plane (Z is the direction of the beam) from a simulated sample with a pileup of 200.
+\ref{fig:tepx_cl} shows the location of TEPX clusters in Disk 4 in the XY plane (Z is the direction of the beam) from a simulated sample with a pileup of 200 \cite{dabrowski2020}.
 %Clusters refer to groups of hits in the pixel detector.
@@
 
-Simlarly, we also studied two-fold coincidences in r which arise from module overlaps between successive rings by only considering one to one module overlap between first two and last two layers in one TEPX double disk.
+Simlarly, we also studied two-fold coincidences in r which arise from module overlaps between successive rings by only considering one to one module overlap between first two and last two layers in one TEPX double disk \cite{BRIL2021}.
 %Table \ref{table:two_fold_coincidences} categorizes various types of two-fold coincidences in r, observed in the TEPX detector.
@@
   \caption[Expected stat.
-precision of TEPX under low pileup] {Expected statistical precision (in $\%$) in head-on collisions during typical vdM conditions with pileup of 0.5 for TEPX clusters and two-fold coincidences over different integration time period.}
+precision of TEPX under low pileup] {Expected statistical precision (in $\%$) in head-on collisions during typical vdM conditions with pileup of 0.5 for TEPX clusters and two-fold coincidences over different integration time period \cite{Collaboration:2759074}.}
 \begin{tabular}{lcccc}
@@
 \caption[Expected stat.
-precision of TEPX under high pileup]{Expected statistical precision (in $\%$) in head-on collisions during physics conditions with pileup of 200 for TEPX clusters and two-fold coincidences over different integration time period.}
+precision of TEPX under high pileup]{Expected statistical precision (in $\%$) in head-on collisions during physics conditions with pileup of 200 for TEPX clusters and two-fold coincidences over different integration time period \cite{Collaboration:2759074}.}
 \begin{small} % this command will decrease the font size

### 2023-12-30 tesis_Ashish/Chapter7/chapter7.tex
Updated thesis 30 Dec 2023

@@
 That is why it will be replaced by a new pixel detector.
-The Phase II upgrade of the CMS tracker comprises of two main components: the Inner Tracker (IT) and the Outer Tracker (OT) \cite{collaboration:2759074}.
+The Phase II upgrade of the CMS tracker comprises of two main components: the Inner Tracker (IT) and the Outer Tracker (OT) \cite{RoyChowdhury:2729279}.
 The Inner Tracker consists of three main sub-components: the Tracker Endcap Pixel detector (TEPX), the Tracker Forward Pixel detector (TFPX), and the Tracker Barrel Pixel (TBPX) detector as shown in Fig.
@@
   \caption[Expected stat.
-precision of TEPX under low pileup] {Expected statistical precision (in $\%$) in head-on collisions during typical vdM conditions with pileup of 0.5 for TEPX clusters and two-fold coincidences over different integration time period \cite{Collaboration:2759074}.}
+precision of TEPX under low pileup] {Expected statistical precision (in $\%$) in head-on collisions during typical vdM conditions with pileup of 0.5 for TEPX clusters and two-fold coincidences over different integration time period \cite{Collaboration:275907420}.}
 \begin{tabular}{lcccc}
@@
 \caption[Expected stat.
-precision of TEPX under high pileup]{Expected statistical precision (in $\%$) in head-on collisions during physics conditions with pileup of 200 for TEPX clusters and two-fold coincidences over different integration time period \cite{Collaboration:2759074}.}
+precision of TEPX under high pileup]{Expected statistical precision (in $\%$) in head-on collisions during physics conditions with pileup of 200 for TEPX clusters and two-fold coincidences over different integration time period \cite{Collaboration:275907420}.}
 \begin{small} % this command will decrease the font size

### 2024-01-01 tesis_Ashish/Chapter7/chapter7.tex
Updated thesis 1 Jan 2024

@@
 
-The Phase II upgrade of the CMS Tracker is a crucial project undertaken to maintain the effectiveness of the CMS experiment during the High Luminosity LHC (HL-LHC) phase, which is expected to start in 2029.
+The Phase II upgrade of the CMS Tracker is a crucial project undertaken to maintain the effectiveness of the CMS experiment during the High Luminosity LHC (HL-LHC) phase, which is expected to start in 2029 \cite{CERN2022}.
 The HL-LHC will significantly increase the instantaneous luminosity, leading to a higher number of proton-proton collisions per bunch crossing.
@@
 
-Data Acquisition (DAQ) system for the Phase II CMS Tracker must handle the increased data rates and complexity associated with the high-luminosity phase of the LHC (HL-LHC).
+Data Acquisition (DAQ) system for the Phase II CMS Tracker must handle the increased data rates and complexity associated with the HL-LHC.
 The HL-LHC is expected to achieve a peak luminosity which is around 5-7 times higher than the current LHC design luminosity which the DAQ system must handle.
@@
 The data rates from the tracker modules are expected to be several terabits per second (Tbps) during the HL-LHC operation.
-The Level-1 Trigger system in the PhaseII Upgrade is designed to accept events at a rate of up to 750 kHz.
+The Level-1 Trigger system in the Phase II Upgrade is designed to accept events at a rate of up to 750 kHz.
 The DAQ system must handle the transmission of trigger primitives to the Level-1 Trigger system and buffer the full event data until the trigger decision is made.
@@
 
-The TBPX occupies the central region along the \( z \)-axis from 0 to just below 300~mm, employing 360 units of \( 1 \times 2 \) modules (modules with two readout chips) and 504 units of \( 2 \times 2 \) modules (modules with four readout chips).
-The TFPX extends from approximately 300~mm to 600~mm in the \( z \)-direction, with 832 units of \( 1 \times 2 \) and 896 units of \( 2 \times 2 \) modules.
-The TEPX covers a broader range from about 600~mm to over 2500~mm and includes 768 units of \( 1 \times 2 \) and 992 units of \( 2 \times 2 \) modules.
-
-The TEPX consists of four double disks per side with each double disk consisting of five rings of modules as shown in Fig.
+The TBPX occupies the central region along the \( z \)-axis from 0 to just below 300~mm, employing 360 units of \( 1 \times 2 \) modules (modules with two readout chips) and 504 units of \( 2 \times 2 \) modules (modules with four readout chips) arranged in four layers parallel to the beam.
+The TFPX extends from approximately 250~mm to 1400~mm in the \( z \)-direction, with 832 units of \( 1 \times 2 \) and 896 units of \( 2 \times 2 \) modules.
+The TEPX covers a range from about 1700~mm to over 2600~mm and includes 768 units of \( 1 \times 2 \) and 992 units of \( 2 \times 2 \) modules.
+Collectively, these sub-detectors boast around 1.947 billion pixels across 13,488 pixel chips, spanning a silicon area of 4.87 square meters.
+
+The TEPX consists of four double-disk per side with each double-disk consisting of five rings of modules as shown in Fig.
 \ref{fig:Innertracker_40}.
-The rings have 20, 28, 36, 44 and 48 modules respectively.
+%The rings have 20, 28, 36, 44 and 48 modules respectively.
 The first two inner rings are equipped with \(1 \times 2\) modules, while the more extensive \(2 \times 2\) modules are mounted on the three outer rings.
-This design is further enhanced by the unique arrangement of modules in four layers as shown in Fig.
+This design is further enhanced by the arrangement of modules in four layers as shown in Fig.
 \ref{fig:Innertracker_41}.
 This allows for modules to be mounted on both the front and back sides of a disk, creating an overlap in the r-\(\phi\) direction.
-Additionally, by mounting modules at varying radii on the two disk that form each double-disk, overlap in the radial direction (r) is also accomplished.
+By mounting modules at varying radii on the two disk that form each double-disk, overlap in the radial direction (r) is also accomplished.
+TEPX will have better radiation tolerance, increased granularity, improved two-track separation, improved estimation of hit rate and statistical precision, extending tracking acceptance beyond $|\eta|=4$.
 
@@
 
-TEPX will have better radiation tolerance, increased granularity, improved two-track separation, improved estimation of hit rate and statistical precision, extending tracking acceptance beyond $|\eta|=4$.
+%TEPX will have better radiation tolerance, increased granularity, improved two-track separation, improved estimation of hit rate and statistical precision, extending tracking acceptance beyond $|\eta|=4$.
 Collectively, these sub-detectors boast around 1.947 billion pixels across 13,488 pixel chips, spanning a silicon area of 4.87 square meters.
@@
   \centering
-  \includegraphics[width=1 \columnwidth]{ashish_thesis/tepx_tt_1.png}
-  \caption[Phase II CMS Inner Tracker]{ \onehalfspacing A layout of the CMS Phase II Inner Tracker showing four TEPX disks, eight TFPX disks and four TBPX layers.}
+  \includegraphics[width=1 \columnwidth]{ashish_thesis/it_newgeometry_.png}
+  \caption[Phase II CMS Inner Tracker]{ \onehalfspacing A layout of the CMS Phase II Inner Tracker showing four TEPX disks, eight TFPX disks and four TBPX layers \cite{Collaboration:275907420}.}
   \label{fig:Innertracker}
@@
   \includegraphics[width=0.5 \columnwidth]{ashish_thesis/tepx_DD.png}
-  \caption[TEPX double disk]{ \onehalfspacing View of one TEPX disk in the $r-\phi$ plane; individual pixel modules on two planes (double-disk) and five rings are outlined by yellow rectangles.
+  \caption[TEPX double disk]{ \onehalfspacing View of one TEPX double-disk in the $r-\phi$ plane; individual pixel modules on two planes (double-disk) and five rings are outlined by yellow rectangles.
+%The planes are separated in z by about 1 cm.
+The first plane holds modules on both front and back faces, with alternating rings to cover the gaps in r; the second plane holds modules in the same way as the first plane, but with an offset in $\phi$ to cover the gaps in $\phi$.
+  }
+  \label{fig:Innertracker_40}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.1 \columnwidth]{ashish_thesis/edited_tepx_alllayer_v5.png}
+  \caption[TEPX double disk]{ \onehalfspacing R-Z view of the TEPX double-disk showing the four layers of modules L1, L2, L3 and L4.
+Layer 1 and 3 has Ring 1, 3 and 5 modules, Layer 2 and 4 has Ring 2 and Ring 4 modules.
 The planes are separated in z by about 1 cm.
 The first plane holds modules on both front and back faces, with alternating rings to cover the gaps in r; the second plane holds modules in the same way as the first plane, but with an offset in $\phi$ to cover the gaps in $\phi$.}
-  \label{fig:Innertracker_40}
-\end{figure}
-
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.1 \columnwidth]{ashish_thesis/tepx_alllayer.png}
-  \caption[TEPX double disk]{ \onehalfspacing R-Z view of the TEPX one double disk showing all four layers L1, L2, L3 and L4.
-Layer 1 and 3 has Ring 1, 3 and 5 modules, Layer 2 and 4 has Ring 2 and Ring 4 modules.}
   \label{fig:Innertracker_41}
@@
 %In terms of data acquisition,
-TEPX adapts to different operational conditions: during standard physics runs, it maintains a baseline luminosity trigger rate of 75 kHz, while during van der Meer (vdM) scans, this rate can significantly increase, potentially up to 1 MHz.
-TEPX readout rate (E-link speed) is estimated to be approximately 1330 Gbps at a pileup of 200  \cite{Collaboration:2706512}.
+TEPX adapts to different operational conditions: during standard physics runs, it maintains a baseline luminosity trigger rate of 75 kHz, while during van der Meer (vdM) scans, this rate can significantly increase, potentially up to 1 MHz \cite{Collaboration:2706512}.
+%TEPX readout rate (E-link speed) is estimated to be approximately 1330 Gbps at a pileup of 200  \cite{Collaboration:2706512}.
 %The DAQ system of TEPX is designed to handle substantial data rates, with link bandwidth requirements varying from about 79.2 Gb/s at a trigger rate of 825 kHz during nominal physics operations to up to 24 Gb/s at the standard rate of 75 kHz  \cite{Collaboration:2706512}.
 
-TEPX Disk 4 Ring 1 (D4R1) is located in the innermost ring of the last double-disk of the TEPX, is uniquely designed for measuring luminosity and beam-induced background (BIB).
-D4R1 is optimally placed due to its low radius, large active area, and high z position, making it highly sensitive and efficient for these measurements.
+TEPX Disk 4 Ring 1 (D4R1) is located in the innermost ring of the last double-disk of the TEPX, is exclusively designed for measuring luminosity and beam-induced background (BIB).
+D4R1 is optimally placed due to its low radius, large active area, and high z position, making it highly efficient for these measurements.
 The D4R1 operational model is distinct from the rest of TEPX \cite{Haranko2023}.
-It employs the entire available trigger rate and readout bandwidth, which varies based on operational mode (binary readout or Time-over-Threshold information).
+It employs the entire available trigger rate and readout bandwidth, which varies based on operational mode.
 This capability ranges from a trigger rate of 825 kHz (similar to the rest of TEPX) up to several MHz, limited by readout bandwidth and the available e-link capacity.
@@
  Simulated data samples for Phase II include full CMS detector description and uses official CMS software (version $\texttt{CMSSW\_10\_6\_0\_patch2}$) which calls GEANT4 for detector simulation \cite{GEANT4:2002zbu}.
-Pixel cluster reconstruction is done by converting raw data to digi format (row, column, charge) and then form clusters from digis.
-The samples used in simulation contain single-neutrino event overlaid with a variable number of minimum-bias events (events with any amount of real energy detected in CMS) to simulate different pileup values.
+Pixel clusters are reconstructed using the standard CMS reconstruction algorithms \cite{cmssw_2024}.
+It is done by converting raw data to digi format (row, column, charge) and then form clusters from digis.
+The samples used in simulation use single-neutrino generated events overlaid with a variable number of minimum-bias events (events with any amount of real energy detected in CMS) to simulate different pileup values.
 The number of simulated events used in this analysis for each pileup value is shown in Table \ref{tab:12}.
@@
 It is transitioning from blue (low density) to red (high density), with the hottest regions indicating the overlap modules within the rings.
-The granularity of the data is high, with the number of bins set to 1000 for both axes and a bin size of 0.1 cm, allowing for a detailed visualization of the clusters across the disk.
+The granularity of the histogram is set to 1000 for both axes and a bin size of 0.1 cm, allowing for a detailed visualization of the clusters across the disk.
 %The TEPX disk in this map consists of 5 rings which are concentric rings of pixel modules at different radial distances from the beamline.
@@
   \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_clusters_1.png}
-  \caption[TEPX Cluster Map]{TEPX cluster map in the XY plane for pileup 200 simulated sample. %Map showing coordinates of TEPX clusters in CMS global coordinate system.
+  \caption[TEPX Cluster Map]{TEPX cluster map in the XY plane for pileup 200 simulated sample having 5000 events. %Map showing coordinates of TEPX clusters in CMS global coordinate system.
     It shows clusters in one TEPX disk consisting of 5 rings.
@@
 
-\newpage
 \subsection{Linearity of TEPX clusters}
@@
 Linearity is one of the systematic uncertainty in the calculation of instantaneous luminosity and PCC visible cross section $\sigma_{vis}$.
-A linear relation between the number of clusters and pileup (PU) imply that \\
-
-$<N_{cl/pp}> = \frac{<N_{cl}>}{\mu} = \frac{\sigma_{vis}}{\sigma_{pp}}$ \\
-
-$<N_{cl}> =  \frac{\sigma_{vis}}{\sigma_{pp}} \mu $ \\
-
+A linear relation between the mean number of clusters and pileup (PU) imply that $<N_{cl/pp}> = \frac{<N_{cl}>}{\mu} = \frac{\sigma_{vis}}{\sigma_{pp}}$ , $<N_{cl}> =  \frac{\sigma_{vis}}{\sigma_{pp}} \mu $.
 Linearity indicates that the PCC visible cross section $\sigma_{vis}$ does not depend on the per bunch instantaneous luminosity (ideal luminometer).
 In ideal scenario, $\sigma_{vis}$ is not dependent on pileup, but this a potential problem with the luminometer.
+A non-linear relation $<N_{cluster}> = \alpha (PU)^{\gamma}, \gamma \neq 1$ would add non-linear terms in the rate equation $R = \sigma_{vis} L_{inst}$ and cause $\sigma_{vis}$ to vary with the per bunch instantaneous luminosity and pileup values.
 TEPX luminometer proposed for Phase II shows excellent linearity over entire pileup range.
-A non-linear relation $<N_{cluster}> = \alpha (PU)^{\gamma}, \gamma \neq 1$ would add non-linear terms in the rate equation $R = \sigma_{vis} L_{inst}$  and cause $\sigma_{vis}$ to vary with the per bunch instantaneous luminosity and pileup values.
 
@@
 \ref{fig:tepx_cl_allPU}.
-The peak of the distribution drops as pileup increases because we have processed different number of events for different pileup values.
-Under low pileup conditions which is crucial for vdM calibration, number of clusters varies from 0 to 35.
-For average pileup value of 0.5 (vdM conditions), number of clusters varies between 0 and 12.
+%The peak of the distribution drops as pileup increases because we have processed different number of events for different pileup values.
+Under low pileup conditions which is crucial for vdM calibration, number of clusters varies from 0 to 35.For average pileup value of 0.5 (vdM conditions), number of clusters varies between 0 and 12.
+The distributions follow Poisson statistics.
 Linearity results for simulated TEPX clusters from low to high pileup values are shown in  Fig.
@@
 A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.
-Right: Deviation from linearity for clusters for  TEPX disks.
-The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.
-}
+Right: %Deviation from linearity for clusters for  TEPX disks.
+The non-linearity is calculated as
+    The relative difference between the data points and the values of the fit function at the respective pileup value. }
   \label{fig:CMS_4205}
@@
 A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.
-Right: Deviation from linearity for clusters for TEPX Disk 4 Ring 1.
-The non-linearity is calculated as the relative difference between the data points and the values of the fit function at the respective pileup value.
-}
+Right: %Deviation from linearity for clusters for TEPX Disk 4 Ring 1.
+The non-linearity is calculated as
+    The relative difference between the data points and the values of the fit function at the respective pileup value. }
   \label{fig:CMS_4206}
@@
 
-Two-fold coincidences are clusters in modules overlap regions formed by modules in front and back layers of TEPX disk.
+Two-fold coincidences are clusters in modules overlap regions formed by modules in front layers (L1-L3) and back layers (L2-L4) separately.
 There are two types of two-fold coincidences namely in $\phi$ and r.
-Two-fold coincidence in $\phi$ involve modules overlap in the same ring  of one double disk and two-fold coincidence in r require modules overlap between successive rings of one double disk.
-Two-fold coincidences are better way to distinguish between a real hit and random electrical noise.
-They are more likely to be real hit than random electrical noise.
-Luminosity determination based on counting coincidences has an advantage over clusters that afterglow effects are tiny in the case of coincidences.
+Two-fold coincidence in $\phi$ involve modules overlap in the same ring of one double-disk and two-fold coincidence in r require modules overlap between successive rings of one double-disk.
+Two-fold coincidences are better way to distinguish between a real hit and random noise.
+%They are more likely to be real hit than random electrical noise.
+Luminosity determination based on counting coincidences has an advantage over clusters that afterglow effects are tiny. %in the case of coincidences. 
 %as shown in Fig. \ref{fig:cluster_ring_4000}. 
@@
 \ref{fig:drdphi_diagram}) to minimize non-linearity for high pileup as these variables take into account track angle and its curvature \cite{sehrawat2020}.
-Proper selections are applied for each TEPX disk based on these variables using low pileup simulated samples and then these selections are extrapolated to high pileup samples for suppressing fake coincidences.
+Proper selections are applied for each TEPX disk based on these variables using low pileup simulated samples and then these selections are applied to high pileup samples for suppressing fake coincidences.
 
@@
 \caption[New Variables For Two Fold Coincidences]{%
-  New r, phi variables used to define coincidence clusters. These variables take into account track angle and curvature.
+  r, phi variables used to define coincidence clusters. %These variables take into account track angle and curvature.
 }
@@
 
-We study the two-fold coincidences in phi for all TEPX Disk and rings using dr, dphi variable for pileup 0.5 and apply pre-selection of 0.15 cm on dr and 0.04 on dphi variable in order to remove fake coincidences.
+We study the two-fold coincidences in $\phi$ for all TEPX Disk and rings using r, phi variable for pileup 0.5.
+Based on pileup 0.5 sample, a pre-selection of 0.15 cm on dr and 0.04 on dphi variable is applied in order to remove fake coincidences.
 
@@
 %The mean of the fit is taken as the offset value and standard deviation is used as the cut on dr, dphi variables.
+A plot of two-fold coincidences in phi after applying all selection based on standard deviation values of all TEPX disks and rings is shown in Fig. \ref{fig:cluster_ring_720}.
 
@@
 
-\begin{table}[h]
+\begin{table}[H]
   \centering
@@
 
+%A plot of two-fold coincidences in phi after applying all selection based on standard deviation values of all TEPX disks and rings is shown in Fig. \ref{fig:cluster_ring_720}.
+
 \newpage
-A plot of two-fold coincidences in phi after applying all selection based on standard deviation values of all TEPX disks and rings is shown in Fig. \ref{fig:cluster_ring_720}.
-
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.6\textwidth]{ashish_thesis/twofoldinphi_sch.png}
-\caption[Map Of Two Fold Coincidences in phi]{%                                                                                                                                                       
-  Map of two fold coincidences in phi showing all module overlap regions.
-}
-\label{fig:cluster_ring_720}
-\end{figure}
-
-Simlarly, we also studied two-fold coincidences in r which arise from module overlaps between successive rings by only considering one to one module overlap between first two and last two layers in one TEPX double disk \cite{BRIL2021}.
+%\begin{figure}[H]
+%\centering
+%\includegraphics[width=0.6\textwidth]{ashish_thesis/twofoldinphi_sch.png}
+%\caption[Map Of Two Fold Coincidences in phi]{%                                                                                                                                                       
+ % Map of two fold coincidences in phi showing all module overlap regions.
+%}
+%\label{fig:cluster_ring_720}
+%\end{figure}
+
+Simlarly, we also studied two-fold coincidences in r which arise from module overlaps between successive rings by only considering one-to-one module overlap between first two and last two layers in one TEPX double-disk \cite{BRIL2021}.
 %Table \ref{table:two_fold_coincidences} categorizes various types of two-fold coincidences in r, observed in the TEPX detector.
@@
 \ref{fig:cluster_ring_770}.
- A one-to-one overlapping of modules is considered between L1L2 and L3L4 module overlap as shown in Fig. \ref{fig:cluster_ring_72034}. %as shown in Fig. \ref{tab:my_label2}. 
+ A one-to-one overlapping of modules is considered between L1L2 and L3L4 modules as shown in Fig. \ref{fig:cluster_ring_72034}. %as shown in Fig. \ref{tab:my_label2}. 
  %The distributions for dr, dphi distribution depicting fake, true, total two fold coincidence in r for pileup 0.5 and 200 are shown in Fig.
@@
 
-\begin{table}[H]
-  \centering
-  \caption[dr mean values]{dr mean values (cm) obtained from fit for all disks and rings for coincidences in r}
+\newpage
+\begin{table}[H]
+  \centering
+  \caption[dr mean values]{dr mean values (cm) obtained from fit to true coincidences in r}
 \begin{tabular}{ccccc}
@@
   \centering
-  \caption[dr cut values]{dr standard deviation (sigma) values obtained from fit for all disks and rings for coincidences in r}
+  \caption[dr cut values]{dr standard deviation (cm) values obtained from fit to true coincidences in r}
 \begin{tabular}{ccccc}
@@
   \centering
-  \caption[dphi cut values]{dphi standard deviation values obtained from fit for all disks and rings for coincidences in r}
+  \caption[dphi cut values]{dphi standard deviation values obtained from fit to true coincidences in r}
 \begin{tabular}{ccccc}
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/l1l2_l3l4_2xinr.png}
+\newpage
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.6\textwidth]{ashish_thesis/twofoldinphi_sch.png}
+\caption[Map Of Two Fold Coincidences in phi]{%                                                                                                            
+  Map of two fold coincidences in phi showing all module overlap regions.
+}
+\label{fig:cluster_ring_720}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.6\textwidth]{ashish_thesis/l1l2_l3l4_2xinr.png}
 \caption[L1L2 and L3L4 Module Overlap Map for Two Fold Coincidences in r]{%
-   Module overlap map in L1L2 and L3L4 layers for two fold coincidences in r.
+   X-Y map of reconstructed two-fold coincidences in r using the selections described in the text.
+We have only reconstructed coincidences in r arising from module overlap in L1L2 and L3L4.
+The gaps in the plot correspond to other types of two fold coincidences in r that will arise from module overlap in L1L4, L3L4 and L2L3.
 }
@@
 The new algorithm is able to remove physics noise at high pileup as can be seen from the high efficiency values and low fake rates for Disk 4 all rings and all pileup samples as shown in Table  \ref{tab:sample} and \ref{tab:combined_sample}.
-
-\begin{equation}
+The fake two-fold coincidence rates for different rings in Disk 4 with a pileup of 200 are presented.
+The rate changes across the rings, starting from 1.1 \% in Ring 1 and increasing to 2.5 \% in Ring 4, before slightly decreasing to 2.3 \% in Ring 5.
+This variation suggests that the fake coincidences is not uniform across the rings of Disk 4, with the middle rings (Rings 3 and 4) showing a higher fake rate.
+There is a general trend of increasing fake rates with pileup.
+For instance, at a pileup of 0.5, the fake rates for "2-fold in phi" and "2-fold in r" are 0.78\% and 0.99\%, respectively.
+These rates gradually increase as the pileup value rises, reaching 1.85\% for "two-fold in phi" and 1.57\% for "two-fold in r" at a pileup of 200.
+Fake rate is defined as\begin{equation}
 \text{Fake rate} = \frac{\text{Number of fake coincidences (Area under the green curve)}}{\text{Total number of coincidences (Area under the black curve)}}
-\end{equation}
+\end{equation} as shown in Fig. 1.9.
 
@@
 
-It is important to study how the number of two-fold coincidences after final selections change with pileup for precise luminosity measurement.
+We study the linearity of two-fold coincidences that is how the number of two-fold coincidences change with pileup to obtain precise luminosity measurement.
 Distribution of two-fold coincidences for TEPX Disk 4 Ring 1 for all pileup values is shown in Fig.
@@
 For pileup 200, mean two-fold coincidences is around 270.
-Under vdM conditions, it range from 0 to 13.
 The new algorithm is able to suppress non-linearity at high pileup values as shown in Fig.
@@
 It is possible to have three fold coincidences in TEPX detector.
-A three-fold coincidence refers to a situation where three hits occur nearly simultaneously and in a close spatial arrangement originating from the same underlying event.
+A three-fold coincidence refers to a situation where three hits occur in a close spatial arrangement originating from the same underlying event.
 In the current algorithm, we look for another cluster in the lower ring after a two fold coincidence cluster in phi or r is found.
@@
 \ref{fig:tepx_3foldcoin_allPU_2}.
-With the current algorithm, three-fold coincidences shows non-linearity at high pileup as shown in Fig.
+With the current algorithm, three-fold coincidences shows non-linearity as shown in Fig.
 \ref{fig:tepx_3foldcoin_allPU_3}.
@@
 \newpage
-\section{Statistical precision for TEPX luminometer}
+\section{Statistical precision}
 
@@
 
-\end{comment}
-
 \newpage
@@
 Statistical precision is also emphasized as a critical factor for achieving the targeted 0.1\% accuracy in HL-LHC luminosity measurement.
+
+\end{comment}

### 2024-01-01 tesis_Ashish/Chapter8/chapter8.tex
Sehrawat A thesis 17 Dec 2023
Updated thesis 1 Jan 2024

@@
-\section{Summary and Plans} 
-\label{sec:con}
+\chapter{Summary}  %Title of the First Chapter
 
-\subsection{Summary of the study and its findings}
-\subsection{Limitations and potential improvements of the pixel cluster counting method}
-\subsection{Future work related to luminosity measurement at the LHC}
-\subsection{Conclusion and final remarks}
+\ifpdf
+    \graphicspath{{Chapter8/Figs/Raster/}{Chapter8/Figs/PDF/}{Chapter8/Figs/}}
+\else
+    \graphicspath{{Chapter8/Figs/Vector/}{Chapter8/Figs/}}
+\fi
+
+The research presented in this thesis on the PCC luminometer offers profound insights and advancements in luminosity measurement.
+The meticulous analysis and improvement in PCC luminosity analysis, including the development of a comprehensive module veto list and innovative calibration techniques, have significantly enhanced the precision of luminosity measurement.
+The implementation of afterglow correction methodologies addresses residual signals, ensuring the accuracy of the PCC data.
+Alongside these achievements, this thesis also contributes substantially to the Phase II upgrade of the CMS detector.
+The Phase II upgrade is a major, multi-year project, currently in its design and development phase, with full operation expected to commence in 2029.
+%This upgrade encompasses the installation of new pixel and strip detectors, a timing layer, and an advanced data acquisition system.
+The new carbon-fiber support structure for the upgraded tracker, scheduled for installation between 2022 and 2023, is part of this extensive revamp.
+The period from 2024 to 2026 will see the installation of these new detectors and electronics, followed by a crucial phase of commissioning and testing from 2027 to 2028 to ensure optimal functionality.
+The advancements in the PCC luminometer, combined with the upcoming Phase II upgrades, position the CMS detector at the forefront of particle physics research.
+The improvements in luminosity measurement techniques and detector capabilities will enable more precise and accurate experiments, paving the way for groundbreaking discoveries in understanding the fundamental forces and particles of our universe.
+The comprehensive approach and innovative methodologies developed in this thesis are pivotal contributions to the field, enhancing not only current research capabilities but also setting a solid foundation for future explorations in high-energy particle physics.
+
+Chapter 1 of the thesis lays the groundwork for understanding the critical role of luminosity in particle physics, particularly in the Large Hadron Collider (LHC).
+The chapter highlights ongoing advancements in enhancing luminosity measurement precision, notably through the CMS pixel detector.
+
+In Chapter 2, we provide a comprehensive overview of the methods and technologies used to measure luminosity at the CMS detector.
+It focuses on various luminosity measurement methods, the role of the pixel detector, and the pixel cluster counting (PCC) method.
+It details the importance of precise luminosity measurement for understanding particle interactions, the challenges involved, and the advancements made in this field, particularly with the PCC method's implementation and its impact on enhancing the accuracy of luminosity measurements.
+
+In Chapter 3, we discuss the calibration of luminosity measurement devices using the van der Meer (vdM) scan method.
+It explains the technique developed by Simon van der Meer for relating the detection rate of a luminometer to absolute luminosity.
+This involves scanning colliding beams across each other and measuring the beam overlap integral, which is proportional to luminosity.
+The chapter also covers background estimation to account for various sources of noise.
+Rate is fitted with gaussian plus polynomial model, a fitting function used to fit signal in the vdM calibration process.
+
+In Chapter 4, the results from Run 2 (2017 and 2018) are comprehensively detailed. %For the year 2018, the integrated luminosity was calculated to be \(60.47 \, \text{fb}^{-1}\).
+The visible cross section was accurately determined as \(960.54 \pm 0.85 \, (\text{stat.}) \, \text{mb}\).
+A total of 155 good pixel modules were selected for the final luminosity measurement.
+Systematic uncertainties were meticulously quantified, including scan to scan (\(0.3\%\)), bunch to bunch (\(0.1\%\)), afterglow (\(0.3\%\)), linearity (\(0.4\%\)), and cross detector stability (\(0.3\%\)).
+Work is ongoing to complete this measurement.
+The total uncertainty is expected to be order of 1\%.
+
+In Chapter 5, significant results from the PCC luminosity measurement during Run 3 (2022) are outlined.
+%The chapter reports that the PCC integrated luminosity for 2022 was computed to be \(38.61 \, \text{fb}^{-1}\) .
+Furthermore, a comprehensive analysis of systematic uncertainties in the luminosity measurement for the year 2022 is presented.
+These uncertainties encompass a range of factors including calibration (1.3\%), integration (0.8\%), and other specific sources such as beam current (0.2\%), orbit drift (0.3\%), and cross-detector linearity (0.54\%), culminating in a total uncertainty of \(1.5\%\).
+
+Chapter 6 of the thesis on the TEPX luminometer for the High Luminosity Large Hadron Collider (HL-LHC) addresses the challenges and solutions in luminosity measurement for the anticipated HL-LHC phase starting in 2029.
+%With the HL-LHC set to increase instantaneous luminosity to up to 200 proton-proton collisions per bunch crossing, the TEPX luminometer is designed for high-precision, real-time measurement using pixel cluster counting and coincidence counting.
+This setup enhances accuracy and handles the expected increase in radiation levels, data rates, and event complexity.
+The TEPX system is noted for its linearity, indicating its effectiveness as a luminometer as the PCC visible cross section remains constant across various luminosity levels.
+Advanced algorithms using dr and $d\phi$ variables effectively manage non-linearity and suppress fake coincidences at high pileup levels, maintaining non-linearity within 1\% across the pileup range.
+Furthermore, the system achieves high efficiency and low fake rates in complex luminosity conditions.
+Statistical precision is also emphasized as a critical factor for achieving the targeted 0.1\% accuracy in HL-LHC luminosity measurement.

### 2024-01-02 tesis_Ashish/Chapter4/chapter4.tex
Sehrawat A thesis 17 Dec 2023
Updated thesis 2 Jan 2024

@@
 A comparison of PCC luminosity with HFOC luminosity as a function of time is shown in Fig.
-\ref{fig:stabprof} depicting slight instabilities in PCC luminosity over time.
+\ref{fig:stabprof_7098} depicting slight instabilities in PCC luminosity over time.
 %Detector Aging and Radiation Damage Detectors used in high-energy physics experiments are subject to aging and radiation damage due to the high-intensity radiation environment they operate in.
@@
 \caption[Luminosity Ratio Profile]{Profile of the PCC/HFOC luminosity as a function of lumi section.}
-\label{fig:stabprof1}
+\label{fig:stabprof_7098}
 \end{figure}
@@
 ndom trigger PCC dataset for all periods are used to make these plots \cite{Sehrawat2023}.}
-  \label{fig:stabprof}
+  \label{fig:stabprof_4012}
 \end{figure}
@@
 \hline
-Normalization & Length scale & 0.2  \\
- & Orbit drift &  0.2  \\
- & x-y nonfactorization & 0.6 \\
- & Beam-beam deflection + Dynamic $\beta^{*}$  & 0.2 \\
- & Beam current calibration  & 0.2 \\
- & Ghost and satellite & 0.1 \\
+Normalization  Length scale & -  \\
+ & Orbit drift &  -  \\
+ & x-y nonfactorization & - \\
+ & Beam-beam deflection + Dynamic $\beta^{*}$  & - \\
+ & Beam current calibration  & - \\
+ & Ghost and satellite & - \\
  & Scan to scan variation & 0.3 \\
@@
  & Linearity  & 0.4 \\
-Total &  &  1.08 \\
+%Total &  &  1.08 \\
 \end{tabular}

### 2024-01-03 tesis_Ashish/Chapter7/chapter7.tex
Updated thesis 1 Jan 2024
Updated thesis 4 Jan 2024

@@
 The DAQ system must handle the transmission of trigger primitives to the Level-1 Trigger system and buffer the full event data until the trigger decision is made.
-The high-speed optical links used for data transmission between the Front-End Electronics (FEE) and off-detector electronics are expected to operate at data rates of 10-25 Gbps or higher to handle the large data volumes generated by the upgraded tracker.
-
-The TBPX occupies the central region along the \( z \)-axis from 0 to just below 300~mm, employing 360 units of \( 1 \times 2 \) modules (modules with two readout chips) and 504 units of \( 2 \times 2 \) modules (modules with four readout chips) arranged in four layers parallel to the beam.
-The TFPX extends from approximately 250~mm to 1400~mm in the \( z \)-direction, with 832 units of \( 1 \times 2 \) and 896 units of \( 2 \times 2 \) modules.
-The TEPX covers a range from about 1700~mm to over 2600~mm and includes 768 units of \( 1 \times 2 \) and 992 units of \( 2 \times 2 \) modules.
+%The high-speed optical links used for data transmission between the Front-End Electronics (FEE) and off-detector electronics are expected to operate at data rates of 10-25 Gbps or higher to handle the large data volumes generated by the upgraded tracker.
+In the Inner Tracker readout system, control signals are sent to the it at 160 Mb/s to coordinate its detection processes.
+It, in turn, outputs data at 1.28 Gb/s per chip to the LpGBT, which acts as a data consolidator for up to three chips.
+This data is then relayed optically to the DTC board, which operates a bidirectional data exchange: 2.5 Gb/s optical down-links channel control information back to the Inner Tracker, while 10 Gb/s up-links carry processed readout data and monitoring details to the DAQ and control system.
+Moreover, the DTC can interface with a Lumi processor via an optional link, designed for a substantial data transfer rate of approximately 4x25 Gb/s, to handle specialized luminosity data processing.
+Finally, the DAQ and control system, which receives the comprehensive data at a substantial rate of 25 Gb/s, undertakes the final processing and storage of data.
+
+The TBPX occupies the central region along the \( z \)-axis from 0 to just below 300~mm, employing \( 1 \times 2 \) modules (modules with two readout chips) and \( 2 \times 2 \) modules (modules with four readout chips) arranged in four layers parallel to the beam.
+The TFPX extends from approximately 250~mm to 1400~mm in the \( z \)-direction, with \( 1 \times 2 \) and \( 2 \times 2 \) modules.
+The TEPX covers a range from about 1700~mm to over 2600~mm and includes  \( 1 \times 2 \) and \( 2 \times 2 \) modules.
 Collectively, these sub-detectors boast around 1.947 billion pixels across 13,488 pixel chips, spanning a silicon area of 4.87 square meters.
@@
 \ref{fig:Innertracker_40}.
-%The rings have 20, 28, 36, 44 and 48 modules respectively.
+The rings have 20, 28, 36, 44 and 48 modules respectively.
 The first two inner rings are equipped with \(1 \times 2\) modules, while the more extensive \(2 \times 2\) modules are mounted on the three outer rings.
@@
 
-\begin{figure}[!htp]
+\begin{figure}[H]
   \centering
@@
 
-\newpage
 \section{TEPX Luminometer}
@@
 It is transitioning from blue (low density) to red (high density), with the hottest regions indicating the overlap modules within the rings.
-The granularity of the histogram is set to 1000 for both axes and a bin size of 0.1 cm, allowing for a detailed visualization of the clusters across the disk.
+The granularity of the histogram is set to 1000 for both axes and a bin size of 0.1 mm, allowing for a detailed visualization of the clusters across the disk.
 %The TEPX disk in this map consists of 5 rings which are concentric rings of pixel modules at different radial distances from the beamline.
@@
   \centering
-  \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_clusters_1.png}
+  \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_clusters_2.png}
   \caption[TEPX Cluster Map]{TEPX cluster map in the XY plane for pileup 200 simulated sample having 5000 events. %Map showing coordinates of TEPX clusters in CMS global coordinate system.
@@
 Number of x bins is 1000, x bins range from -40 to 40.
-    x bin size is 0.1 cm and %Number of y bins is 1000, y bins range from -40 to 40.
-    y bin size is 0.1 cm.}
+    x bin size is 0.1 mm and %Number of y bins is 1000, y bins range from -40 to 40.
+    y bin size is 0.1 mm.}
   \label{fig:tepx_cl}
@@
 We study the two-fold coincidences in $\phi$ for all TEPX Disk and rings using r, phi variable for pileup 0.5.
-Based on pileup 0.5 sample, a pre-selection of 0.15 cm on dr and 0.04 on dphi variable is applied in order to remove fake coincidences.
+Based on pileup 0.5 sample, a pre-selection of 0.15 mm on dr and 0.04 on dphi variable is applied in order to remove fake coincidences.
 
@@
 \centering
-\includegraphics[width=1\textwidth]{ashish_thesis/D4R1_S2_drdphi_cut_1.png}
+\includegraphics[width=1\textwidth]{ashish_thesis/D4R1_S2_drdphi_cut_2.png}
 \caption[Pileup 0.5 Cluster Count in D4R1 vs. dr & dphi]{%
@@
   \centering
-  \caption[dr offset values]{dr mean values obtained from fit for two fold coincidences in phi for all disks and rings}
+  \caption[dr offset values]{dr mean values (mm) obtained from fit for two fold coincidences in phi for all disks and rings}
   \begin{tabular}{cccccc}
@@
   \centering
-  \caption[dr cut values]{dr cut values for two fold coincidences in phi for all disks and rings}
+  \caption[dr cut values]{dr cut values (mm) for two fold coincidences in phi for all disks and rings}
   \begin{tabular}{cccccc}
@@
   \centering
-  \caption[dr mean values]{dr mean values (cm) obtained from fit to true coincidences in r}
+  \caption[dr mean values]{dr mean values (mm) obtained from fit to true coincidences in r}
 \begin{tabular}{ccccc}
@@
   \centering
-  \caption[dr cut values]{dr standard deviation (cm) values obtained from fit to true coincidences in r}
+  \caption[dr cut values]{dr standard deviation (mm) values obtained from fit to true coincidences in r}
 \begin{tabular}{ccccc}
@@
 \centering
-\includegraphics[width=0.6\textwidth]{ashish_thesis/twofoldinphi_sch.png}
+\includegraphics[width=0.6\textwidth]{ashish_thesis/twofoldinphi_sch_1.png}
 \caption[Map Of Two Fold Coincidences in phi]{%                                                                                                            
-  Map of two fold coincidences in phi showing all module overlap regions.
+   X-Y map of reconstructed two-fold coincidences in $\phi$ showing module overlap regions.
 }
@@
 \centering
-\includegraphics[width=0.6\textwidth]{ashish_thesis/l1l2_l3l4_2xinr.png}
+\includegraphics[width=0.6\textwidth]{ashish_thesis/l1l2_l3l4_2xinr_2.png}
 \caption[L1L2 and L3L4 Module Overlap Map for Two Fold Coincidences in r]{%
@@
 A three-fold coincidence refers to a situation where three hits occur in a close spatial arrangement originating from the same underlying event.
-In the current algorithm, we look for another cluster in the lower ring after a two fold coincidence cluster in phi or r is found.
+In the current algorithm, we look for another cluster in the lower ring after a two fold coincidence cluster in phi is found.
+The selections used for finding three-fold coincidences using old dx, dy and dz cut variables are 0.1 mm, 0.1 mm and 0.9 mm.
 The XY map of three-fold coincidences is shown in Fig.
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{ashish_thesis/tepx_threefold_coincidences.png}
+  \includegraphics[width=0.8\columnwidth]{ashish_thesis/tepx_threefold_coincidences_1.png}
   \caption[Regions in XY plane showing three-fold coincidences]{X vs Y map of three fold coincidences.}

### 2024-01-04 tesis_Ashish/Chapter2/chapter2.tex
Updated thesis 4 Jan 2024

@@
 
-The CMS experiment employs several devices to measure luminosity, each covering specific pseudorapidity ranges and regions within the CMS detector \cite{CMS-PAS-LUM-18-002}.
+The CMS experiment employs several devices to measure luminosity, each covering specific pseudorapidity ranges and regions within the CMS detector \cite{pas_18}.
 The use of several luminometers as shown in Fig.~\ref{fig:lumino_cms} offers a multitude of advantages.

### 2024-01-04 tesis_Ashish/Chapter4/chapter4.tex
Updated thesis 4 Jan 2024

@@
 \hline
-Normalization  Length scale & -  \\
+Normalization  & Length scale & -  \\
  & Orbit drift &  -  \\

### 2024-01-04 tesis_Ashish/Chapter5/chapter5.tex
Updated thesis 4 Jan 2024

@@
 
-To investigate the performance of the PCC luminometer during the 2022 data collection period, we segment CMS luminosity data into five distinct periods:  C, D, E, F, and G, as illustrated in Figure \ref{fig:period_bound_1}.
+To investigate the performance of the PCC luminometer during the 2022 data collection period \cite{Hayrapetyan:2870088}, we segment CMS luminosity data into five distinct periods:  C, D, E, F, and G, as illustrated in Figure \ref{fig:period_bound_1}.
 The run ranges associated with each of these periods are outlined in Fig.

### 2024-01-04 tesis_Ashish/Chapter7/chapter7.tex
Updated thesis 4 Jan 2024

@@
 
-We study the linearity of two-fold coincidences that is how the number of two-fold coincidences change with pileup to obtain precise luminosity measurement.
+We study the linearity of two-fold coincidences that is how the number of two-fold coincidences change with pileup to obtain precise luminosity measurement \cite{sehrawat2022optimisation}.
 Distribution of two-fold coincidences for TEPX Disk 4 Ring 1 for all pileup values is shown in Fig.

### 2024-01-04 tesis_Ashish/Chapter2/chapter2.tex
Updated thesis 4 Jan 2024

@@
 As these secondary particles pass through the scintillating fibers, they produce light, which is collected by photodetectors and converted into an electrical signal proportional to the particle's energy.
-Two separate algorithm are used for luminosity measurement in the HF Calorimeter, HFOC and HFET based on the Zero Counting (ZC) method and the Missing Transverse Energy (MET) methods respectively \cite{CMS-PAS-LUM-15-001}.
+Two separate algorithm are used for luminosity measurement in the HF Calorimeter, HFOC and HFET based on the Zero Counting (ZC) method and the Missing Transverse Energy (MET) methods respectively.
+%\cite{CMS-PAS-LUM-15-001}.
 
@@
 The PCC method has been extensively tested and validated by the CMS during the LHC Run 1 and Run 2, which corresponded to proton-proton collisions at center-of-mass energies of 7-8 TeV and 13 TeV, respectively.
-The PCC method has achieved a relative luminosity precision of about 1.5 \%, which is well within the design goals of the CMS \cite{CMS-PAS-LUM-18-002}.
+The PCC method has achieved a relative luminosity precision of about 1.5 \%, which is well within the design goals of the CMS \cite{pas_18}.
 In the future, the PCC method will continue to be a key component of the CMS luminosity measurement strategy, as it provides a precise and robust measurement of the luminosity ratio between different datasets and periods.

### 2024-01-04 tesis_Ashish/Chapter2/chapter2.tex
Updated thesis 4 Jan 2024

@@
 
-The PCC of various layers and disks, normalized to the total PCC, as a function of lumi section can provide crucial insights into the detector's performance and stability over time and under different conditions \cite{CMS-PAS-LUM-15-001}\cite{CMS-PAS-LUM-16-001}.
+The PCC of various layers and disks, normalized to the total PCC, as a function of lumi section can provide crucial insights into the detector's performance and stability over time and under different conditions \cite{CMS-PAS-LUM-16-001}.
 A lumi section is a unit of data-taking time in the LHC, typically lasting about 23.36 seconds, during which the beam conditions are assumed to be stable.

### 2024-01-05 tesis_Ashish/Chapter5/chapter5.tex
Updated thesis 5 Jan 2024

@@
 The vdM fill has 1693 bad modules, which is slightly higher than those in the 2022D period for stability but slightly less for linearity.
-There seems to be a consistent observation that for each given period, the number of bad modules under linearity considerations is either equal to or slightly higher than those under stability considerations \cite{bril2023moduleveto}.
+There seems to be a consistent observation that for each given period, the number of bad modules under linearity considerations is either equal to or slightly higher than those under stability considerations \cite{pas_22}.
+% \cite{bril2023moduleveto}.
 
@@
 The 'Bad Modules' column provides the total number of bad or unreliable pixel modules identified across the listed combination of periods.
-For example, 886 bad modules are found over periods C and D, 1106 bad modules over periods C, D, and E \cite{bril2023moduleveto_1}.
+For example, 886 bad modules are found over periods C and D, 1106 bad modules over periods C, D, and E \cite{pas_22}.
+%\cite{bril2023moduleveto_1}.
 
@@
 PCC visible cross section is 1076 $\pm$ 0.9 (stat) mb as shown in Fig.
-\ref{fig:period_bound_105} \cite{bril2023vdmrecalibration}.
+\ref{fig:period_bound_105} \cite{pas_22} %\cite{bril2023vdmrecalibration}.
 
@@
 \ref{fig:period_bound_102} in run 361957 to compute type 2 afterglow amplitude and decay width.
-The values obtained for type 2 afterglow amplitude and decay parameters are 0.0007915 and 0.00918 respectively \cite{bril2023afterglow}.
+The values obtained for type 2 afterglow amplitude and decay parameters are 0.0007915 and 0.00918 respectively \cite{pas_22}.
+%\cite{bril2023afterglow}.
 %as shown in Table. \ref{table:trains_data}.
@@
 Integrated luminosity accumulates this data over time.
-For 2022, the total PCC integrated luminosity is calculated to be 38.61 $fb^{-1}$ \cite{bril2023randomzerobias}.
+For 2022, the total PCC integrated luminosity is calculated to be 38.61 $fb^{-1}$ \cite{pas_22}.
+%\cite{bril2023randomzerobias}.
 
@@
 Fig.
-\ref{fig:stabprof1_79} shows the projection of the luminosity ratio using 50 lumi section binning strategy.
+\ref{fig:stabprof1_79} shows the projection of the luminosity ratio using 50 lumi section binning strategy \cite{pas_22}.
 %By grouping the lumi sections into larger bins, this visualization enables an aggregated view of luminosity data over broader intervals of the data-taking period.
@@
 To quantify the linearity systematic uncertainty, the slope variability of the detector response against luminosity levels can be analyzed.
-This, combined with the luminosity range, provides a measure of the expected rate variability due to non-linearity, representing the linearity systematic uncertainty.
+This, combined with the luminosity range, provides a measure of the expected rate variability due to non-linearity, representing the linearity systematic uncertainty \cite{pas_22}.
 %Non-linear response during fill 8274 and three consecutive fill 8274, 8275 and 8276 is shown in Fig.

### 2024-01-06 tesis_Ashish/Chapter4/chapter4.tex
Updated thesis 5 Jan 2024
Updated thesis 6 Jan 2024

@@
 
-The calibration of luminosity measurement by the CMS experiment luminometers in the 2018 proton-proton data taking at $\sqrt{s}$ = 13 TeV \cite{CMS-PAS-LUM-18-002} was performed during LHC fill 6868 on June 30 and July 1, 2018 at $\sqrt{s}$ = 13 TeV.
+The calibration of luminosity measurement by the CMS experiment luminometers in the 2018 proton-proton data taking at $\sqrt{s}$ = 13 TeV \cite{pas_18} was performed during LHC fill 6868 on June 30 and July 1, 2018 at $\sqrt{s}$ = 13 TeV.
 Zero-bias triggers on 5 bunch pairs (BCIDs 265, 865, 1780, 2192, and 3380) recorded events rate is 27.7 kHz.
@@
 Each point on this curve accumulates the instantaneous luminosity values up to that specific lumi section.
-The integrated luminosity for entire 2018 is calculated to be 60.47 fb^{-1}.
+%The integrated luminosity for entire 2018 is calculated to be 60.47 fb^{-1}.
 

### 2024-01-06 tesis_Ashish/Chapter5/chapter5.tex
Updated thesis 6 Jan 2024

@@
 
-\begin{figure}[!htp]
+\begin{figure}[H]
 \centering
@@
 
-PCC instantaneous luminosity provides a measure of the collider's performance and is graphically represented in Fig.
+PCC instantaneous luminosity provides a measure of the collider performance and is graphically represented in Fig.
 \ref{fig:period_bound_1000045}.
@@
 This cyclical pattern is evident across all fills, underscoring the systematic nature of the process.
-Integrated luminosity accumulates this data over time.
-For 2022, the total PCC integrated luminosity is calculated to be 38.61 $fb^{-1}$ \cite{pas_22}.
+Integrated luminosity accumulates this data over time \cite{pas_22}.
+%For 2022, the total PCC integrated luminosity is calculated to be 38.61 $fb^{-1}$ \cite{pas_22}.
 %\cite{bril2023randomzerobias}.
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/PCClumivslumisection_2022.png}
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\textwidth]{ashish_thesis/PCClumivslumisection_2022.png}
 \caption[2022 PCC Inst. Luminosity]{%
@@
   \centering
-  \caption{Bunch to bunch variation of visible cross section. $N_b$ is the number of bunches in the vdM scan.}
+  \caption[Bunch uncertainty]{Bunch to bunch variation of visible cross section. $N_b$ is the number of bunches in the vdM scan.}
 \begin{tabular}{cccc}

### 2024-01-06 tesis_Ashish/Chapter7/chapter7.tex
Updated thesis 6 Jan 2024

@@
   \centering
-  \caption[dr offset values]{dr mean values (mm) obtained from fit for two fold coincidences in phi for all disks and rings}
+  \caption[dr offset values for two-fold in phi]{dr mean values (mm) obtained from fit for two fold coincidences in phi for all disks and rings}
   \begin{tabular}{cccccc}
@@
   \centering
-  \caption[dr cut values]{dr cut values (mm) for two fold coincidences in phi for all disks and rings}
+  \caption[dr cut values for two-fold in phi]{dr cut values (mm) for two fold coincidences in phi for all disks and rings}
   \begin{tabular}{cccccc}
@@
   \centering
-  \caption[dphi cut values]{dphi cut values for two fold coincidences in phi for all disks and rings}
+  \caption[dphi cut values for two-fold in phi]{dphi cut values for two fold coincidences in phi for all disks and rings}
   \begin{tabular}{cccccc}
@@
   \centering
-  \caption[dr mean values]{dr mean values (mm) obtained from fit to true coincidences in r}
+  \caption[dr mean values for two-fold in r]{dr mean values (mm) obtained from fit to true coincidences in r}
 \begin{tabular}{ccccc}
@@
   \centering
-  \caption[dr cut values]{dr standard deviation (mm) values obtained from fit to true coincidences in r}
+  \caption[dr cut values for two-fold in r]{dr standard deviation (mm) values obtained from fit to true coincidences in r}
 \begin{tabular}{ccccc}
@@
   \centering
-  \caption[dphi cut values]{dphi standard deviation values obtained from fit to true coincidences in r}
+  \caption[dphi cut values for two-fold in r]{dphi standard deviation values obtained from fit to true coincidences in r}
 \begin{tabular}{ccccc}
@@
   \includegraphics[width=0.8\columnwidth]{ashish_thesis/tepx_threefold_coincidences_1.png}
-  \caption[Regions in XY plane showing three-fold coincidences]{X vs Y map of three fold coincidences.}
+  \caption[Regions in XY plane showing three-fold coincidences]{Reconstructed three fold coincidences in all rings within TEPX double-disk.}
   \label{fig:tepx_3foldcoin_allPU_1}

### 2024-01-14 tesis_Ashish/Acknowledgement/acknowledgement.tex
Updated thesis 14 Jan 2024

@@
-I would like to express my sincere gratitude to all those who have supported and guided me throughout my journey in completing my PhD thesis in particle physics, specifically focusing on the CMS experiment at CERN.
-Their unwavering support, encouragement, and expertise have been invaluable to my success.
+I wish to express my profound gratitude to all those who have supported and guided me throughout my journey towards completing my PhD thesis in particle physics, with a focus on the CMS experiment at CERN.
+Their unwavering support, encouragement, and expertise have been indispensable to my success.
 
-First and foremost, I would like to extend my deepest appreciation to my esteemed thesis supervisor, Dr.
+Foremost, I extend my deepest appreciation to my esteemed thesis supervisor, Dr.
 Jose Feliciano Benitez.
-His exceptional guidance, profound knowledge, and unwavering commitment to scientific exploration have shaped my research endeavors and allowed me to delve into the fascinating world of particle physics.
-His mentorship and continuous support have been instrumental in every step of my thesis, from conceptualization to the final stages of completion.
-I am truly grateful for the opportunity to work under his supervision, and I have grown immensely both as a researcher and as an individual thanks to his invaluable guidance.
+His exceptional guidance, profound knowledge, and commitment to scientific exploration have profoundly shaped my research endeavors.
+Delving into the fascinating world of particle physics under his mentorship has been a privilege, and his continuous support has been pivotal at every stage of my thesis.
+I am immensely grateful for the opportunity to work under his supervision and for the personal and professional growth I have experienced through his invaluable guidance.
 
-I would also like to express my heartfelt gratitude to my loving parents, whose unconditional love, encouragement, and sacrifices have been the cornerstone of my academic journey.
-Their unwavering belief in my abilities and their constant support have given me the strength and motivation to overcome challenges and pursue my passion for scientific exploration.
-I am eternally grateful for their constant presence in my life and their unwavering support throughout this demanding academic endeavor.
+My heartfelt gratitude goes to my parents, Omkar Jagtaran Singh and Anita.
+Their unconditional love, encouragement, and sacrifices have been the bedrock of my academic journey.
+Their unwavering belief in my abilities and constant support have been my source of strength and motivation, enabling me to overcome challenges and pursue my passion for scientific exploration.
+Their constant presence and support throughout this demanding academic endeavor are cherished and deeply appreciated.
 
-Furthermore, I would like to extend my appreciation to my sisters for their unwavering encouragement, understanding, and motivation during the course of my PhD.
-Their belief in my abilities and their continuous support have been an immense source of inspiration and strength, reminding me to remain focused and determined even during the most challenging times.
+I also extend my appreciation to my sisters Priya, Monu, Sonu, Reena, and Seema.
+Their unwavering encouragement, understanding, and motivation have been an immense source of inspiration.
+Their belief in my abilities and continuous support have been a pillar of strength, urging me to remain focused and resilient even during challenging times.
 
-I would also like to acknowledge the collective efforts of the scientific community at CERN and all those who have contributed to the CMS experiment.
-Their collaboration, expertise, and dedication have created an enriching environment for research and have allowed me to be a part of groundbreaking discoveries in the field of particle physics.
+I am thankful for the collective efforts of the scientific community at CERN and all contributors to the CMS experiment.
+Their collaboration, expertise, and dedication have fostered an enriching research environment, allowing me to partake in groundbreaking discoveries in particle physics.
 
-Lastly, I am deeply grateful to all my friends and colleagues who have provided valuable insights, stimulating discussions, and endless support throughout this journey.
-Their encouragement, camaraderie, and intellectual exchanges have played a significant role in shaping my research and personal growth.
+I am indebted to my friends and colleagues, especially Rohit Gupta, for their valuable insights, stimulating discussions, and enduring support.
+Their encouragement, camaraderie, and intellectual exchanges have been instrumental in shaping both my research and personal growth.
 
-To each and every person mentioned above, as well as those who may not be named individually, I offer my sincerest thanks.
-Your contributions have been invaluable, and I am humbled by the generosity and unwavering support I have received.
-This thesis would not have been possible without your guidance, encouragement, and belief in me.
+To everyone mentioned, and those unnamed but equally appreciated, I extend my sincerest thanks.
+Your contributions, large and small, have been invaluable, and I am humbled by the generosity and support I have received.
+This thesis stands as a testament to your guidance, encouragement, and belief in my potential.
 
-Thank you from the bottom of my heart.
+From the bottom of my heart, thank you.

### 2024-01-14 tesis_Ashish/Dedication/dedication.tex
Updated thesis 14 Jan 2024

--- 2024-01-14 tesis_Ashish/Acknowledgement/acknowledgement.tex
@@
-I wish to express my profound gratitude to all those who have supported and guided me throughout my journey towards completing my PhD thesis in particle physics, with a focus on the CMS experiment at CERN.
+\begin{dedication}
+\begin{center}
+    \section*{Acknowledgements}
+\end{center}
+\justify{
+
+I wish to express my profound gratitude to all those who have supported and guided me throughout my journey towards completing my PhD thesis in high energy particle physics, with a focus on the CMS experiment at CERN.
 Their unwavering support, encouragement, and expertise have been indispensable to my success.
@@
 His exceptional guidance, profound knowledge, and commitment to scientific exploration have profoundly shaped my research endeavors.
-Delving into the fascinating world of particle physics under his mentorship has been a privilege, and his continuous support has been pivotal at every stage of my thesis.
-I am immensely grateful for the opportunity to work under his supervision and for the personal and professional growth I have experienced through his invaluable guidance.
+Delving into the fascinating world of particle physics under his mentorship has been a privilege, and his continuoussupport has been pivotal at every stage of my thesis.
+I am immensely grateful for the opportunity to work under his supervision and for the personal and professional growth I h\
+ave experienced through his invaluable guidance.
 
@@
 
-I am thankful for the collective efforts of the scientific community at CERN and all contributors to the CMS experiment.
-Their collaboration, expertise, and dedication have fostered an enriching research environment, allowing me to partake in groundbreaking discoveries in particle physics.
+I am indebted to my friends and colleagues, especially Rohit Gupta and Mohammad Balal, for their valuable insights, stimulating discussions, and enduring support.
+Their encouragement, camaraderie,and intellectual exchanges have been instrumental in shaping both my research and personal growth.
 
-I am indebted to my friends and colleagues, especially Rohit Gupta, for their valuable insights, stimulating discussions, and enduring support.
-Their encouragement, camaraderie, and intellectual exchanges have been instrumental in shaping both my research and personal growth.
+Finally, I would like to thank  University of Sonora and CONACYT for providing finnacial support to my research.
 
-To everyone mentioned, and those unnamed but equally appreciated, I extend my sincerest thanks.
-Your contributions, large and small, have been invaluable, and I am humbled by the generosity and support I have received.
-This thesis stands as a testament to your guidance, encouragement, and belief in my potential.
+%I would like to thank my wife El\'izabeth for her unconditional support in the challenges I set for myself, without her this would not be possible.
+To my advisor, Dr.
+Jos\'e Ben\'itez, for giving me guidance, patience and, above all, the opportunity to work in such a professional team and join the CMS experiment, that was a dream for me.
+To the University of Sonora and CONACYT for supporting me in completing this important challenge in my professional career.
 
-From the bottom of my heart, thank you.
+\end{dedication}

### 2024-01-14 tesis_Ashish/Dedication/dedication.tex
Updated thesis 14 Jan 2024

@@
 \begin{center}
-    \section*{Acknowledgements}
+    \section*{Acknowledgement}
 \end{center}
@@
 His exceptional guidance, profound knowledge, and commitment to scientific exploration have profoundly shaped my research endeavors.
-Delving into the fascinating world of particle physics under his mentorship has been a privilege, and his continuoussupport has been pivotal at every stage of my thesis.
-I am immensely grateful for the opportunity to work under his supervision and for the personal and professional growth I h\
-ave experienced through his invaluable guidance.
+Delving into the fascinating world of particle physics under his mentorship has been a privilege, and his continuous support has been pivotal at every stage of my thesis.
+I am immensely grateful for the opportunity to work under his supervision and for the personal and professional growth I have experienced through his invaluable guidance.
 

### 2024-01-19 tesis_Ashish/Chapter5/chapter5.tex
update

@@
         \hline
-        Beam current & 0.2 \\
-        Ghosts \& satellites & 0.15 \\
+        Beam current & 0.3 \\
         Orbit drift & 0.3 \\
-        Residual beam positions & 0.33 \\
-        Beam-beam effects & 0.37 \\
-        Length scale & 0.12 \\
+        Residual beam positions & 0.4 \\
+        Beam-beam effects & 0.4 \\
+        Length scale & 0.1 \\
         Factorization bias & 0.8 \\
-        Scan-to-scan variation & 0.2 \\
+        Scan-to-scan variation & 0.5 \\
         Bunch-to-bunch variation & 0.1 \\
-        Cross-detector consistency & 0.7 \\
+        Cross-detector consistency & 0.4 \\
         \hline
@@
         Cross-detector stability & 0.5 \\
-        Cross-detector linearity & 0.54 \\
+        Cross-detector linearity & 0.5 \\
         \hline
@@
         \hline
-        \textbf{Total} & 1.5 \\
+        \textbf{Total} & 1.4 \\
     \end{tabular}

### 2024-01-19 tesis_Ashish/Chapter8/chapter8.tex
update

@@
 Furthermore, a comprehensive analysis of systematic uncertainties in the luminosity measurement for the year 2022 is presented.
-These uncertainties encompass a range of factors including calibration (1.3\%), integration (0.8\%), and other specific sources such as beam current (0.2\%), orbit drift (0.3\%), and cross-detector linearity (0.54\%), culminating in a total uncertainty of \(1.5\%\).
+These uncertainties encompass a range of factors including calibration (1.2\%), integration (0.8\%), and other specific sources such as beam current (0.3\%), orbit drift (0.3\%), and cross-detector linearity (0.5\%), culminating in a total uncertainty of \(1.4\%\).
 

### 2024-01-27 tesis_Ashish/Chapter1/chapter1.tex
update 27 Jan 2024

@@
 During these periods, the CMS experiment measured the instantaneous and integrated luminosity of the proton-proton collisions produced by the LHC where the integrated luminosity for each year is shown in Fig.~\ref{fig:lumi}.
-During Run 1, the CMS experiment achieved a peak instantaneous luminosity of up to $5 \times 10^{33} cm^{-2} s^{-1}$, while during Run 2, the luminosity reached a peak value of up to $2 \times 10^{34} cm^{-2} s^{-1}$.
+During Run 1, the CMS experiment achieved a peak instantaneous luminosity of up to $7.6 \times 10^{33} cm^{-2} s^{-1}$, while during Run 2, the luminosity reached a peak value of up to $2.1 \times 10^{34} cm^{-2} s^{-1}$.
 The luminosity measurements during both runs were accompanied by careful assessments of the systematic uncertainties to ensure accurate and reliable results \cite{CMS-PAS-EWK-10-004, CMS-PAS-EWK-11-001, CMS-PAS-SMP-12-008, CMS-PAS-LUM-13-001, Sirunyan:2759951, pas_17, pas_18} as shown in Table.

### 2024-01-27 tesis_Ashish/Chapter2/chapter2.tex
update 27 Jan 2024

@@
 \item Fast Beam Conditions Monitor (BCM1F) : The BCM1F is specifically designed to detect the ionization produced by charged particles passing through its diamond sensors, and to convert this signal into a measurement of the beam intensity and luminosity.
-The BCM1F consists of 24 diamond sensors, each with an active area of 1 cm², arranged in six rings around the beam pipe.
+During Run 2, the BCM1F consisted of 24 diamond sensors, each with an active area of 1 cm², arranged in six rings around the beam pipe.
 The diamond sensors are positioned very close to the CMS detector, just 10 cm away from the beam pipe.
@@
 This placement allows it to cover a pseudorapidity range of 2.9 to 5.2, which is important for measuring particles produced at small angles relative to the beamline.
-The HF Calorimeter is a sampling calorimeter, which means it consists of alternating layers of active and passive materials.
+%The HF Calorimeter is a sampling calorimeter, which means it consists of alternating layers of active and passive materials.
 The active material, in this case, is scintillating quartz fibers, which emit light when they interact with charged particles.
@@
 As these secondary particles pass through the scintillating fibers, they produce light, which is collected by photodetectors and converted into an electrical signal proportional to the particle's energy.
-Two separate algorithm are used for luminosity measurement in the HF Calorimeter, HFOC and HFET based on the Zero Counting (ZC) method and the Missing Transverse Energy (MET) methods respectively.
+Two separate algorithm are used for luminosity measurement in the HF Calorimeter, HFOC and HFET based on the Zero Counting (ZC) method and the sum of transverse energy methods respectively.
 %\cite{CMS-PAS-LUM-15-001}.
@@
 In this method, the luminosity is estimated by counting the number of events with zero particles detected in a specific region of the detector.
-The basic idea behind the zero counting method is that the probability of having zero particles detected in a given region of the detector is proportional to the probability of having no collisions in that region.
+The basic idea behind the zero counting method is that the probability of having zero particles detected in a given region of the detector is proportional to the Poisson probability of having no collisions in that region.
 This probability can be related to the luminosity of the collisions through the following equation:
@@
 One advantage is that it is a simple and robust method that does not require sophisticated detectors or calibration procedures.
-However, it can be affected by background events, such as cosmic rays or beam-gas interactions, which can produce zero particles in the region of interest and increase the uncertainty in the luminosity measurement.
+However, it can be affected by background events, such as cosmic rays or beam-gas interactions.
 \\
-The Missing Energy method is an alternative approach for luminosity measurement in the HF Calorimeter.
+The HFET algorithm measures luminosity by summing transverse energy deposits in the HF calorimeter cells.
+It relies on the direct proportionality between the total transverse energy and the particle flux from the interaction point.
+Accurate calibration of calorimeter cells is crucial for this method, as it ensures that the aggregate transverse energy accurately reflects the luminosity of the particle collisions \cite{Sirunyan:2759951.
+
+%The Missing Energy method is an alternative approach for luminosity measurement in the HF Calorimeter.
 This method relies on measuring the total transverse energy (Et) deposited in the calorimeter and comparing it with the expected average transverse energy for inelastic collisions.
@@
 By measuring the drift time, one can infer the position of the muon's trajectory.
-To use the DT muon rates as a luminometer, one would need to count the rate of detected muons as a function of the delivered luminosity.
-However, the DT muon rate luminometer is not independently calibrated during the Van der Meer (vdM) scan due to low measured rate.
-It is cross calibrated with PCC or HF.
+  %To use the DT muon rates as a luminometer, one would need to count the rate of detected muons as a function of the delivered luminosity.
+However, the DT muon rate luminometer is not independently calibrated during the van der Meer (vdM) scan due to low measured rate. It is cross calibrated with PCC or HF.
 
@@
 When charged particles from the collisions pass through the silicon sensors, they create electric charge that is read out as a signal.
-The signals from adjacent sensors are combined to form clusters, which represent the position of the particle track in the detector.
+The signals from adjacent pixels are combined to form clusters, which represent the position of the particle track in the detector.
 The total number of clusters detected over a certain period of time is used to estimate the luminosity.
@@
 One challange is the multiple proton-proton collisions per bunch crossing (pileup).
-Another challenge is the non-linearity of the pixel detector response, which can lead to inaccuracies in the luminosity measurement.
+Another challenge is the possible non-linearity or instabilities of the pixel detector response, which can lead to inaccuracies in the luminosity measurement.
 Therefore, the motivation of this research work is to develop and test more precise techniques for measuring the luminosity with the pixel detector.
@@
 The proportionality constant is called the pixel detector visible cross section, and it can be determined with a calibration method described in section 3.1.
-The PCC method is implemented in two stages: the online and offline stages.
+The PCC method exclusively utilizes offline luminosity measurement, comprising two stages: the "prompt-lumi," which is delayed by a few days and employs a non-optimized module list, and the "offline reprocessed luminosity" that uses an optimized module list for enhanced accuracy.
+During Run 2, the PCC online role was confined to recording pixel information, with cluster reconstruction occurring offline.
+However, in Run 3, this process evolved, allowing clusters to be reconstructed online within the High-Level Trigger (HLT) system, subsequently recorded for detailed offline analysis.
+%The PCC method is implemented in two stages: the online and offline stages.
 In the online stage, the pixel clusters are counted in real time by the CMS data acquisition system, which uses a custom-designed ASIC chip to process the pixel detector signals.
 %The online luminosity measurement is therefore available within seconds of the collisions, and it is used to monitor the stability of the detector and to provide feedback to the LHC operators.
-In the offline stage, the raw data from the pixel detector is analyzed using dedicated software to determine the pixel clusters and to calculate the luminosity.
+%In the offline stage, the raw data from the pixel detector is analyzed using dedicated software to determine the pixel clusters and to calculate the luminosity.
 The offline luminosity measurement is more accurate than the online measurement, as it takes into account various corrections and calibrations that are not possible in real time.
@@
 The first step in the pixel cluster reconstruction process is to identify individual pixel hits in the data frames obtained from the pixel detector data acquisition system.
-A pixel hit is a small region of the pixel detector where charge has been deposited by a particle.
+%A pixel hit is a small region of the pixel detector where charge has been deposited by a particle.
 The next step is to identify "seed" pixels, which are individual pixels with a high signal-to-noise ratio.
@@
 In the pixel cluster counting process, events of interest are selected from the large dataset obtained from the CMS experiment.
-This is typically done using zero bias triggers that select events that are coming from filled bunch crossing.
+This is typically done using zero bias triggers that randomly select events that are coming from filled bunch crossing.
   %Once the events of interest have been selected, reconstruction the pixel clusters in each event is done using the steps described in the previous bullet point.
@@
 %or more sophisticated algorithms that use machine learning techniques to identify and count clusters.
-  The number of pixel clusters in each event is affected by various sources of background noise. %such as electronic noise and cosmic ray background.
+
+\item The number of pixel clusters in each event is affected by various sources of background noise. %such as electronic noise and cosmic ray background.
   To accurately measure the number of signal clusters in each event, these background sources must be subtracted from the total cluster count.
@@
 The PCC method has several advantages over the other luminosity measurement methods used by the CMS experiment.
-The PCC method is based on the pixel detector, which has a high spatial resolution and can accurately measure the position and energy of charged particles.
+The PCC method is based on the pixel detector, which has a high spatial resolution.
 Another advantage is its high precision and stability, as it is based on a well-understood physical process and has a small systematic uncertainty.
@@
 
-The PCC method has been extensively tested and validated by the CMS during the LHC Run 1 and Run 2, which corresponded to proton-proton collisions at center-of-mass energies of 7-8 TeV and 13 TeV, respectively.
+%The PCC method has been extensively tested and validated by the CMS during the LHC Run 1 and Run 2, which corresponded to proton-proton collisions at center-of-mass energies of 7-8 TeV and 13 TeV, respectively.
 The PCC method has achieved a relative luminosity precision of about 1.5 \%, which is well within the design goals of the CMS \cite{pas_18}.
@@
 \end{comment}
+
+The PCC method has been extensively tested and validated by the CMS during the LHC Run 1 and Run 2, which corresponded to proton-proton collisions at center-of-mass energies of 7-8 TeV and 13 TeV, respectively.
+The PCC method has achieved a relative luminosity precision of about 1.5 \%, which is well within the design goals of the CMS \cite{pas_18}.
+In the future, the PCC method willcontinue to be a key component of the CMS luminosity measurement strategy, as it provides a precise and robust measurement of the luminosity ratio between different datasets and periods.
+The P\
+CC method will also benefit from the upgrades and improvements planned for the CMS pixel detector and the LHC, which will increase the luminosity and the collision rate, and will challenge the performance and the calibration of the PCC method.
+The CMS is planning to install a new pixel detector for the High-Luminosity LHC (HL-LHC) era, which will feature smaller pixel sizes, faster readout electronics, and radiation-hard materials.
+The CMS is also planning to develop new techniques and algorithms for the PCC method, such as machine learning methods, deep neural networks, and real-time analysis tools.

### 2024-01-27 tesis_Ashish/Chapter4/chapter4.tex
update 27 Jan 2024

@@
 To achieve this, a pixel module veto list is created for each period to keep track of  bad modules.
-The stability of each module is determined based on the change in the ratio of module PCC and total PCC, referred to as the module weight as shown in Fig.
+The stability of each module is determined based on the change in the ratio of module PCC and total PCC, referred to as the module weight.
+%as shown in Fig.
 \ref{fig:mod_weight}.
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/Module_weight_2.png}
-\caption[Module Weight]{%
-   Method to obtain module weights as a function of lumi section for categorizing good and bad modules.
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/Module_weight_2.png}
+%\caption[Module Weight]{%
+ %  Method to obtain module weights as a function of lumi section for categorizing good and bad modules.
 X profile of TH2F histogram (module PCC/total PCC per lumi section) is obtained.
@@
 TGraph is normalized with the mean of Y projection of TH2F histogram to obtain module stability profile.
-}
-\label{fig:mod_weight}
-\end{figure}
+%}
+%\label{fig:mod_weight}
+%\end{figure}
 
@@
 \item Contamination or environmental factors: Contamination of the pixel modules by dust, moisture, or other substances can affect their performance or cause them to fail.
-Similarly, external environmental factors, such as magneticfields or vibrations, can impact the operation of the pixel modules.
+Similarly, external environmental factors, such as magnetic fields or vibrations, can impact the operation of the pixel modules.
 
@@
 The plots provide a comparative view of how the luminosity fraction has been impacted by the application of this veto list.
-The 'before' plot shows greater variability, reflecting the natural fluctuations in luminosity across different layers or disks  during each lumi section.
+The 'before' plot shows greater variability, reflecting the fluctuations in luminosity across different layers or disks  during each lumi section.
 In contrast, the 'after' plot  display a more stable profile, indicating that the module selection has effectively reduced the variance in luminosity fraction readings, enhancing data stability.
@@
 For each of these categories, the number of good modules, mean, RMS, and the ratio of RMS to mean are provided.
-Layer 2 has no good modules and all statistical parameters are zero.
+Layer 2 has no good modules.
+%and all statistical parameters are zero.
 Layer 3, on the other hand, has 48 good modules with a mean value of 0.374681, an RMS of 0.000663165 and an RMS-to-mean ratio of 0.00176995, indicating low variability.
@@
 
+PCC visible cross section for various bunch crossing across different scans is shown in Fig.
+\ref{fig:sigmavis_btob_variation}.
+The data points exhibit a scatter around the mean value, with no apparent systematic bias, as they are distributed both above and below this average.
+While there is a certain level of precision suggested by the proximity of the points to the mean line, the varying lengths of the error bars indicate a range in measurement uncertainty.
+This variability in precision could be attributed to fluctuating experimental conditions inherent to each BCID.
+%Overall, the experiment seems to have achieved a degree of accuracy, given that the measurements are clustered around the mean, yet the spread indicated by the error bars suggests that there is potential for optimizing the precision
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=0.7\textwidth]{ashish_thesis/sigma_vis_btob_var_1.png}
+\caption[$\sigma_{vis}$ Bunch Variation]{%                                                                                                                                                       
+ Bunch to bunch variation of PCC visible cross section.
+}
+\label{fig:sigmavis_btob_variation}
+\end{figure}
+
 \newpage
@@
 The model is summed over all bunch crossings.
+
+\begin{equation}
+F(x) = \sum_{k=0}^{N_{\text{bcid}}} N_k \left[ (x - k == 0) + A  (x - k == 1) + B  \exp(-C  (x - k - 1))  (x - k \geq 1) \right]
+\end{equation}
+
 Fill 9036, shown in \ref{fig:af_fit40} and encompassing 900 colliding bunches, serves as the foundation for estimating the Type 2 afterglow parameters.
 A fit is performed to one wagon train, then two, and finally three, refining the parameters for Type 2 afterglow and minimizing the residuals of both afterglow types.
-Fit plots for single colliding bunch is shown in \ref{fig:af_fit99}.
-The values of type 2 afterglow parameter amplitude (a) and decay width (b) for different wagon trains are shown in Table \ref{fig:af_fit4000}.
+Fit plots for single train is shown in \ref{fig:af_fit99}.
+The values of type 2 afterglow parameter amplitude (B) and decay width (C) for different wagon trains are shown in Table \ref{fig:af_fit4000}.
 
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/veto_change_same_af.png}
+\newpage
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.7\textwidth]{ashish_thesis/veto_change_same_af.png}
 \caption[Afterglow background ratio]{%
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/fill_7036_pattern_2.png}
+\newpage
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\textwidth]{ashish_thesis/fill_7036_pattern_2.png}
 \caption[7036 Fill Patern]{%
@@
 
-\begin{figure}[!htp]
-  \centering
-    \includegraphics[width=\textwidth]{ashish_thesis/2018_af_fit_1.png} 
+\begin{figure}[H]
+  \centering
+    \includegraphics[width=0.75\textwidth]{ashish_thesis/2018_af_fit_1.png} 
   %\hfill % or \hspace{5mm} for a specific horizontal space                                                                                                  
@@
   \begin{tabular}{ccc}
-    \textbf{\# of wagon} & \textbf{a} & \textbf{b} \\
+    \textbf{\# of wagon} & \textbf{B} & \textbf{C} \\
      \hline
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/afterglow_correction_factor_1lsblock_315690_1.png}
+\newpage
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\textwidth]{ashish_thesis/afterglow_correction_factor_1lsblock_315690_2.png}
 \caption[Run 315690 Afterglow Background]{%
- Left: Raw and corrected PCC for all bunch crossings. Right: Afterglow scale factor for one 50 lumi section block in run 315690 for the final module veto.
+ Raw and corrected PCC for all bunch crossings.
 }
@@
 
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\textwidth]{ashish_thesis/afterglow_correction_factor_1lsblock_315690_3.png}
+\caption[Run 315690 Afterglow Background]{%
+  Afterglow scale factor for one 50 lumi section block in run 315690 for the final module veto.
+}
+\label{fig:af_change_veto}
+\end{figure}
+
 \section{PCC instantaneous and integrated luminosity}
 
-Instantaneous luminosity refers to the rate of collisions at any given moment in time.
+Instantaneous luminosity is proportional to the rate of collisions at any given moment in time.
 It is a snapshot of the experiment's performance and is represented as \( L_{\text{inst}} \).
@@
 On the other hand, integrated luminosity is represented by a continuously ascending curve.
-Each point on this curve accumulates the instantaneous luminosity values up to that specific lumi section.
+%Each point on this curve accumulates the instantaneous luminosity values up to that specific lumi section.
 %The integrated luminosity for entire 2018 is calculated to be 60.47 fb^{-1}.
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/sigma_vis_btob_var_1.png}
-\caption[$\sigma_{vis}$ Bunch Variation]{%
- Bunch to bunch variation of PCC visible cross section.  
-}
-\label{fig:sigmavis_btob_variation}
-\end{figure}
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=0.7\textwidth]{ashish_thesis/sigma_vis_btob_var_1.png}
+%\caption[$\sigma_{vis}$ Bunch Variation]{%
+ %Bunch to bunch variation of PCC visible cross section.  
+%}
+%\label{fig:sigmavis_btob_variation}
+%\end{figure}
 

### 2024-01-27 tesis_Ashish/Chapter4/chapter4.tex
update 27 Jan

@@
   \caption[$\sigma_{vis}$ bunch variation uncertainty]{Bunch to bunch variation of PCC visible cross section.
-The “bunch spread” is determined as the standard deviation (STD) of the bunches divided by the mean.}
+The “bunch spread” is determined as the standard deviation (STD) of the bunches divided by the mean.
+SEM is the standard error on the mean}
 \begin{tabular}{cccccc}
-\textbf{Scan} & \textbf{Mean} & \textbf{STD} & \textbf{(STD/Mean) [\%]} \\
+\textbf{Scan} & \textbf{Mean} & \textbf{STD} & \textbf{(SEM/$\sigma_{vis}$) [\%]} \\
 \hline
@@
 \hline
-Normalization  & Length scale & -  \\
- & Orbit drift &  -  \\
- & x-y nonfactorization & - \\
- & Beam-beam deflection + Dynamic $\beta^{*}$  & - \\
- & Beam current calibration  & - \\
- & Ghost and satellite & - \\
+Normalization  & Length scale & 0.2  \\
+ & Orbit drift &  0.1  \\
+ & x-y nonfactorization & 2.0 \\
+ & Beam-beam deflection + Dynamic $\beta^{*}$  & 0.2 \\
+ & Beam current calibration  & 0.2 \\
+ & Ghost and satellite & 0.1 \\
  & Scan to scan variation & 0.3 \\
@@
 & Background subtraction  & 0.1 \\
+\hline
 Integration & Afterglow  &  0.3 \\
@@
 & Linearity  & 0.4 \\
-%Total &  &  1.08 \\
+\hline
+Total &  &  2.2 \\
 \end{tabular}

### 2024-01-27 tesis_Ashish/Chapter5/chapter5.tex
update 27 Jan 2024
update 27 Jan

@@
     \item All barrel Layer-0 modules are sidestepped due to their vulnerability to dynamic inefficiency.
-    \item An intial filtering removes modules with 7\% average deviation of the module weight from its mean (shown in Fig.
+    \item An intial filtering removes modules with 2\% average deviation of the module weight from its mean (shown in Fig.
 \ref{fig:stab_deviation_2022}).
@@
     \item Module stability is reviewed using an iterative method.
-In the case of the 2022F dataset, we introduce additional criteria at 2\% and 0.8\%.
+In the case of the 2022F dataset, we introduce additional criteria of 0.8\%.
 For different data periods, the specific values used depend on how good the initial module list is.
@@
 As we progress through the various periods in 2022 (from F to D), there is a general trend of increasing bad modules, both for stability and linearity considerations.
+The total number of bad modules  added to the veto list grows in each period due to the sequential or iterative nature of the procedure where the veto list for each period starts with the veto from the previous period \cite{pas_22}.
+
 This suggests that as time progresses, the number of malfunctioning modules tends to grow.
@@
 \begin{itemize}
-    \item \textbf{Pedestal}: Represents a consistent noise in the pixel cluster count.
+    %\item \textbf{Pedestal}: Represents a consistent noise in the pixel cluster count.
 
@@
 %Post-fitting residuals help in verifying the accuracy of the process.
-While Type 1 residuals are minimal, Type 2 shows a slight deviation of around 0.2\%.
+While Type 1 residuals are minimal, Type 2 shows a slight deviation of around 0.2\% as shown in Fig. \ref{fig:period_bound_45}.
 
@@
 Consequently, direct re-evaluation became unfeasible.
-As a solution, stored afterglow corrections, bolstered by a 1.008 factor from period E data, were applied.
+As a solution, stored afterglow corrections evaluated in the CMS prompt calibration stage, corrected by a factor 1.008 from period E data, were applied.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/afterglow_t1res_vsinstlumi_1.png}
+\caption[2022 PCC Type 1 Afterglow Residuals]{%
+ PCC afterglow correction type 1 residual as a function of instantaneous luminosity for period Run 2022F.
+The residual fraction is given by the ratio of the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch.
+
+}
+\label{fig:period_bound_44}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/afterglow_t2res_vsinstlumi_1.png}
+\caption[2022 PCC Type 2 Afterglow Residuals]{%
+  Type 2 residual as a function of instantaneous luminosity for period 2022F.
+These are given by the ratio of the luminosity of the second and following empty bunches after a colliding bunch to the luminosity of the colliding bunch.
+}
+\label{fig:period_bound_45}
+\end{figure}
 
@@
 \centering
-\includegraphics[width=0.7\textwidth]{ashish_thesis/PCClumivslumisection_2022.png}
+\includegraphics[width=0.9\textwidth]{ashish_thesis/PCClumivslumisection_2022.png}
 \caption[2022 PCC Inst. Luminosity]{%
@@
 
-\newpage
 \section{Systematic uncertainties}
@@
   \centering
-  \caption[Bunch uncertainty]{Bunch to bunch variation of visible cross section. $N_b$ is the number of bunches in the vdM scan.}
+  \caption[Bunch uncertainty]{Bunch to bunch variation of visible cross section (as shown in Fig.
+\ref{fig:period_bound_99}).
+$N_b$ is the number of bunches in the vdM scan.
+SEM is the standard error on the mean.}
 \begin{tabular}{cccc}
-\textbf{Scan} & \textbf{$\sigma_{vis}$ [mb]} & \textbf{RMS [mb]} & $\frac{\frac{\textbf{RMS}}{\sqrt{N_b}}}{\sigma_{\textbf{vis}}}$ [\%] \\
+\textbf{Scan} & \textbf{$\sigma_{vis}$ [mb]} & \textbf{RMS [mb]} & (SEM/$\sigma_{vis}$) [\%] \\
 \hline
@@
 \end{table}
+
+%$\frac{\frac{\textbf{RMS}}{\sqrt{N_b}}}{\sigma_{\textbf{vis}}}$
 
@@
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/afterglow_t1res_vsinstlumi_1.png}
-\caption[2022 PCC Type 1 Afterglow Residuals]{%
- PCC afterglow correction type 1 residual as a function of instantaneous luminosity for period Run 2022F.
+%\begin{figure}[H]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/afterglow_t1res_vsinstlumi_1.png}
+%\caption[2022 PCC Type 1 Afterglow Residuals]{%
+ %PCC afterglow correction type 1 residual as a function of instantaneous luminosity for period Run 2022F.
 The residual fraction is given by the ratio of the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch.
 
-}
-\label{fig:period_bound_44}
-\end{figure}
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=1\textwidth]{ashish_thesis/afterglow_t2res_vsinstlumi_1.png}
-\caption[2022 PCC Type 2 Afterglow Residuals]{%
-  Type 2 residual as a function of instantaneous luminosity for period 2022F.
+%}
+%\label{fig:period_bound_44}
+%\end{figure}
+
+%\begin{figure}[H]
+%\centering
+%\includegraphics[width=1\textwidth]{ashish_thesis/afterglow_t2res_vsinstlumi_1.png}
+%\caption[2022 PCC Type 2 Afterglow Residuals]{%
+ % Type 2 residual as a function of instantaneous luminosity for period 2022F.
 These are given by the ratio of the luminosity of the second and following empty bunches after a colliding bunch to the luminosity of the colliding bunch.
-}
-\label{fig:period_bound_45}
-\end{figure}
+%}
+%\label{fig:period_bound_45}
+%\end{figure}
 

### 2024-01-27 tesis_Ashish/Chapter7/chapter7.tex
update 27 Jan

@@
   \includegraphics[width=0.5 \columnwidth]{ashish_thesis/tepx_DD.png}
-  \caption[TEPX double disk]{ \onehalfspacing View of one TEPX double-disk in the $r-\phi$ plane; individual pixel modules on two planes (double-disk) and five rings are outlined by yellow rectangles.
+  \caption[X-Y view of TEPX double-disk]{ \onehalfspacing View of one TEPX double-disk in the $r-\phi$ plane; individual pixel modules on two planes (double-disk) and five rings are outlined by yellow rectangles.
 %The planes are separated in z by about 1 cm.
@@
   \includegraphics[width=0.1 \columnwidth]{ashish_thesis/edited_tepx_alllayer_v5.png}
-  \caption[TEPX double disk]{ \onehalfspacing R-Z view of the TEPX double-disk showing the four layers of modules L1, L2, L3 and L4.
+  \caption[R-Z view of TEPX double-disk]{ \onehalfspacing R-Z view of the TEPX double-disk showing the four layers of modules L1, L2, L3 and L4.
 Layer 1 and 3 has Ring 1, 3 and 5 modules, Layer 2 and 4 has Ring 2 and Ring 4 modules.
@@
   \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_2.png}
-  \caption[TEPX Clusters Fit And Residuals]{\onehalfspacing Left: Simulated mean number of clusters for TEPX disks as a function of pileup.
+  \caption[TEPX cluster linear fit per disk]{\onehalfspacing Left: Simulated mean number of clusters for TEPX disks as a function of pileup.
 A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.
@@
   \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_3.png}
-  \caption[TEPX Clusters Fit And Residuals]{\onehalfspacing Left: Simulated mean number of clusters for  TEPX Disk 4 Ring 1 as a function of pileup.
+  \caption[TEPX clusters linear fit]{\onehalfspacing Left: Simulated mean number of clusters for  TEPX Disk 4 Ring 1 as a function of pileup.
 A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.
@@
   \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_1.png}
-  \caption[TEPX two-fold coincidences fit And residuals]{\onehalfspacing Left: Simulated mean number of two-fold coincidences for TEPX disks as a function of pileup.
+  \caption[TEPX two-fold coincidences linear fit per disk]{\onehalfspacing Left: Simulated mean number of two-fold coincidences for TEPX disks as a function of pileup.
 A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.
@@
   \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_4.png}
-  \caption[TEPX two-fold coincidences fit And residuals]{\onehalfspacing Left: Simulated mean number of two-fold coincidences in phi for TEPX Disk 4 Ring 1 as a function of pileup.
+  \caption[TEPX two-fold coincidences linear fit for Disk 4 Ring 1]{\onehalfspacing Left: Simulated mean number of two-fold coincidences in phi for TEPX Disk 4 Ring 1 as a function of pileup.
 A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.

### 2024-01-27 tesis_Ashish/Chapter4/chapter4.tex
update 27 Jan

@@
 \includegraphics[width=0.8\textwidth]{ashish_thesis/afterglow_correction_factor_1lsblock_315690_2.png}
-\caption[Run 315690 Afterglow Background]{%
+\caption[Run 315690 PCC without and with afterglow correction]{%
  Raw and corrected PCC for all bunch crossings.
@@
 \includegraphics[width=0.8\textwidth]{ashish_thesis/afterglow_correction_factor_1lsblock_315690_3.png}
-\caption[Run 315690 Afterglow Background]{%
+\caption[Run 315690 afterglow scale factor]{%
   Afterglow scale factor for one 50 lumi section block in run 315690 for the final module veto.

### 2024-01-29 tesis_Ashish/Abstract/abstract.tex
Updated thesis 4 Jan 2024
update
29 Jan update

@@
 The PCC method is studied for its precision in luminosity measurement using 2017, 2018 and 2022  datasets.
-The results of these studies demonstrate that the PCC luminosity measurement method is stable and linear, able to achieve final uncertainty on the luminosity measurement at the level of 1\% or better.
-Final systematic uncertainty achieved on luminosity measurement for 2018 and 2022 datasets are 1.08\% and 1.5\% respectively.
-%1\% systematic uncertainty on the final luminosity measurement.
+The results of these studies demonstrate that the PCC luminosity measurement method is stable and linear.
+%able to achieve final uncertainty on the luminosity measurement at the level of 1\% or better.
+Final systematic uncertainty achieved on luminosity measurement for 2018 and 2022 datasets are 2.2\% and
+is 1.5\% respectively. %1\% systematic uncertainty on the final luminosity measurement.
 Moreover, the clusters and coincidences counting algorithms and their optimization for the Phase II High Luminosity LHC (HL-LHC) luminosity measurement are also developed, using simulated datasets for the proposed Phase II pixel detector.

### 2024-01-29 tesis_Ashish/Chapter5/chapter5.tex
29 Jan update

@@
 \ref{fig:period_bound_102} in run 361957 to compute type 2 afterglow amplitude and decay width.
-The values obtained for type 2 afterglow amplitude and decay parameters are 0.0007915 and 0.00918 respectively \cite{pas_22}.
+The values obtained for type 2 afterglow amplitude and decay parameters are 0.0008406 and 0.01047 respectively \cite{pas_22}.
 %\cite{bril2023afterglow}.
@@
 
-\newpage
 Table \ref{table:correction_uncertainties} provides a detailed breakdown of the systematic uncertainties associated with the luminosity measurement for the year 2022.
@@
   \centering
-  \caption{Systematic uncertainty in luminosity measurement (\%)}
+  \caption{Systematic uncertainty in luminosity measurement (\%) \cite{pas_22}}
     \begin{tabular}{l|c}
@@
         \hline
-        \textbf{Total} & 1.4 \\
+        \textbf{Total} & 1.5 \\
     \end{tabular}

### 2024-01-29 tesis_Ashish/Chapter8/chapter8.tex
update 27 Jan
29 Jan update

@@
 A total of 155 good pixel modules were selected for the final luminosity measurement.
-Systematic uncertainties were meticulously quantified, including scan to scan (\(0.3\%\)), bunch to bunch (\(0.1\%\)), afterglow (\(0.3\%\)), linearity (\(0.4\%\)), and cross detector stability (\(0.3\%\)).
+%Systematic uncertainties were meticulously quantified, including scan to scan (\(0.3\%\)), bunch to bunch (\(0.1\%\)), afterglow (\(0.3\%\)), linearity (\(0.4\%\)), and cross detector stability (\(0.3\%\)).
 Work is ongoing to complete this measurement.
-The total uncertainty is expected to be order of 1\%.
+The total systematic uncertainty is expected to be order of 2.2\% which is better than LUM PAS 18 results.
+Work is ongoing to complete this measurement and we expect significant improvement in beam-beam systematic uncertainties.
 
-In Chapter 5, significant results from the PCC luminosity measurement during Run 3 (2022) are outlined.
+In Chapter 5, results from the PCC luminosity measurement during Run 3 (2022) are outlined.
 %The chapter reports that the PCC integrated luminosity for 2022 was computed to be \(38.61 \, \text{fb}^{-1}\) .
 Furthermore, a comprehensive analysis of systematic uncertainties in the luminosity measurement for the year 2022 is presented.
-These uncertainties encompass a range of factors including calibration (1.2\%), integration (0.8\%), and other specific sources such as beam current (0.3\%), orbit drift (0.3\%), and cross-detector linearity (0.5\%), culminating in a total uncertainty of \(1.4\%\).
+%These uncertainties encompass a range of factors including calibration (1.2\%), integration (0.8\%), and other specific sources such as beam current (0.3\%), orbit drift (0.3\%), and cross-detector linearity (0.5\%)
+Total systematic uncertainty is \(1.5\%\).
 

### 2024-01-29 tesis_Ashish/Dedication/dedication.tex
Updated thesis 14 Jan 2024
29 Jan update

@@
 \begin{dedication}
-\begin{center}
+  \vspace*{-2cm} % Adjust the -2cm to the amount of space you want to move up
+%\centering
+%\begin{center}
 \section*{Acknowledgement}
-\end{center}
+%\end{center}
 \justify{
@@
 I am indebted to my friends and colleagues, especially Rohit Gupta and Mohammad Balal, for their valuable insights, stimulating discussions, and enduring support.
-Their encouragement, camaraderie,and intellectual exchanges have been instrumental in shaping both my research and personal growth.
+Their encouragement, camaraderie and intellectual exchanges have been instrumental in shaping both my research and personal growth.
 

### 2024-01-29 tesis_Ashish/Portada/Portada.tex
29 Jan update

@@
         \vspace{.4cm}   %% DEFINE EL ESPACIO ENTRE LA DOBLE LINEA Y EL NOMBRE DE LA DIVISIÓN
-        {\scshape \large Divisi\'on de Ciencias Exactas y Naturales}
+        %{\scshape \large Divisi\'on de Ciencias Exactas y Naturales}
         {\scshape Departamento de Investigaci\'on en F\'isica} %% NOMBRE DE LA DIVISIÓN

### 2024-01-29 tesis_Ashish/Chapter5/chapter5.tex
29 Jan update

@@
 A value of  $\chi^2$/ndof close to 1 can be seen in the statistics box which signifies a good fit.
-PCC visible cross section is 1076 $\pm$ 0.9 (stat) mb as shown in Fig.
+PCC visible cross section is 1076 $\pm$ 0.9 (stat) mb.
+The bunch to bunch variation and scan to scan variation of PCC visible cross section is shown in Fig.
+\ref{fig:period_bound_99} and Fig.
 \ref{fig:period_bound_105} \cite{pas_22} %\cite{bril2023vdmrecalibration}.
@@
 \centering
+\includegraphics[width=0.8\textwidth]{ashish_thesis/2022_sigma_vis_btob_variation.png}
+\caption[$\sigma_{vis}$ Bunch Variation]{%                                                                                                                                                        
+  Bunch to bunch variation of PCC visible cross section where the red line is the average value. Red band depicts the $\pm$ one RMS of the values.
+}
+\label{fig:period_bound_99}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
 \includegraphics[width=0.8\textwidth]{ashish_thesis/2022_sigma_vis_per_scan.png}
@@
 
-\newpage
+%\newpage
 \subsection{Afterglow background corrections}
@@
 \centering
-\includegraphics[width=1\textwidth]{ashish_thesis/afterglow_t1res_vsinstlumi_1.png}
+\includegraphics[width=0.9\textwidth]{ashish_thesis/afterglow_t1res_vsinstlumi_1.png}
 \caption[2022 PCC Type 1 Afterglow Residuals]{%
@@
 \centering
-\includegraphics[width=1\textwidth]{ashish_thesis/afterglow_t2res_vsinstlumi_1.png}
+\includegraphics[width=0.9\textwidth]{ashish_thesis/afterglow_t2res_vsinstlumi_1.png}
 \caption[2022 PCC Type 2 Afterglow Residuals]{%
@@
 
-\item Bunch to bunch uncertainty: The "bunch to bunch variation of PCC visible cross section" refer to how much the measured visible cross-section (and thus, the measured luminosity) changes from one bunch crossing to another as shown in Fig.
-\ref{fig:period_bound_99}.
+\item Bunch to bunch uncertainty: The "bunch to bunch variation of PCC visible cross section" refer to how much the measured visible cross-section (and thus, the measured luminosity) changes from one bunch crossing to another.
 Variations could arise from different factors such as varying numbers of protons per bunch, spatial distribution of protons within the bunches, and the specific conditions of the pixel detector at the time of each bunch crossing.
@@
 
-\begin{figure}[!htp]
-\centering
-\includegraphics[width=0.8\textwidth]{ashish_thesis/2022_sigma_vis_btob_variation.png}
-\caption[$\sigma_{vis}$ Bunch Variation]{%                                                                                                                                             
-  Bunch to bunch variation of PCC visible cross section where the red line is the average value. Red band depicts the $\pm$ one RMS of the values.
-}
-\label{fig:period_bound_99}
-\end{figure}
+%\begin{figure}[!htp]
+%\centering
+%\includegraphics[width=0.8\textwidth]{ashish_thesis/2022_sigma_vis_btob_variation.png}
+%\caption[$\sigma_{vis}$ Bunch Variation]{%                                                                                                                                             
+ % Bunch to bunch variation of PCC visible cross section where the red line is the average value. Red band depicts the $\pm$ one RMS of the values.
+%}
+%\label{fig:period_bound_99}
+%\end{figure}
 

### 2024-03-15 tesis_Ashish/Chapter5/chapter5.tex
update 15 Mar 2024

@@
 \centering
-\includegraphics[width=1\textwidth]{ashish_thesis/2022_vdM_fit_1.png}
+\includegraphics[width=1\textwidth]{ashish_thesis/2022_PCC_vdM_fit_new.png}
 \caption[2022 PCC vdM Fit]{%                                                                                                                                              
@@
 \centering
-\includegraphics[width=0.8\textwidth]{ashish_thesis/2022_sigma_vis_per_scan.png}
+\includegraphics[width=0.8\textwidth]{ashish_thesis/2022_PCC_sigmavis_per_scan_new.png}
 \caption[2022 PCC Visible Cross Section]{%
@@
 \centering
-\includegraphics[width=1\textwidth]{ashish_thesis/ProjY_ProfileX_h_ratio_all_2022_1.png}
+\includegraphics[width=1\textwidth]{ashish_thesis/ProjY_ProfileX_h_ratio_all_2022_1_new.png}
 \caption[Projection of Luminosity Ratio Profile]{%
@@
 A perfectly linear relationship would imply same luminosity measured by both the luminometers, suggesting an absence of non-linearity in the detector response.
-The plot on the right in \ref{fig:stabprof2_2000} shows the ratio of luminosity values obtained using the PCC method to those from the HFET luminometer.
+The plot in Fig.
+\ref{fig:stabprof2_2000} shows the ratio of luminosity values obtained using the PCC method to those from the HFET luminometer.
 The values are plotted as a function of HFET luminosity.
@@
   %\begin{subfigure}[b]{0.49\textwidth}
-    \includegraphics[width=0.7\textwidth]{ashish_thesis/PCC_HFOCvsHFOC_ProfileX_all_2022_1.png}
+    \includegraphics[width=0.7\textwidth]{ashish_thesis/PCC_HFOCvsHFOC_ProfileX_all_2022_1_new.png}
     %\caption{Image 2}                                                                                                                                                                           
@@
         Afterglow corrections & 0.2 \\
-        Cross-detector stability & 0.5 \\
+        Cross-detector stability & 0.6 \\
         Cross-detector linearity & 0.5 \\

### 2024-03-23 tesis_Ashish/Chapter1/chapter1.tex
Update 23 Mar

@@
 \end{figure}
+
+\begin{table}[h]
+  \centering
+  \caption[Precision for Run1 and Run2]{Summary of center of mass energy, integrated luminosity, and systematic uncertainty per year during the CMS pPb and PbPb luminosity measurement \cite{CMS-PAS-LUM-13-002} \cite{CMS-PAS-LUM-17-002} \cite{CMS-PAS-LUM-18-001}.}
+\begin{tabular}{c c c c}
+  Year & Center of Mass Energy/nucleon & Systematic Uncertainty \\
+  & (TeV) & (\%) \\
+\hline
+2013 & 2.76 & 3.4(3.6)  \\
+2016 &  5.02  & 3.2(3.7)\\
+2018 & 5.02 & 1.5 \\
+\end{tabular}
+\label{tab:lumi}
+\end{table}

### 2024-03-27 tesis_Ashish/Abstract/abstract.tex
update 27 Mar

@@
 Final systematic uncertainty achieved on luminosity measurement for 2018 and 2022 datasets are 2.2\% and
-is 1.5\% respectively. %1\% systematic uncertainty on the final luminosity measurement.
+ 1.4\% respectively. %1\% systematic uncertainty on the final luminosity measurement.
 Moreover, the clusters and coincidences counting algorithms and their optimization for the Phase II High Luminosity LHC (HL-LHC) luminosity measurement are also developed, using simulated datasets for the proposed Phase II pixel detector.
 %This new pixel detector will replace the Run 2 pixel detector.
-Linearity of the Tracker endcap pixel (TEPX) and Disk 4 Ring 1 luminometers are expected to be within 1\% (offline) up to a pileup of 200 and their statistical precision per second is about 0.1\% at pileup 200.
+Linearity of the Tracker endcap pixel (TEPX) and Disk 4 Ring 1 luminometers is expected to be within 1\% (offline) up to a pileup of 200 and their statistical precision per second is about 0.1\% at pileup 200.
 %It is expected to provide excellent statistical precision and linearity performance, which is essential for precision luminosity measurements at the HL-LHC.

### 2024-03-27 tesis_Ashish/Chapter1/chapter1.tex
update 27 Mar

--- 2024-01-27 tesis_Ashish/Chapter1/chapter1.tex
@@
 
-Collider experiments are a type of particle physics experiment that involve that typically involve high energy collisions of electrons or protons.
+Collider experiments are a type of particle physics experiment that typically involve high energy collisions of electrons or protons.
 %colliding particles, typically protons or electrons, at very high energies.
@@
 Luminosity is a measure of the number of particle collisions that occur per unit area per unit time.
-In particle physics, luminosity is a crucial parameter that determines the rate at which interesting particles may be produced in an collider experiment \cite{Herr:941318}.
+In particle physics, luminosity is a crucial parameter that determines the rate at which interesting particles may be produced in a collider experiment \cite{Herr:941318}.
 
-The luminosity of a collider is given by the following equation:
+The instantaneous luminosity of a collider for head-on collisions is given by the following equation:
 
 \begin{equation}
-L = \frac{N_1 N_2 f}{A} 
+L_{inst} = \frac{N_1 N_2 f}{A} 
 \end{equation}
 
-where $N_1$ and $N_2$ are the number of particles in each beam, f is the frequency of bunch crossings, and A is a parameter that takes into account the overlap between the two beams.
+where $N_1$ and $N_2$ are the number of particles in each beam, $f$ is the frequency of bunch crossings, and $A$ is a parameter that takes into account the overlap between the two beams that is the product of beam size.
 
@@
 The production rate of a given particle is the product of the luminosity and the cross-section of the process.
-Thus, luminosity directly affects the ability to detect rare events and make precise measurements.
+Thus, luminosity directly affects the ability to detect rare events.
 %The more collisions that occur, the higher the probability of rare events happening, such as the creation of new particles or the detection of new phenomena.
@@
 \begin{equation}
-R = L  \sigma,
+R = \sigma \: L_{inst} 
 \end{equation}
@@
 where %R is the production rate,
-L is the luminosity, and $\sigma$ is the cross-section of the process that produces the particle.
+$L_{inst}$ is the instantaneous luminosity, and $\sigma$ is the cross-section of the process that produces the particle.
 The cross-section is a measure of the probability that a given process will occur, and it is typically a very small number, on the order of picobarns ($10^{-36} cm^2$).
@@
 Another technique is to use radio frequency cavities to accelerate the particles to higher energies increasing the frequency of bunch crossings.
-In high-energy particle accelerators, such as the Large Hadron Collider (LHC) at CERN, the luminosity is typically measured in units of inverse femtobarns ($fb^{-1}$), which is a measure of the total number of collisions per unit area during the course of an experiment.
+In high-energy particle accelerators, such as the Large Hadron Collider (LHC) at CERN, the integrated luminosity is typically measured in units of inverse femtobarns ($fb^{-1}$), which is a measure of the total number of collisions per unit area during the course of an experiment.
 %For example, the LHC has a design luminosity of $10^{34} cm^{-2}s^{-1}$, which means that there are $10^{34}$ proton-proton collisions per square centimeter area per second.
@@
 In addition to discoveries, high luminosity experiments are also important for precision measurements.
-For example, the measurement of the properties of the top quark, the heaviest known elementary particle, requires a large number of collisions to be able to distinguish the signal from the background noise.
+For example, the precise measurement of the properties of the top quark, the heaviest known elementary particle, benefits significantly from the large number of collisions at the LHC.
+These collisions provide a robust dataset that reduces the uncertainty in the top quark mass measurement, allowing for more precise determination than were possible at the Tevatron.
+%For example, the measurement of the properties of the top quark, the heaviest known elementary particle, requires a large number of collisions to be able to distinguish the signal from the background noise.
 
@@
 %including searches for new particles and measurements of the properties of known particles.
-It is a dominant factor in the measurement of Higgs Boson cross sections and couplings to other gauge bosons and fermions, as shown in Fig~\ref{fig:lum_unc}.
+It is a dominant factor in the measurement of Higgs Boson cross sections and couplings to other gauge bosons and fermions projected for High luminosity (HL)-LHC era, as shown in Fig~\ref{fig:lum_unc}.
 As such, the uncertainty in cross-section and coupling measurements cannot be better than the uncertainty in luminosity measurement.
@@
    Higgs boson production processes cross section projected uncertainty.
-In the most precisely measured Higgs boson production process, gluon fusion (ggH), luminosity uncertainty will dominate other experimental systematic uncertainty at the High Luminosity (HL)-LHC \cite{Dainese:2703572}.
+In the most precisely measured Higgs boson production process, gluon fusion (ggH), luminosity uncertainty will dominate other experimental systematic uncertainty at the HL-LHC \cite{Dainese:2703572}.
 }
@@
 
-\section{Large Hadron Collider (LHC) and the CMS Experiment}
+\section{Large Hadron Collider and the CMS Experiment}
 
 The CERN accelerator complex consists of a series of accelerators that work together to produce beams of particles at ever-increasing energies.
-These beams are then fed into the LHC for further acceleration and collision.
+These beams are then fed into the Large Hadron Collider (LHC) for further acceleration and collision.
 The first step in the accelerator complex is the Linac 2, a linear accelerator that produces beams of protons with an energy of 50 MeV (mega-electronvolts).
@@
 
-LHC consists of a 27-kilometer ring of superconducting magnets, which guide two counter-rotating beams of protons to collide at four different locations around the ring, where four major experiments, ATLAS, the Compact Muon Solenoid (CMS) experiment, ALICE and LHCb are located as shown in Fig.~\ref{fig:lhc}.
+The LHC consists of a 27-kilometer ring of superconducting magnets, which guide two counter-rotating beams of protons to collide at four different locations around the ring, where four major experiments, ATLAS, the Compact Muon Solenoid (CMS) experiment, ALICE and LHCb are located as shown in Fig.~\ref{fig:lhc}.
 The protons are organized into "bunches," with each bunch containing around 100 billion protons.
@@
 \caption[CERN Accelerator Complex]{%
-    CERN accelerator complex consists of Linac 2, Proton Synchrotron Booster (PSB), Proton Synchrotron (PS), Super Proton Synchrotron (SPS) and Large Hadron Collider (LHC).
+    CERN accelerator complex consists of Linac 2, Proton Synchrotron Booster (PSB), Proton Synchrotron (PS), Super Proton Synchrotron (SPS) and Large Hadron Collider (LHC) which is the accelerator chain for proton physics at the LHC.
 LHC ring showing four interaction points where the ALICE, ATLAS, LHCb and CMS detectors are stationed \cite{lhc_complex}.
@@
 
-The CMS experiment is a multi-purpose particle detector that is designed to detect and study the particles produced in the collisions at the LHC.
+The CMS experiment \cite{CMS:2008xjf} is a multi-purpose particle detector that is designed to detect and study the particles produced in the collisions at the LHC.
 The CMS detector is a complex instrument that consists of several layers of sub-detectors, each designed to detect different types of particles and measure different properties of the particles.
-The CMS detector consists of a tracker, an electromagnetic calorimeter, hadron calorimeter and muon detector.
+The CMS detector consists of a tracker, an electromagnetic calorimeter, hadron calorimeter, and a muon detector.
 
@@
 
-\item The tracker is a cylindrical detector made up of two main subsystems: the pixel detector and the silicon strip detector.
+\item The tracker is a cylindrical detector made up of two main subsystems: the pixel detector and the silicon strip detector \cite{CMS:2021ime}.
 The pixel detector, the innermost subsystem near the interaction point, is crucial for precise track reconstruction and vertex identification.
@@
 When charged particles pass through the sensor, they create electron-hole pairs that induce a current, which is amplified, shaped, and digitized.
-The upgraded pixel detector used in Run2 contained over 120 million pixels, ensuring high granularity and hit efficiency.
-The pixel detector has a 4.8 $\mu$m  and 7.99 $\mu$m  spatial resolution along 100 $\mu$m and 150 $\mu$m pixel pitch respectively.
+The upgraded pixel detector used in Run 2 contained over 120 million pixels, ensuring high granularity and hit efficiency.
+The pixel detector has a 4.8 $\mu$m  and 7.99 $\mu$m  spatial resolution along 100 $\mu$m and 150 $\mu$m pixel pitch respectively \cite{Dragicevic:2262932}.
 The silicon strip detector surrounding the pixel detector provides extra tracking points for improved track reconstruction.
@@
 When photons or electrons hit the crystals, they generate a secondary particle shower, producing scintillation light proportional to the energy of the incoming particle.
-By assessing this light in each crystal, the ECAL can precisely determine the energy of the incoming particle.
+By assessing this light in each crystal using avalanche photodiodes and vacuum phototriodes \cite{Hobson:2008zz}, the ECAL can precisely determine the energy of the incoming particle.
 The ECAL covers a pseudorapidity range $|\eta| < 3.0$ \footnote{The pseudorapidity $\eta$ is calculated as $\eta = - \ln(\tan(\frac{\theta}{2}))$ and ranges from $-\infty$ to $+\infty$.}, facilitating measurement of particles at various angles to the beam axis.
@@
 
-\item The Hadron Calorimeter (HCAL) in the CMS detector, positioned outside of the Electromagnetic Calorimeter (ECAL), measures the energy of hadrons—particles comprised of quarks bound by the strong nuclear force.
-Since hadrons are abundantly produced in high-energy LHC collisions, the HCAL's design focuses on absorbing their energy for measurement.
-It is composed of alternating layers of brass, for energy absorption, and plastic scintillator, for light emission when particles pass through.
+\item The Hadron Calorimeter (HCAL) \cite{Isik:2810162} in the CMS detector, positioned outside of the Electromagnetic Calorimeter (ECAL), measures the energy of hadrons—particles comprised of quarks bound by the strong nuclear force.
+Since hadrons are abundantly produced in high-energy LHC collisions, the HCAL design focuses on absorbing their energy for measurement.
+It is composed of alternating layers of brass, for energy absorption, and plastic scintillator, for light emission when particles pass through for the barrel and endcap calorimeters.
+HF uses quartz fibers and steel as active and passive components, respectively.
 Photodetectors convert this light into a measurable electrical signal.
@@
 
-\item The Muon Chambers are a vital part of the CMS detector.
+\item The Muon Chambers \cite{CMS:2018rym} are a vital part of the CMS detector.
 Designed to detect a variety of particles from high-energy collisions, the CMS is particularly equipped for detecting muons, highly penetrative charged particles that often evade other detection methods.
@@
 
-During the operation of the CMS experiment, two main data-taking periods were conducted: Run 1, which spanned from 2010 to 2013, and Run 2, which took place from 2015 to 2018.
+%During the operation of the CMS experiment, two main data-taking periods were conducted: Run 1, which spanned from 2010 to 2013, and Run 2, which took place from 2015 to 2018.
+Since the beginning of the operation of the CMS experiment, three main data-taking periods have taken place: Run 1, Run 2, and Run 3, with the latter starting in 2022 and currently ongoing.
 During these periods, the CMS experiment measured the instantaneous and integrated luminosity of the proton-proton collisions produced by the LHC where the integrated luminosity for each year is shown in Fig.~\ref{fig:lumi}.
@@
 \ref{tab:lumi}.
+Luminosity systematic uncertaintities for heavy ion runs is shown in Table \ref{tab:lumi40}.
 
@@
   \centering
-  \caption[Integrated luminosity and its precision for Run1 and Run2]{Summary of center of mass energy, integrated luminosity, and systematic uncertainty per year during the CMS luminosity measurement.}
+  \caption[Integrated luminosity and its precision for Run1 and Run2]{Summary of center of mass energy, integrated luminosity, and systematic uncertainty per year in CMS.}
 \begin{tabular}{c c c c}
@@
 \end{figure}
+
+\begin{table}[h]
+  \centering
+  \caption[Precision for Run1 and Run2]{Summary of center of mass energy, integrated luminosity, and systematic uncertainty per year during the CMS pPb and PbPb luminosity measurement \cite{CMS-PAS-LUM-13-002, CMS-PAS-LUM-17-002, CMS-PAS-LUM-18-001}.}
+\begin{tabular}{c c c c}
+  Year & Center of Mass Energy/nucleon & Systematic Uncertainty \\
+  & (TeV) & (\%) \\
+\hline
+2013 & 2.76 & 3.4(3.6)  \\
+2016 &  5.02  & 3.2(3.7)\\
+2018 & 5.02 & 1.5 \\
+\end{tabular}
+\label{tab:lumi40}
+\end{table}

### 2024-03-27 tesis_Ashish/Chapter2/chapter2.tex
update 27 Mar

@@
-\chapter{Luminosity measurement at CMS experiment}  %Title of the First Chapter
+\chapter{Luminosity measurement at the CMS experiment}  %Title of the First Chapter
 
@@
 This holistic approach to luminosity measurement significantly improves the robustness and reliability of the data collected.
-In the central region, the Muon Drift Tubes (DT) luminometer is used covering a $\eta$ range from 0 to 1.2.
+In the central region, the Muon Drift Tubes (DT) luminometer is used covering a $|\eta|$ range from 0 to 1.2.
 The Pixel Cluster Counting (PCC) luminometer also operates in this region and extends into the forward region covering a range from 0 to 2.5.
@@
 The Fast Beam Condition Monitor (BCM1F) functions in a range from 3.1 to 4.7.
+The Hadron forward (HF) luminometer caters to the most forward region of the CMS detector \cite{Sirunyan:2759951}, functioning in the pseudorapidity range from 2.9 to 5.2 as shown in Fig.~\ref{fig:lumino_cms_pseudo}.
 The Radiation Monitoring System for Environment and Safety (RAMSES) are located directly behind HF.
-The Hadron forward (HF) luminometer caters to the most forward region of the CMS detector \cite{Sirunyan:2759951}, functioning in the pseudorapidity range from 2.9 to 5.2 as shown in Fig.~\ref{fig:lumino_cms_pseudo}.
 
@@
 
-\item Pixel Luminosity Telescope (PLT) : PLT is positioned 1.75 meters away from the interaction point, the PLT is an ensemble of 16 "telescopes." These are symmetrically distributed around the beam pipe at both extremities of the detector, with each telescope being composed of three individual silicon sensor planes.
-A defining feature of the PLT's functionality is the measurement of per-bunch instantaneous luminosity.
+\item Pixel Luminosity Telescope (PLT) : PLT is positioned 1.75 meters away from the interaction point.
+The PLT is an ensemble of 16 "telescopes".
+These are symmetrically distributed around the beam pipe at both sides of the detector, with each telescope being composed of three individual silicon sensor planes.
+A defining feature of the PLT functionality is the measurement of per-bunch instantaneous luminosity.
 This is accomplished by enumerating events in which all three sensor planes in a given telescope simultaneously register a hit.
-A specialized readout mechanism operating at the LHC's full bunch-crossing frequency of 40 MHz is employed to carry out this task.
+A specialized readout mechanism operating at the LHC full bunch-crossing frequency of 40 MHz is employed to carry out this task.
 The PLT has provisions for reading out full pixel data, albeit at lower frequencies.
@@
 The integrated signal is then converted into a measure of the instantaneous luminosity, which is proportional to the product of the number of charged particles per bunch and the collision frequency.
+Run3 FBCM employs silicon-pad sensors located inside the cold volume of the Tracker, leveraging the zero-counting algorithm for luminosity measurement and also offering timing information with a few nanoseconds precision for beam-induced background measurement.
 
@@
 As these secondary particles pass through the scintillating fibers, they produce light, which is collected by photodetectors and converted into an electrical signal proportional to the particle's energy.
-Two separate algorithm are used for luminosity measurement in the HF Calorimeter, HFOC and HFET based on the Zero Counting (ZC) method and the sum of transverse energy methods respectively.
+Two separate algorithms are used for luminosity measurement in the HF Calorimeter, HFOC and HFET based on the Zero Counting (ZC) method and the sum of transverse energy methods respectively.
 %\cite{CMS-PAS-LUM-15-001}.
@@
 The basic idea behind the zero counting method is that the probability of having zero particles detected in a given region of the detector is proportional to the Poisson probability of having no collisions in that region.
-This probability can be related to the luminosity of the collisions through the following equation:
+This probability can be related to the instantaneous luminosity of the collisions through the following equations,
+
+We consider the Poisson distribution, which gives the probability of observing a certain number of events, $n$, when the average number of events is $\lambda$:
+
+\[
+P(n; \lambda) = \frac{e^{-\lambda} \lambda^n}{n!}
+\]
+
+For zero-counting, we are interested in the probability of observing no events ($n=0$). Substituting $n=0$ into the Poisson distribution equation, we get:
+
+\[
+P(0; \lambda) = \frac{e^{-\lambda} \lambda^0}{0!} = e^{-\lambda}
+\]
+
+The probability of observing zero events, $P(0; \lambda)$, is related to the average number of events $\lambda$, which can be determined by taking the negative natural logarithm of $P(0; \lambda)$:
+
+\[
+\lambda = -\ln(P(0; \lambda))
+\]
+
+The average number of events per bunch crossing, $\lambda$, is related to the instantaneous luminosity, $L_{inst}$, and the total visible cross-section, $\sigma_{\text{vis}}$, by:
+
+\[
+\lambda = L_{inst} \cdot \sigma_{\text{vis}}
+\]
+
+Substituting $\lambda$ in terms of $L$ and $\sigma_{\text{vis}}$ into the equation involving $P(0; \lambda)$, we get:
+
+\[
+L_{inst} \cdot \sigma_{\text{vis}} = -\ln(P(0; \lambda))
+\]
+
+Solving for $L_{inst}$ gives us the equation for instantaneous luminosity based on the zero-counting method:
+
+\[
+L_{inst} = \frac{-\ln(P(0; \lambda))}{\sigma_{\text{vis}}}
+\]
+
+The probability $P(0; \lambda)$ can be written as the ratio $\frac{N}{N_0}$ because it is the fraction of the total number of events where zero particles are detected:
+\[
+P(0; \lambda) = \frac{N}{N_0}
+\]
+
+Substituting $P(0; \lambda) = \frac{N}{N_0}$ into the equation for $L_{inst}$ gives us:
 
 \begin{equation}
-L = \frac{-ln(N/N_0)}{\sigma_{vis}}
+L_{inst} = \frac{-ln(N/N_0)}{\sigma_{vis}}
 \end{equation}
 
-where L is the luminosity, N is the number of events with zero particles detected in the region of interest, $N_0$ is the total number of events, $\sigma_{vis}$ is the visible cross-section.
+where $L_{inst}$ is the luminosity, N is the number of events with zero particles detected in the region of interest, $N_0$ is the total number of events, $\sigma_{vis}$ is the visible cross-section.
 One advantage is that it is a simple and robust method that does not require sophisticated detectors or calibration procedures.
@@
 
-\item Muon drift tubes: The DT system is part of the CMS muon system, %which also includes the Resistive Plate Chambers (RPCs) and the Cathode Strip Chambers (CSCs).
-  Drift Tubes (DTs) in the CMS experiment are designed to accurately measure the trajectory and momentum of muons produced in proton-proton collisions at the LHC.
+\item Muon drift tubes: The DT system is part of the CMS muon system. %which also includes the Resistive Plate Chambers (RPCs) and the Cathode Strip Chambers (CSCs).
+  DTs in the CMS experiment are designed to accurately measure the trajectory and momentum of muons produced in proton-proton collisions at the LHC.
   %The DT system is located in the barrel region of the CMS detector, covering the pseudorapidity range of $|\eta| < 1.2$.
-  The DT system consist of rectangular drift cells filled with a gas mixture, typically of argon and carbon dioxide.
-The use of DT muon rates for luminosity measurement is based on the idea that the rate of single muon production is proportional to the instantaneous luminosity.
-Single muons comes from decay of inclusive, Z, W, top and jets.
+  The DT system consists of rectangular drift cells filled with a gas mixture, typically of argon and carbon dioxide.
+The use of DT muon rates for luminosity measurement is based on the idea that the rate of muon production is proportional to the instantaneous luminosity.
+Muons come from the decay of inclusive, Z, W, top and jets.
 %The DT system in the CMS detector is used for muon detection and precise position measurement.
@@
 \caption[CMS luminometers Location]{%
-    Cross section of the CMS detector in the r-z plane showing all Run 2 luminometer PLT, BCM1F, DTs, and HF location.
+    Cross section of the CMS detector in the r-z plane showing all Run 2 luminometers PLT, BCM1F, DTs, and HF location.
 The two RAMSES monitors used as a luminometer in Run 2 are located directly behind HF \cite{Sirunyan:2759951}.
@@
 The pixel detector is one of the subdetectors of the CMS experiment that is closest to the interaction point where the proton beams collide.
-It consists of four barrel layers (L1-L4) at radii of 29, 68, 109 and 160 mm and three forward disks (D1-D3) on each end at distances of 291, 396, and 516 mm of pixel sensors from the center of the detector as shown in Fig.~\ref{fig:phaseI_upgrade}.
-It is built from 1856 silicon sensor modules, 1184 modules in the barrel layers (BPIX) and 672 modules for the forward disks (FPIX) \cite{Adam:2748381}.
+It consists of four barrel layers (L1-L4) at radii of 29, 68, 109 and 160 mm and three forward disks (D1-D3) on each end at distances of 291, 396, and 516 mm from the center of the detector as shown in Fig.~\ref{fig:phaseI_upgrade}.
+It is built from 1856 silicon sensor modules, 1184 modules in the barrel layers (BPIX) and 672 modules in the forward disks (FPIX) \cite{Adam:2748381}.
 Modules for barrel layers and forward disks are shown in Fig.~\ref{fig:pixelmodule}.
@@
 The FPIX modules are also designed to handle high particle densities and radiation levels.
-Each module in the FPIX consists of a matrix of 16128 pixels, arranged in 160 rows and 101 columns with same pixel size as layer pixels.
+Each module in the FPIX consists of a matrix of 16128 pixels, arranged in 160 rows and 101 columns with same pixel size as barrel layer pixels.
 %It provide high-precision position measurements of the charged particles produced in the collisions.
@@
 The pixel detector is capable of detecting charged particles with a wide range of energies, from a few hundred MeV to several TeV.
-The pixel detector is able to operate at very high particle fluxes, with a hit rate of up to $100 MHz/cm^2$.
+The pixel detector is able to operate at very high particle fluxes, with a hit rate of up to $100 \: MHz/cm^2$.
 To achieve this high rate capability, the pixel detector uses fast readout electronics.
@@
 
-\section{Pixel cluster counting (PCC) method}
+\section{Pixel cluster counting method}
 
-The Pixel Cluster Counting (PCC) method is one of the main luminosity measurement technique used at the CMS experiment.
+The Pixel Cluster Counting (PCC) method is one of the main luminosity measurement techniques used at the CMS experiment.
 The PCC method is based on counting the number of pixel clusters produced by the collisions in the CMS pixel detector, which is a high-resolution silicon detector located close to the collision point.
@@
 %The offline luminosity measurement is also used to determine the absolute luminosity scale, which is obtained from beam parameters.
-There are several steps involved in the PCC method for measuring luminosity like data acquisition, pixel cluster reconstruction, pixel cluster counting as described below.
+There are several steps involved in the PCC method for measuring luminosity like data acquisition, pixel cluster reconstruction and pixel cluster counting as described below.
 
@@
 
-\item The number of pixel clusters is counted over a fixed time intervals, known as lumi section.
+\item The number of pixel clusters is counted over a fixed time interval, known as lumi section.
 One lumi section is 23.36 seconds time interval.
 In the pixel cluster counting process, events of interest are selected from the large dataset obtained from the CMS experiment.
-This is typically done using zero bias triggers that randomly select events that are coming from filled bunch crossing.
+This is typically done using zero bias triggers that randomly select events that are coming from filled bunch crossings.
   %Once the events of interest have been selected, reconstruction the pixel clusters in each event is done using the steps described in the previous bullet point.
@@
 
-\item The number of pixel clusters is used to calculate the luminosity using the following formula:
+\item The number of pixel clusters is used to calculate the instantaneous luminosity using the following formula:
 
 \begin{equation}
- L_b = \frac{N_{cl} f_{rev} } {\sigma_{vis}}   
+ L_{inst} = \frac{N_{cl} f_{rev} } {\sigma_{vis}}   
 \end{equation}
 
-where $L_b$ is the bunch luminosity, $N_{cl}$ is the number of clusters per bunch crossing, $f_{rev}$ is the revolution frequency of the LHC, and $\sigma_{vis}$ is the visible cross section of the pixel detector obtained from calibration.
+where $L_{inst}$ is the bunch luminosity, $N_{cl}$ is the number of clusters per bunch crossing, $f_{rev}$ is the revolution frequency of the LHC, and $\sigma_{vis}$ is the visible cross section of the pixel detector obtained from calibration.
 
@@
 The PCC of various layers and disks, normalized to the total PCC, as a function of lumi section can provide crucial insights into the detector's performance and stability over time and under different conditions \cite{CMS-PAS-LUM-16-001}.
-A lumi section is a unit of data-taking time in the LHC, typically lasting about 23.36 seconds, during which the beam conditions are assumed to be stable.
+A lumi section is a unit of data-taking time in the LHC during which the beam conditions are assumed to be stable.
 The luminosity delivered during each of these lumi sections can vary, leading to different levels of activity in the detector.
@@
 
-The PCC method has been extensively tested and validated by the CMS during the LHC Run 1 and Run 2, which corresponded to proton-proton collisions at center-of-mass energies of 7-8 TeV and 13 TeV, respectively.
-The PCC method has achieved a relative luminosity precision of about 1.5 \%, which is well within the design goals of the CMS \cite{pas_18}.
-In the future, the PCC method willcontinue to be a key component of the CMS luminosity measurement strategy, as it provides a precise and robust measurement of the luminosity ratio between different datasets and periods.
-The P\
-CC method will also benefit from the upgrades and improvements planned for the CMS pixel detector and the LHC, which will increase the luminosity and the collision rate, and will challenge the performance and the calibration of the PCC method.
-The CMS is planning to install a new pixel detector for the High-Luminosity LHC (HL-LHC) era, which will feature smaller pixel sizes, faster readout electronics, and radiation-hard materials.
+The PCC method has been extensively tested and validated by CMS during the LHC Run 1 and Run 2, which corresponded to proton-proton collisions at center-of-mass energies of 7-8 TeV and 13 TeV, respectively.
+The PCC method has achieved a relative luminosity precision of about 1.5 \%, which is well within the design goals of CMS \cite{pas_18}.
+In the future, the PCC method will continue to be a key component of the CMS luminosity measurement strategy, as it provides a precise and robust measurement of the luminosity ratio between different datasets and periods.
+The PCC method will also benefit from the upgrades and improvements planned for the CMS pixel detector and the LHC, which will increase the luminosity and the collision rate, and will challenge the performance and the calibration of the PCC method.
+CMS is planning to install a new pixel detector as extensively discussed in Chapter \ref{TEPX luminometer for HL-LHC} for the High-Luminosity LHC (HL-LHC) era, which will feature smaller pixel sizes, faster readout electronics, and radiation-hard materials.
 The CMS is also planning to develop new techniques and algorithms for the PCC method, such as machine learning methods, deep neural networks, and real-time analysis tools.

### 2024-03-27 tesis_Ashish/Chapter5/chapter5.tex
update 27 Mar

@@
   \centering
-  \caption{Systematic uncertainty in luminosity measurement (\%) \cite{pas_22}}
+  \caption[Systematic uncertainty in 2022 luminosity measurement]{Systematic uncertainty in 2022 luminosity measurement (\%) \cite{pas_22}}
     \begin{tabular}{l|c}
@@
         \hline
-        Beam current & 0.3 \\
-        Orbit drift & 0.3 \\
-        Residual beam positions & 0.4 \\
+        Beam current & 0.2 \\
+        Ghost and satellite charges & 0.2 \\
+        Orbit drift & 0.1 \\
+        Residual beam positions & 0.3 \\
         Beam-beam effects & 0.4 \\
@@
         \hline
-        Calibration & 1.3 \\
+        Calibration & 1.2 \\
         Integration & 0.8 \\
         \hline
-        \textbf{Total} & 1.5 \\
+        \textbf{Total} & 1.4 \\
     \end{tabular}

### 2024-03-27 tesis_Ashish/Chapter3/chapter3.tex
update 27 Jan 2024
Update 23 Mar
update 27 Mar

@@
 It involves scanning the beams across each other in the horizontal and vertical planes to measure the beam overlap integral, which is proportional to the luminosity.
-The first step in the vdM calibration is to scan the colliding beams across each other.
-This is done by displacing the beams in the horizontal (x) and vertical (y) planes independently while keeping the other direction fixed as shown in left part of Fig.
+%The first step in the vdM calibration is to scan the colliding beams across each other.
+This is done by displacing the beams in the horizontal (x) and vertical (y) planes independently while keeping the other direction fixed as shown in the left part of Fig.
 \ref{fig:vdm_scan_method}.
 The scans are performed at several different positions along the collision point, creating a series of data points for each plane.
-The data points collected during the scans are then fitted with  suitable function like single, double gaussian as shown in right part of Fig.
+The data points collected during the scans are then fitted with  suitable function like single, double gaussian as shown in the right part of Fig.
 \ref{fig:vdm_scan_method}  to determine the beam overlap integrals in the x and y directions.
@@
 The event rate is proportional to the luminosity and is given by the product of the cross-section ($\sigma$) and luminosity.
-The total beam overlap is the product of beam overlap width in the horizontal and vertical planes over the entire interaction region \cite{vanderMeer1968}.
-It is an essential parameter in determining the absolute luminosity to calculate visible cross section.
+The total beam overlap is the product of the beam overlap width in the horizontal and vertical planes over the entire interaction region \cite{vanderMeer1968}.
+The total beam overlap is an essential parameter in determining the visible cross section to calculate absolute luminosity.
 
@@
     \centering
-    \includegraphics[width=1\textwidth]{ashish_thesis/vdm_method.png}
+    \includegraphics[width=1\textwidth]{ashish_thesis/vdm_method_new.png}
     \caption[vdM Scan Schematic]{Left: Scanning the beams across each other (±3$\sigma$) in the transverse plane, horizontal (x-scan) and vertical (y-scan) directions.
@@
 
-\section{van der Meer (vdM) method}
+\section{vdM method}
 
-In the van der Meer (vdM) scans,  rate is plotted as a function of beam separation along x and y directions that is used to determine the visible cross section $\sigma_{vis}$.
+In the vdM scans, rate is plotted as a function of beam separation along x and y directions that is used to determine the visible cross section $\sigma_{vis}$.
 %of the pixel detector which is a calibration constant in the relation between rate of a quantity (clusters, coincidences) read out by the detector and the instantaneous luminosity.
@@
 
-The vdM scan determines the bunch  overlap integrals $\int \rho_{1x} (x) \rho_{2x} (x) dx$ and  $\int \rho_{1y}(y) \rho_{2y} (y) dy$ by measuring pixel clusters rate as a function of beam separation $\Delta x$ and $\Delta y$ along x and y directions.
+The vdM scan determines the bunch  overlap integrals $\int \rho_{1x} (x) \rho_{2x} (x) dx$ and  $\int \rho_{1y}(y) \rho_{2y} (y) dy$ by measuring pixel-cluster rate as a function of beam separation $\Delta x$ and $\Delta y$ along x and y directions.
 
@@
 
-The poly2G model, or the "Gaussian function with a polynomial term" model, is a fitting function that combines a second-order polynomial function and a Gaussian function.
+The Poly2G model, or the "Gaussian function with a polynomial term" model, is a fitting function that combines a second-order polynomial function and a Gaussian function.
 It is a versatile and flexible model that can be used to fit various types of data, including the PCC data in the context of the vdM calibration.
@@
 
-To determine the beam overlap $\Sigma$ in this model, we calculate the area under the Poly2G curve between $-\infty$ and  +$\infty$ and divide by its peak value. We integrate the poly2G function
+To determine the beam overlap $\Sigma$ in this model, we calculate the area under the Poly2G curve between $-\infty$ and  +$\infty$ and divide by its peak value. We integrate the Poly2G function
 %\[
@@
 \begin{equation}
-z = \frac{x - \mu}{\frac{\sigma}{1 + r_2}} ,   dx = \frac{\sigma}{1 + r_2} dz 
+z = \frac{x - \mu}{\frac{\sigma}{1 + r_2}} ,  \:  dx = \frac{\sigma}{1 + r_2} dz 
 \end{equation}
@@
 
-Beam overlap width for Poly2G fit function is
+Following the definition presented in equations (3.5) and (3.6), the beam overlap width for the Poly2G fit function is:
+
 \begin{equation}

### 2024-03-27 tesis_Ashish/Chapter4/chapter4.tex
29 Jan update
update 27 Mar

@@
 On the other hand, the Zero-Bias dataset encapsulates events that have passed the trigger system with no bias which means the colliding bunches are randomly triggered without the use of any CMS detector signal.
-The list of colliding bunches is detected by an independent system Beam Pick-up Timing system (BPTX) for Experiments.
+The list of colliding bunches is detected by an independent system Beam Pick-up Timing for eXperiments (BPTX).
 CMS software (CMSSW) version $10{\_}2{\_}2$ is used for reprocessing random trigger PCC dataset and $10{\_}6{\_}30$  \cite{CMSReleaseNotes} is used for reprocessing zero bias PCC datasets.
@@
 
-\item Improved Algorithms or Calibration: As experiments progress, there can be improvements in algorithms or calibration techniques used to process the raw data.
+\item Improved algorithms or calibration: As experiments progress, there can be improvements in algorithms or calibration techniques used to process the raw data.
 This can lead to a more accurate or efficient representation of the collected data.
 
-\item Changes in Detector Conditions: Detector conditions might change over time due to factors like aging or upgrades. These changes can affect the interpretation of the data.
-
-\item Discovery of Issues or Errors: Sometimes, errors or issues in the original data processing might be discovered.
+\item Changes in detector conditions: Detector conditions might change over time due to factors like aging or upgrades. These changes can affect the interpretation of the data.
+
+\item Discovery of issues or errors: Sometimes, errors or issues in the original data processing might be discovered.
 
@@
 
-\item A loose selection of 7\% based on RMS/mean of module weight profile is applied where mean and RMS values are obtained from y projection of module weight profile.
+\item A loose selection of 7\% based on RMS/mean of module weight profile is applied where mean and RMS values are obtained from the projection of module weight profile.
 Modules with significantly large RMS/mean are removed with this loose selection as shown in Fig.
@@
 The calibration of luminosity measurement by the CMS experiment luminometers in the 2018 proton-proton data taking at $\sqrt{s}$ = 13 TeV \cite{pas_18} was performed during LHC fill 6868 on June 30 and July 1, 2018 at $\sqrt{s}$ = 13 TeV.
-Zero-bias triggers on 5 bunch pairs (BCIDs 265, 865, 1780, 2192, and 3380) recorded events rate is 27.7 kHz.
+Zero-bias triggers on 5 bunch pairs (BCIDs 265, 865, 1780, 2192, and 3380) recorded events at a rate of 27.7 kHz.
 Trigger is applied on five colliding bunches due to limitation of the recording bandwidth.
@@
 The first segment involved six x-y scan pairs.
-Two were short ``emittance'' scans, named ``emit1'' and ``emit2,'' where the beams were separated by \(4\sigma_b\) over 9 steps with a 10-second integration time at each step.
+Two were short ``emittance'' scans, named ``emit1'' and ``emit2,'' where the beams were separated by \(4\sigma_b\) (beam size) over 9 steps with a 10-second integration time at each step.
 A standard vdM scan (described in section 3.1), named ``vdM1,'' separated the beams by \(6\sigma_b \approx 600\)~$\mu$m in 25 steps, with a 30-second duration per step.
@@
 vdM scans are typically conducted at least once a year to ensure the luminometer is correctly calibrated.
-Results of these scans that is the visible cross section is used to normalize the data collected by the experiments during physics run.
+The outcomes of these vdM scans, particularly the visible cross-section values, serve as a benchmark to adjust and standardize the data collected during the physics runs.
+
+%Results of these scans that is the visible cross section is used to normalize the data collected by the experiments during physics run.
 
@@
     \caption[2018 vdM Program]{Beam position along x and y is plotted as a function of time showing different types of scans.
-#3 and #10 are vdM scans, #4 and #9 are offset scans, #5, #7 and #8 are beam imaging scans, #6 is emittance scan.}
+#3 and #10 are vdM scans, #4 and #9 are offset scans, #5, #7 and #8 are beam imaging scans, #6 is emittance scan \cite{pas_18}.}
     \label{fig:vdm_prog_2018}
@@
 The background estimation for the PCC rate is done with two super-separation scans SS1 and SS2.
-The mean and error are obtained from the $y$ projection of PCC per NB4 plotted as a function of time as shown in Fig.
+The mean and error are obtained from the $y$ projection of PCC rates per NB4 plotted as a function of time as shown in Fig.
 \ref{fig:sigmavis_ss_backg}.
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/SS1_SS2_bkg_pcc_1.png}
-\caption[Background estimation]{2D histogram filled with the Avg. PCC evaluated per NB4, during head-on collisions (high part) and during the Super-Separation window (low part).}
+\caption[Background estimation]{2D histogram filled with the Avg. PCC rate evaluated per NB4, during head-on collisions (high part) and during the Super-Separation window (low part).}
 \label{fig:sigmavis_ss_backg}
@@
        3380  &  0.02882  &    0.02896   \\
+       Average & 0.02789 & 0.02726  \\
       \end{tabular}
@@
 \ref{fig:sigmaperscan}.
-The $\sigma_{vis}$ value obtained by averaging all scans is for final module veto list is 960.54 $\pm$ 0.85(stat.) mb.
+The $\sigma_{vis}$ value obtained by averaging all scans for the final module veto list is 960.54 $\pm$ 0.85(stat.) mb.
 
@@
 
-PCC visible cross section for various bunch crossing across different scans is shown in Fig.
+The PCC visible cross section for various bunch crossing across different scans is shown in Fig.
 \ref{fig:sigmavis_btob_variation}.
@@
 The reason for the decrease in luminosity over time is the reduction in the number of protons in the beams due to collisions.
-As the protons in the beams collide, the number of protons, and hence the luminosity, diminishes.
+%As the protons in the beams collide, the number of protons, and hence the luminosity, diminishes.
 The rate of this decrease can be influenced by various factors, including beam dynamics, losses, and the efficiency of the collider's operation.
@@
 Type 2 Afterglow (Activation-Induced Background): This noise is a consequence of the gradually diminishing activation of the detector.
-It occurs when the detector material encounters high-energy particles, leading to the creation and decay of radioactive isotopes \cite{CMS-PAS-SMP-12-008} %(as depicted in Fig.
+It occurs when the detector material encounters high-energy particles, leading to the creation and decay of radioactive isotopes \cite{CMS-PAS-SMP-12-008}.
+%(as depicted in Fig.
 \ref{fig:pcc_afterglow}).
@@
 
-In the afterglow correction process, following steps are involved.
+In the afterglow correction process, the following steps are involved,
 
@@
 A fit is performed to one wagon train, then two, and finally three, refining the parameters for Type 2 afterglow and minimizing the residuals of both afterglow types.
-Fit plots for single train is shown in \ref{fig:af_fit99}.
-The values of type 2 afterglow parameter amplitude (B) and decay width (C) for different wagon trains are shown in Table \ref{fig:af_fit4000}.
+Fit plots for single train is shown in Fig.
+\ref{fig:af_fit99}.
+The values of type 2 afterglow parameter amplitude (B) and decay width (C) for different wagon trains are shown in Table Fig.
+\ref{fig:af_fit4000}.
 
@@
 \caption[Run 315690 PCC without and with afterglow correction]{%
- Raw and corrected PCC for all bunch crossings.
+ Raw and corrected PCC rates for all bunch crossings in run 315690.
 }
@@
 
-\item  X-Y nonfactorization: The luminosity calibration often relies on methods that factorize the beam overlap integral into two separate integrals in the horizontal (X) and vertical (Y) directions.
+\item  X-Y non-factorization: The luminosity calibration often relies on methods that factorize the beam overlap integral into two separate integrals in the horizontal (X) and vertical (Y) directions.
 When this factorization is not valid or precise, the XY non-factorization comes into play.
@@
 
-\item Dynamic $\beta$: The beta function ($\beta$*) in the context of particle accelerators like the Large Hadron Collider (LHC) is a measure of the beam size at the collision point \cite{CERNVdMOMC}, and it plays a crucial role in determining the luminosity of the collisions.
+\item Dynamic $\beta$: The beta function ($\beta$*) in the context of particle accelerators like the LHC is a measure of the beam size at the collision point \cite{CERNVdMOMC}, and it plays a crucial role in determining the luminosity of the collisions.
 Lower values of $\beta$* lead to smaller beam sizes at the interaction point and thus higher luminosity, as the probability of proton-proton collisions is increased.
@@
 \item Beam Current Calibration:  Beam current calibration ensures that the \( N \) value (number of particles per bunch) used in the luminosity equation is accurate.
-If the calibration is off, the derived value of \( N \) from the instruments like beam current transformers will be inaccurate, leading to errors in the calculated luminosity \( L \).
-As the luminosity dependence on number of particles per bunch is \( N^2 \), even small errors in beam current calibration can significantly affect the accuracy of \( L \) \cite{CERNLumiDays}.
+If the calibration is off, the derived value of \( N \) from the instruments like beam current transformers will be inaccurate, leading to errors in the calculated luminosity $\( L_{inst} \)$.
+As the luminosity dependence on number of particles per bunch is \( N^2 \), even small errors in beam current calibration can significantly affect the accuracy of $\( L_{inst} \)$ \cite{CERNLumiDays}.
 
@@
   \caption[$\sigma_{vis}$ bunch variation uncertainty]{Bunch to bunch variation of PCC visible cross section.
-The “bunch spread” is determined as the standard deviation (STD) of the bunches divided by the mean.
+The “bunch spread” is determined as the standard deviation (STD) of the bunches divided by the mean visible cross section.
 SEM is the standard error on the mean}
@@
 %This effect is typically modeled and accounted for in the data analysis, but any inaccuracies in the modeling can introduce a systematic uncertainty.
-Fluctuation in the  noise level in the detector can also fluctuate over time due to changes in the experimental conditions.
+The noise level in the detector can also fluctuate over time due to changes in the experimental conditions.
 Noise can lead to spurious signals that can be misinterpreted as genuine events, leading to an overestimate of the luminosity.
-Conversely, high noise levels can also mask genuine events, leading to an overestimate of the luminosity.
+Conversely, high noise levels can also mask genuine events, leading to an underestimate of the luminosity.
 %Noise can be suppressed using data analysis techniques, but this is not always perfect, and residual noise can introduce a systematic uncertainty.
@@
   \caption[2018 PCC linearity]{Left: Linearity of PCC compared to HFOC for fill 6961. Right: Ratio of PCC/HFOC luminosity plotted as a function of HFOC luminosity to determ\
-ine change in detector response over different luminosity levels. Slope of the linear fit is 7.2e^{-7} $in units of$ (Hz/ub)^{-1}.}
+ine change in detector response over different luminosity levels. Slope of the linear fit is 7.2e^{-7} $in units of \:$ (Hz/ub)^{-1}.}
   \label{fig:stabprof2}
@@
 \newpage
-\item Afterglow: Systematic uncertainty due to afterglow background are determined by calculating the mean of the type 1 and type 2 afterglow residuals that are defined as the ratio of the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch and ratio of the luminosity of the second and following empty bunches after a colliding bunch to the luminosity of the colliding bunch respectively.
+\item Afterglow: Systematic uncertainty due to afterglow background is determined by calculating the mean of the type 1 and type 2 afterglow residuals that are defined as the ratio of the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch and ratio of the luminosity of the second and following empty bunches after a colliding bunch to the luminosity of the colliding bunch respectively.
 
@@
   \includegraphics[width=1\textwidth]{ashish_thesis/type1res_gr0p5_1.png}
-  \caption[PCC Afterglow Residuals]{Left: PCC afterglow correction type 1 residual as a function of instantaneous luminosity. The residual fraction is given by the ratio of\
- the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch. Right: Type 2 residual as a function of instantane\
-ous luminosity. These are given by the ratio of the luminosity of the second and following empty bunches after a colliding bunch to the luminosity of the colliding bunch. Ra\
-ndom trigger PCC dataset for all periods are used to make these plots \cite{Sehrawat2023}.}
+  \caption[PCC Afterglow Residuals]{Left: PCC afterglow correction type 1 residual as a function of instantaneous luminosity.
+The residual fraction is given by the ratio of the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch.
+Right: Type 2 residual as a function of instantaneous luminosity.
+These are given by the ratio of the luminosity of the second empty bunches after a colliding bunch to the luminosity of the colliding bunch.
+Random trigger PCC dataset for all periods are used to make these plots \cite{Sehrawat2023}.}
   \label{fig:stabprof_4012}
@@
   \centering
-  \caption[2018 Luminosity systematic uncertainty]{Systematic uncertainty during calibration and physics data taking for the final veto.}
+  \caption[2018 Luminosity systematic uncertainty]{Systematic uncertainty during calibration and physics data taking for the final veto for the 2018 PCC luminosity measurement \cite{pas_18}.}
 \label{tab:systematic-uncertainty}

### 2024-03-27 tesis_Ashish/Chapter5/chapter5.tex
update 27 Mar

@@
 Notably, during period F, specifically during Fill 8381, van der Meer (vdM) scans were implemented to calibrate the PCC luminometer.
-For our current analysis, we employ dataset that align with the 2022 luminosity measurement periods, specifically 2022C, 2022D, 2022E, and 2022F, Run 2022G as highlighted in Table \ref{tab:my_label_1}.
+For our current analysis, we employ dataset that align with the 2022 luminosity measurement periods, specifically 2022C, 2022D, 2022E, 2022F and Run 2022G as highlighted in Table \ref{tab:my_label_1}.
 We extracted these datasets from the Alignment and Calibration (AlCa) project, a critical aspect of the CMS experiment.
@@
   \centering
-  \caption[2022 run ranges]{Run periods, run number ranges and dates.}
+  \caption[2022 run ranges]{Run periods, run number ranges and dates for the 2022 data taking period.}
 \begin{tabular}{ccc}
@@
 Table \ref{tab:2022ldmodules} presents the number of good modules in various layers and disks of the pixel detector after a final selection process.
-Layer 3 has 39 good modules, Layer 4 has 88, Disk 1 has 13, Disk 2 has 19, and Disk 3 has 4, totaling 163 modules.
-The stability of various pixel layers and disks after removing all modules in Layer 0 and for final veto are shown in Fig.
-\ref{fig:stabprof_69a}  and Fig.
-\ref{fig:stabprof_69b} respectively.
+%Layer 3 has 39 good modules, Layer 4 has 88, Disk 1 has 13, Disk 2 has 19, and Disk 3 has 4, totaling 163 modules.
+The stability of various pixel layers and disks after removing all modules in Layer 0 and for final veto are shown in Fig. \ref{fig:stabprof_69a}  and Fig. \ref{fig:stabprof_69b} respectively.
 
@@
   \includegraphics[width=0.7\textwidth]{ashish_thesis/PCC_stability_2022_L0veto_4.png}
-  \caption[Luminosity Fractions w/o Layer 0 Modules]{Luminosity fraction of pixel detector for various layer and disks as a function of lumi section for the entire 2022 data with all Layer 0 modules vetoed.}
+  \caption[Luminosity Fractions w/o Layer 0 Modules]{Luminosity fraction of pixel detector for various layers and disks as a function of lumi section for the entire 2022 data with all Layer 0 modules vetoed.}
   \label{fig:stabprof_69a}
@@
   \includegraphics[width=0.7\textwidth]{ashish_thesis/2022_pcc_stability_2.png}
-  \caption[Stability Profiles For Final Veto]{Stability profiles of pixel detector layer and disk modules for the final module veto list.}
+  \caption[Stability Profiles For Final Veto]{Stability profiles of pixel detector layers and disk modules for the final module veto list.}
   \label{fig:stabprof_69b}
@@
 
-van der Meer (vdM) scan was performed in November 2022, during the LHC fills 8379 and 8381.
-In fill 8381 on 10–11 Nov 2022, data was collected when 144 paired bunches of particles were colliding, with additional unpaired bunches also present, various scan pairs were conducted, including four vdM scans, two Beam Imaging (BI) scans, and one length scale scan.
+THe vdM scan was performed in November 2022, during the LHC fills 8379 and 8381.
+In fill 8381 on 10–11 Nov 2022, data was collected when 144 paired bunches of particles were colliding, with additional unpaired bunches also present.
+Various scan pairs were conducted, including four vdM scans, two Beam Imaging (BI) scans, and one length scale scan.
 Each of these scans consists of two examinations in the x and y transverse planes.
@@
 \caption[2022 vdM Program]{%                                                                                                                                             
-  2022 vdM calibration program. In LHC fill 8381, proton beam positions were recorded, including four vdM scans, two BI scans, one LS scan, and two SS periods.
+  2022 vdM calibration program. In LHC fill 8381, proton beam positions were recorded, including four vdM scans, two BI scans, one LS scan, and two SS periods \cite{pas_22}.
 }
@@
 %Normalized Rates and Resulting Fitted Double Gaussian Scan Curves for Single Bunch in X and Y Directions:
-Figure \ref{fig:period_bound_50} which depict how the detected event rate varies as the beams are scanned across each other in the horizontal (X) and vertical (Y) directions.The rates have been fitted to a double Gaussian curve, which reflects the bell-shaped spatial distribution of the proton bunches.
+Figure \ref{fig:period_bound_50} which depicts how the detected event rate varies as the beams are scanned across each other in the horizontal (X) and vertical (Y) directions.The rates have been fitted to a double Gaussian curve, which reflects the bell-shaped spatial distribution of the proton bunches.
 The peaks of these curves correspond to the maximum event rate, which occurs when the beams are perfectly overlapped.
@@
         \end{tabular}
-        \subcaption{SS1_{avg}= 0.039022 +- 0.000613}
+        \subcaption{SS1_{avg}= 0.0390 +- 0.000613}
     \end{minipage}%
@@
         \end{tabular}
-        \subcaption{SS2_{avg}= 0.0779018 -+ 0.00060436}
+        \subcaption{SS2_{avg}= 0.077902 -+ 0.00060436}
     \end{minipage}
@@
 A value of  $\chi^2$/ndof close to 1 can be seen in the statistics box which signifies a good fit.
-PCC visible cross section is 1076 $\pm$ 0.9 (stat) mb.
-The bunch to bunch variation and scan to scan variation of PCC visible cross section is shown in Fig.
+The PCC visible cross section is 1076 $\pm$ 0.9 (stat) mb.
+The bunch to bunch variation and scan to scan variation of the PCC visible cross section is shown in Fig.
 \ref{fig:period_bound_99} and Fig.
-\ref{fig:period_bound_105} \cite{pas_22} %\cite{bril2023vdmrecalibration}.
+\ref{fig:period_bound_105} \cite{pas_22}.
+%\cite{bril2023vdmrecalibration}.
 
@@
 \caption[2022 PCC Visible Cross Section]{%
-  Visible cross section per scan where red line shows the average value. Red band depicts the RMS of the values.
+  Visible cross section per scan where red line shows the average value. Red band depicts the $\pm$ one RMS of the values.
 }
@@
 
-The Fill cycle in Run 3 includes a leveling part in order to control the very high pileup achieved with upgraded LHC beam optics.
-The Fill luminosity profile for Fill 8274 during 2022 data taking is shown in Fig.
+The fill cycle in Run 3 includes a leveling part in order to control the very high pileup achieved with upgraded LHC beam optics.
+The fill luminosity profile for fill 8395 during 2022 data taking is shown in Fig.
 \ref{fig:period_bound_111}.
-This Fill consists of
+This fill consists of
 
@@
 \caption[Fill 8274 Luminosity Profile]{%
-  PCC luminosity profile for Fill 8395.
+  PCC luminosity profile for fill 8395.
 }
@@
 with $k$ denoting the colliding bunch crossing and $x$ indicating the histogram bin.
-2022 PCC afterglow model uses run number 361957 for doing fit to type 1 and type 2 afterglow effect in the PCC raw data as shown in Fig.
+2022 PCC afterglow model uses run number 361957 for fitting the type 1 and type 2 afterglow effect in the PCC raw data as shown in Fig.
 \ref{fig:period_bound_101}.
-Model consist of a parameter for type 1 afterglow correcton and exponentially decaying function with two parameters amplitude and decay width to model type 2 afterglow correction.
-Fit function is summed over all bunch crossings.
+The model consists of a parameter for type 1 afterglow correction and an exponentially decaying function with two parameters, amplitude and decay width, to model type 2 afterglow correction.
+The fit function
+%correcton and exponentially decaying function with two parameters amplitude and decay width to model type 2 afterglow correction. Fit function
+is summed over all bunch crossings.
 Fit perfomed for 4 wagon train is shown in Fig.
@@
 
-\item Bunch to bunch uncertainty: The "bunch to bunch variation of PCC visible cross section" refer to how much the measured visible cross-section (and thus, the measured luminosity) changes from one bunch crossing to another.
+\item Bunch to bunch uncertainty: The "bunch to bunch variation of PCC visible cross section" refer to how much the measured visible cross-section (and thus, the measured luminosity) changes from one bunch crossing to another as shown in Table \refl{tab:my_labeltt}.
 Variations could arise from different factors such as varying numbers of protons per bunch, spatial distribution of protons within the bunches, and the specific conditions of the pixel detector at the time of each bunch crossing.
@@
 \end{tabular}
-\label{tab:my_label}
+\label{tab:my_labeltt}
 %\caption{Bunch to bunch variation of visible cross section. $N_b$ is the number of bunches in the vdM scan.}
@@
 These variations could be due to slight changes in the experimental conditions.
-The results for each scan are plotted after averaging over five BCIDs.
+The results for each scan are plotted after averaging over five BCIDs as shown in Fig.
+\ref{fig:period_bound_105}.
 Each point on this graph represent the result from one scan.
 A red line is drawn to indicate the average value of the visible cross-section over all the scans.
-This average value provide a useful comparison point to evaluate the consistency of the individual scan results and identify any potential anomalies or systematic errors.
+This average value provides a useful comparison point to evaluate the consistency of the individual scan results and identify any potential anomalies or systematic errors.
 
@@
 
-The left plot in figure \ref{fig:stabprof2_2000} provides a comparison of the linearity of PCC luminosity in relation to HFET luminosity.
+%The plot in figure \ref{fig:stabprof2_2000} provides a comparison of the linearity of PCC luminosity in relation to HFET luminosity.
 A perfectly linear relationship would imply same luminosity measured by both the luminometers, suggesting an absence of non-linearity in the detector response.
@@
 The values are plotted as a function of HFET luminosity.
-The goal of this graph is to examine potential changes in the detector's response across different luminosity levels.
-If the detector's response was perfectly linear, we do expect the ratio to remain constant across the range of HFET luminosity values.
+The goal of this graph is to examine potential changes in the detector response across different luminosity levels.
+If the detector response was perfectly linear, we do expect the ratio to remain constant across the range of HFET luminosity values.
 Deviations from a constant ratio indicate non-linearity in the detector response, thereby contributing to systematic uncertainties.
@@
   \centering
-  \caption[Systematic uncertainty in 2022 luminosity measurement]{Systematic uncertainty in 2022 luminosity measurement (\%) \cite{pas_22}}
+  \caption[Systematic uncertainty in 2022 luminosity measurement]{Systematic uncertainty in 2022 PCC luminosity measurement (\%) \cite{pas_22}}
     \begin{tabular}{l|c}

### 2024-03-27 tesis_Ashish/Chapter7/chapter7.tex
update 27 Mar

@@
 \chapter{TEPX luminometer for HL-LHC}  %Title of the First Chapter
+\label{TEPX luminometer for HL-LHC}
 
@@
 The HL-LHC will significantly increase the instantaneous luminosity, leading to a higher number of proton-proton collisions per bunch crossing.
-Instantaneous luminosity will increase to an unprecedented value of $7.5 \times 10^{34} cm^{-2} \: s^{-1}$ which corresponds to 200 proton-proton collisions per bunch crossing.
+Instantaneous luminosity will increase to an unprecedented value of $7.5 \times 10^{34} cm^{-2} \: s^{-1}$ which corresponds to 200 proton-proton collisions per bunch crossing, on average.
 This higher collision rate poses several challenges, including increased radiation levels, higher data rates, and more complex event environment.
-Run 2 pixel detector will not be able to handle these extreme radiation environment, resolve nearby particle tracks and operate properly to give a reliable estimate of the instantaneous luminosity for such a high pileup.
+The Run 2 pixel detector will not be able to handle these extreme radiation environment, resolve nearby particle tracks and operate properly to give a reliable estimate of the instantaneous luminosity for such a high pileup.
 That is why it will be replaced by a new pixel detector.
@@
 
-Data Acquisition (DAQ) system for the Phase II CMS Tracker must handle the increased data rates and complexity associated with the HL-LHC.
+The Data Acquisition (DAQ) system for the Phase II CMS Tracker must handle the increased data rates and complexity associated with the HL-LHC.
 The HL-LHC is expected to achieve a peak luminosity which is around 5-7 times higher than the current LHC design luminosity which the DAQ system must handle.
@@
 %The high-speed optical links used for data transmission between the Front-End Electronics (FEE) and off-detector electronics are expected to operate at data rates of 10-25 Gbps or higher to handle the large data volumes generated by the upgraded tracker.
-In the Inner Tracker readout system, control signals are sent to the it at 160 Mb/s to coordinate its detection processes.
+In the Inner Tracker readout system, control signals are sent to the inner tracker at 160 Mb/s to coordinate its detection processes.
 It, in turn, outputs data at 1.28 Gb/s per chip to the LpGBT, which acts as a data consolidator for up to three chips.
@@
   \includegraphics[width=0.5 \columnwidth]{ashish_thesis/tepx_DD.png}
-  \caption[X-Y view of TEPX double-disk]{ \onehalfspacing View of one TEPX double-disk in the $r-\phi$ plane; individual pixel modules on two planes (double-disk) and five rings are outlined by yellow rectangles.
+  \caption[X-Y view of TEPX double-disk]{ \onehalfspacing View of one TEPX double-disk in the $r-\phi$ plane; individual pixel modules on two planes (double-disk) and five rings are outlined by orange rectangles \cite{Collaboration:275907420}.
 %The planes are separated in z by about 1 cm.
@@
 
-TEPX is designed to function as a high-precision online bunch-by-bunch luminometer, primarily uses pixel cluster counting for luminosity measurement, a method involving the detection and counting of pixel clusters formed by charged particles from the proton collisions.
+TEPX is designed to function as a high-precision online bunch-by-bunch luminometer, primarily using pixel cluster counting for luminosity measurement, a method involving the detection and counting of pixel clusters formed by charged particles from the proton collisions.
 Additionally, TEPX benefits from coincidence counting due to overlapping modules which enhances accuracy and enables systematic studies.
@@
 %In terms of data acquisition,
-TEPX adapts to different operational conditions: during standard physics runs, it maintains a baseline luminosity trigger rate of 75 kHz, while during van der Meer (vdM) scans, this rate can significantly increase, potentially up to 1 MHz \cite{Collaboration:2706512}.
+TEPX adapts to different operational conditions: during standard physics runs, it maintains a baseline luminosity trigger rate of 75 kHz, while during vdM scans, this rate can significantly increase, potentially up to 1 MHz \cite{Collaboration:2706512}.
 %TEPX readout rate (E-link speed) is estimated to be approximately 1330 Gbps at a pileup of 200  \cite{Collaboration:2706512}.
@@
 
-TEPX Disk 4 Ring 1 (D4R1) is located in the innermost ring of the last double-disk of the TEPX, is exclusively designed for measuring luminosity and beam-induced background (BIB).
+TEPX Disk 4 Ring 1 (D4R1) is located in the innermost ring of the last double-disk of the TEPX and it is exclusively designed for measuring luminosity and beam-induced background (BIB).
 D4R1 is optimally placed due to its low radius, large active area, and high z position, making it highly efficient for these measurements.
-The D4R1 operational model is distinct from the rest of TEPX \cite{Haranko2023}.
+The D4R1 operational mode is distinct from the rest of TEPX \cite{Haranko2023}.
 It employs the entire available trigger rate and readout bandwidth, which varies based on operational mode.
@@
 
-\section{TEPX Luminomter Simulation}
-
- Simulated data samples for Phase II include full CMS detector description and uses official CMS software (version $\texttt{CMSSW\_10\_6\_0\_patch2}$) which calls GEANT4 for detector simulation \cite{GEANT4:2002zbu}.
+\section{TEPX Luminometer Simulation}
+
+ Simulated data samples for Phase II include full CMS detector description and use official CMS software (version $\texttt{CMSSW\_10\_6\_0\_patch2}$) which calls GEANT4 for detector simulation \cite{GEANT4:2002zbu}.
 Pixel clusters are reconstructed using the standard CMS reconstruction algorithms \cite{cmssw_2024}.
@@
 
-Linearity is one of the systematic uncertainty in the calculation of instantaneous luminosity and PCC visible cross section $\sigma_{vis}$.
+Linearity is one of the systematic uncertainties in the calculation of instantaneous luminosity and PCC visible cross section $\sigma_{vis}$.
 A linear relation between the mean number of clusters and pileup (PU) imply that $<N_{cl/pp}> = \frac{<N_{cl}>}{\mu} = \frac{\sigma_{vis}}{\sigma_{pp}}$ , $<N_{cl}> =  \frac{\sigma_{vis}}{\sigma_{pp}} \mu $.
@@
 The non-linearity is calculated as
-    The relative difference between the data points and the values of the fit function at the respective pileup value. }
+    The relative difference between the data points and the values of the fit function at the respective pileup value \cite{Collaboration:275907420}.}
   \label{fig:CMS_4205}
@@
 The non-linearity is calculated as
-    The relative difference between the data points and the values of the fit function at the respective pileup value. }
+    The relative difference between the data points and the values of the fit function at the respective pileup value \cite{Collaboration:275907420}. }
   \label{fig:CMS_4206}
@@
 
-A new algorithm for luminosity measurement based on counting two-fold coincidences is proposed that applies selections using dr and $d\phi$ variables (shown in Fig.
+A new algorithm for luminosity measurement based on counting two-fold coincidences is proposed that applies selections using dr and d$\phi$ variables (shown in Fig.
 \ref{fig:drdphi_diagram}) to minimize non-linearity for high pileup as these variables take into account track angle and its curvature \cite{sehrawat2020}.
@@
 \caption[New Variables For Two Fold Coincidences]{%
-  r, phi variables used to define coincidence clusters. %These variables take into account track angle and curvature.
+  r, $\phi$ variables used to define coincidence clusters. %These variables take into account track angle and curvature.
 }
@@
 
-We study the two-fold coincidences in $\phi$ for all TEPX Disk and rings using r, phi variable for pileup 0.5.
-Based on pileup 0.5 sample, a pre-selection of 0.15 mm on dr and 0.04 on dphi variable is applied in order to remove fake coincidences.
-
-The dr, dphi distribution showing true, fake, total two-fold coincidences for Disk 4 Ring 1 for pileup 0.5 is shown in Fig.
+We study the two-fold coincidences in $\phi$ for all TEPX Disk and rings using r, $\phi$ variable for pileup 0.5.
+Based on pileup 0.5 sample, a pre-selection of 0.15 mm on dr and 0.04 on d$\phi$ variable is applied in order to remove fake coincidences.
+
+The dr, d$\phi$ distribution showing true, fake, total two-fold coincidences for Disk 4 Ring 1 for pileup 0.5 is shown in Fig.
 \ref{fig:cluster_dr_dphi_dist}.
-After obtaining these distributions for all TEPX disks and rings, we carry out fit of the true coincidences distribution (shown in red color) to obtain mean and standard deviation of these distributions.
+After obtaining these distributions for all TEPX disks and rings, we carry out a fit of the true coincidences distribution (shown in red color) to obtain mean and standard deviation of these distributions.
 A two-standard-deviation selection is applied on the dr value about the mean.
@@
 \ref{fig:cluster_ring_1003}, \ref{fig:cluster_ring_70}, \ref{fig:cluster_ring_71}.
-Similarly, two-sigma cut is applied on the dphi variable as well.
-The standard deviation values for dphi variable are shown in Table \ref{tab:mdphi_cuts_values}.
-While doing the fit, mean value for dphi variable is set to zero.
+Similarly, two-sigma cut is applied on the d$\phi$ variable as well.
+The standard deviation values for d$\phi$ variable are shown in Table \ref{tab:mdphi_cuts_values}.
+While doing the fit, the mean value for d$\phi$ variable is set to zero.
 %The mean is taken as the offset value and standard deviation is used as the selection on dr, dphi variables as shown in Table \ref{tab:disk_values}, \ref{tab:mdphi_cuts_values} and \ref{tab:mdr_cuts_offset_values}.
 %The mean of the fit is taken as the offset value and standard deviation is used as the cut on dr, dphi variables.
-A plot of two-fold coincidences in phi after applying all selection based on standard deviation values of all TEPX disks and rings is shown in Fig. \ref{fig:cluster_ring_720}.
+A plot of two-fold coincidences in $\phi$ after applying all selection based on standard deviation values of all TEPX disks and rings is shown in Fig. \ref{fig:cluster_ring_720}.
 
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/D4R1_S2_drdphi_cut_2.png}
-\caption[Pileup 0.5 Cluster Count in D4R1 vs. dr & dphi]{%
-  Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for Disk 4 Ring 1.
+\caption[Pileup 0.5 Cluster Count in D4R1 vs. dr & d$\phi$]{%
+  Distribution of cluster count as a function of dr and d$\phi$ variables for pileup 0.5 for Disk 4 Ring 1.
 The black curve represents the total two-fold coincidence counts, the red curve depicts the true two-fold coincidence counts, and the green curve indicates the fake two-fold coincidence counts.
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/D4R3_S2_drdphi_cut.png}
-\caption[Pileup 0.5 Cluster Count in D4R3 (+Z) vs. dr & dphi]{%
+\caption[Pileup 0.5 Cluster Count in D4R3 (+Z) vs. dr & d$\phi$]{%
   Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 3 (+Z). Appropriate selection on dr, dphi are used to minimize fake two fold coincidences.
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/D4R5_drdphicut.png}
-\caption[Pileup 0.5 Cluster Count in D4R5 (+Z) vs. dr & dphi]{%
+\caption[Pileup 0.5 Cluster Count in D4R5 (+Z) vs. dr & d$\phi$]{%
   Distribution of cluster count as a function of dr and dphi variables for pileup 0.5 for disk 4 Ring 5 (+Z). Appropriate selection on dr, dphi are used to minimize fake two fold coincidences.
@@
   \centering
-  \caption[dr offset values for two-fold in phi]{dr mean values (mm) obtained from fit for two fold coincidences in phi for all disks and rings}
+  \caption[dr offset values for two-fold in $\phi$]{dr mean values (mm) obtained from fit for two fold coincidences in $\phi$ for all disks and rings}
   \begin{tabular}{cccccc}
@@
   \centering
-  \caption[dr cut values for two-fold in phi]{dr cut values (mm) for two fold coincidences in phi for all disks and rings}
+  \caption[dr cut values for two-fold in $\phi$]{dr cut values (mm) for two fold coincidences in $\phi$ for all disks and rings}
   \begin{tabular}{cccccc}
@@
   \centering
-  \caption[dphi cut values for two-fold in phi]{dphi cut values for two fold coincidences in phi for all disks and rings}
+  \caption[d$\phi$ cut values for two-fold in $\phi$]{d$\phi$ cut values for two fold coincidences in $\phi$ for all disks and rings}
   \begin{tabular}{cccccc}
@@
   Fit results for all disks and rings are shown from  Table \ref{tab:my_label_55} to \ref{tab:my_label_54}.
-Similarly, two-sigma standard deviation selections are applied on dr, dphi variables.
+Similarly, two-sigma standard deviation selections are applied on dr, d$\phi$ variables.
 After applying all selections, the XY map of two-fold coincidences in r for L1L2 and L3L4 combined as shown in \ref{fig:cluster_ring_79}.
@@
   \centering
-  \caption[dphi cut values for two-fold in r]{dphi standard deviation values obtained from fit to true coincidences in r}
+  \caption[d$\phi$ cut values for two-fold in r]{d$\phi$ standard deviation values obtained from fit to true coincidences in r}
 \begin{tabular}{ccccc}
@@
 \includegraphics[width=0.6\textwidth]{ashish_thesis/twofoldinphi_sch_1.png}
-\caption[Map Of Two Fold Coincidences in phi]{%                                                                                                            
+\caption[Map Of Two Fold Coincidences in $\phi$]{%                                                                                                            
    X-Y map of reconstructed two-fold coincidences in $\phi$ showing module overlap regions.
@@
 \newpage
-The new algorithm is able to remove physics noise at high pileup as can be seen from the high efficiency values and low fake rates for Disk 4 all rings and all pileup samples as shown in Table  \ref{tab:sample} and \ref{tab:combined_sample}.
+The new algorithm is able to remove physics noise at high pileup as can be seen from the high efficiency values and low fake rates for Disk 4 for all rings and for all pileup samples as shown in Table  \ref{tab:sample} and \ref{tab:combined_sample}.
 The fake two-fold coincidence rates for different rings in Disk 4 with a pileup of 200 are presented.
@@
 There is a general trend of increasing fake rates with pileup.
-For instance, at a pileup of 0.5, the fake rates for "2-fold in phi" and "2-fold in r" are 0.78\% and 0.99\%, respectively.
-These rates gradually increase as the pileup value rises, reaching 1.85\% for "two-fold in phi" and 1.57\% for "two-fold in r" at a pileup of 200.
+For instance, at a pileup of 0.5, the fake rates for "2-fold in $\phi$" and "2-fold in r" are 0.78\% and 0.99\%, respectively.
+These rates gradually increase as the pileup value rises, reaching 1.85\% for "two-fold in $\phi$" and 1.57\% for "two-fold in r" at a pileup of 200.
 Fake rate is defined as\begin{equation}
 \text{Fake rate} = \frac{\text{Number of fake coincidences (Area under the green curve)}}{\text{Total number of coincidences (Area under the black curve)}}
-\end{equation} as shown in Fig. 1.9.
+\end{equation} as shown in Fig. 6.9.
 
@@
   \begin{tabular}{ccccc}
-    \textbf{Pileup} & \textbf{Fake rate 2-fold in phi (\%)} & \textbf{Fake rate 2-fold in r (\%)} & \textbf{Efficiency 2-fold in phi (\%)} & \textbf{Efficiency 2-fold in r (\%)} \\
+    \textbf{Pileup} & \textbf{Fake rate 2-fold in phi (\%)} & \textbf{Fake rate 2-fold in r (\%)} & \textbf{Efficiency 2-fold in $\phi$ (\%)} & \textbf{Efficiency 2-fold in r (\%)} \\
     \hline
@@
     %\cline{2-5}
-    \textbf{Pileup}  & \textbf{2-fold in phi} & \textbf{2-fold in r} & \textbf{2-fold in phi} & \textbf{2-fold in r} \\
+    \textbf{Pileup}  & \textbf{2-fold in $\phi$} & \textbf{2-fold in r} & \textbf{2-fold in $\phi$} & \textbf{2-fold in r} \\
     \hline
@@
 
-We study the linearity of two-fold coincidences that is how the number of two-fold coincidences change with pileup to obtain precise luminosity measurement \cite{sehrawat2022optimisation}.
+We study the linearity of two-fold coincidences, that is how the number of two-fold coincidences change with pileup to obtain precise luminosity measurement \cite{sehrawat2022optimisation}.
 Distribution of two-fold coincidences for TEPX Disk 4 Ring 1 for all pileup values is shown in Fig.
@@
   \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_D4R1_coin_allpu_1.png}
-  \caption[TEPX D4R1 Two-Fold Coincidences All Pileup]{Distribution of number of two-fold coincidences for TEPX Disk 4 Ring 1 for all pileup values.}
+  \caption[TEPX D4R1 Two-Fold Coincidences All Pileup]{Distribution of number of two-fold coincidences for TEPX Disk 4 Ring 1 for all pileup values \cite{Collaboration:275907420}.}
   \label{fig:tepx_coin_allPU}
@@
 A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.
-Right: The relative difference between the data points and the values of the fit function at the respective pileup value.}
+Right: The relative difference between the data points and the values of the fit function at the respective pileup value \cite{Collaboration:275907420}.}
   \label{fig:CMS_420}
@@
 A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.
-Right: The relative difference between the data points and the values of the fit function at the respective pileup value.}
+Right: The relative difference between the data points and the values of the fit function at the respective pileup value \cite{Collaboration:275907420}.}
   \label{fig:CMS_4207}
@@
 A three-fold coincidence refers to a situation where three hits occur in a close spatial arrangement originating from the same underlying event.
-In the current algorithm, we look for another cluster in the lower ring after a two fold coincidence cluster in phi is found.
+In the current algorithm, we look for another cluster in the lower ring after a two fold coincidence cluster in $\phi$ is found.
 The selections used for finding three-fold coincidences using old dx, dy and dz cut variables are 0.1 mm, 0.1 mm and 0.9 mm.
@@
   \includegraphics[width=1\columnwidth]{ashish_thesis/TEPX_threefold_linearity.png}
-  \caption[Disk 4 all rings Three-Fold Coincidences Linearity]{Left: Simulated mean number of three-fold coincidences for all Disk 4 all rings as a function
+  \caption[Disk 4 all rings Three-Fold Coincidences Linearity]{Left: Simulated mean number of three-fold coincidences for all Disk 4 rings as a function
     of pileup. Right: Deviation from linearity for Disk 4 all rings, the relative difference between the data points and the values of the fit function at the respective pileup value.}
@@
 
-Statistical precision is another uncertainty that need to be considered for precise luminosity measurement.
+Statistical precision is another uncertainty that needs to be considered for precise luminosity measurement.
 It must be kept minimal to achieve 1 $\%$ accuracy for HL-LHC luminosity measurement.
-Relative statistical uncertainty in $\%$ = $\frac{\sqrt{N}}{N} \times 100$ where N is the product of the number of counts per event, the trigger frequency and the time integration period.\\
+The relative statistical uncertainty in $\%$ is calculated as  $\frac{\sqrt{N}}{N} \times 100$ where N is the product of the number of counts per event, the trigger frequency and the time integration period.\\
+
+The following tables detail the precision of event counting algorithms at a set pileup of 0.5 and high pileup scenarios across varying integration times to ensure precision luminosity measurement.
 
@@
 TEPXD4R1 Clusters&1000&1.82&0.332\\
-TEPXD4R1 2x Coincidences in phi &1000&5.98&1.09\\
+TEPXD4R1 2x Coincidences in $\phi$ &1000&5.98&1.09\\
 TEPXD4R1 2x Coincidences in r &1000&11.1&2.02\\
@@
 TEPX Clusters&500&0.709&0.129\\
-TEPX 2x Coincidences in phi &500&2.65&0.485\\
+TEPX 2x Coincidences in $\phi$ &500&2.65&0.485\\
 TEPX 2x Coincidences in r &500&4.59&0.838\\
@@
 TEPXD4R1 Clusters & 825 & 0.1 & 0.002  \\
-TEPXD4R1 2x Coincidences in phi & 825 & 0.329 & 0.00659 \\
+TEPXD4R1 2x Coincidences in $\phi$ & 825 & 0.329 & 0.00659 \\
 TEPXD4R1 2x Coincidences in r & 825 & 0.61 & 0.0122  \\
@@
 TEPX Clusters & 75 & 0.0915 & 0.00183  \\
-TEPX 2x Coincidences in phi & 75 & 0.343 & 0.00685 \\
+TEPX 2x Coincidences in $\phi$ & 75 & 0.343 & 0.00685 \\
 TEPX 2x Coincidences in r & 75 & 0.593 & 0.0119  \\

### 2024-03-27 tesis_Ashish/Chapter1/chapter1.tex
update 28 Mar

@@
 Therefore, it is crucial to measure the luminosity with high precision.
+
+Precision in luminosity measurement allows for the accurate determination of the Standard Model parameters, such as the masses of fundamental particles and the strength of their interactions (coupling constants).
+These parameters are critical for making precise predictions about particle behavior in high-energy collisions.
+By refining these parameters, physicists can enhance their understanding of the universe fundamental structure and forces.
+High precision luminosity measurement increase the ability to observe rare processes that occur at very low rates.
+Such processes might be signatures of new physics beyond the Standard Model, including new particles or forces.
+Distinguishing these rare events from the background noise is crucial for advancing our understanding of the universe.
+The electroweak theory, which unifies the weak nuclear force and electromagnetism, makes precise predictions about the production and decay rates of W and Z bosons.
+Accurate luminosity measurements are essential for comparing these theoretical predictions with experimental data.
+Any discrepancies could indicate new physics or the need for adjustments within the Standard Model.
+Quantum Chromodynamics (QCD) describes the strong force, one of the four fundamental forces.
+Experiments that measure jet production rates and other phenomena related to the strong force depend on precise luminosity measurements for validating QCD predictions.
+This understanding is crucial for both the theoretical framework and for interpreting results of particle collision experiments.
+High precision in luminosity measurement allows experimental results to be benchmarked against theoretical models with greater accuracy.
+This benchmarking is essential for validating or refuting theories about the fundamental constituents and forces of the universe.
+
 %The measurement of luminosity with the pixel detector at the CMS experiment is particularly important  as it is a highly precise detector that is capable of measuring luminosity with great accuracy.
@@
 \includegraphics[width=0.8\textwidth]{ashish_thesis/lumi_precision.png}
-\caption[Phase II Uncertainty Projection]{ %
+\caption[Phase 2 uncertainty projection]{ %
    Higgs boson production processes cross section projected uncertainty.
@@
 \includegraphics[width=0.9\textwidth]{ashish_thesis/lhc_schematic.png}
-\caption[CERN Accelerator Complex]{%
+\caption[CERN accelerator complex]{%
     CERN accelerator complex consists of Linac 2, Proton Synchrotron Booster (PSB), Proton Synchrotron (PS), Super Proton Synchrotron (SPS) and Large Hadron Collider (LHC) which is the accelerator chain for proton physics at the LHC.
@@
 \includegraphics[width=0.75\textwidth]{ashish_thesis/cms_exp.png}
-\caption[CMS Experiment Design]{%
+\caption[CMS experiment design]{%
    CMS detector with all of the sub detectors showing silicon tracker, electromagnetic and hadron calorimeters and muon chambers \cite{CMS:2008xjf}. 
@@
   \centering
-  \caption[Integrated luminosity and its precision for Run1 and Run2]{Summary of center of mass energy, integrated luminosity, and systematic uncertainty per year in CMS.}
+  \caption[Integrated luminosity and its precision per year]{Summary of center of mass energy, integrated luminosity, and systematic uncertainty per year in CMS.}
 \begin{tabular}{c c c c}
@@
 \includegraphics[width=0.9\textwidth]{ashish_thesis/CMS_luminosity.png}
-\caption[CMS Integrated luminosity]{%
+\caption[CMS integrated luminosity]{%
     Delivered luminosity versus time for Run 1, Run 2 and Run 3 of the CMS Experiment \cite{wikicern_cc}.
@@
   \centering
-  \caption[Precision for Run1 and Run2]{Summary of center of mass energy, integrated luminosity, and systematic uncertainty per year during the CMS pPb and PbPb luminosity measurement \cite{CMS-PAS-LUM-13-002, CMS-PAS-LUM-17-002, CMS-PAS-LUM-18-001}.}
+  \caption[Precision for pPb and PbPb collisions]{Summary of center of mass energy and systematic uncertainty per year during the CMS pPb and PbPb luminosity measurement \cite{CMS-PAS-LUM-13-002, CMS-PAS-LUM-17-002, CMS-PAS-LUM-18-001}.}
 \begin{tabular}{c c c c}

### 2024-03-27 tesis_Ashish/Chapter2/chapter2.tex
update 28 Mar

@@
 It relies on the direct proportionality between the total transverse energy and the particle flux from the interaction point.
-Accurate calibration of calorimeter cells is crucial for this method, as it ensures that the aggregate transverse energy accurately reflects the luminosity of the particle collisions \cite{Sirunyan:2759951.
+Accurate calibration of calorimeter cells is crucial for this method, as it ensures that the aggregate transverse energy accurately reflects the luminosity of the particle collisions \cite{Sirunyan:2759951}.
+
+%The Hadron Forward Transverse Energy (HFET) algorithm is a method used to determine the luminosity of particle collisions.
+This method is based on the direct proportionality between the transverse energy deposited in the Hadron Forward calorimeter cells and the particle flux from the collision point.
+
+The measurement of instantaneous luminosity, $L_{inst}$, using the HFET algorithm involves the following steps:
+
+\begin{enumerate}
+  \item Initialize the total transverse energy sum: 
+  \[ \Sigma E_T = 0 \]
+
+  \item For each calorimeter cell, do:
+  \begin{enumerate}
+    \item Measure the transverse energy \( E_{T,\text{cell}} \).
+    \item Update the total transverse energy sum: 
+    \[ \Sigma E_T = \Sigma E_T + E_{T,\text{cell}} \]
+  \end{enumerate}
+
+  \item Correct the total transverse energy sum for background energy:
+  \[ \Sigma E_T = \Sigma E_T - E_{T,\text{background}} \]
+
+  \item Multiply by a calibration constant \( k \) to obtain the luminosity:
+  \[ L_{inst} = \( k \ \times \Sigma E_T \]
+\end{enumerate}
+
+The calibration constant \( k \) is empirically determined through a series of calibration procedures, van der Meer scans.
+The constant accounts for the proportionality between the aggregate transverse energy and the actual luminosity of the particle collisions.
 
@@
 \includegraphics[width=0.9\textwidth]{ashish_thesis/luminometer_cms.png}
-\caption[CMS Luminometers]{%
+\caption[CMS luminometers]{%
    CMS detector with all of the luminosity measurement devices showing PLT, BCM1F, HF, DT, PCC and RAMSES \cite{meyer2021luminosity}. 
@@
 \includegraphics[width=0.9\textwidth]{ashish_thesis/luminometer_cms_pseudo.png}
-\caption[CMS luminometers Location]{%
+\caption[CMS luminometers location]{%
     Cross section of the CMS detector in the r-z plane showing all Run 2 luminometers PLT, BCM1F, DTs, and HF location.
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/phaseI_upgrade_pixel_detector.png}
-\caption[Pixel Detector Layout]{%
+\caption[Pixel detector layout]{%
    Layout of the CMS Phase-1 upgraded pixel detector in longitudinal view \cite{Adam:2748381}. 
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/silicon_pixel_module.png}
-\caption[Pixel Module Design]{%
+\caption[Pixel module design]{%
    Pixel detector modules for BPIX L1 (left), BPIX L2-4 (middle), and

### 2024-03-27 tesis_Ashish/Chapter3/chapter3.tex
update 28 Mar

@@
     \includegraphics[width=1\textwidth]{ashish_thesis/vdm_method_new.png}
-    \caption[vdM Scan Schematic]{Left: Scanning the beams across each other (±3$\sigma$) in the transverse plane, horizontal (x-scan) and vertical (y-scan) directions.
+    \caption[vdM scan schematic]{Left: Scanning the beams across each other (±3$\sigma$) in the transverse plane, horizontal (x-scan) and vertical (y-scan) directions.
 Right: Rate is measured as a function of beam separation \cite{karacheban2017luminosity}.}

### 2024-03-27 tesis_Ashish/Chapter4/chapter4.tex
update 28 Mar

@@
 Fig. \ref{fig:period_bound}. Run ranges for each period are shown in Table \ref{tab:period_run_ranges}.
-During period B, specifically corresponding to Fill 6868, van der Meer (vdM) scans were conducted for calibrating the PCC luminometer.
+During period B, specifically corresponding to fill 6868, van der Meer (vdM) scans were conducted for calibrating the PCC luminometer.
 %vdM data is shown during period B corresponding to Fill 6868.
@@
 \includegraphics[width=0.9\textwidth]{ashish_thesis/period_boundary.png}
-\caption[2018 CMS Luminosity Data Period]{%
+\caption[2018 CMS luminosity data period]{%
    2018 luminosity data taking periods showing data taking period boundaries and vdM calibration data (1 July in period B)  \cite{CERNLumiPublicResults}.
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/good_bad_modules_1.png}
-\caption[Good/Bad Module Weights]{%
+\caption[Good/Bad module weights]{%
    Change in normalized module weight with time. Modules showing significant change in module weight (shown in right figure) over time having large RMS/mean values are used to make module veto list.
@@
 
-Module veto list consisting of bad modules is first created for period B, vdM Fill and then for other periods A, C, D1, D2, D3 and D4 as follows,
-
-Run 2018B and vdM Fill:
+Module veto list consisting of bad modules is first created for period B, vdM fill and then for other periods A, C, D1, D2, D3 and D4 as follows,
+
+Run 2018B and vdM fill:
 \begin{itemize}
@@
 \includegraphics[width=0.8\textwidth]{ashish_thesis/cut_selection_1.png}
-\caption[First Iteration For Outlier Module Removal]{%
+\caption[First iteration for outlier modules]{%
    A loose selection of 7\% is applied to remove bad modules. Appropriate selections are applied in each iterative step to remove other bad modules.
@@
 
-    \caption[Second and Final Iteration For Outlier Module Removal]{%
+    \caption[Second and final iteration for outlier modules]{%
         Left: Second iteration on RMS/mean of 3\% is applied to remove more bad modules. 
@@
 \includegraphics[width=0.7\textwidth]{ashish_thesis/mod_weight_comp_2.png}
-\caption[Module Weights Change Removal]{%
+\caption[Module weights change removal]{%
    Projection of change in module weights between period A and B. Modules showing more than 3 sigma change in module weights are added to the module veto list.
@@
 \end{tabular}
-\caption[Mean value change for PCC/HFOC across period.]{%                                                                                                                                       
+\caption[Mean value change for PCC/HFOC across period]{%                                                                                                                                       
  PCC/ HFOC luminosity mean and rms values for  per period veto list showing variation in mean values across period.
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/before_after_vdm_stability_1.png}
-\caption[PCC vdM Stability]{%                                                                                                                                                                      
-   Luminosity fraction per layer or disk (stability plots) before (no veto) and after applying the final module veto with 2\% RMS/mean selection for the vdM fill data.
+\caption[PCC vdM stability]{%                                                                                                                                                                      
+   Luminosity fraction per layer or disk (stability plots) before (no veto) and after applying the final module veto with 2\% RMS/mean selection for the vdM fill 6868 data.
 }
@@
   \centering
-  \caption{Run Period and Good Modules}
+  \caption{Run period and good modules}
 \begin{tabular}{cccc}
@@
 \includegraphics[width=\textwidth]{ashish_thesis/2percentcommonveto_pixellayerdisk_1.png}
-\caption[PCC Stability For Physics Runs]{Left: Luminosity fraction of pixel detector for various layer and disks as a function of lumi section for a module selection excluding only the BPIX Layer 0 for the full 2018 zero-bias dataset.
+\caption[PCC stability for physics runs]{Left: Luminosity fraction of pixel detector for various layer and disks as a function of lumi section for a module selection excluding only the BPIX Layer 0 for the full 2018 zero-bias dataset.
 Right: Stability profiles of pixel detector layer and disk for final module veto list.}
@@
     \includegraphics[width=1\textwidth]{ashish_thesis/vdm_program_2018.png}
-    \caption[2018 vdM Program]{Beam position along x and y is plotted as a function of time showing different types of scans.
+    \caption[2018 vdM program]{Beam position along x and y is plotted as a function of time showing different types of scans.
 #3 and #10 are vdM scans, #4 and #9 are offset scans, #5, #7 and #8 are beam imaging scans, #6 is emittance scan \cite{pas_18}.}
@@
 \ref{fig:sigmavis_ss_backg}.
-The results for five different BCIDs are shown in Table \ref{tab:vdm:SS1_SS2}, using the reprocessed PCC data for Fill 6868.
+The results for five different BCIDs are shown in Table \ref{tab:vdm:SS1_SS2}, using the reprocessed PCC data for fill 6868.
 The overall background correction applied to raw PCC rate is $0.02757\pm0.01987$, which is calculated by taking the average of the mean values of SS1 and SS2.
@@
   \begin{center}
-    \caption[2018 PCC Background]{Mean for the background estimated with the SS1 and SS2 data, separately for all five BCIDs and averaged.}
+    \caption[2018 PCC background]{Mean for the background estimated with the SS1 and SS2 data, separately for all five BCIDs and averaged.}
     \begin{tabular}{ccccc}
@@
     \includegraphics[width=1\textwidth]{ashish_thesis/vdM_fit_cveto_1.png}
-    \caption[PCC Rate Fit]{Rates and the resulting fitted Poly2G scan curves as a function of the beam separation for a single bunch (BCID 265) as recorded by PCC for vdM1 scan in the x (left) and y direction (right).
-Background subtraction and the beam corrections have been applied to the raw data before the fit.}
+    \caption[PCC rate fit]{Rates and the resulting fitted Poly2G scan curves as a function of the beam separation for a single bunch (BCID 265) as recorded by PCC for vdM1 scan in the x (left) and y direction (right).
+Background subtraction and the beam corrections have been applied to the raw data before the fit.
+Residual is defined as (Data-fit)/fit}
     \label{fig:fitquality}
@@
 \includegraphics[width=0.7\textwidth]{ashish_thesis/sigma_vis_btob_var_1.png}
-\caption[$\sigma_{vis}$ Bunch Variation]{%                                                                                                                                                       
+\caption[$\sigma_{vis}$ bunch variation]{%                                                                                                                                                       
  Bunch to bunch variation of PCC visible cross section.
@@
 Some fills last only a few hours, while others can extend for over a day, depending on operational efficiency and the goals for that specific fill.
-Fill profile for Fill 6961 during 2018 data taking is shown in Fig.
+fill profile for fill 6961 during 2018 data taking is shown in Fig.
 \ref{fig:Fill6961} with
@@
     \includegraphics[width=0.9\textwidth]{ashish_thesis/Fill_profile_6961_1.png}
-    \caption[Fill 6961 Profile]{Typical lumi profile for LHC Fill during 2018 data taking period for Fill 6961.}
+    \caption[fill 6961 profile]{Typical lumi profile for LHC fill during 2018 data taking period for fill 6961.}
     \label{fig:Fill6961}
@@
 
-Fill 9036, shown in \ref{fig:af_fit40} and encompassing 900 colliding bunches, serves as the foundation for estimating the Type 2 afterglow parameters.
+fill 9036, shown in \ref{fig:af_fit40} and encompassing 900 colliding bunches, serves as the foundation for estimating the Type 2 afterglow parameters.
 A fit is performed to one wagon train, then two, and finally three, refining the parameters for Type 2 afterglow and minimizing the residuals of both afterglow types.
@@
 \includegraphics[width=0.8\textwidth]{ashish_thesis/fill_7036_pattern_2.png}
-\caption[7036 Fill Patern]{%
-  Fill 7036 pattern (900 b fill).
+\caption[7036 fill patern]{%
+  fill 7036 pattern (900 b fill).
 }
@@
   %\end{subfigure}
-  \caption[Afterglow Effect Fit]{Fit to single train to estimate afterglow parameters.}
+  \caption[Afterglow effect fit]{Fit to single train to estimate afterglow parameters.}
   \label{fig:af_fit99}
@@
 Instantaneous luminosity is proportional to the rate of collisions at any given moment in time.
-It is a snapshot of the experiment's performance and is represented as \( L_{\text{inst}} \).
+It is a snapshot of the experiment performance and is represented as \( L_{\text{inst}} \).
 The unit of instantaneous luminosity is often Hertz per micro barn $(Hz/ub)$.
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/PCClumivslumisection_2018_1.png}
-\caption[2018 PCC Inst. Luminosity]{%                                                                                                                                                                   
+\caption[2018 PCC inst. luminosity]{%                                                                                                                                                                   
  2018 PCC instantaneous luminosity as a function of lumi section.
@@
 This reduction can influence the effectiveness of the experiments conducted, potentially introducing uncertainties in the luminosity measurement \cite{CERNOribLumi}.
+To calculate the systematic uncertainty due to orbit drift in luminosity measurement, the process begins with measuring the particle beam positions during vdM scans using systems like DOROS BPM and arc BPMs.
+Corrections are applied based on linear interpolations of these positions to account for any drift from the intended paths, crucial for maintaining optimal beam overlaps and accurate collision counts.
+The impact of these corrections on the visible cross section is then assessed.
+Systematic uncertainty is estimated by comparing corrected visible cross section values from both measurement systems, with an additional peak position correction applied for discrepancies at the head-on position.
+This comprehensive approach consolidates the uncertainties from orbit drift and peak position corrections into a single value.
+
+%Orbit drift impacts beam path alignment, crucial for maximizing collision rates and, consequently, luminosity, use systems like DOROS BPM and arc BPMs to measure beam positions during vdM scans, detecting any drift, correct for orbit drift by linearly interpolating measured beam positions around each VdM scan, adjusting nominal beam separations to reflect actual positions, evaluate how these corrections affect the visible cross section, compare corrected visible cross section values from DOROS and arc BPM measurements to estimate uncertainty.
+The systematic uncertainty encompasses both orbit drift and peak position corrections, ensuring accuracy in luminosity measurements essential for particle physics experiments.
 
@@
 If the beams' profiles in the X and Y dimensions are not factorized correctly, it can lead to an inaccurate representation of their overlap, thus introducing a systematic uncertainty in the luminosity measurement \cite{CERNLUMPOG}.
+To determine the systematic uncertainty due to X-Y non-factorization in luminosity, a series of specialized beam imaging scans are conducted to capture the actual profiles and overlaps of the colliding beams, challenging the common assumption that beam densities in the X and Y dimensions can be independently factorized.
+Data from these scans are used to model the beam shapes, incorporating potential X-Y correlations using various mathematical functions.
+Simulated vdM scans based on these models then predict the expected luminosity, accounting for the non-factorizable nature of the beams.
+By comparing these predictions with actual vdM scan results which assume factorizable beam profiles a correction factor is estimated to adjust the luminosity.
+The systematic uncertainty related to X-Y non-factorization is finally determined by evaluating the correction factor variability and the model fit quality, ensuring the adjustment accurately reflects the true beam interactions and their impact on the measured luminosity.
 
@@
 However, when two beams cross each other, the electromagnetic fields of the protons in one beam can exert forces on the protons in the other beam, causing them to deviate from their initial trajectory \cite{babaev2023impact}.
+Systematic uncertainty due to beam-beam deflection is computed by modeling the electromagnetic interactions that cause proton beams to deflect when collidingaffecting luminosity.
+Sophisticated simulations predict the deflection impact, allowing for the derivation of a correction factor to adjust luminosity.
+This uncertainty is quantified by evaluating the correction factor variability and confidence across various conditions.
 
@@
  % \cite{CERNVdMOMC}.
+The systematic uncertainty due to dynamic $\beta$ effects is quantified based on beam transport simulations that incorporate both the defocusing effects of beam-beam interactions and the scaling of these effects to the actual beam energies, $\beta$ settings, and measured beam widths.
+The correction and its uncertainty are derived from the modeling of how each beam, under the influence of the other, experiences changes in its focusing properties, thereby affecting the overlap and, consequently, the luminosity.
+The correction is essential to account for the fact that the presence of one beam influences the focusing properties of the other, leading to adjustments in the measured beam sizes and the calculated luminosity.
 
 \item Beam Current Calibration:  Beam current calibration ensures that the \( N \) value (number of particles per bunch) used in the luminosity equation is accurate.
-If the calibration is off, the derived value of \( N \) from the instruments like beam current transformers will be inaccurate, leading to errors in the calculated luminosity $\( L_{inst} \)$.
-As the luminosity dependence on number of particles per bunch is \( N^2 \), even small errors in beam current calibration can significantly affect the accuracy of $\( L_{inst} \)$ \cite{CERNLumiDays}.
+If the calibration is off, the derived value of \( N \) from the instruments like beam current transformers will be inaccurate, leading to errors in the calculated luminosity $L_{inst}$.
+As the luminosity dependence on number of particles per bunch is $N^2$, even small errors in beam current calibration can significantly affect the accuracy of $L_{inst}$ \cite{CERNLumiDays}.
+The systematic uncertainty due to Beam Current Calibration is computed by considering uncertainties from two main sources: the precision of the DC Current Transformers (DCCT) measurements and the correction for spurious charges (ghost and satellite charges) that do not contribute to the luminosity.
+These uncertainties stem from the normalization process where Fast Beam Current Transformers (FBCT) measurements are adjusted based on the more accurate total beam current readings from the DCCT, and from the adjustments made to account for non-contributing charges detected during the calibration process.
+The combination of these factors determines the overall systematic uncertainty associated with calibrating the beam currents.
 
@@
 Though only every tenth bin is typically filled with a particle bunch, stray particles are found in neighboring bins.
-These stray bunches within a \(\pm 12.5 \) ns range of a filled RF bin are termed \textit{"satellite bunches"}, distinct from main bunches and can influence precision luminosity measurement.
- \cite{Alici:1427728}.
+These stray bunches within a \(\pm 12.5 \) ns range of a filled RF bin are termed \textit{"satellite bunches"}, distinct from main bunches and can influence precision luminosity measurement \cite{Alici:1427728}.
+The systematic uncertainty due to ghosts and satellites is computed by first measuring these spurious charges using specific detection methods, such as the LHC longitudinal density monitors (LDM) and the beam-gas imaging method, which provide an assessment of the presence of non-colliding protons within the beam.
+These charges, known as ghosts (protons in nominally empty bunch slots) and satellites (protons outside the main RF bucket but within the colliding bunch crossing), do not contribute to the luminosity but are included in the total beam current measurement.
+To accurately account for the luminosity, corrections are made to the beam intensities to exclude the contributions from these spurious charges.
+The correction ensures that the calculated luminosity accurately reflects only the colliding protons that contribute to collisions.
+The uncertainty associated with this correction is derived from the precision and variability of the measurements used to quantify the ghost and satellite charges.
+This includes considering the limitations and variability inherent in the measurement methods (LDM and beam-gas imaging), as well as the fluctuating nature of these spurious charges over time and under different beam conditions.
 
@@
 A head-on lumi phase during vdm fill is used.
+The systematic uncertainty is computed by comparing luminosity measurement across various detectors over the data-taking period.
+This involves analyzing the ratios of luminosity measurement between pairs of detectors, assessing their stability and linearity under different conditions, and identifying any systematic deviations.
+The variability and consistency between detectors are quantified, typically using the standard deviation of these ratios, after excluding periods with known issues.
+The overall systematic uncertainty reflects the largest observed deviations and variability among the detectors, ensuring a conservative estimate that accounts for differences in detector responses and operational conditions.
 
@@
 \includegraphics[width=0.8\textwidth]{ashish_thesis/PCC_HFOCvsls_ProfileX_all_1.png}
-\caption[Luminosity Ratio Profile]{Profile of the PCC/HFOC luminosity as a function of lumi section.}
+\caption[Luminosity ratio profile]{Profile of the PCC/HFOC luminosity as a function of lumi section.}
 \label{fig:stabprof_7098}
@@
 \includegraphics[width=0.8\textwidth]{ashish_thesis/ProjY_ProfileX_h_ratio_all_1.png}
-\caption[Projection Of Luminosity Ratio Profile]{%
+\caption[Projection of luminosity ratio profile]{%
 Distribution of the ratio of PCC/HFOC luminosity evaluated per 50 lumi section blocks. 
@@
   \includegraphics[width=1\textwidth]{ashish_thesis/type1res_gr0p5_1.png}
-  \caption[PCC Afterglow Residuals]{Left: PCC afterglow correction type 1 residual as a function of instantaneous luminosity.
+  \caption[PCC afterglow residuals]{Left: PCC afterglow correction type 1 residual as a function of instantaneous luminosity.
 The residual fraction is given by the ratio of the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch.
@@
 \end{tabular}
-\caption[Systematic uncertainty]{Systematic uncertainty during calibration and physics data taking for PAS and final veto.}
+\caption[2018 systematic uncertainty]{Systematic uncertainty during calibration and physics data taking for PAS and final veto.}
 \label{tab:systematic-uncertainty}
@@
   \centering
-  \caption[2018 Luminosity systematic uncertainty]{Systematic uncertainty during calibration and physics data taking for the final veto for the 2018 PCC luminosity measurement \cite{pas_18}.}
+  \caption[2018 luminosity systematic uncertainty]{Systematic uncertainty during calibration and physics data taking for the final veto for the 2018 PCC luminosity measurement \cite{pas_18}.}
 \label{tab:systematic-uncertainty}

### 2024-03-27 tesis_Ashish/Chapter5/chapter5.tex
update 28 Mar

@@
 \ref{fig:period_bound_1}.
-Notably, during period F, specifically during Fill 8381, van der Meer (vdM) scans were implemented to calibrate the PCC luminometer.
+Notably, during period F, specifically during fill 8381, van der Meer (vdM) scans were implemented to calibrate the PCC luminometer.
 For our current analysis, we employ dataset that align with the 2022 luminosity measurement periods, specifically 2022C, 2022D, 2022E, 2022F and Run 2022G as highlighted in Table \ref{tab:my_label_1}.
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/2022_lumi_datasets.png}
-\caption[2022 CMS Luminosity Data Periods]{%                                                                                                                                              
+\caption[2022 CMS luminosity data periods]{%                                                                                                                                              
    2022 luminosity data taking periods showing data taking period boundaries.
@@
 \end{subfigure}
-\caption[Good/Bad Module Weight Profile]{Module weight profile as a function of lumi section showing good (left) and bad (right) module during Run 2022F.
+\caption[Good/Bad module weight profile]{Module weight profile as a function of lumi section showing good (left) and bad (right) module during Run 2022F.
 The horizontal red line is the mean of the module weight.}
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/stability_deviation_2022_1.png}
-\caption[Module Weight Standard Deviation]{%
+\caption[Module weight standard deviation]{%
   During Run 2022F, the distribution illustrates the average deviation of the module weight over it's mean for all modules.
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/linearity_deviation_2022_1.png}
-\caption[Module Linearity & Linearity Deviation Distribution]{%
+\caption[Module linearity & linearity deviation distribution]{%
  Left: Linearity profile, module weight as a function of average PCC per module for one module in Run 2022F.
@@
   \includegraphics[width=0.7\textwidth]{ashish_thesis/PCC_stability_2022_L0veto_4.png}
-  \caption[Luminosity Fractions w/o Layer 0 Modules]{Luminosity fraction of pixel detector for various layers and disks as a function of lumi section for the entire 2022 data with all Layer 0 modules vetoed.}
+  \caption[Luminosity fractions w/o layer 0 modules]{Luminosity fraction of pixel detector for various layers and disks as a function of lumi section for the entire 2022 data with all Layer 0 modules vetoed.}
   \label{fig:stabprof_69a}
@@
   \includegraphics[width=0.7\textwidth]{ashish_thesis/2022_pcc_stability_2.png}
-  \caption[Stability Profiles For Final Veto]{Stability profiles of pixel detector layers and disk modules for the final module veto list.}
+  \caption[Stability profiles for final veto]{Stability profiles of pixel detector layers and disk modules for the final module veto list.}
   \label{fig:stabprof_69b}
@@
 
-THe vdM scan was performed in November 2022, during the LHC fills 8379 and 8381.
+The vdM scan was performed in November 2022, during the LHC fills 8379 and 8381.
 In fill 8381 on 10–11 Nov 2022, data was collected when 144 paired bunches of particles were colliding, with additional unpaired bunches also present.
@@
 The length scale scan involved beams being separated by a constant distance and moved in both directions in five steps.
-The scan program during Fill 8381 is shown in Fig.
+The scan program during fill 8381 is shown in Fig.
 \ref{fig:2022_vdM_program}.
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/2022_vdM.png}
-\caption[2022 vdM Program]{%                                                                                                                                             
+\caption[2022 vdM program]{%                                                                                                                                             
   2022 vdM calibration program. In LHC fill 8381, proton beam positions were recorded, including four vdM scans, two BI scans, one LS scan, and two SS periods \cite{pas_22}.
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/2022_PCC_vdM_fit_new.png}
-\caption[2022 PCC vdM Fit]{%                                                                                                                                              
+\caption[2022 PCC vdM fit]{%                                                                                                                                              
   Rates and the resulting fitted double Gaussian scan curves as a function of the beam separation for a single bunch (BCID 282) as recorded by PCC for a vdM1 scan in the x (left) and y direction (right).
@@
 \includegraphics[width=0.8\textwidth]{ashish_thesis/2022_sigma_vis_btob_variation.png}
-\caption[$\sigma_{vis}$ Bunch Variation]{%                                                                                                                                                        
+\caption[$\sigma_{vis}$ bunch variation]{%                                                                                                                                                        
   Bunch to bunch variation of PCC visible cross section where the red line is the average value. Red band depicts the $\pm$ one RMS of the values.
@@
 \includegraphics[width=0.8\textwidth]{ashish_thesis/2022_PCC_sigmavis_per_scan_new.png}
-\caption[2022 PCC Visible Cross Section]{%
+\caption[2022 PCC visible cross section]{%
   Visible cross section per scan where red line shows the average value. Red band depicts the $\pm$ one RMS of the values.
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/Fill_profile_8274_1.png}
-\caption[Fill 8274 Luminosity Profile]{%
+\caption[Fill 8274 luminosity profile]{%
   PCC luminosity profile for fill 8395.
@@
 \includegraphics[width=0.8\textwidth]{ashish_thesis/run_361957_ls_block_1.png}
-\caption[Raw PCC Run 361957]{%                                                                                                                                           
+\caption[Raw PCC run 361957]{%                                                                                                                                           
  PCC per bx for fill 8307 for one 50 LS block. The first and ninth train are used to fit the afterglow tail.
@@
 \includegraphics[width=0.8\textwidth]{ashish_thesis/afterglow_fit_2022_1.png}
-\caption[Afterglow Fit 4-wagon]{%
+\caption[Afterglow fit 4-wagon]{%
  Fit to 4-wagon train.
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/afterglow_t1res_vsinstlumi.png}
-\caption[2022 PCC Type 1 Afterglow Residuals]{%                                                                                                                                             
+\caption[2022 PCC Type 1 afterglow residuals]{%                                                                                                                                             
  PCC afterglow correction type 1 residual as a function of instantaneous luminosity for period Run 2022F.
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/afterglow_t2res_vsinstlumi.png}
-\caption[2022 PCC Type 2 Afterglow Residuals]{%                                                                                                                                             
+\caption[2022 PCC type 2 afterglow residuals]{%                                                                                                                                             
 Type 2 residual as a function of instantaneous luminosity for period 2022F.
-These are given by the ratio of the luminosity of the second and following empty bunches after a colliding bunch to the luminosity of the colliding bunch.
+These are given by the ratio of the luminosity of the second empty bunches after a colliding bunch to the luminosity of the colliding bunch.
 }
@@
 \includegraphics[width=0.9\textwidth]{ashish_thesis/afterglow_t1res_vsinstlumi_1.png}
-\caption[2022 PCC Type 1 Afterglow Residuals]{%
+\caption[2022 PCC type 1 afterglow residuals]{%
  PCC afterglow correction type 1 residual as a function of instantaneous luminosity for period Run 2022F.
@@
 \includegraphics[width=0.9\textwidth]{ashish_thesis/afterglow_t2res_vsinstlumi_1.png}
-\caption[2022 PCC Type 2 Afterglow Residuals]{%
+\caption[2022 PCC type 2 afterglow residuals]{%
   Type 2 residual as a function of instantaneous luminosity for period 2022F.
@@
 \includegraphics[width=0.9\textwidth]{ashish_thesis/PCClumivslumisection_2022.png}
-\caption[2022 PCC Inst. Luminosity]{%
+\caption[2022 PCC inst. luminosity]{%
   PCC instantaneous luminosity as a function of lumi section for entire 2022 year.
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/SS_bkg_2022.png}
-\caption[2022 Backgound Estimation]{%                                                                                                                                              
+\caption[2022 backgound estimation]{%                                                                                                                                              
   2D histogram filled with the Avg. PCC evaluated per NB4, during the Super-Separation window.
@@
   %\end{subfigure}
-  \caption[Luminosity Ratio Profile]{Profile of the PCC/HFET luminosity as a function of integrated luminosity.} %Right: Histogram filled with the ratio of PCC/HFET luminosity per lumi section.}
+  \caption[Luminosity ratio profile]{Profile of the PCC/HFET luminosity as a function of integrated luminosity.} %Right: Histogram filled with the ratio of PCC/HFET luminosity per lumi section.}
 \label{fig:stabprof_78}
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/ProjY_ProfileX_h_ratio_all_2022_1_new.png}
-\caption[Projection of Luminosity Ratio Profile]{%
+\caption[Projection of luminosity ratio profile]{%
  Distribution of the ratio of PCC/HFET luminosity evaluated per 50 lumi section blocks.
@@
 \includegraphics[width=0.6\textwidth]{ashish_thesis/PCC_HFOCvsHFOC_ProfileX_all_2022_1.png}
-\caption[PCC Response To Luminosity]{%                                                                                                                                                                
+\caption[PCC response to luminosity]{%                                                                                                                                                                
    Ratio of PCC/HFET luminosity plotted as a function of HFET luminosity to determine change in detector response over different luminosity levels.                                                    

### 2024-03-27 tesis_Ashish/Declaration/declaration.tex
update 28 Mar

\begin{dedication}
  \vspace*{-2cm} % Adjust the -2cm to the amount of space you want to move up                                                                                                                                                                
%\centering                                                                                                                                                                                                                                  
%\begin{center}                                                                                                                                                                                                                              
\section*{Declaration}
%\end{center}                                                                                                                                                                                                                                
\justify{

I, Ashish Sehrawat, solemnly affirm that the doctoral thesis entitled "Measurement of the Luminosity in Proton-Proton Collisions at the CMS Experiment of the Large Hadron Collider," submitted for the completion of the Doctorado en Ciencias (Física) at the Universidad de Sonora, is my original work. It has not been submitted for any degree or examination at another university.

The results and discussions presented in Chapter 5 of this thesis are part of the collaborative work published as “Luminosity measurement in proton-proton collisions at 13.6 TeV in 2022 at CMS,” CMS Collaboration, 2024, CMS PAS LUM-22-001, accessible at https://cds.cern.ch/record/2890833.

The outcomes of Chapter 6 are included in “The Phase-2 Upgrade of the CMS Beam Radiation Instrumentation and Luminosity Detectors,” by the CMS Collaboration, technical report, CERN, Geneva, 2021, available online at https://cds.cern.ch/record/2759074. These contributions are properly cited and recognized within this document.

This thesis has been prepared with strict adherence to ethical standards of academic conduct. All sourced information has been appropriately cited to respect the intellectual property rights of original authors. This work has been supported by the Universidad de Sonora and the Consejo Nacional de Ciencia y Tecnología (CONACYT), to whom I extend my deepest gratitude for their support.

By signing below, I certify the authenticity and originality of the work submitted herein and affirm all statements made as true and based on my research findings.

Signature:

Ashish Sehrawat

Date: 28 March 2024

Location: New Delhi, India

\end{dedication}

### 2024-03-27 tesis_Ashish/Chapter4/chapter4.tex
update 28 Mar

@@
 \includegraphics[width=1\textwidth]{ashish_thesis/SS1_SS2_bkg_pcc_1.png}
-\caption[Background estimation]{2D histogram filled with the Avg. PCC rate evaluated per NB4, during head-on collisions (high part) and during the Super-Separation window (low part).}
+\caption[Background estimation]{2D histogram filled with the Avg. PCC evaluated per NB4, during head-on collisions (high part) and during the Super-Separation window (low part).}
 \label{fig:sigmavis_ss_backg}
@@
 \newpage
-\item Afterglow: Systematic uncertainty due to afterglow background is determined by calculating the mean of the type 1 and type 2 afterglow residuals that are defined as the ratio of the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch and ratio of the luminosity of the second and following empty bunches after a colliding bunch to the luminosity of the colliding bunch respectively.
+\item Afterglow: Systematic uncertainty due to afterglow background is determined by calculating the mean of the type 1 and type 2 afterglow residuals.
+Type 1 afterglow residuals are determined by the ratio of the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch.
+Type 2 afterglow residuals focus on the luminosity of the second  empty bunches after a colliding bunch, compared to the luminosity of the colliding bunch itself.
+  %that are defined as the ratio of the luminosity of the first empty bunch immediately following a colliding bunch to the luminosity of the colliding bunch and ratio of the luminosity of the second empty bunches after a colliding bunch to the luminosity of the colliding bunch respectively.
 

### 2024-03-28 tesis_Ashish/Chapter7/chapter7.tex
update 28 Mar

@@
   \includegraphics[width=1 \columnwidth]{ashish_thesis/it_newgeometry_.png}
-  \caption[Phase II CMS Inner Tracker]{ \onehalfspacing A layout of the CMS Phase II Inner Tracker showing four TEPX disks, eight TFPX disks and four TBPX layers \cite{Collaboration:275907420}.}
+  \caption[Phase 2 CMS inner tracker]{ \onehalfspacing A layout of the CMS Phase II Inner Tracker showing four TEPX disks, eight TFPX disks and four TBPX layers \cite{Collaboration:275907420}.}
   \label{fig:Innertracker}
@@
 
-\item The CMS Tracker's Phase II upgrade includes the Timing Layer, equipped with Low Gain Avalanche Detectors (LGAD) to improve time measurement of charged particles.
+\item The CMS Tracker Phase II upgrade includes the Timing Layer, equipped with Low Gain Avalanche Detectors (LGAD) to improve time measurement of charged particles.
 This enhancement helps distinguish particles from different vertices, reducing pileup in event reconstruction.
@@
   \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_clusters_2.png}
-  \caption[TEPX Cluster Map]{TEPX cluster map in the XY plane for pileup 200 simulated sample having 5000 events. %Map showing coordinates of TEPX clusters in CMS global coordinate system.
+  \caption[TEPX cluster map]{TEPX cluster map in the XY plane for pileup 200 simulated sample having 5000 events. %Map showing coordinates of TEPX clusters in CMS global coordinate system.
     It shows clusters in one TEPX disk consisting of 5 rings.
@@
   \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_D4R!_clusters._allpu_1.png}
-  \caption[D4R1 Clusters All Pileup]{Distribution of number of clusters for TEPX Disk 4 Ring 1 for all pileup samples.}
+  \caption[D4R1 clusters all pileup]{Distribution of number of clusters for TEPX Disk 4 Ring 1 for all pileup samples.}
   \label{fig:tepx_cl_allPU}
@@
   \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_2.png}
-  \caption[TEPX cluster linear fit per disk]{\onehalfspacing Left: Simulated mean number of clusters for TEPX disks as a function of pileup.
+  \caption[TEPX clusters linear fit per disk]{\onehalfspacing Left: Simulated mean number of clusters for TEPX disks as a function of pileup.
 A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.
@@
 \includegraphics[width=0.6\textwidth]{ashish_thesis/twofoldinphi.png}
-\caption[Module Overlap Two Fold Coincidences in phi]{%                                                                                                                                     
+\caption[Module Overlap two-fold coincidences in phi]{%                                                                                                                                     
   Example of module overlap between same ring modules that can give rise to two fold coincidences in phi.
@@
 \includegraphics[width=0.7\textwidth]{ashish_thesis/dr_dphi_variables1_1.png}
-\caption[New Variables For Two Fold Coincidences]{%
+\caption[New variables for two-fold coincidences]{%
   r, $\phi$ variables used to define coincidence clusters. %These variables take into account track angle and curvature.
@@
 \includegraphics[width=1\textwidth]{ashish_thesis/D4R1_S2_drdphi_cut_2.png}
-\caption[Pileup 0.5 Cluster Count in D4R1 vs. dr & d$\phi$]{%
+\caption[Pileup 0.5 cluster count in D4R1 vs. dr and d$\phi$]{%
   Distribution of cluster count as a function of dr and d$\phi$ variables for pileup 0.5 for Disk 4 Ring 1.
@@
 \includegraphics[width=0.3\textwidth]{ashish_thesis/twofoldinr_exam.png}
-\caption[Examples of two fold coincidences in r]{%
+\caption[Examples of two-fold coincidences in r]{%
   Definition of two-fold coincidences in r from the module overlap regions.
@@
   \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_D4R1_coin_allpu_1.png}
-  \caption[TEPX D4R1 Two-Fold Coincidences All Pileup]{Distribution of number of two-fold coincidences for TEPX Disk 4 Ring 1 for all pileup values \cite{Collaboration:275907420}.}
+  \caption[TEPX D4R1 two-fold coincidences all pileup]{Distribution of number of two-fold coincidences for TEPX Disk 4 Ring 1 for all pileup values \cite{Collaboration:275907420}.}
   \label{fig:tepx_coin_allPU}
@@
   \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_4.png}
-  \caption[TEPX two-fold coincidences linear fit for Disk 4 Ring 1]{\onehalfspacing Left: Simulated mean number of two-fold coincidences in phi for TEPX Disk 4 Ring 1 as a function of pileup.
+  \caption[TEPX two-fold coincidences linear fit for Disk 4 Ring 1]{\onehalfspacing Left: Simulated mean number of two-fold coincidences in $\phi$ for TEPX Disk 4 Ring 1 as a function of pileup.
 A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200.
@@
   \includegraphics[width=0.7\columnwidth]{ashish_thesis/tepx_threefold_allpu.png}
-  \caption[TEPX Disk 4 Ring 2 Three Fold Coincidences]{Distribution of number of three fold coincidences for TEPX Disk 4 Ring 2 for all pileup values.}
+  \caption[TEPX Disk 4 Ring 2 three-fold coincidences]{Distribution of number of three fold coincidences for TEPX Disk 4 Ring 2 for all pileup values.}
   \label{fig:tepx_3foldcoin_allPU_2}
@@
   \includegraphics[width=1\columnwidth]{ashish_thesis/TEPX_threefold_linearity.png}
-  \caption[Disk 4 all rings Three-Fold Coincidences Linearity]{Left: Simulated mean number of three-fold coincidences for all Disk 4 rings as a function
+  \caption[Disk 4 all rings three-fold coincidences linearity]{Left: Simulated mean number of three-fold coincidences for all Disk 4 rings as a function
     of pileup. Right: Deviation from linearity for Disk 4 all rings, the relative difference between the data points and the values of the fit function at the respective pileup value.}

### 2024-03-30 tesis_Ashish/Chapter5/chapter5.tex
update 30 Mar

@@
 
-\item Bunch to bunch uncertainty: The "bunch to bunch variation of PCC visible cross section" refer to how much the measured visible cross-section (and thus, the measured luminosity) changes from one bunch crossing to another as shown in Table \refl{tab:my_labeltt}.
+\item Bunch to bunch uncertainty: The "bunch to bunch variation of PCC visible cross section" refer to how much the measured visible cross-section (and thus, the measured luminosity) changes from one bunch crossing to another as shown in Table \ref{tab:my_labeltt}.
 Variations could arise from different factors such as varying numbers of protons per bunch, spatial distribution of protons within the bunches, and the specific conditions of the pixel detector at the time of each bunch crossing.

### 2024-03-31 tesis_Ashish/Chapter5/chapter5.tex
update 1 April

@@
 A value of  $\chi^2$/ndof close to 1 can be seen in the statistics box which signifies a good fit.
-The PCC visible cross section is 1076 $\pm$ 0.9 (stat) mb.
+The variation of $\chi^2$/ndof across scans is shown in Fig.
+\ref{fig:period_bound_510}.
+From this plot, we can observe that the average fit quality of the data to the model, as measured by the chi-squared per degree of freedom (chi2/ndof), is slightly above the ideal value of 1, with a mean of approximately 1.55.
+This suggests that the model fits the data reasonably well overall, but there may be some systematic deviation.
+The consistency of fit quality across different scans, both X and Y, indicates that no significant discrepancy exists between these two scanning directions within the range of values presented.
+The change in beam overlap width across scans is shown in Fig.
+\ref{fig:period_bound_520}.
+The plot reveals an asymmetry in beam overlap widths, with the X-Scans showing higher CapSigma values than the Y-Scans in all scans, indicating a larger beam width along the X-axis.
+The Y-Scans exhibit narrower and more uniform widths, suggesting a more stable overlap along the Y-axis.
+This consistent difference in the overlap widths between the X and Y scans is evident across various vdM and beam imaging scans.The PCC visible cross section is 1076 $\pm$ 0.9 (stat) mb.
 The bunch to bunch variation and scan to scan variation of the PCC visible cross section is shown in Fig.
@@
 \label{fig:period_bound_50}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/DGConst_chi2.jpeg}
+\caption{%                                                                                                                                                                  
+  $\chi^2$/ndof for all vdM and imaging scans.
+}
+\label{fig:period_bound_510}
+\end{figure}
+
+\begin{figure}[!htp]
+\centering
+\includegraphics[width=1\textwidth]{ashish_thesis/DGConst_CapSigma.jpeg}
+\caption[Beam overlap widths]{%
+
+  Beam overlap widths for each vdM and imaging scans.
+}
+\label{fig:period_bound_520}
 \end{figure}

### 2024-03-31 tesis_Ashish/Chapter7/chapter7.tex
update 1 April

@@
   \centering
-  \caption[dr offset values for two-fold in $\phi$]{dr mean values (mm) obtained from fit for two fold coincidences in $\phi$ for all disks and rings}
+  \caption[dr offset values for two-fold in $\phi$]{dr mean values (mm) obtained from fit for two-fold coincidences in $\phi$ for all disks and rings}
   \begin{tabular}{cccccc}
@@
   \centering
-  \caption[dr cut values for two-fold in $\phi$]{dr cut values (mm) for two fold coincidences in $\phi$ for all disks and rings}
+  \caption[dr cut values for two-fold in $\phi$]{dr cut values (mm) for two-fold coincidences in $\phi$ for all disks and rings}
   \begin{tabular}{cccccc}
@@
   \centering
-  \caption[d$\phi$ cut values for two-fold in $\phi$]{d$\phi$ cut values for two fold coincidences in $\phi$ for all disks and rings}
+  \caption[d$\phi$ cut values for two-fold in $\phi$]{d$\phi$ cut values for two-fold coincidences in $\phi$ for all disks and rings}
   \begin{tabular}{cccccc}
@@
 \includegraphics[width=0.6\textwidth]{ashish_thesis/twofoldinphi_sch_1.png}
-\caption[Map Of Two Fold Coincidences in $\phi$]{%                                                                                                            
+\caption[Map Of two-fold coincidences in $\phi$]{%                                                                                                            
    X-Y map of reconstructed two-fold coincidences in $\phi$ showing module overlap regions.
@@
 \includegraphics[width=0.6\textwidth]{ashish_thesis/l1l2_l3l4_2xinr_2.png}
-\caption[L1L2 and L3L4 Module Overlap Map for Two Fold Coincidences in r]{%
+\caption[L1L2 and L3L4 module overlap map for two-fold coincidences in r]{%
    X-Y map of reconstructed two-fold coincidences in r using the selections described in the text.

### 2024-04-01 tesis_Ashish/Chapter4/chapter4.tex
update 28 Mar
update 1 April

@@
 $\chi^2/ndof$ for vdM and imaging scans has an average value of 0.4514 where the Poly2G fit model converges for all BCIDs.
-Peak value and beam overlap $\Sigma_x$ and $\Sigma_y$ along X and Y are extracted from fit to calculate $\sigma_{vis}$.
+Peak value and beam overlap $\Sigma_x$ and $\Sigma_y$ along X and Y (shown in Fig.
+\ref{fig:fitquality_4040}) are extracted from fit to calculate $\sigma_{vis}$.
 %The $\sigma_{vis}$ per scan is averaged over all BCIDs and its scan to scan variation is shown in Fig.
@@
     \label{fig:fitquality}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1\textwidth]{ashish_thesis/Poly2G_CapSigma.jpeg}
+    \caption[Beam overlap widths]{Beam overlap widths for each vdM and imaging scans.}
+    \label{fig:fitquality_4040}
 \end{figure}
@@
 Noise can lead to spurious signals that can be misinterpreted as genuine events, leading to an overestimate of the luminosity.
-Conversely, high noise levels can also mask genuine events, leading to an underestimate of the luminosity.
+Conversely, high noise levels can also mask genuine events, leading to an overestimate of the luminosity.
 %Noise can be suppressed using data analysis techniques, but this is not always perfect, and residual noise can introduce a systematic uncertainty.

### 2024-04-10 tesis_Ashish/Chapter4/chapter4.tex
update 11 Apr

@@
 
+\begin{comment}
+
 \begin{figure}[h]
@@
 ine change in detector response over different luminosity levels. Slope of the linear fit is 7.2e^{-7} $in units of \:$ (Hz/ub)^{-1}.}
+  \label{fig:stabprof2}
+\end{figure}
+
+\end{comment}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=1\textwidth]{ashish_thesis/PCC_lin_2018.png}
+  \caption[2018 PCC linearity]{Linearity of PCC compared to HFOC for fill 6961.
+Ratio of PCC/HFOC luminosity plotted as a function of HFOC luminosity to determine change in detector response over different luminosity levels.
+Slope of the linear fit is 0.00154614 in units of (Hz/ub)^{-1}.}
   \label{fig:stabprof2}

### 2024-05-31 project_Julio/paper.tex
commit1
commit2

--- 2023-11-14 project_Luis_PhD/paper.tex
@@
 
-\def\Student{Luis Enrique Cuevas  Picos}
+\def\Student{Julio C\'{e}sar Borb\'{o}n Fragoso}
 \def\Title{ANTEPROYECTO}
-\def\Prog{Doctorado en Ciencias (F\'{i}sica) }
+\def\Prog{Maestr\'{i}a en Ciencias (F\'{i}sica) }
 \def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
@@
 
-This research project proposes to enhance the precision of luminosity measurements at the LHC during Run 2 and Run 3, while also developing an upgraded luminosity measurement system for the HL-LHC phase.
+This research project proposes to enhance the precision of luminosity measurements at the LHC during Run 2 and Run 3.
 Accurate luminosity measurements are crucial for understanding particle physics, including Higgs boson production.
 The research involves analyzing the CMS pixel detector, calibrating it for 13.6 TeV collisions, and addressing systematic uncertainties.
-Additionally, it explores the Tracker Endcap
-Pixel Detector's (TEPX) performance for HL-LHC conditions and develops new cluster counting algorithms.
-The project contributes to high-precision particle physics and will result in peer-reviewed publications and conference presentations.
 
@@
 The heavy particles ($W^{\pm}$, $Z^0$, $H$, and top) can only be produced at high energy particle colliders like the Large Hadron Collider (LHC) operating at a center-of-mass energy of 13 TeV in Geneva, Switzerland.
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.6\columnwidth]{./sm1.png}
+  \caption{Particles of the Standard Model
+
+  }
+  \label{figure1}
+\end{figure}
+
+The large hadron collider (LHC) is the world largest and more powerful particle accelerator.
+It first started in 10 september of 2008 and remains the latest addition to CERN's accelerator complex.
+The LHC consist of a 27 kilometer ring of superconducting magnets with a number of accelerating structures to boost the energy of the particles along the way.
+All the controls for the accelerator, its services and technical infrastructure are housed under one roof at the CERN Control Centre.
+From here, the beams inside the LHC are made to collide at four locations around the accelerator ring, corresponding to the positions of four particle detectors; Atlas, CMS, Alice and LHCb.
+
 Until the 90s, existence of almost all the SM particles were confirmed except the top quark and the Higgs boson. 
@@
 \footnote{1 barn is a unit of area corresponding to $10^{-24}$ cm${^2}$ and 1 femtobarn (fb) = $10^{-39}$ cm$^{2}$. For comparison, the total Higgs production cross section is 48600 fb.}.
+
 In the first part of Run 2 (2015-2016), the delivered luminosity has been measured to be \lumi{38.4} with an unprecedented precision of 1.3\% \cite{Sirunyan:2021qkt}.
@@
 The LHC Run 3 began in 2022 and will last until 2024, with an expected integrated luminosity of about \lumi{450} \cite{lumi-run3}.
-
-The  High Luminosity LHC (HL-LHC), and corresponding integrated luminosities of order \lumi{3000} as shown in Figure~\ref{figure6}.
-These datasets will provide  precise measurements of the properties of the Higgs boson and other SM particles as shown in Fig. ~\ref{figureKappasUncs}.
-This figure shows that one of the dominant uncertainties which remain to be determined is due to the luminosity measurement.
 
@@
   }
-  \label{figure5}
+  \label{figure2}
 \end{figure}
@@
   \centering
-   \includegraphics[width=0.7\columnwidth]{./pg.png}
-   \includegraphics[width=0.29\columnwidth]{./higgs_couplings.png}
+  \includegraphics[width=0.8\columnwidth]{./upsche.png}
   \caption{
-     Left: Main production mechanisms for the Higgs boson at the LHC: gluon-gluon fusion (ggF), vector-boson fusion (VBF), associated vector boson (VH), associated top-quark pair (ttH), and  associated single-top quark production (tH)  \cite{Grojean:2017hsb}  \cite{Khachatryan:2015ota} .
-     Right: Expected uncertainties on the Higgs coupling parameters for  \lumi{3000} of proton-proton collision data at 13 TeV center-of-mass energy \cite{Cepeda:2019klc}.
+    Update performance of the LHC until year 2042, notice that some values are different to those show in figure 4.
+Points show instantaneous luminosity while the line shows luminosity accumulated \cite{collaborations2019report}.
   }
-   \label{figureKappasUncs}
+  \label{figure6}
 \end{figure}
@@
 
-In this project, we aim to make the most precise measurements of the luminosity for the Run 2 (2017-2018) as well as for the Run 3 data taking period (2022-2024).
-In addition we expect to perform studies for the design and construction of an upgraded luminosity measurement system to be installed for CMS in the HL-LHC phase \cite{Collaboration:2706512}.
+In this project, we aim to make the most precise measurements of the luminosity for the Run 3 data taking period (2022-2024).
 
@@
 \begin{equation}
-  \sigma_{vis}=\frac{2\pi \Sigma_{x} \Sigma_{y} R(0, 0)}{N_{1}N_{2} f}
+  \sigma_{vis}=\frac{R_{det}}{L_{b}}=\frac{2\pi \Sigma_{x} \Sigma_{y} R(0, 0)}{N_{1}N_{2} f}
   \label{sigmavis_eq}
@@
 
-For the upgrade part of this project, the research consists of studying the expected performance of the TEPX disks of the CMS tracker in the HL-LHC phase.
-The current design of the this tracker is shown in Figure~\ref{fig:tepx}, where the TEPX part consists of the last 4 disks at $|z|>170$ cm.
-In the same figure a transverse view of one disk is shown, and shows the layout of the sensor modules along phi for each ring in the disk \cite{Klein:2017nke}.
-Studies will be performed using simulated samples with HL-LHC beam conditions, currently the expected pileup for these conditions is about 200 proton collisions per bunch crossing.
-The linearity of the cluster counting algorithm will be studied.
-In addition, a new algorithm may be developed to detect cluster coincidences between consecutive layers of a disk.
 %It is expected that coincidences will be less sensitive to backgrounds in HL-LHC pileup conditions and therefore a more robust luminosity measurement can be performed.
@@
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.7\columnwidth]{./TEPX_rz.pdf}
-  \includegraphics[width=0.27\columnwidth]{./TEPX_rphi.pdf}
-  \caption{
-    Left: Longitudial view of the current design of the CMS tracker detector for the HL-LHC phase. The TEPX consists of the last 4 disks on each side at $|z|>$ 1700 mm.
-    Right: Transverse view of one TEPX disk showing the layout of the sensors in each of the 5 rings \cite{Klein:2017nke}.
-  }
-  \label{fig:tepx}
-\end{figure}
-
 \section{SPECIFIC OBJECTIVES}
@@
 \par
-For the development of the HL-LHC upgrade system:
-\begin{itemize}
-\item Study the different parts of the TEPX detector.
-\item Study the pixel cluster counting at the HL-LHC conditions using simulations of the TEPX detector.
-\item Develop algorithms for pixel  cluster counting and coincidence counting.
-\item determine the linearity and  precision of the different methods.
-\end{itemize}
 
@@
 Similar studies as for the Run 2 dataset will be performed completed and a preliminary result of the luminosity measurement will be published.
-\item For the development of the HL-LHC upgrade system, the work  will be based on the previously published Technical Design Report (TDR) with the proposed design and algorithms to use the TEPX detector.
-It is expected that this work will be used for the final design and construction of the system to be installed in the LS3 (2025-2027).  
 \end{itemize}
@@
 Additional benefits entail becoming a member of the CMS collaboration, presenting results at international and national scientific conferences, and contributing to the development of new technology for the HL-LHC project.
-
-\section{CALENDAR OF ACTIVITIES}
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=\columnwidth]{./calendario.pdf}
-  \caption{ Calendar of activities }
-  \label{fig:calendario}
-\end{figure}
 

### 2024-06-05 project_Julio/paper.tex
commit3

@@
 
-This research project proposes to enhance the precision of luminosity measurements at the LHC during Run 2 and Run 3.
+This research project proposes to measure the luminosity from RUN 3 made in 2024 with the CMS data using mainly the PCC method.
 Accurate luminosity measurements are crucial for understanding particle physics, including Higgs boson production.
@@
 
-In this project, we aim to make the most precise measurements of the luminosity for the Run 3 data taking period (2022-2024).
+In this project, we aim to make the measurements of the luminosity for the preliminary data from Run 3 take on 2024 using the Pixel Cluster Counting (PCC) method.
 
@@
 
-The main objective of this work is to improve on the precision of the preliminary luminosity measurements for the different datasets with the aim to provide a final precision at the level of 1\%.
+The main objective of this work is to obtain calibration data for 2024 aiming for a uncertainty less than 2\% in this Run.
+This is results are important for CMS to compare physical process with the Standard Model, these results are likely to be presented on conferences and reviews on 2025.
 This precision is needed for the measurement of many important physics processes, like the Higgs boson production crossection, which define the Standard Model of particle physics.
@@
 This low occupancy makes the PCC  very linear as a function of pileup, an essential property of a good luminometer \cite{Sirunyan:2021qkt}.
+
+In order to evaluate the total number of events we used integrated luminosity, it is a measurement of the collected data size, and it is important value to characterize the performance of an accelerator, defined as: \\
+
+\begin{center}
+$L_{inst} = \int _{0}^{t} L_{inst}(t') dt'$ \\ 
+\end{center}
+
+Because it directly relates to the number of observed events; L_{int} \dot \sigma_{p} = number of events of interest. \\
 
@@
 
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.7\columnwidth]{./integratedlum.png}
+  \caption{
+   Total integrated luminosity from previous data from CMS
+  }
+  \label{Integrated luminosity}
+\end{figure}
+
 \section{SPECIFIC OBJECTIVES}
 
-For the Run 2 and Run 3 luminosity measurements:
+For Run 3 2024 luminosity measurements:
 \begin{itemize}
 \item Understand the CMS pixel detector layout including the barrel layers and endcap disks and their constituent modules.
-\item Study the stability of the modules in the different layers or disks of the pixel detector and select the stable components.
+\item Study the evolution of the parameters of photon beams
 \item Calculate the calibration constant (visible crossection) corresponding to 13.6 TeV proton-proton collision data.
 \item Study the stability and linearity of the PCC luminosity measurement by comparing to other CMS luminometers.
+\item Study the variation function in function of the scan with time
 \item Determine the instantaneous and the total integrated luminosity.
@@
 
-From this project two main publications are expected:
+From this project the following is expected:
 \begin{itemize}
-\item For the Run 2 luminosity mesurement, studies of the selection of good detector modules, calibration, background estimation, and calculation of the integrated luminosity, including the systematic uncertainties will be completed.
-The results of these studies will be published in a peer-reviewed scientific journal.
-\item For the Run 3 luminosity measurement, no measurement of the luminosity precision has been performed at this moment.
-Similar studies as for the Run 2 dataset will be performed completed and a preliminary result of the luminosity measurement will be published.
+\item From 2024 data compute the uncertainty from the calibration to contribute with the luminosity measurement in 2024.  
 \end{itemize}
-
-Additional benefits entail becoming a member of the CMS collaboration, presenting results at international and national scientific conferences, and contributing to the development of new technology for the HL-LHC project.
 

### 2024-06-06 project_Julio/paper.tex
commit4

@@
 The instantaneous luminosity $L(t)$ is the process-independent ratio between the rate $R(t)$ of events produced per unit time and the cross section for a given process $\sigma$:  $R(t) = \sigma L(t)$.
+
+In order to evaluate the total number of events we used integrated luminosity, it is a measurement of the collected data size, and it is important value to characterize the performance of an accelerator, defined as: \\
+
+\begin{center}
+$L_{inst} = \int _{0}^{t} L_{inst}(t') dt'$ \\ 
+\end{center}
+
+Because it directly relates to the number of observed events; $L_{int} \dot \sigma_{p}$ = number of events of interest. \\
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.7\columnwidth]{./integratedlum.png}
+  \caption{
+   Total integrated luminosity from previous data from CMS
+  }
+  \label{Integrated luminosity}
+\end{figure}
+
 During Run 1 (2011-2012) LHC reached a peak instantaneous luminosity of \instlumi{0.77} and delivered an integrated luminosity of about \lumi{25} with a precision of about 2.0\% 
@@
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.8\columnwidth]{./upsche.png}
-  \caption{
-    Update performance of the LHC until year 2042, notice that some values are different to those show in figure 4.
-Points show instantaneous luminosity while the line shows luminosity accumulated \cite{collaborations2019report}.
-  }
-  \label{figure6}
-\end{figure}
-
 \section{PROPOSAL}
@@
 The main objective of this work is to obtain calibration data for 2024 aiming for a uncertainty less than 2\% in this Run.
-This is results are important for CMS to compare physical process with the Standard Model, these results are likely to be presented on conferences and reviews on 2025.
+This results are important for CMS to compare physical process with the Standard Model, these results are likely to be presented on conferences and reviews on 2025.
 This precision is needed for the measurement of many important physics processes, like the Higgs boson production crossection, which define the Standard Model of particle physics.
@@
 
-Based on the previous work on the Run 2 (2015-2016) datasets which have achieved a precision at the level of 1.3\%, we expect that a precision at this level or lower will be possible due to the improved methods we are developing.
-For reference, the current precision on the Run 2 (2017-2018) and Run 3 (2022) datasets is above 2\%~\cite{Sirunyan:2021qkt}.
+Based on the previous work on the Run 2 (2015-2016) datasets which have achieved a uncertainty of  2.3\% \cite{Collaboration:121}, we expect that a precision at 2\% will be possible due to the improved methods we are developing.
+For reference, the current systematic uncertainty on the Run 2 2017 was 2.3\% \cite{Collaboration:122} for 2018 was 2.5\% \cite{Collaboration:123} and for Run 3 (2022) was 1.4\% \cite{Collaboration:124}.
 
@@
 
-The PCC method for measuring luminosity uses the Pixel detector of the CMS tracker, the layout of the  detector used for recording the data during 2016-2018 is shown in Figure~\ref{fig:pixeldet},  this detector is expected to deliver high-quality data until the end of LHC Run 3 (currently expected for 2024).
+The PCC method for measuring luminosity uses the Pixel detector of the CMS tracker, the layout of the  detector used for recording the data during 2016-2018 is shown in Figure~\ref{fig:pixeldet},  this detector is expected to deliver high-quality data until the end of LHC Run 3 (currently expected for 2025).
 The Pixel detector consists of 4 concentric cylindrical layers in the barrel and 3 disks in each endcap.
@@
 This low occupancy makes the PCC  very linear as a function of pileup, an essential property of a good luminometer \cite{Sirunyan:2021qkt}.
-
-In order to evaluate the total number of events we used integrated luminosity, it is a measurement of the collected data size, and it is important value to characterize the performance of an accelerator, defined as: \\
-
-\begin{center}
-$L_{inst} = \int _{0}^{t} L_{inst}(t') dt'$ \\ 
-\end{center}
-
-Because it directly relates to the number of observed events; L_{int} \dot \sigma_{p} = number of events of interest. \\
 
@@
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.7\columnwidth]{./integratedlum.png}
-  \caption{
-   Total integrated luminosity from previous data from CMS
-  }
-  \label{Integrated luminosity}
-\end{figure}
-
 \section{SPECIFIC OBJECTIVES}
@@
 \item Understand the CMS pixel detector layout including the barrel layers and endcap disks and their constituent modules.
-\item Study the evolution of the parameters of photon beams
-\item Calculate the calibration constant (visible crossection) corresponding to 13.6 TeV proton-proton collision data.
+\item Study the evolution of the parameters of proton beams
+\item Calculate the calibration constant $\sigma_{vis}$ corresponding to 13.6 TeV proton-proton collision data.
+\item Study the variation of $\sigma_{vis}$ in function of the scan with time
+\item Determine the systematic uncertainties on the calibration constant.
+\item Determine the systematic uncertainties on the integrated luminosity.
 \item Study the stability and linearity of the PCC luminosity measurement by comparing to other CMS luminometers.
-\item Study the variation function in function of the scan with time
 \item Determine the instantaneous and the total integrated luminosity.
-\item Determine the systematic uncertainties on the calibration constant and on the integrated luminosity.
 \end{itemize}
@@
 \begin{itemize}
+\item Calibration of the PCC luminometer and the corresponding uncertainty.
+\iten Preliminary measurements of the 2024 integrated luminosity for CMS
 \item From 2024 data compute the uncertainty from the calibration to contribute with the luminosity measurement in 2024.  
+\item A presentation of the results at a national conference. 
 \end{itemize}
+
+\section{Semestral calendary of the project}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.7\columnwidth]{./diagram.jpeg}
+  \caption{
+   Diagram of this project
+  }
+  \label{Grantt Diagram}
+\end{figure}
+
+\section{Abilities to be develop by the student}
+\begin{itemize}
+\item Develop software abilities
+\item Learn programation language  C, C++, Python.
+\item Learn how to use Compute Cluster, Latex, Root, etc.
+\item Data analysis 
+\item Statistical analysis
+\item Review publication
+\end{itemize}
+
+\section{Mobility actions}
+We expect to present the results on a congress the next year 2025.
 

### 2024-06-07 project_Julio/paper.tex
commit4_1

@@
 Based on the previous work on the Run 2 (2015-2016) datasets which have achieved a uncertainty of  2.3\% \cite{Collaboration:121}, we expect that a precision at 2\% will be possible due to the improved methods we are developing.
-For reference, the current systematic uncertainty on the Run 2 2017 was 2.3\% \cite{Collaboration:122} for 2018 was 2.5\% \cite{Collaboration:123} and for Run 3 (2022) was 1.4\% \cite{Collaboration:124}.
+For reference, the current systematic uncertainty on the Run 2 2017 was 2.3\% \cite{CMS:2018elu} for 2018 was 2.5\% \cite{CMS:2018} and for Run 3 (2022) was 1.4\% \cite{Collaboration:124}.
 
@@
 \onehalfspacing
-\bibliographystyle{unsrt}
+\bibliographystyle{plain}
 \bibliography{paper}

### 2024-06-07 project_Julio/paper.tex
commit5

@@
 The Higgs boson ($H$), is the last of the gauge bosons, it gives mass to the other SM particles via electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}.
-The heavy particles ($W^{\pm}$, $Z^0$, $H$, and top) can only be produced at high energy particle colliders like the Large Hadron Collider (LHC) operating at a center-of-mass energy of 13 TeV in Geneva, Switzerland.
 
@@
 
-The large hadron collider (LHC) is the world largest and more powerful particle accelerator.
+The heavy particles ($W^{\pm}$, $Z^0$, $H$, and top) can only be produced at high energy particle colliders like the Large Hadron Collider (LHC) operating at a center-of-mass energy of 13 TeV in Geneva, Switzerland.
+The large hadron collider (LHC) is the world largest and most powerful particle accelerator.
 It first started in 10 september of 2008 and remains the latest addition to CERN's accelerator complex.
@@
 All the controls for the accelerator, its services and technical infrastructure are housed under one roof at the CERN Control Centre.
-From here, the beams inside the LHC are made to collide at four locations around the accelerator ring, corresponding to the positions of four particle detectors; Atlas, CMS, Alice and LHCb.
+From here, the beams inside the LHC are made to collide at four locations around the accelerator ring, corresponding to the positions of four particle detectors; ATLAS, CMS, ALICE and LHCb.
 
@@
 
-In order to evaluate the total number of events we used integrated luminosity, it is a measurement of the collected data size, and it is important value to characterize the performance of an accelerator, defined as: \\
+In order to evaluate the total number of events we use integrated luminosity, it is a measurement of the collected data size, and it is important value to characterize the performance of an accelerator, defined as: \\
 
 \begin{center}
-$L_{inst} = \int _{0}^{t} L_{inst}(t') dt'$ \\ 
+$L_{int} = \int _{0}^{t} L(t') dt'$ \\ 
 \end{center}
 
-Because it directly relates to the number of observed events; $L_{int} \dot \sigma_{p}$ = number of events of interest. \\
+Because it directly relates to the number of observed events; $L_{int} \sigma$ = number of events of interest. \\
 
@@
 For the second part of Run 2 (2017-2018), the integrated luminosity is about \lumi{78}, but its precise value and uncertainty remain to be determined \cite{CMS:2018elu}.
-The plan of the LHC till year 2038 is to obtain datasets with up to 10 times higher values of instanteneous luminosities in the final phase.
 The LHC Run 3 began in 2022 and will last until 2024, with an expected integrated luminosity of about \lumi{450} \cite{lumi-run3}.
@@
 
-The main objective of this work is to obtain calibration data for 2024 aiming for a uncertainty less than 2\% in this Run.
+The main objective of this work is to obtain the calibration constant for the PCC luminometer with 2024 data aiming for a uncertainty less than 2\% in this Run.
 This results are important for CMS to compare physical process with the Standard Model, these results are likely to be presented on conferences and reviews on 2025.
@@
 
-Based on the previous work on the Run 2 (2015-2016) datasets which have achieved a uncertainty of  2.3\% \cite{Collaboration:121}, we expect that a precision at 2\% will be possible due to the improved methods we are developing.
-For reference, the current systematic uncertainty on the Run 2 2017 was 2.3\% \cite{CMS:2018elu} for 2018 was 2.5\% \cite{CMS:2018} and for Run 3 (2022) was 1.4\% \cite{Collaboration:124}.
+Based on the previous work on the Run 2 (2015-2016) datasets which have achieved a uncertainty of  2.3\% \cite{Collaboration:121}, the current systematic uncertainty on the Run 2 2017 was 2.3\% \cite{CMS:2018elu} for 2018 was 2.5\% \cite{CMS:2018} and for Run 3 (2022) was 1.4\% \cite{Collaboration:124}.
+We expect that a precision at 2\% will be possible due to the improved methods we are developing.
 
@@
 These scans are performed by varying the separation between the beams in each direction ($x$ and $y$) at a fixed number of separation steps of about 100 micrometers.
-Then these rates are fitted by a Gaussian function to obtain the beam overlaps $\Sigma_{x,y}$ and the peak rate of clusters $R(0,0)$ \cite{CMS:2018}.
+Then these rates are fitted by a Gaussian model to obtain the beam overlaps $\Sigma_{x,y}$ and the peak rate of clusters $R(0,0)$ \cite{CMS:2018}.
 A schematic view of this method is shown in Fig.
@@
 \end{equation}
-Where $f$  is the LHC frecuency and $N_{1},N_{2}$ are the buch current used to normalize  the rates.
+Where $f$  is the LHC frecuency and $N_{1},N_{2}$ are the number of protons in each colliding bunch, determined from the beam currents.
 This calibration constant is then used to determine the luminosity during a normal running throughout the data-taking year \cite{CMS:2018}.
@@
 \item Calibration of the PCC luminometer and the corresponding uncertainty.
-\iten Preliminary measurements of the 2024 integrated luminosity for CMS
+\item Preliminary measurements of the 2024 integrated luminosity for CMS
 \item From 2024 data compute the uncertainty from the calibration to contribute with the luminosity measurement in 2024.  
@@
 
-\section{Semestral calendary of the project}
+\section{Calendar of activites}
 
@@
   \centering
-  \includegraphics[width=0.7\columnwidth]{./diagram.jpeg}
+  \includegraphics[width=0.7\columnwidth]{./diag.jpeg}
   \caption{
@@
 \item Learn programation language  C, C++, Python.
-\item Learn how to use Compute Cluster, Latex, Root, etc.
-\item Data analysis 
-\item Statistical analysis
-\item Review publication
+\item Learn how to use High Performance Computer, Latex and Root
+\item Data analysis and Statistical analysis
+\item Publication of results
 \end{itemize}
@@
 \section{Mobility actions}
-We expect to present the results on a congress the next year 2025.
-
-%\begin{itemize}
-%
-%\item {\bf Semester 1 (2023-2)}:
-%  \SubItem{ Readings on Standard Model of physics theory, LHC, and CMS experiments.}
-%  \SubItem{ Review of the literature.}
-%  \SubItem{ Master Linux computing and data analysis  skills (\textsc{Bash, Emacs, Root, HTCondor parallel processing.})}
-%  \SubItem{ Complete work on the 2022 luminosity measurement for a preliminary  publication.}
-%
-%\item {\bf Semester 2 (2024-1)}:
-%  \SubItem{ Course I on particle physics, particle detection, or data analysis.}
-%  \SubItem{ Continue readings on Standard Model of physics theory, LHC, and CMS experiments.}
-%  \SubItem{ Master Linux computing and data analysis  skills (\textsc{Bash, Emacs, Root, HTCondor parallel processing.})}
-%  \SubItem{ Complete work on the Run 2 luminosity measurement for a final  publication.}
-%  \SubItem{ Start work on the 2023 dataset luminosity measurement. }
-%  
-%\item {\bf Semester 3 (2024-2)}:
-%  \SubItem{ Course II on particle physics, particle detection, or  data analysis.}
-%  \SubItem{ Complete work on the 2023 dataset luminosity measurement.}
-%  \SubItem{ Start work on the 2024 dataset luminosity measurement. }
-%  
-%\item {\bf Semester 4 (2025-1)}:
-%  \SubItem{ Continue work on the 2024 dataset luminosity measurement. }
-%  \SubItem{ Start studies on the TEPX luminometer for the HL-LHC.}
-%  \SubItem{ Writing of the monograph.}
-%
-%\item {\bf Semester 5 (2025-2)}:
-%  \SubItem{ Complete work on the 2024 dataset luminosity measurement. }
-%  \SubItem{ Complete studies on the TEPX luminometer for the HL-LHC.}
-%  \SubItem{ Presentation at national or international conferences of the TEPX upgrade studies.}
-%  
-%\item {\bf Semester 6 (2026-1)}:
-%  \SubItem{ Start final studies of the Run 3 data luminosity measurement for publication in a peer reviewed journal.}
-%
-%\item {\bf Semester 7 (2026-2)}:
-%  \SubItem{ Completion of the studies of the Run 3 data luminosity measurement for publication in a peer reviewed journal.}
-%  \SubItem{ Presentations at national or international conferences of the luminosity measurements and TEPX luminometer for HL-LHC.}
-%  \SubItem{ Writing of the Ph.D thesis.}
-%  
-%\item {\bf Semester 8 (2027-1)}: 
-%  \SubItem{ Publication of the Run 3 data luminosity measurement in a peer reviewed journal.}
-%  \SubItem{ Presentations at national or international conferences of the luminosity measurements and TEPX luminometer for HL-LHC.}
-%  \SubItem{ Defense of the Ph.D thesis.}
-%  
-%\end{itemize}
+We expect to participate in a national conference on a congress the next year 2025.
 

### 2025-03-07 monograph_Luis/Abstract/abstract.tex
monografia

--- 2024-03-27 tesis_Ashish/Abstract/abstract.tex
@@
 
-The Pixel Cluster Counting (PCC) luminosity measurement method has emerged as a reliable offline technique for luminosity measurement developed for the CMS experiment.
-%The PCC method is based on the rate of pixel clusters in the CMS pixel detector, which is the innermost part of the CMS tracker.
-The PCC method is studied for its precision in luminosity measurement using 2017, 2018 and 2022  datasets.
-The results of these studies demonstrate that the PCC luminosity measurement method is stable and linear.
-%able to achieve final uncertainty on the luminosity measurement at the level of 1\% or better.
-Final systematic uncertainty achieved on luminosity measurement for 2018 and 2022 datasets are 2.2\% and
- 1.4\% respectively. %1\% systematic uncertainty on the final luminosity measurement.
-Moreover, the clusters and coincidences counting algorithms and their optimization for the Phase II High Luminosity LHC (HL-LHC) luminosity measurement are also developed, using simulated datasets for the proposed Phase II pixel detector.
-%This new pixel detector will replace the Run 2 pixel detector.
-Linearity of the Tracker endcap pixel (TEPX) and Disk 4 Ring 1 luminometers is expected to be within 1\% (offline) up to a pileup of 200 and their statistical precision per second is about 0.1\% at pileup 200.
-%It is expected to provide excellent statistical precision and linearity performance, which is essential for precision luminosity measurements at the HL-LHC.
-
 \end{abstract}

### 2025-03-07 monograph_Luis/Chapter1/chapter1.tex
monografia

--- 2023-05-03 tesis_Luis/Chapter1/chapter1.tex
@@
 
-%%%%% https://cerncourier.com/a/pushing-the-precision-frontier/
-% https://home.cern/news/news/physics/why-precision-luminosity-measurements-matter
-Particle physics is the branch of physics that focuses on studying the fundamental particles and forces that make up matter and radiation in the universe.
-The Standard Model classifies the fundamental particles and their interactions as fermions, which are matter particles, and bosons, which are force-carrying particles.
-High-energy particle accelerators are used to study these interactions by measuring various parameters and properties of the particles produced during collisions.
-This chapter provides a brief overview of elementary particles, particle colliders, and the measurement of their performance.
-It emphasizes the concepts and definitions necessary for understanding this thesis project.
-
 \section{Particle Physics and The Standard Model}
-
-The universe is composed of several different particles.
-Atoms are bound states of negatively charged electrons $(e^{-})$, which orbit around a central nucleus consisting of positively charged protons $(p)$ and electrically neutral neutrons $(n)$.
-The electrons are bound to the nucleus by the electrostatic attraction between opposite charges, while the protons and neutrons are held together by the strong nuclear force.
-Completing the fundamental interactions of particle physics are the weak force and gravity.
-The weak force is responsible for nuclear $\beta$ decays and nuclear fusion, while gravity, although extremely weak, is always attractive and therefore responsible for the large-scale structure in the universe.
-While this is a simple physical model, at higher energy scales, more complex structures are observed, leading to the discovery of 17 fundamental particles that make up our entire universe.
-These particles are divided into two groups: fermions with spin $1/2$ and bosons with integer spin \cite{thomson_2013}.\\
-
-Fermions are the particles that constitute matter, consisting of twelve fundamental particles classified into two types: leptons and quarks.
-These particles are further divided into three generations, with each member of a higher generation having a greater mass than the corresponding particle of the previous generation.
-The six leptons include three charged particles: electron ($e$\textsuperscript{-}), muon (${\mu}$\textsuperscript{-}), and tau (${\tau}$\textsuperscript{-}), as well as their corresponding neutrinos: electron-neutrino ($\nu_{e}$), muon-neutrino ($\nu_{\mu}$), and tau-neutrino ($\nu_{\tau}$).
-Quarks, on the other hand, can only be found in particles called hadrons.
-The group of quarks consists of the up quark ($u$), down quark ($d$), charm quark ($c$), strange quark ($s$), top quark ($t$), and bottom quark ($b$) \cite{griff,thomson_2013}.
-The properties of these twelve particles are summarized in Table \ref{tab:table1}.
-
-\begin{table}[h!]
-	\begin{center}
-%\centering
-	\caption{The twelve fundamental fermions divided into quarks and leptons.\
-The masses of the quarks are the current masses \cite{thomson_2013}.}
-		\label{tab:table1}
-		\begin{tabular}{lllrcllrc}
-                                                                                & \multicolumn{4}{c}{\textbf{Leptons}}                                                                     & \multicolumn{4}{c}{\textbf{Quarks}}                                                \\
-%\cline{2-9}
- \midrule[1.1pt]
-                            \multicolumn{1}{c}{Generation }& \multicolumn{2}{c}{Particle } & \multicolumn{1}{c}{\textit{Q}} & mass/GeV                          & \multicolumn{2}{c}{Particle} & \multicolumn{1}{c}{\textit{Q}} & mass/GeV  \\
-\hline
-\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}First\end{tabular}}  & electron & ($e$\textsuperscript{-})                 & -1                             & 0.0005                            & down    & ($d$)                & -1/3                           & 0.003     \\
-                                                                                & $e$-neutrino & ($\nu_{e}$)                 & 0                              & \textless{}10\textsuperscript{-9} & up      & ($u$)                & +2/3                           & 0.005     \\
-\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Second\end{tabular}} & muon     & (${\mu}$\textsuperscript{-})                 & -1                             & 0.106                             & strange & ($s$)                & -1/3                           & 0.1       \\
-                                                                                & $\mu$-neutrino & ($\nu_{\mu}$)                 & 0                              & \textless{}10\textsuperscript{-9} & charm   & ($c$)                & +2/3                           & 1.3       \\
-\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Third\end{tabular}} & tau      & ({$\tau}$\textsuperscript{-})                 & -1                             & 1.78                              & bottom  & ($b$)                & -1/3                           & 4.5       \\
-                                                                                & $\tau$-neutrino & ($\nu_{\tau}$)                 & 0                              & \textless{}10\textsuperscript{-9} & top     &($t$)                & +2/3                           & 174
-\end{tabular}
-	\end{center}
-		\end{table}
-
-The bosons are responsible for describing the interactions between fermions through the exchange of particles.
-These exchange particles are known as gauge bosons and include the photon $\gamma$ for electromagnetic force, $W^{\pm}$ and $Z^{0}$ for the weak force and gluons $g$ for the strong force \cite{thomson_2013}.
-Additionally, there is a scalar boson called the "Higgs boson", which is associated with the mechanism that gives mass to all fundamental particles.
-The forces experienced by fermions can be seen in table  \ref{tab:table2}.
-
-\begin{table}[h!]
-  \begin{center}
-    \caption{Force experienced by the fermions \cite{thomson_2013}.}
-    \label{tab:table2}
-    \begin{tabular}{l c c c c}
-    &    &  \textbf{Electromagnetic} & \textbf{Weak} & \textbf{Strong}\\
-      \midrule[1.1pt]
-      \multirow{2}{*}{Leptons} & ${e}$\textsuperscript{-} \hspace{0.3cm}  ${\mu}$\textsuperscript{-} \hspace{0.3cm} ${\tau}$\textsuperscript{-} & \checkmark & \checkmark & \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
-      & $ \nu_{e} $ \hspace{0.3cm}  $\nu_{\mu}$ \hspace{0.3cm} $\nu_{\tau}$  &  & \checkmark\\ % <-- Content of first column omitted.
-      \hline
-      \multirow{2}{*}{Quarks} & $u$ \hspace{0.5cm}  $c$\hspace{0.5cm} $t$ & \checkmark & \checkmark& \checkmark\\
-      & $d$ \hspace{0.5cm}  $s$\hspace{0.5cm} $b$ & \checkmark & \checkmark & \checkmark\\
-
-    \end{tabular}
-  \end{center}
-\end{table}
-
-All of these particles are described by the Standard Model (SM), which is the best theoretical model to date for providing a successful description of experimental data.
-However, most of this data comes from particle colliders since these particles can only be produced and studied through collisions at high energy.
 
@@
 
-Most of the recent breakthroughs in particle physics have resulted from experiments conducted at high-energy particle accelerators.
-These accelerators are the most powerful microscopes for observing the tiniest inner structures of cells, genes, molecules, atoms, and their constituent particles such as protons, neutrons, electrons, neutrinos, and quarks.
-Moreover, they may also help discover yet unknown fundamental building blocks of the universe, such as dark matter and dark energy.\\
-
-Particle colliders produce and accelerate beams of charged particles at high speeds (close to the speed of light) using electromagnetic fields; the high-energy collisions of these beams produce individual interactions referred to as events.
-These collisions produce massive particles, such as the Higgs boson or the top quark.
-These particles  cannot be observed directly, almost immediately they transform (or decay) into lighter particles, which in turn also decay.
-They are measured and identified by a wide range of experiments (particle detectors), whose technologies, techniques and designs are based on the properties of the particles and on the nature of their interactions with matter \cite{thomson_2013}.\\
-
-In general, particle detector is typically constructed as a cylindrical or polygonal barrel section, oriented parallel to the incoming colliding beams.
-Two flat end caps seal the cylindrical structure, ensuring nearly complete solid angle coverage all the way down to the beam pipe.
-This detector comprises multiple layers, each designed to detect the different particles generated during collisions \cite{thomson_2013}.\\
-
-The performance of particle colliders is typically evaluated based on two parameters: the beam energy and the luminosity.
-The available energy for producing new effects is one of the most important parameters, as it determines the types of particles that can be studied or discovered.
-In these experiments, particles are accelerated and two beams are brought together at an intersection point where they collide.\\
-
-Colliding beam machines have the advantage that they can achieve much higher centre-of-mass energies, at various points the beams intersect and scattering takes place.
-If the incident particles have the same energy (equal mass) and therefore equal but opposite momentum, then the experiment is taking place in the centre-of-mass (CM) frame and the full energy delivered by the accelerator, can be used to produce high mass particles  \cite{undergraduate_accelerators_chapter}.
-In particle physics the Lorentz invariant quantity $s$ denote the square of the total incoming energy and is defined as: 
-\begin{equation}
-s = \left ( \sum_{i = 1,2}^{}E_{i} \right )^{2}-\left ( \sum_{i = 1,2}^{}p_{i} \right )^{2}c^{2}
-\end{equation}
-Where $E$ and \textbf{$p$}  are the energy and the momenta of each incoming particle respectively, in the CM frame, where the momenta are equal and opposite, the second term vanishes and  $s = 4E^2$.\\
-
-The second important parameter of the collider's performance is the luminosity, defined as the  quantity that measures the ability of a particle accelerator to produce the required number of interactions and is the proportionality factor  between the number of events of particular physics process per second $dR/dt$ and the quantum mechanical probability for the interaction called cross section \sigma_{p} \cite{ref_lib_vol3}.\\
-
-The technical meaning of "cross section" in particle physics is quite different from its common usage, while "cross section" typically refers to a slice of an object, in particle physics, it often refers to the probability that two particles will collide and react in a specific manner.
-When two beams cross in a particle accelerator, a variety of different processes can occur and  the cross section of a given process depends on the type and energy of the colliding particles.
-At the Large Hadron Collider (LHC), certain particles such as  $W^{\pm}$ and $Z^{0}$ bosons have large cross sections , making their observation more frequent, while the production of a Higgs boson has a much lower cross section, making it more difficult to produce \cite{thomson_2013}.\\
-
-To show better this concept, we present the most simplest scenario, where a beam of particles of type $a$, with a flux denoted by $\phi_{a}$, passes through a region of space containing $n_{b}$ particles per unit volume of type $b$.
-The interaction rate per target particle $r_{b}$ is proportional to the incident particle flux and can be expressed as follows \cite{thomson_2013}:
-
-\begin{equation*}
-  r_{b}=\sigma \phi_{a}
-\end{equation*}
-
-The essence of fundamental physics is encapsulated in $\sigma$, which has units of area and is referred to as the interaction cross section.
-It can be useful to conceptualize $\sigma$ as the effective cross-sectional area associated with each target particle, in general, the cross section merely represents the underlying quantum mechanical likelihood that an interaction will occur \cite{thomson_2013}.
-The definition of the cross section is illustrated in Figure \ref{cross_section}(a), where a single incident particle of type $a$ is travelling with a velocity $v_{a}$ in a region defined by the area $A$, wish contains $n_{b}$ particles of type $b$ per unit volume moving with a velocity $v_{b}$ in the opposite direction to $v_{a}$.
-
-\begin{center}
-  \begin{figure}[h!]
-    \centering
-\includegraphics[scale=.35]{Chapter1/cross_section.png} 
- \caption[Cross section illustration]{Left hand (a): single incident particle of type $a$ traversing a region containing particles of type $b$.
-Right-hand plot (b): projected view of the region traversed by the incident particle in time $\delta t$ \cite{thomson_2013}.}
-    \label{cross_section}
-  \end{figure}
-\end{center}
-
-In  a time $\delta t$, the particle $a$  crosses a region containing $\delta N= nb(v_{a}+v_{b}) A \delta t$ of type $b$.
-The interaction probability can be obtained from the $effective$ total cross sectional area of the $\delta N$ particles divided by the area $A$, which can be thougth of as the probability that the incident particle passes through one of the regions of area $\sigma$ drawn around each of the $\delta N$ target particles, as shown in Fig.
-\ref{cross_section}(b).
-For a beam of particles of type $a$ with number density $n_{a}$ confined to a volume $V$, the total interaction rate is $\text{rate}=(n_{a}v)(n_{b}V) \sigma = \phi N_{b} \sigma$,  more formally, the cross section for a process is defined as \cite{thomson_2013}:
-
-\begin{equation}
-\sigma=\frac{\text{number of interaction per unit time per target particle}}{\text{incident flux}}
-\end{equation}
-
-Where the flux $\phi$ accounts for the relative motion of particles.
-The value of the cross section is crucial as it represents the constant of proportionality between the rate measured by the detector and the luminosity.
-
-%begin{equation}
-%\sigma=\frac{\text{number of interaction per unit time per target particle}}{\text{incident flux}}
-%\end{equation}
-
-%\delta P= \frac{\delta N \sigma}{A}=\frac{n_{b}(v_{a}+v_{b})A\sigma \dela t}{A}= n_{b}v\sigma \delta t$
-%where $v=v_{a}+v_{b}$. The interaction rate for each particle of type $a$ is $r_{a}= \frac{dP}{dt}= n_{b} v\sigma$.
-%For a beam of particles of type $a$ with number density $n_{a}$ confined to a volume $V$, the total interaction rate is:
-%$\text{rate}=r_{a}n_{a}V=(n_{b}v\sigma) n_{a}V= (n_{a}v)(n_{b}V)\sigma$
-
-%$\text{rate}=(n_{a}v)(n_{b}V) \sigma = \phi N_{b} \sigma$
-
-%Thus the total rate is equal to
-%$\text{rate}= \text{flux} \times \text{number of target particles} \times \text{cross section}$
-
-%More formally, the cross section for a process is defined as:
 \section{Luminosity }
-
-In particle physics experiments besides the energy, the number of useful interactions (events) is the most important parameter.
-The quantity that measures the ability of a particle accelerator to produce these interactions is called instantaneous luminosity $\mathcal{L}_{inst}$ and is the proportionality factor between the number of events per second ($dR/dt$) and the cross section $\sigma_{p}$ \cite{concept_of_luminosity}:
-
-\begin{equation}
-\frac{dR}{dt}=\mathcal{L}_{inst} \cdot \sigma_{p}
-\end{equation}
-
-Where the unit of luminosity is $cm^{-2}s^{-1}$.
-
-To derive a general expression for luminosity in the case of two colliding beams, we consider both beams to serve as the target and the incoming beam simultaneously.
-We will assume that the beams are "bunched", meaning that the particles are grouped into packets or bunches.
-
-\begin{center}
-  \begin{figure}[h!]
-    \centering
-\includegraphics[scale=.25]{Chapter1/luminosity.png} 
- \caption[Colliding beam interaction]{Schematic view of a colliding beam interaction\cite{concept_of_luminosity}}
-    \label{luminosity}
-  \end{figure}
-\end{center}
-
-A schematic picture is shown in Fig.
-\ref{luminosity}.
-Since the two beams are not stationary but are moving through each other, the overlap integral depends on the longitudinal position of the bunches, and therefore on time.
-As the beams move towards and through each other, the two beams have different distribution functions and a different number of particles in the beams \cite{concept_of_luminosity}.
-The overlap integral, which is proportional to the luminosity $\mathcal{L}_{inst}$, can then be written as:
-
-\begin{equation}
-  \mathcal{L}_{inst}\propto K\cdot \int\int\int \int_{-\infty}^{\infty} \rho_{1}(x,y,s,-s_{0}) \rho_{2}(x,y,s,s_{0})dxdydsds_{0}
-    \label{lumi_1}
-\end{equation}
-
-Where  $\rho_{1}(x,y,s,-s_{0})$ and $\rho_{2}(x,y,s,s_{0})$ are the time dependent beam density distribution functions.
-We assume, that the two bunches meet at $s_{0} = 0$.
-Because the beams are moving against each other, we have to multiply this expression with a relativistic kinematic factor:
-
-\begin{equation}
- K = \sqrt{(\vec{v_{1}}-\vec{v_{2}})^{2}-(\vec{v_{1}}\times \vec{v_{2}})^{2}/c^{2}}
-    \label{kinematic}
-\end{equation}
-
-Specifically, in the case of exactly head-on collisions of bunches travelling almost at the speed of light, this factor becomes 2.\\
-Assuming uncorrelated densities in all planes and head-on collisions where the velocities of the two bunches are opposite $(\vec{v_{1}}=-\vec{v_{2}})$, the overlap integral can be factorized as:
-
-\begin{equation}
-  \mathcal{L}_{inst}= 2N_{b} N_{1}N_{2}f \int\int\int\int_{-\infty}^{\infty}  \rho_{1x}(x)\rho_{1y}(y)\rho_{1s}(s-s_{0})\rho_{2x}(x)\rho_{2y}(y)\rho_{2s}(s+s_{0}) dxdydsds_{0}
-    \label{luminosity_2}
-\end{equation}
-
-where $N_{1}$ and $N_{2}$ are the particles per bunch, $f$ the revolution frequency and $N_{b}$ is the number of bunches in one beam.\\
-
-%\begin{eqnarray}
-%\rho_{iz}(z)= \frac{1}{\sqrt{2\pi} \sigma_{z}} exp \biggl(-\frac{z^{2}}{2\sigma_{z}^{2}} \biggr)&z=x,y&i=1,2 
-%\end{eqnarray}
-
-%\begin{eqnarray}
-%\rho_{s}(s\pm s_{0})= \frac{1}{\sqrt{2\pi} \sigma_{s}} exp \biggl(-\frac{(s\pm s_{0})^{2}}{2\sigma_{s}^{2}} \biggr)
-%\end{eqnarray}
-
-Assuming Gaussian profiles in all dimensions and approximately equal bunch lengths $(\sigma_{1s}\approx \sigma_{2s})$, the equation \ref{luminosity_2} can be solved.
-For a general case where $\sigma_{1x}\neq \sigma_{2x} \text{ and } \sigma_{1y}\neq \sigma_{2y}$
-
-\begin{equation}
-  \mathcal{L}_{inst}= \frac{N_{1} N_{2} N_{b}f }{2\pi \sqrt{\sigma_{1x}^{2}+\sigma_{2x}^{2}}\sqrt{\sigma_{2y}^{2}+\sigma_{2y}^{2}}}
-  \label{lumi_general}
-\end{equation}
-
-For a specific case, asuming equal beams, $\sigma_{1x}= \sigma_{2x} \text{ and } \sigma_{1y}= \sigma_{2y}$:
-
-\begin{equation}
-  \mathcal{L}_{inst}= \frac{N_{1} N_{2} N_{b}f }{4\pi \sigma_{x} \sigma_{y}}
-  \label{lumi_theor}
-\end{equation}
-
-This is the well known expression for the luminosity of two Gaussian beams colliding head-on.
-It shows how the luminosity depends on the number of particles per bunch and the beam sizes \cite{concept_of_luminosity}.\\
-
-In practice,the integral in  \ref{luminosity_2} cannot be solved analytically because   the properties of the colliding beams are not know precisely, so a experimental technique is implemented with a dedicated machine setup to estimate the integrals, yielding a similar expression as \ref{lumi_theor}.
-
-In order to evaluate the total number of events we use integrated luminosity, it is a measurement of the collected data size, and it is an important value to characterize the performance of an accelerator, defined as \cite{concept_of_luminosity}:
-
-\begin{equation}
-  \mathcal{L}_{int}=\int_{0}^{T} \mathcal {L}_{\text{inst}}(t') dt'
-\end{equation}
-
-Where the value of $\mathcal{L}_{inst}$ is evaluated over time $T$ (excluding possible dead time) because its intensity decreases as the number of protons reduces during the collisions of the fill.
-So $\mathcal{L}_{int}$ is directly related to the number of observed events as:
-
-\begin{equation}
-  \mathcal{L}_{int} \ndot \sigma_{p}= \text{number of events of interest}
-\end{equation}
-
-The integrated luminosity has units of $cm^{-2}$ and is often expressed in inverse barn ($1 barn= 10^{-24}cm^{2}$). \\
-
-Understanding luminosity with the best possible precision is crucial for physics analyses such as searches for new particles, rare processes, or measurements of known particle properties.
-The experimental techniques to determine signal rates are mature enough, where the understanding of acceptances, detector biases, reconstruction efficiencies, or background subtraction is at the sub-percent level, so that the final precision of the physics measurement is dominated by the luminosity uncertainty .
-Ultimately, the greater the precision of the luminosity measurement, the more physicists can understand their observations and delve into hidden corners beyond our current knowledge \cite{luminosity_importance}.
 
@@
 
-The Large Hadron Collider (LHC) is the world’s largest and most powerful particle accelerator.
-It first started up on 10 September 2008, and remains the latest addition to CERN’s accelerator complex.
-The LHC consists of a 27-kilometre ring of superconducting magnets with a number of accelerating structures to boost the energy of the particles along the way.
-Inside the accelerator, two high-energy particle beams travel at close to the speed of light before they are made to collide.
-The beams travel in opposite directions in separate beam pipe where the two tubes kept at ultrahigh vacuum.
-They are guided around the accelerator ring by a strong magnetic field maintained by superconducting electromagnets, these are built from coils of special electric cable that operates in a superconducting state, efficiently conducting electricity without resistance or loss of energy.
-This requires chilling the magnets to -271.3°C  a temperature colder than outer space \cite{LHC}.\\
-
-Magnets of different varieties and sizes are used to direct the beams around the accelerator.
-These include 1232 dipole magnets, 15 metres in length, which bend the beams, and 392 quadrupole magnets, each 5–7 metres long, which focus the beams.
-Just prior to collision, another type of magnet is used to "squeeze" the particles closer together to increase the chances of collisions .
-\\
-
-The production of proton beams for the LHC involves a complex series of pre-acceleration stages.
-To begin with, hydrogen is ionized to produce protons, which are then accelerated in bunches up to 50 MeV within the Linear Accelerator 2 (LINAC2).
-Subsequently, these proton bunches are routed through three circular accelerators - the Booster, the Proton Synchrotron (PS), and the Super Proton Synchrotron (SPS)  in order to gradually increase their energy levels to 1.4 GeV, 26 GeV, and 450 GeV, respectively \cite{lhc_complex}.
-Following these pre-acceleration stages, the proton bunches are injected into the LHC ring where they are accelerated to reach energies of up to 7 TeV per bunch while circulating in opposite directions.
-This entire sequence of steps defines a single LHC fill, which typically involves $10^{14}$ protons that are grouped into bunches to form the proton beam.
-Figure \ref{lhc_com} depicts the complete CERN accelerator complex.
-
-\begin{center}
-  \begin{figure}[h]
-    \centering
-    \includegraphics[scale=.45]{Chapter1/lhc_complex_fig.png}
-    \caption[LHC Complex]{Diagram of the LCH complex \cite{lhc_complex}.}
-    \label{lhc_com}
-  \end{figure}
-\end{center}
-
-The responsibility for overseeing all controls, services, and technical infrastructure of the LHC lies with the CERN Control Centre.
-This is the central location where proton beams are directed to collide at four distinct positions along the accelerator ring, corresponding to the positions of the four particle detectors: CMS and ATLAS, which are general-purpose detectors specifically designed to investigate a broad range of Standard Model (SM) and Beyond SM (BSM) physics, while ALICE and LHCb serve as specialized detectors, specifically focused on studying particular phenomena.
-
 \section{Expected Luminosity precision for LHC Run 3}
-
-Since its inception in 2010 the LHC has undergone three runs and two lengthy shutdowns for maintenance and upgrades. 
-Run1 began in 2010 with proton-proton collisions at a center-of-mass energy of $\sqrt{s}=\text{7 TeV}$ and concluded in 2012 at  $\sqrt{s}=\text{8 TeV}$.
-Run 2, which took place at $\sqrt{s}=\text{13 TeV}$, was divided into two stages; the first  occurred from 2015 to 2016, and the second part  was carried out   from 2017 to 2018, efforts are currently underway to further improve the precision of this run.
-Finally  Run3, which began in 2022 at $\sqrt{s}=\text{13.6 TeV}$ and is currently ongoing.
-This thesis project aims to contribute to the improvement of the precision of the luminosity for Run 3, where it is expected to obtain an approximate luminosity of $450 fb^{-1}$ \cite{
-hl-lhc}. \\
-
-The integrated luminosity for each of these runs and years, and their corresponding uncertainty values are presented in table \ref{lumi_values} (luminosity values includes the time from the start of stable beams until the beam is dumped by the LHC), also a visualization of these values measured with CMS is shown in Figure \ref{lumi_per_year_int}, which depicts the delivered luminosity versus time for each year.
-% ref. TDR Bril para los 390
-%separar por lumpas , poner  referencia, poner periodo en vez de Run
-%-  en incertidumbre  no conocida, dejar solamente 2022
-\begin{table}[h!]
-    \begin{center}
-    \caption{Integrated luminosity values recorder by each Run}
-	\label{lumi_values}
-\begin{tabular}{cccc}
-\textbf{Period} & \textbf{Energy $\sqrt{s}$} & \begin{tabular}[c]{@{}c@{}}\textbf{Integrated}\\\textbf{Luminosity}\end{tabular} & \textbf{Precision}    \\ 
-\toprule
-Run 1(2010-2012) \cite{PCC_PAS_12_001} & 8 TeV                   & $30 fb^{-1}$                         & 2.5\%                 \\
-Run 2(2015-2016) \cite{lumi_precise_2015_2016} & 13 TeV   & $45.9 fb^{-1}$                     & 1.3\%                 \\
-Run 2(2017) \cite{pas_17} & 13 TeV                                                   & $49.8 fb^{-1}$                     & 2.5\%                 \\
-Run 2(2018) \cite{pas_18} & 13 TeV                                                  & $67.9 fb^{-1}$                      & 2.5\%                 \\
-Run 3(2022) \cite{wikicern} & 13.6 TeV                                            & $42 fb^{-1}$                        &      -                       \\
-\end{tabular}
-    \end{center}
-\end{table}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newpage
-  \begin{center}
-  \begin{figure}[ht]
-    \centering
-    \includegraphics[scale=.35]{Chapter1/int_lumi_per_year.png}
-    \caption[CMS Luminosity per year]{Delivered luminosity versus time for Run-1 (2010-2012) and Run-2 (2015-2018) and Run-3 that is still ongoing .
-Cumulative luminosity versus day delivered to CMS during stable beams for pp collisions at nominal center-of-mass energy.
-\cite{wikicern}.}
-    \label{lumi_per_year_int}
-  \end{figure}
-    \end{center}
-%% tabla con ano , luminosidad y presicion

### 2025-03-07 monograph_Luis/Chapter2/chapter2.tex
monografia

--- 2023-04-07 tesis_Luis/Chapter2/chapter2.tex
@@
-\chapter{Experiment Description }
-
-Modern general-purpose detectors used in high-energy colliders typically employ cylindrical detection layers arranged around the beam axis.
-One such example is the Compact Muon Solenoid (CMS), which is part of the LHC at CERN and is considered one of the largest international scientific collaborations in history.
-The CMS is designed for a broad physics program that includes studying the Standard Model.
-This chapter provides a description of the various components of the CMS detector,incliding the several systems to measure the luminosity with a particular focus on the silicon pixel tracker, which is described in greater detail due to its relevance to the thesis.
+\chapter{Experiment Description}
 
@@
 
-The CMS experiment is one of the four general-purpose detectors situated at the LHC.
-The CMS detector is constructed around a massive solenoid magnet, which is a cylindrical coil of superconducting cable generating a magnetic field of 4 tesla, this field is used to separate the calorimeter energy deposits of charged and neutral particles in jets.
-The field is confined by a steel "yoke" which constitutes the bulk of the detector's weight of 14,000 tonnes, the complete detector has a length of 21.6 meters and a diameter of 14.6 meters.
-\cite{CMS_Exp_2008}.
-\\
-
-The CMS detector comprises various detection layers that include separate parts of the detector, these layers are the fine-grained silicon tracker, which provides efficient and precise reconstruction of charged-particle trajectory.
-The highly-segmented electromagnetic calorimeter (ECAL) wish principal purpose is the detection of  electromagnetic energy and the identification of electrons and photons.
-The hadronic calorimeter (HCAL) wish principal purpose is the detection of hadrons in jets  \cite{CMS_Exp_2008}.
-Additionally, there is an excellent muon tracking system.
-A schematic representation of the CMS detector is shown in \ref{detector_CMS}.
-
-\begin{center}
-  \begin{figure}[ht]
-    \centering
-    \includegraphics[scale=.3]{Chapter2/CMS_detector_simple.png}
-    \caption[Perspective view of the CMS detector]{Perspective view of the CMS detector.}
-    \label{detector_CMS}
-  \end{figure}
-\end{center}
-
-A powerful magnet is required to bend charged particles as they travel outward from the collision point.
-Bending the trajectory of the particles serves two purposes: first, it helps identify the charge of the particle, as positively and negatively charged particles bend in opposite directions in the same magnetic field; and second, it enables measurement of the particle's momentum.\\
-
-To achieve high precision identification of the paths of deflected charged particles, the CMS employs a silicon tracker as its most inner detector to the beam pipe.
-This tracker system utilizes silicon strips and pixels that are divided into several layers in order to register the tracks of these particles.
-As a charged particle passes through a Tracker layer, it interacts electromagnetically with the silicon and produces a hit.
-By combining these individual hits, the track of the traversing particle can be identified.
-Further details about the tracker system can be found in the next section.
-\cite{CMS_Exp_2008}\\
-
-ECAL measures the energy of electrons and photons by completely stopping them.
-It is a hermetic, homogeneous calorimeter consisting of 61,200 lead tungstate (PbWO4) crystals mounted in the central barrel part and closed by 7,324 crystals in each of the two endcaps.
-In front of the endcap crystals, a preshower detector is placed.
-Avalanche photodiodes (APDs) are used as photodetectors in the barrel and vacuum phototriodes (VPTs) in the endcaps.\\
-
-The HCAL surrounds the ECAL and together they complete a hermetic calorimetry system designed to measure jets and missing transverse energy.
-When hadrons, which are composite particles consisting of quarks and gluons, travel through the ECAL, they are stopped by the HCAL, to achieve  this, the HCAL is divided into four parts: the hadron barrel (HB), hadron outer (HO), hadron endcap (HE), and hadron forward \cite{det_summary}.\\
-
-The final particle that the CMS directly observes is the muon.
-Muons are approximately 200 times heavier than electrons and are not stopped by the calorimeters.
-Therefore, special sub-detectors have to be constructed to detect them as they traverse the CMS.
-These sub-detectors are interleaved with the return yoke of the solenoid.
-The large magnet of the CMS also allows us to measure each muon's momentum both inside the superconducting coil (using the tracking devices) and outside of it (using the muon chambers) \cite{det_summary}.
-
-A transverse slice of the CMS detector, depicting specific particle interactions, is shown in Figure \ref{slice_CMS}.
-
-\begin{center}
-  \begin{figure}[ht]
-    \centering
-    \includegraphics[scale=.3]{Chapter2/slice_det.png}
-    \caption[Transverse slice fo CMS detector]{Transverse slice of the CMS detector with some particle interactions (from the beam interaction region to the muon detector).  \cite{det_summary}.}
-    \label{slice_CMS}
-  \end{figure}
-\end{center}
-
-The CMS's coordinate system has its origin located at the center of the detector, with the $y$-axis oriented vertically upwards and the $x$-axis directed radially inward, toward the center of the LHC.
-As a result, the z-axis aligns with the direction of the beam.
-In this system, the azimuthal angle $\varphi$ is measured from the $x$-axis within the $x-y$ plane, while the radial coordinate in this plane is represented by $r$.
-Furthermore, the polar angle $\theta$ is measured with respect to the z-axis \cite{CMS_Exp_2008}.
-
 \section{CMS Luminometers}
-
-A total of seven systems are used for measuring luminosity at CMS.
-The Pixel Luminosity Telescope (PLT) and Fast Beam Conditions Monitor (BCM1F) are dedicated systems for luminosity measurement, while the hadronic forward calorimeter (HF) uses a dedicated readout on an existing system.
-Additionally, three other methods, the drift tube luminosity (DT), the pixel cluster counting method (PCC), and the vertex counting method (VTX), use data from existing parts of the CMS detector to perform a luminosity measurement using the main CMS DAQ system.
-The PCC measurement uses the data collected with the standard CMS trigger system with triggers requiring colliding bunches but not any specific event activity, known as "zero-bias" triggers.
-Finally, the RAMSES detectors are part of the LHC environmental protection and monitoring systems, but they can also be used to provide a luminosity measurement readout through Timber(operational data and LHC logging service) \cite{pas_18}.
-A brief overview of the CMS luminometers is provided below:\\
-
-PLT Is a dedicated system for measuring luminosity using silicon pixel sensors.
-There are a total of 48 sensors arranged into 16 “telescopes”,eight at either end of CMS outside the pixel endcap, where each telescope contains three sensor planes arranged nearly parallel to the beam pipe.
-The PLT measures the rate of “triple coincidences”, where a hit is observed in all three planes, typically corresponding to a track from a particle originating at the interaction point.
-The overall mean rate for PLT  is estimated using the zero-counting method, where it is assumed that the number of observed triple coincidences follows a Poisson distribution \cite{pas_18}.
-
-BCM1F comprises a total of 24 sensors mounted on the same carriage as the PLT, consisting of 10 silicon sensors, 10 polycrystalline diamond (pCVD) sensors, and 4 single-crystal diamond (sCVD) sensors.The BCM1F readout features a fast readout with 6.25 ns time resolution; the precise time measurement, in conjunction with the position of BCM1F 1.8 m from the center of CMS, allows hits from collision products to be separated from hits from machine-induced background, because the incoming background is separated in time from the outgoing collision products  \cite{pas_18}.\\
-
-HF luminosity measurement uses a dedicated readout system installed in the HF calorimeter.
-Only two HF rings are used for luminosity measurement to ensure relatively uniform occupancy.
-Two algorithms are available: the first relies on the fraction of occupied towers (HFOC), and the second is based on the sum of the transverse energy ET (HFET)  \cite{pas_18}.\\
-
-Drift tube luminosity (DT), which uses the rate of muon track stubs in the muon barrel track finder and  RAMSES detectors, a CERN radiation and environmental monitoring system, although not designed as a luminometer, function quite well as a luminosity measurement, using the rate observed in the detectors (primarily photons within the energy range of 50 keV to 7 MeV) \cite{pas_18}.\\
-
-RAMSES.
-Althoug is not designed as a luminometer, the rate observed in this detector does function quite well as a luminosity measurement.
-RAMSES is a CERN radiation and environmental monitoring sytem, currently a part of the REMUS supervisory system.
-The sensor itself is a cylindrical plastic ionization chamber filled with 3 L of air at atmospheric ressure and it primarily detects photons.
-The overall rate in the RAMSES detectors is small, which means that it is not capable of making bunch-by-bunch measurements and cannot be independently calibrated using a VdM scan; however, this also means it is less affected by issues such as instability caused by radiation damage or nonlinearity \cite{pas_18}.\\
-
-The PCC method uses the rate of pixel clusters in the CMS pixel detector to provide a luminosity measurement this method will be described in more detail in chapter 3.
-
-The location of the 7 luminometers in the CMS experiment are shown in Figure \ref{luminometers}.
-
-\begin{center}
-  \begin{figure}[ht]
-    \centering
-    \includegraphics[scale=.3]{Chapter2/detectors.png}
-    \caption[CMS Luminometers]{The seven luminometers that make up the CMS luminosity measurement system.
-Multiple independent systems used online: BCM1F, HFET, HFOC, PLT (independently calibrated) ,REMUS and  DT (cross-calibrated) , Pixel cluster counting is used after offline processing.}
-    \label{luminometers}
-  \end{figure}
-\end{center}
+\label{Luminometers}
 
@@
 
-The tracking system plays a crucial role in precisely measuring the trajectories and momenta of charged particles generated by collisions in the LHC, as well as reconstructing secondary vertices.
-It has a total physical size of 5.8 m in length and 2.5 m in diameter.
-The CMS tracking detector relies on semiconductor technology, this is divided in two systems, the pixel detector and the Strip tracker \cite{CMS_Exp_2008}.In Figure \ref{strip_layout}, we can observe the pixel detector at the center, surrounded by the Strip tracker.\\
-
-The Strip tracker is comprised of two subsystems: the first being the Tracker Inner Barrel (TIB) and Disks (TID), which is further divided into four barrel layers and three disks at each endcap.
-The second subsystem is the Tracker Outer Barrel (TOB), which consists of six barrel layers and the Tracker EndCaps (TEC) comprising of nine disks.
-The Strip tracker in total comprises of 15148 silicon modules, covering an active area of about 198$\text{m}^{2}$, and consists of 9.3 million strips \cite{CMS_Exp_2008}.
-\\
-
-The innermost part of the tracking system is made up of the silicon pixel tracker, which consists of four concentric barrel layers (BPIX) and three disks on each endcap (FPIX).
-This component comprises a total of 70 million pixels and extends the tracker's acceptance up to a pseudorapidity of $|\eta| < 2.5$.
-Additionally, the active silicon area of this component covers approximately 200 $m^2$.
-More information about this detector is provided in the following section.
-
-\begin{center}
-  \begin{figure}[ht]
-    \centering
-    \includegraphics[scale=.23]{Chapter2/strip_layout.png}
-    \caption[Schematic cross section through the CMS tracker]{Schematic cross section through the CMS tracker. Each line represents a detector module \cite{CMS_Exp_2008}.}
-    \label{strip_layout}
-  \end{figure}
-\end{center}
-
 \section{Silicon Pixel Detector}
 
-The silicon pixel detector  forms the innermost component of the tracking system.
-This detector facilitates the provides  3-dimensional space points in the area nearest to the interaction point, which, in turn, enables precise tracking of charged particles and vertex reconstruction.
-The pixel detector operates in a radiation-rich environment, marked by high track density \cite{phase1_Pixel_Detector}.\\
-
-The CMS pixel detector encompasses four concentric barrel layers (L1-L4), each with radii measuring 29, 68, 109, and 160 mm, and three disks (D1-D3) on either end positioned at distances of 291, 396, and 516 mm from the detector's center.
-A schematic of the CMS Phase-1 pixel detector's arrangement is depicted in Figure \ref{phase1_pixel_detector} where the total silicon area spans 1.9 $\text{m}^{2}$.
-
-\begin{center}
-  \begin{figure}[h]
-    \centering
-    \includegraphics[scale=.26]{Chapter2/phase1_PixelDetector.png}
-    \caption[CMS Phase-1 pixel detector]{Layout of the CMS Phase-1 pixel detector in longitudinal view\cite{phase1_Pixel_Detector}.}
-    \label{phase1_pixel_detector}
-  \end{figure}
-\end{center}
-
-The BPIX and FPIX detectors are equipped with four service half-cylinders each, with a combined length of 540 mm.
-These cylinders host the readout and control circuits, and provide guidance for the power lines and cooling tubes of the detector.
-%  cambiar a otra palabras ..The BPIX detector is bifurcated into two mechanically self-sufficient halves, both of which are made up of a half detector and two service half-cylinders.
-The orientation of the sensor surface of the modules in both halves is parallel to the magnetic field.
-
-%% separadas
-On the other hand, the FPIX detector is segmented into four mechanically independent quadrants, each of which comprises three half-disks housed in a service half-cylinder.
-The sensor orientation in the FPIX detector is arranged such that the long side of the pixel is aligned with the radial direction.
-The half-disks are additionally subdivided into inner and outer half-rings that support 22 and 34 modules, respectively \cite{phase1_Pixel_Detector}.\\
-
-The pixel detector is built from 1856 segmented silicon sensor modules, where 1184 modules are used in the BPIX and 672 modules are used for the FPIX.
-Each module consists of a sensor with 160$\times$416 pixels connected to 16 readout chips (ROCs).
-In total there are 124 million readout channels \cite{phase1_Pixel_Detector}.
-A pixel detector module is built from a planar silicon sensor with a size of 18.6 $\times$ 66.6 $\text{mm}^{2}$ (active area of 16.2 $\times$ 64.8 $\text{mm}^{2}$), bump-bonded to an array of 2$\times$8 ROCs.
-Each ROC is segmented into 4160 readout channels and reads out the pulse height information for each pixel.
-The standard pixel size is 100$\times$150 $\mu m^{2}$, as in the original pixel detector.
-The figures depicting the modules of the CMS Phase-1 pixel detector can be found in Figure \ref{modules_drawing} \cite{phase1_Pixel_Detector}.
-
-\begin{center}
-  \begin{figure}[h]
-    \centering
-    \includegraphics[scale=.2]{Chapter2/modules_drawing.png}
-    \caption[Pixel detector modules]{ Drawings of the pixel detector modules for BPIX L1 (left), BPIX L2–4 (middle), and the FPIX detector (right)\cite{phase1_Pixel_Detector}.}
-    \label{modules_drawing}
-  \end{figure}
-\end{center}
-
 \section{Pixel Cluster Reconstruction}
-
-The track reconstruction process involves several steps.
-Firstly, zero-suppressed signals above specified thresholds in pixel  channels  are used to form clusters.
-The charge measured within each cluster corresponds to the charge deposited by a single charged particle.
-Next, the cluster positions and their uncertainties are estimated in a local orthogonal coordinate system  in the plane of each sensor \cite{Track_Reco_2014}.
-%The pixel sensor used in this process consists of 100 $\times$ 150$\mu \text{m}^{2}$ pixels  this is shown en the figure \ref{module and hit}. 
-%% cambiar imagen para arriba
-\begin{center}
-  \begin{figure}[h]
-    \centering
-    \includegraphics[scale=.3]{Chapter2/PixelSensor.png} \includegraphics[scale=.3]{Chapter2/hit.png}
-    \caption[PixelSensor]{ left: Pixel sensor diagram, right: hits detection in a corresponding  pixel sensor \citep{thomson_2013}. }
-    \label{module and hit}
-  \end{figure}
-\end{center}
-
-To be considered a valid cluster, each one must have a minimum charge equivalent to 4000 electrons \cite{Track_Reco_2014,phase1_Pixel_Detector}.
-For normally incident minimum-ionizing particles (MIPs) in a silicon sensor with a thickness of 285 $\mu \text{m}$, the most probable value of energy deposition corresponds to approximately 21,000 electrons.
-However, this charge is often spread over more than one pixel due to Lorentz drift and diffusion of collected electrons, leading to charge clusters.\\
-
-Figure \ref{cluster} is shown a pixel cluster example at $\eta$ = 1.83, here the  charge deposition in each pixel is shown in thousands of electrons, the numbers shown in green correspond to charge depositions below the 2000 electron threshold which are not included in the cluster.
-The dotted red line indicates the particle trajectory projection in the module plane and the red cross shows the true hit position.
-Where the corresponding coordinate systems is based in the  geometry of the CMS barrel and forward pixel detectors \cite{Pixel_Hit_Reconstruction}.
-%% quitar el detector
-%%  usar clusters clasicos
-
-\begin{center}
-  \begin{figure}[h]
-    \centering
-    \includegraphics[scale=.3]{Chapter2/pixel_cluster.png} 
-    \caption[Pixel cluster]{ Left: Geometry of the CMS barrel and forward pixel detectors and the corresponding coordinate systems. Right: A pixel cluster example at $\eta$ = 1.83 }
-    \label{cluster}
-  \end{figure}
-\end{center}

### 2025-03-07 monograph_Luis/Chapter3/chapter3.tex
monografia

--- 2023-03-29 tesis_Luis/Chapter3/chapter3.tex
@@
 
-Accurately measuring the luminosity delivered to the CMS experiment by the LHC is essential for various reasons.
-Online, the luminosity measurement provides feedback on the LHC and CMS performance and operations, including measuring trigger rates.
-In offline analysis, the luminosity measurement is a critical component for measuring the cross-section of observed processes or setting upper limits in searches for processes beyond the standard model.
-
-As we see, to measure luminosity, a total of seven luminometers are used at CMS, and each of them reads out a specific quantity observed in the detector, such as hits, tracks, or clusters.
-The rate R measured by the luminometer is proportional to the instantaneous luminosity, $\mathcal{L}_{inst}$, with the constant of proportionality given by the visible cross-section $\sigma{vis}$ \cite{pas_18}.
-
-\begin{equation}
-R(t)=\mathcal{L}_{inst}\sigma_{vis}
-\label{lumi_exp_gen}
-\end{equation}
-
-The determination of $\sigma_{vis}$ is performed through van der Meer (vdM) scans using a specialized LHC machine setup.
-This chapter provides a description of this procedure, specifically applied with the PCC method.
-Additionally, the selection of stable "good" modules necessary for precise luminosity measurements will also be discussed.
-
-\section{Pixel Cluster Counting method}
-
-The PCC method utilizes the rate of pixel clusters in the CMS silicon pixel detector to determine an offline luminosity measurement, this method exploits the very large number of pixels in the inner part of the CMS tracking system,it means that the probability of a given pixel being hit by two different charged particles from the same bunch crossing is exceedingly small, this large area and low occupancy yield measurements with excellent linear response with the pile-up (number of interactions per bunch crossing)$\mu$ \citep{lumi_precise_2015_2016}, therefore an accurate measure of instantaneous luminosity with a high statistical precision.\\
-
-However, the statistical precision for a single 23-second period or "luminosity section" is not as high as for online luminometers due to the limited CMS trigger bandwidth available for collecting data.
-Nonetheless, over longer time periods, this method provides a stable and highly precise luminosity measurement.
-On average, the detector occupancy is less than 0.1\% \cite{pas_18}.\\
-
-Figure  \ref{pileup} shows a simulation made in 2016 with a representative PCC distribution at $\mu$ = 45 and the average PCC as a function of $\mu$.
-The latter distribution is fitted with a first-order polynomial, assuming no correlations among different values of $\mu$.
-Good agreement is seen based on the estimated goodness-of-fit $\chi^{2}$ per degree of freedom (dof) value of about 0.5 , indicating linearity under simulated conditions \cite{lumi_precise_2015_2016}.
-
-\begin{center}
-  \begin{figure}[h!]
-    \centering
-    \includegraphics[scale=.3]{Chapter3/pileup_lineality.png} 
-    \caption[Linearity with pile-up]{ The left plot shows the number of pixel clusters and their statistical uncertainty from simulation of pileup following a Poisson distribution with a mean of 45.
-The right plot shows the mean number of pixel clusters from simulation as a function of mean pileup.
-The red curve is a first-order polynomial fit with slope and $\chi^{2}/ndof$ values shown in the legend.
-The lower panel of the right plot shows the difference between the simulation and the linear fit in black points.
-The green band is the final linearity uncertainty for the 2016 data set \cite{lumi_precise_2015_2016} }
-    \label{pileup}
-  \end{figure}
-\end{center}
-
-To obtain the mean number of pixel clusters per event, several zero-bias events are averaged. This value is given by :
-
-\begin{equation}
-\left < N_{\text{cluster}} \right > = \left < N_{\text{pixel}/\text{interaction}} \right >  \left < N_{\text{interactions}} \right > \equiv \left < N_{\text{pixel}/\text{interaction}} \right > \mu
-\end{equation}
-
-where $\mu$ is the average number of interactions per bunch crossing and is refered as pileup \cite{PCC_PAS_12_001}. Under minimum bias conditions, $\mu$ can be expressed as:
-
-\begin{equation}
-\mu = \frac{\sigma_{\text{minBias}}}{f} \cdot \mathcal{L}_{inst}
-\end{equation}
-
-where $f$ is the LHC revolution frequency and $\mathcal{L}_{inst}$ is the single bunch instantaneous luminosity (SBIL).
-The minimum bias cross section here is related to the PCC visible cross section by the mean number of clusters per interaction:
-
-\begin{equation}
-\sigma_{vis}^{PCC}= \left < N_{\text{pixel}/\text{interaction}} \right >\cdot \sigma_{\text{minBias}}
-\end{equation}
-
-Combining everything, the PCC luminosity measurement is obtained as:
-
-\begin{equation}
-\mathcal{L}_{inst}=\frac{\left < N_{\text{cluster}} \right >}{\sigma_{vis}^{PCC}} \cdot f
-\end{equation}
-
-In the PCC measurement, the innermost layer of the pixel detector is excluded from the analysis due to significant dynamic inefficiency effects \cite{pas_18}.
-At higher $\mathcal{L}_{inst}$, the hit efficiency in this layer decreases because the readout chip cannot process all of the hits.
-Only modules that consistently perform well for luminosity purposes throughout the year are utilized in the measurement.
-
-For the VdM measurement, a special trigger mode is employed, which enables a higher data rate for PCC to acquire the required statistical precision.
-However, this mode is only active for five bunch crossings, and data are taken exclusively during this period.
-
-\section{2022 CMS Data Summary}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{2017 and 2018 CMS Data collected}
 
@@
 
-To ensure accurate luminosity measurement, a veto list is created to remove any modules exhibiting long-term performance variations, indicating a non-physical shift in their cluster counts.
-With a total of 1856 modules in the pixel system, all of them can be considered in the luminosity measurement; however, non-zero occupancy and non-linear effects can pose challenges for accurate measurement.
-Thus, to identify "good" and "stable" modules, a subset is selected by eliminating  underperforming or "bad" modules and comparing their relative contributions to the cross section.
-Those with relatively consistent contributions across standard physics runs are kept, while those with significant changes in their relative cross section compared to the averaged relative contribution are rejected.
-The Module selection is made as:
-
-\begin{itemize}
-\item Poor statistics lumisections are removed by applying selection on total PCC.
-\item Barrel layer-1 modules are removed, as these modules are significantly affected by dynamic inefficiency.
-\item A loose selection of 7\% based on RMS/mean of module weight is applied. Modules with significantly large RMS/mean are removed with this selection as shown in \ref{goodmodule}.
-\item The module stability is re-evaluated based on RMS/mean values using an iterative method where appropriate selections are applied to remove underperforming modules until a stable luminosity is attained.
-\end{itemize}
-
-\begin{center}
-  \begin{figure}[h!]
-    \centering
-    \includegraphics[scale=.20]{Chapter4/RMSmean.png}
-    \caption[RMS/mean Module  Stability]{ RMS/mean values of module weight for all pixel modules. Each pixel module is represented by a module number index.} 
-    \label{goodmodule}
-  \end{figure}
-\end{center}
-
-To ensure accurate measurements, a pixel module veto list is established for each period, recognizing that different periods may have varying numbers of well-performing modules.
-The pixel detector is subject to changing conditions over time, such as detector noise, aging effects, and radiation damage.
-Stability of the pixel modules is assessed based on changes in the module PCC ratio relative to the total PCC, known as module weight.
-These variations are evaluated over an interval of 23 seconds, corresponding to the granularity of the luminosity database.
-The pixel module veto list is first generated for the period 2022F containing the vdM fill and subsequently for the periods ,C, D, E and G,  following the same procedure.
-
-To further improve the stability of the PCC measurement, a 4\% RMS common module vetolist is created as shown in table \ref{common  veto module}.
-The approach to derive the common module veto list is to start by combining module vetolists of period C and D; then combine C, D and E; and so on.
-The zero-bias PCC data is reprocessed using this common module vetolist.
-
-\begin{table}[ht]
-\centering
-\caption{Number of good and bad modules for the combined vetolist, after each iteration of the 4\% RMS selection with an additional period.}
-\begin{tabular}{ccc}
-\textbf{Period} & \textbf{\# bad modules} & \textbf{\# good modules}  \\ 
-\toprule
-2022C+D         & 886                     & 970                       \\
-2022C+D+E       & 1106                    & 750                       \\
-2022C+D+E+F     & 1307                    & 549                       \\
-2022C+D+E+F+G   & 1411                    & 445                   
-\label{common  veto module}   
-\end{tabular}
-\end{table}
-
-\noindent This final common veto in conjunction with background subtraction  is used for the last reprocesing data analysed with the VdM scan.
-
 \section{Luminosity calibration: van der Meer method}
-
-As discussed in Chapter 1, the instantaneous luminosity for a single colliding bunch is described by Eq.
-(\ref{luminosity_2}).
-In practice, while the measurement of the beam currents $N_{1,2}$ is well determined, the individual proton density functions cannot be directly measured.
-To address this, the VdM method involves a specific machine setup that allows for the determination of the two beam overlap integrals.
-This is achieved by varying the separation between the beams and measuring the resulting rates, which can be used to obtain density profiles that are close to normal distributions.
-
-\begin{equation}
-\int \rho_{x1}(x) \rho_{x2}(x) dx = \frac{R_{x}(0)}{\int R_{x}(\Delta) d\Delta}
-\end{equation}
-
-where $R_{x}(\Delta)$ is the rate measured when the two beams are separated in $x$ by a distance $\Delta$; a asimilar equation can be written in $y$.
-Then the beam overlap width $\Sigma_{x}$ (and similarly $\Sigma_{y}$) is defined as \cite{pas_18}:
-
-\begin{equation}
-\Sigma_{x}= \frac{1}{\sqrt{2\pi}} \frac{\int R_{x}(\Delta)d\Delta}{R_{x}(0)}
-\label{CapSigma}
-\end{equation}
-
-This process leads to the final expression for luminosity for a single colliding bunch:
-
-\begin{equation}
-\mathcal{L}_{inst}=\frac{N_{1} N_{2}f}{2 \pi \Sigma_{x}\Sigma_{y}}
-\end{equation}
-
-where $N_{1,2}$ are the particles per bunch (bunch current) and  $f= 11246$ Hz is the bunch orbit frequency around the LHC ring.\\
-
-Therefore, the formula used to measure the visible cross sections $\sigma_{vis}$ takes the following form:
-
-\begin{equation}
-  \sigma_{vis}=\frac{2\pi \Sigma_{x} \Sigma_{y} R(0, 0)}{N_{1}N_{2} f}
-  \label{sigmavis_eq}
-\end{equation}
-
-Experimentally, the quantities $\Sigma_{x}$ and $\Sigma_{y}$, as defined in Eq.
-(\ref{CapSigma}), are determined by conducting two separate scans in the $x$ and $y$ directions, respectively.
-These scans are performed by varying the separation between the beams in each direction and measuring the rate $R(0,0)$, which is normalized by the product of the beam currents, at a fixed number of separation steps.
-The separation steps are determined through curve fitting of the scan data based on the luminometer rate measurements obtained during the vdM scans.
-While the beam widths are the same for all luminometers, the peaks of the corresponding scan curves are luminometer-specific.
-Figure \ref{vdm_sketch} depicts a schematic of the beam positions during vdM scans in the $x$ and $y$ planes, along with the detector rate as a function of beam separation  \cite{pas_18}.
-
-Only modules that are found to operate consistently well for luminosity purposes during the year of the VdM scan are used in the measurement, a brief description of the procedure to the selection of these a presented in the next section.
-
-\begin{center}
-  \begin{figure}[h!]
-    \centering
-    \includegraphics[scale=.37]{Chapter3/vdm_sketch.png}
-    \caption[Sketch of a vdM scan in x and y planes and example of fitting resulting rates]{ The sketch of a vdM scan in $x$ and $y$ planes.
-The indent sketch is an example of the fitting of the resulting rates \cite{vdM_sketch}.}
-    \label{vdm_sketch}
-  \end{figure}
-\end{center}

### 2025-03-07 monograph_Luis/Chapter4/chapter4.tex
monografia

--- 2023-05-05 tesis_Luis/Chapter4/chapter4.tex
@@
 
-\section{2022 vdM scan program}
+\section{2017 and 2018 vdM scan program}
+\label{2017 and 2018 vdM scan program}
 
-In 2022, the main vdM scan program for the CMS experiment was conducted during LHC fills 8379 and 8381 on 10 and 11 November.
-During fill 8381, a total of 144 bunch pairs were collided head-on , with a proton-proton collision energy $\sqrt{s}$ of 13.6 TeV.
-During this fill, various types of scan pairs with different characteristics were conducted.
-These scan pairs are described below.
-Each scan pair consisted of two scans in the transverse planes $x$ and $y$.
-In addition to these scans, other types of scans were also conducted, which are not included in this analysis.\\
-
-The calibration program included four scan pairs, vdM1,vdM2, vdM3 and vdM4, these are considered the standard vdM scans in the program, used specifically to compute $\sigma_{vis}$.
-In this type of scan the two beams are separated by $6\sigma_{b} \thickapprox 578\mu m$, where $\sigma_{b}$ represents the transverse bunch size.
-The beams are then scanned across each other in a sequence of 25 steps, each lasting 30 seconds with a step size of $0.5\sigma_{b} \thickapprox 48 \mu m$.\\
-
-The calibration program also included two beam-imaging scan pairs, BI1 and BI2 .
-These scans were developed for studies on beam shapes, estimating the uncertainty caused by the not strictly valid assumption seen in previous sections that the bunch proton density function is factorizable into independent $x$ and $y$ densitys, this correction is called  ($x$-$y$ nonfactorization).
-BI acans also are used to compute of $\sigma_{vis}$, independent of the standard vdM's scans.
-During the BI scans, one beam is kept fixed at its nominal head-on position, while the other beam is separated and scanned in 19 steps, each step lasts 46 seconds and covers a range from $-4.5\sigma_{b}$ to $+4.5\sigma_{b} \thickapprox 433 \mu m$.\\
-
-Two length scale LS scans were conducted, one during fill 8381 and another during fill 8379.
-The LS scan is a special scan designed to apply a correction to the results of  $\sigma_{vis}$ obtained from the vdM scan program, this correction will be described further in this section.
-During this scan, the beams are separated by a constant amount of $\sqrt{2} \sigma_{b} \thickapprox 106 \mu m$, and they are moved coherently forward and backward in five steps each, all in the same transverse direction.\\
-
-Finally two super separation periods SS1 and SS2 were performed for the background estimation, here the two beams were sepated at a distance of $6\sigma_{b}$ during 5 minutes, at this distance the overlap of the beams is minimal and the contribution of collision is negligible.
-%23:31-23:36 11:47-11:52
-
-The scan program during fill 8381 is summarized in Figure \ref{scan_prog} where all the scans mentioned and described above are labeled.
-
-\begin{center}
-  \begin{figure}[h]	
-    \centering
-    \includegraphics[scale=.35]{Chapter4/2022Scanprorgam.png}
-    \caption[2022 vdM scan program]{Nominal horizontal and vertical positions of the proton beams during LHC fill 8381, showing the four standard vdM scans, two BI scans, one LS scan and the two Super Separation Periods (SS)}
-    \label{scan_prog}
-  \end{figure}
-\end{center}
-
-\section{Data aquisition and processing}
+\section{Data acquisition and processing}
 \label{data}
-In order to achieve a high statistical precision in data for each colliding bunch pairs the system trigger  bandwidth  limitations do not allow the use of all of them, beacause this, CMS implemented a zero-bias triggers only on five Bunch crossing id (BCID): 282, 822, 2944, 3123, and 3302.
-This data is saved randomly with the highest possible rate of 27.23 kHz using the High Level Trigger (HLT) through the CMS data acquisition (DAQ) system.
-Due to the weight of the events, 16 different streams are required to save the full data.
-Here the datasets are in their RAW format, which contains information per event (bunch crossing) and the amount of charge deposited in each pixel.\\
-During the vdM2 scan pair, the central CMS data taking was not operational, so no data was recorded for PCC, and this scan pair was skipped from the full calibration.\\
-
-The data is then reprocessed by the CMS collaboration to enable a cluster reconstruction, resulting in the datasets (ALCARECO version) that contain a module collection and their number of clusters per event , the data here is in the CMSSW format.
-These datasets will be used as the starting point for our own data reprocessing and analysis.\\
-
-The ALCARECO samples are processed using CMSSW software (written in Python and C++) to extract the clusters per module.
-Due to the large size of the datasets, all the datasets were sent for reprocessing through The Worldwide LHC Computing Grid (WLCG), wish consists of a grid-based computer network infrastructure,designed by CERN to handle the big volume of data produced by LHC experiments.
-In this  process, we obtained the required cluster counts, which was saved in a dataset with a ROOT format.
-This format uses TTrees and TBranches, that are containers to maintain the information in a hierarchical and organized manner.
-The information is stored in one TTree that contains the information per event distributed in several TBranches, such as the number of pixel clusters, the BCID, the module identifiers, number of run, the number of lumisection (where 1 LS = 23 s), the number of luminible LN (where 1 LN is equivalent to 0.32 s) and time where that event took place (timestamp begin).\\
-
-In order to maintain full statistical precision despite the limitations of the vdM framework (vdMFW), which was utilized for the final fit of our data, the rates were stored  each 1.32 s (NB4) time that corresponding to 4 LN, this was done making  an average  between clusters and the number of events that fall within this time span.
-During this process, the module veto list mentioned in the previous section is introduced and the modules detected in these list were removed.
-In this phase, the information is merged into a single file using a hierarchical data format (hd5) that organizes the data into tables, this final format is the required by the vdMFW.
-All the  process is carried out using lxbatch, a cluster of computers located within CERN.\\
-
-Finally the hd5 file containing the rates collected during the vdM scans  is analyzed using the vdMFW, which is written in Python and uses the ROOT data analysis package through the PyRoot library.
-The vdMFW  extracts the necessary information using its analysis tools.
-During the process, several corrections are applied to the rates which will be described later.
-In the processing the vdMFW generates the final information and plots, which contain the normalized rates ($R/N_{1}N_{2}$) and beam position.
-A mathematical function is then used to fit the points to extract $\Sigma_{x,y}$ and peak values to compute $\sigma_{\text{vis}}$ for all the bunches in the scan.
 
@@
 \label{bkg}
-To perform accurate fitting of the data, it is necessary to take into account the following background contributions to the PCC rates.
-These contributions are estimated independently during the Super Separation (SS) periods discussed in the previous section.
-Three primary sources of beam-induced background should be considered:
-
-\begin{itemize}
-
-\item Beam Gas Elastic (BGE).
-The elastic beam gas contribution are all coherent and quasi-elastic, nuclear elastic and coulomb scattering for multi-turn beam-gas interactions around the ring.
-Typically the interaction of the primary beam proton and the takes place at the tertiary TCT collimator jaw \cite{bkg_source}.
-
-\item Beam Gas Inelastic (BGI).
-These are all inelastic interactions of primary beam protons with rest gas in the beam pipe.
-The interaction rate is dominated by the vacuum quality in the various beam line elements upstream CMS.
-Therefore the origin of this contribution is distributed all along the long straight section \cite{bkg_source}.
-
-\item Beam Halo (BH).
-This component of the machine induced background is caused by the inefficiency of the main collimation system.
-Protons can escape from one collimator and being intercepted by another collimator \cite{bkg_source}.
-\end{itemize}
-
-In order to illustrate the two SS periods for this analisys, Figure \ref{ssp_wide_bx282} displays the PCC per NB4 versus time for BCID 282.
-The lower regions of the plot correspond to a time window of 5 minutes during which the beams were separated by a distance of $6\sigma_{b}$.\\
-
-\begin{center}
-\begin{figure}[h!]
-\centering
-\includegraphics[width=.49\textwidth]{Chapter4/BX_282_Rates_SS1.png}
-\includegraphics[width=.49\textwidth]{Chapter4/BX_282_Rates_SS2.png}
-\caption[Super Separation periods for BCID 282]{PCC per NB4 versus time for BCID 282. The lower regions corresponds to the super separation period I (left) and II (right).}
-\label{ssp_wide_bx282}
-\end{figure}
-\end{center}
-
-To estimate the background value in each BCID, the mean value of the PCC per NB4 rates distribution is computed.
-The mean and error per super separation (SS) period are obtained by plotting the PCC per NB4 as a function of time and then taking the $y$ projection.
-The error is calculated using the formula $AvgErr = \sqrt{SEM_1^2 + SEM_2^2 + \cdots + SEM_N}/N$.
-To illustrate this process for each BCID, the distribution or profile of PCC per NB4 for each SS period is plotted.
-Figure \ref{ss1_hist_282} displays the PCC per NB4 distribution for SS period I, specifically for BCID 282, but the same plot is created for every BCID.\\
-
-\begin{center}
-  \begin{figure}[h!]
-    \centering
-    \includegraphics[scale=.30]{Chapter4/ss1_histo_bx282.png}
-    \caption[PCC per NB4 profile for BCID 282 from SS period I]{ PCC per NB4 profile for BCID 282 from SS period I.} 
-    \label{ss1_hist_282}
-  \end{figure}
-\end{center}
-
-\begin{table}[h!]
-  \begin{center}
-    \caption[Background values for the two super separation periods]{Mean and standard error on mean (SEM) for the PCC background estimated with the SS1 and SS2 data, separately for all five BCIDs and averaged.}
-    \label{ss_per_bx}
-    \begin{tabular}{|c | c | c | }
-      \multicolumn{1}{c}{} & \multicolumn{1}{c}{\textbf{SS period I}} & \multicolumn{1}{c}{}  \\
-      \hline
- \textbf{BCID}   & \textbf{Mean}   &  \textbf{SEM}\\
-     \hline %\midrule[1.1pt]
-      282 & 0.7712 & 0.0054\\
-      \hline
-      822 & 0.7744 & 0.0055\\ 
-      \hline
-      2944 & 0.7695 & 0.0057\\ 
-      \hline
-      3123 & 0.7469 & 0.0049\\ 
-      \hline
-      3302 & 0.7708 & 0.0049\\ 
-      \hline
-      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}\\
-      \multicolumn{1}{c}{$\text{SSI}_{\text{Avg}}=$} & \multicolumn{1}{l}{$0.7665 \pm 0.0023$} & \multicolumn{1}{c}{}\\
-%      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}
-    \end{tabular}
-    \hspace{0.5cm}
-    \begin{tabular}{|c | c | c | }
-      \multicolumn{1}{c}{} & \multicolumn{1}{c}{\textbf{SS period II}} & \multicolumn{1}{c}{ }  \\
-      \hline
- \textbf{BCID}   & \textbf{Mean}   &  \textbf{SEM}\\
-     \hline %\midrule[1.1pt]
-      282 & 0.7192 & 0.0048\\
-      \hline
-      822 & 0.7257 & 0.0057\\ 
-      \hline
-      2944 & 0.7292 & 0.0058\\ 
-      \hline
-      3123 & 0.7028 & 0.0052\\ 
-      \hline
-      3302 & 0.7208 & 0.0053\\ 
-      \hline
-      \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}\\
-      \multicolumn{1}{c}{$\text{SSII}_{\text{Avg}}=$} & \multicolumn{1}{l}{$ 0.7195 \pm 0.0024$} & \multicolumn{1}{c}{}
-    \end{tabular}   
-  \end{center}
-\end{table}
-
-Table  \ref{ss_per_bx} shows the results for five different BCIDs, using the reprocessed PCC data for Fill 8381.
-This analysis reveals notable inconsistencies in the background values obtained from the two Super Separation (SS) periods.
-As a result, the quality of the fit was affected, and thus, this data was excluded from subsequent analyses.
-Further details on this matter will be discussed in a later section.
 
 \section{Beam Corrections}
-
-There are several systematic effects that affect the measurement of beam overlap width and therefore the extraction of $\sigma_{vis}$ from the vdM scan procedure.
-These effects are measured and, where applicable, corrected as described below.
-A systematic uncertainty is assigned to the resulting measured cross section $\sigma_{vis}$, and the following corrections are applied in the vdM Framework:
-
-\begin{enumerate}
-
-\item Ghost and Satellite.
-Corrects the presence of spurious charges, which affect bunch currents.
-Satellite charges refer to additional charges outside the actual colliding bunch, while ghost charges refer to charge not in any nominally filled bunch slot, these results in corrections of up to 0.5\% to $\sigma_{vis}$.
-The overall uncertaintys estimate the bunch current measurement  to be 0.4\%.
-
-\item Orbit drift.
-This correction accounts for potential movement of the LHC orbit during the vdM scans.
-Time-dependent changes of the transverse beam positions for fixed machine parameters can alter the beam separation, this correction is composed of two independent corrections:
-
-Orbit drift separation "ODS", correction that aims to correct for the orbit drift in the scanning direction and only affects beam separation and  Orbit drift rate "ODR", correction that aims to correct for the orbit drift in the direction orthogonal to the scanning direction and only affects the luminometer rate.
-%The derived correction assumes that the beam overlap has a single Gaussian shape. The correction reads the $\sigma_{vis}$ in the orthogonal direction from the previous correction.
-
-Applying this correction improves the agreement between the $\sigma_{vis}$ values derived with different scan pairs and changes the average $\sigma_{vis}$ by about 0.3\%, considering the full size of the correction is as uncertainty.
-
-\item Beam Beam corrections.  The electromagnetic interaction between the two colliding proton bunches leads to two effects in beam-separation scans:
-
-Beam Beam deflection (BB).
-Corrects Beam Beam deflection that happens during bunch crossings at the collision point.
-Accounts for the electrical repulsion of the beams, which increases the lateral separation.
-The deflection is calculated and added to the nominal separation.
-
-Dynamic Beta.
-The so-called dynamic $\beta^{*}$  effect, which accounts for any changes in the proton density distributions of the bunches due to the single-particle interactions.
-As a result, the non-linear change during separation steps in transverse bunch profiles is observed, and can described by the effective change of the $\beta^{*}$  value.
-
-The corrections are calculated for each proton bunch pair individually, and the combined effect of the two corrections is an increase of $\sigma_{vis}$ by 1.0\%, with an uncertainty of 0.5\%.
-
-\item Length Scale.
-It applies a linear scaling to the beam separation to convert it from the "CMS scale" to the actual "physics scale".
-This is  calibrated by analyzing pp collision vertices reconstruced by the CMS tracker using data from the five length scale scan pairs performed in fills 8178, 8379, and 8381.This correction reduces $\sigma_{vis}$ by 1.0\% and results in an uncertainty of 0.12\%.
-
-\end{enumerate}
+\label{bbcorrections}
+%https://cms.cern.ch/iCMS/analysisadmin/cadilines?line=LUM-22-001
 
@@
 
-As we have seen in previous sections, the points generated for each step of the scan need to be fitted using a mathematical function.
-This allows us to extract the parameters we need, such as $\Sigma_{x,y}$ and peak values for all the bunches in the scan, in order to finally compute $\sigma_{\text{vis}}$.
-Within vdMFW, there are several pre-defined functions that use a combination of Gaussian functions with different adjustable parameters to achieve a better fit.
-These functions include Double Gaussian (DG), Single Gaussian (SG), Poly Gaussians (PG), among others.
-All of the above functions exist in versions with an additive constant to the entire function, typically used to fit to the background levels.\\
-
-For this analysis, various fit functions were tested, and the one with the best quality of fit was selected.
-The quality of the fit is primarily based on the convergence of the function with the points being fitted for each BCID.
-The convergence is assessed based on the covariance matrix, which measure the linear relationship between each pair of elements or variables.
-A  covariance status equal to 3 means a good convergence of the function.\\
-
-The second most important parameter for measuring the quality of the fit is having a good  Chi-square $\chi^2$.
-The  Chi-square goodness of fit test is a statistical hypothesis test that helps to determine whether a variable is likely to come from a specified distribution or not.
-This test provides a way to assess whether the data values have a good enough fit to our model, or if the model is questionable.
-In more general terms, this test compares observed values with expected or theoretical values according to the hypothesis.
-The goal is to minimize the calculation of the $\chi^2$ as defined in equation \ref{x^2}, from here is  inferred that the lower the value of $\chi^2$, the better the fit is considered to be.
-
-\begin{equation}
-\chi^{2}(\theta)=\sum_{i=1}^{N} \frac{(y_{i}-f(x_{i},\theta))^{2}}{\sigma_{i}^{2}}
-\label{x^2}
-\end{equation}
-
-where the observed values $y_{1}$,···, $y_{N}$ are measured with errors $\sigma_{1}$,···,$\sigma_{N}$" at the values of $x$ given without error by $x_{1}$,..., $x_{N}$.
-The theoretical  value is given by the function $f(x_{i},\theta)$.
-The value of $\theta$ is adjusted to minimize the value of $\chi^2$ \cite{Statistical_Data_Analysis}.
-
-After testing several mathematical fit models, those requiring background subtraction from SS periods analysis were ultimately discarded due to the unacceptably high chi-square values obtained, this was due to the inconsistencies mentioned the section \ref{bkg}.
-Therefore, it was decided to use functions that include a constant to model the background in the fit.
-The chosen model with the best fit quality and after applying all the corrections mentioned earlier, was a double Gaussian function plus a constant:
-%https://gitlab.cern.ch/bril/VdMFramework/-/blob/main/src/plotting/capsigma_over_time.py#L90
-%\begin{equation}
-%DG+Const= C+P \cdot \Biggl[ F \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 \sigma_{1}^{2} } \Biggr) + (1-F) \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 \sigma_{2}^{2} } \Biggr) \Biggr] 
-%\end{equation}
-\begin{equation}
-f(x)= C+P \cdot \Biggl[ F \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2(\frac{\Sigma\cdot R}{F \cdot R+1-F} )^{2} } \Biggr) + (1-F) \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 (\frac{\Sigma}{F \cdot R+1-F} )^{2} } \Biggr) \Biggr]
-\end{equation}
-%[5] + [2]*([3]*exp(-(x-[4])**2/(2*([0]*[1]/([3]*[1]+1-[3]))**2))
-    %    + (1-[3])*exp(-(x-[4])**2/(2*([0]/([3]*[1]+1-[3]))**2)) )
-%("#Sigma","#sigma_{1}/#sigma_{2}","peak","Frac","Mean","Const")
-%[0] -> [0]*[1]/([3]*[1]+1-[3])
- %[1] -> [0]/([3]*[1]+1-[3])"""
-\begin{itemize}
-\item $C$ is the constant value.
-\item $P$ the $peak$ rate.
-\item $F$ is the fraction of the peak rate attributed to the first Gaussian in the sum.
-\item $x$ is the beam position.
-\item $\bar{x}$ is the mean.
-\item $\Sigma$ is the overllap between the beams.
-\item $R$ is the ratio between the standard deviations of the  Gaussians (first over the second).
-\end{itemize}
-
-Figure \ref{vdM1_282_XYscan} shows the fit graphs of the first vdM scan pair for BCID 282 where  all the corrections described in the previous section have been applied and where  rates are normalized by the beam currents ($N_{1}N_{2}$), which is according of Eq.
-\ref{sigmavis_eq}.
-
-\begin{center}
-\begin{figure}[h!]
-\centering
-\includegraphics[width=.45\textwidth]{Chapter4/xscan.png}
-\includegraphics[width=.45\textwidth]{Chapter4/yscan.png}\\
-\caption[Fit for the vdM1 BCIDs 282 (x and y directions)]{Normalized rates and the resulting fitted curves with  fit model as a function of the beam separation ($\Delta$) for BCID 282 for $x$ (left) and $y$ (right) scan for the first vdM scan.}
-\label{vdM1_282_XYscan}
-\end{figure}
-\end{center}
-For the remaining BCID's, the fits for both vdM and BI scans exhibit a very similar behavior, and in all cases, the fits have converged successfully.
-The evaluation of the goodness of fit is shown in Fig.
-\ref{chi2/ndof} where displays a plot of the $\chi^{2}/ndof$ for all the five scan pairs, which has a mean value of 1.88.
-
-\begin{center}
-  \begin{figure}[h!]
-    \centering
-    \includegraphics[scale=.030]{Chapter4/DGConst_chi2.png}
-    \caption[$\chi^{2}$/ndof per BCID for all scan pairs]{ chi2/ndof for all the scan pairs.
-where the red dots represent the $x$-scans, and the blue dots represent the $y$-scans.
-It is important to note that in each scan, the BCIDs follow the same order, which is 282, 822, 2944, 3123, and 3302.}
-    \label{chi2/ndof}
-  \end{figure}
-\end{center}
-
 \section{Results}
 
-To compute $\sigma_{vis}$, the $\Sigma_{x,y}$ and $peak_{x,y}$ values have been extracted, the behavior of these values ​​for all scans pair are shown in the  Fig.
-\ref{capsigma_peak} (left) for $\Sigma_{x,y}$ and Fig.
-\ref{capsigma_peak} (right) for the $peak_{x,y}$ values , where those belonging to the scan in $x$ are presented in red and those belonging to the scan in $y$ are shown in blue.\\
-
-The values of $\Sigma_{x,y}$ wish provide a direct measurement of the beam shape show a decrease in both the $x$ and $y$ directions during the fill time, this is due to a phenomenon called "damping", which occurs due to the interaction between the particles in the beam and the electromagnetic fields in the LHC ring, these fields exert a force on the particles, causing them to lose energy and amplitude, which causes the beam to gradually focus with time.
-On the other hand the values ​​for the $peak$ are then a direct consequence of this effect, since a more focused beam means more collisions and thus a higher rate.\\
-
-The figure also displays a discontinuity in values between the BI2 and vdM3 scans, which can be attributed to the exclusion of the vdM2 scan for the reasons mentioned in the section \ref{data} .
-
-\begin{center}
-  \begin{figure}[h!]
-    \centering
-    \includegraphics[width=.49\textwidth]{Chapter4/DGConst_CapSigma.png}
-    \includegraphics[width=.48\textwidth]{Chapter4/DGConst_peak.png}
-    \caption[$\Sigma_{x,y}$ and peak values per BCID for all scan pairs]{$\Sigma_{x,y}$ (left) and peak values (right) extracted from the fit to compute $\sigma_{vis}$, where the red dots represent the $x$-scans, and the blue dots represent the $y$-scans, note that in each scan, the BCIDs follow the same order, which is 282, 822, 2944, 3123, and 3302.}
-    \label{capsigma_peak}
-  \end{figure}
-\end{center}
-
-The $\sigma_{vis}$ for all BCIDs (vdM and BI scans) is then computed from the fit results $\Sigma_{x,y}$ and $peak_{x,y}$ shown above, this is done using the Eq.
-\ref{sigmavis_eq}.
-The value of $R(0,0)$ is obtained is obtained by taking the average of the peaks in the $x$ and $y$ scans, which has already been normalized.
-As a result, Equation \ref{sigmavis_eq} is rewritten as:
-
-\begin{equation}
- \sigma_{vis}= 2\pi \Sigma_{x} \Sigma_{y} \Biggl( \frac{peak_{x}+peak_{y}}{2} \Biggr)
- \end{equation}
-
-Figure \ref{sigmavis_perbcid} shows the  value of $\sigma_{vis}$ per BCID for all the scans where the error on $\sigma_{vis}$ is assigned as:
-
-\begin{equation}
-\sigma_{vis\text{Err}}= 2 \pi \sqrt{ (\Sigma_{y} \cdot P \cdot \Sigma_{x\text{Err}})^{2} + (\Sigma_{x} \cdot P \cdot \Sigma_{y \text{Err}})^{2} + (\Sigma_{x} \Sigma_{y} P_{\text{Err}})^{2} }
-\end{equation}
-
-\begin{center}
-  \begin{figure}[h!]
-    \centering
-    \includegraphics[scale=.22]{Chapter4/DGConst_xsec.png}
-    \caption[$\sigma_{vis}$ per BCID for all scans]{ $\sigma_{vis}$ per BCID for all the scans,  in each scan, the BCIDs follow the same order, which is 282, 822, 2944, 3123, and 3302.}
-    \label{sigmavis_perbcid}
-  \end{figure}
-\end{center}
-
-To obtain the final value of sigma visible , we first perform a weighted average using 5 BCIDs for each scan as shown in Figure \ref{sigmavis_perscan} with blue dots.
-Subsequently, we perform another weighted average among the results of these 5 scans, this final value is represented by the red line in Figure \ref{sigmavis_perscan}.
-In both calcuation, it is assumed that there is no correlation between the BCIDs and the scans.
-Therefore, the computation of the weighted average and the total error  follows Equations \ref{average} and \ref{error} respectively, where the weight is assigned as $w_{i} = 1/\sigma_{visErr}^{2}$.
-
-\begin{eqnarray}
-\sigma_{vis}^{Avg}=\Biggl(\displaystyle\sum_{i} w_{i}\sigma_{vis}^{i} \Biggr)\Biggl( \displaystyle\sum_{i} w_{i} \Biggr)^{-1}
-\label{average}
-\end{eqnarray}
-
-\begin{eqnarray}
-\sigma_{vis,Err}^{Avg}=\frac{1}{\sqrt{ \displaystyle\sum_{i} w_{i}}} 
-\label{error}
-\end{eqnarray}
-
-The final result obtained is:
-\begin{equation}
-\sigma_{vis}=4163.3 \pm 3.3 \text{ (stat)  mb}
-\end{equation}
-
-\begin{center}
-  \begin{figure}[ht]
-    \centering
-    \includegraphics[scale=0.45]{Chapter4/xsec_perscan_v2.png}
-    \caption[$\sigma_{vis}$ average per scan and final result]{ $\sigma_{vis}$  per scan.} 
-    \label{sigmavis_perscan}
-  \end{figure}
-\end{center}
-
-As depicted in Figure \ref{sigmavis_perscan}, the scans demonstrate an RMS of $12.8 \text{ mb}$ for the $\sigma_{vis}$ values, which is larger than the statistical uncertainty.
-Notably, vdM1 and vdM3 exhibit the largest variations, deviating by approximately 2 standard deviations from the mean.
-These discrepancies can be attributed to systematic effects in the detector during the scans.
-Given that other luminometers display a similar trend, this could be due to a common systematic effect such as beam position or beam current $(N_{1}*N_{2})$.
-A study of the sources of systematic uncertainty will be performed in the future.
-In this work, we assign the RMS value as an estimate of the systematic uncertainty.
+\section{Systematic Uncertainties}

### 2025-03-07 monograph_Luis/Portada/Portada.tex
monografia

--- 2023-09-14 tesis_Luis/Portada/Portada.tex
@@
       \vspace{2cm}
-        {\Large \scshape {Development and calibration of the luminosity measurement system CMS Silicon Pixel Detector}}
+        {\Large \scshape {Desarrollo y calibración del sistema de medición de luminosidad del detector de píxeles de silicio CMS}}
 
@@
 
-        \makebox[5cm][c]{\LARGE THESIS}  \\[20pt]
-         in partial fulfillment of the
-requirements for the degree of:\\[5pt]
-        {\Large \textbf{{Maestr\'ia en Ciencias (F\'isica)}}}\\[40pt]
+        \makebox[5cm][c]{\LARGE Monograf\'ia}  \\[20pt]
+         En cumplimiento parcial de los requisitos para el grado de:\\[5pt]
+        {\Large \textbf{{Doctorado en Ciencias (F\'isica)}}}\\[40pt]
         By:\\[12pt]
-        \textbf{  {\large Luis Enrique CUEVAS PICOS}}
+        \textbf{  {\large Luis Enriquue Enrique CUEVAS PICOS}}
 
@@
 
-        { Hermosillo, Sonora} \hskip2.5cm {August 15, 2023}
+        { Hermosillo, Sonora} \hskip2.5cm { - - -, 2025}
       \end{center}

### 2025-03-21 tesis_David_Lic/Abstract/resumen.tex
tesis final

\chapter{Resumen}
En este trabajo se presenta un estudio detallado del modelo de ruido para la medición de luminosidad utilizando el método de conteo de clusters de píxeles (Pixel Cluster Counting, PCC) en el experimento CMS del Gran Colisionador de Hadrones (LHC). La luminosidad es un parámetro fundamental en los experimentos de física de partículas, ya que permite cuantificar la tasa de colisiones y, por ende, la producción de eventos de interés. El método PCC aprovecha la alta granularidad del detector de píxeles de silicio del CMS para medir la luminosidad con una excelente linealidad respecto al número de interacciones por cruce de haces (pile-up).

Se analizan datos adquiridos durante el año 2022, con un enfoque particular en la observación del fenómeno de afterglow, que consiste en señales residuales que afectan las mediciones posteriores a los bunches principales. Se propone un modelo matemático que describe tanto el afterglow tipo 1, de naturaleza electrónica, como el afterglow tipo 2, generado por partículas secundarias provenientes de la activación del material circundante. Además, se estudia la evolución temporal de los parámetros del modelo, lo que permite evaluar la estabilidad y consistencia del mismo. Los resultados obtenidos demuestran la capacidad del método PCC para proporcionar mediciones precisas de luminosidad, contribuyendo así a una mejor comprensión de los efectos que influyen en la detección de partículas en el LHC.

### 2025-03-21 tesis_David_Lic/Acknowledgement/acknowledgement.tex
tesis final

\chapter*{Agradecimientos}

En primer lugar, quiero agradecer a mis padres, quienes han sido mi mayor apoyo durante todo este proceso. Nunca se echaron para atrás y siempre estuvieron dispuestos a darme las herramientas y el respaldo necesario para llevar a cabo esta tarea. Quiero que sepan que no tengo ninguna queja ni arrepentimientos; al contrario, estoy profundamente agradecido por todo lo que han hecho por mí. Siempre confiaron en mí, siempre me alentaron a ser mejor y, sobre todo, siempre estuvieron a mi lado. Gracias, de todo corazón.

A mis hermanas, Elizabeth y Cinthya, les agradezco su apoyo incondicional en todo momento. Sus risas, sus abrazos y sus palabras de aliento fueron un impulso constante para seguir adelante. Ustedes siempre me recordaron que tengo la capacidad suficiente para completar este proyecto, incluso en los momentos en los que yo mismo dudaba. Gracias por estar ahí, siempre.

Al Dr. Feliciano Benítez, mi director de tesis, quiero expresarle mi más sincero agradecimiento por su paciencia, dedicación y confianza. Siempre tuvo la disposición y el tiempo para explicarme y guiarme paso a paso en este proyecto. Su apoyo constante fue vital para mí; sin su guía, no habría logrado ni la mitad de lo que hoy he conseguido. Estaré eternamente agradecido por sus palabras y por haberme acompañado en este camino.

A mis amigos y a todas las personas que me rodearon durante este proceso, especialmente a Val y Johana, les doy las gracias por empujarme a seguir adelante y por nunca dejarme solo. Su apoyo incondicional y su compañía fueron un faro en los momentos más complicados. Gracias por creer en mí incluso cuando yo no lo hacía.

Finalmente, y más importante, le doy gracias a Dios. Soy consciente de que esto fue posible porque, en mi debilidad, Él mostró Su fortaleza. Este proyecto, así como mi carrera en general, no hubieran sido posibles sin Su gracia y ayuda constante en mi día a día. A Él le doy toda la gloria y el honor.

### 2025-03-21 tesis_David_Lic/Chapter1/chapter1.tex
tesis final

\chapter{Introducción}
\label{ch1}

%%%%% https://cerncourier.com/a/pushing-the-precision-frontier/
% https://home.cern/news/news/physics/why-precision-luminosity-measurements-matter
La física de partículas es una rama de la física que se dedica al estudio de las partículas fundamentales y las fuerzas que constituyen la materia y la radiación en el universo. El Modelo Estándar clasifica a las partículas fundamentales y sus interacciones en dos grandes categorías: los fermiones, que son las partículas que forman la materia, y los bosones, que son las partículas responsables de transmitir las fuerzas fundamentales. Para investigar estas interacciones, se utilizan aceleradores de partículas de alta energía, los cuales permiten medir diversos parámetros y propiedades de las partículas generadas en las colisiones. En este capítulo, se presenta una visión general de las partículas elementales, los colisionadores de partículas y la evaluación de su rendimiento, destacando los conceptos y definiciones clave que son esenciales para la comprensión de este proyecto de tesis.

\section{Física de Partículas y el Modelo Estándar}

El universo está formado por una variedad de partículas diferentes. Los átomos, por ejemplo, están constituidos por electrones ($e$\textsuperscript{-}) con carga negativa, que se encuentran en estado ligado orbitando alrededor de un núcleo central. Este núcleo está compuesto por protones $(p)$, que poseen carga positiva, y neutrones $(n)$, que son eléctricamente neutros. Los electrones se mantienen unidos al núcleo debido a la atracción electrostática entre sus cargas opuestas, mientras que los protones y neutrones están cohesionados por la fuerza nuclear fuerte. Además de estas interacciones, también influyen la gravedad y la fuerza débil. La fuerza débil es responsable de fenómenos como la radiactividad nuclear, mientras que la gravedad, aunque extremadamente débil en comparación con las otras fuerzas, es la que determina la estructura del universo a gran escala debido a su naturaleza atractiva universal \cite{thomson_2013}.

A pesar de que este modelo físico es útil para describir la materia a bajas energías, cuando se exploran escalas de energía más altas, se descubren estructuras mucho más complejas. Este tipo de estudios ha permitido identificar 17 partículas fundamentales que constituyen la totalidad del universo conocido. Estas partículas se dividen en dos categorías principales: los fermiones, que son las partículas que forman la materia y tienen un espín de $1/2$, y los bosones, que son los mediadores de las fuerzas fundamentales y presentan un espín entero.

Comenzando con los fermiones, estos componenen a la materia en el universo y estos consisten en doce partículas fundamentales las cuales se clasifican en dos grupos: leptones y quarks. A su vez, estos se organizan en tres generaciones,

La materia está compuesta por fermiones, que incluyen un total de doce partículas fundamentales, divididas en dos tipos: los leptones y los quarks. Estas partículas se agrupan en tres generaciones, donde los miembros de generaciones superiores poseen una mayor masa que sus contrapartes en las generaciones anteriores. Los seis leptones se dividen en tres partículas con carga: el electrón ($e$\textsuperscript{-}), el muón ((${\mu}$\textsuperscript{-}), y el tau (${\tau}$\textsuperscript{-}), junto con sus correspondientes neutrinos: el neutrino electrónico ($\nu_{e}$), el neutrino muónico ($\nu_{\mu}$), y el neutrino tau ($\nu_{\tau}$).

Por otro lado, los quarks solo existen confinados dentro de hadrones, y su grupo está compuesto por seis tipos: el quark arriba ($u$), quark abajo ($d$), quark encanto ($c$), quark extraño ($s$), quark cima ($t$) y quark fondo ($b$). Las propiedades de estas doce partículas fundamentales se detallan en la Tabla 1.1, proporcionando una visión general de sus características y su papel en la estructura de la materia.

\begin{table}[h!]
	\begin{center}
%\centering
	\caption[Los doce fermiones fundamentales y sus propiedades]{Los doce fermiones fundamentales y sus propiedades}
		\label{tab:table1}
		\begin{tabular}{lllrcllrc}
                                                                                & \multicolumn{4}{c}{\textbf{Leptones}}                                                                     & \multicolumn{4}{c}{\textbf{Quarks}}                                                \\ 
%\cline{2-9}
 \midrule[1.1pt]
                            \multicolumn{1}{c}{Generación }& \multicolumn{2}{c}{Particula } & \multicolumn{1}{c}{\textit{Q}} & masa/GeV                          & \multicolumn{2}{c}{Particula} & \multicolumn{1}{c}{\textit{Q}} & masa/GeV  \\ 
\hline
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Primera\end{tabular}}  & electrón & ($e$\textsuperscript{-})                 & -1                             & 0.0005                            & down    & ($d$)                & -1/3                           & 0.003     \\
                                                                                & $e$-neutrino & ($\nu_{e}$)                 & 0                              & \textless{}10\textsuperscript{-9} & up      & ($u$)                & +2/3                           & 0.005     \\
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Segunda\end{tabular}} & muon     & (${\mu}$\textsuperscript{-})                 & -1                             & 0.106                             & strange & ($s$)                & -1/3                           & 0.1       \\
                                                                                & $\mu$-neutrino & ($\nu_{\mu}$)                 & 0                              & \textless{}10\textsuperscript{-9} & charm   & ($c$)                & +2/3                           & 1.3       \\
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Tercera\end{tabular}} & tau      & ({$\tau}$\textsuperscript{-})                 & -1                             & 1.78                              & bottom  & ($b$)                & -1/3                           & 4.5       \\
                                                                                & $\tau$-neutrino & ($\nu_{\tau}$)                 & 0                              & \textless{}10\textsuperscript{-9} & top     &($t$)                & +2/3                           & 174      
\end{tabular}
	\end{center}
		\end{table}

Los bosones son las partículas encargadas de mediar las interacciones entre los fermiones, a través del intercambio de partículas denominadas bosones gauge. La fuerza electromagnética es transmitida por el fotón ($\gamma$), mientras que la fuerza débil es mediada por los bosones $W^{\pm}$ y $Z^{0}$, y la fuerza fuerte por los gluones ($g$). También existe un bosón escalar, el bosón de Higgs, cuya función principal es conferir masa a las partículas fundamentales. La Tabla 1.2  presenta un resumen detallado de las fuerzas fundamentales que afectan a los fermiones, mostrando cómo estas fuerzas son transportadas por sus respectivos bosones mediadores.

\begin{table}[h!]
  \begin{center}
    \caption[Fuerzas experimentadas por los fermiones]{Fuerzas experimentadas por los fermiones.}
    \label{tab:table2}
    \begin{tabular}{l c c c c}
    &    &  \textbf{Electromagnetica} & \textbf{Débil} & \textbf{Fuerte}\\
      \midrule[1.1pt]
      \multirow{2}{*}{Leptones} & ${e}$\textsuperscript{-} \hspace{0.3cm}  ${\mu}$\textsuperscript{-} \hspace{0.3cm} ${\tau}$\textsuperscript{-} & \checkmark & \checkmark & \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
      & $ \nu_{e} $ \hspace{0.3cm}  $\nu_{\mu}$ \hspace{0.3cm} $\nu_{\tau}$  &  & \checkmark\\ % <-- Content of first column omitted.
      \hline
      \multirow{2}{*}{Quarks} & $u$ \hspace{0.5cm}  $c$\hspace{0.5cm} $t$ & \checkmark & \checkmark& \checkmark\\
      & $d$ \hspace{0.5cm}  $s$\hspace{0.5cm} $b$ & \checkmark & \checkmark & \checkmark\\

    \end{tabular}
  \end{center}
\end{table}

Las partículas mencionadas están descritas dentro del Modelo Estándar de la física de partículas, el cual es, hasta ahora, la teoría más sólida para explicar con éxito los resultados experimentales. Sin embargo, la mayoría de estos datos provienen de colisionadores de partículas, ya que dichas partículas se pueden producir y estudiar cuando se generan colisiones a energías muy elevadas.

\section{Colisionadores de Partículas y Sección Eficaz de Producción}

En los últimos años, la física de partículas ha logrado grandes avances, impulsados por el uso de aceleradores de partículas de alta energía. Estos dispositivos funcionan como microscópicos muy poderosos, permitiendo examinar las estructuras más pequeñas de la materia y sus partículas fundamentales, tales como electrones, protones, neutrones, neutrinos y quarks. Además, los aceleradores de partículas ofrecen la posibilidad de resolver misterios sobre los componentes desconocidos del universo, como la materia y la energía oscura.\\

Los colisionadores de partículas aceleran haces de partículas cargadas a velocidades cercanas a la de la luz mediante el uso de campos electromagnéticos. Cuando estos haces chocan a altas energías, se producen interacciones llamadas eventos, en los que se generan varias partículas nuevas (como el bosón de Higgs). La mayoría de estas partículas no se pueden observar directamente, ya que se desintegran rápidamente en otras partículas. Sin embargo, los experimentos con detectores de partículas permiten medir e identificar estas partículas mediante tecnologías y diseños especializados, que se basan en las propiedades de las partículas y sus interacciones con la materia \cite{thomson_2013}.\\

Un detector de partículas se suele construir en forma de un barril cilíndrico o poligonal, colocado en paralelo con los haces que colisionan. Dos tapas planas en los extremos sellan la estructura, permitiendo una cobertura casi completa del ángulo sólido alrededor del tubo de haces. Este tipo de detector consta de varias capas, cada una diseñada para registrar diferentes partículas creadas durante las colisiones \cite{thomson_2013}.\\

Los colisionadores de partículas se miden principalmente por dos factores: la energía disponible en el centro de masas y la luminosidad, que es la tasa de colisiones. La cantidad de energía disponible para la creación de nuevas partículas es crucial, ya que define el rango de partículas que pueden producirse y estudiarse. Durante los experimentos, las partículas se aceleran y se dirigen unas contra otras, generando nuevas partículas e interacciones que luego pueden ser analizadas \cite{undergraduate_accelerators_chapter}.\\

Los colisionadores de haces enfrentados permiten alcanzar energías extremadamente altas en el punto donde los haces se cruzan. Cuando las partículas en los haces tienen la misma energía y un momentum opuesto (es decir, cuando las masas son iguales), el experimento tiene lugar en el marco de referencia del centro de masas (CM), lo que permite que toda la energía del acelerador se emplee para crear partículas de gran masa. En física de partículas, la cantidad invariante de Lorentz ($s$) se utiliza para representar el cuadrado de la energía total entrante, y se define como:

\begin{equation}
s = \left ( \sum_{i = 1,2}^{}E_{i} \right )^{2}-\left ( \sum_{i = 1,2}^{}p_{i} \right )^{2}c^{2}
\end{equation}

Donde \( p \) y \( E \) representan el momento y la energía de cada partícula entrante, respectivamente. En el sistema de referencia del centro de masas (CM), donde los momentos de las partículas son iguales pero de direcciones opuestas, el segundo término en la ecuación de la cantidad invariante de Lorentz (\( s \)) se anula. Como resultado, la expresión se simplifica a \( s = 4E^2 \), donde \( E \) es la energía de cada partícula en el marco del centro de masas. Esta simplificación es crucial para calcular la energía disponible en las colisiones de partículas \cite{undergraduate_accelerators_chapter}.\\

El segundo parámetro importante para evaluar el desempeño de los colisionadores es la luminosidad, que indica la capacidad del acelerador para generar suficientes interacciones. La luminosidad se determina a través de un factor de proporcionalidad entre la probabilidad cuántica de que ocurra una interacción (llamada sección eficaz) y la cantidad de eventos por segundo para un proceso físico específico ($R$) \cite{ref_lib_vol3}.\\

En física de partículas, el término sección eficaz tiene un significado especializado que difiere de su uso cotidiano. Mientras que normalmente "sección" hace referencia a una parte o corte de un objeto, en este contexto se refiere a la probabilidad de que dos partículas interactúen durante una colisión, expresada en metros cuadrados. Cuando dos haces de partículas chocan en un acelerador, pueden darse varios procesos, y la sección eficaz de cada uno depende del tipo y la energía de las partículas que colisionan.\\

Por ejemplo, en el Gran Colisionador de Hadrones (LHC), algunas partículas como los bosones  $W^{\pm}$ y $Z^{0}$ tienen secciones eficaces grandes, lo que hace más frecuentes sus observaciones. En cambio, el bosón de Higgs tiene una sección eficaz mucho menor, lo que complica su producción y detección.\\

Para comprender mejor este concepto, imaginemos un caso simple: un haz de partículas del tipo $a$ atraviesa una región donde hay partículas del tipo $b$. La tasa de interacciones entre estos dos tipos de partículas depende de la densidad de partículas $b$ por unidad de volumen, denotada como $n_{b}$, y del flujo de partículas incidentes $a$, representado por $\phi_{a}$ . La tasa de interacción por partícula objetivo $b$ se puede expresar de la siguiente forma:

\begin{equation*}
  r_{b}=\sigma \phi_{a}
\end{equation*}

El concepto central en la física fundamental se puede describir mediante la sección eficaz de interacción, simbolizada por $\sigma$. Este parámetro, que se mide en unidades de área, refleja la probabilidad de que una interacción tenga lugar entre una partícula incidente y una partícula objetivo. Para visualizarlo, se puede pensar que cada partícula objetivo tiene un área efectiva, y la sección eficaz de interacción corresponde a esa área. En la figura 1.1(a), se muestra una representación de este concepto, donde una partícula del tipo $a$, que viaja con velocidad $v_{a}$, se mueve a través de una región con área $A$, que contiene partículas del tipo $b$ con velocidad $v_{b}$ en dirección opuesta. El valor de la sección eficaz de interacción depende de la probabilidad cuántica de que ocurra la interacción, lo cual es esencial para entender cómo se comportan las partículas durante las colisiones \cite{thomson_2013}.

\begin{center}
  \begin{figure}[h!]
    \centering
\includegraphics[scale=.35]{Chapter1/cross_section.png} 
 \caption[Ilustración de la sección eficaz]{Izquierda (a): haz incidente de partículas de tipo $a$ atravesando una región que contiente partículas de tipo $b$. Derecha (b):  vista proyectada de la región atravesada por la partícula incidente en un intervalo de tiempo $\delta t$.}
    \label{cross_section}
  \end{figure}
\end{center}

Para comprender la probabilidad de una interacción entre partículas de los tipos $a$ y $b$, supongamos que, durante un intervalo de tiempo $\delta t$, la partícula $a$ pasa a través de una región que contiene  $\delta N= n_{b}(v_{a}+v_{b}) A \delta t$ partículas de tipo $b$. La probabilidad de que ocurra una interacción se calcula dividiendo el área total efectiva de la sección transversal de las $\delta N$ partículas por el área $A$. Este cálculo puede interpretarse como la probabilidad de que la partícula incidente atraviese una de las regiones de área $\sigma$ que rodean a cada una de las partículas objetivo, tal como se muestra en la figura 1.1(b).

En este sentido, la sección eficaz de un proceso se define como el área efectiva asociada con el objetivo para ese proceso en particular, y se mide en unidades de área. Formalmente, se expresa mediante la ecuación 1.2.

\begin{equation}
\sigma=\frac{\text{número de interacciones por unidad de tiempo por partícula objetivo}}{\text{flujo incidente}}
\label{cross}
\end{equation}

%begin{equation}
%\sigma=\frac{\text{number of interaction per unit time per target particle}}{\text{incident flux}}
%\end{equation}

%\delta P= \frac{\delta N \sigma}{A}=\frac{n_{b}(v_{a}+v_{b})A\sigma \dela t}{A}= n_{b}v\sigma \delta t$
%where $v=v_{a}+v_{b}$. The interaction rate for each particle of type $a$ is $r_{a}= \frac{dP}{dt}= n_{b} v\sigma$.
%For a beam of particles of type $a$ with number density $n_{a}$ confined to a volume $V$, the total interaction rate is:
%$\text{rate}=r_{a}n_{a}V=(n_{b}v\sigma) n_{a}V= (n_{a}v)(n_{b}V)\sigma$

%$\text{rate}=(n_{a}v)(n_{b}V) \sigma = \phi N_{b} \sigma$

%Thus the total rate is equal to
%$\text{rate}= \text{flux} \times \text{number of target particles} \times \text{cross section}$

%More formally, the cross section for a process is defined as:
\section{Luminosidad }

En los experimentos de física de partículas, el número de interacciones útiles (o eventos) es tan crucial como la energía involucrada. La capacidad de un acelerador de partículas para generar estas interacciones se mide mediante un parámetro llamado "luminosidad instantánea" \( \mathcal{L}_{inst} \). Esta luminosidad es directamente proporcional al número de eventos producidos por segundo y a la sección eficaz \( \sigma_p \) del proceso de interés \cite{concept_of_luminosity}.

\begin{equation}
R=\mathcal{L}_{inst} \cdot \sigma_{p}
\end{equation}

Donde las unidades de la luminosidad son $cm^{-2}s^{-1}$.

Para derivar una expresión general para la luminosidad en el caso de dos haces que colisionan, consideramos que ambos haces actúan simultáneamente como el objetivo y el haz incidente. Supondremos que los haces están "agrupados", es decir, que las partículas se organizan en paquetes o "bunches".

En este escenario, cada paquete de partículas se considera como una región de alta densidad de partículas que interactúan entre sí. La luminosidad instantánea se puede entonces expresar en términos del número de partículas por paquete, el tamaño del paquete y la velocidad de los haces. El número de interacciones por unidad de tiempo dependerá tanto de la densidad de las partículas en los paquetes como de la sección eficaz de la interacción entre ellas.

\begin{center}
  \begin{figure}[h!]
    \centering
\includegraphics[scale=.25]{Chapter1/luminosity.png} 
 \caption[Interacción entre dos haces de partículas]{Esquema de una interacción entre dos haces de partículas\cite{concept_of_luminosity}.}
    \label{luminosity}
  \end{figure}
\end{center}

%A schematic picture is shown in Fig. \ref{luminosity}. Since the two beams are not stationary but are moving through each other, the overlap integral depends on the longitudinal position of the bunches, and therefore on time. As the beams move towards and through each other, the two beams have different distribution functions and a different number of particles in the beams \cite{concept_of_luminosity}. The overlap integral, which is proportional to the luminosity $\mathcal{L}_{inst}$, can then be written as:

En la Figura 1.2 se muestra un diagrama que ilustra cómo dos haces se intersectan entre sí. Dado que estos haces no están estáticos, sino en movimiento, la forma en que se superponen depende del tiempo y la posición de los paquetes de partículas. Mientras los haces se desplazan, también tienen distribuciones y números de partículas diferentes en su interior \cite{concept_of_luminosity}.

La luminosidad instantánea  \( \mathcal{L}_{inst} \) , que es proporcional a la integral de superposición de los haces, se puede expresar de la siguiente manera:

\begin{equation}
  \mathcal{L}_{inst}\propto K\cdot \int\int\int \int_{-\infty}^{\infty} \rho_{1}(x,y,s,-s_{0}) \rho_{2}(x,y,s,s_{0})dxdydsds_{0}
    \label{lumi_1}
\end{equation}

Donde las funciones $\rho_{1}(x,y,s,-s_{0})$ y $\rho_{2}(x,y,s,s_{0})$ representan la distribución de densidad del haz en un tiempo $t$. Ahora, asumimos que los bunches interaccionan en el punto $s_{0} = 0$. Debido a que los haces estan en movimiento y en dirección contraria, debemos considerar un factor cinético relativista de la forma:

\begin{equation}
 K = \sqrt{(\vec{v_{1}}-\vec{v_{2}})^{2}-(\vec{v_{1}}\times \vec{v_{2}})^{2}/c^{2}}
    \label{kinematic}
\end{equation}

Cuando los paquetes de partículas colisionan de manera frontal y se desplazan casi a la velocidad de la luz, el factor cinético relativista toma un valor de 2.

Asumiendo que las densidades son no correlacionadas en todos los planos y que las colisiones son frontales, donde las velocidades de los dos paquetes son opuestas $(\vec{v_{1}}=-\vec{v_{2}})$, la integral de superposición puede factorizarse de la siguiente manera:

\begin{equation}
  \mathcal{L}_{inst}= 2N_{b} N_{1}N_{2}f \int\int\int\int_{-\infty}^{\infty}  \rho_{1x}(x)\rho_{1y}(y)\rho_{1s}(s-s_{0})\rho_{2x}(x)\rho_{2y}(y)\rho_{2s}(s+s_{0}) dxdydsds_{0}
    \label{luminosity_2}
\end{equation}

donde $N_{b}$ es el número de bunches en un haz, $N_{1}$ y $N_{2}$ son las particulas por bunche y $f$ la frecuencia de revolución.\\

%\begin{eqnarray}
%\rho_{iz}(z)= \frac{1}{\sqrt{2\pi} \sigma_{z}} exp \biggl(-\frac{z^{2}}{2\sigma_{z}^{2}} \biggr)&z=x,y&i=1,2 
%\end{eqnarray}

%\begin{eqnarray}
%\rho_{s}(s\pm s_{0})= \frac{1}{\sqrt{2\pi} \sigma_{s}} exp \biggl(-\frac{(s\pm s_{0})^{2}}{2\sigma_{s}^{2}} \biggr)
%\end{eqnarray}

Suponiendo perfiles gaussianos en todas las dimensiones y longitudes de los paquetes aproximadamente iguales $(\sigma_{1s}\approx \sigma_{2s})$, la ecuación (1.6) se puede resolver para obtener la luminosidad instantánea en función de la superposición de los haces \cite{concept_of_luminosity}.

Para el caso general en el que $\sigma_{1x}\neq \sigma_{2x}$ y $\sigma_{1y}\neq \sigma_{2y}$, las distribuciones de densidad de las partículas en los planos $x$ y $y$ serán diferentes. En este caso, la integral de superposición debe tener en cuenta las diferentes dispersión de los haces en las direcciones transversales, lo que implica que las ecuaciones para calcular la luminosidad instantánea se vuelve mas compleja.

\begin{equation}
  \mathcal{L}_{inst}= \frac{N_{1} N_{2} N_{b}f }{2\pi \sqrt{\sigma_{1x}^{2}+\sigma_{2x}^{2}}\sqrt{\sigma_{2y}^{2}+\sigma_{2y}^{2}}}
  \label{lumi_general}
\end{equation}

Asumiendo haces iguales, $\sigma_{1x}= \sigma_{2x} \text{ y } \sigma_{1y}= \sigma_{2y}$:

\begin{equation}
  \mathcal{L}_{inst}= \frac{N_{1} N_{2} N_{b}f }{4\pi \sigma_{x} \sigma_{y}}
  \label{lumi_theor}
\end{equation}

Esta expresión es ampliamente reconocida como la fórmula para la luminosidad de dos haces gaussianos que colisionan frontalmente. Muestra cómo la luminosidad está relacionada con el número de partículas en cada paquete y el tamaño de los haces.\\

En la práctica, la integral en la ecuación (1.6) no se puede resolver de manera analítica debido a que las propiedades de los haces que colisionan no se conocen con precisión. Por lo tanto, se implementa una técnica experimental con una configuración específica de la máquina para estimar estas integrales, obteniendo una expresión similar a la ecuación (1.8).

Para determinar el número total de eventos, utilizamos la luminosidad integrada, que es una medida de la cantidad total de datos recopilados. Este valor es fundamental para evaluar la efectividad de un acelerador, y se puede expresar de la siguiente manera:

\begin{equation}
  \mathcal{L}_{int}=\int_{0}^{T} \mathcal {L}_{\text{inst}}(t') dt'
\end{equation}

El valor de $\mathcal{L}_{inst}$ se evalúa a lo largo del tiempo $T$, excluyendo el posible tiempo muerto, ya que su intensidad disminuye a medida que el número de protones se reduce durante las colisiones de cada ciclo de llenado. Por lo tanto, la luminosidad integrada $\mathcal{L}_{int}$ está directamente relacionada con el número de eventos observados según la siguiente expresión:

\begin{equation}
  \mathcal{L}_{int} \ndot \sigma_{p}= \text{número de eventos de interés}
\end{equation}

La luminosidad integrada tiene unidades de $cm^{-2}$ y a menudo se expresa en barns inversos. Un barn es equivalente a $10^{-24}cm^{2}$, lo que facilita la comparación de los resultados experimentales en términos de colisiones efectivas a lo largo del tiempo.\\

Comprender con precisión la luminosidad es fundamental para los análisis en física, como la búsqueda de nuevas partículas, la medición de las propiedades de partículas conocidas o la detección de procesos raros. La exactitud de nuestras mediciones físicas se ve principalmente afectada por las incertidumbres en la luminosidad. Si se logra aumentar la precisión de las mediciones de luminosidad, los físicos podrán interpretar mejor sus observaciones y explorar áreas de la física que aún desconocemos.

Un ejemplo de esto se muestra en la Figura 1.3, donde se ilustra la producción de bosones $W$ y $Z$ en el Gran Colisionador de Hadrones (LHC). En esta figura, las barras de error internas representan las incertidumbres experimentales, mientras que las barras de error externas incluyen las incertidumbres en las predicciones teóricas. Además, la caja sombreada indica las incertidumbres en la medición de la luminosidad, que son mayores que las incertidumbres estadísticas y otras sistemáticas \cite{lumi_uncertainties}.

\begin{center}
  \begin{figure}[h]
    \centering
\includegraphics[scale=.28]{Chapter1/lumi_uncertainty.png} 
 \caption[Incertidumbre de la Luminosidad en un proceso]{Producción de bosones $W^+$, $W^-$, $W$ y $Z$ y sus predicciones teoricas. La caja sombreada indica las incertidumbres en la medición de la luminosidad, mostrando que estas son mayores que las incertidumbres experimentales (barras azules) y las incertidumbres teóricas (barras verdes). Los valores de las mediciones y las predicciones teóricas se encuentran en la parte derecha de la figura.}
    \label{lumi_incertainty}
  \end{figure}
\end{center}

\section{El Gran Colisionador de Hadrones (LHC)}

El Gran Colisionador de Hadrones (LHC) es el acelerador de partículas más grande y potente del mundo. Comenzó a operar el 10 de septiembre de 2008 y es la adición más reciente al complejo de aceleradores de CERN. El LHC consta de un anillo de 27 kilómetros que contiene imanes superconductores, además de varias estructuras utilizadas para acelerar las partículas mientras se desplazan a lo largo del anillo. Dentro del acelerador, dos haces de partículas viajan a velocidades cercanas a la de la luz hasta que colisionan. Los haces se mueven en direcciones opuestas dentro de tubos separados, que se mantienen en un vacío ultra alto \cite{LHC}.\\

Los electroimanes superconductores generan un potente campo magnético que guía los haces de partículas a lo largo del anillo del acelerador. Estos imanes están formados por bobinas de un cable eléctrico especial que funciona en un estado superconductor. En este estado, el cable puede conducir electricidad sin resistencia ni pérdida de energía. El acelerador utiliza una variedad de imanes, entre ellos 1232 imanes dipolares de 15 metros de longitud que desvían los haces, y 392 imanes cuadrupolares de entre 5 y 7 metros de longitud que enfocan los haces. Justo antes de la colisión, se emplea un tipo diferente de imán para "comprimir" las partículas, aumentando así la probabilidad de colisiones. Para mantener estos imanes en estado superconductor, deben ser enfriados a una temperatura extremadamente baja de -271.3°C.\\

El proceso de generar haces de protones para el LHC es complejo y se lleva a cabo en varias etapas. Primero, se ioniza el hidrógeno para obtener protones, los cuales son acelerados en paquetes hasta alcanzar una energía de $50 MeV$ en el Acelerador Lineal 2 (LINAC2). Posteriormente, estos paquetes pasan por tres aceleradores circulares: el Booster, el Sincrotrón de Protones (PS) y el Super Sincrotrón de Protones (SPS), donde se aumenta su energía gradualmente a $1.4 GeV, 26 GeV$ y $450 GeV$, respectivamente. Después de estas fases de preaceleración, los paquetes de protones son inyectados en el anillo del LHC, donde se aceleran aún más hasta alcanzar energías de hasta $7 TeV$ por paquete, mientras circulan en direcciones opuestas. Este ciclo se denomina un "llenado" del LHC y generalmente involucra alrededor de \(10^{14}\) protones, organizados en paquetes que forman el haz de protones. La figura 1.4 muestra una representación esquemática de todo el complejo de aceleradores del CERN.

\begin{center}
  \begin{figure}[h]
    \centering
    \includegraphics[scale=.35]{Chapter1/lhc_complex_fig.png}
    \caption[Complejo LHC]{Diagrama de llenado del LHC.}
    \label{lhc_com}
  \end{figure}
\end{center}

El Centro de Control del CERN es el centro neurálgico encargado de gestionar todos los controles, servicios e infraestructura técnica del LHC. Desde allí, se dirigen los haces de protones para que colisionen en cuatro ubicaciones diferentes a lo largo del anillo del acelerador, las cuales corresponden a las posiciones de cuatro detectores de partículas. CMS y ATLAS son detectores de propósito general diseñados para explorar una amplia variedad de física del Modelo Estándar (SM) y más allá del Modelo Estándar (BSM), mientras que ALICE y LHCb son detectores especializados que se centran en el estudio de fenómenos específicos.

### 2025-03-21 tesis_David_Lic/Chapter2/chapter2.tex
tesis final

\chapter{Descripción del Experimento}

 Los detectores de propósito general en colisionadores de alta energía suelen tener capas de detección dispuestas en forma cilíndrica alrededor del eje del haz. Un ejemplo destacado de este tipo de detector es el Solenoide Compacto de Muones (CMS), una de las colaboraciones científicas internacionales más grandes de la historia y parte del LHC en el CERN. El CMS está diseñado para llevar a cabo una variedad de experimentos, incluidos los dedicados al estudio del Modelo Estándar. Este capítulo describe los componentes principales del detector CMS, con especial atención a los sistemas encargados de medir la luminosidad, enfocándose particularmente en el rastreador de píxeles de silicio, cuyo detalle es crucial para esta tesis.

\section{CMS (Compact Muon Solenoid)}

El experimento CMS es un detector de propósito general del LHC, compuesto por varias capas dedicadas a funciones específicas. El sistema central es un imán solenoide que genera un campo magnético de 4 teslas, el cual desvía partículas cargadas para medir su energía y momento. El detector tiene 21.6 metros de largo y 14.6 metros de diámetro, con un peso total de 14,000 toneladas \cite{CMS_Exp_2008}.\\

Las partículas cargadas deben ser desviadas al alejarse del punto de colisión, lo que se logra mediante un fuerte campo magnético. Este campo cumple dos funciones clave: primero, permite diferenciar las partículas cargadas positivamente de las negativamente cargadas, ya que se desplazan en direcciones opuestas bajo la influencia del mismo campo magnético; segundo, posibilita la medición del momento de la partícula.\\

Entre sus componentes, destaca el rastreador de silicio, que permite reconstruir trayectorias de partículas cargadas mediante píxeles y tiras de silicio. Este rastreador registra "hits" en las capas de detección, que luego se usan para calcular la trayectoria de las partículas.\\

\begin{center}
  \begin{figure}[ht]
    \centering
    \includegraphics[scale=.3]{Chapter2/CMS_detector_simple.png}
    \caption[Vista panorámica del detector CMS]{Vista panorámica del detector CMS.}
    \label{detector_CMS}
  \end{figure}
\end{center}

El calorímetro electromagnético (ECAL) mide la energía de electrones y fotones a través de cristales de tungstato de plomo (PbWO4), mientras que el calorímetro hadrónico (HCAL) detecta hadrones y mide la energía de jets y la energía transversa perdida. Ambos calorímetros cubren diferentes secciones: el barril, los endcaps y el preshower para ECAL, y las secciones forward, endcap, barrel y outer para HCAL \cite{det_summary}.\\

Finalmente, el CMS cuenta con un sistema de detección de muones, que al ser más pesados que los electrones, atraviesan los calorímetros y son detectados en subdetectores ubicados dentro del yugo de acero del solenoide. Estos detectores permiten medir el momento de los muones dentro y fuera del campo magnético del CMS \cite{det_summary}.\\

\begin{center}
  \begin{figure}[ht]
    \centering
    \includegraphics[scale=.3]{Chapter2/slice_det.png}
    \caption[Vista transversal del detector CMS.]{Vista transversal del detector CMS con algunas interacciones de partículas (desde la región de interacción del haz hasta el detector de muones).}
    \label{slice_CMS}
  \end{figure}
\end{center}

El sistema de coordenadas del CMS está centrado en el detector, con el eje $y$ orientado hacia arriba, el $x$ hacia el centro del LHC, y el $z$ alineado con el haz, permitiendo definir parámetros como el ángulo acimutal y la pseudorapidez \cite{det_summary}.\\

\section{Luminómetros en CMS}
\label{Luminometers}

El CMS utiliza siete sistemas para medir la luminosidad. Dos de ellos, el Pixel Luminosity Telescope (PLT) y el Fast Beam Condition Monitor (BCM1F), están diseñados específicamente para esta función, mientras que el calorímetro Hadronic Forward (HF) emplea un sistema de lectura dedicado. Además, existen tres métodos más: Drift Tube Luminosity (DT), el Pixel Cluster Counting Method (PCC) y el Vertex Counting Method (VTX), que utilizan datos del detector CMS y su sistema de adquisición de datos. Por último, los detectores RAMSES, destinados al monitoreo ambiental, también contribuyen a las mediciones de luminosidad \cite{pas_18}.\\

El PLT usa sensores de píxeles de silicio distribuidos en telescopios para medir coincidencias triples, lo que permite identificar trayectorias de partículas. En el HF, la medición se realiza con dos algoritmos: HFOC, basado en la ocupación de torres, y HFET, que usa la energía transversal. El método DT mide la tasa de "muon track stubs", pero no permite mediciones individuales por colisión. El BCM1F, con sensores de silicio y diamante, ofrece mediciones precisas y separa impactos de colisiones de los inducidos por la máquina. RAMSES, aunque no diseñado como luminómetro, puede medir la luminosidad detectando fotones. Finalmente, el PCC cuenta los clústeres de píxeles en el detector, proporcionando una medición adicional de luminosidad \cite{pas_18}.\\

La ubicación de los 7 luminómetros antes mencionados se muestran en la figura 2.3.\\

\begin{center}
  \begin{figure}[ht]
    \centering
    \includegraphics[scale=.3]{Chapter2/detectors.png}
    \caption[Luminómetros en CMS]{Los siete luminómetros que componen el sistema de medición de luminosidad de CMS son: BCM1F, HFET, HFOC, PLT, REMUS, DT y PCC.}
    \label{luminometers}
  \end{figure}
\end{center}

\section{Sistema de Rastreo del CMS}

El sistema de rastreo en el CMS es esencial para medir con precisión las trayectorias y momentos de las partículas cargadas y para reconstruir vértices secundarios. Este sistema tiene 5.8 metros de largo y 2.5 metros de diámetro, y está compuesto por dos subsistemas principales: el detector de píxeles y el rastreador de tiras (Strip tracker). El detector de píxeles se encuentra en el centro, rodeado por el rastreador de tiras, como se ilustra en la Figura 2.4 \cite{pas_18}.\\

El rastreador de tiras se divide en el Tracker Inner Barrel (TIB) y Tracker Inner Disks (TID), que tienen cuatro capas de barril y tres discos en cada endcap, y el Tracker Outer Barrel (TOB) junto con los Tracker EndCaps (TEC), que consisten en seis capas y nueve discos en los extremos. Este sistema cubre 198 $m^{2}$ con 15,148 módulos de silicio y alrededor de 9.3 millones de tiras, proporcionando una alta resolución en la medición de trayectorias.\\

El sistema permite medir la curvatura de las partículas en el campo magnético del solenoide, lo que facilita determinar su momento. Es crucial para identificar partículas como muones y electrones, y para reconstruir eventos complejos de colisiones de alta energía.\\

El rastreador de píxeles, la parte más interna, consta de cuatro capas concéntricas en el barril y tres discos en los endcaps. Con 124 millones de píxeles, permite una resolución extremadamente alta para medir las trayectorias de las partículas cercanas al punto de interacción. Su cobertura llega a una pseudorapidez de \( | \eta | < 2.5 \) y es clave para detectar partículas en eventos de alta densidad.\\

Los píxeles en cada capa se organizan en una matriz, permitiendo la medición de las coordenadas en dos dimensiones $(r, z)$, lo que contribuye a la reconstrucción precisa de las trayectorias de las partículas. En la siguiente sección, se detallarán más aspectos técnicos de este detector, incluyendo su funcionamiento y las características que lo hacen fundamental en la reconstrucción de eventos a alta precisión.\\

\begin{center}
  \begin{figure}[ht]
    \centering
    \includegraphics[scale=.23]{Chapter2/strip_layout.png}
    \caption[Corte transversal esquemático a través del rastreador del CMS.]{Corte transversal esquemático a través del rastreador del CMS.}
    \label{strip_layout}
  \end{figure}
\end{center}

\section{Silicon Pixel Detector}

El detector de píxeles de silicio forma el componente más interno del sistema de rastreo. Este detector proporciona una cobertura espacial completa en el área más cercana al punto de interacción, lo que permite un seguimiento preciso de las partículas cargadas y la reconstrucción de vértices. La cobertura del detector de píxeles se encuentra en el rango de pseudorapidez $(|\eta| < 2.5)$, operando en un entorno rico en radiación, caracterizado por una alta densidad de trayectorias \cite{phase1_Pixel_Detector}.\\

El detector de píxeles del CMS está compuesto por cuatro capas concéntricas en forma de barril (L1-L4), cada una con radios de 29, 68, 109 y 160 mm, y tres discos (D1-D3) en cada extremo, ubicados a distancias de 291, 396 y 516 mm del centro del detector. Todo el detector consta de 1856 módulos de sensores de silicio segmentados \cite{CMS_Exp_2008}.\\

La Figura 2.5 muestra un esquema de la disposición del detector de píxeles de la Fase 1 del CMS, el cual cubre un área total de silicio de $1.9 m^{2}$. Los detectores BPIX y FPIX están equipados con cuatro medios cilindros de servicio cada uno, que tienen una longitud combinada de $540 mm$. Estos cilindros albergan los circuitos de lectura y control, además de proporcionar soporte para las líneas de alimentación y los tubos de refrigeración del detector \cite{phase1_Pixel_Detector}.\\

\begin{center}
  \begin{figure}[h]
    \centering
    \includegraphics[scale=.26]{Chapter2/phase1_PixelDetector.png}
    \caption[Fase 1 del detector de pixeles en CMS]{Disposición del detector de píxeles de la Fase 1 del CMS en vista longitudinal.}
    \label{phase1_pixel_detector}
  \end{figure}
\end{center}

El detector BPIX está compuesto por dos mitades independientes, cada una de estas es autosuficiente desde el punto de vista mecánico. Cada mitad incluye un medio detector y dos semi-cilindros de servicio. Este detector consta de 1184 módulos de sensores de silicio segmentados, y la orientación de las superficies de cada módulo es paralela al campo magnético en ambas mitades.\\

A diferencia del BPIX, el detector FPIX está dividido en cuatro cuadrantes, que operan de manera independiente entre sí. Cada cuadrante incluye tres medio-discos que se alojan dentro de un semi-cilindro de servicio. La disposición de los sensores se ajusta de modo que el lado más largo de los píxeles esté alineado radialmente. El detector FPIX está compuesto por un total de 672 módulos de sensores de silicio segmentados, que se distribuyen entre anillos internos y externos, con 22 y 34 módulos respectivamente.\\

Un módulo del detector de píxeles está formado por un sensor de silicio plano con dimensiones de 18.6 $\times$ 66.6 $mm^{2}$, que abarca un área activa de 116.2 $\times$ 64.8 $mm^{2}$. Este sensor está compuesto por 160 $\times$ 416 píxeles, que están conectados a una matriz de 2 por 8 chips de lectura (ROC) mediante una soldadura de bump. Cada chip de lectura contiene 4160 canales, encargados de medir la altura del pulso de cada píxel. En total, el detector cuenta con 124 millones de canales de lectura. El tamaño estándar de cada píxel es de 100 $\times$ 150 $\mu m^{2}$.\\

\begin{center}
  \begin{figure}[h]
    \centering
    \includegraphics[scale=.2]{Chapter2/modules_drawing.png}
    \caption[Tipos de módulos en el detector de pixeles]{Estas son ilustraciones de los módulos del detector de píxeles utilizados en los detectores BPIX L1 (izquierda), BPIX L2-L4 (centro) y FPIX (derecha).}
    \label{modules_drawing}
  \end{figure}
\end{center}

La Figura 2.6 ilustra los módulos del detector de píxeles de la Fase-1 del CMS, mientras que la Figura 2.7, a la izquierda, muestra el diseño del sensor de silicio conectado al chip de lectura. En el lado derecho de la Figura 2.7, se puede ver una partícula cargada atravesando un píxel, proporcionando suficiente energía para expulsar electrones de los átomos de silicio. Un voltaje aplicado al sensor permite la recolección de estas cargas como una pequeña señal eléctrica, que luego es amplificada por un chip electrónico de lectura \cite{phase1_Pixel_Detector}.\\

\begin{center}
  \begin{figure}[h]
    \centering
    \includegraphics[scale=.3]{Chapter2/PixelSensor.png} \includegraphics[scale=.3]{Chapter2/hit.png}
    \caption[Vista esquemática de un sensor de píxeles y su conexión a los canales de lectura]{Izquierda: diseño del sensor de píxeles conectado a un chip de lectura. Derecha: detección de impactos en un píxel correspondiente del sensor.}
    \label{module and hit}
  \end{figure}
\end{center}

\section{Reconstrucción del Pixel Cluster}

El proceso de reconstrucción de trayectorias involucra varios pasos. Primero, se identifican las señales que superan un umbral específico en los canales de píxeles y se utilizan para crear clústeres. Cada clúster representa la carga depositada por una sola partícula cargada. Posteriormente, se estiman la posición y las incertidumbres de los clústeres en un sistema de coordenadas local y ortogonal con respecto al plano del sensor \cite{Track_Reco_2014}.\\

Para que un clúster sea considerado válido, debe tener una carga de al menos 4000 electrones \cite{Track_Reco_2014,phase1_Pixel_Detector}. Las partículas mínimamente ionizantes (MIP) que atraviesan un sensor de silicio con un grosor de 285 $\mu m$ suelen depositar una energía equivalente a unos 21,000 electrones cuando inciden normalmente. Sin embargo, esta carga generalmente se dispersa en más de un píxel debido a la deriva de Lorentz, que provoca que los electrones sean desplazados por la fuerza generada por el campo electromagnético, lo que lleva a la formación de clústeres de carga.\\

La Figura 2.8 muestra un ejemplo de cómo se construye un clúster de píxeles. Cada cuadro en la figura representa un píxel. Los píxeles rojos indican que tienen la carga requerida, de hasta 2000 electrones, para ser considerados píxeles válidos y, por lo tanto, se incluyen en el clúster. Por otro lado, los píxeles verdes corresponden a depósitos de carga por debajo del umbral de 2000 electrones y no se incluyen en el clúster. La línea azul punteada en la figura representa la trayectoria de la partícula que viaja paralela al plano $xz$. A medida que avanza, activa píxeles en su camino de manera precisa, así como píxeles que se desvían de su trayectoria debido a la deriva de Lorentz \cite{Pixel_Hit_Reconstruction}.

\begin{center}
  \begin{figure}[h]
    \centering
    \includegraphics[scale=.25]{Chapter2/pixel_cluster.png} 
    \caption[Construcción de un pixel cluster]{La figura ilustra un ejemplo de un clúster de píxeles con una carga total de 4,000 electrones, que es el umbral necesario para que el clúster sea válido. Los píxeles rojos tienen la carga requerida, mientras que el píxel verde no alcanza el umbral.}
    \label{cluster}
  \end{figure}
\end{center}

### 2025-03-21 tesis_David_Lic/Chapter3/chapter3.tex
tesis final

\chapter{Mediciones de Luminosidad y Afterglow}
\label{ch3}

La medición precisa de la luminosidad suministrada al experimento CMS por el LHC es fundamental por varias razones. En tiempo real, la medición de la luminosidad ofrece información sobre el rendimiento del LHC y CMS, incluyendo el monitoreo de las tasas de activación de los disparadores. En el análisis fuera de línea, la luminosidad es un componente clave para calcular la sección eficaz de los procesos observados o para establecer límites superiores en la búsqueda de procesos más allá del modelo estándar.

Como se ha mencionado, para medir la luminosidad en CMS se utilizan un total de siete luminómetros, cada uno de los cuales mide una cantidad específica en el detector, como impactos, trazas o cúmulos. La tasa $R$ medida por el luminómetro es proporcional a la luminosidad instantánea $\mathcal{L}_{inst}$ , con una constante de proporcionalidad dada por la sección eficaz visible $\sigma_{vis}$.

\begin{equation}
R(t)=\mathcal{L}_{inst}\sigma_{vis}
\label{lumi_exp_gen}
\end{equation}

La determinación de \( \sigma_{\text{vis}} \) se realiza mediante escaneos de van der Meer (vdM) utilizando una configuración especial del LHC.

\section{Pixel Cluster Counting method (PCC)}

El método PCC utiliza el número promedio de cúmulos (clústers) de píxeles en el detector de píxeles de silicio del CMS para determinar una medición de luminosidad offline. Este método aprovecha la alta densidad de píxeles en la región interna del sistema de rastreo de CMS. Esto significa que la probabilidad de que un solo píxel sea impactado por dos partículas cargadas provenientes del mismo cruce de haces es extremadamente baja. Esta gran granularidad y baja ocupación proporcionan mediciones con una excelente respuesta lineal respecto al pile-up (número de interacciones por cruce de haces) $\mu$. En promedio, la ocupación del detector es inferior al 0.1\%\cite{lumi_precise_2015_2016}.\\

La Figura 3.1 muestra una simulación con eventos de colisión $pp$ de cero sesgo, en la que se presenta la tasa de conteo de clústers de píxeles como una función del pile-up en el rango observado en la Run 2, que va de 0 a aproximadamente 50 $\mu$. El número promedio de clusters de píxeles es del orden de 111 por evento. La curva roja es un ajuste polinomial de primer orden con pendiente. Los resultados indican un alto nivel de concordancia, evidenciado por el ajuste estimado de bondad de ajuste $\chi^{2}$  por grado de libertad (dof), de aproximadamente 0.5, lo que demuestra que la tasa PCC es altamente lineal en este rango bajo condiciones simuladas \cite{ Phase2_Upgrade,lumi_precise_2015_2016}.

\begin{center}
  \begin{figure}[h!]
    \centering
    \includegraphics[scale=.35]{Chapter3/pileup_lineality.png} 
    \caption[Linealidad del PCC con pile-up]{ Linealidad del conteo de clústers de píxeles en el rango de pile-up observado en la Run 2 (de 0 a aproximadamente 50) a partir de simulaciones. La línea roja es un ajuste lineal a los puntos.}
    \label{pileup}
  \end{figure}
\end{center}

Para obtener el número promedio de clústers de píxeles por evento, se promedian varios eventos de cero sesgo. Este valor se define como::

\begin{equation}
\left < N_{\text{cluster}} \right > \equiv \left < N_{\text{cluster}/\text{interaction}} \right > \mu
\end{equation}

Bajo condiciones de sesgo mínimo, $\mu$ se puede expresar como:

\begin{equation}
\mu = \frac{\sigma_{\text{minBias}}}{f} \cdot \mathcal{L}_{inst}
\end{equation}

donde $f$ es la frecuencia de revolución del LHC y $\mathcal{L}_{inst}$ es la luminosidad instantánea de un solo paquete (SBIL, por sus siglas en inglés). La sección eficaz de sesgo mínimo ($\sigma_{text{minBias}}$) está relacionada con la sección eficaz visible del PCC mediante el número promedio de clústers por interacción:

\begin{equation}
\sigma_{vis}= \left < N_{\text{cluster}/\text{interaction}} \right >\cdot \sigma_{\text{minBias}}
\end{equation}

Juntando todo, la luminosidad obtenida será:

\begin{equation}
\mathcal{L}_{inst}=\frac{\left < N_{\text{cluster}} \right >}{\sigma_{vis}} \cdot f
\end{equation}

%This method is capable of providing a precise luminosity measurement over longer time periods, but it cannot do so for a single luminosity section (23 seconds) as is possible with online luminometers. The reason for this limitation is the limited CMS trigger bandwidth available for collecting data \cite{pas_18}. A detailed discussion on this topic can be found in the next chapter.\\

%PCC si calcula lumi por cada lumi section.  Esto no tiene que ver con online vs offline.  PCC es un offline luminometro, quiere decir que los datos llegan tarde.  Con PCC solo podemos calcular lumi cada lumi section, debido a la baja estadistica (por la lectura de los datos de zero bias).  otros luminometros tienen precision con NB4 (HF, PLT, BCM1F).

\section{Datos adquiridos en 2022}

El 12 de julio de 2022, comenzó la recolección de datos para Run 3 del Gran Colisionador de Hadrones (LHC), lo que resultó en una luminosidad total registrada de 38.48 fb⁻¹ durante ese año. Estos datos se recolectaron durante colisiones protón-protón con una energía en el centro de masa de √s = 13.6 TeV. El periodo de recolección de datos comenzó con el inicio de los haces estables y concluyó cuando el haz fue detenido intencionalmente o cuando se interrumpieron los haces estables momentáneamente para realizar estudios del haz. La luminosidad entregada por el LHC al CMS (representada en azul) y la luminosidad registrada por CMS (mostrada en naranja) durante este periodo se ilustran en la Figura 3.2 \citep{wikicern}.

\begin{center}
  \begin{figure}[h!]
    \centering
    \includegraphics[width=.45\textwidth]{Chapter3/lumi_per_day_cumulative_pp_2022.png}
    \includegraphics[width=.45\textwidth]{Chapter3/lumi_per_day_pp_2022.png}
    \caption[Luminosidad integrada acumulada día a día en 2022]{(izquierda) Luminosidad integrada acumulada día a día. (derecha) Luminosidad integrada día a día en 2022, como el primer gráfico, pero no acumulativa.} 
    \label{Lumi_2022}
  \end{figure}
\end{center}

\section{PCC sobre la orbita del LHC}

En esta sección se presenta el análisis del Pixel Cluster Counting (PCC) a lo largo de toda la órbita del LHC, que comprende 3564 espacios disponibles para colisiones (buckets). El objetivo es estudiar cómo varía el conteo de cúmulos de píxeles en función de la posición de las interacciones dentro de la órbita y analizar la estructura específica de los trenes de protones y las secciones vacías entre ellos.\\

El LHC no utiliza todos los espacios disponibles para colisiones de manera continua; en su lugar, los protones se agrupan en lo que se conocen como trenes. Cada tren está compuesto por una serie de bunches o "vagones", que son grupos de protones que circulan de manera sincronizada alrededor del anillo del acelerador. Entre estos trenes existen espacios vacíos llamados gaps, que se emplean para evitar la superposición de señales no deseadas y permitir la estabilidad del sistema de inyección de los haces.\\

La gráfica obtenida (Figura 3.3) muestra el número de clusters de píxeles contados por el sistema PCC a lo largo de toda la órbita del LHC, lo cual incluye tanto las regiones donde ocurren colisiones como las regiones de espacio vacío donde no hay interacciones. En la gráfica, los trenes de protones son claramente identificables como picos que se agrupan en ciertas regiones, mientras que las secciones vacías entre los trenes aparecen como caídas abruptas en el conteo de clusters.\\

En la gráfica, los trenes de protones son observados como series de bunches sucesivos que producen un alto número de cúmulos de píxeles en el detector de CMS. A medida que el haz de protones interactúa con los bunches, los cúmulos de píxeles detectados aumentan significativamente debido a las colisiones de partículas dentro del detector.\\

Los gaps son esenciales para prevenir la acumulación excesiva de efectos indeseables, como el afterglow o el ruido residual, y garantizar un funcionamiento estable del sistema de inyección y detección.\\

\begin{center}
  \begin{figure}[h!]
    \centering
    \includegraphics[width=.55\textwidth]{Chapter3/full_orbit_data_only_no_fit.png}
    \caption[Llenado (fill) de una orbita]{Se presenta el número de clusters de píxeles contados por el sistema PCC a lo largo de toda la órbita del LHC, mostrando la estructura de trenes y gaps entre bunches.} 
    \label{Lumi_2022}
  \end{figure}
\end{center}

Esta gráfica es fundamental para visualizar cómo se distribuyen las colisiones y los espacios vacíos a lo largo de la órbita, lo que permite comprender mejor la estructura de los bunches y el impacto de los trenes en el conteo de cúmulos de píxeles.\\

\section{Observación del Afterglow}

En la Figura 3.4 se presenta un tren de bunches con la medición del número de clusters de píxeles detectados por el método PCC a lo largo de un tren de bunches en la órbita. En este caso, se puede observar el fenómeno conocido como afterglow, que afecta las mediciones posteriores a los bunches principales debido a la persistencia de señales residuales en el detector. Este afterglow se divide en dos tipos:\\

El \textbf{afterglow de tipo 1} es el resultado de un desbordamiento de la señal electrónica de un bunch crossing ID (BCID) al siguiente. En otras palabras, la señal medida en un bunch es afectada por un rezago de la señal electrónica de bunches anteriores. Este fenómeno es notable en la caída abrupta de las mediciones de PCC justo después de los bunches activos, tal como se muestra en la gráfica. La contribución del afterglow tipo 1 es predominantemente electrónica y tiene una caída rápida en los bunches inmediatamente posteriores al bunch principal.\\

El \textbf{afterglow de tipo 2} proviene de partículas secundarias generadas por la activación del material circundante debido a las interacciones del haz principal. Estas partículas tienen vidas medias más largas y decaen exponencialmente con el tiempo, lo que genera una señal residual en bunches posteriores durante un intervalo de tiempo más extenso. A diferencia del afterglow tipo 1, la caída del afterglow tipo 2 es más gradual, y está presente a lo largo de un rango más amplio de BCIDs, como se observa en la gráfica en bunches posteriores a los 40 BCID.\\

\begin{center}
  \begin{figure}[h!]
    \centering
    \includegraphics[width=.55\textwidth]{Chapter3/singleTrainNoFit.png}
    \caption[Gráfica de un tren]{La gráfica permite visualizar claramente ambos tipos de afterglow: el afterglow tipo 1 es visible en la caída abrupta en los primeros BCIDs (cerca del BCID 40), mientras que el afterglow tipo 2 se manifiesta como una disminución exponencial más suave a lo largo de los bunches posteriores (más allá del BCID 40).} 
    \label{Lumi_2022}
  \end{figure}
\end{center}

\section{Ajuste de Datos y Residuos}

Para ajustar los datos obtenidos en la medición del número de clusters de píxeles detectados, se utiliza un modelo compuesto que describe tanto el fenómeno de afterglow de tipo 1 como el de tipo 2, así como la contribución residual de interacciones previas. El modelo que se emplea para el ajuste de los datos está dado por la siguiente expresión analítica:

\[
f(x) = \sum_{k=0}^{N-1} n_k \left[ \delta_{x, x_k} + A \cdot \delta_{x, x_k + 1} + B_k \cdot e^{-C_k(x - x_k)} \cdot \Theta(x - x_k) \right] + D \cdot e^{-E \cdot x}
\]

Donde los términos son definidos de la siguiente manera:

\begin{itemize}
    \item $\delta_{x, x_k}$: Delta de Kronecker, que representa un pico en la medición exactamente en $x_k$, correspondiente a la señal principal del bunch colisionante.
    \item $A$: Amplitud del afterglow tipo 1, que es constante para todos los BCIDs.
    \item $\delta_{x, x_k + 1}$: Delta de Kronecker que representa el afterglow tipo 1 en el BCID inmediatamente siguiente ($x_k + 1$).
    \item $B_k$: Amplitud del afterglow tipo 2, que describe el decaimiento exponencial debido a la generación de partículas secundarias por activación del material circundante.
    \item $C_k$: Tasa de decaimiento exponencial del afterglow tipo 2.
    \item $\Theta(x - x_k)$: Función escalón de Heaviside, que asegura que el decaimiento exponencial del afterglow tipo 2 solo se aplique para $x \geq x_k$.
    \item $D$: Amplitud del ruido residual.
    \item $E$: Tasa de decaimiento exponencial del ruido residual.
\end{itemize}

Este modelo compuesto tiene en cuenta tanto las contribuciones puntuales de los bunches colisionantes como el comportamiento más gradual del afterglow tipo 2, además de la influencia de colisiones previas que pueden generar señales persistentes en el detector.

A continuación, se presenta un ajuste de los datos experimentales utilizando este modelo. En la Figura 3.5, se observa el resultado del ajuste realizado a los datos obtenidos mediante el método Pixel Cluster Counting (PCC). El ajuste incluye tanto los picos asociados al afterglow de tipo 1, como las contribuciones del afterglow tipo 2 y la componente residual de interacciones previas.

\begin{center}
  \begin{figure}[h!]
    \centering
    \includegraphics[width=.55\textwidth]{Chapter3/fitAfterglowTrain_fit.png}
    \caption[Ajuste de los Datos Experimentales]{ Ajuste de los datos obtenidos mediante el método Pixel Cluster Counting (PCC) utilizando el modelo compuesto que incluye las contribuciones del afterglow tipo 1, tipo 2 y residual. Los parámetros $A_{k}$, $B_{k}$, $C_{k}$, $D$ y $E$ son ajustados a los datos experimentales, mostrando cómo el modelo describe las señales detectadas a lo largo de los bunches.} 
    \label{Lumi_2022}
  \end{figure}
\end{center}

Por otro lado, se muestran los residuos del ajuste en la Figura 3.6, que representan la diferencia entre los datos observados y el modelo ajustado. Estos residuos permiten evaluar la calidad del ajuste y detectar posibles desviaciones o inconsistencias en la modelización de los datos.

\begin{center}
  \begin{figure}[h!]
    \centering
    \includegraphics[width=.55\textwidth]{Chapter3/fitAfterglowTrain_residuals.png}
    \caption[Residuos del Ajuste]{Residuos del ajuste realizado a los datos experimentales, representando la diferencia entre los datos observados y el modelo ajustado. Los residuos se distribuyen alrededor de cero, lo que indica la calidad del ajuste y la capacidad del modelo para capturar las características del fenómeno observado.} 
    \label{Lumi_2022}
  \end{figure}
\end{center}

El análisis de los residuos es fundamental para asegurar que el modelo propuesto sea adecuado para describir el comportamiento del afterglow en los datos experimentales. Los residuos deben distribuirse de manera aleatoria alrededor de cero, sin patrones sistemáticos, lo que indicaría que el modelo ha capturado de manera adecuada las características del fenómeno observado.

\section{Evolución de los Parámetros en Función del Tiempo}

En esta sección, se presenta un análisis de la evolución temporal de los parámetros del modelo matemático utilizado para ajustar los datos obtenidos mediante el método de conteo de clusters de píxeles (Pixel Cluster Counting, PCC). Como se describió en la sección 3.5, el modelo matemático empleado para el ajuste de los datos incluye contribuciones del afterglow tipo 1, tipo 2 y una componente residual de interacciones previas. Los parámetros clave del modelo son \(A\), \(B_k\), \(C_k\) y \(E\), cuyas propiedades ya fueron definidas en la sección anterior.

Para analizar la evolución de estos parámetros en función del tiempo, se realizó un ajuste de los datos utilizando el modelo descrito en la sección 3.5. Los valores de los parámetros \(A\) y \(B_k\) se obtuvieron para diferentes momentos durante la toma de datos, lo que permitió graficar su comportamiento a lo largo del tiempo.

\begin{figure}[h!]
    \centering
    \includegraphics[width=.4\textwidth]{Chapter3/T1F_vs_tiempo.png}\hspace{0.1 cm}     \includegraphics[width=.4\textwidth]{Chapter3/T2A_vs_tiempo.png}

    \caption{Evolución de los parámetros en función del tiempo.}
    \label{fig:T1F_vs_tiempo}
\end{figure}

%\begin{figure}[h!]
 %   \centering
  %  \caption{Evolución de $T2A$ en función del tiempo.}
   % \label{fig:T2A_vs_tiempo}
%\end{figure}

\newpage

Las gráficas obtenidas permiten evaluar la consistencia del modelo matemático utilizado para el ajuste de los datos. Si los parámetros $T1\_frac$ y $T2A$ muestran una evolución estable a lo largo del tiempo, esto sugiere que el modelo es robusto y capaz de capturar adecuadamente las características del afterglow en diferentes condiciones experimentales. Por otro lado, fluctuaciones significativas en los parámetros podrían indicar la necesidad de ajustar el modelo o considerar factores adicionales que no han sido incluidos en el análisis inicial.\\

En resumen, el análisis de la evolución temporal de los parámetros del modelo proporciona información valiosa sobre la dinámica del afterglow en el detector CMS. Estos resultados son fundamentales para garantizar la precisión de las mediciones de luminosidad y para mejorar la comprensión de los efectos que influyen en la detección de partículas en el LHC.\\

### 2025-03-21 tesis_David_Lic/Chapter4/chapter4.tex
tesis final

--- 2023-08-07 tesis_Luis/Chapter4/chapter4.tex
@@
 %https://indico.cern.ch/event/1244981/contributions/5230942/attachments/2581191/4452030/POG_pres.pdf
-\item Residual beam positions.
+%\item Residual beam positions.
 To investigate additional deviations of the beams, a fit model is created by combining the nominal beam positions, the orbit drift correction, and the beam-beam deflection.
@@
 
-In general, the residual deviations are less than 2 $\mum$.
+%In general, the residual deviations are less than 2 $\mum$.
 The primary source of uncertainty here is from the scale of the beam-beam deflection.
@@
 Taking into account the above considerations, the total systematic uncertainty is found to be 0.73\% ($30.3 \text{ mb}$).
-\newpage
+%\newpage
 \begin{table}[!ht]

### 2025-03-21 tesis_David_Lic/Conclusion/conclusion.tex
tesis final

\chapter{Conclusiones}

En esta tesis se ha llevado a cabo un análisis exhaustivo del modelo de ruido para la medición de luminosidad utilizando el método de conteo de clusters de píxeles (PCC) en el experimento CMS. A través de este estudio, se ha demostrado que el método PCC es una herramienta robusta y precisa para medir la luminosidad, gracias a su alta granularidad y baja ocupación en el detector de píxeles de silicio. La observación y caracterización del afterglow, tanto de tipo 1 como de tipo 2, ha permitido comprender mejor los efectos residuales que influyen en las mediciones de luminosidad, lo que es crucial para garantizar la precisión de los datos obtenidos en el LHC.

El modelo matemático propuesto, que incluye contribuciones del afterglow y del ruido residual, ha mostrado un buen ajuste a los datos experimentales, como lo evidencian los residuos distribuidos aleatoriamente alrededor de cero. Además, el análisis de la evolución temporal de los parámetros del modelo ha revelado que estos presentan un comportamiento estable a lo largo del tiempo, lo que refuerza la validez del modelo utilizado.

En resumen, este trabajo contribuye a mejorar la precisión de las mediciones de luminosidad en el experimento CMS, lo que es fundamental para la búsqueda de nuevas partículas, la medición de las propiedades de partículas conocidas y la detección de procesos raros. Los resultados obtenidos abren nuevas perspectivas para futuros estudios en física de partículas, especialmente en lo que respecta a la optimización de los métodos de medición de luminosidad en colisionadores de alta energía.

### 2025-03-21 tesis_David_Lic/Portada/Portada.tex
tesis final

--- 2022-12-29 tesis_Rodolfo/Portada/Portada.tex
@@
         \vspace{.4cm}   %% DEFINE EL ESPACIO ENTRE LA DOBLE LINEA Y EL NOMBRE DE LA DIVISIÓN
-        {\scshape \large Divisi\'on de Ciencias Exactas y Naturales}
-        {\scshape Departamento de Investigaci\'on en F\'isica} %% NOMBRE DE LA DIVISIÓN
+        {\scshape \large Facultad Interdisciplinaria de Ciencias Exactas y Naturales}\\
+        {\scshape Departamento de F\'isica} %% NOMBRE DE LA DIVISIÓN
     \end{center}
@@
       \vspace{2cm}
-        {\Large \scshape {Measurements of the Large Hadron Collider luminosity using the CMS silicon pixel detector}}
+        {\Large \scshape {Estudio del modelo de ruido para la medici\'on de luminosidad con Pixel Cluster Counting en CMS}}
 
@@
 
-        \makebox[5cm][c]{\LARGE THESIS}  \\[20pt]
-         in partial fulfillment of the
-requirements for the degree of:\\[5pt]
-        {\Large \textbf{{Maestr\'ia en Ciencias (F\'isica)}}}\\[40pt]
-        By:\\[12pt]
-        \textbf{  {\large Jesus Rodolfo MORENO CHAVEZ}}
+        \makebox[5cm][c]{\LARGE TESIS}  \\[20pt]
+         en cumplimiento parcial para conseguir el grado de:\\[5pt]
+        {\Large \textbf{{LICENCIADO EN FISICA}}}\\[40pt]
+        Por:\\[12pt]
+        \textbf{  {\large David Alonso Guzm\'an L\'opez}}
 
@@
 
-        { \large Director}:\\Dr. Jose Feliciano BENITEZ RUBIO
+        { \large Director}:\\Dr. Jose Feliciano Benitez Rubio
 
@@
 
-        { Hermosillo, Sonora} \hskip2.5cm {December 08, 2022}
+        { Hermosillo, Sonora} \hskip2.5cm {2025}
       \end{center}

### 2025-03-21 tesis_David_Lic/chap_originales/Chapter2/chapter2.tex
tesis final

--- 2023-05-05 tesis_Luis/Chapter2/chapter2.tex
@@
     \includegraphics[scale=.3]{Chapter2/slice_det.png}
-    \caption[Transverse slice view of the CMS detector]{Transverse slice of the CMS detector with some particle interactions (from the beam interaction region to the muon detector) \cite{det_summary}.}
+    \caption[Transverse slice fo CMS detector]{Transverse slice of the CMS detector with some particle interactions (from the beam interaction region to the muon detector) \cite{det_summary}.}
     \label{slice_CMS}
@@
     \includegraphics[scale=.3]{Chapter2/detectors.png}
-    \caption[Layout of the luminometers in the CMS detector]{The seven luminometers that make up the CMS luminosity measurement system.
+    \caption[CMS Luminometers]{The seven luminometers that make up the CMS luminosity measurement system.
 Multiple independent systems used online: BCM1F, HFET, HFOC, PLT (independently calibrated) ,REMUS and  DT (cross-calibrated) , Pixel cluster counting is used after offline processing.}
@@
     \includegraphics[scale=.2]{Chapter2/modules_drawing.png}
-    \caption[Types of modules in the pixel detector]{ Drawings of the pixel detector modules for BPIX L1 (left), BPIX L2–4 (middle), and the FPIX detector (right)\cite{phase1_Pixel_Detector}.}
+    \caption[Pixel detector modules]{ Drawings of the pixel detector modules for BPIX L1 (left), BPIX L2–4 (middle), and the FPIX detector (right)\cite{phase1_Pixel_Detector}.}
     \label{modules_drawing}
@@
     \includegraphics[scale=.3]{Chapter2/PixelSensor.png} \includegraphics[scale=.3]{Chapter2/hit.png}
-    \caption[Schematic view of a pixel sensor and its connection to the readout channels]{ left: layout pixel sensor conected to a readout chip , right: hits detection in a corresponding  pixel sensor \citep{thomson_2013}.
-}
+    \caption[PixelSensor]{ left: layout pixel sensor conected to a readout chip , right: hits detection in a corresponding  pixel sensor \citep{thomson_2013}. }
     \label{module and hit}
@@
     \includegraphics[scale=.25]{Chapter2/pixel_cluster.png} 
-    \caption[Construction of a pixel cluster]{ The figure illustrates a pixel cluster example with a total charge up of 4,000 electrons, required to be a valid cluster.
+    \caption[Pixel cluster]{ The figure illustrates a pixel cluster example with a total charge up of 4,000 electrons, required to be a valid cluster.
 The red pixels have the required charge while the green one does not.}

### 2025-03-21 project_Omar/paper.tex
Add files via upload

--- 2022-05-24 project_Luis/paper.tex
@@
 
-\def\Student{Luis Enrique CUEVAS PICOS }
+\def\Student{OMAR ALEJANDRO ANGULO GIL }
 \def\Title{MASTERS THESIS PROJECT}
@@
 \def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
-\def\ProjectTitle{Studies of the CMS Pixel Cluster Counting luminometer using Run 3 data}
-\def\ProjectTitleESP{Estudios del luminometro Pixel Cluster Counting del CMS usando datos de la corrida 3}
+\def\ProjectTitle{}
+\def\ProjectTitleESP{}
 \def\ResearchLine{Fisica Matematica}
@@
 %%header and footer
-\lhead{\Student\ / \ \Dept}
+\lhead{\Student\ }
 \rhead{\TitleESP}
@@
   {\bf \Prog \par}
-  {\Dept \par}
+  %{\Dept \par}
   {\Institution \par}
@@
 \newpage
-\hspace{2pt}
-\vfill
+
+%\hspace{2pt}
+%\vfill
 
   \begin{center}
-    {\Large \ProjectTitle \par}
-    \vspace{1cm}
+%    {\Large \ProjectTitle \par}
+%    \vspace{1cm}
     {\itshape\textbf{Abstract}\par}
@@
   \centering
-  \includegraphics[width=0.8\columnwidth]{./HL-LHC_2022.pdf}
+  \includegraphics[width=0.8\columnwidth]{./HLLHCLumi.png}
   \caption{Forecast for peak luminosity (red dots) and integrated luminosity (violetline) in the HL-LHC era with nominal HL-LHC parameters\cite{BejarAlonso:2749422}.}  %\cite{collaborations2019report} era la [5] de la ant fig2
@@
 %To develop the upgraded luminosity measurement system for Run 3 and the HL-LHC phases.
-This will allows us precise tests of the Standard Model and searches for new physics like dark matter and supersymmetry theories.
+The calibration of this luminometer allows for precise measurement of the LHC luminosity and subsequent tests of the Standard Model and searches for new physics like dark matter and supersymmetry theories.
 
@@
 
-\item Understand the CMS silicon pixel detector including the barrel and endcap sensors.
+\item Understand the CMS silicon pixel detector and the PCC method for luminosity measurement using this detector.
 
-\item Study the stability and linearity of the sensors in the different layers or disks of the pixel detector and select the stable components.
+\item Process the PCC data from Run 2 (2018) for understanding the tools.
 
-\item Determine new methods for measurement of the stability and linearity of the system.
+\item Process the PCC data from Run 3 (2022) to obtain the calibration constant.
+
+\item Study the vdM Calibration method, including the fit models and systematic uncertainties.
 
@@
 \begin{itemize}
-\item
-
+\item Determination of PCC luminometer calibration constant for the 2022 data to be collected in September 2022.
+\item Estimation of the background noise for PCC during vdM calibration program.
+\item Estimation of statistical and systematic uncertainties.
 \end{itemize}
@@
 
-\item {\bf Summer 2021}:
+\item {\bf Summer 2022}:
   \SubItem{ Readings on Standard Model of particle physics,  the LHC and CMS experiments}
   \SubItem{ Linux/Computing skills (\textsc{Bash, Emacs, c/c++, python, ROOT})}
-  \SubItem{ Computing accounts at CERN and Fermilab}
-  \SubItem{ Initial planning of the analysis strategy}
+  \SubItem{ Computing account and usage of the computing center CERN-lxplus}
+  \SubItem{ Understanding luminosity and the methodology for the measurement}
 
-\item {\bf Semester 2021-2}:
-  \SubItem{ Course I: on particle physics, particle detection, or data analysis}
+\item {\bf Semester 2022-2}:
+  \SubItem{ Elective course I on particle physics, particle detection, or data analysis}
   \SubItem{ Analysis/Computing skills (\textsc{Bash, Emacs, c/c++, python, ROOT})}
-  \SubItem{ Analysis of the LHC Run 3 luminosity data using the PCC method}
+  \SubItem{ Practice analysis using Run 2 luminosity data}
+  \SubItem{ Initial processing and analysis of Run 3 vdM data}
 
-\item {\bf Semester 2022-1}:
-  \SubItem{ Course II on particle physics, particle detection, or  data analysis}
-  \SubItem{ Completion of the analysis of the LHC Run 3 luminosity data using the PCC method}
+\item {\bf Semester 2023-1}:
+  \SubItem{ Elective course II on particle physics, particle detection, or  data analysis}
+  \SubItem{ Completion of the analysis of the LHC Run 3 vdM data and determination of the calibration constant}
   \SubItem{ Presentation of results at national or international conference}

### 2025-03-21 monograph_Luis/Chapter1/chapter1.tex
update

@@
 
+%%%%% https://cerncourier.com/a/pushing-the-precision-frontier/
+% https://home.cern/news/news/physics/why-precision-luminosity-measurements-matter
+Particle physics is the branch of physics that studies the fundamental components of matter and the interactions that govern their behavior.
+It is based on the Standard Model, a theoretical framework that classifies elementary particles into fermions, which make up matter, and bosons, which mediate the fundamental forces (except gravity, which is not yet incorporated into this model).
+To investigate these particles and their interactions, high-energy particle accelerators are used to generate collisions that allow scientists to measure particle properties and study fundamental phenomena.
+
+This introduction provides a general overview of elementary particles, particle colliders, and the measurement of their properties, establishing the groundwork for studying theoretical and experimental models in particle physics.
+It highlights key concepts and definitions essential for understanding this project.
+
 \section{Particle Physics and The Standard Model}
+
+Matter and its fundamental interactions are governed by 17 elementary particles that make up the \textbf{Standard Model} of particle physics.
+These particles are divided into two main groups: fermions, which have a spin of \( \frac{1}{2} \), and bosons, which have an integer spin.
+Matter is primarily composed of fermions, which include twelve fundamental particles classified into two types: leptons and quarks.
+These particles are organized into three generations, with each successive generation having a greater mass than its corresponding particle in the previous generation \cite{thomson_2013}.\\
+
+The group of six leptons includes three charged particles: the electron (\(e^-\)), the muon (\(\mu^-\)), and the tau (\(\tau^-\)), along with their corresponding neutrinos: the electron neutrino (\(\nu_e\)), the muon neutrino (\(\nu_\mu\)), and the tau neutrino (\(\nu_\tau\)).
+On the other hand, quarks are only found in hadrons.
+The group of six quarks consists of: the up quark (\(u\)), the down quark (\(d\)), the charm quark (\(c\)), the strange quark (\(s\)), the top quark (\(t\)), and the bottom quark (\(b\)) \cite{griff,thomson_2013}.
+The properties of these twelve particles are summarized in Table \ref{tab:table1}.
+
+\begin{table}[h!]
+	\begin{center}
+%\centering
+	\caption[The twelve fundamental fermions and their properties]{Classification and properties of the twelve fundamental Fermions divided between Quarks and Leptons\cite{thomson_2013}.}
+		\label{tab:table1}
+		\begin{tabular}{lllrcllrc}
+                                                                                & \multicolumn{4}{c}{\textbf{Leptons}}                                                                     & \multicolumn{4}{c}{\textbf{Quarks}}                                                \\
+%\cline{2-9}
+ \midrule[1.1pt]
+                            \multicolumn{1}{c}{Generation }& \multicolumn{2}{c}{Particle } & \multicolumn{1}{c}{\textit{Q}} & mass/GeV                          & \multicolumn{2}{c}{Particle} & \multicolumn{1}{c}{\textit{Q}} & mass/GeV  \\
+\hline
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}First\end{tabular}}  & electron & ($e$\textsuperscript{-})                 & -1                             & 0.0005                            & down    & ($d$)                & -1/3                           & 0.003     \\
+                                                                                & $e$-neutrino & ($\nu_{e}$)                 & 0                              & \textless{}10\textsuperscript{-9} & up      & ($u$)                & +2/3                           & 0.005     \\
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Second\end{tabular}} & muon     & (${\mu}$\textsuperscript{-})                 & -1                             & 0.106                             & strange & ($s$)                & -1/3                           & 0.1       \\
+                                                                                & $\mu$-neutrino & ($\nu_{\mu}$)                 & 0                              & \textless{}10\textsuperscript{-9} & charm   & ($c$)                & +2/3                           & 1.3       \\
+\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Third\end{tabular}} & tau      & ({$\tau}$\textsuperscript{-})                 & -1                             & 1.78                              & bottom  & ($b$)                & -1/3                           & 4.5       \\
+                                                                                & $\tau$-neutrino & ($\nu_{\tau}$)                 & 0                              & \textless{}10\textsuperscript{-9} & top     &($t$)                & +2/3                           & 174
+\end{tabular}
+	\end{center}
+		\end{table}
+
+Bosons act as mediators of interactions between fermions by exchanging particles known as gauge bosons.
+The electromagnetic force is mediated by the photon (\(\gamma\)), which interacts with charged particles such as electrons (\(e^-\)) and protons (\(p\)).
+The weak force is mediated by the \(W^{\pm}\) and \(Z^{0}\) bosons, interacting with all leptons and quarks, facilitating processes like beta decay in nuclei.
+The strong force, responsible for holding quarks together within protons and neutrons, is carried by gluons (\(g\)), and it only interacts with quarks and gluons themselves, forming the strong interaction that binds hadrons together.
+Additionally, the Higgs boson, a scalar boson, plays a crucial role in providing mass to all fundamental particles through the Higgs mechanism, which affects both fermions and bosons \cite{thomson_2013}.
+Table \ref{tab:table2} provides a comprehensive overview of the forces experienced by fermions.
+
+\begin{table}[h!]
+  \begin{center}
+    \caption[Force experienced by the fermions]{Force experienced by the fermions \cite{thomson_2013}.}
+    \label{tab:table2}
+    \begin{tabular}{l c c c c}
+    &    &  \textbf{Electromagnetic} & \textbf{Weak} & \textbf{Strong}\\
+      \midrule[1.1pt]
+      \multirow{2}{*}{Leptons} & ${e}$\textsuperscript{-} \hspace{0.3cm}  ${\mu}$\textsuperscript{-} \hspace{0.3cm} ${\tau}$\textsuperscript{-} & \checkmark & \checkmark & \\ % <-- Combining 2 rows with arbitrary with (*) and content 12
+      & $ \nu_{e} $ \hspace{0.3cm}  $\nu_{\mu}$ \hspace{0.3cm} $\nu_{\tau}$  &  & \checkmark\\ % <-- Content of first column omitted.
+      \hline
+      \multirow{2}{*}{Quarks} & $u$ \hspace{0.5cm}  $c$\hspace{0.5cm} $t$ & \checkmark & \checkmark& \checkmark\\
+      & $d$ \hspace{0.5cm}  $s$\hspace{0.5cm} $b$ & \checkmark & \checkmark & \checkmark\\
+
+    \end{tabular}
+  \end{center}
+\end{table}
+
+So far, the Standard Model (SM) of particle physics is the most precise and successful theoretical model for describing experimental data available to date.
+This model provides a detailed explanation of the fundamental interactions between elementary particles.
+However, most of this data comes from experiments conducted at particle colliders, as these devices allow the production and study of particles through high-energy collisions, making it possible to observe phenomena that cannot be studied otherwise.
+Despite its success, the Standard Model still has limitations and cannot explain some aspects of the universe, such as gravity, dark matter, and dark energy.
 
@@
 
+Particle colliders are powerful scientific instruments used to produce, accelerate, and collide beams of particles at relativistic speeds, enabling scientists to explore the fundamental properties of matter and the universe.
+These experiments function as powerful microscopes that allow researchers to study subatomic particles such as electrons, protons, neutrons, neutrinos, and quarks.
+They also provide a means to test predictions made by the Standard Model.
+
+The high speeds required for the collisions are achieved through the use of powerful superconducting magnets, which accelerate particles to the necessary velocities.
+These particles are then collided at specific points along the accelerator, where detectors are located.
+These detectors are capable of measuring individual interactions, known as events, generated by the collisions.
+Some of the particles produced, such as the Higgs boson, cannot be directly observed.
+Instead, they are detected and analyzed using advanced technologies, which measure their interactions with matter \cite{thomson_2013}.\\
+
+In general, a particle detector is typically constructed as a cylindrical or polygonal barrel section, oriented parallel to the incoming colliding beams.
+Two flat end caps seal the cylindrical structure, ensuring nearly complete solid angle coverage all the way down to the beam pipe.
+This detector comprises multiple layers, each designed to detect the different particles generated during collisions \cite{thomson_2013}.\\
+
+Particle colliders are evaluated based on two important measures, which are the available center of mass energy and the rate at which particles collide (luminosity).
+The amount of energy that is available to create new particles and study their properties is particularly significant because it determines the range of particles that can be produced.
+During experiments, particles are accelerated and directed toward each other, and when they collide, they produce new particles and interactions that can be analyzed by scientists.\\
+
+Colliding beam machines are capable of achieving significantly higher energies at the point where the beams intersect and scatter.
+When the particles in the beams have equal energy and opposite momentum (equal mass), the experiment occurs in the center-of-mass (CM) frame.
+This allows for the entire energy delivered by the accelerator to be utilized in generating high-mass particles \cite{undergraduate_accelerators_chapter}.
+In particle physics, the Lorentz invariant quantity $s$ represents the square of the total incoming energy and is defined as:
+
+\begin{equation}
+s = \left ( \sum_{i = 1,2}^{}E_{i} \right )^{2}-\left ( \sum_{i = 1,2}^{}p_{i} \right )^{2}c^{2}
+\end{equation}
+Where  \textbf{$p$} and $E$ are the momenta and the energy of each incoming particle respectively.In the center-of-mass (CM) frame, where the momenta of the particles are equal and opposite, the second term in the equation for the Lorentz invariant quantity ($s$) disappears, leaving only $s = 4E^2$.\\
+
+The second important parameter used to evaluate the performance of colliders is luminosity, which measures the accelerator's ability to produce the necessary number of interactions.
+It is determined by the proportionality factor between the quantum mechanical probability for the interaction (known as the cross section) and the number of events for a specific physics process per second ($R$) \cite{ref_lib_vol3}.\\
+
+The technical meaning of "cross section" in particle physics is quite different from its common usage, while "cross section" typically refers to a slice of an object, in particle physics, it quantifies the probability of a collision and is a property of the interaction of one particle with another, this is expressed in units of square meters.
+When two beams cross in a particle accelerator, a variety of different processes can occur and  the cross section of a given process depends on the type and energy of the colliding particles.
+At the Large Hadron Collider (LHC), certain particles such as  $W^{\pm}$ and $Z^{0}$ bosons have large cross sections , making their observation more frequent, while the production of a Higgs boson has a much lower cross section, making it more difficult to produce \cite{thomson_2013}.\\
+
+To explain this concept more clearly, let's consider a simple scenario where a beam of particles of type $a$ passes through a region of space that contains particles of type $b$.
+The interaction rate between the two types of particles depends on the number of particles per unit volume of type $b$, denoted as $n_{b}$, and the flux of the incident particles, denoted as $\phi_{a}$.
+The rate of interaction per target particle of type $b$ can be expressed as follows:
+
+\begin{equation*}
+  r_{b}=\sigma \phi_{a}
+\end{equation*}
+
+The essence of fundamental physics can be encapsulated in the interaction cross section, denoted by $\sigma$.
+This parameter, which is measured in area units, represents the likelihood that an interaction will occur between an incident particle and a target particle.
+It's helpful to imagine each target particle as having an effective cross-sectional area, and the interaction cross section as representing that area.
+Figure \ref{cross_section}(a) shows an illustration of this concept, where an incident particle of type $a$ moves with velocity $v_{a}$ through a region of area $A$ that contains target particles of type $b$ with velocity $v_{b}$ moving in the opposite direction.
+The value of the interaction cross section is determined by the underlying quantum mechanical probability of interaction and is fundamental to understanding the behavior of particles in collisions.
+\cite{thomson_2013}
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+\includegraphics[scale=.35]{Chapter1/cross_section.png} 
+ \caption[Cross section illustration]{Left hand (a): single incident particle of type $a$ traversing a region containing particles of type $b$.
+Right-hand plot (b): projected view of the region traversed by the incident particle in time $\delta t$.}
+    \label{cross_section}
+  \end{figure}
+\end{center}
+
+To understand the probability of an interaction between particles of types $a$ and $b$, imagine that in a time interval $\delta t$, particle $a$ passes through a region containing $\delta N= nb(v_{a}+v_{b}) A \delta t$ particles of type $b$.
+The probability of interaction can be obtained by dividing the effective total cross-sectional area of the $\delta N$ particles by the area $A$.
+This can be thought of as the probability that the incident particle passes through one of the regions of area $\sigma$ drawn around each of the $\delta N$ target particles, as shown in Figure \ref{cross_section}(b).
+So the cross section for a particular process is defined as the effective target area for that process and has units of area, more formally is expresed as \ref{cross} \cite{thomson_2013}.
+
+%For a beam of particles of type $a$ with number density $n_{a}$ confined to a volume $V$, the total interaction rate can be expressed as $\text{rate}=(n_{a}v)(n_{b}V) \sigma = \phi N_{b} \sigma$, where $v$ is the velocity of the beam particles, $N_{b}$ is the number of target particles per unit volume, and $\phi$ is the flux of incident particles per unit area per unit time.
+The cross section for a particular process is defined as the effective target area for that process and has units of area, more formally is expresed as \cite{thomson_2013}:
+\begin{equation}
+\sigma=\frac{\text{number of interaction per unit time per target particle}}{\text{incident flux}}
+\label{cross}
+\end{equation}
+
 \section{Luminosity }
+
+In experiments conducted in particle physics, the number of useful interactions (or events) is just as important as the energy.
+The ability of a particle accelerator to produce these interactions is measured by a parameter called instantaneous luminosity $\mathcal{L}_{inst}$.
+It is directly proportional to the number of events produced per second and the cross section $\sigma_{p}$ \cite{concept_of_luminosity}.
+
+\begin{equation}
+R=\mathcal{L}_{inst} \cdot \sigma_{p}
+\end{equation}
+
+Where the unit of luminosity is $cm^{-2}s^{-1}$.
+
+To derive a general expression for luminosity in the case of two colliding beams, we consider both beams to serve as the target and the incoming beam simultaneously.
+We will assume that the beams are "bunched", meaning that the particles are grouped into packets or bunches.
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+\includegraphics[scale=.25]{Chapter1/luminosity.png} 
+ \caption[Colliding beam interaction]{Schematic view of a colliding beam interaction\cite{concept_of_luminosity}}
+    \label{luminosity}
+  \end{figure}
+\end{center}
+
+%A schematic picture is shown in Fig.
+\ref{luminosity}.
+Since the two beams are not stationary but are moving through each other, the overlap integral depends on the longitudinal position of the bunches, and therefore on time.
+As the beams move towards and through each other, the two beams have different distribution functions and a different number of particles in the beams \cite{concept_of_luminosity}.
+The overlap integral, which is proportional to the luminosity $\mathcal{L}_{inst}$, can then be written as:
+ In Figure \ref{luminosity}, you can see a diagram that illustrates how two beams intersect with each other.
+Because these beams are not still, but rather in motion, the way they overlap depends on the time and the position of the bunches.
+While the beams move, they also have different distributions and numbers of particles in them \cite{concept_of_luminosity}.
+The luminosity $\mathcal{L}_{inst}$, which is proportional to the overlap integral, can be expressed as:
+
+\begin{equation}
+  \mathcal{L}_{inst}\propto K\cdot \int\int\int \int_{-\infty}^{\infty} \rho_{1}(x,y,s,-s_{0}) \rho_{2}(x,y,s,s_{0})dxdydsds_{0}
+    \label{lumi_1}
+\end{equation}
+
+The functions $\rho_{1}(x,y,s,-s_{0})$ and $\rho_{2}(x,y,s,s_{0})$ represent the beam density distribution at a given time.
+We assume that the two bunches meet at the point $s_{0} = 0$.
+Since the beams are in motion towards each other, we need to take into account a relativistic kinematic factor (Eq.
+\ref{kinematic}) by multiplying this expression.
+
+\begin{equation}
+ K = \sqrt{(\vec{v_{1}}-\vec{v_{2}})^{2}-(\vec{v_{1}}\times \vec{v_{2}})^{2}/c^{2}}
+    \label{kinematic}
+\end{equation}
+
+When the bunches collide head-on and are traveling at nearly the speed of light, the relativistic kinematic factor takes on a value of 2.\\
+Assuming uncorrelated densities in all planes and head-on collisions where the velocities of the two bunches are opposite $(\vec{v_{1}}=-\vec{v_{2}})$, the overlap integral can be factorized as:
+
+\begin{equation}
+  \mathcal{L}_{inst}= 2N_{b} N_{1}N_{2}f \int\int\int\int_{-\infty}^{\infty}  \rho_{1x}(x)\rho_{1y}(y)\rho_{1s}(s-s_{0})\rho_{2x}(x)\rho_{2y}(y)\rho_{2s}(s+s_{0}) dxdydsds_{0}
+    \label{luminosity_2}
+\end{equation}
+
+where $N_{b}$ is the number of bunches in one beam, $N_{1}$ and $N_{2}$ are the particles per bunch and $f$ the revolution frequency.\\
+
+%\begin{eqnarray}
+%\rho_{iz}(z)= \frac{1}{\sqrt{2\pi} \sigma_{z}} exp \biggl(-\frac{z^{2}}{2\sigma_{z}^{2}} \biggr)&z=x,y&i=1,2 
+%\end{eqnarray}
+
+%\begin{eqnarray}
+%\rho_{s}(s\pm s_{0})= \frac{1}{\sqrt{2\pi} \sigma_{s}} exp \biggl(-\frac{(s\pm s_{0})^{2}}{2\sigma_{s}^{2}} \biggr)
+%\end{eqnarray}
+
+Assuming Gaussian profiles in all dimensions and approximately equal bunch lengths $(\sigma_{1s}\approx \sigma_{2s})$, the equation \ref{luminosity_2} can be solved.
+For a general case where $\sigma_{1x}\neq \sigma_{2x} \text{ and } \sigma_{1y}\neq \sigma_{2y}$
+
+\begin{equation}
+  \mathcal{L}_{inst}= \frac{N_{1} N_{2} N_{b}f }{2\pi \sqrt{\sigma_{1x}^{2}+\sigma_{2x}^{2}}\sqrt{\sigma_{2y}^{2}+\sigma_{2y}^{2}}}
+  \label{lumi_general}
+\end{equation}
+
+For a specific case, asuming equal beams, $\sigma_{1x}= \sigma_{2x} \text{ and } \sigma_{1y}= \sigma_{2y}$:
+
+\begin{equation}
+  \mathcal{L}_{inst}= \frac{N_{1} N_{2} N_{b}f }{4\pi \sigma_{x} \sigma_{y}}
+  \label{lumi_theor}
+\end{equation}
+
+This expression is widely recognized as the formula for the luminosity of two Gaussian beams that collide head-on.
+It reveals how the luminosity is related to the number of particles in each bunch and the size of the beams \cite{concept_of_luminosity}.\\
+
+In practice,the integral in  \ref{luminosity_2} cannot be solved analytically because   the properties of the colliding beams are not know precisely, so a experimental technique is implemented with a dedicated machine setup to estimate the integrals, yielding a similar expression as \ref{lumi_theor}.
+
+To determine the overall number of events, we rely on integrated luminosity, which is a measurement of the total amount of collected data.
+This value is crucial for evaluating the effectiveness of an accelerator and it can be expressed as: \cite{concept_of_luminosity}:
+
+\begin{equation}
+  \mathcal{L}_{int}=\int_{0}^{T} \mathcal {L}_{\text{inst}}(t') dt'
+\end{equation}
+
+Where the value of $\mathcal{L}_{inst}$ is evaluated over time $T$ (excluding possible dead time) because its intensity decreases as the number of protons reduces during the collisions of the fill.
+So $\mathcal{L}_{int}$ is directly related to the number of observed events as:
+\begin{equation}
+  \mathcal{L}_{int} \ndot \sigma_{p}= \text{number of events of interest}
+\end{equation}
+
+The integrated luminosity has units of $cm^{-2}$ and is often expressed in inverse barn ($1 barn= 10^{-24}cm^{2}$). \\
+
+Precisely understanding luminosity is really important for physics analyses like finding new particles, measuring known particle properties, or detecting rare processes.
+The accuracy of our physics measurements is mainly affected by uncertainties in luminosity.
+If we can increase the precision of luminosity measurements, then physicists will have a better understanding of their observations and be able to explore parts of physics that we don't currently know about \cite{luminosity_importance}.
+
+An example of this can be seen in Fig.
+\ref{lumi_incertainty}, which illustrates the production of $W$ and $Z$ bosons in the large hadron collider.
+In this figure, the inner error bars represent the experimental uncertainties, while the outer error bars encompass the uncertainties in the theoretical predictions.
+Additionally, the shaded box indicates the uncertainties in the luminosity measurement, which is bigger that statistical and other systematics uncertainties \cite{lumi_uncertainties}.
+
+\begin{center}
+  \begin{figure}[h]
+    \centering
+\includegraphics[scale=.28]{Chapter1/lumi_uncertainty.png} 
+ \caption[Luminosity uncertainty in a process]{Production of $W^+$, $W^-$, $W$ and $Z$ bosons and their theoretical predictions.
+The shaded box indicates the uncertainties in the luminosity measurement, showing that is bigger than the experimental (blue bars) and heoretical (green bars) uncertainties.
+The measurements and theoretical predictions values are on the right}
+    \label{lumi_incertainty}
+  \end{figure}
+\end{center}
 
@@
 
-\section{Expected Luminosity precision for LHC Run 3}
+The Large Hadron Collider (LHC) is the world's biggest and most potent particle accelerator.
+It became operational on 10th September 2008 and is the most recent addition to CERN's accelerator complex.
+The LHC consists of a 27-kilometer ring that contains superconducting magnets, and various structures are used to accelerate particles as they move along the ring.
+Inside the accelerator, two particle beams travel at almost the speed of light until they collide.
+The beams move in opposite directions in separate beam pipes, which are kept at an ultra-high vacuum.\\
+
+Superconducting electromagnets generate a powerful magnetic field that guides the particle beams around the accelerator ring.
+These magnets are made up of coils of a unique electric cable that functions in a superconducting state.
+In this state, the cable can conduct electricity with zero resistance or energy loss.
+The accelerator uses a variety of magnets, including 1232 dipole magnets that are 15 metres in length and bend the beams, and 392 quadrupole magnets that are 5-7 metres long and focus the beams.
+Just before the collision, a different type of magnet is employed to "squeeze" the particles together, increasing the likelihood of collisions.
+To keep these magnets in the superconducting state, they must be cooled to a temperature as low as -271.3°C \cite{LHC}.\\
+
+The process of generating proton beams for the LHC is a complex and multi-stage procedure.
+Initially, hydrogen is ionized to create protons, which are then accelerated in bunches up to 50 MeV in the Linear Accelerator 2 (LINAC2).
+The proton bunches are then routed through three circular accelerators: the Booster, the Proton Synchrotron (PS), and the Super Proton Synchrotron (SPS).
+These accelerators gradually increase the energy levels of the proton bunches to 1.4 GeV, 26 GeV, and 450 GeV, respectively \cite{lhc_complex}.
+Once these pre-acceleration stages are completed, the proton bunches are injected into the LHC ring where they are further accelerated to achieve energies of up to 7 TeV per bunch while circulating in opposite directions.
+This entire process constitutes a single LHC fill and typically involves $10^{14}$ protons that are grouped into bunches to form the proton beam.
+The complete CERN accelerator complex is illustrated in Figure \ref{lhc_com}.
+
+\begin{center}
+  \begin{figure}[h]
+    \centering
+    \includegraphics[scale=.45]{Chapter1/lhc_complex_fig.png}
+    \caption[LHC Complex]{Diagram of the LCH complex \cite{lhc_complex}.}
+    \label{lhc_com}
+  \end{figure}
+\end{center}
+
+The CERN Control Centre serves as the central hub responsible for managing all controls, services, and technical infrastructure of the LHC.
+It directs the proton beams to collide at four distinct locations along the accelerator ring, corresponding to the positions of four particle detectors: CMS and ATLAS, which are general-purpose detectors designed to explore a broad range of Standard Model (SM) and Beyond SM (BSM) physics, while ALICE and LHCb are specialized detectors that focus on studying specific phenomena.
+
+\section{Results in Luminosity precision for LHC Run 2}
+
+Since its inception in 2010 the LHC has undergone three runs and two lengthy shutdowns for maintenance and upgrades. 
+Run1 began in 2010 with proton-proton collisions at a center-of-mass energy of $\sqrt{s}=\text{7 TeV}$ and concluded in 2012 at  $\sqrt{s}=\text{8 TeV}$.
+Run 2, which took place at $\sqrt{s}=\text{13 TeV}$, was divided into two stages; the first  occurred from 2015 to 2016.\\
+
+The second stage (2017–2018) had preliminary results published in the Public Analysis Summaries, CMS-PAS-LUM-17-001 \cite{pas_17} for 2018 and CMS-PAS-LUM-18-002 \cite{pas_18} for 2017.
+However, the desired uncertainty values were not achieved.
+Efforts are currently underway to further improve the precision of these measurements and present them in a final publication.
+This project is primarily focused on contributing to this publication by analyzing the PCC luminometer and refining the uncertainty, aiming to achieve values of approximately 1\%.\\
+
+The integrated luminosity for Run 2, along with its corresponding uncertainty values, is presented in Table \ref{lumi_values}.
+These luminosity values account for the period from the start of stable beams until the beam is dumped by the LHC.
+Additionally, Figure \ref{lumi_per_year_int} provides a visualization of the delivered luminosity over time for each year, as measured by CMS.
+
+% for both years.
+% ref. TDR Bril para los 390
+%separar por lumpas , poner  referencia, poner periodo en vez de Run
+%-  en incertidumbre  no conocida, dejar solamente 2022
+\begin{table}[h!]
+    \begin{center}
+    \caption[Integrated luminosity values delivered by Run 2]{Integrated luminosity values delivered by Run 2 (precision values ​​for the years 2017 and 2018 show preliminary results)}
+	\label{lumi_values}
+\begin{tabular}{cccc}
+\textbf{Period} & \textbf{Energy $\sqrt{s}$} & \begin{tabular}[c]{@{}c@{}}\textbf{Integrated}\\\textbf{Luminosity}\end{tabular} & \textbf{Precision}    \\ 
+\toprule
+Run 1(2010-2012) \cite{PCC_PAS_12_001} & 8 TeV                   & $30 fb^{-1}$                         & 2.2\%                 \\
+Run 2(2015-2016) \cite{lumi_precise_2015_2016} & 13 TeV   & $45.9 fb^{-1}$                     & 1.6\%-1.2\%                \\
+Run 2(2017) \cite{pas_17} & 13 TeV                                                   & $49.8 fb^{-1}$                     & 2.3\%                 \\
+Run 2(2018) \cite{pas_18} & 13 TeV                                                  & $67.9 fb^{-1}$                      & 2.5\%                 \\
+\end{tabular}
+    \end{center}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+  \begin{center}
+  \begin{figure}[ht]
+    \centering
+    \includegraphics[scale=.55]{Chapter1/int_lumi_cumulative_pp_2_run2.pdf}
+    \caption[Delivered integrated luminosity per year]{Delivered luminosity versus time for Run-1 (2010-2012) and Run-2 (2015-2018) and Run-3 that is still ongoing .
+Cumulative luminosity versus day delivered to CMS during stable beams for pp collisions at nominal center-of-mass energy.
+\cite{wikicern}.}
+    \label{lumi_per_year_int}
+  \end{figure}
+    \end{center}
+
+\section{Motivation for precise luminosity measurement}
+
+%% tabla con ano , luminosidad y presicion

### 2025-03-21 monograph_Luis/Chapter3/chapter3.tex
update

@@
 
-\section{2017 and 2018 CMS Data collected}
+Accurate measurement of the luminosity delivered to the CMS experiment by the LHC is essential for various reasons.
+Online, the luminosity measurement provides feedback on the LHC and CMS performance and operations, including measuring trigger rates.
+In offline analysis, the luminosity measurement is a critical component for measuring the cross-section of observed processes or setting upper limits in searches for processes beyond the standard model.
 
-\section{Module selection}
+As we see, to measure luminosity, a total of seven luminometers are used at CMS, and each of them reads out a specific quantity observed in the detector, such as hits, tracks, or clusters.
+The rate R measured by the luminometer is proportional to the instantaneous luminosity, $\mathcal{L}_{inst}$, with the constant of proportionality given by the visible cross-section $\sigma_{vis}$ \cite{pas_18}.
+
+\begin{equation}
+R(t)=\mathcal{L}_{inst}\sigma_{vis}
+\label{lumi_exp_gen}
+\end{equation}
+
+The determination of $\sigma_{vis}$ is performed through van der Meer (vdM) scans using a specialized LHC machine setup.
+This chapter provides a description of this procedure, specifically applied with the PCC method.
+
+\section{Pixel Cluster Counting method}
+\label{Pixel Cluster Counting method}
+
+The PCC method is an offline technique that provides a luminosity measurement using the rate of pixel clusters.
+Due to the large area of the pixel detector and the relatively low occupancy of its sensors, the probability of a single pixel being struck by two charged particles from the same bunch crossing is extremely low.
+This high granularity and low occupancy result in an excellent linear response to pile-up (\(\mu\), the number of interactions per bunch crossing) \cite{PCC_PAS_12_001}.
+On average, the detector occupancy (# hit pixels/# total pixels) is less than 0.1\% \cite{lumi_precise_2015_2016}.
+Although the statistical precision per Lumisection (23-second period) is lower than that of online luminometers due to CMS trigger bandwidth limitations, PCC still provides a linear measurement with good precision over time.
+When integrated over longer periods, it delivers a stable and highly precise luminosity measurement.
+
+Figure \ref{pileup} shows a simulation with pp collision zero-bias events with the pixel cluster counting rate as a function of pileup in the pileup range observed in Run 2 from 0 to about 50 $\mu$.
+Where the mean number of pixel clusters is of the order of  111 per event.
+The red curve is a first-order polynomial fit with slope, the results indicate a high level of agreement, as evidenced by the estimated goodness-of-fit $\chi^{2}$ per degree of freedom (dof) of approximately 0.5, showing that the PCC rate is highly linear in this range under simulated conditions \cite{ Phase2_Upgrade,lumi_precise_2015_2016}.
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[scale=.35]{Chapter3/pileup_lineality.png} 
+    \caption[PCC linearity with pile-up]{ Linearity of pixel cluster counting over the pileup range observed in Run 2 (from 0 to about 50) from simulation.
+The red line is a linear fit to the points \cite{Phase2_Upgrade} }
+    \label{pileup}
+  \end{figure}
+\end{center}
+
+For physics conditions, two data streams are recorded via the CMS DAQ: "zero-bias" and "random." The zero-bias stream consists of triggered data for colliding bunches at a bandwidth of approximately 2 kHz, while the random stream collects triggered data from all bunch crossings at a bandwidth of 500 Hz, primarily used for background estimation.
+The luminosity measurement is performed using the zero-bias data, whereas the random trigger helps evaluate background contributions.
+
+Under vdM conditions, a special trigger mode is employed to achieve higher data rates for PCC.
+This mode focuses on a selected set of five colliding bunch crossings, as detailed for each year in the next chapter, ensuring the necessary statistical precision.
+
+To derive the luminosity measurement from the PCC method, the mean number of pixel clusters per event is computed by averaging over several zero-bias events. This value is given by:
+
+\begin{equation}
+\left < N_{\text{cluster}} \right > \equiv \left < N_{\text{cluster}/\text{interaction}} \right > \mu
+\end{equation}
+
+Under minimum bias conditions, $\mu$ can be expressed as:
+
+\begin{equation}
+\mu = \frac{\sigma_{\text{minBias}}}{f} \cdot \mathcal{L}_{inst}
+\end{equation}
+
+where $f$ is the LHC revolution frequency and $\mathcal{L}_{inst}$ is the single bunch instantaneous luminosity (SBIL).
+The minimum bias cross section $\sigma_{\text{minBias}}$ here is related to the PCC visible cross section by the mean number of clusters per interaction:
+
+\begin{equation}
+\sigma_{vis}= \left < N_{\text{cluster}/\text{interaction}} \right >\cdot \sigma_{\text{minBias}}
+\end{equation}
+
+Combining everything, the PCC luminosity measurement is obtained as:
+
+\begin{equation}
+\mathcal{L}_{inst}=\frac{\left < N_{\text{cluster}} \right> f}{\sigma_{vis}}
+\end{equation}
+
+In the PCC measurement, the innermost layer (Layer 0) of the pixel detector is excluded due to significant dynamic inefficiency effects.
+At high instantaneous luminosities, the hit efficiency decreases because the readout chip cannot process all hits in time.
+
+For PCC rate measurements, only the pixel detector modules that remain stable throughout the entire data-taking period (year) are used.
+Modules known to be defective or significantly affected by the limited size of the readout buffer are excluded from the analysis.
+
+The final number of excluded modules, referred to as "veto modules," is detailed for each year in the next chapter.
+
+%This method is capable of providing a precise luminosity measurement over longer time periods, but it cannot do so for a single luminosity section (23 seconds) as is possible with online luminometers.
+The reason for this limitation is the limited CMS trigger bandwidth available for collecting data \cite{pas_18}.
+A detailed discussion on this topic can be found in the next chapter.\\
+
+%PCC si calcula lumi por cada lumi section.
+Esto no tiene que ver con online vs offline.
+PCC es un offline luminometro, quiere decir que los datos llegan tarde.
+Con PCC solo podemos calcular lumi cada lumi section, debido a la baja estadistica (por la lectura de los datos de zero bias).
+otros luminometros tienen precision con NB4 (HF, PLT, BCM1F).
 
 \section{Luminosity calibration: van der Meer method}
+\label{vdM method}
+
+As discussed in Chapter 1, the instantaneous luminosity for a single colliding bunch is described by Eq.
+(\ref{luminosity_2}).
+In practice, while the measurement of the beam currents $N_{1,2}$ is well determined, the individual proton density functions cannot be directly measured.
+To address this, the vdM method involves a specific machine setup that allows for the determination of the two beam overlap integrals.
+This is achieved by varying the separation between the beams and measuring the resulting rates, which can be used to obtain density profiles that are close to normal distributions.
+The beam overlap can be expressed in terms of the measured rates as follows:
+
+\begin{equation}
+\int \rho_{x1}(x) \rho_{x2}(x) dx = \frac{R_{x}(0)}{\int R_{x}(\Delta) d\Delta}
+\end{equation}
+
+where $R_{x}(\Delta)$ is the rate measured when the two beams are separated in $x$ by a distance $\Delta$; a similar equation can be written in $y$.
+Then the beam overlap width $\Sigma_{x}$ (and similarly $\Sigma_{y}$) is defined as \cite{pas_18}:
+
+\begin{equation}
+\Sigma_{x}= \frac{1}{\sqrt{2\pi}} \frac{\int R_{x}(\Delta)d\Delta}{R_{x}(0)}
+\label{CapSigma}
+\end{equation}
+
+This process leads to the final expression for luminosity for a single colliding bunch:
+
+\begin{equation}
+\mathcal{L}_{inst}=\frac{N_{1} N_{2}f}{2 \pi \Sigma_{x}\Sigma_{y}}
+\end{equation}
+
+where $N_{1,2}$ are the particles per bunch (bunch current) and  $f= 11246$ Hz is the bunch orbit frequency around the LHC ring determined by the energy of the protons.\\
+
+Therefore, the equation ~\ref{lumi_exp_gen} used to measure the visible cross sections $\sigma_{vis}$ takes the following form:
+
+\begin{equation}
+  \sigma_{vis}=2\pi \frac{ R(0, 0)}{N_{1}N_{2} f} \Sigma_{x} \Sigma_{y}
+  \label{sigmavis_eq}
+\end{equation}
+
+Experimentally, the quantities $\Sigma_{x}$ and $\Sigma_{y}$, as defined in Eq. (\ref{CapSigma}), are determined by conducting two separate scans in the $x$ and $y$ directions, respectively. 
+These scans are performed by varying the separation between the beams in each direction  at a fixed number of separation steps.The separation steps are determined through curve fitting of the scan data based on the luminometer rate measurements obtained during the vdM scans.\\
+
+The measured rate, denoted by $R(0,0)$, is determined as the average value among the rates obtained in the $x$-scan $R_x(0)$, and the rates obtained in the $y$-scan $R_y(0)$.
+Although the beam widths are identical for all luminometers, the peaks of the scan curves are specific for each luminometer.\\
+
+Figure \ref{vdm_sketch} depicts a schematic of the beam positions during vdM scans in the $x$ and $y$ planes, along with the detector rate as a function of beam separation  \cite{pas_18}.
+\newpage
+\begin{center}
+  \begin{figure}[ht]
+    \centering
+    \includegraphics[scale=.50]{Chapter3/vdm_sketch.png}
+    \caption[Sketch of a vdM scan in $x$ and $y$ directions and example of fitting resulting rates]{ The sketch of a vdM scan in $x$ and $y$ planes.
+The indent sketch is an example of the fit of the resulting rates \cite{vdM_sketch}.}
+    \label{vdm_sketch}
+  \end{figure}
+\end{center}
+
+\section{2017 and 2018 data Collected}
+\label{Run 2 data Collected}
+
+In June 2017, data collection for the second phase of Run 2 of the Large Hadron Collider (LHC) began, covering the years 2017 and 2018.
+As a result, a total recorded luminosity of \(49.81 \, \text{fb}^{-1}\) for 2017 and \(67.86 \, \text{fb}^{-1}\) for 2018 was achieved.
+This data was collected during proton-proton collisions at a center-of-mass energy of \(\sqrt{s} = 13\) TeV.
+
+The data-taking period started with the establishment of stable beams and ended either when the beam was intentionally stopped or when stable beams were temporarily interrupted for beam studies.
+
+Each year, a dedicated setup is allocated for the van der Meer (vdM) program, which will be discussed in a later chapter.
+This program is essential for the calibration of luminosity and the determination of its associated uncertainty, which plays a crucial role in the analyses where luminosity is a key factor.
+
+The luminosity delivered by the LHC to CMS (shown in blue) and the luminosity recorded by CMS (depicted in orange) during 2017 are illustrated in Figure~\ref{Lumi_2017}, while Figure~\ref{Lumi_2018} presents the corresponding data for 2018~\citep{wikicern}.
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[width=.45\textwidth]{Chapter3/Luminosity/int_lumi_per_day_cumulative_pp_2017_Normtag.pdf}
+    \includegraphics[width=.45\textwidth]{Chapter3/Luminosity/int_lumi_per_day_pp_2017_Normtag.pdf}
+    \caption[Cumulative day-by-day integrated luminosity in 2017]{(left) Cumulative day by day integrated luminosity.
+(rigth) Day by day integrated luminosity, 2017 as the first plot, but not cumulative.}
+    \label{Lumi_2017}
+  \end{figure}
+\end{center}
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[width=.45\textwidth]{Chapter3/Luminosity/int_lumi_per_day_cumulative_pp_2018_Normtag.pdf}
+    \includegraphics[width=.45\textwidth]{Chapter3/Luminosity/int_lumi_per_day_pp_2018_Normtag.pdf}
+    \caption[Cumulative day-by-day integrated luminosity in 2022]{(left) Cumulative day by day integrated luminosity.
+(rigth) Day by day integrated luminosity, 2018 as the first plot, but not cumulative.}
+    \label{Lumi_2018}
+  \end{figure}
+\end{center}
+
+\section{vdM program and Scan types}
+\label{vdM program and Scan types}
+
+Each year, the vdM scan program for the CMS experiment is conducted during specific LHC fills using a dedicated setup.
+The LHC filling schemes are designed with a specific number of bunch pairs at the CMS interaction point (IP5), for the especific case of 2017 an 2018 was at a proton-proton collision energy of \(\sqrt{s} = 13\) TeV.
+These scans play a crucial role in the precise determination of the luminosity by measuring the transverse beam profiles and overlap integral.
+
+To minimize long-range beam-beam effects and detector afterglow, the bunches are arranged in a way that optimizes the measurement conditions.
+During these special fills, the beams are systematically displaced in the transverse plane, allowing for a detailed study of beam dynamics and interaction rates.
+Various types of scan pairs with different characteristics were conducted to refine the accuracy of the luminosity determination.
+
+Each scan pair consisted of two scans in the transverse \(x\) and \(y\) planes.
+These included standard vdM scans, emittance scans, beam imaging scans, offset scans, and length scale calibration scans, each serving a specific purpose in the measurement process.
+A detailed description of each scan is provided below.
+
+\noindent \textbf{Standard vdM}: used specifically to compute $\sigma_{vis}$, in this scan the two beams are separated by $6\sigma_{b} \thickapprox 578\mu m$, where $\sigma_{b}$ represents the transverse bunch size.
+and scanned across each other in a se quence of 25 steps with 30 seconds per step with a step size of $0.5\sigma_{b} \thickapprox 48 \mu m$ in either the horizontal (x) or vertical (y) direction.\\
+
+\noindent \textbf{Emittance}: same procedure as the standard vdM scans except the maximum separation (2.5 − 4σb), the number of steps (7 or 9) and the time per step (10 seconds) are smaller, so that the scan takes a shorter time.
+These type of scans are also performed in physics conditions as discussed in Section.\\
+
+\noindent \textbf{Beam imaging}: in these scans, one beam (beam 1 and beam 2, respectively) is kept fixed at its nominal head-on position, while the other beam is separated and scanned in 19 steps, each step lasts 46 seconds and covers a range from $-4.5\sigma_{b}$ to $+4.5\sigma_{b} \thickapprox 433 \mu m$.
+These scans were developed for studies on beam shapes, estimating the uncertainty caused by the correction called $x$-$y$ non-factorization described in the next chapter.
+BI scans are also analyzed as traditional vdM scans and used to compute of $\sigma_{vis}$.\\
+
+\noindent \textbf{Constant-Separation Length Scale}: during this scan the two beams are separated by $\sqrt{2} \sigma_{b} \thickapprox 106 \mu m$ (approximately equal to $1 \Sigma_{b}$) and moved together in steps of $1\sigma_{b}$ forward and backward in five steps each, for a total of 10 steps with 70 seconds per step.\\
+
+\noindent \textbf{Variable-Separation length scale}: one beam (starting with beam 1) is moved to $-2.5\sigma_{b}$ and then a three-point scan is performed with the other beam (starting with beam 2) at arelative position of $+-1.25\sigma_{b}$, 0, and $+1.25\sigma_{b}$.
+The position of the first beam is then stepped in five steps to $+2.5\sigma_{b}$, repeating the three-point scan (“miniscan”) at each step.
+This procedure is repeated four times, with two directions for each of the two beams.
+Each scan point has a duration of about 46 s.
+
+The two types of Length scale are pecial scan designed to apply a correction to the results of  $\sigma_{vis}$ obtained from the vdM scan program, this correction will be described further in this section.\\
+
+\noindent \textbf{Offset}: same procedure as the standard vdM scans except that the beams are separated by  range from $-3\sigma_{b}$ to $+3\sigma_{b}$ in the non-scanning direction.\\
+
+\noindent \textbf{Super Separation}: this type of scan is performed for background estimation.
+In this scan, the two beams are separated by a distance of \(6\sigma_{b}\) for 5 minutes.
+At this distance, the beam overlap is minimal, and the contribution from collisions is negligible.
+There can be more than one Super Separation scan per scan program, this is useful to understanding the behavior of the background throughout the year and for subtracting it accordingly.
+
+The data collected from these scans provide the essential input for luminosity calibration, which is critical for cross-section measurements and precision physics analyses at the LHC.
+
+\subsection{2017 vdM scan program}
+\label{2017 vdM scan program}
+
+The 2017 vdM scan program was performed during LHC fill 6016 on 28 July 2017, at a center-of-mass energy of 13 TeV.
+The LHC filling scheme included 32 colliding bunch pairs at the CMS interaction point (IP5).
+In the special case of PCC, to ensure a dataset with a high event count at large beam separations, CMS gated the zero-bias triggers on 5 bunch pairs (BCIDs 41, 281, 872, 1783, and 2063) and recorded events at a total rate of 18 kHz.
+
+The bunch intensities were approximately \(9 \times 10^{10}\) protons per filled bunch, resulting in a total beam intensity of approximately \(4.5 \times 10^{12}\) protons per beam.
+The total beam intensities were measured with the DC Current Transformers (DCCT) ~\citep{LHC_DCCT_calibration}.
+The beam orbit was monitored using two systems: the DOROS beam position monitors (BPMs) ~\citep{BPM__electronics}, located near IP5, and the arc BPMs, located in the LHC arcs adjacent to CMS.
+
+The vdM scan program consisted of a total of eight orthogonal (x-y) scan pairs.
+It started with a short emittance scan, em1.
+Four scans were standard vdM scans: vdM1 (2), vdM3 (6), and vdM4 (11).
+These scans were performed first in the x direction and then in the y direction.
+The intermediate scan, vdM2 (3), was performed first in the y direction and then in the x direction.
+This was done to check reproducibility.
+
+Two scan pairs of beam imaging scans were performed, with beam 1 and beam 2 scanning.
+Pairs Im1 and Im2 corresponded to scans 4 and 5, respectively.
+Scan pair 7 was an offset scan (off) performed just after vdM3, but it is not used in this analysis.
+
+A length scale calibration (LSC) program was performed at the end of the vdM program using two different LS methods.
+The first method was the constant-separation scan (cLS), performed as scan 8 in this program.
+This type of scan had been previously used in the 2015–2016 publication  ~\citep{lumi_precise_2015_2016} for the CMS length scale calibration.
+
+The second method consisted of variable-separation scans, vLS1 and vLS2, which were scans 9 and 10, respectively, in the LS program.
+This method was used for the first time in 2017, following the scan protocol originally developed by ATLAS.
+
+The top of Figure~\ref{BeamPosition_2017} shows the beam positions for the two beams in the x and y directions as measured by the DOROS BPMs during the 2017 scan program, showing the four regular scan pairs, the two beam imaging scan pairs, the offset scan pair, and the two length scale scan programs, with the abbreviations used for the scans introduced.
+
+%\begin{center}
+  \begin{figure}[h]
+    \hspace{-.4cm}
+    %\centering
+    \includegraphics[scale=.17]{Chapter3/BeamPosition/doros_vs_time_6016.pdf}
+    \caption[Doros]{ Vertical (V) and horizontal (H) beam positions as a function of time measured by the DOROS beam position monitors during LHC fill 6016.
+The orbit is averaged over the bunches and monitored throughout the scan program with 1 second time granularity.
+The individual scans are delimited by the vertical lines.
+Each scan pair consists of two scans orthogonal to each other and labelled with the abbreviation of the specific scan type}
+    \label{BeamPosition_2017}
+  \end{figure}
+%\end{center}
+
+\subsection{2018 vdM scan program}
+\label{2018 vdM scan program}
+
+The 2018 vdM scan program was conducted during LHC fill 6868 from June 30 to July 1, 2018, at a center-of-mass energy of 13 TeV.
+The LHC filling scheme included 124 colliding bunch pairs at the CMS interaction point (IP5).
+For the special case of PCC, to ensure a dataset with a high event count at large beam separations, CMS gated the zero-bias triggers on 5 bunch pairs (BCIDs 265, 865, 1780, 2192, and 3380) and recorded events at a total rate of 27 kHz.
+
+The bunch intensities were approximately \(7-9 \times 10^{10}\) protons per filled bunch, resulting in a total beam intensity of approximately \(4.5 \times 10^{13}\) protons per beam.
+The total beam intensities were measured with the DC Current Transformers (DCCT) ~\citep{LHC_DCCT_calibration}.
+The beam orbit was monitored using two systems: the DOROS beam position monitors (BPMs) ~\citep{BPM__electronics}, located near IP5, and the arc BPMs, located in the LHC arcs adjacent to CMS.
+
+The vdM scan program was conducted in two parts due to an alarm and a power cut.
+The first part consisted of a total of five x-y scan pairs.First, two short emittance scans, em1 (1) and em2 (2), were conducted, respectively.
+Then, a standard vdM scan pair, vdM1 (3), was performed, followed by an offset scan, off1 (4).
+Finally, a pair of beam imaging scans, BI1 (5) and BI2 (6), were onducted, but only the first was completed before the alarm interrupted the program.
+
+The second part of the program was conducted approximately 7.5 hours later and consisted of 12 scan pairs.
+Scan pair em3 (6) was a short emittance scan, followed by beam imaging scan pairs Im3 (7) and Im4 (8), then an offset scan pair, off2 (9), and finally two standard vdM scan pairs, vdM2 (10) and vdM3 (11).
+The latter two allowed us to test the reproducibility of the measurement.
+
+A length scale calibration program was performed after vdM3 using constant-separation and variable-separation scan pairs: cLS (12), vLS1 (13), and vLS2 (14).
+Finally, a standard vdM scan pair, vdM4 (15), and two short emittance scan pairs, em4 (16) and em5 (17), concluded the program.
+
+In each scan pair, the scan was performed first in the x direction and then in the y direction, with the exception of the variable vLS calibration scan pairs, which were performed in the opposite order.
+
+Additionally, two Super Separation periods were conducted.
+The first, SS1, took place right after vdM3 was completed, and the second, SS2, followed vdM4.
+These periods are not included in the final count of scan pairs since they only involve separating the beams in a single direction.
+They are used for the final estimation of background noise, which will be subtracted in the final analysis.
+The details of these periods will be discussed in the following chapter.
+
+The bottom of Figure~\ref{BeamPosition_2018} shows the beam positions for the two beams in the x and y directions as measured by the DOROS BPMs during the 2018 scan program, showing the 17 scan pairs.4 regular scan pairs, the 3 beam imaging scan pairs, the 2 offset scan pair, and the 3 length scales, the emitance scan a the 2 Superseparation periods with the corrsponding abbreviations used.
+
+%[15] M. Gasior, J. Olexa, and R. Steinhagen, “BPM electronics based on compensated diode detectors — results from development systems”, Conf. Proc. C1204151 (2012) 44.
+%[7] C. Barschel et al., “Results of the LHC DCCT calibration studies”, Technical Report 2349 CERN-ATS-Note-2012-026 PERF, 2012.
+
+%\begin{center}
+  \begin{figure}[h]
+  \hspace{-0.4cm}
+    %\centering
+    \includegraphics[scale=.17]{Chapter3/BeamPosition/doros_vs_time_6868.pdf}
+    \caption[Doros]{Vertical (V) and horizontal (H) beam positions as a function of time measured by the DOROS beam position monitors during LHC fill 6868.
+The orbit is averaged over the bunches and monitored throughout the scan program with 1 second time granularity.
+The individual scans are delimited by the vertical lines.
+Each scan pair consists of two scans orthogonal to each other and labelled with the abbreviation of the specific scan type.}
+    \label{BeamPosition_2018}
+  \end{figure}
+%\end{center}

### 2025-03-21 monograph_Luis/Chapter4/chapter4.tex
update

@@
 
-\section{2017 and 2018 vdM scan program}
-\label{2017 and 2018 vdM scan program}
+The analysis of the luminosity calibration obtained with the PCC detector for the publication "Precision luminosity measurement at CMS in proton-proton collisions at 13 TeV in 2017 and 2018" was successfully conducted, yielding final results that will be included in the official publication of this study.
+
+This chapter presents a detailed explanation of the entire analysis and processing workflow, from raw data acquisition, background analysis, and the selection of valid modules (veto modules), to the final calibration, which consists of the determination of the detector's visible cross-section \sigma_{vis}.
+
+Finally, cross-checks were performed with other luminometers, along with final comparisons against the integrated luminosity of the entire year, to evaluate and determine the final uncertainties.
 
@@
 
+\section{Module selection}
+
+To ensure accurate luminosity measurement, a module selection process is performed to exclude modules exhibiting instability or non-linearity across different data-taking periods, as these indicate non-physical shifts in cluster counts.
+Only stable pixel detector modules are used for PCC rate measurements, excluding defective modules or those significantly affected by readout buffer limitations [25].
+
+The pixel system consists of 1856 modules, all initially considered for luminosity measurement.
+However, instabilities and non-linear effects can compromise accuracy.
+To identify "good" and "stable" modules, a selection is made by eliminating underperforming modules based on their relative contribution to the cross section.
+Modules with consistent contributions across standard physics runs are retained, while those showing significant deviations from the average are excluded.
+
+The pixel detector undergoes changes over time due to factors such as detector noise, aging, and radiation damage, leading to variations in the number of well-performing modules.
+These variations are assessed at a 23-second granularity, matching the luminosity database.
+
+The procesos para module selection follows these steps:
+
+\begin{itemize}
+\item Low statistics lumisections are removed from the analisys for each period.
+\item The innermost layer (layer 0) of the pixel detector is excluded from the analysis due to significant dynamic inefficiency effects \cite{pas_18}.
+At higher $\mathcal{L}_{inst}$, the hit efficiency in this layer decreases because the readout chip cannot process all of the hits.
+\item A loose selection of 7\% based on RMS/mean from the module weight distribution (changes in the module PCC ratio relative to the total PCC) is applied.
+Modules with significantly large RMS/mean are removed with this selection as shown in \ref{goodmodule}.
+\item The module stability is re-evaluated based on RMS/mean values using an iterative method where the second iteration is made with a loose selection of 2\%.
+\end{itemize}
+
+%\item Using a stability profile for each module a Mean weight and the corresponding RMS  is calculated.
+Fig.~\ref{fig:goodbadmodules} shows examples of stability profiles for stable and unstable modules.
+Fig.~\ref{fig:outliermodules} shows the RMS/Mean values for all modules in this step.
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[scale=.17]{Chapter4/good_module.png}\includegraphics[scale=.15]{Chapter4/RMSmean.png}
+    \caption[Profile of good and bad modules stability]{ left: stability profile for good and bad modules where weight is plotted as a function of lumi section.
+Right: RMS/mean values of module weight for all pixel modules  where each pixel module is represented by a module number index (same happen for the 4\% iteration).}
+    \label{goodmodule}
+  \end{figure}
+\end{center}
+
+To ensure accuracy, pixel module veto lists were generated for different time periods using the procedure described above.
+To further improve stability, a common module veto list was created by merging the lists from all periods.
+Modules consistently identified as "bad" across multiple periods were excluded.
+The PCC data with zero bias was then reprocessed using this common veto list for the final vdM analysis.
+
+%[25] CMS Collaboration, “Description and performance of track and primary-vertex reconstruction with the CMS tracker”, JINST 9 (2014) P10009, doi:10.1088/1748-0221/9/10/P10009, arXiv:1405.6569
+
+\subsection{2017 Pixel Detector module selection}
+\label{sec:pcc_perf_moduleselection_2017}
+
+%% Sam's presentation of the module veto: https://indico.cern.ch/event/704864/contributions/2891738/attachments/1599873/2536088/PCCUpdate20180213.pdf
+
+The 2017 PCC data is divided into five periods (datasets) throughout the year: B, C, D, E, and F.
+The selection of stable ("good") detector modules is based on analyzing each module's cluster count relative to the total (module weight), as described earlier in this section.
+The module weight is computed for each data period and compared across periods to assess stability.
+
+During the final part of the 2017 run, power supply failures led to a significant number of non-operational modules, which were excluded from the final measurement.
+In particular, the Pixel detector experienced issues with DC-DC power converters during period F, resulting in a large number of unstable modules.
+Therefore, the stability analysis begins by comparing module weights between periods D and F.
+
+Variations in module weight across periods are used to identify unstable modules.
+Table~\ref{tab:pcc_2017_module_selections} presents the selection criteria applied in each comparison and the number of modules that meet these criteria.
+
+\begin{table}[h]
+    \caption{PCC 2017 detector module stability selections applied to the module weights}
+    \label{tab:pcc_2017_module_selections}
+  \begin{center}
+    \begin{tabular}{cc}  
+    \textbf{Periods}   & \textbf{\# Good modules} \\ \hline
+     D + F      & 945           \\ 
+     D + B      & 945           \\ 
+     D + C      & 945           \\ 
+     D + E      & 859           \\ 
+     B + F      & 819          \\ 
+     B + C      & 807          \\ 
+     B + E      & 810          \\ 
+     E + C      & 901          \\ 
+     E + F      & 756          \\ 
+     C + F      & 907          \\ \hline
+     \textbf{Combined}   & \textbf{633}  \\ \hline
+      \end{tabular}
+  \end{center}
+\end{table}
+
+%The final list of good modules ("Combined") is obtained by requiring that modules be selected in all comparisons (i.e.
+the intersection of all sets).
+Figure~\ref{fig:pcc2017modulevetofinal} shows the distribution of module weight ratios between periods B and D with the initial and final module selections, a large improvement is observed in the standard deviation of the distribution.
+
+\begin{comment}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.48\textwidth]{figures/performance_PCC/PCC_2017_moduleveto_DB_initialveto.png}
+    \includegraphics[width=0.48\textwidth]{figures/performance_PCC/PCC_2017_moduleveto_DB_finalveto.png}
+    \caption{Distribution of module weight ratios for the 2017 periods B and D with the initial (left) and final (right) module selections.}
+    \label{fig:pcc2017modulevetofinal}
+\end{figure}
+\end{comment}
+
+The number of selected modules for the final analysis was \textbf{633 (34.1\%) for 2017}.
+
+\clearpage \newpage
+\subsection{2018 Pixel Detector module selection}
+\label{sec:pcc_perf_moduleselection}
+
+The recorded data from 2018 is divided into seven periods: A, B, C, D1, D2, D3, and D4.
+The vdM calibration data (LHC Fill 6868) is part of period B.
+The module vetolist is first created for period B and the vdM fill, and then extended to the other periods (A, C, D1, D2, D3, and D4).
+
+To determine the list of good modules, the ZeroBias data is processed by analyzing the cluster count of each module relative to the total count (module weight), following the method described at the beginning of this section.
+A bootstrap procedure is then applied to remove unstable modules.
+
+As explained earlier, as a first steps, for each period, lumisections with poor PCC statistics are removed by applying a selection based on total PCC and all barrel layer 1 modules are excluded due to their significant sensitivity to dynamic inefficiency effects.
+The following describes the procedure applied to different periods.
+
+For period B and the vdM fill, an initial 7\% selection is applied to remove unstable modules.
+The stability of the remaining modules is then re-evaluated based on updated module weights, and a final 2\% selection is applied using the recalculated RMS/Mean values.
+
+In periods A, C, and D, the module selection from period B serves as the starting point.
+The same procedure is applied, including the two-step selection with 7\% and 2\% thresholds.
+Additionally, module weight variations between period B and these periods are examined, and modules with a deviation greater than three sigma from the mean are removed.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.6\textwidth]{Chapter4/module_selection/RMSmean.png}
+    \caption{rms/mean of module weight profile for all modules.
+A loose selection of 7\% is applied to remove bad modules.
+Appropriate selections are applied in each iterative step to remove other bad modules.}
+    \label{fig:outliermodules}
+\end{figure}
+
+A common module list was created by combining all exclusive module lists from different period combinations.
+Table~\ref{tab:2commonveto} presents the number of good modules after sequentially combining each period.
+
+\begin{comment}
+\clearpage
+\newpage
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1\textwidth]{figures/performance_PCC/good_bad_modules.png}
+    \caption{Variation of normalized module weight with time.
+Modules showing significant change in module weight (shown in right figure) over time having large rms/mean values are used to make module vetolist.}
+    \label{fig:goodbadmodules}
+\end{figure}
+\end{comment}
+
+%\clearpage
+%\newpage
+
+\begin{table}[h]
+\caption{Common module vetolist created by combining module vetolists for each period using a 2\% quality selection as described in the text.}
+    \label{tab:2commonveto}
+  \begin{center}
+    \begin{tabular}{ccccc}  
+    \textbf{Period}   & \textbf{\# bad modules} & \textbf{\# good modules} \\  \hline
+     B      &  802   &  1054    \\ 
+     B + C      &  1076   &  780    \\ 
+     A + B + C      &  1417   &  439    \\  
+     A + B + C + D1      &   1534  &   322    \\ 
+     A + B + C + D1 + D2      &   1629 &    227   \\ 
+     A + B + C + D1 + D2 + D3     &   1668 &   188    \\ 
+     A + B + C + D1 + D2 + D3 + D4     &  1701 &     155  \\ 
+   \end{tabular}
+  \end{center}
+\end{table}
+
+The number of selected modules for the final analysis was \textbf{155 (8.35\%) in 2018}.
+
+The relative contribution of each pixel detector layer and disk to the total PCC, after applying the final module selection, is shown in Fig.~\ref{fig:stabprof} as a function of time throughout the year.
+%\includegraphics[scale=.17]
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.7\textwidth, height=7cm]{Chapter4/module_selection/ProfileX_combined_testing_LUM_20-001.png}
+    \caption{Stability profiles of Pixel detector layers and disks with the final module selection.}
+    \label{fig:stabprof}
+\end{figure}
+
+%Run range for each period is shown in Table \ref{tab:period run ranges}. 
+ \begin{comment}
+ Bad modules found after applying this 2\% selection in the final iterative step are used to constitute a 2 $\%$ rms module veto list for each period as shown in Table \ref{tab:per period veto}.
+
+\begin{table}
+  \begin{center}
+    \begin{tabular}{ccccc}  
+    \textbf{Period}   & \textbf{\# bad modules} & \textbf{\# good modules} \\ \hline
+     2018A      &   1276   &  580    \\  
+     2018B      &    802  &     1054  \\ 
+     2018C      &   1076  &    780   \\ 
+     2018D1     &  1169  &     687  \\ 
+     2018D2     &  1184  &    672   \\ 
+     2018D3     &  1081  &    775   \\ 
+     2018D4     &  1032  &     824  \\ 
+      \end{tabular}
+    \caption{2 \% rms module vetolist for each period showing number of good and bad modules.}
+    \label{tab:per period veto}
+  \end{center}
+\end{table}
+\end{comment}
+
+\begin{comment}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.8\textwidth]{figures/performance_PCC/period_boundary.png}
+    \caption{2018 luminosity data taking periods showing data taking period boundaries and vdM calibration data.}
+    \label{fig:period_bound}
+\end{figure}
+\end{comment}
+
+\begin{comment}
+\begin{table}[h]
+    \caption{2018 luminosity data periods with run ranges.}
+    \label{tab:period run ranges}
+  \begin{center}
+    \begin{tabular}{ccccc}  
+    \textbf{Period}   & \textbf{Run range} \\ \hline
+     2018A      &        315252-316995         \\ 
+     2018B      &        317080-319311         \\ 
+     2018C      &        319337-320065         \\ 
+     2018D1     &        320500-321665        \\ 
+     2018D2     &        321710-322964         \\ 
+     2018D3     &        323363-324420         \\ 
+     2018D4     &        324564-325175        \\ 
+      \end{tabular}
+  \end{center}
+\end{table}
+\end{comment}
+
+\clearpage
+\newpage
 \section{Background estimation}
 \label{bkg}
+
+To perform accurate fitting of the data, it is necessary to take into account the following background contributions to the PCC rates.
+These contributions are estimated independently during the Super Separation (SS) periods discussed in the previous section.
+Three primary sources of beam-induced background should be considered:
+
+\begin{itemize}
+
+\item Beam Halo (BH): This component occurs when the secondary particles reach the experimental cavern from the LHC tunnel.
+The primary beam halo is  the population of beam protons characterized by offsets in the transverse coordinates, travelling in  radial amplitude around the beam axis and being captured mostly by the LHC collimation system.
+In every step of the multi-stage cleaning system of the LHC, more halo particles are captured but also secondary showers are created by the interaction of the beam particles with the collimator material.
+The largest contribution of the  beam halo to the background consist of secondary particles  that stem from the interactions of the beam halo particles at the tertiary collimators and arrive in large radius into the CMS cavern \cite{beam_halo}.
+
+\item  Beam Gas Inelastic (BGI): This component arises from all inelastic interactions between primary beam protons and residual gas in the beam pipe.
+The interaction rate is largely influenced by the quality of the vacuum in the various beam line elements upstream of CMS, so the source of this contribution is distributed throughout the long straight section \cite{bkg_source}.
+
+\item Beam Gas Elastic (BGE): The elastic beam gas contribution is made up of all the coherent and quasi-elastic, nuclear elastic, and Coulomb scattering for multi-turn beam-gas interactions around the ring.
+\cite{bkg_source}.
+
+\end{itemize}
+
+\subsection{Background estimation for 2017 data}
+\label{bkg}
+
+\begin{comment}
+For the 2017 vdM calibration program there were no Super-Separation data obtained.
+For this dataset a different strategy was implemented.
+In a first analysis the vdM scans have been fit without prior background subtraction on the rates, but including a floating constant term in the fit.
+However, this constant term was poorly constrained in the fit.
+A a detailed analysis of the tails of the vdM scans was performed where the PCC rates are studied at the most separated beam positions (last point in the tails), these tail rates have been used to study the background level for each BCID and as a function of time.
+Significant variation has been observed for different BCID's.
+
+\begin{table}[h]    
+\caption{PCC background estimated for the 2017 vdM fill.}
+\label{tab:vdm_bkg_2017}
+  \begin{center}
+    \begin{tabular}{cc}
+    \textbf{BCID}   & \textbf{Background Rate}  \\  \hline
+      41     &  0.463     \\
+        281  &     0.466   \\
+       872    &   0.434   \\
+       1783  &    0.382   \\
+        2063  &     0.385   \\
+      \end{tabular}
+  \end{center}
+\end{table}
+\end{comment}
+
+\subsection{Background estimation for 2018 data}
+\label{bkg}
+\begin{comment}
+In order to illustrate a SS period for this analisys, the Fig.
+\ref{ssp_wide_bx282}, correspnding to the BCID 282, displays the $<\text{PCC}>$  that is the average of pixel clusters per event in a time of 1.32s (NB4).
+The lower regions of the plot correspond to a time window of 5 minutes during which the beams were separated by a distance of $6\sigma_{b}$.\\
+
+\begin{center}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=.80\textwidth]{Chapter4/BX_282_Rates_SS1.png}
+\caption[Super Separation period I for BCID 282]{Background  level for BCID 282, where $<\text{PCC}>$ is the average of pixel clusters per event in a time of 1.32s (NB4)  .
+The lower region correspond to the super separation period I.}
+\label{ssp_wide_bx282}
+\end{figure}
+\end{center}
+
+To estimate the background value and its conrresponding statistical error (SEM) for each super separation period, the mean value and the standard deviation are taken from the distribution resulting  by making a Y-projection from the rates of $<\text{PCC}>$ shown in the Fig \ref{ssp_wide_bx282}.
+To illustrate this process Fig. \ref{ss1_hist_282} displays a distribution for these values for the SS period I, specifically for BCID 282. The same plot and analysis were done  for each BCID.\\
+
+The background estimation for the PCC rates in 2018 is done in two Super-Separation scans (SS1 and SS2) where the beams are separated and the PCC rates correspond to detector noise. 
+An example of a SS period shown in Fig. \ref{fig:SS_rates}, the mean and error are obtained from the $y$ projection of this distribution during the SS period.
+
+The background values  for the five different BCID's in 2017 and 2018 are shown in Table~\ref{tab:vdm_bkg}. 
+For 2018 the background correction applied to the PCC rate is $0.02757 \pm 0.01987$, calculated by taking the average of the BCD's and SS periods. 
+For 2017 each BCID was corrected separately.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.44\textwidth]{figures/performance_PCC/PCCRawRate2017vdM_bcid41.png}
+    \includegraphics[width=0.54\textwidth,height=0.35\textwidth]{figures/performance_PCC/PCC_Rates_SS1.pdf}
+    \caption{Left: PCC raw rates for BCID  41 in the vdM fill 6016 (2017). 
+    Right: PCC raw rates in Super Separation Period I in fill 6868 (2018) for BCID 265.}
+    \label{fig:SS_rates}
+\end{figure}
+
+\begin{table}[h]    
+\caption{PCC background estimated with the SS1 and SS2 data in 2018 for all BCID's.}
+\label{tab:vdm_SS1_SS2}
+  \begin{center}
+    \begin{tabular}{ccccc}
+    \textbf{BCID}   & \textbf{Mean (SS1)} & \textbf{Mean (SS2)} \\ \hline
+      265     &  0.02902    &  0.02743    \\
+        865  &    0.02572  &     0.0281  \\
+       1780    &  0.02862   &     0.0286  \\
+       2192   &  0.02729  &     0.02323  \\
+        3380  &  0.02882  &    0.02896   \\
+      \end{tabular}
+  \end{center}
+\end{table}
+
+\begin{comment}
+\begin{table}[h]    
+\caption{PCC background estimated for 2017 and 2018 vdM data.}
+\label{tab:vdm_bkg}
+  \begin{center}
+    \begin{tabular}{|cc|ccc|}
+    \hline\hline
+   \multicolumn{2}{|c|}{\textbf{ 2017 Fill 6016}}   & \multicolumn{3}{|c|}{\textbf{2018 Fill 6868}}  \\ 
+   BCID   & Bkg.  & BCID   &  Bkg.(SS1)  &  Bkg.(SS2) \\ \hline
+    41     &  0.463 &  265     &  0.02902    &  0.02743    \\
+     281  &     0.466 &  865  &    0.02572  &     0.0281  \\
+     872    &   0.434  & 1780    &  0.02862   &     0.0286  \\
+      1783  &    0.382  & 2192   &  0.02729  &     0.02323  \\
+       2063  &     0.385 & 3380  &  0.02882  &    0.02896   \\
+       \hline\hline
+      \end{tabular}
+  \end{center}
+\end{table}
+
+\begin{comment}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.8\textwidth]{figures/performance_PCC/PCC_Projection_SS1.pdf}
+    \caption{PCC distribution corresponding to the Super Separation Period I for BCID 265.}
+    \label{fig:SS_Projection}
+\end{figure}
+
+Fig.
+\ref{fig:fitquality} shows chi2/ndof for vdM and imaging scans with an average value of 0.4514 where the Poly2G fit model converges for all BCIDs.
+Peak value and beam overlap along X and Y are extracted from fit to calculate PCC visible cross section $\sigma_{vis}$.
+$\sigma_{vis}$ for $2\%$ rms common module vetolist is 960.601 $\pm$ 0.851(stat.) mb.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.6\textwidth]{figures/performance_PCC/fit_quality_chisquare.png}
+    \caption{chi2/ndof for all vdM and imaging scans.}
+    \label{fig:fitquality}
+\end{figure}
+
+The visible cross section per scan is averaged over all BCIDs and its scan to scan variation as shown in Fig. \ref{fig:sigmaperscan}.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.7\textwidth]{figures/performance_PCC/sigma_vis_per_scan.png}
+    \caption{$\sigma_{vis}$ per scan where red line shows the average value.}
+    \label{fig:sigmaperscan}
+\end{figure}
+\end{comment}
 
@@
 
-\section{Results}
+After testing several mathematical fit models, the chosen model with the best fit quality and after applying all the corrections mentioned earlier, was a double Gaussian function:
+%https://gitlab.cern.ch/bril/VdMFramework/-/blob/main/src/plotting/capsigma_over_time.py#L90
+%\begin{equation}
+%DG+Const= C+P \cdot \Biggl[ F \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 \sigma_{1}^{2} } \Biggr) + (1-F) \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 \sigma_{2}^{2} } \Biggr) \Biggr] 
+%\end{equation}
+%\begin{equation}
+%f(x)= P \cdot \Biggl[ F \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2(\frac{\Sigma\cdot R}{F \cdot R+1-F} )^{2} } \Biggr) + (1-F) \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 (\frac{\Sigma}{F \cdot R+1-F} )^{2} } \Biggr) \Biggr]
+%\end{equation}
+%[5] + [2]*([3]*exp(-(x-[4])**2/(2*([0]*[1]/([3]*[1]+1-[3]))**2))
+    %    + (1-[3])*exp(-(x-[4])**2/(2*([0]/([3]*[1]+1-[3]))**2)) )
+%("#Sigma","#sigma_{1}/#sigma_{2}","peak","Frac","Mean","Const")
+%[0] -> [0]*[1]/([3]*[1]+1-[3])
+ %[1] -> [0]/([3]*[1]+1-[3])"""
+
+\begin{equation} 
+Poly4G(x)= A \Biggl[ 1+a_{2} \Biggl( \frac{-(x-\bar{x})}{\sigma} \Biggr)^{2} +a_{4} \Biggl( \frac{-(x-\bar{x})}{\sigma} \Biggr)^{4} \Biggr]\exp \Biggl[ -\frac{-(x-\bar{x})^{2}}{2\sigma^{2}}\Biggr]
+\end{equation}
+
+\begin{equation} 
+Poly4G(x)= A \Biggl( 1+a_{2} \biggl( \frac{-(x-\bar{x})}{\sigma} \biggr)^{2} +a_{4} \biggl( \frac{-(x-\bar{x})}{\sigma} \biggr)^{4} \Biggr)\exp \Biggl( -\frac{-(x-\bar{x})^{2}}{2\sigma^{2}}\Biggr)
+\end{equation}
+
+\begin{itemize}
+%\item $C$ is the constant value.
+\item $P$ the $peak$ rate.
+\item $F$ is the fraction of the peak rate attributed to the first Gaussian in the sum.
+\item $x$ is the beam position.
+\item $\bar{x}$ is the mean.
+\item $\Sigma$ is the overlap between the beams.
+\item $R$ is the ratio between the standard deviations of the  Gaussians (first over the second).
+\end{itemize}
+
+\section{Visible cross section results}
+
+\section{Cross-detector comparisons}
+
+\begin{comment}
+For each luminometer, the calibrations derived using the van der Meer method and the final corrections are applied to the collected data.
+SBIL measurements are aggregated over time periods corresponding to LHC orbits, each lasting approximately 23.3 seconds (known as a "lumi-section"), and then integrated across the entire year.
+The luminometers measure the luminosity delivered to CMS by the LHC.
+However, the luminosity of interest for most physics analyses corresponds to the periods when the CMS detector operated correctly and the data was successfully recorded by its DAQ system.
+This recorded luminosity is reduced by a factor of (1 - dead time), where the dead time is determined by the CMS timing and control distribution (TCDS) system [21].
+The resulting total integrated luminosity is TO DO: X for 2017 and TO DO: Y for 2018.
+
+Normalization uncertainties are considered correlated across the years studied if they arise.
+
+Table 2: Summary of contributions to the relative systematic uncertainty in σvis (in \%) at √s = 13 TeV in 2017 and 2018.
+The systematic uncertainties are divided into groups affecting the vdM calibration at low luminosity (normalization), and the measurement of the luminosity in physics conditions (integration).
+The fourth column indicates whether the uncertainties are considered correlated between the two years, while the fifth column contains the accordingly combined uncertainty.
+TO DO: PCC only calibration is quoted in the table.
+To be discussed.
+
+The sources of systematic uncertainties that limit the precision of the measured luminosity have been thoroughly discussed above.
+We categorize these uncertainties into two types, as detailed in Table 2: "normalization" uncertainties, which impact the absolute luminosity scale determined by the vdM scan method, and "integration" uncertainties, which relate to the linearity and stability of response of the detectors.
+
+The dominant sources of normalization uncertainty are associated with transverse factorizability, beam-beam effects, and, to a lesser extent, scan-to-scan variations and cross-detector consistency at vdM (as described in Section 3).
+Both integration uncertainties (discussed in Section 5) are significant, with each surpassing any individual normalization uncertainty.
+\end{comment}
+
+\begin{figure}[h]
+  %\centering
+  \hspace{-1.9cm}
+  \begin{minipage}{0.48\textwidth}
+    \centering
+    \includegraphics[scale=.4]{Chapter3/2017_stability/ratio__hfet-pcc-plt-hfocdivmean_PCConly.pdf}
+    \raggedleft
+    \caption[Doros]{Beam Position at the vdM Scan Program 2017 \cite{lhc_complex}.}
+    \label{BeamPosition_2017}
+  \end{minipage}
+  \hspace{1cm} %\hfill
+  \begin{minipage}{0.48\textwidth}
+    \centering
+    \raisebox{0.3cm}{
+    \includegraphics[scale=.4]{Chapter3/2017_stability/stacked__hfet-pcc-plt-hfocdivmean_PCConly.pdf}
+    }
+    \caption{Another image caption.}
+    \label{AnotherImage}
+  \end{minipage}
+\end{figure}
+
+\begin{figure}[h]
+  %\centering
+  \hspace{-1.9cm}
+  \begin{minipage}{0.48\textwidth}
+    \centering
+    \includegraphics[scale=.4]{Chapter3/2018_stability/ratio__hfet-pcc-plt-hfocdivmean_PCConly.pdf}
+    \raggedleft
+    \caption[Doros]{Beam Position at the vdM Scan Program 2017 \cite{lhc_complex}.}
+    \label{BeamPosition_2017}
+  \end{minipage}
+  \hspace{1cm} %\hfill
+  \begin{minipage}{0.48\textwidth}
+    \centering
+    \raisebox{0.3cm}{
+    \includegraphics[scale=.4]{Chapter3/2018_stability/stacked__hfet-pcc-plt-hfocdivmean_PCConly.pdf}
+    }
+    \caption{Another image caption.}
+    \label{AnotherImage}
+  \end{minipage}
+\end{figure}
+
+\begin{figure}[h]
+  %\centering
+  \hspace{-1.9cm}
+  \begin{minipage}{0.48\textwidth}
+    \centering
+    \includegraphics[scale=.4]{Chapter3/2017_stability/means_clean__hfet-pcc-plt-hfocdivmean_PCConly.pdf}
+    \raggedleft
+    \caption[Doros]{Beam Position at the vdM Scan Program 2017 \cite{lhc_complex}.}
+    \label{BeamPosition_2017}
+  \end{minipage}
+  \hspace{1cm} %\hfill
+  \begin{minipage}{0.48\textwidth}
+    \centering
+    \raisebox{0.3cm}{
+    \includegraphics[scale=.4]{Chapter3/2018_stability/means_clean__hfet-pcc-plt-hfocdivmean_PCConly.pdf}
+    }
+    \caption{Another image caption.}
+    \label{AnotherImage}
+  \end{minipage}
+\end{figure}
 

### 2025-03-21 monograph_Luis/compile.sh

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-thesis="thesis";
+thesis="thesis";  #thesis
 
 if [ $1 = "clean" ]
 then

### 2025-04-02 thesis_julio/Chapter1/chapter1.tex
commit1

\chapter{Introduction}
\label{ch1}

%%%%% https://cerncourier.com/a/pushing-the-precision-frontier/
% https://home.cern/news/news/physics/why-precision-luminosity-measurements-matter

\section{Particle Physics and the Standard Model}

Elementary particle physics is the study of the particles at the most fundamental level, the constituents of the universe as well as the interactions between them which are called, electromagnetic force, nuclear weak force and nuclear strong force and there is also the gravity force but this one doesn't have a satisfactory quantum theory for it. Each of these forces are mediated by exchange particles, in the case of the electromagnetic force the mediator is the photon, for the strong force the gluons, for the weak force the bosons W and Z and for the gravity we have the hypothetical graviton.  \cite{Griff}

\includegraphics[scale=1]{table1.png}
\caption{Forces magnitude compared}

Each of these forces have a mathematical description for the physical systems of these interactions using the Quantum Field Theory (QFT). The one that describes systems under the electromagnetic force is called Quantum Electrodynamics (QED) this force dictates the electronic structure of atoms being the low energy manifestation of the electromagnetic theory. For the strong force Quantum Chromodynamics (QCD) is the fundamental theory of strong interactions, this force is responsible of maintaining protons and neutrons together in the atomic nucleus. For the weak interactions there is no particular name in the same way as the previous two, this force is is carried by all quarks and leptons and is responsible for the $\beta$ Decay of some radioactive isotopes and nuclear processes of the sun. \cite{mppthomson}

Almost all the physical phenomena can be explained with only the electron, the electron neutrino, the proton and the neutron interacting with the electromagnetic force, the strong force and the weak one. When higher levels of energy are present new particles are observed, all of this is known as the elementary particles which are embodied in the standard model of particle physics that is by far the best theorical model that describes interaction of this elementary particles. Is divided into two categories the bosonic sector and the fermionic sector.  \cite{mppthomson}

\includegraphics[scale=0.7]{sm.png}

The fermionic sector contains particle the particles that make up all known matter in the universe and is divided into the leptons and the quarks, both of this particles are divided into three generations, each generation being heavier than the one before. For the leptons we have electron and Its neutrino for the first generation, the second generation is. the $\mu$ and Its neutrino and the third one is the $\tao$ with Its neutrino. In the case of quearks we have the queark up and the quark down for the first generation, the second generation que have the quark charmd and the quark strange and for the third generation que have the quark top and the quark bottom. The bosons are the mediator particles called the gauge bosons already mentions, the photon, the gluon, the bosons $W\pm$ and the boson Z. There is also de Higgs bosson, which is the last gauge bossons and It's the responsible to give mass to the other SM particles

One of the main sources to obtain elementary particles is particle accelerators, in this you acelerrate a particle into high energy and smash them with a target, with the proper  arrangements of magnets you can study the debris from the collision, for more heavy particles you need higher level of energy to the collision.

\section{Large Hadron Collider}

The Large Hadron Collider (LHC) is the biggest and powerful particle accelerator in the world, it consist in a 27 kilometers ring with superconducting magnets that boost the energy of the particles alongs the way. It uses proton beams from hydrogen tanks and there is four colliding points corresponding to different particle detectors, the ATLAS, the CMS, ALICE and LHCb. \cite{LHC}

\includegraphics[scale=0.35]{LHC.png}

\section{Luminosity}
Luminosity is as key parameter in particle colliders

The luminosity is a quantity that measures the ability of the acelerator to produce the required number of interactions an is:

$\frac{dR}{dt} = \mathcal{L} \cdot \sigma_{p} $ \cite{Lum}

In which \cite{Lum}

In order to check the numbers of events the integrated luminosity is used and is defined as:

$ L_{int} = \int L (t') dt' $

### 2025-04-02 thesis_julio/Chapter2/chapter2.tex
commit1

\chapter{Experiments}
\label{ch2}

\section{CMS experiment}

The CMS is a detector that consist on different detectors made for detecting different particles, like the silicon tracker, the electromagnetic calorimeter, the hadron calorimeter the superconducting solenoid and the muon chamber. Its a cylindrical onion with several  \cite{CMS}

\includegraphics[scale=0.35]{cms.png}

\section{Pixel Detector}

This is one of the detectors of the CMS \cite{pxd}

\includegraphics[scale=0.7]{pixeldetector.png}

\section{PCC method}

The Pixel Cluster Counting (PCC) method

\section{Van Der Meer Method}

The Van Der Meer Method \cite{Vdm}

\section{Calibration Constant}

The calibration constant

$\sigma_{vis} = \frac{R_{det}}}{L_{b}} = \frac{2 \pi \Sigma_{x} \Sigma_{y} R(0,0)}{N_{1}N_{2}f}$  \cite{Lumvdm}

### 2025-04-02 thesis_julio/Chapter3/chapter3.tex
commit1

\chapter{Data Processing}
\label{ch3}

\section{Datasets}

\section{Background Estimation}

\section{Corrections}

### 2025-04-02 thesis_julio/Chapter4/chapter4.tex
commit1

\chapter{Results}
\label{ch4}

\section{}
\section{}
\sectin{}

### 2025-04-10 thesis_julio/Chapter1/chapter1.tex
commit2

@@
 the $\mu$ and Its neutrino and the third one is the $\tao$ with Its neutrino.
-In the case of quearks we have the queark up and the quark down for the first generation, the second generation que have the quark charmd and the quark strange and for the third generation que have the quark top and the quark bottom.
+In the case of quarks we have the quark up and the quark down for the first generation, the second generation que have the quark charmd and the quark strange and for the third generation que have the quark top and the quark bottom.
 The bosons are the mediator particles called the gauge bosons already mentions, the photon, the gluon, the bosons $W\pm$ and the boson Z.
@@
 
-One of the main sources to obtain elementary particles is particle accelerators, in this you acelerrate a particle into high energy and smash them with a target, with the proper  arrangements of magnets you can study the debris from the collision, for more heavy particles you need higher level of energy to the collision.
+One of the main sources to obtain elementary particles is particle accelerators, in this you accelerate a particle into high energy and smash them with a target, with the proper  arrangements of magnets you can study the debris from the collision, for more heavy particles you need higher level of energy to the collision.
 
@@
 
-The Large Hadron Collider (LHC) is the biggest and powerful particle accelerator in the world, it consist in a 27 kilometers ring with superconducting magnets that boost the energy of the particles alongs the way.
-It uses proton beams from hydrogen tanks and there is four colliding points corresponding to different particle detectors, the ATLAS, the CMS, ALICE and LHCb.
+The Large Hadron Collider (LHC) is the biggest and powerful particle accelerator in the world at this moment, It is a 27 kilometers ring of superconducting magnets, this magnets boost the particles energies to obtain speeds that are close to the light speed before collisions.
+These particles are introduced as to the accelerator as particles beams this beams travel in opposing directions in tubes that are kept at ultrahigh vacuum, with the help of a electromagnetic field made by the electromagnets operating in superconduct state at low temperatures thanks to liquid helium this particles are guided across the whole accelerator.
 \cite{LHC}
@@
 
+The LHC is part of an accelerator complex in CERN that is a succession of different machines that increase the energy of the beam of particles before passing into the next one on the sequence the particles at last are introduced on the LHC which is the last element in the sequence.
+The particles start at the linear accelerator 4 (Linac4) which is the source of the protons beams, it accelerates the particles in this case negative hydrogen ions to 160 MeV to enter the Proton Synchroton Booster (PSB), this is were the hydrogen loses Its two electrons leaving only protons and accelerating the beam to 2 GeV  and then are injected into the Proton Synchroton (PS), in where the protons are accelerated up to 26 GeV and then they are sent into the Super Proton Synchroton (SPS) here they are accelerated up to 450 GeV and then they're finally introduced into two beams pipes on the LHC, it takes about 4 minutes and 20 seconds to fill the LHC rings reaching energies up to 6.5 TeV, there are 4 collisions points where the detectors are located Alice, Atlas, CMS and LHCb, in the collision the total energy is of 13.6 TeV.
+\cite{LHCII}
+
+The LHC has been working since 2009 with the discovery of the Higgs Boson on 2012 and looking for new physics It has been working on different periods called Runs, Run 1 was on the period of (2009-2013), Run 2 was on (2015-2018), Run 3 is currently on going since 2022.
+
 \section{Luminosity}
-Luminosity is as key parameter in particle colliders
 
-The luminosity is a quantity that measures the ability of the acelerator to produce the required number of interactions an is:
+The performance of a collider is determined by the beam energy and the luminosity, the luminosity is a key parameter in particle colliders is a quantity that measures the ability of a particle accelerator to produce a required number of interactions and is given by: \cite{Lum}
 
-$\frac{dR}{dt} = \mathcal{L} \cdot \sigma_{p} $ \cite{Lum}
+$\frac{dR}{dt} = \mathcal{L} \cdot \sigma_{p} $
 
-In which \cite{Lum}
+In which $\frac{dR}{dt}$ is the number of events per second, the $\simga_{p}$ is the cross section and $\matchcal{L}$ the instantanious luminosity luminosity.
+The unity of $\mathcal{L}$ is  $cm^{-2} s^{-1}$ a higher luminosity means greater probability that the particles will collide and produce the desired interactions, luminosity can be increased then in two ways, packing more particles into the beams or focusing this beams more.
 
-In order to check the numbers of events the integrated luminosity is used and is defined as:
+ \includegraphics[scale=0.80]{lumii.png}
+
+To compute the luminosity of two there is a few things that need to be taken in consideration.
+First the density distribution of each beam in the transverse and longitudinal plane, with the.
+two beams moving towards each other, the position and the time as the cross each other also need to be considered and calling the distance to the collision point $s_{0}$.
+In principle each of the distributions is different the overlap integral can be written as follow:
+
+ \includegraphics[scale=0.80]{lumi.png}
+
+$ N_{1}N{2}fN_{b} K \int \int \int^{\infty}_{-\infty}  \rho_{1} (x,y,s,s_{0}) \rho_{x}(x,y,s,s_{0})  dxdydsds_{0}  $
+
+With N1 and N2 being the bunch intensitie, f the revolution frecuency, $N_{b}$ the number of colliding bunches, $\rho_{1}$ and $\rho_{2}$ time dependent beam density distribution functions and K being the Kinematic factor defined as:
+
+$K = sqrt{(v_{1} - x_{2})^{2} - \frac{(v_{1} x v_{2})^{2}}{c^{2}} }
+
+So now assuming that the velocity on the beams is $v1 = -v2$ and the densities are uncorrelated in all planes the overlap integral takes the form of: \cite{Lumvdm}
+
+$ 2N_{1}N{2}fN_{b} \int \int \int^{\infty}_{-\infty}  \rho_{1x} (x) \rho_{1y}(y) \rho_{1s} (s-s_{0}) \rho_{2x}(x) \rho_{2y}(y) \rho_{2s} (s+s_{0}) dxdydsds_{0}  $
+
+For solving this integral one should known all distributions and an analytical solutions might not be possible and numerical numerical integration might be required.
+
+The instantaneous luminosity is important  but the final important number is called integrated luminosity.
+The integrated luminosity considers the total number of events during a data period is defined as:
 
 $ L_{int} = \int L (t') dt' $
+
+it is related directly to the number of observed events
+
+$\mathcal{L}_{int} \cdot \sigma_{p} =$ number of events of interest
+
+There have been different luminosities reached on the LHC for the Run 1 a luminosity of $0.77 x 10^{34}$ was reached and a integrated luminosity of 25 $fb^{-1}$  with a precision of 2.0\% for the first part and second part of the Run 2 the luminosity measured was of 38.4 $fb^{-1}$ with a precision of 1.3\% and 78$fb^{-1}$ respectively\cite{LHClum}.
+The following image show shows the integrated luminosity for the CMS experiment on different years.
+
+ \includegraphics[scale=1.25]{integratedlum.png}

### 2025-04-10 thesis_julio/Chapter2/chapter2.tex
commit2

@@
-\chapter{Experiments}
+\chapter{CMS Experiment}
 \label{ch2}
 
-\section{CMS experiment}
+\section{CMS detector}
 
-The CMS is a detector that consist on different detectors made for detecting different particles, like the silicon tracker, the electromagnetic calorimeter, the hadron calorimeter the superconducting solenoid and the muon chamber.
-Its a cylindrical onion with several  \cite{CMS}
+The CMS is one of the four interactions points on the LHC.
+Its a cylindrical onion with several concentric layers this layers consist on different detectors made for detecting different particles, like the silicon tracker, the electromagnetic calorimeter, the hadron calorimeter the superconducting solenoid and the muon chamber.
+Its a cylindrical onion with several concentric layers.
+\cite{CMS}
+
+The Sylicon Tracker is composed of different substructures Its main purpose It's to reconstruct the trajectories of charged particles, in the point closest to the collision of the beams tis where the Sylicon Pixel Detector is located.
+%NEEDED\cite{CMS}
 
 \includegraphics[scale=0.35]{cms.png}
+
+The other parts of the detector are for locating different types of particles depending on their interactions , the electromagnetic calorimeter
 
@@
 
-\section{PCC method}
+\section{PCC}
 
@@
 
-\section{Van Der Meer Method}
-
-The Van Der Meer Method \cite{Vdm}
-
-\section{Calibration Constant}
-
-The calibration constant
-
-$\sigma_{vis} = \frac{R_{det}}}{L_{b}} = \frac{2 \pi \Sigma_{x} \Sigma_{y} R(0,0)}{N_{1}N_{2}f}$  \cite{Lumvdm}
+\section{Module Selection}

### 2025-04-21 thesis_julio/Chapter1/chapter1.tex
commit4

@@
 
+\begin{figure}[h]
+    \centering
     \includegraphics[scale=1]{table1.png}
-\caption{Forces magnitude compared}
+    \caption{The magnitude of the four forces compared}
+    \label{fig:four-forces}
+\end{figure}
 
@@
 
- \includegraphics[scale=0.80]{lumii.png}
-
 To compute the luminosity of two there is a few things that need to be taken in consideration.
@@
 
-$ N_{1}N{2}fN_{b} K \int \int \int^{\infty}_{-\infty}  \rho_{1} (x,y,s,s_{0}) \rho_{x}(x,y,s,s_{0})  dxdydsds_{0}  $
-
-With N1 and N2 being the bunch intensitie, f the revolution frecuency, $N_{b}$ the number of colliding bunches, $\rho_{1}$ and $\rho_{2}$ time dependent beam density distribution functions and K being the Kinematic factor defined as:
-
-$K = sqrt{(v_{1} - x_{2})^{2} - \frac{(v_{1} x v_{2})^{2}}{c^{2}} }
-
-So now assuming that the velocity on the beams is $v1 = -v2$ and the densities are uncorrelated in all planes the overlap integral takes the form of: \cite{Lumvdm}
+%$K = sqrt{(v_{1} - x_{2})^{2} - \frac{(v_{1} x v_{2})^{2}}{c^{2}} }
 
 $ 2N_{1}N{2}fN_{b} \int \int \int^{\infty}_{-\infty}  \rho_{1x} (x) \rho_{1y}(y) \rho_{1s} (s-s_{0}) \rho_{2x}(x) \rho_{2y}(y) \rho_{2s} (s+s_{0}) dxdydsds_{0}  $
+
+With N1 and N2 being the bunch intensity, f the revolution frecuency, $N_{b}$ the number of colliding bunches, $\rho_{1}$ and $\rho_{2}$ time dependent beam density distribution functions, this is assuming the velocity on the beams is $v1 = -v2$ and the densities are uncorrelated in all planes the overlap integral takes the form of: \cite{Lumvdm}
 

### 2025-04-21 thesis_julio/Chapter2/chapter2.tex
commit4

--- 2025-04-02 thesis_julio/Chapter2/chapter2.tex
@@
-\chapter{Experiments}
+\chapter{CMS Experiment}
 \label{ch2}
 
-\section{CMS experiment}
+\section{CMS detector}
 
-The CMS is a detector that consist on different detectors made for detecting different particles, like the silicon tracker, the electromagnetic calorimeter, the hadron calorimeter the superconducting solenoid and the muon chamber.
-Its a cylindrical onion with several  \cite{CMS}
+The Compact Muon Solenoid (CMS) detector is one of the four interactions points on the LHC.
+It consist on different detectors made for different purposes, the silicon tracker, the electromagnetic calorimeter (ECAL), the hadron calorimeter (HCAL) the superconducting solenoid and the muon chamber.
+\\
+\includegraphics[scale=0.50]{cms2.png}
+\\
+The CMS has the form of a cylindrical onion with several concentric layers of components, this components are important to determine the properties of different particles all of this by bending their trajectories with a magnet that bend charged particles, this helps to identify the charges of the particles since they bend in different directions and allows to measure the momentum of a particle sine high momentum particles bend less than the low momentum ones.
+The principal magnet of the CMS is called Super Conducting Solenoid this magnet generates a field of about 4 Teslas and is very large 6.3m cold bore, 12.5 meters of length and 200 t of mass.
+The high magnetic field is confined to the volume of the detectors using the "return yoke", this yoke have a magnetic field strength of 2 Teslas and acts as the main support as well as the muon filter Its made of a high amount of steel and It weights more than 11000 tonnes.
+\cite{CMS3}
 
+One of the principal objectives of the CMS is identify with very high precision the paths taken by the particles that were bend by the magnetic field they called this part the inner tracker which is composed of different substructures, closest to the interaction point we have the Silicon Pixel Detector, then after the silicon strip detectors which are divided into the inner barrel part and the outer barrel part, the outer barrel and the outer end caps.
+When a charged particle pass through this layers interacts electromagnetically with the sensors leaving a hit that can be used to identify the path that a particle took.
+\cite{CMS1}
+
+%Might update about the composition of this parts later.
+
+Having information of the energy is important to understand what is happening at the collision point for this purpose there are two calorimeters on the CMS.
+The ECAL is made of 61200 lead tungstate crystals in the central barrel cap closed by 7324 crystals in the two of the endcaps in front of this crystals there is a press shower detector, the high density crystals allow  the calorimeter to be fast, have a fine granularity and being radiation resistant, Its capabilities are improved by the good crystal resolution which are provided by a homogeneous crystal calorimeter.
+It's surrounding the tracker and aims to measure the the energy of electrons, positrons or photons and stop them completely.
+The other calorimeter is the HCAL which is surrounding the ECAL and plays an essential role on the measurements of the energy of hadrons like the quarks, gluons, neutrinos and some exotic particles.
+which are also stopped here.
+\\
 \includegraphics[scale=0.35]{cms.png}
+\\
+The CMS was optimized for the detections of muons and is the last particle that the CMS observe directly with the help of the muon chambers that is composed by many subdetectors which are interleaved with the return of the yoke of the solenoid located after the super conducting solenoid, muons are similar to electrons but 200 times heavier so they are not stopped by the calorimeters, the muon chambers have 3 main purposes; muon identification, momentum measurement and triggering.
+\cite{CMS2}
 
@@
 
-This is one of the detectors of the CMS \cite{pxd}
+In the innermost part part of the CMS experiment there is a silicon pixel detector which is part of the tracking system.
+It has the task of provide high resolution 3D space points close to the collision point for track patter recognition and vertex reconstruction.
+It is located in a place where there is a harsh radiation environment giving Its high track density, in the CMS there was an pixel detector that was later changed during the first long shut down of the LHC during LS1 (2013-2014) and replaced by the CMS Phase-1 Pixel Detector in order to mantain efficient and robust tracking giving that with the upgrade of the accelerators the luminosity have doubled compared to the design value.
+It is expected that this detector to deliver high quality data until the end of the LHC Run 3 (Currently in process) after which the whole track detector on the CMS will be replaced.
 
+Overall, is the closest detector to the beam pipe with cylindrical layers in the range of 3cm and 16cm at either end so It's vital to reconstruct the tracks of particles with very short live spans.
+It contains 124 millions pixels that allows to the tracking of the particles emerging from the collision with a extreme accuracy.
+It has 4 layers, each one of these layers is composed of silicon modules that are splitted into tiny silicon sensors this is what is called the pixels.
+These pixels have a size of 100 $\mu m$ -150 $\mu m$, when a charged particle pass through this pixels it gives the electrons on the silicon enough energy to be ejected with an applied voltage these charges are collected as a small signal which is amplified by an electronic readout ship.
+With these signals we can know which pixels were touched, allowing  us to recreate the track using the 2D tiles detectors and with the help of Its 4 layers can also generate a 3D picture.
+Nevertheless, the rate of the particles passing through this detectors is big at 3cm to the beam pipe the rate is about 600 million of particles $\cm^{2} / s$ the pixel detector is able to reconstruct all the tracks the particles leave behind.
+Each of the 124 million pixels are kept to a minimum power, even with only 50 microwatts per pixel the total power output of the whole detector is it about 7.5kW.
+It also has a freezing system of cooling tubes and kept about 20 degrees celsius reducing the damage to the modules made by the large stream of particles.
+
+The layout of the detector is optimized to have four hit coverage over the pseudorapidity range of  $|\eta| < 2.5$ which is important to improve the pattern recognition and track reconstruction and added redundancy to cope with hit loses.
+Apart from this the detector consist in the already mentioned four concentric barrel layers (L1-L4) with specific radius of 29mm, 68mm, 109 mm and 160 mm and three disks (D1-D3) on the ends with distances to the center of 291mm, 396mm and 516mm and the total silicon area is of 1.9 $m^{2}$.
+The detector is built from 1856 silicon sensor modules, 1184 of these are on the barrel pixel detectors (BPIX) and the rest one are on the forward pixel detectors (FPIX), each module consist in a sensor of 160x416 pixels connected to 16 readout chips (ROCs) for a total of 124 millions readout channels.
+\cite{pxd}
+
+The BPIX and FPIX detectors are independent components, the BPIX consist in two half barrels with a length of 540mm each of the four layers are called half shells and is divided into two mechanically independent halves both composed of one half detector and two service half-cylinders.
+The FPIX is assembled from twelve disks which are divided into inner and outer half rings which supports 22 and 34 modules respectively and is divided into four mechanically independent quadrants each formed by three half-disks installed in a service half cylinder.
+This detectors are supplied with four service half-cylinders that hold the readout and control circuits.
+\\
 \includegraphics[scale=0.7]{pixeldetector.png}
+\\
+In order to optimize the resolution of the tracking and the vertexing the materials used in the detector were minimized.
+Even with the additional layers the material budget for the CMS Phase-1 Pixel in the central region is almost the same as the original detector while reducing the forward region.
+This is possible thanks to the advanced nano carbon-fiber materials for the mechanical structure that adopt the usage of lower mass, and two phases $CO_{2}$ cooling systems.
+The electronics boards on the service half-cylinders are placed in higher pseudorapidity regions outside of the tracking acceptance.
 
-\section{PCC method}
+The innermost layer have to support high levels of radiation and hit rates a hadron fluence of $3.6x10^{15} n_{eq}/cm^{2}$ (neq is the units of 1 MeV of neutrons equivalent) is expected in the innermost layer after collecting a integrated luminosity of 500 $fb^{-1}$.
+In the outer layers of the BPIX and on the FPIX the expected hit rates are of about $600 MHz/cm^{2}$ for BPIX L1.
 
-The Pixel Cluster Counting (PCC) method
+The silicon detector modules is built from a planar silicon sensor bonded to an array of 2x8 ROCs.
+Each ROC is segmented on 4160 readout channels and reads information about each pixel.
+Since 2 ROCs can only be placed at a minimum distance between each other pixels along the ROC boundaries have twice the area and those at the corners have four times the area of a pixel, in the other side of the silicon sensor there is a high density interconnect (HDI).
+To simplify the module production as well Its maintenance, the same rectangular module geometry is used for both BPIX and FPIX detectors.
+In the BPIX detector the orientation of the sensor surface is parallel to the magnetic field, this means that the pixels are oriented parallel to the beam line.
+The FPIX detectors in the outer rings are rotated 20 degrees, in the inner ring the modules are arranged in an inverted cone array with an angle of 12 degrees respect to the beam line combined with the 20 degrees rotation.
+The orientation for the FPIX is made such as the long side of the pixels is in the radial direction.
 
-\section{Van Der Meer Method}
+\\
+\includegraphics[scale=1]{BPIXFPIX.png}
+\\
+The sensors of BPIX and FPIX were designed by two different companies, BPIX was made by CiS Forschungsinstitut fur Mikrosensorik in efurt on germany and FPIX was made on SINTEF micro-systems and sensors in Norway.
+The BPIX sensors were made on approximately 285 $\mu m$ of phosphorous-dope 4-inch wafers from silicon mono-crystals, all of this sensors were produced using silicon from the same ingot.
+In the other side, the FPIX sensors were made on 300 $\mu m$ thick 6 inch float-zone wafers, eight sensors were placed on one wafer, the wafers were accepted if at least six of It's sensors fulfill their specifications.
 
-The Van Der Meer Method \cite{Vdm}
+The readout chips are made using 250 nm CMOS technology, this are named PSI46dig and PROC600.
+The PSI46dig is used on the outer BPIX layers (L2-L4) and in the FPIX detectors, meanwhile the PROC600 was designed for the innermost layer, taking into the consideration the expected hight hit rates.
+The single pixel efficiency of the PSI46dig at high rates was measured using internal calibration signal while exposing the ROCS to high-rate X-rays, the data loses for both of the detectors were of less thant 2 \% at the expected maximum hit rate of 120 MHz/$cm^{2}$ and the PROC600 efficiency is above 95 \% at rates up to 600 Mhz MHz/$cm^{2}$.
 
-\section{Calibration Constant}
+\section{Pixel Cluster Counting}
 
-The calibration constant
+The Pixel Cluster Counting (PCC) method consist in counting the average number of pixel clusters on the detector to measure luminosity.
+This occurs during a zero bias event, an event that is trigged by requiring only that two proton bunches cross at the CMS interaction point.
+Giving that the number of pixels in really big the probability that a pixel is being hit by two different tracks by the same bunch crossing is really small.
+The mean number of pixel clusters in a simulated zero bias event is in the order of 100 per pp collision.
+The number of pixel clusters per bunch crossing is linearly dependent on pileup and therefore an accurate measure of the instantaneous luminosity.
+The mean number of pixel cluster per trigger is \\
 
-$\sigma_{vis} = \frac{R_{det}}}{L_{b}} = \frac{2 \pi \Sigma_{x} \Sigma_{y} R(0,0)}{N_{1}N_{2}f}$  \cite{Lumvdm}
+$<N_{cluster}> = <N_{Pixel/Interaction}> <N_{interaction}> = <N_{Pixel/interaction}> \mu$ \\
+
+here the $\mu$ is the number of interactions and with this the following equation gives us
+
+Only the modules of the pixel subdetector that are stable during the entire period of the data taking are used for the PCC measurements, excluding the pixels that are known to be defective or affected by the limited size of the readout buffer.
+
+\section{Pixel Detector Module Selection}
+
+For the selection of modules

### 2025-04-23 monograph_Luis/Chapter2/chapter2.tex
update
updated

@@
-\chapter{Experiment Description}
+\chapter{Experiment Description and PCC method}
+
+ General-purpose detectors used in high-energy colliders have cylindrical detection layers that are arranged around the beam axis.
+The Compact Muon Solenoid (CMS), which is one of the largest international scientific collaborations in history and is part of the LHC at CERN, is an example of such a detector.
+The CMS detector is designed to carry out a wide range of experiments that include studying the Standard Model.
+This chapter provides a description of the various components of the CMS detector, including the several systems to measure the luminosity with a particular focus on the silicon pixel tracker, which is described in greater detail due to its relevance to this work.
 
 \section{The Compact Muon Solenoid}
+
+The CMS experiment is a general purpose detector and is part of the LHC's four detectors.
+This detector is built around a massive cylindrical solenoid magnet, which is made of superconducting cable that produces a powerful magnetic field of 4 tesla.
+This magnetic field is utilized to distinguish the energy deposits of charged and neutral particles in jets within the calorimeter.
+The magnet's field is confined by a steel "yoke," which comprises most of the detector's mass, totaling 14,000 tonnes.
+The CMS detector itself has dimensions of 21.6 meters in length and 14.6 meters in diameter \cite{CMS_Exp_2008}.\\
+
+The CMS detector comprises various detection layers that include separate parts of the detector, these layers are the fine-grained silicon tracker, which provides efficient and precise reconstruction of charged-particle trajectory.
+The highly-segmented electromagnetic calorimeter (ECAL) wish principal purpose is the detection of  electromagnetic energy and the identification of electrons and photons.
+The hadronic calorimeter (HCAL) wish principal purpose is the detection of hadrons in jets  \cite{CMS_Exp_2008}.
+Additionally, there is an excellent muon tracking system.
+A schematic representation of the CMS detector is shown in Fig.
+\ref{detector_CMS}.
+
+\begin{center}
+  \begin{figure}[ht]
+    \centering
+    \includegraphics[scale=.3]{Chapter2/CMS_detector_simple.png}
+    \caption[Panoramic view of the CMS detector]{Panoramic view of the CMS detector.}
+    \label{detector_CMS}
+  \end{figure}
+\end{center}
+
+To achieve high precision identification of the paths of deflected charged particles, the CMS employs a silicon tracker as its most inner detector to the beam pipe.
+This tracker system utilizes silicon strips and pixels that are divided into several layers in order to register the tracks of these particles.
+When a charged particle moves through one of the Tracker layers, it creates an interaction with the silicon material, producing a hit.
+By combining all the hits created by the particle, we can trace its trajectory, or track \cite{CMS_Exp_2008}.
+Further details about the tracker system can be found in the next section.\\
+
+ECAL is a detector that measures the energy of electrons and photons by absorbing them completely.
+It is a hermetic, homogeneous calorimeter consisting of 61,200 lead tungstate (PbWO4) crystals mounted in the central barrel part and closed by 7,324 crystals in each of the two endcaps.
+The preshower detector is placed in front of the endcap crystals.
+The photodetectors used in the barrel are avalanche photodiodes (APDs), while vacuum phototriodes (VPTs) are used in the endcaps.\\
+
+The HCAL surrounds the ECAL and together they complete a hermetic calorimetry system designed to measure jets and missing transverse energy.
+When hadrons, which are composite particles consisting of quarks and gluons, travel through the ECAL, they are stopped by the HCAL, to achieve  this, the HCAL is divided into four parts: the hadron forward (HF),  hadron endcap (HE), the hadron barrel (HB) and the hadron outer (HO) \cite{det_summary}.\\
+
+The final particle that the CMS directly observes is the muon, these are about 200 times heavier than electrons and cannot be stopped by the calorimeters.
+To detect muons, special sub-detectors are built, which are integrated with the return yoke of the solenoid.
+The magnet's size enables us to measure the momentum of each muon both inside the superconducting coil by using the tracking devices and outside it with the help of the muon chambers \cite{det_summary}.
+
+A transverse slice of the CMS detector, depicting specific particle interactions, is shown in Figure \ref{slice_CMS}.
+
+\begin{center}
+  \begin{figure}[ht]
+    \centering
+    \includegraphics[scale=.3]{Chapter2/slice_det.png}
+    \caption[Transverse slice view of the CMS detector]{Transverse slice of the CMS detector with some particle interactions (from the beam interaction region to the muon detector) \cite{det_summary}.}
+    \label{slice_CMS}
+  \end{figure}
+\end{center}
+
+The coordinate system used by the CMS is centered on the detector and has its origin at this point.
+The $y$-axis is oriented vertically upwards while the $x$-axis is directed radially inward, toward the center of the LHC.
+The z-axis aligns with the direction of the beam.
+Within this coordinate system, the azimuthal angle $\varphi$ is measured from the $x$-axis within the $x-y$ plane.
+The radial coordinate in this plane is represented by $r$.
+The polar angle $\theta$ is measured with respect to the z-axis.
+Seudorapidity $\eta$ is defined as $\eta = − ln[tan(\theta/2)]$ \cite{CMS_Exp_2008}.
 
@@
 
-\section{CMS Tracking System}
+A total of seven systems are used for measuring luminosity at CMS.
+The Pixel Luminosity Telescope (PLT) and Fast Beam Conditions Monitor (BCM1F) are dedicated systems for luminosity measurement, while the hadronic forward calorimeter (HF) uses a dedicated readout on an existing system.
+Additionally, three other methods, the drift tube luminosity (DT), the pixel cluster counting method (PCC), and the vertex counting method (VTX), use data from existing parts of the CMS detector to perform a luminosity measurement using the main CMS DAQ system.
+The PCC measurement uses the data collected with the standard CMS trigger system with triggers requiring colliding bunches but not any specific event activity, known as "zero-bias" triggers.
+Finally, the RAMSES detectors are part of the LHC environmental protection and monitoring systems, but they can also be used to provide a luminosity measurement readout through Timber (operational data and LHC logging service) \cite{pas_18}.
+A brief overview of the CMS luminometers is provided below.\\
 
-\section{Silicon Pixel Detector}
+PLT is a system designed to measure luminosity, using silicon pixel sensors.
+It consists of a total of 48 sensors, which are arranged into 16 "telescopes" placed at both ends of the CMS, outside the pixel endcap.
+Each telescope comprises three sensor planes, which are nearly parallel to the beam pipe.
+The PLT system measures the rate of "triple coincidences," where a hit is detected in all three planes.
+These coincidences typically correspond to tracks from particles originating at the interaction point.
+To estimate the overall mean rates for PLT, the zero-counting method is used.
+This method assumes that the number of observed triple coincidences follow a Poisson distribution \cite{pas_18}.\\
+
+In Run 2, BCM1F was equipped with a total of 24 sensors mounted on the same carriages as PLT.
+This system included 10 silicon sensors, 10 polycrystalline diamond sensors, and 4 single-crystal diamond sensors.
+The BCM1F readout has a fast readout time with a 6.25 ns time resolution.
+The combination of precise time measurement and the location of BCM1F at 1.8 m from the center of CMS allows for the separation of hits resulting from collision products and those resulting from the machine-induced background.
+This is because the incoming background is separated in time from the outgoing collision products \cite{pas_18}.\\
+
+HF luminosity measurement uses a dedicated readout system installed in the HF calorimeter readout electronics.
+Only two HF rings are used for luminosity measurement to ensure relatively uniform occupancy.
+Two algorithms are available: the first relies on the fraction of occupied towers (HFOC), and the second is based on the sum of the transverse energy ET (HFET)  \cite{pas_18}.\\
+
+The DT luminosity measurement technique relies on the rate of muon track stubs in the muon barrel track finder.
+However, it is important to note that the DT algorithm used does not provide bunch-by-bunch measurements.
+Therefore, this technique can only be used for total luminosity measurements.
+DT measurement is generally  stable and linear so it provides a complementary offline reference measurement.
+The rate in DT during vdM fills is too low to allow for calibration using the vdM scan, so it is cross-calibrated to another detector \cite{pas_18}.\\
+
+RAMSES  is a CERN radiation and environmental monitoring system.
+Although is not designed as a luminometer, the rate observed in this detector does function quite well as a luminosity measurement.
+The sensor itself is a cylindrical plastic ionization chamber filled with 3 L of air at atmospheric pressure and it primarily detects photons.
+The overall rate is small, which means that it is not capable of making bunch by bunch measurements and cannot be independently calibrated using a vdM scan; however, this also means it is less affected by issues such as instability caused by radiation damage or nonlinearity \cite{pas_18}.\\
+
+The PCC method uses the rate of pixel clusters in the CMS pixel detector to provide a luminosity measurement this method will be described in more detail in chapter 3.
+
+The location of the 7 luminometers in the CMS experiment are shown in Figure \ref{luminometers}.
+
+\begin{center}
+  \begin{figure}[ht]
+    \centering
+    \includegraphics[scale=.3]{Chapter2/detectors.png}
+    \caption[Layout of the luminometers in the CMS detector]{The seven luminometers that make up the CMS luminosity measurement system.
+Multiple independent systems used online: BCM1F, HFET, HFOC, PLT (independently calibrated) ,REMUS and  DT (cross-calibrated) , Pixel cluster counting is used after offline processing.}
+    \label{luminometers}
+  \end{figure}
+\end{center}
+
+\section{CMS Tracking System and Pixel Detector}
+
+The tracking system plays a crucial role in precisely measuring the trajectories and momenta of charged particles generated by collisions in the LHC, as well as reconstructing secondary vertices.
+It has a total physical size of 5.8 m in length and 2.5 m in diameter.
+The CMS tracking detector relies on semiconductor technology, this is divided in two systems, the pixel detector and the Strip tracker \cite{CMS_Exp_2008}.
+In Figure \ref{strip_layout}, we can observe the pixel detector at the center, surrounded by the Strip tracker.\\
+
+The Strip tracker is comprised of two subsystems: the first being the Tracker Inner Barrel (TIB) and Disks (TID), which are further divided into four barrel layers and three disks at each endcap.
+The second subsystem is the Tracker Outer Barrel (TOB), which consists of six barrel layers and the Tracker EndCaps (TEC) comprising of nine disks.
+The Strip tracker in total comprises of 15148 silicon modules, covering an active area of about 198$\text{m}^{2}$, and consists of 9.3 million strips \cite{CMS_Exp_2008}.
+\\
+
+The innermost part of the tracking system is made up of the silicon pixel tracker, which consists of four concentric barrel layers (BPIX) and three disks on each endcap (FPIX).
+This component comprises a total of 124 million pixels and extends the tracker's acceptance up to a pseudorapidity of $|\eta| < 2.5$.
+More information about this detector is provided in the following section.
+
+\begin{center}
+  \begin{figure}[ht]
+    \centering
+    \includegraphics[scale=.23]{Chapter2/strip_layout.png}
+    \caption[Schematic cross section through the CMS tracker]{Schematic cross section through the CMS tracker \cite{CMS_Exp_2008}.}
+    \label{strip_layout}
+  \end{figure}
+\end{center}
+
+The silicon pixel detector  forms the innermost component of the tracking system.
+This detector facilitates the provides complete spatial coverage over the area nearest to the interaction point, which, in turn, enables precise tracking of charged particles and vertex reconstruction.
+The coverage of the pixel detector is in the pseudorapidity range $(|\eta| < 2.5)$, operating in a radiation rich environment, marked by high track density \cite{phase1_Pixel_Detector}.\\
+
+The CMS pixel detector is composed of four concentric barrel layers (L1-L4), each having radii of 29, 68, 109, and 160 mm, and three disks (D1-D3) on each end placed at distances of 291, 396, and 516 mm from the center of the detector.
+The entire detector is comprised of 1856 segmented silicon sensor modules.\\
+
+A schematic of the CMS Phase-1 pixel detector's arrangement is depicted in Figure \ref{phase1_pixel_detector} where the total silicon area spans 1.9 $\text{m}^{2}$, here The BPIX and FPIX detectors are equipped with four service half-cylinders each, with a combined length of 540 mm.
+These cylinders host the readout and control circuits, and provide guidance for the power lines and cooling tubes of the detector.
+
+\begin{center}
+  \begin{figure}[h]
+    \centering
+    \includegraphics[scale=.26]{Chapter2/phase1_PixelDetector.png}
+    \caption[CMS Phase-1 pixel detector]{Layout of the CMS Phase-1 pixel detector in longitudinal view\cite{phase1_Pixel_Detector}.}
+    \label{phase1_pixel_detector}
+  \end{figure}
+\end{center}
+
+The BPIX detector is divided into two independent halves that are self-sufficient mechanically.
+Each half comprises of a half detector and two service half-cylinders.
+The BPIX detector is made up of 1184 segmented silicon sensor modules where the orientation of the surface of each module is parallel to the magnetic field, in both halves.\\
+
+In contrast to the BPIX detector, the FPIX detector is split into four quadrants, which are mechanically independent from each other.
+Each quadrant is composed of three half-disks that are contained within a service half-cylinder.
+The sensor orientation is such that the longer side of the pixel is aligned radially.
+The FPIX detector contains a total of 672 segmented silicon sensor modules that are subdivided into inner and outer half-rings, supporting 22 and 34 modules, respectively  \cite{phase1_Pixel_Detector}.\\
+
+A pixel detector module is composed of a flat silicon sensor with a dimension of 18.6 $\times$ 66.6 $\text{mm}^{2}$, which contains an active area of 116.2 $\times$ 64.8 $\text{mm}^{2}$.
+The sensor is comprised of 160$\times$416 pixels that are bump-bonded to an array of 2 by 8 readout chips (ROC's).
+Each ROC contains 4160 readout channels, responsible for measuring the pulse height of each pixel.
+In total, the detector has 124 million readout channels.
+The standard pixel size is 100$\times$150 $\mu m^{2}$.
+
+\begin{center}
+  \begin{figure}[h]
+    \centering
+    \includegraphics[scale=.2]{Chapter2/modules_drawing.png}
+    \caption[Types of modules in the pixel detector]{ These are illustrations of the pixel detector modules used in the BPIX L1 (left), BPIX L2-L4 (middle), and FPIX (right) detectors \cite{phase1_Pixel_Detector}.}
+    \label{modules_drawing}
+  \end{figure}
+\end{center}
+
+Figure \ref{modules_drawing} illustrates the modules of the CMS Phase-1 pixel detector \cite{phase1_Pixel_Detector}, while Figure \ref{module and hit} on the left depicts the layout of the silicon sensor connected to the readout chip.
+On the right side of Figure \ref{module and hit}, a charged particle can be seen passing through a pixel, providing enough energy to eject electrons from the silicon atoms.
+A voltage applied to the sensor allows the collection of these charges as a small electric signal, which is then amplified by an electronic readout chip.
+
+\begin{center}
+  \begin{figure}[h]
+    \centering
+    \includegraphics[scale=.3]{Chapter2/PixelSensor.png} \includegraphics[scale=.3]{Chapter2/hit.png}
+    \caption[Schematic view of a pixel sensor and its connection to the readout channels]{ left: layout pixel sensor connected to a readout chip , right: hits detection in a corresponding  pixel sensor \citep{thomson_2013}.
+}
+    \label{module and hit}
+  \end{figure}
+\end{center}
 
 \section{Pixel Cluster Reconstruction}
+
+The track reconstruction process involves several steps.
+Firstly, the signals above a specific threshold in the pixel channels are identified and utilized to create clusters.
+Each cluster represents the charge deposited by a single charged particle.
+Subsequently, the position and uncertainties of the clusters are estimated in a coordinate system that is local and orthogonal, with respect to the sensor plane \cite{Track_Reco_2014}.\\
+
+To be considered a valid cluster, each one should have a charge of at least 4000 electrons \cite{Track_Reco_2014,phase1_Pixel_Detector}.
+The minimum-ionizing particles (MIPs) passing through a silicon sensor with a 285 $\mu \text{m}$ thickness typically deposit an energy equivalent to about 21,000 electrons when they are normally incident.
+However, this charge is often spread over more than one pixel due to Lorentz drift,  which causes the electrons to be pushed due to the force generated by the electromagnetic field, leading to charge clusters.\\
+
+Figure \ref{cluster}  shows an example of how a pixel cluster is constructed.
+Each square in the figure represents a pixel.
+The red pixels indicate that they have the required charge up to 2000 electrons to be considered valid pixels and are therefore included in the cluster.
+On the other hand, the green pixels correspond to charge depositions below the 2000 electron threshold and are not included in the cluster.
+The dotted blue line in the figure represents the trajectory of the particle traveling parallel to the x-z plane.
+As it travels, it activates pixels in its path precisely, as well as pixels that are deviated from its trajectory due to the Lorentz drift \cite{Pixel_Hit_Reconstruction}.\\
+
+\begin{center}
+  \begin{figure}[h]
+    \centering
+    \includegraphics[scale=.25]{Chapter2/pixel_cluster.png} 
+    \caption[Construction of a pixel cluster]{ The figure illustrates a pixel cluster example with a total charge up of 4,000 electrons, required to be a valid cluster.
+The red pixels have the required charge while the green one does not.}
+    \label{cluster}
+  \end{figure}
+\end{center}
+
+\section{Pixel Cluster Counting method}
+\label{Pixel Cluster Counting method}
+
+The PCC method is an offline technique that provides a luminosity measurement using the rate of pixel clusters.
+Due to the large area of the pixel detector and the relatively low occupancy of its sensors, the probability of a single pixel being struck by two charged particles from the same bunch crossing is extremely low.
+This high granularity and low occupancy result in an excellent linear response to pile-up (\(\mu\), the number of interactions per bunch crossing) \cite{PCC_PAS_12_001}.
+On average, the detector occupancy (# hit pixels/# total pixels) is less than 0.1\% \cite{lumi_precise_2015_2016}.
+Although the statistical precision per Lumisection (23-second period) is lower than that of online luminometers due to CMS trigger bandwidth limitations, PCC still provides a linear measurement with good precision over time.
+When integrated over longer periods, it delivers a stable and highly precise luminosity measurement.
+
+Figure \ref{pileup} shows a simulation with pp collision zero-bias events with the pixel cluster counting rate as a function of pileup in the pileup range observed in Run 2 from 0 to about 50 $\mu$.
+Where the mean number of pixel clusters is of the order of  111 per event.
+The red curve is a first-order polynomial fit with slope, the results indicate a high level of agreement, as evidenced by the estimated goodness-of-fit $\chi^{2}$ per degree of freedom (dof) of approximately 0.5, showing that the PCC rate is highly linear in this range under simulated conditions \cite{ Phase2_Upgrade,lumi_precise_2015_2016}.
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+    \includegraphics[scale=.35]{Chapter3/pileup_lineality.png} 
+    \caption[PCC linearity with pile-up]{ Linearity of pixel cluster counting over the pileup range observed in Run 2 (from 0 to about 50) from simulation.
+The red line is a linear fit to the points \cite{Phase2_Upgrade} }
+    \label{pileup}
+  \end{figure}
+\end{center}
+
+For physics conditions, two data streams are recorded via the CMS DAQ: "zero-bias" and "random." The zero-bias stream consists of triggered data for colliding bunches at a bandwidth of approximately 1.5 kHz, while the random stream collects triggered data from all bunch crossings at a bandwidth of 500 Hz.
+The luminosity measurement is performed using the zero-bias data, whereas the random trigger helps evaluate background contributions.
+
+Under vdM conditions, a special trigger mode is employed to achieve higher data rates for PCC.
+This mode focuses on a selected set of five colliding bunch crossings, as detailed for each year in the next chapter, ensuring the necessary statistical precision.
+
+To derive the luminosity measurement from the PCC method, the mean number of pixel clusters per event is computed by averaging over several zero-bias events. This value is given by:
+
+\begin{equation}
+\left < N_{\text{cluster}} \right > \equiv \left < N_{\text{cluster}/\text{interaction}} \right > \mu
+\end{equation}
+
+Where the pile-up ($\mu$) is determined by the minimum-bias cross section:
+
+\begin{equation}
+\mu = \frac{\sigma_{\text{minBias}}}{f} \cdot \mathcal{L}_{inst}
+\end{equation}
+
+where $f$ is the LHC revolution frequency and $\mathcal{L}_{inst}$ is the single bunch instantaneous luminosity (SBIL).
+The minimum bias cross section $\sigma_{\text{minBias}}$ here is related to the PCC visible cross section by the mean number of clusters per interaction:
+
+\begin{equation}
+\sigma_{vis}= \left < N_{\text{cluster}/\text{interaction}} \right >\cdot \sigma_{\text{minBias}}
+\end{equation}
+
+Combining everything, the PCC luminosity measurement is obtained as:
+
+\begin{equation}
+\mathcal{L}_{inst}=\frac{\left < N_{\text{cluster}} \right> f}{\sigma_{vis}}
+\end{equation}
+
+In the PCC measurement, the innermost layer (Layer 0) of the pixel detector is excluded due to significant dynamic inefficiency effects, as at high instantaneous luminosities, the hit efficiency decreases because the readout chip cannot process all hits in time.
+For PCC rate measurements, only the pixel detector modules that remain stable throughout the entire data-taking period (year) are used.
+Modules known to be defective or significantly affected by the limited size of the readout buffer are excluded from the analysis.
+The final number of excluded modules, referred to as "veto modules," is detailed for each year in the next chapter.
+
+%This method is capable of providing a precise luminosity measurement over longer time periods, but it cannot do so for a single luminosity section (23 seconds) as is possible with online luminometers.
+The reason for this limitation is the limited CMS trigger bandwidth available for collecting data \cite{pas_18}.
+A detailed discussion on this topic can be found in the next chapter.\\
+
+%PCC si calcula lumi por cada lumi section.
+Esto no tiene que ver con online vs offline.
+PCC es un offline luminometro, quiere decir que los datos llegan tarde.
+Con PCC solo podemos calcular lumi cada lumi section, debido a la baja estadistica (por la lectura de los datos de zero bias).
+otros luminometros tienen precision con NB4 (HF, PLT, BCM1F).

### 2025-04-23 monograph_Luis/Chapter3/chapter3.tex
updated

--- 2025-03-07 monograph_Luis/Chapter3/chapter3.tex
@@
-\chapter{Luminosity  Measurement and Calibration}
+\chapter{Luminometer Calibration}
 \label{ch3}
 
-\section{2017 and 2018 CMS Data collected}
+Accurate measurement of the luminosity delivered to the CMS experiment by the LHC is essential for various reasons.
+Online, the luminosity measurement provides feedback on the performance of both the LHC and CMS during operations, including monitoring trigger rates.
+In offline analysis, it is a critical component for measuring the cross-section of observed processes \cite{pas_18}.
 
-\section{Module selection}
+The determination of \( \sigma_{\text{vis}} \) is performed using the van der Meer (vdM) method, which is carried out through a specialized scan program using a dedicated LHC machine setup.
+This chapter describes this procedure and the final calibration of the PCC luminometer.
 
-\section{Luminosity calibration: van der Meer method}
+\section{van der Meer (vdM) method}
+\label{vdM method}
+
+The instantaneous luminosity for a single colliding bunch pair at head-on, seperated by $(\Delta x, \Delta y)$ is described by:
+
+\begin{equation}
+\label{eq:lumidef}
+\mathcal{L} (\Delta x, \Delta y) = N_1 N_2 f\int_{-\infty}^{\infty}\rho_1(x,y)\rho_2(x+\Delta x,y+\Delta y) \,dx\,dy
+\end{equation}
+
+where $N_1$ and $N_2$ are the numbers of protons in the two colliding bunches, respectively, $f = 11245.6$ Hz is the revolution frequency of the LHC, and $\rho_i$ denotes the proton density distribution of the $i^{\text{th}}$ bunch.
+While the bunch populations can be measured with good precision, accurately determining the proton density profiles entering Equation~\ref{eq:lumidef} is more challenging.
+The van der Meer (vdM) scan method, used by LHC experiments, enables the measurement of the integral over the bunch proton densities appearing in Equation~\ref{eq:lumidef}.
+
+For the vdM method to be applicable, it is assumed that the proton density distributions of the two bunches factorize in the transverse directions $x$ and $y$:
+
+\begin{equation}
+\label{eq:fact}
+\int_{-\infty}^{\infty} \rho_1(x,y) \rho_2(x+\Delta x, y+\Delta y) \, dx \, dy = \int_{-\infty}^{\infty} \rho_1(x) \rho_2(x+\Delta x) \, dx  \times  \int_{-\infty}^{\infty} \rho_1(y) \rho_2(y+\Delta y) \, dy.
+\end{equation}
+
+Both sides of Equation~\ref{eq:lumidef} can then be integrated independently over $\Delta x$ and $\Delta y$, while keeping the other separation fixed. This yields:
+
+\begin{equation}
+\label{eq:evaldense}
+N_1 N_2 f \int_{-\infty}^{\infty} \rho_1(y)\rho_2(y+\Delta y_0) \,dy = \int_{-\infty}^{\infty} \mathcal{L}(\Delta x, \Delta y_0) \,d(\Delta x),
+\end{equation}
+
+and therefore,
+
+\begin{equation}
+\label{eq:evaldense2}
+\int_{-\infty}^{\infty} \rho_1(x)\rho_2(x+\Delta x_0) \,dx = \frac{\mathcal{L} (\Delta x_0, \Delta y_0)}{\int_{-\infty}^{\infty} \mathcal{L}(\Delta x, \Delta y_0) \,d(\Delta x)}.
+\end{equation}
+
+Likewise for $y$.
+Experimentally, the integration over $\Delta x$ and $\Delta y$ is implemented by scanning the two beams against each other, and the integral on the right-hand side of Equation~\ref{eq:evaldense} is evaluated by measuring the luminometer rate as a function of the beam-beam separation.
+Equation~\ref{eq:lumidef} then becomes, after replacing the beam overlap integrals in $x$ and $y$ according to Equation~\ref{eq:evaldense2}, for a particular head-on working point $(\Delta x_0, \Delta y_0)$:
+
+\begin{equation}
+\label{eq:lumidefVdM}
+\mathcal{L} (\Delta x_0, \Delta y_0) = N_1 N_2 f  \frac{R (\Delta x_0, \Delta y_0) R (\Delta x_0, \Delta y_0)}{\int_{-\infty}^{\infty} R (\Delta x, \Delta y_0) \,d(\Delta x) \int_{-\infty}^{\infty} R(\Delta x_0, \Delta y) \,d(\Delta y)},
+\end{equation}
+
+where the luminosity is replaced by the measurable rate $R(\Delta x, \Delta y)$ when  the two beams are seperated by ($\Delta x$,$\Delta y$).
+Since the Van der Meer procedure is a physical convolution of the two beams, it is common to re-write the beam overlap width $\Sigma_x$ (and similarly $\Sigma_y$) as:
+
+\begin{equation}
+\label{eq:capsigma}
+\Sigma_x = \frac{1}{\sqrt{2\pi}}\frac{\int_{-\infty}^{\infty} R_x{} (\Delta) d(\Delta)}{R_{x}(0)},
+\end{equation}
+
+giving
+
+\begin{equation}
+\label{eq:lumidefVdMcSig}
+\mathcal{L}_{inst} =\frac{N_1 N_2 f}{2\pi\Sigma_x \Sigma_y},
+\end{equation}
+
+such that the final formula used to measure the visible cross sections is
+
+\begin{equation}
+\label{eq:sigVisX}
+ \sigma_{vis}=\frac{2\pi\Sigma_x \Sigma_y R(0,0)}{N_1 N_2 f}.
+\end{equation}
+
+In practice, while all quantities on the right-hand side of Equation \ref{eq:sigVisX}, such as the beam currents $N_{1,2}$ and the orbit frequency $f$, are well determined, the overlap integrals $\Sigma_x$ and $\Sigma_y$ cannot be directly measured.
+Instead, they are extracted from fits to the scan curves obtained from the luminometer rate measurements during the vdM scans.
+The vdM method involves a specific machine setup (vdM program) that enables the determination of the beam overlap integrals.
+This is achieved by varying the transverse separation between the beams and recording the resulting interaction rates, which typically yield beam density profiles approximated by normal distributions.
+
+The measured rate, denoted by $R(\Delta x_0, \Delta y_0)$, is defined as the average value of the peak rates obtained during the $x$- and $y$-scans.
+Although the beam widths are identical for all luminometers, the peaks of the scan curves are specific to each luminometer.
+
+Figure \ref{vdm_sketch} depicts a schematic of the beam positions during vdM scans in the $x$ and $y$ planes, along with the detector rate as a function of beam separation  \cite{pas_18}.
+
+\begin{center}
+  \begin{figure}[h]
+    \centering
+    \includegraphics[scale=.40]{Chapter3/vdm_sketch.png}
+    \caption[Sketch of a vdM scan in $x$ and $y$ directions and example of fitting resulting rates]{ The sketch of a vdM scan in $x$ and $y$ planes.
+The indent sketch is an example of the fit of the resulting rates \cite{vdM_sketch}.}
+    \label{vdm_sketch}
+  \end{figure}
+\end{center}
+
+\section{vdM program and Scan types}
+\label{vdM program and Scan types}
+
+Each year, the vdM scan program for the CMS experiment is conducted during specific LHC fills using a dedicated setup.
+The LHC filling schemes are designed with a specific number of bunch pairs at the CMS interaction point (IP5), for the especific case of 2017 an 2018 was at a proton-proton collision energy of \(\sqrt{s} = 13\) TeV.
+These scans play a crucial role in the precise determination of the luminosity by measuring the transverse beam profiles and overlap integral.
+
+To minimize long-range beam-beam effects and detector background (afterglow), the bunches are arranged in a way that optimizes the measurement conditions.
+During these special fills, the beams are systematically displaced in the transverse plane, allowing for a detailed study of beam dynamics and interaction rates.
+Various types of scan pairs with different characteristics were conducted to refine the accuracy of the luminosity determination.
+
+Each scan pair consisted of two scans in the transverse \(x\) and \(y\) planes.
+These included standard vdM scans, emittance scans, beam imaging scans, offset scans, and length scale calibration scans, each serving a specific purpose in the calibracion and luminosity measurement process.
+A detailed description of each scan is provided below.
+
+\noindent \textbf{Standard vdM}: used specifically to compute $\sigma_{vis}$, in this scan the two beams are separated by $6\sigma_{b} \thickapprox 578\mu m$, where $\sigma_{b}$ represents the transverse bunch size.
+and scanned across each other in a se quence of 25 steps with 30 seconds per step with a step size of $0.5\sigma_{b} \thickapprox 48 \mu m$ in either the horizontal (x) or vertical (y) direction.\\
+
+\noindent \textbf{Emittance}: same procedure as the standard vdM scans except the maximum separation (2.5 − $4 \sigma_{b}$), the number of steps (7 or 9) and the time per step (10 seconds) are smaller, so that the scan takes a shorter time.
+These type of scans are also performed in physics conditions as discussed in Section.\\
+
+\noindent \textbf{Beam imaging}: in these scans, one beam (beam 1 and beam 2, respectively) is kept fixed at its nominal head-on position, while the other beam is separated and scanned in 19 steps, each step lasts 46 seconds and covers a range from $-4.5\sigma_{b}$ to $+4.5\sigma_{b} \thickapprox 433 \mu m$.
+These scans were developed for studies on beam shapes, estimating the uncertainty caused by the correction called $x$-$y$ non-factorization described in the next chapter.
+BI scans are also analyzed as traditional vdM scans and used to compute of $\sigma_{vis}$.\\
+
+\noindent \textbf{Constant-Separation Length Scale}: during this scan the two beams are separated by $\sqrt{2} \sigma_{b} \thickapprox 106 \mu m$ (approximately equal to $1 \Sigma_{b}$) and moved together in steps of $1\sigma_{b}$ forward and backward in five steps each, for a total of 10 steps with 70 seconds per step.\\
+
+\noindent \textbf{Variable-Separation length scale}: one beam (starting with beam 1) is moved to $-2.5\sigma_{b}$ and then a three-point scan is performed with the other beam (starting with beam 2) at arelative position of $+-1.25\sigma_{b}$, 0, and $+1.25\sigma_{b}$.
+The position of the first beam is then stepped in five steps to $+2.5\sigma_{b}$, repeating the three-point scan (“miniscan”) at each step.
+This procedure is repeated four times, with two directions for each of the two beams.
+Each scan point has a duration of about 46 s.
+
+The two types of Length scale are pecial scan designed to apply a correction to the results of  $\sigma_{vis}$ obtained from the vdM scan program, this correction will be described further in this section.\\
+
+\noindent \textbf{Offset}: same procedure as the standard vdM scans except that the beams are separated by  range from $-3\sigma_{b}$ to $+3\sigma_{b}$ in the non-scanning direction.\\
+
+\noindent \textbf{Super Separation}: this type of scan is performed for background estimation.
+In this scan, the two beams are separated by a distance of \(6\sigma_{b}\) for 5 minutes.
+At this distance, the beam overlap is minimal, and the contribution from collisions is negligible.
+There can be more than one Super Separation scan per scan program, this is useful to understanding the behavior of the background throughout the year and for subtracting it accordingly.
+
+The data collected from these scans provide the essential input for luminosity calibration, which is critical for cross-section measurements and precision physics analyses at the LHC.
+
+\subsection{2017 vdM scan program}
+\label{2017 vdM scan program}
+
+The 2017 vdM scan program was performed during LHC fill 6016 on 28 July 2017, at a center-of-mass energy of 13 TeV.
+The LHC filling scheme included 32 colliding bunch pairs at the CMS interaction point (IP5).
+In the special case of PCC, to ensure a dataset with a high event count at large beam separations, CMS gated the zero-bias triggers on 5 bunch pairs (BCIDs 41, 281, 872, 1783, and 2063) and recorded events at a total rate of 18 kHz.
+
+The bunch intensities were approximately \(9 \times 10^{10}\) protons per filled bunch, resulting in a total beam intensity of approximately \(4.5 \times 10^{12}\) protons per beam.
+The total beam intensities were measured with the DC Current Transformers (DCCT) ~\citep{LHC_DCCT_calibration}.
+The beam orbit was monitored using two systems: the DOROS beam position monitors (BPMs) ~\citep{BPM__electronics}, located near IP5, and the arc BPMs, located in the LHC arcs adjacent to CMS.
+
+The vdM scan program consisted of a total of eight orthogonal (x-y) scan pairs.
+It started with a short emittance scan, em1.
+Four scans were standard vdM scans: vdM1 (2), vdM3 (6), and vdM4 (11).
+These scans were performed first in the x direction and then in the y direction.
+The intermediate scan, vdM2 (3), was performed first in the y direction and then in the x direction.
+This was done to check reproducibility.
+
+Two scan pairs of beam imaging scans were performed, with beam 1 and beam 2 scanning.
+Pairs Im1 and Im2 corresponded to scans 4 and 5, respectively.
+Scan pair 7 was an offset scan (off) performed just after vdM3, but it is not used in this analysis.
+
+A length scale calibration (LSC) program was performed at the end of the vdM program using two different LS methods.
+The first method was the constant-separation scan (cLS), performed as scan 8 in this program.
+This type of scan had been previously used in the 2015–2016 publication  ~\citep{lumi_precise_2015_2016} for the CMS length scale calibration.
+
+The second method consisted of variable-separation scans, vLS1 and vLS2, which were scans 9 and 10, respectively, in the LS program.
+This method was used for the first time in 2017, following the scan protocol originally developed by ATLAS.
+
+The top of Figure~\ref{BeamPosition_2017} shows the beam positions for the two beams in the x and y directions as measured by the DOROS BPMs during the 2017 scan program, showing the four regular scan pairs, the two beam imaging scan pairs, the offset scan pair, and the two length scale scan programs, with the abbreviations used for the scans introduced.
+
+%\begin{center}
+  \begin{figure}[h]
+    \hspace{-.4cm}
+    %\centering
+    \includegraphics[scale=.17]{Chapter3/BeamPosition/doros_vs_time_6016.pdf}
+    \caption[Beam Position in vdM scan 2017]{ Vertical (V) and horizontal (H) beam positions as a function of time measured by the DOROS beam position monitors during LHC fill 6016.
+The orbit is averaged over the bunches and monitored throughout the scan program with 1 second time granularity.
+The individual scans are delimited by the vertical lines.
+Each scan pair consists of two scans orthogonal to each other and labelled with the abbreviation of the specific scan type}
+    \label{BeamPosition_2017}
+  \end{figure}
+%\end{center}
+
+\subsection{2018 vdM scan program}
+\label{2018 vdM scan program}
+
+The 2018 vdM scan program was conducted during LHC fill 6868 from June 30 to July 1, 2018, at a center-of-mass energy of 13 TeV.
+The LHC filling scheme included 124 colliding bunch pairs at the CMS interaction point (IP5).
+For the special case of PCC, to ensure a dataset with a high event count at large beam separations, CMS gated the zero-bias triggers on 5 bunch pairs (BCIDs 265, 865, 1780, 2192, and 3380) and recorded events at a total rate of 27 kHz.
+
+In this year the bunch intensities were approximately \(7-9 \times 10^{10}\) protons per filled bunch, resulting in a total beam intensity of approximately \(4.5 \times 10^{13}\) protons per beam.
+The beam intensities and the beam orbit were measured and monitored in the same way as in 2017.
+
+The vdM scan program was conducted in two parts due to an alarm and a power cut.
+The first part consisted of a total of five x-y scan pairs.First, two short emittance scans, em1 (1) and em2 (2), were conducted, respectively.
+Then, a standard vdM scan pair, vdM1 (3), was performed, followed by an offset scan, off1 (4).
+Finally, a pair of beam imaging scans, BI1 (5) and BI2 (6), were onducted, but only the first was completed before the alarm interrupted the program.
+
+The second part of the program was conducted approximately 7.5 hours later and consisted of 12 scan pairs.
+Scan pair em3 (6) was a short emittance scan, followed by beam imaging scan pairs Im3 (7) and Im4 (8), then an offset scan pair, off2 (9), and finally two standard vdM scan pairs, vdM2 (10) and vdM3 (11).
+The latter two allowed us to test the reproducibility of the measurement.
+
+A length scale calibration program was performed after vdM3 using constant-separation and variable-separation scan pairs: cLS (12), vLS1 (13), and vLS2 (14).
+Finally, a standard vdM scan pair, vdM4 (15), and two short emittance scan pairs, em4 (16) and em5 (17), concluded the program.
+
+In each scan pair, the scan was performed first in the x direction and then in the y direction, with the exception of the variable vLS calibration scan pairs, which were performed in the opposite order.
+
+Additionally, two Super Separation periods were conducted.
+The first, SS1, took place right after vdM3 was completed, and the second, SS2, followed vdM4.
+These periods are not included in the final count of scan pairs since they only involve separating the beams in a single direction.
+They are used for the final estimation of background noise, which will be subtracted in the final analysis.
+The details of these periods will be discussed in the following chapter.
+
+The bottom of Figure~\ref{BeamPosition_2018} shows the beam positions for the two beams in the x and y directions as measured by the DOROS BPMs during the 2018 scan program, showing the 17 scan pairs.4 regular scan pairs, the 3 beam imaging scan pairs, the 2 offset scan pair, and the 3 length scales, the emitance scan a the 2 Superseparation periods with the corrsponding abbreviations used.
+
+%[15] M. Gasior, J. Olexa, and R. Steinhagen, “BPM electronics based on compensated diode detectors — results from development systems”, Conf. Proc. C1204151 (2012) 44.
+%[7] C. Barschel et al., “Results of the LHC DCCT calibration studies”, Technical Report 2349 CERN-ATS-Note-2012-026 PERF, 2012.
+
+%\begin{center}
+  \begin{figure}[h]
+  \hspace{-0.4cm}
+    %\centering
+    \includegraphics[scale=.17]{Chapter3/BeamPosition/doros_vs_time_6868.pdf}
+    \caption[Beam Position in vdM scan 2017]{Vertical (V) and horizontal (H) beam positions as a function of time measured by the DOROS beam position monitors during LHC fill 6868.
+The orbit is averaged over the bunches and monitored throughout the scan program with 1 second time granularity.
+The individual scans are delimited by the vertical lines.
+Each scan pair consists of two scans orthogonal to each other and labelled with the abbreviation of the specific scan type.}
+    \label{BeamPosition_2018}
+  \end{figure}
+%\end{center}
+
+\section{Data acquisition and processing}
+\label{data}
+
+As specified in the vdM program, achieving high statistical precision for each colliding bunch pair is constrained by system trigger bandwidth limitations, which prevent the use of all bunches.
+To address this, CMS implemented zero-bias triggers (defined in Section \ref{Luminometers}) on only five Bunch Crossing IDs (BCIDs): 41, 281, 872, 1783, and 2063 for 2017, and 265, 865, 1780, 2192, and 3380 for 2018.\\
+
+The data is recorded randomly at the highest possible rate of 18 kHz for 2017 and 27 kHz  for 2018, using the High-Level Trigger (HLT) through the CMS Data Acquisition (DAQ) system.
+Due to the weight of the events, eight different streams per year are required to store the full dataset.
+These datasets are saved in CMS RAW format, containing event-by-event and bunch-by-bunch information, including the amount of charge deposited in each pixel.\\
+
+The data is then reprocessed by the CMS collaboration to enable cluster reconstruction, resulting in datasets (ALCARECO version) that contain a collection of modules and their number of clusters per event.
+The data is in CMSSW format.
+These datasets will serve as the starting point for our own data reprocessing and analysis.\\
+
+The ALCARECO samples are processed using CMSSW software to extract clusters per module.
+Due to the large size of the datasets, all the datasets were sent for reprocessing through The Worldwide LHC Computing Grid (WLCG).
+During this process, the required cluster counts were obtained and saved in a dataset with ROOT format (a data analysis framework used in high-energy physics) \cite{ROOT}.
+This format uses TTrees and TBranches, which are containers that organize and store information hierarchically.
+The data is stored per event and includes details such as the number of pixel clusters, the BCID, module identifiers, the run number, the number of lumisections (LS = 23 s), the number of luminible (LN = 0.32 s), and the time at which the event occurred.
+\\
+
+The vdM framework (vdMFW), developed by the collaboration for the vdM calibration analysis and the extraction of \( \sigma_{\text{vis}} \), has limitations in its performance.
+As a result, in previous analisys, not all available statistics were used for PCC detector.
+To improve this and maintain full statistical precision, rates were stored every 1.32 seconds (NB4), which corresponds to 4 LN.
+This was achieved by averaging the clusters and the number of events that fall within this time span.
+During this process, bad modules were removed from the analysis (a detailed discussion of the module veto criteria appears in the following chapter).
+In this phase, the information is merged into a single file using a hierarchical data format (HDF5) \cite{HD5}, which organizes the data into tables.
+This final format constitutes a requirement for the vdMFW.
+The entire processing chain was executed on LxBatch, CERN's computing cluster infrastructure.\\
+
+Finally, the HDF5 file containing the rates collected during the vdM scans is analyzed using the vdMFW.
+The vdMFW extracts the necessary information using its analysis tools, while subtracting the background and applying several corrections to the measured rates (described in sections \ref{bkg} and \ref{bbcorrections}).
+During the processing, the vdMFW generates the final information and plots, which contain the normalized rates ($R/N_{1}N_{2}$) and beam position.
+A fit is then performed on the data points of the scan to extract $\Sigma_{x,y}$ and peak values, which are used to compute $\sigma_{\text{vis}}$ for all the bunches in the scan.
+
+\section{Background estimation}
+\label{bkg}
+
+To perform accurate fitting of the data, it is necessary to take into account the following background contributions to the PCC rates.
+These contributions are estimated independently during the Super Separation (SS) periods discussed in the previous section.
+Three primary sources of beam-induced background should be considered:
+
+\begin{itemize}
+
+\item Beam Halo (BH): This component occurs when the secondary particles reach the experimental cavern from the LHC tunnel.
+The primary beam halo is  the population of beam protons characterized by offsets in the transverse coordinates, travelling in  radial amplitude around the beam axis and being captured mostly by the LHC collimation system.
+In every step of the multi-stage cleaning system of the LHC, more halo particles are captured but also secondary showers are created by the interaction of the beam particles with the collimator material.
+The largest contribution of the  beam halo to the background consist of secondary particles  that stem from the interactions of the beam halo particles at the tertiary collimators and arrive in large radius into the CMS cavern \cite{beam_halo}.
+
+\item  Beam Gas Inelastic (BGI): This component arises from all inelastic interactions between primary beam protons and residual gas in the beam pipe.
+The interaction rate is largely influenced by the quality of the vacuum in the various beam line elements upstream of CMS, so the source of this contribution is distributed throughout the long straight section \cite{bkg_source}.
+
+\item Beam Gas Elastic (BGE): The elastic beam gas contribution is made up of all the coherent and quasi-elastic, nuclear elastic, and Coulomb scattering for multi-turn beam-gas interactions around the ring.
+\cite{bkg_source}.
+
+\end{itemize}
+
+As mentioned in the previous chapter, the background analysis requires a special scan known as the Super Separation Period.
+However, for the 2017 vdM calibration program, no Super Separation Period was conducted, and therefore, no data was obtained for the standard analysis.
+Therefore, a different strategy was implemented: a detailed analysis of the PCC rate tails from the vdM scans.
+This approach examines PCC rates at the most separated beam positions (i.e., the last points in the tails) to evaluate background levels for each BCID over time.
+While the standard method averages values across different BCIDs, significant variations were observed among them.
+Consequently, a different background value was assigned to each BCID used in this year (41, 281, 872, 1783 and 2063).
+Fig.~\ref{fig:SS_rates} shows the study in which the tail rates were extracted for the four standard vdM scans conducted in 2017.
+The average rate for each BCID is taken as the measured background to be subtracted, while the standard deviation of these values is used as the error.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.44\textwidth,height=0.27\textwidth]{Chapter4/scan_rates.png}
+    \includegraphics[width=0.5\textwidth,height=0.30\textwidth]{Chapter4/scan_rates_PerBX.png}
+    \caption[Background Per BCID (2017)]{Left: Example of the average rates in a vdM scan for a single BCID.
+The tail values used in the study are highlighted with red circles.
+Right: Tail values from the scans and the mean background values per BCID.}
+    \label{fig:SS_rates}
+\end{figure}
+
+For the 2018 vdM program, two Super-Separation scans (SS1 and SS2) were conducted to estimate the background value and its corresponding statistical error (SEM).
+The mean and standard deviation are obtained from the distribution resulting from the Y-projection of the $<\text{PCC}>$ rates during the period.
+This is done for each of the five BCIDs (265, 865, 1780, 2190, and 3380) selected for data acquisition that year.
+The process is performed individually for each SS period.
+Since the background noise values are consistent across different BCIDs, the final background value is determined by first averaging the five BCIDs within each SS period and then averaging the final values from both Super-Separation periods.
+
+An example of an SS period I for BCID 265 and the calculation of the background level is shown in Fig.~\ref{fig:bx_265}.
+The left plot displays $<\text{PCC}>$, which represents the average number of pixel clusters per event over a period of 1.32s (NB4).
+The lower regions of the plot correspond to a 5-minute time window during which the beams were separated by a distance of $6\sigma_{b}$.
+The right plot shows the Y-projection of this distribution during the SS period, from which the mean and error are obtained.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.44\textwidth,height=0.30\textwidth]{figures/performance_PCC/PCC_Rates_SS1.pdf}
+    \includegraphics[width=0.54\textwidth,height=0.30\textwidth]{figures/performance_PCC/PCC_Projection_SS1.pdf}
+    \caption[Background in BCID 265 during SS1 (2018)]{Left: PCC raw rates in Super Separation Period I in fill 6868 (2018) for BCID 265. 
+    Right:PCC distribution corresponding to the Super Separation Period I for BCID 265.}
+    \label{fig:bx_265}
+\end{figure}
+
+Finally, the background values for the five different BCIDs in 2017 and 2018 are shown in Table~\ref{tab:vdm_bkg}.
+In 2017, each BCID was corrected individually.
+For 2018, the final background correction applied to the PCC rate is $0.02757 \pm 0.01987$, obtained by averaging the BCIDs and SS periods.
+
+\begin{table}[h]
+    \caption{PCC background estimated for 2017 and 2018 vdM data.}
+    \label{tab:vdm_bkg}
+    \centering
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \textbf{2017 Fill 6016} \\ 
+        \begin{tabular}{cc}
+            BCID & Bkg. \\ \hline
+            41   & 0.463 \\
+            281  & 0.466 \\
+            872  & 0.434 \\
+            1783 & 0.382 \\
+            2063 & 0.385 \\
+        \end{tabular}
+    \end{minipage}
+    %\hfill
+     \hspace{1mm}
+    \begin{minipage}{0.45\textwidth}
+        \centering
+        \textbf{2018 Fill 6868} \\ 
+        \begin{tabular}{ccc}
+            BCID  & Bkg. (SS1) & Bkg. (SS2) \\ \hline
+            265   & 0.02902    & 0.02743    \\
+            865   & 0.02572    & 0.02810    \\
+            1780  & 0.02862    & 0.02860    \\
+            2192  & 0.02729    & 0.02323    \\
+            3380  & 0.02882    & 0.02896    \\
+        \end{tabular}
+    \end{minipage}
+\end{table}
+
+\section{Beam Corrections}
+\label{bbcorrections}
+%https://cms.cern.ch/iCMS/analysisadmin/cadilines?line=LUM-22-001
+
+There are several systematic effects that affect the measurement of beam overlap width and therefore the extraction of $\sigma_{vis}$ from the vdM scan procedure.
+These effects are measured and, where applicable, corrected as described below.
+A systematic uncertainty is assigned to the resulting measured cross section $\sigma_{vis}$, and the following corrections are applied in the vdM Framework:
+
+\begin{enumerate}
+
+\item \textbf{Ghost and Satellites correction}.
+This correction addresses spurious charges in the machine that affect bunch currents.
+Satellite charges refer to additional charges beyond the 2.5 ns RF window containing the colliding bunch.
+Ghost charges correspond to charges beyond the 25 ns time window of nominally filled bunch slots.
+
+The Longitudinal Density Monitors (LDMs) \cite{ghost_charge} measure these charges, and their correction follows the procedure described in Ref.
+\cite{lumi_precise_2015_2016}.
+If left uncorrected, they would bias the bunch population measurement and affect the determination of $\sigma_{\mathrm{vis}}$.
+
+The correction to $\sigma_{\mathrm{vis}}$ is 0.02$\pm$0.05\% in 2017 and 0.09$\pm$0.03\% in 2018.
+Systematic uncertainties of 0.06\% and 0.07\% are assigned for 2017 and 2018, respectively.
+These uncertainties, attributed to instrumental effects, are considered correlated across both years.
+
+\item \textbf{Bunch Current correction}.
+The LHC beam intensities, defined as the number of protons per bunch, are estimated from the bunch currents measured by the Fast Bunch Current Transformers (FBCT).
+These devices can resolve the particle multiplicity of individual bunches, denoted as $N_{\mathrm{FBCT}}^j$ \cite{LHC_bunch_populations}.
+A precise measurement of the total beam current, obtained by summing the individual bunch currents, is provided by the Direct Current Current Transformers (DCCTs).
+The total current, denoted as $N_{\mathrm{DCCT}$, is normalized to match the measured values with a relative precision of 0.2\%.
+This precision is directly assigned as a systematic uncertainty \cite{DCCT_calibration_studies}.
+
+\item \textbf{Beam Beam corrections}. The electromagnetic interaction between colliding proton bunches affects beam-separation scans in two ways:
+
+\textbf{Beam-Beam Deflection}.
+This correction accounts for the deflection of proton bunches during collisions, which causes a coherent shift in the nominal orbit.
+The electrical repulsion between the beams increases their lateral separation.
+This deflection is calculated and added to the nominal separation.
+
+\textbf{Dynamic Beta}.
+The dynamic $\beta^{}$ effect, also known as the incoherent effect, accounts for changes in proton density distributions within the bunches due to single-particle interactions.
+These interactions alter the transverse bunch profiles during separation steps, which can be described as an effective change in the $\beta^{}$ value.
+
+The corrections are calculated and applied individually for each bunch in each vdM scan.
+The average beam-beam interaction correction to $\sigma_{\mathrm{vis}}$ is 0.36\% for both years.
+The total uncertainties are 0.29\% in 2017 and 0.30\% in 2018, and they are considered fully correlated between the two years.
+
+\item \textbf{Orbit drift correction}.
+This correction accounts for potential LHC orbit movements, including stochastic jumps and jitters (random changes in beam positions) during vdM scans.
+Time-dependent variations in transverse beam positions, even with fixed machine parameters, can alter beam separation.
+These changes are measured using beam position monitor (BPM) systems.
+The correction consists of two independent components:
+
+\textbf{Linear Orbit drift}.
+This correction is divided into two components: Orbit Drift Separation (ODS), which accounts for orbit drift in the scanning direction and affects only beam separation, and Orbit Drift Rate (ODR), which corrects for orbit drift in the direction orthogonal to the scan, impacting only the luminometer rate.
+These effects result in a 0.13\% change in $\sigma_{\mathrm{vis}}$ in 2017 and 0.05\% in 2018.
+
+\textbf{Residual orbit drift corrections}: accounts for beam position shifts not captured by linear orbit drift, length scale differences, or beam-beam deflection effects.
+A smooth function models the time-dependent drift, incorporating parameters to correct BPM scaling, beam-beam interaction magnitude and coordinate misalignments .The model is fitted using both scanning and non-scanning BPM data to ensure consistency.
+
+The final correction to the visible cross section including residual and linear orbit drift is 0.20\% in 2017 and 0.13\% in 2018, with uncertainties of 0.09\% and 0.19\%, respectively, which are correlated across years.
+
+\item \textbf{Length Scale}.
+During beam separation scans, the beam positions are controlled by LHC dipole magnets, with separation determined by the magnet currents.
+To calibrate the absolute scale of these "nominal" positions, dedicated length scale calibration scans are conducted.
+These scans use a combination of methods: the constant-separation length scale scans, which track the movement of the luminous region (LR) through the mean reconstructed vertex position to calibrate the average length scale of the two beams in the transverse directions, and the variable-separation scans, which determine the LR position at the head-on configuration and compare it to the nominal beam position to compute the length scale.
+This approach measures the length scale of each beam separately in each direction.
+
+The procedure follows the method described in Ref.
+\cite{lumi_precise_2015_2016}.
+The correction to the visible cross section due to the length scale is -0.87 $\pm$ 0.12\% in 2017 and -0.66 $\pm$ 0.14\% in 2018.
+
+\item \textbf{Transverse factorization}.
+
+As mentioned in Section~\ref{vdM method}, the vdM method assumes that the bunch proton density is factorizable into independent $x$ and $y$ components, which can introduce a bias in the estimation of the beam overlap area.
+To evaluate and correct for this bias, dedicated beam imaging scans are used.
+Simulated vdM scan pairs are generated using the fitted transverse bunch density profiles, and the resulting luminous area ($2\pi\Sigma_{x}\Sigma_{y}$) is compared to the true beam overlap integral to quantify the factorization bias.
+This procedure, repeated multiple times, also accounts for statistical fluctuations and potential mismodeling associated with the chosen vdM fit function.
+To validate the modeling of the tails, luminous region fits are also performed using the scan combinations applied in the 2D rate-fit analysis.
+The average difference between the correction derived from the on-axis-only fit and that from the combined fit is added in quadrature to the uncertainty, yielding final uncertainties of 0.33\% and 0.36\% for 2017 and 2018, respectively.
+
+\end{enumerate}
+
+%https://indico.cern.ch/event/1244981/contributions/5230942/attachments/2581191/4452030/POG_pres.pdf
+%\item Residual beam positions.
+To investigate additional deviations of the beams, a fit model is created by combining the nominal beam positions, the orbit drift correction, and the beam-beam deflection.
+In order to accommodate the unknown response of the Beam Position Monitors (BPM) to the beam-beam deflection, the beam-beam deflection is scaled using a parameter that is allowed to freely vary \cite{lumi_precise_2015_2016}.
+Moreover, length scale factors are also included as freely floating parameters.
+
+%In general, the residual deviations are less than 2 $\mum$.
+The primary source of uncertainty here is from the scale of the beam-beam deflection.
+Varying the scale parameter within the range of values found by the fit results in a change of $\sigma_{vis}$ of up to 1.0\%.
+This value is assigned as an uncertainty.\\
+
+%\item Factorization bias.
+As we mentioned in section \ref{2022 vdM scan program} the vdM method assumes that the bunch proton density function is factorizable into dependent $x$ and $y$ distributions and this can lead to a biased estimate of the beam overlap area.
+For this, the special beam imaging scans are used.
+Wherein the measured vertex\footnote{A vertex is a hit recontruction that allow measure the location and the associated uncertainty, of all proton-proton interaction in each event \cite{vertex}} position distributions for $x$ and $y$ scans are fitted using aDouble Gaussian function \cite{BI_calibration,Measuring_luminosity}.
+
+%\noindent For each fit result, the factorization bias is evaluated by comparing the luminous area ($2\pi\Sigma_{x}\Sigma_{y}$) with a simulation of a vdM scan pair that uses the fitted transverse proton bunch densities.
+This simulation is repeated several times to evaluate the impact of statistical fluctuations on the factorization bias.
+The  fit model results in a predicted factorization bias of about 0.7\% in $\sigma_{vis}$ .
+To account for potential additional contributions from higher order x-y correlations , twice the bias value is assigned as uncertainty.\\
+
+%to estimate the rate at each scan step
+%in the transverse bunch proton densities
+ \\
+
+\begin{comment}
+
+\section{Fit Model  Selection}
+
+After testing several mathematical fit models, the chosen model with the best fit quality and after applying all the corrections mentioned earlier, was a double Gaussian function:
+%https://gitlab.cern.ch/bril/VdMFramework/-/blob/main/src/plotting/capsigma_over_time.py#L90
+%\begin{equation}
+%DG+Const= C+P \cdot \Biggl[ F \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 \sigma_{1}^{2} } \Biggr) + (1-F) \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 \sigma_{2}^{2} } \Biggr) \Biggr] 
+%\end{equation}
+%\begin{equation}
+%f(x)= P \cdot \Biggl[ F \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2(\frac{\Sigma\cdot R}{F \cdot R+1-F} )^{2} } \Biggr) + (1-F) \cdot \exp \Biggl( \frac{-(x-\bar{x})^{2}}{2 (\frac{\Sigma}{F \cdot R+1-F} )^{2} } \Biggr) \Biggr]
+%\end{equation}
+%[5] + [2]*([3]*exp(-(x-[4])**2/(2*([0]*[1]/([3]*[1]+1-[3]))**2))
+    %    + (1-[3])*exp(-(x-[4])**2/(2*([0]/([3]*[1]+1-[3]))**2)) )
+%("#Sigma","#sigma_{1}/#sigma_{2}","peak","Frac","Mean","Const")
+%[0] -> [0]*[1]/([3]*[1]+1-[3])
+ %[1] -> [0]/([3]*[1]+1-[3])"""
+
+\begin{equation} 
+Poly4G(x)= A \Biggl[ 1+a_{2} \Biggl( \frac{-(x-\bar{x})}{\sigma} \Biggr)^{2} +a_{4} \Biggl( \frac{-(x-\bar{x})}{\sigma} \Biggr)^{4} \Biggr]\exp \Biggl[ -\frac{-(x-\bar{x})^{2}}{2\sigma^{2}}\Biggr]
+\end{equation}
+
+\begin{equation} 
+Poly4G(x)= A \Biggl( 1+a_{2} \biggl( \frac{-(x-\bar{x})}{\sigma} \biggr)^{2} +a_{4} \biggl( \frac{-(x-\bar{x})}{\sigma} \biggr)^{4} \Biggr)\exp \Biggl( -\frac{-(x-\bar{x})^{2}}{2\sigma^{2}}\Biggr)
+\end{equation}
+
+\begin{itemize}
+%\item $C$ is the constant value.
+\item $P$ the $peak$ rate.
+\item $F$ is the fraction of the peak rate attributed to the first Gaussian in the sum.
+\item $x$ is the beam position.
+\item $\bar{x}$ is the mean.
+\item $\Sigma$ is the overlap between the beams.
+\item $R$ is the ratio between the standard deviations of the  Gaussians (first over the second).
+\end{itemize}
+
+\end{comment}
+
+\section{Visible cross section results}
+\label{Visible cross section results}
+
+In order to compute $\sigma_{\text{vis}}$, different combinations of Gaussian functions with adjustable parameters were tested to achieve the best fit.
+The selected model was the one that provided the highest fit quality, primarily determined by its convergence with the data points.
+This convergence is assessed using the covariance matrix, which quantifies the linear relationships between variables.
+
+Another key criterion for evaluating fit quality is the chi-square ($\chi^2$) test, which determines whether the observed data follows a specified distribution (reference needed).
+A lower ($\chi^2$) value indicates a better fit.
+
+After testing multiple mathematical models, the function that provided the best fit quality for both years, 2017 and 2018 data, was the "Poly4G" function, a combination of four Gaussian functions:
+
+\begin{equation} 
+Poly4G(x)= A \Biggl( 1+a_{2} \biggl( \frac{-(x-\bar{x})}{\sigma} \biggr)^{2} +a_{4} \biggl( \frac{-(x-\bar{x})}{\sigma} \biggr)^{4} \Biggr)\exp \Biggl( -\frac{-(x-\bar{x})^{2}}{2\sigma^{2}}\Biggr)
+\end{equation}
+
+\noindent where $A$ represents the peak rate, while $x$ corresponds to the beam position and $\bar{x}$ to the mean.
+The parameter $\sigma$ defines the overlap between the beams.
+Additionally, $a_{2}$ and $a_{4}$ are the coefficients associated with the Gaussian terms scaled by $x^2$ and $x^4$, respectively.
+
+%\begin{center}
+\begin{figure}[h]
+\centering
+\includegraphics[width=.4\textwidth,height=0.4\textwidth]{Chapter4/2017_X_Scan_41.png}
+\includegraphics[width=.4\textwidth,height=0.4\textwidth]{Chapter4/2018_Y_Scan_2192.png}
+\caption[Examples of Fits for vdM1: BCID 41 (2017) and BCID 2192 (2018)]{Normalized rates and the resulting fitted curves with  fit model as a function of the beam separation ($\Delta$) for the year 2017 BCID 41 in $x$ direction (left) and 2018 BCID 2192 in $y$ direction (right) both years for the vdM1 .}
+\label{vdM1}
+\end{figure}
+%\end{center}
+
+Finally, to compute $\sigma_{\text{vis}}$, the values of $\Sigma_{x,y}$ and $peak_{x,y}$ are extracted from each fit in the $x$ and $y$ directions.
+The visible cross section for each BCID (vdM and BI scans) is then determined using these fitted parameters, as illustrated in Fig.
+\ref{vdM1}.
+The final $peak$ value (P) is obtained by averaging the peaks from the $x$ and $y$ scans.
+For each bunch crossing, $\sigma_{\text{vis}}$ is computed using Eq.
+\ref{eq:sigVisX}.
+The error bars represent the uncertainty propagated from the fit, assigned as shown in Eq.
+\ref{sigma_err}, where $P = (R_{x}(0,0) + R_{y}(0,0))/2$.
+
+\begin{equation}
+ \sigma_{vis}= \pi \Sigma_{x} \Sigma_{y}P
+ \end{equation}
+
+\begin{equation}
+\sigma_{vis\text{Err}}= 2 \pi \sqrt{ (\Sigma_{y} \cdot P \cdot \Sigma_{x\text{Err}})^{2} + (\Sigma_{x} \cdot P \cdot \Sigma_{y \text{Err}})^{2} + (\Sigma_{x} \Sigma_{y} P_{\text{Err}})^{2} }
+\label{sigma_err}
+\end{equation}
+
+Figure \ref{sigmavis_perbcid} shows the value of $\sigma_{vis}$ per BCID along with its statistical error.
+The left panel corresponds to 2017 (4 vdM scans and 2 Img scans) for BCIDs 41, 281, 872, 1783, and 2063, while the right panel corresponds to 2018 (4 vdM scans and 3 Img scans) for BCIDs 265, 865, 1780, 2192, and 3380.
+A consistency within 0.1\% is observed among comparable channels for all luminometers, which we take as the uncertainty associated with the bunch-to-bunch variation of the derived visible cross sections.
+
+\begin{center}
+  \begin{figure}[h!]
+    \centering
+   \includegraphics[width=.49\textwidth]{figures/vdMfitting/sigVis/Sigma_vis_6016_new_Per_BCID.png}
+   \includegraphics[width=.49\textwidth]{figures/vdMfitting/sigVis/Sigma_vis_6868_new_Per_BCID.png}
+    \caption[$\sigma_{vis}$ per BCID for all scans]{ $\sigma_{vis}$ per BCID for all scans.
+In each scan, the BCIDs follow the same order: 41, 281, 872, 1783, and 2063 for 2017 (fill 6016), and 265, 865, 1780, 2192, and 3380 for 2018 (fill 6868).}
+    \label{sigmavis_perbcid}
+  \end{figure}
+\end{center}
+
+To obtain the final value of $\sigma_{\text{vis}}$, we first perform a weighted average using the five BCIDs for each scan.
+Then, we compute another weighted average across the results of these five scans.
+In both cases, we assume no correlation between the BCIDs and the scans.
+The weighted average per scan  and total error per scan  are calculated following Equations \ref{average} and \ref{error}, respectively, where the weight is defined as $ w_{i} = 1/\sigma_{\text{visErr}}^{2} $.
+
+\begin{eqnarray}
+\sigma_{vis}^{Avg}=\Biggl(\displaystyle\sum_{i} w_{i}\sigma_{vis}^{i} \Biggr)\Biggl( \displaystyle\sum_{i} w_{i} \Biggr)^{-1}
+\label{average}
+\end{eqnarray}
+
+\begin{eqnarray}
+\sigma_{vis,Err}^{Avg}=\frac{1}{\sqrt{ \displaystyle\sum_{i} w_{i}}} 
+\label{error}
+\end{eqnarray}
+
+The final result for $\sigma_{\text{vis}}$ is \textbf{4666.4 $\pm$ 14.7 mb} for 2017 and \textbf{964.9 $\pm$ 2.2 mb} for 2018.
+The final uncertainties are determined from the average standard deviation of the scan-to-scan results.
+These scan variations, along with those from other detectors, contribute to the final scan-to-scan variation uncertainty.
+Figure \ref{sigmavis_perscan} illustrates the per-scan values of the measured $\sigma_{\text{vis}}$ for PCC after all corrections.
+%A detailed summary of the visible cross-section values and their uncertainties for PCC in 2017 and 2018, for each applied correction, is presented in Table \ref{table:xsec3}, along with the percentage change in $\sigma_{\text{vis}}$.
+
+%\begin{center}
+\begin{figure}[h]
+\centering
+\includegraphics[width=.49\textwidth]{figures/vdMfitting/sigVis/Sigma_vis_6016_new.png}
+\includegraphics[width=.49\textwidth]{figures/vdMfitting/sigVis/Sigma_vis_6868_new.png}
+\caption[$\sigma_{vis}$ average per scan and final result]{$\sigma_{vis}$ average per scan and final result}
+\label{sigmavis_perscan}
+\end{figure}
+%\end{center}
+
+\begin{comment}
+\begin{table}[h]
+\caption{ 
+Summary of visible cross-section results for PCC in 2017 and 2018.
+Ghost and satellite corrections are applied in all rows.
+The corrections include BG for background correction, P2P for peak-to-peak correction, OD1 for orbit drift (OD) rate correction, OD2 for OD rate and separation correction, OD3 for OD2 plus residual orbit drift correction, BB for beam-beam correction, DB for dynamic $\beta^*$ correction, LS for length scale calibration, and XY for x-y correlations.}
+\label{table:xsec3}
+\begin{center}
+\begin{tabular}{|c||c|c|}
+\hline 
+Correction & 2017 [mb] & 2018 [mb] \\ \hline 
+ BG\_OD3\_BB\_DB\_LS\_P2P\_XY\_EC   & 4666.4$\pm$14.7 & 964.9$\pm$2.2 \\ 
+ BG\_OD3\_BB\_DB\_LS\_P2P\_XY      & 4659.4$\pm$15.1 & 962.7$\pm$2.2 \\ 
+ BG\_OD3\_BB\_DB\_LS\_P2P         & 4642.5$\pm$8.5 & 962.4$\pm$3.7 \\ 
+ BG\_OD3\_BB\_DB\_LS             & 4641.4$\pm$9.6 & 962.3$\pm$3.7 \\ 
+ BG\_OD2\_BB\_DB\_LS             & 4631.5$\pm$18.8 & 960.9$\pm$3.4 \\  BG\_OD2\_BB\_DB                & 4672.0$\pm$18.9 & 967.3$\pm$3.4 \\ 
+ BG\_OD2\_BB                   & 4723.3$\pm$19.3 & 978.2$\pm$3.7 \\ 
+ BG\_OD2                      & 4644.2$\pm$18.8 & 962.0$\pm$3.2 \\ 
+ BG\_OD1                      & 4640.3$\pm$22.0 & 961.5$\pm$3.0 \\ 
+ BG                          & 4638.0$\pm$20.5 & 961.4$\pm$4.0 \\ 
+ noCorr                      & 5087.9$\pm$70.1 & 995.3$\pm$6.2 \\
+\hline \hline
+Emittance Change            & 0.15\% & 0.22\% \\ 
+ Non-factorisation           & 0.36\% & 0.04\% \\ 
+ Peak to Peak                & 0.02\% & 0.01\% \\ 
+ Residual OD                 & 0.22\% & 0.14\% \\ 
+ Length Scale                & -0.87\% & -0.66\% \\ 
+ Dynamic Beta                & -1.09\% & -1.11\% \\ 
+ Beam-Beam                   & 1.70\% & 1.68\% \\ 
+ OD Rate                     & 0.08\% & 0.05\% \\ 
+ OD Sep                      & 0.05\% & 0.01\% \\ 
+ Background                  & -8.84\% & -3.41\% \\
+\hline 
+\end{tabular}
+\end{center}
+\end{table}
+\end{comment}
+
+Finally, Figure~\ref{fig:vdM_fit_sigVis_All} shows the scan-by-scan variations of the $\sigma_{\text{vis}}$ with all corrections for all detectors (PLT, PCC, HFET, and HFOC) and normalized to their average value taken over all scans to bring them onto the same scale.
+The average standard deviation of 0.26\% in 2017 and 0.27\% in 2018 is then taken into account as the final scan-to-scan uncertainty.
+
+\begin{figure}[!h]
+\centering
+  \includegraphics[width=0.49\textwidth]{figures/visible_cross_section_results/sigVisPerScanNormalized_fill6016_XY_EC.pdf}
+  %\hspace{0.05\textwidth}
+  \includegraphics[width=0.49\textwidth]{figures/visible_cross_section_results/sigVisPerScanNormalized_fill6868_XY_EC.pdf}
+ \caption[$\sigma_{\text{vis}}$ Stability Across Scans for All Detectors (2017 & 2018)]{The BCID averaged  $\sigma_{\text{vis}}$ divided by its average value taken over all scans for all independently calibrated detectors and all scans using the Poly4G fit function in 2017 (left) and 2018 (right).
+The error bars signify the standard deviation over the BCIDs.
+The numbers in the legend show the standard deviation over the scans.}
+\label{fig:vdM_fit_sigVis_All}
+\end{figure}
+
+\section{Cross-detector comparisons in vdM Fill}
+
+A closure test of the calibration is performed during the vdM fill by using the luminometers to measure the integrated luminosity during head-on periods.
+Figure~\ref{fig:vdM_xdet} illustrates the calibration consistency in the vdM fill by showing the ratio of the luminosity measured by each detector with respect to a reference.
+While other detectors cover a larger number of BCIDs, only five BCIDs are used to ensure compatibility with PCC data.
+The uncertainty is determined as the standard deviation of the measured ratio, expressed as a percentage.
+In 2018, BCM1F is excluded.
+In Figure~\ref{fig:vdM_xdet2}, the shaded area represents the standard deviation of the individual ratio averages, which defines the uncertainty assigned to the vdM calibration consistency.
+This uncertainty is \textbf{0.41\%} in 2017 and \textbf{0.14\%} in 2018.
+
+\begin{figure}[!h]
+\centering
+  \includegraphics[width=0.49\textwidth]{figures/vdMfitting/vdMconsistency/lumi_sum5_fill6016_HFOC-HFET-PLT-PCCHD5div_HFET+HFOC+PLT+PCCHD5_ratioTrue_nls10_Xsecleg317.pdf}
+  \includegraphics[width=0.49\textwidth]{figures/vdMfitting/vdMconsistency/lumi_sum5_fill6868_HFOC-HFET-PLT-PCCHD5div_HFOC+HFET+PLT+PCCHD5_ratioTrue_nls2_Xsecleg318.pdf}
+ \caption[Instantaneous Luminosity Ratio with PCC Gated BCIDs (2017 & 2018)]{Instantaneous luminosity ratioin the vdM fill during head-on periods using the gated BCIDs available for PCC for 2017 (left) and 2018 (right).
+plot shows the values divided by a reference luminometer.
+The numbers in the legend signify the deviation of the integrated luminosity from the mean.}
+\label{fig:vdM_xdet}
+\end{figure}
+
+\begin{figure*}[!ht]
+\centering
+  \includegraphics[width=0.49\textwidth]{figures/visible_cross_section_results/lumi_sum5_histMean_fill6016_HFOC-HFET-PLT-PCCHD5div_HFET+HFOC+PLT+PCCHD5_ratioTrue_nls10_Xsecleg317.pdf}
+  \includegraphics[width=0.49\textwidth]{figures/visible_cross_section_results/lumi_sum5_histMean_fill6868_HFOC-HFET-PLT-PCCHD5div_HFOC+HFET+PLT+PCCHD5_ratioTrue_nls2_Xsecleg318.pdf}
+ \caption[Luminosity Ratios to Detector Average – vdM Head-On Periods (2017 & 2018)]{The ratios of HFET, HFOC, PLT and PCC luminosity to the detector averaged luminosity in the vdM fill for the head-on periods for 2017 (left) and 2018 (right).
+The points signify the average ratio, while the error bars represent the standard deviation of the ratio distribution of each of the detectors.
+The shaded area represents the standard deviation of the individual averages.}
+\label{fig:vdM_xdet2}
+\end{figure*}
+
+\begin{comment}
+\begin{table}
+  \begin{center}
+    \begin{tabular}{|l||c|c|} 
+\hline
+&  2017 [nb$^{-1}$]  &  2018 [nb$^{-1}$]  \\ \hline
+BCM1F         & 4.299 &  --- \\
+HFOC          & 4.331 & 1.132 \\
+HFET          & 4.319 & 1.130 \\
+PLT           & 4.320 & 1.134 \\
+PCCHD5        & 4.289 & 1.133 \\
+\hline \hline
+Lumisections used & 445    &  138\\\hline
+  \end{tabular}
+\caption{Integrated luminosity in the head-on periods of the vdM fill using the five zero-bias gated BCIDs as measured by a set of luminometers in 2017 and 2018. }
+\label{tab:vdM_xdet_intlumi}
+\end{center}
+\end{table}
+\end{comment}

### 2025-04-23 monograph_Luis/Chapter4/chapter4.tex
updated

--- 2025-03-07 monograph_Luis/Chapter4/chapter4.tex
@@
-\chapter{Analysis and Results}
+\chapter{Luminosity Measurement}
 
-\section{2017 and 2018 vdM scan program}
-\label{2017 and 2018 vdM scan program}
+Once the final calibration constant of the PCC detector has been obtained using data primarily from the vdM program, the next step is to apply this calibration to the luminosity measured by the detector throughout the entire year of data acquisition.
+This chapter will detail the specifications of these so-called physics data and the various analyses conducted to determine the final luminosity, including the analysis of detector modules and background (afterglow) for each year.
+Additionally, cross-checks with other luminometers will be performed to ultimately determine the final uncertainty in the luminosity measurement.
 
-\section{Data acquisition and processing}
-\label{data}
+\section{Physics Data}
 
-\section{Background estimation}
-\label{bkg}
+In June 2017, data collection for the second phase of Run 2 of the Large Hadron Collider (LHC) began, covering the years 2017 and 2018.
+This period resulted in a total recorded luminosity of \(49.81 \, \text{fb}^{-1}\) for 2017 and \(67.86 \, \text{fb}^{-1}\) for 2018, collected during proton-proton collisions at a center-of-mass energy of \(\sqrt{s} = 13\) TeV.
 
-\section{Beam Corrections}
-\label{bbcorrections}
-%https://cms.cern.ch/iCMS/analysisadmin/cadilines?line=LUM-22-001
+The data-taking process started with the establishment of stable beams and continued until either the beam was intentionally stopped or temporarily interrupted for beam studies.
+The total luminosity delivered by the LHC to CMS (in blue) and the luminosity recorded by CMS (in orange) for 2017 and 2018 are illustrated in Figures~\ref{Lumi_2017} and~\ref{Lumi_2018}, respectively~\citep{wikicern}.
 
-\section{Fit Model  Selection}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=.45\textwidth]{Chapter3/Luminosity/int_lumi_per_day_cumulative_pp_2017_Normtag.pdf}
+    \includegraphics[width=.45\textwidth]{Chapter3/Luminosity/int_lumi_per_day_pp_2017_Normtag.pdf}
+    \caption[Cumulative day-by-day integrated luminosity in 2017]{(Left) Cumulative daily integrated luminosity. (Right) Daily integrated luminosity, 2017.}
+    \label{Lumi_2017}
+\end{figure}
 
-\section{Results}
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=.45\textwidth]{Chapter3/Luminosity/int_lumi_per_day_cumulative_pp_2018_Normtag.pdf}
+    \includegraphics[width=.45\textwidth]{Chapter3/Luminosity/int_lumi_per_day_pp_2018_Normtag.pdf}
+    \caption[Cumulative day-by-day integrated luminosity in 2018]{(Left) Cumulative daily integrated luminosity. (Right) Daily integrated luminosity, 2018.}
+    \label{Lumi_2018}
+\end{figure}
+
+The Large Hadron Collider (LHC) operates in cycles known as fills, during which protons are injected, accelerated, and stabilized before collisions begin.
+Luminosity rises sharply after beam stabilization, reaching a peak before gradually decreasing due to proton depletion.
+The stable beams phase is when most data is collected.
+A fill ends when proton levels drop too low or technical issues arise, leading to a controlled beam dump and a sudden drop in luminosity.
+
+Within each fill, data is recorded in runs, which represent continuous periods of data acquisition under stable detector and accelerator conditions.
+A single fill can contain one or more runs, depending on machine stability and configuration adjustments.
+
+The Pixel Cluster Counting (PCC) physics data from each year is divided into datasets corresponding to specific time periods, defined by a range of runs.
+In 2017, five datasets were established: B, C, D, E, and F, with their respective run ranges listed in Table~\ref{tab:period_run_ranges_2017}.
+In 2018, the data was split into seven periods: A, B, C, D1, D2, D3, and D4, detailed in Table~\ref{tab:period_run_ranges_2018}.
+
+\begin{comment}
+\begin{table}[h!]
+  \centering
+  \caption[Run ranges for 2017 periods]{2017 luminosity data periods with run ranges.}
+  \begin{tabular}{cc}
+    \textbf{Period} & \textbf{Run range} \\ \hline
+    2017B & 297046-299329 \\
+    2017C & 299368-302029 \\
+    2017D & 302031-302663 \\
+    2017E & 303824-304797 \\
+    2017F & 305040-306462 \\
+  \end{tabular}
+  \label{tab:period_run_ranges_2017}
+\end{table}
+
+\begin{table}[h!]
+  \centering
+  \caption[Run ranges for 2018 periods]{2018 luminosity data periods with run ranges.}
+  \begin{tabular}{cc}
+    \textbf{Period} & \textbf{Run range} \\ \hline
+    2018A & 315252-316995 \\
+    2018B & 317080-319311 \\
+    2018C & 319337-320065 \\
+    2018D1 & 320500-321665 \\
+    2018D2 & 321710-322964 \\
+    2018D3 & 323363-324420 \\
+    2018D4 & 324564-325175 \\
+  \end{tabular}
+  \label{tab:period_run_ranges_2018}
+\end{table}
+\end{comment}
+
+\begin{table}[h!]
+  \centering
+  \begin{minipage}[t]{0.45\linewidth}
+    \centering
+    \caption[Run ranges for 2017 periods]{2017 luminosity data periods with run ranges.}
+    \begin{tabular}{cc}
+      \textbf{Period} & \textbf{Run range} \\ \hline
+      2017B & 297046-299329 \\
+      2017C & 299368-302029 \\
+      2017D & 302031-302663 \\
+      2017E & 303824-304797 \\
+      2017F & 305040-306462 \\
+    \end{tabular}
+    \label{tab:period_run_ranges_2017}
+  \end{minipage}%
+  \hspace{0.05\linewidth} % Espacio entre tablas
+  \begin{minipage}[t]{0.45\linewidth}
+    \centering
+    \caption[Run ranges for 2018 periods]{2018 luminosity data periods with run ranges.}
+    \begin{tabular}{cc}
+      \textbf{Period} & \textbf{Run range} \\ \hline
+      2018A & 315252-316995 \\
+      2018B & 317080-319311 \\
+      2018C & 319337-320065 \\
+      2018D1 & 320500-321665 \\
+      2018D2 & 321710-322964 \\
+      2018D3 & 323363-324420 \\
+      2018D4 & 324564-325175 \\
+    \end{tabular}
+    \label{tab:period_run_ranges_2018}
+  \end{minipage}
+\end{table}
+
+The datasets used in the analysis are derived from the Alignment and Calibration (AlCa) project within CMS and include two subsets: Random Trigger and Zero-Bias.
+The Random Trigger dataset contains events triggered in both colliding and non-colliding bunches, while the Zero-Bias dataset consists of unbiased events randomly selected among colliding bunches, identified using the Beam Pick-up Timing for eXperiments (BPTX) system.
+
+The Random Trigger data is reprocessed with an updated module veto list (as described in the next section) to improve background subtraction, known as afterglow corrections, which are further detailed in the next chapter.
+Similarly, the Zero-Bias dataset undergoes reprocessing with refined afterglow corrections to obtain the total yearly luminosity for PCC and to study stability and linearity in comparison with other luminometers.
+
+In 2017, vdM program was conducted during period C (fill 6016), while in 2018, it took place during period B (fill 6868).
+
+\section{Module selection}
+
+The pixel detector experiences time-dependent variations in performance due to factors such as noise, aging, and radiation damage, which affect the number of well-performing modules.
+To maintain accurate luminosity measurements, a selection is applied to the 1856 pixel detector modules, retaining only those that remain stable and linear across different data-taking periods.
+Modules exhibiting instability, non-physical shifts in cluster counts, or significant effects from readout buffer limitations are excluded.
+This selection is based on each module’s relative contribution to the total statistics in standard physics runs, ensuring that only consistently performing modules are used in PCC rate measurements, thereby preserving measurement reliability.
+
+To ensure accuracy, pixel module veto lists were generated for different time periods following the procedure described below for each year.
+These lists were processed using the data to improve both stability and linearity.
+Modules that were consistently identified as "bad" across multiple periods were excluded from the analysis.
+Finally PCC data with ZeroBias triggers was then reprocessed using this common veto list for final vdM analysis.
+
+\subsection{2017 Pixel Detector module selection}
+\label{sec:pcc_perf_moduleselection_2017}
+
+%% Sam's presentation of the module veto: https://indico.cern.ch/event/704864/contributions/2891738/attachments/1599873/2536088/PCCUpdate20180213.pdf
+
+The 2017 PCC data is divided into five periods (datasets) throughout the year: B, C, D, E, and F.
+The selection of stable ("good") detector modules is based on analyzing each module's cluster count relative to the total (module weight).
+The module weight is computed for each data period and compared across periods to assess stability.
+
+During the final part of the 2017 run, power supply failures led to a significant number of non-operational modules, which were excluded from the final measurement.
+In particular, the Pixel detector experienced issues with DC-DC power converters during period F, resulting in a large number of unstable modules.
+Therefore, the stability analysis begins by comparing module weights between periods D and F.
+
+Variations in module weight across periods are used to identify unstable modules.
+The selection threshold applied to the distribution ranged from 3\% to 5\%, depending on each pair of analysis periods.
+Table~\ref{tab:pcc_2017_module_selections} shows the number of modules that meet these criteria for every analyzed period pair.
+
+\begin{table}[h]
+    \caption{PCC 2017 detector module stability selections applied to the module weights}
+    \label{tab:pcc_2017_module_selections}
+  \begin{center}
+    \begin{tabular}{cc}  
+    \textbf{Periods}   & \textbf{\# Good modules} \\ \hline
+     D + F      & 945           \\ 
+     D + B      & 945           \\ 
+     D + C      & 945           \\ 
+     D + E      & 859           \\ 
+     B + F      & 819          \\ 
+     B + C      & 807          \\ 
+     B + E      & 810          \\ 
+     E + C      & 901          \\ 
+     E + F      & 756          \\ 
+     C + F      & 907          \\ \hline
+     \textbf{Combined}   & \textbf{633}  \\ \hline
+      \end{tabular}
+  \end{center}
+\end{table}
+
+%The final list of good modules ("Combined") is obtained by requiring that modules be selected in all comparisons (i.e.
+the intersection of all sets).
+Figure~\ref{fig:pcc2017modulevetofinal} shows the distribution of module weight ratios between periods B and D with the initial and final module selections, a large improvement is observed in the standard deviation of the distribution.
+
+\begin{comment}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.48\textwidth]{figures/performance_PCC/PCC_2017_moduleveto_DB_initialveto.png}
+    \includegraphics[width=0.48\textwidth]{figures/performance_PCC/PCC_2017_moduleveto_DB_finalveto.png}
+    \caption{Distribution of module weight ratios for the 2017 periods B and D with the initial (left) and final (right) module selections.}
+    \label{fig:pcc2017modulevetofinal}
+\end{figure}
+\end{comment}
+
+The number of selected modules for the final analysis was \textbf{633 (34.1\%) for 2017}.
+
+\subsection{2018 Pixel Detector module selection}
+\label{sec:pcc_perf_moduleselection}
+
+%[25] CMS Collaboration, “Description and performance of track and primary-vertex reconstruction with the CMS tracker”, JINST 9 (2014) P10009, doi:10.1088/1748-0221/9/10/P10009, arXiv:1405.6569
+
+For the year 2018, the selection of good pixel modules is based on the analysis of ZeroBias data by evaluating the contribution of each module to the total cluster count (module weight).
+This method enables the identification and progressive removal of unstable modules through the analysis of fluctuations in their response.
+The data for this year is divided into seven periods: A, B, C, D1, D2, D3, and D4.
+The procedure applied to these periods is as follows.
+
+First, the innermost pixel layer (Layer 0) is excluded from the analysis due to its known susceptibility to dynamic inefficiency at high instantaneous luminosity, where the readout chip becomes incapable of processing all incoming signals~\cite{pas_18}.
+
+Then, a two-step selection is applied: initially, a 7\% cut is used to discard modules with large fluctuations.
+After recalculating the module weights using the updated sample, a refined 2\% cut is applied.
+
+The vdM calibration data (Fill 6868), which belongs to period B, is treated first.
+Based on this dataset, an initial module veto list is constructed.
+The same procedure is then extended to the remaining periods—A, C, D1, D2, D3, and D4—using the results from period B as a reference.
+For each period, the two-step selection is repeated, and additional modules are excluded if their weight deviates by more than three standard deviations from the mean value observed in period B.
+
+Figure~\ref{goodmodule} illustrates the Profile of good and bad modules and the stability profiles and RMS/mean distribution used for the selection.
+
+\begin{center} \begin{figure}[h!] 
+\centering 
+\includegraphics[scale=.17]{Chapter4/good_module.png}
+\includegraphics[scale=.15]{Chapter4/RMSmean.png} 
+\caption[Profile of good and bad modules stability and module cut of 7\%]{Left: stability profiles of typical good and bad modules, showing the module weight as a function of lumi section.
+Right: RMS/mean values for all pixel modules, each represented by a module index.
+The 7\% cut is applied to this distribution in the first iteration.} \label{goodmodule} \end{figure} \end{center}
+
+A common module list was created by combining all exclusive module lists from different period combinations.
+Table~\ref{tab:2commonveto} presents the number of good modules after sequentially combining each period.
+
+\begin{comment}
+\clearpage
+\newpage
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1\textwidth]{figures/performance_PCC/good_bad_modules.png}
+    \caption{Variation of normalized module weight with time.
+Modules showing significant change in module weight (shown in right figure) over time having large rms/mean values are used to make module vetolist.}
+    \label{fig:goodbadmodules}
+\end{figure}
+\end{comment}
+
+%\clearpage
+%\newpage
+
+\begin{table}[h]
+\caption[Common Module Vetolist with Quality Selection]{Common module vetolist created by combining module vetolists for each period using a 2\% quality selection.}
+    \label{tab:2commonveto}
+  \begin{center}
+    \begin{tabular}{ccccc}  
+    \textbf{Period}   & \textbf{\# bad modules} & \textbf{\# good modules} \\  \hline
+     B      &  802   &  1054    \\ 
+     B + C      &  1076   &  780    \\ 
+     A + B + C      &  1417   &  439    \\  
+     A + B + C + D1      &   1534  &   322    \\ 
+     A + B + C + D1 + D2      &   1629 &    227   \\ 
+     A + B + C + D1 + D2 + D3     &   1668 &   188    \\ 
+     A + B + C + D1 + D2 + D3 + D4     &  1701 &     155  \\ 
+   \end{tabular}
+  \end{center}
+\end{table}
+
+The number of selected modules for the final analysis was \textbf{155 (8.35\%) in 2018}.
+
+The relative contribution of each pixel detector layer and disk to the total PCC, after applying the final module selection, is shown in Fig.~\ref{fig:stabprof} as a function of time throughout the year.
+%\includegraphics[scale=.17]
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.7\textwidth, height=7cm]{Chapter4/module_selection/ProfileX_combined_testing_LUM_20-001.png}
+    \caption[Stability Profiles of Pixel Layers and Disks After Final Module Selection]{Stability profiles of Pixel detector layers and disks with the final module selection.}
+    \label{fig:stabprof}
+\end{figure}
+
+%Run range for each period is shown in Table \ref{tab:period run ranges}. 
+ \begin{comment}
+ Bad modules found after applying this 2\% selection in the final iterative step are used to constitute a 2 $\%$ rms module veto list for each period as shown in Table \ref{tab:per period veto}.
+
+\begin{table}
+  \begin{center}
+    \begin{tabular}{ccccc}  
+    \textbf{Period}   & \textbf{\# bad modules} & \textbf{\# good modules} \\ \hline
+     2018A      &   1276   &  580    \\  
+     2018B      &    802  &     1054  \\ 
+     2018C      &   1076  &    780   \\ 
+     2018D1     &  1169  &     687  \\ 
+     2018D2     &  1184  &    672   \\ 
+     2018D3     &  1081  &    775   \\ 
+     2018D4     &  1032  &     824  \\ 
+      \end{tabular}
+    \caption{2 \% rms module vetolist for each period showing number of good and bad modules.}
+    \label{tab:per period veto}
+  \end{center}
+\end{table}
+\end{comment}
+
+\section{Afterglow Corrections}
+
+The extended waveform of the signal recorded in silicon, along with the production of secondary particles from high-energy interactions with the detector material, defines the afterglow effects observed in PCC.
+The concept of afterglow is inherent to the detector and its recorded events, independent of the specific modules used for data collection.
+Consequently, a consistent afterglow correction is always necessary, regardless of module performance or operational state.
+
+In precision PCC luminosity measurements, understanding and correcting afterglow effects is crucial.
+Afterglow corrections are estimated using a dedicated data stream recorded with a random trigger (raw PCC), as mentioned in the previous chapter.
+It is essential to use raw PCC data from both colliding and non-colliding bunches.
+Colliding bunches provide genuine signals from particle interactions, while non-colliding bunches capture background noise and any lingering afterglow from previous collisions.
+This data is collected at a total bandwidth of approximately 500 Hz, covering all bunch crossings in the LHC orbit.
+For analysis, the data is averaged over periods of approximately 50 lumisections (around 20 minutes).
+An example of raw data for Fill the 9036 is shown in Fig.~\ref{fig:af_fit40}.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.8\textwidth]{figures/fill_7036_pattern_2.png}
+\caption[7036 fill patern]{fill 7036,  and encompassing 900 colliding bunches, serves as the foundation for estimating the afterglow parameters.
+}
+\label{fig:af_fit40}
+\end{figure}
+
+Two main types of afterglow noise have been identified:
+
+Type 1 Afterglow (Electronic Spillover): This noise originates from the prolonged signal waveform in silicon after a collision event.
+
+Type 2 Afterglow (Activation-Induced Background): This exponentially decaying noise results from the activation of detector material by high-energy particles, leading to the production and decay of radioactive isotopes \cite{CMS-PAS-SMP-12-008}.
+
+Both types can be observed in Fig.~\ref{fig:afterglow}.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.6\textwidth]{figures/performance_PCC/afterglow.png}
+    \caption[Type 1 and Type 2 Afterglow Responses in CMS Run 315690]{Train and afterglow tail showing type 1 and type 2 afterglow response in CMS Run 315690.}
+    \label{fig:afterglow}
+\end{figure}
+
+In the afterglow correction process, the following steps are involved:
+
+First, a mathematical fit function is used to model the afterglow tail from a single colliding bunch.
+This model incorporates parameters for Type 1 afterglow and an exponentially decaying function for Type 2, accounting for both amplitude and decay width.
+The function is summed over all bunch crossings and fine-tuned based on the luminosity associated with each bunch.tThe model expresses the amount of afterglow as follows:
+
+\begin{equation}
+F(x) = \sum_{k\in colliding } n_k \left[ \delta_{x,k} + A  \delta_{x,k+1} + B e^{-C(x - k - 1)}  \Theta(x-k-1) \right]
+\end{equation}
+
+Where $x$ is the BCID in the orbit, $k$ is an index over colliding bunches, $n_k$ is the cluster count for a colliding BCID excluding the afterglow and he first term $\delta_{x,k}$ corresponds to the colliding bunch.
+The term $A$ represents the Type 1 afterglow fraction (\( x = k+1 \)).
+For each 50 LS block, it is determined by iterating the model until a good fit to the data is achieved.
+This fraction, relative to the colliding bunch, is fitted in each block.
+and the last terms $B$ and $C$ corresponds to the Type 2 afterglow, which becomes relevant for $x\geq k+1$ and  are obtained from representative fills.
+This exponentially decaying component is characterized by two parameters: one for normalization relative to the colliding bunch rate and another for the decay constant.
+An example  for single train fit is shown in Fig.
+\ref{fig:af_fit99}.
+
+\begin{figure}
+  \centering
+    \includegraphics[width=0.75\textwidth]{figures/2018_af_fit_1.png} 
+  \caption[Afterglow effect fit]{Fit to single train to estimate afterglow parameters.}
+  \label{fig:af_fit99}
+\end{figure}
+
+\begin{comment}
+Fig.~\ref{fig:pcc_type1f} shows the Type 1 parameter $A$ as a function of the PCC for both 2017 and 2018.
+
+\begin{figure}[b]
+    \centering
+\includegraphics[width=0.48\textwidth]{figures/performance_PCC/afterglow_t1f_vsinstlumi_2017.png}
+\includegraphics[width=0.48\textwidth]{figures/performance_PCC/afterglow_t1f_vsinstlumi_2018.png}
+    \caption{PCC afterglow type 1 fraction as a function of PCC for the 2017 (left) and 2018 (right) datasets. Each point corresponds to one 50 LS block.}
+    \label{fig:pcc_type1f}
+\end{figure}
+
+Fig. \ref{fig:pcc_residuals} shows the distribution residual counts in non-colliding BCID's relative to the average rate in colliding bunches.
+
+\begin{figure}
+    \centering
+\includegraphics[width=0.48\textwidth]{figures/performance_PCC/afterglow_noncolliding_residual_2017.png}
+\includegraphics[width=0.48\textwidth]{figures/performance_PCC/afterglow_noncolliding_residual_2017.png}
+    \caption{PCC afterglow residuals the 2017 (left) and 2018 (right) datasets.
+The distributions are filled with the residual cluster count in non-colliding bunches after subtracting the afterglow and dividing by the average cluster count in colliding bunches.
+The residuals are evaluated for blocks of 50 LS's.}
+    \label{fig:pcc_residuals}
+\end{figure}
+\end{comment}
+
+ The values of %of type 1 Fraction (A), 
+ type 2 afterglow parameter amplitude (B) and decay width (C) for both years are shown in Table \ref{fig:af_fit4000}.
+
+%\FloatBarrier
+\begin{table}[H]
+  \centering
+  \caption[Type 2 afterglow parameters estimation]{Type 2 afterglow parameters obtained from fit to raw pcc data for both years}
+  \begin{tabular}{ccc}
+    \textbf{year} & \textbf{B} & \textbf{C} \\
+     \hline
+   %1-wagon train  & 0.001246  & 0.01261 \\
+   2017  & 0.0008228 &  0.01316\\
+   2018  & 0.0008265 &  0.01231\\
+  \end{tabular}
+  %\caption{Type 2 afterglow parameters obtained from fit to raw pcc data}
+  \label{fig:af_fit4000}
+\end{table}
+
+The afterglow correction is determined by the ratio of corrected to uncorrected PCC, which serves as a scale factor applied to individual bunch-by-bunch histograms in the zero-bias data.
+Figure \ref{fig:afterglowcorrection} illustrates this scale factor for a 50-lumi-section block in run 315690.
+On the left, both the Random PCC data and corrected PCC values are shown for all bunch crossings, highlighting the differences between the initial data and the adjusted counts.
+On the right, the afterglow scale factor for a single 50-lumi-section block is displayed, representing the correction applied for the final module veto.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.48\textwidth]{figures/performance_PCC/afterglow_correction_factor_1lsblock_315690_2.png}
+    \includegraphics[width=0.48\textwidth]{figures/performance_PCC/afterglow_correction_factor_1lsblock_315690_3.png}
+    \caption[PCC Random Rates vs BCID Before and After Afterglow Subtraction (Fill 6639)]{Left: PCC Random rates vs BCID for one 50 LS block in fill 6639 before and after the afterglow subtraction.
+Right: The ratio of raw and afterglow corrected rates, these ratios are applied to the ZeroBias data for the luminosity measurement.}
+    \label{fig:afterglowcorrection}
+\end{figure}
+
+During the correction process, a histogram of collision events, including bunch trains, is adjusted by subtracting the afterglow model, scaled by the luminosity of each colliding pair, from all subsequent events.
+This ensures that each bunch is fully corrected.
+Finally, the correction scale factor is defined as the ratio of corrected to uncorrected PCC and is applied to the final PCC in the zero-bias (ZB) data.
+
+\begin{comment}
+
+Figure~\ref{fig:pcc_afterglow} shows per-bunch pixel cluster counts per event from a 2018 fill before and after the application of the OOT corrections in the vicinity of the last bunch train before the abort gap: the increased contribution from spillover is clearly visible for the first bunch after the train on top of the exponential activation tail.
+
+\begin{figure*}[htbp]
+    \centering
+    \includegraphics[width=0.66\textwidth]{figures/detector_corrections/PCCAfterglow_zoomed_range.pdf}
+
+\caption{The number of clusters in the pixel tracker per event as a function of the BCIDs for the last bunch train of the orbit, with blue points representing the values before, and red crosses showing the results after the out-of-time corrections are applied.
+The upper panel focuses on the full count range for colliding and empty BCIDs, while the lower panel shows the empty bunch crossings with a different scale for better visibility.
+In the lower panel, the red crosses indicating the residual rate are near zero, illustrating the excellent performance of the correction.}
+\label{fig:pcc_afterglow}
+\end{figure*}
+
+\begin{figure}
+    \centering
+\includegraphics[width=0.48\textwidth]{figures/performance_PCC/afterglow_avgsf_vsLSBlock_2017.png}
+\includegraphics[width=0.48\textwidth]{figures/performance_PCC/afterglow_avgsf_vsLSBlock_2018.png}
+    \caption{PCC average afterglow scale factors per orbit for the 2017 (left) and 2018 (right) datasets. Each point corresponds to one 50 LS block time ordered during the year.}
+    \label{fig:pcc_afterglow_avgsf}
+\end{figure}
+
+\end{comment}
+
+\section{Luminosity integration}
+\label{sec:luminosity_integration_and_uncertainty}
+
+The luminosity integration entails applying the afterglow correction and the absolute vdM calibration to the luminometer rates, with all corrections applied as described in Sec.
+\ref{bbcorrections} over a full year of physics data-taking.
+These yearly datasets, collected for each luminometer, are used to estimate systematic uncertainties related to cross-detector consistency (stability) and linearity.
+
+An example of the calibrated instantaneous luminosity for PCC in 2017 is shown in Fig.
+\ref{Lumi_2017}.
+The plot on the left displays the calibrated Instantaneous luminosity throughout the entire year where data is presented as discrete measurements for each lumi section, reflecting the collision rate at that specific time.
+On the right, the luminosity evolution for a single fill (Fill 6120) is shown, where the gradual decrease in luminosity over time is clearly visible, this decline results from the loss of protons as collisions take place during the fill.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=.47\textwidth]{figures/performance_PCC/Lumi_2017.png}
+    \includegraphics[width=.45\textwidth]{figures/LumiVsTime_fill7270.pdf}
+    %\includegraphics[width=.47\textwidth]{figures/performance_PCC/Lumi_2017_fill_6120.png}
+    \caption[PCC Instantaneous Luminosity (Entire Year 2017) and Fill 7270 (2018)]{2017 PCC instantaneous luminosity as a function of lumi section for the entire year .
+(right) Instantaneous luminosity as measured offline as a function of time for LHC fill 7270 corresponding to the year 2018.
+The drops in luminosity correspond to emittance scans performed at the beginning and end of the fill, and to luminosity adjustments steps.}
+    \label{Lumi_2017}
+\end{figure}
+
+The total CMS luminosity for 2017 and 2018 relies on multiple independently calibrated detectors: HFET, HFOC, PLT, and PCC.
+The final luminosity is obtained by averaging the measurements from these detectors.
+Ideally, all detectors would measure the same luminosity, making the average equivalent to any individual measurement.
+However, differences among the luminometers arise due to statistical fluctuations, applied rate corrections, the limited precision of the absolute calibrations and uncorrected instrumental effects.
+
+Additional variations stem from time-dependent changes in detector performance and environmental conditions.
+These include factors such as detector aging, radiation damage, and noise fluctuations.
+In particular, detector aging can lead to gradual degradation in performance over time.
+
+The stability systematic uncertainty is evaluated by assessing the consistency of each individual measurement with respect to the mean luminosity.
+This is done by computing the ratio of the luminosity measured by each independently calibrated luminometer (HFET, HFOC, PCC, and PLT) to the mean luminosity.
+Each ratio is averaged over time intervals of approximately 20 minutes (50 lumi sections), as shown in Fig.~\ref{fig:stabilitylinearity:stability}, where the upper row of the figure shows these ratios as a function of integrated luminosity, while the lower row displays their luminosity-weighted averages.
+
+Finally, the standard deviation of the four averaged ratio values is taken as the stability uncertainty, amounting to \textbf{0.21\%} for 2017 and \textbf{0.30\%} for 2018.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.45\textwidth]{figures/luminosity_integration_and_uncertainty/ratio__hfet-pcc-plt-hfocdivmean_PCConly_17.pdf}
+\hspace*{0.05\textwidth}
+\includegraphics[width=0.45\textwidth]{figures/luminosity_integration_and_uncertainty/ratio__hfet-pcc-plt-hfocdivmean_PCConly_18.pdf}
+\includegraphics[width=0.45\textwidth]{figures/luminosity_integration_and_uncertainty/means_clean__hfet-pcc-plt-hfocdivmean_PCConly_17.pdf}
+\hspace*{0.05\textwidth}
+\includegraphics[width=0.45\textwidth]{figures/luminosity_integration_and_uncertainty/means_clean__hfet-pcc-plt-hfocdivmean_PCConly_18.pdf}
+\caption[Luminosity Ratios (HFET, HFOC, PLT, PCC) to Mean per 50 LS Blocks (2017 & 2018)]{The ratio of the luminosity measured by HFET, HFOC, PLT and PCC to their mean per 50 LSblocks for 2017 (left) and 2018 (right).
+The upper row shows the ratio as a function of integrated luminosity, while the lower row displays the luminosity-weighted average of the ratios.
+The error bars signify the weighted standard deviation over the 20-minute units.
+The striped area represents the unweighted standard deviation of the four average ratio values.}
+\label{fig:stabilitylinearity:stability}
+\end{figure}
+
+The linearity systematic uncertainty arises from the fact that a detector’s response may vary at different luminosity levels.
+This uncertainty is evaluated following the methodology described in previous publications~\cite{pas_17, pas_18}.
+The method consists of performing a linear fit to the ratio of the detector’s measured instantaneous luminosity to that of a reference luminometer, as a function of the reference single-bunch instantaneous luminosity (SBIL), taking advantage of the natural luminosity decay during each fill.
+
+Only fills with a span of at least 2 Hz/$\mu$b and containing a minimum of five data points are considered.
+Each point represents an average over approximately six minutes (15 LS).
+Figure~\ref{fig:stabilitylinearity:linearity3}(right) shows an example of the linearity ratio for 2018 from fill 7272, comparing different detectors to the reference detector HFOC.
+
+Due to their robust linear response, the final publication uses either DT or RAMSES~\cite{CMS:2021xjt} as the reference luminometer.
+The luminosity-weighted mean and standard deviation of the slopes obtained from comparisons with DT and RAMSES are shown in Figure~\ref{fig:stabilitylinearity:linearity3}.
+The larger of the two standard deviations is taken as the uncertainty estimate, yielding 0.081\%/(Hz/$\mu$b) for 2017 and 0.082\%/(Hz/$\mu$b) for 2018.
+The final linearity uncertainty on the integrated luminosity is computed by multiplying these values by the corresponding mean SBIL, resulting in uncertainties of 0.43\% for 2017 and 0.42\% for 2018.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.45\textwidth]{figures/luminosity_integration_and_uncertainty/linearity_means_clean3.pdf}
+\hspace*{0.05\textwidth}
+\includegraphics[width=0.45\textwidth]{figures/linearity_7270.pdf}
+\caption[Residual Nonlinearity and Luminosity Ratios (2017 & 2018)]{(Right)The luminosity weighted average of the measured residual nonlinearity between the mean luminosity and DT or RAMSES (RAM) for 2017 and 2018.
+For 2017, the value is reported also for the mean without PCC, which is used for the low pile-up fills.
+The error bars signify the weighted standard deviation over the individual fills.
+(left)Ratios of instantaneous luminosity as measured offline by the CMS luminometers as a function of the instantaneous luminosity measured by HFOC for LHC fill 7270.
+The points correspond to intervals of 40 LS}
+\label{fig:stabilitylinearity:linearity3}
+\end{figure}
+
+%The low pileup (low PU) data, recorded in a handful of fills in 2017, featuring an average SBIL of only 0.41 Hz/\(\mu\)b, are handled in an identical manner.
+In this region, PCC is not available for luminosity measurement due to poor statistical performance.
+%The sample standard deviation of the remaining three luminosity sources is 0.67\%, which is taken as the consistency uncertainty.
+
+%The linearity uncertainty is estimated using the relative non-linearity slopes derived in high pileup conditions for the mean of HFOC, HFET and PLT with respect to DT and RAMSES.
+The value used (0.113\%(Hz/\(\mu\)b)$^{-1}$
+%is the average relative slope between the three-detector mean and RAMSES. 
+%Multiplied by the mean SBIL in the low pileup era, this results in a 0.04\% uncertainty.
 
 \section{Systematic Uncertainties}
+
+The methods used to determine the integrated luminosity for the CMS proton-proton data collected in 2017 and 2018 at 13 TeV, as well as the sources of systematic uncertainty limiting its precision, have been discussed throughout this document.
+The final uncertainties are grouped into two main categories, normalization and integration.
+
+Normalization includes all uncertainties related to corrections applied during the final detector calibration with the determination of the visible cross section ($\sigma_{\text{vis}}$) using the vdM scan method, as described in Chapters~\ref{bbcorrections} and~\ref{Visible cross section results}.
+The dominant sources of uncertainty in this category are related to x-y factorizability, scan-to-scan variations, and cross-detector consistency during the vdM fills.
+
+As discussed throughout the calibration corrections, the normalization uncertainties are considered correlated across years when they originate from the same underlying physical processes or instrumental sources, or when an identical methodology is the dominant contributor to the uncertainty.
+Exceptions include scan-to-scan and bunch-to-bunch variations in the measured $\sigma_{\text{vis}}$, as well as inconsistencies between the results from independent luminometers during the vdM fill.
+These factors are partly statistical or random in nature, and their underlying causes may vary from year to year.
+
+The second actegory refers to the integration uncertainties, which relate to the efficiency and linearity of the detector response, as discussed in the previous chapter.
+These uncertainties arise from the stability and linearity of the different luminometers over the course of the entire year.
+In this case, cross-detector luminosity comparisons are treated as uncorrelated, whereas linearity uncertainties associated with the measured mean luminosity (calculated as the average of the values provided by the four bunch-by-bunch capable systems) are considered correlated.
+
+Summing up the normalization and integration uncertainties, which contribute similarly to the total, the relative precision is 0.86\% in 2017 and 0.83\% in the high-pileup periods of 2018.
+Table \ref{TAB:SystematicError} provides a detailed summary of the uncertainties associated with the two main categories (normalization and integration) as well as the final consistency among the independently calibrated systems.
+
+\begin{table}[H]
+    %\centering
+    \caption[Summary of the luminosity uncertainty components in 2017 and 2018]{Summary of the luminosity uncertainty components in 2017 and 2018, divided into normalization and integration categories.}
+    \label{TAB:SystematicError}
+    \begin{tabular}{|l|l|c|c|}
+      \hline
+      & Source                                        & 2017 [\%] & 2018 [\%] \\
+      \hline\hline
+      \multirow{10}{*}{Normalization} 
+      & \hspace{+2mm} Ghost and satellite charge      & 0.06 & 0.07 \\
+      & \hspace{+2mm} Beam current normalization      & 0.20 & 0.20 \\
+      & \hspace{+2mm} Orbit drift                     & 0.09 & 0.19 \\
+      & \hspace{+2mm} Beam-beam effects               & 0.29 & 0.30 \\
+      & \hspace{+2mm} Length scale calibration        & 0.12 & 0.14 \\
+      & \hspace{+2mm} Transverse factorizability      & 0.33 & 0.36 \\
+      & \hspace{+2mm} Scan to scan variation          & 0.26 & 0.27 \\
+      & \hspace{+2mm} Bunch to bunch variation        & 0.10 & 0.10 \\
+      & \hspace{+2mm} Cross-detector consistency at vdM  & 0.41 & 0.14 \\
+      \hline\hline
+      \multirow{2}{*}{Integration} 
+      & \hspace{+2mm} Cross-detector consistency per year & 0.21 & 0.30 \\
+      & \hspace{+2mm} Linearity                       & 0.43 & 0.42 \\
+      \hline\hline
+      & \textbf{Total normalization uncertainty}      & \textbf{0.71} & \textbf{0.65} \\
+      & \textbf{Total integration uncertainty}        & \textbf{0.48} & \textbf{0.52} \\
+      & \textbf{Total uncertainty}                    & \textbf{0.86} & \textbf{0.83} \\
+      \hline
+    \end{tabular}
+\end{table}

### 2025-04-23 monograph_Luis/Chapter5/chapter5.tex
updated

\chapter{Summary and Outlook}

The main objective of this work was the calibration of the luminosity measured using the PCC detector through the van der Meer (vdM) method, contributing to the publication, which focuses on the second part of Run 2, covering the years 2017 and 2018. Throughout the process, the PCC results were developed in parallel with those from other CMS luminometers, ultimately achieving a final uncertainty below the 1\% target required for publication. The work addressed key topics such as the importance of luminosity, the LHC and the CMS experiment, the PCC method and the calibration procedure for estimating $\sigma_{\text{vis}}$, and the treatment of all systematic uncertainties.

This study provided a comprehensive overview of how Run 2 data were collected and processed. For each year, the vdM calibration program is described, detailing the full processing chain for the PCC detector, from raw data files with cluster reconstruction to the selection of "good" pixel detector modules. The study also includes the afterglow corrections to the physics data to achieve the most accurate luminosity possible. For the calibration the optimal fit model selected was a Poly4G function, using a background substraction per bunch for 2017 and a constant value for 2018, based on the analysis of Super Separation periods.

The PCC detector showed good performance compared to the other CMS luminometers. After all corrections, the final results for $\sigma_{\text{vis}}$ were \textbf{4666.4 $\pm$ 14.7 mb} for 2017 and \textbf{964.9 $\pm$ 2.2 mb} for 2018. The variations remained within acceptable ranges across different comparisons, such as scan-to-scan and bunch-by-bunch during the calibration procedure. Moreover, the PCC demonstrated excellent stability and linearity in the integrated luminosity throughout the year, contributing directly to the overall analysis and to the final uncertainties reported in the publication: \textbf{0.86\%} for 2017 and \textbf{0.83\%} for 2018.

### 2025-05-06 thesis_julio/Chapter2/chapter2.tex
commit5

@@
 \\
-\includegraphics[scale=0.50]{cms2.png}
+\begin{figure}[h]
+    \centering
+     \includegraphics[width=1\textwidth]{cms2.png}
+     \caption{The CMS detector size comparison with each of their components}
+    \label{fig:four-forces}
+\end{figure}
+
 \\
@@
 \\
-\includegraphics[scale=0.35]{cms.png}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1\textwidth]{cms.png}
+     \caption{Different particles travelling across the different detectors of the CMS experiment}
+    \label{fig:four-forces}
+\end{figure}
+
 \\
@@
 \\
-\includegraphics[scale=0.7]{pixeldetector.png}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1\textwidth]{pixeldetector.png}     
+    \caption{Pixel detector outter rings and inner rings structure}
+    \label{fig:PixelDetector}
+\end{figure}
+
 \\
@@
 \\
-\includegraphics[scale=1]{BPIXFPIX.png}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1\textwidth]{BPIXFPIX.png}
+    \caption{Barrel Pixel Detector moudles and Forward Pixel Detector Modules}
+    \label{fig:BPIXFPIX}
+\end{figure}
+
 \\
@@
 The mean number of pixel clusters in a simulated zero bias event is in the order of 100 per pp collision.
-The number of pixel clusters per bunch crossing is linearly dependent on pileup and therefore an accurate measure of the instantaneous luminosity.
-The mean number of pixel cluster per trigger is \\
+The number of pixel clusters per bunch crossing is linearly dependent on pileup and therefore an accurate measure of the instantaneous luminosity.\cite{PCC1} The mean number of pixel cluster per trigger is \\
 
-$<N_{cluster}> = <N_{Pixel/Interaction}> <N_{interaction}> = <N_{Pixel/interaction}> \mu$ \\
+\begin{equation}
+<N_{cluster}> = <N_{Pixel/Interaction}> <N_{interaction}> = <N_{Pixel/interaction}> \mu 
+\end{equation}
 
-here the $\mu$ is the number of interactions and with this the following equation gives us
+here the $\mu$ is the number of interactions and with this the following equation and gives us a relation with the cross section $\simga_{i}$, instant luminosity and $\mu$
 
-Only the modules of the pixel subdetector that are stable during the entire period of the data taking are used for the PCC measurements, excluding the pixels that are known to be defective or affected by the limited size of the readout buffer.
+\begin{equation}
+\mu = \frac{\sigma_{i}}{f}\frac{dL}{dt}
+\end{equation}
+
+here f is the frequency of the LHC, defining a new quantity $\simga_{cluster}$ = $\simga_{i}<N_{Pixel/Interaction}> $ and combining equation (2.1) and (2.2) we got
+
+\begin{equation}
+<N_{cluster}> = \frac{\sigma_{cluster}}{f} \frac{dL}{dt}
+\end{equation}
+
+Here, the value of $N_{cluster}$ is the mean number of pixel clusters on the pixel detector during a zero bias trigger at a head on period, the value of $\sigma_{cluster}$ can be obtained using the Van Der Meer scan and from the equation (2.3) we can obtain the luminosity from \cite{PCC2}
+
+\begin{equation}
+\sigma_{cluster} = <N_{cluster}> f (\frac{dL}{dt})^{-1}
+\end{equation}
 
@@
 
-For the selection of modules
+To be applicable to a van der mer scan the cluster cross section must use exactly the same detector configuration during the whole of the data taking and the calibration scan.
+This means if any of the modules of the detector didn't work at any point of the scans and didn't gave any readout It must be excluded from the calibration and the luminosity analysis, the stability of each module is determined in a ratio of module PCC and total PCC.
+\cite{PCC3}
+
+From the total of 1856 modules on the pixel detector (1184 on the BPIX and 672 on FPIX) so in the analysis for the pcc vdm calibration onf 2024 for the fill 9639a total of 240 modules were used.

### 2025-05-06 thesis_julio/Chapter3/chapter3.tex
commit2
commit4
commit5

@@
-\chapter{Data Processing}
+\chapter{Luminometer Calibration}
 \label{ch3}
 
+\section{Van Der Meer Method}
+
+The Van Der Meer (vdM) scan let us obtain the value of $\sigma_{visible}$ using different luminometers.
+For this case the detector of interest is the pixel detector with which are going to obtain a calibration of the luminosity using the vdM scan in combination with the PCC method.
+The scan consist on separating particle the beams from each other between the X and Y axis by $\Delta X$ and $\Delta Y$ values moving them and recording values of luminosity independently, when the scan on X and scan on Y are imposed over each other we said that they're on head on giving the maximum value of luminosity.
+Usually a single gaussian fit is used to obtain beam overlap widths also denoted as $\Sigma_{x}$ and $\Sigma_{y}$, other fit models may be used like the doble gaussian depending on the quality of the fit \cite{Vdm}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1\textwidth]{vdm1.png}
+    \caption{The vdm scan on the left showing the beams for X and Y. On the right a curve of the different values of rate for the beams displacement, the peak occurs during the head on part.}
+    \label{fig:vdm1}
+\end{figure}
+
+For obtaining the importnat parameters on the vdm scan we return to the equation (1.2) and apply it to and individual bunch crossing, the values of N1 and N2 being the number of protons colliding can be obtained since is a known quantity from the experiment, the frequency f is also a known quantity, the frequency of the LHC which is 11,245 kHz but the proton densities $\rho_{1}$ and $\rho{2}$ are more difficult to obtain, this is were the vdM scan help us to measure integral over the bunch proton densities.
+The luminosity integral evaluated with the beams separated by a distance $\Delta_{x}$ and $\Delta_{y}$ can take the form of:
+
+\begin{equation}
+ L(\Delta x, \Delta Y) = N_{1} N_{2} f  \int \int \rho_{1}(x,y)\rho_{2}(x+\Delta x, y+\Delta y) dxdy 
+\end{equation}
+
+Because of the scan method is it assumed that the two bunches of proton densities are factorizable since they act independently between each other so we can turn the right part of (3.1) into two integrals:
+
+ \begin{equation}
+N_{1} N_{2} f  \int \int \rho_{1}(x,y)\rho_{2}(x+\Delta x, y+\Delta y) dxdy   = N_{1} N_{2} f (\int \rho_{1}(x)\rho_{2}(x + \Delta x) dx) (\int rho_{1}(y) \rho_{2}(y + \Delta y) dy)
+\end{equation}
+
+Integrating both sides on $\Delta y$ and using in combination with (3.1) while we fix $\Delta x_{0}$ = 0 and $\Delta y_{0}$ = 0 as the head on point,  we obtain:
+
+ \begin{equation}
+N_{1} N_{2} f \int \rho_{1}(x) \rho_{2}(x + \Delta x_{0}) dx = \int L (\Delta x_{0}, d\Delta y) d(\Delta y)
+\end{equation}
+
+A similar result is obtained when we integrate both sides for $\Delta x$ using this and combining equation (3.1), (3.2) and (3.3) we can obtain that
+
+\begin{equation}
+N_{1} N_{2} f \int \rho_{1}(x) \rho_{2}(x + \Delta x_{0}) dx = \frac{L (\Delta X_{0}, Delta y_{0})}{\int L(\Delta x_{0}, \Delta y) d(\Delta y)}
+\end{equation}
+
+Similarly to the previous step we can obtain the value of the other factor of (3.2) with an analogous process.
+The integrals resulting on the right side can be evaluated by evaluated by obtaining the rate in function of the beam-beam separation which are $\Delta x$ and $\Delta y$  this because the luminosity has a linear relationship with the rate.
+The Luminosity can be expresed on terms of the rate during the head on points using the following:
+
+\begin{equation}
+L(\Delta x, \Delta y) = N_{1} N_{2} f \frac{2R(\Delta x_{0}, \Delta y_{0}}{\int L(\Delta x_{0}, \Delta y) d(\Delta y) \int L(\Delta x, \Delta y_{0}) d(\Delta x)}
+\end{equation}
+
+Here the luminosity is replaced by the rate R, it is convenient to write this integral in terms of the convoluted beam widths which are denoted by $\Sigma_{x}$ and $\Sigma_{Y}$, this convoluted widths are defined by:
+
+\begin{equation}
+\Sigma_{x} = \frac{1}{2 \pi} \frac{\int R(\Delta x, \Delta y_{0} d(\Delta x) )}{R(\Delta x_{0}, \Delta y_{0})}
+\end{equation}
+
+For $\Sigma_{y}$ the result is analogous. With (3.6) we can write (3.5) in a different manner:
+
+\begin{equation}
+L(\Delta x, \Delta y) = \frac{N_{1}N_{2}f}{2 \pi \Sigma_{x} \Sigma_{y}}
+\end{equation}
+
+This in combination with (1.4) make us possible to obtain the following expression for the visible cross section
+
+\begin{equation}
+\sigma_{vis} = \frac{2 \pi \Sigma_{x} Sigma_{y} R(\Delta x_{0} \Delta y_{0})}{N_{1} N_{2}f}
+\end{equation}
+
+This makes possible obtain $\sigma_{vis}$ only by experiment since all of the right values can be obtained via the experiment, the maximum rate R($\Delta x_{0}$, $\Delta y_{0}$) is obtained at the maximum PCC obtained during the vdm scan, this means during the head-on process, while the $\Sigma_{x}$ and $\Sigma_{y}$ are obtained with the information of the fit model.
+
+This calculations are done on several Bunch Cross Identifier which so you obtain several values of $\simga_{vis}$ and then they are weight averaged according to the uncertainties in order to obtain $\sigma_{vis}$ for the scan.
+
 \section{Datasets}
+
+In order to analyze the data of the experiment \cite{datasets1}
+
+\section{Scans}
 
@@
 \section{Corrections}
+
+\section{Fit model}
+
+\section{Beam Parameters}
+
+The calibration constant
+
+$\sigma_{vis} = \frac{R_{det}}}{L_{b}} = \frac{2 \pi \Sigma_{x} \Sigma_{y} R(0,0)}{N_{1}N_{2}f}$  \cite{Lumvdm}

### 2025-05-06 monograph_Luis/Abstract/abstract.tex

@@
 
+This work presents the calibration of the CMS Pixel Cluster Counting (PCC) luminometer and the absolute luminosity determination using the van der Meer (vdM) method, as part of the publication \textit{``Precision luminosity measurement in proton-proton collisions at $\sqrt{s} = 13$ TeV with the CMS detector''}, which covers the second part of Run 2 corresponding to the 2017 and 2018 data-taking periods.
+The final results for the PCC visible cross section $\sigma_{\text{vis}}$ are 4666.4 $\pm$ 14.7 mb for 2017 and 964.9 $\pm$ 2.2 mb for 2018.
+The final integrated luminosity is obtained from a combination of multiple independently calibrated luminometers.
+A precision of 0.86\% for 2017 and 0.83\% for 2018 is achieved, with dominant uncertainties arising from luminometer non-linearity and the x–y factorization correction.
+
 \end{abstract}

### 2025-05-06 monograph_Luis/Chapter1/chapter1.tex

@@
 
-\section{Particle Colliders and production cross section}
+\section{Luminosity}
 
@@
 These experiments function as powerful microscopes that allow researchers to study subatomic particles such as electrons, protons, neutrons, neutrinos, and quarks.
-They also provide a means to test predictions made by the Standard Model.
+They areevaluated based on two important measures, which are the available center of mass energy and the rate at which particles collide (luminosity).
 
-The high speeds required for the collisions are achieved through the use of powerful superconducting magnets, which accelerate particles to the necessary velocities.
-These particles are then collided at specific points along the accelerator, where detectors are located.
-These detectors are capable of measuring individual interactions, known as events, generated by the collisions.
-Some of the particles produced, such as the Higgs boson, cannot be directly observed.
-Instead, they are detected and analyzed using advanced technologies, which measure their interactions with matter \cite{thomson_2013}.\\
-
-In general, a particle detector is typically constructed as a cylindrical or polygonal barrel section, oriented parallel to the incoming colliding beams.
-Two flat end caps seal the cylindrical structure, ensuring nearly complete solid angle coverage all the way down to the beam pipe.
-This detector comprises multiple layers, each designed to detect the different particles generated during collisions \cite{thomson_2013}.\\
-
-Particle colliders are evaluated based on two important measures, which are the available center of mass energy and the rate at which particles collide (luminosity).
-The amount of energy that is available to create new particles and study their properties is particularly significant because it determines the range of particles that can be produced.
-During experiments, particles are accelerated and directed toward each other, and when they collide, they produce new particles and interactions that can be analyzed by scientists.\\
-
-Colliding beam machines are capable of achieving significantly higher energies at the point where the beams intersect and scatter.
 When the particles in the beams have equal energy and opposite momentum (equal mass), the experiment occurs in the center-of-mass (CM) frame.
@@
 \end{equation}
+
 Where  \textbf{$p$} and $E$ are the momenta and the energy of each incoming particle respectively.In the center-of-mass (CM) frame, where the momenta of the particles are equal and opposite, the second term in the equation for the Lorentz invariant quantity ($s$) disappears, leaving only $s = 4E^2$.\\
@@
 
-The technical meaning of "cross section" in particle physics is quite different from its common usage, while "cross section" typically refers to a slice of an object, in particle physics, it quantifies the probability of a collision and is a property of the interaction of one particle with another, this is expressed in units of square meters.
 When two beams cross in a particle accelerator, a variety of different processes can occur and  the cross section of a given process depends on the type and energy of the colliding particles.
@@
 
-To explain this concept more clearly, let's consider a simple scenario where a beam of particles of type $a$ passes through a region of space that contains particles of type $b$.
+To illustrate this concept more clearly, let's consider a simple scenario where a beam of particles of type $a$ passes through a region of space that contains particles of type $b$.
 The interaction rate between the two types of particles depends on the number of particles per unit volume of type $b$, denoted as $n_{b}$, and the flux of the incident particles, denoted as $\phi_{a}$.
@@
 
-The essence of fundamental physics can be encapsulated in the interaction cross section, denoted by $\sigma$.
-This parameter, which is measured in area units, represents the likelihood that an interaction will occur between an incident particle and a target particle.
-It's helpful to imagine each target particle as having an effective cross-sectional area, and the interaction cross section as representing that area.
-Figure \ref{cross_section}(a) shows an illustration of this concept, where an incident particle of type $a$ moves with velocity $v_{a}$ through a region of area $A$ that contains target particles of type $b$ with velocity $v_{b}$ moving in the opposite direction.
-The value of the interaction cross section is determined by the underlying quantum mechanical probability of interaction and is fundamental to understanding the behavior of particles in collisions.
-\cite{thomson_2013}
+Figure \ref{cross_section}(a) shows an illustration of this concept, where an incident particle of type $a$ moves with velocity $v_{a}$ through a region of area $A$ that contains target particles of type $b$ with velocity $v_{b}$ moving in the opposite direction \cite{thomson_2013}.
 
@@
 
-To understand the probability of an interaction between particles of types $a$ and $b$, imagine that in a time interval $\delta t$, particle $a$ passes through a region containing $\delta N= nb(v_{a}+v_{b}) A \delta t$ particles of type $b$.
-The probability of interaction can be obtained by dividing the effective total cross-sectional area of the $\delta N$ particles by the area $A$.
-This can be thought of as the probability that the incident particle passes through one of the regions of area $\sigma$ drawn around each of the $\delta N$ target particles, as shown in Figure \ref{cross_section}(b).
-So the cross section for a particular process is defined as the effective target area for that process and has units of area, more formally is expresed as \ref{cross} \cite{thomson_2013}.
+In particle physics experiments, the number of useful interactions (or events) is a crucial, the capability of a particle accelerator to produce such interactions is quantified by a parameter known as the instantaneous luminosity, denoted as $\mathcal{L}_{\text{inst}}$.
+The significance of luminosity lies in its direct relationship with the production rate of particles of interest.
+Specifically, the rate at which a particular process occurs is proportional to the product of the luminosity and the corresponding cross section.
+As such, luminosity directly impacts the ability to observe rare events.
+Furthermore, achieving precise measurements of particle properties often requires a large number of collisions to ensure sufficient statistical significance.
 
-%For a beam of particles of type $a$ with number density $n_{a}$ confined to a volume $V$, the total interaction rate can be expressed as $\text{rate}=(n_{a}v)(n_{b}V) \sigma = \phi N_{b} \sigma$, where $v$ is the velocity of the beam particles, $N_{b}$ is the number of target particles per unit volume, and $\phi$ is the flux of incident particles per unit area per unit time.
-The cross section for a particular process is defined as the effective target area for that process and has units of area, more formally is expresed as \cite{thomson_2013}:
+The event rate $R$ for a given process is defined as the product of the instantaneous luminosity and the process cross section $\sigma_p$~\cite{concept_of_luminosity}:
+
 \begin{equation}
-\sigma=\frac{\text{number of interaction per unit time per target particle}}{\text{incident flux}}
-\label{cross}
+R = \mathcal{L}_{\text{inst}} \cdot \sigma_p
+\label{eq.lumi}
 \end{equation}
 
-\section{Luminosity }
+Here, luminosity is expressed in units of $cm^{-2}s^{-1}$.
 
-In experiments conducted in particle physics, the number of useful interactions (or events) is just as important as the energy.
-The ability of a particle accelerator to produce these interactions is measured by a parameter called instantaneous luminosity $\mathcal{L}_{inst}$.
-It is directly proportional to the number of events produced per second and the cross section $\sigma_{p}$ \cite{concept_of_luminosity}.
+The cross section of the process that produces the particle is a measure of the probability that a given interaction will occur.
+It is typically a very small quantity, on the order of picobarns ($10^{-36}~\text{cm}^2$).
+To achieve high luminosity, particle accelerators employ various techniques to increase the number of particles in the beams and to focus them into a small cross-sectional area.
+This is accomplished through the use of superconducting magnets, which guide and confine the particles to a narrow path.
+Additionally, radio frequency (RF) cavities are used to accelerate the particles to higher energies, thereby increasing the frequency of bunch crossings and enhancing the overall collision rate.
+
+In high-energy particle accelerators, such as the Large Hadron Collider (LHC) at CERN, integrated luminosity is a key quantity that measures the total number of collisions per unit area accumulated during an experiment.
+It quantifies the total amount of data collected and is crucial for evaluating the performance of the accelerator.
+Integrated luminosity is defined as~\cite{concept_of_luminosity}:
 
 \begin{equation}
-R=\mathcal{L}_{inst} \cdot \sigma_{p}
+  \mathcal{L}_{\text{int}} = \int_{0}^{T} \mathcal{L}_{\text{inst}}(t')\,dt'
 \end{equation}
 
-Where the unit of luminosity is $cm^{-2}s^{-1}$.
-
-To derive a general expression for luminosity in the case of two colliding beams, we consider both beams to serve as the target and the incoming beam simultaneously.
-We will assume that the beams are "bunched", meaning that the particles are grouped into packets or bunches.
-
-\begin{center}
-  \begin{figure}[h!]
-    \centering
-\includegraphics[scale=.25]{Chapter1/luminosity.png} 
- \caption[Colliding beam interaction]{Schematic view of a colliding beam interaction\cite{concept_of_luminosity}}
-    \label{luminosity}
-  \end{figure}
-\end{center}
-
-%A schematic picture is shown in Fig.
-\ref{luminosity}.
-Since the two beams are not stationary but are moving through each other, the overlap integral depends on the longitudinal position of the bunches, and therefore on time.
-As the beams move towards and through each other, the two beams have different distribution functions and a different number of particles in the beams \cite{concept_of_luminosity}.
-The overlap integral, which is proportional to the luminosity $\mathcal{L}_{inst}$, can then be written as:
- In Figure \ref{luminosity}, you can see a diagram that illustrates how two beams intersect with each other.
-Because these beams are not still, but rather in motion, the way they overlap depends on the time and the position of the bunches.
-While the beams move, they also have different distributions and numbers of particles in them \cite{concept_of_luminosity}.
-The luminosity $\mathcal{L}_{inst}$, which is proportional to the overlap integral, can be expressed as:
-
-\begin{equation}
-  \mathcal{L}_{inst}\propto K\cdot \int\int\int \int_{-\infty}^{\infty} \rho_{1}(x,y,s,-s_{0}) \rho_{2}(x,y,s,s_{0})dxdydsds_{0}
-    \label{lumi_1}
-\end{equation}
-
-The functions $\rho_{1}(x,y,s,-s_{0})$ and $\rho_{2}(x,y,s,s_{0})$ represent the beam density distribution at a given time.
-We assume that the two bunches meet at the point $s_{0} = 0$.
-Since the beams are in motion towards each other, we need to take into account a relativistic kinematic factor (Eq.
-\ref{kinematic}) by multiplying this expression.
-
-\begin{equation}
- K = \sqrt{(\vec{v_{1}}-\vec{v_{2}})^{2}-(\vec{v_{1}}\times \vec{v_{2}})^{2}/c^{2}}
-    \label{kinematic}
-\end{equation}
-
-When the bunches collide head-on and are traveling at nearly the speed of light, the relativistic kinematic factor takes on a value of 2.\\
-Assuming uncorrelated densities in all planes and head-on collisions where the velocities of the two bunches are opposite $(\vec{v_{1}}=-\vec{v_{2}})$, the overlap integral can be factorized as:
-
-\begin{equation}
-  \mathcal{L}_{inst}= 2N_{b} N_{1}N_{2}f \int\int\int\int_{-\infty}^{\infty}  \rho_{1x}(x)\rho_{1y}(y)\rho_{1s}(s-s_{0})\rho_{2x}(x)\rho_{2y}(y)\rho_{2s}(s+s_{0}) dxdydsds_{0}
-    \label{luminosity_2}
-\end{equation}
-
-where $N_{b}$ is the number of bunches in one beam, $N_{1}$ and $N_{2}$ are the particles per bunch and $f$ the revolution frequency.\\
-
-%\begin{eqnarray}
-%\rho_{iz}(z)= \frac{1}{\sqrt{2\pi} \sigma_{z}} exp \biggl(-\frac{z^{2}}{2\sigma_{z}^{2}} \biggr)&z=x,y&i=1,2 
-%\end{eqnarray}
-
-%\begin{eqnarray}
-%\rho_{s}(s\pm s_{0})= \frac{1}{\sqrt{2\pi} \sigma_{s}} exp \biggl(-\frac{(s\pm s_{0})^{2}}{2\sigma_{s}^{2}} \biggr)
-%\end{eqnarray}
-
-Assuming Gaussian profiles in all dimensions and approximately equal bunch lengths $(\sigma_{1s}\approx \sigma_{2s})$, the equation \ref{luminosity_2} can be solved.
-For a general case where $\sigma_{1x}\neq \sigma_{2x} \text{ and } \sigma_{1y}\neq \sigma_{2y}$
-
-\begin{equation}
-  \mathcal{L}_{inst}= \frac{N_{1} N_{2} N_{b}f }{2\pi \sqrt{\sigma_{1x}^{2}+\sigma_{2x}^{2}}\sqrt{\sigma_{2y}^{2}+\sigma_{2y}^{2}}}
-  \label{lumi_general}
-\end{equation}
-
-For a specific case, asuming equal beams, $\sigma_{1x}= \sigma_{2x} \text{ and } \sigma_{1y}= \sigma_{2y}$:
-
-\begin{equation}
-  \mathcal{L}_{inst}= \frac{N_{1} N_{2} N_{b}f }{4\pi \sigma_{x} \sigma_{y}}
-  \label{lumi_theor}
-\end{equation}
-
-This expression is widely recognized as the formula for the luminosity of two Gaussian beams that collide head-on.
-It reveals how the luminosity is related to the number of particles in each bunch and the size of the beams \cite{concept_of_luminosity}.\\
-
-In practice,the integral in  \ref{luminosity_2} cannot be solved analytically because   the properties of the colliding beams are not know precisely, so a experimental technique is implemented with a dedicated machine setup to estimate the integrals, yielding a similar expression as \ref{lumi_theor}.
-
-To determine the overall number of events, we rely on integrated luminosity, which is a measurement of the total amount of collected data.
-This value is crucial for evaluating the effectiveness of an accelerator and it can be expressed as: \cite{concept_of_luminosity}:
-
-\begin{equation}
-  \mathcal{L}_{int}=\int_{0}^{T} \mathcal {L}_{\text{inst}}(t') dt'
-\end{equation}
-
-Where the value of $\mathcal{L}_{inst}$ is evaluated over time $T$ (excluding possible dead time) because its intensity decreases as the number of protons reduces during the collisions of the fill.
-So $\mathcal{L}_{int}$ is directly related to the number of observed events as:
-\begin{equation}
-  \mathcal{L}_{int} \ndot \sigma_{p}= \text{number of events of interest}
-\end{equation}
-
-The integrated luminosity has units of $cm^{-2}$ and is often expressed in inverse barn ($1 barn= 10^{-24}cm^{2}$). \\
+Here, $\mathcal{L}_{\text{inst}}$ is evaluated over the duration $T$ of the data-taking period (excluding possible dead time), as its intensity typically decreases over time due to the reduction in the number of protons during the fill.
 
@@
 
-\section{Results in Luminosity precision for LHC Run 2}
+\section{Current Luminosity precision for LHC Run 2}
 
@@
 
-The second stage (2017–2018) had preliminary results published in the Public Analysis Summaries, CMS-PAS-LUM-17-001 \cite{pas_17} for 2018 and CMS-PAS-LUM-18-002 \cite{pas_18} for 2017.
-However, the desired uncertainty values were not achieved.
+The second stage (2017–2018) had preliminary results published in the Public Analysis Summaries for 2017 and 2018 \cite{pas_17,pas_18}. However, the desired uncertainty values were not achieved.
 Efforts are currently underway to further improve the precision of these measurements and present them in a final publication.
@@
     \end{center}
-
-\section{Motivation for precise luminosity measurement}
-
-%% tabla con ano , luminosidad y presicion

### 2025-05-06 monograph_Luis/Portada/Portada.tex

@@
         \vspace{.4cm}   %% DEFINE EL ESPACIO ENTRE LA DOBLE LINEA Y EL NOMBRE DE LA DIVISIÓN
-        {\scshape \large Facultad Interdisciplinaria de Ciencias Exactas y Naturales}
+        {\scshape \large Facultad Interdisciplinaria de Ciencias Exactas y Naturales}\\
         {\scshape Departamento de Investigaci\'on en F\'isica} %% NOMBRE DE LA DIVISIÓN
@@
         By:\\[12pt]
-        \textbf{  {\large Luis Enriquue Enrique CUEVAS PICOS}}
+        \textbf{  {\large Luis Enrique CUEVAS PICOS}}
 
@@
 
-        { Hermosillo, Sonora} \hskip2.5cm { - - -, 2025}
+        { Hermosillo, Sonora} \hskip2.5cm {2025}
       \end{center}

### 2025-05-07 thesis_julio/Chapter2/chapter2.tex
7may

@@
 
-One of the principal objectives of the CMS is identify with very high precision the paths taken by the particles that were bend by the magnetic field they called this part the inner tracker which is composed of different substructures, closest to the interaction point we have the Silicon Pixel Detector, then after the silicon strip detectors which are divided into the inner barrel part and the outer barrel part, the outer barrel and the outer end caps.
-When a charged particle pass through this layers interacts electromagnetically with the sensors leaving a hit that can be used to identify the path that a particle took.
+One of the principal objectives of the CMS is identify with very high precision the paths taken by the particles that were bend by the magnetic field they called this part the inner tracker which is composed of different substructures, closest to the interaction point we have the Silicon Pixel Detector which will be detailled more on a later section.
+
+Apart from the pixel detector the inner track is composed of strip detectors which are divided into the inner barrel (TIB) part and the outer barrel par(TOB), as well as the inner disks (TID) and the outer end caps (TEC).
+The TIB and TOB are made of four and six concentric layers barrel shell structures respectively, the TID system is made of three disk structures each divided in three concentric rings and the TEC is made of nine disk structures on each side each of these made of four to seven rings as we can see on the figure 2.2.
+The tracker is composed of 15,148 modules distributed among the TIB, TOB, TID and TEC each module has one or two silicon sensors for a total of 24,244 sensors  When a charged particle pass through this layers interacts electromagnetically with the sensors leaving a hit that can be used to identify the path that a particle took.
 \cite{CMS1}
+
+\begin{figure}[h]
+    \centering
+     \includegraphics[width=1\textwidth]{cms3.png}
+     \caption{Layout of the CMS Innertracker includin the Pixel Detector, and other substructures TIB, TOB, TID and TEC}
+    \label{fig:inner-track}
+\end{figure}
 
@@
 
+For the tracking
+
 \section{Pixel Cluster Counting}
@@
 To be applicable to a van der mer scan the cluster cross section must use exactly the same detector configuration during the whole of the data taking and the calibration scan.
-This means if any of the modules of the detector didn't work at any point of the scans and didn't gave any readout It must be excluded from the calibration and the luminosity analysis, the stability of each module is determined in a ratio of module PCC and total PCC.
+This means if any of the modules of the detector didn't work at any point of the scans and didn't gave any readout It must be excluded from the calibration and the luminosity analysis so only a specific number of modules is selected during this.
+After this we obtain the stability of the modules that can be determined by a ratio of module PCC and total PCC.
 \cite{PCC3}

### 2025-05-07 thesis_julio/Chapter3/chapter3.tex
7may

@@
 
-In order to analyze the data of the experiment \cite{datasets1}
+The data on the CMS is a complex set of inter-dependent workflows made in a way that assure the full physics exploitation of the CMS detector potential and the collisions delivered by the LHC, this data provides analyses with reconstructed collision events from the experiment and are designed to use the CMS computing resources efficiently.
+This stream of events is organized into datasets according to the results of the High Level Trigger (HLT) which defines primary datasets since they are defined by the paths of the HLT.
+The design of the primary datasets is centered around candidates for particles that are reconstructed on the final state by the hLT and follows the principle of grouping together events with similar physics content.
+\cite{datasets1}
+
+The datasets used for the obtention of the $\sigma_{visible}$ for 2024 were the ones from the Fill 9639 which is divided in 3 blocks, a fill is a process that generates beams for the LHC this tipycally involves particles around the number of $10^{14}$ that are grouped in bunches that form the proton beam.
+This is what we use the bcid number to identify this bunches, there are a total of 3564 bunches that are empty or filled depending on the fill all of this part of the LHC bunch train.
+For this fill in the calibration the bcids of relevance were a total of 12 which are identified by the numbers: 303, 324, 345, 506, 527, 822, 1081, 1102, 1397, 2000, 2965, 3123.
+This fill started on may 16 at 13:39 and ended at may 17 at 23:50.
+
+In the case for our datasets each bcid is processed by the CMS collaboration to enable cluster reconstruction resulting in the ALCARECO datasets that contain a module collection and their number of cluster per event in CMSWW format.
+This samples are processed using the CMSWW software to extract the clusters per module to obtain the dataset in the ROOT format.
+ROOT is a software framework born at CERN It is open source and used for high energy physics to analyze data while providing packages for storage, processing and visualization while minimizes the computing resources needed.
+
+The root format saves the data in form of TTrees which behaves like an array of data structure and storage data.
+This tree consist on branches and leaves, a branch is a list of independent columns that can contain values of any fundamental type and are represented by TBranch.
+While the leaves represented by TLeaf give access to actual data in difference to the TBranch which represent a structure.
+After the datasets are processed, the rates of the Pixel detector were stored each 1.32 seconds periods called NB4 this to make an average of clusters and the number of events that fall into that time span.
+
+This dataset were processed (...) getting a lot of root files for each of the different zero bias streams there were a total of 32 zero bias streams.
+The data then was processed again to obtain a hd5file a format that can supports n-dimensional datasets and facilitates the reading of the datasets, this hd5 files contained relevant information about the root files like the average rate per NB4, this was made for each of the files for almost all of the available streams excluding two of them that were not ready by the moment (the ones that were identified by ZB21 and ZB28) after one stream got all of his files processed into an hd5 file they were converged into a single file containing relevant information for all the stream, once all of the files in all of the data streams were processed into hd5 files a single hd5file was made containing all of the information about the streams also a single csv file was made containing only the average rate file per NB4 for each of the bcids.
 
@@
 
+During the duration of the fill and for the calibration a few scans of interest were realized the first of them being the vdm scans which was explained in the first section of the chapter, also the BI scans, there were a total of five vdm scans during and two BI scans in the following table we see the time were this scans started and the time w    \\
+
+Also we got the super separation scans which consist on making a complete separation on the colliding beams so the rate would be zero, there were five of each super separations each of them with a duration of 300 seconds in the table we have information about the beggining and end of each super separation (SS) period.
+
+\begin{table} [H]
+\begin{center}
+\caption{Super Separation Period time}
+\begin{tabular}{|c c c|} 
+ \hline
+ Scan & Time Start & Time End  \\ [0.5ex] 
+ \hline\hline
+ SS1 & 1715883182 & 1715883481  \\ 
+ \hline
+ SS2 & 1715902185 & 1715902484  \\
+ \hline
+ SS3 & 1715919164 & 1715919463 \\
+ \hline
+ SS6 & 1715943045 & 1715943343  \\
+ \hline
+ SS5 & 1715987303 & 1715987602  \\ [1.0ex]
+ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+In the following image we show a histogram of the average rate vs time during the super separation period number 2:
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1\textwidth]{SS1.jpeg}
+    \caption{Histogram of rates during the second super separation scan}
+    \label{fig:SS1}
+\end{figure}
+
+In the image we can see that the average rate suddenly drops, this is the beggining of the second super separation scan for the bcid 506 where the avarage rate drop but is non zero, then the rate goes up again meaning the end to the super separation scan.
+
 \section{Background Estimation}
+
+The background estimation is obtained during the super separation (SS) process, since the SS scan separates the beams so they shouldn't be colliding the expected value on the rate is expected to be a rate associated with the background, this is then estimated by checking each of the SS scans on the time window referred on the table (3.1), the mean value during this period is assumed to be the mean value of the SS period, in the following table we see the mean PCC value for each period.
+
+\begin{table} [H]
+\begin{center}
+\caption{Different Scans}
+\begin{tabular}{|c c c|} 
+ \hline
+ Scan & Mean & std  \\ [0.5ex] 
+ \hline\hline
+ SS1 &  & 1715883481  \\ 
+ \hline
+ SS2 &  & 1715902484  \\
+ \hline
+ SS3 &  & 1715919463 \\
+ \hline
+ SS6 &  & 1715943343  \\
+ \hline
+ SS5 &  & 1715987602  \\ [1.0ex]
+ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+This is the mean value of each super separation off al the bcids a total of 60 mean values were obtained
 
@@
 
+There are different fit models at the time to do the vdm calibration, the most common one is Single Gaussian but also other models like the Double Gaussian, QG, Poly2g or Poly 4G.
+Each of these models have different parameters and restrictions making some of them better than other on the fit quality.
+
 \section{Beam Parameters}
-
-The calibration constant
-
-$\sigma_{vis} = \frac{R_{det}}}{L_{b}} = \frac{2 \pi \Sigma_{x} \Sigma_{y} R(0,0)}{N_{1}N_{2}f}$  \cite{Lumvdm}

### 2025-05-16 thesis_julio/Chapter1/chapter1.tex
commit5
may16

@@
     \includegraphics[scale=1]{table1.png}
-    \caption{The magnitude of the four forces compared}
+    \caption{Comparison of the strength magnitude of the four fundamental forces}
     \label{fig:four-forces}
@@
 
-\includegraphics[scale=0.7]{sm.png}
+\begin{figure}[h]
+    \centering
+   \includegraphics[width=1\textwidth]{sm.png}
+    \caption{The standard model of particle physics}
+    \label{fig:four-forces}
+\end{figure}
 
@@
 
- \includegraphics[scale=0.35]{LHC.png}
+\begin{figure}[h]
+    \centering
+   \includegraphics[width=1\textwidth]{LHC.png}
+    \caption{The accelerator facility at cern for the LHC}
+    \label{fig:LHC}
+\end{figure}
 
@@
 
-The performance of a collider is determined by the beam energy and the luminosity, the luminosity is a key parameter in particle colliders is a quantity that measures the ability of a particle accelerator to produce a required number of interactions and is given by: \cite{Lum}
+%The performance of a collider is determined by the beam energy and the luminosity, in order to compute the luminosity we need to define the cross section of the accelerator first this is for the calculation of the interest rates, which have to take in consideration the flux which is defined as the number of particles crossing a unit are per unit of time, the cross section is denoted by $\sigma$ and every scattering process has a cross section $\simga_{i}$ but the one that we are interested on is the total cross section which is the sum of all the $\simga_{i}$.
 
-$\frac{dR}{dt} = \mathcal{L} \cdot \sigma_{p} $
+The performance of a collider is determined by the beam energy and the luminosity. The cross section It's known as parameter like "the size of a target"
+
+%The define of cross section can be understand in a situation where a single particle is travelling to a velocity $v _{a}$in a region defined by A, which contains $n_{b}$ particles of a particle type b moving to a velocity $v_{b}$ in the opposite direction of $v_{a}$ if in a time $\delta t$  the particle a cross a region contained a total of $nb(v_{a} + v_{b})A\delta t$ particles of type b, the interaction probability can be obtained from the effective total cross seciotanl area divided by A which can be seen as the probability of that hte incident particles passes through one of the region of area $\sigma$ around each of the $\delta N$ particles then we can talk about the total rate being:
+
+\begin{equation}
+rate = flux x number of target particles x cross section
+\end{equation}
+
+And we can define the cross section as follow:
+
+\begin{equation}
+\sigma = \frac{number of interaction per unit of time per target particle}{incident flux}
+\end{equation}
+
+The luminosity is a key parameter in particle colliders is a quantity that measures the ability of a particle accelerator to produce a required number of interactions and is given by: \cite{Lum}
+
+\begin{equation}
+\frac{dR}{dt} = \mathcal{L} \cdot \sigma_{p} 
+\end{equation}
 
@@
 
- \includegraphics[scale=0.80]{lumi.png}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1\textwidth]{lumi.png}
+    \caption{Two beams colliding}
+    \label{fig:beamslumi}
+\end{figure}
 
@@
 
-$ 2N_{1}N{2}fN_{b} \int \int \int^{\infty}_{-\infty}  \rho_{1x} (x) \rho_{1y}(y) \rho_{1s} (s-s_{0}) \rho_{2x}(x) \rho_{2y}(y) \rho_{2s} (s+s_{0}) dxdydsds_{0}  $
+\begin{equation}
+ 2N_{1}N{2}fN_{b} \int \int \int^{\infty}_{-\infty}  \rho_{1x} (x) \rho_{1y}(y) \rho_{1s} (s-s_{0}) \rho_{2x}(x) \rho_{2y}(y) \rho_{2s} (s+s_{0}) dxdydsds_{0}  
+\end{equation}
 
@@
 
-$ L_{int} = \int L (t') dt' $
+\begin{equation}
+ L_{int} = \int L (t') dt' 
+\end{equation}
 
@@
 
-$\mathcal{L}_{int} \cdot \sigma_{p} =$ number of events of interest
+\begin{equation}
+L_{int} \cdot \sigma_{p} = number of events of interest 
+\end{equation}
 
@@
 
+\begin{figure}[h]
+    \centering
      \includegraphics[scale=1.25]{integratedlum.png}
+     \caption{Integrated luminosity at CMS}
+    \label{fig:CMS-Luminosity}
+\end{figure}

### 2025-05-16 thesis_julio/Chapter2/chapter2.tex
may16

@@
 It consist on different detectors made for different purposes, the silicon tracker, the electromagnetic calorimeter (ECAL), the hadron calorimeter (HCAL) the superconducting solenoid and the muon chamber.
-\\
-\begin{figure}[h]
+
+\begin{figure}[H]
     \centering
-     \includegraphics[width=1\textwidth]{cms2.png}
+     \includegraphics[height=0.73\textwidth, width=1\textwidth]{cms2.png}
      \caption{The CMS detector size comparison with each of their components}
@@
 
-\\
 The CMS has the form of a cylindrical onion with several concentric layers of components, this components are important to determine the properties of different particles all of this by bending their trajectories with a magnet that bend charged particles, this helps to identify the charges of the particles since they bend in different directions and allows to measure the momentum of a particle sine high momentum particles bend less than the low momentum ones.
@@
 
-\begin{figure}[h]
-    \centering
-     \includegraphics[width=1\textwidth]{cms3.png}
-     \caption{Layout of the CMS Innertracker includin the Pixel Detector, and other substructures TIB, TOB, TID and TEC}
-    \label{fig:inner-track}
-\end{figure}
+%\begin{figure}[H]
+   % \centering
+     %\includegraphics[width=1\textwidth]{cms3.png}
+     %\caption{Layout of the CMS Innertracker includin the Pixel Detector, and other substructures TIB, TOB, TID and TEC}
+    %\label{fig:inner-track}
+%\end{figure}
 
@@
 which are also stopped here.
-\\
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
@@
 
-\\
 The CMS was optimized for the detections of muons and is the last particle that the CMS observe directly with the help of the muon chambers that is composed by many subdetectors which are interleaved with the return of the yoke of the solenoid located after the super conducting solenoid, muons are similar to electrons but 200 times heavier so they are not stopped by the calorimeters, the muon chambers have 3 main purposes; muon identification, momentum measurement and triggering.
@@
 
-For the tracking
-
-\section{Pixel Cluster Counting}
+\section{Cluster Identification}
 
@@
 The mean number of pixel clusters in a simulated zero bias event is in the order of 100 per pp collision.
-The number of pixel clusters per bunch crossing is linearly dependent on pileup and therefore an accurate measure of the instantaneous luminosity.\cite{PCC1} The mean number of pixel cluster per trigger is \\
+The number of pixel clusters per bunch crossing is linearly dependent on pileup and therefore an accurate measure of the instantaneous luminosity.\cite{PCC1} The mean number of pixel cluster per trigger is
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1\textwidth]{cluster2.jpg}
+    \caption{Cluster}
+    \label{fig:cluster}
+\end{figure}
 
@@
 
-here f is the frequency of the LHC, defining a new quantity $\simga_{cluster}$ = $\simga_{i}<N_{Pixel/Interaction}> $ and combining equation (2.1) and (2.2) we got
+here f is the frequency of the LHC, defining a new quantity $\sigma_{cluster}$ = $\sigma_{i}<N_{Pixel/Interaction}> $ and combining equation (2.1) and (2.2) we got
 
@@
 
-From the total of 1856 modules on the pixel detector (1184 on the BPIX and 672 on FPIX) so in the analysis for the pcc vdm calibration onf 2024 for the fill 9639a total of 240 modules were used.
+A module veto list is created that removes modules that have unstable behavior in the cluster counting, to the determine the number of modules excluded the stability of their contribution to the total (the module weight) is studied.
+This selection is made using the zero bias datasets using two steps, first a selection on the stability over time and then a selection of stability vs instantaneous luminosity.
+For the stability selection different datasets are used, depending on the dataset you obtain time profiles per module and the absolute value of the deviation from the mean weight and averaged, this process is iterate for every module to remove outlier modules.
+For the linearity selection the module weight is evaluated as a function of quantity which is proportional to the instantaneous luminosity this quantity being the average PCC per module, the image (2.6) shows the difference between a good module and a bad module.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[height=0.35\textwidth ,width=1\textwidth]{module.png}
+    \caption{Comparison between two modules with average PCC in 100 LS. Good module on the left, bad module on the right.}
+    \label{fig:modules}
+\end{figure}
+
+To obtain the number of modules that are damaged and can exhibit issues with stability and linearity and can affect the final luminosity measurements the following steps were followed:
+
+\begin{itemize}
+  \item First, all of the BPIX Layer 0 Modules are removed since they are consistently unstable.
+  \item Then modules based on the noise level are removed in the vdm fill super separation data. 
+  \item Remove modules with no clusters in the vdm fill this means with weight=0 
+  \item Compare stability parameters between modules and remove outliers in the vdm fill
+  \item Compare stability parameter for each block of data and perform a second iteration if necessary
+  \item Compare linearity parameter between modules and remove outliers
+\end{itemize}
+
+The pixel detector has a total of 1856 modules (1184 on the BPIX and 672 on FPIX) in this analysis for the pcc vdm calibration on 2024 for the fill 9639, a total of 1616 modules were removed for a total of 240 modules with 193 in the BPIX part of the detector and the other ones on the FPIX part.

### 2025-05-16 thesis_julio/Portada/Portada.tex
commit1
may16

--- 2022-12-29 tesis_Rodolfo/Portada/Portada.tex
@@
         \vspace{.4cm}   %% DEFINE EL ESPACIO ENTRE LA DOBLE LINEA Y EL NOMBRE DE LA DIVISIÓN
-        {\scshape \large Divisi\'on de Ciencias Exactas y Naturales}
+        {\scshape \large Facultad Interdisciplinaria de Ciencias Exactas y Naturales} \\
         {\scshape Departamento de Investigaci\'on en F\'isica} %% NOMBRE DE LA DIVISIÓN
@@
       \vspace{2cm}
-        {\Large \scshape {Measurements of the Large Hadron Collider luminosity using the CMS silicon pixel detector}}
+        {\Large \scshape {Calibration of the Pixel Detector at CMS}}
 
@@
         By:\\[12pt]
-        \textbf{  {\large Jesus Rodolfo MORENO CHAVEZ}}
+        \textbf{  {\large JULIO C\'ESAR BORB\'ON FRAGOSO}}
 
@@
 
-        { \large Director}:\\Dr. Jose Feliciano BENITEZ RUBIO
+        { \large Director}:\\DR. JOSE FELICIANO BENITEZ RUBIO
 

### 2025-05-23 thesis_julio/Chapter1/chapter1.tex
23may

@@
 
-\section{Luminosity}
+\section{Cross Section}
 
@@
 
-The performance of a collider is determined by the beam energy and the luminosity. The cross section It's known as parameter like "the size of a target"
+The performance of a collider is determined by the beam energy and the luminosity.
+First we are going to define the cross section in a classical way the cross section area is parameter of interest that could say that measure the size of a target, this cross sectional area is presented to a stream of incoming particles, this is similar in the case of the scattering in elementary particles, if you fire a electron beam into a proton tank the parameters of interest are the size of the proton and the cross sectional area $\sigma$ that presents the incident beam.
+This collision differs to the classic case in some ways, first you could call the target soft since It's not a possible collision more like the closer you get the greater the deflection, the electrons scatters off the hydrogen, various interactions are happening during this and each one has a It's own scattering cross section $\sigma_{i}$ nevertheless in the experiment we are interested in the total cross section which can be seen as the sum of all the cross sections.
+
+\begin{equation}
+\sigma_{tot} = \Sigma^{n}_{i=1} \sigma_{i}
+\end{equation}
+
+Each of this cross sections depends typically in the velocity of the incident particle, It's expected that the cross section would be proportional to the time that the incident particle spends close to It's target which means that $\sigma$ is inversely proportional to the velocity but this behavior is altered close to the region of a energy that particles involved to interact forming a short lived semi-state before breaking apart, things like this make the cross section for elementary particles different to the classic one.
+
+To explain the cross section when a target is soft lets supposed a electron encounter a potential and scatters at the angle $\theta$, this scatter is angle is a function of a impact parameter b the distance by which this particle would have missed the scattering center had it continued on its original trajectory.
+The form of $\theta(B)$ depends on the potential and the smaller the impact parameter b, larger the deflection.
+If the particle comes with an impact parameter between b and b + db it will merge in a angle between $\theta$ and $\theta + d\theta$ and even in a more general case if it passes through a infinitesimal area $d\sigma$ it will scatter into a corresponding solid angle $d\Omega$, the larger $d\sigma$ is the larger $d\Sigma$ the proportionality factor between these two is called the differential cross section D this can be illustrated in the next image:
+
+\begin{figure}[h]
+    \centering
+   \includegraphics[width=1\textwidth]{cross1.png}
+    \caption{Particle scattering}
+    \label{fig:cross}
+\end{figure}
+
+The relation between $d\sigma$ and $d\Omega$ is:
+
+\begin{equation}
+d\sigma = D(\theta)d\Omega
+\end{equation}
+
+Supposing a beam of incoming particles with a value L that is associated with the number of particles passing down the line per unit of time and per unit of area $dN = L d\sigma $ is the number of particles per unit time passing trough area $d\sigma$ and hence also the number per unit of time scattered into solid the solid angle $d\Omega$
+
+\begin{equation}
+dN = L d\sigma = LD(\theta) d\Omega 
+\end{equation}
+
+This could be seeing as the one who controls the number of particles going through the detector also determined the solid angle.
 
@@
 
+%\begin{equation}
+%rate = flux x number of target particles x cross section
+%\end{equation}
+
+%And we can define the cross section as follow:
+
+%\begin{equation}
+%\sigma = \frac{number of interaction per unit of time per target particle}{incident flux}
+%\end{equation}
+
+\section{Luminosity}
+
+The performance of a collider is determined by the beam energy and the luminosity, theluminosity is a key parameter in particle colliders is a quantity that measures the ability of a particle accelerator to produce a required number of interactions\cite{Lum}
+
 \begin{equation}
-rate = flux x number of target particles x cross section
+N = L \cdot \sigma_{p} 
 \end{equation}
 
-And we can define the cross section as follow:
-
-\begin{equation}
-\sigma = \frac{number of interaction per unit of time per target particle}{incident flux}
-\end{equation}
-
-The luminosity is a key parameter in particle colliders is a quantity that measures the ability of a particle accelerator to produce a required number of interactions and is given by: \cite{Lum}
-
-\begin{equation}
-\frac{dR}{dt} = \mathcal{L} \cdot \sigma_{p} 
-\end{equation}
-
-In which $\frac{dR}{dt}$ is the number of events per second, the $\simga_{p}$ is the cross section and $\matchcal{L}$ the instantanious luminosity luminosity.
-The unity of $\mathcal{L}$ is  $cm^{-2} s^{-1}$ a higher luminosity means greater probability that the particles will collide and produce the desired interactions, luminosity can be increased then in two ways, packing more particles into the beams or focusing this beams more.
+In which N is the number of events per second, the $\simga_{p}$ is the cross section and L the instantanious luminosity luminosity.
+The unity of L is  $cm^{-2} s^{-1}$ a higher luminosity means greater probability that the particles will collide and produce the desired interactions, luminosity can be increased then in two ways, packing more particles into the beams or focusing this beams more.
 
@@
 two beams moving towards each other, the position and the time as the cross each other also need to be considered and calling the distance to the collision point $s_{0}$.
-In principle each of the distributions is different the overlap integral can be written as follow:
+The figure (1.x) shows a  In principle each of the distributions is different the overlap integral can be written as follow:
 
@@
 
+In principle each of the distributions is different and we can write the overlap integral as follow:
 %$K = sqrt{(v_{1} - x_{2})^{2} - \frac{(v_{1} x v_{2})^{2}}{c^{2}} }
@@
 
-it is related directly to the number of observed events
+it is related directly to the number of observed events $L_{int} \cdot \sigma_{p}$ number of events of interest.
+
+In the LHC there are various ways to measure the luminosity, in the CMS there are various of them, the Pixel Luminosity Telescope, the BCM1F, the radiation monitoring system for environment & safety, the muon drift tubes, the forward hadron calorimeter and the Pixel Cluster Counting (PCC).
+
+The PCC luminometer method consist in counting the average number of pixel clusters on the detector to measure luminosity.
+This occurs during a zero bias event, an event that is trigged by requiring only that two proton bunches cross at the CMS interaction point.
+Giving that the number of pixels in really big the probability that a pixel is being hit by two different tracks by the same bunch crossing is really small.
+The mean number of pixel clusters in a simulated zero bias event is in the order of 100 per pp collision.
+The number of pixel clusters per bunch crossing is linearly dependent on pileup and therefore an accurate measure of the instantaneous luminosity.\cite{PCC1} The mean number of pixel cluster per trigger is
 
 \begin{equation}
-L_{int} \cdot \sigma_{p} = number of events of interest 
+<N_{cluster}> = <N_{Pixel/Interaction}> <N_{interaction}> = <N_{Pixel/interaction}> \mu 
 \end{equation}
+
+here the $\mu$ is the number of interactions and with this the following equation and gives us a relation with the cross section $\simga_{i}$, instant luminosity and $\mu$ and for the obtention of the luminosity value:
+
+\begin{equation}
+<N_{cluster}> = \frac{\sigma_{cluster}}{f} \frac{dL}{dt}
+\end{equation}
+
+Here, the value of $N_{cluster}$ is the mean number of pixel clusters on the pixel detector during a zero bias trigger at a head on period, the value of $\sigma_{cluster}$ can be obtained using the Van Der Meer scan and from the equation (2.3) we can obtain the luminosity from \cite{PCC2}
 

### 2025-05-23 thesis_julio/Chapter2/chapter2.tex
23may

@@
 
+\begin{figure}[H]
+    \centering
+    \includegraphics[height=0.55\textwidth, width=1\textwidth]{PixelSensor.png}
+    \caption{The pixel detector silicon sensor and the readout chip.}
+    \label{fig:sensor}
+\end{figure}
+
 \section{Cluster Identification}
 
-The Pixel Cluster Counting (PCC) method consist in counting the average number of pixel clusters on the detector to measure luminosity.
-This occurs during a zero bias event, an event that is trigged by requiring only that two proton bunches cross at the CMS interaction point.
-Giving that the number of pixels in really big the probability that a pixel is being hit by two different tracks by the same bunch crossing is really small.
-The mean number of pixel clusters in a simulated zero bias event is in the order of 100 per pp collision.
-The number of pixel clusters per bunch crossing is linearly dependent on pileup and therefore an accurate measure of the instantaneous luminosity.\cite{PCC1} The mean number of pixel cluster per trigger is
+In the pixel detector the charged produce by charged particles passing through the silicon layers, this charge is collected by the read-out chips.
+This charge in general is shared between more than one pixel forming a pixel cluster, this clusters can be made by either the particle track which have a small angle of incidence with the silicon sensor or because of the charge drifting in the magnetic field of 4 Tesla in which the tracking system is immersed.
+Before the process of irradiation the charge sharing is uniform in local X and Y directions, even then, the reconstructions of the true hits It's not trivial.
+After the detector is irradiated, the defects developed in the silicon lattice act as charges traps so that the free charge can only partially reach the readout chips, consequently the pixel clusters become smaller \cite{cluster1}
 
@@
     \centering
-    \includegraphics[width=1\textwidth]{cluster2.jpg}
+    \includegraphics[width=1\textwidth]{cluster3.png}
     \caption{Cluster}
@@
 
-\begin{equation}
-<N_{cluster}> = <N_{Pixel/Interaction}> <N_{interaction}> = <N_{Pixel/interaction}> \mu 
-\end{equation}
-
-here the $\mu$ is the number of interactions and with this the following equation and gives us a relation with the cross section $\simga_{i}$, instant luminosity and $\mu$
-
-\begin{equation}
-\mu = \frac{\sigma_{i}}{f}\frac{dL}{dt}
-\end{equation}
-
-here f is the frequency of the LHC, defining a new quantity $\sigma_{cluster}$ = $\sigma_{i}<N_{Pixel/Interaction}> $ and combining equation (2.1) and (2.2) we got
-
-\begin{equation}
-<N_{cluster}> = \frac{\sigma_{cluster}}{f} \frac{dL}{dt}
-\end{equation}
-
-Here, the value of $N_{cluster}$ is the mean number of pixel clusters on the pixel detector during a zero bias trigger at a head on period, the value of $\sigma_{cluster}$ can be obtained using the Van Der Meer scan and from the equation (2.3) we can obtain the luminosity from \cite{PCC2}
-
-\begin{equation}
-\sigma_{cluster} = <N_{cluster}> f (\frac{dL}{dt})^{-1}
-\end{equation}
+The first step to the reconstruction process is referred to as local reconstruction.
+It consist of the clustering of zero-suppressed signals above specific thresholds in pixel and strip channels into hits, and then estimating the cluster positions and their uncertainties defined in a local orthogonal coordinate system (u, v) in the plane of each sensor.
+\cite{cluster2}
 

### 2025-05-30 thesis_julio/Chapter1/chapter1.tex
30may

@@
 
-Supposing a beam of incoming particles with a value L that is associated with the number of particles passing down the line per unit of time and per unit of area $dN = L d\sigma $ is the number of particles per unit time passing trough area $d\sigma$ and hence also the number per unit of time scattered into solid the solid angle $d\Omega$
+Supposing a beam of incoming particles with a value F that is associated with the number of particles passing down the line per unit of time and per unit of area $dN = F d\sigma $ is the number of particles per unit time passing trough area $d\sigma$ and hence also the number per unit of time scattered into solid the solid angle $d\Omega$
 
 \begin{equation}
-dN = L d\sigma = LD(\theta) d\Omega 
+dN = F d\sigma = fD(\theta) d\Omega 
 \end{equation}
 
-This could be seeing as the one who controls the number of particles going through the detector also determined the solid angle.
+This is a classical description of scattering and could be seen as the one who controls the number of particles going through the detector also determined the solid angle.
+Here we have the incident flux F and a cross sectional area and are a way to interpret collision rates in modern particle accelerators since in high energy physics this structure is similar with a quantity called luminosity L with Its own cross section $\sigma$.
+
+Even when the dynamics are different for the quantum field theory case, the general principle remains the same, when we have a  higher the cross section we obtain a higher luminosity and Its more likely to observer determined events.
 
@@
 
-The performance of a collider is determined by the beam energy and the luminosity, theluminosity is a key parameter in particle colliders is a quantity that measures the ability of a particle accelerator to produce a required number of interactions\cite{Lum}
+The performance of a collider is determined by the beam energy and the luminosity, the luminosity is a key parameter in particle colliders is a quantity that measures the ability of a particle accelerator to produce a required number of interactions\cite{Lum}
 
 \begin{equation}
-N = L \cdot \sigma_{p} 
+R = L \cdot \sigma_{p} 
 \end{equation}
 
-In which N is the number of events per second, the $\simga_{p}$ is the cross section and L the instantanious luminosity luminosity.
+In which R is the number of events per second or rate, the $\sigma_{p}$ is the cross section which in the quantum case is a probability of interaction which can be obtained from the standar model of particle physics and L the instantanious luminosity.
 The unity of L is  $cm^{-2} s^{-1}$ a higher luminosity means greater probability that the particles will collide and produce the desired interactions, luminosity can be increased then in two ways, packing more particles into the beams or focusing this beams more.
@@
 two beams moving towards each other, the position and the time as the cross each other also need to be considered and calling the distance to the collision point $s_{0}$.
-The figure (1.x) shows a  In principle each of the distributions is different the overlap integral can be written as follow:
+The figure (1.x) shows two beams colliding which depends on a variety of factors:
 
@@
 
-In principle each of the distributions is different and we can write the overlap integral as follow:
+Following this we can write the integral for luminosity, in principle each of the distributions is different and we can write the overlap integral as follow:
 %$K = sqrt{(v_{1} - x_{2})^{2} - \frac{(v_{1} x v_{2})^{2}}{c^{2}} }
@@
 \begin{equation}
- 2N_{1}N{2}fN_{b} \int \int \int^{\infty}_{-\infty}  \rho_{1x} (x) \rho_{1y}(y) \rho_{1s} (s-s_{0}) \rho_{2x}(x) \rho_{2y}(y) \rho_{2s} (s+s_{0}) dxdydsds_{0}  
+ L = 2N_{1}N{2}fN_{b} \int \int \int^{\infty}_{-\infty}  \rho_{1x} (x) \rho_{1y}(y) \rho_{1s} (s-s_{0}) \rho_{2x}(x) \rho_{2y}(y) \rho_{2s} (s+s_{0}) dxdydsds_{0}  
 \end{equation}
 
-With N1 and N2 being the bunch intensity, f the revolution frecuency, $N_{b}$ the number of colliding bunches, $\rho_{1}$ and $\rho_{2}$ time dependent beam density distribution functions, this is assuming the velocity on the beams is $v1 = -v2$ and the densities are uncorrelated in all planes the overlap integral takes the form of: \cite{Lumvdm}
+With N1 and N2 being the bunch intensity, f the revolution frecuency, $N_{b}$ the number of colliding bunches, $\rho_{1}$ and $\rho_{2}$ time dependent beam density distribution functions and assuming the densities are uncorrelated in all planes.
+\cite{Lumvdm}
 

### 2025-05-30 thesis_julio/Chapter2/chapter2.tex
30may

@@
 It consist of the clustering of zero-suppressed signals above specific thresholds in pixel and strip channels into hits, and then estimating the cluster positions and their uncertainties defined in a local orthogonal coordinate system (u, v) in the plane of each sensor.
+The sensor has a total of 100 x 150 $\mu m^{2}$ pixels with the u axis oriented parallel to the shorter pixel edge and for the strip sensors the u-axis is perpendicular to the central strip in the sensors.
 \cite{cluster2}
+
+During the data acquisition on the pixel detector a zero suppresion is performed in the readout chips of the sensors, with adjustable threshold for each pixel.
+This pixels read-out threshold is set to a single pixel equivalent to a charge of 3200 electrons.
+Offline, pixel clusters are formed from adjacent pixels.
+Each of these clusters must have a minimum charge of at least 4000 electrons.
+Misscalibration of residual charges caused by the pixel to pixel differences of the charge injection capacitors, which are used to calibrate pixel gain are extracted from laboratory measurements and the Monter Carlo simulator.
+
+There are two algorithms for determine the positions of the pixel clusters, a fast one that is called first pass hit reconstruction and is used during the track seeding and pattern recognition and the second algorithm called template based hit reconstruction which is more precise and is based on cluster shapes and used in the final track fit.
 
@@
 
-The pixel detector has a total of 1856 modules (1184 on the BPIX and 672 on FPIX) in this analysis for the pcc vdm calibration on 2024 for the fill 9639, a total of 1616 modules were removed for a total of 240 modules with 193 in the BPIX part of the detector and the other ones on the FPIX part.
+On summary, in the analysis for the PCC vdm calibration on 2024 for the fill 9639, a total of 1616 modules were removed for a total of 240 good modules with 193 in the BPIX part of the detector and the other ones on the FPIX part.

### 2025-05-30 thesis_julio/Chapter3/chapter3.tex
30may

@@
  \begin{equation}
-N_{1} N_{2} f  \int \int \rho_{1}(x,y)\rho_{2}(x+\Delta x, y+\Delta y) dxdy   = N_{1} N_{2} f (\int \rho_{1}(x)\rho_{2}(x + \Delta x) dx) (\int rho_{1}(y) \rho_{2}(y + \Delta y) dy)
+N_{1} N_{2} f  \int \int \rho_{1}(x,y)\rho_{2}(x+\Delta x, y+\Delta y) dxdy   = N_{1} N_{2} f (\int \rho_{1}(x)\rho_{2}(x + \Delta x) dx) (\int \rho_{1}(y) \rho_{2}(y + \Delta y) dy)
 \end{equation}
@@
 \begin{equation}
-N_{1} N_{2} f \int \rho_{1}(x) \rho_{2}(x + \Delta x_{0}) dx = \frac{L (\Delta X_{0}, Delta y_{0})}{\int L(\Delta x_{0}, \Delta y) d(\Delta y)}
+N_{1} N_{2} f \int \rho_{1}(x) \rho_{2}(x + \Delta x_{0}) dx = \frac{L (\Delta X_{0}, \Delta y_{0})}{\int L(\Delta x_{0}, \Delta y) d(\Delta y)}
 \end{equation}
@@
 \begin{equation}
-L(\Delta x, \Delta y) = N_{1} N_{2} f \frac{2R(\Delta x_{0}, \Delta y_{0}}{\int L(\Delta x_{0}, \Delta y) d(\Delta y) \int L(\Delta x, \Delta y_{0}) d(\Delta x)}
+L(\Delta x, \Delta y) = N_{1} N_{2} f \frac{2R(\Delta x_{0}, \Delta y_{0}}){\int L(\Delta x_{0}, \Delta y) d(\Delta y) \int L(\Delta x, \Delta y_{0}) d(\Delta x)}
 \end{equation}
@@
 \begin{equation}
-\sigma_{vis} = \frac{2 \pi \Sigma_{x} Sigma_{y} R(\Delta x_{0} \Delta y_{0})}{N_{1} N_{2}f}
+\sigma_{vis} = \frac{2 \pi \Sigma_{x} \Sigma_{y} R(\Delta x_{0} \Delta y_{0})}{N_{1} N_{2}f}
 \end{equation}
@@
  \hline
- SS6 &  & 1715943343  \\
+ SS4 &  & 1715943343  \\
  \hline
@@
 
-This is the mean value of each super separation off al the bcids a total of 60 mean values were obtained
+This is the mean value of each super separation off al the bcids a total of 60 mean values were obtained and was $ss_background$ = 0.0251 +-0.0018 in the following picture we can see the
 
 \section{Corrections}
+
+A few corrections were taken into consideration to eliminate noise data from another sources during this vdm calibration, this corrections are applied by the vdm framework.
+
+\begin{itemize}
+  \item \textbf{Background} The rates substracted on the SS periods and is associated with the luminometer itself see section (3.x) for more.
+  \item \textbf {Ghost Satellite} This correction have to be with the charge that comes from the non colliding bunches, which are called ghost and those who are leaking from the main radio frequency bucket into another bucket which are called satellite.
+This currents have an effect on the $\sigma_{visible}$ measure because of the contribution on the charges, this charges are substracted from the beam currents.
+\cite{ghost}
+  \item \textbf{BeamBeam} This are deflections that happen between bunch crossings, accounting for the electrical repulsion of the beams which increases the lateral separation.   \cite{beambeam}
+  \item \textbf{Dynamic beta} This correction accounts for any changes in the proton density distributions of the bunches due to the single particle interaction, resulting into a non linear change during separation steps in transverse bunch profiles and can be described as the effective changes of a called $\beta$ value.
+\cite{LHClum}
+\end{itemize}
 
@@
 
+For the main calibration we used the QG fit this fit uses the parameter $\sigma$, the peak and a q values as the parameters. This fit is given by the following equation:
+
+\begin{equation}
+f_{qg}(x,y) = \frac{V}{C(q) \sigma_{x} \sigma_{y}\sqrt{1-\chi^{2}}} e_{q}(\frac{\ r^{2}}{(4-2q)}) 
+\end{equation}
+
+with $e_{q}$ being a function of x defined as:
+
+\begin{equation}
+e_{q}(x) = (1+(1-q)x)^{\frac{1}{1-q}}
+\end{equation}
+
+and $c(q)$ having two different values depending on the value of the q, for q < 1:
+
+\begin{equation}
+c(q) = \frac{4-2q}{1-q} \pi \frac{\Gamma (\frac{2-q}{1-q})}{\Gamma (\frac{2-q}{1-q} + 1)}
+\end{equation}
+
+and for the other cases:
+
+\begin{equation}
+c(q) = \frac{4-2q}{q-1} \pi \frac{\Gamma (\frac{1}{q-1} - 1)}{\Gamma (\frac{1}{q-1})}
+\end{equation}
+
 \section{Beam Parameters}
+
+The beam parameters of the vdm scan were obtained after the vdm framework run on the fit, one of the parameters obtained was the peak:

### 2025-06-02 thesis_julio/Chapter3/chapter3.tex
2june1

@@
 
-The background estimation is obtained during the super separation (SS) process, since the SS scan separates the beams so they shouldn't be colliding the expected value on the rate is expected to be a rate associated with the background, this is then estimated by checking each of the SS scans on the time window referred on the table (3.1), the mean value during this period is assumed to be the mean value of the SS period, in the following table we see the mean PCC value for each period.
+The background estimation is obtained during the super separation (SS) process, since the SS scan separates the beams so they shouldn't be colliding the expected value on the rate is expected to be a rate associated with the background, this was obtained checking the mean values for each bcid for all the entries of pcc rates for each of the 5 periods of super separation, is is illustrated in the next image:
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.8\textwidth]{sshist.png}
+    \caption{SS periods histograms showing entries for bcid 5 }
+    \label{fig:SShist}
+\end{figure}
+
+this is then estimated by checking each of the SS scans on the time window referred on the table (3.1), the mean value during this period is assumed to be the mean value of the SS period, in the following table we see the mean PCC value for each period.
 
@@
 
-This is the mean value of each super separation off al the bcids a total of 60 mean values were obtained and was $ss_background$ = 0.0251 +-0.0018 in the following picture we can see the
+This is the mean value of each super separation off al the bcids
+
+ a total of 60 mean values were obtained and was $ss_background$ = 0.0251 +-0.0018 in the following picture we can see the
 
@@
 
+The fit model on the vdm data is illustrated in both planes X and Y in the following image:
+
+%\begin{figure}[H]
+  %  \begin{subfigure}{0.5\textwidth}
+    %\centering
+    %\includegraphics[width=0.5\textwwidth]{fitqg1.png}
+    %\includegraphics[width=0.5\columnwidth]{fitqg2.png}
+    %\caption{QG Fit on X plane and Y plane}
+    %\label{fig:QGfit}
+%\end{figure}
+
+As well we can see that the matrix values of the fit converged since the matrix covalue is 3 which is expected when a convergence ocurres.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.9\textwidth]{QG_covStatus.png}
+    \caption{Covariance value showing that all bcids converged with the fit}
+    \label{fig:QGfit}
+\end{figure}
+
+And for the fit quality the value $\chi^{2}$
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.9\textwidth]{QG_chi2.png}
+    \caption{Fit quality values}
+    \label{fig:QGchi2}
+\end{figure}
+
 \section{Beam Parameters}
 
-The beam parameters of the vdm scan were obtained after the vdm framework run on the fit, one of the parameters obtained was the peak:
+The beam parameters of the vdm scan were obtained after the vdm framework run on the fit, one of the parameters obtained is the peak:
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.9\textwidth]{QG_peak.png}
+    \caption{QG peak values important on the computing of $\sigma_{visible}$}
+    \label{fig:QGpeak}
+\end{figure}
+
+And the $\Sigma_{x, y}$ values:
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.9\textwidth]{QG_CapSigma.png}
+    \caption{QG $\Sigma$ important to compute value of $\sigma_{visible}$}
+    \label{fig:QGcapsigma}
+\end{figure}

### 2025-06-03 project_Omar/paper.tex
to do: figures, references and final corrections

--- 2022-05-20 project_Luis/paper.tex
@@
 \usepackage{fancyhdr}
+\usepackage{amsmath}
+\usepackage{array}
+\usepackage[table]{xcolor}
 \pagestyle{fancy}
@@
 
-\def\Student{Luis Enrique CUEVAS PICOS }
-\def\Title{MASTERS THESIS PROJECT}
-\def\TitleESP{(ANTEPROYECTO)}
+\def\Student{OMAR ALEJANDRO ANGULO GIL}
+\def\Title{}
+\def\TitleESP{ANTEPROYECTO}
 \def\Prog{Maestria en Ciencias (F\'{i}sica) }
@@
 \def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
-\def\ProjectTitle{Studies of the CMS Pixel Cluster Counting luminometer using Run 3 data}
-\def\ProjectTitleESP{Estudios del luminometro Pixel Cluster Counting del CMS usando datos de la corrida 3}
-\def\ResearchLine{Fisica Matematica}
+\def\ProjectTitle{Determination of the calibration constant for the 2025 luminosity measurement in the CMS experiment}
+\def\ProjectTitleESP{}
+\def\ResearchLine{F\'{i}sica de altas energ\'{i}as}
 
 %%header and footer
-\lhead{\Student\ / \ \Dept}
+\lhead{\Student}
 \rhead{\TitleESP}
@@
 \newcommand{\instlumi}[1]{#1$\times 10^{34}$ cm$^{-2}$s$^{-1}$}
+%\newcommand{\Lum}[1]{}
 
@@
     {\bf \large \ProjectTitle  \par}
-    \vspace{\baselineskip}   
+
     \vspace{0.4cm}
-    TITULO:\par
-    {\bf \large \ProjectTitleESP \par}
+    %TITULO:\par
+    %{\bf \large \ProjectTitleESP \par}
   }
@@
   {
-    RESEARCH LINE (LGAC): \par
+    LGAC: \par
     \ResearchLine \par
@@
   {\bf \scshape \Student \par}
-  {Student\par}
+  {Estudiante\par}
 
@@
 
-%%%% Abstract Page
+%% Resumen
 \newpage
+\begin{center}
+  {\itshape\textbf{Resumen}\par}
+\end{center}
+
+\vspace{1 cm}
+
+El proyecto busca realizar análisis y calibración de los datos de luminosidad correspondiente a las mediciones hechas por el experimento CMS para la recta final de la Run 3, durante 2025.
+Se utiliza para la medición el método PCC (por sus siglas en inglés, Pixel Cluster Counting) que consiste en el conteo de grupos de píxeles activados en el detector.
+Esto nos permitirá medir con precisión el valor de luminosidad para los datos recabados durante este año.
+La luminosidad y su incertidumbre sistemática son parámetros de suma importancia para las mediciones de física realizadas en los experimentos en el LHC.
+
 \hspace{2pt}
@@
 
+%%%% Abstract Page
+\newpage
+
+%\hspace{2pt}
+%\vfill
+
   \begin{center}
-    {\Large \ProjectTitle \par}
-    \vspace{1cm}
+%    {\Large \ProjectTitle \par}
+%    \vspace{1cm}
     {\itshape\textbf{Abstract}\par}
@@
 
-  This  project consists on  perform an analysis and calibration of the LHC luminosity data recorded
-  by the CMS experiment during the new phase starting in 2022 (Run 3) using the Pixel Cluster Counting (PCC) method.
-%to develop the upgraded luminosity measurement system for Run 3 and the HL-LHC phases.
-Luminosity gives a measure of how many collisions are happening in a particle accelerator  and a precise determination of this will allows us precise tests of the Standard Model and searches for new physics like dark matter and supersymmetry theories.
-The PCC method is an offline technique for the calculation of instantaneous luminosity  by counting the number of pixel clusters in the detector.
-The high densities of pixels of the Inner Tracker of the CMS detector gives a low hit occupancy in the sensors during the proton-proton collisions, this leads to a very linear response and small  uncertainties for the luminosity measurement.
+The projects seeks to analyze and calibrate the luminosity corresponding to the measurements made by the CMS experiment for the final stretch of run 3, during 2025.
+The method used to measure this is Pixel Cluster Counting (PCC), which consists in counting groups of activated pixels in the detector.
+This will let us measure with precision the value of the luminosity parameter for data collected this period.
+Along with its systematic uncertainty, luminosity are parameters of utmost importance for physics measurements in LHC experiments.
+
   \hspace{2pt}
@@
 
-The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary particles mediated by three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the weak nuclear force.
-The SM is divided into two categories, the bosonic sector and the fermionic sector.
-The bosonic sector contains particles which mediate the fundamental forces of nature and the fermionic sector contains particles which make up all known matter in our universe.
-There are three generations of fermion particles: the first generation consists of up (u) quark, down (d) quark, electron and electron neutrino, the second generation consist of charm (c) quark, strange (s) quark, muon and muon neutrino, and the third generation has the top (t) quark, bottom (b) quark, tau and tau neutrino.
-The bosonic sector consists of the gauge bosons: gluon, photon, $W^{\pm}$, $Z^0$ which mediate strong nuclear force, electromagnetic force and weak nuclear force respectively.
-The Higgs boson ($H$), is the last of the gauge bosons, it gives mass to the other SM particles via electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}.
-The heavy particles ($W^{\pm}$, $Z^0$, $H$, and top) can only be produced at high energy particle colliders like the Large Hadron Collider (LHC) operating at a center-of-mass energy of 13 TeV in Geneva, Switzerland (Figure ~\ref{figure5}).
-Until the 90s, existence of almost all the SM particles were confirmed except the top quark and the Higgs boson. 
-These had eluded previous experiments due to difficulties in the production and reconstruction of its decay products.
-The top quark was discovered in 1995 at the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center-of-mass energy of 1.8 TeV until 2010.
-In 2012, the ATLAS and CMS experiments, with detectors placed at two points where the proton beams collide in the LHC, announced the discovery of a new particle with a mass of 125 GeV.
-This particle has been identified as the Higgs boson by measuring its properties and comparing to those predicted by the SM.
+The fundamental forces are the most elemental known interactions in nature, and the four recognized are gravity, electromagnetism, and the weak and strong forces.
+Gravity and electromagnestism are long-range interactions, and thus easily noticeable, while the weak and strong forces are essential to describe interatomic interactions.
+Particle physics, also refered as high energy physics, are in charge of studying said interactions, in addition to the fundamental particles that form all matter, and the standard model (SM) has been the most successful theoretical model, describing with precision these forces, with the important exception of gravity.
+The SM is separated between bosons, which are known as the mediators of the aforementioned forces, and fermions, consisting of elementary particles that compose every other particle.
 
-Luminosity, $L$, is a key parameter at particle colliders along with the energy available in the collision.
-$L$ is one of the  main figures of merit that quantify the potential for observing new particles and measuring their properties.
-The instantaneous luminosity $L(t)$ is the process-independent ratio between the rate $R(t)$ of events produced per unit time and the cross section for a given process $\sigma$: $L(t) = R(t)/\sigma$.
+In the fermionic sector, leptons and quarks fall into three generations: first generation has the up (u) and down (d) quarks, as well as the electron and electron neutrino; second generation consists of charm (c) and strange (s) quarks, muon and muon neutrino; and the third generation contains the top (t) and bottom (b), plus the tau and tau neutrino.
+Each one of these has its corresponding antiparticle, having their properties (such as charge) reversed in sign.
+
+On the other hand, the bosonic sector is composed of the gauge bosons, which mediate every interaction: the gluon ($g$) for the strong nuclear force, $W^{\pm}$ and $Z^0$ bosons for weak nuclear force, and the photon ($\gamma$) for electromagnetic force.
+The model also includes the Higgs boson ($H$), which is the way to account for the mass of other SM particles, via electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}.
+
+Particles on the heavier side, such as the Higgs boson and the top quark (which were in fact, the last to be discovered), need a really high energy particle collider to be produced, like the Large Hadron Collider (LHC), that operates at a center-of-mass energy of 13.6 TeV in Geneva, Switzerland.
+It took multiple experiments, different colliders, and several years of upgrades on a long term plan to reach such high energies.
+So, it is indisputable that the energy of collision is one the most important parameter at particle colliders, but it is of similar significance to discuss and improve another parameter, called Luminosity.
+
+Luminosity measures the number of useful events in a collider experiment.
+Instantaneous luminosity shows the ability of a particle accelerator to produce said interactions.
+It is the process-independent ratio between the rate of events per second $R(t)$, and the cross section of the process $\sigma_p$, and its defined by\\
+
+\begin{equation}
+  R=\mathcal{L}_{inst} \cdot \sigma_{p}\\
+\end{equation}
+
+To evaluate the total number of events, the integrated luminosity is used. It measures the collected data size, and characterizes the performance of an accelerator, given by:\\
+
+\begin{equation}
+  \mathcal{L}_{int} = \int _{0}^{t} \mathcal{L}(t') dt' \\ 
+\end{equation}
+
 During Run 1 (2011-2012) LHC reached a peak instantaneous luminosity of \instlumi{0.77} and delivered an integrated luminosity of about \lumi{25} with a precision of about 2.0\% 
-\footnote{1 barn is a unit of area corresponding to $10^{-24}$ cm${^2}$ and 1 femtobarn (fb) = $10^{-39}$ cm$^{2}$.
-For comparison, the total Higgs production cross section is 48600 fb.}.
-In the first part of Run 2 (2015-2016), the delivered luminosity has been measured to be \lumi{38.4} with an unprecedented precision of 1.3\% \cite{Sirunyan:2021qkt-corr}.
-For the second part of Run 2 (2017-2018), the integrated luminosity is about \lumi{78}.
-%but its precise value and uncertainty remain to be determined and is the main objective of this thesis project \cite{CMS:2018elu-corr}.
-After many upgrades to the different parts of the experiment, Run 3 is restarting this year 2022.
-The main objective of this thesis project is to analize the first data recorded this year and provide a preliminary result of the luminosity recorded by the CMS experiment.
-
-The plan of the LHC till year 2038 is to obtain datasets with up to 10 times higher values of instanteneous luminosities in the final phase,
-the  High Luminosity LHC (HL-LHC), and corresponding integrated luminosities of order \lumi{3000} \cite{Dainese:3};
-the most updated projected luminosity performance along the  whole  life  of  LHC/HL-LHC  machine is shown Figure~\ref{figure6}.
-These final datasets will provide  precise measurements of the properties of the Higgs boson and other SM particles as shown in Fig. ~\ref{figureKappasUncs}.
-This figure shows that one of the dominant uncertainties which remain to be determined is due to the luminosity measurement.
-
+\footnote{1 barn is a unit of area corresponding to $10^{-24}$ cm${^2}$ and 1 femtobarn (fb) = $10^{-39}$ cm$^{2}$. For comparison, the total Higgs production cross section is 48600 fb.}
+In the first part of Run 2 (2015-2016), the delivered luminosity has been measured to be \lumi{38.4} with an unprecedented precision of 1.3\% \cite{Sirunyan:2021qkt}.
+For the second part of Run 2 (2017-2018), the integrated luminosity is about \lumi{78}, but its precise value and uncertainty remain to be determined \cite{CMS:2018elu-corr}.
+On the current LHC/HL-LHC plan, Run 3 began in 2022 and is planned to last until the first half of 2026, expecting and integrated luminosity of about \lumi{500}, as seen in figure \ref{figure1}.
+%The main porpuse is to determine the measurement corresponding to 2025 data
 \begin{figure}[H]
   \centering
-  \includegraphics[width=0.7\columnwidth]{./LHC-cpx-book.png}
-  \caption{Diagram of the LHC accelerator complex located near Geneva, Switzerland.
-The complex consists of the accelerator stages: Linear accelerator 2 (LINAC2; linear accelerator in which the protons are accelerated in bunches) , the Proton Synchrotron (PS), the Super Proton Synchrotron (SPS), and the 27 km LHC ring.
-Four collision points are shown corresponding to the ALICE, ATLAS, LHCb, and CMS detectors \cite{Zinser2018}.} % \cite{wiki:xxx}.} % Mobs:2684277
-  \label{figure5}
+  \includegraphics[width=0.85\columnwidth]{./LHCPlan.png}
+  \caption{CERN's current plan for reaching the High Luminosity LHC.
+The Long Shutdown 3 (LS3) is now scheduled starting July 2026, seven and a half months later than planned, and with a duration increased by four months.
+The start of Run 4 is now programmed for 2030 \cite{Lamont:2024}.}
+  \label{figure1}
 \end{figure}
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.8\columnwidth]{./lumint.png}
-  \caption{Forecast for peak luminosity (red dots) and integrated luminosity (violetline) in the HL-LHC era with nominal HL-LHC parameters\cite{BejarAlonso:2749422}.}  %\cite{collaborations2019report} era la [5] de la ant fig2
-  \label{figure6}
-\end{figure}
+CERN's LHC has four major colliding points, each one with its respective detector: CMS, ATLAS, ALICE and LHCb.
+The detector that will be worked here corresponds to the CMS, which stands for Compact Muon Solenoid, and its experiment has the general objective to investigate a wide range of physics within the standard model and beyond, primarily with proton collisions.
 
- \begin{figure}[H]
-   \centering
-   \includegraphics[width=0.7\columnwidth]{./pg.png}
-   \includegraphics[width=0.29\columnwidth]{./higgs_couplings.png}
-   \caption{
-     Left: Main production mechanisms for the Higgs boson at the LHC: gluon-gluon fusion (ggF), vector-boson fusion (VBF), associated vector boson (VH), associated top-quark pair (ttH), and  associated single-top quark production (tH)  \cite{Grojean:2017hsb-corr}  \cite{Khachatryan:2015ota} .
-     Right: Expected uncertainties on the Higgs coupling parameters for  \lumi{3000} of proton-proton collision data at 13 TeV center-of-mass energy \cite{Cepeda:2019klc-corr}.
-   }
-   \label{figureKappasUncs}
- \end{figure}
+The detector uses a powerful magnet to bend charged particles as they leave the point of collision, allowing to analyze its curvature to identify charge and measure their momentum.
+A silicon tracker, consisting of about 75 million sensors arranged in concentric layers, is in charge of measuring said curvature with high precision.
+It has the form of multiple cylindrical layers, and a large number of components.
+The electromagnetic calorimeter detects photons and electrons while the hadron calorimeter detects mostly pions ($\pi$) and kaons ($K$).
+Muons ($\mu$) are detected by special chambers outside the solenoid, as shown in .
 
-\section{PROPOSAL}
+%insertar imagen del detector
 
-We propose to perform an analysis and calibration of the LHC luminosity data recorded by the CMS experiment during the new phase starting in 2022 (Run 3) using the Pixel Cluster Counting (PCC) method.
-In particular, we plan to perform studies of detector components and the calibration data recording using the van Der Meer (vdM) scans that allow to obtain the calibration of this luminometer with high precision.
-%To develop the upgraded luminosity measurement system for Run 3 and the HL-LHC.
+The CMS silicon pixel detector consists of four concentric cylindrical layers and three disks on each end, placed at certain distances from the center of the detector.
+The detector consists of 1856 sensor modules, and gives complete coverage over the interaction point, resulting in precise tracking.
+This yields a large amount of total pixels, so, adding the sensor's fine granularity, the hit occupancy is very low.
+Due to this, the Pixel Cluster Counting (PCC) method brings forth a linear function of pile up, which is an essential property of a luminometer.
+The PCC method has been used as one of main luminometers for more than a decade, showing its reliability.
 
-\section{GENERAL OBJECTIVE}
+%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
 
-To perform an analysis and calibration of the LHC luminosity data recorded by the CMS experiment during the new phase starting in 2022 (Run 3) using the Pixel Cluster Counting (PCC) method.
-%To develop the upgraded luminosity measurement system for Run 3 and the HL-LHC phases.
-This will allows us precise tests of the Standard Model and searches for new physics like dark matter and supersymmetry theories.
+%\begin{figure}[H]
+  %\centering
+  %\includegraphics[width=0.8\columnwidth]{./HLLHCLumi.png}
+  %\caption{Forecast for peak luminosity (red dots) and integrated luminosity (violetline) in the HL-LHC era with nominal HL-LHC parameters\cite{BejarAlonso:2749422}.}  %\cite{collaborations2019report} era la [5] de la ant fig2
+  %\label{figure6}
+%\end{figure}
+
+ %\begin{figure}[H]
+   %\centering
+   %\includegraphics[width=0.6\columnwidth]{./pg.png}
+   %\includegraphics[width=0.39\columnwidth]{./Higgs-cross-sections-for-several-production-channels.png}
+   %\caption{
+     %Left: Main production mechanisms for the Higgs boson at the LHC: gluon-gluon fusion (ggF), vector-boson fusion (VBF), associated vector boson (VH), associated top-quark pair (ttH), and  associated single-top quark production (tH)  \cite{Grojean:2017hsb-corr}  \cite{Khachatryan:2015ota} .
+     %Right: Higgs boson cross sections for several production channels versus the LHC centre of mass energy  \cite{Cepeda:2019klc-corr}.
+   %}
+   %\label{figureKappasUncs}
+ %\end{figure}
+
+\section{OBJECTIVE}
+
+The objective is to analyze and calibrate the PCC luminometer for the 2025 recorded data by the CMS experiment, working with the PCC method and the van Der Meer (vdM) scans, allowing for a precise measurement of luminosity, and so, having access to more useful information to search for new discoveries.
 
@@
 
-For this preliminary measurement of the luminosity data collected in 2022, we expect that the methods used in this analisis will lead to a measurement uncertainty better than 2\%. 
-% \cite{Dainese:3}.
+Based on the analysis corresponding to previous years, a similar or better result is expected.
+With a systematic uncertainty of 1.4\% for 2022, and 1.3\% for 2023, it is possible to achieve a precision as good as this, if not an improvement.
 
@@
 
-~\ref{fig:CMS}.
+A pixel cluster is for a group of contiguous pixels activated by a charged particle.
+The method of choice, PCC, exploits the huge number of pixel in the interior part of the CMS pixel detector, which means that the probability that a single pixel is hit by two charged particles from the same bunch crossing is extremely small.%Be more specific about the interior part
 
-The PCC method for measuring luminosity uses the Pixel detector of the CMS tracker, the layout of the  detector used for recording the data during 2016-2018 is shown in Figure~\ref{fig:pixeldet}.
-The Pixel detector consists of 4 concentric cylindrical layers in the barrel and 2 disks in each endcap.
-Each detector part is composed of pixel sensors, a schematic of one sensor is shown in Figure~\ref{fig:pixeldet}.
-The entire Pixel detector contains 1856 sensor modules and a total of 65 million pixels.
+To ensure accurate and stable luminosity measurement, there is a detector module selection process, where a veto list is made each period and then combined for the entire year.
+This process involves determining the reliability of each module based on analyzing what is referred as the module weight, which is the change in the ratio of module PCC and total PCC.
+The veto list consists of modules excluded due to their known and suspected issues that affect the accuracy of the measurement, such as radiation damage, material defects, contamination, along other issues.
+At the end of said process, around 10\% of all modules are used.
 
-The PCC method consists of the reconstruction of track clusters produced by charged particle tracks as shown in Figure~\ref{fig:trackcluster}.
-Due to the fine granularity of the pixel sensors and the large number of total pixels, the hit occupancy in the sensors remains very small (order of 1\%) during physics runs.
-This low occupancy makes the PCC  very linear as a function of pileup, an essential property of a good luminometer.
+The LHC has two main types of runs: physics runs (which could be proton-proton, heavy-ion, or proton-lead collisions,) and callibration runs.
+As the title of the project suggests, callibration runs are the matter at hand, and consist of more controlled collisions to be able to measure luminosity and other parameters.
+In these runs, it is necessary to take into consideration a background noise contribution to the PCC rates.
+Each type of contribution is estimated independently during Super Separation (SS) periods, that are performed to separate two beams a certain distance for a selected period of time.
+To estimate the background value and its statistical error, the mean value and standard deviation are taken from the distribution resulting of a Y-projection of an average of pixel clusters per event ($\langle PCC \rangle$).
+Once the noise is taken into account, the data provided can be saved.
 
-The calibration of the luminometer consists of a van der Meer (vdM) scan performed in a special LHC run usually at the beginning of the run period (year).
-In this calibration setup, proton beams are moved across each other in separation steps of about 100 micrometers,
-by measuring the rates of clusters with the PCC algorithm and knowledge of the beam parameters during the vdM conditions, the calibration constant ($\sigma_{vis}$) is determined.
-This calibration constant is then used to normalize the measured PCC rates during normal running throughout the data-taking year \cite{pas:2018vdm}.
+To get the van der Meer (vdM) scan data, the pixel detector is read with a trigger of aproximately 50 kHz for about 10 BCIDs of the 140 that collide.
+The data is then saved distributed in 32 different datasets of events.
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.7\columnwidth]{./cms_layers.png}
-  \caption{Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimeter, superconducting solenoid and muon chambers \cite{Chatrchyan:2008aa}.}
-  \label{fig:CMS}
-\end{figure}
+%----------------------------------------------------------------------------------------------------------------------------------------------------
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.7\columnwidth]{./PixelDetectorPhase1.png}
-  \includegraphics[width=0.27\columnwidth]{./PixelSensor.png}
-  \caption{
-    Left: diagram showing the layout of the CMS Pixel detector used during 2016-2018.
-    The layout consists of 4 barrel layers and 2 endcap disks with two rings each.
-    Right: a diagram showing the structure of one pixel sensor.
-    The entire detector consists of 1856 sensors and 65 million pixels \cite{TrackerGroupoftheCMS:2020bgg}.
-  }
-  \label{fig:pixeldet}
-\end{figure}
+To calibrate the luminometer, the vdM scan technique is employed in a special LHC run, usually at the beginning of the year or period.
+To perform these scans, the separation between proton beams is varied in two dimensions, in separation steps of 100 micrometers.
+It measures the rates of clusters using the PCC algorithm and the beam parameters during vdM, to determine the calibration constant ($\sigma_{vis}$).
 
-\begin{figure}[H]
-  \centering
-  \includegraphics[width=0.5\columnwidth]{./bunchcrossing.jpg}
-  \includegraphics[width=0.4\columnwidth]{./vectorhit1.jpg}
-  \caption{
-    Left: Diagram showing the collision of two proton bunches at LHC, bunches contain about $10^{11}$ protons  \cite{deMaria:2008zzb}.
-    Right: diagram showing example tracks originating from the collision at the beamspot and producing clusters at the pixel sensors in two detector layers.
-  }
-  \label{fig:trackcluster}
-\end{figure}
+The definition of instantaneous luminosity for a single colliding bunch pair is
+
+\begin{align}
+  \mathcal{L}(\Delta x, \Delta y) &= N_1N_2f\int_{-\infty}^{\infty}\rho_1(x,y)\rho_2(x+\Delta x,y+\Delta y)dxdy \\
+  &= N_1N_2f\int_{-\infty}^{\infty}\rho_1(x)\rho_2(x+\Delta x)dx\int_{-\infty}^{\infty}\rho_1(y)\rho_2(y+\Delta y)dy
+\end{align}
+
+Where $N_1$ and $N_2$ correspond to the number of protons in colliding bunches, $f = 11245.6$ Hz is the frequency of revolution of the LHC, and $\rho_i$ is the proton density distribution of the i-th bunch, assumed Gaussian.
+For the method to be applicable, it is assumed that the density distributions factorize in the tranverse direction $x$ and $y$, as shown above.
+
+By integrating over either $\Delta$ (e.g. $x$)and substituting into (4), leads to
+
+\begin{center}
+  $\int\rho_1(y)\rho_2(y+\Delta y)dy=\frac{\int\mathcal{L}(\Delta x, \Delta y)d(\Delta x)}{N_1 N_2 f} \Rightarrow \mathcal{L}(\Delta x, \Delta y)=\int\rho_1(x)\rho_2(x+\Delta x)dx\int\mathcal{L}(\Delta x', \Delta y)d(\Delta x')$
+\end{center}
+
+and therefore
+
+\begin{equation}
+  \int\rho_1(x)\rho_2(x+\Delta x)dx=\frac{\mathcal{L}(\Delta x,\Delta y)}{\int\mathcal{L}(\Delta x', \Delta y)d(\Delta x')}
+\end{equation}
+
+Now, from equations (1), (4) and (5), taking $\Delta x=\Delta y=0$
+
+\begin{equation}
+  \mathcal{L}(0,0)=\frac{N_1N_2fR(0,0)R(0,0)}{\int R(\Delta x',0)d(\Delta x')\int R(0,\Delta y')d(\Delta y')}=\frac{N_1N_2f 2\pi}{\Sigma_x\Sigma_y}
+\end{equation}
+
+where the beam overlap widths $\Sigma_{x,y}$ are defined:
+
+\begin{equation}
+  \Sigma_{x,y}=\frac{1}{\sqrt{2\pi}}\frac{\int R_{x,y}(\Delta)d\Delta}{R_{x,y}(0)}
+\end{equation}
+
+and once again, from (1), we can define
+
+\begin{equation}
+  \sigma_{vis}=\frac{R(0,0)}{\mathcal{L}}=\frac{2\pi\Sigma_x\Sigma_yR(0,0)}{N_1N_2f}\\
+\end{equation}
+%%Si los dos haces son iguales, la dist estandar de ambas seria esta formula. El raiz de dos pi es asumiendo que las rho son distribuciones gaussianas
+
+The parameter $\sigma_{vis}$ is known as the calibration constant, and is used to normalize the measured PCC rates so the luminosity can be determined during normal running throughout the data-taking year.%reFERENCES!!!!!!!!!!!
+
+%----------------------------------------------------------------------------------------------------------------------------------------------------
+
+% \cite{pas:2018vdm}.
+
+%\begin{figure}[H]
+  %\centering
+  %\includegraphics[width=0.7\columnwidth]{./cms_layers.png}
+  %\caption{Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimeter, superconducting solenoid and muon chambers \cite{Chatrchyan:2008aa}.}
+  %\label{fig:CMS}
+%\end{figure}
+
+%\begin{figure}[H]
+  %\centering
+  %\includegraphics[width=0.7\columnwidth]{./PixelDetectorPhase1.png}
+  %\includegraphics[width=0.27\columnwidth]{./PixelSensor.png}
+  %\caption{
+    %Left: diagram showing the layout of the CMS Pixel detector used during 2016-2018.
+    %The layout consists of 4 barrel layers and 2 endcap disks with two rings each.
+    %Right: a diagram showing the structure of one pixel sensor.
+    %The entire detector consists of 1856 sensors and 65 million pixels \cite{TrackerGroupoftheCMS:2020bgg}.
+  %}
+  %\label{fig:pixeldet}
+%\end{figure}
+
+%\begin{figure}[H]
+  %\centering
+  %\includegraphics[width=0.5\columnwidth]{./bunchcrossing.jpg}
+  %\includegraphics[width=0.4\columnwidth]{./vectorhit1.jpg}
+  %\caption{
+    %Left: Diagram showing the collision of two proton bunches at LHC, bunches contain about $10^{11}$ protons  \cite{deMaria:2008zzb}.
+    %Right: diagram showing example tracks originating from the collision at the beamspot and producing clusters at the pixel sensors in two detector layers.
+  %}
+  %\label{fig:trackcluster}
+%\end{figure}
 
@@
 
+To warrant stable luminosity measurement for Run 3 2025, the set goals are:
+
 \begin{itemize}
-\item
-
+  %\item Process all the datasets. %% not a specific objective, a que se refiere %%
+  \item Apply a selection of good modules from the detector: To assure an accurate measurement, a veto list is made, taking only modules with relatively consistent contributions, and then used to only process zero bias PCC data for the vdM analysis.%Check module selection part
+  \item Measure the noise in the modules: A calculation of the background contributions, made during selected time windows, to account for secondary particles, and other unwanted parts.
+% Estimation over separation periods
+  %\item Select the time windows corresponding to the vdM scans. % Mentira, no entendi
+  \item Set the ideal model adjustment: The generated rates of the scan need to be fitted a mathematical function to extract the parameters needed.
+%% igual, no es especifico, basicamente checar ajuste segun el ruido %%
+  \item Measure the beam parameters $\Sigma_i$, conducting scans in the $x$ and $y$ directions, determined through curved fitting of the scan data. 
+  \item Measure the calibration constant $\sigma_{vis}$ to normalize the PCC rates. 
+  \item Determine the systematic uncertainties on the integrated luminosity: It is necessary to recognize the effects on the beam overlap measurement, and therefore the calculation of $\sigma_{vis}$, so corrections are to be applied.
 \end{itemize}
@@
 
+The work done in this thesis project is expected to yield the following results:
+
 \begin{itemize}
-\item
-
+  \item Obtain the PCC luminometer calibration constant $\sigma_{vis}$ for the 2025 data.
+  \item Estimate the background contribution for PCC during vdM calibration program.
+  \item Calculate the parts of the systematic uncertainty corresponding the work group.
 \end{itemize}
@@
 
-\begin{itemize}
-
-\item {\bf Summer 2021}:
-  \SubItem{ Readings on Standard Model of particle physics,  the LHC and CMS experiments}
-  \SubItem{ Linux/Computing skills (\textsc{Bash, Emacs, c/c++, python, ROOT})}
-  \SubItem{ Computing accounts at CERN and Fermilab}
-  \SubItem{ Initial planning of the analysis strategy}
-
-\item {\bf Semester 2021-2}:
-  \SubItem{ Course I: on particle physics, particle detection, or data analysis}
-  \SubItem{ Analysis/Computing skills (\textsc{Bash, Emacs, c/c++, python, ROOT})}
-  \SubItem{ Analysis of the LHC Run 2 luminosity data using the PCC method}
-
-\item {\bf Semester 2022-1}:
-  \SubItem{ Course II on particle physics, particle detection, or  data analysis}
-  \SubItem{ Completion of the analysis of the LHC Run 2 luminosity data using the PCC method}
-  \SubItem{ Presentation of results at national or international conference}
-  \SubItem{ Thesis writing}
-
-\end{itemize}
+\begin{center}
+  \begin{tabular}{|c|c|c|c|c|}
+    \hline
+    Task / Period & 2025-1 & Summer 2025 & 2025-2 & 2026-1 \\
+    \hline
+    Practice the programming tools & \cellcolor[HTML]{28B463} & \cellcolor[HTML]{28B463} & & \\
+    \hline
+    Study the literature involved & \cellcolor[HTML]{28B463} & \cellcolor[HTML]{28B463} & & \\
+    \hline
+    Calculate $\sigma_{vis}$ and its systematic uncertainty & & & \cellcolor[HTML]{F4D03F} & \\
+    \hline
+    Estimate the background contribution & & & \cellcolor[HTML]{F4D03F} & \\
+    \hline
+    Write the thesis & & & & \cellcolor[HTML]{E53935} \\
+    \hline
+    Defend the thesis & & & & \cellcolor[HTML]{E53935} \\
+    \hline
+  \end{tabular}
+\end{center}
 
 \onehalfspacing
-\bibliographystyle{unsrt}
+\bibliographystyle{unsrt} % y esto...........
 \bibliography{paper}

### 2025-06-03 project_Omar/compile.sh

@@ -1,0 +1,43 @@
+#!/bin/bash
+
+thesis="paper";
+
+if [ $1 = "clean" ]
+then
+	echo "Cleaning please wait ..."
+	rm -f *~
+	rm -rf *.aux
+	rm -rf *.bbl
+	rm -rf *.blg
+	rm -rf *.d
+	rm -rf *.fls
+	rm -rf *.ilg
+	rm -rf *.ind
+	rm -rf *.toc*
+	rm -rf *.lot*
+	rm -rf *.lof*
+	rm -rf *.log
+	rm -rf *.idx
+	rm -rf *.out*
+	rm -rf *.nlo
+	rm -rf *.nls
+	rm -rf $thesis.pdf
+	rm -rf $thesis.ps
+	rm -rf $thesis.dvi
+	rm -rf $thesis.spl
+	rm -rf *#* 
+	echo "Cleaning complete!"
+
+else
+	echo "Compiling ...!"
+	pdflatex -interaction=nonstopmode $thesis.tex
+	bibtex $thesis.aux 	
+	makeindex $thesis.aux
+	makeindex $thesis.idx
+	makeindex $thesis.nlo -s nomencl.ist -o $thesis.nls
+	pdflatex -interaction=nonstopmode $thesis.tex
+	makeindex $thesis.nlo -s nomencl.ist -o $thesis.nls
+	pdflatex -interaction=nonstopmode $thesis.tex
+	echo "Success!"
+
+fi

### 2025-06-06 project_Omar/paper.tex
to do: references

@@
 \def\Prog{Maestria en Ciencias (F\'{i}sica) }
-%\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
 \def\Dept{DIFUS}
@@
 
-%%%%Title Page
+%%%%%%%%%%%%%%%%%%%%%%%%TITLE PAGE%%%%%%%%%%%%%%%%%%%%%%%%%%%5
 \begin{titlepage}
@@
 
-%%%%% white page for print out
+%%%%%%%%%%%%%%%%%%%%%%%%%%%% white page for print out %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \shipout\null
 
-%% Resumen
+%%%%%%%%%%%%%%55% Resumen %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage
@@
 
-%%%% Abstract Page
+%%%%%%%%%%%%%%%%%%%%%%% Abstract Page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage
 
-%\hspace{2pt}
-%\vfill
-
   \begin{center}
-%    {\Large \ProjectTitle \par}
-%    \vspace{1cm}
     {\itshape\textbf{Abstract}\par}
@@
 
-%%%%%% Begin the body
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Begin the body %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage
@@
 In the first part of Run 2 (2015-2016), the delivered luminosity has been measured to be \lumi{38.4} with an unprecedented precision of 1.3\% \cite{Sirunyan:2021qkt}.
-For the second part of Run 2 (2017-2018), the integrated luminosity is about \lumi{78}, but its precise value and uncertainty remain to be determined \cite{CMS:2018elu-corr}.
+For the second part of Run 2 (2017-2018), the integrated luminosity is about \lumi{78}.
 On the current LHC/HL-LHC plan, Run 3 began in 2022 and is planned to last until the first half of 2026, expecting and integrated luminosity of about \lumi{500}, as seen in figure \ref{figure1}.
-%The main porpuse is to determine the measurement corresponding to 2025 data
+
 \begin{figure}[H]
@@
 The Long Shutdown 3 (LS3) is now scheduled starting July 2026, seven and a half months later than planned, and with a duration increased by four months.
-The start of Run 4 is now programmed for 2030 \cite{Lamont:2024}.}
+The start of Run 4 is now programmed for 2030 \cite{Lamont_2024}.}
   \label{figure1}
@@
 The electromagnetic calorimeter detects photons and electrons while the hadron calorimeter detects mostly pions ($\pi$) and kaons ($K$).
-Muons ($\mu$) are detected by special chambers outside the solenoid, as shown in .
+Muons ($\mu$) are detected by special chambers outside the solenoid, as shown in \ref{figure3}.
 
-%insertar imagen del detector
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.6\columnwidth]{./LHCcomplex.png}
+  \caption{Diagram of the LHC accelerator complex.
+It consists of three accelerator stages: the particle source, the Proton Synchrotron (PS), the Super Proton Synchrotron (SPS), and then the 27 km LHC ring.
+There are four collision points corresponding to the ALICE, ATLAS, LHCb, and CMS detectors  \cite{Mobs:2684277}.}
+  \label{figure2}
+\end{figure}
 
@@
 
-%------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.7\columnwidth]{./cms12.png}
+  \caption{Transverse cut of the CMS detector, showing the layers and disks mentioned, as well as the muon chambers \cite{Chatrchyan:2008aa}.}
+  \label{figure3}
+\end{figure}
 
@@
   %\centering
-  %\includegraphics[width=0.8\columnwidth]{./HLLHCLumi.png}
-  %\caption{Forecast for peak luminosity (red dots) and integrated luminosity (violetline) in the HL-LHC era with nominal HL-LHC parameters\cite{BejarAlonso:2749422}.}  %\cite{collaborations2019report} era la [5] de la ant fig2
-  %\label{figure6}
+  %\includegraphics[width=0.45\columnwidth]{./integratedlum.png}
+  %\caption{ }
+  %\label{figure 3}
 %\end{figure}
 
- %\begin{figure}[H]
-   %\centering
-   %\includegraphics[width=0.6\columnwidth]{./pg.png}
-   %\includegraphics[width=0.39\columnwidth]{./Higgs-cross-sections-for-several-production-channels.png}
-   %\caption{
-     %Left: Main production mechanisms for the Higgs boson at the LHC: gluon-gluon fusion (ggF), vector-boson fusion (VBF), associated vector boson (VH), associated top-quark pair (ttH), and  associated single-top quark production (tH)  \cite{Grojean:2017hsb-corr}  \cite{Khachatryan:2015ota} .
-     %Right: Higgs boson cross sections for several production channels versus the LHC centre of mass energy  \cite{Cepeda:2019klc-corr}.
-   %}
-   %\label{figureKappasUncs}
- %\end{figure}
+%%%%%%%%BUSCAR VERSION ACTUALIZADA DE ESTA%%%%%%%%%
 
@@
 A pixel cluster is for a group of contiguous pixels activated by a charged particle.
-The method of choice, PCC, exploits the huge number of pixel in the interior part of the CMS pixel detector, which means that the probability that a single pixel is hit by two charged particles from the same bunch crossing is extremely small.%Be more specific about the interior part
+The method of choice, PCC, exploits the huge number of pixel in the interior part of the CMS pixel detector, which means that the probability that a single pixel is hit by two charged particles from the same bunch crossing is extremely small, so it yields measurements with a great linear response with the pile-up (number of interactions per bunch crossing, $\mu$).
+To calibrate the luminometer, the van der Meer (vdM) scan technique is employed in special runs, usually at the beginning of the year or period.
+The LHC has two main types of runs: physics runs (which could be proton-proton, heavy-ion, or proton-lead collisions) and callibration (or vdM) runs.
+As the title of the project suggests, callibration runs are the subject of study, and consist of more controlled collisions to be able to determine luminosity from the beam parameters.
+
+% detector de pixeles
+
+During the vdM runs, the pixel detector is recorded with a trigger of aproximately 50 kHz distributed 10 BCIDs of the 140 that collide, compared to the 2400 that colliding bunches on physics runs; and in turn, the pile-up is much less, giving $\mu \~ 0.5$, against an average of 57 in recent physics runs.
+The data is then distributed in 32 different datasets of events.
+%referencia pa la imagen de pile-up en runs de fisica
 
@@
 This process involves determining the reliability of each module based on analyzing what is referred as the module weight, which is the change in the ratio of module PCC and total PCC.
-The veto list consists of modules excluded due to their known and suspected issues that affect the accuracy of the measurement, such as radiation damage, material defects, contamination, along other issues.
+The veto list consists of modules excluded due to their long-term instabilities.
 At the end of said process, around 10\% of all modules are used.
 
-The LHC has two main types of runs: physics runs (which could be proton-proton, heavy-ion, or proton-lead collisions,) and callibration runs.
-As the title of the project suggests, callibration runs are the matter at hand, and consist of more controlled collisions to be able to measure luminosity and other parameters.
-In these runs, it is necessary to take into consideration a background noise contribution to the PCC rates.
+It is necessary to take into consideration a background noise contribution to the PCC rates.
 Each type of contribution is estimated independently during Super Separation (SS) periods, that are performed to separate two beams a certain distance for a selected period of time.
-To estimate the background value and its statistical error, the mean value and standard deviation are taken from the distribution resulting of a Y-projection of an average of pixel clusters per event ($\langle PCC \rangle$).
-Once the noise is taken into account, the data provided can be saved.
+To estimate the background value and its statistical error, the mean value and standard deviation are taken from the distribution resulting of the average of pixel clusters per event ($\langle PCC \rangle$).
 
-To get the van der Meer (vdM) scan data, the pixel detector is read with a trigger of aproximately 50 kHz for about 10 BCIDs of the 140 that collide.
-The data is then saved distributed in 32 different datasets of events.
+% a couple graphs, maybe??
 
-%----------------------------------------------------------------------------------------------------------------------------------------------------
-
-To calibrate the luminometer, the vdM scan technique is employed in a special LHC run, usually at the beginning of the year or period.
-To perform these scans, the separation between proton beams is varied in two dimensions, in separation steps of 100 micrometers.
+ The separation between proton beams is varied in two dimensions, in steps of 100 micrometers.
 It measures the rates of clusters using the PCC algorithm and the beam parameters during vdM, to determine the calibration constant ($\sigma_{vis}$).
-
-The definition of instantaneous luminosity for a single colliding bunch pair is
+The instantaneous luminosity for a single colliding bunch pair can be calculated with the following formalism:
 
@@
 
-The parameter $\sigma_{vis}$ is known as the calibration constant, and is used to normalize the measured PCC rates so the luminosity can be determined during normal running throughout the data-taking year.%reFERENCES!!!!!!!!!!!
+The parameter $\sigma_{vis}$ is known as the calibration constant, and is used to normalize the measured PCC rates so the luminosity can be determined during normal running throughout the data-taking year.
+In order to compute the constant, a mathematical function needs to be used to fit the averaged cluster rates, so the parameters needed, such as $\Sigma_{x,y}$ and $R(0,0)$, can be extracted.
 
-%----------------------------------------------------------------------------------------------------------------------------------------------------
+For the analysis, the quality of multiple functions is tested.
+The convergence of the function is the first evaluation on this quality, based on the covariance matrix and its status.
+Then, another important analysis is doing a $\chi^2$ test, which helps determine how likely a variable can come from a specified distribution.
+The value of $\chi^2$ is determined by
 
-% \cite{pas:2018vdm}.
+\begin{equation}
+  \chi^2(\theta)=\sum_{i=1}^{N}\frac{(y_i-f(x_i,\theta))^2}{\sigma_i^2}
+\end{equation}
 
-%\begin{figure}[H]
-  %\centering
-  %\includegraphics[width=0.7\columnwidth]{./cms_layers.png}
-  %\caption{Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimeter, superconducting solenoid and muon chambers \cite{Chatrchyan:2008aa}.}
-  %\label{fig:CMS}
-%\end{figure}
+where $y_i$ are the observed values measured with errors $\sigma_i$ at the values of $x_i$ given without error, with the theoretical value given by $f(x_i,\theta)$.
+How low the value of $\chi^2$ determines how good the fit is, and the parameter $\theta$ is adjusted to minimize it \cite{Statistical_Data_Analysis}.
 
-%\begin{figure}[H]
-  %\centering
-  %\includegraphics[width=0.7\columnwidth]{./PixelDetectorPhase1.png}
-  %\includegraphics[width=0.27\columnwidth]{./PixelSensor.png}
-  %\caption{
-    %Left: diagram showing the layout of the CMS Pixel detector used during 2016-2018.
-    %The layout consists of 4 barrel layers and 2 endcap disks with two rings each.
-    %Right: a diagram showing the structure of one pixel sensor.
-    %The entire detector consists of 1856 sensors and 65 million pixels \cite{TrackerGroupoftheCMS:2020bgg}.
-  %}
-  %\label{fig:pixeldet}
-%\end{figure}
+After finishing the tests, the chosen fit model is used, and with corresponding noise corrections, the calibration constant can finally be calculated.
 
-%\begin{figure}[H]
-  %\centering
-  %\includegraphics[width=0.5\columnwidth]{./bunchcrossing.jpg}
-  %\includegraphics[width=0.4\columnwidth]{./vectorhit1.jpg}
-  %\caption{
-    %Left: Diagram showing the collision of two proton bunches at LHC, bunches contain about $10^{11}$ protons  \cite{deMaria:2008zzb}.
-    %Right: diagram showing example tracks originating from the collision at the beamspot and producing clusters at the pixel sensors in two detector layers.
-  %}
-  %\label{fig:trackcluster}
-%\end{figure}
+% Numero de colisiones entre protones (pileup) del total en un bonche (10^11)
 
@@
 
-To warrant stable luminosity measurement for Run 3 2025, the set goals are:
+To guarantee stable luminosity measurement for Run 3 2025, the set goals are:
 
 \begin{itemize}
-  %\item Process all the datasets. %% not a specific objective, a que se refiere %%
-  \item Apply a selection of good modules from the detector: To assure an accurate measurement, a veto list is made, taking only modules with relatively consistent contributions, and then used to only process zero bias PCC data for the vdM analysis.%Check module selection part
-  \item Measure the noise in the modules: A calculation of the background contributions, made during selected time windows, to account for secondary particles, and other unwanted parts.
-% Estimation over separation periods
-  %\item Select the time windows corresponding to the vdM scans. % Mentira, no entendi
+  \item Apply a selection of good modules from the detector: To assure an accurate measurement, a veto list is made, taking only modules with relatively consistent contributions, and then used to only process zero bias PCC data for the vdM analysis.
+  \item Measure the noise in the modules: A calculation of the background contributions, made during selected time windows along every scan of the calibration program.
   \item Set the ideal model adjustment: The generated rates of the scan need to be fitted a mathematical function to extract the parameters needed. 
-%% igual, no es especifico, basicamente checar ajuste segun el ruido %%
-  \item Measure the beam parameters $\Sigma_i$, conducting scans in the $x$ and $y$ directions, determined through curved fitting of the scan data. 
-  \item Measure the calibration constant $\sigma_{vis}$ to normalize the PCC rates. 
-  \item Determine the systematic uncertainties on the integrated luminosity: It is necessary to recognize the effects on the beam overlap measurement, and therefore the calculation of $\sigma_{vis}$, so corrections are to be applied.
+  \item Extract the beam parameters $\Sigma_i$, conducting scans in the $x$ and $y$ directions, determined through curved fitting of the scan data. 
+  \item Compute the calibration constant $\sigma_{vis}$. 
+  \item Determine the systematic uncertainties on the integrated luminosity: It is necessary to recognize the noise effects on the beam overlap measurement, and therefore the calculation of $\sigma_{vis}$, so corrections are to be applied.
 \end{itemize}
@@
   \item Estimate the background contribution for PCC during vdM calibration program.
-  \item Calculate the parts of the systematic uncertainty corresponding the work group.
+  \item Calculate the systematic uncertainty.
 \end{itemize}
@@
     \hline
+    Estimate the background contribution & & & \cellcolor[HTML]{F4D03F} & \\
+    \hline
+    Test the fit functions & & & \cellcolor[HTML]{F4D03F} & \\
+    \hline
     Calculate $\sigma_{vis}$ and its systematic uncertainty & & & \cellcolor[HTML]{F4D03F} & \\
     \hline
-    Estimate the background contribution & & & \cellcolor[HTML]{F4D03F} & \\
+    Write the thesis & & & & \cellcolor[HTML]{E53935} \\
     \hline
-    Write the thesis & & & & \cellcolor[HTML]{E53935} \\
+    Present results at a congress & & & & \cellcolor[HTML]{E53935} \\
     \hline 

### 2025-06-07 project_Omar/paper.tex
bibtex issues. Maybe minor corrections

@@
 
-% detector de pixeles
+% vdm graph
 
-During the vdM runs, the pixel detector is recorded with a trigger of aproximately 50 kHz distributed 10 BCIDs of the 140 that collide, compared to the 2400 that colliding bunches on physics runs; and in turn, the pile-up is much less, giving $\mu \~ 0.5$, against an average of 57 in recent physics runs.
+During the vdM runs, the pixel detector is recorded with a trigger of aproximately 50 kHz distributed 10 BCIDs of the 140 that collide, compared to the 2400 that colliding bunches on physics runs; and in turn, the pile-up is much less, giving $\mu \approx 0.5$, against an average of 57 in recent physics runs.
 The data is then distributed in 32 different datasets of events.
@@
 To estimate the background value and its statistical error, the mean value and standard deviation are taken from the distribution resulting of the average of pixel clusters per event ($\langle PCC \rangle$).
-
-% a couple graphs, maybe??
 

### 2025-06-11 thesis_julio/Chapter3/chapter3.tex
10june

--- 2025-05-30 thesis_julio/Chapter3/chapter3.tex
@@
 For this fill in the calibration the bcids of relevance were a total of 12 which are identified by the numbers: 303, 324, 345, 506, 527, 822, 1081, 1102, 1397, 2000, 2965, 3123.
-This fill started on may 16 at 13:39 and ended at may 17 at 23:50.
 
@@
 
-This dataset were processed (...) getting a lot of root files for each of the different zero bias streams there were a total of 32 zero bias streams.
-The data then was processed again to obtain a hd5file a format that can supports n-dimensional datasets and facilitates the reading of the datasets, this hd5 files contained relevant information about the root files like the average rate per NB4, this was made for each of the files for almost all of the available streams excluding two of them that were not ready by the moment (the ones that were identified by ZB21 and ZB28) after one stream got all of his files processed into an hd5 file they were converged into a single file containing relevant information for all the stream, once all of the files in all of the data streams were processed into hd5 files a single hd5file was made containing all of the information about the streams also a single csv file was made containing only the average rate file per NB4 for each of the bcids.
+This dataset were first processed by the CMS collaboration enabling a cluster reconstruction resulting in the ALCARECO datasets getting a lot of root files for each of the different zero bias streams that were the starting point of this analysis.
+
+After this the data then was processed again to obtain a hd5file a format that can supports n-dimensional datasets and facilitates the reading of the datasets, this hd5 files contained relevant information about the root files like the average rate per NB4, this was made for each of the files for almost all of the available streams excluding two of them that were not ready by the moment (the ones that were identified by ZB21 and ZB28) after one stream got all of his files processed into an hd5 file they were converged into a single file containing relevant information for all the stream, once all of the files in all of the data streams were processed into hd5 files a single hd5file was made containing all of the information about the streams also a single csv file was made containing only the average rate file per NB4 for each of the bcids.
 
@@
 
-During the duration of the fill and for the calibration a few scans of interest were realized the first of them being the vdm scans which was explained in the first section of the chapter, also the BI scans, there were a total of five vdm scans during and two BI scans in the following table we see the time were this scans started and the time w    \\
+For the calibration of 2024 in the LHC fill 9639 during may 15 to may 16 at collision proton proton with a energy of 13.6 TeV, the vdm scans were made there were a total of 5 vdm X and vdm Y scans and 2 beam img X and beam img Y and the Super Separation period which is a scan used to obtain a background estimation, this were the scans used on this analysis to compute the value of $\singa_{visible}$.
+The figure (3.x) shows a DOROS image of the fill and all the scans that were made during that period of time.
 
-Also we got the super separation scans which consist on making a complete separation on the colliding beams so the rate would be zero, there were five of each super separations each of them with a duration of 300 seconds in the table we have information about the beggining and end of each super separation (SS) period.
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=1\textwidth, height=0.4\textheight]{scans.png}
+    \caption{Fill 9639 scans}
+    \label{fig:scans}
+\end{figure}
+
+The 5 vdm scans vdM1, vdM2..., vdM5 are the scans usually used in the calibration to compute $\simga_{visible}$ two beams are separated the transverse bunch size and then scanned across one another in sequence of 25 steps with 30 seconds per step.
+The beam imaging scan is kept on a nominal position while the other is separated and scanned in 19 steps, the scan is performed first in the X direction and then in the Y direction.
+The Super Separation scans separates the beams a distance were the overlap of the beams is negligible, the minimum possible.
+
+\section{Background Estimation}
+
+The background estimation were obtained using the 5 Super Separation scans, the time on which this super separations were used was on UNIX time each of these super separations lasted a total of 5 minutes in the following table we got more information about the start and ending of the scans.
 
@@
 
-In the following image we show a histogram of the average rate vs time during the super separation period number 2:
+The data of this scans were processed and analyzed, in the following image we show the mean value of the PCC rates during the Super Separation period scan in one bcid.
 
-\begin{figure}[h]
+\begin{figure}[H]
     \centering
     \includegraphics[width=1\textwidth]{SS1.jpeg}
-    \caption{Histogram of rates during the second super separation scan}
+    \caption{Mean rates during the second super separation scan}
     \label{fig:SS1}
@@
 
-In the image we can see that the average rate suddenly drops, this is the beggining of the second super separation scan for the bcid 506 where the avarage rate drop but is non zero, then the rate goes up again meaning the end to the super separation scan.
+The reason why the background estimation is obtained during the super separation (SS) process, It's because the SS scan separates the beams so they shouldn't be colliding the expected value on the rate is expected to be a rate associated with the background, this was obtained checking the mean values for each bcid for all the entries of pcc rates for each of the 5 periods of super separation, the following image illustrate a case for one SS period and bcid 50x:
 
-\section{Background Estimation}
+\begin{figure}[H]
+    \centering
+    \includegraphics[height=0.4\textheight, width=0.8\textwidth]{sshist.png}
+    \caption{SS periods histograms showing entries for bcid 345}
+    \label{fig:SShist}
+\end{figure}
 
-The background estimation is obtained during the super separation (SS) process, since the SS scan separates the beams so they shouldn't be colliding the expected value on the rate is expected to be a rate associated with the background, this is then estimated by checking each of the SS scans on the time window referred on the table (3.1), the mean value during this period is assumed to be the mean value of the SS period, in the following table we see the mean PCC value for each period.
+The mean value during this period is assumed to be the background noise value of this SS period, in the following table we see the mean PCC value for all of the bcids and how it changes in each of the five super separation periods.
 
-\begin{table} [H]
-\begin{center}
-\caption{Different Scans}
-\begin{tabular}{|c c c|} 
- \hline
- Scan & Mean & std  \\ [0.5ex] 
- \hline\hline
- SS1 &  & 1715883481  \\ 
- \hline
- SS2 &  & 1715902484  \\
- \hline
- SS3 &  & 1715919463 \\
- \hline
- SS4 &  & 1715943343  \\
- \hline
- SS5 &  & 1715987602  \\ [1.0ex]
- \hline
-\end{tabular}
-\end{center}
-\end{table}
+\begin{figure}[H]
+    \centering
+    \includegraphics[height=0.30\textheight,width=1\textwidth]{SSmean.png}
+    \caption{Mean per bcid}
+    \label{fig:SSmean}
+\end{figure}
 
-This is the mean value of each super separation off al the bcids a total of 60 mean values were obtained and was $ss_background$ = 0.0251 +-0.0018 in the following picture we can see the
+In principle this value is a single value so we obtain a histogram obtaining a mean for all the mean values for all the 60 values this is shown in the following image:
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=1\textwidth]{ssthist.png}
+    \caption{Histogram of all means}
+    \label{fig:Histogram}
+\end{figure}
+
+With this que obtained that the value for super separation is $ss_{background}$ = 0.0251 +-0.0018 this value would be extracted from the PCC rates during the fit for the vdm scans.
 
@@
 \begin{equation}
-f_{qg}(x,y) = \frac{V}{C(q) \sigma_{x} \sigma_{y}\sqrt{1-\chi^{2}}} e_{q}(\frac{\ r^{2}}{(4-2q)}) 
+f_{qg}(x,y) = peak e_{q}(-\beta(x - mean)^{2},q)
 \end{equation}
@@
 
-and $c(q)$ having two different values depending on the value of the q, for q < 1:
+q being a parameter and peak the maximum rate.
 
-\begin{equation}
-c(q) = \frac{4-2q}{1-q} \pi \frac{\Gamma (\frac{2-q}{1-q})}{\Gamma (\frac{2-q}{1-q} + 1)}
-\end{equation}
+This fit model were applied to the data using vdmfamework software for all bcids, the following image shows this fit on the x plane and on the y plane on one bcid other bcids showed a similar result.
 
-and for the other cases:
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.45\textwidth]{fitqg1.png}
+    \includegraphics[width=0.45\textwidth]{fitqg2.png}
+    \caption{QG Fit on X plane and Y plane}
+    \label{fig:QGfit}
+\end{figure}
 
-\begin{equation}
-c(q) = \frac{4-2q}{q-1} \pi \frac{\Gamma (\frac{1}{q-1} - 1)}{\Gamma (\frac{1}{q-1})}
-\end{equation}
+To see if the fit converged we check the covariance matrix with the covalue, if this value is 3 the fit converge as we can see in the following image all of the bcids converged in all of the scans for the vdm and BI.
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.9\textwidth]{QG_covStatus.png}
+    \caption{Covariance value showing that all bcids converged with the fit}
+    \label{fig:QGfit}
+\end{figure}
+
+Also to see the fit quality we obtain the value of $\chi^{2}$ divided by the numbers of degree freedom the following image shows this:
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.9\textwidth]{QG_chi2.png}
+    \caption{Fit quality values}
+    \label{fig:QGchi2}
+\end{figure}
 
@@
 
-The beam parameters of the vdm scan were obtained after the vdm framework run on the fit, one of the parameters obtained was the peak:
+The beam parameters of the vdm scan were obtained after the vdm framework run on the fit, one of the parameters obtained is the peak:
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.9\textwidth]{QG_peak.png}
+    \caption{QG peak values important on the computing of $\sigma_{visible}$}
+    \label{fig:QGpeak}
+\end{figure}
+
+Here we can see that the peak values are increasing with the time which doesn't have sense since the number of particles through time should be lower, this behavior is then explained if we observe the results for the $\Sigma_{x, y}$ in the following image:
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.9\textwidth]{QG_CapSigma.png}
+    \caption{QG $\Sigma$ important to compute value of $\sigma_{visible}$}
+    \label{fig:QGcapsigma}
+\end{figure}
+
+Here we see that the $\Sigma_{x, y}$ values are decreasing for each scan reducing the thickness of the beams and thus observing a higher peak value even if the number of particles is decreasing through time.
+
+Now with all the values obtained we can compute the value of $sigma_{visible}$, the values for each bcid is shown on the following image:
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.9\textwidth]{sigbcid.png}
+    \caption{QG $\Sigma$ important to compute value of $\sigma_{visible}$}
+    \label{fig:sigbcid}
+\end{figure}
+
+We are expecting a constant value of $\sigma_v{visible}$ here it appears to be changing each scan this could be to other uncertainties.
+Then in the following image we show the result for the weighted mean of the $\sigma_{visible}$ for each scan:
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.9\textwidth]{sigscan.png}
+    \caption{QG $\Sigma$ important to compute value of $\sigma_{visible}$}
+    \label{fig:sigscan}
+\end{figure}
+
+Which give us a $\sigma_{visible}$ value of
+
+\begin{equation}
+\sigma_{visible} = 1460890 \pm 546
+\end{equation}
+
+Which is the value for $\sigma_{vis}$ that we have been looking for the calibration using the vdm scans.
+
+\newpage
+
+\section{Systematics}
+
+We obtained a systematic uncertainties comparing the fit made but with different corrections, in the following table we check this uncertanties with citing a relative change per correction:
+
+\begin{table}[H]
+\begin{center}
+\small
+\begin{tabular}{|c c c|} 
+ \hline
+ Correction & $\sigma_{visible}$ & Relative Change(\%) \\ [0.5ex] 
+ \hline\hline
+ No correction & $1452589 \pm 2041$ & - \\ 
+ \hline
+ Background & $1448801 \pm 676$ & \\
+ \hline
+ Background + Ghost Satellite & $1450154 \pm 560$ & \\
+ \hline
+ Background + Ghost Satellite + Beam Beam + Dynamic Beta & $1460890 \pm 546$ & \\ [1.0ex]
+ \hline
+\end{tabular}
+\caption{Comparison of $\sigma_{visible}$ values with different corrections}
+\end{center}
+\end{table}

### 2025-06-11 thesis_julio/Chapter4/chapter4.tex
commit4
10june

@@
-\chapter{Results}
+\chapter{Summary}
 \label{ch4}
 
-\section{}
-\section{}
-\sectin{}
+This work aims to focus on the calibration of hte luminosity for the PCC luminometer base on the Van Der Meer scans conducted by the CMS collaboration on 2024 for the fill 9639 in the proton proton collisions of the LHC at $\sqrt{s}$ 13.6 TeV obtaining the calibration value from seven scan pairs (5 vdM's and 2 BI's), the concept of luminosity, the LHC, CMS, PCC luminometer and calibration method to estimate $\sigma_{visible}$ were covered in this work.
+
+This works also explains the reprocess of the ALCARECO dataset to then using a veto list to select the good modules of the pixel detector to remove any inastabilitie in the measurement of the luminosity.
+Also more data were processed obtaining a value for the background analyzing the five super separation scans to correct the rates of the PCC luminometer.
+The model used for this calibration was QG function, and 3 corrections were applied to fhe final value of the calibration, the background correction, the ghost satellite correction, the beam beam and dynamic beta corrections.
+
+The obtained value for the calibration constant was $\sigma_{visible}$ = 1460890 \pm 546$ the analysis and results reported in this work will be useful for an analysis of the pre eliminary luminosity measurement for Run 3 in the CMS experiment of the lHC, where the rest of the luminometers and It's certainties will be studied along with this one.

### 2025-06-12 project_Omar/paper.tex
hopefully final version

@@
 \footnote{1 barn is a unit of area corresponding to $10^{-24}$ cm${^2}$ and 1 femtobarn (fb) = $10^{-39}$ cm$^{2}$. For comparison, the total Higgs production cross section is 48600 fb.}
-In the first part of Run 2 (2015-2016), the delivered luminosity has been measured to be \lumi{38.4} with an unprecedented precision of 1.3\% \cite{Sirunyan:2021qkt}.
+In the first part of Run 2 (2015-2016), the delivered luminosity has been measured to be \lumi{38.4} with a precision of 1.3\% \cite{Sirunyan:2021qkt}.
 For the second part of Run 2 (2017-2018), the integrated luminosity is about \lumi{78}.
@@
 The CMS silicon pixel detector consists of four concentric cylindrical layers and three disks on each end, placed at certain distances from the center of the detector.
-The detector consists of 1856 sensor modules, and gives complete coverage over the interaction point, resulting in precise tracking.
+The detector consists of 1856 sensor modules, and gives complete coverage over the interaction point, resulting in precise tracking \cite{TrackerGroupoftheCMS:2020bgg}.
 This yields a large amount of total pixels, so, adding the sensor's fine granularity, the hit occupancy is very low.
@@
 
-\section{OBJECTIVE}
+\section{OBJECTIVE}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\section{HYPOTHESIS}
+\section{HYPOTHESIS}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 Based on the analysis corresponding to previous years, a similar or better result is expected.
-With a systematic uncertainty of 1.4\% for 2022, and 1.3\% for 2023, it is possible to achieve a precision as good as this, if not an improvement.
+With a systematic uncertainty of 1.4\% for 2022 \cite{Collaboration:124}, and 1.3\% for 2023 \cite{CMS-DP-2024-068}, it is possible to achieve a precision as good as this, if not an improvement.
 
-\section{METHODOLOGY}
+\section{METHODOLOGY}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
 
@@
 The method of choice, PCC, exploits the huge number of pixel in the interior part of the CMS pixel detector, which means that the probability that a single pixel is hit by two charged particles from the same bunch crossing is extremely small, so it yields measurements with a great linear response with the pile-up (number of interactions per bunch crossing, $\mu$).
-To calibrate the luminometer, the van der Meer (vdM) scan technique is employed in special runs, usually at the beginning of the year or period.
+To calibrate the luminometer, the van der Meer (vdM) scan technique is employed in special runs, usually at the beginning of the year or period \cite{CMS:2018}.
 The LHC has two main types of runs: physics runs (which could be proton-proton, heavy-ion, or proton-lead collisions) and callibration (or vdM) runs.
@@
 
-% vdm graph
+% vdm graph?
 
-During the vdM runs, the pixel detector is recorded with a trigger of aproximately 50 kHz distributed 10 BCIDs of the 140 that collide, compared to the 2400 that colliding bunches on physics runs; and in turn, the pile-up is much less, giving $\mu \approx 0.5$, against an average of 57 in recent physics runs.
+During the vdM runs, the pixel detector is recorded with a trigger of aproximately 50 kHz distributed 10 BCIDs of the 140 that collide, compared to the 2400 that colliding bunches on physics runs; and in turn, the pile-up is much less, giving $\mu \approx 0.5$, against an average of 57 in recent physics runs \cite{eysermans_cms_mw_lowPU} \cite{cms_new_record_2024}.
 The data is then distributed in 32 different datasets of events.
-%referencia pa la imagen de pile-up en runs de fisica
 
@@
 
-\begin{center}
-  $\int\rho_1(y)\rho_2(y+\Delta y)dy=\frac{\int\mathcal{L}(\Delta x, \Delta y)d(\Delta x)}{N_1 N_2 f} \Rightarrow \mathcal{L}(\Delta x, \Delta y)=\int\rho_1(x)\rho_2(x+\Delta x)dx\int\mathcal{L}(\Delta x', \Delta y)d(\Delta x')$
-\end{center}
+\begin{align*}
+  \int\rho_1(y)\rho_2(y+\Delta y)dy &= \frac{\int\mathcal{L}(\Delta x, \Delta y)d(\Delta x)}{N_1 N_2 f}\\
+  \Rightarrow \mathcal{L}(\Delta x, \Delta y) &=\int\rho_1(x)\rho_2(x+\Delta x)dx\int\mathcal{L}(\Delta x', \Delta y)d(\Delta x')
+\end{align*}
 
@@
 
-The parameter $\sigma_{vis}$ is known as the calibration constant, and is used to normalize the measured PCC rates so the luminosity can be determined during normal running throughout the data-taking year.
+The parameter $\sigma_{vis}$ is known as the calibration constant, and is used to normalize the measured PCC rates so the luminosity can be determined during normal running throughout the data-taking year \cite{CMS:2018}.
 In order to compute the constant, a mathematical function needs to be used to fit the averaged cluster rates, so the parameters needed, such as $\Sigma_{x,y}$ and $R(0,0)$, can be extracted.
@@
 
-\section{SPECIFIC OBJECTIVES}
+\section{SPECIFIC OBJECTIVES}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\section{EXPECTED RESULTS}
+\section{EXPECTED RESULTS}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\section{CALENDAR OF ACTIVITIES}
+\section{CALENDAR OF ACTIVITIES}%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \onehalfspacing
-\bibliographystyle{unsrt} % y esto...........
+\bibliographystyle{unsrt} 
 \bibliography{paper}

### 2025-06-16 thesis_julio/Chapter1/chapter1.tex
16jun

@@
 
-Elementary particle physics is the study of the particles at the most fundamental level, the constituents of the universe as well as the interactions between them which are called, electromagnetic force, nuclear weak force and nuclear strong force and there is also the gravity force but this one doesn't have a satisfactory quantum theory for it.
+Elementary particle physics is the study of the particles at the most fundamental level, the constituents of the universe as well as the interactions between them which are called, electromagnetic force, nuclear weak force, nuclear strong force and there is also the gravity force but this one doesn't have a satisfactory quantum theory for it.
 Each of these forces are mediated by exchange particles, in the case of the electromagnetic force the mediator is the photon, for the strong force the gluons, for the weak force the bosons W and Z and for the gravity we have the hypothetical graviton.
@@
 
-Each of these forces have a mathematical description for the physical systems of these interactions using the Quantum Field Theory (QFT).
+Each of these forces has a mathematical description for the physical systems of these interactions using the Quantum Field Theory (QFT).
 The one that describes systems under the electromagnetic force is called Quantum Electrodynamics (QED) this force dictates the electronic structure of atoms being the low energy manifestation of the electromagnetic theory.
-For the strong force Quantum Chromodynamics (QCD) is the fundamental theory of strong interactions, this force is responsible of maintaining protons and neutrons together in the atomic nucleus.
-For the weak interactions there is no particular name in the same way as the previous two, this force is is carried by all quarks and leptons and is responsible for the $\beta$ Decay of some radioactive isotopes and nuclear processes of the sun.
+For the strong force Quantum Chromodynamics (QCD) is the fundamental theory of strong interactions, this force is responsible for maintaining protons and neutrons together in the atomic nucleus.
+For the weak interactions there is no particular name in the same way as the previous two, this force is carried by all quarks and leptons and is responsible for the $\beta$ Decay of some radioactive isotopes and nuclear processes of the sun.
 \cite{mppthomson}
@@
 Almost all the physical phenomena can be explained with only the electron, the electron neutrino, the proton and the neutron interacting with the electromagnetic force, the strong force and the weak one.
-When higher levels of energy are present new particles are observed, all of this is known as the elementary particles which are embodied in the standard model of particle physics that is by far the best theorical model that describes interaction of this elementary particles.
-Is divided into two categories the bosonic sector and the fermionic sector.
+When higher levels of energy are present new particles are observed, all of this is known as the elementary particles which are embodied in the standard model of particle physics that is by far the best theoretical model that describes the interaction of these elementary particles.
+They are divided into two categories the bosonic sector and the fermionic sector.
 \cite{mppthomson}
@@
 
-The fermionic sector contains particle the particles that make up all known matter in the universe and is divided into the leptons and the quarks, both of this particles are divided into three generations, each generation being heavier than the one before.
-For the leptons we have electron and Its neutrino for the first generation, the second generation is.
+The fermionic sector contains particle the particles that make up all known matter in the universe and is divided into the leptons and the quarks, both of these particles are divided into three generations, each generation being heavier than the one before.
+For the leptons we have the electron and Its neutrino for the first generation, the second generation is.
 the $\mu$ and Its neutrino and the third one is the $\tao$ with Its neutrino.
@@
 
-With N1 and N2 being the bunch intensity, f the revolution frecuency, $N_{b}$ the number of colliding bunches, $\rho_{1}$ and $\rho_{2}$ time dependent beam density distribution functions and assuming the densities are uncorrelated in all planes.
+With N1 and N2 being the bunch intensity, f the revolution frequency, $N_{b}$ the number of colliding bunches, $\rho_{1}$ and $\rho_{2}$ time dependent beam density distribution functions and assuming the densities are uncorrelated in all planes.
 \cite{Lumvdm}
@@
 
-it is related directly to the number of observed events $L_{int} \cdot \sigma_{p}$ number of events of interest.
+This is related directly to the number of observed events $L_{int} \cdot \sigma_{p}$ number of events of interest.
 
@@
 The PCC luminometer method consist in counting the average number of pixel clusters on the detector to measure luminosity.
-This occurs during a zero bias event, an event that is trigged by requiring only that two proton bunches cross at the CMS interaction point.
+This occurs during a zero bias event, an event that is triggered by requiring only that two proton bunches cross at the CMS interaction point.
 Giving that the number of pixels in really big the probability that a pixel is being hit by two different tracks by the same bunch crossing is really small.

### 2025-06-16 thesis_julio/Chapter3/chapter3.tex
16jun

@@
 
-For obtaining the importnat parameters on the vdm scan we return to the equation (1.2) and apply it to and individual bunch crossing, the values of N1 and N2 being the number of protons colliding can be obtained since is a known quantity from the experiment, the frequency f is also a known quantity, the frequency of the LHC which is 11,245 kHz but the proton densities $\rho_{1}$ and $\rho{2}$ are more difficult to obtain, this is were the vdM scan help us to measure integral over the bunch proton densities.
+For obtaining the important parameters on the vdm scan we return to the equation (1.2) and apply it to and individual bunch crossing, the values of N1 and N2 being the number of protons colliding can be obtained since is a known quantity from the experiment, the frequency f is also a known quantity, the frequency of the LHC which is 11,245 kHz but the proton densities $\rho_{1}$ and $\rho{2}$ are more difficult to obtain, this is were the vdM scan help us to measure integral over the bunch proton densities.
 The luminosity integral evaluated with the beams separated by a distance $\Delta_{x}$ and $\Delta_{y}$ can take the form of:
@@
 The integrals resulting on the right side can be evaluated by evaluated by obtaining the rate in function of the beam-beam separation which are $\Delta x$ and $\Delta y$  this because the luminosity has a linear relationship with the rate.
-The Luminosity can be expresed on terms of the rate during the head on points using the following:
+The Luminosity can be expresed on terms of the rate during the head on positions, R(\Delta_{x0}, \Delta_{y0}) like in the equation (3.5)
 
 \begin{equation}
-L(\Delta x, \Delta y) = N_{1} N_{2} f \frac{2R(\Delta x_{0}, \Delta y_{0}}){\int L(\Delta x_{0}, \Delta y) d(\Delta y) \int L(\Delta x, \Delta y_{0}) d(\Delta x)}
+L(\Delta x, \Delta y) = N_{1} N_{2} f \frac{2R(\Delta x_{0}, \Delta y_{0}){\int L(\Delta x_{0}, \Delta y) d(\Delta y) \int L(\Delta x, \Delta y_{0}) d(\Delta x)}}
 \end{equation}
@@
 \begin{equation}
-\Sigma_{x} = \frac{1}{2 \pi} \frac{\int R(\Delta x, \Delta y_{0} d(\Delta x) )}{R(\Delta x_{0}, \Delta y_{0})}
+\Sigma_{x} = \frac{1}{2 \pi} \frac{\int R(\Delta x, \Delta y_{0}) d(\Delta x) )}{R(\Delta x_{0}, \Delta y_{0})}
 \end{equation}
@@
 \begin{equation}
-\sigma_{vis} = \frac{2 \pi \Sigma_{x} \Sigma_{y} R(\Delta x_{0} \Delta y_{0})}{N_{1} N_{2}f}
+\sigma_{vis} = \frac{2 \pi \Sigma_{x} \Sigma_{y} R(\Delta x_{0}, \Delta y_{0})}{N_{1} N_{2}f}
 \end{equation}
@@
 
+This scans were analyzed using the vdM framework, a CMS tool to obtain different parameters using a fit model on the vdM scans, this framework read hd5 files and with a set of instructions the value of $\sigma_{visible}$ can be obtained.
+
 \section{Scans}
 
-For the calibration of 2024 in the LHC fill 9639 during may 15 to may 16 at collision proton proton with a energy of 13.6 TeV, the vdm scans were made there were a total of 5 vdm X and vdm Y scans and 2 beam img X and beam img Y and the Super Separation period which is a scan used to obtain a background estimation, this were the scans used on this analysis to compute the value of $\singa_{visible}$.
+For the calibration of 2024 in the LHC fill 9639 during may 15 to may 16 at collision proton proton with a energy of 13.6 TeV, the vdm scans were made there were a total of 5 vdm X and vdm Y scans and 2 beam img X and beam img Y and the Super Separation period which is a scan used to obtain a background estimation, this were the scans used on this analysis to compute the value of $\sigma_{visible}$.
 The figure (3.x) shows a DOROS image of the fill and all the scans that were made during that period of time.
@@
     \centering
-    \includegraphics[width=1\textwidth, height=0.4\textheight]{scans.png}
-    \caption{Fill 9639 scans}
+    \includegraphics[width=1\textwidth]{scans.png}
+    \caption[Doros for fill 9639]{DOROS beam position during LHC Fill 9639 for the vdM scans. Horizontal and vertical beams are shown over time}
     \label{fig:scans}
@@
 
-The 5 vdm scans vdM1, vdM2..., vdM5 are the scans usually used in the calibration to compute $\simga_{visible}$ two beams are separated the transverse bunch size and then scanned across one another in sequence of 25 steps with 30 seconds per step.
+The 5 vdm scans vdM1, vdM2..., vdM5 are the scans usually used in the calibration to compute $\sigma_{visible}$ two beams are separated the transverse bunch size and then scanned across one another in sequence of 25 steps with 30 seconds per step.
 The beam imaging scan is kept on a nominal position while the other is separated and scanned in 19 steps, the scan is performed first in the X direction and then in the Y direction.
@@
 
-The background estimation were obtained using the 5 Super Separation scans, the time on which this super separations were used was on UNIX time each of these super separations lasted a total of 5 minutes in the following table we got more information about the start and ending of the scans.
+The background estimation were obtained using the 5 Super Separation scans, the time on which this super separations were used was on UNIX time, this time can be defined as a system for tracking a point in time as the number of seconds that have happened since January 1 at 00:00 in universal time (UTC).
+Each of these super separations lasted a total of 5 minutes in the following table we got more information about the start and ending of the scans.
 
@@
     \includegraphics[height=0.4\textheight, width=0.8\textwidth]{sshist.png}
-    \caption{SS periods histograms showing entries for bcid 345}
+    \caption{Distribution of average PCC for bcid 345 during SS number 2. The PCC values are computed in NB4 time intervals.}
     \label{fig:SShist}
@@
     \centering
-    \includegraphics[height=0.30\textheight,width=1\textwidth]{SSmean.png}
-    \caption{Mean per bcid}
+    \includegraphics[width=1\textwidth]{SSmean.png}
+    \caption{This plot shows the evolution of the PCC value for the twelve differents bcids during the SS periods, it also shows the mean of each bcid.}
     \label{fig:SSmean}
@@
 
-In principle this value is a single value so we obtain a histogram obtaining a mean for all the mean values for all the 60 values this is shown in the following image:
+In principle this value is a single value so we obtain a histogram obtaining a mean for all the mean values for all the 60 values as It's shown on figure (3.6)
 
@@
     \centering
-    \includegraphics[width=1\textwidth]{ssthist.png}
-    \caption{Histogram of all means}
+    \includegraphics[height = 0.45 \textwidth ,width=1\textwidth]{ssthist.png}
+    \caption{This plots shows an histogram with all SS values for all bcids, the mean of all this values is used as the final result.}
     \label{fig:Histogram}
@@
 
-With this que obtained that the value for super separation is $ss_{background}$ = 0.0251 +-0.0018 this value would be extracted from the PCC rates during the fit for the vdm scans.
+With this it was obtained that the value for super separation is $ss_{background}$ = 0.0251 +-0.0018 this value will be removed from the PCC rates during the fit for the vdm scans.
 
@@
 
-A few corrections were taken into consideration to eliminate noise data from another sources during this vdm calibration, this corrections are applied by the vdm framework.
+A few corrections were taken into consideration to eliminate noise data from another sources during this vdm calibration, this corrections are applied by the vdM framework.
 
@@
 
-There are different fit models at the time to do the vdm calibration, the most common one is Single Gaussian but also other models like the Double Gaussian, QG, Poly2g or Poly 4G.
+There are different fit models at the time to do the vdm calibration, the most common one is Single Gaussian but also other models like the Double Gaussian, QG, Poly2G or Poly4G.
 Each of these models have different parameters and restrictions making some of them better than other on the fit quality.
 
-For the main calibration we used the QG fit this fit uses the parameter $\sigma$, the peak and a q values as the parameters. This fit is given by the following equation:
+For the nominal calibration we used the QG fit model this fit model uses the parameter $\beta$, the peak value which is the maximum rate obtained during the head on period, the mean and a q values which is also a parameter.
+This fit model is given by the following equation:
 
 \begin{equation}
-f_{qg}(x,y) = peak e_{q}(-\beta(x - mean)^{2},q)
+f_{qg}(\Delta x) = peak * e_{q}(-\beta(\Delta x - mean)^{2},q)
 \end{equation}
@@
 \begin{equation}
-e_{q}(x) = (1+(1-q)x)^{\frac{1}{1-q}}
+e_{q}(x, q) = (1+(1-q)x)^{\frac{1}{1-q}}
 \end{equation}
 
-q being a parameter and peak the maximum rate.
-
-This fit model were applied to the data using vdmfamework software for all bcids, the following image shows this fit on the x plane and on the y plane on one bcid other bcids showed a similar result.
+This fit model were applied to the data using vdM famework software for all bcids, the figure (3.7) shows this fit on the x plane and on the y plane for one bcid. Other bcids showed a similar result.
 
@@
 
-To see if the fit converged we check the covariance matrix with the covalue, if this value is 3 the fit converge as we can see in the following image all of the bcids converged in all of the scans for the vdm and BI.
+To see if the fit converged we check the status of the covariance matrix if this value is 3 the fit is converged as we can see in the figure (3.8) shows all of the bcids converged in all of the scans for the vdm and BI.
 \begin{figure}[H]
@@
     \includegraphics[width=0.9\textwidth]{QG_covStatus.png}
-    \caption{Covariance value showing that all bcids converged with the fit}
+    \caption{Status of the covariance matrix gives 3 for all values showing that all bcids converged with the fit}
     \label{fig:QGfit}
@@
 
-Also to see the fit quality we obtain the value of $\chi^{2}$ divided by the numbers of degree freedom the following image shows this:
+Also to see the fit quality we obtain the value of $\chi^{2}$ divided by the numbers of degree freedom this graphic is shown on the figure (3.9).
 
@@
     \includegraphics[width=0.9\textwidth]{QG_chi2.png}
-    \caption{Fit quality values}
+    \caption{Chi2 values to see the fit quality, the green line represent the mean}
+    \label{fig:QGchi2}
+\end{figure}
+
+\section{Fit model optimization}
+
+Two fit models were used for this, the first one described above and the second Poly2G.
+The poly2G model consist on a value r2 which is a parameter, the value $\Sigma$ related to the beam width, the peak which is the maximum rate during the head on period and the mean.
+Its defined as:
+
+\begin{equation}
+f_{Poly2G}(\Delta x) = peak * ( 1 + r_2 \left( \frac{x - mean}{\sigma / (1 + r_2)} \right)^2 \right) \exp\left( -\frac{1}{2} \left( \frac{x - mean}{\sigma / (1 + r_2)} \right)^2 \right)
+\end{equation}
+
+Once the Poly2G fit model was used the chi2 value was compared with the nominal fit model, in the figure (3.9) we can see the chi2 values for each scan.
+The mean value of the chi2 is lower than the QG that's the reason we used it as the nominal fit model.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.9\textwidth]{poly2g.jpeg}
+    \caption{Chi2 values to see the fit quality of the poly2g fit model the green line represent the mean, notice that the mean is lower than with the nominal fit model.}
     \label{fig:QGchi2}
@@
 
-The beam parameters of the vdm scan were obtained after the vdm framework run on the fit, one of the parameters obtained is the peak:
+The beam parameters of the vdm scan were obtained after the vdM framework run whit the QG fit model one of the parameters obtained is the peak value, figure 3.12 shows the peak values obtained with the fits to the different vdM scans.
 
@@
     \includegraphics[width=0.9\textwidth]{QG_peak.png}
-    \caption{QG peak values important on the computing of $\sigma_{visible}$}
+    \caption{QG model fit peak values obtained for the different scans in X and Y.}
     \label{fig:QGpeak}
@@
 
-Here we can see that the peak values are increasing with the time which doesn't have sense since the number of particles through time should be lower, this behavior is then explained if we observe the results for the $\Sigma_{x, y}$ in the following image:
+Here we can see that the peak values are increasing with the time in the fill, this behavior is then explained if we observe the results for the $\Sigma_{x, y}$ shown in the figure (3.13).
+Here we see that the $\Sigma_{x, y}$ values are decreasing for each scan reducing the thickness of the beams and thus observing a higher peak value even if the number of particles is decreasing through time.
 
@@
     \includegraphics[width=0.9\textwidth]{QG_CapSigma.png}
-    \caption{QG $\Sigma$ important to compute value of $\sigma_{visible}$}
+    \caption{QG model fit $\Sigma$ values obtained for the different scans in X and Y in the vdM fill.}
     \label{fig:QGcapsigma}
@@
 
-Here we see that the $\Sigma_{x, y}$ values are decreasing for each scan reducing the thickness of the beams and thus observing a higher peak value even if the number of particles is decreasing through time.
+\section{Results}
 
-Now with all the values obtained we can compute the value of $sigma_{visible}$, the values for each bcid is shown on the following image:
+After the obtention of the beam parameters  the value of $\sigma_{visible}$ can be obtained, the values for each bcid is shown are shown on the image (3.13).
 
@@
     \includegraphics[width=0.9\textwidth]{sigbcid.png}
-    \caption{QG $\Sigma$ important to compute value of $\sigma_{visible}$}
+    \caption{The value of $\sigma_{visible}$ of all twelve bcids and the seven used scans}
     \label{fig:sigbcid}
@@
 
-We are expecting a constant value of $\sigma_v{visible}$ here it appears to be changing each scan this could be to other uncertainties.
-Then in the following image we show the result for the weighted mean of the $\sigma_{visible}$ for each scan:
+We are expecting a constant value of $\sigma_{visible}$ here it appears to be changing each scan this could be to other uncertainties.
+Then in the image (3.14) Its shown the result on each scan for the weighted mean which is a mean taken into consideration a value mean that is defined as:
+
+\begin{equation}
+w_{i}=\frac{1}{\sigma^{2}}
+\end{equation}
+
+So then the weighted mean value of $\sigma_{visible}$ would be:
+
+\begin{equation}
+\sigma_{vis} = \frac {\Sigma_{i} w_{i} \sigma^{i}_{vis}}{\Sigma_{i} w_{i}} 
+\end{equation}
+
+With the error defined as:
+
+\begin{equation}
+\sigma_{visErr} = \frac{1}{\sqrt{\Sigma_{i} w_{i}}}
+\end{equation}
 
@@
     \includegraphics[width=0.9\textwidth]{sigscan.png}
-    \caption{QG $\Sigma$ important to compute value of $\sigma_{visible}$}
+    \caption{$\sigma_{visible}$ weighted mean per each scan}
     \label{fig:sigscan}
@@
 
-\newpage
+The uncertainties from systematics are also taken into consideration, the uncertainties taken in consideration are the one from Background noise, the one from Scan to scan variation and the bunch to bunch variation.
 
-\section{Systematics}
+Starting for the Background there were analysis made with the QG model fit which doesn't extract the background PCC, the sigma visible obtained in this case was of $\sigma_{visnobg}$ = 1452589 compared to the value that we obtained $\sigma_{vis}$ = 1450890 can be concluded that the uncertainty is 0.11\%.
 
-We obtained a systematic uncertainties comparing the fit made but with different corrections, in the following table we check this uncertanties with citing a relative change per correction:
+In the case of scan to scan variation the standard deviation of the seven scans is taken as uncertainty with a value of 0.30\%.
 
-\begin{table}[H]
+For the bunch to bunch uncertainty the value of $\sigma_{vis}$ was obtained on each scan to each value there is a standard deviation assigned which is divided by the mean of the twelve BCIDS.
+This value is then divided by the square root of the number of bunches, all of this results are show in in the table (3.2).
+The uncertainty value was 0.02\%.
+
+\begin{table} [H]
 \begin{center}
-\small
-\begin{tabular}{|c c c|} 
+\caption{Bunch to bunch uncertainty table.}
+\begin{tabular}{|c c c c|} 
  \hline
- Correction & $\sigma_{visible}$ & Relative Change(\%) \\ [0.5ex] 
+ Scan & \sigma_{vis} & STD & Syst. Error  \\ [0.5ex] 
  \hline\hline
- No correction & $1452589 \pm 2041$ & - \\ 
+ vdM1 & 1463330 & 1220 & 0.02  \\ 
  \hline
- Background & $1448801 \pm 676$ & \\
+ vdM2 & 1453795 & 1212 & 0.02 \\
  \hline
- Background + Ghost Satellite & $1450154 \pm 560$ & \\
+ vdM3 & 1464237 & 953 & 0.01 \\
  \hline
- Background + Ghost Satellite + Beam Beam + Dynamic Beta & $1460890 \pm 546$ & \\ [1.0ex]
+ vdM4 & 1454363 & 1170 & 0.02 \\
+ \hline
+ vdM5 & 1465271 & 1200 & 0.02  \\ 
+ \hline
+ BI1 & 1457208 & 1169 & 0.02 \\ 
+ \hline
+ BI2 & 1464367 & 1233 & 0.02\\
+ \hline
+ vdM6 &1462515  & 1155 & 0.02 \\ 
+ \hline
+    \textbf{mean}        &             &            & 0.2 \\ [1.0ex]
  \hline
 \end{tabular}
-\caption{Comparison of $\sigma_{visible}$ values with different corrections}
 \end{center}
 \end{table}
+
+The sum between all the uncertainties can be see in detail in the table (3.3), the total systematic uncertainty is 0.43\% (6281) taking into consideration only those systematic uncertainties.
+
+\begin{table} [H]
+\begin{center}
+\caption{Systematic uncertainties total.}
+\begin{tabular}{|c c|} 
+ \hline
+ Systematic  & Systematic uncertainty \\ [0.5ex] 
+ \hline\hline
+ Background & 0.11\%   \\ 
+ \hline
+ Bunch to Bunch & 0.02\%  \\
+ \hline
+ Scan to scan & 0.30\% \\
+ \hline
+  Total          &     0.43\%  \\ [1.0ex]
+ \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+%\begin{table}[H]
+%\begin{center}
+%\small
+%\caption{Comparison of $\sigma_{visible}$ values with different corrections}
+%\begin{tabular}{| c| c| c|} 
+ %\hline
+ %Correction & $\sigma_{visible}$ & Relative Change(\%) \\ [0.5ex] 
+ %\hline\hline
+% No correction & $1452589 \pm 2041$ & - \\ 
+ %\hline
+% Background & $1448801 \pm 676$ & +0.26 \\
+ %\hline
+ %Background + Ghost Satellite & $1450154 \pm 560$ & -0.09 \\
+ %\hline
+% Background + Ghost Satellite + Beam Beam + Dynamic Beta & $1460890 \pm 546$ & -0.74 \\ [1.0ex]
+ %\hline
+%\end{tabular}
+%\end{center}
+%\end{table}

### 2025-06-16 thesis_julio/Chapter4/chapter4.tex
16jun

@@
 
-The obtained value for the calibration constant was $\sigma_{visible}$ = 1460890 \pm 546$ the analysis and results reported in this work will be useful for an analysis of the pre eliminary luminosity measurement for Run 3 in the CMS experiment of the lHC, where the rest of the luminometers and It's certainties will be studied along with this one.
+The obtained value for the calibration constant was $\sigma_{visible}$ = 1460890 \pm 546 \pm 6281(systematics)$ the analysis and results reported in this work will be useful for an analysis of the pre eliminary luminosity measurement for Run 3 in the CMS experiment of the lHC, where the rest of the luminometers and It's certainties will be studied along with this one.

### 2025-06-18 thesis_julio/Chapter3/chapter3.tex
18june
18jun2

@@
 For obtaining the important parameters on the vdm scan we return to the equation (1.2) and apply it to and individual bunch crossing, the values of N1 and N2 being the number of protons colliding can be obtained since is a known quantity from the experiment, the frequency f is also a known quantity, the frequency of the LHC which is 11,245 kHz but the proton densities $\rho_{1}$ and $\rho{2}$ are more difficult to obtain, this is were the vdM scan help us to measure integral over the bunch proton densities.
-The luminosity integral evaluated with the beams separated by a distance $\Delta_{x}$ and $\Delta_{y}$ can take the form of:
+The luminosity integral evaluated with the beams separated by a distance $\Delta_{x}$ and $\Delta_{y}$ can take the form of shown ins equation (3.1)
 
@@
 The integrals resulting on the right side can be evaluated by evaluated by obtaining the rate in function of the beam-beam separation which are $\Delta x$ and $\Delta y$  this because the luminosity has a linear relationship with the rate.
-The Luminosity can be expresed on terms of the rate during the head on positions, R(\Delta_{x0}, \Delta_{y0}) like in the equation (3.5)
+The Luminosity can be expresed on terms of the rate during the head on positions, $R(\Delta_{x0}, \Delta_{y0})$ like in the equation (3.5)
 
 \begin{equation}
-L(\Delta x, \Delta y) = N_{1} N_{2} f \frac{2R(\Delta x_{0}, \Delta y_{0}){\int L(\Delta x_{0}, \Delta y) d(\Delta y) \int L(\Delta x, \Delta y_{0}) d(\Delta x)}}
+L(\Delta x, \Delta y) = N_{1} N_{2} f \frac{2R(\Delta x_{0}, \Delta y_{0})}{\int L(\Delta x_{0}, \Delta y) d(\Delta y) \int L(\Delta x, \Delta y_{0}) d(\Delta x)}
 \end{equation}
@@
 \begin{equation}
-\sigma_{visible} = 1460890 \pm 546
+\sigma_{visible} = 1460890 \mu b \pm 546
 \end{equation}
@@
 
-Starting for the Background there were analysis made with the QG model fit which doesn't extract the background PCC, the sigma visible obtained in this case was of $\sigma_{visnobg}$ = 1452589 compared to the value that we obtained $\sigma_{vis}$ = 1450890 can be concluded that the uncertainty is 0.11\%.
+Starting for the Background there were analysis made with the QG model fit which doesn't extract the background PCC, the sigma visible obtained in this case was of $\sigma_{visnobg}$ = 1452589 $\mu b$ compared to the value that we obtained $\sigma_{vis}$ = 1450890 $\mu b$ can be concluded that the uncertainty is 0.11\%.
 
@@
  \hline
- Scan & \sigma_{vis} & STD & Syst. Error  \\ [0.5ex] 
+ Scan & \sigma_{vis} \mu b & STD & Syst. Error  \\ [0.5ex] 
  \hline\hline

### 2025-06-18 thesis_julio/Chapter4/chapter4.tex
18jun2

--- 2025-06-11 thesis_julio/Chapter4/chapter4.tex
@@
 
-The obtained value for the calibration constant was $\sigma_{visible}$ = 1460890 \pm 546$ the analysis and results reported in this work will be useful for an analysis of the pre eliminary luminosity measurement for Run 3 in the CMS experiment of the lHC, where the rest of the luminometers and It's certainties will be studied along with this one.
+The obtained value for the calibration constant was $\sigma_{visible}$ = 1460890 $\mu b$ \pm 546 \pm 6281(systematics)$ the analysis and results reported in this work will be useful for an analysis of the pre eliminary luminosity measurement for Run 3 in the CMS experiment of the lHC, where the rest of the luminometers and It's certainties will be studied along with this one.

### 2025-06-24 thesis_julio/Abstract/abstract.tex
thesis24june

\begin{abstract}
\begin{center}
     {\huge Abstract}
\end{center}

This job reports the calibration of the luminosity measurement using the analysis of the van der Meer scan program by the CMS experiment in 2024 proton-proton collision at $\sqrt{s}$ = 13 TeV with the Silicon Pixel detector in the CMS. The data used and processed for this analysis was during the period of May 16 to May 17 corresponding to the LHC fill 9369. The background was obtained and the analysis on the van der Meer scan with some corrections results in the calibration constant $\sigma_{vis}$ = 1460890  \pm 546 (stat) \pm 7304(syst)$ $\mu b$.

\end{abstract}

### 2025-06-24 thesis_julio/Abstract/resumen.tex
thesis24june

\begin{abstract}
\begin{center}
     {\huge Resumen}
\end{center}

El trabajo de este reporte es acerca la calibracion de la luminosidad usando el analisis del programa de van der Meer del experimento CMS en 2024 durante las colisiones proto-proton a $\sqrt{13}$ = TeV con el detector de pixeles en el CMS. Los datos fueron usados y procesador para este analisis que ocurrio en el periodo del 16 de mayo al 17 de mayo correspondiendo al fill 9639 del LHC. Fueron obtenidos valores de fondo y el analisis de los scans de van der Meer dio un resultado de la constante de calibracion de $\sigma_{vis}$ = 1460890  \pm 546 (stat) \pm 7304(syst) $\mu b$

\end{abstract}

### 2025-06-24 thesis_julio/Chapter1/chapter1.tex
thesis24june

@@
    \includegraphics[width=1\textwidth]{sm.png}
-    \caption{The standard model of particle physics}
+    \caption{The standard model of particle physics.\cite{pic2}}
     \label{fig:four-forces}
@@
 The fermionic sector contains particle the particles that make up all known matter in the universe and is divided into the leptons and the quarks, both of these particles are divided into three generations, each generation being heavier than the one before.
-For the leptons we have the electron and Its neutrino for the first generation, the second generation is.
-the $\mu$ and Its neutrino and the third one is the $\tao$ with Its neutrino.
-In the case of quarks we have the quark up and the quark down for the first generation, the second generation que have the quark charmd and the quark strange and for the third generation que have the quark top and the quark bottom.
-The bosons are the mediator particles called the gauge bosons already mentions, the photon, the gluon, the bosons $W\pm$ and the boson Z.
-There is also de Higgs bosson, which is the last gauge bossons and It's the responsible to give mass to the other SM particles
+For the leptons we have the electron and It's neutrino for the first generation, the second generation is the $\mu$ and It's neutrino and the third one is the $\tau$ with It's neutrino.
+In the case of quarks we have the quark up and the quark down for the first generation, the second generation we have the quark charm and the quark strange and for the third generation we have the quark top and the quark bottom.
+The bosons are the mediator particles, the photon, the gluon, the bosons W+, W- and the boson Z.
+There is also de Higgs boson which is the responsible to give mass to the other SM particles
 
-One of the main sources to obtain elementary particles is particle accelerators, in this you accelerate a particle into high energy and smash them with a target, with the proper  arrangements of magnets you can study the debris from the collision, for more heavy particles you need higher level of energy to the collision.
+One of the main sources to obtain elementary particles is particle accelerators, in this you accelerate a particle into high energy and smash them with a target, with the proper  arrangements of magnets you can study the debris from the collision, to produce heavy particles you need higher level of energy to the collision.
 
@@
 
-The Large Hadron Collider (LHC) is the biggest and powerful particle accelerator in the world at this moment, It is a 27 kilometers ring of superconducting magnets, this magnets boost the particles energies to obtain speeds that are close to the light speed before collisions.
-These particles are introduced as to the accelerator as particles beams this beams travel in opposing directions in tubes that are kept at ultrahigh vacuum, with the help of a electromagnetic field made by the electromagnets operating in superconduct state at low temperatures thanks to liquid helium this particles are guided across the whole accelerator.
+The Large Hadron Collider (LHC) is the biggest and powerful particle accelerator in the world at this moment.
+It is a 27 kilometers ring of superconducting magnets, this magnets mantain the particle in orbits meanwhile meanwhile radio frequency cavities increase the particles energies to obtain speeds that are close to the light speed before collisions.
+These particles are introduced into the accelerator as beams that are traveling in opposing directions in tubes that are kept at ultrahigh vacuum.
+All of this with the help of a electromagnetic field made by the electromagnets operating in superconduct state at low temperatures thanks to liquid helium this particles are guided across the whole accelerator.
 \cite{LHC}
@@
    \includegraphics[width=1\textwidth]{LHC.png}
-    \caption{The accelerator facility at cern for the LHC}
+    \caption{The accelerator facility at cern for the LHC. \cite{lhcpic}}
     \label{fig:LHC}
@@
 The LHC is part of an accelerator complex in CERN that is a succession of different machines that increase the energy of the beam of particles before passing into the next one on the sequence the particles at last are introduced on the LHC which is the last element in the sequence.
-The particles start at the linear accelerator 4 (Linac4) which is the source of the protons beams, it accelerates the particles in this case negative hydrogen ions to 160 MeV to enter the Proton Synchroton Booster (PSB), this is were the hydrogen loses Its two electrons leaving only protons and accelerating the beam to 2 GeV  and then are injected into the Proton Synchroton (PS), in where the protons are accelerated up to 26 GeV and then they are sent into the Super Proton Synchroton (SPS) here they are accelerated up to 450 GeV and then they're finally introduced into two beams pipes on the LHC, it takes about 4 minutes and 20 seconds to fill the LHC rings reaching energies up to 6.5 TeV, there are 4 collisions points where the detectors are located Alice, Atlas, CMS and LHCb, in the collision the total energy is of 13.6 TeV.
+The particles start at the linear accelerator 4 (Linac4) which is the source of the protons beams, hydrogen ions to 160 MeV to enter the Proton Synchroton Booster (PSB), this is were the hydrogen loses Its two electrons leaving only protons and accelerating the beam to 2 GeV  and then are injected into the Proton Synchroton (PS).
+Here the protons are accelerated up to 26 GeV and then they are sent into the Super Proton Synchroton (SPS) here they are accelerated up to 450 GeV.
+Finally they're fintroduced into two beams pipes on the LHC, it takes about 4 minutes and 20 seconds to fill the LHC rings reaching energies up to 6.5 TeV.
+There is a total of four collisions points and this is where the detectors are located Alice, Atlas, CMS and LHCb, in the collision the total energy is of 13.6 TeV.
 \cite{LHCII}
 
-The LHC has been working since 2009 with the discovery of the Higgs Boson on 2012 and looking for new physics It has been working on different periods called Runs, Run 1 was on the period of (2009-2013), Run 2 was on (2015-2018), Run 3 is currently on going since 2022.
+The LHC has been working since 2009 with the discovery of the Higgs Boson on 2012 and looking for new physics.
+It has been working on different periods called Runs, Run 1 was on the period of (2009-2013), Run 2 was on (2015-2018).
+Run 3 is currently on going since 2022.
 
@@
 The performance of a collider is determined by the beam energy and the luminosity.
-First we are going to define the cross section in a classical way the cross section area is parameter of interest that could say that measure the size of a target, this cross sectional area is presented to a stream of incoming particles, this is similar in the case of the scattering in elementary particles, if you fire a electron beam into a proton tank the parameters of interest are the size of the proton and the cross sectional area $\sigma$ that presents the incident beam.
-This collision differs to the classic case in some ways, first you could call the target soft since It's not a possible collision more like the closer you get the greater the deflection, the electrons scatters off the hydrogen, various interactions are happening during this and each one has a It's own scattering cross section $\sigma_{i}$ nevertheless in the experiment we are interested in the total cross section which can be seen as the sum of all the cross sections.
+First we are going to define the cross section in a classical way, the cross section area is parameter of interest that measures the size of a target, this cross sectional area is presented to a stream of incoming particles, similar to the case of the scattering in elementary particles, if you fire a electron beam into a proton, the parameters of interest are the size of the proton and the cross sectional area $\sigma$ that presents the incident beam.
+
+This collision differs to the classic case in some ways, first you could call the proton target soft since It's not a possible collision, instead as the electron becomes closer it gradually deflects due to the electromagnetic interactions.
+There are two main interactions each that can happen in this case, the first one the elastic scattering, here neither the electron or the proton changes their internal states.
+The other one the inelastic scattering where the target absorbs energy.
+In the case of the later the cross section $\sigma_{total}$ would be the sum of all the possible inelastic process $\sigma_{i}$ as shown in equation (1.1).
 
@@
 
-Each of this cross sections depends typically in the velocity of the incident particle, It's expected that the cross section would be proportional to the time that the incident particle spends close to It's target which means that $\sigma$ is inversely proportional to the velocity but this behavior is altered close to the region of a energy that particles involved to interact forming a short lived semi-state before breaking apart, things like this make the cross section for elementary particles different to the classic one.
+Each of this cross sections depends typically in the velocity of the incident particle, It's expected that the cross section would be proportional to the time that the incident particle spends close to Ithe target which means that $\sigma$ is inversely proportional to the velocity.
+This behavior is altered close to the region of energy that particles involved to interact forming a short lived semi-state before breaking apart, things like this make the cross section for elementary particles different to the classic one.
 
-To explain the cross section when a target is soft lets supposed a electron encounter a potential and scatters at the angle $\theta$, this scatter is angle is a function of a impact parameter b the distance by which this particle would have missed the scattering center had it continued on its original trajectory.
+To understand an elastic process lets consider an electron beam which encounters a potential and scatters at the angle $\theta$, this scatter is angle is a function of a impact parameter b the distance by which this particle would have missed the scattering center had it continued on its original trajectory.
 The form of $\theta(B)$ depends on the potential and the smaller the impact parameter b, larger the deflection.
@@
 This is a classical description of scattering and could be seen as the one who controls the number of particles going through the detector also determined the solid angle. 
-Here we have the incident flux F and a cross sectional area and are a way to interpret collision rates in modern particle accelerators since in high energy physics this structure is similar with a quantity called luminosity L with Its own cross section $\sigma$.
-
-Even when the dynamics are different for the quantum field theory case, the general principle remains the same, when we have a  higher the cross section we obtain a higher luminosity and Its more likely to observer determined events.
-
 %The define of cross section can be understand in a situation where a single particle is travelling to a velocity $v _{a}$in a region defined by A, which contains $n_{b}$ particles of a particle type b moving to a velocity $v_{b}$ in the opposite direction of $v_{a}$ if in a time $\delta t$  the particle a cross a region contained a total of $nb(v_{a} + v_{b})A\delta t$ particles of type b, the interaction probability can be obtained from the effective total cross seciotanl area divided by A which can be seen as the probability of that hte incident particles passes through one of the region of area $\sigma$ around each of the $\delta N$ particles then we can talk about the total rate being:
@@
 
-In which R is the number of events per second or rate, the $\sigma_{p}$ is the cross section which in the quantum case is a probability of interaction which can be obtained from the standar model of particle physics and L the instantanious luminosity.
+In which R is the number of colision events per second or rate, the $\sigma_{p}$ is the cross section which in the quantum case is a probability of interaction which can be obtained from the standar model of particle physics and L the instantanious luminosity.
 The unity of L is  $cm^{-2} s^{-1}$ a higher luminosity means greater probability that the particles will collide and produce the desired interactions, luminosity can be increased then in two ways, packing more particles into the beams or focusing this beams more.
 
-To compute the luminosity of two there is a few things that need to be taken in consideration.
-First the density distribution of each beam in the transverse and longitudinal plane, with the.
-two beams moving towards each other, the position and the time as the cross each other also need to be considered and calling the distance to the collision point $s_{0}$.
-The figure (1.x) shows two beams colliding which depends on a variety of factors:
+To compute the luminosity there is a few things that need to be taken in consideration.
+First the density distribution of each beam in the transverse and longitudinal plane, with the two beams moving towards each other, the position and the time as the cross each other also need to be considered and calling the distance to the collision point $s_{0}$.
+The figure (1.5) shows two beams colliding which depends on a variety of factors:
 
@@
 \begin{equation}
- L = 2N_{1}N{2}fN_{b} \int \int \int^{\infty}_{-\infty}  \rho_{1x} (x) \rho_{1y}(y) \rho_{1s} (s-s_{0}) \rho_{2x}(x) \rho_{2y}(y) \rho_{2s} (s+s_{0}) dxdydsds_{0}  
+ L = 2N_{1}N_{2}fN_{b} \int \int \int \int^{\infty}_{-\infty}  \rho_{1x} (x) \rho_{1y}(y) \rho_{1s} (s-s_{0}) \rho_{2x}(x) \rho_{2y}(y) \rho_{2s} (s+s_{0}) dxdydsds_{0}  
 \end{equation}
@@
 
-This is related directly to the number of observed events $L_{int} \cdot \sigma_{p}$ number of events of interest.
+This is related directly to the number of observed events $L_{int} \cdot \sigma_{p}$.
 
@@
 This occurs during a zero bias event, an event that is triggered by requiring only that two proton bunches cross at the CMS interaction point.
-Giving that the number of pixels in really big the probability that a pixel is being hit by two different tracks by the same bunch crossing is really small.
+Giving that the number of pixels is really big the probability that a pixel is being hit by two different tracks by the same bunch crossing is really small.
 The mean number of pixel clusters in a simulated zero bias event is in the order of 100 per pp collision.
@@
 \begin{equation}
-<N_{cluster}> = <N_{Pixel/Interaction}> <N_{interaction}> = <N_{Pixel/interaction}> \mu 
+<N_{cluster}> = <N_{Cluster/Interaction}> <N_{interaction}> = <N_{Cluster/interaction}> \mu 
 \end{equation}
 
-here the $\mu$ is the number of interactions and with this the following equation and gives us a relation with the cross section $\simga_{i}$, instant luminosity and $\mu$ and for the obtention of the luminosity value:
+here the $\mu$ is the number of interactions, now we define the collision rate in the equation (1.8):
 
 \begin{equation}
-<N_{cluster}> = \frac{\sigma_{cluster}}{f} \frac{dL}{dt}
+R = \mu * f_{LHC} = L * \sigma_{p}
+\end{equation}
+
+Solving for $\mu$ we got:
+
+\begin{equation}
+\mu = \frac{L * \sigma_{p}}{f_{LHC}} 
+\end{equation}
+
+And combining equation (1.7) and (1.9) we obtain:
+
+\begin{equation}
+<N_{cluster}> = \frac{\sigma_{p}* L}{f_{LHC}}  <N_{Cluster/Interaction}>
 \end{equation}
@@
 
-There have been different luminosities reached on the LHC for the Run 1 a luminosity of $0.77 x 10^{34}$ was reached and a integrated luminosity of 25 $fb^{-1}$  with a precision of 2.0\% for the first part and second part of the Run 2 the luminosity measured was of 38.4 $fb^{-1}$ with a precision of 1.3\% and 78$fb^{-1}$ respectively\cite{LHClum}.
-The following image show shows the integrated luminosity for the CMS experiment on different years.
+There have been different luminosities reached on the LHC for the Run 1 a luminosity of $0.77 x 10^{34} cm^{-2} s^{-1}$ was reached and a integrated luminosity of 25 $fb^{-1}$  with a precision of 2.0\% for the first part and second part of the Run 2 the luminosity measured was of 38.4 $fb^{-1}$ with a precision of 1.3\% and 78$fb^{-1}$ respectively\cite{LHClum}.
+The figure (1.6) show shows the integrated luminosity for the CMS experiment on different years.
 
@@
      \includegraphics[scale=1.25]{integratedlum.png}
-     \caption{Integrated luminosity at CMS}
+     \caption{Integrated luminosity at CMS.}
     \label{fig:CMS-Luminosity}

### 2025-06-24 thesis_julio/Chapter2/chapter2.tex
thesis24june

@@
      \includegraphics[height=0.73\textwidth, width=1\textwidth]{cms2.png}
-     \caption{The CMS detector size comparison with each of their components}
+     \caption{The CMS detector size comparison with each of their components.\cite{cmspic}}
     \label{fig:four-forces}
@@
 
-The CMS has the form of a cylindrical onion with several concentric layers of components, this components are important to determine the properties of different particles all of this by bending their trajectories with a magnet that bend charged particles, this helps to identify the charges of the particles since they bend in different directions and allows to measure the momentum of a particle sine high momentum particles bend less than the low momentum ones.
+The CMS has the form of a cylindrical onion with several concentric layers of components, this components are important to determine the properties of different particles.
+All of this is made by bending their trajectories with a magnet that bend charged particles, this helps to identify the charges of the particles since they bend in different directions.
+It also allows to measure the momentum of a particle sine high momentum particles bend less than the low momentum ones.
 The principal magnet of the CMS is called Super Conducting Solenoid this magnet generates a field of about 4 Teslas and is very large 6.3m cold bore, 12.5 meters of length and 200 t of mass.
-The high magnetic field is confined to the volume of the detectors using the "return yoke", this yoke have a magnetic field strength of 2 Teslas and acts as the main support as well as the muon filter Its made of a high amount of steel and It weights more than 11000 tonnes.
+The high magnetic field is confined to the volume of the detectors using the "return yoke", this yoke have a magnetic field strength of 2 Teslas and acts as the main support as well as the muon filter it's made of a high amount of steel and it weights more than 11000 tonnes.
 \cite{CMS3}
 
-One of the principal objectives of the CMS is identify with very high precision the paths taken by the particles that were bend by the magnetic field they called this part the inner tracker which is composed of different substructures, closest to the interaction point we have the Silicon Pixel Detector which will be detailled more on a later section.
+One of the principal objectives of the CMS is identify with very high precision the paths taken by the particles that were bend by the magnetic field they called this part the inner tracker which is composed of different substructures, closest to the interaction point we have the Silicon Pixel Detector which will be detailed more on a later section.
 
-Apart from the pixel detector the inner track is composed of strip detectors which are divided into the inner barrel (TIB) part and the outer barrel par(TOB), as well as the inner disks (TID) and the outer end caps (TEC).
+Apart from the pixel detector the inner track is composed of strip detectors which are divided into the inner barrel (TIB) part and the outer barrel part (TOB), as well as the inner disks (TID) and the outer end caps (TEC).
 The TIB and TOB are made of four and six concentric layers barrel shell structures respectively, the TID system is made of three disk structures each divided in three concentric rings and the TEC is made of nine disk structures on each side each of these made of four to seven rings as we can see on the figure 2.2.
@@
 Having information of the energy is important to understand what is happening at the collision point for this purpose there are two calorimeters on the CMS.
-The ECAL is made of 61200 lead tungstate crystals in the central barrel cap closed by 7324 crystals in the two of the endcaps in front of this crystals there is a press shower detector, the high density crystals allow  the calorimeter to be fast, have a fine granularity and being radiation resistant, Its capabilities are improved by the good crystal resolution which are provided by a homogeneous crystal calorimeter.
-It's surrounding the tracker and aims to measure the the energy of electrons, positrons or photons and stop them completely.
-The other calorimeter is the HCAL which is surrounding the ECAL and plays an essential role on the measurements of the energy of hadrons like the quarks, gluons, neutrinos and some exotic particles.
-which are also stopped here.
+The ECAL is made of 61200 lead tungstate crystals in the central barrel cap closed by 7324 crystals in the two of the endcaps in front of this crystals there is a pre shower detector.
+The high density crystals allow the calorimeter to be fast, have a fine granularity and being radiation resistant, Its capabilities are improved by the good crystal resolution which are provided by a homogeneous crystal calorimeter.
+It is surrounding the tracker and aims to measure the the energy of electrons, positrons or photons and stop them completely.
+The other calorimeter is the HCAL which is surrounding the ECAL and plays an essential role on the measurements of the energy of hadrons.
 
@@
     \includegraphics[width=1\textwidth]{cms.png}
-     \caption{Different particles travelling across the different detectors of the CMS experiment}
+     \caption[Particles in different detectors on CMS]{Different particles travelling across the different detectors of the CMS detector.\cite{cmspic2}}
     \label{fig:four-forces}
@@
 
-The CMS was optimized for the detections of muons and is the last particle that the CMS observe directly with the help of the muon chambers that is composed by many subdetectors which are interleaved with the return of the yoke of the solenoid located after the super conducting solenoid, muons are similar to electrons but 200 times heavier so they are not stopped by the calorimeters, the muon chambers have 3 main purposes; muon identification, momentum measurement and triggering.
+The CMS was optimized for the detections of muons and is the particle that the CMS observe directly with the help of the muon chambers that is composed by many subdetectors which are interleaved with the return of the yoke of the solenoid located after the super conducting solenoid, muons are similar to electrons but 200 times heavier so they are not stopped by the calorimeters, the muon chambers have 3 main purposes; muon identification, momentum measurement and triggering.
 \cite{CMS2}
@@
 It is located in a place where there is a harsh radiation environment giving Its high track density, in the CMS there was an pixel detector that was later changed during the first long shut down of the LHC during LS1 (2013-2014) and replaced by the CMS Phase-1 Pixel Detector in order to mantain efficient and robust tracking giving that with the upgrade of the accelerators the luminosity have doubled compared to the design value.
-It is expected that this detector to deliver high quality data until the end of the LHC Run 3 (Currently in process) after which the whole track detector on the CMS will be replaced.
+It is expected that this detector to deliver high quality data until the end of the LHC Run 3 (in process) after which the whole track detector on the CMS will be replaced.
 
@@
     \includegraphics[width=1\textwidth]{pixeldetector.png}     
-    \caption{Pixel detector outter rings and inner rings structure}
+    \caption{Pixel detector outter rings and inner rings structure. \cite{pxdpic}}
     \label{fig:PixelDetector}
@@
 
-The silicon detector modules is built from a planar silicon sensor bonded to an array of 2x8 ROCs.
+The silicon detector modules is built from a planar silicon sensor bonded to an array of 2x8 read out chips(ROC).
 Each ROC is segmented on 4160 readout channels and reads information about each pixel.
-Since 2 ROCs can only be placed at a minimum distance between each other pixels along the ROC boundaries have twice the area and those at the corners have four times the area of a pixel, in the other side of the silicon sensor there is a high density interconnect (HDI).
+Since 2 ROCs can only be placed at a minimum distance between each other pixels along the ROC boundaries have twice the area and those at the corners have four times the area of a pixel.
+Meanwhile in the other side of the silicon sensor there is a high density interconnect (HDI).
+
 To simplify the module production as well Its maintenance, the same rectangular module geometry is used for both BPIX and FPIX detectors.
@@
     \includegraphics[width=1\textwidth]{BPIXFPIX.png}
-    \caption{Barrel Pixel Detector moudles and Forward Pixel Detector Modules}
+    \caption{Barrel Pixel Detector moudles and Forward Pixel Detector Modules.}
     \label{fig:BPIXFPIX}
@@
 \\
-The sensors of BPIX and FPIX were designed by two different companies, BPIX was made by CiS Forschungsinstitut fur Mikrosensorik in efurt on germany and FPIX was made on SINTEF micro-systems and sensors in Norway.
+The sensors of BPIX and FPIX were designed by two different companies, BPIX was made by CiS Forschungsinstitut fur Mikrosensorik in Erfurt on Germany and FPIX was made on SINTEF micro-systems and sensors in Norway.
 The BPIX sensors were made on approximately 285 $\mu m$ of phosphorous-dope 4-inch wafers from silicon mono-crystals, all of this sensors were produced using silicon from the same ingot.
@@
     \includegraphics[height=0.55\textwidth, width=1\textwidth]{PixelSensor.png}
-    \caption{The pixel detector silicon sensor and the readout chip.}
+    \caption{The pixel detector silicon sensor and the readout chip. \cite{sensorpic}}
     \label{fig:sensor}
@@
 Before the process of irradiation the charge sharing is uniform in local X and Y directions, even then, the reconstructions of the true hits It's not trivial.
-After the detector is irradiated, the defects developed in the silicon lattice act as charges traps so that the free charge can only partially reach the readout chips, consequently the pixel clusters become smaller \cite{cluster1}
+After the detector is irradiated, the defects developed in the silicon lattice act as charges traps so that the free charge can only partially reach the readout chips, consequently the pixel clusters become smaller.
+\cite{cluster1}
 
@@
     \includegraphics[width=1\textwidth]{cluster3.png}
-    \caption{Cluster}
+    \caption{Charge collection in a pixel cluster for 2 different cases.}
     \label{fig:cluster}
@@
 The first step to the reconstruction process is referred to as local reconstruction.
-It consist of the clustering of zero-suppressed signals above specific thresholds in pixel and strip channels into hits, and then estimating the cluster positions and their uncertainties defined in a local orthogonal coordinate system (u, v) in the plane of each sensor.
-The sensor has a total of 100 x 150 $\mu m^{2}$ pixels with the u axis oriented parallel to the shorter pixel edge and for the strip sensors the u-axis is perpendicular to the central strip in the sensors.
+It consist of the clustering of zero-suppressed signals above specific thresholds in pixelinto hits, and then estimating the cluster positions and their uncertainties defined in a local orthogonal coordinate system (u, v) in the plane of each sensor.
+The sensor has a total of 100 x 150 $\mu m^{2}$ pixels with the u axis oriented parallel to the shorter pixel edge.
 \cite{cluster2}
@@
 
-To be applicable to a van der mer scan the cluster cross section must use exactly the same detector configuration during the whole of the data taking and the calibration scan.
+To be applicable to a van deer Mer scan the cluster cross section must use exactly the same detector configuration during the whole of the data taking and the calibration scan.
 This means if any of the modules of the detector didn't work at any point of the scans and didn't gave any readout It must be excluded from the calibration and the luminosity analysis so only a specific number of modules is selected during this.
@@
 For the stability selection different datasets are used, depending on the dataset you obtain time profiles per module and the absolute value of the deviation from the mean weight and averaged, this process is iterate for every module to remove outlier modules.
-For the linearity selection the module weight is evaluated as a function of quantity which is proportional to the instantaneous luminosity this quantity being the average PCC per module, the image (2.6) shows the difference between a good module and a bad module.
+For the linearity selection the module weight is evaluated as a function of quantity which is proportional to the instantaneous luminosity this quantity being the average PCC per module, the figure (2.7) shows the difference between a good module and a bad module.
 
@@
     \includegraphics[height=0.35\textwidth ,width=1\textwidth]{module.png}
-    \caption{Comparison between two modules with average PCC in 100 LS. Good module on the left, bad module on the right.}
+    \caption[Comparison good module and bad module.]{Comparison between two modules with average PCC in 100 LS. Good module on the left, bad module on the right.}
     \label{fig:modules}
@@
   \item First, all of the BPIX Layer 0 Modules are removed since they are consistently unstable.
+  \item Remove modules with no clusters in the vdm fill this means with weight=0 
   \item Then modules based on the noise level are removed in the vdm fill super separation data. 
-  \item Remove modules with no clusters in the vdm fill this means with weight=0 
   \item Compare stability parameters between modules and remove outliers in the vdm fill
-  \item Compare stability parameter for each block of data and perform a second iteration if necessary
+  \item Compare stability parameter for each block of data during the physics runs of the year and perform a second iteration if necessary
   \item Compare linearity parameter between modules and remove outliers

### 2025-06-24 thesis_julio/Chapter3/chapter3.tex
thesis24june

@@
 
-\section{Van Der Meer Method}
+\section{van der Meer Method}
 
-The Van Der Meer (vdM) scan let us obtain the value of $\sigma_{visible}$ using different luminometers.
+The van der Meer (vdM) scan let us obtain the value of $\sigma_{vis}$ which previously was defined as $\sigma_{cluster}$ using different luminometers.
 For this case the detector of interest is the pixel detector with which are going to obtain a calibration of the luminosity using the vdM scan in combination with the PCC method.
-The scan consist on separating particle the beams from each other between the X and Y axis by $\Delta X$ and $\Delta Y$ values moving them and recording values of luminosity independently, when the scan on X and scan on Y are imposed over each other we said that they're on head on giving the maximum value of luminosity.
-Usually a single gaussian fit is used to obtain beam overlap widths also denoted as $\Sigma_{x}$ and $\Sigma_{y}$, other fit models may be used like the doble gaussian depending on the quality of the fit \cite{Vdm}
+The scan consist on separating particle beams from each other on the X and Y axis by $\Delta X$ and $\Delta Y$ values moving them and recording values of rates independently, when the scan on X and scan on Y are imposed over each other we said that they're on head on giving the maximum value of luminosity.
+Usually a single gaussian fit is used to obtain beam overlap widths also denoted as $\Sigma_{x}$ and $\Sigma_{y}$, other fit models may be used like the double gaussian depending on the quality of the fit \cite{Vdm}
 
@@
     \includegraphics[width=1\textwidth]{vdm1.png}
-    \caption{The vdm scan on the left showing the beams for X and Y. On the right a curve of the different values of rate for the beams displacement, the peak occurs during the head on part.}
+    \caption[vdM scan beams and curve.]{The vdM scan on the left showing the beams for X and Y.
+On the right a curve of the different values of rate for the beams displacement, the peak occurs during the head on part.}
     \label{fig:vdm1}
@@
 
-For obtaining the important parameters on the vdm scan we return to the equation (1.2) and apply it to and individual bunch crossing, the values of N1 and N2 being the number of protons colliding can be obtained since is a known quantity from the experiment, the frequency f is also a known quantity, the frequency of the LHC which is 11,245 kHz but the proton densities $\rho_{1}$ and $\rho{2}$ are more difficult to obtain, this is were the vdM scan help us to measure integral over the bunch proton densities.
+For obtaining the important parameters on the vdm scan we return to the equation (1.2) and apply it to and individual bunch crossing, the values of N1 and N2 being the number of protons colliding can be obtained since is a known quantity from the experiment, the frequency f is also a known quantity, the frequency of the LHC which is 11,245 Hz but the proton densities $\rho_{1}$ and $\rho_{2}$ are more difficult to obtain, this is were the vdM scan help us to measure integral over the bunch proton densities.
 The luminosity integral evaluated with the beams separated by a distance $\Delta_{x}$ and $\Delta_{y}$ can take the form of shown ins equation (3.1)
@@
  \begin{equation}
-N_{1} N_{2} f \int \rho_{1}(x) \rho_{2}(x + \Delta x_{0}) dx = \int L (\Delta x_{0}, d\Delta y) d(\Delta y)
+N_{1} N_{2} f \int \rho_{1}(x) \rho_{2}(x + \Delta x_{0}) dx = \int L (\Delta x_{0}, \Delta y) d(\Delta y)
 \end{equation}
@@
 \begin{equation}
-N_{1} N_{2} f \int \rho_{1}(x) \rho_{2}(x + \Delta x_{0}) dx = \frac{L (\Delta X_{0}, \Delta y_{0})}{\int L(\Delta x_{0}, \Delta y) d(\Delta y)}
+N_{1} N_{2} f \int \rho_{1}(x) \rho_{2}(x + \Delta x_{0}) dx = \frac{L (\Delta x_{0}, \Delta y_{0})}{\int L(\Delta x_{0}, \Delta y) d(\Delta y)} = \frac{R (\Delta x_{0}, \Delta y_{0})}{\int L(\Delta x_{0}, \Delta y) d(\Delta y)}
 \end{equation}
@@
 \begin{equation}
-L(\Delta x, \Delta y) = N_{1} N_{2} f \frac{2R(\Delta x_{0}, \Delta y_{0})}{\int L(\Delta x_{0}, \Delta y) d(\Delta y) \int L(\Delta x, \Delta y_{0}) d(\Delta x)}
+L(\Delta x, \Delta y) = N_{1} N_{2} f \frac{(R(\Delta x_{0}, \Delta y_{0}))^{2}}{\int L(\Delta x_{0}, \Delta y) d(\Delta y) \int L(\Delta x, \Delta y_{0}) d(\Delta x)}
 \end{equation}
@@
 \begin{equation}
-\Sigma_{x} = \frac{1}{2 \pi} \frac{\int R(\Delta x, \Delta y_{0}) d(\Delta x) )}{R(\Delta x_{0}, \Delta y_{0})}
+\Sigma_{x} = \frac{1}{\sqrt{2 \pi}} \frac{\int R(\Delta x, \Delta y_{0}) d(\Delta x) )}{R(\Delta x_{0}, \Delta y_{0}}
 \end{equation}
@@
 
-This calculations are done on several Bunch Cross Identifier which so you obtain several values of $\simga_{vis}$ and then they are weight averaged according to the uncertainties in order to obtain $\sigma_{vis}$ for the scan.
+This calculations are done on several Bunch Crossing Identifier(BCID's) which so you obtain several values of $\sigma_{vis}$ and then they are weight averaged according to the uncertainties in order to obtain $\sigma_{vis}$ for the scan.
 
@@
 This stream of events is organized into datasets according to the results of the High Level Trigger (HLT) which defines primary datasets since they are defined by the paths of the HLT.
-The design of the primary datasets is centered around candidates for particles that are reconstructed on the final state by the hLT and follows the principle of grouping together events with similar physics content.
+The design of the primary datasets is centered around candidates for particles that are reconstructed on the final state by the HLT and follows the principle of grouping together events with similar physics content.
 \cite{datasets1}
 
-The datasets used for the obtention of the $\sigma_{visible}$ for 2024 were the ones from the Fill 9639 which is divided in 3 blocks, a fill is a process that generates beams for the LHC this tipycally involves particles around the number of $10^{14}$ that are grouped in bunches that form the proton beam.
-This is what we use the bcid number to identify this bunches, there are a total of 3564 bunches that are empty or filled depending on the fill all of this part of the LHC bunch train.
+The datasets that were used for the determination of the $\sigma_{vis}$ for 2024 were the ones from the Fill 9639 from 16 may to may 17 which is divided in 3 blocks.
+We call a fill the process that generates beams for the LHC this tipycally involves particles around the number of $10^{14}$ that are grouped in bunches that form the proton beam.
+The bcid number is used to identify this bunches, there are a total of 3564 bunches that are empty or filled depending on the fill all of this part of the LHC bunch train.
 For this fill in the calibration the bcids of relevance were a total of 12 which are identified by the numbers: 303, 324, 345, 506, 527, 822, 1081, 1102, 1397, 2000, 2965, 3123.
@@
 This samples are processed using the CMSWW software to extract the clusters per module to obtain the dataset in the ROOT format.
-ROOT is a software framework born at CERN It is open source and used for high energy physics to analyze data while providing packages for storage, processing and visualization while minimizes the computing resources needed.
+ROOT is a software framework born at CERN.
+It is open source and used for high energy physics to analyze data while providing packages for storage, processing and visualization while minimizes the computing resources needed.
 
-The root format saves the data in form of TTrees which behaves like an array of data structure and storage data.
+The ROOT format saves the data in form of TTrees which behaves like an array of data structure and storage data.
 This tree consist on branches and leaves, a branch is a list of independent columns that can contain values of any fundamental type and are represented by TBranch.
@@
 
-This dataset were first processed by the CMS collaboration enabling a cluster reconstruction resulting in the ALCARECO datasets getting a lot of root files for each of the different zero bias streams that were the starting point of this analysis.
+the data was processed to obtain a hd5 file, a format that can supports n-dimensional datasets and facilitates reading them.
+These hd5 files contained relevant information about the root files like the average rate per NB4.
+This process was made for each of the files for all of the available streams ready to use.
+After processing all the files of a single stream into hd5 files they were converged into a single file containing relevant information for all the streams.
+once all of the files in all of the data streams were processed into hd5 files a single, hd5 file was made containing all of the information about the streams also a single csv file was made containing only the average rate file per NB4 for each of the bcids.
 
-After this the data then was processed again to obtain a hd5file a format that can supports n-dimensional datasets and facilitates the reading of the datasets, this hd5 files contained relevant information about the root files like the average rate per NB4, this was made for each of the files for almost all of the available streams excluding two of them that were not ready by the moment (the ones that were identified by ZB21 and ZB28) after one stream got all of his files processed into an hd5 file they were converged into a single file containing relevant information for all the stream, once all of the files in all of the data streams were processed into hd5 files a single hd5file was made containing all of the information about the streams also a single csv file was made containing only the average rate file per NB4 for each of the bcids.
-
-This scans were analyzed using the vdM framework, a CMS tool to obtain different parameters using a fit model on the vdM scans, this framework read hd5 files and with a set of instructions the value of $\sigma_{visible}$ can be obtained.
+This scans were analyzed using the vdM framework, a CMS tool to obtain different parameters using a fit model on the vdM scans, this framework read hd5 files and with a set of instructions the value of $\sigma_{vis}$ can be obtained.
 
@@
 
-For the calibration of 2024 in the LHC fill 9639 during may 15 to may 16 at collision proton proton with a energy of 13.6 TeV, the vdm scans were made there were a total of 5 vdm X and vdm Y scans and 2 beam img X and beam img Y and the Super Separation period which is a scan used to obtain a background estimation, this were the scans used on this analysis to compute the value of $\sigma_{visible}$.
-The figure (3.x) shows a DOROS image of the fill and all the scans that were made during that period of time.
+For the calibration of 2024 in the LHC fill 9639 during may 15 to may 16 at collision proton proton with a energy of 13.6 TeV, the vdm scans were made there were a total of 5 vdm X and vdm Y scans and 2 beam img X and beam img Y and the Super Separation period which is a scan used to obtain a background estimation, this were the scans used on this analysis to compute the value of $\sigma_{vis}$.
+
+The Diode ORbit and OScillation (DOROS) system is a system that process signals from the beam position monitors\cite{DOROS} and permit us to show a detailed information of the scans that were made in the fill during that period of time as shown in the the figure (3.2).
 
@@
 
-The 5 vdm scans vdM1, vdM2..., vdM5 are the scans usually used in the calibration to compute $\sigma_{visible}$ two beams are separated the transverse bunch size and then scanned across one another in sequence of 25 steps with 30 seconds per step.
+The 5 vdm scans vdM1, vdM2..., vdM5 are the scans usually used in the calibration to compute $\sigma_{vis}$ two beams are separated the transverse bunch size and then scanned across one another in sequence of 25 steps with 30 seconds per step.
 The beam imaging scan is kept on a nominal position while the other is separated and scanned in 19 steps, the scan is performed first in the X direction and then in the Y direction.
@@
 
-The background estimation were obtained using the 5 Super Separation scans, the time on which this super separations were used was on UNIX time, this time can be defined as a system for tracking a point in time as the number of seconds that have happened since January 1 at 00:00 in universal time (UTC).
+The background estimation were obtained using the 5 Super Separation scans, the time on which this super separations were used was on UNIX time, this time can be defined as a system for tracking a point in time as the number of seconds that have happened since January 1 at 00:00 of 1970 in universal time (UTC).
 Each of these super separations lasted a total of 5 minutes in the following table we got more information about the start and ending of the scans.
@@
 
-The data of this scans were processed and analyzed, in the following image we show the mean value of the PCC rates during the Super Separation period scan in one bcid.
+The data of this scans were processed and analyzed, in the figure  (3.3) It's shown the mean value of the PCC rates during the Super Separation period scan for one bcid.
 
@@
 
-The reason why the background estimation is obtained during the super separation (SS) process, It's because the SS scan separates the beams so they shouldn't be colliding the expected value on the rate is expected to be a rate associated with the background, this was obtained checking the mean values for each bcid for all the entries of pcc rates for each of the 5 periods of super separation, the following image illustrate a case for one SS period and bcid 50x:
+The reason why the background estimation is obtained during the super separation (SS) process, It's because the SS scan separates the beams so they shouldn't be colliding the expected value on the rate is expected to be a rate associated with the background, this was obtained checking the mean values for each bcid for all the entries of pcc rates for each of the 5 periods of super separation, the figure (3.4) illustrates a case for one SS period and bcid 345:
 
@@
     \centering
-    \includegraphics[height=0.4\textheight, width=0.8\textwidth]{sshist.png}
-    \caption{Distribution of average PCC for bcid 345 during SS number 2. The PCC values are computed in NB4 time intervals.}
+    \includegraphics[height=0.45\textheight, width=0.8\textwidth]{sshist.png}
+    \caption[Average PCC bcid 345.]{Distribution of average PCC for bcid 345 during SS number 2. The PCC values are computed in NB4 time intervals.}
     \label{fig:SShist}
@@
 
-The mean value during this period is assumed to be the background noise value of this SS period, in the following table we see the mean PCC value for all of the bcids and how it changes in each of the five super separation periods.
+The mean value during this period is assumed to be the background noise value of this SS period, in figure (3.5) we see a plot with the mean PCC value for the twelve bcids on the 5 super separation periods.
 
@@
     \includegraphics[width=1\textwidth]{SSmean.png}
-    \caption{This plot shows the evolution of the PCC value for the twelve differents bcids during the SS periods, it also shows the mean of each bcid.}
+    \caption[PCC evolution during SS periods.]{The evolution of the PCC value for the twelve differents bcids during the SS periods, it also shows the mean of each bcid.}
     \label{fig:SSmean}
@@
     \centering
-    \includegraphics[height = 0.45 \textwidth ,width=1\textwidth]{ssthist.png}
-    \caption{This plots shows an histogram with all SS values for all bcids, the mean of all this values is used as the final result.}
+    \includegraphics[height = 0.6 \textwidth ,width=1\textwidth]{ssthist.png}
+    \caption[Histogram of all SS values]{A histogram with all SS values for all bcids, the mean of all this values is used as the final result.}
     \label{fig:Histogram}
@@
 \begin{itemize}
-  \item \textbf{Background} The rates substracted on the SS periods and is associated with the luminometer itself see section (3.x) for more.
+  \item \textbf{Background} The rates substracted on the SS periods.
   \item \textbf {Ghost Satellite} This correction have to be with the charge that comes from the non colliding bunches, which are called ghost and those who are leaking from the main radio frequency bucket into another bucket which are called satellite.
-This currents have an effect on the $\sigma_{visible}$ measure because of the contribution on the charges, this charges are substracted from the beam currents.
+This currents have an effect on the $\sigma_{vis}$ measure because of the contribution on the charges, this charges are substracted from the beam currents.
 \cite{ghost}
@@
 
-There are different fit models at the time to do the vdm calibration, the most common one is Single Gaussian but also other models like the Double Gaussian, QG, Poly2G or Poly4G.
-Each of these models have different parameters and restrictions making some of them better than other on the fit quality.
+There are different fit models at the time to do the vdm calibration, the one used for this fit are QG and Poly2G.
+Each of these models have different parameters and restrictions making some of them better than other on the fit quality depending on the case.
 
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{QG_covStatus.png}
-    \caption{Status of the covariance matrix gives 3 for all values showing that all bcids converged with the fit}
+    \includegraphics[width=0.9\textwidth]{QG_covStatus2.png}
+    \caption[Covariance matrix status QG fit model]{Status of the covariance matrix gives 3 for all values showing that this fit model converged for all bcids and scans fort he QG fit model.}
     \label{fig:QGfit}
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{QG_chi2.png}
-    \caption{Chi2 values to see the fit quality, the green line represent the mean}
+    \includegraphics[width=0.9\textwidth]{QG_chi22.png}
+    \caption[Chi2 values QG fit model.]{Chi2 values to see the fit quality, the green line represent the mean.}
     \label{fig:QGchi2}
@@
 
-\section{Fit model optimization}
-
-Two fit models were used for this, the first one described above and the second Poly2G.
-The poly2G model consist on a value r2 which is a parameter, the value $\Sigma$ related to the beam width, the peak which is the maximum rate during the head on period and the mean.
+The Poly2G fit model consist on a value $r_{2}$ which is a parameter, the value $\sigma$ related to the beam width, the peak which is the maximum rate during the head on period and the mean.
 Its defined as:
@@
 
-Once the Poly2G fit model was used the chi2 value was compared with the nominal fit model, in the figure (3.9) we can see the chi2 values for each scan.
-The mean value of the chi2 is lower than the QG that's the reason we used it as the nominal fit model.
+Once the Poly2G fit model was used the chi2 value was compared with the nominal fit model, in the figure (3.10) we can see the chi2 values for each scan.
+The mean value of the chi2 is higher than the QG that's the reason we used it as the nominal fit model.
 
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{poly2g.jpeg}
-    \caption{Chi2 values to see the fit quality of the poly2g fit model the green line represent the mean, notice that the mean is lower than with the nominal fit model.}
+    \includegraphics[width=0.9\textwidth]{Poly2G_chi2.png}
+    \caption[Chi2 values Poly2G fit model.]{Chi2 values to see the fit quality of the poly2g fit model the green line represent the mean, notice that the mean is lower than with the nominal fit model.}
     \label{fig:QGchi2}
@@
 
-The beam parameters of the vdm scan were obtained after the vdM framework run whit the QG fit model one of the parameters obtained is the peak value, figure 3.12 shows the peak values obtained with the fits to the different vdM scans.
-
-\begin{figure}[H]
-    \centering
-    \includegraphics[width=0.9\textwidth]{QG_peak.png}
-    \caption{QG model fit peak values obtained for the different scans in X and Y.}
-    \label{fig:QGpeak}
-\end{figure}
-
-Here we can see that the peak values are increasing with the time in the fill, this behavior is then explained if we observe the results for the $\Sigma_{x, y}$ shown in the figure (3.13).
+The beam parameters of the vdM scan were obtained after the vdM framework run with the QG fit model one of the parameters obtained is the peak value.
+The figure (3.11) shows the peak values obtained with the fits to the different vdM scans.
+Here we can see that the peak values are increasing with the time in the fill, this behavior is then explained if we observe the results for the $\Sigma_{x, y}$ shown in the figure (3.12).
 Here we see that the $\Sigma_{x, y}$ values are decreasing for each scan reducing the thickness of the beams and thus observing a higher peak value even if the number of particles is decreasing through time.
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{QG_CapSigma.png}
-    \caption{QG model fit $\Sigma$ values obtained for the different scans in X and Y in the vdM fill.}
+    \includegraphics[width=0.9\textwidth]{QG_peak2.png}
+    \caption[Peak values QG fit model.]{QG model fit peak values obtained for the different scans in X and Y.}
+    \label{fig:QGpeak}
+\end{figure}
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.9\textwidth]{QG_CapSigma2.png}
+    \caption[$\Sigma$ values QG fit model.]{QG model fit $\Sigma$ values obtained for the different scans in X and Y in the vdM fill.}
     \label{fig:QGcapsigma}
@@
 
-After the obtention of the beam parameters  the value of $\sigma_{visible}$ can be obtained, the values for each bcid is shown are shown on the image (3.13).
+After the determination of the beam parameters  the value of $\sigma_{vis}$ can be obtained, the values for each bcid is shown are shown on the image (3.13).
 
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{sigbcid.png}
-    \caption{The value of $\sigma_{visible}$ of all twelve bcids and the seven used scans}
+    \includegraphics[width=0.9\textwidth]{QG_xsec2.png}
+    \caption{The value of $\sigma_{vis}$ of all twelve bcids and the seven used scans}
     \label{fig:sigbcid}
@@
 
-We are expecting a constant value of $\sigma_{visible}$ here it appears to be changing each scan this could be to other uncertainties.
+We are expecting a constant value of $\sigma_{vis}$ here it appears to be changing each scan this could be to other uncertainties.
 Then in the image (3.14) Its shown the result on each scan for the weighted mean which is a mean taken into consideration a value mean that is defined as:
@@
 
-So then the weighted mean value of $\sigma_{visible}$ would be:
+So then the weighted mean value of $\sigma_{vis}$ would be:
 
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{sigscan.png}
-    \caption{$\sigma_{visible}$ weighted mean per each scan}
+    \includegraphics[width=0.9\textwidth]{sigscan2.png}
+    \caption{$\sigma_{vis}$ weighted mean per each scan}
     \label{fig:sigscan}
@@
 
-Which give us a $\sigma_{visible}$ value of
+Which give us a $\sigma_{vis}$ value of
 
 \begin{equation}
-\sigma_{visible} = 1460890 \mu b \pm 546
+\sigma_{visible} = 1460890 \pm 546 \mu b
 \end{equation}
@@
 
-Starting for the Background there were analysis made with the QG model fit which doesn't extract the background PCC, the sigma visible obtained in this case was of $\sigma_{visnobg}$ = 1452589 $\mu b$ compared to the value that we obtained $\sigma_{vis}$ = 1450890 $\mu b$ can be concluded that the uncertainty is 0.11\%.
+Starting for the Background systematics, the value of $\sigma_{vis}$ was obtained separately by using a different background noise of $\sigma \pm$ difference.We then obtained the systematic uncertainty subtracting this values and divide them by two.
+With this we conclude that the systematic uncertainty of the background on $\sigma_{vis}$ is 0.03\%.
 
-In the case of scan to scan variation the standard deviation of the seven scans is taken as uncertainty with a value of 0.30\%.
+In the case of scan to scan variation the standard deviation of the seven scans is taken as uncertainty with a systematic value of 0.5\%.
 
@@
 \begin{center}
-\caption{Bunch to bunch uncertainty table.}
+\caption[Bunch to bunch uncertainties.]{Bunch to bunch uncertainty shows $\sigma_{vis}$ per each scan and the It's standard deviation the systematic error is then obtained dividing the STD for the mean of the second column then divided by the square root of the number of bcids which in this case is twelve.
+}
 \begin{tabular}{|c c c c|} 
  \hline
- Scan & \sigma_{vis} \mu b & STD & Syst. Error  \\ [0.5ex] 
+ Scan & \sigma_{vis} (\mu b) & STD & Syst. Error \%  \\ [0.5ex] 
  \hline\hline
@@
  \hline
-    \textbf{mean}        &             &            & 0.2 \\ [1.0ex]
+    \textbf{Mean}        &             &            & 0.02 \\ [1.0ex]
  \hline
@@
 
-The sum between all the uncertainties can be see in detail in the table (3.3), the total systematic uncertainty is 0.43\% (6281) taking into consideration only those systematic uncertainties.
+The total uncertainty is obtained summing the square of each uncertainty and taking the square root of the sum.
+This can be see in detail in the table (3.3), the total systematic uncertainty is 0.50\% (7304) taking into consideration only those systematic uncertainties.
 
@@
  \hline\hline
- Background & 0.11\%   \\ 
+ Background & 0.03\%   \\ 
  \hline
@@
  \hline
- Scan to scan & 0.30\% \\
+ Scan to scan & 0.50\% \\
  \hline
-  Total          &     0.43\%  \\ [1.0ex]
+  Total          &     0.50\%  \\ [1.0ex]
  \hline

### 2025-06-24 thesis_julio/Chapter4/chapter4.tex
thesis24june

--- 2025-06-11 thesis_julio/Chapter4/chapter4.tex
@@
 
-This work aims to focus on the calibration of hte luminosity for the PCC luminometer base on the Van Der Meer scans conducted by the CMS collaboration on 2024 for the fill 9639 in the proton proton collisions of the LHC at $\sqrt{s}$ 13.6 TeV obtaining the calibration value from seven scan pairs (5 vdM's and 2 BI's), the concept of luminosity, the LHC, CMS, PCC luminometer and calibration method to estimate $\sigma_{visible}$ were covered in this work.
+This work aims to focus on the calibration of the luminosity for the PCC luminometer based on the van der Meer scans conducted by the CMS collaboration on 2024 for the fill 9639 in the proton proton collisions of the LHC at $\sqrt{s}$ 13 TeV obtaining the calibration value from seven scan pairs (5 vdM's and 2 BI's), the concept of luminosity, the LHC, CMS, PCC luminometer and calibration method to estimate $\sigma_{vis}$ were covered in this work.
 
@@
 
-The obtained value for the calibration constant was $\sigma_{visible}$ = 1460890 \pm 546$ the analysis and results reported in this work will be useful for an analysis of the pre eliminary luminosity measurement for Run 3 in the CMS experiment of the lHC, where the rest of the luminometers and It's certainties will be studied along with this one.
+The obtained value for the calibration constant was $\sigma_{vis}$ = 1460890  \pm 546 (stat) \pm 7304(syst)$ $\mu b$ the analysis and results reported in this work will be useful for an analysis of the preliminary luminosity measurement for Run 3 in the CMS experiment of the LHC, where the rest of the luminometers and It's certainties will be studied along with this one.
